### 2020-08-14 presymplectic.tex
creating files

\documentclass[11pt]{amsart}

\pdfoutput = 1

\usepackage{macros,slashed,amsaddr}

\linespread{1.5}

\setcounter{tocdepth}{2}
\numberwithin{equation}{section}
\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup}
\newcommand{\changelocaltocdepth}[1]{%
  \addtocontents{toc}{\protect\setcounter{tocdepth}{#1}}%
  \setcounter{tocdepth}{#1}%
}
\setcounter{tocdepth}{1}

\def\brian{\textcolor{ForestGreen}{BW: }\textcolor{ForestGreen}}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\def\PV{{\rm PV}}

\begin{document}

\title{An interacting presymplectic BV theory}

\maketitle

\tableofcontents

Here was my understanding of the theory you told me. 
It's a $\ZZ/2$-graded theory with two sets of fields
\begin{align*}
\mu & \in \Omega^\bu (\RR) \otimes \bigg(\PV^{1,\bu}(\CC^5) \xto{\partial} \PV^{0,\bu}(\CC^5) \bigg) \\
\gamma & \in \Omega^{\bu}(\RR) \otimes \Omega^{1,\bu}(\CC^5)
\end{align*}

There is a pairing of the form
\[
\omega(\gamma, \mu) = \int_{\RR \times \CC^5} \gamma \wedge (\mu \vdash \Omega) .
\]
Here $(-) \vdash \Omega$ is the isomorphism $\PV^{k, \bu} \cong \Omega^{5-k, \bu}$.
Note that the $\PV^{0,\bu}(\CC^5)$ component of $\mu$ does not appear in the pairing.

If we get the shifts right 
\[
\Omega^\bu (\RR) \otimes \bigg(\PV^{1,\bu}(\CC^5) \xto{\partial} \PV^{0,\bu}(\CC^5) \bigg)
\] 
forms a dg Lie algebra defined by the Schouten bracket. 
Then the $\gamma$-fields form a module for this.

There is a sort of ``modified BF theory" whose action is of the form
\[
\omega\left(\gamma, \d \mu + \frac{1}{2} \{\mu, \mu\} \right) = \int \gamma \bigg(\d \mu + \frac12 \{\mu, \mu\} \bigg) \vdash \Omega .
\]

We consider a deformation of this action by the functional
\[
\int \gamma \partial \gamma \partial \gamma .
\]
\end{document}

### 2020-08-19 BCOV with potentials/BCOV with potentials.tex
added statements about dimensional reduction of M-theory

% Created 2020-08-18 Tue 22:24
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{macros}
\author{Surya Raghavendran}
\date{\today}
\title{Holomorphic M-theory and the $\SU(4)$-invariant twist of type $\IIA$ }
\hypersetup{
 pdfauthor={Surya Raghavendran},
 pdftitle={BCOV with potentials},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

\maketitle

BCOV with potentials refers to a modification of minimal BCOV theory where we impose certain constraints on the fields so as to make the Poisson BV structure of the theory invertible. These constraints amount to requiring that certain fields lie in the image of the divergence operator \(\del\), or better yet replacing $\del$-closed fields in a summand \(\PV^{d,\bullet}\) with all of \(\PV^{d,\bullet}\) and using a fixed choice of splitting of \(\del: \PV^{d,\bullet}\to \PV^{d-1,\bullet}\) to rewrite \(\PV^{d,\bullet}\cong\im\del\oplus\ker\del\).

Under the conjectures of Costello-Li that describe twisted type II supergravity in terms of BCOV theory, these primitives correspond to certain components of Ramond-Ramond fields, which are chosen as potentials for Ramond-Ramond field strengths.

\section{BCOV theory with potentials on a CY4}
\label{sec:org3d6a090}

Let \(X\) be a CY4. BCOV theory on \(X\) with potentials will be the \(\mb{Z}/2\) graded BV theory defined as follows. Fix splittings \(C_1: (\im\del\subset\PV^{3,\bullet})\to \PV^{4,\bullet}\) of  \[0\to\ker\del\to \PV^{4,\bullet}\to(\im\del\subset\PV^{3,\bullet}\to 0\] and \(C_2: (\im\del\subset\PV^{2,\bullet})\to\PV^{3,\bullet}\) of \[0\to\ker\del\to\PV^{3,\bullet}\to(\im\del\subset\PV^{2,\bullet}(X))\to 0.\] And let \(\phi_{C_1} : \PV^{4,\bullet}\cong(\ker\del\subset\PV^{4,\bullet})\oplus(\im\del\subset\PV^{3,\bullet})\), \(\phi_{C_2}: \PV^{3,\bullet}\cong(\ker\del\subset\PV^{3,\bullet})\oplus(\im\del\subset\PV^{2,\bullet})\) be the resulting isomorphisms.
\begin{itemize}
\item The fields of the theory are
 \[\begin{aligned} \mc E_{mBCOV}^{C_1,C_2} = \PV^{0,\bullet} \oplus (\ker\del\subset\PV^{1,\bullet})\oplus & (\im\del\subset\PV^{2,\bullet} \oplus\ker\del\subset\PV^{3,\bullet})\\ \oplus &(\im\del\subset\PV^{3,\bullet}\oplus\ker\del\subset\PV^{4,\bullet})\end{aligned}\]
\item The Poisson kernel is given by $(\del\otimes 1)\delta_{Diag}$
\item The \(L_\infty\) structure is defined as follows
\begin{itemize}
\item \(\ell_1=\delbar\)
\item \(\ell_2\) is a certain modification of the Schouten bracket, defined as follows. Let \([-,-]\) denote the usual Schouten bracket of polyvector fields. Then

\begin{enumerate}
\item \(\mu\in\PV^{0,\bullet}, \nu\in\ker\del\subset\PV^{1,\bullet}\), \(\ell_2(\mu,\nu)=[\mu,\nu]\).
\item \(\mu\in\PV^{0,\bullet}, \nu\in\im\del\subset\PV^{2,\bullet}\), \(\ell_2(\mu,\nu)=(-1)^{|\mu|-1}\del[\mu,\phi^{_1}_{C_1}\nu]\) and \(\ell_2(\nu,\mu)=\del[\mu,\phi^{-1}_{C_1}\nu]\)
\item \(\mu\in\PV^{0,\bullet}, \nu\in(\im\del\subset\PV^{3,\bullet})\oplus(\ker\del\subset\PV^{4,\bullet})\), \(\ell_2(\mu,\nu)=(-1)^{|\mu|-1}\phi_{C_1}[\mu, \phi^{-1}_{C_2}\nu]\) and \(\ell_2(\nu, \mu)=\phi_{C_1}[\mu, \phi^{-1}_{C_2}\nu]\).
\item \(\mu,\nu\in\ker\del\subset\PV^{1,\bullet}\), \(\ell_2(\mu,\nu)=[\mu,\nu]\).
\item \(\mu\in\ker\del\subset\PV^{1,\bullet}, \nu\in(\im\del\subset\PV^{2,\bullet})\oplus(\ker\del\subset\PV^{3,\bullet})\), \(\ell_2(\mu,\nu)=(-1)^{|\mu|-1}\phi_{C_1}[\mu, \phi^{-1}_{C_1}\nu]\) and \(\ell_2(\nu, \mu)=\phi_{C_1}[\phi^{-1}_{C_1}\nu, \mu]\)
\item \(\mu\in\ker\del\subset\PV^{1,\bullet}, \nu\in(\im\del\subset\PV^{3,\bullet})\oplus(\ker\del\subset\PV^{5,\bullet})\), \(\ell_2(\mu,\nu)=(-1)^{|\mu|-1}\phi_{C_2}[\mu, \phi^{-1}_{C_2}\nu]\) and \(\ell_2(\nu, \mu)=\phi_{C_2}[\phi^{-1}_{C_2}\nu, \mu]\)
\item All other brackets vanish for degree reasons.
\end{enumerate}
\end{itemize}
\end{itemize}

\begin{prop}
The above in fact defines a (shifted) $L_\infty$-structure.
\end{prop}

\begin{rmk}
\begin{itemize}
\item Note that the complex underlying $\mc E_{mBCOV}^{C_1,C_2}$ does not arise as sections of a graded vector bundle due to the presence of the constraints.
\item Recall that minimal BCOV theory has fields $\mc E_{mBCOV}=\oplus_{i\leq 3} (\ker\del\subset\PV^{\i,\bullet}$. As we have mentioned above, we may view the underlying complex of $\mc E_{mBCOV}^{C_1,C_2}$ as gotten by replacing $\ker\del\subset\PV^{2/3,\bullet}\subset\mc E_{mBCOV}$ with $\PV^{3/4,\bullet}$ in the same degree, and using the isomorphisms $\phi_{C_1,C_2}$. The $L_\infty$ structure is gotten by simply transporting the ordinary Schouten-Nijenhuis bracket on \[\PV^{0,\bullet}\oplus(\ker\del\subset\PV^{1,\bullet}\oplus\PV^{3,\bullet}[]\oplus\PV^{4,\bullet}[]\] and applying the fact that since $\del$ is a derivation of $[-,-]$, for $\mu\in\ker\del$, $[\mu,\del\gamma]=(-1)^{|\mu|-1}\del[\mu,\gamma]$ and $[\del\gamma,\mu]=\del[\gamma,\mu]$. Hopefully this demystifies the above formulas.
\item Suppose we were to naively try to define a BV pairing $\omega$ on $\mc E_{mBCOV}^{C_1,C_2}$ by $\omega(-,-)=\int (-)\wedge\del^{-1}(-)$ and write an "action functional" using the above $L_\infty$-structure. Then the resulting action functional would be equivalent to one coming from an honest BV pairing and an $L_\infty$-structure involving a composition of $\del$ and the ordinary Schouten-Nijenhuis bracket. Note that we could have accomplished the same thing by choosing splittings of $\del$ from any $\im\del\subset \PV^{d_1,\bullet}$, $\im\del\subset\PV^{d_2,\bullet}$ such that $d_1+d_2\neq d-1$. However, it seems like these two choices of splittings are favored in a sense (articulated below). 
\end{itemize}
\end{rmk}

\section{Dimensional Reduction}
Let's consider the holomorphic twist of M-theory on $\R\times\C^\times\times\C^4$. We may decompose the fields as
\begin{itemize}
\item \[\mu=\mu_{01}+\mu_{10}\in\Omega^\bullet(\R)\otimes\left (\begin{aligned} &( \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4)) \\ \oplus & (\PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4))\end{aligned} \to\PV^{0,\bullet}(\C^\times\times\C^4)\right ).\]
\item $\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4))$.
\end{itemize}

\begin{prop}
There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\times\mc E_{mBCOV}^{C_1,C_2}$ given by 
\begin{itemize}
\item $[\mu_{01}]\mapsto\mu^1\in\ker\del\subset\PV^{1,\bullet}(\C^4)\subset\mc E_{mBCOV}^{C_1,C_2}$
\item $[\mu_{10}]\mapsto\mu^3 =\del_{\C^4}(\mu_{10}\Omega^{-1}_{\C^4})\subset\im\del\subset\PV^{3,\bullet}\subset\mc E_{mBCOV}^{C_1,C_2}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
\item $[\gamma_{01}]\mapsto\mu^2 = \del_{C^4}(\gamma_{01}\vee\Omega^{-1}_{\C^4})\subset\im\del\subset\PV^{2,\bullet}\subset\mc E_{mBCOV}^{C_1,C_2}$.
\item $[\gamma_{10}]\mapsto\mu^0\in\PV^0\subset\mc E_{mBCOV}^{C_1,C_2}$
\end{itemize}
preserving the relevant pairings.
\end{prop}

That is, the reduction of the holomorphic M theory on a holomorphic circle should be the $\SU(4)$ invariant twist of $\IIA$. 
\end{document}

### 2020-08-27 BCOV with potentials/BCOV with potentials.tex
2d BCOV

@@
 \usepackage{macros}
+\usepackage{tikz,tikz-cd}
+
+%brian's macros
+\newcommand\bu{\bullet}
+
 \author{Surya Raghavendran}
@@
 Under the conjectures of Costello-Li that describe twisted type II supergravity in terms of BCOV theory, these primitives correspond to certain components of Ramond-Ramond fields, which are chosen as potentials for Ramond-Ramond field strengths.
+
+\section{Warm-up: Kodaira--Spencer theory on a Calabi--Yau surface}
+
+Let $X$ be a Calabi--Yau surface. 
+Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded theory described by two fundamental sets of fields:
+\begin{itemize}
+\item An odd field given by a divergence-free holomorphic vector field $\mu^1$. 
+\item An even field given by a holomorphic function $\mu^0$.
+\end{itemize}
+These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
+There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.
+
+The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \PV^{0,\bu} \\
+ \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} .
+\end{tikzcd}
+\]
+We refer to this locally free description by $\mc E$. 
+The Lie bracket on $\Pi \mc E^{\rm hol}$ described above extends to a Lie bracket on $\Pi \mc E$.
+Together with the differential this gives $\Pi \mc E$ the structure of a local dg Lie algebra.
+
+The bundle $\mc E$ is equipped with an odd Poisson tensor defined by 
+\[
+\Pi = (\partial \otimes 1) \delta_{\rm Diag} .
+\]
+
+We introduce another theory called minimal Kodaira--Spencer theory ``with potentials" that we will refer to as $\mc E_{\rm pot}$. 
+The underlying vector bundle is 
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \PV^{0,\bu} \\
+ \PV^{2,\bu}  .
+\end{tikzcd}
+\]
+The parity shifted bundle $\Pi \mc E_{\rm pot}$ also has the structure of a local Lie algebra described in the following way.
+
+First, we note that any Calabi--Yau service comes equipped with a holomorphic symplectic structure and hence there is a Poisson bracket of holomorphic functions. 
+First, $\PV^{2, \bu}$ has a Lie bracket defined by the equation
+\[
+[\alpha, \alpha']_{\PV^2} = \Omega^{-1} [\Omega \alpha, \Omega \alpha'] .
+\]
+
+The theory $\mc E_{\rm pot}$ is a non-degenerate BV theory with BV pairing defined by the wedge-and-integrate pairing
+\[
+\alpha, \beta \mapsto \int \alpha \wedge \beta  .
+\]
+
+There is a map of bundles $\Phi : \mc E_{\rm Pot} \to \mc E$ which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
+It is a direct calculation to check that $\Phi$ defines a map on the parity shifted local Lie algebras.
+In fact, we have the following.
+
+\begin{prop}
+The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
+\[
+\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
+\]
+\end{prop}
 

### 2020-09-04 unconstrained.tex
unconstrained

\documentclass[11pt]{amsart}

\pdfoutput = 1

\usepackage{macros,slashed,amsaddr}
%\usepackage[dvipsnames]{xcolor}

\linespread{1.5}

\setcounter{tocdepth}{2}
\numberwithin{equation}{section}
\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup}
\newcommand{\changelocaltocdepth}[1]{%
  \addtocontents{toc}{\protect\setcounter{tocdepth}{#1}}%
  \setcounter{tocdepth}{#1}%
}
\setcounter{tocdepth}{1}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\newcommand{\defterm}[1]{\textbf{\emph{#1}}}

\def\PV{{\rm PV}}

\begin{document}

\title{Quantization of the unconstrained theory}

\maketitle

Consider the $\ZZ/2$-graded theory on $\CC^5 \times \RR$ with two sets of fundamental fields:
\begin{align*}
\mu & \in \Pi \Omega^\bu (\RR) \, \Hat{\otimes} \, \PV^{1,\bu}(\CC^5) \\
\gamma & \in \Omega^{\bu}(\RR) \, \Hat{\otimes} \, \Omega^{1,\bu}(\CC^5) .
\end{align*}
We will denote the full space of fields of the theory by $\cE$.

This is a non-degenerate BV theory with pairing defined by
\[
\int \gamma \wedge (\mu \vdash \Omega) .
\]

The action is 
\[
S = \int \gamma \bigg(\d \mu + \frac12 [\mu, \mu] \bigg) \vdash \Omega + \frac13 \int \gamma \partial \gamma \partial \gamma .
\]
where $[\cdot, \cdot]$ denotes the Lie bracket of vector fields.

The first term describes a theory of BF type based on the local Lie algebra 
\[
\cL = \Omega^\bu(\RR) \, \Hat{\otimes} \, \PV^{1,\bu}(\CC^5) .
\]
With the term $\frac13\int \gamma \partial \gamma \partial \gamma$ we will view this theory as a deformation of a BF type theory.

Let $\oloc(\cE)$ denote the cochain complex of local functionals.
It is equipped with the classical BRST operator 
\[
\{S, -\} = \d + \d_{\rm CE} + \delta 
\]
where $\d_{\rm CE}$ denotes (roughly) the Chevalley--Eilenberg differential for holomorphic vector fields and $\delta$ is the operator $\left\{\frac13 \int \gamma \partial \gamma \partial \gamma \;, \; \cdot \; \right\}$.

The anomaly to satisfying the quantum master equation is a class in $H^1 (\oloc(\cE))$.

There is a decreasing filtration on $\oloc(\cE)$ whose $p$th layer $F^p \oloc(\cE)$ consists of local functionals which are at least $p$-linear in the field $\gamma$. 
\brian{I'm worried that this isn't a complete filtration.}

Roughly, the $p$th layer in the associated graded of this filtration is the local cohomology of holomorphic vector fields on $\CC^5$ with values in a particular local module corresponding to $p$-linear local functionals of the field $\gamma$.

\begin{itemize}
\item At the zeroth layer $p=0$, the associated graded is the local Lie algebra cochains $\cloc^\bu(\cL)$. 
By an argument similar to \brian{Brian and Chris}, we see that at this stage there the class of the anomaly can be  identified with a class in  $H^{12} (\fw_5)$ where $\fw_5$ is the Lie algebra of vector fields on the formal $5$-disk.
This cohomology is trivial $H^{12}(\fw_5) = H^{13}({\rm BU}(5)) = 0$. 
\brian{check this first isomorphism, there might be a connecting differential}

\item \brian{at the next layer it seems like we should be looking at $H^\bu(\fw_5, \fw_5)$.}
\end{itemize}

\end{document}

zshhjknbhucvvgbbnhhggFDGFGRTRYYRTDFSXR465768787YHGBCVBNBVBCBVNBCGFH,J.LK;K,HNGDGFgyggcbgnhHKJLK;OLLJGjhhjghuykjogfytcjfukkh

CGFTHFHXCVXBGFVFSGDYGFHDGYGdvffdfgdrt544465y7hgff

 dgfhjgyfhghj dfdgfsdgfdgfgdff 
 dhgngsfhffdgfgdtd

 tdtdg
 f
 hy
 ftttegfdtrfgdfdfdgfgdffgdtrgdfdfrredfr4wertryutrt45
 6

 Laszlofuyryjgfghfjhhfgth
 dfxgcfdtfhgyugdghjgytfghdfgnhghytfdhghdttrhykuscvbghkiotgf

### 2020-09-04 BCOV with potentials/BCOV with potentials.tex

@@
 \usepackage{tikz,tikz-cd}
-
+\newcommand{\surya}[1]{(\textcolor{red}{Surya: #1})}
 %brian's macros
@@
 
-\author{Surya Raghavendran}
 \date{\today}
@@
 \label{sec:org3d6a090}
+Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\Z/2$-graded theory with the following fundamental fields:
+\begin{itemize}
+\item The even fields are a holomorphic function $\mu^0$ and a $\del$-closed holomorphic bivector $\mu^0$.
+\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\del$-closed holomorphic section of $\wedge^3 T_X$. 
+\end{itemize}
 
+As before, these fields combine to define a $\Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$.
+The parity reversed sheaf $\Pi\mc E^{\rm hol}$ has a graded Lie algebra structure given by the Schouten-Nijenhuis bracket of holomorphic polyvector fields.
+
+The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
+& & & \PV^{0,\bu} \\
+& & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\
+& \PV^{2,\bu} \ar[r,"\del"] & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\ 
+\PV^{3,\bu}\ar[r, "\del"]& \PV^{2,\bu} \ar[r,"\del"] & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\ 
+\end{tikzcd}
+\]
+
+We denote this locally free description as $\mc E$.
+As before, the Lie bracket induced from the one on $\Pi\mc E^{\rm hol}$ and the differntial conspire to give $\Pi\mc E$ the structure of a local dg Lie algebra.
+Furthermore, the sheaf $\mc E$ is equipped with an odd Poisson tensor given by $\Pi = (\del\otimes 1)\delta_{\rm Diag}$.
+Together, this data equips $\mc E$ with the structure of a $\Z/2$-graded Poisson BV theory.
+
+As in the surface case, there is a closely related BV theory gotten by adding "potentials" - we will again refer to this as $\mc E_{\rm pot}$. The underlying vector bundle is 
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
+& & & \PV^{0,\bu} \\
+& & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\
+& \PV^{3,\bu} & &  \\ 
+\PV^{4,\bu}&  &  & \\ 
+\end{tikzcd}
+\]
+
+There is a bundle map $\Phi: \mc E_{\rm pot}\to \mc E$ given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$.
+We may equip the parity shifted bundle $\Pi\mc E_{\rm pot}$ with the structure of a local dg Lie algebra such that $\Phi$ is a map of Lie algebras.
+\surya{Will add explicit description of the brackets}.
+Together with the wedge and integrate pairing, $\mc E_{\rm pot}$ has the structure of a nondegenerate BV theory.
+
+In fact, we have the following, analogous to the case of a Calabi-Yau surface:
+\begin{prop}
+The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
+\[
+\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
+\]
+\end{prop}
+
+\iffalse
 Let \(X\) be a CY4.
@@
 \end{rmk}
+\fi
 

### 2020-09-23 BCOV with potentials/BCOV with potentials.tex
added remark about dimensional reduction, fixing mistake from discussion

@@
 \begin{itemize}
-\item The even fields are a holomorphic function $\mu^0$ and a $\del$-closed holomorphic bivector $\mu^0$.
+\item The even fields are a holomorphic function $\mu^0$ and a $\del$-closed holomorphic bivector $\mu^2$.
 \item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\del$-closed holomorphic section of $\wedge^3 T_X$. 
@@
 \ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
-& & & \PV^{0,\bu} \\
-& & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\
-& \PV^{3,\bu} & &  \\ 
-\PV^{4,\bu}&  &  & \\ 
+& & & \mu^{0}\in\PV^{0,\bu} \\
+& & \mu^{1}\in\PV^{1,\bu} \ar[r, "\partial"] & \mu^{c}\in\PV^{0,\bu} \\
+& \gamma^{3}\in\PV^{3,\bu} & &  \\
+\gamma^{4}\in\PV^{4,\bu}&  &  & \\
 \end{tikzcd}
@@
 \begin{itemize}
-\item \[\mu=\mu_{01}+\mu_{10}\in\Omega^\bullet(\R)\otimes\left (\begin{aligned} &( \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4)) \\ \oplus & (\PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4))\end{aligned} \to\PV^{0,\bullet}(\C^\times\times\C^4)\right ).\]
+\item \[(\mu^{1}, \mu^{0})=(\mu_{01}+\mu_{10}, \mu^{0})\in\Omega^\bullet(\R)\otimes\left (\begin{aligned} &( \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4)) \\ \oplus & (\PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4))\end{aligned} \to\PV^{0,\bullet}(\C^\times\times\C^4)\right ).\]
 \item $\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4))$.
@@
 \begin{prop}
-There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\times\mc E_{mBCOV}^{C_1,C_2}$ given by 
+There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\otimes\mc E_{Pot}$ given by
 \begin{itemize}
-\item $[\mu_{01}]\mapsto\mu^1\in\ker\del\subset\PV^{1,\bullet}(\C^4)\subset\mc E_{mBCOV}^{C_1,C_2}$
-\item $[\mu_{10}]\mapsto\mu^3 =\del_{\C^4}(\mu_{10}\Omega^{-1}_{\C^4})\subset\im\del\subset\PV^{3,\bullet}\subset\mc E_{mBCOV}^{C_1,C_2}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
-\item $[\gamma_{01}]\mapsto\mu^2 = \del_{C^4}(\gamma_{01}\vee\Omega^{-1}_{\C^4})\subset\im\del\subset\PV^{2,\bullet}\subset\mc E_{mBCOV}^{C_1,C_2}$.
-\item $[\gamma_{10}]\mapsto\mu^0\in\PV^0\subset\mc E_{mBCOV}^{C_1,C_2}$
+\item $[\gamma_{10}]\mapsto\mu^0\in\PV^{0,\bullet}\subset\mc E_{Pot}$.
+  \item $[\mu_{01}]\mapsto\mu^1\in\PV^{1,\bullet}(\C^4)\subset\mc E_{Pot}$.
+\item $[\mu^{0}]\mapsto\mu^{c}\in\PV^{0, \bullet}(\C^{4})\subset\mc E_{Pot}$.
+\item $[\gamma_{01}]\mapsto\mu^3 = \gamma_{01}\vee\Omega^{-1}_{\C^4}\in\PV^{3,\bullet}\subset\mc E_{Pot}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
+\item $[\mu_{10}]\mapsto\mu^4 =\mu_{10}\vee\Omega^{-1}_{\C^4}\in\PV^{4,\bullet}\subset\mc E_{Pot}$ .
+
 \end{itemize}
@@
 That is, the reduction of the holomorphic M theory on a holomorphic circle should be the $\SU(4)$ invariant twist of $\IIA$.
+
+\begin{rmk}
+Note that the field $\mu^{c}\in \mc E_{\mr Pot}$ is nonpropating.
+It must pair against a field in $\PV^{3}$.
+In order for the field $\mu^{0}$ in M-theory to propogate, it must pair against a field $\gamma^{0}\in \Omega^{0,\bullet}$ which is the ghost for the gauge transformation for $\gamma^{1}$.
+This suggests an enlargement of $\mc E_{\mr Pot}$ where we add an additional field in $\PV^{3}$ which will be the image of the ghost of $\gamma^{1}$ in M-theory under dimensional reduction.
+\end{rmk}
+
+\surya{ When we discussed dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$.
+I realized this was wrong - the resulting map cannot be a Lie map.
+Indeed, there is certainly a nontrivial bracket between $\gamma_{10}$ and $\gamma_{10}$ in M-theory, from expanding the $\gamma\del\gamma\del\gamma$ term.
+However, there is no nontrivial bracket between $\PV^{3,\bullet}$ and $\PV^{4,\bullet}}$ in $\mc E_{\rm Pot}$ }
+
 \end{document}

### 2020-09-29 BCOV with potentials/BCOV with potentials.tex
cy4

@@
 \newcommand{\surya}[1]{(\textcolor{red}{Surya: #1})}
+\newcommand{\brian}[1]{(\textcolor{blue}{Brian: #1})}
 %brian's macros
 \newcommand\bu{\bullet}
+\newcommand\dbar{\overline{\partial}}
 
@@
 
-We introduce another theory called minimal Kodaira--Spencer theory ``with potentials" that we will refer to as $\mc E_{\rm pot}$. 
+We introduce another theory on the Calabi--Yau surface $X$ that we call minimal Kodaira--Spencer theory {\em with potentials}.
 The underlying vector bundle is 
@@
 \]
-The parity shifted bundle $\Pi \mc E_{\rm pot}$ also has the structure of a local Lie algebra described in the following way.
+We will denote the resulting $\mb Z/2$-graded sheaf of cochain complexes by $\mc E_{\rm pot}$.
 
-First, we note that any Calabi--Yau service comes equipped with a holomorphic symplectic structure and hence there is a Poisson bracket of holomorphic functions. 
-First, $\PV^{2, \bu}$ has a Lie bracket defined by the equation
+We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way. 
+There is a map of bundles $\Phi : \mc E_{\rm Pot} \to \mc E$ which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
+It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes.
+
+In fact, the parity shifted bundle $\Pi \mc E_{\rm pot}$ also has the structure of a local Lie algebra, and the map $\Phi$ intertwines these local Lie algebra structures.
+
+To describe the local Lie algebra structure on minimal Kodaira--Spencer theory with potentials we use the Calabi--Yau form $\Omega$ to identify $\mc E_{\rm Pot}$ with the sheaf of cochain complexes
 \[
-[\alpha, \alpha']_{\PV^2} = \Omega^{-1} [\Omega \alpha, \Omega \alpha'] .
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \Omega^{2,\bu} \\
+ \Omega^{0,\bu}  .
+\end{tikzcd}
 \]
 
-The theory $\mc E_{\rm pot}$ is a non-degenerate BV theory with BV pairing defined by the wedge-and-integrate pairing
+Now, note that any Calabi--Yau surface comes equipped with a holomorphic symplectic structure and there is a Poisson bracket defined on the sheaf of holomorphic functions.
+Since the bracket is defined in terms of holomorphic differential operators, it extends to a bracket on the Dobleault complex $\Omega^{0,\bu}(X)$.
+
+This further extends to a local Lie algebra structure on the semi-direct product 
+\[
+\Omega^{0,\bu}(X) \ltimes \Pi \Omega^{2,\bu}(X)
+\]
+which describes the local Lie structure on $\Pi \mc E_{\rm Pot}$. 
+It is immediate to verify that the map $\Phi : \mc E_{\rm pot} \to \mc E$ intertwines the two $L_\infty$-structures.
+
+%Using the isomorphism $\Omega : \PV^{2, \bu} (X) \cong \Omega^{0,\bu}(X)$ we thus obtain a Lie bracket on $\PV^{2,\bu}(X)$ defined by the equation
+%\[
+%[\alpha, \alpha']_{\PV^2} = \Omega^{-1} [\Omega \alpha, \Omega \alpha'] .
+%\]
+%This endows $\PV^{2,\bu}(X)$ 
+%
+%The sheaf $\PV^{0,\bu}(X)$ is a module for
+
+Finally, the theory $\mc E_{\rm pot}$ is a non-degenerate BV theory with BV pairing defined by the wedge-and-integrate pairing
 \[
@@
 \]
-
-There is a map of bundles $\Phi : \mc E_{\rm Pot} \to \mc E$ which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
-It is a direct calculation to check that $\Phi$ defines a map on the parity shifted local Lie algebras.
-In fact, we have the following.
 
@@
 \item The even fields are a holomorphic function $\mu^0$ and a $\del$-closed holomorphic bivector $\mu^2$.
-\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\del$-closed holomorphic section of $\wedge^3 T_X$. 
+\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\del$-closed holomorphic section $\mu^3$ of $\wedge^3 T_X$. 
 \end{itemize}
 
-As before, these fields combine to define a $\Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$.
+%As before, these fields combine to define a $\Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$.
 The parity reversed sheaf $\Pi\mc E^{\rm hol}$ has a graded Lie algebra structure given by the Schouten-Nijenhuis bracket of holomorphic polyvector fields.
 
-The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
+The space of fields admits a locally free description obtained by including the ``descendants". 
+The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
+Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$. 
+The sheaf of cochain complexes $\mc E$ underlying minimal Kodaira--Spencer theory on $X$ is 
 \[
@@
 \ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
-& & & \PV^{0,\bu} \\
-& & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\
-& \PV^{2,\bu} \ar[r,"\del"] & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\ 
-\PV^{3,\bu}\ar[r, "\del"]& \PV^{2,\bu} \ar[r,"\del"] & \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} \\ 
+& & & \mu^0 \in \PV^{0,\bu} \\
+& & \sum u^k \mu^1 \in \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
+& \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \del"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\ 
+\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \del"]& u \PV^{2,\bu} \ar[r,"u \del"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\ 
 \end{tikzcd}
 \]
+The differential on this sheaf of cochain complexes is given by $\dbar + u \partial$.
 
-We denote this locally free description as $\mc E$.
-As before, the Lie bracket induced from the one on $\Pi\mc E^{\rm hol}$ and the differntial conspire to give $\Pi\mc E$ the structure of a local dg Lie algebra.
+There is a local Lie algebra structure on $\Pi\mc E$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
+On the fields (including the descendants) it is defined by the formula
+\[
+[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} [\mu^i, \mu^j]_{\rm Sch} .
+\]
+
 Furthermore, the sheaf $\mc E$ is equipped with an odd Poisson tensor given by $\Pi = (\del\otimes 1)\delta_{\rm Diag}$.
@@
 
-As in the surface case, there is a closely related BV theory gotten by adding "potentials" - we will again refer to this as $\mc E_{\rm pot}$. The underlying vector bundle is 
+As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
+The underlying sheaf of cochain complexes is 
 \[
@@
 & & & \mu^{0}\in\PV^{0,\bu} \\
-& & \mu^{1}\in\PV^{1,\bu} \ar[r, "\partial"] & \mu^{c}\in\PV^{0,\bu} \\
-& \gamma^{3}\in\PV^{3,\bu} & &  \\
-\gamma^{4}\in\PV^{4,\bu}&  &  & \\
+& & \sum u^k \mu^{1}\in\PV^{1,\bu} \ar[r, "\partial"] & \mu^{c}\in\PV^{0,\bu} \\
+u^{-1} \gamma^3 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
+\gamma^{4} \in\PV^{4,\bu} &  &  & \\
 \end{tikzcd}
 \]
+We will again refer to this sheaf as $\mc E_{\rm pot}$.
 
-There is a bundle map $\Phi: \mc E_{\rm pot}\to \mc E$ given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$.
-We may equip the parity shifted bundle $\Pi\mc E_{\rm pot}$ with the structure of a local dg Lie algebra such that $\Phi$ is a map of Lie algebras.
+There is a local Lie algebra structure described as follows.
+\brian{It's mostly the Schouten bracket, but there is the additional ``weird" bracket
+\[
+[\gamma^3, \gamma^{3'}] = [\partial \gamma^3 , \gamma^{3'}] \pm [\gamma^3, \partial \gamma^{3'}] .
+\]
+}
+
+There is a map of sheaves of cochain complexes $\Phi: \mc E_{\rm pot}\to \mc E$ given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$.
+Explicitly, in formulas
+\[
+\begin{array}{ccccccccc}
+\Phi(t^k \mu^{i}) & = & u^k \mu^i & \in & u^k \PV^{i, \bu} & i = 0,1 \\
+\Phi(u^{-1} \gamma^3) & = & 0 \\
+\Phi(\gamma^3) & = & \partial \gamma^3 & \in & \PV^{2,\bu} \\
+\Phi(\gamma^4) & = & \partial \gamma^4 & \in & \PV^{3,\bu} .
+\end{array} 
+\]
+
+%We may equip the parity shifted bundle $\Pi\mc E_{\rm pot}$ with the structure of a local dg Lie algebra such that $\Phi$ is a map of Lie algebras.
 \surya{Will add explicit description of the brackets}.
+
 Together with the wedge and integrate pairing, $\mc E_{\rm pot}$ has the structure of a nondegenerate BV theory.
@@
 
-\iffalse
+%\iffalse
 Let \(X\) be a CY4.
@@
 \end{rmk}
-\fi
+%\fi
 
@@
 It must pair against a field in $\PV^{3}$.
-In order for the field $\mu^{0}$ in M-theory to propogate, it must pair against a field $\gamma^{0}\in \Omega^{0,\bullet}$ which is the ghost for the gauge transformation for $\gamma^{1}$.
+In order for the field $\mu^{0}$ in M-theory to propagate, it must pair against a field $\gamma^{0}\in \Omega^{0,\bullet}$ which is the ghost for the gauge transformation for $\gamma^{1}$.
 This suggests an enlargement of $\mc E_{\mr Pot}$ where we add an additional field in $\PV^{3}$ which will be the image of the ghost of $\gamma^{1}$ in M-theory under dimensional reduction.
@@
 
-\surya{ When we discussed dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$.
+\surya{ When we discussewd dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$.
 I realized this was wrong - the resulting map cannot be a Lie map.
 Indeed, there is certainly a nontrivial bracket between $\gamma_{10}$ and $\gamma_{10}$ in M-theory, from expanding the $\gamma\del\gamma\del\gamma$ term.
-However, there is no nontrivial bracket between $\PV^{3,\bullet}$ and $\PV^{4,\bullet}}$ in $\mc E_{\rm Pot}$ }
+However, there is no nontrivial bracket between $\PV^{3,\bullet}$ and $\PV^{4,\bullet}$ in $\mc E_{\rm Pot}$ }
 

### 2020-09-29 BCOV with potentials/BCOV with potentials.tex
small changes

@@
 Let $X$ be a Calabi--Yau surface. 
-Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded theory described by two fundamental sets of fields:
+Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded Poisson BV theory described by two fundamental sets of fields:
 \begin{itemize}
@@
  & \PV^{0,\bu} \\
- \PV^{1,\bu} \ar[r, "\partial"] & \PV^{0,\bu} .
+ \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
 \end{tikzcd}
@@
 
-%\iffalse
+\iffalse
 Let \(X\) be a CY4.
@@
 \end{rmk}
-%\fi
+\fi
 
 \section{Dimensional Reduction}
-Let's consider the holomorphic twist of M-theory on $\R\times\C^\times\times\C^4$. We may decompose the fields as
-\begin{itemize}
-\item \[(\mu^{1}, \mu^{0})=(\mu_{01}+\mu_{10}, \mu^{0})\in\Omega^\bullet(\R)\otimes\left (\begin{aligned} &( \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4)) \\ \oplus & (\PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4))\end{aligned} \to\PV^{0,\bullet}(\C^\times\times\C^4)\right ).\]
-\item $\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4))$.
-\end{itemize}
+Let's consider the $11$-dimensional theory on the manifold
+\[
+\R\times\C^\times\times\C^4 .
+\]
+
+The fields decompose as follows.
+For the ``base" direction, fields we labeled by $\mu$, we have
+\[
+\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ \oplus & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
+\]
+
+For the ``fiber" direction, fields we labeled by $\gamma$, we have
+\[
+\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ \oplus & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
+\]
+
+The ``zero modes" of the reduction along the circle $S^1 \subset \mb C^\times$ will be denoted by the same symbols.
+\brian{write down this sheaf on $\mb C^4 \times \mb R^2$.}
+
+Define the map of sheaves of cochain complexes 
+\[
+\Psi : \pi_* \mc E_{11d} \to \mc E_{\rm pot} \Hat{\otimes} \Omega^\bu(\mb R^2) 
+\] 
+by
+\[
+\begin{array}{cccccccc}
+\Psi (\mu_{01}) & = & \mu_{01} & \in & \PV^{1,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\
+\Psi (\mu_{10}) & = & \mu_{10} \vee \Omega^{-1}_{\mb C^4} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) .
+\end{array}
+\]
+
+%\[
+%\gamma=\gamma_{01}+\gamma_{10}\in \Omega^\bullet(\R)\otimes(\Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\oplus\Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)) .
+%\]
 
@@
 
+\section{Compactification to five dimensions}
+
+Now, consider placing the $11$-dimensional theory on the manifold
+\[
+X \times Y \times \mb R 
+\]
+where $X$ is compact Calabi--Yau three-fold and $Y$ is a Calabi--Yau surface.
+We consider the compactification of the theory along the projection map 
+\[
+\pi : X \times Y \times \mb R \to Y \times \mb R .
+\]
+Recall, the space of fields of the $11$-dimensional theory is
+\begin{equation}\label{eqn:cotangent1}
+T^* [-1] \bigg(\PV^{\leq 1,\bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) [1] \bigg) .
+\end{equation}
+
+Since $X$ is compact and Calabi--Yau, we have a sequence of quasi-isomorphisms 
+\[
+\PV^{j, \bu}(X) \cong_{\Omega_X} \Omega^{3-j, \bu} (X) \simeq H^{3-j, \bu}(X) .
+\]
+The first isomorphism is simply contraction with the Calabi--Yau form $\Omega_X \in \Omega^{3,hol}(X)$ and the second quasi-isomorphism follows from formality of $X$.
+
+In particular, at the level of sheaves one has a quasi-isomorphism
+\[
+\pi_* \bigg(\PV^{\leq 1,\bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) [1] \bigg) \simeq H^{\geq 2, \bu}(X) \otimes \PV^{\leq 1, \bu} (Y) \Hat{\otimes} \Omega^\bu (\mb R) [1] .
+\]
+This describes the ``base" direction, fields we labeled by $\mu$, of the space of fields (\ref{eqn:cotangent1}) upon compactification.
+
+We extract the piece of the above sheaf which involves the top cohomology $H^{3,3}(X) \cong H^6(X) \cong \mb C$. 
+This is the sheaf
+\begin{equation}\label{eqn:pair1}
+\PV^{\leq 1, \bu}(Y) \Hat{\otimes} \Omega^\bu (\mb R) [1] .
+\end{equation}
+(Recall, we are only working with sheaves of $\mb Z/2$-graded cochain complexes.)
+
+Likewise, the ``fiber" direction of (\ref{eqn:cotangent1}) becomes, after compactification:
+\[
+\pi_* \bigg(\Omega^{\leq 1, \bu}(X \times Y) \Hat{\otimes} \Omega^\bu(\mb R) \bigg) \simeq H^{\leq 1, \bu}(X) \otimes \Omega^{\leq 1, \bu} (X) \Hat{\otimes} \Omega^\bu (\mb R)  .
+\]
+Under the BV pairing, the piece of this sheaf of cochain complexes with (\ref{eqn:pair1}) is the part involving $H^0(X) \cong \mb C$.
+This is precisely
+\[
+\Omega^{\leq 1}(X) \Hat{\otimes} \Omega^\bu (\mb R) .
+\]
+
 \end{document}

### 2020-10-14 oldstuff/unconstrained.tex
update

\documentclass[11pt]{amsart}

\pdfoutput = 1

\usepackage{macros,slashed,amsaddr}
%\usepackage[dvipsnames]{xcolor}

\linespread{1.5}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}

\begin{document}

\title{Quantization of the unconstrained theory}

\maketitle

Consider the $\ZZ/2$-graded theory on $\CC^5 \times \RR$ with two sets of fundamental fields:
\begin{align*}
\mu & \in \Pi \Omega^\bu (\RR) \, \Hat{\otimes} \, \PV^{1,\bu}(\CC^5) \\
\gamma & \in \Omega^{\bu}(\RR) \, \Hat{\otimes} \, \Omega^{1,\bu}(\CC^5) .
\end{align*}
We will denote the full space of fields of the theory by $\cE$.

This is a non-degenerate BV theory with pairing defined by
\[
\int \gamma \wedge (\mu \vdash \Omega) .
\]

The action is 
\[
S = \int \gamma \bigg(\d \mu + \frac12 [\mu, \mu] \bigg) \vdash \Omega + \frac13 \int \gamma \partial \gamma \partial \gamma .
\]
where $[\cdot, \cdot]$ denotes the Lie bracket of vector fields.

The first term describes a theory of BF type based on the local Lie algebra 
\[
\cL = \Omega^\bu(\RR) \, \Hat{\otimes} \, \PV^{1,\bu}(\CC^5) .
\]
With the term $\frac13\int \gamma \partial \gamma \partial \gamma$ we will view this theory as a deformation of a BF type theory.

Let $\oloc(\cE)$ denote the cochain complex of local functionals.
It is equipped with the classical BRST operator 
\[
\{S, -\} = \d + \d_{\rm CE} + \delta 
\]
where $\d_{\rm CE}$ denotes (roughly) the Chevalley--Eilenberg differential for holomorphic vector fields and $\delta$ is the operator $\left\{\frac13 \int \gamma \partial \gamma \partial \gamma \;, \; \cdot \; \right\}$.

\section{One-loop Feynman diagrams}

To construct the one-loop quantization we must first construct a one-loop effective family. 
This is a family of functionals $\{I[L]\}_{L>0}$ which satisfies the renormalization group equations.

The $11$-dimensional theory on $\CC^5 \times \RR$ that we consider is a mixed holomorphic-topological theory. 
Heuristically, this means that the theory depends holomorphically on $\CC^5$ and topologically on $\RR$.

%\begin{dfn}
%Let $X$ be a complex manifold and $M$ a smooth manifold.
%A {\em mixed holomorphic-topological} elliptic complex on $X \times M$ is an elliptic complex of the form
%\[
%\Omega^{0,\bu}(X , V) \Hat{\otimes} \Omega^{\bu} (M, E)
%\]
%where $V$ is a holomorphic vector bundle on $X$ and $E$ is a flat vector bundle on $M$. 
%\end{dfn}

\begin{thm}[\cite{GWR}] \label{thm:oneloop}
For any mixed holomorphic-topological theory on $\CC^n \times \RR^m$, $n,m \geq 0$, there exists 
a translation-invariant effective family $\{I[L]\}$ which to first order in $\hbar$ is finite. 
\end{thm}

We briefly recount the main elements involved in the proof of this theorem. 
The result relies on the existence of a propagator corresponding to the ``holomorphic-topological" gauge that enjoys particularly desirable analytic properties. 
At the level of the free theory, the linear BRST operator for the $11$-dimensional theory in question is of the form 
\[
\dbar + \partial_\Omega + \d_{\rm dR} .
\]
The first term denotes the $\dbar$-operator corresponding to a graded holomorphic vector bundle built from polyvector fields on $X = \CC^5$. 
The second term term is the holomorphic differential operator action by the divergence operator on the same bundle of polyvector fields. 
The third term is the de Rham operator along $\RR$.

The ``holomorphic-topological gauge" refers to the choice of the following gauge fixing operator
\[
Q^{\rm GF} = \dbar^* + \d_{\rm dR}^* .
\]

The heat kernel is
\begin{align*}
K_{t} (z, t ; w , s) & = \frac{1}{(2\pi i)^{11/2}} e^{|z-w|^2/4t + (t-s)^2/4t} \times \\
& \sum_{i=1}^5 \left(\partial_{z^i} - \partial_{w^i} \right) \otimes (\d z^i - \d w^j) \otimes \prod_{j=1}^5 (\d \zbar^j - \d \wbar^j) \otimes (\d t - \d s)
\end{align*}

The propagator is
\[
P_{\epsilon < L} (z, t ; w , s) = \int_{T=\epsilon}^L Q^{\rm GF} K_{t} (z, t ; w , s) \d T .
\]

\section{The quantum master equation}

The anomaly to satisfying the scale $L$ quantum master equation is 
\[
\Theta[L] =
Q I[L] + \hbar \triangle_L I[L] + \frac{1}{2} \{I[L], I[L]\}_L .
\]
Here $\triangle_L$ is the well-defined regularized scale $L$ BV Laplacian, and $\{-,-\}_L$ is a regularized version of the classical BV bracket.
The $\hbar \to 0$, $L \to 0$ limit of the above equation is precisely the classical master equation. 
An effective family $\{I[L]\}$ is a quantum field theory if it satisfies the scale $L$ QME for every $L > 0$. 
For more complete details we refer to \cite[Chapter 8]{Book2}.

In general, not every effective theory satisfies the QME. 
The {\em scale} $L$ {\em anomaly} to satisfying the QME describes the failure of $I[L]$ to satisfy the scale $L$ QME.
Since $I[L]$ is filtered by powers of $\hbar$, so is the anomaly.
For theories of cotangent type as considered in this paper, $I[L]$ truncates at order $\hbar$, hence we only need to consider the $\hbar$-linear anomaly which we denote by $\hbar \Theta[L]$. 
The $L \to 0$ limit of $\Theta[L]$ is defined and determines a cohomological degree $+1$ {\em local functional}
\[
\Theta \define \lim_{L \to 0} \Theta [L] \in \oloc(\cE) .
\]
Moreover, $\Theta$ is closed for the classical differential $\{S,-\}_{\rm BV}$, hence determines a cohomology class 
\[
[\Theta] \in H^1(\oloc(\cE), \{S,-\}_{\rm BV}),
\]
see \cite[\S 5.11]{CostelloBook}.

\subsection{The obstruction deformation complex}

There is a decreasing filtration on $\oloc(\cE)$ whose $p$th layer $F^p \oloc(\cE)$ consists of local functionals which are at least $p$-linear in the field $\gamma$. 
\brian{I'm worried that this isn't a complete filtration.}

Roughly, the $p$th layer in the associated graded of this filtration is the local cohomology of holomorphic vector fields on $\CC^5$ with values in a particular local module corresponding to $p$-linear local functionals of the field $\gamma$.

\begin{itemize}
\item At the zeroth layer $p=0$, the associated graded is the local Lie algebra cochains $\cloc^\bu(\cL)$. 
By an argument similar to \brian{Brian and Chris}, we see that at this stage there the class of the anomaly can be  identified with a class in  $H^{12} (\fw_5)$ where $\fw_5$ is the Lie algebra of vector fields on the formal $5$-disk.
This cohomology is trivial $H^{12}(\fw_5) = H^{13}({\rm BU}(5)) = 0$. 
\brian{check this first isomorphism, there might be a connecting differential}

\item \brian{at the next layer it seems like we should be looking at $H^\bu(\fw_5, \fw_5)$.}
\end{itemize}

\subsection{Characterizing the anomaly cocycle}

A general result of Costello \cite[Corollary 16.0.5]{CostelloWittengenus} states that the one-loop anomaly of any BV theory reduces to the weight of a sum of wheel graphs.
Furthermore, using the holomorphic-topological gauge, the types of wheels that appear are those with a fixed number of vertices as we will soon explain.

To state the following result, we fix some notation. 
If $\Gamma$ is a graph with a distinguished internal edge $e$, let $W_{\Gamma,e}(P_{\epsilon<L},K_{\epsilon}, I)$ denote the following modified weight. 
Instead of placing $P_{\epsilon <L}$ at each internal edge, we place $K_\epsilon$ at the edge labeled $e$ and $P_{\epsilon<L}$ on the remaining internal edges.

\begin{lem}
The one-loop anomaly cocycle $\Theta \in \oloc(\cE)$ is cohomologous to the $L \to 0$ limit of the expression
\[
\lim_{\epsilon \to 0} \sum_{\Gamma \in {\rm Wheel}_7, e} W_\Gamma(P_{\epsilon < L}, K_\epsilon,I) .
\]
Here the sum is over all wheels with seven vertices equipped with a distinguished edge $e$. 
\end{lem}

\end{document}

zshhjknbhucvvgbbnhhggFDGFGRTRYYRTDFSXR465768787YHGBCVBNBVBCBVNBCGFH,J.LK;K,HNGDGFgyggcbgnhHKJLK;OLLJGjhhjghuykjogfytcjfukkh

CGFTHFHXCVXBGFVFSGDYGFHDGYGdvffdfgdrt544465y7hgff

 dgfhjgyfhghj dfdgfsdgfdgfgdff 
 dhgngsfhffdgfgdtd

 tdtdg
 f
 hy
 ftttegfdtrfgdfdfdgfgdffgdtrgdfdfrredfr4wertryutrt45
 6

 Laszlofuyryjgfghfjhhfgth
 dfxgcfdtfhgyugdghjgytfghdfgnhghytfdhghdttrhykuscvbghkiotgf

### 2020-10-14 paper.tex
update

% Created 2020-10-14 Wed 13:57
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Surya and Brian}
\date{\today}
\title{Twisted \$M\$-theory and its perturbative quantization.}
\hypersetup{
 pdfauthor={Surya and Brian},
 pdftitle={Twisted \$M\$-theory and its perturbative quantization.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section{Definition of twisted supergravity}
\label{sec:orgea6ebfa}
\subsection{The classical BV theory}
\label{sec:org23fe8d4}
\subsection{Moduli theoretic interpretation}
\label{sec:orgd709323}
\section{Quantization of holomorphic-topological theories}
\label{sec:orgec1821a}
\subsection{Effective renormalization}
\label{sec:org2b54a17}
\subsection{The \$11\$-dimensional theory}
\label{sec:org553e6b1}
\subsection{The moduli space of quantizations}
\label{sec:orgefb666b}
\section{Relationship to the Type IIA string}
\label{sec:org22f4829}
\subsection{Kodaira--Spencer theory with potentials}
\label{sec:org9f736c1}
\subsubsection{Warm-up: four-dimensional Kodaira--Spencer theory}
\label{sec:org0b90e8b}
\subsubsection{Eight-dimensional Kodaira--Spencer theory}
\label{sec:org3b2a900}
\subsection{The Type IIA topological string}
\label{sec:org02b0f82}
\subsection{Reduction of twisted supergravity}
\label{sec:org59003d2}
\subsubsection{Calabi--Yau compactifications}
\label{sec:org55d712d}
\subsection{Twisted supergravity on a three-fold}
\label{sec:org7c4a220}
\section{The non-minimal G2 twist}
\label{sec:orgc520304}
\end{document}

### 2020-10-14 oldstuff/BCOV with potentials/BCOV with potentials.tex
update2

--- 2020-09-29 BCOV with potentials/BCOV with potentials.tex
@@
 \newcommand\dbar{\overline{\partial}}
+\newcommand\CC{{\mb C}}
+\newcommand \RR{{\mb R}}
+\def\Hat{\widehat}
 
@@
 
-Let $X$ be a Calabi--Yau surface. 
-Minimal Kodaira--Spencer theory is a $\mb Z/2$-graded Poisson BV theory described by two fundamental sets of fields:
+On a Calabi--Yau surface $X$, minimal Kodaira--Spencer theory is the $\mb Z/2$-graded theory described by two fundamental sets of fields:
 \begin{itemize}
@@
 \end{itemize}
-These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
-There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.
+%These fields combine to define a $\mb Z/2$-graded sheaf $\mc E^{\rm hol}$ on $X$. 
+%There is a Lie algebra structure the parity reversed sheaf $\Pi \mc E^{\rm hol}$ using the Lie bracket of holomorphic vector fields together with the natural action of holomorphic vector fields on holomorphic functions.
 
-The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
+%The sheaf $\mc E^{\rm hol}$ admits the following locally free description:
+
+In the BV formalism, minimal Kodaira--Spencer theory on $X$ is a (degenerate) Poisson BV theory with space of fields given by
 \[
@@
 \]
-We refer to this locally free description by $\mc E$. 
-The Lie bracket on $\Pi \mc E^{\rm hol}$ described above extends to a Lie bracket on $\Pi \mc E$.
-Together with the differential this gives $\Pi \mc E$ the structure of a local dg Lie algebra.
+We will denote this sheaf of $\mb Z/2$-graded cochain complexes by $\mc E_{\rm KS}$.
 
-The bundle $\mc E$ is equipped with an odd Poisson tensor defined by 
+There is a local (dg) Lie algebra structure on the parity shifted object $\Pi \mc E_{\rm KS}$. 
+The Lie bracket is defined using the Schouten-Nijenhuis bracket $[-,-]_{\rm NS}$ on polyvector fields and is given by the formula
 \[
-\Pi = (\partial \otimes 1) \delta_{\rm Diag} .
+[u^k \alpha , u^\ell \beta] = u^{k+\ell} [\alpha, \beta]_{\rm NS} .
+\]
+where $k, \ell = 0,1$.
+Together with the differential this equips the parity shifted sheaf of cochain complexes $\Pi \mc E_{\rm KS}$ with the structure of a local (dg) Lie algebra.
+
+The fields of minimal Kodaira--Spencer theory $\mc E_{\rm KS}$ is equipped with an odd Poisson tensor defined by 
+\[
+\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
 \]
@@
 We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way. 
-There is a map of bundles $\Phi : \mc E_{\rm Pot} \to \mc E$ which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
+There is a map of sheaves of cochani complexes 
+\[
+\Phi : \mc E_{\rm Pot} \to \mc E_{\rm KS}
+\]
+which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component. 
 It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes. 
+The theory $\mc E_{\rm pot}$ is equipped with a non-degenerate BV pairing defined by the wedge-and-integrate pairing
+\[
+\omega_{\rm pot} (\alpha, \beta) = \int \alpha \wedge \beta  .
+\]
+It is immediate to verify that $\Phi$ intertwines the resulting bivector $\omega_{\rm pot}^{-1}$ and the Kodaira--Spencer Poisson bivector $\Pi_{\rm KS}$.
 
@@
 
+This equipped $\mc E_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory. 
+It's relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.
+
 %Using the isomorphism $\Omega : \PV^{2, \bu} (X) \cong \Omega^{0,\bu}(X)$ we thus obtain a Lie bracket on $\PV^{2,\bu}(X)$ defined by the equation
@@
 
-Finally, the theory $\mc E_{\rm pot}$ is a non-degenerate BV theory with BV pairing defined by the wedge-and-integrate pairing
+\begin{prop}
+The map $\Phi : \mc E_{\rm pot} \to \mc E_{\rm KS}$ determines a map of $\mb P_0$-factorization algebras on $X$:
 \[
-\alpha, \beta \mapsto \int \alpha \wedge \beta  .
-\]
-
-\begin{prop}
-The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
-\[
-\Phi^* : {\rm Obs}_{\mc E} \to {\rm Obs}_{\mc E_{\rm Pot}} .
+\Phi^* : {\rm Obs}_{\mc E_{\rm KS}} \to {\rm Obs}_{\mc E_{\rm Pot}} .
 \]
@@
 \[
-[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} [\mu^i, \mu^j]_{\rm Sch} .
+[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} [\mu^i, \mu^j]_{\rm NS} .
 \]
 
-Furthermore, the sheaf $\mc E$ is equipped with an odd Poisson tensor given by $\Pi = (\del\otimes 1)\delta_{\rm Diag}$.
-Together, this data equips $\mc E$ with the structure of a $\Z/2$-graded Poisson BV theory.
+The space of fields of minimal Kodaira--Spencer theory $\mc E_{\rm KS}$ is equipped with an odd Poisson tensor defined by 
+\[
+\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
+\]
+Together with the local Lie algebra structure, this data equips $\mc E$ with the structure of a $\Z/2$-graded Poisson BV theory.
 
@@
 & & & \mu^{0}\in\PV^{0,\bu} \\
-& & \sum u^k \mu^{1}\in\PV^{1,\bu} \ar[r, "\partial"] & \mu^{c}\in\PV^{0,\bu} \\
+& & \sum u^k \mu^{1}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
 u^{-1} \gamma^3 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
@@
 There is a local Lie algebra structure described as follows.
-\brian{It's mostly the Schouten bracket, but there is the additional ``weird" bracket
+\begin{itemize}
+\item 
+There is a self bracket between the $\mu$-fields defined by
 \[
-[\gamma^3, \gamma^{3'}] = [\partial \gamma^3 , \gamma^{3'}] \pm [\gamma^3, \partial \gamma^{3'}] .
+[u^k \mu^i, u^\ell \Tilde{\mu}^j] = u^{k+j} [\mu^i, \Tilde{\mu}^j]_{\rm NS} .
 \]
-}
+\item Next, there is a self-bracket between the $\gamma$-fields defined by 
+\[
+[\gamma^3, \Tilde{\gamma}^3] = [\partial \gamma^3 , \Tilde{\gamma}^{3}]_{\rm NS} \pm [\gamma^3, \partial \Tilde{\gamma}^{3}]_{\rm NS} \in {\rm PV}^{4,\bu} 
+\]
+\item Finally, there are mixed terms in the bracket defined by
+\[
+[u^{-k} \gamma^i , u^\ell \mu^j] = u^{-k + \ell} [\partial \gamma^i, \mu^j]_{\rm NS}
+\]
+\end{itemize}
 
-There is a map of sheaves of cochain complexes $\Phi: \mc E_{\rm pot}\to \mc E$ given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$.
+Together with the wedge and integrate pairing, $\mc E_{\rm pot}$ has the structure of a nondegenerate BV theory.
+
+Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes 
+\[
+\Phi: \mc E_{\rm pot}\to \mc E_{\rm KS} .
+\] 
+It is given by the identity map on $\PV^{1,\bu}$ and $\PV^{0,\bu}$ and the $\del$ operator on $\PV^{3,\bu}$ and $\PV^{4,\bu}$. 
 Explicitly, in formulas
 \[
+\arraycolsep=1.4pt\def\arraystretch{2.2}
 \begin{array}{ccccccccc}
-\Phi(t^k \mu^{i}) & = & u^k \mu^i & \in & u^k \PV^{i, \bu} & i = 0,1 \\
+\Phi(u^k \mu^{i}) & = & u^k \mu^i & \in & u^k \PV^{i, \bu} & i = 0,1 \\
 \Phi(u^{-1} \gamma^3) & = & 0 \\
@@
 
-Together with the wedge and integrate pairing, $\mc E_{\rm pot}$ has the structure of a nondegenerate BV theory.
+In fact, we have the following result, in analogy with the case of a Calabi-Yau surface.
 
-In fact, we have the following, analogous to the case of a Calabi-Yau surface:
 \begin{prop}
-The map $\Phi$ determines a map of $\mb P_0$-factorization algebras on $X$:
+The map $\Phi$ intertwines the local Lie algebra structures and Poisson BV structures on $\mc E_{\rm KS}$ and $\mc E_{\rm pot}$. 
+So, it induces a map of $\mb P_0$-factorization algebras:
 \[
@@
 The fields decompose as follows.
-For the ``base" direction, fields we labeled by $\mu$, we have
+For the ``base'' direction, fields we labeled by $\mu$, we have
 \[
-\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ \oplus & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
+\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{0,\bullet}(\C^\times)\otimes\PV^{1,\bullet}(\C^4) \\ & \PV^{1,\bullet}(\C^\times)\otimes\PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^\times\times\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R) [1] .
 \]
 
-For the ``fiber" direction, fields we labeled by $\gamma$, we have
+For the ``fiber'' direction, fields we labeled by $\gamma$, we have
 \[
-\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ \oplus & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
+\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^\times\times\C^4) \to \begin{aligned} & \Omega^{0,\bullet}(\C^\times)\otimes\Omega^{1,\bullet}(\C^4)\\ & \Omega^{1,\bullet}(\C^\times)\otimes\Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R).
 \]
 
-The ``zero modes" of the reduction along the circle $S^1 \subset \mb C^\times$ will be denoted by the same symbols.
-\brian{write down this sheaf on $\mb C^4 \times \mb R^2$.}
+We consider the dimensional reduction of the theory along the circle $S^1 \subset \mb C^\times$.
+The dimensional reduction has the affect of replacing $\PV^{i,\bu}(\mb C^\times)$ and $\Omega^{1,\bu}(\mb C^\times)$ by the de Rham along the radial direction in $\mb C^\times$, see Proposition 1.59 of \cite{ESW}.
+Denote the space of fields of the dimensional reduction by $\oint_{S^1} \mc E_{11d}$.
 
-Define the map of sheaves of cochain complexes 
+We will use the same symbols for the fields in the dimensionally reduced ten-dimensional theory: for the dimensionally reduced $\mu$-fields we have
 \[
-\Psi : \pi_* \mc E_{11d} \to \mc E_{\rm pot} \Hat{\otimes} \Omega^\bu(\mb R^2) 
+\mu = \begin{pmatrix} \mu_{01} \\ \mu_{10} \end{pmatrix} + u \mu_{11d}^0 \in \left (\begin{aligned} & \PV^{1,\bullet}(\C^4) \\ & \PV^{0,\bullet}(\C^4)\end{aligned} \to u \PV^{0,\bullet}(\C^4)\right ) \Hat{\otimes} \Omega^\bullet(\R^2) [1] .
 \]
-by
+and for the dimensionally reduced $\gamma$-fields we have
 \[
+\gamma = u^{-1} \gamma_{11d}^0 + \begin{pmatrix} \gamma_{01} \\ \gamma_{10} \end{pmatrix} \in \left (u^{-1} \Omega^{0,\bullet}(\C^4) \to \begin{aligned} & \Omega^{1,\bullet}(\C^4)\\ & \Omega^{0,\bullet}(\C^4)\end{aligned} \right ) \Hat{\otimes} \Omega^\bullet(\R^2).
+\]
+
+So far, we have only described how the fields of the $11$-dimensional theory behave upon dimensional reduction. 
+One can rename the fields of the dimensionally reduced theory to match precisely with the fields of the conjectural minimal twist of  Type IIA supergravity with potentials $\mc E_{\rm pot}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2)$.
+In fact, we have the following stronger result, which identifies the interacting BV theories of the dimensionally reduced theory with the conjectural twist of Type IIA supergravity with potentials.
+
+\begin{prop}
+There is an equivalence of interacting classical BV theories on $\mb C^2 \times \mb R^2$
+\[
+\Psi : \oint_{S^1} \mc E_{11d} \to \mc E_{\rm pot} (\CC^4) \Hat{\otimes} \Omega^\bu(\mb R^2) 
+\] 
+defined on the fields by
+\[
+\arraycolsep=1.4pt\def\arraystretch{2.2}
 \begin{array}{cccccccc}
 \Psi (\mu_{01}) & = & \mu_{01} & \in & \PV^{1,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\
-\Psi (\mu_{10}) & = & \mu_{10} \vee \Omega^{-1}_{\mb C^4} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) .
-\end{array}
+\Psi (\mu_{10}) & = & \Omega^{-1}_{\mb C^4} \vee \mu_{10} & \in & \PV^{4,\bu}(\mb C^4) \Hat{\otimes} \Omega^\bu(\mb R^2) \\ 
+\Psi(u \mu^0_{11d}) & = & u \mu^0_{11d} & \in & u \PV^{0,\bu} (\CC^4) \Hat{\otimes} \Omega^\bu (\RR^4) \\ 
+\Psi (u^{-1} \gamma_{11d}^0) & = & u^{-1} \Omega^{-1}_{\CC^4} \vee \gamma_{11d}^0 & \in & u^{-1} \PV^{4,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) \\ \Psi(\gamma_{01}) &  = & \Omega^{-1}_{\CC^4} \vee \gamma_{01} & \in & \PV^{3,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) \\
+\Psi (\gamma_{10}) & = & \gamma_{10} & \in & \PV^{0,\bu}(\CC^4) \Hat{\otimes} \Omega^\bu(\RR^2) .
+\end{array} .
 \]
+\end{prop}
 
@@
 
-\begin{prop}
-There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\otimes\mc E_{Pot}$ given by
-\begin{itemize}
-\item $[\gamma_{10}]\mapsto\mu^0\in\PV^{0,\bullet}\subset\mc E_{Pot}$.
-  \item $[\mu_{01}]\mapsto\mu^1\in\PV^{1,\bullet}(\C^4)\subset\mc E_{Pot}$.
-\item $[\mu^{0}]\mapsto\mu^{c}\in\PV^{0, \bullet}(\C^{4})\subset\mc E_{Pot}$.
-\item $[\gamma_{01}]\mapsto\mu^3 = \gamma_{01}\vee\Omega^{-1}_{\C^4}\in\PV^{3,\bullet}\subset\mc E_{Pot}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
-\item $[\mu_{10}]\mapsto\mu^4 =\mu_{10}\vee\Omega^{-1}_{\C^4}\in\PV^{4,\bullet}\subset\mc E_{Pot}$ .
-
-\end{itemize}
-preserving the relevant pairings.
-\end{prop}
+%
+%\begin{prop}
+%There is a homomorphism of $L_\infty$-algebras from the $\delbar_{\C^\times}$-cohomology of M theory on $\R\times\C^\times\times\C$ to $\Omega^\bullet(\R^2)\otimes\mc E_{Pot}$ given by
+%\begin{itemize}
+%\item $[\gamma_{10}]\mapsto\mu^0\in\PV^{0,\bullet}\subset\mc E_{Pot}$.
+%  \item $[\mu_{01}]\mapsto\mu^1\in\PV^{1,\bullet}(\C^4)\subset\mc E_{Pot}$.
+%\item $[\mu^{0}]\mapsto\mu^{c}\in\PV^{0, \bullet}(\C^{4})\subset\mc E_{Pot}$.
+%\item $[\gamma_{01}]\mapsto\mu^3 = \gamma_{01}\vee\Omega^{-1}_{\C^4}\in\PV^{3,\bullet}\subset\mc E_{Pot}$ where $\Omega_{\C^4}$ denotes the holomorphic volume form on $\C^4$.
+%\item $[\mu_{10}]\mapsto\mu^4 =\mu_{10}\vee\Omega^{-1}_{\C^4}\in\PV^{4,\bullet}\subset\mc E_{Pot}$ .
+%
+%
+%\end{itemize}
+%preserving the relevant pairings.
+%\end{prop}
 
@@
 
-\begin{rmk}
-Note that the field $\mu^{c}\in \mc E_{\mr Pot}$ is nonpropating.
+%\begin{rmk}
+%Note that the field $\mu^{c}\in \mc E_{\mr Pot}$ is nonpropating.
 It must pair against a field in $\PV^{3}$.
@@
 This suggests an enlargement of $\mc E_{\mr Pot}$ where we add an additional field in $\PV^{3}$ which will be the image of the ghost of $\gamma^{1}$ in M-theory under dimensional reduction.
-\end{rmk}
+%\end{rmk}
 
-\surya{ When we discussewd dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$.
+%\surya{ When we discussewd dimensional reduction on 9/22 over Zoom, I accidentally switched the roles of $\gamma_{10}$ and $\mu_{10}$.
 I realized this was wrong - the resulting map cannot be a Lie map.

### 2020-11-03 paper.tex
update

@@
-% Created 2020-10-14 Wed 13:57
+% Created 2020-10-14 Wed 14:51
 % Intended LaTeX compiler: pdflatex
-\documentclass[11pt]{article}
+\documentclass[11pt]{amsart}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{hyperref}
+
+\usepackage{macros-mtheory}
+
 \author{Surya and Brian}
 \date{\today}
-\title{Twisted \$M\$-theory and its perturbative quantization.}
+\title{Twisted \(M\)-theory and its perturbative quantization.}
 \hypersetup{
  pdfauthor={Surya and Brian},
- pdftitle={Twisted \$M\$-theory and its perturbative quantization.},
+ pdftitle={Twisted \(M\)-theory and its perturbative quantization.},
  pdfkeywords={},
@@
  pdflang={English}}
+
+\def\pv{{\rm PV}}
+
 \begin{document}
@@
 \section{Definition of twisted supergravity}
-\label{sec:orgea6ebfa}
+
+\label{sec:org24653eb}
 \subsection{The classical BV theory}
-\label{sec:org23fe8d4}
-\subsection{Moduli theoretic interpretation}
-\label{sec:orgd709323}
+\label{sec:org5c9d94b}
+In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
+The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold with volume form $\Omega$ and $L$ is a smooth oriented one-manifold.
+
+Before stating the definition, we recall some general objects in complex geometry that will play a central role.
+For now, let $X$ be any complex manifold and let $V$ be a holomorphic vector bundle on $X$.
+If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of Dolbeault forms of type $j$ on with values in $V$.
+The $\dbar$ operator for $V$ is of the form $\dbar : \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$.
+This operator defines the Dolbeault complex of $V$
+\[
+  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right)
+\]
+which is a free resolution for the sheaf of holomorphic sections of $V$.
+
+Denote by $TX$ the holomorphic tangent bundle of $X$.
+Then, the Lie bracket of holomorphic vector fields extends to a Lie bracket on the Dolbeault $\Omega^{0,\bu}(X, TX)$ thus endowing it with the structure of a dg Lie algebra.
+
+By definition, the Dolbeault complex for the trivial bundle $\Omega^{0,\bu}(X)$ is a dg module for the dg Lie algebra $\Omega^{0,\bu}(X, TX)$.
+We can thus consider the following semi-direct product dg Lie algebra
+\beqn\label{eqn:div1}
+  \Omega^{0,\bu}(X, TX) \oplus \Omega^{0,\bu}(X) [-1] .
+\eeqn
+Notice that $\Omega^{0,\bu}(X)$ has been shifted to a seemingly unnatural cohomological degree, with $(0,j)$-forms sitting in degree $j+1$.
+
+Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
+The holomorphic divergence operator with respect to $\Omega$ is an operator of the form
+\[
+  \partial_\Omega : \Omega^{0,\bu}(X, TX) \to \Omega^{0,\bu}(X)
+\]
+defined by the formula
+\[
+  \partial_\Omega (\mu) \wedge \Omega = L_\mu (\Omega)
+\]
+where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
+
+Using the holomorphic divergence operator $\partial_\Omega$ we can consider the following deformation of the dg Lie algebra (\ref{eqn:div1}).
+The Lie bracket remains the same but the differential is deformed from $\dbar$ to $\dbar + \partial_\Omega$.
+Here, $\partial_{\Omega}$ denotes the holomorphic divergence operator thought of as a degree one operator from $\Omega^{0,\bu}(X, TX)$ to $\Omega^{0,\bu}(X)$.
+We will denote the resulting dg Lie algebra by $\cS(X)$.
+
+It is easy to see that $\cS(X)$ provides a free resolution of the sheaf of holomorphic divergence free vector fields on $X$.
+
+%We will mostly consider the sub dg Lie algebra of $(\ref{eqn:pvlie1})$ consisting of the polyvector fields of type $i\leq 1$:
+%\beqn\label{eqn:pvlie2}
+%  \pv^{\leq 1, \bu} (X)[1] =
+%\eeqn
+
+%We note that this deformation is only in the $\ZZ/2$-graded sense.
+
+%For $X$ a Calabi--Yau manifold let $\cS^{\bu,\bu}(X)$ be the $\ZZ/2$-graded dg Lie algebra whose underlying $\ZZ/2$-graded vector space is $\pv^{\bu,\bu}(X)[1]$ (with gradings defined modulo $2$), whose differential is
+%\beqn\label{differential}
+%\dbar + \partial_{\Omega}
+%\eeqn
+%and the bracket is the Nijenhuis--Schouten bracket $\{\cdot,\cdot\}_{\rm NS}$.
+%We notice that in the original $\ZZ$-grading on $\pv^{\bu,\bu}(X)$ the operator $\partial_{\Omega}$ has cohomological degree $-1$, which is why the above deformation is only defined in a $\ZZ/2$-graded sense.
+
+%The differential (\ref{differential}) clearly preserves the subspace $\pv^{\leq 1, \bu}(X)$.
+%We let $\cS^{\leq 1,\bu}(X) \subset \cS^{\bu,\bu}(X)$ denote the $\ZZ/2$-graded sub dg Lie algebra consisting of polyvector fields of type $i\leq 1$ equipped with the differential $\dbar + \partial_{\Omega}$.
+
+%\begin{rmk}
+%  There is a way to regrade $\cS^{\leq 1,\bu}(X)$ while keeping the differential the same in such a way that it has the structure of a $\ZZ$-graded dg Lie algebra.
+%  Explicitly, this is
+%  \[
+%    \begin{array}{ccccc}
+%      \ul{0} & & \ul{1} \\
+%      \pv^{1,\bu}(X) &\xto{\partial_{\Omega}} & \pv^{0,\bu}(X) .
+%    \end{array}
+%  \]
+%  This is a $\ZZ$-graded dg Lie algebra which agrees with $\cS^{\leq 1, \bu}(X)$ as a $\ZZ/2$- graded dg Lie algebra.
+%  This dg Lie algebra is a free resolution for the Lie algebra of holomorphic divergence-free vector fields on $X$.
+%  That is, holomorphic vector fields which preserve the holomorphic volume form $\Omega$.
+% \end{rmk}
+
+The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
+By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
+\beqn\label{localLie}
+  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
+\eeqn
+where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
+In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.
+
+Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory''.
+Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
+The fields of the associated BV theory are pairs
+\[
+(A, B) \in \cL[1] \oplus \cL^{!}[-1]\]
+and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
+Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
+Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cL A + \frac12 [A,A] = 0$.
+For the $B$-field the equations of motion read $\d_\cL B + [A, B] = 0$.
+
+For the case at hand, we consider the BF theory associated to the local dg Lie algebra (\ref{localLie}) defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(L)$.
+
+The fields decompose as follows
+\[
+(\mu, \gamma) = (\mu^{1,\bu} + \mu^{0,\bu}, \gamma^{0,\bu}+\gamma^{1,\bu})
+\]
+where
+\[
+  \begin{array}{ccl}
+    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
+  \end{array}
+\]
+Notice that what we called the ``$A$''-field in the general definition of BF theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
+By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
+
+While the definition of $\mu$ is independent of the dimension, the field $\gamma$ depends on $d$.
+This is in order for the BV antibracket to be of the appropriate degree.
+Additionally, we have utilized the holomorphic volume form in the definition of the field $\gamma$.
+Indeed, in this presentation the BV antipairing on fields reads
+\[
+  \int_{X \times L} (\mu \vdash \gamma) \wedge \Omega = \int_{X \times L} (\mu^{1,\bu} \vdash \gamma^{1,\bu} + \mu^{0,\bu} \vdash \gamma^{0,\bu}) \wedge \Omega .
+\]
+
+\subsubsection{}
+We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $L$ is a real one-dimensional manifold.
+In this case $d = 6$ so the field $\gamma$ takes the form
+\[
+  \gamma \in \left(\Omega^{0,\bu}(X)[6] \oplus \Omega^{1,\bu}(X)[5] \right) \otimes \Omega^\bu(L).
+\]
+
+What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$, but a certain deformation of it.
+We consider a theory whose fields are that of the BF theory but whose action functional is of the form $S_{\rm BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
+It is defined by the following formula
+\[
+J(\gamma) = \frac13 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
+\]
+
+First off, we notice an inconsistency in the cohomological degrees of the functionals $S_{\rm BF}$ and $J$.
+Being a classical action functional $S_{\rm BF}$ is, of course, ghost degree zero.
+However, we observe that $J$ is of ghost degree $??$.
+In order to make sense of the deformed theory, therefore, we must consider the space of fields as a $\ZZ/2$-graded object rather than a $\ZZ$-graded one.
+
+So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ/2$-graded space of fields takes the form
+\[
+  \begin{array}{ccl}
+    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
+  \end{array}
+\]
+Here, we have used the following convention for $\ZZ/2$-graded complexes.
+If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.
+
+With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
+In order for this to be true, we must know that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation $\{S_{\rm BF} + J , S_{\rm BF} + J\} = 0$.
+Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
+Additionally, since $\gamma$ does not pair with itself under the antibracket, we also see that $\{J,J\}=0$.
+What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.
+
+\begin{lem}
+The functional $J = \frac13 \int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
+In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
+\end{lem}
+
+\begin{proof}
+It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
+It remains to see that
+\end{proof}
+
+\begin{dfn}
+Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
+Define the $\ZZ/2$-graded BV theory $\cT$ on
+      \[
+        X \times L
+      \]
+to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS^{\leq 1,\bu}(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional
+
+\end{dfn}
+
+The BV action functional for the theory splits as a sum
+\[
+  S_{\rm BF} + J
+\]
+where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
+\[
+  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
+\]
+We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.
+
+For this deformation to be a well-defined BV theory, we must know that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation $\{S_{\rm BF} + J , S_{\rm BF} + J\} = 0$.
+Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
+Additionally, simply by type reasons do we see that $\{J,J\}=0$.
+What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.
+
+\begin{lem}
+  The functional $J = \frac13 \int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
+  In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
+\end{lem}
+\begin{proof}
+  It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
+  It remains to see that :
+\end{proof}
+
+There is a similar deformation of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$ when $X$ is any {\em odd dimensional} Calabi--Yau manifold and $L$ is a smooth one-dimensional manifold.
+
+\subsection{Equations of motion}
+\label{sec:org2973a4d}
+In this section we analyze the equations of motion and provide a moduli theoretic interpretation of the solution space.
+
+\subsection{Evidence for twisted supergravity}
+
+In parts of the remainder of the paper we will provide evidence, and consistency checks, that the eleven-dimensional theory that we have just defined is a candidate for the minimal twist of supergravity.
+In this section, we discuss a more direct relationship by exhibiting the fields of the theory we have outlined as components of the supergravity multiplet that are expected to survive in the twist.
+
 \section{Quantization of holomorphic-topological theories}
-\label{sec:orgec1821a}
+\label{sec:org297a559}
 \subsection{Effective renormalization}
-\label{sec:org2b54a17}
-\subsection{The \$11\$-dimensional theory}
-\label{sec:org553e6b1}
+\label{sec:orga5cd4ed}
+\subsection{The \(11\)-dimensional theory}
+\label{sec:org8b189fc}
 \subsection{The moduli space of quantizations}
-\label{sec:orgefb666b}
+\label{sec:orgf278b4e}
 \section{Relationship to the Type IIA string}
-\label{sec:org22f4829}
+\label{sec:org355a726}
+
+Let $TX$ denote the holomorphic tangent bundle and define
+\[
+\pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX) .\]
+This is the space of $i$-pvvectors of Dolbeault type $j$.
+Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields of type $i$.
+
+There is a bracket on the space of holomorphic polyvector fields called the Nijenhuis--Schouten bracket.
+This bracket is defined using holomorphic pvdifferential operators, so extends to a bracket on the Dolbeault complex to define a bracket of the form
+\[
+  \{\cdot, \cdot\}_{\rm NS} \colon \pv^{i,j}(X) \times \pv^{k,\ell}(X) \to \PV^{i+k-1, j+\ell}(X) .
+\]
+This bracket endows the total complex
+\beqn\label{eqn:pvlie1}
+\pv^{\bu,\bu}(X)[1] = \left(\oplus_{i,j} \pv^{i,j}(X)[-i-j+1] , \dbar \right)
+\eeqn
+with the structure of a dg Lie algebra.
+Here, we note that in this dg Lie algebra the space $\pv^{i,j}(X)$ lies in cohomological degree $i+j-1$.
+
+So far, $X$ has been an arbitrary complex manifold.
+When $X$ is Calabi--Yau of complex dimension $n$, the holomorphic volume form $\Omega$ defines an isomorphism
+\[
+  \vdash \Omega : \pv^{i,j}(X) \cong \Omega^{n-i, j}(X).
+\]
+In turn, the holomorphic de Rham operator $\partial : \Omega^{p, j}(X) \to \Omega^{p+1,j}$ defines a holomorphic differential operator
+\[
+  \partial_{\Omega} : \pv^{i,j}(X) \to \pv^{i-1,j}(X) .
+\]
+This is the holomorphic analog of the divergence operator with respect to $\Omega$.
+
 \subsection{Kodaira--Spencer theory with potentials}
-\label{sec:org9f736c1}
+\label{sec:org5e18f8e}
 \subsubsection{Warm-up: four-dimensional Kodaira--Spencer theory}
-\label{sec:org0b90e8b}
+\label{sec:org91dc4ca}
 \subsubsection{Eight-dimensional Kodaira--Spencer theory}
-\label{sec:org3b2a900}
+\label{sec:orgeb2dd4d}
 \subsection{The Type IIA topological string}
-\label{sec:org02b0f82}
+\label{sec:org1f7e793}
 \subsection{Reduction of twisted supergravity}
-\label{sec:org59003d2}
+\label{sec:orgcf7b6a4}
 \subsubsection{Calabi--Yau compactifications}
-\label{sec:org55d712d}
+\label{sec:org16a2c98}
 \subsection{Twisted supergravity on a three-fold}
-\label{sec:org7c4a220}
+\label{sec:org774abb4}
 \section{The non-minimal G2 twist}
-\label{sec:orgc520304}
+\label{sec:org590ab85}
+Does math mode \(work here = e^x\)?
 \end{document}

### 2020-11-04 paper.tex
merge
changes

@@
 where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
+The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(L)$ by the formula
+\[
+  [\mu \otimes \alpha, \nu \otimes \beta] = [\mu, \nu] \otimes (\alpha \wedge \beta) .
+\]
+
 We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
@@
 \[
-(A, B) \in \cL[1] \oplus \cL^{!}[-1]\]
+  (A, B) \in \cL[1] \oplus \cL^{!}[-2]
+\]
 and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
@@
       \]
-to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS^{\leq 1,\bu}(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional
+to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional
 
@@
 
-There is a similar deformation of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$ when $X$ is any {\em odd dimensional} Calabi--Yau manifold and $L$ is a smooth one-dimensional manifold.
+\subsubsection{}
+
+We briefly discuss a generalization of this deformation of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$ when $X$ is any {\em odd dimensional} Calabi--Yau manifold of dimension at least three and $L$ is a smooth one-dimensional manifold.
+
+Suppose $X$ is a Calabi--Yau manifold of complex dimension $2m+1$ where $m > 0$.
+Then, the fields of BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^{\bu}(L)$ are of the form
+\[
+  \begin{array}{ccl}
+    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[depends on m] .
+  \end{array}
+\]
+
+The deformation we consider is of the form
+\[
+  J_m (\gamma) = \int_{X \times L} \gamma \underbrace{\partial \gamma \cdots \partial \gamma}_{m} .
+\]
+That is, this deformation is $(m+1)$-linear and contains $m$ holomorphic derivatives.
+As in the $m=2$ ($X$ is a five-fold) case that we discussed above, we see that $J_m$ is closed for the differential $\{S_{\rm BF},\cdot\}$ defining the BF theory.
+
+\begin{lem}
+  The functional $J_m$ is closed for the differential $\{S_{\rm BF}, \cdot \}$.
+\end{lem}
+
+A simple count reveals that the ghost degree of the functional $J_m$ is $depends on m$.
+In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ defines a $\ZZ/2$-graded classical BV theory.
+
+When $m=1$, the action $S_{\rm BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
+Another feature of the case $m=1$ is that the deformed theory is actually a {\em topological} field theory.
+It will be useful to spell out this theory in more detail.
+
+In this case $X$ is a Calabi--Yau three-fold.
+Using the isomorphism
+\[
+ (-) \vee \Omega : \PV^{i,\bu} (X) \cong \Omega^{3-i, \bu}(X)
+\]
+we can identify the $\mu$-fields of the theory in terms of differential forms
+\[
+  \alpha^2 + \alpha^3 \in \left(\Omega^{2,\bu}(X)[1] \oplus \Omega^{3,\bu}(X)\right) \; \Hat{\otimes} \; \Omega^\bu(L)
+\]
+by the formula $\alpha^{3-i} = \mu^{i} \vee \Omega$, for $i=0,1$.
+We will also write $\alpha^{j} = \gamma^{j}$ for $j=0,1$, so the remaining fields are
+\[
+  \alpha^0 + \alpha^1 \in \left(\Omega^{0,\bu}(X)[3] \oplus \Omega^{1,\bu}(X)[2] \right) \; \Hat{\otimes} \; \Omega^\bu(L).
+\]
+
+Let us write the theory as $S_{\rm BF} + c J_1$ where $c$ is a complex number.
+We denote by $\cT_c [X \times L]$ the resulting BV theory which depends on this coupling constant $c$.
+Also, let $\cM_c[X]$ denote the moduli space of solutions on the Calabi--Yau three-fold $X$.
+
+Using this decomposition of the fields we can write the underlying {\em free} theory by the following action functional
+\[
+  \int_{X\times L} \left(\alpha^0 (\dbar + \d_{\rm dR}) \alpha^3 + \alpha^1 (\dbar + \d_{\rm dR}) \alpha^2 \right) + \int_{X \times L} \alpha^0 \partial \alpha^2 + c \int_{X \times L} \alpha^1 \partial \alpha^1 .
+\]
+Here, as above, $\partial$ denotes the holomorphic de Rham operator on $X$.
+
+Now, for $c \ne 0$, we observe that this free action is equivalent to abelian seven-dimensional Chern--Simons theory on $X \times L$.
+Indeed, by the above formula the linear BRST complex of the theory is given by the following cochain complex
+\[
+  \bigg(\Omega^{\bu, \bu} (X) \; \Hat{\otimes} \; \Omega^{\bu}(L) [3] \; , \; \dbar + \Hat{\partial} + \d_{\rm dR} + c \partial_{\Omega^{1} \to \Omega^{2}} \bigg)
+\]
+Here, $\Hat{\partial}$ denotes the components of the holomorphic de Rham differential mapping $\Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ and $\Omega^{2,\bu}(X) \to \Omega^{3,\bu}(X)$, and $\partial_{\Omega^1 \to \Omega^2}$ denotes the component $\Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.
+When $c \ne 0$ we see that this cochain complex is isomorphic to the full (shifted) de Rham complex $\Omega^\bu(X \times L)[3]$.
+
+In the BV formalism, seven-dimensional Chern--Simons theory is described by the fields $\alpha^i \in \Omega^{i,\bu}(X) \Hat{\otimes} \Omega^\bu(L)[3-i]$, $i=0, \ldots 3$ which we can now decompose as a de Rham type field $C^\bu \in \Omega^\bu(X \times L)[3]$ so that $C^j$ has total de Rham degree $j$.
+The BV antipairing is the wedge and integrate pairing $\int C \wedge C'$ and the action reads
+\[
+  \frac{1}{2} \int_{X \times L} C \d C,
+\]
+where $\d$ is the full de Rham differential on $X \times L$.
+Sometimes, this is referred to as ``three-form Chern--Simons theory'' since its fundamental field is a three-form $C^3$ and the equations of motion read $\d C^3 = 0$.
+
+We have seen that when $c \ne 0$, the free theory underlying $\cT_c[X \times L]$ is equivalent to seven-dimensional Chern--Simons theory.
+In particular, the moduli space of solutions $\cM_c[X]$, for $c \ne 0$, has as its free limit the moduli space of circle $3$-bundles on $X$ with connection.
+
+We can consider a different limit of $\cM_c[X]$, namely the one where $c \to 0$.
+This is precisely the cotangent bundle to the moduli space of Calabi--Yau structures $\cM_{CY}[X]$ on the three-fold $X$:
+\[
+  \cM_0[X] = T^* \left(\cM_{\rm CY} [X]\right) .
+\]
+
+In summary, we have seen that $\cM_c[X]$ provides a roof of deformations between the moduli space of Calabi--Yau structures on $X$ and the moduli of circle $3$-bundles:
+\[
+  \begin{tikzcd}
+    & \cM_c[X] \ar[dr, "c \ne 0"', "{\rm free\;limit}"] \ar[dl, "c \to 0"'] & \\ T^* \left(\cM_{\rm CY} [X] \right) & & \left\{ \begin{array}{ccc} \mbox{circle\;3-bundles} \\ {\rm on} \; X \end{array} \right\} .
+  \end{tikzcd}
+\]
 
@@
 
+\brian{state conjecture about twist.}
+
 In parts of the remainder of the paper we will provide evidence, and consistency checks, that the eleven-dimensional theory that we have just defined is a candidate for the minimal twist of supergravity.
 In this section, we discuss a more direct relationship by exhibiting the fields of the theory we have outlined as components of the supergravity multiplet that are expected to survive in the twist.
+
+We recall that our eleven-dimensional theory is only $\ZZ/2$-graded.
+This is consistent with the minimal twist of supergravity.
+Indeed, since the $R$-symmetry group is trivial there is no way to regrade the twisted theory in such a way that the BRST differential and twisting supercharge are of homogenous $\ZZ$-degree.
+
+The conjecture implies that the even fields of our eleven dimensional theory should correspond to certain components of the fundamental fields supergravity that survive the minimal twist.
+The even components of the field $\mu$ and $\gamma$ are of the form
+\[
+  \mu^{0, i ; j} \; , \; \mu^{1, i ; j} \; , \; \gamma^{0, i ; j} \; , \; \gamma^{1, i ; j}
+\]
+where $i+j$ is an even integer and $i = 0,\ldots 5$ and $j=0,1$.
+Here, as in the previous section, we have used the following index notation:
+\[
+  \begin{array}{ccccc}
+    \mu^{k, i ; j} & \in & \pv^{k,i} (\CC^5) \; \Hat{\otimes} \; \Omega^j(\RR) \\
+    \gamma^{k, i ; j} & \in & \Omega^{k,i}(\CC^5) \; \Hat{\otimes} \; \Omega^j(\RR).
+  \end{array}
+\]
+
+Let us now turn to the field content of eleven-dimensional supergravity.
+In Euclidean signature, in the flat background, the fundamental fields of eleven-dimensional supergravity are
+\[
+  \begin{array}{ccll}
+    e & \in & \Omega^1(\RR^{11}) \otimes \CC^{11} & \mbox{vielbien} \\
+    \omega & \in & \Omega^1(\RR^{11}) \otimes \fs \fo(11) & \mbox{spin connection} \\
+    C & \in & \Omega^3(\RR^{11}) & \mbox{supergravity $3$-form} \\
+    \psi & \in & \Omega^1(\RR^{11}) \otimes S & \mbox{gravitino} .
+  \end{array}
+\]
+We note that the fields above have been complexified from the usual presentation of supergravity in terms of real fields.
+Here, $S$ denotes the $128$ dimensional complex spin representation of $\fs \fo(11)$.
 

### 2020-11-24 paper.tex
macros
eom

@@
 
-The fields decompose as follows
+The fields decompose as
 \[
-(\mu, \gamma) = (\mu^{1,\bu} + \mu^{0,\bu}, \gamma^{0,\bu}+\gamma^{1,\bu})
+(\mu, \gamma) = (\mu^1 + \mu^0, \gamma^0 + \gamma^1)
 \]
@@
   \begin{array}{ccl}
-    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
+    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
   \end{array}
@@
 \[
-  \int_{X \times L} (\mu \vdash \gamma) \wedge \Omega = \int_{X \times L} (\mu^{1,\bu} \vdash \gamma^{1,\bu} + \mu^{0,\bu} \vdash \gamma^{0,\bu}) \wedge \Omega .
+  \int_{X \times L} (\mu \vdash \gamma) \wedge \Omega = \int_{X \times L} (\mu^1 \vdash \gamma^1 + \mu^0 \vdash \gamma^0) \wedge \Omega .
 \]
@@
   \begin{array}{ccl}
-    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
+    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
   \end{array}
@@
 With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
-In order for this to be true, we must know that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation $\{S_{\rm BF} + J , S_{\rm BF} + J\} = 0$.
+In order for this to be true, we must see that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation
+\[
+  \{S_{\rm BF} + J , S_{\rm BF} + J\} = 0 .
+\]
 Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
@@
 
+\begin{rmk}
+  We have actually shown something slightly stronger here.
+  Namely, for any constant $c$ the functional $S_{\rm BF} + c J$ satisfies the classical master equation.
+  This dependence on a coupling constant will be important later on in this paper.
+\end{rmk}
+
 \begin{dfn}
@@
 \]
-to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional
-
+to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac13 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
 \end{dfn}
 
-The BV action functional for the theory splits as a sum
-\[
-  S_{\rm BF} + J
-\]
-where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
-\[
-  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
-\]
-We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.
+%Unpacking this a bit, we see that the BV action functional for the theory $\cT$ splits as a sum
+%\begin{equation}\label{11daction}
+%  S_{\rm BF} + J
+%\end{equation}
+%where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
+%\[
+%  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
+%\]
+%We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.
 
-For this deformation to be a well-defined BV theory, we must know that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation $\{S_{\rm BF} + J , S_{\rm BF} + J\} = 0$.
-Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
-Additionally, simply by type reasons do we see that $\{J,J\}=0$.
-What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.
-
-\begin{lem}
-  The functional $J = \frac13 \int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
-  In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
-\end{lem}
-\begin{proof}
-  It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
-  It remains to see that :
-\end{proof}
-
-\subsubsection{}
+\subsubsection{A generalization of the theory}
 
@@
   \begin{array}{ccl}
-    \mu = \mu^{1,\bu}+\mu^{0,\bu} & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^{0,\bu} + \gamma^{1,\bu} & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[depends on m] .
+    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[depends on m] .
   \end{array}
@@
 \[
-  J_m (\gamma) = \int_{X \times L} \gamma \underbrace{\partial \gamma \cdots \partial \gamma}_{m} .
+  J_m (\gamma) = \frac{1}{m+1} \int_{X \times L} \gamma \underbrace{\partial \gamma \cdots \partial \gamma}_{m} .
 \]
@@
 
-A simple count reveals that the ghost degree of the functional $J_m$ is $depends on m$.
+A simple count reveals that the ghost degree of the functional $J_m$ is \brian{figure out}.
 In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ defines a $\ZZ/2$-graded classical BV theory.
+
+\subsubsection{The case of a CY three-fold}
 
@@
 Another feature of the case $m=1$ is that the deformed theory is actually a {\em topological} field theory.
-It will be useful to spell out this theory in more detail.
+It is instructive to spell out this case in more detail.
 
@@
 by the formula $\alpha^{3-i} = \mu^{i} \vee \Omega$, for $i=0,1$.
-We will also write $\alpha^{j} = \gamma^{j}$ for $j=0,1$, so the remaining fields are
+We will also write $\alpha^{j} = \gamma^{j}$ for $j=0,1$, so the remaining fields read
 \[
-  \alpha^0 + \alpha^1 \in \left(\Omega^{0,\bu}(X)[3] \oplus \Omega^{1,\bu}(X)[2] \right) \; \Hat{\otimes} \; \Omega^\bu(L).
+  \alpha^0 + \alpha^1 \in \left(\Omega^{0,\bu}(X)[3] \oplus \Omega^{1,\bu}(X)[2] \right) \; \Hat{\otimes} \; \Omega^\bu (L).
 \]
-
-Let us write the theory as $S_{\rm BF} + c J_1$ where $c$ is a complex number.
-We denote by $\cT_c [X \times L]$ the resulting BV theory which depends on this coupling constant $c$.
-Also, let $\cM_c[X]$ denote the moduli space of solutions on the Calabi--Yau three-fold $X$.
-
-Using this decomposition of the fields we can write the underlying {\em free} theory by the following action functional
+Let us write the theory as $S_{\rm BF} + c J_1$ where $c$ is a constant.
+We denote by $\cT_c [X \times L]$ the resulting BV theory which depends on this coupling constant.
+Also, let $\cM_c[X]$ denote the moduli space of solutions on the Calabi--Yau three-fold.
+Using this decomposition of the fields we can write the underlying {\em free} theory by the following action
 \[
-  \int_{X\times L} \left(\alpha^0 (\dbar + \d_{\rm dR}) \alpha^3 + \alpha^1 (\dbar + \d_{\rm dR}) \alpha^2 \right) + \int_{X \times L} \alpha^0 \partial \alpha^2 + c \int_{X \times L} \alpha^1 \partial \alpha^1 .
+  \int_{X\times L} \left(\alpha^0 (\dbar + \d_{\rm dR}) \alpha^3 + \alpha^1 (\dbar + \d_{\rm dR}) \alpha^2 \right) + \int_{X \times L} \alpha^0 \partial \alpha^2 + \frac{c}{2} \int_{X \times L} \alpha^1 \partial \alpha^1
 \]
@@
 Now, for $c \ne 0$, we observe that this free action is equivalent to abelian seven-dimensional Chern--Simons theory on $X \times L$.
-Indeed, by the above formula the linear BRST complex of the theory is given by the following cochain complex
+Indeed, by the above formula the linearized BV complex of the theory is given by the following cochain complex
 \[
@@
 \]
-Here, $\Hat{\partial}$ denotes the components of the holomorphic de Rham differential mapping $\Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ and $\Omega^{2,\bu}(X) \to \Omega^{3,\bu}(X)$, and $\partial_{\Omega^1 \to \Omega^2}$ denotes the component $\Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.
+Here, $\Hat{\partial}$ denotes the components of the holomorphic de Rham differential $\Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ and $\Omega^{2,\bu}(X) \to \Omega^{3,\bu}(X)$.
+Also, $\partial_{\Omega^1 \to \Omega^2}$ denotes the component $\Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.
 When $c \ne 0$ we see that this cochain complex is isomorphic to the full (shifted) de Rham complex $\Omega^\bu(X \times L)[3]$.
@@
 \label{sec:org2973a4d}
-In this section we analyze the equations of motion and provide a moduli theoretic interpretation of the solution space.
+We return to the case of the theory $\cT$ on $X\times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a one-manifold.
+In this section we analyze the equations of motion for the eleven-dimensional theory and provide partial moduli theoretic interpretation of the solution space.
+
+The action functional of the theory (\ref{11daction}) on $X \times L$ is of the form
+\[
+  \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega + \frac{c}{3} \int \gamma \partial \gamma \partial \gamma .
+\]
+Notice that just as in the last section we have included a coupling constant $c$ into the term which deforms the classical BF type theory.
+
+From this, we read off the equations of motion as
+\begin{equation}\label{eqn:eom}
+  \begin{array}{rccc}
+    \left(\dbar + \partial_\Omega + \d_{\rm dR} \right) \mu + \frac12 \{\mu, \mu\}_{\rm NS} + c \partial \gamma \partial \gamma \vdash \Omega & = & 0 \\
+    \left(\dbar + \partial_\Omega + \d_{\rm dR} \right) \gamma + L_\mu (\gamma) & = & 0 .
+  \end{array}
+\end{equation}
+Here, $L_\mu(\gamma)$ denotes the Lie derivative of $\gamma$ with respect to the vector field $\mu$.
+
+On $L = \RR_t$ we proceed to describe the classical phase space of the model which is the space of solutions to the above equations at $t = 0$.
+Upon taking into account the gauge transformations, we will denote the resulting moduli space by $\cM_c[X]$.
+When $X$ is compact, the BV pairing in the bulk eleven-dimensional theory induces a symplectic structure on this moduli space.
+
+Notice that just as in the case of the phase space of the $7$-dimensional theory on a Calabi--Yau three-fold, at $c=0$ this moduli space is precisely the cotangent bundle to the moduli space of Calabi--Yau five-folds $\cM_0 [X] = T^*(\cM_{\rm CY}(X))$.
+
+In the general case, we begin to decompose the two equations of motion above according to their form degree.
+When $c = 0$, the field $\mu^{1,1}$ is a Beltrami differential which provides the parameter describing the deformation of complex structure on the Calabi--Yau $X$.
+For $c \ne 0$, it makes an appearance in the following equation
+\begin{equation}\label{eqn:mu11}
+  \dbar \mu^{1,1} + \frac12 \{\mu^{1,1}, \mu^{1,1}\}_{\rm NS} + c \partial \gamma^{1,0} \partial \gamma^{1,2} \vdash \Omega = 0 .
+\end{equation}
+(Notice that the term $\partial \gamma^{1,1} \partial \gamma^{1,1} = 0$ by form type reasons.)
+
+The field $\gamma^{1,0}$ also appears in the second class of equations of motion in (\ref{eqn:eom}) as
+\[
+  \dbar \gamma^{1,0} + \partial \gamma^{0,1} + L_{\mu^{1,1}} \gamma^{1,0} + L_{\mu^{1,0}} \gamma^{0,1} = 0 .
+\]
+We choose a gauge so that $\gamma^{0,1} = 0$, \brian{Why is this allowed.} so that this equation reads
+\begin{equation}\label{eqn:gamma10}
+  \dbar \gamma^{1,0} + L_{\mu^{1,1}} \gamma^{1,0} = 0 .
+\end{equation}
+
+Denote by $\beta^{2,0} = \partial \gamma^{1,0}$ the $(2,0)$-form obtained from $\gamma^{1,0}$ and consider the sequence of maps of holomorphic vector bundles
+\[
+  \begin{tikzcd}
+    \wedge^{2,0} T^{*1,0} \ar[r, "\beta^{2,0} \wedge"] & \wedge^4 T_X^{*1,0} \ar[r, "\Omega", "\cong"'] & T^{1,0}_X .
+  \end{tikzcd}
+\]
+The image of this map is a holomorphic distribution $F \subset T_X^{1,0}$.
+It follows from the fact that $\partial \beta = 0$ that $F$ defines a holomorphic foliation on $X$.
+
+Using the foliation $F$, the holomorphic tangent bundle splits as $T^{1,0} = F \oplus Q$ where $Q = T^{1,0}_X / F$ is the quotient bundle.
+Using this splitting, we can split the components of $\mu^{1,1}$ according to
+\[
+  T^{1,0}_X \otimes T^{*0,1}_X = (F \otimes\Bar{F}^*) \oplus (F \otimes \Bar{Q}^*) \oplus (Q \otimes \Bar{F}^*) \oplus (Q \otimes \Bar{Q}^*) .
+\]
+
+There is a component $\mu_{Q\Bar{Q}}^{1,1}$ of $\mu^{1,1}$ which is a Beltrami differential for the quotient bundle $Q$.
+At the level of the quotient bundle Equation (\ref{eqn:mu11}) becomes
+\[
+  \dbar \mu^{1,1}_{Q \Bar{Q}} + \frac12 \{\mu^{1,1}_{Q \Bar{Q}} , \mu^{1,1}_{Q \Bar{Q}}\}_{\rm NS} = 0 .
+\]
+In other words $\mu^{1,1}_F$ is a Beltrami differential for this quotient bundle and hence determines a deformation of complex structure of $T^{1,0}_X / F$.
 
@@
     C & \in & \Omega^3(\RR^{11}) & \mbox{supergravity $3$-form} \\
-    \psi & \in & \Omega^1(\RR^{11}) \otimes S & \mbox{gravitino} .
+    \psi & \in & \Pi \Omega^1(\RR^{11}) \otimes S & \mbox{gravitino} .
   \end{array}

### 2020-11-24 paper.tex
added bit about conjectures on twists of supergravity and KS with potentials on surface

--- 2020-11-04 paper.tex
@@
 
-A simple count reveals that the ghost degree of the functional $J_m$ is $depends on m$.
+A simple count reveals that the ghost degree of the functional $J_m$ is \brian{figure out}.
 In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ defines a $\ZZ/2$-graded classical BV theory.
@@
 \label{sec:org355a726}
+In the remainder of the paper, we wish to establish various consistency checks corroborating the claim that the 11d theory of interest describes a twist of 11d supergravity.
+In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of type IIA supergravity due to \cite{}.
 
-Let $TX$ denote the holomorphic tangent bundle and define
+Before recalling this conjecture, we first fix some notation. For a complex manifold $X$, let $TX$ denote the holomorphic tangent bundle and define
 \[
@@
 
-So far, $X$ has been an arbitrary complex manifold.
 When $X$ is Calabi--Yau of complex dimension $n$, the holomorphic volume form $\Omega$ defines an isomorphism
@@
 
+With this in hand, the conjecture of \cite{} is as follows:
+
+\begin{conj}
+  [Costello-Li \cite{}]
+  Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold.
+Consider perturbative type IIA supergravity on $M\times X$ around a background where the graviton is set to $h_{M}+ h_{X}$, the bosonic ghost for local supersymmetries takes a VEV $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$, and all other background fields are set to zero.
+The resulting theory admits a description as a Poisson BV theory with fields $\Omega^{\bullet}(M)\otimes \pv^{\bullet, \bullet}(X)[\![t]\!]$ where $t$ is a parameter of degree 2, $L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
+\end{conj}
+
+Type II supergravity around such backgrounds where the bosonic ghost takes a nonzero VEV is what the authors call twisted supergravity.
+In fact, the authors further conjecture that type IIA superstring theory on $M\times X$ around a particular Ramond-Ramond background is equivalent to a topological string theory given by the A-model on $M$ and the B-model on $X$.
+This implies the above conjecture at the level of closed string field theory.
+Indeed the above description of twisted supergravity is a combination of Kodaira--Spencer theory on $X$ with the zero-winding sector of Kahler gravity on $M$.
+
+The authors of \cite{} establish a strand of evidence via residual supersymmetry.
+Namely, they construct an $L_{\infty}$ map from the $Q$-cohomology of the 10d $\cN = (1,1)$ algebra to the fields of the above theory, realizing the former as a collection of ghosts in the latter.
+This allows us to make sense of further twists of the above twist.
+
+The goal of this section is to identify the above conjectural twist of IIA supergravity with an $S^{1}$ reduction of our 11d theory.
+In order to do so, we will need to introduce a slight modification of the Kodaira-Spencer theory.
+We turn to this in the next subsection.
+
 \subsection{Kodaira--Spencer theory with potentials}
-\label{sec:org5e18f8e}
+\label{KSPot}
+
+One property of the description of the twist of type II supergravity in terms of Kodaira--Spencer theory is that the Ramond-Ramond fields of type II do not correspond to fundamental fields in Kodaira--Spencer theory.
+Rather it is certain components of the Ramond-Ramond field strengths that appear.
+However, in the identification of type IIA supergravity as the $S^{1}$ reduction of 11d supergravity, certain components of the C-field become components of the Ramond-Ramond 2-form.
+This suggests that in order to match the dimensional reduction of our 11d theory with a twist of type IIA, we must modify the description of the twist of type IIA to include certain components of Ramond-Ramond fields as potentials for those components of Ramond-Ramond field strengths that one finds in the twisted theory.
+
 \subsubsection{Warm-up: four-dimensional Kodaira--Spencer theory}
 \label{sec:org91dc4ca}
+In the BV formalism, minimal Kodaira--Spencer theory on $X$ is a (degenerate) Poisson BV theory with space of fields given by
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \PV^{0,\bu} \\
+ \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
+\end{tikzcd}
+\]
+We will denote this sheaf of $\ZZ /2$-graded cochain complexes by $\cE_{\rm KS}$.
+
+There is a local (dg) Lie algebra structure on the parity shifted object $\Pi \cE_{\rm KS}$.
+The Lie bracket is defined using the Schouten-Nijenhuis bracket $[-,-]_{\rm NS}$ on polyvector fields and is given by the formula
+\[
+[u^k \alpha , u^\ell \beta] = u^{k+\ell} [\alpha, \beta]_{\rm NS} .
+\]
+where $k, \ell = 0,1$.
+Together with the differential this equips the parity shifted sheaf of cochain complexes $\Pi \cE_{\rm KS}$ with the structure of a local (dg) Lie algebra.
+
+The fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
+\[
+\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
+\]
+
+We introduce another theory on the Calabi--Yau surface $X$ that we call minimal Kodaira--Spencer theory {\em with potentials}.
+The underlying vector bundle is
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \PV^{0,\bu} \\
+ \PV^{2,\bu}  .
+\end{tikzcd}
+\]
+We will denote the resulting $\ZZ /2$-graded sheaf of cochain complexes by $\cE_{\rm pot}$.
+
+We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way.
+There is a map of sheaves of cochani complexes
+\[
+\Phi : \cE_{\rm Pot} \to \cE_{\rm KS}
+\]
+which is the identity on $\PV^{0,\bu}$ and given by $\partial : \PV^{2,\bu} \to \PV^{1,\bu}$ on the remaining component.
+It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes.
+The theory $\cE_{\rm pot}$ is equipped with a non-degenerate BV pairing defined by the wedge-and-integrate pairing
+\[
+\omega_{\rm pot} (\alpha, \beta) = \int \alpha \wedge \beta  .
+\]
+It is immediate to verify that $\Phi$ intertwines the resulting bivector $\omega_{\rm pot}^{-1}$ and the Kodaira--Spencer Poisson bivector $\Pi_{\rm KS}$.
+
+In fact, the parity shifted bundle $\Pi \cE_{\rm pot}$ also has the structure of a local Lie algebra, and the map $\Phi$ intertwines these local Lie algebra structures.
+
+To describe the local Lie algebra structure on minimal Kodaira--Spencer theory with potentials we use the Calabi--Yau form $\Omega$ to identify $\cE_{\rm Pot}$ with the sheaf of cochain complexes
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} \\
+ & \Omega^{2,\bu} \\
+ \Omega^{0,\bu}  .
+\end{tikzcd}
+\]
+
+Now, note that any Calabi--Yau surface comes equipped with a holomorphic symplectic structure and there is a Poisson bracket defined on the sheaf of holomorphic functions.
+Since the bracket is defined in terms of holomorphic differential operators, it extends to a bracket on the Dobleault complex $\Omega^{0,\bu}(X)$.
+
+This further extends to a local Lie algebra structure on the semi-direct product
+\[
+\Omega^{0,\bu}(X) \ltimes \Pi \Omega^{2,\bu}(X)
+\]
+which describes the local Lie structure on $\Pi \cE_{\rm Pot}$.
+It is immediate to verify that the map $\Phi : \cE_{\rm pot} \to \cE$ intertwines the two $L_\infty$-structures.
+
+This equipped $\cE_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory.
+It's relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.
+
+\begin{prop}
+The map $\Phi : \cE_{\rm pot} \to \cE_{\rm KS}$ determines a map of $\PP_0$-factorization algebras on $X$:
+\[
+\Phi^* : {\rm Obs}_{\cE_{\rm KS}} \to {\rm Obs}_{\cE_{\rm Pot}} .
+\]
+\end{prop}
+
 \subsubsection{Eight-dimensional Kodaira--Spencer theory}
@@
 \subsection{The Type IIA topological string}
-\label{sec:org1f7e793}
+\label{IIAtop}
 \subsection{Reduction of twisted supergravity}

### 2020-11-24 paper.tex
merge

--- 2020-11-24 paper.tex
@@
 \]
-In other words $\mu^{1,1}_F$ is a Beltrami differential for this quotient bundle and hence determines a deformation of complex structure of $T^{1,0}_X / F$.
+In other words $\mu^{1,1}_{Q \Bar{Q}}$ is a Beltrami differential for this quotient bundle and hence determines a deformation of complex structure of $Q = T^{1,0}_X / F$.
+
+So, after fixing the value of $\beta \partial \gamma^{1,0}$.
+The remaining components of $\mu^{1,1}$ determine deformations of complex structure of the bundle $F \subset T^{1,0}_X$.
+For instance, the $\mu^{1,1}_{F \Bar{F}}$ determines a deformation of the complex structure on $F$.
+Furthermore, by Equation (\ref{eqn:gamma10}) we see that $\gamma^{1,0}$, hence $\beta = \partial \gamma^{1,0}$, is holomorphic for this deformed complex structure.
 

### 2020-11-27 paper.tex
paper

@@
 \def\pv{{\rm PV}}
+\def\PV{{\rm PV}}
 
@@
 In the remainder of the paper, we wish to establish various consistency checks corroborating the claim that the 11d theory of interest describes a twist of 11d supergravity.
-In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of type IIA supergravity due to \cite{}.
+In this section, we demonstrate that this claim is consistent with a conjectural description of a twist of Type IIA supergravity due to \cite{CLsugra}.
 
-Before recalling this conjecture, we first fix some notation. For a complex manifold $X$, let $TX$ denote the holomorphic tangent bundle and define
+Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string.
+For $i,j$ integers define the space of $(i,j)$-polyvector fields to be
 \[
-\pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX) .\]
-This is the space of $i$-pvvectors of Dolbeault type $j$.
-Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields of type $i$.
+  \pv^{i,j}(X) \define \Omega^{0,j}(X, \wedge^{i} TX)
+\]
+where $TX$ is the holormorphic tangent bundle.
+Using the $\dbar$ operator for the holomorphic bundle $\wedge^{i}TX$ we obtain a cochain complex $\pv^{i,\bu}(X) = \left(\oplus_{j} \pv^{i,j}(X) [-j], \dbar \right)$ which provides a free resolution of the sheaf of holomorphic polyvector fields $\PV^{i}_{\rm hol}(X)$ of type $i$.
 
@@
 
-With this in hand, the conjecture of \cite{} is as follows:
+There is compelling evidence \cite{CLsugra} for the existence of a twist of the Type IIA string on the ten-manifold $M \times X$ where $M$ is a real surface and $X$ is a Calabi--Yau four-fold.
+Roughly, the twist behaves like the A-model topological string along $M$ and the $B$-model topological string along $X$.
+The conjectural state space is
+\[
+  \Omega^\bu(M) \; \Hat{\otimes} \; \PV^{\bu, \bu} (X) .
+\]
+The linear BRST differential on this state space is given by $\d_{\rm dR} + \dbar$.
+The fields of the closed string are given by the $S^1$-equivariant states, which is modeled \cite{CLbcov} by
+\[
+  \Omega^\bu(M) \; \Hat{\otimes} \; \PV^{\bu, \bu} (X) [\![u]\!]
+\]
+where $u$ is the equivariant parameter and the new linear BRST operator is $\d_{\rm dR} + \dbar + u \partial_\Omega$.
+
+With this informal description of the twist of the Type IIA closed string in hand, one can deduce the following low energy limit of the description which gives a conjectural description of Type IIA supergravity.
 
 \begin{conj}
-  [Costello-Li \cite{}]
+  [Costello-Li \cite{CLsugra}]
   Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold.
-Consider perturbative type IIA supergravity on $M\times X$ around a background where the graviton is set to $h_{M}+ h_{X}$, the bosonic ghost for local supersymmetries takes a VEV $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$, and all other background fields are set to zero.
-The resulting theory admits a description as a Poisson BV theory with fields $\Omega^{\bullet}(M)\otimes \pv^{\bullet, \bullet}(X)[\![t]\!]$ where $t$ is a parameter of degree 2, $L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
+  Consider perturbative type IIA supergravity on $M\times X$ around a background where:
+  \begin{itemize}
+    \item the graviton is set to $h_{M}+ h_{X}$,
+    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
+    \item all other background fields are set to zero.
+  \end{itemize}
+  In this background, the resulting theory is equivalent to the Kodaira--Spencer type theory whose fields are
+  \[
+    \Omega^{\bullet}(M) \; \Hat{\otimes} \; \PV^{\bullet, \bullet}(X)[\![u]\!]
+  \]
+  where $u$ is a parameter of cohomological degree $2$.
+  \brian{this theory is only $\ZZ/2$-graded, right?}
+  %$L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
 \end{conj}
 
-Type II supergravity around such backgrounds where the bosonic ghost takes a nonzero VEV is what the authors call twisted supergravity.
+Type II supergravity around such backgrounds where the bosonic ghost takes a nonzero VEV is what is referred to as {\em twisted supergravity} in \cite{CLsugra}.
 In fact, the authors further conjecture that type IIA superstring theory on $M\times X$ around a particular Ramond-Ramond background is equivalent to a topological string theory given by the A-model on $M$ and the B-model on $X$.
@@
 
-The authors of \cite{} establish a strand of evidence via residual supersymmetry.
-Namely, they construct an $L_{\infty}$ map from the $Q$-cohomology of the 10d $\cN = (1,1)$ algebra to the fields of the above theory, realizing the former as a collection of ghosts in the latter.
+There is further evidence for this claim through studying the residual supersymmetry.
+Namely, they construct an $L_{\infty}$ map from the $Q$-cohomology of the 10d $\cN = (1,1)$ algebra to the fields of the above theory \cite{CLsugra}, realizing the former as a collection of ghosts in the latter.
 This allows us to make sense of further twists of the above twist.
@@
 \label{sec:org590ab85}
-Does math mode \(work here = e^x\)?
+
+\brian{some general background on G2 twist, state main result}
+
+We consider the eleven-dimensional theory on the space
+\[
+  X \times Z \times \RR
+\]
+where $Z$ is a hyper-K\"{a}hler surface and $X$ is a Calabi--Yau three-fold.
+Denote by $\Omega_Z$ the holomorphic volume form on $Z$ and $\Omega_X$ the holomorphic volume form on $X$.
+We will work in a background where the $(1,0)$-component of the field $\gamma$ satisfies the following equations:
+\begin{equation}\label{eqn:background}
+  \begin{array}{rcccc}
+    \partial \gamma^{1,0} & = & \Omega_Z \\
+    \dbar \gamma^{1,0} + \d_{\rm dR} \gamma^{1,0} & = & 0 .
+  \end{array}
+\end{equation}
+The second equation implies that $\gamma^{1,0}$ is constant along $\RR$ and holomorphic along $X \times Z$.
+The first equation says that $\gamma^{1,0}$ is a trivialation of the holomorphic volume form on $Z$.
+
+To see that this is a consistent background of the eleven-dimensional theory we must check that $\gamma^{1,0}$ satisfies the appropriate equations of motion.
+
+\begin{lem}
+  Any field $\gamma^{1,0}$ satisfying the equations in (\ref{eqn:background}) satisfies the Maurer--Cartan equation of the eleven-dimensional theory.
+\end{lem}
+
+\begin{proof}
+  We must show that $\gamma^{1,0}$ satisfies the following Maurer--Cartan equation
+  \[
+    Q_{\rm BRST} \gamma^{1,0} + \frac12 [\gamma^{1,0} ,\gamma^{1,0}] = 0
+  \]
+  where $Q_{\rm BRST}$ is the linear BRST operator and $[-,-]$ is the Lie bracket defining the interacting piece of the eleven-dimensional theory.
+
+  Recall, the linear BRST differential is of the form
+  \[
+    \dbar + \partial_{\Omega} + \partial_{\Omega^0 \to \Omega^1} + \d_{\rm dR}
+  \]
+  Here, $\partial_\Omega$ is the divergence operator which only acts on the $\mu$-type fields and $\partial_{\Omega^0 \to \Omega^1}$ is the first piece of the holomorphic de Rham operator acting on $\Omega^{0,\bu}(X \times Z)$.
+  Since $(\dbar + \d_{\rm dR}) \gamma^{1,0} = 0$ by assumption, we see that $\gamma^{1,0}$ is closed for the linear BRST operator.
+
+  The only component of the Lie bracket involving two fields of type $\gamma$ is of the form
+  \[
+    [\gamma, \gamma] = (\partial \gamma \wedge \partial \gamma) \vdash \Omega \in \PV^{1,\bu}(X \times Z) \; \Hat{\otimes} \; \Omega^\bu(L) .
+  \]
+  Since $\partial \gamma^{1,0}$ is a $(2,0)$ form along $Z$, we see that $\partial \gamma^{1,0} \wedge \partial \gamma^{1,0} =0$.
+  We conclude that $\gamma^{1,0}$ satisfies the Maurer--Cartan equation.
+\end{proof}
+
+Next, we expand the action functional near the background where $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ where $\gamma^{1,0}$ satisfies equations (\ref{eqn:background}).
+This will generate new kinetic and interacting terms which we can extract by inserting a formal parameter $\delta$ and expression the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
+
+There are two interaction terms
+\begin{equation}\label{eqn:int1}
+  \frac12 \int_{X\times Z \times L} \left(\gamma \vee \{\mu, \mu\} \right) \wedge (\Omega_Z \wedge \Omega_X)
+\end{equation}
+and
+\begin{equation} \label{eqn:int2}
+  \frac16\int_{X \times Z \times L} \gamma \partial \gamma \partial \gamma .
+\end{equation}
+
+We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.
+Expanding this expression around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$ we obtain
+\[
+  \frac12 \int \left(\gamma \vee \{\mu, \mu\} \right) \wedge (\Omega_Z \wedge \Omega_X) + \frac{\delta}{2} \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) .
+\]
+Here, we have used the identity $\partial \gamma^{1,0} = \Omega_Z$.
+
+Next, we expand Equation (\ref{eqn:int2}) around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
+This becomes
+\[
+  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z .
+\]
+Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
+
+So far, we have written everything in terms of action functionals.
+There is a completely equivalent statement in terms of the resulting dg Lie algebra structure describing the eleven-dimensional theory in this background which we summarize as follows.
+
+\begin{lem} \label{lem:background}
+  The dg Lie algebra describing the eleven-dimensional theory placed in a background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is isomorphic to the the dg Lie algebra whose differential is
+  \begin{equation}\label{eqn:newdiff}
+    Q_{\rm BRST} + \frac{1}{2} \left\{ \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) + \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z , \; - \; \right\}
+  \end{equation}
+  and whose Lie bracket is unchanged.
+  Here, $Q_{\rm BRST}$ is the original linear BRST differential of the eleven-dimensional theory.
+\end{lem}
+
+This lemma followed directly from our analysis of the way the action functional of the theory decomposed around the background.
+The next result we state is an equivalence with a theory which exists on any product of manifolds $Z \times M$ where $Z$ is a hyper-K\"{a}hler surface as above but now $M$ is any smooth seven-dimensional manifold.
+
+\begin{prop}
+  The eleven-dimensional theory on $X \times Z \times L$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is equivalent to the theory whose fields are
+  \[
+    \alpha \in \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(X \times L)
+  \]
+  and whose action functional reads
+  \[
+    \frac12 \int \alpha \d\alpha + \frac16 \int \alpha \{\alpha, \alpha\}
+  \]
+  where $\{-,-\}$ is the Poisson bracket on $\Omega^{0,\bu}(Z)$.
+\end{prop}
+
+As stated above, this theory clearly does not depend on the complex structure on the Calabi--Yau three-fold $X$.
+The theory only depends on the smooth structure on $M = X \times L$.
+\brian{cite Surya and Phil, Chris and B, Kevin}
+
+\begin{proof}
+To unpack this new differential (\ref{eqn:newdiff}) as in Lemma \ref{lem:background} we need to reidentify the fields of the eleven-dimensional theory.
+First, note that we have natural identifications
+\begin{align}
+  \PV^{1,\bu}(X \times Z) & = \PV^{1,\bu}(X) \; \Hat{\otimes} \; \PV^{0,\bu}(Z)\; \oplus \; \PV^{0,\bu}(X) \; \Hat{\otimes} \; \PV^{1,\bu}(Z) \\ & \cong \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu} (Z) \; \oplus \; \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z) \label{eqn:decomposevf}
+\end{align}
+The isomorphism uses both the holomorphic volume forms $\Omega_X$ and $\Omega_Z$.
+
+From Lemma \ref{lem:background} we see that the new terms in the linear BRST differential arise from the quadratic terms in the action
+\begin{equation}\label{eqn:newterms}
+  \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) + \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z .
+\end{equation}
+
+Recall that the linear BRST complex of the original eleven-dimensional theory is obtained by taking the tensor product of the cochain complexes $\PV^{1,\bu}(X \times Z) \xto{\partial_\Omega} \PV^{0,\bu}(X \times Z)$ and $\Omega^{0,\bu}(X \times Z) \xto{\partial} \Omega^{1,\bu}(X \times Z)$ with the de Rham complex $\Omega^\bu(L)$ on the one-manifold $L$.
+
+Using the decomposition (\ref{eqn:decomposevf}) we see that the deformed linear BRST complex takes is the tensor product of the de Rham complex $\Omega^{\bu}(L)$ with the cochain complex
+\[
+  \begin{tikzcd}
+  & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z) \ar[dr, "\partial_Z"] \\
+  & & \Omega^{3,\bu}(X) \; \Hat{\otimes} \; \Omega^{2,\bu}(Z) \\
+ & \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ur, "\partial_X"'] & \\
+\;_{\cong}  & & \Omega^{1,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ul, dashed, bend left = 10, "\partial_X"]\\
+ & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu}(Z) \ar[ur, "\partial_X"] \ar[dr,"\partial_Z"'] \\
+  & & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z)
+\ar[dashed, rounded corners, to path={ -- ([yshift=-2ex]\tikztostart.south) -| ([xshift=-1.5ex]\tikztotarget.west) -- (\tikztotarget)}, uuuuul]
+  %\ar[uuuuul, start anchor =  {[yshift = 0ex, xshift=0ex]}, end anchor = {[yshift=1.0ex, xshift=-5ex]}, bend left = 90, dotted] .
+  \end{tikzcd}
+\]
+Here, the dashed arrow along the outside of the diagram corresponds to the BV antibracket with the first term in (\ref{eqn:newterms}).
+Note that this is the identity morphism on $\Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z)$.
+The other dashed arrow corresponds to the BV antibracket with the second term in (\ref{eqn:newterms}).
+It is given by the holomorphic de Rham operator $\partial_X : \Omega^{1,\bu}(X) \to \Omega^{2,\bu}(X)$.
+
+\brian{cochain homotopy finish}
+Since the outer dashed arrow is an isomorphism, we see that this cochain map is a quasi-isomorphism.
+It is immediate to check that this quasi-isomorphism intertwines the Lie brackets.
+
+\end{proof}
+
 \end{document}

### 2021-01-27 paper.tex
merge

@@
 \def\PV{{\rm PV}}
+\def\T{{\rm T}}
 
@@
 
-Before stating the definition, we recall some general objects in complex geometry that will play a central role.
-For now, let $X$ be any complex manifold and let $V$ be a holomorphic vector bundle on $X$.
+One of the fundamental geometric objects will be the sheaf of divergence-free holomorphic vector fields on $X$. 
+We will utilize a convenient semi-free resolution of this sheaf in the category of $C^\infty$-modules.
+
 If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of Dolbeault forms of type $j$ on with values in $V$.
@@
 which is a free resolution for the sheaf of holomorphic sections of $V$.
+Applying this to the holomorphic tangent bundle $V = \T_X$, we obtain a resolution of the sheaf of holomorphic vector fields.
 
-Denote by $TX$ the holomorphic tangent bundle of $X$.
-Then, the Lie bracket of holomorphic vector fields extends to a Lie bracket on the Dolbeault $\Omega^{0,\bu}(X, TX)$ thus endowing it with the structure of a dg Lie algebra.
-
-By definition, the Dolbeault complex for the trivial bundle $\Omega^{0,\bu}(X)$ is a dg module for the dg Lie algebra $\Omega^{0,\bu}(X, TX)$.
-We can thus consider the following semi-direct product dg Lie algebra
-\beqn\label{eqn:div1}
-  \Omega^{0,\bu}(X, TX) \oplus \Omega^{0,\bu}(X) [-1] .
-\eeqn
-Notice that $\Omega^{0,\bu}(X)$ has been shifted to a seemingly unnatural cohomological degree, with $(0,j)$-forms sitting in degree $j+1$.
+%Denote by $TX$ the holomorphic tangent bundle of $X$.
+%Then, the Lie bracket of holomorphic vector fields extends to a Lie bracket on the Dolbeault $\Omega^{0,\bu}(X, TX)$ thus endowing it with the structure of a dg Lie algebra.
+%
+%By definition, the Dolbeault complex for the trivial bundle $\Omega^{0,\bu}(X)$ is a dg module for the dg Lie algebra $\Omega^{0,\bu}(X, TX)$.
+%We can thus consider the following semi-direct product dg Lie algebra
+%\beqn\label{eqn:div1}
+%  \Omega^{0,\bu}(X, TX) \ltimes \Omega^{0,\bu}(X) [-1] .
+%\eeqn
+%Notice that $\Omega^{0,\bu}(X)$ has been shifted to a seemingly unnatural cohomological degree, with $(0,j)$-forms sitting in degree $j+1$.
+%We will see the reason for this shift momentarily.
 
 Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
-The holomorphic divergence operator with respect to $\Omega$ is an operator of the form
+The holomorphic divergence operator extends to the Dolbeault complex to take the form
 \[
-  \partial_\Omega : \Omega^{0,\bu}(X, TX) \to \Omega^{0,\bu}(X)
+  \partial_\Omega : \Omega^{0,\bu}(X, \T_X) \to \Omega^{0,\bu}(X)
 \]
-defined by the formula
+and is defined by the formula
 \[
@@
 
-Using the holomorphic divergence operator $\partial_\Omega$ we can consider the following deformation of the dg Lie algebra (\ref{eqn:div1}).
-The Lie bracket remains the same but the differential is deformed from $\dbar$ to $\dbar + \partial_\Omega$.
-Here, $\partial_{\Omega}$ denotes the holomorphic divergence operator thought of as a degree one operator from $\Omega^{0,\bu}(X, TX)$ to $\Omega^{0,\bu}(X)$.
-We will denote the resulting dg Lie algebra by $\cS(X)$.
+Using the divergence operator, we define the double complex of sheaves
+\[
+\Omega^{0,\bu}(X, \T_X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] 
+\]
+where the horizontal differential is the divergence operator and the vertical differential is the $\dbar$ operator (which we have left implicit). 
+We denote the totalization of this double complex of sheaves $\cS$.
 
-It is easy to see that $\cS(X)$ provides a free resolution of the sheaf of holomorphic divergence free vector fields on $X$.
+It is immediate to check that $\cS$ provides a free resolution of the sheaf of holomorphic divergence-free vector fields on $X$.
+Furthermore, there is a natural Lie bracket on $\cS$ given by the Schouten--Nijenhous bracket $\{-,-\}_{\rm NS}$ which is compatible with the usual Lie bracket of holomorphic vector fields. 
+In other words, $\cS$ is a sheaf of dg Lie algebras and the inclusion of holomorphic divergence-free vector fields is a quasi-isomorphism of sheaves of Lie algebras.
+
+%Using the holomorphic divergence operator $\partial_\Omega$ we can consider the following deformation of the dg Lie algebra (\ref{eqn:div1}).
+%The Lie bracket remains the same but the differential is deformed from $\dbar$ to $\dbar + \partial_\Omega$.
+%Here, $\partial_{\Omega}$ denotes the holomorphic divergence operator thought of as a degree one operator from $\Omega^{0,\bu}(X, TX)$ to $\Omega^{0,\bu}(X)$.
+%We will denote the resulting dg Lie algebra by $\cS(X)$.
 
@@
 \[
-  [\mu \otimes \alpha, \nu \otimes \beta] = [\mu, \nu] \otimes (\alpha \wedge \beta) .
+  [\mu \otimes \alpha, \nu \otimes \beta] = \{\mu, \nu\}_{\rm NS} \otimes (\alpha \wedge \beta) .
 \]
@@
 
-Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory''.
+Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory'' and it is defined as follows.
 Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
@@
 
-For the case at hand, we consider the BF theory associated to the local dg Lie algebra (\ref{localLie}) defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+For the case at hand, we consider the $BF$ theory associated to the local dg Lie algebra  $\cS(X) \otimes \Omega^\bu(L)$ defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
 Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(L)$.
@@
   \begin{array}{ccl}
-    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[-1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
+    \mu = \mu^1+\mu^0 & \in & \left(\Omega^{0,\bu}(X, \T_X)[1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
   \end{array}
 \]
-Notice that what we called the ``$A$''-field in the general definition of BF theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
-By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
+Notice that what we called the ``$A$''-field in the general definition of $BF$ theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
+The action of this version of $BF$ theory simply reads 
+\[
+\int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
+\]
+This theory is defined on any geometry $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a one-dimensional smooth manifold.
+There is a deformation of this theory that we will be most concerned with.
 
-While the definition of $\mu$ is independent of the dimension, the field $\gamma$ depends on $d$.
-This is in order for the BV antibracket to be of the appropriate degree.
-Additionally, we have utilized the holomorphic volume form in the definition of the field $\gamma$.
-Indeed, in this presentation the BV antipairing on fields reads
-\[
-  \int_{X \times L} (\mu \vdash \gamma) \wedge \Omega = \int_{X \times L} (\mu^1 \vdash \gamma^1 + \mu^0 \vdash \gamma^0) \wedge \Omega .
-\]
+%By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
+%Notice that while the definition of $\mu$  of the dimension, the field $\gamma$
 
-\subsubsection{}
+%This is in order for the BV antibracket to be of the appropriate degree.
+%Additionally, we have utilized the holomorphic volume form in the definition of the field $\gamma$.
+%Indeed, in this presentation the BV antipairing on fields reads
+%\[
+%  \int_{X \times L} (\mu \vee \gamma) \wedge \Omega = \int_{X \times L} (\mu^1 \vee \gamma^1 + \mu^0 \gamma^0) \wedge \Omega .
+%\]
+
+\subsubsection{Chern--Simons deformation}
+The theory we have just described admits a deformation by a higher Chern--Simons term.
+We explain how this relates to the familiar Chern--Simons term in eleven-dimensional supergravity in Section \ref{sec:evidence}.
+
 We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $L$ is a real one-dimensional manifold.
-In this case $d = 6$ so the field $\gamma$ takes the form
+In the notation of the last section, $d = 6$, so the field $\gamma$ takes the form
 \[
@@
 \[
-J(\gamma) = \frac13 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
+J(\gamma) = \frac16 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
 \]
@@
 Being a classical action functional $S_{\rm BF}$ is, of course, ghost degree zero.
-However, we observe that $J$ is of ghost degree $??$.
+However, we observe that $J$ is of ghost degree $+6$.
 In order to make sense of the deformed theory, therefore, we must consider the space of fields as a $\ZZ/2$-graded object rather than a $\ZZ$-graded one.
@@
     \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X)[1] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
+    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
   \end{array}
@@
 \begin{lem}
-The functional $J = \frac13 \int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
+The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
 In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
@@
 It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
-It remains to see that
+It remains to see that\brian{finish}
 \end{proof}
@@
 
-\begin{dfn}
+\begin{dfn}\label{dfn:11dtheory}
 Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
-Define the $\ZZ/2$-graded BV theory $\cT$ on
+Define the $\ZZ/2$-graded BV theory $\cT_{X \times L}$ (or simply just $\cT$) on
 \[
@@
 \]
-to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac13 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
+to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac16 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
 \end{dfn}
@@
 
-A simple count reveals that the ghost degree of the functional $J_m$ is \brian{figure out}.
-In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ defines a $\ZZ/2$-graded classical BV theory.
+A simple count reveals that the ghost degree of the functional $J_m$ is $2m^2 - 2$.
+In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ only defines a $\ZZ/2$-graded classical BV theory.
 
@@
 
-When $m=1$, the action $S_{\rm BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
+When $m=1$, hence $X$ is a CY three-fold, the action $S_{\rm BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
 Another feature of the case $m=1$ is that the deformed theory is actually a {\em topological} field theory.
@@
 
-In this case $X$ is a Calabi--Yau three-fold.
 Using the isomorphism
@@
 
-The action functional of the theory (\ref{11daction}) on $X \times L$ is of the form
+The action functional of the theory in Definition \ref{dfn:11dtheory} on $X \times L$ is of the form
 \[
-  \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega + \frac{c}{3} \int \gamma \partial \gamma \partial \gamma .
+  \int_{X \times L} \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int_{X \times L} \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega + \frac{c}{3} \int_{X \times L} \gamma \partial \gamma \partial \gamma .
 \]
@@
 
-\subsection{Evidence for twisted supergravity}
+\subsection{Evidence for twisted supergravity}\label{sec:evidence}
 
@@
 Here, $S$ denotes the $128$ dimensional complex spin representation of $\fs \fo(11)$.
+
+\subsubsection{Residual supersymmetry}
+
+\def\m2{\mathfrak{m}2\mathfrak{brane}}
+\def\susy{\mathfrak{susy}}
+\def\so{\mathfrak{so}}
+\def\siso{\mathfrak{siso}}
+\def\fsl{\mathfrak{sl}}
+
+Recall, the (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
+\[
+  \ft_{11d} = V \oplus \Pi S
+\]
+where $V$ is the fundamental representation of $\so(11 , \CC)$ and $S$ is the irreducible (complex) spin representation.
+The only non-trivial Lie bracket is
+\[
+  [Q, Q'] = \Gamma_{\Omega^1}(Q \otimes Q')
+\]
+where
+\[
+  \Gamma_{\Omega^1} : \Sym^2(S) \to V 
+\]
+is the unique $\so(11, \CC)$-equivariant \brian{finish}
+The super Poincar\'{e} algebra is
+\[
+  \siso_{11d} = \so(11 , \CC) \ltimes \ft_{11d} .
+\]
+
+Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$. 
+Let
+\[
+  \Gamma_{\Omega^2} : \Sym^2(S) \to \wedge^2 V \subset \Omega^2(\RR^{11}) 
+\]
+be the \brian{finish}.
+
+\begin{dfn}
+  The super dg Lie algebra $\m2$ is the central extension of $\siso_{11d}$ by the cocycle
+  \[
+    c_{M2} \in \clie^2\left(\siso_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
+  \]
+  defined by the formula $c_{M2} (Q, Q') = \Gamma_{\Omega^2}(Q \otimes Q') \in \Omega^2(\RR^{11})$.
+\end{dfn}
+
+Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
+
+\begin{lem}
+  Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the $Q$-cohomology of $\m2$.
+  There is an isomorphism of $\ZZ/2$-graded Lie algebras
+  \[
+    \m2^Q \simeq \fsl(5;\CC) \ltimes ???
+  \]
+\end{lem}
+
+Consider now the eleven-dimensional theory $\cT = \cT_{\CC^5 \times \RR}$ defined on $\CC^5 \times \RR$. 
+The BV action induces the structure of a dg Lie algebra on $\cT[1]$.
+
+\begin{prop}
+The assignment
+\brian{??} defines a map of $\ZZ/2$-graded dg Lie algebras 
+\[
+\m2 \to \cT[1] .
+\]
+In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+\end{prop}
 
@@
 where $k, \ell = 0,1$.
-Together with the differential this equips the parity shifted sheaf of cochain complexes $\Pi \cE_{\rm KS}$ with the structure of a local (dg) Lie algebra.
+Together with the differential this equips the parity shifted sheaf of cochain complexes $\Pi \cE_{\rm KS}$ with the structure of a local dg Lie algebra.
 
@@
 \]
-We will denote the resulting $\ZZ /2$-graded sheaf of cochain complexes by $\cE_{\rm pot}$.
+We will denote the resulting $\ZZ /2$-graded sheaf of cochain complexes by $\cE_{\rm Pot}$.
 
@@
 \begin{prop}
-The map $\Phi : \cE_{\rm pot} \to \cE_{\rm KS}$ determines a map of $\PP_0$-factorization algebras on $X$:
+  The map $\Phi : \cE_{\rm pot} \to \cE_{\rm KS}$ is a map of Poisson BV theories.
+  In particular, it determines a map of $\PP_0$-factorization algebras on $X$:
 \[
@@
   \[
-    [\gamma, \gamma] = (\partial \gamma \wedge \partial \gamma) \vdash \Omega \in \PV^{1,\bu}(X \times Z) \; \Hat{\otimes} \; \Omega^\bu(L) .
+    [\gamma, \gamma] = (\partial \gamma \wedge \partial \gamma) \vee (\Omega_X \wedge \Omega_Z) \in \PV^{1,\bu}(X \times Z) \; \Hat{\otimes} \; \Omega^\bu(L) .
   \]
@@
 Next, we expand the action functional near the background where $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ where $\gamma^{1,0}$ satisfies equations (\ref{eqn:background}).
-This will generate new kinetic and interacting terms which we can extract by inserting a formal parameter $\delta$ and expression the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
+This will generate new kinetic and interacting terms which we can extract by inserting a formal parameter $\delta$ and expressing the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
 
-There are two interaction terms
+There are two interaction terms in the original theory.
+The first is
 \begin{equation}\label{eqn:int1}
@@
 \end{equation}
-and
+and the second is
 \begin{equation} \label{eqn:int2}
@@
 
-We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.
+We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.\brian{there might be some factors I'm being sloppy with here}
 Expanding this expression around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$ we obtain
@@
 
-This lemma followed directly from our analysis of the way the action functional of the theory decomposed around the background.
+This lemma followed directly from our analysis of the way the action functional of the theory decomposed around this particular background.
 The next result we state is an equivalence with a theory which exists on any product of manifolds $Z \times M$ where $Z$ is a hyper-K\"{a}hler surface as above but now $M$ is any smooth seven-dimensional manifold.
@@
 \begin{prop}
-  The eleven-dimensional theory on $X \times Z \times L$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is equivalent to the theory whose fields are
-  \[
-    \alpha \in \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(X \times L)
-  \]
+  The eleven-dimensional theory on $X \times Z \times L$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is equivalent to the $\ZZ/2$-graded theory whose fields are
+    $\alpha \in \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(X \times L) [1]$
   and whose action functional reads
@@
 
-As stated above, this theory clearly does not depend on the complex structure on the Calabi--Yau three-fold $X$.
+As stated in this proposition, it is clear that the theory does not depend on the complex structure on the Calabi--Yau three-fold $X$ even though this is not {\em a priori} obvious from the description in Lemma \ref{lem:background}.
 The theory only depends on the smooth structure on $M = X \times L$.
@@
 \begin{proof}
-To unpack this new differential (\ref{eqn:newdiff}) as in Lemma \ref{lem:background} we need to reidentify the fields of the eleven-dimensional theory.
-First, note that we have natural identifications
-\begin{align}
-  \PV^{1,\bu}(X \times Z) & = \PV^{1,\bu}(X) \; \Hat{\otimes} \; \PV^{0,\bu}(Z)\; \oplus \; \PV^{0,\bu}(X) \; \Hat{\otimes} \; \PV^{1,\bu}(Z) \\ & \cong \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu} (Z) \; \oplus \; \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z) \label{eqn:decomposevf}
-\end{align}
-The isomorphism uses both the holomorphic volume forms $\Omega_X$ and $\Omega_Z$.
+To unpack this new differential (\ref{eqn:newdiff}) in Lemma \ref{lem:background} we need to reidentify the fields of the eleven-dimensional theory.
+Using the holomorphic volume forms $\Omega_X$ and $\Omega_Z$ we make the following identifications
+\begin{equation}\label{eqn:decomposevf}
+\begin{array}{ccccc}
+  \PV^{1,\bu}(X \times Z) & = & \PV^{1,\bu}(X) \; \Hat{\otimes} \; \PV^{0,\bu}(Z) & \oplus & \PV^{0,\bu}(X) \; \Hat{\otimes} \; \PV^{1,\bu}(Z) \\ & \cong & \Omega^{2,\bu}(X) \; \Hat{\otimes} \; \Omega^{0,\bu} (Z) & \oplus & \Omega^{0,\bu}(X) \; \Hat{\otimes} \; \Omega^{1,\bu}(Z)
+\end{array}
+\end{equation}
 
@@
 Recall that the linear BRST complex of the original eleven-dimensional theory is obtained by taking the tensor product of the cochain complexes $\PV^{1,\bu}(X \times Z) \xto{\partial_\Omega} \PV^{0,\bu}(X \times Z)$ and $\Omega^{0,\bu}(X \times Z) \xto{\partial} \Omega^{1,\bu}(X \times Z)$ with the de Rham complex $\Omega^\bu(L)$ on the one-manifold $L$.
-
-Using the decomposition (\ref{eqn:decomposevf}) we see that the deformed linear BRST complex takes is the tensor product of the de Rham complex $\Omega^{\bu}(L)$ with the cochain complex
+Using the decomposition (\ref{eqn:decomposevf}) we see that the deformed linear BRST complex is the tensor product of the de Rham complex $\Omega^{\bu}(L)$ with the cochain complex
 \[
@@
 \end{document}
+
+TO DO:
+
+-- m2 brane twist
+
+-- intro to renormalization section
+
+-- email Kevin about moduli of quantizations.
+
+-- CY3 compactification
+
+-- G2 compactification.

### 2021-01-27 paper.tex
L_\infty map from IIA to potentials

--- 2020-11-27 paper.tex
@@
 
-Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string.
+Before recalling this conjecture, we first fix some notation which is useful to describe the state space for the Type IIA string. \surya{move earlier?}
 For $i,j$ integers define the space of $(i,j)$-polyvector fields to be
@@
 
-This equipped $\cE_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory.
-It's relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.
+This equips $\cE_{\rm pot}$ with the structure of an interacting (non-degenerate) BV theory.
+Its relationship to (minimal) Kodaira--Spencer theory can be summarized as follows.
 
@@
 \label{sec:orgeb2dd4d}
+
+Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\Z/2$-graded theory with the following fundamental fields:
+\begin{itemize}
+\item The even fields are a holomorphic function $\mu^0$ and a $\partial$-closed holomorphic bivector $\mu^2$.
+\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\partial$-closed holomorphic section $\mu^3$ of $\wedge^3 T_X$.
+\end{itemize}
+
+The space of fields admits a locally free description obtained by including the ``descendants" \surya{maybe should be more formal here}
+The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
+Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$.
+The sheaf of cochain complexes $\cE$ underlying minimal Kodaira--Spencer theory on $X$ is
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
+& & & \mu^0 \in \PV^{0,\bu} \\
+& & \sum u^k \mu^1 \in \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
+& \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \partial"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\
+\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \del"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
+\end{tikzcd}
+\]
+The differential on this sheaf of cochain complexes is given by $\dbar + u \partial$.
+
+There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
+On the fields (including the descendants) it is defined by the formula
+\[
+[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS} .
+\]
+
+The space of fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
+\[
+\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
+\]
+Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\Z/2$-graded Poisson BV theory.
+
+As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
+The underlying sheaf of cochain complexes is
+\[
+\begin{tikzcd}
+\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
+& & & \eta^{0}\in\PV^{0,\bu} \\
+& & \mu^{1}+u\mu^{0}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
+u^{-1} \gamma^4 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
+\beta^{4} \in\PV^{4,\bu} &  &  & \\
+\end{tikzcd}
+\]
+We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify $cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu}))$.
+
+\begin{dfn}
+  Let $X$ be a Calabi-Yau 4-fold, and let $\mc L$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket.
+Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\mc L$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}
+
+To facillitate the calculations in this section, it will be useful to explicate the Lie structure. We have the following brackets:
+
+\begin{align}
+  \PV^{1,\bu}\times\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}\\
+  \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
+  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS}
+  \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
+  \PV^{4,\bu}\times \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}}\\
+  \PV^{3,\bu}\times \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}\\
+  \PV^{3,\bu}\times \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS}\\
+  u^{-1}\PV^{4,\bu}\times u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}
+\end{align}
+\surya{explain more}
+
+Together with the wedge and integrate pairing, $\cE_{\rm pot}$ has the structure of a nondegenerate BV theory.
+
+Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes $\Phi^{(1)}: \cE_{\rm pot}\to \cE_{\rm KS}$ given by
+
+\[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\mapsto \begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ \partial\gamma^{3} \\ \partial\beta^{4}\end{pmatrix}\]
+
+This fails to be a map of local dg Lie algebras, but the induced map on $\partial$-cohomology is indeed a map of local Lie algebras. Therefore, we still have the following:
+
+\begin{prop}
+There is a local $L_{\infty}$ map $\cE_{\rm pot}\to \cE_{\rm KS}$.
+\end{prop}
+\begin{proof}
+  Consider the collection of linear maps $\{\Phi^{(n)}: \cE_{\rm Pot}^{\otimes n}\to \cE_{\rm KS}[n-1]\}$ where $\Phi^{(1)}$ is given as above and $\Phi^{{(2)}}$ is given by \[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\otimes \begin{pmatrix}\tilde{\nu}^{0} \\ \tilde{\mu}^{1}+u\tilde{\mu}^{0}\\ u^{-1}\tilde{\gamma}^{4}+\tilde{\gamma}^{3} \\ \tilde{\beta}^{4} \end{pmatrix}\to \begin{pmatrix} 0 \\ 0 \\ [\mu^{0},\tilde{\gamma}^{3}]_{\rm NS}\pm [\tilde{\mu}^{0},\gamma^{3}] \\ 0\end{pmatrix}.\]
+
+  We claim that the $\Phi^{(n)}$ define an $L_{\infty}$ map. To this end, there are three kinds of conditions to check.
+  \begin{itemize}
+    \item A 2-linear condition which expresses that $\Phi^{(2)}$ renders the failure of $\Phi^{(1)}$ to preserve the brackets homotopically trivial.
+That is, for $a,b\in\cE_{\rm Pot},$ \[\Phi^{(1)}([a,b])-[\Phi^{(1)}(a),\Phi^{(1)}(b)]=d_{\rm KS}\Phi^{(2)}(a,b)-\Phi^{(2)}(d_{\rm Pot}a, b)-(-1)^{|a|}\Phi^{(2)}(a,d_{\rm Pot}b).\] Note that $\Phi^{(1)}$ in fact preserves all brackets other than the brackets $\PV^{3,\bu}\otimes \PV^{1,\bu}\to \PV^{3,\bu}$ and $u^{-1}\PV^{4,\bu}\otimes u\PV^{0,\bu}\to \PV^{3,\bu}$
+      \surya{to finish}
+  \end{itemize}
+\end{proof}
+
 \subsection{The Type IIA topological string}

### 2021-01-29 paper.tex
fixed illegal commands and formatting errors

@@
 \usepackage{hyperref}
-
+\usepackage{amsfonts}
 \usepackage{macros-mtheory}
@@
 
-So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ/2$-graded space of fields takes the form
+So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
 \[
@@
     \item the graviton is set to $h_{M}+ h_{X}$,
-    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
+    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\rm SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
     \item all other background fields are set to zero.
@@
 
-Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\Z/2$-graded theory with the following fundamental fields:
+Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\ZZ/2$-graded theory with the following fundamental fields:
 \begin{itemize}
@@
 
-The space of fields admits a locally free description obtained by including the ``descendants" \surya{maybe should be more formal here}
-The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
+The space of fields admits a locally free description obtained by including the ``descendants". The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
 Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$.
 The sheaf of cochain complexes $\cE$ underlying minimal Kodaira--Spencer theory on $X$ is
-\[
-\begin{tikzcd}
+\[\begin{tikzcd}
 \ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
@@
 & \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \partial"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\
-\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \del"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
+\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \partial"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
 \end{tikzcd}
@@
 \[
-[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS} .
+[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS}.
 \]
@@
 \]
-Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\Z/2$-graded Poisson BV theory.
+Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\ZZ/2$-graded Poisson BV theory.
 
-As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
-The underlying sheaf of cochain complexes is
+As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory. The underlying sheaf of cochain complexes is
 \[
@@
 \]
-We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify $cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu}))$.
+We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify \[\cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})).\]
 
 \begin{dfn}
-  Let $X$ be a Calabi-Yau 4-fold, and let $\mc L$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket.
-Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\mc L$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}
+  Let $X$ be a Calabi-Yau 4-fold, and let $\cL$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket.
+Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\cL$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}
 
@@
   \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
-  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS}
+  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS} \\
   \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
@@
 \end{align}
-\surya{explain more}
 

### 2021-02-04 paper.tex
Finished L_\infty map E_pot\to E_KS

@@
 
-There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
+There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $\{-,-\}_{\rm NS}$ on polyvector fields.
 On the fields (including the descendants) it is defined by the formula
@@
   Let $X$ be a Calabi-Yau 4-fold, and let $\cL$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket.
-Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\cL$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}
+Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\cL$ by the local functional \[ J(\nu^{0}, \gamma^{3})=\frac{1}{3}\int_{X}\left((\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\vdash\Omega\right) \wedge \Omega\]\end{dfn}
 
@@
 
+\begin{itemize}
+\item The dg Lie structure on $\cL$ is given by the following brackets:
+\begin{align*}
+  \PV^{1,\bu}\otimes\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}  \\
+  \PV^{1,\bu}\otimes\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS} \\
+  \PV^{1,\bu}\otimes u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS}.
+\end{align*}
+
+\item Next we have the action of $\cL$ on $\Pi\cL^{*}$, given by the brackets:
 \begin{align}
-  \PV^{1,\bu}\times\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}\\
-  \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
-  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS} \\
-  \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
-  \PV^{4,\bu}\times \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}}\\
-  \PV^{3,\bu}\times \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}\\
-  \PV^{3,\bu}\times \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS}\\
-  u^{-1}\PV^{4,\bu}\times u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}
+  \PV^{4,\bu}\otimes \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}} \nonumber\\
+  \PV^{3,\bu}\otimes \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS} \label{funnybracket}\\
+  u^{-1}\PV^{4,\bu}\otimes u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}\label{funnybracketdesc}.
 \end{align}
 
-Together with the wedge and integrate pairing, $\cE_{\rm pot}$ has the structure of a nondegenerate BV theory.
+\item The deformation $J(\nu^{0},\gamma^{3})$ is given by the brackets:
+\begin{align*}
+  \PV^{3,\bu}\otimes \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
+\PV^{3,\bu}\otimes \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}.
+\end{align*}
+\end{itemize}
 
-Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes $\Phi^{(1)}: \cE_{\rm pot}\to \cE_{\rm KS}$ given by
+Like in the case of Kodaira--Spencer theory on a complex surface, there is a  map of sheaves of cochain complexes $\Phi^{(1)}: \cE_{\rm pot}\to \cE_{\rm KS}$ given by testing
 
@@
 \begin{prop}
-There is a local $L_{\infty}$ map $\cE_{\rm pot}\to \cE_{\rm KS}$.
+There is a map of local $L_{\infty}$-algebras $\cE_{\rm pot}\to \cE_{\rm KS}$ extending $\Phi^{(1)}$.
 \end{prop}
 \begin{proof}
-  Consider the collection of linear maps $\{\Phi^{(n)}: \cE_{\rm Pot}^{\otimes n}\to \cE_{\rm KS}[n-1]\}$ where $\Phi^{(1)}$ is given as above and $\Phi^{{(2)}}$ is given by \[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\otimes \begin{pmatrix}\tilde{\nu}^{0} \\ \tilde{\mu}^{1}+u\tilde{\mu}^{0}\\ u^{-1}\tilde{\gamma}^{4}+\tilde{\gamma}^{3} \\ \tilde{\beta}^{4} \end{pmatrix}\to \begin{pmatrix} 0 \\ 0 \\ [\mu^{0},\tilde{\gamma}^{3}]_{\rm NS}\pm [\tilde{\mu}^{0},\gamma^{3}] \\ 0\end{pmatrix}.\]
+  Consider the collection of linear maps $\{\Phi^{(n)}: \cE_{\rm Pot}^{\otimes n}\to \cE_{\rm KS}[n-1]\}$ where $\Phi^{(1)}$ is given as above, $\Phi^{{(2)}}$ is given by \[\begin{pmatrix}\nu^{0} \\ \mu^{1}+u\mu^{0} \\ u^{-1}\gamma^{4}+\gamma^{3} \\ \beta^{4}\end{pmatrix}\otimes \begin{pmatrix}\tilde{\nu}^{0} \\ \tilde{\mu}^{1}+u\tilde{\mu}^{0}\\ u^{-1}\tilde{\gamma}^{4}+\tilde{\gamma}^{3} \\ \tilde{\beta}^{4} \end{pmatrix}\mapsto \begin{pmatrix} 0 \\ 0 \\ \{\mu^{0},\tilde{\gamma}^{3}\}_{\rm NS}-(-1)^{(|\tilde \mu^{0}|-1)(|\gamma^{3}|-1)}\{\tilde{\mu}^{0},\gamma^{3}\}_{\rm NS} \\ 0\end{pmatrix}\] and $\Phi^{(n)}=0$ for all $n\neq 1,2$
 
@@
     \item A 2-linear condition which expresses that $\Phi^{(2)}$ renders the failure of $\Phi^{(1)}$ to preserve the brackets homotopically trivial.
-That is, for $a,b\in\cE_{\rm Pot},$ \[\Phi^{(1)}([a,b])-[\Phi^{(1)}(a),\Phi^{(1)}(b)]=d_{\rm KS}\Phi^{(2)}(a,b)-\Phi^{(2)}(d_{\rm Pot}a, b)-(-1)^{|a|}\Phi^{(2)}(a,d_{\rm Pot}b).\] Note that $\Phi^{(1)}$ in fact preserves all brackets other than the brackets $\PV^{3,\bu}\otimes \PV^{1,\bu}\to \PV^{3,\bu}$ and $u^{-1}\PV^{4,\bu}\otimes u\PV^{0,\bu}\to \PV^{3,\bu}$
-      \surya{to finish}
+That is, for $a,b\in\cE_{\rm Pot},$ \begin{align*}\Phi^{(1)}([a,b])-[\Phi^{(1)}(a),\Phi^{(1)}(b)]=d_{\rm KS}\Phi^{(2)}(a,b)-\Phi^{(2)}(d_{\rm Pot}a, b)-(-1)^{|a|}\Phi^{(2)}(a,d_{\rm Pot}b)\label{2-linear}.\end{align*} Note that $\Phi^{(1)}$ in fact preserves all brackets other than the brackets \ref{funnybracket}, \ref{funnybracketdesc}.
+It is immediate from the expression for $\Phi^{(2)}$ that the right-hand side of \ref{2-linear} vanishes for $a, b$ in the domain of brackets other than \ref{funnybracket}, \ref{funnybracketdesc}.
+Therefore, we need only check that \ref{2-linear} in two cases.
+
+      Consider $\gamma^{3}\otimes \tilde \mu^{1}\in \PV^{3,\bu}\otimes \PV^{1,\bu}$. We have that
+      \begin{align*}
+        \Phi^{(1)}([\gamma^{3},\tilde \mu^{1}]) &-\{\Phi^{1}(\gamma^{3}),\Phi^{1}(\tilde \mu^{1})\}_{\rm NS} \\
+        &= \partial\{\gamma^{3}, \tilde \mu^{1}\}_{\rm NS}-\{\partial \gamma^{3}, \tilde \mu^{1}\}_{\rm NS} \\
+        &= \{\partial \gamma^{3}, \tilde \mu^{1}\}_{\rm NS}+(-1)^{|\gamma^{3}|-1}\{\gamma^{3}, \partial \tilde \mu^{1}\}_{\rm NS} - \{\partial\gamma^{3}, \tilde \mu^{1}\}_{\rm NS} \\
+        &= (-1)^{|\gamma^{3}|-1}\{\gamma^{3}, \partial \tilde \mu^{1}\}_{\rm NS}
+      \end{align*}
+
+      On the other hand, we have that
+      \begin{align*}
+        d_{\rm KS}\Phi^{(2)}(\gamma^{3},\tilde\mu^{1}) & -\Phi^{(2)}(d_{\rm Pot}\gamma^{3}, \tilde \mu^{1})-(-1)^{|a|}\Phi^{(2)}(\gamma^{3},d_{\rm Pot}\tilde\mu^{1})\\
+        &= -(-1)^{|\gamma^{3}|}\Phi^{(2)}(\gamma^{3}, u\partial \tilde \mu^{1}) \\
+        &= -(-1)^{|\gamma^{3}|-1}(-1)^{(|\partial\tilde\mu^{1}|-1)(|\gamma^{3}|-1)}\{\partial \tilde\mu^{1},\gamma^{3}\}_{\rm NS}\\
+        &= (-1)^{|\gamma^{3}|-1}\{\gamma^{3},\partial\tilde\mu^{1}\}_{\rm NS}
+      \end{align*}
+
+      Next consider $u^{-1}\gamma^{4}\otimes u \tilde\mu^{0}\in u^{-1}\PV^{4,\bu}\otimes u\PV^{0}$. We have that
+       \begin{align*}
+         \Phi^{(1)}([u^{-1}\gamma^{4},u\tilde \mu^{0}])-\{\Phi^{1}(u^{-1}\gamma^{4}),\Phi^{1}(\tilde u\mu^{0})\}_{\rm NS} &= \partial\{\gamma^{4}, \tilde \mu^{0}\}_{\rm NS} \\
+         &= \{\partial \gamma^{4}, \tilde\mu^{0}\}_{\rm NS}
+      \end{align*}
+
+      On the other hand, we have that
+      \begin{align*}
+        d_{\rm KS}\Phi^{(2)}(u^{-1}\gamma^{4},\tilde\mu^{0}) & -\Phi^{(2)}(d_{\rm Pot}u^{-1}\gamma^{4}, \tilde \mu^{0})-(-1)^{|u^{-1}\gamma^{4}|}\Phi^{(2)}(u^{-1}\gamma^{4},d_{\rm Pot}u\tilde\mu^{0}) \\
+        &=\Phi^{(2)}(\partial\gamma^{4},u\tilde\mu^{0})\\
+        &= -(-1)^{(|\tilde \mu^{0}|-1)(|\del\gamma^{4}|-1)}\{\tilde\mu^{0}, \partial\gamma^{4}\}_{\rm NS} \\
+        &= \{\partial \gamma^{4}, \tilde\mu^{0}\}_{\rm NS}
+      \end{align*}
+      Therefore the 2-linear condition holds.
+
+    \item Next we have a 3-linear condition; since $\Phi^{(3)} = 0$, the condition becomes \[0=\sum_{\sigma\in S_{3}} \{\Phi^{(2)}(x_{\sigma(1)}, x_{\sigma(2)}), \Phi^{(1)}(x_{\sigma (k)})\}_{\rm NS} + \sum_{\sigma \in S_{3}}\Phi^{(2)}([x_{\sigma(1)}, x_{\sigma(2)}], x_{\sigma (3)}).\]
+
+      This should vanish because of the Jacobi identity for the Schouten-Nijenhius bracket.
+
+    \item Finally we have a 4-linear condition; since $\Phi^{(3)}=\Phi^{(4)}=0$, the condition reads \[0=\sum_{\sigma\in S_{4}} \{\Phi^{(2)}(x_{\sigma(1)}, x_{\sigma (2)}), \Phi^{(2)}(x_{\sigma(3)}, x_{\sigma (4)})\}_{\rm NS}.\]
   \end{itemize}
+  \surya{signs in last two conditions? comment on why they vanish}
 \end{proof}
+
+\begin{cor}
+The $\{\Phi^{(n)}\}$ determine a map of Poisson BV theories $\cE_{pot}\to \cE_{KS}$.
+In particular it determines a map of $\PP_{0}$-factorization algebras $\Phi^{*} : \Obs_{\cE_{\rm KS}}\to \Obs_{\cE_{\rm Pot}}$.
+\end{cor}
 

### 2021-02-12 paper.tex
merge

@@
 \def\T{{\rm T}}
+\def\del{\partial}
 
@@
 Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
+Fix a rank one supercharge $Q \in S \subset \ft_{11d}$ satisfying $Q^2 = 0$. 
+We will characterize the cohomology of the algebra $\m2$ with respect to this supercharge. 
+Before doing this, let us set up some notation.
+
+Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
+As $\fsl(L ; \CC) = \fsl(5 ; \CC)$-modules the supersymmetry algebra decomposes as
+\[
+L \oplus L^* \oplus \CC_t
+\]
+and $\so(11, \CC)$ decomposes as
+\[
+\wedge^2 L \oplus \wedge^2 L^* \oplus L \oplus L^* .
+\]
+Furthermore, the spinorial representation can be identified with
+\[
+S = \wedge^\bu (L^*) = \CC \oplus L^* \oplus \wedge^2 L^* \oplus \wedge^3 L^* \oplus \wedge^4 L^* \oplus \wedge^5 L^* .
+\]
+The element $Q$ lives in the first summand.
 
@@
   \[
-    \m2^Q \simeq \fsl(5;\CC) \ltimes ???
+    \m2^Q \simeq \fsl(5;\CC) \ltimes \Pi (\wedge^2 L^* \oplus \CC\cdot c)
   \]
 \end{lem}
+\begin{proof}
+According to the $\ZZ \times \ZZ/2$ bigrading, $Q$ is degree $(0,{\rm odd})$.
+Since the differential on $\m2$ is degree $(1,{\rm even})$, the total cohomology with respect to $\d + [Q,-]$ will only be $\ZZ/2$ graded.
+
+We spell out the action of $[Q,-]$ on $S$ according to the above decompositions.
+First, note that
+\[
+[Q,-] \colon S \to L^* \oplus \CC_t
+\]
+is surjective and has $26$-dimensional kernel. 
+\end{proof}
 
@@
 \[
-  \vdash \Omega : \pv^{i,j}(X) \cong \Omega^{n-i, j}(X).
+  \vee \Omega : \pv^{i,j}(X) \cong \Omega^{n-i, j}(X).
 \]

### 2021-02-16 paper.tex
merge

@@
 
+It will be useful to introduce the notation $\PV^{k,\bu}(X)$ for the complex $\Omega^{0,\bu}(X, \wedge^k \T_X)$; this is the Dolbeault resolution of holomorphic $k$-polyvector fields. 
 Using the divergence operator, we define the double complex of sheaves
 \[
-\Omega^{0,\bu}(X, \T_X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] 
+\PV^{1,\bu}(X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] 
 \]
@@
 
-The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
+The space of differential forms on any smooth manifold $M$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(M)[-k], \d_{\dR}\right)$.
 By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
 \beqn\label{localLie}
-  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
+  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(M)
 \eeqn
-where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
 The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
-The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(L)$ by the formula
+The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(M)$ by the formula
 \[
@@
 We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
-In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.
-
-Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory'' and it is defined as follows.
-Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
+In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times M$, see Definition ?? \ref{CG2}.
+
+Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``BF-theory'' and it is defined as follows.
+Denote the local dg Lie algebra by $\cL$; it is the sheaf of sections of some $\ZZ$-graded vector bundle $L$. 
 The fields of the associated BV theory are pairs
 \[
-  (A, B) \in \cL[1] \oplus \cL^{!}[-2]
-\]
-and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
+  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
+\]
+Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
+The action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
 Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
@@
 
-For the case at hand, we consider the $BF$ theory associated to the local dg Lie algebra  $\cS(X) \otimes \Omega^\bu(L)$ defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
-Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(L)$.
+For the case at hand, we consider the BF theory associated to the local dg Lie algebra $\cL = \cS(X) \Hat{\otimes} \Omega^\bu(M)$.
+%defined on the product $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
+Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(M)$.
+We will use the holomorphic volume form $\Omega$ on $X$ to make the identification
+\begin{equation}\label{eqn:modified}
+\begin{tikzcd}
+\cL^!
+= \cS^!
+(X) \; \Hat{\otimes} \; \Omega^\bu (M) [\dim_{\RR}(M)] \ar[r, "\Omega^{-1}", "\cong"'] & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X)\right) \; \Hat{\otimes} \; \Omega^{\bu}(M)[d] .
+\end{tikzcd}
+\end{equation}
+Rather than the ``$B$'' fields of our BF theory taking values in $\cL^!$ we will take them to be valued in the target of the isomorphism above.
 
@@
   \begin{array}{ccl}
-    \mu = \mu^1+\mu^0 & \in & \left(\Omega^{0,\bu}(X, \T_X)[1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \mu = \mu^1+\mu^0 & \in & \left(\PV^{1,\bu}(X) [1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
     \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
@@
 \]
-Notice that what we called the ``$A$''-field in the general definition of $BF$ theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
-The action of this version of $BF$ theory simply reads 
-\[
-\int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
-\]
-This theory is defined on any geometry $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a one-dimensional smooth manifold.
+Notice that what we called the ``$A$''-field in the general definition of BF theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
+The action of this modified version of BF theory reads 
+\[
+\Tilde{S}_{BF} (\mu,\gamma) = \int_{X \times M} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
+\]
+This theory is defined on any geometry $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
+We have used the tilde in the notation to indicate that we have made a small re-identification of the fields of BF theory in Equation \eqref{eqn:modified}. 
 There is a deformation of this theory that we will be most concerned with.
 
-%By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
+%By force of habit, we will still refer to the theory with these particular fields as BF-theory.
 %Notice that while the definition of $\mu$  of the dimension, the field $\gamma$
@@
 
-We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $L$ is a real one-dimensional manifold.
+We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $M=L$ is a real one-dimensional manifold.
 In the notation of the last section, $d = 6$, so the field $\gamma$ takes the form
@@
 
-What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$, but a certain deformation of it.
-We consider a theory whose fields are that of the BF theory but whose action functional is of the form $S_{\rm BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
+What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \Hat{\otimes} \Omega^\bu(L)$, but a certain deformation of it.
+We consider a theory whose fields are that of the BF theory but whose action functional is of the form $\Tilde{S}_{BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
 It is defined by the following formula
@@
 
-First off, we notice an inconsistency in the cohomological degrees of the functionals $S_{\rm BF}$ and $J$.
-Being a classical action functional $S_{\rm BF}$ is, of course, ghost degree zero.
+First off, we notice an inconsistency in the cohomological degrees of the functionals $\Tilde{S}_{BF}$ and $J$.
+Being a classical action functional $\Tilde{S}_{BF}$ is, of course, ghost degree zero.
 However, we observe that $J$ is of ghost degree $+6$.
@@
 
-So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
+So, in order to make sense of the action functional $\Tilde{S}_{BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
 \[
   \begin{array}{ccl}
-    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
+    \mu = \mu^1+\mu^0 & \in & \left(\Pi \pv^{1,\bu}(X) \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
   \end{array}
 \]
-Here, we have used the following convention for $\ZZ/2$-graded complexes.
-If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.
+The $\Pi(\cdot)$ denotes parity shift. 
+%Here, we have used the following convention for $\ZZ/2$-graded complexes.
+%If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.
 
 With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
-In order for this to be true, we must see that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation
-\[
-  \{S_{\rm BF} + J , S_{\rm BF} + J\} = 0 .
-\]
-Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
+In order for this to be true, we must see that the total action functional $\Tilde{S}_{BF} + J$ satisfies the classical master equation
+\[
+  \{\Tilde{S}_{BF} + J , \Tilde{S}_{BF} + J\} = 0 .
+\]
+Of course, we know the undeformed BF-theory satisfies the classical master equation $\{\Tilde{S}_{BF}, \Tilde{S}_{BF}\} = 0$.
 Additionally, since $\gamma$ does not pair with itself under the antibracket, we also see that $\{J,J\}=0$.
-What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.
+What remains is to see that $J$ is closed for the differential $\{\Tilde{S}_{BF}, \cdot\}$.
 
 \begin{lem}
-The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
-In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
+The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{\Tilde{S}_{BF},\cdot\}$.
+In particular, $\Tilde{S}_{BF} + J$ is a well-defined classical BV action.
 \end{lem}
@@
 \begin{proof}
+Let $\cL = \cS(X) \Hat{\otimes} \Omega^\bu(L)$ be the dg Lie algebra we started with, now thought of as a $\ZZ/2$-graded dg Lie algebra. 
+Recall, that the action $\Tilde{S}_{BF}$ was defined as a modified version of BF theory for this local dg Lie algebra. 
+We first spell out how this modified version of BF theory is equivalent to the non-modified BF theory.
+
+For BF theory on $\cL$, the fields are described by the local dg Lie algebra
+\[
+\cL \ltimes \Pi \cL^!  
+\]
+whose underlying graded sheaf is $\cL \oplus \Pi \cL^!$ (notice that we have broke the usual $\ZZ$-grading to a $\ZZ/2$-grading). 
+In \eqref{eqn:modified} we have chosen to identify $\cL^!$ with a slightly different $\cL$-module, using the holomorphic volume form. 
+However, the map 
+\[
+\Pi \cL^!  \xto{\Omega^{-1}} \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+\]
+is {\em not} a map of $\cL$-modules.
+
+There is, however, an $L_\infty$-map $\Phi$ of $\cL$-modules whose linear part is the map $\Phi^{(1)} = \Omega^{-1}$ above. 
+There is a higher order map of the form
+\[
+\Phi^{(2)} \colon \cL \otimes \Pi \cL^! \to \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+\]
+defined as follows. 
+Recall that 
+\[ 
+\Pi \cL^! = \left(\Omega^{5, \bu}(X) \xto{\partial_\Omega^!} \Pi \Omega^{5,\bu} (X, \T^*_X) \right) \; \Hat{\otimes} \; \Omega^\bu(L) 
+\]
+where $\partial_\Omega^!$ sends $f \Omega$ to $(\partial f) \otimes \Omega$. 
+The $\cL$-module structure is the one by which $\PV^{1,\bu}(X)$ acts by Lie derivative everywhere. 
+Denote by $b^0 \Omega + b^1 \Omega$ the fields in the decomposition above.
+
+The $L_\infty$ $\cL$-module map $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is defined by
+\begin{align*}
+\Phi^{(1)} (b^0 \Omega + b^1 \Omega) & = b^0 + b^1 \in \Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X) \\
+\Phi^{(2)} (\mu^0 \otimes (b^0\Omega + b^1\Omega)) & = \mu^0 b^0 + \mu^0 b^1 \in \Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X) .
+\end{align*}
+Let us sketch why this is an $L_\infty$ $\cL$-module map.
+Suppose $\mu^1 \in \PV^{1,\bu}(X) \Hat{\otimes} \Omega^\bu(L)$.
+Then $\mu^1$ acts on $\Pi \cL^!$ by
+\begin{align*}
+\mu^1 \cdot (b^0 \Omega + b^1 \Omega) & = L_{\mu^1} (b^0 \Omega) + L_{\mu^1} (b^1 \Omega) \\ & = (L_{\mu^1} b^0 + L_{\mu^1} b^1) \Omega + (b^0 + b^1) L_{\mu^1} \Omega .
+\end{align*}
+So, 
+\[
+\Phi^{(1)} (\mu^1 \cdot (b^0 \Omega + b^1 \Omega)) - \mu^1 \cdot \Phi^{(1)} (b^0 \Omega + b^1 \Omega) = (b^0 + b^1) L_{\mu^1} \Omega .
+\]
+The right-hand side is precisely
+\[
+\Phi^{(2)} ((\partial_\Omega \mu^1) \otimes (b^0 \Omega + b^1 \Omega))
+\]
+showing that $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is an $L_\infty$ module map.
+
+Now, $\Phi$ determines an equivalence of BV theories 
+\[
+\Phi \colon (\cL \ltimes \cL^! [-3]) \xto{\simeq} \cL \ltimes \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+\]
+where on the left-hand side appears the local Lie algebra underlying BF theory for $\cL$ and the right-hand side appears the local Lie algebra of our modified BF theory, whose action functional we have denoted $\Tilde{S}_{BF}$.
+
+Now, consider the functional $J$ which is a local functional on the local Lie algebra describing modified BF theory. 
+One computes the restriction of $J$ along $\Phi$ as
+\[
+(\Phi^* J) (\mu^0 + \mu^1 , b^0 \Omega + b^1 \Omega) = \frac16 \int_{X \times L} b^1 \partial b^1 \partial b^1 + \frac16 \int \mu^0 b^1 \partial b^1 \partial b^1 .
+\]
+
 It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
@@
   We have actually shown something slightly stronger here.
-  Namely, for any constant $c$ the functional $S_{\rm BF} + c J$ satisfies the classical master equation.
+  Namely, for any constant $c$ the functional $\Tilde{S}_{BF} + c J$ satisfies the classical master equation.
   This dependence on a coupling constant will be important later on in this paper.
@@
 %\begin{equation}\label{11daction}
-%  S_{\rm BF} + J
+%  \Tilde{S}_{BF} + J
 %\end{equation}
-%where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
+%where $J$ is as in the definition above and $\Tilde{S}_{BF}$ is the action functional for the underlying BF theory which takes the form
 %\[
-%  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
+%  \Tilde{S}_{BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
 %\]
-%We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.
+%We will furthermore decompose $\Tilde{S}_{BF} = S_{\rm free}+I_{BF}$ into its free and interacting pieces.
 
@@
 That is, this deformation is $(m+1)$-linear and contains $m$ holomorphic derivatives.
-As in the $m=2$ ($X$ is a five-fold) case that we discussed above, we see that $J_m$ is closed for the differential $\{S_{\rm BF},\cdot\}$ defining the BF theory.
+As in the $m=2$ ($X$ is a five-fold) case that we discussed above, we see that $J_m$ is closed for the differential $\{\Tilde{S}_{BF},\cdot\}$ defining the BF theory.
 
 \begin{lem}
-  The functional $J_m$ is closed for the differential $\{S_{\rm BF}, \cdot \}$.
+  The functional $J_m$ is closed for the differential $\{\Tilde{S}_{BF}, \cdot \}$.
 \end{lem}
@@
 A simple count reveals that the ghost degree of the functional $J_m$ is $2m^2 - 2$.
-In particular, when $m \ne 1$, the above lemma implies that the action functional $S_{\rm BF} + J_m$ only defines a $\ZZ/2$-graded classical BV theory.
+In particular, when $m \ne 1$, the above lemma implies that the action functional $\Tilde{S}_{BF} + J_m$ only defines a $\ZZ/2$-graded classical BV theory.
 
@@
 
-When $m=1$, hence $X$ is a CY three-fold, the action $S_{\rm BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
+When $m=1$, hence $X$ is a CY three-fold, the action $\Tilde{S}_{BF} + J_1$ actually defines a $\ZZ$-graded BV theory.
 Another feature of the case $m=1$ is that the deformed theory is actually a {\em topological} field theory.
@@
 \]
-Let us write the theory as $S_{\rm BF} + c J_1$ where $c$ is a constant.
+Let us write the theory as $\Tilde{S}_{BF} + c J_1$ where $c$ is a constant.
 We denote by $\cT_c [X \times L]$ the resulting BV theory which depends on this coupling constant.
@@
 \[
-  \int_{X \times L} \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int_{X \times L} \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega + \frac{c}{3} \int_{X \times L} \gamma \partial \gamma \partial \gamma .
+  \int_{X \times L} \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int_{X \times L} \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega + \frac{c}{3!} \int_{X \times L} \gamma \partial \gamma \partial \gamma .
 \]

### 2021-02-17 paper.tex
overhaul section 1

--- 2021-02-12 paper.tex
@@
 
-One of the fundamental geometric objects will be the sheaf of divergence-free holomorphic vector fields on $X$. 
+Let $V$ be a holomorphic vector bundle. 
+If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
+The $\dbar$ operator for $V$ is of the form $\dbar : \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$.
+This operator is used to define the Dolbeault complex of $V$
+\[
+  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right)
+\]
+which is a free resolution for the sheaf of holomorphic sections of $V$.
+Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
+
+Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
+The holomorphic divergence operator extends to the Dolbeault complex to take the form
+\[
+  \partial_\Omega : \PV^{1,\bu}(X) \to \PV^{0,\bu}(X)
+\]
+and is defined by the formula
+\[
+  \partial_\Omega (\mu) \wedge \Omega = L_\mu (\Omega)
+\]
+where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
+
+\begin{dfn} \label{dfn:classical}
+Let $X$ be a Calabi--Yau five-fold and $L$ a smooth one-dimensional manifold.
+{\em Eleven-dimensional twisted supergravity} on $X \times L$ is the $\ZZ/2$-graded BV theory on $X$ whose fields are pairs
+\begin{align*}
+\mu & \in \bigg(\Pi \PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+\gamma & \in \bigg(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu} (X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) 
+\end{align*}
+The BV pairing is $\int (\gamma \vee \mu) \wedge \Omega$ and the BV action is
+\begin{equation}\label{eqn:bvaction}
+S = \int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu\right) \right] \wedge \Omega +  \frac12 \int_{X \times L} \left(\gamma \vee [\mu, \mu] \right) \wedge \Omega  + \frac16 \int_{X \times L} (1+\mu) \gamma \partial \gamma \partial \gamma .
+\end{equation}
+\end{dfn}
+
+\begin{prop} \label{prop:cme}
+The action functional $S$ satisfies the classical master equation~
+\[
+\{S, S\}=0.
+\] 
+\end{prop}
+
+\subsubsection{Divergence-free vector fields}
+
+Suppose that $X$ is a Calabi--Yau manifold of any dimension. 
+One of the fundamental geometric objects in this paper will be the sheaf of divergence-free holomorphic vector fields on $X$. 
 We will utilize a convenient semi-free resolution of this sheaf in the category of $C^\infty$-modules.
-
-If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of Dolbeault forms of type $j$ on with values in $V$.
-The $\dbar$ operator for $V$ is of the form $\dbar : \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$.
-This operator defines the Dolbeault complex of $V$
-\[
-  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right)
-\]
-which is a free resolution for the sheaf of holomorphic sections of $V$.
-Applying this to the holomorphic tangent bundle $V = \T_X$, we obtain a resolution of the sheaf of holomorphic vector fields.
 
@@
 
-Now, suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
-The holomorphic divergence operator extends to the Dolbeault complex to take the form
-\[
-  \partial_\Omega : \Omega^{0,\bu}(X, \T_X) \to \Omega^{0,\bu}(X)
-\]
-and is defined by the formula
-\[
-  \partial_\Omega (\mu) \wedge \Omega = L_\mu (\Omega)
-\]
-where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
-
 Using the divergence operator, we define the double complex of sheaves
-\[
-\Omega^{0,\bu}(X, \T_X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] 
-\]
+\begin{equation}\label{eqn:div}
+\PV^{1,\bu}(X) \xto{\partial_\Omega} \PV^{0,\bu}(X) [-1] 
+\end{equation}
 where the horizontal differential is the divergence operator and the vertical differential is the $\dbar$ operator (which we have left implicit). 
-We denote the totalization of this double complex of sheaves $\cS$.
-
-It is immediate to check that $\cS$ provides a free resolution of the sheaf of holomorphic divergence-free vector fields on $X$.
-Furthermore, there is a natural Lie bracket on $\cS$ given by the Schouten--Nijenhous bracket $\{-,-\}_{\rm NS}$ which is compatible with the usual Lie bracket of holomorphic vector fields. 
-In other words, $\cS$ is a sheaf of dg Lie algebras and the inclusion of holomorphic divergence-free vector fields is a quasi-isomorphism of sheaves of Lie algebras.
+%We denote the totalization of this double complex of sheaves $\cS$.
+
+It is immediate to check that the totalization of this double complex provides a free resolution of the sheaf of holomorphic divergence-free vector fields on $X$.
+Furthermore, there is a natural Lie bracket on this complex given by the Schouten--Nijenhuis bracket $\{-,-\}_{\rm NS}$ which is compatible with the usual Lie bracket of holomorphic vector fields. 
+In other words, the complex is a sheaf of dg Lie algebras and the inclusion of holomorphic divergence-free vector fields is a quasi-isomorphism of sheaves of Lie algebras.
 
@@
 
-The space of differential forms on any smooth manifold $L$ is a commutative dg algebra $\Omega^{\bu}(L) = \left(\oplus_{k}\Omega^{k}(L)[-k], \d_{\dR}\right)$.
-By taking the tensor product with the dg Lie algebra $\cS(X)$ we obtain the dg Lie algebra
+The space of differential forms on any smooth manifold $M$ is a commutative dg algebra $\Omega^{\bu}(M) = \left(\oplus_{k}\Omega^{k}(M)[-k], \d_{\dR}\right)$.
+By taking the tensor product with the dg Lie algebra \eqref{eqn:div} we obtain the dg Lie algebra
 \beqn\label{localLie}
-  \cS(X) \; \Hat{\otimes} \; \Omega^{\bu}(L)
+  \cS \define \left(\PV^{1,\bu}(X) \xto{\partial_\Omega} \Omega^{0,\bu}(X) [-1] \right) \; \Hat{\otimes} \; \Omega^{\bu}(M) 
 \eeqn
-where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
+where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
+According to the direct sum decomposition, we will write sections of $\cS$ as $\mu^1 +\mu^0$. 
 The differential in this dg Lie algebra is of the form $\dbar \otimes 1 + \partial_\Omega \otimes 1 + 1 \otimes \d_{\rm dR}$, which we will abbreviate by $\dbar + \partial_\Omega + \d_{\rm dR}$.
-The bracket is defined using the bracket on $\cS(X)$ together with the wedge product of forms on $\Omega^\bu(L)$ by the formula
+The bracket is defined using the bracket $\{\cdot,\cdot\}_{\rm NS}$ of polyvector fields together with the wedge product of forms on $\Omega^\bu(M)$ by the formula
 \[
@@
 We remark that the structure maps of this Lie algebra, namely the differential and bracket, are given by differential and bidifferential operators, respectively.
-In this sense, it fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times L$, see Definition ?? \ref{CG2}.
-
-Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as ``$BF$-theory'' and it is defined as follows.
-Denote the sheaf of sections of the local dg Lie algebra by $\cL$.
-The fields of the associated BV theory are pairs
-\[
-  (A, B) \in \cL[1] \oplus \cL^{!}[-2]
-\]
-and the action functional reads $\int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
-Here $\d_{\cL}$ denotes the differential on $\cL$ and $[\cdot,\cdot]$ is the Lie bracket.
-Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cL A + \frac12 [A,A] = 0$.
-For the $B$-field the equations of motion read $\d_\cL B + [A, B] = 0$.
-
-For the case at hand, we consider the $BF$ theory associated to the local dg Lie algebra  $\cS(X) \otimes \Omega^\bu(L)$ defined on the product $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a smooth manifold.
-Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(L)$.
-
-The fields decompose as
-\[
-(\mu, \gamma) = (\mu^1 + \mu^0, \gamma^0 + \gamma^1)
-\]
-where
-\[
-  \begin{array}{ccl}
-    \mu = \mu^1+\mu^0 & \in & \left(\Omega^{0,\bu}(X, \T_X)[1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
-  \end{array}
-\]
-Notice that what we called the ``$A$''-field in the general definition of $BF$ theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
-The action of this version of $BF$ theory simply reads 
-\[
-\int_{X \times L} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
-\]
-This theory is defined on any geometry $X \times L$ where $X$ is a Calabi--Yau manifold and $L$ is a one-dimensional smooth manifold.
-There is a deformation of this theory that we will be most concerned with.
-
-%By force of habit, we will still refer to the theory with these particular fields as $BF$-theory.
+In this sense, $\cS$ fits the definition of a {\em local dg Lie algebra} on the product manifold $X \times M$, see Definition \cite[??]{CG2}.
+
+\begin{lem}
+A (perturbative) classical field theory in the BV formalism consists of two pieces of data:
+\begin{itemize}
+\item A local dg Lie algebra $(\cL, \d, [\cdot, \cdot])$, where $\cL$ is the sheaf of sections of a $\ZZ$-graded vector bundle $L$.
+\item An $\cL$-invariant fiberwise non-degenerate map of vector bundles of degree $(-3)$:
+\[
+\< \cdot , \cdot \> \colon L \otimes L \to {\rm Dens} [-3] 
+\]
+where ${\rm Dens}$ is the bundle of densities. 
+\end{itemize}
+\end{lem}
+
+Using the pairing, one reads of the BV action of the theory as
+\[
+S(\phi) = \frac12 \int \<\phi, \d \phi\> + \frac16 \int \<\phi, [\phi,\phi]\> 
+\]
+where $\phi \in \cL[1]$. 
+The $\cL$-invariance of the pairing together with the Jacobi identity for the dg Lie algebra $\cL$ implies that $S$ automatically satisfies the classical master equation $\{S,S\} = 0$. 
+To prove Proposition \ref{prop:cme} we will exhibit the theory in Definition \ref{dfn:classical} in terms of a local dg Lie algebra.
+
+This local dg Lie algebra is built from the local dg Lie algebra $\cS$ together with a certain module. 
+Denote by $d \in \ZZ$ the sum $\dim_{\CC}(X) + \dim_{\RR}(M)$.
+Define the following sheaf of cochain complexes
+\[
+\cM \define \left(\Omega^{0,\bu} (X)[1] \xto{\partial} \Omega^{1,\bu} (X) \right) \; \Hat{\otimes} \; \Omega^\bu(M)[d]  . 
+\]
+The reason for the cohomological shifts will be apparent momentarily. 
+According the direct sum decomposition, we will write sections of $\cM$ as $\gamma^0 + \gamma^1$.
+
+The sheaf $\cM$ has the structure of a module over $\cS$, defined by Lie derivative:
+\begin{align*}
+[\mu^1, \gamma^0 + \gamma^1] \define L_{\mu^1} (\gamma^0) + L_{\mu^1} (\gamma^1) .
+\end{align*}
+Strictly speaking, the Lie derivative uses just the component of $\mu^1$ and $\gamma^i$ along $X$.
+Along the manifold $M$ we simply take the wedge product of forms.
+
+We now form the semi-direct product dg Lie algebra
+\begin{equation}\label{eqn:dglie}
+\cS \ltimes \cM^! [-3] .
+\end{equation}
+Recall, that we are decomposing the sections as $(\mu , \gamma) = (\mu^1 + \mu^0 , \gamma^0 + \gamma^1)$. 
+One immediately verifies that this semi-direct product has the structure of a local dg Lie algebra.
+Additionally, there is a non-degenerate pairing defined using the holomorphic volume form $\Omega$ on $X$ by the formula
+\[
+(\mu^1 + \mu^0 , \gamma^0 + \gamma^1) = \int_{X \times M} (\mu^1 \vee \gamma^1)\wedge \Omega + \int_{X \times M} (\mu^0 \gamma^0) \Omega
+\]
+which one can readily check is graded antisymmetric of degree $(-3)$ due to our cohomological shifts in the definition of $\cM$.
+
+The associated BV action functional is of the form
+\begin{equation}\label{eqn:modbfaction}
+S_{0} (\mu,\gamma) = \int_{X \times M} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu\right) \right] \wedge \Omega +  \frac12 \int_{X \times M} \left(\gamma \vee [\mu, \mu] \right) \wedge \Omega .
+\end{equation}
+The fact that this BV action functional satisfies the classical master equation 
+\[
+\{S_0, S_0\} = 0 .
+\]
+follows automatically from the axioms of the dg Lie algebra structure on \eqref{eqn:dglie}.
+
+The action $S_0$ is not the same as the action in Definition \ref{dfn:classical}--they differ by the last term in Equation \eqref{eqn:bvaction}. 
+Before moving on to this term, we mention a relationship of the BV theory described by $S_0$ to ``BF'' theory.
+%defined on the product $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
+
+%The fields decompose as
+%\[
+%(\mu, \gamma) = (\mu^1 + \mu^0, \gamma^0 + \gamma^1)
+%\]
+%where
+%\[
+%  \begin{array}{ccl}
+%    \mu = \mu^1+\mu^0 & \in & \left(\PV^{1,\bu}(X) [1] \oplus \Omega^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+%    \gamma = \gamma^0 + \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[-1] \oplus \Omega^{1,\bu}(X)[-2] \right) \; \Hat{\otimes}\; \Omega^{\bu}(L)[d] .
+%  \end{array}
+%\]
+%Notice that what we called the ``$A$''-field in the general definition of BF theory we are now calling $\mu$ and what we called the ``$B$''-field we are now calling $\gamma$.
+%The action of this modified version of BF theory reads 
+%\[
+%\Tilde{S}_{BF} (\mu,\gamma) = \int_{X \times M} \left[\gamma \vee \left(\dbar \mu + \partial_\Omega \mu + \d_{\dR} \mu + \frac12 [\mu, \mu] \right) \right] \wedge \Omega .
+%\]
+%This theory is defined on any geometry $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold.
+%We have used the tilde in the notation to indicate that we have made a small re-identification of the fields of BF theory in Equation \eqref{eqn:modified}. 
+%There is a deformation of this theory that we will be most concerned with.
+
+%By force of habit, we will still refer to the theory with these particular fields as BF-theory.
 %Notice that while the definition of $\mu$  of the dimension, the field $\gamma$
@@
 
+\subsubsection{Relationship to ``BF'' theory}
+
+Associated to any local dg Lie algebra is a classical field theory in the BV formalism that one refers to as BF-theory and it is defined as follows.
+Denote the local dg Lie algebra by $\cA$, it is the sheaf of sections of some $\ZZ$-graded vector bundle $A$. 
+The fields of the associated BV theory are pairs
+\[
+  (A, B) \in \cA[1] \oplus \cA^{!}[-2] .
+\]
+Here $\cA^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
+The action functional reads $S_{\rm BF} = \int B F_{A} = \int B (\d_{\cL}A + \frac12 [A,A])$.
+In terms of the local Lie algebra description, the action is completely determined by the dg Lie algebra structure on $\cA \ltimes \cA^![-3]$. 
+Here $\d_{\cA}$ denotes the differential on $\cA$ and $[\cdot,\cdot]$ is the Lie bracket.
+Notice that the equations of motion for the $A$-field is simply the Maurer--Cartan equation $\d_\cA A + \frac12 [A,A] = 0$.
+For the $B$-field the equations of motion read $\d_\cA B + [A, B] = 0$.
+
+The theory described in the previous section is closely related to BF theory for the local Lie algebra $\cA = \cS$. 
+Indeed, using the holomorphic volume form, one has an isomorphism of sheaves of cochain complexes
+\begin{equation}\label{eqn:modified}
+\Omega \colon \cM \xto{\cong} \cS^! .
+\end{equation}
+So, at the level of fields, $\Omega$ determines an isomorphism of cochain complexes
+\begin{equation}\label{eqn:omega}
+\Omega \colon \cS \oplus \cM [-3] \xto{\cong} \cS \oplus \cS^![-3]  .
+\end{equation}
+On the left-hand side is the underlying space of fields of the theory defined in the last section \eqref{eqn:modified}, and on the right-hand side is the underlying space of fields of BF theory for $\cA = \cS$.
+However, this identification is {\em not} a map of local dg Lie algebras.
+
+Nevertheless, the BV theory described by $\cS \ltimes \cM [-3]$ and BF theory are equivalent. 
+The point is that there is an $L_\infty$ morphism between the two underlying local dg Lie algebras, whose linear component agrees with the map \eqref{eqn:omega}.
+
+\begin{prop}
+There is an $L_\infty$ map of local Lie algebras
+\[
+\Phi \colon \cS \ltimes \cM[-3] \to \cS \ltimes \cS^! [-3]
+\]
+whose linear term $\Phi^{(1)}$ is an isomorphism of cochain complexes that preserves the local pairings.
+In particular, the BV theory described by the action functional $S_0$ in \eqref{eqn:modbfaction} and BF theory for the local Lie algebra $\cS$ are equivalent. 
+\end{prop}
+
+\begin{proof} 
+The $L_\infty$ map is the identity on $\cS$ and so arrises from a map of $\cS$-modules 
+\[
+\Phi \colon \cM [-3] \to \cS^![-3]
+\]
+that we denote by the same symbol.
+
+One has
+\[ 
+\cS^! [-3] = \left(\Omega^{5, \bu}(X) \xto{\partial_\Omega^!} \Pi \Omega^{5,\bu} (X, \T^*_X) \right) \; \Hat{\otimes} \; \Omega^\bu(M) 
+\]
+\brian{fix shifts}
+where $\partial_\Omega^!$ sends $f \Omega$ to $(\partial f) \otimes \Omega$ (and is the identity on $\Omega^\bu(M))$. 
+The $\cS$-module structure is the one by which $\PV^{1,\bu}(X)$ acts by Lie derivative everywhere. 
+Denote by $b^0 \Omega + b^1 \Omega$ the fields in the decomposition of $\cS^!$ above.
+
+The $L_\infty$ $\cL$-module map $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is defined by
+\begin{align*}
+\Phi^{(1)} (\gamma^0 + \gamma^1) & = \gamma^0 \Omega + \gamma^1 \Omega \in \Omega^{5,\bu}(X) \oplus \Pi \Omega^{5,\bu}(X, \T^*_X) \\
+\Phi^{(2)} (\mu^0 \otimes (\gamma^0 + \gamma^1)) & = \mu^0 \gamma^0 \Omega + \mu^0 \gamma^1 \in \Omega^{5,\bu}(X) \oplus \Pi \Omega^{5,\bu}(X, \T^*) .
+\end{align*}
+Let us sketch an argument that this is an $L_\infty$ $\cS$-module map.
+Suppose $\mu^1 \in \PV^{1,\bu}(X) \Hat{\otimes} \Omega^\bu(M)$.
+Then $\mu^1$ acts on $\cM$ by Lie derivative
+\[
+\mu^1 \cdot (\gamma^0 + \gamma^1) = L_{\mu^1} (\gamma^0) + L_{\mu^1} (\gamma^1) .
+\]
+So, 
+\[
+\Phi^{(1)} (\mu^1 \cdot (\gamma^0 + \gamma^1)) - \mu^1 \cdot \Phi^{(1)} (\gamma^0 + \gamma^1) = (\gamma^0 + \gamma^1) L_{\mu^1} \Omega .
+\]
+The right-hand side is precisely
+\[
+\Phi^{(2)} ((\partial_\Omega \mu^1) \otimes (\gamma^0 + \gamma^1))
+\]
+which implies that $\Phi = \Phi^{(1)} + \Phi^{(2)}$ is an $L_\infty$ module map.
+
+%Now, $\Phi$ determines an equivalence of BV theories 
+%\[
+%\Phi \colon (\cL \ltimes \cL^! [-3]) \xto{\simeq} \cL \ltimes \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+%\]
+%where on the left-hand side appears the local Lie algebra underlying BF theory for $\cL$ and the right-hand side appears the local Lie algebra of our modified BF theory, whose action functional we have denoted $\Tilde{S}_{BF}$.
+
+%For BF theory on $\cL$, the fields are described by the local dg Lie algebra
+%\[
+%\cL \ltimes \Pi \cL^!  
+%\]
+%whose underlying graded sheaf is $\cL \oplus \Pi \cL^!$ (notice that we have broke the usual $\ZZ$-grading to a $\ZZ/2$-grading). 
+%In \eqref{eqn:modified} we have chosen to identify $\cL^!$ with a slightly different $\cL$-module, using the holomorphic volume form. 
+%However, the map 
+%\[
+%\Pi \cL^!  \xto{\Omega^{-1}} \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+%\]
+%is {\em not} a map of $\cL$-modules. 
+%
+%There is, however, an $L_\infty$-map $\Phi$ of $\cL$-modules whose linear part is the map $\Phi^{(1)} = \Omega^{-1}$ above. 
+%There is a higher order map of the form
+%\[
+%\Phi^{(2)} \colon \cL \otimes \Pi \cL^! \to \left(\Omega^{0,\bu}(X) \oplus \Pi \Omega^{1,\bu}(X)\right)
+%\]
+%defined as follows. 
+%
+%
+%
+%Now, consider the functional $J$ which is a local functional on the local Lie algebra describing modified BF theory. 
+%One computes the restriction of $J$ along $\Phi$ as
+%\[
+%(\Phi^* J) (\mu^0 + \mu^1 , b^0 \Omega + b^1 \Omega) = \frac16 \int_{X \times L} b^1 \partial b^1 \partial b^1 + \frac16 \int_{X \times L} \mu^0 b^1 \partial b^1 \partial b^1 .
+%\]
+%
+%
+%It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
+%It remains to see that\brian{finish}
+\end{proof}
+
 \subsubsection{Chern--Simons deformation}
-The theory we have just described admits a deformation by a higher Chern--Simons term.
-We explain how this relates to the familiar Chern--Simons term in eleven-dimensional supergravity in Section \ref{sec:evidence}.
-
-We will be mostly interested in the case that $X$ is a Calabi--Yau five-fold and $L$ is a real one-dimensional manifold.
-In the notation of the last section, $d = 6$, so the field $\gamma$ takes the form
-\[
-  \gamma \in \left(\Omega^{0,\bu}(X)[6] \oplus \Omega^{1,\bu}(X)[5] \right) \otimes \Omega^\bu(L).
-\]
-
-What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \otimes \Omega^\bu(L)$, but a certain deformation of it.
-We consider a theory whose fields are that of the BF theory but whose action functional is of the form $S_{\rm BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
-It is defined by the following formula
-\[
-J(\gamma) = \frac16 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
-\]
-
-First off, we notice an inconsistency in the cohomological degrees of the functionals $S_{\rm BF}$ and $J$.
-Being a classical action functional $S_{\rm BF}$ is, of course, ghost degree zero.
-However, we observe that $J$ is of ghost degree $+6$.
-In order to make sense of the deformed theory, therefore, we must consider the space of fields as a $\ZZ/2$-graded object rather than a $\ZZ$-graded one.
-
-So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
+We return back to the theory described by the action functional $S_0$ in \eqref{eqn:modbfaction}. 
+We will show that this action admits a deformation which puts it precisely in the form of the action in Definition \ref{dfn:classical}.
+We explain how this deformation relates to the familiar Chern--Simons term in eleven-dimensional supergravity in Section \ref{sec:evidence}.
+
+As we defined it, $S_0$ is an action that makes sense on $X \times M$ where $X$ is a Calabi--Yau manifold and $M$ is a smooth manifold, both of arbitrary dimension. 
+We are mostly interested in the case that $X$ is a Calabi--Yau five-fold and $M=L$ is a real one-dimensional manifold.
+Also, for the deformed action to make sense, we must break the $\ZZ$-grading on the fields described by $S_0$ to a $\ZZ/2$-grading. 
+Thus, as a $\ZZ/2$-graded space of fields we have 
 \[
   \begin{array}{ccl}
-    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
-    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
+    \mu = \mu^1+\mu^0 & \in & \left(\Pi \pv^{1,\bu}(X) \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
+    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
   \end{array}
 \]
-Here, we have used the following convention for $\ZZ/2$-graded complexes.
-If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.
-
-With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
-In order for this to be true, we must see that the total action functional $S_{\rm BF} + J$ satisfies the classical master equation
-\[
-  \{S_{\rm BF} + J , S_{\rm BF} + J\} = 0 .
-\]
-Of course, we know the undeformed BF-theory satisfies the classical master equation $\{S_{\rm BF}, S_{\rm BF}\} = 0$.
-Additionally, since $\gamma$ does not pair with itself under the antibracket, we also see that $\{J,J\}=0$.
-What remains is to see that $J$ is closed for the differential $\{S_{\rm BF}, \cdot\}$.
-
-\begin{lem}
-The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{S_{\rm BF},\cdot\}$.
-In particular, $S_{\rm BF} + J$ is a well-defined classical BV action.
-\end{lem}
-
-\begin{proof}
-It is clear that $J$ is closed for the part of the differential arising from the kinetic term $\{S_{\rm free},\cdot\}$.
-It remains to see that\brian{finish}
-\end{proof}
-
-\begin{rmk}
-  We have actually shown something slightly stronger here.
-  Namely, for any constant $c$ the functional $S_{\rm BF} + c J$ satisfies the classical master equation.
-  This dependence on a coupling constant will be important later on in this paper.
-\end{rmk}
-
-\begin{dfn}\label{dfn:11dtheory}
-Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
-Define the $\ZZ/2$-graded BV theory $\cT_{X \times L}$ (or simply just $\cT$) on
-\[
-  X \times L
-\]
-to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac16 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
-\end{dfn}
+The $\Pi(\cdot)$ denotes the $\ZZ/2$ parity shift.
+
+The action $S_0$ describes the local dg Lie algebra structure on $\cS \ltimes \cM[-3]$ with differential $\dbar + \partial + \d_{dR}$ and brackets
+\begin{align*}
+[\mu_1, \mu_2] & = \{\mu_1, \mu_2\}_{\rm NS} \\
+[\mu^1, \gamma] & = L_{\mu^1} \gamma .
+\end{align*}
+
+Consider the following deformation of $S_0$ by the functional 
+\[
+J = \frac16 \int_{X \times L} (1 + \mu) \gamma \partial \gamma \partial \gamma .
+\]
+This has the affect of deforming the dg Lie structure to the $L_\infty$ structure described by the same differential and the following $2$-ary $[\cdot, \cdot]$ and $3$-ary operations $[\cdot, \cdot, \cdot]_3$ described by
+%\[
+%\begin{array}{cccccc}
+%[\mu_1, \mu_2] & = & \{\mu_1, \mu_2\}_{\rm NS} \\ 
+%[\mu^1, \gamma] & = & L_{\mu^1} \gamma \\
+%\]
+
+\[
+\begin{array}{rllllll}
+[\mu_1, \mu_2] & = & \{\mu_1, \mu_2\}_{\rm NS} \\
+{[\mu, \gamma]} & = &  L_{\mu^1} \gamma \\
+{[\gamma^1_1, \gamma^1_2]} & = & \Omega \vee \left(\gamma^1_1 \partial \gamma^1_2 \pm \gamma^1_2 \partial \gamma^1_1\right) & \in & \PV^{1,\bu}(X) \,\Hat{\otimes} \, \Omega^\bu(L) . \\
+{[\gamma^1_1, \gamma^1_2 , \mu^0]}_3 & = & \mu^0 \Omega \vee \left(\gamma^1_1 \partial \gamma^1_2 \pm \gamma^1_2 \partial \gamma^1_1\right) & \in & \PV^{1,\bu}(X) \, \Hat{\otimes} \, \Omega^\bu(L) \\
+{[\gamma^1_1, \gamma^1_2 , \gamma_3^1]}_3 & = & \Omega \vee (\gamma_1^1 \partial \gamma_2^1 \partial \gamma^1_3) & \in & \Omega^{0,\bu}(X) \, \Hat{\otimes} \,\Omega^\bu(L) .
+
+\end{array}
+\]
+
+%In the notation of the last section, $d = 6$, so the field $\gamma$ takes the form
+%\[
+%  \gamma \in \left(\Omega^{0,\bu}(X)[6] \oplus \Omega^{1,\bu}(X)[5] \right) \otimes \Omega^\bu(L).
+%\]
+%
+%What is important for us is not simply BF theory for the dg Lie algebra $\cS(X) \Hat{\otimes} \Omega^\bu(L)$, but a certain deformation of it.
+%We consider a theory whose fields are that of the BF theory but whose action functional is of the form $\Tilde{S}_{BF} + J$, where $J$ is a local functional that purely depends on the fields $\gamma$.
+%It is defined by the following formula
+%\[
+%J(\gamma) = \frac16 \int_{X\times L} \gamma \partial \gamma \partial \gamma .
+%\]
+%
+%First off, we notice an inconsistency in the cohomological degrees of the functionals $\Tilde{S}_{BF}$ and $J$.
+%Being a classical action functional $\Tilde{S}_{BF}$ is, of course, ghost degree zero.
+%However, we observe that $J$ is of ghost degree $+6$.
+%In order to make sense of the deformed theory, therefore, we must consider the space of fields as a $\ZZ/2$-graded object rather than a $\ZZ$-graded one.
+%
+%
+%%Here, we have used the following convention for $\ZZ/2$-graded complexes.
+%%If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.
+%
+%With the issue of gradings out of the way, we turn to the question of whether this is a well-defined classical BV theory.
+%In order for this to be true, we must see that the total action functional $\Tilde{S}_{BF} + J$ satisfies the classical master equation
+%\[
+%  \{\Tilde{S}_{BF} + J , \Tilde{S}_{BF} + J\} = 0 .
+%\]
+%Of course, we know the undeformed BF-theory satisfies the classical master equation $\{\Tilde{S}_{BF}, \Tilde{S}_{BF}\} = 0$.
+%Additionally, since $\gamma$ does not pair with itself under the antibracket, we also see that $\{J,J\}=0$.
+%What remains is to see that $J$ is closed for the differential $\{\Tilde{S}_{BF}, \cdot\}$.
+%
+%\begin{lem}
+%The functional $J = \frac16\int \gamma \partial \gamma \partial \gamma$ is closed for the differential $\{\Tilde{S}_{BF},\cdot\}$.
+%In particular, $\Tilde{S}_{BF} + J$ is a well-defined classical BV action.
+%\end{lem}
+%
+%
+%
+%\begin{rmk}
+%  We have actually shown something slightly stronger here.
+%  Namely, for any constant $c$ the functional $\Tilde{S}_{BF} + c J$ satisfies the classical master equation.
+%  This dependence on a coupling constant will be important later on in this paper.
+%\end{rmk}
+%
+%\begin{dfn}\label{dfn:11dtheory}
+%Let $X$ be a Calabi--Yau five-fold and $L$ a one-dimensional smooth manifold.
+%Define the $\ZZ/2$-graded BV theory $\cT_{X \times L}$ (or simply just $\cT$) on
+%\[
+%  X \times L
+%\]
+%to be the deformation of BF theory for the $\ZZ/2$-graded local Lie algebra $\cS(X) \Hat{\otimes} \Omega^{\bu}(L)$ by the local functional $J (\gamma) = \frac16 \int_{X \times L} \gamma \partial \gamma \partial \gamma.$
+%\end{dfn}
 
@@
 %\begin{equation}\label{11daction}
-%  S_{\rm BF} + J
+%  \Tilde{S}_{BF} + J
 %\end{equation}
-%where $J$ is as in the definition above and $S_{BF}$ is the action functional for the underlying BF theory which takes the form
-%\[
-%  S_{\rm BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
-%\]
-%We will furthermore decompose $S_{\rm BF} = S_{\rm free}+I_{\rm BF}$ into its free and interacting pieces.
+%where $J$ is as in the definition above and $\Tilde{S}_{BF}$ is the action functional for the underlying BF theory which takes the form
+%\[
+%  \Tilde{S}_{BF} = \int \gamma \vdash \left(\dbar + \d_{\rm dR} + \partial_{\Omega}\right) \mu \wedge \Omega + \frac12 \int \gamma \vdash \{\mu,\mu\}_{\rm NS} \wedge \Omega .
+%\]
+%We will furthermore decompose $\Tilde{S}_{BF} = S_{\rm free}+I_{BF}$ into its free and interacting pieces.
 

### 2021-03-01 4dks.tex
scratch work

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory}

\def\PV{{\rm PV}}
\begin{document}

\subsection{Warm-up: four-dimensional Kodaira--Spencer theory}

In the BV formalism, minimal Kodaira--Spencer theory on $X$ is a (degenerate) Poisson BV theory with space of fields given by
\[
\begin{tikzcd}
& \ul{\rm odd} & \ul{\rm even} \\
\mu^0 \in & & \PV^{0,\bu} \\
\mu^1 + u \mu^0 \in & \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
\end{tikzcd}
\]
We will denote this sheaf of $\ZZ /2$-graded cochain complexes by $\cE_{\rm KS}$, the differential is denoted $\dbar + u \partial_\Omega$.

The fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]

As with Kodaira--Spencer theory in any dimension, there are two, equivalent, $L_\infty$-structures on the parity shift $\Pi \cE_{\rm KS}$ of the fields whose $1$-ary operation is the differential $\dbar + u \partial \Omega$.

The first $L_\infty$ structure is actually a strict dg Lie algebra.
The Lie bracket is defined using the Schouten-Nijenhuis bracket $[-,-]_{\rm NS}$ on polyvector fields and is given by the formula
\[
[u^k \mu , u^\ell \mu'] = u^{k+\ell} [\mu, \mu']_{\rm NS} .
\]
where $k, \ell = 0,1$.
Together with the differential $\dbar + u \partial_\Omega$ this equips the parity shifted sheaf of cochain complexes $\Pi \cE_{\rm KS}$ with the structure of a local dg Lie algebra.

The second $L_\infty$ structure is defined in terms of the BCOV action $I^{\rm BCOV}$ which we recall is of the form
\[
I^{\rm BCOV} (\Sigma) = \sum_{\\ k_1 + \cdots + k_n = n-3} \frac{1}{n!} \int_X^{\rm PV} \<\Sigma^{\otimes n}\>_0 .
\]
\brian{$L_\infty$}
We will be most interested in this second $L_\infty$ structure in what follows.

We introduce another theory on the Calabi--Yau surface $X$ that we call minimal Kodaira--Spencer theory {\em with potentials}.
This is a (non-degenerate) BV theory whose underlying free limit is defined as follows.
The fields are
\[
\begin{tikzcd}
& \ul{\rm odd} & \ul{\rm even} \\
\Tilde{\beta} \in & & \Omega^{0,\bu} \\
\alpha \in & \Omega^{0,\bu}  
\end{tikzcd}
\]
with linear BRST differential $\dbar$ left implicit. 
We will denote the resulting $\ZZ /2$-graded sheaf of cochain complexes by $\cE_{\rm Pot}$.
The BV pairing is $\int_X (\alpha \Tilde{\beta}) \Omega$.

We interpret this as the theory of  ``potentials"  of minimal Kodaira--Spencer theory in the following way.
There is a map of sheaves of cochain complexes
\[
\Phi \colon \cE_{\rm Pot} \to \cE_{\rm KS}
\]
defined by
\begin{align*}
\Phi (\Tilde{\beta}) & = \Tilde{\beta} \in \PV^{0,\bu}(X) \\
\Phi(\alpha) & = \Omega \vee (\partial \alpha) \in \PV^{1,\bu}(X)
\end{align*}
where $\partial \colon \Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ is the holomorphic de Rham operator. 
It is immediate to see that $\Phi$ defines a map of sheaves of cochain complexes which describe the underlying free theories. 
Furthermore, $\Phi$ also preserves the odd Poisson tensors.

%The theory $\cE_{\rm pot}$ is equipped with a non-degenerate BV pairing defined by the wedge-and-integrate pairing
%\[
%\omega_{\rm pot} (\alpha, \beta) = \int \alpha \wedge \beta  .
%\]
%It is immediate to verify that $\Phi$ intertwines the resulting bivector $\omega_{\rm pot}^{-1}$ and the Kodaira--Spencer Poisson bivector $\Pi_{\rm KS}$.

The parity shifted bundle $\Pi \cE_{\rm pot}$ inherits the structure of a local Lie algebra, from the BCOV action as follows. 
By restricting along $\Phi$, we obtain the functional $\Phi^* I^{\rm BCOV}$ on $\cE_{\rm Pot}$. 
Explicitly, one finds that this restricted functional is given by
%\[
%\Phi^* I^{\rm BCOV} = \frac12 \int_{X} e^{\Tilde{\beta}} \partial \alpha \partial \alpha  .
%\]
\[
\Phi^* I^{\rm BCOV} = \frac12 \int_{X} \Tilde{\beta} \partial \alpha \partial \alpha 
\]
Since $\Phi$ preserves the odd Poisson bracket, it is automatic that $\Phi^* I^{\rm BCOV}$ satisfies the classical master equation
\[
\dbar \Phi^* I^{\rm BCOV} + \frac12 \{\Phi^* I^{\rm BCOV} , \Phi^* I^{\rm BCOV} \} = 0 .
\]
So, this functional defines an interacting (non-degenerate) BV theory. 
Notice that there are terms in $\Phi^* I^{\rm BCOV}$ of every order.
In fact, it is equivalent to a much simpler BV theory.

%\begin{prop}
%The change of coordinates $\Tilde{\beta} \mapsto \beta = e^{\Tilde{\beta}}$ determines a equivalence between the classical field theory described by $\Phi^* I^{\rm BCOV}$ and the theory described by the {\em cubic} interaction
%\[
%I = \int_X \beta \partial \alpha \partial \alpha .
%\]
%\end{prop}

The interaction $\Phi^*I^{\rm BCOV}$ has the following geometric interpretation. 
Note that any Calabi--Yau surface comes equipped with a holomorphic symplectic structure and there is a Poisson bracket defined on the sheaf of holomorphic functions.
Since the bracket is defined in terms of holomorphic differential operators, it extends to a bracket on the Dobleault complex $\Omega^{0,\bu}(X)$.

The theory described by the fields $\cE_{\rm Pot}$ with interaction $\Phi^*I^{\rm BCOV}$ is equivalent to BF theory for this local dg Lie algebra. 
Indeed, the fields of BF theory are given by
\[
\begin{tikzcd}
& \ul{\rm odd} & \ul{\rm even} \\
\beta \in & & \Omega^{2,\bu} \\
\alpha \in & \Omega^{0,\bu}   .
\end{tikzcd}
\]
There is an equivalence with $\cE_{\rm Pot}$ given by setting $\beta = \Omega \Tilde{\beta}$.

\begin{rmk}
We notice that BF theory lifts to the structure of a $\ZZ$-graded theory by declaring that the field $\alpha$ have degree $(-1)$ and $\beta$ have degree zero. 
\end{rmk}

\subsection{A variant}
Consider the following cochain complex 
\[
\begin{tikzcd}
& \ul{\rm odd} & \ul{\rm even} \\
u^{-1} \gamma^0 + \gamma^1 \in & u^{-1} \Omega^{0,\bu}  \ar[r,"u \partial"] & \Omega^{1,\bu} \\
\mu^1 + u \mu^0 \in & \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} .
\end{tikzcd}
\]
which we denote by $\Tilde{\cE}_{\rm Pot}$.

Notice that $\Tilde{\cE}_{\rm Pot}$ has the structure of a (non-degenerate) free BV theory with BV pairing defined by
\[
\int (\mu^1 \vee \gamma^1) \wedge \Omega + \int (\mu^0 \gamma^0) \wedge \Omega .
\]

There is a map of sheaves of cochain complexes
\[
\Tilde{\Phi} \colon \Tilde{\cE}_{\rm Pot} \to \cE_{\rm KS}
\]
defined by
\begin{align*}
\Tilde{\Phi} (\gamma^1) & = \Omega \vee \partial \gamma^1 \in \PV^{0,\bu}(X) \\
\Tilde{\Phi} (u^{-1}\gamma^0) & = 0 \\
\Tilde{\Phi}(\mu^1 + u \mu^0 ) & =  \mu^1 + u \mu^0 \in \PV^{1,\bu} \oplus u \PV^{0,\bu} .
\end{align*}
where $\partial \colon \Omega^{0,\bu}(X) \to \Omega^{1,\bu}(X)$ is the holomorphic de Rham operator. 
It is immediate to see that $\Tilde{\Phi}$ defines a map of sheaves of cochain complexes which describe the underlying free theories. 
Crucially, $\Tilde{\Phi}$ also preserves the odd Poisson tensors.

Set
\[
\Tilde{I} \define \Tilde{\Phi}^* I^{\rm BCOV} .
\]
Explicitly, one has
\[
\Tilde{I} = \frac12 \int (e^{\mu^0} \Omega) \left[ (\partial \gamma^1) \vee (\mu^1 \wedge \mu^1) \right].
\]
Since $\Tilde{\Phi}$ preserves the odd Poisson bracket, the interaction $\Tilde{I}$ automatically solves the CME for $\Tilde{\cE}_{\rm Pot}$
\[
(\dbar + u \partial) \Tilde{I} + \frac12 \{\Tilde{I}, \Tilde{I}\} = 0 .
\]

\section{11d redux}

\begin{dfn} \label{dfn:classical}
Let $X$ be a Calabi--Yau five-fold and $L$ a smooth one-dimensional manifold.
{\em Eleven-dimensional twisted supergravity} on $X \times L$ is the $\ZZ/2$-graded BV theory on $X$ whose fields are pairs
\begin{align*}
\mu = \mu^1 + \mu^0 & \in \bigg(\Pi \PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
\gamma = \gamma^0 + \gamma^1 & \in \bigg(\Pi \Omega^{0,\bu}(X) \oplus \Omega^{1,\bu} (X) \bigg) \; \Hat{\otimes} \; \Omega^{\bu}(L) 
\end{align*}
The BV pairing is $\int (\gamma \vee \mu) \wedge \Omega$ and the BV action is
\begin{equation}\label{eqn:bvaction}
\begin{array}{lllllll}
S & = & \displaystyle \int \left[\gamma \vee \left(\dbar \mu + \d_{\dR} \mu\right) \right] \wedge \Omega  + \int \left[(\partial \gamma^0 - \gamma^0 \partial \mu^0) \mu^1 \right] \wedge \Omega \\ & + &  \displaystyle \frac12 \int e^{\mu^0} \left(\partial \gamma^1 \vee (\mu^1 \wedge \mu^1) \right) \wedge \Omega  + \frac16 \int e^{\mu^0} \gamma^1 \partial \gamma^1 \partial \gamma^1 .
\end{array}
\end{equation}
\end{dfn}

Let us expand the action into kinetic and interacting parts $S = S_{\rm kin} + I$.
The kinetic part of the action reads 
\[
S_{\rm kin} = \int \left[\gamma \vee \left(\dbar \mu + \d_{\dR} \mu\right) \right] \Omega  + \int \left[\partial \gamma^0 \vee \mu^1 \right] \Omega .
\]
If we expand the interaction $I = \sum_{n \geq 3} I_n$ into homogenous polynomials, the first few terms read
\begin{align*}
I_3 & = - \int \left[\gamma^0 (\partial \mu^0) \vee \mu^1\right] \Omega + \frac12 \int \left[\partial \gamma^1 \vee (\mu^1 \wedge \mu^1)\right] \Omega + \frac16 \int \gamma^1 \partial \gamma^1 \partial \gamma^1 . \\
I_4 & = \frac12 \int \left[ (\mu^0)^2 \partial \gamma^0 \vee \mu^1 \right] \Omega + \frac12 \int \left[ \mu^0 \partial \gamma^1 \vee (\mu^1 \wedge \mu^1) \right] \Omega + \frac16 \int \mu^0 \gamma^1 \partial \gamma^1 \partial \gamma^1 \\
& \vdots 
\end{align*} 
\end{document}

### 2021-03-26 modules.tex
modules

% Created 2020-10-14 Wed 14:51
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{macros-mtheory}

\date{\today}
\title{Twisted \(M\)-theory and its perturbative quantization.}
\hypersetup{
 pdfauthor={Surya and Brian},
 pdftitle={Twisted \(M\)-theory and its perturbative quantization.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.4)}, 
 pdflang={English}}

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}
\def\Vect{{\rm Vect}}

\begin{document}

\section{Modules}
Suppose $X$ is a Calabi--Yau manifold of complex dimension $n$. 
Consider the cochain complex
\[
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Vect(X) \ar[r, "\partial_\Omega"] & \cO (X) 
\end{tikzcd}
\]
which we will refer to as $\cL$ in this section.
Here, $\Vect(X)$ is the space of holomorphic vector fields and $\cO(X)$ is the space of holomorphic functions.
The differential is the divergence operator with respect to the holomorphic volume form.
There is the natural structure of a dg Lie algebra on this cochain complex defined by
\begin{align*}
[\mu, \mu'] & = L_\mu \mu' \\
[\mu, \nu] & = L_\mu \nu 
\end{align*}
for $\mu,\mu' \in \Vect(X)$ and $\nu \in \cO(X)$. 
To see that this is a dg Lie algebra we observe that the divergence operator acts as a derivation on the Lie bracket of vector fields.

In the next three subsections we will describe three equivalent descriptions of the same $\cL$-module.

\subsection{Differential form description}

Next, consider the following cochain complex 
\[
\begin{tikzcd}
\ul{0} & \ul{1} \\
\cO(X) \ar[r, "\partial"] & \Omega^1 (X) 
\end{tikzcd}
\]
that we denote by $\cM$ in this section. 
This cochain complex consists of holomorphic functions and one-forms together with the holomorphic de Rham differential between them. 
We denote by $\beta \in \cO(X)$ a holomorphic function and $\gamma \in \Omega^1(X)$ a holomorphic one-form.

\begin{dfn}
Define the following dg $\cL$-module structure $\rho$ on $\cM$:
\[
\begin{array}{cclcc}
\rho (\mu) \beta & = & L_\mu(\beta) + (\partial_\Omega \mu) \beta & \in &\cO(X) \\
\rho (\mu) \gamma & = & L_\mu (\gamma) + (\partial_\Omega \mu) \gamma & \in &\Omega^1(X) \\ 
\rho(\nu) \beta & = & (\partial \nu) \beta & \in & \Omega^1(X) .
\end{array}
\]
\end{dfn}

\begin{lem}
$\rho$ defines the structure of a dg $\cL$-module.
\end{lem}
\begin{proof}
First, we must show that $\rho$ is compatible with the differentials.
This amounts to checking the following relations:
\begin{itemize}
\item $\partial (\rho(\mu) \beta) = \rho(\partial_\Omega \mu) \beta + \rho(\mu) \partial \beta$.
\item $\rho(\partial_\Omega \mu) \gamma = 0$. 
\item $\rho (\nu) \partial \beta = 0$. 
\end{itemize}
The last two relations follow immediately from the definition of $\rho$.
The left-hand side of the first item is
\begin{equation}\label{eqn:lhs1}
\partial L_\mu( \beta) + \partial ((\partial_\Omega \mu) \beta) =  L_\mu( \partial \beta) + (\partial \partial_\Omega \mu) \beta + (\partial_\Omega \mu) \partial \beta .
\end{equation}
The right-hand side of the first item is
\begin{equation}\label{eqn:rhs1}
(\partial \partial_\Omega \mu) \beta + L_\mu (\partial \beta) + (\partial_\Omega \mu) \partial \beta 
\end{equation}
which clearly agrees with \eqref{eqn:lhs1}.

Next, we show that $\rho$ is compatible with the Lie bracket. 
This amounts to showing the following relations:
\begin{itemize}
\item $[\rho(\mu), \rho(\mu')] \beta = \rho(L_\mu \mu')\beta$.
\item $[\rho(\mu), \rho(\mu')] \gamma = \rho(L_\mu \mu')\gamma$.
\item $[\rho(\mu),\rho(\nu)] \beta = \rho(L_\mu \nu) \beta$. 
\end{itemize}
\end{proof}

\subsection{Schouten bracket description}

Consider the dg Lie algebra of {\em all} polyvector fields on $X$:
\[
\left(\PV^{-\bu} (X) [-1] \; , \; \partial_\Omega \; , \; \{\cdot, \cdot\} \right)
\]
where the differential \brian{finish}

The Lie algebra $\cL$ resolving divergence free vector fields is clearly a sub Lie algebra of $\PV^{-\bu} (X) [-1]$. 
In particular, $\cL$ acts on $\PV^{-\bu} (X) [k]$ for any shift $k \in \ZZ$.

Consider the submodule 
\[
\PV^{- \bu\leq n-2} (X) [k] = \bigg(\PV^{n-2}(X) [k+n-2] \xto{\partial_\Omega} \PV^{n-3}(X) [k+n-3] \to \cdots \to \PV^{0} [k] \bigg) 
\]
of $\PV^{-\bu}(X)[k]$. 
Its quotient is the $\cL$-module $\Tilde{\cM}$ which is given by the two-term complex
\[
\Tilde{\cM} = \bigg(\PV^{n}(X) [k+n] \xto{\partial_\Omega}  \PV^{n-1}(X) [k+n-1] \bigg) .
\]
The action of $\cL$ on $\Tilde{\cM}$ is simply the restriction of the Schouten bracket.

The following lemma is a direct calculation.

\begin{lem}
Contraction with the holomorphic volume form $\Omega$ defines an isomorphism of $\cL$-modules
\[
\Omega \vee (-) \colon \Tilde{\cM} \to \cM .
\] 
\brian{fix shifts}
\end{lem}

\subsection{Contragradient description}

Define the following cochain complex
\[
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Omega^{n} (X) \ar[r, "\partial^\vee_\Omega"] & \Omega^{n}(X) \otimes_{\cO} \Omega^1 (X) 
\end{tikzcd}
\]
which is isomorphic to the contragradient bundle $\cL^!$ \brian{shifts}. 
Here, the differential is defined by the formula
\[
\partial^\vee_\Omega (\Omega f) = \Omega \otimes (\partial f) .
\]
The cochain complex has the natural structure of an $\cL$-module defined by the formulas
\[
\begin{array}{cclcc}
\Tilde{\rho}(\mu) \Tilde{\beta} & = & L_\mu(\Tilde{\beta}) & \in &\Omega^n \\
\Tilde{\rho} (\mu) \Tilde{\gamma} & = & L_\mu (\Tilde{\gamma}) & \in &\Omega^n \otimes \Omega^1 \\ 
\rho(\nu) \Tilde{\beta} & = & \Tilde{\beta} (\partial \nu)  & \in & \Omega^n \otimes \Omega^1 .
\end{array}
\]

\begin{lem}
The map $\Omega (-) \colon \cM \to \Tilde{\cM}$ is an isomorphism of $\cL$-modules.
\end{lem}
%\[
%\<\partial^\vee_\Omega (\Tilde{\beta}) , \mu\> = \<\Tilde{\beta}, \partial_\Omega \mu\> .
%\]

%$\cL$ is the sub Lie algebra of the dg Lie algebra consisting of all holomorphic polyvector fields $\PV^{\bu}(X)[1]$.

\section{$L_\infty$ deformations}
We will describe a family of deformations of the dg Lie algebra $\cL \ltimes \Pi \cM$ defined when the dimension of the Calabi--Yau manifold is odd.

\subsection{$n=2$} 
Consider the case $\dim_{\CC}(X) = 5$. 
Introduce the new brackets
\begin{align*}
[\gamma_1, \gamma_2]_2 &= (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) \\
[\gamma_1, \gamma_2, \gamma_3]_3 & = (\gamma_1 \partial \gamma_2 \partial \gamma_2)\vee \Omega \in \Omega^0(X) \\
[\gamma_1, \gamma_2, \nu]_3 & = \nu (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) .
\end{align*}

The fact that the the differential is a biderivation for the new $2$-ary brackets is obvious. 
The $3$-ary relations we must check are
\begin{itemize}
\item[(1)] $[[\gamma_1, \gamma_2] , \gamma_3] + [[\gamma_2, \gamma_3], \gamma_1] + [[\gamma_3, \gamma_1], \gamma_2] = 0 .$
\item[(2)] $[[\mu, \gamma_1], \gamma_2] + [[\gamma_1, \gamma_2], \mu] + [[\gamma_2, \mu], \gamma_1] = [\gamma_1, \gamma_2, \partial_\Omega \mu]_3$.
\end{itemize}

Let us first check (1).

\end{document}

### 2021-03-29 modules.tex
modules update

@@
 \def\Vect{{\rm Vect}}
+\def\div{\partial_\Omega}
 
@@
 [\gamma_1, \gamma_2]_2 &= (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) \\
-[\gamma_1, \gamma_2, \gamma_3]_3 & = (\gamma_1 \partial \gamma_2 \partial \gamma_2)\vee \Omega \in \Omega^0(X) \\
+[\gamma_1, \gamma_2, \gamma_3]_3 & = (\gamma_1 \partial \gamma_2 \partial \gamma_3)\vee \Omega \in \Omega^0(X) \\
 [\gamma_1, \gamma_2, \nu]_3 & = \nu (\partial \gamma_1 \partial \gamma_2)\vee \Omega \in \PV^1(X) .
@@
 
+\section{Type IIA}
+
+Let $X$ be a Calabi--Yau manifold of dimension four. 
+Consider the following $\ZZ/2$-graded cochain complex
+\[
+\begin{tikzcd}
+\ul{even} & \ul{odd} \\
+& \PV^0(X)_\eta \\
+\PV^1(X)_\mu \ar[r, "\partial_\Omega"] & \PV^0 (X)_\nu \\
+\PV^4(X)_\beta \ar[r, "\partial_\Omega"] & \PV^3(X)_\gamma \\
+\PV^4(X)_\theta
+\end{tikzcd}
+\]
+
+There is a $\ZZ/2$-graded dg Lie algebra structure on this complex defined by the nontrivial brackets
+\begin{align*}
+[\eta, \theta] & = \{\eta, \theta\} \in \PV^3_\gamma \\
+[\nu, \beta] & = \{\nu, \beta\} \in \PV^3_\gamma \\ 
+[\mu, \Phi] & = \{\mu, \Phi\} \in \PV^k_\Phi
+\end{align*}
+where in the last equation $\Phi$ stands for any polyvector field of type $k$ in the complex.
+
+\begin{prop}
+The formulas 
+\begin{align*}
+[\gamma, \gamma'] & = (\partial_\Omega \gamma) (\partial_\Omega \gamma') \in \PV^4_\theta \\
+[\eta, \gamma] & = \{\eta, \div \gamma\} \in \PV^1_\mu \\
+%[\gamma, \theta] & = 0 \in \PV^4_\theta ?? \\
+[\eta, \gamma, \gamma']_3 & = \frac12 \left(\{\{\eta, \gamma\}, \gamma'\} + symm\right) \in \PV^4_\beta \\
+[\nu, \gamma, \gamma']_3 & = \frac12 \left(\{\{\nu, \gamma\}, \gamma'\} + \cdots \right) \in \PV^4_\theta
+\end{align*}
+\end{prop}
+define an $L_\infty$ deformation of the dg Lie algebra. 
+\begin{proof}
+First, we observe that the new $2$-ary bracket is trivially compatible with the differential. 
+Next, we check the $3$-ary $L_\infty$ relations involving the new $2,3$-ary brackets. 
+The only nontrivial $3$-ary relations to check are
+\begin{itemize}
+\item[(1)] $\div [\eta, \gamma, \gamma']_3 = \{\eta, [\gamma, \gamma']\} + \{[\eta, \gamma], \gamma'\} + \{[\eta, \gamma'], \gamma\}.$
+\item[(2)] $- [\div \mu, \gamma, \gamma']_3  = \{\mu, [\gamma, \gamma']\} + \{\{\mu, \gamma\}, \gamma'\} + \{\{\mu, \gamma'\}, \gamma\}$.
+
+\end{itemize}
+
+Substituting the definitions of the $2$-ary Lie brackets, we see that (1) follows from the following lemma. 
+\begin{lem}
+For all $\eta, \gamma, \gamma'$ one has
+\begin{equation}\label{eqn:C43ary}
+\div \{\{\eta, \gamma\}, \gamma'\} = \{\eta, \div \gamma \div \gamma'\} + \{\{\eta, \div \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
+\end{equation}
+\end{lem}
+\begin{proof}
+This is a direct calculation. 
+Consider the last two terms on the right hand side:
+\[
+\{\{\eta, \div \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
+\]
+Since $\div$ is a derivation for $\{\cdot,\cdot\}$ we can rewrite this expression as
+\[
+\{\div\{\eta, \gamma\}, \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} = \div \{\{\eta, \gamma\}, \gamma'\} - \{\{\eta, \gamma\}, \div \gamma'\} + \{\{\eta, \div \gamma'\}, \gamma\} .
+\]
+By the Jacobi identity for $\{\cdot, \cdot\}$ this expression is equal to
+\[
+\div\{\{\eta, \gamma\}, \gamma'\} - \{\{\gamma, \div \gamma'\}, \eta\} 
+\]
+The lemma reduces to the following BV relation:
+\[
+\{\eta, \div \gamma \div \gamma'\} = \{\eta, \{\gamma, \div \gamma'\}\} .
+\]
+
+%By the BV relation, the left hand side is 
+%\[
+% \{\eta, \div(\gamma \div \gamma')\} = \{\eta, \{\gamma, \div \gamma'\}\} + \{\eta, (\div\gamma) (\div \gamma')\}.
+% \]
+\end{proof}
+
+Finally, there are the following $4$-ary $L_\infty$ relations to check. 
+\begin{itemize}
+\item[(1)] $\{\nu, [\eta, \gamma, \gamma']_3\} + \{\eta, [\nu, \gamma, \gamma']_3\} = 0.$ 
+\item[(2)]
+\end{itemize}
+
+\brian{Maybe we need to symmetrize to use $[\eta, \gamma, \gamma']_3 = \{\eta, \{\gamma, \gamma'\}\}$.}
+\end{proof}
+
 \end{document}

### 2021-04-01 new_paper.tex
new paper

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory}

%% Bib stuff

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
            isbn=false,
            doi=false,
            maxbibnames=5,
            %giveninits=true,
            style=alphabetic,
            citestyle=alphabetic]{biblatex}
\usepackage{url}
\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}
\renewbibmacro{in:}{}
\bibliography{references.bib}
\renewcommand*{\bibfont}{\footnotesize}

\usepackage{xcolor}
\definecolor{e-mail}{rgb}{0,.40,.80}
\definecolor{reference}{rgb}{.40,.60,.2}
\definecolor{citation}{rgb}{0,.25,.5}

\usepackage[colorlinks=true,
            linkcolor=reference,
            citecolor=citation,
            urlcolor=e-mail]{hyperref}
\usepackage{cleveref}

%% Formatting. We can change this in the final version, just makes it easier for me to read in the meantime.

\usepackage[top=1in, bottom=1.25in, left=1.3in, right=1.3in]{geometry}
\setlength{\parskip}{8pt}
\setlength\parindent{0pt}
\setcounter{tocdepth}{2}
\numberwithin{equation}{section}
\let\emptyset\varnothing

%% Comments

\def\owen{\textcolor{magenta}{BW: }\textcolor{magenta}}
\def\gene{\textcolor{blue}{SR: }\textcolor{blue}}
\def\brian{\textcolor{red}{IS: }\textcolor{red}}

%% Random macros

\def\vectdiv{\fL}
\def\PV{{\rm PV}}
\def\div{\partial_\Omega}

%\usepackage[style = alphabetic]{biblatex}
%\addbibresource{references.bib}
%\AtBeginBibliography{\scriptsize}

\begin{document}

\title{Something about classical M-theory}

%\author{Brian R. Williams}
%\address{School of Mathematics\\
%University of Edinburgh \\ 
%Edinburgh \\ 
%UK}
%\email{brian.williams@ed.ac.uk}

\begin{abstract}
something here
\end{abstract}

\maketitle
\thispagestyle{empty}
\setcounter{tocdepth}{1}
%\tableofcontents

\section{Introduction}

\section{The $L_\infty$ algebras at play}

\subsection{Divergence-free vector fields}

Let $X$ be a Calabi--Yau manifold of dimension $n$ with holomorphic volume form $\Omega \in \Omega^n_X$. 
Let $\vectdiv_X$ be the sheaf of holomorphic divergence-free vector fields, which is of course a sub Lie algebra of $\PV^1_X$. 
Here is a resolution of holomorphic divergence-free vector fields that will be of interest to us.

\begin{dfn}
Let $\cL_X$ be the sheaf of dg Lie algebras which as a sheaf of cochain complexes is 
\[
\PV^1_X \xto{\div} \PV^0_X [-1] 
\]
concentrated in degree zero and one. 
The brackets read:
\begin{align*}
[\mu, \mu'] & = L_\mu(\mu') \\
[\mu, \nu] & = L_\mu(\nu)
\end{align*}
for $\mu,\mu' \in \PV^1_X$, $\nu \in \PV^0_X$. 
\end{dfn}

There is an obvious map of sheaves of dg Lie algebras $\vectdiv_X \to \cL_X$, which exhibits $\cL_X$ as a resolution of divergence-free vector fields. 
%\[
%\begin{tikzcd}
%\ul{0} & \ul{1} \\
%\PV^1_X \ar[r, "\partial_\Omega"] & \PV^0_X . 
%\end{tikzcd}
%\]

The dg Lie algebra $\cL_X$ is a sub dg Lie algebra of a bigger dg Lie algebra, consisting of {\em all} polyvector fields on $X$. 
The Schouten bracket 
\[
\{\cdot, \cdot\} \colon \PV^{i}_X \times \PV^{j}_X \to \PV^{i+j-1}_X 
\]
endows the sheaf of cochain complexes
\[
\left(\PV^{-\bu}_X [-1] , \div \right) \define \bigg( \PV^n_X [n-1] \xto{\div} \PV^{n-1}_X [n-2] \to \cdots \to \PV^1_X \xto{\div} \PV^0_X[-1] \bigg)
\] 
with the structure of a sheaf of dg Lie algebras.
The obvious embedding 
\[
\cL_X \hookrightarrow \PV^{-\bu}_X [-1]
\] 
is a map of dg Lie algebras.

Consider, instead, the following sub complex of $\PV^{-\bu}_X$ 
\[
\left(\cS^\bu , \div\right) \define \bigg(\PV^{n-2}_X [n-3] \to \cdots \to \PV^1_X \xto{\div} \PV^0_X[-1] \bigg) .
\]
Notice that this is {\em not} a sub dg Lie algebra. 
Nevertheless, it is naturally a module for $\cL_X$, and we can define the quotient dg module.

\begin{dfn}
Let 
\[
\cM^\bu \define \PV^{-\bu}_X [-1] \; / \; \cS^\bu  .
\]
be the quotient dg $\cL_X$-module.
Explicitly, as a sheaf of cochain complexes $\cM_X$ is given by the two-term complex
\[
\PV^n_X [n-1] \xto{\div} \PV^{n-1}_X [n-2] .
\]
The action of $\cL_X$ on $\cM_X$ is through the Schouten bracket $\{\cdot,\cdot\}$. 
\end{dfn}

We will denote sections of this dg module by $\beta \in \PV^n_X$ and $\gamma \in \PV^{n-1}_X$.

\begin{dfn}
Let $\fg_X$ be the sheaf of dg Lie algebras obtained by the semi-direct product of $\cL_X$ with $\cM_X$
\[
\fg_X \define \cL_X \ltimes \cM_X .
\]
\end{dfn}

\subsection{An $L_\infty$-deformation}

Suppose now that $X$ is a Calabi--Yau manifold of odd dimension $n=2k+1$. 
In this section it is also necessary to forget $\ZZ$-gradings to $\ZZ/2$-gradings. 
So, for instance, the sheaf of $\ZZ$-graded dg Lie algebras becomes the sheaf of $\ZZ/2$-graded dg Lie algebras which as a sheaf of graded vector spaces is
\[
\fg_X = \bigg(\PV^1_X \oplus \Pi \PV^0_X \bigg) \oplus \bigg(\PV^{2k+1} \oplus \Pi \PV^{2k}_X \bigg) .
\]

The first piece of business is to define a $k$-linear map which we will use to define an $L_\infty$ deformation of the dg Lie algebra $\fg_X$. 
To define it, notice that contraction with the holomorphic volume form determines an isomorphism 
\[
\Omega \vee \colon \PV^{\ell}_X \cong \Omega^{2k +1 - \ell}_X ,
\]
for any $\ell$. 
In particular, any section $\gamma \in \PV^{2k}_X$ determines a one-form $\Omega \vee \gamma \in \Omega^1_X$. 
Also, if $\omega \in \Omega^{\ell}_X$ is an $\ell$-form, let $\omega \vee \Omega^{-1} \in \PV^{2k+1-\ell}_X$ be the polyvector field satisfying
\[
\Omega \vee (\omega \vee \Omega^{-1}) = \omega .
\]

\begin{dfn}
Let
\[
\mu_k \colon \PV^{2k}_X \times \cdots \times \PV^{2k}_X \to \PV^1_X 
\]
be the $(k+1)$-linear map of sheaves defined by the formula
\[
\mu_k (\gamma_1,\ldots, \gamma_k) \define \bigg[\partial \left(\Omega \vee \gamma_1\right)\cdots \partial \left(\Omega \vee \gamma_k\right)\bigg] \vee \Omega^{-1} .
\]
\end{dfn}

\begin{dfn}
\label{dfn:def}
Suppose $X$ is a Calabi--Yau manifold of dimension $2k+1$. 
Define the multinear maps of sheaves
\[
[\cdot, \ldots, \cdot]_j \colon \fg_X \times \cdots \times \fg_X \to \fg_X
\]
for $j=1,2,k,k+1$ by the formulas
\begin{itemize}
\item $[\cdot]_1 = \partial_\Omega$, the divergence operator;
\item $[\cdot,\cdot]_2 = \{\cdot,\cdot\}$, the Schouten bracket;
\item the only nonzero component of the $k$-ary bracket is
\[
[\gamma_1,\ldots, \gamma_k]_k = \mu_k(\gamma_1,\ldots, \gamma_k) \in \PV^1_X .
\]
\item there are two nonzero components of the $(k+1)$-ary bracket:
\[
[\gamma_1,\ldots, \gamma_k, \gamma_{k+1}]_{k+1} = \sum_{i_1 < \cdots < i_{k+1}} \gamma_{i_1} \wedge \mu_k(\gamma_{i_2},\ldots, \gamma_{i_{k+1}}) \in \PV^{2k+1}_X .
\]
and 
\[
[\nu, \gamma_1, \ldots, \gamma_k]_{k+1} = \nu \mu_k (\gamma_1,\ldots, \gamma_k) \in \PV^{1}_X .
\]
\end{itemize}
\end{dfn}

\begin{thm}
The operations of Definition \ref{dfn:def} endow $\fg_X$ with the structure of a sheaf of $L_\infty$-algebras.
\end{thm}

\begin{proof}
Before turning on the brackets built from $\mu_k$ we know that $\fg_X$ defines the structure of a dg Lie algebra.
Thus, it suffices to check that the new $(k+1)$-ary and $(k+2)$-ary higher Jacobi relations involving $\mu_k$ are satisfied.

The $(k+1)$-ary relations we must check are:
\begin{itemize}
\item[(1)] $\div [\gamma_1,\ldots, \gamma_k,\gamma_{k+1}]_{k+1} = \sum \{\gamma_{i_1}, [\gamma_{i_2},\ldots, \gamma_{i_{k+1}}]\}$. 
\item[(2)] $[\div \mu, \gamma_1, \ldots, \gamma_k]_{k+1} = \{\mu, [\gamma_1,\ldots, \gamma_k]_k\}$.
\item[(3)] $\div [\nu,\gamma_1,\ldots, \gamma_k]_{k+1} = \{\nu, [\gamma_1,\ldots, \gamma_{k}]_k\}$.
\end{itemize}
\end{proof}
\end{document}

### 2021-04-02 new_paper.tex
3jacobi

@@
 
-\def\owen{\textcolor{magenta}{BW: }\textcolor{magenta}}
-\def\gene{\textcolor{blue}{SR: }\textcolor{blue}}
-\def\brian{\textcolor{red}{IS: }\textcolor{red}}
+\def\brian{\textcolor{violet}{BW: }\textcolor{violet}}
+\def\surya{\textcolor{blue}{SR: }\textcolor{blue}}
+\def\ingmar{\textcolor{magenta}{IS: }\textcolor{magenta}}
 
@@
 \]
-be the $(k+1)$-linear map of sheaves defined by the formula
+be the $k$-linear map of sheaves defined by the formula
 \[
@@
 \end{dfn}
+
+\begin{lem}
+For any $\gamma_1,\ldots, \gamma_k$, the vector field $\mu_k(\gamma_1,\ldots, \gamma_k)$ is divergence-free. 
+\end{lem}
 
@@
 \[
-[\cdot, \ldots, \cdot]_j \colon \fg_X \times \cdots \times \fg_X \to \fg_X
+[\cdot, \ldots, \cdot]_j \colon \fg_X \times \cdots \times \fg_X \to \Pi^j \fg_X
 \]
@@
 \[
-[\nu, \gamma_1, \ldots, \gamma_k]_{k+1} = \nu \mu_k (\gamma_1,\ldots, \gamma_k) \in \PV^{1}_X .
+[\nu, \gamma_1, \ldots, \gamma_k]_{k+1} = \# \nu \mu_k (\gamma_1,\ldots, \gamma_k) + \sum_{i=1}^k \bigg[\left(\Omega \vee \{\nu, \gamma_1\}\right)\cdots \Hat{\partial \left(\Omega \vee \gamma_k\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] \vee \Omega^{-1} \in \PV^{1}_X .
 \]
@@
 \item[(1)] $\div [\gamma_1,\ldots, \gamma_k,\gamma_{k+1}]_{k+1} = \sum \{\gamma_{i_1}, [\gamma_{i_2},\ldots, \gamma_{i_{k+1}}]\}$. 
-\item[(2)] $[\div \mu, \gamma_1, \ldots, \gamma_k]_{k+1} = \{\mu, [\gamma_1,\ldots, \gamma_k]_k\}$.
+\item[(2)] $[\div \mu, \gamma_1, \ldots, \gamma_k]_{k+1} = \{\mu, [\gamma_1,\ldots, \gamma_k]_k\} + \sum [\{\mu, \gamma_{i_1}\}, \gamma_{i_2}, \ldots, \gamma_{i_{k}}]_{k}$.
 \item[(3)] $\div [\nu,\gamma_1,\ldots, \gamma_k]_{k+1} = \{\nu, [\gamma_1,\ldots, \gamma_{k}]_k\}$.
 \end{itemize}
+
+\ul{(1)}:
+We apply the BV relation to the left hand side.
+Since $\mu_k(\gamma_1,\ldots,\gamma_k)$ is divergence-free, the left hand side is
+\[
+\sum \left(\div \gamma_{i_1} \wedge \mu_k(\gamma_{i_2}, \ldots, \gamma_{i_{k+1}}) + \{\gamma_{i_1}, \mu_k(\gamma_{i_2},\ldots, \gamma_{i_{k+1}})\} \right) .
+\]
+The second terms in the sum cancels with the right hand side of the Jacobi identity.
+Thus, it suffices to show that 
+\[
+\sum \div \gamma_{i_1} \wedge \mu_k(\gamma_{i_2}, \ldots, \gamma_{i_{k+1}}) = 0 .
+\]
+Notice that this expression only depends on the divergences of the polyvector fields $\gamma_1,\ldots, \gamma_{k+1}$. 
+Moreover, it is totally symmetric in the inputs. 
+Thus, we can write it as $L(\div \gamma_1,\ldots, \div \gamma_{k+1})$ where
+\[
+L \colon \Sym^{k+1} \left(\wedge^{2k-2} V \right) \to V
+\]
+is some ${\rm SL}(2k+1)$-invariant map. 
+Here $V$ denotes the defining ${\rm SL}(2k+1)$ representation.
+As such $L= 0$ \brian{justify}.
+
+\ul{(2)}: 
+The left hand side of the Jacobi identity reads
+\begin{equation}\label{eqn:3jacobi2a}
+(\div \mu) \mu_k (\gamma_1,\ldots, \gamma_k) + \sum_{i=1}^k \{\div \mu, \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg]
+\end{equation}
+Consider the first term on the right hand side of the Jacobi identity. 
+Expanding out, we can write this as
+\begin{equation}\label{eqn:3jacobi2b}
+\sum_{i=1}^k \{\mu, \div \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] + \# (\div \mu) \mu_k(\gamma_1,\ldots, \gamma_k) .
+\end{equation}
+The final term cancels with the first term of \eqref{eqn:3jacobi2a}. 
+The remaining terms on the right hand side of the Jacobi relation read
+\[
+\sum_{i=1}^k \partial \{\mu, \gamma_i\} \vee \bigg[\left(\Omega \vee \gamma_1\right) \cdots \Hat{\partial \left(\Omega \vee \gamma_i\right)} \cdots \partial \left(\Omega \vee \gamma_k\right) \bigg] .
+\]
+This cancels with the sum of the second term in \eqref{eqn:3jacobi2a} and the first term in \eqref{eqn:3jacobi2b}.
 \end{proof}

### 2021-06-16 cme.tex
cme

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory}

%% Bib stuff

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
            isbn=false,
            doi=false,
            maxbibnames=5,
            %giveninits=true,
            style=alphabetic,
            citestyle=alphabetic]{biblatex}
\usepackage{url}
\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}
\renewbibmacro{in:}{}
\bibliography{references.bib}
\renewcommand*{\bibfont}{\footnotesize}

\usepackage{xcolor}
\definecolor{e-mail}{rgb}{0,.40,.80}
\definecolor{reference}{rgb}{.40,.60,.2}
\definecolor{citation}{rgb}{0,.25,.5}

\usepackage[colorlinks=true,
            linkcolor=reference,
            citecolor=citation,
            urlcolor=e-mail]{hyperref}
\usepackage{cleveref}

%% Formatting. We can change this in the final version, just makes it easier for me to read in the meantime.

\usepackage[top=1in, bottom=1.25in, left=1.3in, right=1.3in]{geometry}
\setlength{\parskip}{8pt}
\setlength\parindent{0pt}
\setcounter{tocdepth}{2}
\numberwithin{equation}{section}
\let\emptyset\varnothing

%% Comments

\def\brian{\textcolor{violet}{BW: }\textcolor{violet}}
\def\surya{\textcolor{blue}{SR: }\textcolor{blue}}
\def\ingmar{\textcolor{magenta}{IS: }\textcolor{magenta}}

%% Random macros

\def\vectdiv{\fL}
\def\PV{{\rm PV}}
\def\div{\partial_\Omega}
\def\im{{\rm i}}
\def\til{\Tilde}

%\usepackage[style = alphabetic]{biblatex}
%\addbibresource{references.bib}
%\AtBeginBibliography{\scriptsize}

\begin{document}

\title{The classical master equation}

%\author{Brian R. Williams}
%\address{School of Mathematics\\
%University of Edinburgh \\ 
%Edinburgh \\ 
%UK}
%\email{brian.williams@ed.ac.uk}

\maketitle
\thispagestyle{empty}
\setcounter{tocdepth}{1}
%\tableofcontents

\begin{lem}\label{lem:pi}
Let $\gamma_1,\gamma_2$ be any two elements of $\PV^{4,\bu}(X)$ and define
\[
\Pi(\gamma_1,\gamma_2) = \gamma_1 \vee (\div \gamma_2 \vee \Omega) \in \PV^{2,\bu}(X) .
\]
Then
\[
\div \Pi(\gamma_1,\gamma_2) = \div \gamma_1 \vee (\div \gamma_2 \vee \Omega) .
\]
\end{lem}

\begin{dfn} \label{dfn:classical}
Let $X$ be a Calabi--Yau five-fold and $L$ a smooth one-dimensional manifold.
{\em Eleven-dimensional twisted supergravity} on $X \times L$ is the $\ZZ/2$-graded BV theory on $X$ whose fields are
\begin{align*}
(\mu, \nu) & \in \big[\Pi \PV^{1,\bu}(X) \; \Hat{\otimes} \;
\Omega^{\bu}(L)\big] \oplus \big[\PV^{0,\bu}(X) \; \Hat{\otimes} \;
\Omega^{\bu}(L)\big] \\
(\beta, \gamma) & \in \big[\Pi \PV^{5,\bu}(X) \; \Hat{\otimes} \;
\Omega^{\bu}(L)\big] \oplus \big[\PV^{4,\bu}(X) \; \Hat{\otimes} \;
\Omega^{\bu}(L)\big]
\end{align*}
The BV pairing is 
\beqn
\int^\Omega \gamma \wedge \mu + \int^\Omega \beta \nu
\eeqn
and the BV action is
\begin{multline}\label{eqn:bvaction}
\int^\Omega \gamma \wedge \dbar \mu + \int^\Omega \beta \dbar \nu + \int^\Omega \beta \div \mu + \frac12 \int^\Omega \frac{1}{1-\nu} \mu \wedge \mu \wedge \div \gamma \\ 
+ \frac{c}{6} \int^\Omega \frac{1}{1-\nu} \gamma \wedge \big[\div \gamma \vee (\div \gamma \vee \Omega) \big] .
\end{multline}
\end{dfn}

Notice that the last term in the action can be written as
\[
\frac{c}{6} \int^\Omega \frac{1}{1-\nu} \gamma \wedge \div \Pi(\gamma, \gamma)
\]
with $\Pi(\gamma, \gamma)$ as in Lemma \ref{lem:pi}.

In order to see that this definition is sound we must check that the BV action satisfies the classical master equation. 
Before doing that, we remark on a simplification of this action that is bit easier to understand.

The action takes a relatively simpler form if instead of resolving the constraint that $\mu$ be divergence-free we impose it. 
Imposing the constraint $\div \mu = 0$ has the effect of throwing out the fields $\nu, \beta$ and imposes the gauge condition that $\gamma$ is only defined up to a total divergence. \footnote{Really, the zero-mode part of $\beta$ also survives, but we throw this out by hand since it does not interact with the remaining fields.}
That is, the fields become 
\beqn\label{eqn:bvonshell2}
\mu \in \ker \div \subset \PV^{1,\bu}(X) \; \Hat{\otimes} \;
\Omega^{\bu}(L) , \quad \gamma \in \left(\PV^{4,\bu} (X) / \div \right) \; \Hat{\otimes} \;
\Omega^{\bu}(L) .
\eeqn
Doing this, we see that the action becomes 
\beqn\label{eqn:bvonshell2}
\int^\Omega \gamma \wedge \dbar \mu + \frac12 \int^\Omega \mu \wedge \mu \wedge \div \gamma \\ 
+ \frac{c}{6} \int^\Omega \gamma \wedge \big[\div \gamma \vee (\div \gamma \vee \Omega) \big] .
\eeqn
By integrating by parts with respect to $\dbar$ it follows that the operator $\{\int^\Omega \gamma \wedge \dbar \mu, -\}$ annihilates the second two terms in the above action. 
The middle term in \eqref{eqn:bvonshell} can be rewritten as $\frac12 \int \gamma \wedge \{\mu, \mu\}$. 
From this observation, the equation 
\beqn\label{eqn:cmeos1}
\left\{\frac12 \int^\Omega \mu \wedge \mu \wedge \div \gamma, \frac12 \int^\Omega \mu \wedge \mu \wedge \div \gamma \right\} = 0
\eeqn
follows from the Jacobi identity for the Schouten bracket. 
Next, we have
\begin{multline}
\left\{\frac12 \int^\Omega \mu \wedge \mu \wedge \div \gamma, \frac16 \int^\Omega \gamma \wedge \big[\div \gamma \vee (\div \gamma \vee \Omega) \big] \right\} = \int^\Omega \mu \wedge \div \gamma \wedge \big[\div \gamma \vee (\div \gamma \vee \Omega) \big] \\ + ??
\end{multline}
%Since $\mu$ is divergence-free, the Lagrangian on the right hand side is a total derivative. 
Integrating by parts, we see that this can be written as
\[ 
\int^\Omega \gamma \wedge \{\mu, \big[\div \gamma \vee (\div \gamma \vee \Omega) \big]\} + \int^\Omega \mu \wedge \gamma \wedge \div \big[\div \gamma \vee (\div \gamma \vee \Omega) \big] + ?? .
\]
The second term vanishes by Lemma \ref{lem:divfree}, thus 
\beqn\label{eqn:cmeos2}
\left\{\frac12 \int \div \gamma \mu^2 , \frac16 \int \gamma [\div \gamma \vee (\div \gamma \vee \Omega)]\right\} = 0 .
\eeqn
This piece of the master equation is equivalent to the relations
\begin{align*}
\{\mu, \div \gamma \vee (\div \gamma' \vee \Omega)\} & = \{\mu, \div \gamma\} \vee (\div \gamma' \vee \Omega) \pm \div \gamma \vee (\{\mu, \div \gamma'\} \vee \Omega) \\
0 & = \{\gamma, \div \gamma' \vee (\div \gamma'')\} + perm .
\end{align*}
for $\mu$ divergence-free.

In conclusion, we see that the simplified BV action \ref{eqn:bvonshell} does satisfy the classical master equation.

\begin{prop}
The full BV action \eqref{eqn:bvaction} satisfies the classical master equation.
\end{prop}
\begin{proof}
The claim follows from the following series of relations
\beqn\label{eqn:cme1}
\left\{\int^\Omega \beta \div \mu,\frac12 \int^\Omega e^\nu \mu \wedge \mu \wedge \div \gamma\right\} + \left\{\frac12 \int^\Omega e^\nu \mu \wedge \mu \wedge \div \gamma, \frac12 \int^\Omega e^\nu \mu \wedge \mu \wedge \div \gamma \right\} = 0
\eeqn
\end{proof}

\section{Kodaira--Spencer theory with potentials}

Let
\[
\cE_{\rm KS} = \PV^{\bu,\bu} [[u]] [2] .
\]
be the full space of fields of Kodaira--Spencer theory.

Suppose that $d \ne 3$ and consider the subspace $\cE \subset \cE_{\rm KS}$ of Kodaira--Spencer fields
\[
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots &&  \\
\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & & \subset & \cE_{\rm KS} \\
& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots & &  .
\end{tikzcd}
\]
%We will write the fields in the above decomposition as $(\eta, \mu, u \nu) \in \cE$. 
This is a subcomplex equipped with differential $\dbar - u \div$.

The trace pairing leads to isomorphisms
\begin{align*}
\cE^\vee_{\rm KS} & \cong u^{-1} \Bar{\PV} [u^{-1}] [2d-4] \\
\Bar{\cE}^\vee_{\rm KS} & \cong u^{-1} \PV [u^{-1}] [2d-4]
\end{align*} 
where we identify the dual of $\CC[[u]]$ with $u^{-1} \CC[u^{-1}]$ by the residue pairing. 
Similarly, for the subspace $\cE \subset \cE_{\rm KS}$ we see that $\cE^\vee$ is 
\[
\begin{tikzcd}
\ul{??} & \ul{??} & \cdots & \ul{??} & \ul{??}  \\
u^{-d+1}\Bar{\PV}^{d,\bu} \ar[r] & u^{-d+2}\PV^{d-1,\bu} \ar[r] & \cdots & & & \\
& & & u^{-2} \Bar{\PV}^{d, \bu} \ar[r] & u^{-1} \PV^{d-1, \bu} & .
\end{tikzcd}
\]
There is a similar presentation for $\Bar{\cE}^\vee$. 
%\begin{align*}
%\cE^\vee & \cong u^{-1} \Bar{\PV}^{d,\bu}[2d-4] \oplus u^{-1} \Bar{\PV}^{d-1,\bu}[2d-3] \oplus u^{-2} \Bar{\PV}^{d,\bu} [2d-2] \\
%\Bar{\cE}^\vee & \cong u^{-1} \PV^{d,\bu}[2d-4] \oplus u^{-1} \PV^{d-1,\bu}[2d-3] \oplus u^{-2} \PV^{d,\bu}[2d-2]
%\end{align*}

The bracket on $\cO(\Bar{\cE}_{\rm KS})$ is constructed from the pairing on $\Bar{\cE}^\vee_{\rm KS}$ defined by
\beqn\label{eqn:pairing}
f(u) \alpha \otimes g(u) \beta \mapsto \frac1{2\pi \im} {\rm Res}_{u=0} u f(u) g(u) \, \int^\Omega (\div \alpha) \beta .
\eeqn
This induced a Poisson bracket on $\cO(\Bar{\cE}_{\rm KS})$ of degree $2d -5$.

\begin{lem} \label{lem:pairing}
This pairing descends to a well-defined pairing on $\Bar{\cE}^\vee$ and hence a Poisson bracket on $\cO(\Bar{\cE})$ of degree $2d-5$. 
The map 
\[
\cO(\Bar{\cE}_{\rm KS}) \to \cO(\Bar{\cE})
\]
intertwines the resulting Poisson brackets. 
\end{lem}
\begin{proof}
\end{proof}

The BCOV action $I_{\rm BCOV} \in \oloc(\cE_{\rm KS})$ 
satisfies the classical master equation.
%\[
%Q I_{\rm BCOV} + \frac12 \{I_{\rm BCOV}, I_{\rm BCOV}\} = 0.
%\]
Let $I \in \oloc(\cE)$ denote the restriction of $I_{\rm BCOV}$ to the subspace $\cE$.
By Lemma \ref{lem:pairing} the local functional $I$ satisfies the classical master equation
\beqn\label{eqn:IE}
Q I + \frac12 \{I,I\} = 0 , \qquad {\rm in } \quad \oloc(\cE).
\eeqn

\subsection{}

Let $\til{\cE}$ denote the cochain complex of vector bundles
\beqn\label{eqn:tilE}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & \cdots & & \\
& & & u^{-1} \PV^{d, \bu} \ar[r] & \PV^{d-1, \bu} 
\end{tikzcd}
\eeqn
There is a non-degenerate pairing on this complex of bundles defined by 
\[
(f(u) \alpha, g(u) \beta) \mapsto {\rm Res}_{u=0} \frac{f(u) g(u)}{u} \int^\Omega \alpha \wedge \beta .
\]
This pairing is graded anti-symmetric of degree $-2d+5$ and so induces a Poisson bracket on $\oloc(\til\cE)$ of degree $2d-5$.

Define the map
\[
\Phi\colon \til\cE \to \cE 
\]
as follows:
\begin{itemize}
\item on the first line of \eqref{eqn:tilE} the map $\Phi$ is the identity. 
\item on the second line of \eqref{eqn:tilE} the map is
\[
\Phi(f(u) \otimes \alpha) = {\rm Res}_{u=0} \frac{f(u)}{u} \partial \alpha .
\]
\end{itemize}

\begin{prop}
The map $\Phi$ induces a cochain map
\[
\Phi^* \colon \oloc(\cE) \to \oloc(\til \cE) 
\]
which intertwines the graded Poisson brackets. 
\end{prop}

As a corollary of this result we obtain from the BCOV action a local functional 
\[
\til I = \Phi^* I \in \oloc(\til\cE)
\] 
which solves the classical master equation
\[
Q \til I + \frac12 \{\til I, \til I\} = 0, \qquad {\rm in } \quad \oloc(\til \cE) .
\]

\end{document}

### 2021-07-13 residual.tex
flux

% Created 2020-10-14 Wed 14:51
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{macros-mtheory}
\usepackage{cmupint}

\author{Surya and Brian}
\date{\today}
\title{Twisted \(M\)-theory and its perturbative quantization.}
\hypersetup{
 pdfauthor={Surya and Brian},
 pdftitle={Twisted \(M\)-theory and its perturbative quantization.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.4)}, 
 pdflang={English}}

\def\pv{{\rm PV}}
\def\PV{{\rm PV}}
\def\T{{\rm T}}
\def\del{\partial}
\def\hotimes{\, \otimes \,}
\def\ep{\epsilon}
\def\div{\partial_{\Omega}}
\def\m2{\mathfrak{m}2\mathfrak{brane}}
\def\susy{\mathfrak{susy}}
\def\so{\mathfrak{so}}
\def\siso{\mathfrak{siso}}
\def\fsl{\mathfrak{sl}}
\def\lie#1{\ensuremath{\mathfrak{#1}}}

\begin{document}

\maketitle
\tableofcontents

\section{Residual supersymmetry}

Recall, the (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
\[
  \ft_{11d} = V \oplus \Pi S
\]
where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
this decomposes into three irreducibles, 
\beqn\label{eqn:decomp}
  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
\eeqn
Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
The bracket in $\ft_{11d}$ is defined using the first projection
\[
[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
\]
The super Poincar\'{e} algebra is
\[
  \siso_{11d} = \so(11 , \CC) \ltimes \ft_{11d} .
\]
The $R$-symmetry is trivial in 11-dimensional supersymmetry.

We recall the so-called M2 brane central extension of the super Poincar\'e algebra.
Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.  
Let
\[
  \Gamma_{\wedge^2} : \Sym^2(S) \to \wedge^2 V \subset \Omega^2(\RR^{11}) 
\]
be the $\lie{so}(11,\CC)$-equivariant projection onto the $\wedge^2 V$ summand.

The super dg Lie algebra $\m2$ is the central extension of $\siso_{11d}$ by the cocycle
  \[
    c_{M2} \in \clie^2\left(\siso_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
  \]
  defined by the formula 
  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$ as in the decomposition \eqref{eqn:decomp}.

Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$ for which we use to perform the a holomorphic twist of 11-dimensional supergravity.  
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
We can decompose the algebra into $\lie{sl}(5)$ representations, using the isomorphisms
\deq{
  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
}
As $\fsl(L) = \fsl(5)$-modules we have
\[
V = L \oplus L^\vee \oplus \CC_t
\]
and $\so(11, \CC)$ decomposes as
\[
\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
\]
Furthermore, the spinorial representation can be identified with
\[
S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
\]
The element $Q$ lives in the first summand.
Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.

\begin{prop}\label{prop:model}
Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
The cohomology $H^\bu(\m2^Q)$ is
\[
    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \wedge^3 L^\vee \oplus \CC\cdot c
  \]
whose elements we denote by $(v, m, \psi, c)$. 
\begin{itemize}
\item[(1)] 
Let $\fg$ denote the following dg Lie algebra which as a cochain complex is
\[
H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
\]
Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
The nontrivial Lie brackets are
\begin{align*}
[v,\lambda] & = \<v, \lambda\> \in \CC_c \\ 
[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v 
\end{align*}
where we use the isomorphism $\wedge^4 L \cong L^\vee$.
There is an $L_\infty$ map 
\[
\fg \to \m2^Q
\] 
which is a quasi-isomorphism of complexes.  
\item[(2)]
  The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is \brian{finish}
\end{itemize}
\end{prop}
\begin{proof}
The supercharge $Q$ is odd and of cohomological degree zero.
Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.

The cohomology of the non-centrally extended algebra was computed in \cite{SWpure}, we briefly recall the result. 
The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
So, as expected, of the translations only the holomorphic ones $L^\vee$ survive.
The map 
\[
[Q,-] \colon \lie{so}(11;\CC) \to S 
\] 
is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.

In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
This completes the calculation of the cohomology.

We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
It remains to declare where $\psi \in \wedge^2 L$ is mapped.

Define the map
\[
H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
\]
which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
\[
(H \alpha) (x) = \int_0^x \alpha .
\]

Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
\[
\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
\]
Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.

The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
On the other hand, in $\m2^Q$ there is the Lie bracket 
\[
[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
\]
The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
\[
v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
\] 
Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.

\end{proof}

Consider now the eleven-dimensional theory $\cT = \cT_{\CC^5 \times \RR}$ defined on $\CC^5 \times \RR$. 
The BV action induces the structure of a dg Lie algebra on $\cT[1]$.

\begin{prop}
The assignment
\brian{??} defines a map of $\ZZ/2$-graded dg Lie algebras 
\[
\m2 \to \cT[1] .
\]
In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
\end{prop}

\subsection{$L_\infty$ extension}

In this section we compare to the work of ??.
In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\siso_{11d}$.

Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
Using this two-form we can define the following four-linear expression
\[
\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
\]
This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
In \cite{??} it is shown that this cocycle $\mu_2$ is

\subsection{Embedding $\m2^Q$ in twisted supergravity}

In Proposition \ref{prop:model} we have proposed a dg model $\fg$ for the $Q$-deformed M2-brane algebra.

%For clarity we adjust notation for $\lie{sl}(5)$-representations. Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$. 
The model $\fg$ takes the following form
\beqn 
\begin{tikzcd}
\ul{even} & \ul{odd} & \ul{even} \\
 L_a & \wedge^2 L & L^\vee \\
\wedge^2 L & & \\
\lie{sl}(5) \\
L_b \ar[r, "\id"] & L_c .
\end{tikzcd}
\eeqn
The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.

The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
\begin{align*}
 \in L_a & \mapsto ?? \\
z_i \wedge z_j \in \wedge^2 L & \mapsto z_i \d z_j - z_j \d z_i \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
\end{align*}

\section{M5 brane}

The minimal twist of the abelian maximally supersymmetric tensor multiplet on $\RR^6$ was computed in \cite{SWpre}. 
The is a holomorphic field theory on $\CC^3$ and admits the following two descriptions in the BV formalism.

\begin{itemize}
\item Presymplectic. 
\[
(\alpha, \varphi) \in \Omega^{\leq 1, \bu}(\CC^3)[2] \oplus \Omega^{0,\bu}(\CC^3) \otimes \Pi R [1] .
\]
\item Poisson.
\[
(\chi, \varphi) \in \Omega^{\geq 2, \bu}(\CC^3)[1] \oplus \Omega^{0,\bu}(\CC^3) \otimes \Pi R [1].
\]
\end{itemize}

Explicitly, the fields of twisted 11-dimensional supergravity couple to the theory on M5 brane as follows:
\begin{itemize}
\item[(1)] The holomorphic vector fields $\frac{\partial}{\partial z_i}$ couple to the theory on the brane by the quadratic term
\[
\frac12 \int_{\CC^3} \chi \wedge \left(\frac{\partial}{\partial z_i} \vee \chi\right) + \frac12 \int_{\CC^3} \ep_{ab} \varphi_a \wedge \frac{\partial}{\partial z_i} \varphi_b .
\]
\item[(2)] The odd supercharges $\d z_i \otimes e_a$ couple to the theory on the brane by the quadratic term 
\[
\frac12 \int_{\CC^3} \ep_{ab} \chi \wedge \d z_i \wedge e_a \varphi_b .
\]
\end{itemize}

\subsection{Residual supersymmetry}

The residual $\cN=(2,0)$ supersymmetry algebra after performing the holomorphic twist is the $\ZZ/2$ graded algebra 
\[
Z \oplus \Pi (Z^\vee \otimes R)
\]
where $Z = \CC^3$ is the fundamental representation of $\lie{sl}(3)$. 
The bosonic summand consists of the holomorphic translations $\frac{\partial}{\partial z_i}$ and we schematically write a basis for the odd summand by $\d z_i \otimes e_a$ where $i=1,2,3$, $a=1,2$ and $\{e_1,e_2\}$ form a symplectic basis for $R$.  
The bracket is given by the composition 
\[
(Z^\vee \otimes R) \otimes (Z^\vee \otimes R) \to \wedge^2 Z^\vee \otimes \wedge^2 R \xto{1 \otimes \omega_R} \wedge^2 Z^\vee \cong Z
\]
where $\omega_R$ is the symplectic form on $R$. 
In our basis the bracket reads
\[
[\d z_i \otimes e_a, \d z_j \otimes e_b] = \ep_{ab} \ep_{ijk} \frac{\partial}{\partial z_k}.
\]

\begin{itemize}
\item[(1)] The bosonic holomorphic translations $\frac{\partial}{\partial z_i}$ couple to the theory on the brane by the quadratic term
\[
\frac12 \int_{\CC^3} \chi \wedge \left(\frac{\partial}{\partial z_i} \vee \chi\right) + \frac12 \int_{\CC^3} \ep_{ab} \varphi_a \wedge \frac{\partial}{\partial z_i} \varphi_b \wedge \d^3 z .
\]
\item[(2)] The odd supercharges $\d z_i \otimes e_a$ couple to the theory on the brane by the quadratic term 
\[
\frac12 \int_{\CC^3} \ep_{ab} \chi \wedge \d z_i \wedge e_a \varphi_b .
\]
\end{itemize}

\section{Sources for branes}

The leading term in the action of twisted supergravity in the presence of an M5 brane is
\[
blah
\]

\subsection{$D4$ branes in Type IIA}

In \cite{CLsugra} it is shown how $D2k$ branes couple to type IIA supergravity in the twisted situation. 
We have already shown how the dimensional reduction of 11-dimensional supergravity along a holomorphic circle $S^1 \subset \CC^\times$ is equivalent to the $\SU(4)$ invariant twist of type IIA supergravity
\[
\CC^4 \times \RR^2 .
\]

In this twist, a D4 brane wraps 
\[
\{w_i = 0\} \times \CC^2 \times \RR \times \{t_2 = 0\} \subset \CC^4 \times \RR^2 .
\]
Along the brane the theory is given by mixed holomorphic-topological Chern--Simons theory with two odd variables $\ep_1,\ep_2$.

Recall that in the twist of type IIA supergravity are the fields
\begin{align*}
\mu & \in \Pi \PV^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2) \\
\pi & \in \PV^{2,\bu} (\CC^4) \otimes \Omega^{\bu}(\RR^2) .
\end{align*} 
\brian{we could probably do a better job with gradings, Ingmar?}
The relevant leading term in the action is
\[
\int_{\CC^4 \times \RR^2} \pi (\dbar + \d) \div^{-1} \mu + \int_{\CC^2 \times \RR} (\div^{-1} \mu) \vee \Omega .
\]
Notice that only the component of $\mu$ which is a polyvector field of type $(1,2)$ along $\CC^4$ and a one-form along $\RR^2$ appears in the second term above; denote this component by $\mu^{1,2;1}$.  
The components of $\pi$ which couple to this component of $\mu$ are $\pi^{2,2;1}$ and $\pi^{2,1;0}$---by this we mean a polyvector field of type $(2,2)$ (respectively $(2,1)$) along $\CC^4$ and a de Rham form of type $1$ (respectively $0$) along $\RR^2$.

We conclude that in the presence of a $D4$ brane, the linearized equations of motion for $\pi^{2,2;1}$ reads
\[
\d \pi^{2,2;0} + \dbar \pi^{2,1;1} = \Omega^{-1} \delta_{\CC^2 \times \RR} .
\]
where the distributional form $\Omega^{-1} \delta_{\CC^2 \times \RR}$ is the image of the $\delta$-distribution along the isomorphism
\[
\Omega^{-1} \colon \Bar{\Omega}^{2,2} (\CC^4) \hotimes \Bar{\Omega}^1 (\RR^2) \; \cong \; \Bar{\PV}^{2,2} (\CC^4) \hotimes \Bar{\Omega}^1 (\RR^2) 
\]
determined the Calabi--Yau form.

An explicit solution to the equations of motion for $\pi$ is 
\[
\pi_{BR} = \pi^{2,2;0} + \pi^{2,1;1} = \# \frac{1}{r^5} \left(t \d \wbar_1 \d \wbar_2 - \wbar_1 \d t \d \wbar_2 + \wbar_2 \d t \d \wbar_1\right) \frac{\partial}{\partial z_1} \frac{\partial}{\partial z_2} .
\]

\end{document}

### 2021-07-30 g2twist.tex
g2update

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory,amsaddr}

\addbibresource{cfs.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\author{Surya and Brian}
\date{\today}
\title{Twisted \(M\)-theory and its perturbative quantization.}
\hypersetup{
 pdfauthor={Surya and Brian},
 pdftitle={Twisted \(M\)-theory and its perturbative quantization.},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.4)}, 
 pdflang={English}}

\begin{document}

\maketitle
%\tableofcontents

\section{G2 twist}

\paragraph{We consider the eleven-dimensional theory on the space
\[
  Z \times X \times \RR
\]
where $Z$ is a hyper-K\"{a}hler surface and $X$ is a Calabi--Yau three-fold.
Denote by 
\[
\omega_Z^{2,0} \in \Omega^{2,0}_Z , \quad \Omega_X \in \Omega^{3,0}_X
\]
the holomorphic symplectic form on $Z$ and the holomorphic volume form on $X$, respectively.
We will work in a background where the $(1,0)$-component of the field $\gamma$ satisfies the following equations:
\begin{equation}\label{eqn:background}
  \begin{array}{rcccc}
    \partial \gamma^{1,0} & = & \omega_Z^{2,0} \\
    \dbar \gamma^{1,0} + \d_{\RR} \gamma^{1,0} & = & 0 .
  \end{array}
\end{equation}
The second equation implies that $\gamma^{1,0}$ is constant along $\RR$ and holomorphic along $X \times Z$.
The first equation says that $\gamma^{1,0}$ is a trivialation of the holomorphic volume form on $Z$.}

\paragraph{To see that this is a consistent background of the eleven-dimensional theory we must check that $\gamma^{1,0}$ satisfies the appropriate equations of motion.}

\begin{lem}
  Any field $\gamma^{1,0}$ satisfying the equations in (\ref{eqn:background}) satisfies the equations of motion of the eleven-dimensional theory.
\end{lem}

\begin{proof}
  We must show that $\gamma^{1,0}$ satisfies the following Maurer--Cartan equation
  \[
    Q_{\rm BRST} \gamma^{1,0} + \frac12 [\gamma^{1,0} ,\gamma^{1,0}] = 0
  \]
  where $Q_{\rm BRST}$ is the linear BRST operator and $[-,-]$ is the Lie bracket defining the interacting piece of the eleven-dimensional theory.

Recall, the linear BRST differential is of the form
  \[
    \dbar + \partial_{\Omega} + \partial_{\Omega^0 \to \Omega^1} + \d_{\rm dR}
  \]
  Here, $\partial_\Omega$ is the divergence operator which only acts on the $\mu$-type fields and $\partial_{\Omega^0 \to \Omega^1}$ is the first piece of the holomorphic de Rham operator acting on $\Omega^{0,\bu}(X \times Z)$.
  Since $(\dbar + \d_{\rm dR}) \gamma^{1,0} = 0$ by assumption, we see that $\gamma^{1,0}$ is closed for the linear BRST operator.

The only component of the Lie bracket involving two fields of type $\gamma$ is of the form
  \[
    [\gamma, \gamma] = (\partial \gamma \wedge \partial \gamma) \vee (\Omega_X \wedge \Omega_Z) \in \PV^{1,\bu}(X \times Z) \; \Hat{\otimes} \; \Omega^\bu(L) .
  \]
  Since $\partial \gamma^{1,0}$ is a $(2,0)$ form along $Z$, we see that $\partial \gamma^{1,0} \wedge \partial \gamma^{1,0} =0$.
  We conclude that $\gamma^{1,0}$ satisfies the Maurer--Cartan equation.
\end{proof}

Next, we expand the action functional near the background where $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying Equation \eqref{eqn:background}.
This will generate new kinetic and interacting terms which we can extract by inserting a formal parameter $\delta$ and expressing the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.

There are two types of interactions in the original theory.
The first is
\begin{equation}\label{eqn:int1}
  \frac12 \int_{X\times Z \times L} \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_X)
\end{equation}
and the second is
\begin{equation} \label{eqn:int2}
  \frac16\int_{X \times Z \times L} \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma .
\end{equation}

%We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.\brian{there might be some factors I'm being sloppy with here}
Expanding \eqref{eqn:int1} around the field configuration $\gamma \to \gamma + \delta \gamma^{1,0}$ we obtain
\[
  \frac12 \int \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_X) + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\omega_Z \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_X) .
\]
Here, we have used the equation of motion $\partial \gamma^{1,0} = \Omega_Z$.
It will be convenient to further expand this into the components $\mu_X, \mu_Y, \gamma_X, \gamma_Y$:
\begin{multline}
 \int \frac{1}{1-\nu} \left(\frac12 \del^X \gamma_X \vee \mu_X^2  + \del^Z \gamma_X \vee \mu_X \mu_Z + \del^X \gamma_Z \vee \mu_X\mu_Z + \frac12 \del^Z \gamma_Z \vee \mu_Z^2 \right) \wedge (\omega_Z \wedge \Omega_X) 
 \\
  \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\omega_Z \vee \mu_Z^2 \right) \wedge (\omega_Z \wedge \Omega_X) .
  \label{eqn:delta1}
\end{multline}

Next, we expand Equation (\ref{eqn:int2}) around $\gamma \to \Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
This is
\[
  \frac16 \int \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma \partial \gamma\right) \wedge \omega_Z .
\]
Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
Again, we further expand this into holomorphic components along $X,Z$:
\begin{multline}
\frac16 \int \frac{1}{1-\nu} \left(\gamma_X \partial^Z \gamma_X \partial^Z \gamma_X +\gamma_X \partial^X \gamma_X \partial^Z \gamma_Z +  \gamma_X \partial^X \gamma_Z \partial^X \gamma_Z \right)
\\
\frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma_X \partial^X \gamma_X \right) \wedge \omega_Z 
\label{eqn:delta2}
\end{multline}

So far, we have written everything in terms of action functionals.
There is a completely equivalent statement in terms of the resulting dg Lie algebra structure describing the eleven-dimensional theory in this background which we summarize as follows.

\begin{lem} \label{lem:background}
  The dg Lie algebra describing the eleven-dimensional theory placed in a background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is isomorphic to the the dg Lie algebra whose differential is
  \begin{equation}\label{eqn:newdiff}
    Q_{\rm BRST} + \frac{1}{2} \left\{ \int \left[\Omega_Z \vee (\mu \wedge \mu) \right] \wedge (\Omega_Z \wedge \Omega_X) + \int \left(\gamma \partial \gamma\right) \wedge \Omega_Z , \; - \; \right\}
  \end{equation}
  and whose Lie bracket is unchanged.
  Here, $Q_{\rm BRST}$ is the original linear BRST differential of the eleven-dimensional theory.
\end{lem}

This lemma followed directly from our analysis of the way the action functional of the theory decomposed around this particular background.
The next result we state is an equivalence with a theory which exists on any product of manifolds $Z \times M$ where $Z$ is a hyper-K\"{a}hler surface as above but now $M$ is any smooth seven-dimensional manifold.

\begin{prop}
  The eleven-dimensional theory on $Z \times X \times L$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma^{1,0}$ satisfying (\ref{eqn:background}) is equivalent to the $\ZZ/2$-graded theory whose fields are
\[
\alpha \in \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(X \times L) [1]
\]
  and whose action functional reads
  \[
    \frac12 \int_{Z \times X \times L} (\alpha \wedge \d\alpha) \wedge \omega_Z  + \frac16 \int_{Z\times X \times L} \alpha \wedge \{\alpha, \alpha\} \wedge \omega_Z
  \]
  where $\{-,-\}$ is the Poisson bracket induced from the symplectic form $\omega_Z$ on $Z$. 
\end{prop}

As stated in this proposition, it is clear that the theory does not depend on the complex structure on the Calabi--Yau three-fold $X$ even though this is not {\em a priori} obvious from the description in Lemma \ref{lem:background}. 
The theory only depends on the smooth structure on $M = X \times L$.
\brian{cite Surya and Phil, Chris and B, Kevin}

\begin{proof}
To unpack this new differential (\ref{eqn:newdiff}) in Lemma \ref{lem:background} we need to reidentify the fields of the eleven-dimensional theory.
Notice that polyvector fields on $Z \times X$ decompose as
\begin{equation}\label{eqn:decomposevf}
\begin{array}{ccccc}
  \PV^{1,\bu}_{Z \times X} & = & \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_X & \oplus & \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_X \\ 
  \PV^{0,\bu}_{Z \times X} & = & \PV^{0,\bu}_Z \hotimes \PV^{0,\bu}_X .
%  & \cong & \PV^{1,\bu}_Z \hotimes \Omega^{0,\bu} _X & \oplus & \Omega^{0,\bu}_Z \hotimes \Omega^{2,\bu}_X
\end{array}
\end{equation}
There is a similar decomposition for differential forms.
For a holomorphic vector field $\mu$ on $Z \times X$, we write $\mu = \mu_Z + \mu_X$ according to the above decomposition. 
Similarly, for a holomorphic one-form $\gamma$ on $Z \times X$, we write $\gamma = \gamma_Z + \gamma_X$ where $\gamma_Z, \gamma_X$ carry a holomorphic one-form component along $Z,X$, respectively.

Let $\div^X, \div^Z$ denote the divergence operators, with respect to the fixed holomorphic volume forms, acting on polyvector fields on $X,Z$, respectively. 
Similarly, let $\del^X, \del^Z$ denote the holomorphic de Rham operators on $X,Z$, respectively.

The new terms in the linear BRST differential arise from the quadratic terms in the action in Equations \eqref{eqn:delta1} and \eqref{eqn:delta2}:
\begin{equation}\label{eqn:newterms}
  \frac{\delta}{2} \int (\omega_Z \vee \mu_Z^2) \wedge (\omega_Z \wedge \Omega_X) + \frac{\delta}{2} \int \left(\gamma_X \wedge \partial^X \gamma_X \right) \wedge \omega_Z .
\end{equation}
Denote by $Q_{\gamma^{1,0}}$ the resulting new term in the linear BRST differential.

%Recall that the linear BRST complex of the original eleven-dimensional theory is obtained by taking the tensor product of the cochain complexes $\PV^{1,\bu}(X \times Z) \xto{\partial_\Omega} \PV^{0,\bu}(X \times Z)$ and $\Omega^{0,\bu}(X \times Z) \xto{\partial} \Omega^{1,\bu}(X \times Z)$ with the de Rham complex $\Omega^\bu(L)$ on the one-manifold $L$.
%Using the decomposition (\ref{eqn:decomposevf}) we see that the deformed linear BRST complex is the tensor product of the de Rham complex $\Omega^{\bu}(L)$ with the cochain complex

The deformed linear BRST complex is $(\cE, Q + \delta Q_{\gamma^{1,0}})$. 
That is, the linear BRST complex of the eleven-dimensional theory in the background specified by $\gamma^{1,0}$. 
This complex takes the form
\[
  \begin{tikzcd}
  & \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_X \ar[dr, "\div^Z"] \ar[dashed, rounded corners, to path={ -- ([yshift=-2ex]\tikztostart.west) |- ([xshift=-1.5ex]\tikztotarget.west) -- (\tikztotarget)}, dddddr]\\
  & & \PV^{0,\bu}_Z \hotimes \PV^{0,\bu}_X \\
 & \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_X \ar[ur, "\div^X"'] & \\
\;_{\cong}  & & \Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_X \ar[ul, dashed, bend left = 10, "\Omega^{-1}_X \partial^X"]\\
 & \Omega^{0,\bu}_Z \hotimes \Omega^{0,\bu}_X \ar[ur, "\partial^X"] \ar[dr,"\partial^Z"'] \\
  & & \Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_X
  %\ar[uuuuul, start anchor =  {[yshift = 0ex, xshift=0ex]}, end anchor = {[yshift=1.0ex, xshift=-5ex]}, bend left = 90, dotted] .
  \end{tikzcd}
\]

Here, the dashed arrow along the outside of the diagram corresponds to the BV antibracket with the first term in (\ref{eqn:newterms}).
It is given by the isomorphism 
\[
\Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_X \xto{\omega^{2,0}_Z \otimes \id} \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_X
\]
induced holomorphic symplectic form on $Z$. 
The other dashed arrow corresponds to the BV antibracket with the second term in (\ref{eqn:newterms}).
It is given by the composition
\[
\Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_X \xto{\id \otimes \del^X} \Omega^{0,\bu}_Z \hotimes \Omega^{2,\bu}_X \xto{\id \otimes \Omega_X} \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_X
\]
given by applying the holomorphic de Rham operator along $X$ followed by contracting with the inverse holomorphic volume form along $X$.

We identify this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L [-k] 
\eeqn
which is equipped with the differential $\dbar^Z + \dbar^X + \del^X + \d^L_{\dR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.

There is a map from this smaller BRST complex to the original defined by the following equations 
\begin{multline}
\mu_Z = \omega_Z^{-1} \del^Z \alpha^0, \quad \mu_X = \Omega_X^{-1} \alpha^2, \quad \nu = \Omega_X^{-1} \alpha^3 \\
\beta = \alpha^0, \quad \gamma_X = \alpha^1 , \quad \gamma_Z = 0 .
\end{multline}
This map is a quasi-isomorphism of linear BRST complexes.

Restricting the deformed BV action $I(\gamma+\gamma^{1,0})$ along this map we obtain a new interaction $\Tilde{I}(\alpha)$. 
It has the following form
\begin{multline}
\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
\end{multline}

More invariantly, we can write the total BV action as
\[
\Tilde{I} = I_{CS} + I' 
\]
where $I_{CS} = \frac16 \int \alpha\{\alpha,\alpha\}$ and 
\beqn
I' = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha [\alpha \vee (\alpha \vee \Omega_X^{-1})] + \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} .
\label{eqn:Iprime}
\eeqn

Consider the odd functional
\[
K = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] .
\]

\begin{lem}
$Q K + \{I_{CS}, K\} = I'$ .
\end{lem}
\begin{proof}
The linear differential applied to $K$ is 
\[
\frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] \omega_Z .
\]
This is the first term in \eqref{eqn:Iprime}.

Next, we compute
\[
\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} 
\]
which is the second term in \eqref{eqn:Iprime}. 
\end{proof}
\end{proof}
\end{document}

### 2021-08-04 draft.tex
draft

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory,amsaddr}

\addbibresource{cfs.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics, University of Edinburgh, Edinburgh, UK}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle

\section{The 11-dimensional theory}

\subsection{Divergence-free vector fields}

\subsection{A family of deformations}

%check CME

\subsection{Equations of motion}

%whatever we can say about the formal moduli space

\subsection{Boundary conditions}

%foreshadow the Horava--Witten picture

\subsection{One-loop quantization}

%cite result on thf quantization.

\section{Relationship to physical supergravity}

\subsection{Component fields}

%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.

\subsection{Residual supersymmetry}

%m2brane

\subsection{Superconformal algebras}

%6d suco 
%what about 3d N=8 suco?

\section{Dimensional reduction and compactifications}

\subsection{Relationship to the topological string}

%conjecture for minimal twist of IIA
%check the SU(4) twist

\subsection{The theory on a three-fold}

%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris

\section{The non-minimal twist}

\end{document}

### 2021-08-04 draft.tex
merge
update

@@
 
+In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
+The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
+
 \subsection{Divergence-free vector fields}
+
+\subsubsection{}
+We set up some notations and conventions in the context of complex geometry. 
+Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
+If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
+The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
+\[
+  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
+\]
+This is a free resolution for the sheaf of holomorphic sections of $V$.
+
+Suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
+The divergence $\div(\mu)$ of a holomorphic vector field $\mu$ is defined by the formula
+\[
+\div (\mu) \wedge \Omega = L_\mu (\Omega)
+\]
+where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
+
+Let $\T_X$ denote the holomorphic tangent bundle and consider its Dolbeault complex $\Omega^{0,\bu}(X , \T_X)$ resolving the sheaf of holomorphic vector fields. 
+The divergence operator extends to the Dolbeault complex to yield a map of cochain complexes 
+\[
+\div \colon \Omega^{0,\bu}(X , \T_X) \to \Omega^{0,\bu}(X) .
+\]
+
+The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0^{hol}(X)$.
+In fact, we can form the complex 
+\beqn\label{eqn:cplx1}
+\begin{tikzcd}
+\ul{0} & \ul{1} \\
+\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
+\end{tikzcd}
+\eeqn
+The $\dbar$ operator, as always, is left implicit. 
+By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect^{hol}_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
+
+There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
+Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
+The Lie bracket defined by the formulas
+\begin{align*}
+[\mu, \mu'] & = L_\mu \mu' \\
+[\mu, \nu] & = L_\mu \nu 
+\end{align*}
+is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.\footnote{This is a local dg Lie algebra, see \cite[??]{CG2}.}
+
+\subsubsection{}
+It will be convenient for us to cast this dg Lie algebra in a slightly different way.
+We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
+The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
+
+The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
+We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
+
+Let $X$ be a Calabi--Yau manifold of dimension $d$. 
+Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$. 
+In particular, $\PV^{k,j}(X)$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
+With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X)[-1]$ with differential $\dbar + \div$.
+
+Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
+\beqn\label{eqn:pv1}
+\PV^{\bu,\bu} (X) [[u]] [1]
+\eeqn
+with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
+With our conventions, notice that $u^l \PV^{k,j}(X)$ sits in cohomological degree $2l +k + j - 1$.
+
+The Schouten--Nijenhuis bracket 
+\[
+[-,-]_{NS} \colon \PV^{k,j} (X) \times \PV^{p,q} (X) \to \PV^{p+k-1,j+q} (X) 
+\]
+extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
+We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
+We refer to the further cohomological shift 
+\[
+\cE_{KS} = \PV^{\bu,\bu} (X) [[u]] [2]
+\]
+as the space of fields of Kodaira--Spencer theory.
+
+Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu}(X) \oplus u \PV^{0,\bu}(X)[1]$.
+
+\subsubsection{}
+
+\brian{bv bracket}
+
+\subsubsection{}
+
+Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_c$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
+
+\begin{thm}[\cite{CLbcov1}]
+The BCOV action 
+\[
+I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
+\]
+satisfies the classical master equation 
+\[
+Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_c = 0 .
+\]
+In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE)[-2d+5]$.
+\end{thm}
+
+This action induces the square-zero operator 
+\[
+\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
+\]
+acting on observables of the Kodaira--Spencer fields. 
+In other words, it defines a non-linear BRST operator; in turn it
+induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q = \dbar + u\div$.
+
+This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
+Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
+
+It is easiest to describe this automorphism at the level of observables.
+Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
+Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
+\[
+\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma]_{NS} .
+\]
+
+The non-linear change of coordinates relating the two structures is defined by
+\[
+\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
+\]
+where $[-]_+$ projects onto the non-negative powers of $u$.
+
+\subsubsection{}
+
+The complex resolving the (shift of) divergence-free vector fields 
+\[
+\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
+\]
+is a subcomplex of $\cE_{KS}$.
+If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
+In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
+
+If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{\rm KS}$ defined by:
+\[
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
+\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
+& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
+\end{tikzcd}
+\]
+And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
+Thus, we have the following.
+
+\begin{prop}
+\label{prop:tilbcov}
+The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
+\end{prop}
+%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
+
+\subsubsection{}
+
+Consider the following cochain complex $\cE$:
+\beqn\label{eqn:E}
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
+\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
+& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
+\end{tikzcd}
+\eeqn
+We will write the fields using the notation
+\begin{align*}
+(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
+(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
+\end{align*}
+
+Let 
+\[
+\begin{array}{rccc}
+\int^\Omega \colon \Omega^{0,\bu}(X) & \to & \CC [6] \\
+\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
+\end{array}
+\]
+be integration along the holomorphic volume form.
+
+Define the pairing 
+\[
+\omega \colon \cE_c \times \cE \to \cE [??] 
+\]
+by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$
+
+\brian{defines Poisson bivector $\Pi$.}
+
+\subsubsection{}
+
+Define the map of cochain complexes
+\[
+\Phi \colon \cE \to \til{\cE}_{KS}
+\]
+by the formulas
+\[
+\Phi (\mu,\nu) = \mu + u \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
+\]
+In the last expression we have used the isomorphism
+\[
+(-) \vee \Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu} 
+\]
+so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}$.
+
+\begin{prop}
+\label{prop:pot}
+The map $\Phi \colon  \cE \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
+In particular, it defines a map of dg Lie algebras
+\[
+\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE),\{-,-\}, Q \big)
+\]
+\end{prop}
+
+\begin{proof}
+prove this
+\end{proof}
+
+As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result.
+
+\begin{cor}
+The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE$:
+\begin{align*}
+I & = \Phi^* \til{I}_{BCOV} \\
+Q I + \frac12 \{I,I\} & = 0 .
+\end{align*} 
+\end{cor}
+
+\subsubsection{}
 
@@
 
+\section{The twisted $\Omega$-backround}
+
 \section{The non-minimal twist}

### 2021-08-04 draft.tex
merge

@@
 \subsubsection{}
+\label{sec:divfree}
 We set up some notations and conventions in the context of complex geometry. 
@@
 
-Let $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$. 
-In particular, $\PV^{k,j}(X)$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X)[-1]$ with differential $\dbar + \div$.
+Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
+Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
+In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
+With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
 
@@
 \beqn\label{eqn:pv1}
-\PV^{\bu,\bu} (X) [[u]] [1]
+\PV^{\bu,\bu} [[u]] [1]
 \eeqn
 with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}(X)$ sits in cohomological degree $2l +k + j - 1$.
+With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
 
@@
 \[
-[-,-]_{NS} \colon \PV^{k,j} (X) \times \PV^{p,q} (X) \to \PV^{p+k-1,j+q} (X) 
+[-,-]_{NS} \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
 \]
@@
 \[
-\cE_{KS} = \PV^{\bu,\bu} (X) [[u]] [2]
+\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
 \]
@@
 
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu}(X) \oplus u \PV^{0,\bu}(X)[1]$.
+Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
 
@@
 \]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE)[-2d+5]$.
+In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
 \end{thm}
@@
 
-Consider the following cochain complex $\cE$:
+Consider the following cochain complex $\cE_{pot}$:
 \beqn\label{eqn:E}
@@
 \[
-\omega \colon \cE_c \times \cE \to \cE [??] 
+\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
 \]
@@
 \[
-\Phi \colon \cE \to \til{\cE}_{KS}
+\Phi \colon \cE_{pot} \to \til{\cE}_{KS}
 \]
@@
 \]
-so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}$.
+so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
 
@@
 \label{prop:pot}
-The map $\Phi \colon  \cE \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
+The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
 In particular, it defines a map of dg Lie algebras
 \[
-\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE),\{-,-\}, Q \big)
+\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
 \]
@@
 \begin{cor}
-The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE$:
+The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
 \begin{align*}
-I & = \Phi^* \til{I}_{BCOV} \\
-Q I + \frac12 \{I,I\} & = 0 .
+I_{pot} & = \Phi^* \til{I}_{BCOV} \\
+Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
 \end{align*} 
@@
 \subsubsection{}
+
+Define the action by the group $\CC^\times$ on $\cE$ as follows. 
+Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
+The linear BRST operator is of weight zero and the pairing $\omega$ is of weight $+1$. 
+Thus, the shifted Poisson bracket $\{-,-\}$ is of $\CC^\times$ weight $-1$.
+
+\begin{lem}
+The restricted action $I_{pot} = \Phi^* I_{BCOV}$ has $\CC^\times$ weight $+1$. 
+In particular, the non-linear BRST operator 
+\[
+\delta_{pot} = Q_{pot} + \{I_{pot},-\}
+\]
+is $\CC^\times$ weight zero.
+\end{lem}
+
+Consider the cochain complex $\left(\oloc(\cE_{pot}) \, , \, \delta_{pot} \right)$ of all local functionals equipped with the non-linear BRST differential $\delta_{pot}$. 
+The $\CC^\times$ weight zero subcomplex is 
+\[
+\big(\oloc(\cE_{pot})^{(0)} \, , \, \delta_{pot} \big) = \big(\oloc(\cE_0) \, , \, \delta_{pot} \big) 
+\]
+where $\cE_0 = \PV^{1,\bu}[1] \oplus \PV^{0,\bu}$ is the subcomplex of the fields $\cE_{pot}$ consisting of just the $\mu$ and $\nu$ fields.
+
+\begin{prop}
+\label{prop:Linfty}
+The differential $\delta_{pot}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
+\[
+\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
+\]
+with $[-]_1 = \dbar + \div$. 
+Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
+\end{prop}
+
+\subsubsection{}
+
+The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
+Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
+
+We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
+Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
+The first few nonzero brackets are
+\begin{align*}
+[\mu]_1 & = \dbar \mu + \div \mu \\
+[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
+[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
+[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
+\end{align*}
+For $k \geq 2$ the general formula for the $k$-ary bracket is 
+\[
+[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
+\]
+
+\subsection{The 11-dimensional theory}
 

### 2021-08-05 draft.tex
descendant

@@
 If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{\rm KS}$ defined by:
-\[
+\beqn\label{eqn:tilks}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\eeqn
 And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
@@
 
+There is also a $\CC^\times$ action on the fields $\til{\cE}_{KS}$ of Kodaira--Spencer theory by declaring the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$.
+
 \begin{lem}
-The restricted action $I_{pot} = \Phi^* I_{BCOV}$ has $\CC^\times$ weight $+1$. 
+The restricted action $I_{pot} = \Phi^* \til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
 In particular, the non-linear BRST operator 
@@
 \end{lem}
+\begin{proof}
+The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $I_{BCOV}$ is weight $+1$. 
+We will make use of two gradings on $\til{\cE}_{KS}$. 
+The first is by holomorphic polyvector field type, and the second is by descendant degree.
+The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
+
+We introduce notation in this proof that won't be used later on. 
+Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
+If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
+If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
+
+A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is linear combination of functionals of the form
+\[
+\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
+\]
+Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
+In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
+\begin{align*}
+\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
+\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
+\end{align*}
+The first constraint ensures that the integrand is of top polyvector degree. 
+The second constraint is on the descendant degree, see \brian{ref above}.
+
+Simplifying these two equations, one finds the condition
+\[
+m+n-3 = m+(d-2)n - d 
+\]
+which implies $n=1$, as desired. 
+\end{proof}
 

### 2021-08-05 draft.tex
bf theory

@@
 \eeqn
-We will write the fields using the notation
+We will refer to the components of the fields using the notation
 \begin{align*}
@@
 \end{align*}
+The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree.
 
@@
 \begin{array}{rccc}
-\int^\Omega \colon \Omega^{0,\bu}(X) & \to & \CC [6] \\
+\int^\Omega \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
 \alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
@@
 be integration along the holomorphic volume form. 
-
 Define the pairing 
@@
 
-Define the map of cochain complexes
-\[
-\Phi \colon \cE_{pot} \to \til{\cE}_{KS}
-\]
+Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
 by the formulas
 \[
-\Phi (\mu,\nu) = \mu + u \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
+\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
 \]
-In the last expression we have used the isomorphism
-\[
-(-) \vee \Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu} 
-\]
+In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
 so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
@@
 
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is linear combination of functionals of the form
+A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
 \[
@@
 \subsubsection{}
+\label{sec:Linfty}
 
@@
 \subsection{The 11-dimensional theory}
+
+\subsubsection{}
+Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
+The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
+\begin{align*}
+[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
+[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
+\end{align*}
+
+We apply this construction to the case of the $L_\infty$ algebra $\cL_0 = \cL_0 (X)$ of \S \ref{sec:Linfty} resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ and the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
+We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
+One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.
+
+\subsubsection{}
+
+Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
+We recall the construction. 
+Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
+For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
+\[
+\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
+\]
+
+The fields of the associated BV theory are pairs
+\[
+  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
+\]
+Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
+The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.
+
+The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
 

### 2021-08-05 draft.tex
Linfty

@@
 \begin{proof}
-The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $I_{BCOV}$ is weight $+1$. 
+The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
 We will make use of two gradings on $\til{\cE}_{KS}$. 
@@
 \]
+
+We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
+The linear term $\Psi^{(1)} = \id$ is the identity map. 
+The higher terms $\Psi^{(n)}$ are defined by 
+\begin{align*}
+\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=2} \nu_1 \cdots \nu_{n-2} \mu_1 \mu_2 . \\
+\end{align*}
+\brian{someone check me}
 

### 2021-08-05 draft.tex
simpler

@@
 
-\subsubsection{}
+%\subsubsection{}
+%
+%Consider the following cochain complex $\cE_{pot}$:
+%\beqn\label{eqn:E}
+%\begin{tikzcd}
+%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
+%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
+%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
+%\end{tikzcd}
+%\eeqn
+%We will refer to the components of the fields using the notation
+%\begin{align*}
+%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
+%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
+%\end{align*}
+%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
+%
+%Let 
+%\[
+%\begin{array}{rccc}
+%\int^\Omega \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
+%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
+%\end{array}
+%\]
+%be integration along the holomorphic volume form. 
+%Define the pairing 
+%\[
+%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
+%\]
+%by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$
+%
+%\brian{defines Poisson bivector $\Pi$.}
+%
+%\subsubsection{}
 
-Consider the following cochain complex $\cE_{pot}$:
-\beqn\label{eqn:E}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-\end{tikzcd}
-\eeqn
-We will refer to the components of the fields using the notation
-\begin{align*}
-(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-\end{align*}
-The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree.
-
-Let 
-\[
-\begin{array}{rccc}
-\int^\Omega \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-\end{array}
-\]
-be integration along the holomorphic volume form. 
-Define the pairing 
-\[
-\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-\]
-by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$
-
-\brian{defines Poisson bivector $\Pi$.}
+%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
+%by the formulas
+%\[
+%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
+%\]
+%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
+%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
+%
+%\begin{prop}
+%\label{prop:pot}
+%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
+%In particular, it defines a map of dg Lie algebras
+%\[
+%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
+%\]
+%\end{prop}
+%
+%\begin{proof}
+%prove this
+%\end{proof}
+%
+%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
+%
+%\begin{cor}
+%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
+%\begin{align*}
+%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
+%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
+%\end{align*} 
+%\end{cor}
 
@@
 
-Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-by the formulas
-\[
-\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-\]
-In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-
-\begin{prop}
-\label{prop:pot}
-The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-In particular, it defines a map of dg Lie algebras
-\[
-\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-\]
-\end{prop}
-
-\begin{proof}
-prove this
-\end{proof}
-
-As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result.
-
-\begin{cor}
-The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-\begin{align*}
-I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-\end{align*} 
-\end{cor}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on $\cE$ as follows. 
-Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is of weight zero and the pairing $\omega$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}$ is of $\CC^\times$ weight $-1$.
-
-There is also a $\CC^\times$ action on the fields $\til{\cE}_{KS}$ of Kodaira--Spencer theory by declaring the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$.
+Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
+Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
+%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
+The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
+Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $-1$.
 
 \begin{lem}
-The restricted action $I_{pot} = \Phi^* \til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
+The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
 In particular, the non-linear BRST operator 
-\[
-\delta_{pot} = Q_{pot} + \{I_{pot},-\}
-\]
+\beqn\label{eqn:KSbrst}
+\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}
+\eeqn
 is $\CC^\times$ weight zero.
@@
 \begin{proof}
-The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
+%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
 We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is by holomorphic polyvector field type, and the second is by descendant degree.
+The first is holomorphic polyvector field type, and the second is descendant degree.
 The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
@@
 
-Consider the cochain complex $\left(\oloc(\cE_{pot}) \, , \, \delta_{pot} \right)$ of all local functionals equipped with the non-linear BRST differential $\delta_{pot}$. 
+Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
 The $\CC^\times$ weight zero subcomplex is 
 \[
-\big(\oloc(\cE_{pot})^{(0)} \, , \, \delta_{pot} \big) = \big(\oloc(\cE_0) \, , \, \delta_{pot} \big) 
+\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
 \]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus \PV^{0,\bu}$ is the subcomplex of the fields $\cE_{pot}$ consisting of just the $\mu$ and $\nu$ fields.
+where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
 
@@
 \label{prop:Linfty}
-The differential $\delta_{pot}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
+The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
 \[
@@
 \begin{align*}
-\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=2} \nu_1 \cdots \nu_{n-2} \mu_1 \mu_2 . \\
+\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
 \end{align*}

### 2021-08-05 draft.tex
dumb merge

@@
 
-\section{The 11-dimensional theory}
+\section{A family of moduli spaces}
 
@@
 \[
-[-,-]_{NS} \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
+[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
 \]
@@
 
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_c$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
+Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
 
@@
 \[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_c = 0 .
+Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
 \]
@@
 In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q = \dbar + u\div$.
+induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
 
@@
 \[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma]_{NS} .
+\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
 \]
@@
 
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{\rm KS}$ defined by:
+If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
 \beqn\label{eqn:tilks}
@@
 The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $-1$.
+Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
 
 \begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $+1$. 
+The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
 In particular, the non-linear BRST operator 
 \beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}
+\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
 \eeqn

### 2021-08-05 draft.tex
typos
all chopped up

@@
 is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.\footnote{This is a local dg Lie algebra, see \cite[??]{CG2}.}
+
+\parsec 
+\ingmar{a section defining polyvector fields; not sure where this belongs}
+Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
+\deq{
+  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
+}
+\ingmar{Wedges look super fucked up}
+The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
+Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
+We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
+
+\parsec[sec:Linfty]
+
+Recall that an $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
+\deq{
+  \Phi^*: C^\bu(\cL') \to C^\bu(\cL)
+}
+between their respective Lie algebra cochains.
+It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra $C^\bu(\cL)$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\d_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.
+
+Let $\cL$ be the 
+We consider the following two automorphisms
+
+The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
+Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
+
+We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
+Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
+The first few nonzero brackets are
+\begin{align*}
+[\mu]_1 & = \dbar \mu + \div \mu \\
+[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
+[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
+[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
+\end{align*}
+For $k \geq 2$ the general formula for the $k$-ary bracket is 
+\[
+[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
+\]
+
+We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
+The linear term $\Psi^{(1)} = \id$ is the identity map. 
+The higher terms $\Psi^{(n)}$ are defined by 
+\begin{align*}
+\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
+\end{align*}
+\brian{someone check me}
+
+\subsection{Theories of BF type}
+
+\subsubsection{}
+Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
+The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
+\begin{align*}
+[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
+[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
+\end{align*}
+
+We apply this construction, taking $\lie{g}$ to be the sheaf of dg Lie algebras resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$, as discussed above, and $A$ to be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
+We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
+One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.
+
+\subsubsection{}
+
+Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
+We recall the construction. 
+Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
+For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
+\[
+\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
+\]
+
+The fields of the associated BV theory are pairs
+\[
+  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
+\]
+Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
+The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.
+
+The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
+
+\parsec
+For concreteness, we recall that the fields of the theory we have constructed on $\C^{2k+1}\times\R$ are given by the sheaf $\cE$ presented in the following diagram:
+\begin{equation}
+  \label{eq:sympfields} 
+  \begin{tikzcd}[row sep = 1 ex]
+    -n & -n + 1 & -1 & 0 \\ \hline
+    \Omega^{0}(X;L) \ar[r] & \Omega^{1}(X;L) & 
+     \PV^{1}(X; L) \ar[r] & \PV^{0}(X; L).
+\end{tikzcd}
+\end{equation}
+We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^*(L), \dbar + \d_{dR}))$, so that the pairing beween $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$.
+As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
+\deq{
+  n = \dim_\C(X) + \dim_\R(L) - 1.
+}
+Note, though, that the interactions we consider do not preserve this grading, and as such only define $\Z/2\Z$-graded theories. We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
+
+Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above.
+Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on.
+The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket).
+This takes the form
+\deq{
+  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
+}
+The other action is of infinite order, and is related to the BCOV action functional via the procedure outlined above \ingmar{or somewhere}. Explicitly, this action functional is given by 
+\deq{
+  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2,
+}
+
+\subsection{A family of deformations}
+
+%check CME
+
+\subsection{Equations of motion}
+
+%whatever we can say about the formal moduli space
+
+\subsection{Boundary conditions}
+
+%foreshadow the Horava--Witten picture
+
+\subsection{One-loop quantization}
+
+%cite result on thf quantization.
+
+\subsection{Relation to BCOV theory}
 
@@
 
-\subsubsection{}
-\label{sec:Linfty}
-
-The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
-Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
-
-We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
-Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
-\end{align*}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\[
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
-\]
-
-We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
-The linear term $\Psi^{(1)} = \id$ is the identity map. 
-The higher terms $\Psi^{(n)}$ are defined by 
-\begin{align*}
-\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
-\end{align*}
-\brian{someone check me}
-
-\subsection{The 11-dimensional theory}
-
-\subsubsection{}
-Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
-The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
-\begin{align*}
-[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
-[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
-\end{align*}
-
-We apply this construction to the case of the $L_\infty$ algebra $\cL_0 = \cL_0 (X)$ of \S \ref{sec:Linfty} resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ and the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
-We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
-One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.
-
-\subsubsection{}
-
-Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
-We recall the construction. 
-Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
-For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
-\[
-\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
-\]
-
-The fields of the associated BV theory are pairs
-\[
-  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
-\]
-Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
-The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.
-
-The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
-
-\subsection{A family of deformations}
-
-%check CME
-
-\subsection{Equations of motion}
-
-%whatever we can say about the formal moduli space
-
-\subsection{Boundary conditions}
-
-%foreshadow the Horava--Witten picture
-
-\subsection{One-loop quantization}
-
-%cite result on thf quantization.
-
 \section{Relationship to physical supergravity}

### 2021-08-06 draft.tex
more hash

@@
 \author{Surya Raghavendran}
-\address{Perimeter Institute}
+\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
+Waterloo, Ontario N2L 2Y5\\ Canada}
 \email{??}
@@
 \author{Brian R. Williams}
-\address{School of Mathematics, University of Edinburgh, Edinburgh, UK}
+\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
 \email{brian.williams@ed.ac.uk}
@@
 \maketitle
+
+\newpage
 
@@
 
-Let $\cL$ be the 
-We consider the following two automorphisms
+Let $\cL$ be the sheaf~\eqref{eqn:cplx1} of dg Lie algebras resolving divergence-free vector fields constructed above.
+We consider the following automorphism of~$C^\bu(\cL)$, defined by its action on generators:\ingmar{notation for operators vs fields}
+\deq[eq:newbase]{
+%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
+    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^\nu \mu.
+}
+This map defines a new model of the local $L_\infty$ algebra, which we will call $\cL_\infty$.
+The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order.
+It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).
+\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
 
-The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
-Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
+%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
+%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
 
-We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
-Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
+%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
+We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
+Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
 The first few nonzero brackets are
@@
 }
-The other action is of infinite order, and is related to the BCOV action functional via the procedure outlined above \ingmar{or somewhere}. Explicitly, this action functional is given by 
+The other action is of infinite order. (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} Explicitly, this action functional is given by 
 \deq{
-  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2,
+  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2.
 }
 
+We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent.
+As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to a Poisson automorphism of the Lie algebra cochains of the BF theory, which defines an equivalence of cyclic $L_\infty$ algebras.
+\ingmar{how should we say this} Explicitly, the map is given by
+\deq{
+  \nu \mapsto 1-e^{-\nu}, \ldots
+}
 \subsection{A family of deformations}
@@
 %check CME
+
+\subsection{Further equivalences}
 

### 2021-08-06 draft.tex
merge

@@
 \end{align*}
-is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.\footnote{This is a local dg Lie algebra, see \cite[??]{CG2}.}
+is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
+We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.
 
-\parsec 
-\ingmar{a section defining polyvector fields; not sure where this belongs}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
+The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
+This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
 
@@
 
-Recall that an $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
+Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
+The Chevalley--Eilenberg cochain complex is 
+\[
+\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
+\]
+The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.
+
+An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
 \deq{
-  \Phi^*: C^\bu(\cL') \to C^\bu(\cL)
+  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
 }
 between their respective Lie algebra cochains.
-It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra $C^\bu(\cL)$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\d_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.
+It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.
 
-Let $\cL$ be the sheaf~\eqref{eqn:cplx1} of dg Lie algebras resolving divergence-free vector fields constructed above.
-We consider the following automorphism of~$C^\bu(\cL)$, defined by its action on generators:\ingmar{notation for operators vs fields}
+$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
+We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
 \deq[eq:newbase]{
 %    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
-    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^\nu \mu.
+    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
 }
-This map defines a new model of the local $L_\infty$ algebra, which we will call $\cL_\infty$.
+This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
+The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.
+
 The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
 It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).
-\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
 
@@
 \end{align*}
+\brian{coefficients}
 For $k \geq 2$ the general formula for the $k$-ary bracket is 
@@
 
-We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
-The linear term $\Psi^{(1)} = \id$ is the identity map. 
-The higher terms $\Psi^{(n)}$ are defined by 
-\begin{align*}
-\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
-\end{align*}
-\brian{someone check me}
+%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
+%The linear term $\Psi^{(1)} = \id$ is the identity map. 
+%The higher terms $\Psi^{(n)}$ are defined by 
+%\brian{someone check me}
+%\begin{align*}
+%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
+%\end{align*}
+
+\parsec
+There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
+\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
 
@@
 
-\subsubsection{}
-Suppose that $\fg$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\fg_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
-The graded vector space $\fg \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
+\parsec
+Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
+The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
 \begin{align*}
-[x \otimes a]_1 & = [x]^\fg_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
-[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\fg_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
+[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
+[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
 \end{align*}
 
-We apply this construction, taking $\lie{g}$ to be the sheaf of dg Lie algebras resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$, as discussed above, and $A$ to be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
-We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
-One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.
+We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
+The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
+
+We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
+These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.
 
@@
 We recall the construction. 
-Let $\cL$ be any local $L_\infty$ algebra, it is the sheaf of sections of some graded vector bundle $L$. 
+Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
 For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
@@
 
-The action functional reads $S_{\rm BF} = \int B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
+The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
+
+We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.
 
 \parsec
-For concreteness, we recall that the fields of the theory we have constructed on $\C^{2k+1}\times\R$ are given by the sheaf $\cE$ presented in the following diagram:
+For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
+In both cases, the space of fields equipped with the linear BRST operator is
 \begin{equation}
@@
     -n & -n + 1 & -1 & 0 \\ \hline
-    \Omega^{0}(X;L) \ar[r] & \Omega^{1}(X;L) & 
-     \PV^{1}(X; L) \ar[r] & \PV^{0}(X; L).
+    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
+     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
 \end{tikzcd}
 \end{equation}
-We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^*(L), \dbar + \d_{dR}))$, so that the pairing beween $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$.
+We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
+We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.
+
+The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
 As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
@@
 }
-Note, though, that the interactions we consider do not preserve this grading, and as such only define $\Z/2\Z$-graded theories. We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
 
-Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above.
-Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on.
-The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket).
-This takes the form
+We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.
+
+Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
 \deq{
-  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
+  S_\strict = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \int^\Omega \beta\partial_\Omega \mu + \frac{1}{2} \int^\Omega \gamma [\mu,\mu] + \int^\Omega \beta[\mu,\nu].
 }
-The other action is of infinite order. (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} Explicitly, this action functional is given by 
+As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.
+
+The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is of infinite order. 
+(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
+Explicitly, this action functional is
 \deq{
-  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2.
+  S_\infty = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \frac12 \int^\Omega \beta \partial_\Omega \mu + \int^\Omega\frac{1}{1-\nu} (\partial \gamma) \mu^2.
 }
@@
 We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent.
-As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to a Poisson automorphism of the Lie algebra cochains of the BF theory, which defines an equivalence of cyclic $L_\infty$ algebras.
-\ingmar{how should we say this} Explicitly, the map is given by
-\deq{
-  \nu \mapsto 1-e^{-\nu}, \ldots
-}
+As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
+Explicitly, the automorphism is
+\begin{multline}
+  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
+  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
+\end{multline}
 \subsection{A family of deformations}
@@
 \subsection{Relation to BCOV theory}
+
+\parsec[sec:pv] 
+\ingmar{a section defining polyvector fields; not sure where this belongs}
+Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
+\deq{
+  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
+}
+\ingmar{Wedges look super fucked up}
+The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
+Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
+We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
 
@@
 \[
-\int_\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
+\int^\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
 \]

### 2021-08-06 draft.tex
stuff merge

--- 2021-08-06 draft.tex
@@
 
+\parsec
 %check CME
+We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
+In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type.
+That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.
+
+Recall that such deformations are governed by the classical master equation: the parameterized family of actions $I + \alpha J$ is sensible only if 
+\deq{
+  \{I+ \alpha J, I + \alpha J \} = 0.
+}
+Since this must hold for all $\alpha$, and since the undeformed action $I$ is already a solution to the classical master equation, this reduces to the two conditions 
+\deq[eq:2cond]{
+  \{I,J\} = \{J,J\} = 0.
+}
+\begin{thm}
+  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, I_\infty)$ on $X \times L$ constructed above.
+The local functional
+  \deq{
+    J = \gamma (\del \gamma)^k,
+  }
+  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,I_\infty)$ as a $\Z/2\Z$-graded BV theory.
+\end{thm}
+\begin{proof}
+  First off, we consider grading issues.
+In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$.
+The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$.
+As such, we have
+  \deq{
+    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
+  }
+  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.
+
+  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}.
+It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
+It remains to check that $\{I_\infty,J\} = 0$.
+For the quadratic term, we note that
+  \deq{
+    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
+  }
+  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
+  \deq{
+    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
+}
+This expression is zero for symmetry reasons.
+Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form.
+We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form
+\end{proof}
 

### 2021-08-06 draft.tex
m2brane

@@
 \deq{
-  S_\strict = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \int^\Omega \beta\partial_\Omega \mu + \frac{1}{2} \int^\Omega \gamma [\mu,\mu] + \int^\Omega \beta[\mu,\nu].
+  S_\strict =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
 }
@@
 \deq{
-  S_\infty = \int^\Omega \beta (\dbar + \d_L) \nu + \int^\Omega \gamma (\dbar + \d_L) \mu + \frac12 \int^\Omega \beta \partial_\Omega \mu + \int^\Omega\frac{1}{1-\nu} (\partial \gamma) \mu^2.
+  S_\infty =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
 }
@@
 %\begin{array}{rccc}
-%\int^\Omega \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
+% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
 %\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
@@
 %\]
-%by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$
+%by the formula $ \gamma \vee \mu +  \beta \nu.$
 %
@@
 \[
-\int^\Omega \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
+ \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
 \]
@@
 
+\parsec[sec:susy]
+
+The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
+\[
+  \ft_{11d} = V \oplus \Pi S
+\]
+where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
+The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
+this decomposes into three irreducibles, 
+\beqn\label{eqn:decomp}
+  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
+\eeqn
+Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
+The bracket in $\ft_{11d}$ is defined using the first projection
+\[
+[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
+\]
+The super Poincar\'{e} algebra is
+\[
+  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
+\]
+The $R$-symmetry is trivial in 11-dimensional supersymmetry.
+
+\parsec[sec:m2brane]
+
+Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
+In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
+We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
+
+The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
+
+The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
+  \[
+    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
+  \]
+  defined by the formula 
+  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
+  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.
+
+We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
+
+\parsec[sec:m2branetwist]
+
+Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
+This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
+\brian{cite \cite{SWspinor}}
+We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
+
+Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
+We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
+\deq{
+  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
+}
+In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
+Also, $\lie{so}(11, \CC)$ decomposes as
+\[
+\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
+\]
+Furthermore, the spinorial representation can be identified with
+\[
+S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
+\]
+The element $Q$ lives in the first summand.
+Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
+This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
+
+\begin{prop}\label{prop:model}
+Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
+As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
+\[
+    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
+  \]
+whose elements we denote by $(v, m, \psi, c)$. 
+\begin{itemize}
+\item[(1)] 
+Let $\fg$ denote the following dg Lie algebra which as a cochain complex is
+\[
+H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
+\]
+Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
+The nontrivial Lie brackets are
+\begin{align*}
+[v,\lambda] & = \<v, \lambda\> \in \CC_c \\ 
+[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
+[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v 
+\end{align*}
+where we use the isomorphism $\wedge^4 L \cong L^\vee$.
+There is an $L_\infty$ map 
+\[
+\fg \rightsquigarrow \m2^Q
+\] 
+which is a quasi-isomorphism of complexes.  
+\item[(2)]
+  The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is \brian{finish}
+\end{itemize}
+\end{prop}
+\begin{proof}
+The supercharge $Q$ is odd and of cohomological degree zero.
+Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
+
+The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
+The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
+The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
+So, of the translations, only the holomorphic ones $L^\vee$ survive.
+The map 
+\[
+[Q,-] \colon \lie{so}(11,\CC) \to S 
+\] 
+is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
+The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
+
+In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
+This completes the calculation of the cohomology.
+
+We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
+The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
+The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
+It remains to declare where $\psi \in \wedge^2 L$ is mapped.
+
+Define the map
+\[
+H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
+\]
+which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
+\[
+(H \alpha) (x) = \int_0^x \alpha .
+\]
+
+Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
+It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
+\[
+\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
+\]
+Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.
+
+The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
+On the other hand, in $\m2^Q$ there is the Lie bracket 
+\[
+[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
+\]
+The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
+The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
+\[
+v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
+\] 
+Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.
+
+\end{proof}
+
+Consider now the eleven-dimensional theory $\cT = \cT_{\CC^5 \times \RR}$ defined on $\CC^5 \times \RR$. 
+The BV action induces the structure of a dg Lie algebra on $\cT[1]$.
+
+\begin{prop}
+The assignment
+\brian{??} defines a map of $\ZZ/2$-graded dg Lie algebras 
+\[
+\m2 \to \cT[1] .
+\]
+In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+\end{prop}
+
+\subsection{$L_\infty$ extension}
+
+In this section we compare to the work of \brian{refs}.
+In these references, the algebra $\m2$ is defined as an $L_\infty$  
+central extension of $\lie{siso}_{11d}$.
+
+Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
+Using this two-form we can define the following four-linear expression
+\[
+\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
+\]
+This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
+In \cite{??} it is shown that this cocycle $\mu_2$ is
+
+\subsection{Embedding $\m2^Q$ in twisted supergravity}
+
+In Proposition \ref{prop:model} we have proposed a dg model $\fg$ for the $Q$-deformed M2-brane algebra.
+
+%For clarity we adjust notation for $\lie{sl}(5)$-representations.
+Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
+The model $\fg$ takes the following form
+\beqn 
+\begin{tikzcd}
+\ul{even} & \ul{odd} & \ul{even} \\
+ L_a & \wedge^2 L & L^\vee \\
+\wedge^2 L & & \\
+\lie{sl}(5) \\
+L_b \ar[r, "\id"] & L_c .
+\end{tikzcd}
+\eeqn
+The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
+
+The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
+\begin{align*}
+ \in L_a & \mapsto ?? \\
+z_i \wedge z_j \in \wedge^2 L & \mapsto z_i \d z_j - z_j \d z_i \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
+\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
+\end{align*}
+
 \subsection{Superconformal algebras}

### 2021-08-06 draft.tex
blah blah blah

--- 2021-08-06 draft.tex
@@
 
-Recall that such deformations are governed by the classical master equation: the parameterized family of actions $I + \alpha J$ is sensible only if 
+Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
 \deq{
-  \{I+ \alpha J, I + \alpha J \} = 0.
+  \{S + g J, S + g J \} = 0.
 }
-Since this must hold for all $\alpha$, and since the undeformed action $I$ is already a solution to the classical master equation, this reduces to the two conditions 
+Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
 \deq[eq:2cond]{
-  \{I,J\} = \{J,J\} = 0.
+  \{S,J\} = \{J,J\} = 0.
 }
 \begin{thm}
-  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, I_\infty)$ on $X \times L$ constructed above.
+  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above.
 The local functional
@@
   }
-  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,I_\infty)$ as a $\Z/2\Z$-graded BV theory.
+  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
 \end{thm}

### 2021-08-09 draft.tex
merge

@@
 \deq{
-  S_\strict =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
+  S_0 =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
 }
@@
 \end{proof}
+
+\subsection{An alternative description} 
+So far, we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
+The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
+
+There is a related, alternative description of this formal moduli space which is almost equivalent. 
+Consider the resolution of holomorphic closed two-forms 
+\beqn\label{eqn:twoform}
+\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
+\eeqn
+where we have left the $\dbar$-differential implicit, as always.
+
+There is a map from the two-term complex 
+\[
+\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
+\]
+to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
+This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
+
+Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
+\[
+\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
+\]
+Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
+The left-hand side contains the fields $(\beta, \gamma)$. 
+This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
+
+The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolutoin of closed two-forms. 
+The new space of fields is 
+\begin{equation}
+  \label{eq:poissfields} 
+  \begin{tikzcd}[row sep = 1 ex]
+     - & + & - & + \\ \hline
+     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
+     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
+\end{tikzcd}
+\end{equation}
+
+\begin{prop}
+The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory. 
+\end{prop}
+
+Heuristically, we can write the action in the following non-local form
+\[
+\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
+\]
+
+\subsection{Global symmetry algebra}
 
@@
 whose elements we denote by $(v, m, \psi, c)$.
-\begin{itemize}
-\item[(1)] 
-Let $\fg$ denote the following dg Lie algebra which as a cochain complex is
+
+The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
+\begin{align*}
+[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
+[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
+\end{align*}
+\end{prop}
+
+\parsec[]
+
+As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
+Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
+
+\begin{prop}
+\label{prop:gmodel}
+Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
 \[
@@
 \begin{align*}
-[v,\lambda] & = \<v, \lambda\> \in \CC_c \\ 
+[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
 [v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
-[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v 
+[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
 \end{align*}
-where we use the isomorphism $\wedge^4 L \cong L^\vee$.
 There is an $L_\infty$ map 
@@
 which is a quasi-isomorphism of complexes.  
-\item[(2)]
-  The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is \brian{finish}
-\end{itemize}
 \end{prop}
@@
 
-Consider now the eleven-dimensional theory $\cT = \cT_{\CC^5 \times \RR}$ defined on $\CC^5 \times \RR$. 
-The BV action induces the structure of a dg Lie algebra on $\cT[1]$.
+\parsec[]
+Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
 
 \begin{prop}
-The assignment
-\brian{??} defines a map of $\ZZ/2$-graded dg Lie algebras 
+There is a map of $\ZZ/2$-graded dg Lie algebras 
 \[
-\m2 \to \cT[1] .
+\fg \to \cL 
 \]
-In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
+In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
 \end{prop}
+\begin{proof}
+Recall the model $\fg$ takes the following form
+\beqn 
+\begin{tikzcd}
+\ul{even} & \ul{odd} & \ul{even} \\
+ L_a & \wedge^2 L_b & L^\vee \\
+\wedge^2 L_a & & \\
+\lie{sl}(5) \\
+L_b \ar[r, "\id"] & L_c .
+\end{tikzcd}
+\eeqn
+The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
 
-\subsection{$L_\infty$ extension}
+The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
+\begin{align*}
+ L_a & \mapsto 0 \\
+ \wedge^2 L_a & \mapsto 0 \\
+z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
+\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
+\end{align*}
+One immediately verifies that this is a map of dg Lie algebras. 
+\end{proof}
 
-In this section we compare to the work of \brian{refs}.
+\parsec[]
+
+In this section we compare to the work of \brian{Linfty refs}.
 In these references, the algebra $\m2$ is defined as an $L_\infty$  
@@
 
-\subsection{Embedding $\m2^Q$ in twisted supergravity}
-
-In Proposition \ref{prop:model} we have proposed a dg model $\fg$ for the $Q$-deformed M2-brane algebra.
-
 %For clarity we adjust notation for $\lie{sl}(5)$-representations.
 Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
-The model $\fg$ takes the following form
-\beqn 
-\begin{tikzcd}
-\ul{even} & \ul{odd} & \ul{even} \\
- L_a & \wedge^2 L & L^\vee \\
-\wedge^2 L & & \\
-\lie{sl}(5) \\
-L_b \ar[r, "\id"] & L_c .
-\end{tikzcd}
-\eeqn
-The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
-
-The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
-\begin{align*}
- \in L_a & \mapsto ?? \\
-z_i \wedge z_j \in \wedge^2 L & \mapsto z_i \d z_j - z_j \d z_i \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
-\end{align*}
 

### 2021-08-09 draft.tex
draft

@@
 The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
+Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
 \end{prop}
@@
 \]
+\brian{are there more terms involving higher forms?}
+
+The first few nonzero brackets are
+\begin{align*}
+[\mu]_1 & = \dbar \mu + \div \mu \\
+[\eta]_1 & = \dbar \eta + \del \eta \\ 
+[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
+[\mu, \eta]_2 & = \mu \vee \del \eta \\
+[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
+[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
+[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
+\end{align*}
+\brian{coefficients}
+For $k \geq 2$ the general formula for the $k$-ary bracket is 
+\begin{align*}
+[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
+[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
+[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
+\end{align*}
+
+\parsec[]
+Consider the theory on $\CC^3 \times \RR$. 
+There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
+
+\parsec[]
+Consider the theory on $\CC^5 \times \RR$.
+
+\begin{prop}
+There is a quasi-isomorphism of super $L_\infty$ algebras 
+\[
+E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
+\]
+This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
+\end{prop}
 
@@
 %cite result on thf quantization.
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belongs}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\subsubsection{}
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
 
@@
 
+\appendix
+
+\subsection{Relation to BCOV theory}
+
+\parsec[sec:pv] 
+\ingmar{a section defining polyvector fields; not sure where this belongs}
+Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
+\deq{
+  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
+}
+\ingmar{Wedges look super fucked up}
+The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
+Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
+We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
+
+\subsubsection{}
+It will be convenient for us to cast this dg Lie algebra in a slightly different way.
+We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
+The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
+
+The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
+We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
+
+Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
+Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
+In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
+With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
+
+Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
+\beqn\label{eqn:pv1}
+\PV^{\bu,\bu} [[u]] [1]
+\eeqn
+with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
+With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
+
+The Schouten--Nijenhuis bracket 
+\[
+[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
+\]
+extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
+We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
+We refer to the further cohomological shift 
+\[
+\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
+\]
+as the space of fields of Kodaira--Spencer theory.
+
+Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
+
+\subsubsection{}
+
+\brian{bv bracket}
+
+\subsubsection{}
+
+Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
+
+\begin{thm}[\cite{CLbcov1}]
+The BCOV action 
+\[
+I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
+\]
+satisfies the classical master equation 
+\[
+Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
+\]
+In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
+\end{thm}
+
+This action induces the square-zero operator 
+\[
+\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
+\]
+acting on observables of the Kodaira--Spencer fields. 
+In other words, it defines a non-linear BRST operator; in turn it
+induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
+
+This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
+Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
+
+It is easiest to describe this automorphism at the level of observables.
+Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
+Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
+\[
+\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
+\]
+
+The non-linear change of coordinates relating the two structures is defined by
+\[
+\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
+\]
+where $[-]_+$ projects onto the non-negative powers of $u$.
+
+\subsubsection{}
+
+The complex resolving the (shift of) divergence-free vector fields 
+\[
+\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
+\]
+is a subcomplex of $\cE_{KS}$.
+If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
+In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
+
+If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
+\beqn\label{eqn:tilks}
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
+\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
+& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
+\end{tikzcd}
+\eeqn
+And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
+Thus, we have the following.
+
+\begin{prop}
+\label{prop:tilbcov}
+The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
+\end{prop}
+%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
+
+%\subsubsection{}
+%
+%Consider the following cochain complex $\cE_{pot}$:
+%\beqn\label{eqn:E}
+%\begin{tikzcd}
+%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
+%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
+%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
+%\end{tikzcd}
+%\eeqn
+%We will refer to the components of the fields using the notation
+%\begin{align*}
+%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
+%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
+%\end{align*}
+%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
+%
+%Let 
+%\[
+%\begin{array}{rccc}
+% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
+%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
+%\end{array}
+%\]
+%be integration along the holomorphic volume form. 
+%Define the pairing 
+%\[
+%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
+%\]
+%by the formula $ \gamma \vee \mu +  \beta \nu.$
+%
+%\brian{defines Poisson bivector $\Pi$.}
+%
+%\subsubsection{}
+
+%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
+%by the formulas
+%\[
+%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
+%\]
+%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
+%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
+%
+%\begin{prop}
+%\label{prop:pot}
+%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
+%In particular, it defines a map of dg Lie algebras
+%\[
+%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
+%\]
+%\end{prop}
+%
+%\begin{proof}
+%prove this
+%\end{proof}
+%
+%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
+%
+%\begin{cor}
+%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
+%\begin{align*}
+%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
+%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
+%\end{align*} 
+%\end{cor}
+
 \end{document}

### 2021-08-09 draft.tex
suca

@@
 
+Choose a splitting 
+\[
+\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
+\]
+and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
+
+\begin{prop}
+The $Q$-twist of the 6d $\cN=(2,0)$ superconformal algebra is $\lie{osp}(6|1)$. 
+\end{prop}
+
+\parsec[]
+
+\begin{itemize}
+\item
+The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+\[
+\lie{sl}(4) \oplus \lie{sl}(2)
+\]
+which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+\item
+The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
+\[
+\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) , \quad i=1,2,3.
+\]
+
+\item
+The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
+rotations
+\[
+a_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5) , \quad (a_{ij}) \in \lie{sl}(3) .
+\]
+
+\item
+The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
+\[
+\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5)  .
+\]
+
+\item 
+The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
+\[
+z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) .
+\]
+
+\item 
+The bosonic summand $\lie{sl}(2)$ is mapped to the triple
+\[
+w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5).
+\]
+\end{itemize}
+
+\parsec[]
+
+The odd part of $\lie{osp}(6|1)$ is 
+\[
+\wedge^2 \CC^4 \otimes \CC^2 
+\]
+which we can write as $\wedge^2 W \otimes R$. 
+Let us further split $W = L \oplus \CC$, with $L = \CC^3$ the fundamental $\lie{sl}(3)$ representation. 
+Then the odd part decomposes as
+\[
+\wedge L \otimes R \oplus \wedge^2 L \otimes R .
+\]
+
+\begin{itemize} 
+\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
+It is mapped to the fields 
+\[
+z_i \d w_a \in \Omega^{1,0}(\CC^3) .
+\] 
+\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
+It is mapped to the fields
+\[
+\ep_{ij} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3) , \quad a = 1,2, \quad i,j = 1,2,3. 
+\]
+\end{itemize}
+
 %6d suco 
@@
 
-\subsubsection{}
+\parsec[]
 

### 2021-08-10 draft.tex
merge
dimensional reduction modulo proof

@@
 
-\subsection{Superconformal algebras}
+\subsection{Supersymmetric indices}
+
+\brian{SU(5) and SU(2) character calculations}
+
+\subsection{6d superconformal algebra and the M5 brane}
 
@@
 \begin{prop}
-The $Q$-twist of the 6d $\cN=(2,0)$ superconformal algebra is $\lie{osp}(6|1)$. 
+The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
 \end{prop}
@@
 
-\begin{itemize}
-\item
 The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
@@
 which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+\begin{itemize}
 
@@
 \[
-\wedge L \otimes R \oplus \wedge^2 L \otimes R .
+L \otimes R \oplus \wedge^2 L \otimes R .
 \]
@@
 \[
-z_i \d w_a \in \Omega^{1,0}(\CC^3) .
+z_i \d w_a \in \Omega^{1,0}(\CC^3),\quad a=1,2, \quad i =1,2,3.
 \] 
@@
 
-%6d suco 
+\subsection{3d superconformal algebra and the M2 brane}
+
 %what about 3d N=8 suco?
@@
 
-\section{The twisted $\Omega$-backround}
+\section{The twisted $\Omega$-background}
 
@@
 \appendix
+
+\section{BCOV stuff}
 

### 2021-08-10 dimred.tex

In this section we wish to demonstrate that our proposal for the interactions for twisted 11-dimensional supergravity agree with conjectural descriptions of twisted type IIA and type I supergravities due to \cite{CLSugra}. We begin by introducing certain variants of Kodaira-Spencer theory which will feature in the descriptions of twists of type IIA and type I.

\parsec[sec:SU(4)twist]

Let $X$ be a Calabi-Yau manifold. Recall the $\Z/2$ graded Poisson BV theory denoted $\cE_{KS}$ defined in section \surya{}. Let $\cE_{{mKS}}\subset \cE_{KS}$ denote the smallest subcomplex containing those fields with nonzero pairing under the Poisson tensor. Explicitly, we have that $cE_{mKS}$ is the sheaf of cochain complexes
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r] & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn

Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory. Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.

With this in hand the conjecture of \cite{CLSugra} takes the following form.

\begin{conj}
  Let $M$ be a real symplectic surface and $X$ a Calabi-Yau fourfold. The $SU(4)$-invariant twist of type IIA supergravity on $M\times X$ is the $\Z/2$-graded Poisson BV theory with fields \[\Omega^{\bu}(M)\otimes \cE_{mKS}.\] The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

\parsec[sec:IIApot]

Our goal is to compare the dimensional reduction of our 11d theory $\cE$ on $\R\times \C^{\times}\times X$ where $X$ is a Calabi-Yau 4-fold with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$. Doing so will require some additional modifications to the above conjectural description. Indeed, recall that in the physical theory, the components of the C-field in 11d that are not supported along the M-theory circle become the components of the Ramond-Ramond 2-form of type IIA. However, as noted in \cite{CLSugra} components of Ramond-Ramond fields do not appear as fields in Kodaira-Spencer theory; rather it is components of their field strengths that appear. Since components of the C-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

Minimal Kodaira-Spencer theory with potentials on a Calabi-Yau fourfold $X$ is defined to be the $\Z/2$-graded BV theory whose space of fields is the sheaf of cochain complexes $\cE_{pot}$
\beqn
\begin{tikzcd}
& {\PV^{0,\bu}}_\eta  \\
{\PV^{1,\bu}}_\mu \arrow[r, "u\div"] & {u\PV^{0,\bu}}_\nu \\
{u^{-1}\PV^{4,\bu}}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu}}_\gamma  \\
{\PV^{4,\bu}}_\theta &
\end{tikzcd}
\eeqn.

The interaction is given by \[I_{pot} = \int \frac{1}{1-\nu}(\mu\mu\del\gamma + \eta\del\gamma\del\gamma + \eta\mu\del\theta).\]

Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
\beqn
\begin{tikzcd}
                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation.

\parsec[sec:dimred]
The main result of this section is then as follows:

\begin{prop}
Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$. Consider the map of sheaves of cochain complexes \[\int : \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] Then $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
\end{prop}
\begin{proof}
  \surya{write this}
\end{proof}

### 2021-08-10 draft.tex
m2brane

@@
 
-The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
 \[
-\lie{sl}(4) \oplus \lie{sl}(2)
+\lie{sl}(4) \oplus \lie{sl}(2) .
 \]
 which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+The embedding of the bosonic piece can roughly be described as follows. 
+The Lie algebra $\lie{sl}(4)$ represents special conformal transformations along the plane $\CC^3_z$.
+Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
+The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
 
@@
 \[
-a_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5) , \quad (a_{ij}) \in \lie{sl}(3) .
+A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5) , \quad (A_{ij}) \in \lie{sl}(3) .
 \]
@@
 \] 
-
+Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
 \item 
@@
 \] 
-
+Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
 \item 
@@
 
+We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
+\[
+\CC_z \times \CC^4_w \times \RR .
+\]
+
+\parsec[]
+
+Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
+For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
+The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
+The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
+
+\begin{itemize}
+\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
+\[
+\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) .
+\]
+Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
+\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
+\[
+\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} , \quad (B_{ab}) \in \lie{sl}(4) .
+\]
+\end{itemize}
+
 %what about 3d N=8 suco?
@@
 
-%conjecture for minimal twist of IIA
-%check the SU(4) twist
+In this section we wish to demonstrate that our proposal for the interactions for twisted 11-dimensional supergravity agree with conjectural descriptions of twisted type IIA and type I supergravities due to \cite{CLSugra}.
+We begin by introducing certain variants of Kodaira-Spencer theory which will feature in the descriptions of twists of type IIA and type I.
+
+\parsec[sec:SU(4)twist]
+
+Let $X$ be a Calabi-Yau manifold.
+Recall the $\Z/2$ graded Poisson BV theory denoted $\cE_{KS}$ defined in section \surya{}.
+Let $\cE_{{mKS}}\subset \cE_{KS}$ denote the smallest subcomplex containing those fields with nonzero pairing under the Poisson tensor.
+Explicitly, we have that $\cE_{mKS}$ is the sheaf of cochain complexes
+\beqn
+\begin{tikzcd}
+                        &                          &                                     & {\PV^{0,\bu}}    \\
+                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
+                        & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
+{\PV^{3,\bu}} \arrow[r] & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
+\end{tikzcd}.
+\eeqn
+
+Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory.
+Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.
+
+With this in hand the conjecture of \cite{CLSugra} takes the following form.
+
+\begin{conj}
+  Let $M$ be a real symplectic surface and $X$ a Calabi-Yau fourfold.
+The $SU(4)$-invariant twist of type IIA supergravity on $M\times X$ is the $\Z/2$-graded Poisson BV theory with fields \[\Omega^{\bu}(M)\otimes \cE_{mKS}.\] The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
+\end{conj}
+
+\parsec[sec:IIApot]
+
+Our goal is to compare the dimensional reduction of our 11d theory $\cE$ on $\R\times \C^{\times}\times X$ where $X$ is a Calabi-Yau 4-fold with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$.
+Doing so will require some additional modifications to the above conjectural description.
+Indeed, recall that in the physical theory, the components of the C-field in 11d that are not supported along the M-theory circle become the components of the Ramond-Ramond 2-form of type IIA.
+However, as noted in \cite{CLSugra} components of Ramond-Ramond fields do not appear as fields in Kodaira-Spencer theory; rather it is components of their field strengths that appear.
+Since components of the C-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
+
+Minimal Kodaira-Spencer theory with potentials on a Calabi-Yau fourfold $X$ is defined to be the $\Z/2$-graded BV theory whose space of fields is the sheaf of cochain complexes $\cE_{pot}$
+\beqn
+\begin{tikzcd}
+{\rm even} & {\rm odd} \\ \hline
+& {\PV^{0,\bu}}_\eta  \\
+{\PV^{1,\bu}}_\mu \arrow[r, "u\div"] & {u\PV^{0,\bu}}_\nu \\
+{u^{-1}\PV^{4,\bu}}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu}}_\gamma  \\
+{\PV^{4,\bu}}_\theta &
+\end{tikzcd}
+\eeqn.
+
+The interaction is given by \[I_{pot} = \int \frac{1}{1-\nu}(\mu\mu\del\gamma + \eta\del\gamma\del\gamma + \eta\mu\del\theta).\]
+
+Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
+\beqn
+\begin{tikzcd}
+                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
+{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
+{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
+{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
+\end{tikzcd}.
+\eeqn
+This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation.
+
+\parsec[sec:dimred]
+The main result of this section is then as follows:
+
+\begin{prop}
+Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.
+Consider the map of sheaves of cochain complexes \[\int : \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] Then $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
+\end{prop}
+\begin{proof}
+  \surya{write this}
+\end{proof}
+
+\include{dimred.tex}
 

### 2021-08-10 draft.tex
suca

--- 2021-08-10 draft.tex
@@
 
+\begin{prop}
+The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
+\end{prop}
+
 Choose a splitting 
@@
 
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
 \parsec[]
 
-The even part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
 \[
-\lie{sl}(4) \oplus \lie{sl}(2)
+\lie{sl}(4) \oplus \lie{sl}(2) .
 \]
 which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+The embedding of the bosonic piece can roughly be described as follows. 
+The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
+Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
+The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
 
@@
 
-\subsection{Relationship to the topological string}
-
-%conjecture for minimal twist of IIA
-%check the SU(4) twist
+\include{dimred}
 

### 2021-08-10 draft.tex
test
merge

@@
 
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\subsection{6d superconformal algebra and the M5 brane}
+\section{Twisted supergavity on AdS space}
+
+\subsection{Superconformal algebras}
 
@@
 
+\subsection{The ${\rm AdS}_7 \times S^4$ background}
+
+\parsec[]
+
 Choose a splitting 
@@
 and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-\parsec[]
 
@@
 \[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) , \quad i=1,2,3.
+\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
 \]
@@
 \[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5) , \quad (A_{ij}) \in \lie{sl}(3) .
+A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
 \]
@@
 \[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5)  .
+\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
 \] 
@@
 \[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) .
+z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
 \] 
@@
 \[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5).
+w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
 \]
@@
 
-\parsec[]
-
-The odd part of $\lie{osp}(6|1)$ is 
-\[
-\wedge^2 \CC^4 \otimes \CC^2 
-\]
-which we can write as $\wedge^2 W \otimes R$. 
-Let us further split $W = L \oplus \CC$, with $L = \CC^3$ the fundamental $\lie{sl}(3)$ representation. 
+The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
+It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
 Then the odd part decomposes as
 \[
-L \otimes R \oplus \wedge^2 L \otimes R .
+L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
 \]
@@
 \[
-z_i \d w_a \in \Omega^{1,0}(\CC^3),\quad a=1,2, \quad i =1,2,3.
+z_i \d w_a \in \Omega^{1,0}(\CC^3) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
 \] 
@@
 \[
-\ep_{ij} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3) , \quad a = 1,2, \quad i,j = 1,2,3. 
+\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
 \]
@@
 
-\subsection{3d superconformal algebra and the M2 brane}
+\subsection{The ${\rm AdS}_4 \times S^7$ background}
+
+\parsec[]
+\brian{discuss coupling}
+
+\parsec[]
 
@@
 \]
+Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
+
+The differential form which sources this submanifold is an element
+\[
+\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
+\]
+Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
+\[
+\dbar \til{F} = \delta_{w=0} 
+\]
+where $\delta_{w=0}$ is the Dirac $\delta$-distributional along the submanifold $\{w=0\} = \CC_z \times \RR$.
+
+Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
+Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
+\[
+F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
+\]
+For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
+
+\begin{lem}
+The field 
+\[
+F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
+\]
+satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
+\[
+\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
+\]
+where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
+\end{lem}
+
+\begin{proof}
+The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
+It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
+\end{proof}
 
@@
 \[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) .
+\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
 \]
@@
 \[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} , \quad (B_{ab}) \in \lie{sl}(4) .
+\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
 \]
@@
 
-%what about 3d N=8 suco?
+The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
+It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
+\[
+(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
+\]
+
+\begin{itemize}
+\item 
+The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
+It is mapped to the fields: 
+\[
+\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\] 
+\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
+It is mapped to the fields: 
+\[
+\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\] 
+\end{itemize}
+
+\subsection{Supersymmetric indices}
+
+\brian{SU(5) and SU(2) character calculations}
 
 \section{Dimensional reduction and compactifications} 
-
 \include{dimred}

### 2021-08-19 draft.tex
merge

@@
 \section{A family of moduli spaces} 
+\label{s:dfn}
 
@@
 
-The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is of infinite order. 
+The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is non polynomial.
+\brian{I think the phrasing ``infinite order'' can mean a lot of different things. I've changed it to ``non polynomial''.} 
 (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
@@
 
-\subsection{An alternative description} 
-So far, we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
+\subsection{Global symmetry algebra}
+
+\subsection{Further equivalences}
+
+\subsection{Equations of motion}
+
+%whatever we can say about the formal moduli space
+
+\subsection{Boundary conditions}
+
+%foreshadow the Horava--Witten picture
+
+\subsection{One-loop quantization}
+
+%cite result on thf quantization.
+
+\section{Symmetries of the 11-dimensional theory}
+
+\subsection{Component fields}
+
+%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
+
+\subsection{Residual supersymmetry}
+
+%m2brane
+
+\parsec[sec:susy]
+
+The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
+\[
+  \ft_{11d} = V \oplus \Pi S
+\]
+where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
+The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
+this decomposes into three irreducibles, 
+\beqn\label{eqn:decomp}
+  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
+\eeqn
+Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
+The bracket in $\ft_{11d}$ is defined using the first projection
+\[
+[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
+\]
+The super Poincar\'{e} algebra is
+\[
+  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
+\]
+The $R$-symmetry is trivial in 11-dimensional supersymmetry.
+
+\parsec[sec:m2brane]
+
+Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
+In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
+We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
+
+The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
+
+The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
+  \[
+    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
+  \]
+  defined by the formula 
+  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
+  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.
+
+We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
+
+\parsec[sec:m2branetwist]
+
+Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
+This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
+\brian{cite \cite{SWspinor}}
+We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
+
+Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
+We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
+\deq{
+  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
+}
+In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
+Also, $\lie{so}(11, \CC)$ decomposes as
+\[
+\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
+\]
+Furthermore, the spinorial representation can be identified with
+\[
+S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
+\]
+The element $Q$ lives in the first summand.
+Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
+This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
+
+\begin{prop}\label{prop:model}
+Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
+As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
+\[
+    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
+  \]
+whose elements we denote by $(v, m, \psi, c)$.
+
+The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
+\begin{align*}
+[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
+[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
+\end{align*}
+\end{prop}
+
+\parsec[]
+
+As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
+Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
+
+\begin{prop}
+\label{prop:gmodel}
+Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
+\[
+H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
+\]
+Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
+The nontrivial Lie brackets are
+\begin{align*}
+[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
+[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
+[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
+\end{align*}
+There is an $L_\infty$ map 
+\[
+\fg \rightsquigarrow \m2^Q
+\] 
+which is a quasi-isomorphism of complexes.  
+\end{prop}
+\begin{proof}
+The supercharge $Q$ is odd and of cohomological degree zero.
+Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
+
+The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
+The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
+The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
+So, of the translations, only the holomorphic ones $L^\vee$ survive.
+The map 
+\[
+[Q,-] \colon \lie{so}(11,\CC) \to S 
+\] 
+is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
+The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
+
+In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
+This completes the calculation of the cohomology.
+
+We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
+The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
+The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
+It remains to declare where $\psi \in \wedge^2 L$ is mapped.
+
+Define the map
+\[
+H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
+\]
+which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
+\[
+(H \alpha) (x) = \int_0^x \alpha .
+\]
+
+Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
+It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
+\[
+\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
+\]
+Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.
+
+The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
+On the other hand, in $\m2^Q$ there is the Lie bracket 
+\[
+[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
+\]
+The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
+The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
+\[
+v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
+\] 
+Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.
+
+\end{proof}
+
+\parsec[s:residual]
+Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
+
+\begin{prop}
+There is a map of $\ZZ/2$-graded dg Lie algebras 
+\[
+\fg \to \cL 
+\]
+where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
+In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+\end{prop}
+\begin{proof}
+Recall the model $\fg$ takes the following form
+\beqn 
+\begin{tikzcd}
+\ul{even} & \ul{odd} & \ul{even} \\
+ L_a & \wedge^2 L_b & L^\vee \\
+\wedge^2 L_a & & \\
+\lie{sl}(5) \\
+L_b \ar[r, "\id"] & L_c .
+\end{tikzcd}
+\eeqn
+The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
+
+The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
+\begin{align*}
+ L_a & \mapsto 0 \\
+ \wedge^2 L_a & \mapsto 0 \\
+z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
+\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
+\end{align*}
+One immediately verifies that this is a map of dg Lie algebras. 
+\end{proof}
+
+\parsec[]
+
+In this section we compare to the work of \brian{Linfty refs}.
+In these references, the algebra $\m2$ is defined as an $L_\infty$  
+central extension of $\lie{siso}_{11d}$.
+
+Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
+Using this two-form we can define the following four-linear expression
+\[
+\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
+\]
+This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
+In \cite{??} it is shown that this cocycle $\mu_2$ is
+
+%For clarity we adjust notation for $\lie{sl}(5)$-representations.
+Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
+
+\section{Twisted supergavity on AdS space}
+
+\subsection{Superconformal algebras}
+
+\begin{prop}
+The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
+\end{prop}
+
+\subsection{The ${\rm AdS}_7 \times S^4$ background}
+
+\parsec[]
+
+Choose a splitting 
+\[
+\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
+\]
+and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
+
+The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+\[
+\lie{sl}(4) \oplus \lie{sl}(2) .
+\]
+which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+The embedding of the bosonic piece can roughly be described as follows. 
+The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
+Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
+The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
+
+\begin{itemize}
+
+\item
+The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
+\[
+\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
+\]
+
+\item
+The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
+rotations
+\[
+A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
+\]
+
+\item
+The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
+\[
+\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
+\] 
+Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
+\item 
+The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
+\[
+z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+\] 
+Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
+\item 
+The bosonic summand $\lie{sl}(2)$ is mapped to the triple
+\[
+w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+\]
+\end{itemize}
+
+The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
+It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
+Then the odd part decomposes as
+\[
+L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
+\]
+
+\begin{itemize} 
+\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
+It is mapped to the fields 
+\[
+z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
+\] 
+\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
+It is mapped to the fields
+\[
+\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
+\]
+\end{itemize}
+
+\subsection{The ${\rm AdS}_4 \times S^7$ background}
+
+\parsec[]
+\brian{discuss coupling}
+
+\parsec[]
+
+We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
+\[
+\CC_z \times \CC^4_w \times \RR .
+\]
+Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
+
+The differential form which sources the brane is an element
+\[
+\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
+\]
+Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
+\[
+\dbar \til{F} = N \delta_{w=0} 
+\]
+where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
+
+Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
+Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
+\[
+F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
+\]
+For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
+
+\begin{lem}
+The field 
+\[
+F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
+\]
+satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
+\[
+\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
+\]
+where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
+\end{lem}
+
+\begin{proof}
+The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
+It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
+\end{proof}
+
+\parsec[]
+
+Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
+For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
+The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
+The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
+
+\begin{itemize}
+\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
+\[
+\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+\]
+Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
+\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
+\[
+\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
+\]
+\end{itemize}
+
+The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
+It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
+\[
+(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
+\]
+
+\begin{itemize}
+\item 
+The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
+It is mapped to the fields: 
+\[
+\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\] 
+\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
+It is mapped to the fields: 
+\[
+\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\] 
+\end{itemize}
+
+\subsection{Supersymmetric indices}
+
+\brian{SU(5) and SU(2) character calculations}
+
+\section{Dimensional reduction and compactifications} 
+\include{dimred}
+
+\subsection{The theory on a three-fold}
+
+%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
+
+\section{The non-minimal twist}
+
+We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
+We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
+In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
+
+On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
+We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
+In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
+\[
+A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
+\]
+where $\Pi$, as always, denotes parity shift.
+The equations of motion are of the form
+\[
+\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
+\]
+The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
+We give a precise definition below.
+
+More generally, the twist can be defined \brian{finish}
+
+\subsection{The non-minimal supercharge}
+
+Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
+We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
+
+There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
+\brian{fix this}
+
+Recall that the odd component of this residual supersymmetry algebra is
+\[
+\wedge^2 L \cong \wedge^2(\CC^5) 
+\]
+which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
+Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
+
+Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
+Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
+\[
+\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
+\]
+where $i,j=1,\ldots, 5$ and $i \ne j$.
+
+\parsec[-]
+
+The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
+
+\begin{thm}
+The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
+\[
+\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
+\]
+\end{thm}
+
+Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
+
+\section{The twisted $\Omega$-background}
+
+\subsection{$\Omega$-deformed symmetry algebra}
+
+On flat space, we have
+
+\subsection{M2 branes in the $\Omega$-background}
+
+\parsec[]
+
+In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
+\beqn\label{eqn:m2omega}
+\{0\} \times \RR \subset \CC^2 \times \RR .
+\eeqn
+
+The field which sources this brane is a distributional differential form $F$.
+The linear equation of motion for $F$ is the distributional equation 
+\[
+\d^2 z \wedge \dbar F = N \delta_{z=0} 
+\]
+where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
+In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
+
+The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
+Explicitly, we can characterize it as follows.
+
+\begin{prop}
+The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
+\[
+F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
+\] 
+satisfies the non-linear equation of motion 
+\[
+\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
+\]
+\end{prop}
+\begin{proof}
+The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
+Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
+\end{proof}
+
+\parsec[]
+
+We can interpret $F$ geometrically in the following way. 
+Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
+
+On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
+\[
+0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
+\]
+where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
+The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
+$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
+
+Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
+Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
+\[
+\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
+\]
+
+In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
+\[
+(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
+\]
+of the $(0,1)$-form
+\[
+F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
+\] 
+The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
+\[
+\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
+\]
+
+\appendix
+
+\section{An alternative description of the 11-dimensional theory} 
+In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
 The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
@@
 
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolutoin of closed two-forms. 
+The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
 The new space of fields is 
@@
 \end{equation}
+
+It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
+We'd like to point out two main differences:
+\begin{itemize}
+\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
+Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
+For this reason, we will refer to the theory as a ``Poisson BV theory''. 
+\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
+However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
+Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
+\end{itemize}
 
@@
 
-\subsection{Global symmetry algebra}
-
-\subsection{Further equivalences}
-
-\subsection{Equations of motion}
-
-%whatever we can say about the formal moduli space
-
-\subsection{Boundary conditions}
-
-%foreshadow the Horava--Witten picture
-
-\subsection{One-loop quantization}
-
-%cite result on thf quantization.
+\section{BCOV stuff}
+
+\subsection{Relation to BCOV theory}
+
+\parsec[sec:pv] 
+\ingmar{a section defining polyvector fields; not sure where this belong}
+Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
+\deq{
+  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
+}
+\ingmar{Wedges look super fucked up}
+The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
+Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
+We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
+
+\subsubsection{}
+It will be convenient for us to cast this dg Lie algebra in a slightly different way.
+We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
+The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
+
+The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
+We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
+
+Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
+Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
+In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
+With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
+
+Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
+\beqn\label{eqn:pv1}
+\PV^{\bu,\bu} [[u]] [1]
+\eeqn
+with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
+With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
+
+The Schouten--Nijenhuis bracket 
+\[
+[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
+\]
+extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
+We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
+We refer to the further cohomological shift 
+\[
+\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
+\]
+as the space of fields of Kodaira--Spencer theory.
+
+Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
+
+\subsubsection{}
+
+\brian{bv bracket}
+
+\subsubsection{}
+
+Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
+
+\begin{thm}[\cite{CLbcov1}]
+The BCOV action 
+\[
+I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
+\]
+satisfies the classical master equation 
+\[
+Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
+\]
+In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
+\end{thm}
+
+This action induces the square-zero operator 
+\[
+\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
+\]
+acting on observables of the Kodaira--Spencer fields. 
+In other words, it defines a non-linear BRST operator; in turn it
+induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
+
+This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
+Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
+
+It is easiest to describe this automorphism at the level of observables.
+Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
+Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
+\[
+\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
+\]
+
+The non-linear change of coordinates relating the two structures is defined by
+\[
+\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
+\]
+where $[-]_+$ projects onto the non-negative powers of $u$.
+
+\parsec[]
+
+The complex resolving the (shift of) divergence-free vector fields 
+\[
+\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
+\]
+is a subcomplex of $\cE_{KS}$.
+If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
+In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
+
+If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
+\beqn\label{eqn:tilks}
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
+\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
+& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
+\end{tikzcd}
+\eeqn
+And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
+Thus, we have the following.
+
+\begin{prop}
+\label{prop:tilbcov}
+The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
+\end{prop}
 
@@
 
-\section{Relationship to physical supergravity}
-
-\subsection{Component fields}
-
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
-
-\subsection{Residual supersymmetry}
-
-%m2brane
-
-\parsec[sec:susy]
-
-The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
-\[
-  \ft_{11d} = V \oplus \Pi S
-\]
-where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
-The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
-this decomposes into three irreducibles, 
-\beqn\label{eqn:decomp}
-  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
-\eeqn
-Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
-The bracket in $\ft_{11d}$ is defined using the first projection
-\[
-[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
-\]
-The super Poincar\'{e} algebra is
-\[
-  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
-\]
-The $R$-symmetry is trivial in 11-dimensional supersymmetry.
-
-\parsec[sec:m2brane]
-
-Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
-In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
-We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
-
-The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
-Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
-
-The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
-  \[
-    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
-  \]
-  defined by the formula 
-  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
-  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.
-
-We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
-
-\parsec[sec:m2branetwist]
-
-Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
-\brian{cite \cite{SWspinor}}
-We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
-
-Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
-We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
-\deq{
-  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
-}
-In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
-Also, $\lie{so}(11, \CC)$ decomposes as
-\[
-\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
-\]
-Furthermore, the spinorial representation can be identified with
-\[
-S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
-\]
-The element $Q$ lives in the first summand.
-Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
-This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
-
-\begin{prop}\label{prop:model}
-Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
-As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
-\[
-    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
-  \]
-whose elements we denote by $(v, m, \psi, c)$.
-
-The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
-\begin{align*}
-[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
-[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
-\end{align*}
-\end{prop}
-
-\parsec[]
-
-As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
-
-\begin{prop}
-\label{prop:gmodel}
-Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
-\[
-H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
-\]
-Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
-The nontrivial Lie brackets are
-\begin{align*}
-[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
-[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
-[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
-\end{align*}
-There is an $L_\infty$ map 
-\[
-\fg \rightsquigarrow \m2^Q
-\] 
-which is a quasi-isomorphism of complexes.  
-\end{prop}
-\begin{proof}
-The supercharge $Q$ is odd and of cohomological degree zero.
-Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
-
-The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
-The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
-The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
-So, of the translations, only the holomorphic ones $L^\vee$ survive.
-The map 
-\[
-[Q,-] \colon \lie{so}(11,\CC) \to S 
-\] 
-is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
-The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
-
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
-This completes the calculation of the cohomology.
-
-We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
-The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
-The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
-It remains to declare where $\psi \in \wedge^2 L$ is mapped.
-
-Define the map
-\[
-H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
-\]
-which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
-\[
-(H \alpha) (x) = \int_0^x \alpha .
-\]
-
-Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
-It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
-\[
-\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
-\]
-Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.
-
-The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
-On the other hand, in $\m2^Q$ there is the Lie bracket 
-\[
-[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
-\]
-The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
-The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
-\[
-v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
-\] 
-Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.
-
-\end{proof}
-
-\parsec[]
-Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a map of $\ZZ/2$-graded dg Lie algebras 
-\[
-\fg \to \cL 
-\]
-where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
-\end{prop}
-\begin{proof}
-Recall the model $\fg$ takes the following form
-\beqn 
-\begin{tikzcd}
-\ul{even} & \ul{odd} & \ul{even} \\
- L_a & \wedge^2 L_b & L^\vee \\
-\wedge^2 L_a & & \\
-\lie{sl}(5) \\
-L_b \ar[r, "\id"] & L_c .
-\end{tikzcd}
-\eeqn
-The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
-
-The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
-\begin{align*}
- L_a & \mapsto 0 \\
- \wedge^2 L_a & \mapsto 0 \\
-z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
-\end{align*}
-One immediately verifies that this is a map of dg Lie algebras. 
-\end{proof}
-
-\parsec[]
-
-In this section we compare to the work of \brian{Linfty refs}.
-In these references, the algebra $\m2$ is defined as an $L_\infty$  
-central extension of $\lie{siso}_{11d}$.
-
-Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
-Using this two-form we can define the following four-linear expression
-\[
-\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
-\]
-This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
-In \cite{??} it is shown that this cocycle $\mu_2$ is
-
-%For clarity we adjust notation for $\lie{sl}(5)$-representations.
-Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
-
-\section{Twisted supergavity on AdS space}
-
-\subsection{Superconformal algebras}
-
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-\parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^3) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^3)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-\parsec[]
-\brian{discuss coupling}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \CC^4_w \times \RR .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
-
-The differential form which sources this submanifold is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional along the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
-\subsection{The theory on a three-fold}
-
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
-\section{The twisted $\Omega$-background}
-
-\section{The non-minimal twist}
-
-\appendix
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belongs}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
 %Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.

### 2021-08-24 dimred.tex
not much new

@@
 \eeqn
-This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation.
+This is easily seen to be a Poisson map.
+We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation.
+Therefore, $I_{pot}$ determines an $L_{\infty}$ structure on $\cE_{pot}$, and hence one on $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
+In what follows, the $SU(4)$-invariant twist of IIA will refer to the BV theory $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
 
 \parsec[sec:dimred]
-The main result of this section is then as follows:
-
 \begin{prop}
-Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.
-Consider the map of sheaves of cochain complexes \[\int : \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] Then $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
+The $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$ is the dimensional reduction of the 11d theory $\cE$ on $\R\times \C^{\times}\times X.$
 \end{prop}
 \begin{proof}
-  \surya{write this}
+We use the notion of dimensional reduction as defined in \cite{}.
+Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.
+Note that there is an isomorphism \[\int: \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] It is clear that this isomorphism presrves the BV pairings; we need only check that $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
+
+We readily compute:
+\[\int^{*}I = \]
 \end{proof}

### 2021-08-25 draft.tex
g2

@@
 Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
+
+\parsec[sec:nmsymmetry]
+Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
+
+We start with the global symmetry algebra $E(5,10)$ of the holomorphic twist of the 11-dimensional theory. 
+From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
+\[
+\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
+\]
+We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
+
+Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
+\begin{align*}
+[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
+[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
+\end{align*}
+where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
+
+From these relations, it is easy to see that any divergence-free vector field of the form:
+\begin{itemize}
+\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
+\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
+\end{itemize}
+are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
+Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
+
+Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
+\[
+H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
+\]
+Notice that on $\CC^2$, there is an exactly sequence of Lie algebras
+\[
+0 \to \ul\CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
+\]
+where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$:
+\[
+[f(z_1,z_2) , g(z_1,z_2)] = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
+\]
 

### 2021-08-25 draft.tex
merge

@@
 
+\subsection{Global symmetry algebra}
+
+\begin{thm}
+There is a map of super Lie algebras from the super Lie algebra $E^{hol}(5,10)$ to the Lie algebra of gauge symmetries of the 11-dimensional theory on $\CC^5 \times \RR$. 
+This map is an embedding at the level of cohomology. 
+\end{thm}
+
+\begin{proof}
+We define the map directly. 
+The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
+We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory.
+
+The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
+To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
+We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
+\[
+(H \alpha) (z) = \int_{0}^z \alpha .
+\]
+Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
+We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$.
+
+All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
+The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
+We will do this in coordinates. 
+Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
+On one hand, in $E(5,10)$ we have 
+\[
+[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
+\]
+
+On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
+\begin{align*}
+[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
+& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
+\end{align*}
+as desired.
+
+The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
+In $E(5,10)$ we have
+\[
+[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
+\]
+This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
+On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
+\begin{align*}
+[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
+& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
+& = f_i g^{il} \d z_l + \del - \text{exact} .
+\end{align*}
+
+\end{proof}
+
 \section{Twisted supergavity on AdS space}
@@
 
+\brian{introduce PCS}
+Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
+\[
+\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
+\]
+
 \begin{thm}
@@
 
+The Lie algebra of gauge symmetries of this model on flat space is 
+\[
+\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
+\]
+which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
+
 \parsec[sec:nmsymmetry]
@@
 
-We start with the global symmetry algebra $E(5,10)$ of the holomorphic twist of the 11-dimensional theory. 
+Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
 From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
@@
 \]
-Notice that on $\CC^2$, there is an exactly sequence of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$:
-\[
-[f(z_1,z_2) , g(z_1,z_2)] = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
+Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
+\[
+0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
+\]
+where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
+Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
 

### 2021-08-26 draft.tex
mege

--- 2021-08-25 draft.tex
@@
 
-The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0^{hol}(X)$.
+The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
 In fact, we can form the complex 
@@
 The $\dbar$ operator, as always, is left implicit. 
-By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect^{hol}_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
+By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
 
@@
 
+\subsection{Global symmetry algebra}
+
+We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
+Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
+Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
+
+The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
+\[
+E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
+\]
+whose elements we continue to denote by $\mu$. 
+The odd piece is the module 
+\[
+E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
+\]
+whose elements we denote by $\alpha$. 
+Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
+The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
+\beqn\label{eqn:e510}
+[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
+\eeqn
+One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
+In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
+
+To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
+It is this dense sub super Lie algebra which is simple.
+
+In this short section, we prove the following.
+
+\begin{thm}\label{thm:global}
+Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$.
+\end{thm}
+
+\parsec[]
+
+On $\CC^5 \times \RR$ the solutions to the linearized equations of motion of the 11-dimensional theory consists of the space of fields $(\mu, [\gamma], b)$ where:
+\begin{itemize}
+\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
+\[
+\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
+\]
+Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
+\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
+\[
+[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
+\]
+\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
+This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
+This element is also a ghost in the $\ZZ/2$-graded theory. 
+\end{itemize}
+
+\parsec[]
+
+If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
+This is the algebra of gauge symmetries, or global symmetry algebra, of the theory. 
+In the $\ZZ/2$ graded world, the parity shifted object $\Pi \cE$ has the structure of a super Lie algebra.
+
+Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
+Equivalently, this is encoded by the full BV action of the 11-dimensional theory. 
+After applying the equations of motion this $L_\infty$ structure becomes a (strict) super Lie algebra which we now explicitly describe.
+
+After parity shifted, we've identified the solutions to the linear equations of motion with pairs
+\[
+(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \Pi \CC .
+\]
+The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
+Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
+The elements $b$ are central.
+
+The final term in the BV action $\int \gamma \del \gamma \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
+\beqn\label{eqn:eqb}
+\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
+\eeqn
+Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
+
+\parsec[]
+
+We complete the proof of Theorem \ref{thm:global}. 
+The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
+
+On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
+In other words, there is an isomorphism
+\[
+\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
+\]
+induced by the holomorphic de Rham differential.
+This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
+It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and 11-dimensional supergravity. 
+This completes the proof.
+
+%\begin{proof}
+%We define the map directly. 
+%The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
+%We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory. 
+%
+%The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
+%To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
+%We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
+%\[
+%(H \alpha) (z) = \int_{0}^z \alpha .
+%\]
+%Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
+%We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$. 
+%
+%All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
+%The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
+%We will do this in coordinates. 
+%Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
+%On one hand, in $E(5,10)$ we have 
+%\[
+%[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
+%\]
+%
+%On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
+%\begin{align*}
+%[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
+%& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
+%\end{align*}
+%as desired. 
+%
+%The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
+%In $E(5,10)$ we have
+%\[
+%[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
+%\]
+%This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
+%On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
+%\begin{align*}
+%[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
+%& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
+%& = f_i g^{il} \d z_l + \del - \text{exact} .
+%\end{align*}
+%
+%
+%\end{proof}
+
 \section{Twisted supergavity on AdS space}

### 2021-09-13 draft.tex
merge

@@
 We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
-The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
+The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_S)$ where $L$ is any smooth manifold.
 
@@
 \deq{
-  S_0 =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
+  S_0 =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
 }
@@
 \deq{
-  S_\infty =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
+  S_\infty =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
 }
@@
 \end{multline}
+
 \subsection{A family of deformations}
@@
 
-In this short section, we prove the following.
+In this section, we prove the following.
 
@@
 
-After parity shifted, we've identified the solutions to the linear equations of motion with pairs
+After parity shifted, we've identified the solutions to the linear equations of motion with triples
 \[
@@
 This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and 11-dimensional supergravity. 
+It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
 This completes the proof.

### 2021-09-13 symmetry.tex
merge

--- 2021-09-13 draft.tex
@@
 
-\title{Twisted 11-dimensional supergravity, I}
-\author{Surya Raghavendran}
-\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
-Waterloo, Ontario N2L 2Y5\\ Canada}
-\email{??}
-\author{Ingmar Saberi}
-\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
-\email{i.saberi@physik.uni-muenchen.de}
-\author{Brian R. Williams}
-\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
-\email{brian.williams@ed.ac.uk}
-\begin{abstract}
-to do
-\end{abstract}
-\maketitle
-
-\newpage
-
-\section{A family of moduli spaces} 
-\label{s:dfn}
-
-In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
-The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
-
-\subsection{Divergence-free vector fields}
-
-\subsubsection{}
-\label{sec:divfree}
-We set up some notations and conventions in the context of complex geometry. 
-Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
-If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
-The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
-\[
-  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
-\]
-This is a free resolution for the sheaf of holomorphic sections of $V$.
-
-Suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
-The divergence $\div(\mu)$ of a holomorphic vector field $\mu$ is defined by the formula
-\[
-\div (\mu) \wedge \Omega = L_\mu (\Omega)
-\]
-where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
-
-Let $\T_X$ denote the holomorphic tangent bundle and consider its Dolbeault complex $\Omega^{0,\bu}(X , \T_X)$ resolving the sheaf of holomorphic vector fields. 
-The divergence operator extends to the Dolbeault complex to yield a map of cochain complexes 
-\[
-\div \colon \Omega^{0,\bu}(X , \T_X) \to \Omega^{0,\bu}(X) .
-\]
-
-The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
-In fact, we can form the complex 
-\beqn\label{eqn:cplx1}
-\begin{tikzcd}
-\ul{0} & \ul{1} \\
-\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
-\end{tikzcd}
-\eeqn
-The $\dbar$ operator, as always, is left implicit. 
-By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
-
-There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
-Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
-The Lie bracket defined by the formulas
-\begin{align*}
-[\mu, \mu'] & = L_\mu \mu' \\
-[\mu, \nu] & = L_\mu \nu 
-\end{align*}
-is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
-We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.
-
-The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
-This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
-
-\parsec[sec:Linfty]
-
-Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
-The Chevalley--Eilenberg cochain complex is 
-\[
-\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
-\]
-The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.
-
-An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
-\deq{
-  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
-}
-between their respective Lie algebra cochains.
-It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.
-
-$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
-We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
-\deq[eq:newbase]{
-%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
-    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
-}
-This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
-The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.
-
-The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
-It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).
-
-%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
-%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
-
-%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
-We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
-Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\[
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
-\]
-
-%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
-%The linear term $\Psi^{(1)} = \id$ is the identity map. 
-%The higher terms $\Psi^{(n)}$ are defined by 
-%\brian{someone check me}
-%\begin{align*}
-%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
-%\end{align*}
-
-\parsec
-There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
-\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
-
-\subsection{Theories of BF type}
-
-\parsec
-Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
-The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
-\begin{align*}
-[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
-[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
-\end{align*}
-
-We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
-The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_S)$ where $L$ is any smooth manifold.
-
-We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
-These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.
-
-\subsubsection{}
-
-Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
-We recall the construction. 
-Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
-For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
-\[
-\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
-\]
-
-The fields of the associated BV theory are pairs
-\[
-  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
-\]
-Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
-The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.
-
-The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
-
-We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.
-
-\parsec
-For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
-In both cases, the space of fields equipped with the linear BRST operator is
-\begin{equation}
-  \label{eq:sympfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-    -n & -n + 1 & -1 & 0 \\ \hline
-    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
-\end{tikzcd}
-\end{equation}
-We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
-We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.
-
-The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
-As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
-\deq{
-  n = \dim_\C(X) + \dim_\R(L) - 1.
-}
-
-We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.
-
-Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
-\deq{
-  S_0 =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
-}
-As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.
-
-The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is non polynomial.
-\brian{I think the phrasing ``infinite order'' can mean a lot of different things. I've changed it to ``non polynomial''.} 
-(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
-Explicitly, this action functional is
-\deq{
-  S_\infty =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
-}
-
-We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent.
-As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
-Explicitly, the automorphism is
-\begin{multline}
-  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
-  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
-\end{multline}
-
-\subsection{A family of deformations}
-
-\parsec
-%check CME
-We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
-In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type.
-That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.
-
-Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
-\deq{
-  \{S + g J, S + g J \} = 0.
-}
-Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
-\deq[eq:2cond]{
-  \{S,J\} = \{J,J\} = 0.
-}
-\begin{thm}
-  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above.
-The local functional
-  \deq{
-    J = \gamma (\del \gamma)^k,
-  }
-  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
-\end{thm}
-\begin{proof}
-  First off, we consider grading issues.
-In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$.
-The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$.
-As such, we have
-  \deq{
-    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
-  }
-  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.
-
-  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}.
-It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
-It remains to check that $\{I_\infty,J\} = 0$.
-For the quadratic term, we note that
-  \deq{
-    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
-  }
-  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
-  \deq{
-    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
-}
-This expression is zero for symmetry reasons.
-Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form.
-We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form
-\end{proof}
+\section{Symmetries of the 11-dimensional theory}
+\label{sec:symmetry}
 
 \subsection{Global symmetry algebra}
+\label{sec:global}
 
-\subsection{Further equivalences}
+Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
+This is encoded by the full BV action of the 11-dimensional theory.
+We describe a simpler (strict) super Lie algebra structure present in the cohomology of the space of fields.
 
-\subsection{Equations of motion}
+In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
+More generally, the full cohomology of a $\ZZ/2$ graded space of states with respect to the linear BRST operator results in a super Lie algebra. 
+We will refer to this as the global symmetry algebra of the theory.
 
-%whatever we can say about the formal moduli space
+The main result of this section is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional simple super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
 
-\subsection{Boundary conditions}
+We recall the definition of this exceptional simple super Lie algebra.
+Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
+Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
 
-%foreshadow the Horava--Witten picture
+The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
+\[
+E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
+\]
+whose elements we continue to denote by $\mu$. 
+The odd piece is the module 
+\[
+E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
+\]
+whose elements we denote by $\alpha$. 
+Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
+The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
+\beqn\label{eqn:e510}
+[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
+\eeqn
+One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
+In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
 
-\subsection{One-loop quantization}
+More precisely, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
+It is this dense sub super Lie algebra which is simple.
 
-%cite result on thf quantization.
+In this section, we prove the following.
 
-\section{Symmetries of the 11-dimensional theory}
+\begin{thm}\label{thm:global}
+Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a one-dimensional central extension of the super Lie algebra $E^{hol}(5,10)$ defined by the even cocycle
+\begin{align*}
+E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to \CC \\
+(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
+\end{align*} 
+\end{thm}
 
-\subsection{Component fields}
+The parity of the functional in the theorem is odd, but it is also trilinear. 
+Thus, as a cocycle in the Chevalley--Eilenberg complex of $E^{hol}(5,10)$ it is of total even parity.
 
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
+\parsec[]
+
+If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cL = \cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
+In the $\ZZ/2$ graded world, the parity shifted object $\cL = \Pi \cE$ has the structure of a super $L_\infty$ algebra.
+
+The full BRST operator is given by the BV bracket with the BV action. 
+For us, this~is 
+\[
+\delta = \{S_{BF,\infty} + J, -\} .
+\]
+The linear BRST operator comes only from the quadratic summands in $S_{BF,\infty}$ and is of the form
+\beqn\label{eqn:linearBRST}
+\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma} .
+\eeqn
+The cohomology with respect to $\delta^{(1)}$ is what we referred to above as the global symmetry algebra.
+To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$.
+
+On $\CC^5 \times \RR$ the cohomology with respect to the linearized BRST operator $\delta^{(1)}$ consists of the space of triples $(\mu, [\gamma], b)$ where:
+\begin{itemize}
+\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
+\[
+\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
+\]
+Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
+\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
+\[
+[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
+\]
+\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
+This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
+This element is also a ghost in the $\ZZ/2$-graded theory. 
+\end{itemize}
+
+\parsec[]
+
+After parity shifting, we've identified the solutions to the linear equations of motion with triples
+\[
+(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \CC .
+\]
+The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
+Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
+The elements $b$ are central.
+
+The final term in the BV action $\int \gamma \wedge \del \gamma \wedge \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
+\beqn\label{eqn:eqb}
+\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
+\eeqn
+Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
+
+\parsec[]
+
+We complete the proof of Theorem \ref{thm:global}. 
+The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
+
+On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
+In other words, there is an isomorphism
+\[
+\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
+\]
+induced by the holomorphic de Rham differential.
+This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
+It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
+This completes the proof.
 
@@
 %m2brane
+
+In this section we consider the minimal twist of 11-dimensinoal supersymmetry explicitly. 
+We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
+In order for this to be a symmetry of the 11-dimensional theory that we proposed in Section \ref{sec:dfn} it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
 
@@
 Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
-In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
-We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
+In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the M5 brane.
+We begin by describing a dg Lie algebra model for the $M2$ brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
 
-The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+The $M2$ brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
 Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
@@
 
-The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
+The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given by the extension of ${\rm Stab}(Q)$ together with the brackets
 \begin{align*}
@@
 As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
+Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to the 11-dimensional theory. 
+This lemma implies Proposition \ref{prop:model}.
 
-\begin{prop}
-\label{prop:gmodel}
+\begin{lem}
+\label{lem:gmodel}
 Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
@@
 \] 
-which is a quasi-isomorphism of complexes.  
-\end{prop}
+which is a quasi-isomorphism of cochain complexes.  
+\end{lem}
 \begin{proof}
@@
 \parsec[s:residual]
-Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
+Consider now the super $L_\infty$ algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
 
 \begin{prop}
-There is a map of $\ZZ/2$-graded dg Lie algebras 
+There is a linear map of super $L_\infty$ algebras 
 \[
@@
 \]
-where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
+In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
 \end{prop}
@@
 \ul{even} & \ul{odd} & \ul{even} \\
- L_a & \wedge^2 L_b & L^\vee \\
-\wedge^2 L_a & & \\
+ L_1 & \wedge^2 L_2 & L^\vee \\
+\wedge^2 L_1 & & \\
 \lie{sl}(5) \\
-L_b \ar[r, "\id"] & L_c .
+L_2 \ar[r, "\id"] & L_3 \\ 
+\CC_c & .
 \end{tikzcd}
 \eeqn
-The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
+The subscripts in $L_1, L_2, L_3$ are used to distinguish between the various copies of $L$.
 
@@
 \begin{align*}
- L_a & \mapsto 0 \\
- \wedge^2 L_a & \mapsto 0 \\
-z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
+ L_1 & \mapsto 0 \\
+ \wedge^2 L_1 & \mapsto 0 \\
+z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
 A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
+\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+c \in \CC_c & \mapsto c \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
 \end{align*}
-One immediately verifies that this is a map of dg Lie algebras. 
+
+It is immediate to check that this is a map of cochain complexes where one equips $\cL$ with the linear BRST differential \eqref{eqn:linearBRST}.
+Since $\nu$ does not appear in the image of this map, to check that the higher Lie brackets are preserved one only needs to check that the $2$-ary bracket is preserved and this is immediate. 
 \end{proof}
+
+Because this map preserves differentials, it descends to a map in cohomology. 
+We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$, it is the trivial one-dimensional central extension of $E (5,10)$. 
+The cohomology of $\fg$ is described in Proposition \ref{prop:model}. 
+The map
+\[
+L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC_c \to E (5,10) \oplus \CC_{c'}
+\]
+is defined by very similar formulas as above
+\begin{align*}
+ L_1 & \mapsto 0 \\
+ \wedge^2 L_1 & \mapsto 0 \\
+z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \d z_i \wedge \d z_j \in \Omega^{2}_{cl} (\CC^5) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \Vect_0(\CC^5) \\ \frac{\partial}{\partial z_j} \in L^\vee & \mapsto
+\frac{\partial}{\partial z_i} \in \Vect_0(\CC^5) \\
+c \in \CC_c & \mapsto c \in \CC_{c'} .
+\end{align*}
 
@@
 
-\subsection{Global symmetry algebra}
-
-We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
-Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
-Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
-
-The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
-\[
-E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
-\]
-whose elements we continue to denote by $\mu$. 
-The odd piece is the module 
-\[
-E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
-\]
-whose elements we denote by $\alpha$. 
-Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
-The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
-\beqn\label{eqn:e510}
-[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
-\eeqn
-One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
-In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
-
-To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
-It is this dense sub super Lie algebra which is simple.
-
-In this section, we prove the following.
-
-\begin{thm}\label{thm:global}
-Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$.
-\end{thm}
-
-\parsec[]
-
-On $\CC^5 \times \RR$ the solutions to the linearized equations of motion of the 11-dimensional theory consists of the space of fields $(\mu, [\gamma], b)$ where:
-\begin{itemize}
-\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
-\[
-\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
-\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
-\[
-[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
-\]
-\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
-This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
-This element is also a ghost in the $\ZZ/2$-graded theory. 
-\end{itemize}
-
-\parsec[]
-
-If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
-This is the algebra of gauge symmetries, or global symmetry algebra, of the theory. 
-In the $\ZZ/2$ graded world, the parity shifted object $\Pi \cE$ has the structure of a super Lie algebra.
-
-Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
-Equivalently, this is encoded by the full BV action of the 11-dimensional theory. 
-After applying the equations of motion this $L_\infty$ structure becomes a (strict) super Lie algebra which we now explicitly describe.
-
-After parity shifted, we've identified the solutions to the linear equations of motion with triples
-\[
-(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \Pi \CC .
-\]
-The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
-Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
-The elements $b$ are central.
-
-The final term in the BV action $\int \gamma \del \gamma \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
-\beqn\label{eqn:eqb}
-\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
-\eeqn
-Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
-
-\parsec[]
-
-We complete the proof of Theorem \ref{thm:global}. 
-The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
-
-On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
-In other words, there is an isomorphism
-\[
-\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
-\]
-induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
-This completes the proof.
-
-%\begin{proof}
-%We define the map directly. 
-%The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
-%We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory. 
-%
-%The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
-%To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
-%We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
-%\[
-%(H \alpha) (z) = \int_{0}^z \alpha .
-%\]
-%Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
-%We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$. 
-%
-%All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
-%The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
-%We will do this in coordinates. 
-%Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
-%On one hand, in $E(5,10)$ we have 
-%\[
-%[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
-%\]
-%
-%On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
-%\begin{align*}
-%[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
-%& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
-%\end{align*}
-%as desired. 
-%
-%The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
-%In $E(5,10)$ we have
-%\[
-%[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
-%\]
-%This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
-%On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
-%\begin{align*}
-%[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
-%& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
-%& = f_i g^{il} \d z_l + \del - \text{exact} .
-%\end{align*}
-%
-%
-%\end{proof}
-
-\section{Twisted supergavity on AdS space}
-
-\subsection{Superconformal algebras}
-
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-\parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-\parsec[]
-\brian{discuss coupling}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \CC^4_w \times \RR .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
-
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
-\subsection{The theory on a three-fold}
-
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
-\section{The non-minimal twist}
-
-We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
-We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
-
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
-\[
-A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
-\]
-where $\Pi$, as always, denotes parity shift.
-The equations of motion are of the form
-\[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
-\]
-The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
-We give a precise definition below.
-
-More generally, the twist can be defined \brian{finish}
-
-\subsection{The non-minimal supercharge}
-
-Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
-We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
-
-There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
-\brian{fix this}
-
-Recall that the odd component of this residual supersymmetry algebra is
-\[
-\wedge^2 L \cong \wedge^2(\CC^5) 
-\]
-which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
-Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
-
-Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
-Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
-\[
-\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
-\]
-where $i,j=1,\ldots, 5$ and $i \ne j$.
-
-\parsec[-]
-
-The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
-
-\brian{introduce PCS}
-Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
-\[
-\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
-
-\begin{thm}
-The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
-\[
-\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
-\]
-\end{thm}
-
-Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-The Lie algebra of gauge symmetries of this model on flat space is 
-\[
-\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-\]
-which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
-
-\parsec[sec:nmsymmetry]
-Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
-
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
-From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
-\[
-\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
-\]
-We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
-
-Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
-\begin{align*}
-[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
-[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
-\end{align*}
-where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
-
-From these relations, it is easy to see that any divergence-free vector field of the form:
-\begin{itemize}
-\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
-\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
-\end{itemize}
-are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
-Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
-
-Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
-\[
-H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
-\]
-Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
-\[
-0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
-Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
-
-\section{The twisted $\Omega$-background}
-
-\subsection{$\Omega$-deformed symmetry algebra}
-
-On flat space, we have
-
-\subsection{M2 branes in the $\Omega$-background}
-
-\parsec[]
-
-In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
-\beqn\label{eqn:m2omega}
-\{0\} \times \RR \subset \CC^2 \times \RR .
-\eeqn
-
-The field which sources this brane is a distributional differential form $F$.
-The linear equation of motion for $F$ is the distributional equation 
-\[
-\d^2 z \wedge \dbar F = N \delta_{z=0} 
-\]
-where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
-In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
-
-The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
-Explicitly, we can characterize it as follows.
-
-\begin{prop}
-The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
-\[
-F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
-\] 
-satisfies the non-linear equation of motion 
-\[
-\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
-\]
-\end{prop}
-\begin{proof}
-The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
-Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
-\end{proof}
-
-\parsec[]
-
-We can interpret $F$ geometrically in the following way. 
-Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
-
-On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
-\]
-where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
-The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
-$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
-
-Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
-Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
-\[
-\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
-\]
-
-In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
-\[
-(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
-\]
-of the $(0,1)$-form
-\[
-F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
-\] 
-The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
-\[
-\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
-\]
-
-\appendix
-
-\section{An alternative description of the 11-dimensional theory} 
-In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
-The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
-
-There is a related, alternative description of this formal moduli space which is almost equivalent. 
-Consider the resolution of holomorphic closed two-forms 
-\beqn\label{eqn:twoform}
-\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
-\eeqn
-where we have left the $\dbar$-differential implicit, as always.
-
-There is a map from the two-term complex 
-\[
-\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
-\]
-to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
-This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
-
-Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
-\[
-\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
-\]
-Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
-The left-hand side contains the fields $(\beta, \gamma)$. 
-This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
-
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
-The new space of fields is 
-\begin{equation}
-  \label{eq:poissfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-     - & + & - & + \\ \hline
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
-     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
-\end{tikzcd}
-\end{equation}
-
-It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
-We'd like to point out two main differences:
-\begin{itemize}
-\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
-Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
-For this reason, we will refer to the theory as a ``Poisson BV theory''. 
-\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
-However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
-Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
-\end{itemize}
-
-\begin{prop}
-The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
-Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
-\end{prop}
-
-Heuristically, we can write the action in the following non-local form
-\[
-\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
-\]
-\brian{are there more terms involving higher forms?}
-
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\eta]_1 & = \dbar \eta + \del \eta \\ 
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
-[\mu, \eta]_2 & = \mu \vee \del \eta \\
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\begin{align*}
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
-\end{align*}
-
-\parsec[]
-Consider the theory on $\CC^3 \times \RR$. 
-There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
-
-\parsec[]
-Consider the theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a quasi-isomorphism of super $L_\infty$ algebras 
-\[
-E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
-\]
-This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
-\end{prop}
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belong}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
-Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
-%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
-
-\begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
-In particular, the non-linear BRST operator 
-\beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
-\eeqn
-is $\CC^\times$ weight zero.
-\end{lem}
-\begin{proof}
-%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
-We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is holomorphic polyvector field type, and the second is descendant degree.
-The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
-
-We introduce notation in this proof that won't be used later on. 
-Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
-If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
-If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
-
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
-\[
- \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
-\]
-Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
-In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
-\begin{align*}
-\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
-\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
-\end{align*}
-The first constraint ensures that the integrand is of top polyvector degree. 
-The second constraint is on the descendant degree, see \brian{ref above}.
-
-Simplifying these two equations, one finds the condition
-\[
-m+n-3 = m+(d-2)n - d 
-\]
-which implies $n=1$, as desired. 
-\end{proof}
-
-Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
-The $\CC^\times$ weight zero subcomplex is 
-\[
-\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
-\]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
-
-\begin{prop}
-\label{prop:Linfty}
-The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
-\[
-\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
-\]
-with $[-]_1 = \dbar + \div$. 
-Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
-\end{prop}
-
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
-
 \end{document}

### 2021-09-13 draft.tex
index

--- 2021-08-26 draft.tex
@@
 
+As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
+We will find a match between indices counting local operators supported at a point.
+
+Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$.
+Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table
+
+\begin{tabluar}
+
+\end{tabular}
+
 \subsection{The non-minimal supercharge}

### 2021-09-13 dfn.tex

--- 2021-08-26 draft.tex
@@
 
-\title{Twisted 11-dimensional supergravity, I}
-\author{Surya Raghavendran}
-\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
-Waterloo, Ontario N2L 2Y5\\ Canada}
-\email{??}
-\author{Ingmar Saberi}
-\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
-\email{i.saberi@physik.uni-muenchen.de}
-\author{Brian R. Williams}
-\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
-\email{brian.williams@ed.ac.uk}
-\begin{abstract}
-to do
-\end{abstract}
-\maketitle
-
-\newpage
-
-\section{A family of moduli spaces} 
+\section{The minimal twist of 11-dimensional supergravity} 
 \label{s:dfn}
@@
 
-Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
+Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta_\cL$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
 The Chevalley--Eilenberg cochain complex is 
 \[
-\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
+\left(\Sym\left(\cL^\vee [-1] \right), \delta_\cL\right) .
 \]
-The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.
+The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$. 
+The condition that the differential is square-zero $\delta_\cL \circ \delta_\cL = 0$ is equivalent to the higher Jacobi relations.
 
@@
 $\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
-We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
+We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:
 \deq[eq:newbase]{
@@
 }
-This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
+This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$.\footnote{We are being slightly abusive and using the symbols $\nu,\mu$ dually as coordinates, or operators, on the graded linear space $\cL[1]$.}
 The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.
@@
 [\mu]_1 & = \dbar \mu + \div \mu \\
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
+[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
+[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \wedge \mu_2) 
+%\\
+%[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
 \end{align*}
@@
 \[
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
+[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) .
 \]
@@
 \parsec
-Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
-The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
+Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(\cA, \d_\cA)$ is a commutative dg algebra. 
+The graded vector space $\cL \otimes \cA$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
 \begin{align*}
-[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
+[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_\cA a \\
 [x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
@@
 We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
-The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold.
+The algebra $\cA$ will be the smooth de Rham complex $(\Omega^\bu(S) , \d_S)$ where $S$ is a smooth manifold (we will specialize the dimension of this smooth manifold shortly, but the constructions in this section make sense in any dimension).
 
-We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
-These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.
+We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(S)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(S)$.
+These define equivalent local $L_\infty$ algebras on the product manifold~$X \times S$.
 
@@
 
-Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
-We recall the construction. 
-Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
+Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism.
+Let $\cL$ be a local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
 For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
@@
 The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
+We refer to this as the ``BF theory'' associated to $\cL$.
 
-We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.
+We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(S)$ and $\cL_\infty(X) \otimes \Omega^\bu(S)$.
 
 \parsec
-For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
+For concreteness, we spell out the fields of the theories we have constructed on $X \times S$.
 In both cases, the space of fields equipped with the linear BRST operator is
@@
     -n & -n + 1 & -1 & 0 \\ \hline
-    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
+    \Omega^{0,\bu}(X;S) \ar[r, "\del"] & \Omega^{1,\bu}(X;S) & 
+     \PV^{1,\bu}(X; S) \ar[r, "\div"] & \PV^{0,\bu}(X; S).
 \end{tikzcd}
@@
 We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
-We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.
+We are using the shorthand notation $\PV^{i}(X;S) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(S), \dbar + \d_{S}))$.
 
-The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
+The natural pairing between $\PV^i(X;S)$ and~$\Omega^i(X;S)$ is of degree $-\dim_\C(X) -\dim_\R(S)$. 
 As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
 \deq{
-  n = \dim_\C(X) + \dim_\R(L) - 1.
+  n = \dim_\C(X) + \dim_\R(S) - 1.
 }
@@
 We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.
-
-Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
+Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(S)$ is
 \deq{
-  S_0 =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
+  S_{BF,0} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu + \frac{1}{2}  \gamma \wedge [\mu,\mu] +  \beta \wedge [\mu,\nu].
 }
@@
 
-The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is non polynomial.
-\brian{I think the phrasing ``infinite order'' can mean a lot of different things. I've changed it to ``non polynomial''.} 
+The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(S)$ is non polynomial. 
 (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
@@
 \deq{
-  S_\infty =  \beta (\dbar + \d_L) \nu +  \gamma (\dbar + \d_L) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
+  S_{BF,\infty} =  \beta \wedge (\dbar + \d_L) \nu +  \gamma \wedge (\dbar + \d_L) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \vee \mu^2.
 }
@@
 Explicitly, the automorphism is
-\begin{multline}
+\begin{multline}\label{eqn:auto1}
   \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
-  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
+  \beta \mapsto (\beta - \mu \vee \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
 \end{multline}
-\subsection{A family of deformations}
+
+\parsec[]
+
+In what follows, we specialize to the case that $X$ is a Calabi--Yau five-fold and that $S$ is a one-dimensional smooth orientable manifold. 
+In this case, with $n = 5 + 1 - 1 = 5$ the theories described in this section are $\ZZ$-graded in the BV formalism.
+Momentarily, we consider a new term in the action which will break this grading, so this integer shift will not play an essential role.
+
+\subsection{A deformation of BF theory}
 
@@
 %check CME
-We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
-In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type.
-That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.
 
-Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
+Recall that $X$ is a complex five-dimensional Calabi--Yau manifold and $S$ is a one-dimensional smooth manifold.
+We finally arrive at the definition of the classical field theory on $X \times S$.
+
+We consider a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
+Such deformations are governed by the classical master equation: the parameterized family of actions 
+\beqn\label{eqn:defaction}
+S_{BF} + g J
+\eeqn
+defines a consistent theory in the BV formalism if and only if
 \deq{
-  \{S + g J, S + g J \} = 0.
+  \{S_{BF} + g J, S_{BF} + g J \} = 0.
 }
-Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
+Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces the condition
 \deq[eq:2cond]{
-  \{S,J\} = \{J,J\} = 0.
+  \{S_{BF},J\} + \frac12 \{J,J\} = 0.
 }
+
+The form of $J$ depends on which presentation we use for BF theory.
+To begin, we will use the presentation of BF theory $S_{BF, \infty}$ which uses the the non-strict $L_\infty$ structure on divergence-free holomorphic vector fields.
+The deformation $J$ does not make reference to the Calabi--Yau structure explicitly, but it does involve the holomorphic de Rham operator $\del$ on $X$.
+
+The main result of this section is the following.
+
 \begin{thm}
-  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above.
-The local functional
+Let $X$ be a Calabi--Yau five-fold and $S$ a smooth one-dimensional manifold, and consider the BV theory $(\cE, S_{BF,\infty})$ on $X \times S$ defined above. The local functional 
   \deq{
-    J = \gamma (\del \gamma)^k,
+    J = \frac16 \gamma \wedge \del \gamma \wedge \del \gamma ,
   }
-  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
-\end{thm}
-\begin{proof}
-  First off, we consider grading issues.
-In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$.
-The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$.
-As such, we have
-  \deq{
-    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
-  }
-  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.
-
-  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}.
-It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
-It remains to check that $\{I_\infty,J\} = 0$.
-For the quadratic term, we note that
-  \deq{
-    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
-  }
-  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
-  \deq{
-    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
-}
-This expression is zero for symmetry reasons.
-Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form.
-We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form
-\end{proof}
-
-\subsection{Global symmetry algebra}
-
-\subsection{Further equivalences}
-
-\subsection{Equations of motion}
-
-%whatever we can say about the formal moduli space
-
-\subsection{Boundary conditions}
-
-%foreshadow the Horava--Witten picture
-
-\subsection{One-loop quantization}
-
-%cite result on thf quantization.
-
-\section{Symmetries of the 11-dimensional theory}
-
-\subsection{Component fields}
-
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
-
-\subsection{Residual supersymmetry}
-
-%m2brane
-
-\parsec[sec:susy]
-
-The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
-\[
-  \ft_{11d} = V \oplus \Pi S
-\]
-where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
-The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
-this decomposes into three irreducibles, 
-\beqn\label{eqn:decomp}
-  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
-\eeqn
-Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
-The bracket in $\ft_{11d}$ is defined using the first projection
-\[
-[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
-\]
-The super Poincar\'{e} algebra is
-\[
-  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
-\]
-The $R$-symmetry is trivial in 11-dimensional supersymmetry.
-
-\parsec[sec:m2brane]
-
-Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
-In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
-We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
-
-The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
-Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
-
-The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
-  \[
-    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
-  \]
-  defined by the formula 
-  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
-  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.
-
-We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
-
-\parsec[sec:m2branetwist]
-
-Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
-\brian{cite \cite{SWspinor}}
-We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
-
-Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
-We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
-\deq{
-  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
-}
-In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
-Also, $\lie{so}(11, \CC)$ decomposes as
-\[
-\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
-\]
-Furthermore, the spinorial representation can be identified with
-\[
-S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
-\]
-The element $Q$ lives in the first summand.
-Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
-This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
-
-\begin{prop}\label{prop:model}
-Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
-As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
-\[
-    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
-  \]
-whose elements we denote by $(v, m, \psi, c)$.
-
-The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
-\begin{align*}
-[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
-[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
-\end{align*}
-\end{prop}
-
-\parsec[]
-
-As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
-
-\begin{prop}
-\label{prop:gmodel}
-Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
-\[
-H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
-\]
-Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
-The nontrivial Lie brackets are
-\begin{align*}
-[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
-[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
-[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
-\end{align*}
-There is an $L_\infty$ map 
-\[
-\fg \rightsquigarrow \m2^Q
-\] 
-which is a quasi-isomorphism of complexes.  
-\end{prop}
-\begin{proof}
-The supercharge $Q$ is odd and of cohomological degree zero.
-Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
-
-The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
-The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
-The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
-So, of the translations, only the holomorphic ones $L^\vee$ survive.
-The map 
-\[
-[Q,-] \colon \lie{so}(11,\CC) \to S 
-\] 
-is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
-The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
-
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
-This completes the calculation of the cohomology.
-
-We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
-The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
-The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
-It remains to declare where $\psi \in \wedge^2 L$ is mapped.
-
-Define the map
-\[
-H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
-\]
-which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
-\[
-(H \alpha) (x) = \int_0^x \alpha .
-\]
-
-Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
-It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
-\[
-\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
-\]
-Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.
-
-The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
-On the other hand, in $\m2^Q$ there is the Lie bracket 
-\[
-[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
-\]
-The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
-The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
-\[
-v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
-\] 
-Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.
-
-\end{proof}
-
-\parsec[s:residual]
-Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a map of $\ZZ/2$-graded dg Lie algebras 
-\[
-\fg \to \cL 
-\]
-where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
-\end{prop}
-\begin{proof}
-Recall the model $\fg$ takes the following form
-\beqn 
-\begin{tikzcd}
-\ul{even} & \ul{odd} & \ul{even} \\
- L_a & \wedge^2 L_b & L^\vee \\
-\wedge^2 L_a & & \\
-\lie{sl}(5) \\
-L_b \ar[r, "\id"] & L_c .
-\end{tikzcd}
-\eeqn
-The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
-
-The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
-\begin{align*}
- L_a & \mapsto 0 \\
- \wedge^2 L_a & \mapsto 0 \\
-z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
-\end{align*}
-One immediately verifies that this is a map of dg Lie algebras. 
-\end{proof}
-
-\parsec[]
-
-In this section we compare to the work of \brian{Linfty refs}.
-In these references, the algebra $\m2$ is defined as an $L_\infty$  
-central extension of $\lie{siso}_{11d}$.
-
-Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
-Using this two-form we can define the following four-linear expression
-\[
-\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
-\]
-This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
-In \cite{??} it is shown that this cocycle $\mu_2$ is
-
-%For clarity we adjust notation for $\lie{sl}(5)$-representations.
-Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
-
-\subsection{Global symmetry algebra}
-
-We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
-Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
-Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
-
-The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
-\[
-E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
-\]
-whose elements we continue to denote by $\mu$. 
-The odd piece is the module 
-\[
-E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
-\]
-whose elements we denote by $\alpha$. 
-Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
-The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
-\beqn\label{eqn:e510}
-[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
-\eeqn
-One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
-In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
-
-To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
-It is this dense sub super Lie algebra which is simple.
-
-In this short section, we prove the following.
-
-\begin{thm}\label{thm:global}
-Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$.
+  where $\gamma \in \Omega^{1,\bu}(X;S)$, defines a deformation of~$(\cE,S_{BF,\infty})$ as a $\Z/2$-graded BV theory.
 \end{thm}
@@
 
-On $\CC^5 \times \RR$ the solutions to the linearized equations of motion of the 11-dimensional theory consists of the space of fields $(\mu, [\gamma], b)$ where:
-\begin{itemize}
-\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
+First off, we remark on grading issues. 
+In the original $\Z$-grading on the BF theory given in \eqref{eq:sympfields} with $n=5$, the component $\gamma^{1,i;j}$ sits in degree $-4+i+j$. 
+Thus, we see that in the original $\Z$-grading on BF theory one has
+  \deq{
+    \deg(J) = 6.
+  }
+Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading.
+
+This is completely reasonable \brian{finish}
+
+Nevertheless, if we break to the obvious $\ZZ/2$ grading, the functional $S_{BF} + g J$ defines an even action functional.
+Unless otherwise stated, we will work with this $\ZZ/2$ grading for the remainder of this section.
+
+\parsec[]
+We proceed to show that $S_{BF,\infty} + g J$ solves the classical master equation.
+By apparent field type reasons, the equation \eqref{eq:2cond} is equivalent to the following two equations
 \[
-\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
+\{S_{BF,\infty}, J\} = 0, \qquad \{J,J\} = 0.
 \] 
-Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
-\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
-\[
-[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
-\]
-\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
-This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
-This element is also a ghost in the $\ZZ/2$-graded theory. 
-\end{itemize}
+It is furthermore immediate from the form of the BV bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
+
+It remains to check that $\{S_{BF,\infty},J\} = 0$. 
+For the quadratic term in the BF action, we note that 
+  \deq{
+    \{\beta \wedge \div\mu, J\} = \frac12 \del\beta \wedge \del \gamma \wedge \del \gamma = 0,
+  }
+  because total derivatives are equivalent to zero as local functionals.
+
+The contribution from the remaining BF action takes the form
+\begin{multline}
+    \left\{ \frac12 \frac{1}{1-\nu} \del\gamma \vee \mu^2, \frac16 \gamma \wedge \del\gamma \wedge \del \gamma \right\} \\ = \frac12 \frac{1}{1-\nu} \bigg[ (\del\gamma\vee\mu) \wedge \del\gamma \wedge \del \gamma \pm \del\gamma \wedge (\del\gamma\vee\mu) \wedge \del \gamma \pm \del\gamma \wedge \del \gamma \wedge (\del\gamma\vee\mu) \bigg].
+\end{multline}
+This expression is zero for symmetry reasons.
+Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional which is cubic in this two-form.
+We can ask whether such a  contraction exists just at the level of $\lie{sl}(5)$ representation theory by computing the decomposition of the two-form
+\ingmar{finish}
 
@@
 
-If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
-This is the algebra of gauge symmetries, or global symmetry algebra, of the theory. 
-In the $\ZZ/2$ graded world, the parity shifted object $\Pi \cE$ has the structure of a super Lie algebra.
+We remark on an alternative, equivalent, description of the deformed theory which involves the strict dg Lie algebra structure on divergence-free holomorphic vector fields.
 
-Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
-Equivalently, this is encoded by the full BV action of the 11-dimensional theory. 
-After applying the equations of motion this $L_\infty$ structure becomes a (strict) super Lie algebra which we now explicitly describe.
+We can replace $S_{BF,\infty}$ by $S_{BF,0}$ via applying the field automorphism \eqref{eqn:auto1}.
+Doing this we see that $J$ becomes 
+\[
+\til{J} = \frac16 e^\nu \gamma \wedge \del (e^\nu \gamma) \wedge \del(e^\nu \gamma) .
+\]
+Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equations and are equivalent as~$\ZZ/2$ graded BV theories.
 
-After parity shifted, we've identified the solutions to the linear equations of motion with pairs
+\subsection{Equations of motion}
+
+Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + J$ is the minimal twist of $11$-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form.
+For the moment, we briefly read off the equations of motion of the general theory on $X \times S$.
+Let $\Omega$ denote the Calabi--Yau form on $X$.
+
+We consider the action $S_{BF, \infty} + gJ$.
+The equation of motion obtained by varying $\beta$ is especially simple, in fact linear, since it only appears in the action via a quadratic term. 
+It is
+\beqn\label{eqn:eombeta}
+\dbar \nu + \d_S \nu + \div \mu = 0 .
+\eeqn
+Varying $\gamma$ we obtain the equation of motion
+\beqn\label{eqn:eomgamma}
+\dbar \mu + \d_S \mu + \frac12 \frac{1}{1-\nu} \div (\mu^2) + \frac12 (\del \gamma \wedge \del \gamma) \vee (g \Omega^{-1}) = 0 .
+\eeqn
+The last term represents the contraction of an element of $\Omega^{4,\bu}(X;S)$ with the section $\Omega^{-1} \in \PV^{5,\bu}(X;S)$ to yield an element of $\PV^{1,\bu}(X;S)$.
+
+Let us make the simplifying assumption that $\mu$ is divergence-free and locally constant along $S$: $\div \mu = 0$ and $\d_S \mu = 0$.
+Then, $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
+Then \eqref{eqn:eomgamma} can be written as 
+\beqn\label{eqn:eomgamma1}
+\dbar \mu + \frac12 [\mu,\mu] + \frac12 (\del \gamma \wedge \del \gamma) \vee (g \Omega^{-1}) = 0 
+\eeqn
+where $[-,-]$ is the Schouten bracket.
+
+The equation of motion \eqref{eqn:eomgamma1} must hold for any inhomogenous field $\mu \in \PV^{1,\bu}(X;S)$. 
+The most geometrically relevant component is the case where 
 \[
-(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \Pi \CC .
+\mu^{1;0} \in \PV^{1,1}(X) \otimes \Omega^0(S) 
 \]
-The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
-Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
-The elements $b$ are central.
-
-The final term in the BV action $\int \gamma \del \gamma \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
-\beqn\label{eqn:eqb}
-\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
-\eeqn
-Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
-
-\parsec[]
-
-We complete the proof of Theorem \ref{thm:global}. 
-The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
-
-On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
-In other words, there is an isomorphism
-\[
-\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
-\]
-induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and 11-dimensional supergravity. 
-This completes the proof.
-
-%\begin{proof}
-%We define the map directly. 
-%The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
-%We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory. 
-%
-%The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
-%To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
-%We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
-%\[
-%(H \alpha) (z) = \int_{0}^z \alpha .
-%\]
-%Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
-%We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$. 
-%
-%All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
-%The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
-%We will do this in coordinates. 
-%Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
-%On one hand, in $E(5,10)$ we have 
-%\[
-%[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
-%\]
-%
-%On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
-%\begin{align*}
-%[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
-%& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
-%\end{align*}
-%as desired. 
-%
-%The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
-%In $E(5,10)$ we have
-%\[
-%[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
-%\]
-%This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
-%On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
-%\begin{align*}
-%[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
-%& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
-%& = f_i g^{il} \d z_l + \del - \text{exact} .
-%\end{align*}
-%
-%
-%\end{proof}
-
-\section{Twisted supergavity on AdS space}
-
-\subsection{Superconformal algebras}
-
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-\parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-\parsec[]
-\brian{discuss coupling}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \CC^4_w \times \RR .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
-
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
-\subsection{The theory on a three-fold}
-
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
-\section{The non-minimal twist}
-
-We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
-We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
-
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
-\[
-A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
-\]
-where $\Pi$, as always, denotes parity shift.
-The equations of motion are of the form
-\[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
-\]
-The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
-We give a precise definition below.
-
-More generally, the twist can be defined \brian{finish}
-
-\subsection{The non-minimal supercharge}
-
-Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
-We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
-
-There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
-\brian{fix this}
-
-Recall that the odd component of this residual supersymmetry algebra is
-\[
-\wedge^2 L \cong \wedge^2(\CC^5) 
-\]
-which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
-Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
-
-Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
-Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
-\[
-\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
-\]
-where $i,j=1,\ldots, 5$ and $i \ne j$.
-
-\parsec[-]
-
-The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
-
-\brian{introduce PCS}
-Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
-\[
-\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
-
-\begin{thm}
-The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
-\[
-\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
-\]
-\end{thm}
-
-Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-The Lie algebra of gauge symmetries of this model on flat space is 
-\[
-\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-\]
-which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
-
-\parsec[sec:nmsymmetry]
-Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
-
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
-From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
-\[
-\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
-\]
-We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
-
-Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
-\begin{align*}
-[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
-[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
-\end{align*}
-where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
-
-From these relations, it is easy to see that any divergence-free vector field of the form:
-\begin{itemize}
-\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
-\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
-\end{itemize}
-are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
-Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
-
-Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
-\[
-H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
-\]
-Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
-\[
-0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
-Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
-
-\section{The twisted $\Omega$-background}
-
-\subsection{$\Omega$-deformed symmetry algebra}
-
-On flat space, we have
-
-\subsection{M2 branes in the $\Omega$-background}
-
-\parsec[]
-
-In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
-\beqn\label{eqn:m2omega}
-\{0\} \times \RR \subset \CC^2 \times \RR .
+which is an even field in our $\ZZ/2$ graded BV theory.
+The superscript denotes anti-holomorphic; de Rham form type. 
+For this component of $\mu$, the only components of $\gamma$ which appear in the above equations of motion are $\gamma^{0;0}$, $\gamma^{1;0}$, and $\gamma^{2;0}$.
+Expanding these components out, we obtain
+\beqn\label{eqn:eomgamma1}
+\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + (\del \gamma^{0;0} \wedge \del \gamma^{2;0}) \vee (g \Omega^{-1}) + \frac12 (\del \gamma^{1;0} \wedge \del \gamma^{1;0}) \vee (g \Omega^{-1}) = 0 .
 \eeqn
 
-The field which sources this brane is a distributional differential form $F$.
-The linear equation of motion for $F$ is the distributional equation 
-\[
-\d^2 z \wedge \dbar F = N \delta_{z=0} 
-\]
-where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
-In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
+\subsection{Component fields}
 
-The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
-Explicitly, we can characterize it as follows.
-
-\begin{prop}
-The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
-\[
-F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
-\] 
-satisfies the non-linear equation of motion 
-\[
-\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
-\]
-\end{prop}
-\begin{proof}
-The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
-Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
-\end{proof}
-
-\parsec[]
-
-We can interpret $F$ geometrically in the following way. 
-Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
-
-On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
-\]
-where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
-The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
-$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
-
-Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
-Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
-\[
-\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
-\]
-
-In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
-\[
-(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
-\]
-of the $(0,1)$-form
-\[
-F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
-\] 
-The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
-\[
-\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
-\]
-
-\appendix
-
-\section{An alternative description of the 11-dimensional theory} 
-In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
-The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
-
-There is a related, alternative description of this formal moduli space which is almost equivalent. 
-Consider the resolution of holomorphic closed two-forms 
-\beqn\label{eqn:twoform}
-\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
-\eeqn
-where we have left the $\dbar$-differential implicit, as always.
-
-There is a map from the two-term complex 
-\[
-\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
-\]
-to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
-This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
-
-Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
-\[
-\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
-\]
-Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
-The left-hand side contains the fields $(\beta, \gamma)$. 
-This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
-
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
-The new space of fields is 
-\begin{equation}
-  \label{eq:poissfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-     - & + & - & + \\ \hline
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
-     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
-\end{tikzcd}
-\end{equation}
-
-It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
-We'd like to point out two main differences:
-\begin{itemize}
-\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
-Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
-For this reason, we will refer to the theory as a ``Poisson BV theory''. 
-\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
-However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
-Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
-\end{itemize}
-
-\begin{prop}
-The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
-Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
-\end{prop}
-
-Heuristically, we can write the action in the following non-local form
-\[
-\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
-\]
-\brian{are there more terms involving higher forms?}
-
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\eta]_1 & = \dbar \eta + \del \eta \\ 
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
-[\mu, \eta]_2 & = \mu \vee \del \eta \\
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\begin{align*}
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
-\end{align*}
-
-\parsec[]
-Consider the theory on $\CC^3 \times \RR$. 
-There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
-
-\parsec[]
-Consider the theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a quasi-isomorphism of super $L_\infty$ algebras 
-\[
-E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
-\]
-This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
-\end{prop}
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belong}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
-Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
-%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
-
-\begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
-In particular, the non-linear BRST operator 
-\beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
-\eeqn
-is $\CC^\times$ weight zero.
-\end{lem}
-\begin{proof}
-%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
-We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is holomorphic polyvector field type, and the second is descendant degree.
-The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
-
-We introduce notation in this proof that won't be used later on. 
-Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
-If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
-If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
-
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
-\[
- \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
-\]
-Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
-In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
-\begin{align*}
-\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
-\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
-\end{align*}
-The first constraint ensures that the integrand is of top polyvector degree. 
-The second constraint is on the descendant degree, see \brian{ref above}.
-
-Simplifying these two equations, one finds the condition
-\[
-m+n-3 = m+(d-2)n - d 
-\]
-which implies $n=1$, as desired. 
-\end{proof}
-
-Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
-The $\CC^\times$ weight zero subcomplex is 
-\[
-\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
-\]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
-
-\begin{prop}
-\label{prop:Linfty}
-The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
-\[
-\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
-\]
-with $[-]_1 = \dbar + \div$. 
-Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
-\end{prop}
-
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
+\subsection{One-loop quantization}
 

### 2021-09-13 draft.tex
input

--- 2021-09-13 draft.tex
@@
 \maketitle
-
 \newpage
 
-\section{A family of moduli spaces} 
-\label{s:dfn}
+%\section{Symmetries of the 11-dimensional theory}
+\input{dfn}
 
-In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
-The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
-
-\subsection{Divergence-free vector fields}
-
-\subsubsection{}
-\label{sec:divfree}
-We set up some notations and conventions in the context of complex geometry. 
-Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
-If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
-The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
-\[
-  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
-\]
-This is a free resolution for the sheaf of holomorphic sections of $V$.
-
-Suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
-The divergence $\div(\mu)$ of a holomorphic vector field $\mu$ is defined by the formula
-\[
-\div (\mu) \wedge \Omega = L_\mu (\Omega)
-\]
-where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.
-
-Let $\T_X$ denote the holomorphic tangent bundle and consider its Dolbeault complex $\Omega^{0,\bu}(X , \T_X)$ resolving the sheaf of holomorphic vector fields. 
-The divergence operator extends to the Dolbeault complex to yield a map of cochain complexes 
-\[
-\div \colon \Omega^{0,\bu}(X , \T_X) \to \Omega^{0,\bu}(X) .
-\]
-
-The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
-In fact, we can form the complex 
-\beqn\label{eqn:cplx1}
-\begin{tikzcd}
-\ul{0} & \ul{1} \\
-\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
-\end{tikzcd}
-\eeqn
-The $\dbar$ operator, as always, is left implicit. 
-By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
-
-There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
-Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
-The Lie bracket defined by the formulas
-\begin{align*}
-[\mu, \mu'] & = L_\mu \mu' \\
-[\mu, \nu] & = L_\mu \nu 
-\end{align*}
-is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
-We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.
-
-The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
-This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
-
-\parsec[sec:Linfty]
-
-Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
-The Chevalley--Eilenberg cochain complex is 
-\[
-\left(\Sym\left(\cL^\vee [-1] \right), \delta\right) .
-\]
-The Taylor components of $\delta$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$.
-
-An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
-\deq{
-  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
-}
-between their respective Lie algebra cochains.
-It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.
-
-$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
-We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:\ingmar{notation for operators vs fields}
-\deq[eq:newbase]{
-%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
-    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
-}
-This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$. 
-The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.
-
-The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
-It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).
-
-%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
-%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.
-
-%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
-We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
-Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\[
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
-\]
-
-%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
-%The linear term $\Psi^{(1)} = \id$ is the identity map. 
-%The higher terms $\Psi^{(n)}$ are defined by 
-%\brian{someone check me}
-%\begin{align*}
-%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
-%\end{align*}
-
-\parsec
-There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
-\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
-
-\subsection{Theories of BF type}
-
-\parsec
-Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(A, \d_A)$ is a commutative dg algebra. 
-The graded vector space $\cL \otimes A$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
-\begin{align*}
-[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_A a \\
-[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
-\end{align*}
-
-We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
-The algebra $A$ will be the smooth de Rham complex $(\Omega^\bu(L) , \d_S)$ where $L$ is any smooth manifold.
-
-We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(L)$.
-These define equivalent local $L_\infty$ algebras on the product manifold $X \times L$.
-
-\subsubsection{}
-
-Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism that one refers to as BF theory.
-We recall the construction. 
-Let $\cL$ be any local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
-For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
-\[
-\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
-\]
-
-The fields of the associated BV theory are pairs
-\[
-  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
-\]
-Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
-The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.
-
-The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$.
-
-We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(L)$ and $\cL_\infty(X) \otimes \Omega^\bu(L)$.
-
-\parsec
-For concreteness, we spell out the fields of the theories we have constructed on $X \times L$.
-In both cases, the space of fields equipped with the linear BRST operator is
-\begin{equation}
-  \label{eq:sympfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-    -n & -n + 1 & -1 & 0 \\ \hline
-    \Omega^{0,\bu}(X;L) \ar[r, "\del"] & \Omega^{1,\bu}(X;L) & 
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L).
-\end{tikzcd}
-\end{equation}
-We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
-We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(L), \dbar + \d_{L}))$.
-
-The natural pairing between $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. 
-As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
-\deq{
-  n = \dim_\C(X) + \dim_\R(L) - 1.
-}
-
-We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.
-
-Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(L)$ is
-\deq{
-  S_0 =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +  \beta\partial_\Omega \mu + \frac{1}{2}  \gamma [\mu,\mu] +  \beta[\mu,\nu].
-}
-As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.
-
-The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(L)$ is non polynomial.
-\brian{I think the phrasing ``infinite order'' can mean a lot of different things. I've changed it to ``non polynomial''.} 
-(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
-Explicitly, this action functional is
-\deq{
-  S_\infty =  \beta (\dbar + \d_S) \nu +  \gamma (\dbar + \d_S) \mu +   \beta \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \mu^2.
-}
-
-We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent.
-As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
-Explicitly, the automorphism is
-\begin{multline}
-  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
-  \beta \mapsto (\beta - \mu \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
-\end{multline}
-
-\subsection{A family of deformations}
-
-\parsec
-%check CME
-We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
-In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type.
-That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.
-
-Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
-\deq{
-  \{S + g J, S + g J \} = 0.
-}
-Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
-\deq[eq:2cond]{
-  \{S,J\} = \{J,J\} = 0.
-}
-\begin{thm}
-  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above.
-The local functional
-  \deq{
-    J = \gamma (\del \gamma)^k,
-  }
-  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
-\end{thm}
-\begin{proof}
-  First off, we consider grading issues.
-In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$.
-The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$.
-As such, we have
-  \deq{
-    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
-  }
-  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.
-
-  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}.
-It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
-It remains to check that $\{I_\infty,J\} = 0$.
-For the quadratic term, we note that
-  \deq{
-    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
-  }
-  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
-  \deq{
-    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
-}
-This expression is zero for symmetry reasons.
-Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form.
-We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form
-\end{proof}
-
-\subsection{Global symmetry algebra}
-
-\subsection{Further equivalences}
-
-\subsection{Equations of motion}
-
-%whatever we can say about the formal moduli space
-
-\subsection{Boundary conditions}
-
-%foreshadow the Horava--Witten picture
-
-\subsection{One-loop quantization}
-
-%cite result on thf quantization.
-
-\section{Symmetries of the 11-dimensional theory}
-
-\subsection{Component fields}
+\input{symmetry}
 
 %Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
-
-\subsection{Residual supersymmetry}
-
-%m2brane
-
-\parsec[sec:susy]
-
-The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
-\[
-  \ft_{11d} = V \oplus \Pi S
-\]
-where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
-The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
-this decomposes into three irreducibles, 
-\beqn\label{eqn:decomp}
-  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
-\eeqn
-Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
-The bracket in $\ft_{11d}$ is defined using the first projection
-\[
-[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
-\]
-The super Poincar\'{e} algebra is
-\[
-  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
-\]
-The $R$-symmetry is trivial in 11-dimensional supersymmetry.
-
-\parsec[sec:m2brane]
-
-Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
-In 11d, there are two such extensions corresponding to the M2 brane and the M5 brane.
-We begin by describing a dg Lie algebra model for the M2 brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
-
-The M2 brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
-Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
-
-The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
-  \[
-    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
-  \]
-  defined by the formula 
-  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
-  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.
-
-We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
-
-\parsec[sec:m2branetwist]
-
-Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
-\brian{cite \cite{SWspinor}}
-We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
-
-Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
-We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
-\deq{
-  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
-}
-In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
-Also, $\lie{so}(11, \CC)$ decomposes as
-\[
-\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
-\]
-Furthermore, the spinorial representation can be identified with
-\[
-S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
-\]
-The element $Q$ lives in the first summand.
-Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
-This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
-
-\begin{prop}\label{prop:model}
-Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
-As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
-\[
-    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
-  \]
-whose elements we denote by $(v, m, \psi, c)$.
-
-The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given the obvious extension of ${\rm Stab}(Q)$ together with the brackets
-\begin{align*}
-[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
-[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
-\end{align*}
-\end{prop}
-
-\parsec[]
-
-As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to twist of 11d supergravity.
-
-\begin{prop}
-\label{prop:gmodel}
-Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
-\[
-H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
-\]
-Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
-The nontrivial Lie brackets are
-\begin{align*}
-[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
-[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
-[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
-\end{align*}
-There is an $L_\infty$ map 
-\[
-\fg \rightsquigarrow \m2^Q
-\] 
-which is a quasi-isomorphism of complexes.  
-\end{prop}
-\begin{proof}
-The supercharge $Q$ is odd and of cohomological degree zero.
-Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
-
-The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
-The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
-The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
-So, of the translations, only the holomorphic ones $L^\vee$ survive.
-The map 
-\[
-[Q,-] \colon \lie{so}(11,\CC) \to S 
-\] 
-is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
-The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
-
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
-This completes the calculation of the cohomology.
-
-We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
-The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
-The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
-It remains to declare where $\psi \in \wedge^2 L$ is mapped.
-
-Define the map
-\[
-H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
-\]
-which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
-\[
-(H \alpha) (x) = \int_0^x \alpha .
-\]
-
-Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
-It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
-\[
-\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
-\]
-Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.
-
-The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
-On the other hand, in $\m2^Q$ there is the Lie bracket 
-\[
-[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
-\]
-The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
-The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
-\[
-v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
-\] 
-Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.
-
-\end{proof}
-
-\parsec[s:residual]
-Consider now the $\ZZ/2$ graded dg Lie algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a map of $\ZZ/2$-graded dg Lie algebras 
-\[
-\fg \to \cL 
-\]
-where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{prop:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
-\end{prop}
-\begin{proof}
-Recall the model $\fg$ takes the following form
-\beqn 
-\begin{tikzcd}
-\ul{even} & \ul{odd} & \ul{even} \\
- L_a & \wedge^2 L_b & L^\vee \\
-\wedge^2 L_a & & \\
-\lie{sl}(5) \\
-L_b \ar[r, "\id"] & L_c .
-\end{tikzcd}
-\eeqn
-The subscripts in $L_a, L_b, L_c$ are used to distinguish between the various copies of $L$.
-
-The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
-\begin{align*}
- L_a & \mapsto 0 \\
- \wedge^2 L_a & \mapsto 0 \\
-z_i \wedge z_j \in \wedge^2 L_b & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_b & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_c & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR)
-\end{align*}
-One immediately verifies that this is a map of dg Lie algebras. 
-\end{proof}
-
-\parsec[]
-
-In this section we compare to the work of \brian{Linfty refs}.
-In these references, the algebra $\m2$ is defined as an $L_\infty$  
-central extension of $\lie{siso}_{11d}$.
-
-Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
-Using this two-form we can define the following four-linear expression
-\[
-\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
-\]
-This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
-In \cite{??} it is shown that this cocycle $\mu_2$ is
-
-%For clarity we adjust notation for $\lie{sl}(5)$-representations.
-Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
-
-\subsection{Global symmetry algebra}
-
-We recall the definition of an exceptional simple super Lie algebras studied by Kac \cite{KacClass,KR}. 
-Recall that $\Vect_0 (\CC^5)$ the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
-Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
-
-The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
-\[
-E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
-\]
-whose elements we continue to denote by $\mu$. 
-The odd piece is the module 
-\[
-E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
-\]
-whose elements we denote by $\alpha$. 
-Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
-The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
-\beqn\label{eqn:e510}
-[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
-\eeqn
-One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
-In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
-
-To be precise, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
-It is this dense sub super Lie algebra which is simple.
-
-In this section, we prove the following.
-
-\begin{thm}\label{thm:global}
-Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a trivial one-dimensional extension of the super Lie algebra $E^{hol}(5,10)$.
-\end{thm}
-
-\parsec[]
-
-On $\CC^5 \times \RR$ the solutions to the linearized equations of motion of the 11-dimensional theory consists of the space of fields $(\mu, [\gamma], b)$ where:
-\begin{itemize}
-\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
-\[
-\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
-\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
-\[
-[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
-\]
-\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
-This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
-This element is also a ghost in the $\ZZ/2$-graded theory. 
-\end{itemize}
-
-\parsec[]
-
-If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
-This is the algebra of gauge symmetries, or global symmetry algebra, of the theory. 
-In the $\ZZ/2$ graded world, the parity shifted object $\Pi \cE$ has the structure of a super Lie algebra.
-
-Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
-Equivalently, this is encoded by the full BV action of the 11-dimensional theory. 
-After applying the equations of motion this $L_\infty$ structure becomes a (strict) super Lie algebra which we now explicitly describe.
-
-After parity shifted, we've identified the solutions to the linear equations of motion with triples
-\[
-(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \Pi \CC .
-\]
-The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
-Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
-The elements $b$ are central.
-
-The final term in the BV action $\int \gamma \del \gamma \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
-\beqn\label{eqn:eqb}
-\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
-\eeqn
-Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
-
-\parsec[]
-
-We complete the proof of Theorem \ref{thm:global}. 
-The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
-
-On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
-In other words, there is an isomorphism
-\[
-\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
-\]
-induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
-This completes the proof.
-
-%\begin{proof}
-%We define the map directly. 
-%The even part of $E^{hol}(5,10)$ is precisely the Lie algebra of holomorphic divergence-free vector fields on $\CC^5$. 
-%We simply embed this in the space $\PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$ of $\mu$-fields in the 11-dimensional theory. 
-%
-%The odd part of $E^{hol}(5,10)$ is the space of holomorphic closed two-forms on $\CC^5$. 
-%To embed this in the space of fields of the 11-dimensional theory we need to choose primitives. 
-%We do this by fixing a homotopy $H \colon \Omega^{2,hol}_{cl} (\CC^5) \to \Omega^{1,hol} (\CC^5)$ by
-%\[
-%(H \alpha) (z) = \int_{0}^z \alpha .
-%\]
-%Since $\alpha$ is closed, one has $\partial H \alpha = \alpha$.
-%We send $\alpha$ to the $\gamma$-type field $H \alpha$ viewed as an element of $\Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR)$. 
-%
-%All embedded elements of $E(5,10)$ are $\dbar$, $\d_{\RR}$, and $\div$-closed and so descends to a map in cohomology. 
-%The first nontrivial Lie bracket compatibility we check is between two $\alpha$-type elements. 
-%We will do this in coordinates. 
-%Suppose $f^{ij} \d z_i \wedge \d z_j$, $g^{ij} \d z_i \wedge \d z_j$ are two closed two-forms. 
-%On one hand, in $E(5,10)$ we have 
-%\[
-%[f^{ij} \d z_i \wedge \d z_j, g^{kl} \d z_k \wedge \d z_l] = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} .
-%\]
-%
-%On the other hand, in the 11-dimensional theory there is the following Lie bracket between $\gamma$-type fields
-%\begin{align*}
-%[H (f^{ij} \d z_i \wedge \d z_j), H(g^{kl} \d z_k \wedge \d z_l)] & = \big(\del H (f^{ij} \d z_i \wedge \d z_j) \wedge \del H(g^{kl} \d z_k \wedge \d z_l) \big) \vee \partial_{z_1} \wedge \cdots \wedge \partial_{z_5} \\
-%& = \ep_{ijklm} f^{ij}g^{kl} \partial_{z_m} 
-%\end{align*}
-%as desired. 
-%
-%The final Lie bracket compatibility we need to check is between a divergence-free vector field $f_i \partial_{z_i}$ and a closed two-form $g^{ij} \d z_i \wedge \d z_j$. 
-%In $E(5,10)$ we have
-%\[
-%[f_i \partial_{z_i} , g^{kl} \d z_k \wedge \d z_l] = \del (f_i g^{il} \d z_l) . 
-%\]
-%This is embedded as the one-form $f_i g^{il} \d z_l$ up to exact terms. 
-%On the other hand, in the 11-dimensional theory we have the following $[\mu,\gamma]$ type bracket
-%\begin{align*}
-%[f_i \partial_{z_i}, H(g^{kl} \d z_k \wedge \d z_l)] & = L_{f_i \partial_{z_i}} H(g^{kl} \d z_k \wedge \d z_l) \\ 
-%& = \iota_{f_i \partial_{z_i}} g^{kl} \d z_k \wedge \d z_l + \del \iota_{f_i \partial_{z_i}} H g^{kl} \d z_k \wedge \d z_l \\
-%& = f_i g^{il} \d z_l + \del - \text{exact} .
-%\end{align*}
-%
-%
-%\end{proof}
 

### 2021-09-13 draft.tex

@@
 More generally, the twist can be defined \brian{finish}
+
+As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
+We will find a match between indices counting local operators supported at a point.
+
+Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$.
+Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table
+
+\begin{tabluar}
+
+\end{tabular}
 

### 2021-09-14 dfn.tex
input
reorg

@@
-\documentclass[11pt]{amsart}
-
-\usepackage{macros-mtheory,amsaddr}
-
-\addbibresource{cfs.bib}
-
-%\linespread{1.2} %for editing
-%\usepackage{mathpazo}
-
-\begin{document}
-
 \section{The minimal twist of 11-dimensional supergravity} 
@@
 \deq{
-  S_{BF,0} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu + \frac{1}{2}  \gamma \wedge [\mu,\mu] +  \beta \wedge [\mu,\nu].
+  S_{BF,0} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu + \frac{1}{2} [\mu,\mu] \vee \gamma +  [\mu,\nu] \beta .
 }
@@
 \deq{
-  S_{BF,\infty} =  \beta \wedge (\dbar + \d_L) \nu +  \gamma \wedge (\dbar + \d_L) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} (\partial \gamma) \vee \mu^2.
+  S_{BF,\infty} =  \beta \wedge (\dbar + \d_L) \nu +  \gamma \wedge (\dbar + \d_L) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma .
 }
@@
 \begin{thm}
+\label{thm:dfn}
 Let $X$ be a Calabi--Yau five-fold and $S$ a smooth one-dimensional manifold, and consider the BV theory $(\cE, S_{BF,\infty})$ on $X \times S$ defined above. The local functional 
@@
 
-\parsec[]
+\parsec[s:altdfn]
 
@@
 \subsection{One-loop quantization}
-
-\end{document}

### 2021-09-14 matrix.tex
reorg

\section{Twisted BFFS matrix model}

\subsection{Global symmetry algebra}
\label{sec:global}

In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
More generally, after shifting the cohomological degree by one the full cohomology of states with respect to the linear BRST operator results in a graded Lie algebra. 
If we forget the grading to a $\ZZ/2$ grading then the global symmetry algebra has the structure of a super Lie algebra.

In general, taking cohomology loses information. 
If the dg Lie, or $L_\infty$ algebra, we start with is not formal then there exists higher order operations present in the linearized BRST cohomology. 
We will refer to this as the global symmetry algebra of the theory.

Before taking cohomology with respect to the linear BRST operator, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the previous section. 
This is encoded by the full BV action of the 11-dimensional theory.
The cubic component of the full BV action induces the super Lie algebra structure present in the linearized BRST cohomology.

Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional simple super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
We recall the definition below.

\begin{thm}\label{thm:global}
Let $\Pi\cE(\CC^5 \times \RR)$ be the parity shift of the fields of 11-dimensional supergravity on $\CC^5 \times \RR$ and denote by $\delta^{(1)}$ the linearized BRST operator. 
\begin{enumerate}
\item 
As a super Lie algebra, the $\delta^{(1)}$-cohomology of $\Pi\cE(\CC^5 \times \RR)$ is isomorphic to the trivial one-dimensional central extension of the super Lie algebra $E^{hol}(5,10)$.
\item 
The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E^{hol}(5,10)$ determined by the even cocycle \eqref{eqn:cocycle}. 
\end{enumerate}
\end{thm}
%defined by the even cocycle
%\begin{align*}
%E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to \CC \\
%(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
%\end{align*}

%The parity of the functional in the theorem is odd, but it is also trilinear. 
%Thus, as a cocycle in the Chevalley--Eilenberg complex of $E^{hol}(5,10)$ it is of total even parity.

The super Lie algebra $E^{hol}(5,10)$ is very closely related to the super Lie algebra $E(5,10)$ studied by Kac; there is a dense embedding of super Lie algebras $E(5,10) \hookrightarrow E^{hol}(5,10)$.

\subsection{Linearized BRST cohomology}

We compute the linearized BRST cohomology of 11-dimensional supergravity.
Then, we will describe the induced structure of a super Lie algebra present in the parity shift of the cohomology thus proving part (1) of Theorem \ref{thm:global}.

\parsec[]

First, we recall the definition of the exceptional simple super Lie algebra $E(5,10)$. 
Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.

The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
\[
E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
\]
whose elements we continue to denote by $\mu$. 
The odd piece is the module 
\[
E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
\]
whose elements we denote by $\alpha$. 
Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
\beqn\label{eqn:e510}
[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
\eeqn
One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.

More precisely, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
It is this dense sub super Lie algebra which is simple.

\parsec[]

If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cL = \cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
In the $\ZZ/2$ graded world, the parity shifted object $\cL = \Pi \cE$ has the structure of a super $L_\infty$ algebra.

In this section, we use the description of the 11-dimensional theory as the deformation of the BF action $S_{BF,\infty}$ by the functional $J$ of Theorem \ref{thm:dfn}. 
We will obtain the exact same results if we use the equivalent model of the 11-dimensional theory explained in \S \ref{s:altdfn}. 
We remark on this below in \S \ref{s:altglobal}.

The full BRST operator is given by the BV bracket with the BV action. 
For us, this~is 
\[
\delta = \{S_{BF,\infty} + J, -\} .
\]
The linear BRST operator comes only from the quadratic summands in $S_{BF,\infty}$ and is of the form
\beqn\label{eqn:linearBRST}
\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma} .
\eeqn

To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$. 
By the $\dbar$ and de Rham Poincar\'e lemmas, the cohomology of the space of fields of the 11-dimensional theory on $\CC^5 \times \RR$ with respect $\dbar + \d_{\RR}$ results in the cochain complex
\begin{equation}
  \label{eq:lin1} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + \\ \hline
    \Vect(\CC^5) \ar[r, "\div"] & \cO(\CC^5) \\ 
     \cO(\CC^5) \ar[r, "\del"] & \Omega^{1}(\CC^5).
\end{tikzcd}
\end{equation}
Recall that $\Vect(\CC^5), \cO(\CC^5)$, and $\Omega^1(\CC^5)$ denote the space of holomorphic vector fields, functions, and one-forms, respectively.

The cohomology with respect to the remaining linearized BRST operator consists of the space of triples $(\mu, [\gamma], b)$ where:
\begin{itemize}
\item $\mu$ is a divergence-free holomorphic vector field on $\CC^5$, which is constant along $\RR$
\[
\mu = \mu \otimes 1 \in \Pi \Vect_0(\CC^5) \otimes \Omega^0(\RR) .
\]
Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact holomorphic one-forms along $\CC^5$, which are also constant along $\RR$
\[
[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1}(\CC^5) / \d \cO(\CC^5) \right) \otimes \Omega^0(\RR) .
\]
\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
This element is also a ghost in the $\ZZ/2$-graded theory. 
\end{itemize}

\parsec[]

After parity shifting, we've identified the solutions to the linear equations of motion with triples
\[
(\mu, [\gamma], b) \in \Vect_0(\CC^5) \oplus \Pi \Omega^{1}(\CC^5) / \del \cO(\CC^5) \oplus \CC .
\]
The bracket induced by the cubic component of $S_{BF, \infty}$ in the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
The elements $b$ are central.

The final term in the BV action $J = \frac16\int \gamma \wedge \del \gamma \wedge \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
\beqn\label{eqn:eqb}
\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') \in \Vect_0(\CC^5) .
\eeqn
where $\Omega^{-1}$ denotes the section of $\PV^{5,hol}(\CC^5)$ which is inverse to the Calabi--Yau form $\Omega$ on $\CC^5$. 
Notice that this bracket is well-defined as it does not depend on the particular equivalence classes and that the resulting vector field is automatically divergence-free.

\parsec[]

We complete the proof of the first part of Theorem \ref{thm:global}.

The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is apparent.

Next, we need to relate the equivalence classes $[\gamma]$ with the closed two-forms $\alpha$ in $E(5,10)$. 
On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
In other words, there is an isomorphism
\[
\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
\]
induced by the holomorphic de Rham differential.
This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
This completes the proof of part (1) of Theorem \ref{thm:global}.

\subsection{(Non)formality and homotopy transfer}

We produce the following homotopy data:
\begin{equation}
\begin{tikzcd}
\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E^{hol}(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
\end{tikzcd}
\end{equation}

\begin{itemize}
\item On the $\nu$'s we take $K$ be any operator $K \colon \cO \to \Vect$ such that $\div K \nu = \nu$. 
On the $\gamma$'s we take $K$ be any operator $K \colon \Omega^1 \to \Omega^0$ such that $\del K(\gamma) = \gamma$. 
Also, introduce the auxiliary operator $\til{K} \colon \Omega^2_{cl} \to \Omega^1$ which satisfies the homotopy relation
\beqn\label{eqn:htpy1}
\til{K} \del \gamma + \del K \gamma = \gamma . 
\eeqn
The precise form of each of these operators will not be needed.
The existence of such operators is guaranteed by the holomorphic Poincar\'e lemma.
The operator $K$ annihilates fields $\beta$ and $\mu$. 
\item 
The map $q$ is described as follows. 
First $q(\mu) = \mu - K \div (\mu)$.
Notice that $q(\mu)$ is automatically divergence-free.
Next, $q(\gamma) = [\gamma]$, the equivalence class in $\Omega^1 / \d$. 
If $\beta$ is a holomorphic function, then $q(\beta) = \beta (z=0)$.
\item 
The map $i$ embeds $\mu$ and $b$ in the obvious way.
On the equivalence class $[\gamma] \in \Omega^1 / \d$ we define $i([\gamma]) = \gamma - \til{K} \del \gamma$. 
Notice that this is independent of the choice of representative $\gamma$. 
\end{itemize}

It is straightforward to check that this comprises well-defined homotopy data, the only nontrivial thing to check is the relation $\id - i \circ q = \delta^{(1)} K - K \delta^{(1)}$. 
Plugging in the field $\gamma$ we see that we must check that
\[
\gamma - \til{K} \del \gamma = \del K \gamma 
\]
which is precisely \eqref{eqn:htpy1}.

Given this homotopy data, we can compute the homotopy transferred $L_\infty$ structure on the linearized BRST cohomology following \brian{??}. 
Since $\nu$ does not survive to cohomology and the fact that there are no nontrivial Lie brackets involving the field $\beta$, this transferred structure is easy to compute.

There is a single diagram which contributes to the transferred structure, it is given by
\brian{do it}

This diagram leads to a new $3$-ary bracket on $E^{hol}(5,10) \oplus \CC_b$
\[
\big[\mu,\mu',[\gamma]\big]_3 = \varphi(\mu,\mu',[\gamma])
\]
where $\varphi \in \clie^{even} (E^{hol}(5,10))$ is the even Lie algebra cocycle defined by the formula
\beqn
\begin{array}{rclr}
\varphi \colon E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to & \CC_b \\
\varphi(\mu,\mu',\alpha) & = & \<\mu \wedge \mu', \alpha\>|_{z=0} .
\label{eqn:cocycle}
\end{array}
\eeqn
Since $b$ is central, this cocycle defines a central extension of $E^{hol}(5,10)$.

\parsec[]
We briefly remark on Lie algebra cohomology for super Lie algebras.
The Lie algebra cohomology $\clie^{\bu,\bu}(\cL)$ of any super Lie algebra $\cL$ is graded by $\ZZ \times \ZZ/2$. 
The first grading is by the symmetric degree in the Chevalley--Eilenberg complex.
The second grading is the internal parity of the super Lie algebra $\cL$. 
The Chevalley--Eilenberg differential is degree $(1,+)$.

The cocycle $\varphi$ has homogenous bigrading $(3,-)$.
In the above discussion we forgot the bigrading to a totalized $\ZZ/2$ grading where 
\begin{align*}
\clie^{even} (\cL) & = \clie^{2\bu , +} (\cL) \oplus \clie^{2\bu+1, -}(\cL) \\
\clie^{odd} (\cL) & = \clie^{2\bu , -} (\cL) \oplus \clie^{2\bu+1, +}(\cL) .
\end{align*}
With this totalization, $\varphi$ is an even cocycle and hence determines a super $L_\infty$ central extension by the one-dimensional even vector space $\CC$.

\parsec[s:altglobal]

In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.

\subsection{Twisted matrix model}

### 2021-09-14 susy.tex
reorg

--- 2021-09-13 symmetry.tex
@@
-\documentclass[11pt]{amsart}
-
-\usepackage{macros-mtheory,amsaddr}
-
-\addbibresource{cfs.bib}
-
-%\linespread{1.2} %for editing
-%\usepackage{mathpazo}
-
-\begin{document}
-
-\section{Symmetries of the 11-dimensional theory}
-\label{sec:symmetry}
-
-\subsection{Global symmetry algebra}
-\label{sec:global}
-
-Before applying the linear equations of motion, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the first section. 
-This is encoded by the full BV action of the 11-dimensional theory.
-We describe a simpler (strict) super Lie algebra structure present in the cohomology of the space of fields.
-
-In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
-More generally, the full cohomology of a $\ZZ/2$ graded space of states with respect to the linear BRST operator results in a super Lie algebra. 
-We will refer to this as the global symmetry algebra of the theory.
-
-The main result of this section is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional simple super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
-
-We recall the definition of this exceptional simple super Lie algebra.
-Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
-Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
-
-The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
-\[
-E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
-\]
-whose elements we continue to denote by $\mu$. 
-The odd piece is the module 
-\[
-E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
-\]
-whose elements we denote by $\alpha$. 
-Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
-The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
-\beqn\label{eqn:e510}
-[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
-\eeqn
-One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
-In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
-
-More precisely, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
-It is this dense sub super Lie algebra which is simple.
-
-In this section, we prove the following.
-
-\begin{thm}\label{thm:global}
-Upon applying the linearized equations of motion, the global symmetry algebra of the holomorphic twist of 11-dimensional supergravity is a one-dimensional central extension of the super Lie algebra $E^{hol}(5,10)$ defined by the even cocycle
-\begin{align*}
-E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to \CC \\
-(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
-\end{align*} 
-\end{thm}
-
-The parity of the functional in the theorem is odd, but it is also trilinear. 
-Thus, as a cocycle in the Chevalley--Eilenberg complex of $E^{hol}(5,10)$ it is of total even parity.
-
-\parsec[]
-
-If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cL = \cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
-In the $\ZZ/2$ graded world, the parity shifted object $\cL = \Pi \cE$ has the structure of a super $L_\infty$ algebra.
-
-The full BRST operator is given by the BV bracket with the BV action. 
-For us, this~is 
-\[
-\delta = \{S_{BF,\infty} + J, -\} .
-\]
-The linear BRST operator comes only from the quadratic summands in $S_{BF,\infty}$ and is of the form
-\beqn\label{eqn:linearBRST}
-\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma} .
-\eeqn
-The cohomology with respect to $\delta^{(1)}$ is what we referred to above as the global symmetry algebra.
-To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$.
-
-On $\CC^5 \times \RR$ the cohomology with respect to the linearized BRST operator $\delta^{(1)}$ consists of the space of triples $(\mu, [\gamma], b)$ where:
-\begin{itemize}
-\item $\mu$ is a divergence-free vector field on $\CC^5$, which is constant along $\RR$
-\[
-\mu = \mu \otimes 1 \in \Pi \Vect^{hol}_0(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
-\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact one-forms along $\CC^5$, which are also constant along $\RR$
-\[
-[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1,hol}(\CC^5) / \d \cO^{hol}(\CC^5) \right) \otimes \Omega^0(\RR) .
-\]
-\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
-This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
-This element is also a ghost in the $\ZZ/2$-graded theory. 
-\end{itemize}
-
-\parsec[]
-
-After parity shifting, we've identified the solutions to the linear equations of motion with triples
-\[
-(\mu, [\gamma], b) \in \Vect^{hol}_0(\CC^5) \oplus \Pi \Omega^{1,hol}(\CC^5) / \del \cO^{hol}(\CC^5) \oplus \CC .
-\]
-The bracket induced by the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
-Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
-The elements $b$ are central.
-
-The final term in the BV action $\int \gamma \wedge \del \gamma \wedge \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
-\beqn\label{eqn:eqb}
-\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') .
-\eeqn
-Notice that this bracket is well-defined as it does not depend on the particular equivalence classes.
-
-\parsec[]
-
-We complete the proof of Theorem \ref{thm:global}. 
-The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is the obvious one.
-
-On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
-In other words, there is an isomorphism
-\[
-\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
-\]
-induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
-This completes the proof.
-
-\subsection{Residual supersymmetry}
-
+\section{Residual supersymmetry} 
+\label{sec:susy}
 %m2brane
@@
 Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.
-
-\end{document}

### 2021-09-14 draft.tex
merge
reorg
index update

@@
 
+\parsec
+
 As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
@@
 
-\begin{tabluar}
+\[\begin{array}{|c|c|c|c|c|c|}
+& z_1 & z_2 & z_3 & w_1 & w_2 \\
+\hline
+q & & & & 1 & -1 \\
+t_1 & 1 & -1 & & & \\
+t_2 & & 1 & -1 & & \\
+y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
+\end{array}\]
 
-\end{tabular}
+We wish to compute the character of the space of holomorphic local operators $\Obs_0$ with respect to the above action.
+We first identify a convenient basis for the space of holomorphic local operators.
+Note that the vector space of solutions to the linearized unconstrained equations of motion is parametrized by
+\begin{align*}
+\mu^{z_i} & \in \cO(\C^5)\partial_{z_i},\ \ \ \ \ \mu^{w_j}\in\cO (\C^5)\partial_{w_j}  \\
+\nu & \in \cO (\C^5) \\
+\gamma^{z_i} & \in \cO (\C^5)dz_i, \ \ \ \ \ \gamma^{w_j}\in\cO (\C^5)d_{w_j} \\
+\beta & \in \cO (\C^5)
+\end{align*}
+
+Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_i, n_j) = (m_1, m_2, m_3, n_1,  n_2)\in \Z^5_{\geq 0}$; these are given by
+\begin{align*}
+\mu^{z_i/w_j}_{(m_i, n_j)} &: \mu^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\mu^{z_i/w_j} (0) \\
+\nu_{(m_i, n_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\nu (0) \\
+\gamma^{z_i/w_j}_{(m_i, n_j)} &: \gamma^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\gamma^{z_i/w_j} (0) \\
+\beta_{(m_i, n_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\beta (0) \\
+\end{align*}
+
+With this basis in hand we can readily compute the character. 
+\begin{lem}
+\[\chi (\Obs_0) = \frac{t_1^{-1}y+ t_1t_2^{-1}y+t_2y+q^{-1}y^{-3/2}+qy^{-3/2}-t_1y- t_1^{-1}t_2y^{-1}-t_2^{-1}y^{-1}-qy^{3/2}-q^{-1}y^{3/2}}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\]
+\end{lem}
 

### 2021-09-14 dfn.tex

@@
 
+\parsec[s:coupling]
+
+We make note of the dependence on the coupling constant $g$ in the definition of the deformed action $S_{BF,\infty} + g J$.
+
+When $g = 0$ we return to BF theory for the $L_\infty$ algebra $\cL_\infty(\CC^5) \otimes \Omega^\bu(\RR)$. 
+For any $g \ne 0$ the theories are essentially equivalent in perturbation theory. 
+Indeed, if $g \ne 0$ we can make the following field redefinition 
+\[
+\gamma \mapsto \sqrt{g} \gamma, \quad \beta \mapsto \sqrt{g} \beta 
+\]
+to write the action as 
+\[
+\frac{1}{\sqrt{g}} \left(S_{BF,\infty} + J \right)  .
+\]
+
+In perturbation theory, this has the affect of modifying the quantization parameter $\hbar$ to $\hbar / \sqrt{g}$.
+Thus, after modifying $\hbar$ and making the above field redefinition, the perturbative expansion of any theory is equivalent to the one with $g = 1$.
+
 \parsec[s:altdfn]

### 2021-09-14 susy.tex

@@
 We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the 11-dimensional theory that we proposed in Section \ref{sec:dfn} it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
+In order for this to be a symmetry of the 11-dimensional theory it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
+We will see how this central extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
 

### 2021-09-15 susy.tex
susy

@@
 
-\parsec[sec:susy]
+\subsection{Supersymmetry in 11 dimensions}
+\label{sec:11dsusy}
 
@@
 
-\parsec[sec:m2brane]
+\subsection{Central extensions of the supersymmetry algebra} 
+\label{sec:m2brane}
 
-Extensions of the supersymmetry algebra correspond to the existence of branes in the original theory of supergravity \brian{good reference?}. 
-In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the M5 brane.
-We begin by describing a dg Lie algebra model for the $M2$ brane algebra, then we will discuss its relationship to other descriptions as a Lie 3-algebra \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
+Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory \brian{good reference?}. 
+In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
+We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
+In the next section we will explain the relationship to other descriptions in terms of $L_\infty$ algebras \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
 
-The $M2$ brane algebra is dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+Our model for the $M2$ brane algebra is a dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
 Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
 
-The super dg Lie algebra $\m2$ is the extension of $\lie{siso}_{11d}$ by the cocycle
+The $M2$ brane algebra arises as a central extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
 \[
-    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
+    c_{M2} \in \clie^{2,+} \left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right) .
 \]
-  defined by the formula 
+The formula is
   \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
@@
 
-We view $\m2$ as a $\ZZ \times \ZZ/2$-graded dg Lie algebra where the bracket is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
+Here, we are using a bigrading by $\ZZ \times \ZZ/2$. 
+The super Poincar\'e algebra is concentrated in zero integer grading and carries is natural $\ZZ/2$ grading as a super Lie algebra.
+The complex $\Omega^{\bu}(\RR^{11})[2]$ is concentrated in integer degrees $[-2,9]$ and has even parity.
 
-\parsec[sec:m2branetwist]
+\begin{dfn}
+The algebra $\m2$ is the $\ZZ \times \ZZ/2$-graded dg Lie algebra defined by the central extension of $\lie{siso}_{11d}$ by the cocycle $c_{M2}$.  
+\end{dfn}
+
+The bracket in $\m2$ is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
+
+\subsection{The minimal twist}
+\label{sec:mintwist}
 
 Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-This supercharge defines the holomorphic twist of 11-dimensional supergravity. 
+Such a supercharge defines the minimal twist of 11-dimensional supersymmetry. 
 \brian{cite \cite{SWspinor}}
@@
 
-Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
-We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
+$Q$ defines a maximal isotropic subspace $L \subset V$. 
+In turn, we will decompose the super Poincar\'e algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations.
+First, the defining and spinor representations decompose as
 \deq{
@@
 
-\begin{prop}\label{prop:model}
-Fix a holomorphic supercharge $Q \in S$ and let $\m2^Q$ be the dg Lie algebra with bracket that on $\m2$ and with the differential $\d + [Q,-]$. 
-As a $\ZZ/2$ graded space, the cohomology $H^\bu(\m2^Q)$ is
-\[
-    L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC
-  \]
+\subsection{$Q$-cohomology of $\m2$}
+\label{sec:m2branetwist}
+
+Any element $Q \in S$ satisfying $Q^2 = 0$ determines a deformation of the dg Lie algebra $\m2$.
+To deform $\d$ by $Q$ we must break the $\ZZ \times \ZZ/2$ bigrading.
+The supercharge $Q$ is odd and of cohomological degree zero.
+Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the central summand and is even of cohomological degree $+1$.
+Thus, only the totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
+
+\begin{dfn}
+The $Q$-twist $\m2^Q$ of $\m2$ is the super dg Lie algebra whose differential is $\d + [Q,-]$.
+The bracket is unchanged.
+\end{dfn}
+
+We now assume that $Q$ is a rank one, or minimal, supercharge satisfying $Q^2 = 0$.
+
+\begin{prop}\label{prop:susycoh}
+As a $\ZZ/2$ graded space, the cohomology of the $Q$-twist $\m2^Q$ is
+\beqn\label{eqn:susycoh}
+L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^2 L\right) \oplus \CC
+\eeqn
 whose elements we denote by $(v, m, \psi, c)$.
 
-The transferred $L_\infty$ structure on $H^\bu(\fg) \cong H^\bu(\m2^Q)$ is a Lie-3 algebra given by the extension of ${\rm Stab}(Q)$ together with the brackets
-\begin{align*}
-[\psi, \psi']_2 & = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
-[v, v', \psi]_3 & = \<v \wedge v', \psi\> \in \CC_c .
-\end{align*}
+\begin{enumerate}
+\item As a super Lie algebra, the cohomology of $\m2^Q$ is the natural extension of ${\rm Stab}(Q)$ together with the bracket
+\beqn\label{eqn:susy2bra}
+[\psi, \psi']_2 = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
+\eeqn
+\item 
+$\m2^Q$ is not formal as a super dg Lie algebra.
+As a super $L_\infty$ algebra, the $Q$-twist is equivalent to \eqref{eqn:susycoh} with $2$-brackets described in (1) where we additionally introduce the $3$-ary bracket 
+\beqn\label{eqn:susy3bra}
+[v, v', \psi]_3 = \<v \wedge v', \psi\> \in \CC_c .
+\eeqn
+\end{enumerate}
 \end{prop}
@@
 
-As a consequence of the above proposition, we see that the dg Lie algebra $(\m2,Q)$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-Instead of this $L_\infty$ description, there is the following minimal model of this dg Lie algebra, which we will use to relate to the 11-dimensional theory. 
-This lemma implies Proposition \ref{prop:model}.
+One outcome of this proposition is that the dg Lie algebra $\m2^Q$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
+One way to prove the proposition above is to use homotopy transfer directly to $\m2^Q$, just as we did in \S \ref{s:ht} to deduce the form of the $3$-ary bracket. 
+Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition \ref{prop:susycoh}.
+This minimal model also has the advantage of being more directly related to the 11-dimensional supergravity theory.
 
@@
 \[
-H^\bu(\m2^Q) \oplus (\Pi L \xto{\id} L)  .
+H^\bu(\m2^Q) \oplus (L \xto{\id} \Pi L)  .
 \]
-Denote the elements of the second summand by $(\tilde{\lambda}, \lambda)$. 
-The nontrivial Lie brackets are
+Denote the elements of the second summand by $(\lambda, \til\lambda)$. 
+The Lie structure extends the one on $H^\bu(\m2^Q)$ described in (1) of Proposition \ref{prop:susycoh} together with the brackets
 \begin{align*}
-[v,\lambda] & = \<v, \til\lambda\> \in \CC_c \\ 
-[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}} \\
-[\psi, \psi'] & = \psi \wedge \psi' \in L^\vee_v  .
+[v,\lambda] & = \<v, \lambda\> \in \CC_c \\ 
+[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}}.
 \end{align*}
+
 There is an $L_\infty$ map 
@@
 \begin{proof}
-The supercharge $Q$ is odd and of cohomological degree zero.
-Since the differential on $\m2$ is even of cohomological degree $+1$, only a totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
 
@@
 is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
-The kernel of $[Q,-]$ is the stabilizer ${\rm Stab}(Q)$.
+The kernel of $[Q,-]$ is the stabilizer~${\rm Stab}(Q)$.
 
@@
 We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
-The central element maps to $c \mapsto \pm 1 \in \Omega^0(\RR^{11})$.
+The central element maps to $c \mapsto - 1 \in \Omega^0(\RR^{11})$.
 The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
-It remains to declare where $\psi \in \wedge^2 L$ is mapped.
+It remains to define where $\psi \in \wedge^2 L$ is mapped.
 
-Define the map
+Notice that naively, $\psi \in \wedge^2 L$ is not $Q$-closed due to the presence of the central extension. 
+To embed $\wedge^2 L$ we introduce the following operator
 \[
@@
 \]
-which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula
-\[
-(H \alpha) (x) = \int_0^x \alpha .
-\]
+which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula $(H \alpha) (x) = \int_0^x \alpha$
+where we integrate over a straight line path from $0$ to $x$.
 
@@
 \[
-[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi) - \d \<v, H \Gamma_{\wedge^2}(Q, \psi) .
+[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi)\> - \d \<v, H \Gamma_{\wedge^2}(Q, \psi)\> .
 \]
@@
 \[
-v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} \> \in L_\lambda .
+v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} (Q,\psi) \> \in L_\lambda .
 \] 
@@
 
-\parsec[s:residual]
+\parsec[]
+
+Using the model $\fg$ the first part of Proposition \ref{prop:susycoh} follows immediately. 
+We deduce the second part using homotopy transfer.
+
+Recall that we described the cohomology of $\m2^Q$ in \eqref{eqn:susycoh}.
+Let $\delta$ denote the differential on $\fg$ which simply maps $\Pi L$ to $L$ by the identity map. 
+We produce the homotopy data
+\begin{equation}
+\begin{tikzcd}
+\arrow[loop left]{l}{K}(\fg , \delta)\arrow[r, shift left, "q"] &(H^\bu(\m2^Q) \, , \, 0)\arrow[l, shift left, "i"] \: ,
+\end{tikzcd}
+\end{equation}
+as follows.
+\begin{itemize}
+\item The operator $K$ annihilates $H^\bu(\m2^Q)$ and is the identity map~$K \colon \Pi L_{\til \lambda} \to L_\lambda$. 
+\item The map $q$ is the identity on $H^\bu(\m2^Q)$ and annihilates the summand~$L \to \Pi L$. 
+\item The map $i$ embeds $H^\bu(\m2^Q)$ in the obvious way. 
+\end{itemize}
+
+It is immediate to verify this data prescribes valid homotopy data.
+There is only a single term in the $L_\infty$ structure generated by homotopy transfer. 
+It is determined by the following tree diagram. 
+\brian{do it}
+This recovers the formula in (2) of Proposition \ref{prop:susycoh}.
+
+\subsection{Embedding supersymmetry into the 11-dimensional theory} \label{s:residual}
+
 Consider now the super $L_\infty$ algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.
@@
 \begin{prop}
-There is a linear map of super $L_\infty$ algebras 
+There is a map of super $L_\infty$ algebras 
 \[
-\fg \to \cL 
+\fg \rightsquigarrow \cL 
 \]
@@
 
-The map from the dg model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory is as follows. 
+The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece
+The linear piece $\Phi^{(1)} \colon \fg \to \cL$ is
 \begin{align*}
@@
 z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-c \in \CC_c & \mapsto c \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
+1 \in \CC_c & \mapsto 1 \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
 \end{align*}
@@
 It is immediate to check that this is a map of cochain complexes where one equips $\cL$ with the linear BRST differential \eqref{eqn:linearBRST}.
-Since $\nu$ does not appear in the image of this map, to check that the higher Lie brackets are preserved one only needs to check that the $2$-ary bracket is preserved and this is immediate. 
+Since $\nu$ does not appear in the image of this map, to check that the higher Lie brackets are preserved one only needs to check that the $2$-ary brackets along with a single $3$-ary bracket. 
+The preservation of the $2$-ary brackets are clear, however the linear map $\Phi^{(1)}$ defined above is {\em not} compatible with the $3$-ary bracket present in the 11-dimensional theory
+\[
+\left[\partial_{z_i}, \partial_{z_j} , \frac12 (z_k \d z_\ell - z_\ell \d z_k) \right]_3 = \delta_k^i \delta_\ell^j - \delta_\ell^i \delta_k^j \in \Omega^{0,0}(\CC^5) \otimes \Omega^0(\RR) 
+\]
+which arises from the quartic part of the action $\frac12 \int \frac{1}{1-\nu} \mu^2 \vee \del \gamma$.
+
+To remedy this, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \times \fg \to \Pi \cL$ defined by 
+\[
+\Phi^{(2)} \left(\partial_{z_i} , z_k \wedge z_\ell\right) = \delta^i_k z_\ell - \delta^i_\ell z_k .
+\]
+To see that $\Phi^{(1)} + \Phi^{(2)}$ prescribes an $L_\infty$ map $\fg \rightsquigarrow \cL$ we need to observe the relation
+\[
+\left[\Phi^{(1)}(\partial_{z_i}), \Phi^{(1)} (\partial_{z_j}), \Phi^{(1)}(z_k \wedge z_\ell) \right]_3 = \left[\partial_{z_i}, \Phi^{(2)}(\partial_{z_j}, z_k \wedge z_\ell) \right]_2
+\]
+which is apparent. 
 \end{proof}
+
+\parsec[]
 
@@
 We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$, it is the trivial one-dimensional central extension of $E (5,10)$. 
-The cohomology of $\fg$ is described in Proposition \ref{prop:model}. 
+The Lie algebra structure present in the cohomology of $\m2^Q$ is described in part (1) of Proposition \ref{prop:susycoh}. 
 The map
@@
 \end{align*}
+
+The relationship between the transferred $L_\infty$ structures can be described as follows. 
+Recall, that the linear BRST cohomology of the parity shift of the fields of the 11-dimensional theory is equivalent to the super $L_\infty$ 
+algebra $\Hat{E(5,10)}$ which is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}.
+Also, we described the $L_\infty$ structure present in the cohomology of $\m2^Q$ in part (2) of Proposition \ref{prop:susycoh}. 
+Each of these $L_\infty$ structure involved introducing a single new $3$-ary bracket, which are easily seen to be compatible.
 

### 2021-09-15 susy.tex
susy reorg

@@
 \beqn\label{eqn:susy3bra}
-[v, v', \psi]_3 = \<v \wedge v', \psi\> \in \CC_c .
+[v, v', \psi]_3 = 4 \<v \wedge v', \psi\> \in \CC_c .
 \eeqn
@@
 \end{prop}
+
+It will be useful to list the formulas for the brackets in terms of coordinates. 
+Let $\{z_i\}$ denote a basis for $L$, which we will also think of as a linear coordinate on $\CC^5$. 
+Let $\{\partial_{z_i}\}$ be a dual basis for $L^\vee$, which we will also think of as translation invariant vector fields.
+The $2$-ary bracket above is 
+\[
+[z_i \wedge z_j, z_k \wedge z_l]_2 = \ep_{ijklm} \partial_{z_m} 
+\]
+and the $3$-ary bracket is
+\[
+[\partial_{z_i}, \partial_{z_j}, z_{k} \wedge z_{\ell}]_3 = 4 (\delta^i_k \delta^j_\ell - \delta^i_\ell \delta^j_k) .
+\]
 
@@
 \begin{prop}
+Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying 11-dimensional supergravity on $\CC^5 \times \RR$.
 There is a map of super $L_\infty$ algebras 
 \[
-\fg \rightsquigarrow \cL 
+H^\bu(\m2^Q) \rightsquigarrow \cL (\CC^5 \times \RR)
 \]
@@
 \begin{proof}
-Recall the model $\fg$ takes the following form
+Recall the cohomology of $\m2^Q$ takes the following form
 \beqn 
@@
 \ul{even} & \ul{odd} & \ul{even} \\
- L_1 & \wedge^2 L_2 & L^\vee \\
+ L & \wedge^2 L_2 & L^\vee \\
 \wedge^2 L_1 & & \\
-\lie{sl}(5) \\
-L_2 \ar[r, "\id"] & L_3 \\ 
-\CC_c & .
+\lie{sl}(5) && \CC_c  \\
+%L_2 \ar[r, "\id"] & L_3 \\ 
+ .
 \end{tikzcd}
 \eeqn
-The subscripts in $L_1, L_2, L_3$ are used to distinguish between the various copies of $L$.
+The lefthand column is ${\rm Stab}(Q)$. 
+The subscripts in $\wedge^2 L_1, \wedge^2 L_2$ are used to distinguish between the two copies of $\wedge^2 L$.
 
-The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece
-The linear piece $\Phi^{(1)} \colon \fg \to \cL$ is
+The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
+
+Define the linear map $\Phi^{(1)} \colon \fg \to \cL$ as follows:
 \begin{align*}
- L_1 & \mapsto 0 \\
+ L & \mapsto 0 \\
  \wedge^2 L_1 & \mapsto 0 \\
 z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\\frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ z_i \in L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\ \partial_{z_j} \in L^\vee & \mapsto
+\partial_{z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ %z_i \in %L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
+%z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
 1 \in \CC_c & \mapsto 1 \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
@@
 
-It is immediate to check that this is a map of cochain complexes where one equips $\cL$ with the linear BRST differential \eqref{eqn:linearBRST}.
-Since $\nu$ does not appear in the image of this map, to check that the higher Lie brackets are preserved one only needs to check that the $2$-ary brackets along with a single $3$-ary bracket. 
-The preservation of the $2$-ary brackets are clear, however the linear map $\Phi^{(1)}$ defined above is {\em not} compatible with the $3$-ary bracket present in the 11-dimensional theory
+It is immediate to check that this is a map of cochain complexes since all elements in the image of this map lie in the kernel of the linearized BRST operator \eqref{eqn:linearBRST}.
+
+This map also preserves the bracket between odd elements in $\wedge^2 L_2$. 
+In the cohomology of $\m2^Q$ we have the bracket
 \[
-\left[\partial_{z_i}, \partial_{z_j} , \frac12 (z_k \d z_\ell - z_\ell \d z_k) \right]_3 = \delta_k^i \delta_\ell^j - \delta_\ell^i \delta_k^j \in \Omega^{0,0}(\CC^5) \otimes \Omega^0(\RR) 
+[z_i\wedge z_j , z_k \wedge z_l] = \ep_{ijklm} \partial_{z_m}
 \]
-which arises from the quartic part of the action $\frac12 \int \frac{1}{1-\nu} \mu^2 \vee \del \gamma$.
+which is precisely the bracket induced by the cubic term in the action $J = \frac16 \in \gamma \del \gamma \del \gamma$.
 
-To remedy this, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \times \fg \to \Pi \cL$ defined by 
+This map does not preserve all of the brackets, however. 
+Indeed, in the 11-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
 \[
-\Phi^{(2)} \left(\partial_{z_i} , z_k \wedge z_\ell\right) = \delta^i_k z_\ell - \delta^i_\ell z_k .
+\left[\partial_{z_i}, z_j \d z_k - z_k \d z_j\right] = \delta^i_j \d z_k - \delta^i_k \d z_j 
 \]
-To see that $\Phi^{(1)} + \Phi^{(2)}$ prescribes an $L_\infty$ map $\fg \rightsquigarrow \cL$ we need to observe the relation
+arising from the cubic term in $\frac12 \int \frac{1}{1-\nu} \mu^2 \del \gamma$. 
+To remedy the failure for $\Phi^{(1)}$ to preserve the brackets, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \times \fg \to \Pi \cL$ defined by 
+\beqn\label{eqn:phi2}
+\Phi^{(2)} \left(\partial_{z_i} , z_j \wedge z_k\right) = \frac12 (\delta^i_j z_k - \delta^i_k z_j) .
+\eeqn
+Notice that the field on the right hand side is of type $\beta$.
+
+The bilinear map $\Phi^{(2)}$ provides a homotopy trivialization for the failure for $\Phi^{(1)}$ to preserve the $2$-ary bracket: 
 \[
-\left[\Phi^{(1)}(\partial_{z_i}), \Phi^{(1)} (\partial_{z_j}), \Phi^{(1)}(z_k \wedge z_\ell) \right]_3 = \left[\partial_{z_i}, \Phi^{(2)}(\partial_{z_j}, z_k \wedge z_\ell) \right]_2
+[\Phi^{(1)} (\partial_{z_i}) , \Phi^{(1)}(z_j \wedge z_k)] = \del \Phi^{(2)}\left(\partial_{z_i} , z_j \wedge z_k\right).
 \]
-which is apparent. 
+The lefthand side is $\frac12 (\delta_j^i \d z_k - \delta_k^i \d z_j)$ which is precisely the de Rham differential applied to \eqref{eqn:phi2}.
+
+To define an $L_\infty$ morphism $\Phi^{(1)} + \Phi^{(2)}$ must satisfy additional higher relations. 
+There is a single nontrivial cubic relation to verify:
+\begin{multline} \label{eqn:cubicrln}
+\Phi^{(1)}\left[\partial_{z_i}, \partial_{z_j}, z_k \wedge z_l\right]_3 = [\Phi^{(1)}(\partial_{z_i}), \Phi^{(1)}(\partial_{z_i}), \Phi^{(1)}(z_k \wedge z_l)]_3 \\ + [\del_{z_i}, \Phi^{(2)}(\partial_{z_j}, z_k \wedge z_l)] + [\del_{z_j}, \Phi^{(2)}(\del_{z_i}, z_k \wedge z_l)]
+\end{multline}
+where $[-]_3$ on the left hand side is the $3$-ary bracket defined in Proposition \ref{prop:susycoh} and $[-]_3$ on the right hand side is the $3$-ary bracket defined by the quartic part of the action $\frac12 \int \frac{1}{1-\nu} \mu^2 \vee \del \gamma$.
+The two terms in the second line of \eqref{eqn:cubicrln} cancel for symmetry reasons and the quartic term in the BV action induces precisely the correct $3$-ary bracket.
+
+%$[\Phi^{(1)}(z_i \wedge z_j), \Phi^{(1)}(z_k \wedge z_l), \Phi^{(1)} (z_m \wedge z_n)]_3 = \Phi^{(2)} ([z_i \wedge z_j, z_k\wedge z_l)], z_m \wedge z_n) + $permutations, where $[-]_3$ is the $3$-ary bracket arising from the
 \end{proof}

### 2021-09-15 draft.tex
suco

@@
 
-\input{symmetry}
+\input{matrix}
+
+\input{susy}
 
 %Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists. 
-
-\section{Twisted supergavity on AdS space}
-
-\subsection{Superconformal algebras}
-
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-\parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-\parsec[]
-\brian{discuss coupling}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \CC^4_w \times \RR .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
-
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
-\subsection{The theory on a three-fold}
+\input{suco}
 

### 2021-09-16 draft.tex
finished index

--- 2021-09-13 draft.tex
@@
 
-\input{symmetry}
+\input{matrix}
+
+\input{susy}
 
@@
 
-\subsection{Supersymmetric indices}
-
 \brian{SU(5) and SU(2) character calculations}
@@
 \section{Dimensional reduction and compactifications} 
-\include{dimred}
+\input{dimred}
 
@@
 
+\subsection{Supersymmetric indices}
+
 As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
-We will find a match between indices counting local operators supported at a point.
+We will find a match between local characters.
+We begin with descriptions of holomorphic local operators for the holomorphic twist and Poisson Chern-Simons.
 
-Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$.
-Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table
+For the holomorphic twist, note that the vector space of solutions to the linearized unconstrained equations of motion is parametrized by 
+\begin{align*}
+\mu^{z_i}\partial_{z_i} & \in \cO(\C^5)\partial_{z_i},\ \ \ \ \ \mu^{w_j}\partial_{w_j}\in\cO (\C^5)\partial_{w_j}  \\
+\nu & \in \cO (\C^5) \\
+\gamma^{z_i}dz_i & \in \cO (\C^5)dz_i, \ \ \ \ \ \gamma^{w_j}d_{w_j}\in\cO (\C^5)d_{w_j} \\
+\beta & \in \cO (\C^5)
+\end{align*}
 
-\begin{tabluar}
+Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_i; n_j) = (m_1, m_2, m_3, n_1,  n_2)\in \Z^5_{\geq 0}$; these are given by
+\begin{align*}
+ \mu^{z_i/w_j}_{(m_i; n_j)} &: \mu^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\mu^{z_i/w_j} (0) \\
+\nu_{(m_i; n_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\nu (0) \\
+\gamma^{z_i/w_j}_{(m_i; n_j)} &: \gamma^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\gamma^{z_i/w_j} (0) \\
+ \beta_{(m_i; n_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\beta (0) \\
+\end{align*}
 
-\end{tabular}
+Similarly, for the $G2\times SU(2)$ twist, the space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$.
+The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by \[A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).\]
+
+Note that there is an action of $SU(5)$ on the fields of the holomorphic twist is induced from an action on $\C^5$.
+We choose generators of the Cartan subgroup that act on $\C^5$ with weights as in the following table
+
+\[\begin{array}{|c|c|c|c|c|c|}
+& z_1 & z_2 & z_3 & w_1 & w_2 \\
+\hline
+q & & & & 1 & -1 \\
+t_1 & 1 & -1 & & & \\
+t_2 & & 1 & -1 & & \\
+y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
+\end{array}\]
+
+Upon performing the further twist, the $SU(5)$ symmetry is broken to an $SU(3)\times SU(2)$ symmetry; the cartan of the unbroken symmetries corresponds to the fugacities $q, t_1, t_2$ in the above table.
+
+We can now readily compute the characters.
+\begin{prop}
+The local character of the holomorphic twist of 11d supergravity on flat space is given by 
+\begin{align*}
+\chi_{SU(5)} (\Obs_0^\cE) &=  \\
+\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}} & \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
+\end{align*}
+Likewise, the  local character of the $G2\times SU(2)$ twist of 11d supergravity on flat space is given by
+\[
+\chi_{SU(3)\times SU(2)}(\Obs_0^{\cE_{G2\times SU(2)}}) = \prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
+\] 
+Upon specializing at $y=1$, we have that $\chi_{SU(5)} (\Obs_0^\cE)|_{y=1} =  \chi_{SU(3)\times SU(2)}(\Obs_0^{\cE_{G2\times SU(2)}}).$
+\end{prop}
+\begin{proof}
+We compute the local character as the plethystic exponential of the character of linear local operators.
+
+For the holomorphic twist, note that the linear local operators $ \nu_{(m_i, n_j)}$ and $\beta_{(m_i, n_j)}$ are of the same weight but opposite parity so contribute to the character with opposite sign.
+These contributions therefore cancel.
+Next, there is a summand of the linear local operators of the form
+\[
+\bigoplus _{(m_i;n_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\mu^{z_1}_{(m_i; n_j)}\partial_{z_1}\oplus \C\mu^{z_2}_{(m_i; n_j)}\partial_{z_2}\oplus \C\mu^{z_3}_{(m_i; n_j)}\partial_{z_3}\oplus\C\mu^{w_1}_{(m_i; n_j)}\partial_{w_1}\oplus \C\mu^{w_2}_{(m_i; n_j)}\partial_{w_2}\right).
+\] 
+This contributes 
+\[
+\sum_{(m_i;n_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
+\] 
+Finally, there is a summand of the form 
+\[
+\bigoplus _{(m_i;n_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\gamma^{z_1}_{(m_i; n_j)}d{z_1}\oplus \C\gamma^{z_2}_{(m_i; n_j)}d{z_2}\oplus\C\gamma^{z_3}_{(m_i; n_j)}d{z_3}\oplus\C\gamma^{w_1}_{(m_i; n_j)}d{w_1}\oplus \C\gamma^{w_2}_{(m_i; n_j)}d {w_2}\right).
+\] 
+This likewise contributes 
+\[
+\sum_{(m_i;n_j)\in \Z^5_{\geq 0 }}t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right).
+\] 
+In sum, the character of linear local operators is the geometric series 
+\[
+\sum_{(m_i;n_j)\in \Z^5_{\geq 0 }}-t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right).
+\] 
+The plethystic exponential of this expression is then 
+\[
+\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}}\frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (n_1+n_2)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
+\]
+
+Analogously, for the $G2\times SU(2)$ twist, linear local operators are given by \[\bigoplus_{(n_1,n_2)\in \Z^2_{\geq 0}} \C A_{(n_1,n_2)}.\] We readily see that the resulting character is \[\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}.\] The plethystic exponential is then \[\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.\]
+
+For the last part, it suffices to show that the characters of linear local operators agree upon evaluating $y=1$.
+Summing the geometric series giving the character of linear local operators in the holomorphic twist yields the rational function \[\frac{\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y &+ q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right)}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\] Specializing $y=1$, the numerator cancels with the factors in the denominator involving the $t_i$.
+The result is \[\frac{1}{(1-q^{-1})(1-q)}\] which is exactly the sum of the geometric series we found as the character of linear local operators in the $G2\times SU(2)$ twist.
+\end{proof}
 

### 2021-09-16 index.tex

--- 2021-09-16 draft.tex
@@
-\documentclass[11pt]{amsart}
-
-\usepackage{macros-mtheory,amsaddr}
-
-\addbibresource{cfs.bib}
-
-%\linespread{1.2} %for editing
-%\usepackage{mathpazo}
-
-\begin{document}
-
-\title{Twisted 11-dimensional supergravity, I}
-\author{Surya Raghavendran}
-\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
-Waterloo, Ontario N2L 2Y5\\ Canada}
-\email{??}
-\author{Ingmar Saberi}
-\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
-\email{i.saberi@physik.uni-muenchen.de}
-\author{Brian R. Williams}
-\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
-\email{brian.williams@ed.ac.uk}
-\begin{abstract}
-to do
-\end{abstract}
-\maketitle
-\newpage
-
-%\section{Symmetries of the 11-dimensional theory}
-\input{dfn}
-
-\input{matrix}
-
-\input{susy}
-
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
-
-\section{Twisted supergavity on AdS space}
-
-\subsection{Superconformal algebras}
-
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-\parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-\parsec[]
-\brian{discuss coupling}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \CC^4_w \times \RR .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
-
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\input{dimred}
-
-\subsection{The theory on a three-fold}
-
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
-\section{The non-minimal twist}
-
-We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
-We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
-
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
-\[
-A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
-\]
-where $\Pi$, as always, denotes parity shift.
-The equations of motion are of the form
-\[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
-\]
-The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
-We give a precise definition below.
-
-More generally, the twist can be defined \brian{finish}
-
 \subsection{Supersymmetric indices}
@@
 \end{proof}
-
-\subsection{The non-minimal supercharge}
-
-Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
-We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
-
-There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
-\brian{fix this}
-
-Recall that the odd component of this residual supersymmetry algebra is
-\[
-\wedge^2 L \cong \wedge^2(\CC^5) 
-\]
-which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
-Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
-
-Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
-Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
-\[
-\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
-\]
-where $i,j=1,\ldots, 5$ and $i \ne j$.
-
-\parsec[-]
-
-The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
-
-\brian{introduce PCS}
-Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
-\[
-\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
-
-\begin{thm}
-The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
-\[
-\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
-\]
-\end{thm}
-
-Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-The Lie algebra of gauge symmetries of this model on flat space is 
-\[
-\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-\]
-which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
-
-\parsec[sec:nmsymmetry]
-Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
-
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
-From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
-\[
-\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
-\]
-We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
-
-Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
-\begin{align*}
-[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
-[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
-\end{align*}
-where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
-
-From these relations, it is easy to see that any divergence-free vector field of the form:
-\begin{itemize}
-\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
-\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
-\end{itemize}
-are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
-Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
-
-Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
-\[
-H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
-\]
-Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
-\[
-0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
-Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
-
-\section{The twisted $\Omega$-background}
-
-\subsection{$\Omega$-deformed symmetry algebra}
-
-On flat space, we have
-
-\subsection{M2 branes in the $\Omega$-background}
-
-\parsec[]
-
-In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
-\beqn\label{eqn:m2omega}
-\{0\} \times \RR \subset \CC^2 \times \RR .
-\eeqn
-
-The field which sources this brane is a distributional differential form $F$.
-The linear equation of motion for $F$ is the distributional equation 
-\[
-\d^2 z \wedge \dbar F = N \delta_{z=0} 
-\]
-where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
-In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
-
-The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
-Explicitly, we can characterize it as follows.
-
-\begin{prop}
-The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
-\[
-F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
-\] 
-satisfies the non-linear equation of motion 
-\[
-\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
-\]
-\end{prop}
-\begin{proof}
-The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
-Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
-\end{proof}
-
-\parsec[]
-
-We can interpret $F$ geometrically in the following way. 
-Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
-
-On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
-\]
-where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
-The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
-$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
-
-Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
-Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
-\[
-\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
-\]
-
-In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
-\[
-(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
-\]
-of the $(0,1)$-form
-\[
-F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
-\] 
-The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
-\[
-\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
-\]
-
-\appendix
-
-\section{An alternative description of the 11-dimensional theory} 
-In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
-The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
-
-There is a related, alternative description of this formal moduli space which is almost equivalent. 
-Consider the resolution of holomorphic closed two-forms 
-\beqn\label{eqn:twoform}
-\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
-\eeqn
-where we have left the $\dbar$-differential implicit, as always.
-
-There is a map from the two-term complex 
-\[
-\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
-\]
-to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
-This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
-
-Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
-\[
-\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
-\]
-Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
-The left-hand side contains the fields $(\beta, \gamma)$. 
-This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
-
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
-The new space of fields is 
-\begin{equation}
-  \label{eq:poissfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-     - & + & - & + \\ \hline
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
-     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
-\end{tikzcd}
-\end{equation}
-
-It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
-We'd like to point out two main differences:
-\begin{itemize}
-\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
-Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
-For this reason, we will refer to the theory as a ``Poisson BV theory''. 
-\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
-However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
-Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
-\end{itemize}
-
-\begin{prop}
-The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
-Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
-\end{prop}
-
-Heuristically, we can write the action in the following non-local form
-\[
-\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
-\]
-\brian{are there more terms involving higher forms?}
-
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\eta]_1 & = \dbar \eta + \del \eta \\ 
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
-[\mu, \eta]_2 & = \mu \vee \del \eta \\
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\begin{align*}
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
-\end{align*}
-
-\parsec[]
-Consider the theory on $\CC^3 \times \RR$. 
-There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
-
-\parsec[]
-Consider the theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a quasi-isomorphism of super $L_\infty$ algebras 
-\[
-E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
-\]
-This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
-\end{prop}
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belong}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
-Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
-%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
-
-\begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
-In particular, the non-linear BRST operator 
-\beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
-\eeqn
-is $\CC^\times$ weight zero.
-\end{lem}
-\begin{proof}
-%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
-We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is holomorphic polyvector field type, and the second is descendant degree.
-The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
-
-We introduce notation in this proof that won't be used later on. 
-Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
-If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
-If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
-
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
-\[
- \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
-\]
-Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
-In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
-\begin{align*}
-\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
-\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
-\end{align*}
-The first constraint ensures that the integrand is of top polyvector degree. 
-The second constraint is on the descendant degree, see \brian{ref above}.
-
-Simplifying these two equations, one finds the condition
-\[
-m+n-3 = m+(d-2)n - d 
-\]
-which implies $n=1$, as desired. 
-\end{proof}
-
-Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
-The $\CC^\times$ weight zero subcomplex is 
-\[
-\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
-\]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
-
-\begin{prop}
-\label{prop:Linfty}
-The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
-\[
-\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
-\]
-with $[-]_1 = \dbar + \div$. 
-Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
-\end{prop}
-
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
-
-\end{document}

### 2021-09-16 suco.tex

--- 2021-09-14 draft.tex
@@
-\documentclass[11pt]{amsart}
+\section{Twisted supergavity on AdS space}
 
-\usepackage{macros-mtheory,amsaddr}
-
-\addbibresource{cfs.bib}
-
-%\linespread{1.2} %for editing
-%\usepackage{mathpazo}
-
-\begin{document}
-
-\title{Twisted 11-dimensional supergravity, I}
-\author{Surya Raghavendran}
-\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
-Waterloo, Ontario N2L 2Y5\\ Canada}
-\email{??}
-\author{Ingmar Saberi}
-\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
-\email{i.saberi@physik.uni-muenchen.de}
-\author{Brian R. Williams}
-\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
-\email{brian.williams@ed.ac.uk}
-\begin{abstract}
-to do
-\end{abstract}
-\maketitle
-\newpage
-
-%\section{Symmetries of the 11-dimensional theory}
-\input{dfn}
-
-\input{symmetry}
-
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists.
-
-\section{Twisted supergavity on AdS space}
+\brian{need to motivate osp}
 
@@
 \subsection{The ${\rm AdS}_7 \times S^4$ background}
+
+In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
+In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 
-\parsec[]
-\brian{discuss coupling}
+In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
+In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 \[
-\CC_z \times \CC^4_w \times \RR .
+\CC_z \times \RR \times \CC^4_w .
 \]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\}\subset \CC^5$.
+Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
 
@@
 \[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Dol\left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
+\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Omega^{\bu} \left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
 \]
@@
 \[
-F \in \Bar{\PV}^{1,4}(\CC^5) \otimes \Omega^0 (\RR) .
+F \in \Bar{\PV}^{1,3}(\CC^5) \otimes \Omega^0 (\RR) .
 \]
@@
 
-Recall the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the M2 brane as compared to the M5 brane. 
+To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory and those in the twisted theory.
+
+We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
+We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w=0\}$ which corresponds to the twist of the 3d superconformal algebra.
+We first focus on the case where the flux $N=0$, in this case the embedding can be extended to all of $\CC^5 \times \RR$.
+
+\parsec[]
+
+The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
+For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the $M2$ brane as compared to the $M5$ brane. 
 The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
@@
 
+\begin{lem}
+These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the 11-dimensional theory on $\CC^5 \times \RR$. 
+Equivalently, it defines an embedding
+\[
+\lie{osp}(6|1) \hookrightarrow E(5,10) .
+\]
+\end{lem}
+
+The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
+Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
+To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above:
+\begin{itemize}
+\item 
+The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
+\[
+\d w_a \wedge \d w_b, \quad a,b=1,2,3,4. 
+\] 
+\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
+\[
+(z \d w_a  \wedge \d w_b + \ep^{abcd} w_c \d z \wedge \d w_d) , \quad a,b=1,2,3,4. 
+\] 
+\end{itemize}
+
+\parsec[]
+
+Next, we turn on a nontrivial unit of flux $N \ne 0$. 
+Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N\til F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
+Nevertheless, we have the following.
+
+\begin{prop}
+There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N \til F,-]$. 
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the $\delta^{(1)} + [N \til F,-]$ cohomology of the fields of 11-dimensional supergravity on $\CC^5 \times \RR \setminus \CC \times \RR$.
+\end{prop}
+
+\begin{proof}
+Let $\cL(\CC^5 \times \RR \setminus \CC \times \RR)$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory. 
+We make the identification $\CC^5 \times \RR \setminus \{w=0\} \cong (\CC_w^4 \setminus 0) \times \CC_z \times \RR$. 
+Recall that we are viewing $\til F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
+As such, the operator $[N \til F,-]$ acts on the fields according to two types of maps:
+\begin{align*}
+[N \til F ,-] & \colon \PV^{i,\bu}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \PV^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \\
+[N \til F,-] & \colon \Omega^{i,\bu}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \Omega^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR).
+\end{align*}
+
+\brian{get the filtration straight}
+
+The first page of the spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$. 
+Recall that the linearized BRST differential decomposes as
+\[
+\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma}  .
+\]
+To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
+This first page of this auxiliary spectral sequence is simply given by the cohomology with respect to $\dbar + \d_{\RR}$. 
+This cohomology is given by
+\begin{equation}
+  \label{eqn:ads4ss} 
+  \begin{tikzcd}[row sep = 1 ex]
+    + & - \\ \hline
+H^\bu(\CC^4\setminus 0, \T) \otimes H^\bu(\CC, \cO) & H^\bu(\CC^4 \setminus 0, \cO) \otimes H^\bu(\CC, \cO) \\
+H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \T) \\
+H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \cO) & H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \Omega^1) \\ & H^\bu(\CC^4\setminus 0, \Omega^1) \otimes H^\bu(\CC, \cO)  
+\end{tikzcd}
+\end{equation}
+where $\T$ denotes the holomorphic tangent sheaf, $\Omega^1$ denotes the sheaf of holomorphic one-forms, and $\cO$ is the sheaf of holomorphic functions.
+
+The cohomology of $\CC$ is concentrated in degree zero and there is a dense embedding
+\[
+\CC[z] \hookrightarrow H^\bu(\CC, \cF) 
+\]
+for $\cF = \cO, \T$, or $\Omega^1$.
+
+For $\cF = \cO, \T$, or $\Omega^1$, the cohomology $H^\bu(\CC^4 \setminus 0, \cF)$ is concentrated in degrees $0$ and $3$. 
+There are the following dense embeddings 
+\begin{align*}
+\CC[w_1,\ldots, w_4] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
+\CC[w_1,\ldots, w_4] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
+\CC[w_1,\ldots, w_4] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) 
+\end{align*}
+and
+\begin{align*}
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) .
+\end{align*}
+
+It follows that (up to completion) the cohomology 
+\[
+H^\bu(\cL(\CC^5 \times \RR \setminus \CC \times \RR) , \dbar)
+\]
+is the direct sum of $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with 
+\begin{equation}
+  \label{eqn:ads4ss2} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + \\ \hline
+H^3(\CC^4\setminus 0, \T)[z] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & H^3(\CC^4 \setminus 0, \cO) [z] \\
+H^3(\CC^4\setminus 0, \cO) [z] \partial_z \ar[ur, dotted, "\div"] \\
+H^3(\CC^4\setminus 0, \cO) [z] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"] & H^3(\CC^4\setminus 0, \cO)[z] \d z \\ & H^3(\CC^4\setminus 0, \Omega^1)[z] \{\d w_i\} .
+\end{tikzcd}
+\end{equation}
+The remaining piece of the original BRST operator is drawn in dotted lines. 
+The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N\til F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
+In this description the image of the flux $\til F$ at this page in the spectral sequence corresponds to the following class 
+\[
+[\til F] = (w_1 \cdots w_4)^{-1} \partial_z \in H^3(\CC^4\setminus 0, \cO) [z] \partial_z .
+\]
+
+The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N \til F,-]$. 
+As observed above, this operator maps Dolbeault degree zero elements to Dolbeault degree three elements. 
+For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.
+
+The embedding of $\lie{osp}(6|1)$ we wrote down above lives in the kernel of the original BRST operator $\delta^{(1)}$. 
+To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [\til F] , - \big]$. 
+This is a direct calculation. 
+For instance, recall that an element in the image of the odd summand $(\wedge^2 \CC^2)_{-1}$ (which corresponds to a superconformal transformation) is of the form $z w_a \wedge \d w_b = z(w_a \d w_b - w_b \d w_a)$.
+We have
+\[
+\big[ N [\til F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
+\]
+since the class $(w_1\cdots w_4)^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for any $a = 1,\ldots 4$. 
+\end{proof}
 \subsection{Supersymmetric indices}
@@
 \subsection{The theory on a three-fold}
-
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
-\section{The non-minimal twist}
-
-We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
-We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
-
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
-\[
-A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
-\]
-where $\Pi$, as always, denotes parity shift.
-The equations of motion are of the form
-\[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
-\]
-The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
-We give a precise definition below.
-
-More generally, the twist can be defined \brian{finish}
-
-\parsec
-
-As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
-We will find a match between indices counting local operators supported at a point.
-
-Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$.
-Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table
-
-\[\begin{array}{|c|c|c|c|c|c|}
-& z_1 & z_2 & z_3 & w_1 & w_2 \\
-\hline
-q & & & & 1 & -1 \\
-t_1 & 1 & -1 & & & \\
-t_2 & & 1 & -1 & & \\
-y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
-\end{array}\]
-
-We wish to compute the character of the space of holomorphic local operators $\Obs_0$ with respect to the above action.
-We first identify a convenient basis for the space of holomorphic local operators.
-Note that the vector space of solutions to the linearized unconstrained equations of motion is parametrized by
-\begin{align*}
-\mu^{z_i} & \in \cO(\C^5)\partial_{z_i},\ \ \ \ \ \mu^{w_j}\in\cO (\C^5)\partial_{w_j}  \\
-\nu & \in \cO (\C^5) \\
-\gamma^{z_i} & \in \cO (\C^5)dz_i, \ \ \ \ \ \gamma^{w_j}\in\cO (\C^5)d_{w_j} \\
-\beta & \in \cO (\C^5)
-\end{align*}
-
-Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_i, n_j) = (m_1, m_2, m_3, n_1,  n_2)\in \Z^5_{\geq 0}$; these are given by
-\begin{align*}
-\mu^{z_i/w_j}_{(m_i, n_j)} &: \mu^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\mu^{z_i/w_j} (0) \\
-\nu_{(m_i, n_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\nu (0) \\
-\gamma^{z_i/w_j}_{(m_i, n_j)} &: \gamma^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\gamma^{z_i/w_j} (0) \\
-\beta_{(m_i, n_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\beta (0) \\
-\end{align*}
-
-With this basis in hand we can readily compute the character. 
-\begin{lem}
-\[\chi (\Obs_0) = \frac{t_1^{-1}y+ t_1t_2^{-1}y+t_2y+q^{-1}y^{-3/2}+qy^{-3/2}-t_1y- t_1^{-1}t_2y^{-1}-t_2^{-1}y^{-1}-qy^{3/2}-q^{-1}y^{3/2}}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\]
-\end{lem}
-
-\subsection{The non-minimal supercharge}
-
-Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
-We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
-
-There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
-\brian{fix this}
-
-Recall that the odd component of this residual supersymmetry algebra is
-\[
-\wedge^2 L \cong \wedge^2(\CC^5) 
-\]
-which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
-Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
-
-Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
-Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
-\[
-\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
-\]
-where $i,j=1,\ldots, 5$ and $i \ne j$.
-
-\parsec[-]
-
-The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
-
-\brian{introduce PCS}
-Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
-\[
-\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
-
-\begin{thm}
-The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
-\[
-\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
-\]
-\end{thm}
-
-Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-The Lie algebra of gauge symmetries of this model on flat space is 
-\[
-\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-\]
-which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
-
-\parsec[sec:nmsymmetry]
-Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
-
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
-From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
-\[
-\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
-\]
-We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
-
-Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
-\begin{align*}
-[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
-[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
-\end{align*}
-where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
-
-From these relations, it is easy to see that any divergence-free vector field of the form:
-\begin{itemize}
-\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
-\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
-\end{itemize}
-are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
-Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
-
-Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
-\[
-H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
-\]
-Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
-\[
-0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
-Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
-
-\section{The twisted $\Omega$-background}
-
-\subsection{$\Omega$-deformed symmetry algebra}
-
-On flat space, we have
-
-\subsection{M2 branes in the $\Omega$-background}
-
-\parsec[]
-
-In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
-\beqn\label{eqn:m2omega}
-\{0\} \times \RR \subset \CC^2 \times \RR .
-\eeqn
-
-The field which sources this brane is a distributional differential form $F$.
-The linear equation of motion for $F$ is the distributional equation 
-\[
-\d^2 z \wedge \dbar F = N \delta_{z=0} 
-\]
-where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
-In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
-
-The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
-Explicitly, we can characterize it as follows.
-
-\begin{prop}
-The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
-\[
-F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
-\] 
-satisfies the non-linear equation of motion 
-\[
-\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
-\]
-\end{prop}
-\begin{proof}
-The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
-Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
-\end{proof}
-
-\parsec[]
-
-We can interpret $F$ geometrically in the following way. 
-Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
-
-On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
-\]
-where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
-The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
-$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
-
-Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
-Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
-\[
-\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
-\]
-
-In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
-\[
-(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
-\]
-of the $(0,1)$-form
-\[
-F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
-\] 
-The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
-\[
-\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
-\]
-
-\appendix
-
-\section{An alternative description of the 11-dimensional theory} 
-In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
-The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
-
-There is a related, alternative description of this formal moduli space which is almost equivalent. 
-Consider the resolution of holomorphic closed two-forms 
-\beqn\label{eqn:twoform}
-\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
-\eeqn
-where we have left the $\dbar$-differential implicit, as always.
-
-There is a map from the two-term complex 
-\[
-\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
-\]
-to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
-This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
-
-Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
-\[
-\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
-\]
-Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
-The left-hand side contains the fields $(\beta, \gamma)$. 
-This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
-
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
-The new space of fields is 
-\begin{equation}
-  \label{eq:poissfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-     - & + & - & + \\ \hline
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
-     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
-\end{tikzcd}
-\end{equation}
-
-It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
-We'd like to point out two main differences:
-\begin{itemize}
-\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
-Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
-For this reason, we will refer to the theory as a ``Poisson BV theory''. 
-\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
-However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
-Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
-\end{itemize}
-
-\begin{prop}
-The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
-Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
-\end{prop}
-
-Heuristically, we can write the action in the following non-local form
-\[
-\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
-\]
-\brian{are there more terms involving higher forms?}
-
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\eta]_1 & = \dbar \eta + \del \eta \\ 
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
-[\mu, \eta]_2 & = \mu \vee \del \eta \\
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\begin{align*}
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
-\end{align*}
-
-\parsec[]
-Consider the theory on $\CC^3 \times \RR$. 
-There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
-
-\parsec[]
-Consider the theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a quasi-isomorphism of super $L_\infty$ algebras 
-\[
-E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
-\]
-This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
-\end{prop}
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belong}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
-Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
-%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
-
-\begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
-In particular, the non-linear BRST operator 
-\beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
-\eeqn
-is $\CC^\times$ weight zero.
-\end{lem}
-\begin{proof}
-%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
-We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is holomorphic polyvector field type, and the second is descendant degree.
-The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
-
-We introduce notation in this proof that won't be used later on. 
-Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
-If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
-If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
-
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
-\[
- \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
-\]
-Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
-In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
-\begin{align*}
-\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
-\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
-\end{align*}
-The first constraint ensures that the integrand is of top polyvector degree. 
-The second constraint is on the descendant degree, see \brian{ref above}.
-
-Simplifying these two equations, one finds the condition
-\[
-m+n-3 = m+(d-2)n - d 
-\]
-which implies $n=1$, as desired. 
-\end{proof}
-
-Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
-The $\CC^\times$ weight zero subcomplex is 
-\[
-\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
-\]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
-
-\begin{prop}
-\label{prop:Linfty}
-The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
-\[
-\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
-\]
-with $[-]_1 = \dbar + \div$. 
-Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
-\end{prop}
-
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
-
-\end{document}

### 2021-09-16 dimred.tex
merge

@@
-In this section we wish to demonstrate that our proposal for the interactions for twisted 11-dimensional supergravity agree with conjectural descriptions of twisted type IIA and type I supergravities due to \cite{CLSugra}.
-We begin by introducing certain variants of Kodaira-Spencer theory which will feature in the descriptions of twists of type IIA and type I.
+\section{Dimensional reduction and 10-dimensional supergravity}
+
+In this section we demonstrate that our proposal for the action of minimally twisted 11-dimensional supergravity agrees with conjectural descriptions of twisted type IIA and type I supergravities due to Costello and Li.
+
+The original motivation for $M$-theory was as the strong coupling limit for type IIA string theory.
+Roughly, the radius of the $M$-theory circle plays the role of this coupling constant. 
+Additionally, at low energies $M$-theory is expected to be approximated by 11-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity.
+Combining these two pictures, various checks have been made that the dimensional reduction of 11-dimensional supergravity along the $M$-theory circle is type IIA supergravity.
+
+Motivated by the topological string, Costello and Li have laid out a series of conjectures for twists of type IIA/IIB supergravity \cite{CLsugra} and type I supergravity \cite{CLtypeI}. 
+Their description was inspired by the model of the open and closed $B$-model topological string on a Calabi--Yau manifold. 
+The open sector is holomorphic Chern--Simons theory \cite{WittenOpen} and the closed sector is called Kodaira--Spencer theory \cite{BCOV}. 
+There are a few different versions of Kodaira--Spencer theory, but the shared characteristic is that they are all `gravitational' in nature; they describe fluctuations of the Calabi--Yau structure. 
+From this point of view, Kodaira--Spencer theory is at the heart of the formulation of the various flavors of twisted 10-dimensional supergravity.
+
+We begin by introducing certain variants of Kodaira--Spencer theory which will feature in the descriptions of twists of type IIA and type I supergravity.
+
+\subsection{Kodaira--Spencer theory}
+
+Let $X$ be a Calabi--Yau manifold; for now it can be of arbitrary complex dimension. 
+Define
+\deq{
+  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
+}
+We will consider the graded space $\PV^{\bu,\bu}(X) = \oplus_{i,j} \PV^{i,j}(X)[-i-j]$ where the piece of type $(i,j)$ sits in degree $i+j$.
+
+For each fixed $i$, while we let $j$ vary, the $\dbar$ operator defines a cochain complex $\PV^{i,\bu}(X) = (\oplus_j\PV^{i,j}(X) [-j], \dbar)$ which provides a resolution for the sheaf of holomorphic polyvector fields of type $i$.
+The divergence operator extends to an operator of the form
+\[
+\div \colon \PV^{i,\bu}(X) \to \PV^{i-1,\bu}(X) .
+\]
+
+Motivated by the states of the topological $B$-model, one defines the fields of Kodaira--Spencer gravity on $X$ to be the cochain complex
+\beqn\label{eqn:ks1}
+\left(\PV^{\bu,\bu} (X)[[u]] [2] \, , \, \dbar + u \div\right) .
+\eeqn 
+Here, $u$ is a parameter of cohomological degree $+2$, which turns $\delta_{KS}^{(1)} = \dbar + u \div$ into an operator of homogenous degree $+1$. 
+We also have performed an overall cohomological shift by $2$ so that $u^k \PV^{i,j}$ sits in degree $i+j+2k-2$. 
+More precisely, this is a model for the $S^1$-equivariant cohomology of the states of the $B$-model on a closed disk. 
+We refer to \cite{CLtypeI, CLsugra} for detailed justification for this ansatz.
+
+\brian{surya, could fill these parsecs in?}
+
+\parsec[s:poisson]
+
+%describe odd poisson structure
+
+\parsec[s:ksaction]
+
+%recall genus zero BCOV action.
+
+\parsec[s:minimalks]
+
+%define minimal ks
+
+\subsection{The $SU(4)$ twist of type IIA supergravity}
 
@@
 
-Let $X$ be a Calabi-Yau manifold.
-Recall the $\Z/2$ graded Poisson BV theory denoted $\cE_{KS}$ defined in section \surya{}.
-Let $\cE_{{mKS}}\subset \cE_{KS}$ denote the smallest subcomplex containing those fields with nonzero pairing under the Poisson tensor.
-Explicitly, we have that $cE_{mKS}$ is the sheaf of cochain complexes
+Let $X$ be a Calabi-Yau manifold of complex dimension four. 
+The complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
 \beqn
@@
                         &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
-                        & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
-{\PV^{3,\bu}} \arrow[r] & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
+                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
+{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
 \end{tikzcd}.
 \eeqn
+Denote this complex by $\cE_{mKS}(X)$. 
+The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.
 
-Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory.
+\brian{I've commented this out below, since we should just introduce minimal BCOV in general up above}
+
+%Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory.
 Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.
@@
 \begin{conj}
-  Let $M$ be a real symplectic surface and $X$ a Calabi-Yau fourfold.
-The $SU(4)$-invariant twist of type IIA supergravity on $M\times X$ is the $\Z/2$-graded Poisson BV theory with fields \[\Omega^{\bu}(M)\otimes \cE_{mKS}.\] The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
+The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields \[
+\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).\] 
+The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
+%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
 \end{conj}
+
+We will need a more detailed description of the classical action. 
+For the moment, let us introduce some notations for the fields of this IIA model, as always we leave the internal Dolbeault degree implicit:
+\begin{multline}
+\eta \in \PV^{0,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2), \quad \mu + u \nu \in \PV^{1, \bu}(\CC^4) \otimes \Omega^\bu (\RR^2) \oplus u \PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) \\
+\Pi \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2), \quad \sigma \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2) .
+\end{multline}
+We will not need an explicit notation for the remaining descendant fields.
+
+With this notation in hand, we have the more precise form of the action appearing in the conjecture:
+\beqn\label{eqn:IIAaction}
+I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \Pi + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \sigma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \Pi^2 + \cdots
+\eeqn
+where the $\cdots$ denote terms involving higher order descendants.
 
@@
 
-Our goal is to compare the dimensional reduction of our 11d theory $\cE$ on $\R\times \C^{\times}\times X$ where $X$ is a Calabi-Yau 4-fold with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$.
+Our goal is to compare the dimensional reduction of our 11-dimensional theory on $\CC^5 \times \RR$
+%where $X$ is a Calabi-Yau 4-fold 
+with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times \CC^4$. 
 Doing so will require some additional modifications to the above conjectural description.
-Indeed, recall that in the physical theory, the components of the C-field in 11d that are not supported along the M-theory circle become the components of the Ramond-Ramond 2-form of type IIA.
-However, as noted in \cite{CLSugra} components of Ramond-Ramond fields do not appear as fields in Kodaira-Spencer theory; rather it is components of their field strengths that appear.
-Since components of the C-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
 
-Minimal Kodaira-Spencer theory with potentials on a Calabi-Yau fourfold $X$ is defined to be the $\Z/2$-graded BV theory whose space of fields is the sheaf of cochain complexes $\cE_{pot}$
-\beqn
+Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA.
+However, as noted in \cite{CLSugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
+Since components of the $C$-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
+
+Explicitly, to define this theory we introduce a potential for both the $\Pi$ and $\sigma$ fields. 
+First, we introduce a field $\gamma$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi = \div \gamma$.
+This condition does not uniquely fix $\gamma$. 
+There is a new linear gauge symmetry determined by $\gamma \to \gamma + \div \beta$ where $\beta$ is a ghost that we must also introduce. 
+Similarly, we introduce a field $\theta$ which satisfies $\sigma = \div \theta$, there is no extra gauge symmetry present in this condition.
+
+In diagrammatic detail, the potential theory we are considering has underlying cochain complex of fields
+\beqn\label{eqn:IIApot}
 \begin{tikzcd}
-& {\PV^{0,\bu}}_\eta  \\
-{\PV^{1,\bu}}_\mu \arrow[r, "u\div"] & {u\PV^{0,\bu}}_\nu \\
-{u^{-1}\PV^{4,\bu}}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu}}_\gamma  \\
-{\PV^{4,\bu}}_\theta &
+- & + \\ \hline
+& {\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) }_\eta  \\
+{\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
+u^{-1}{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
+{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
 \end{tikzcd}
@@
 
-The interaction is given by \[I_{pot} = \int \frac{1}{1-\nu}(\mu\mu\del\gamma + \eta\del\gamma\del\gamma + \eta\mu\del\theta).\]
+Recall that the original fields of the IIA supergravity model on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
+In other words, it did not define a theory in the conventional BV formalism. 
+One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd non-degenerate pairing thus equipping it with the structure of a theory in the conventional BV formalism.
 
-Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
-\beqn
-\begin{tikzcd}
-                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
-{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
-{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
-{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
-\end{tikzcd}.
+The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \wedge \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
+Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
+\[
+\int^\Omega_{\CC^4 \times \RR^2} \eta \wedge \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \wedge \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \wedge \beta .
+\]
+This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$. \brian{finish}
+
+The type IIA action completely determines the action of this theory with potentials. 
+One simply takes the \eqref{eqn:IIAaction} and replaces all appearances of $\Pi$ with $\div \gamma$ and all appearances of $\sigma$ with $\div \theta$. 
+This yields the interaction of the potential theory
+\beqn\label{eqn:IIAactionpot}
+\til I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \div \gamma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \div \theta + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \div \gamma \wedge \div \gamma
 \eeqn
-This is easily seen to be a Poisson map.
+Notice that the terms involving higher descendants vanishes since these fields are set to zero in the potential theory.
+
+%Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
+%\beqn
+%\begin{tikzcd}
+%                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
+%{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
+%{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
+%{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
+%\end{tikzcd}.
+%\eeqn
+%This is easily seen to be a Poisson map.
 We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation.
@@
 \parsec[sec:dimred]
+
+We turn to the proof of the main result of this section that the dimensional reduction of our 11-dimensional theory agrees with the twist of IIA supergravity just introduced.
+
+We recall the notion of dimensional along a holomorphic direction following \cite{ESW}. 
+Suppose that $V_\RR$ is a real vector space and denote by $V$ its complexification. 
+We consider a field theory defined on $M \times V$, which is holomorphic along $V$ (in particular, this means that the theory is translation invariant along $V$).  
+We consider the dimensional reduction along the projection 
+\beqn\label{eqn:dimred}
+M \times V \to M \times V_\RR
+\eeqn
+induced by ${\rm Re} \colon V \to V_\RR$.
+Most relevant for us is the case when $V = \CC$ and $M$ is $\CC^4 \times \RR$, but the explicit form of the theory along $M$ is not important at the moment.
+
+In fact, we might as well assume that $M$ is a point and that the space of fields is of the form $\Omega^{0,\bu}(V) \otimes W$ for $W$ some graded vector space. 
+As properly formulated in \cite{ESW}, it is shown that the dimensional reduction along $V \to V_\RR$ is equivalent to the theory whose fields are $\Omega^\bu(V_\RR) \otimes W$. 
+In other words, the dimensional reduction of the holomorphic theory on $V$ is a topological theory on $V_\RR$.
+
+If we put $M$ back in, the result is similar. 
+Suppose the original theory is of the form $\cE(M) \otimes \Omega^{0,\bu}(V) \otimes W$.
+Then, the dimensional reduction along \eqref{eqn:dimred} is the theory whose space of fields is $\cE(M) \otimes \Omega^\bu(V_\RR) \otimes W$.
+
+An explicit model for this reduction can be described as follows. 
+Suppose $V \cong \CC^n$ and place the theory on $(\CC^\times)^{\times n} \subset \CC^n$. 
+The dimensional reduction along $\CC^n \to \RR^n$ agrees with the compactification of the theory along $S^1 \times \cdots \times S^1$ where one throws away all nonzero winding modes around each circle.
+
 \begin{prop}
-The $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$ is the dimensional reduction of the 11d theory $\cE$ on $\R\times \C^{\times}\times X.$
+The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is equivalent to the dimensional reduction of the 11-dimensional along  
+\[
+\CC^4 \times \CC \times \RR \to \CC^4 \times \RR \times \RR \cong \CC^4 \times \RR^2 .
+\]
 \end{prop}
 \begin{proof}
-We use the notion of dimensional reduction as defined in \cite{}.
 Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.

### 2021-09-16 draft.tex
merge

--- 2021-09-15 draft.tex
@@
 
-%\section{Symmetries of the 11-dimensional theory}
 \input{dfn}
@@
 
-%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists. 
-\input{suco}
+\input{dimred}
 
 %count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
+
+\input{suco}
 
@@
 
-\parsec
-
-As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons.
-We will find a match between indices counting local operators supported at a point.
-
-Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$.
-Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table
-
-\[\begin{array}{|c|c|c|c|c|c|}
-& z_1 & z_2 & z_3 & w_1 & w_2 \\
-\hline
-q & & & & 1 & -1 \\
-t_1 & 1 & -1 & & & \\
-t_2 & & 1 & -1 & & \\
-y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
-\end{array}\]
-
-We wish to compute the character of the space of holomorphic local operators $\Obs_0$ with respect to the above action.
-We first identify a convenient basis for the space of holomorphic local operators.
-Note that the vector space of solutions to the linearized unconstrained equations of motion is parametrized by
-\begin{align*}
-\mu^{z_i} & \in \cO(\C^5)\partial_{z_i},\ \ \ \ \ \mu^{w_j}\in\cO (\C^5)\partial_{w_j}  \\
-\nu & \in \cO (\C^5) \\
-\gamma^{z_i} & \in \cO (\C^5)dz_i, \ \ \ \ \ \gamma^{w_j}\in\cO (\C^5)d_{w_j} \\
-\beta & \in \cO (\C^5)
-\end{align*}
-
-Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_i, n_j) = (m_1, m_2, m_3, n_1,  n_2)\in \Z^5_{\geq 0}$; these are given by
-\begin{align*}
-\mu^{z_i/w_j}_{(m_i, n_j)} &: \mu^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\mu^{z_i/w_j} (0) \\
-\nu_{(m_i, n_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\nu (0) \\
-\gamma^{z_i/w_j}_{(m_i, n_j)} &: \gamma^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\gamma^{z_i/w_j} (0) \\
-\beta_{(m_i, n_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\beta (0) \\
-\end{align*}
-
-With this basis in hand we can readily compute the character. 
-\begin{lem}
-\[\chi (\Obs_0) = \frac{t_1^{-1}y+ t_1t_2^{-1}y+t_2y+q^{-1}y^{-3/2}+qy^{-3/2}-t_1y- t_1^{-1}t_2y^{-1}-t_2^{-1}y^{-1}-qy^{3/2}-q^{-1}y^{3/2}}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\]
-\end{lem}
+\input{index}
 

### 2021-09-16 dimred.tex
merge

@@
+\def\im{{\rm i}}
+
 \section{Dimensional reduction and 10-dimensional supergravity}
@@
 \beqn\label{eqn:IIAaction}
-I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \Pi + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \sigma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \Pi^2 + \cdots
+I_{IIA} = \frac12 {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \Pi + {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \sigma + \frac12 {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \Pi^2 + \cdots
 \eeqn
@@
 Explicitly, to define this theory we introduce a potential for both the $\Pi$ and $\sigma$ fields. 
-First, we introduce a field $\gamma$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi = \div \gamma$.
+First, we introduce a field $\gamma \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi \vee \Omega = \del \gamma$ where $\Omega$ is the Calabi--Yau form on $\CC^4$.
 This condition does not uniquely fix $\gamma$. 
 There is a new linear gauge symmetry determined by $\gamma \to \gamma + \div \beta$ where $\beta$ is a ghost that we must also introduce. 
-Similarly, we introduce a field $\theta$ which satisfies $\sigma = \div \theta$, there is no extra gauge symmetry present in this condition.
+Similarly, we introduce a field $\theta \in \Omega^{0,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ which satisfies $\sigma \vee \Omega = \del \theta$, there is no extra gauge symmetry present in this condition.\footnote{Using the Calabi--Yau form we have normalized the potential fields $\gamma, \beta,\theta$ to be written as differential forms instead of polyvector fields.}
 
@@
 {\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
-u^{-1}{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
-{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
+u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
+{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
 \end{tikzcd}
@@
 
-The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \wedge \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
+The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \vee \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
 Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
 \[
-\int^\Omega_{\CC^4 \times \RR^2} \eta \wedge \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \wedge \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \wedge \beta .
+\int^\Omega_{\CC^4 \times \RR^2} \eta \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \vee \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \beta .
 \]
@@
 \beqn\label{eqn:IIAactionpot}
-\til I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \div \gamma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \div \theta + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \div \gamma \wedge \div \gamma
+\til I_{IIA} = \frac12 \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\eta \wedge \mu) \vee \del \theta + \frac12 \int_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \del \gamma \wedge \del \gamma
 \eeqn
@@
 \[
-\CC^4 \times \CC \times \RR \to \CC^4 \times \RR \times \RR \cong \CC^4 \times \RR^2 .
+\CC^4 \times \CC \times \RR_t \to \CC^4 \times \RR_x \times \RR_t \cong \CC^4 \times \RR^2 .
 \]
@@
 \begin{proof}
-Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.
+Let us denote the holomorphic coordinate we are reducing along by $z_5 = x + \im y$. 
+We first read off the dimensional reduction of each component field of the 11-dimensional theory. 
+Per the above discussion, this is obtained by taking all fields to be independent of $y$ and replacing $\d \zbar_5$ by $\d x$. 
+To not confuse the notations of fields in 10 and 11 dimensions, we use the notation $\alpha_{11d}$ to denote an 11-dimensional field.
+
+The reductions of the 11d fields $\nu_{11d}, \beta_{11d}$ are easy to describe. 
+Recall that 
+\[
+\nu_{11d} \in \PV^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR) .
+\]
+The reduction of this field is a 10d $\nu$ field
+\[
+\nu (z_i,x,t) = \nu_{11d} (z_i, x, y=0, t) |_{\d \zbar_5 = \d x}  .
+\]
+Similarly, the reduction of $\beta_{11d}$ is a 10d $\beta$ field
+\[
+\beta (z_i,x,t) = \beta_{11d} (z_i, x, y=0, t) |_{\d \zbar_5 = \d x}  .
+\]
+
+The reduction of the 11d fields $\mu_{11d}$ and $\gamma_{11d}$ require a bit of massaging. 
+We break the $SU(5)$ symmetry to $SU(4)$ to write
+\[
+\mu_{11d} = \mu^0_{11d} + \theta_{11d} \partial_{z_5} 
+\]
+where
+\begin{align*}
+\mu^0_{11d} & \in \PV^{1,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) \\
+\theta_{11d} & \in \Omega^{0,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) .
+\end{align*}
+The dimensional reduction of $\mu^0_{11d}$ is a 10d $\mu$ field
+\[
+\mu(z_i,x,t) = \mu_{11d}^0 (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
+\]
+The dimensional reduction of $\theta_{11d}$ is a $\theta$ field
+\[
+\theta(z_i,x,t) = \theta_{11d} (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
+\]
+
+Finally, write the 11d field $\gamma_{11d}$ as
+\[
+\gamma_{11d} = \gamma_{11d}^0 + \eta_{11d} \d z_5
+\]
+where
+\begin{align*}
+\gamma^0_{11d} & \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) \\
+\eta_{11d} & \in \PV^{0,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) .
+\end{align*}
+The dimensional reduction of $\gamma^0_{11d}$ is a 10d $\gamma$ field
+\[
+\gamma(z_i,x,t) = \gamma_{11d}^0 (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
+\]
+The dimensional reduction of $\eta_{11d}$ is an $\eta$ field
+\[
+\eta(z_i,x,t) = \eta_{11d} (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
+\]
+
+Next, we read off the dimensional reduction of the 11d action. 
+Let us first focus on the term present in BF theory of the form
+\[
+\int^\Omega_{\CC^5 \times \RR} \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \vee \del \gamma_{11d} .
+\]
+Upon reduction, this becomes 
+\beqn\label{eqn:bfred}
+\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\theta \wedge \mu) \vee  \del \eta 
+\eeqn
+
+Next, consider the cubic term in the 11d action $J = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
+Upon reduction, this becomes 
+\beqn\label{eqn:jred}
+\int_{\CC^4 \times \RR^2} \eta \wedge \del \gamma \wedge \del \gamma .
+\eeqn
+
+%
+%Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$.
 Note that there is an isomorphism \[\int: \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] It is clear that this isomorphism presrves the BV pairings; we need only check that $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
-
-We readily compute:
-\[\int^{*}I = \]
+%
+%We readily compute:
+%\[\int^{*}I = \]
 \end{proof}

### 2021-09-17 dimred.tex
couplings to m2 m5

@@
 
-\begin{prop}
+\begin{prop}\label{prop:dimred}
 The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is equivalent to the dimensional reduction of the 11-dimensional along  

### 2021-09-17 suco.tex
couplings to m2 m5

@@
 \end{prop} 
+ and ${\rm AdS}_4 \times S^7$ in the holomorphic twist will arise as backreactions of M2 and M5 branes. To this end, we begin by discussing how the theory couples to M2 and M5 branes.
 
@@
 
+\parsec[sec:m5coupling]
+
+Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting M5 branes.
+To this effect, we begin by discussing how the 11d theory couples to M5 branes.
+Consider a stack of N M5 branes wrapping $\C^3_z \times \{0\} \subset \C^3_z\times \C^2_w\times \R$.
+It is natural to consider the interaction
+\[
+I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega.
+\]
+ Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$.
+We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
+\surya{Finish}
+
 \subsection{The ${\rm AdS}_4 \times S^7$ background}
@@
 \]
+
+Analogous to before, the ${\rm AdS}_4 \times S^7$ background will arise from backreacting M2 branes. Consider a stack of N M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
+\[
+I_{M2}(\gamma) = N\int_{\C_z} \gamma
+\] 
+which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
+Unlike the case of M5 branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
+
+Once again, this coupling is justified by comparison with the physical theory and by dimensional reduction.
+Indeed, as discussed in section \surya{}, the component of $\gamma$ which participates in the above coupling is a component of the C-field of eleven dimensional supergravity.
+Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the C-field over the worldvolume theory of the brane.
+
+Moreover, reducing on a holomorphic direction transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$.
+As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of IIA is given by
+\[
+I_{D2}(\gamma) = \int_{\R\times\C_z} \gamma
+\] 
+where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA.
+It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.
+
+\surya{restructure below to derive eom from above}
 Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
@@
 \end{proof}
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
-\subsection{The theory on a three-fold}

### 2021-09-17 suco.tex
merge

--- 2021-09-16 suco.tex
@@
 Next, we turn on a nontrivial unit of flux $N \ne 0$. 
-Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N\til F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
+Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
 Nevertheless, we have the following.
@@
 \begin{prop}
-There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N \til F,-]$. 
-Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the $\delta^{(1)} + [N \til F,-]$ cohomology of the fields of 11-dimensional supergravity on $\CC^5 \times \RR \setminus \CC \times \RR$.
+There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F,-]$. 
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F,-]$.
 \end{prop}
@@
 Recall that we are viewing $\til F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
-As such, the operator $[N \til F,-]$ acts on the fields according to two types of maps:
+As such, the operator $[N F,-]$ acts on the fields according to two types of maps:
 \begin{align*}
@@
 
-\section{Dimensional reduction and compactifications} 
-\include{dimred}
-
 \subsection{The theory on a three-fold}

### 2021-09-17 dimred.tex
merge

@@
 Next, we read off the dimensional reduction of the 11d action. 
-Let us first focus on the term present in BF theory of the form
-\[
-\int^\Omega_{\CC^5 \times \RR} \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \vee \del \gamma_{11d} .
-\]
+Let us first focus on the term present in BF theory which is
+$\int^\Omega \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \vee \del \gamma_{11d}$.
 Upon reduction, this becomes 
@@
 
+The sum of the action functionals \eqref{eqn:bfred} and \eqref{eqn:jred} does not precisely agree with the IIA action $\til I_{IIA}$. 
+To relate the two actions we must make the following field redefinition:
+\[
+\til \theta = \frac{1}{1-\nu} \theta, \quad \til \eta = (1- \nu) \eta .
+\]
+Notice that this change of coordinates is compatible with the odd symplectic pairing on the fields. 
+Under this field redefinition the total dimensionally reduced action can be written as
+\begin{multline}
+\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma \\ + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) .
+\end{multline}
+The first line agrees with the first and third terms in \eqref{eqn:IIAactionpot}.
+
+The second line is very close to the second term in \eqref{eqn:IIAactionpot}, but they are still not quite the same. 
+They are, however, cohomologous. 
+Integrating by parts and applying the BV relation, we can write the second line as
+\[
+\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right)\wedge \div (\til\theta \wedge \mu)  = \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\til\eta \wedge \mu) \vee \partial \til \theta + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til \eta \wedge \div \mu \wedge \til \theta .
+\]
+The first term in this equation agrees precisely with the second term in \eqref{eqn:IIAactionpot}. 
+The final term is cohomological trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
 %

### 2021-09-17 dimred.tex
dimred

@@
 
-\subsection{The $SU(4)$ twist of type IIA supergravity}
+\subsection{The $SU(4)$ twist of type IIA supergravity}\label{sec:SU(4)twist}
 
-\parsec[sec:SU(4)twist]
+We recall the description of the $SU(4)$ twist of type IIA supergravity conjectured in \cite{CLsugra}. 
+In principal, there is also a minimal, $SU(5)$ invariant, twist of type IIA supergravity but so far no description, even conjecturally, exists.
+We turn to this in Section \ref{sec:SU(5)twistIIA}.
 
@@
 The complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
+\brian{I have an issue with how this is organized}
 \beqn
@@
 
-\parsec[sec:IIApot]
+\subsection{Reduction to IIA supergravity}
 
-Our goal is to compare the dimensional reduction of our 11-dimensional theory on $\CC^5 \times \RR$
+We now turn back to our 11-dimensional theory. 
+The first goal is to compare the dimensional reduction of our 11-dimensional theory on $\CC^5 \times \RR$
 %where $X$ is a Calabi-Yau 4-fold 
 with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times \CC^4$. 
-Doing so will require some additional modifications to the above conjectural description.
+Doing so will require a slight modification to the description of the $SU(4)$ twist of IIA supergravity recollected in \S \ref{sec:SU(4)twist}.
+
+\parsec[sec:IIApot]
 
@@
 However, as noted in \cite{CLSugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
-Since components of the $C$-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
+Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
 
-Explicitly, to define this theory we introduce a potential for both the $\Pi$ and $\sigma$ fields. 
+The fundamental fields of the $SU(4)$ twist of IIA supergravity were given in \eqref{eqn:IIAfields}. 
+We modify the space of fields by introducing potentials for both the $\Pi$ and $\sigma$ fields. 
 First, we introduce a field $\gamma \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi \vee \Omega = \del \gamma$ where $\Omega$ is the Calabi--Yau form on $\CC^4$.
@@
 \end{proof}
+
+\subsection{The twist of type I supergravity}
+
+We now turn to a different type of redution of the 11-dimensional theory, this time involving type I supergravity. 
+In this section, we briefly recall the description of type I supergravity following \cite{CLtypeI} which was motivated by the unoriented $B$-model. 
+In \cite{SWspinor}, the second two authors verified the conjectural description of the space of fields recalled below using the pure spinor formalism. 
+Unlike type IIA supergravity, there only exists an $SU(5)$ invariant twist of type I supergravity and it is holomorphic in the maximal number of dimensions.
+
+Concretely, the space of fields of the $SU(5)$ twist of type I supergravity is a subspace of minimal Kodaira--Spencer theory on $\CC^5$. 
+The $\ZZ/2$ graded space of field equipped with its linear BRST operator is 
+\beqn\label{eqn:IIApot}
+\begin{tikzcd}
+- & + & - & +  \\ \hline
+{\PV^{1,\bu}}(\CC^5) \arrow[r, "u\div"]    & {u\PV^{0,\bu}}(\CC^5) \\
+{\PV^{3,\bu}} (\CC^5)\arrow[r, "u\div"] & {u\PV^{2,\bu}} (\CC^5)\arrow[r, "u\div"] & {u^2\PV^{1,\bu}}(\CC^5) \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}(\CC^5)
+\end{tikzcd}.
+\eeqn
+
+Let us give a description of the classical action. 
+Introduce notations for the fields of this type I model:
+\beqn\label{eqn:Ifields}
+\mu + u \nu \in \PV^{1, \bu}(\CC^5) \oplus u \PV^{0,\bu} (\CC^5), \quad \sigma \in \PV^{3,\bu}(\CC^5) .
+\eeqn
+We will not need an explicit notation for the remaining descendant fields.
+
+\begin{conj}
+The twist of type I supergravity on $\CC^5$ is the $\Z/2$-graded theory with fields $\mu+u\nu, \sigma$ as above and with classical action
+\beqn\label{eqn:typeIaction}
+I_{{\rm type\, I}} = {\rm Tr}_{\CC^5} \frac{1}{1-\nu} \mu^2 \vee \sigma + \cdots
+\eeqn
+where the $\cdots$ stands for terms involving the higher descendant fields. 
+%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
+\end{conj}
+
+\parsec[s:typeIpot]
+
+Like in the type IIA discussion, there is a slight modification of the type I model above which is most directly related to 11-dimensional supergravity.
+
+This modification involves replacing the field $\sigma$ above by a potential $\til \gamma \in \Omega^{1,\bu}(\CC^5)$ which satisfies $\Omega \vee \sigma = \del \til \gamma$. 
+This condition does not fix $\til \gamma$ uniquely, there is a gauge symmetry of the form $\til \gamma \to \til \gamma + \del \til \beta$.
+
+In detail, this potential theory we are considering has underlying cochain complex of fields
+\begin{equation}
+  \label{eq:Ipot} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + & -\\ \hline
+    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  \\
+         & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} .
+\end{tikzcd}
+\end{equation}
+
+The type I action \eqref{eqn:typeIaction} completely determines the action of this theory with potentials. 
+One simply takes the action and replaces all appearances of $\sigma$ with $\Omega^{-1} \vee \del \til\gamma$. 
+This yields the interaction of the potential theory
+\beqn\label{eqn:Iactionpot}
+\til I_{\text{type I}} = \frac12 \int^\Omega_{\CC^5} \frac{1}{1-\nu} \mu^2 \vee \del \til\gamma .
+\eeqn
+Notice that the terms involving higher descendants vanishes since these fields are set to zero in the potential theory.
+
+\subsection{Slab compactification}
+
+To this end, we consider placing 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
+In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.
+
+The phase space of the theory at $t=0$ or $t=1$ is 
+\begin{equation}
+  \label{eq:lin1} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + \\ \hline
+    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu \\ 
+     \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_\gamma.
+\end{tikzcd}
+\end{equation}
+The wedge an integrate pairing between the top and bottom lines induces an {\em even} symplectic structure on the phase space. 
+Denote this phase space by $\cE_{\del}$ for the moment.
+
+The phase space is equipped with the restriction of the linear BRST operator of the full 11-dimensional theory. 
+There is also a non linear BRST operator, just like in the bulk theory.
+The BV action induces a $L_\infty$ structure on the parity shift $\Pi\cE_{\del}$ whose cohomology is still a trivial central extension of $E(5,10)$.
+
+A boundary condition is given by a Lagrangian subspace of $\cE_{\del}$ with respect to this even symplectic structure. 
+To make sense of the theory on $\CC^5 \times [0,1]$ we must make the choice of two separate boundary conditions 
+\[
+\cM_{t=0} , \cM_{t=1} \subset \cE_{\del} .
+\]
+Moreover, these boundary conditions carry non linear BRST endowing their parity shifts $\Pi \cM_{t=0} , \Pi\cM_{t=1}$ with the structures of $L_\infty$ algebras. 
+These $L_\infty$ structures must be compatible with the one on the phase space.
+In fact, in our context these boundary conditions are abstractly isomorphic. 
+We will explain the explicit boundary conditions momentarily.
+
+In \cite{?} an explicit model has been given for the theory compactified along the slab for theories which are topological in the direction normal to the boundary.
+The fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
+\[
+\cM_{t=0} \overset{\LL}{\underset{\cE_{\del}}{\times}}\cM_{t=1}.
+\]
+
+\parsec[s:boundary]
+At $t=0$, the boundary condition of the 11-dimensional theory is determined by declaring 
+\[
+\cM_{t=0}: \quad \gamma|_{t=0} = \beta|_{t=0} = 0 .
+\]
+To place the theory on $\CC^5 \times [0,1]$ we take the same boundary condition at $t=1$:
+\[
+\cM_{t=1}: \quad \gamma|_{t=1} = \beta|_{t=1} = 0 .
+\]
+
+\begin{prop}
+With these boundary conditions of the classical 11-dimensional theory on $\CC^5 \times [0,1]$, the compactification along 
+\[
+\CC^5 \times [0,1] \to \CC^5
+\]
+is equivalent to the twist of type I supergravity on $\CC^5$. 
+\end{prop}
+\begin{proof}
+Notice that both $\cM_{t=0}$ and $\cM_{t=0}$ are abstractly isomorphic to the complex resolving divergence-free vector fields
+\begin{equation}
+  \label{eq:lin2} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + \\ \hline
+    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  .
+\end{tikzcd}
+\end{equation}
+
+To compute the derived intersection between the two Lagrangians at $t=0$ and $t=1$ we replace the Lagrangian morphism $\cM_{t=0} \hookrightarrow \cE_{\del}$. 
+Consider the cochain complex $\til \cM_{t=0}$ defined by
+\begin{equation}
+  \label{eq:lin3} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + & - \\ \hline
+    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu \\ 
+     \Omega^{0,\bu}(\CC^5)_\beta \ar[dr,dotted,"\id"]\ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_\gamma \ar[dr,dotted,"\id"] \\
+     & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} .
+\end{tikzcd}
+\end{equation}
+Notice that as a graded vector space, this complex is of the form $\cE_{\del} \oplus (\Omega^{0,\bu} \oplus \Pi \Omega^{1,\bu})$. 
+The $L_\infty$ structure on $\Pi \til \cM_{t=0}$ extends the one on $\cE_{\del}$ coming from the bulk BV action. 
+Notice that the obvious embedding $\cM_{t=0} \hookrightarrow \til \cM_{t=0}$ is a quasi-isomorphism.
+
+The projection map $\til \cM_{t=0} \twoheadrightarrow \cE_{\del}$ factors the original Lagrangian inclusion as
+\[
+\cM_{t=0} \hookrightarrow \til \cM_{t=0} \twoheadrightarrow \cE_{\del} .
+\]
+To compute the derived intersection of $\cM_{t=0}$ and $\cM_{t=1}$ we can compute the ordinary intersection of $\til \cM_{t=0}$ and $\cM_{t=1}$.
+
+Let $\mu_{t=1}$ and $\nu_{t=1}$ denote the fields present in the other boundary condition $\cM_{t=1}$. 
+The intersection $\til \cM_{t=0} \times_{\cE_{\del}} \cM_{t=1}$ is computed by setting the fields $\beta, \gamma$ to zero and $\mu=\mu_{t=1}$, $\nu = \nu_{t=1}$. 
+Thus, we are left with
+\begin{equation}
+  \label{eq:lin3} 
+  \begin{tikzcd}[row sep = 1 ex]
+    - & + & -\\ \hline
+    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  \\
+         & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} 
+\end{tikzcd}
+\end{equation}
+This is precisely the underlying cochain complex of fields for the type I model with potentials. 
+\end{proof}

### 2021-09-17 dfn.tex
char

@@
 
-\subsubsection{}
+\parsec[s:bf]
 
@@
     -n & -n + 1 & -1 & 0 \\ \hline
-    \Omega^{0,\bu}(X;S) \ar[r, "\del"] & \Omega^{1,\bu}(X;S) & 
-     \PV^{1,\bu}(X; S) \ar[r, "\div"] & \PV^{0,\bu}(X; S).
+    \Omega^{0}(X;S) \ar[r, "\del"] & \Omega^{1}(X;S) & 
+     \PV^{1}(X; S) \ar[r, "\div"] & \PV^{0}(X; S).
 \end{tikzcd}
@@
 We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
-We are using the shorthand notation $\PV^{i}(X;S) = (\PV^{i,\bu}(X)\otimes \Omega^\bu(S), \dbar + \d_{S}))$.
+We are using the shorthand notation
+\begin{align*}
+\Omega^{i}(X;S) & = \Omega^{i , \bu;\bu}(X;S) \\
+ & = \oplus_{j,k} \PV^{i,j}(X) \otimes \Omega^k(S) [-j-k] .
+\end{align*}
+which is equipped with the $\dbar + \d_S$ operator and similarly for $\PV^{i}(X;S)$.
 
@@
 
+\subsection{Local character}
+
+We consider the 11-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
+On this background, the theory is manifestly $SU(5)$ invariant. 
+In this section, we compute the corresponding character of the local operators at the origin.
+
+The local character is only sensitive to the free limit of the theory.
+Furthermore, the linear BRST operator is an $SU(5)$-invariant deformation of the $(\dbar + \d_{\RR})$ operator. 
+Therefore, to compute the character it suffices to compute the $SU(5)$-equivariant character of the $\dbar$ cohomology.
+
+The solutions to the $(\dbar + \d_{\RR})$-equations of motion simply say that all fields are holomorphic along $\CC^5$ and constant along $\RR$. 
+Thus, the solutions can be identified with 
+\begin{align*}
+\mu^{i}\partial_{z_i} & \in \Vect(\CC^5) \cong \cO(\C^5)\partial_{z_i},\quad 
+\nu \in \cO (\C^5) \\
+\beta & \in \cO (\C^5), \quad \gamma^{i} \d z_i \in \Omega^{1}(\CC^5) \cong \cO (\C^5)\d z_i 
+\end{align*}
+where $z_i$ is a holomorphic coordinate on $\CC^5$.
+
+Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_j) = (m_1, m_2, m_3, m_4, m_5)\in \Z^5_{\geq 0}$; these are given by
+\begin{align*}
+ \mu^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
+\nu_{(m_i)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
+\gamma^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
+ \beta_{(m_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\beta (0) \\
+\end{align*}
+
+We choose generators of the Cartan subgroup for the $SU(5)$ action with the following weights:
+
+\[\begin{array}{|c|c|c|c|c|c|}
+& z_1 & z_2 & z_3 & z_4 & z_5 \\
+\hline
+q & & & & 1 & -1 \\
+t_1 & 1 & -1 & & & \\
+t_2 & & 1 & -1 & & \\
+y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
+\end{array}\]
+We are choosing the weights in this way as a matter of convenience for the later sections. 
+For instance, upon performing the further twist of the 11-dimensional theory, the $SU(5)$ symmetry is broken to an $SU(3)\times SU(2)$ symmetry; the Cartan of the unbroken symmetries corresponds to the fugacities $q, t_1, t_2$ in the above table.
+
+We can now readily compute the characters.
+\begin{prop}
+The $SU(5)$ local character of the holomorphic twist of the 11-dimensional theory on flat space is
+\begin{multline}
+\chi_{SU(5)} = 
+\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
+\\ 
+\times \frac{t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2}}{t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2}}.
+\end{multline}
+\end{prop}
+
 \subsection{Component fields}

### 2021-09-21 dimred.tex
cy3

@@
 \end{proof}
+
+\subsection{Compactification along a CY3}
+
+In the first section we saw that the 11-dimensional theory can be defined on any manifold that is a product of a Calabi--Yau five-fold with a smooth oriented one-manifold. 
+In this section, we investigate an important compactification of the 11-dimensional theory which involves the Calabi--Yau manifold $X \times \CC^2$ where $X$ is a simply connected compact Calabi--Yau three-fold.
+
+The compactification of the theory along the three-fold $X$ 
+\[
+X \times \CC^2 \times \RR \to \CC^2 \times \RR
+\]
+yields an effective five-dimensional theory which is holomorphic along $\CC^2$ and topological along $\RR$. 
+Upon compactification, we will find a match with a description of the twist of five-dimensional minimally supersymmetric supergravity.
+
+\begin{prop}
+\label{prop:5dsugra}
+The compactification of the 11-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of 5d $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hyper multiplets.
+\end{prop}
+
+\parsec[s:5dsugra]
+
+We give a conjectural capitulation of the twist of 5d $\cN=1$ supergravity. 
+Before twisting, a general 5d $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hyper multiplets. 
+The twist of the vector and hyper multiplet has been computed in \cite{ESW}, and we recall it below. 
+The twist of the gravity multiplet is less clear. 
+A thorough computation of the twist has yet to appear, though some checks have been established by Elliott and the last author in \cite{EWpois}. 
+We give a description of the twist now, but leave a detailed computation from first principles to future work.
+
+The gravity multiplet, see \cite{CCDF} for instance, consists of a graviton $e$, a gravitino $\psi$, and a one-form gauge field $\cA_{grav}$.
+After twisting, the graviton and components of gravitino decompose into two Dolbeault-de Rham valued fields 
+\[
+\alpha, \eta \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) ,
+\]
+whose lowest components both carry odd parity. 
+The one-form gauge field $\cA_{grav}$ and the remaining components of the gravitino decompose into two more Dolbeault-de Rham valued fields
+\[
+A_{grav} , B_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) ,
+\]
+whose lowest components also both carry odd parity.
+
+\begin{conj}
+\label{conj:5dsugra}
+The twist of 5d supergravity with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representations $V$ has BV fields
+\begin{itemize}
+\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate fields $\eta, B_{grav}$,
+\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate field $B$,
+\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate field $\psi$.
+\end{itemize}
+
+The action is
+\begin{multline}
+\label{eqn:5daction} 
+\int^\Omega_{\CC^2 \times \RR} \left(\eta \dbar \alpha + B_{grav} \dbar A_{grav} + B \dbar A + \psi \dbar \chi \right) \\
+  \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
++ \frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
+\end{multline}
+\end{conj}
+
+\brian{general background on susy. Why expect 5d $\cN=1$ susy}
+
+\parsec[-]
+
+With this description of the twist of five-dimensional supergravity, we turn to the proof of Proposition \ref{prop:5dsugra}.
+
+First, we set up some notation. 
+Let $\Omega_X$ be the holomorphic volume form on $X$. 
+To define the $11$-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
+Let $\omega \in \Omega^{1,1}(X)$ be a fixed K\"ahler form on $X$.
+For any $k$, let $H^k(X, \Omega^k_X)_\perp$ denote the cohomology of the primitive elements. 
+\brian{good notation?}
+
+Consider the 11-dimensional field $\nu_{11d}$. 
+Under the equivalence
+\begin{align*}
+\PV^{0,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq H^{\bu}(X, \cO) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & = \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Pi \Bar{\Omega}_X \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)
+\end{align*}
+the $\nu_{11d}$ field decomposes as 
+\[ 
+\nu_{11d} = \nu + \Bar{\Omega}_X \til \nu .
+\]
+Here $\Bar{\Omega}_X$ is the complex conjugate to the holomorphic volume form on $X$. 
+Notice that the zero form component of $\til \nu$ is a field with even parity.
+
+Next, consider the 11-dimensional field $\mu_{11d}$. 
+Under the equivalence 
+\begin{align*}
+\Pi \PV^{1,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq \Pi H^{\bu}(X, \cO) \otimes \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus \Pi H^\bu(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR) \\ & = \Pi \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Bar{\Omega}_X \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus H^{1}(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR) \oplus \Pi H^{2}(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR)
+\end{align*}
+the field $\mu_{11d}$ decomposes as 
+\begin{align*}
+\mu_{11d} & = \mu + \Bar{\Omega}_X \til \mu \\ 
+& + e^i \chi_i + f^a A_a +  (\Omega_X^{-1} \vee \omega^2)A_{grav} .  
+\end{align*} 
+Here, $\{e^i\}_{i=1,\ldots, h^{2,1}}$ is a basis for $H^{1}(X, \T_X)$ and $\{f^a\}_{a=1,\ldots, h^{1,1}-1}$ is a basis for 
+\[
+H^2 (X, \Omega^2_X)_\perp \subset H^2(X, \Omega^2_X) \cong H^2(X, \T_X) . 
+\]
+Notice that the zero form part of $\til{\mu}$ is an even field, the zero form part of $\chi_i$ is an even field, the zero form part of $A_a$ is an odd field, and the zero form part of $\mu_\omega$ is an odd field.
+
+The decomposition for the 11d fields $\gamma_{11d}$ and $\beta_{11d}$ is similar. 
+We record it here:
+\begin{align*}
+\beta_{11d} & = \beta + \Bar{\Omega}_X \til \beta \\ 
+\gamma_{11d} & = \gamma + \Bar{\Omega}_X \til \gamma + e_i \psi^i + f_a B^a + \omega \wedge B_{grav}  . 
+\end{align*}
+Here, $\{e_i\}_{i=1,\ldots,h^{2,1}}$ is a basis for $H^2 (X, \Omega^1_X)$ dual to the basis $\{e^i\}$ under the Serre pairing.
+Also, $\{f_a\}_{a=1,\ldots,h^{1,1}-1}$ is a basis for $H^{1}(X, \Omega^1_X)_\perp$ dual to the basis $\{f^a\}$.
+
+To compare most directly to the description of the twist of 5d $\cN=1$ supergravity we modestly modify the fields. 
+Let $\del$ be the holomorphic de Rham differential along $\CC^2$. 
+First, we introduce a potential for the fields $\mu$ and $\til \mu$. 
+Let 
+\[
+\alpha, \chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)
+\]
+be differential forms satisfying $\del \alpha = \mu \vee \Omega_{\CC^2}$ and $\del \chi = \til \mu \vee \Omega_{\CC^2}$. 
+The fields $\nu, \til \nu$ are set to zero. 
+Dually, we replace the fields $\gamma, \til \gamma$ their `field strengths', suitably renormalized with respect to the volume form
+\[
+\eta = (\d^2 z)^{-1} \vee \del \til \gamma , \quad \psi = (\d^2 z)^{-1} \vee \del \gamma \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) .
+\]
+The roles of $\beta, \til \beta$ were as gauge symmetries implementing $\gamma \to \gamma + \del \beta$ and $\til \gamma \to \til \gamma + \del \til \beta$. 
+Since we are replacing $\gamma, \til \gamma$ by their images under the operator $\del$, these gauge symmetries are set to zero.
+
+In summary, we are left with the following fields 
+\[
+\begin{array}{cccccccccc}
+\alpha,A_{grav} & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & \eta, B_{grav} & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\
+\chi, \chi_i & \in & \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR),  & \psi, \psi^i & \in & \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & i=1,\ldots, h^{2,1}  \\
+A_a & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & B^a & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) , & a = 1, \ldots, h^{1,1}-1.
+\end{array}
+\]
+
+Let us plug these fields in to the 11-dimensional action.
+First, consider the BF term $\frac12 \int^{\Omega} \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \gamma_{11d}$. 
+With the field redefinitions above, this decomposes as
+\begin{multline}\label{eqn:5dsugra1}
+ \int_{\CC^2 \times \RR}^\Omega \left( \frac12 \del \alpha \wedge \del \alpha \wedge \eta + \del A_{grav} \wedge \del A_{grav} \wedge B_{grav} \right) \\
+ + \int_{\CC^2 \times \RR}^\Omega \left( \del \alpha \wedge \del \chi \wedge \psi + \del \alpha \wedge \del \chi_i \wedge \psi^i + \del \alpha \wedge \del A_a \wedge B^a \right) .
+\end{multline}
+This term agrees with the second line in the 5d action \eqref{eqn:5daction}.
+
+Finally, consider the term in the 11-dimensional action $J(\gamma_{11d}) = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
+This induces the five-dimensional Chern--Simons term 
+\beqn\label{eqn:5dsugra2}
+\frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
+\eeqn
+This completes the proof.
+
+\subsection{The $SU(5)$ twist of type IIA supergravity}

### 2021-09-22 dimred.tex
merge

@@
 \begin{align*}
-\Pi \PV^{1,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq \Pi H^{\bu}(X, \cO) \otimes \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus \Pi H^\bu(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR) \\ & = \Pi \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Bar{\Omega}_X \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus H^{1}(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR) \oplus \Pi H^{2}(X, \T_X) \otimes \PV^{0,\bu}(X) \otimes \Omega^\bu(\RR)
+\Pi \PV^{1,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq \Pi H^{\bu}(X, \cO) \otimes \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus \Pi H^\bu(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & = \Pi \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Bar{\Omega}_X \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus H^{1}(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Pi H^{2}(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)
 \end{align*}
@@
 
+\parsec[s:5dglobal]
+
+In \S \ref{sec:global} we computed the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ and found a close relationship to the exceptional super Lie algebra $E(5,10)$. 
+In this section we deduce the form of the global symmetry algebra of the five-dimensional compactified theory on $\CC^2 \times \RR$.
+
+Denote the full de Rham cohomology of $X$ by
+\[
+\cA(X) = H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
+\]
+This is a graded commutative algebra using the wedge product of differential forms. 
+Next, consider the space of holomorphic functions $\cO(\CC^2)$ on $\CC^2$. 
+The Poisson bracket $\{-,-,\}$ associated to the standard holomorphic symplectic structure on $\CC^2$ endows $\cO(\CC^2)$ with the structure of a Lie algebra. 
+In particular, we can tensor $\cO(\CC^2)$ with $\cA_X$ to obtain the structure of a graded Lie algebra on $\cA(X) \otimes \cO(\CC^2)$.
+
+The global symmetry algebra of the compactified theory is a deformation of this graded Lie algebra. 
+Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$. 
+The deformation of $\cA(X) \otimes \cO(\CC^2)$ introduces the following Lie bracket 
+\[
+\big[ [\omega] \otimes f, [\omega] \otimes g\big] = [\omega^2] \otimes \{f,g\} \in H^{2,2}(X, \Omega^2) \otimes \cO(\CC^2) . 
+\]
+
+First, let's compute the global symmetry algebra of the twist of the pure gravity theory on $\CC^2 \times \RR$. 
+This arises from terms in the BV action \eqref{eqn:5daction} involving only $\alpha, \eta, A_{grav}$, and $B_{grav}$.
+
+The underlying graded vector space of the resulting Lie algebra is equivalent to
+\[
+\cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} .
+\]
+The non trivial Lie brackets are
+%\begin{multline}
+%[\alpha, \alpha'] = \{\alpha, \alpha'\} \in \cO(\CC^2)_\alpha , \quad [\alpha, \eta] = \{\alpha, \eta\} \in \cO(\CC^2)_\eta , \quad [\alpha, A_{grav}] = \{\alpha, A_{grav}\} \in \cO(\CC^2)_{A_{grav}} \\
+%[\alpha, B_{grav}] = \{\alpha, B_{grav}\} \in \cO(\CC^2)_{B_{grav}} , \quad [B_{grav}, B'_{grav}] = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
+%\end{multline}
+\begin{align*}
+[\alpha, \alpha' + \eta + A_{grav} + B_{grav}] & = \{\alpha,  \alpha'\} + \{\alpha, \eta\} + \{\alpha, A_{grav}\} + \{\alpha, B_{grav}\} \\ & \in \cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} \\
+[B_{grav}, B'_{grav}] & = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
+\end{align*}
+Denote this Lie algebra by $\fg_{grav}$.
+
+The contribution of the vector and hypermultiplets form a module for $\fg_{grav}$. 
+As a graded vector space, this module is
+\[
+M_X = \cO(\CC^2) \otimes H^{1}(X, \Omega^1_X)_\perp [-1] \oplus \cO(\CC^2) \otimes 
+\]
+
 \subsection{The $SU(5)$ twist of type IIA supergravity}

### 2021-09-22 dfn.tex
iia

@@
 
+Let $X$ be a Calabi--Yau five-fold and $S$ be a smooth oriented one-dimensional real manifold. 
+We will break the $\ZZ$-grading present in BF theory discussed in the previous section to a $\ZZ/2$ grading. 
+For reference, this means that linear BRST complex of fields of the model now take the following form.
+
+\begin{equation}
+  \label{eq:sympfields} 
+  \begin{tikzcd}[row sep = 1 ex]
+    {\rm odd} & {\rm even} & {\rm odd} & {\rm even} \\ \hline
+    \Omega^{0}(X;S)_\beta \ar[r, "\del"] & \Omega^{1}(X;S)_\gamma & 
+     \PV^{1}(X; S)_\mu \ar[r, "\div"] & \PV^{0}(X; S)_\nu.
+\end{tikzcd}
+\end{equation}
+
 \parsec
@@
 
-Recall that $X$ is a complex five-dimensional Calabi--Yau manifold and $S$ is a one-dimensional smooth manifold.
-We finally arrive at the definition of the classical field theory on $X \times S$.
-
-We consider a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
+To define our classical field theory on $X \times S$ we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
 Such deformations are governed by the classical master equation: the parameterized family of actions 
@@
 \chi_{SU(5)} = 
-\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
+\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
 \\ 
@@
 \subsection{One-loop quantization}
+
+In \cite{GRWthf} an existence result for one-loop quantizations of mixed topological-holomorphic theories was established. 
+We apply this to the 11-dimensional model at hand.
+
+The 11-dimensional theory is a mixed topological-holomorphic theory.
+On flat space $\CC^5_z \times \RR_t$, this means that the theory is translation invariant and that the following act homotopically trivially:
+\begin{itemize}
+\item the vector fields $\del_{\zbar_1}, \ldots, \del_{\zbar_{5}}$ corresponding to infinitesimal anti-holomorphic translations,
+\item the vector field $\partial_t$ corresponding to infinitesimal translations in the $\RR_t$ direction. 
+\end{itemize}
+
+Recall that the action functional of the 11-dimensional theory is $S_{BF, \infty} + c J$. 
+Since the cubic and higher interactions only involve holomorphic derivatives, we obtain the following directly from the main result of \cite{GRWthf}.
+
+\begin{thm}
+There exists a gauge fixing condition for the 11-dimensional theory on $\CC^5 \times \RR$ which renders its one-loop quantization finite and anomaly-free. 
+\end{thm}
+
+When $c=0$, this result is actually exact
+since there are no Feynman diagrams present past one-loop in this case. 
+When $c \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge invariant perturbative quantization to higher orders in $\hbar$. 
+The presence of the functional $J = \frac16 \int \gamma \del \gamma \del \gamma$ allows one to construct Feynman graphs at arbitrary loop order.
+
+Upon performing the $\Omega$-background, see \S \ref{s:omega}, the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
+Costello has shown via a cohomological argument that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory \cite{CostelloM5}. 
+We will return to the existence and uniqueness of a higher order quantization of the 11-dimensional theory in future work.

### 2021-09-22 dimred.tex
iia

@@
 \label{conj:5dsugra}
-The twist of 5d supergravity with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representations $V$ has BV fields
+The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representations $V$ has BV fields
 \begin{itemize}
@@
 \subsection{The $SU(5)$ twist of type IIA supergravity}
+
+\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}
+
+Thus, given that our 11-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction.
+This results in a $SU(5)$ invariant, holomorphic, theory on $\CC^5$.
+
+Let us briefly spell out the fields present in this dimensional reduction. 
+The reduction is obtained by replacing $\Omega^\bu(\RR)$ with its translation invariant subalgebra $\CC[\ep] = \CC[\d t]$. 
+Here, $\ep$ is an odd parameter playing the role of the translation invariant one-form $\d t \in \Omega^1(\RR)$. 
+Equivalently, we are compactifying the theory along 
+\[
+\CC^5 \times S^1 \to \CC^5 .
+\]
+
+The 11-dimensional the field $\mu_{11d}$ is replaced by the field 
+\[
+\mu + \ep \mu' \in \Pi \PV^{1,\bu}(\CC^5) [\ep] .
+\]
+Notice that the lowest component of $\mu$ is odd (just like $\mu_{11d})$, but the lowest component of $\mu'$ is now even. 
+Completely similarly, the remaining fields reduce as $\nu + \ep \nu'$, $\gamma + \ep \gamma'$, and $\beta + \ep \beta'$.
+
+In summary, the linear complex of fields of the dimensionally reduced theory on $\CC^5$ is
+\begin{equation}
+  \label{eqn:IIAsu5} 
+  \begin{tikzcd}[row sep = 1 ex]
+    {\rm odd} & {\rm even} & {\rm even} & {\rm odd} \\ \hline
+    \PV^{1,\bu}(\CC^5)_{\mu} \ar[r, "\del"] & \PV^{0,\bu}(\CC^5)_\nu & \\ 
+     & \ep\Omega^{0,\bu}(\CC^5)_{\beta'} \ar[r, "\div"] & \ep\Omega^{1,\bu}(\CC^5)_{\gamma'} . \\
+     &  \ep \PV^{1,\bu}(\CC^5)_{\mu'} \ar[r, "\div"] & \ep \PV^{0,\bu}(\CC^5)_{\nu'} \\
+     & & \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\div"] & \Omega^{1,\bu}(\CC^5)_\gamma.
+\end{tikzcd}
+\end{equation}
+
+We can compute the dimensional reduction of the 11-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
+We arrive at the action functional described below.
+
+\begin{conj}
+\label{conj:IIAsu5}
+The $SU(5)$ twist of type IIA supergravity on $\CC^5$ is equivalent to the theory whose linear BRST complex of fields is displayed in \eqref{eqn:IIAsu5}. 
+The full action functional is 
+\begin{multline}
+\label{eqn:su5action}
+\int^\Omega_{\CC^5}\bigg(\beta' \wedge \dbar \nu + \beta \wedge \dbar \nu' + \gamma' \wedge \dbar \mu + \gamma \wedge \dbar \mu' +  \beta' \wedge \div \mu + \beta \wedge \div \mu' \bigg) \\
++ \int^\Omega_{\CC^5} \bigg( \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma' +  \frac{1}{1-\nu} (\mu \wedge \mu') \vee \del \gamma' + \frac12 \frac{\nu'}{(1-\nu)^2} \mu^2 \vee \del \gamma \bigg) \\
++ \frac12 \int_{\CC^5} \gamma' \wedge \del \gamma \wedge \del \gamma .
+\end{multline} 
+\end{conj}
+
+The first two lines in \eqref{eqn:su5action} arise from the reduction of the BF action $S_{BF,\infty}$. 
+The final line arises from the reduction of $J = \frac16 \int \gamma_{11d} \del \gamma_{11d} \del \gamma_{11d}$.
+
+\parsec[]
+
+The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the 11-dimensional theory. 
+We offer another point of view of this $S^1 / \ZZ/2$ reduction.
+
+First off, there is the following $\ZZ/2$ action on the 11-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
+We obtain it by the following tensor product of $\ZZ/2$ actions. 
+First, $\ZZ/2$ acts on $\Omega^\bu(S^1)$ by orientation reversing diffeomorphisms. 
+Second, we declare that the eigenvalue of the $\ZZ/2$ action on $\PV^{k,\bu}(\CC^5)$, for $k=0,1$ is $+1$ and the eigenvalue of the $\ZZ/2$ action on $\Omega^{k,\bu}(\CC^5)$ for $k=0,1$ is $-1$. 
+This determines a $\ZZ/2$ action on the full space of fields of the 11-dimensional theory.
+
+Upon $S^1$ compactification the $\ZZ/2$ action is easy to describe: $\mu,\nu$ both have eigenvalue $+1$, $\mu',\nu'$ both have eigenvalue $-1$, $\gamma,\beta$ both have eigenvalue $-1$, and $\gamma',\beta'$ both have eigenvalue $+1$.
+In particular, we see that the $\ZZ/2$ fixed points simply pick out the $\mu, \nu, \gamma', \beta'$ fields; this comprises the first two lines of \eqref{eqn:IIAsu5}.
+
+The fields match precisely with the fields in the twist of type I supergravity that we recalled in \S \ref{s:typeIpot} (Under the relabeling $\gamma' \leftrightarrow \til \gamma, \beta' \leftrightarrow \til \beta$).
+Furthermore, restricting the action in the above conjecture agrees precisely with the action of this twisted type I model.

### 2021-09-22 suco.tex
couplings

@@
 \end{prop}
- and ${\rm AdS}_4 \times S^7$ in the holomorphic twist will arise as backreactions of M2 and M5 branes. To this end, we begin by discussing how the theory couples to M2 and M5 branes.
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
-In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 
+\subsection{The ${\rm AdS}_7 \times S^4$ background}
+
+In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
+In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
+
 \parsec[sec:m5coupling]
@@
 Consider a stack of N M5 branes wrapping $\C^3_z \times \{0\} \subset \C^3_z\times \C^2_w\times \R$.
-It is natural to consider the interaction
+It is natural to consider the nonlocal interaction
 \[
@@
 \]
- Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$.
-We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
-\surya{Finish}
+Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
+
+Indeed, $\mu^{1,3}$ is a component of the hodge star of the G-flux in the physical theory \surya{}.
+In the physical theory, M5 branes magnetically couple to the C-field; the coupling involves choosing a primitive for the hodge star of the G-flux and integrating it over the M5 worldvolume.
+Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.
+
+Moreover, reducing on a circle aong the directions the M5 branes wrap yields the $SU(4)$ invariant twist of IIA on $\R^2\times \C^4$ with N D4 branes wrapping $\R\times \C^2$.
+\cite{CLSugra} argue that a magnetic coupling of D4 branes to the $SU(4)$ twist of IIA is given by
+\[
+\int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
+\]
+
+\surya{finish}
 
@@
 
-Analogous to before, the ${\rm AdS}_4 \times S^7$ background will arise from backreacting M2 branes. Consider a stack of N M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
+Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of N M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
 \[
@@
 Indeed, as discussed in section \surya{}, the component of $\gamma$ which participates in the above coupling is a component of the C-field of eleven dimensional supergravity.
-Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the C-field over the worldvolume theory of the brane.
+Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the C-field over the worldvolume of the brane.
 
-Moreover, reducing on a holomorphic direction transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$.
+Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$.
 As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of IIA is given by
@@
 
-\surya{restructure below to derive eom from above}
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
+% Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
 
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Omega^{\bu} \left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
+% The differential form which sources the brane is an element
+% \[
+% \til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Omega^{\bu} \left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
+% \]
+% Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
+% \[
+% \dbar \til{F} = N \delta_{w=0} 
+% \]
+% where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
 
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,3}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
+% Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
+% Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
+% \[
+% F \in \Bar{\PV}^{1,3}(\CC^5) \otimes \Omega^0 (\RR) .
+% \]
+% For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
+
+\parsec[sec:m2backreact]
+
+The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$.
 

### 2021-09-23 ads7.tex
merge

--- 2021-09-17 suco.tex
@@
-\section{Twisted supergavity on AdS space}
+\documentclass[11pt]{amsart}
 
-\brian{need to motivate osp}
+\usepackage{macros-mtheory,amsaddr}
 
-\subsection{Superconformal algebras}
+\addbibresource{cfs.bib}
 
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
+%\linespread{1.2} %for editing
+%\usepackage{mathpazo}
+
+\begin{document}
 
@@
 
+\parsec[sec:m5coupling]
+
+Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting $M5$ branes.
+To this effect, we begin by discussing how the 11d theory couples to M5 branes.
+Consider a stack of $N M5$ branes wrapping
+\[
+\{w_1=w_2=t=0\} \subset \C^3_z\times \C^2_w\times \R 
+\]
+
+It is natural to consider the nonlocal interaction 
+\[
+I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega.
+\]
+Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
+
+Indeed, $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory \ref{s:components}. 
+In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the hodge star of the $G$-flux and integrating it over the $M5$ worldvolume.
+Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.
+
 \parsec[]
 
-Choose a splitting 
+We obtain further justification for this coupling through dimensional reduction to type IIA. 
+Reducing on the circle along the directions the $M5$ branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.
+
+In \cite{CLSugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
 \[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
+N \int _{\C^2 \times \RR} \div^{-1} \mu \vee \Omega_{\C^4} + \cdots .
 \]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
+\brian{should we write $\cdots$ here? This is just the first-order piece.}
+
+\parsec[s:m5backreact]
+
+The backreacted geometry will be given by a solution to the equations of motion upon deforming the 11-dimensional action by the interaction $I_{M5}(\mu)$.
+
+To deduce the equations of motion we deform the 11-dimensional action by the term $I_{M_5}(\mu)$.
+Varying the potential $\div^{-1} \mu$, we obtain the following equation of motion involving the field $\gamma$:
+\[
+\dbar \del \gamma + \div \left(\frac{1}{1-\nu} \mu\right) \wedge \del \gamma = N \delta_{w_1=w_2=t=0} .
+\]
+Notice that there is an extra derivative compared to the equation of motion arising from varying the field $\mu$. 
+This equation only depends on $\gamma$ through its field strength $\del \gamma$.
+
+\begin{lem}
+Let
+\[
+F = \# N \frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
+\]
+%and suppose 
+%\[
+%\til F \in \Bar{\Omega}^{1,2} (\CC^5) \otimes \Bar{\Omega}^1(\RR)
+%\]
+%satisfies $\del \til F = F$. 
+Then, $F$ satisfies the $F = \del\gamma$-equation of motion in the presence of a stack of $N$ $M5$ branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
+\[
+\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0} 
+\]
+where we set the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
+\end{lem}
+
+\begin{proof}
+The equation 
+\[
+\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0}
+\]
+characterizes the kernel representing $N$ times the residue class for a $4$-sphere in 
+\[
+(\CC^2 \times \RR) \setminus 0 \simeq S^4 \times \RR .
+\] 
+That is
+\[
+\oint_{S^4} F = N 
+\]
+for any $4$-sphere centered at $0 \in \CC^2 \times \RR$.
+\end{proof}
+
+\parsec[]
+
+To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory on ${\rm AdS}_7 \times S^4$ and those in the twisted theory.
+
+We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
+We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$ which corresponds to the twist of the 6d superconformal algebra.
+
+We first focus on the case where the flux $N=0$.
+In this case the embedding can be extended to all of $\CC^5 \times \RR$.
 
@@
 
-The embedding of the bosonic piece can roughly be described as follows. 
+Recall that we have chosen coordinates of the form
+\[
+\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR_t
+\]
+with $z_i, i=1,2,3$ and $w_a, a=1,2$.
+The stack of $M5$ branes wrap $w_1=w_2=t=0$.
+
+The embedding of the bosonic piece of $\lie{osp}(6|1)$ can be described as follows. 
 The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
@@
 The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
+In more detail, the embedding of the bosonic piece can be given by the following explicit formulas.
 
@@
 
-\subsection{The ${\rm AdS}_4 \times S^7$ background}
-
-In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
-In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
-
-\parsec[]
-
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
-\[
-\CC_z \times \RR \times \CC^4_w .
-\]
-Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
-
-The differential form which sources the brane is an element
-\[
-\til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Omega^{\bu} \left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-\]
-Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-\[
-\dbar \til{F} = N \delta_{w=0} 
-\]
-where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-\[
-F \in \Bar{\PV}^{1,3}(\CC^5) \otimes \Omega^0 (\RR) .
-\]
-For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
-\begin{lem}
-The field 
-\[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
-\]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
-\end{lem}
-
-\begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
-\end{proof}
-
-\parsec[]
-
-To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory and those in the twisted theory.
-
-We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w=0\}$ which corresponds to the twist of the 3d superconformal algebra.
-We first focus on the case where the flux $N=0$, in this case the embedding can be extended to all of $\CC^5 \times \RR$.
-
-\parsec[]
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the $M2$ brane as compared to the $M5$ brane. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
-The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
-
-\begin{itemize}
-\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
-\[
-\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
-\[
-\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
-\[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
-\]
-
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
-It is mapped to the fields: 
-\[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
-
 \begin{lem}
@@
 \[
-\lie{osp}(6|1) \hookrightarrow E(5,10) .
+i_{M5} \colon {\lie{osp}(6|1) \hookrightarrow E(5,10) .
 \]
 \end{lem}
-
-The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
-Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
-To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above:
-\begin{itemize}
-\item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
-\[
-\d w_a \wedge \d w_b, \quad a,b=1,2,3,4. 
-\] 
-\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
-\[
-(z \d w_a  \wedge \d w_b + \ep^{abcd} w_c \d z \wedge \d w_d) , \quad a,b=1,2,3,4. 
-\] 
-\end{itemize}
 
@@
 Next, we turn on a nontrivial unit of flux $N \ne 0$. 
-Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
+Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
 Nevertheless, we have the following.
@@
 \begin{prop}
-There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F,-]$. 
+There exists $N$-dependent corrections to the embedding $i_{M5}$ which is compatible with the modified BRST differential $\delta^{(1)} + [N F,-]$. 
 Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F,-]$.
@@
 
+\parsec[s:thfcohomology]
+
+The proof of the above proposition follows from an indirect cohomological argument. 
+Before getting to the proof, we introduce the relevant cohomology theory.
+
+The 
 \begin{proof}
-Let $\cL(\CC^5 \times \RR \setminus \CC \times \RR)$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory. 
-We make the identification $\CC^5 \times \RR \setminus \{w=0\} \cong (\CC_w^4 \setminus 0) \times \CC_z \times \RR$. 
-Recall that we are viewing $\til F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
-As such, the operator $[N F,-]$ acts on the fields according to two types of maps:
-\begin{align*}
-[N \til F ,-] & \colon \PV^{i,\bu}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \PV^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \\
-[N \til F,-] & \colon \Omega^{i,\bu}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \Omega^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR).
-\end{align*}
 
-\brian{get the filtration straight}
+\brian{same as above}
 
@@
 To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
-This first page of this auxiliary spectral sequence is simply given by the cohomology with respect to $\dbar + \d_{\RR}$. 
+This first page of this auxiliary spectral sequence is simply given by the cohomology of the fields supported on 
+\[
+\CC^5 \times \RR \setminus \{w_1=w_2=t=0\} \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0)
+\]
+with respect to $\dbar + \d_{\RR}$.
+
 This cohomology is given by
@@
 
-The cohomology of $\CC$ is concentrated in degree zero and there is a dense embedding
-\[
-\CC[z] \hookrightarrow H^\bu(\CC, \cF) 
-\]
-for $\cF = \cO, \T$, or $\Omega^1$.
-
-For $\cF = \cO, \T$, or $\Omega^1$, the cohomology $H^\bu(\CC^4 \setminus 0, \cF)$ is concentrated in degrees $0$ and $3$. 
-There are the following dense embeddings 
-\begin{align*}
-\CC[w_1,\ldots, w_4] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
-\CC[w_1,\ldots, w_4] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
-\CC[w_1,\ldots, w_4] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) 
-\end{align*}
-and
-\begin{align*}
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) .
-\end{align*}
-
-It follows that (up to completion) the cohomology 
-\[
-H^\bu(\cL(\CC^5 \times \RR \setminus \CC \times \RR) , \dbar)
-\]
-is the direct sum of $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with 
-\begin{equation}
-  \label{eqn:ads4ss2} 
-  \begin{tikzcd}[row sep = 1 ex]
-    - & + \\ \hline
-H^3(\CC^4\setminus 0, \T)[z] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & H^3(\CC^4 \setminus 0, \cO) [z] \\
-H^3(\CC^4\setminus 0, \cO) [z] \partial_z \ar[ur, dotted, "\div"] \\
-H^3(\CC^4\setminus 0, \cO) [z] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"] & H^3(\CC^4\setminus 0, \cO)[z] \d z \\ & H^3(\CC^4\setminus 0, \Omega^1)[z] \{\d w_i\} .
-\end{tikzcd}
-\end{equation}
-The remaining piece of the original BRST operator is drawn in dotted lines. 
-The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N\til F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
-In this description the image of the flux $\til F$ at this page in the spectral sequence corresponds to the following class 
-\[
-[\til F] = (w_1 \cdots w_4)^{-1} \partial_z \in H^3(\CC^4\setminus 0, \cO) [z] \partial_z .
-\]
-
-The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N \til F,-]$. 
-As observed above, this operator maps Dolbeault degree zero elements to Dolbeault degree three elements. 
-For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.
-
-The embedding of $\lie{osp}(6|1)$ we wrote down above lives in the kernel of the original BRST operator $\delta^{(1)}$. 
-To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [\til F] , - \big]$. 
-This is a direct calculation. 
-For instance, recall that an element in the image of the odd summand $(\wedge^2 \CC^2)_{-1}$ (which corresponds to a superconformal transformation) is of the form $z w_a \wedge \d w_b = z(w_a \d w_b - w_b \d w_a)$.
-We have
-\[
-\big[ N [\til F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
-\]
-since the class $(w_1\cdots w_4)^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for any $a = 1,\ldots 4$. 
-\end{proof}
-\subsection{Supersymmetric indices}
-
-\brian{SU(5) and SU(2) character calculations}
-
-\subsection{The theory on a three-fold}
+\end{document}

### 2021-09-23 suco.tex
merge

@@
 \] 
+\brian{should we write $\cdots$ here? This is just the first-order piece.}
 which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
@@
 \[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
+F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \wedge \cdots \Hat{\d \wbar_a} \cdots \wedge \d \wbar_4}{\|w\|^{8}} \partial_z .
 \]
@@
 \]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
+where we set the field $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero (as well as the fields $\nu,\beta$). 
 \end{lem}
@@
 \[
-\lie{osp}(6|1) \hookrightarrow E(5,10) .
+i_{M2} \colon \lie{osp}(6|1) \hookrightarrow E(5,10) .
 \]

### 2021-09-23 suco.tex
backreaction eqns

--- 2021-09-22 suco.tex
@@
 \[
-\int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
+I_{D4} = \int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
 \]
 
-\surya{finish}
+Upon dimensionally reducing the interaction $I_{M5}$ along a direction wrapped by the M5 brane, the term depending on the $\theta$ field of type IIA vanishes for type reasons.
+The result is exactly $I_{D4}$.
+
+To determine the backreacted geometry, we deform the 11d interaction $S_{BF,\infty} + J$ by $I_{M5}$ and look at the $\gamma$-equation of motion.
+Varying with respect to $\div^{-1}\mu$ and $\gamma$ respectively yield the equations
+\begin{align*}
+N \delta_{\C^3_z} &= \left (\dbar + d + \div (\frac{\mu}{1-\nu} \right)\partial\gamma \\
+0 &= (\dbar + d)\mu + \partial\gamma\partial\gamma
+\end{align*}
+
+\begin{lem}
+Any background $(\mu = 0, \nu = 0, \gamma = F_{{\rm AdS_7}\times S^4}, \beta = 0)$ where $F_{{\rm AdS_7}\times S^4}$ is such that
+\[
+\partial F_{{\rm AdS_7}\times S^4} = \# N \frac{dw_1dw_2}{(w_1^2+w_2^2+t^2)^{5/2}}(td \wbar_1\wbar_2 - \wbar_1dtd\wbar_2 + \wbar_2dtd\wbar_1)
+\]
+satisfies the above equations of motion.
+\end{lem}
+\begin{proof}
+Since $\nu = \mu = 0$, the first equation tells us that $\partial\gamma$ must be the Bochner kernel representing the residue class on $\R\times\C^2 - \{0\}$.
+The second equation is satisfied for type reasons.
+\end{proof}
 
@@
 \[
-I_{D2}(\gamma) = \int_{\R\times\C_z} \gamma
+I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma
 \] 
@@
 The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$.
+Varying the deformed action with respect to $\gamma$ and $\beta$ respectively yield the equations of motion
+
+\begin{align*}
+N \Omega^{-1} \delta_{w=0}  & = \dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma \\
+0 & = \div \mu
+\end{align*}
 
 \begin{lem}
-The field 
+The background $(\mu = F_{\rm{AdS}_4 \times S^7}, \nu = 0, \gamma = 0, \beta = 0 )$ where 
 \[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
+ F_{\rm{AdS}_4 \times S^7} = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
 \]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
+satisfies the above equation of motion.
 \end{lem}
@@
 \begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
+Upon specializing $\gamma = 0$, the last term in the first equation above vanishes.
+The equation $\dbar F_{\rm{AdS}_4 \times S^7} = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$.
+It is clear that $\div F_{\rm{AdS}_4 \times S^7} = 0$ and $[F_{\rm{AdS}_4 \times S^7}, F_{\rm{AdS}_4 \times S^7}] = 0$ by simple type reasons.
 \end{proof}

### 2021-09-24 ads7.tex
ads7

@@
 
-In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
+In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of 11-dimensional supergravity. 
 In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
@@
 \]
-Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
+Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. 
+We argue that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
 
-Indeed, $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory \ref{s:components}. 
+The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory \ref{s:components}. 
 In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the hodge star of the $G$-flux and integrating it over the $M5$ worldvolume.
@@
 
-We obtain further justification for this coupling through dimensional reduction to type IIA. 
+We obtain a deeper justification for this coupling through dimensional reduction to type IIA supergravity. 
 Reducing on the circle along the directions the $M5$ branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.
@@
 \[
-i_{M5} \colon {\lie{osp}(6|1) \hookrightarrow E(5,10) .
+i_{M5} \colon \lie{osp}(6|1) \hookrightarrow E(5,10) .
 \]
@@
 The proof of the above proposition follows from an indirect cohomological argument. 
-Before getting to the proof, we introduce the relevant cohomology theory.
+Before getting to the proof, we introduce the relevant cohomology.
 
-The 
+The 11-dimensional theory is built from fields which live in the following tensor product of complexes 
+\[
+\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR).
+\]
+Precisely, this is where the $\beta,\nu$ fields live. 
+The $\mu,\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.
+
+Another way to think about this complex is to first consider the full de Rham complex $\Omega^\bu(\CC^5 \times \RR)$, which includes both holomorphic and anti-holomorphic forms in the $\CC^5$ direction.
+The dg algebra of all de Rham forms on $\CC^5 \times \RR$ has an ideal generated by the holomorphic one forms $\{\d z_i\}_{i=1,\ldots,5}$.
+There is an isomorphism of dg algebras
+\[
+\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR) \cong \Omega^\bu(\CC^5 \times \RR) \, / \, (\d z_1,\ldots, \d z_5) .
+\]
+The advantage of this presentation is that we can define a complex associated to more general manifolds that are not products of a complex manifold with a smooth manifold.\footnote{More generally, we are describing the cohomology of a manifold equipped with a topological holomorphic foliation.}
+
+For the M5 brane it was convenient to relabel the holomorphic coordinates on $\CC^5$ by $z_1,z_2,z_3,w_1,w_2$. 
+At the twisted level, the geometry arising from backreacting $M5$ branes is based on the manifold 
+\[
+\CC^5 \times \RR \setminus \CC^3 \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0) .
+\]
+The $\beta,\nu$ fields of 11-dimensional theory on this submanifold of $\CC^5 \times \RR$ live in the complex 
+\[
+\Omega^\bu\bigg(\CC^5 \times \RR \setminus \CC^3\bigg) \, / \, (\d z_1,\d z_2,\d z_3, \d w_1, \d w_2)  .
+\]
+The $\mu,\gamma$ fields live in similar complexes.
+
+Since the $\CC^3$ wraps $w_1=w_2=t=0$ we can apply a version of the K\"unneth formula to identify this complex with 
+\[
+\Omega^{0,\bu}(\CC^3_z) \otimes \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
+\]
+
+The Dolbeault complex of $\CC^3_z$ is easy to compute. 
+The cohomology of the bit in parentheses is concentrated in degrees zero and two. 
+In degree zero there is an isomorphism
+\[
+H^\bu \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg) \, \cong \, \cO(\CC^2_w) . 
+\]
+
 \begin{proof}
@@
 where $\T$ denotes the holomorphic tangent sheaf, $\Omega^1$ denotes the sheaf of holomorphic one-forms, and $\cO$ is the sheaf of holomorphic functions.
+\end{proof}
 

### 2021-09-24 suco.tex
merge

--- 2021-09-23 suco.tex
@@
 \end{prop}
-
- \parsec[]
-
-Choose a splitting 
-\[
-\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR
-\]
-and denote coordinates $z_i, i=1,2,3$ and $w_a, a=1,2$.
-
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
-The embedding of the bosonic piece can roughly be described as follows. 
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
-
-\begin{itemize}
-
-\item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
-\[
-\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
-\]
-
-\item
-The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
-rotations
-\[
-A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
-
-\item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
-\item 
-The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
-\[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\] 
-Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
-\item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
-\[
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
-\]
-\end{itemize}
-
-The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
-Then the odd part decomposes as
-\[
-L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
-\]
-
-\begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
-It is mapped to the fields 
-\[
-z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
-\] 
-\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
-It is mapped to the fields
-\[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
-\]
-\end{itemize}
-
-\subsection{The ${\rm AdS}_7 \times S^4$ background}
-
-In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
-In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
-
-\parsec[sec:m5coupling]
-
-Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting M5 branes.
-To this effect, we begin by discussing how the 11d theory couples to M5 branes.
-Consider a stack of N M5 branes wrapping $\C^3_z \times \{0\} \subset \C^3_z\times \C^2_w\times \R$.
-It is natural to consider the nonlocal interaction
-\[
-I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega.
-\]
-Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. We claim that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
-
-Indeed, $\mu^{1,3}$ is a component of the hodge star of the G-flux in the physical theory \surya{}.
-In the physical theory, M5 branes magnetically couple to the C-field; the coupling involves choosing a primitive for the hodge star of the G-flux and integrating it over the M5 worldvolume.
-Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.
-
-Moreover, reducing on a circle aong the directions the M5 branes wrap yields the $SU(4)$ invariant twist of IIA on $\R^2\times \C^4$ with N D4 branes wrapping $\R\times \C^2$.
-\cite{CLSugra} argue that a magnetic coupling of D4 branes to the $SU(4)$ twist of IIA is given by
-\[
-\int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
-\]
-
-\surya{finish}
 
@@
 
-Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of N M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
+Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of $N$ $M2$ branes wrapping $\R\times \C_z$. A natural interaction to consider is 
 \[
@@
 which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
-Unlike the case of M5 branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
+Unlike the case of $M5$ branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
 
-Once again, this coupling is justified by comparison with the physical theory and by dimensional reduction.
-Indeed, as discussed in section \surya{}, the component of $\gamma$ which participates in the above coupling is a component of the C-field of eleven dimensional supergravity.
-Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the C-field over the worldvolume of the brane.
+This coupling is justified by comparison with the physical theory and by dimensional reduction. 
+Indeed, as discussed in section \surya{}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
+Thus, the proposal mirrors electric couplings of $M2$ branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.
 
-Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$.
-As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of IIA is given by
+Moreover, reducing on a circle transverse to the $M2$ brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$.
+As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by
 \[
-I_{D2}(\gamma) = \int_{\R\times\C_z} \gamma
+I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma
 \] 
-where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA.
+where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA supergravity.
 It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.
@@
 The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$. 
+Varying the deformed action with respect to $\gamma$ 
+we obtain the equation of motion
+\beqn\label{eqn:ads4eom1}
+\dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma = N \Omega^{-1} \delta_{w=0} \\
+\eeqn
+Here $[-,-]$ is the Schouten bracket. 
+Varying $\beta$ we obtain the equation of motion
+\beqn\label{eqn:adseom2}
+\div \mu = 0 .
+\eeqn
 
 \begin{lem}
-The field 
+Let
 \[
-F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \wedge \cdots \Hat{\d \wbar_a} \cdots \wedge \d \wbar_4}{\|w\|^{8}} \partial_z .
+ F_{M2} = \# \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
 \]
-satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
-\[
-\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
-\]
-where we set the field $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero (as well as the fields $\nu,\beta$). 
+Then, the background where $\mu = N F_{M2}$ 
+satisfies the above equations of motion
+\begin{align*}
+\dbar (N F_{M2}) + \frac12 [N F_{M2}, N F_{M2}] & = N \Omega^{-1} \delta_{w=0} \\
+\div (N F_{M2}) & = 0  .
+\end{align*}
+Here, we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
 \end{lem}
@@
 \begin{proof}
-The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
-It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
+Upon specializing $\gamma = 0$, the last term in the first equation above vanishes.
+The equation $\dbar F_{\rm{AdS}_4 \times S^7} = \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$.
+It is clear that $\div F_{\rm{AdS}_4 \times S^7} = 0$ and 
+\[
+[F_{\rm{AdS}_4 \times S^7}, F_{\rm{AdS}_4 \times S^7}] = 0
+\] 
+by simple type reasons. 
 \end{proof}
@@
 Next, we turn on a nontrivial unit of flux $N \ne 0$. 
-Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
+Since not all of the fields we wrote down above commute with the flux $N F_{M2}$, they are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
 Nevertheless, we have the following.
@@
 \begin{prop}
-There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F,-]$. 
-Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F,-]$.
+\label{prop:brads4}
+There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N F_{M2},-]$.
 \end{prop}
@@
 \begin{proof}
-Let $\cL(\CC^5 \times \RR \setminus \CC \times \RR)$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory. 
-We make the identification $\CC^5 \times \RR \setminus \{w=0\} \cong (\CC_w^4 \setminus 0) \times \CC_z \times \RR$. 
-Recall that we are viewing $\til F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
-As such, the operator $[N F,-]$ acts on the fields according to two types of maps:
+Let $\cL(\CC^5 \times \RR \setminus \{w=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory. 
+We make the identification 
+\[
+(\CC^5 \times \RR) \setminus \{w=0\} \cong (\CC_w^4 \setminus 0) \times \CC_z \times \RR .
+\]
+
+Set $F = F_{M2}$ for notational convenience. Recall that we are viewing $F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
+The operator $[F,-]$ acts on the fields according to two types of maps:
 \begin{align*}
-[N \til F ,-] & \colon \PV^{i,\bu}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \PV^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \\
-[N \til F,-] & \colon \Omega^{i,\bu}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \Omega^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR).
+[F ,-] & \colon \PV^{i,\bu}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \PV^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \\
+[F,-] & \colon \Omega^{i,\bu}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \Omega^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR).
 \end{align*}
@@
 \[
-H^\bu(\cL(\CC^5 \times \RR \setminus \CC \times \RR) , \dbar)
+H^\bu(\cL(\CC^5 \times \RR \setminus \{w=0\}) , \dbar)
 \]
@@
     - & + \\ \hline
-H^3(\CC^4\setminus 0, \T)[z] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & H^3(\CC^4 \setminus 0, \cO) [z] \\
-H^3(\CC^4\setminus 0, \cO) [z] \partial_z \ar[ur, dotted, "\div"] \\
-H^3(\CC^4\setminus 0, \cO) [z] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"] & H^3(\CC^4\setminus 0, \cO)[z] \d z \\ & H^3(\CC^4\setminus 0, \Omega^1)[z] \{\d w_i\} .
+H^3(\CC^4\setminus 0, \cO)[z] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & H^3(\CC^4 \setminus 0, \cO) [z] \\
+H^3(\CC^4\setminus 0, \cO) [z] \partial_z \ar[ur, dotted, "\div"'] \\
+H^3(\CC^4\setminus 0, \cO) [z] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"'] & H^3(\CC^4\setminus 0, \cO)[z] \d z \\ & H^3(\CC^4\setminus 0, \Omega^1)[z] \{\d w_i\} .
 \end{tikzcd}
@@
 The remaining piece of the original BRST operator is drawn in dotted lines. 
-The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N\til F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
-In this description the image of the flux $\til F$ at this page in the spectral sequence corresponds to the following class 
+The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
+In this description the image of the flux $F$ at this page in the spectral sequence corresponds to the following class 
 \[
-[\til F] = (w_1 \cdots w_4)^{-1} \partial_z \in H^3(\CC^4\setminus 0, \cO) [z] \partial_z .
+[F] = (w_1 \cdots w_4)^{-1} \partial_z \in H^3(\CC^4\setminus 0, \cO) [z] \partial_z .
 \]
 
-The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N \til F,-]$. 
+The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. 
 As observed above, this operator maps Dolbeault degree zero elements to Dolbeault degree three elements. 
@@
 The embedding of $\lie{osp}(6|1)$ we wrote down above lives in the kernel of the original BRST operator $\delta^{(1)}$. 
-To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [\til F] , - \big]$. 
+To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [F] , - \big]$. 
 This is a direct calculation. 
@@
 \[
-\big[ N [\til F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
+\big[[F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
 \]
@@
 \end{proof}
+
+\subsection{The ${\rm AdS}_7 \times S^4$ background}
+
+In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of 11-dimensional supergravity. 
+In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
+
+\parsec[sec:m5coupling]
+
+Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting $M5$ branes.
+To this effect, we begin by discussing how the 11d theory couples to M5 branes.
+Consider a stack of $N M5$ branes wrapping 
+\[
+\{w_1=w_2=t=0\} \subset \C^3_z\times \C^2_w\times \R 
+\]
+
+It is natural to consider the nonlocal interaction 
+\[
+I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega.
+\]
+Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. 
+We argue that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
+
+The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory \ref{s:components}. 
+In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the hodge star of the $G$-flux and integrating it over the $M5$ worldvolume.
+Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.
+
+\parsec[]
+
+We obtain a deeper justification for this coupling through dimensional reduction to type IIA supergravity. 
+Reducing on the circle along the directions the $M5$ branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.
+
+In \cite{CLSugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
+\[
+N \int _{\C^2 \times \RR} \div^{-1} \mu \vee \Omega_{\C^4} + \cdots .
+\]
+\brian{should we write $\cdots$ here? This is just the first-order piece.}
+
+\parsec[s:m5backreact]
+
+The backreacted geometry will be given by a solution to the equations of motion upon deforming the 11-dimensional action by the interaction $I_{M5}(\mu)$.
+
+To deduce the equations of motion we deform the 11-dimensional action by the term $I_{M_5}(\mu)$.
+Varying the potential $\div^{-1} \mu$, we obtain the following equation of motion involving the field $\gamma$:
+\beqn\label{eqn:m5eom1}
+\dbar \del \gamma + \div \left(\frac{1}{1-\nu} \mu\right) \wedge \del \gamma = N \delta_{w_1=w_2=t=0} .
+\eeqn
+Notice that there is an extra derivative compared to the equation of motion arising from varying the field $\mu$. 
+This equation only depends on $\gamma$ through its field strength $\del \gamma$.
+
+Varying $\gamma$ we obtain the equation of motion 
+\beqn\label{eqn:m5eom2}
+(\dbar + \d_\RR) \mu + \del \gamma \del \gamma = 0 .
+\eeqn 
+Again, this only depends on $\gamma$ through its field strength $\del \gamma$.
+
+\begin{lem}
+\label{lem:ads7flux}
+Let
+\[
+F_{M5} = \# N \frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
+\]
+%and suppose 
+%\[
+%\til F \in \Bar{\Omega}^{1,2} (\CC^5) \otimes \Bar{\Omega}^1(\RR)
+%\]
+%satisfies $\del \til F = F$. 
+Then, $F$ satisfies the $F = \del\gamma$-equations of motion in the presence of a stack of $N$ $M5$ branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
+\begin{align*}
+\dbar F + \d_{\RR} F & = N \delta_{w_1=w_2=t=0}  \\ 
+F \wedge F & = 0 .
+\end{align*}
+Here, we set all components of the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
+\end{lem}
+
+\begin{proof}
+The first equation equation 
+\[
+\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0}
+\]
+characterizes the kernel representing $N$ times the residue class for a $4$-sphere in 
+\[
+(\CC^2 \times \RR) \setminus 0 \simeq S^4 \times \RR .
+\] 
+That is
+\[
+\oint_{S^4} F = N 
+\]
+for any $4$-sphere centered at $0 \in \CC^2 \times \RR$.
+
+The second equation $F \wedge F = 0$ follows by simple type reasons. 
+\end{proof}
+
+\parsec[]
+
+To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory on ${\rm AdS}_7 \times S^4$ and those in the twisted theory.
+
+We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
+We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$ which corresponds to the twist of the 6d superconformal algebra.
+
+We first focus on the case where the flux $N=0$.
+In this case the embedding can be extended to all of $\CC^5 \times \RR$.
+
+The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+\[
+\lie{sl}(4) \oplus \lie{sl}(2) .
+\]
+which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+
+Recall that we have chosen coordinates of the form
+\[
+\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR_t
+\]
+with $z_i, i=1,2,3$ and $w_a, a=1,2$.
+The stack of $M5$ branes wrap $w_1=w_2=t=0$.
+
+The embedding of the bosonic piece of $\lie{osp}(6|1)$ can be described as follows. 
+The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
+Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
+The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
+In more detail, the embedding of the bosonic piece can be given by the following explicit formulas.
+
+\begin{itemize}
+
+\item
+The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
+\[
+\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
+\]
+
+\item
+The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
+rotations
+\[
+A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
+\]
+
+\item
+The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
+\[
+\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
+\] 
+Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
+\item 
+The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
+\[
+z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+\] 
+Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
+\item 
+The bosonic summand $\lie{sl}(2)$ is mapped to the triple
+\[
+w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+\]
+\end{itemize}
+
+The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
+It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
+Then the odd part decomposes as
+\[
+L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
+\]
+
+\begin{itemize} 
+\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
+It is mapped to the fields 
+\[
+z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
+\] 
+\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
+It is mapped to the fields
+\[
+\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
+\]
+\end{itemize}
+
+\begin{lem}
+These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the 11-dimensional theory on $\CC^5 \times \RR$. 
+Equivalently, it defines an embedding
+\[
+i_{M5} \colon \lie{osp}(6|1) \hookrightarrow E(5,10) .
+\]
+\end{lem}
+
+\parsec[]
+
+Next, we turn on a nontrivial unit of flux $N \ne 0$. 
+Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
+Nevertheless, we have the following.
+
+\begin{prop}
+\label{prop:brads7}
+There exists $N$-dependent corrections to the embedding $i_{M5}$ which is compatible with the modified BRST differential $\delta^{(1)} + [N F,-]$. 
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F,-]$.
+\end{prop}
+
+\parsec[s:thfcohomology]
+
+The proof of the above proposition follows from an indirect cohomological argument. 
+Before getting to the proof, we introduce the relevant cohomology.
+
+The 11-dimensional theory is built from fields which live in the following tensor product of complexes 
+\[
+\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR).
+\]
+Precisely, this is where the $\beta,\nu$ fields live. 
+The $\mu,\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.
+
+Another way to think about this complex is to first consider the full de Rham complex $\Omega^\bu(\CC^5 \times \RR)$, which includes both holomorphic and anti-holomorphic forms in the $\CC^5$ direction.
+The dg algebra of all de Rham forms on $\CC^5 \times \RR$ has an ideal generated by the holomorphic one forms $\{\d z_i\}_{i=1,\ldots,5}$.
+There is an isomorphism of dg algebras
+\[
+\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR) \cong \Omega^\bu(\CC^5 \times \RR) \, / \, (\d z_1,\ldots, \d z_5) .
+\]
+The advantage of this presentation is that we can define a complex associated to more general manifolds that are not products of a complex manifold with a smooth manifold.\footnote{More generally, we are describing the cohomology of a manifold equipped with a topological holomorphic foliation.}
+
+For the M5 brane it was convenient to relabel the holomorphic coordinates on $\CC^5$ by $z_1,z_2,z_3,w_1,w_2$. 
+At the twisted level, the geometry arising from backreacting $M5$ branes is based on the manifold 
+\[
+\CC^5 \times \RR \setminus \CC^3 \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0) .
+\]
+The $\beta,\nu$ fields of 11-dimensional theory on this submanifold of $\CC^5 \times \RR$ live in the complex 
+\[
+\Omega^\bu\bigg(\CC^5 \times \RR \setminus \CC^3\bigg) \, / \, (\d z_1,\d z_2,\d z_3, \d w_1, \d w_2)  .
+\]
+The $\mu,\gamma$ fields live in similar complexes where we introduce a (trivial) vector bundle on $\CC^5 \times \RR \setminus \CC^3$.
+
+Since the $\CC^3$ wraps $w_1=w_2=t=0$ we can apply a version of the K\"unneth formula to identify this complex with 
+\[
+\Omega^{0,\bu}(\CC^3_z) \otimes \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
+\]
+
+The cohomology of the Dolbeault complex of $\CC^3_z$ is easy to compute. 
+The cohomology of the bit in parentheses is concentrated in degrees zero and two. 
+In degree zero, there is a dense embedding
+\[
+\CC[w_1,w_2] \hookrightarrow H^0 \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg)
+\]
+In degree two, there is a dense embedding
+\[
+w_{1}^{-1} w_2^{-1} \CC[w_1,w_2] \hookrightarrow H^2 \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
+\]
+
+It will be useful to explain this last embedding in more detail. 
+Consider the homogenous element $w_1^{-1} w_2^{-1}$. 
+This represents the class of the Dolbeault-de Rham $2$-form
+\[
+\frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} .
+\]
+Notice that if we wedge with the volume form $\d w_1 \d w_2$ this is the unit $N=1$ flux introduced in Lemma \ref{lem:ads7flux}. 
+The homogenous element $w_1^{-n-1} w_2^{-m-1}$ represents the class of the holomorphic derivatives $\partial_{w_1}^n \partial_{w_2}^{m}$ applied to this $2$-form.
+
+Observe that when restricted to $\CC^5 \times \RR \setminus \CC^3$ the holomorphic tangent bundle along $\CC^5$ is still trivializable.
+
+\parsec[]
+
+Let's turn to the proof of Proposition \ref{prop:brads7}.
+We proceed completely analogously to the case of backreacted $M2$ branes as in the proof of Proposition \ref{prop:brads4}.
+
+Let $\cL (\CC^5 \times \RR \setminus \{w_1=w_2=t=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
+
+There is a spectral sequence which converges to the cohomology of the fields with respect to the deformed linear BRST differential $\delta^{(1)} + [N F_{M5},-]$ whose first page
+is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$. 
+Recall that the linearized BRST differential decomposes as
+\[
+\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma}  .
+\]
+To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
+This first page of this auxiliary spectral sequence is simply given by the cohomology of the fields supported on 
+\[
+\CC^5 \times \RR \setminus \{w_1=w_2=t=0\} \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0)
+\]
+with respect to $\dbar + \d_{\RR}$.
+
+To compute this cohomology we follow the discussion in \S \ref{s:thfcohomology}.
+Just as in the case of the $M2$ brane, we see that the $\dbar + \d_{\RR}$ cohomology is (up to completions) is the direct sum of the cohomology on flat space $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with
+\begin{equation}
+  \label{eqn:ads7ss2} 
+  \begin{tikzcd}[row sep = 1 ex]
+    + & - \\ \hline
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "\div"'] \\
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
+\end{tikzcd}
+\end{equation}
+
+Recall that the flux $F$ was defined as the image under $\del$ of some $\gamma$-type field. 
+Therefore, the class $[F]$ does not live inside this page of the spectral sequence, but the operator $[[F], -]$ does act on this page nevertheless. 
+For instance, if $f^i(z,w) \d z_i$ is a one-form living in $H^0(\CC^5, \Omega^1) \otimes H^0(\RR)$, then
+\[
+[ [F] , f^i (z,w) \d z_i ] = \ep_{ijk} w_1^{-1} w_2^{-1} \partial_{z_j} f^i(z,w) \del_{z_k} 
+\]
+which is an element in 
+\[
+\CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\del_{z_i}\} \subset H^0(\CC^3, \T) \otimes H^2 \big(\Omega^\bu(\CC^2 \times \RR \setminus 0) / (\d w_1 , \d w_2) \big) .
+\]
+
+The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to dotted line operators in \eqref{eqn:ads7ss2}.
+
+The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. 
+This operator maps Dolbeault-de Rham degree zero elements to Dolbeault-de Rham degree two elements. 
+For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.
+
+The embedding of $\lie{osp}(6|1)$ for $N=0$ lives in the kernel of the original BRST operator $\delta^{(1)}$. 
+To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [F] , - \big]$. 
+This is a direct calculation. 
+For instance, recall that an element in the image of the odd summand $\wedge^2 L \otimes R = \wedge^2 \CC^3 \otimes \CC^2$ (which corresponds to a superconformal transformation) is of the form $w_a (z_i \d z_j - z_j \d z_i)$, $a=1,2, i,j=1,2,3$.
+We have
+\[
+\big[[F] , w_a (z_i \d z_j - z_j \d z_i)\big] = 2 \ep_{ijk} (w_1^{-1} w_2^{-1}) \cdot w_a \del_{z_k} = 0
+\]
+since the class $w_1^{-1} w_2^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for $a=1,2$.
+Verifying that the remaining elements in the image of $i_{M5}$ are in the kernel of $\big[ [F], -\big]$ is similar.
+This completes the proof.

### 2021-09-28 dimred.tex
update

@@
 {\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
-u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
+u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\del"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
 {\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
@@
 \label{conj:5dsugra}
-The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representations $V$ has BV fields
+The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
 \begin{itemize}

### 2021-09-28 draft.tex
update

@@
 \maketitle
+
+\tableofcontents
+
 \newpage
@@
 
-%count hypers and vectors in 5d N=1 sugra relate to Kevin and my work with Chris
-
 \input{suco}
-
-\section{The non-minimal twist}
-
-We have provided numerous consistency checks that the 11-dimensional theory defined on $\CC^5 \times \RR$ is a twist of supergravity. 
-We have referred to this theory as holomorphic as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.
-
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
-\[
-A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
-\]
-where $\Pi$, as always, denotes parity shift.
-The equations of motion are of the form
-\[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
-\]
-The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
-We give a precise definition below.
-
-More generally, the twist can be defined \brian{finish}
 
@@
 
-\subsection{The non-minimal supercharge}
+\input{nonmin}
 
-Let $Q^{hol}$ denote the fixed holomorphic supercharge. 
-We have argued in \S \ref{s:residual} that the $Q^{hol}$-cohomology of the 11-dimensional supersymmetry algebra is a symmetry of our proposed holomorphic twist of 11-dimensional supergravity.
-
-There is a twist of supergravity which can be witnessed as a further deformation of the $Q^{hol}$-twist. 
-\brian{fix this}
-
-Recall that the odd component of this residual supersymmetry algebra is
-\[
-\wedge^2 L \cong \wedge^2(\CC^5) 
-\]
-which we can identify with constant coefficient holomorphic $(2,0)$ forms on $\CC^5 \times \RR$ (they are zero-forms along the $\RR$-direction). 
-Because these forms are constant coefficient, they are also closed, and hence lift to $(1,0)$ forms on $\CC^5 \times \RR$ in a way that is unique up to $\del$-exact terms.
-
-Using this observation, we constructed an embedding of $\wedge^2(L)$ into the fields of supergravity. 
-Explicitly, the element $z_i \wedge z_j \in \wedge^2 L$ was mapped to the $\gamma$-type field
-\[
-\Psi_{ij} = \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0(\RR) ,
-\]
-where $i,j=1,\ldots, 5$ and $i \ne j$.
-
-\parsec[-]
-
-The first main result of this section is to characterize the twist of our 11-dimensional theory on $\CC^5 \times \RR$ by the element $\Psi_{ij}$.
-
-\brian{introduce PCS}
-Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
-\[
-\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
-\]
-
-\begin{thm}
-The $\Psi_{ij}$-twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
-\[
-\CC_{z_i} \times \CC_{z_j} \times \RR^7 .
-\]
-\end{thm}
-
-Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-The Lie algebra of gauge symmetries of this model on flat space is 
-\[
-\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-\]
-which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$.
-
-\parsec[sec:nmsymmetry]
-Before proceeding to the proof of the theorem above, we perform a very simple calculation of the global symmetry algebra present in the $\Psi_{ij}$-twisted theory.
-
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
-From this point of view, the global symmetry algebra of the $\Psi_{ij}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
-\[
-\partial \Psi_{ij} = \d z_i \wedge \d z_j \in \Omega^{2,hol}_{cl}(\CC^5) .
-\]
-We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.
-
-Notice that there are the following brackets in the super Lie algebra $E(5,10)$ 
-\begin{align*}
-[f_l \partial_{z_l} , \d z_i \wedge \d z_j] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
-[g^{kl} \d z_k \wedge \d z_l , \d z_i \wedge \d z_j ] & = \ep_{ijklm} g^{kl} \partial_{z_m} .
-\end{align*}
-where $f_l \partial_{z_l}$ is a divergence-free vector field on $\CC^5$ and $g^{kl} \d z_k \wedge \d z_l$ is a closed two-form.
-
-From these relations, it is easy to see that any divergence-free vector field of the form:
-\begin{itemize}
-\item $f(z_i, z_j) \partial_{z_i} + g(z_i, z_j) \partial_{z_j}$ for holomorphic functions $f,g$ on $\CC_i \times \CC_j$ or 
-\item $f(z_1,\ldots,z_5) \partial_{z_k}$ for $k \ne i$ or $j$
-\end{itemize}
-are closed for the differential $\d = [\d z_i \wedge \d z_j  , -]$, and that these are the only nonzero closed elements. 
-Any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
-
-Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
-\[
-H^\bu\big(E(5,10), [\partial \Psi_{ij}, -] \big) \cong \Vect^{hol}_0(\CC_i \times \CC_j) .
-\]
-Notice that on $\CC^2$, there is a split exact sequence of Lie algebras
-\[
-0 \to \CC \to \cO^{hol}(\CC^2) \to \Vect_0^{hol} (\CC^2) \to 0
-\]
-where $\cO^{hol}(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form $\d z_i \wedge \d z_j$.
-Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.
-
-\section{The twisted $\Omega$-background}
-
-\subsection{$\Omega$-deformed symmetry algebra}
-
-On flat space, we have
-
-\subsection{M2 branes in the $\Omega$-background}
-
-\parsec[]
-
-In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
-\beqn\label{eqn:m2omega}
-\{0\} \times \RR \subset \CC^2 \times \RR .
-\eeqn
-
-The field which sources this brane is a distributional differential form $F$.
-The linear equation of motion for $F$ is the distributional equation 
-\[
-\d^2 z \wedge \dbar F = N \delta_{z=0} 
-\]
-where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
-In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.
-
-The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
-Explicitly, we can characterize it as follows.
-
-\begin{prop}
-The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
-\[
-F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
-\] 
-satisfies the non-linear equation of motion 
-\[
-\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
-\]
-\end{prop}
-\begin{proof}
-The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
-Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
-\end{proof}
-
-\parsec[]
-
-We can interpret $F$ geometrically in the following way. 
-Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.
-
-On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
-\[
-0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
-\]
-where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
-The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
-$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.
-
-Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$.
-Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
-\[
-\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
-\]
-
-In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
-\[
-(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
-\]
-of the $(0,1)$-form
-\[
-F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
-\] 
-The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
-\[
-\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
-\]
+\end{document}
 

### 2021-09-28 nonmin.tex
update

\section{The non-minimal twist}

We have provided numerous consistency checks that the 11-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
We have referred to this theory as minimal as it depends on the complex structure in the maximal number of directions. 
In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.

On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one as in the holomorphic twist. 
We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
\[
A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
\]
where $\Pi$, as always, denotes parity shift.
The equations of motion are of the form
\[
\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
\]
The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
We give a precise definition below.

The main result of this section is the following.

\begin{thm}
The non-minimal twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
\[
\CC^2 \times \RR^7 .
\]
\end{thm}

%Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.

%The Lie algebra of gauge symmetries of this model on flat space is 
%\[
%\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
%\]
%which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$. 
%
%More generally, the twist can be defined \brian{finish}

\subsection{The non-minimal supercharge}

From the point of view of the untwisted theory, the non-minimal twist is defined by working in a background where the fermionic ghost in the physical theory is equal to a supertranslation of the form
\[
Q + Q_{nm} 
\]
where $Q$ is the supertranslation which defines the minimal twist, see \S \ref{sec:mintwist}.
The minimal twist of supergravity is obtained by setting a fermionic ghost equal to $Q$.

In the language of the minimal twist, the supercharge $Q_{nm}$ determines a square-zero element in the $Q$-cohomology of the original supersymmetry algebra (which we will denote by the same letter). 
The characterization of this cohomology in Proposition \ref{prop:susycoh} implies that $Q_{nm}$ is an element 
\[
Q_{nm} \in \wedge^2 L 
\]
where $L \cong \CC^5$ is the defining $SU(5)$ representation. 
In other words, $Q$ is a translation invariant holomorphic two-form on $\CC^5$. 
The condition that $[Q_{nm}, Q_{nm}] = 0$ simply says that $Q_{nm}\wedge Q_{nm} = 0$ as a translation invariant four-form on $\CC^5$. 
By a linear change of coordinates, all such two-forms $Q$ are of the form $Q_{nm} = \d z_i \wedge \d z_j$ where $i,j=1,\ldots, 5$.

From hereon in this section we will rename coordinates by
\[
\CC^5 \times \RR = \CC^2_{z_i} \times \CC^3_{w_a} \times \RR
\]
which is most natural from the point of view of the non-minimal twist. 
We will fix the non-minimal supercharge 
\[
Q_{nm} = \d z_1 \wedge \d z_2 .
\]
Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(2)$.

We constructed an embedding of the $Q$-cohomology of the supersymmetry algebra into the fields of our 11-dimensional theory on $\CC^5 \times \RR$. 
The further twist is obtained by working in a background where a certain field on $\CC^5 \times \RR$ takes nonzero value $Q_{nm}$. 
Explicitly, the element $Q_{nm} \in \wedge^2 L$ corresponds to the image under $\del$ of a $\gamma$-field of type $\Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR)$. 
According to the embedding in \S \ref{s:residual} this is the $\gamma$-field 
\[
\gamma_{nm} = \frac12 (z_1 \d z_2 - z_2 \d z_1) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) 
\]
Notice that $\del \gamma_{nm} = \d z_1 \wedge \d z_2$ as desired.

\parsec[sec:nmsymmetry]
Before proceeding to the proof of the theorem above, we perform a simple calculation of the global symmetry algebra present in the $Q_{nm}$-twisted theory.

Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
From this point of view, the global symmetry algebra of the $Q_{nm}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\d z_1 \wedge \d z_2 \in \Omega^{2}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

We compute the cohomology of $E(5,10)$ with respect to the differential which is bracketing with this Maurer--Cartan element. 
Recall that we are using the holomorphic coordinates $(z_1,z_2,w_1,w_2,w_3)$ on $\CC^5$.

There are the following brackets in the super Lie algebra $E(5,10)$ 
\begin{align*}
[f_l \partial_{z_l} , \d z_1 \wedge \d z_2] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
[g_a \partial_{w_a} , \d z_1 \wedge \d z_2] & = 0 \\
[h^{ab} \d w_a \wedge \d w_b , \d z_1 \wedge \d z_2 ] & = \ep_{abc} h^{ab} \partial_{w_c} .
\end{align*}
where $f_l \partial_{z_l}$, $g_a \partial_{w_a}$ are divergence-free vector fields on $\CC^5$ and $h^{ab} \d w_a \wedge \d w_b$ is a closed two-form.

From these relations, we see that the following elements are in the kernel of $[\d z_1 \wedge \d z_2, -]$:
\begin{itemize}
\item $f(z_i) \partial_{z_1} + g(z_i) \partial_{z_2}$ for holomorphic functions $f,g$ on $\CC_{z_1} \times \CC_{z_2}$ which satisfy 
\[
\del_{z_1} f + \del_{z_2} g = 0 .
\]
In other words, this is a divergence-free vector field on $\CC_{z_1} \times \CC_{z_2}$. 
\item $f_b(z_i, w_a) \partial_{w_b}$ for $f_b$ a holomorphic function on $\CC^5$ where $b=1,2,3$. 
\end{itemize}
It is immediate to check that these are the only nonzero elements in the kernel. 
Further, any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\d z_1 \wedge \d z_2, -] \big) \simeq \Vect_0(\CC^2) .
\]

We proved in Theorem \ref{thm:global} that the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension $\Hat{E(5,10)}$ of the super Lie algebra~$E(5,10)$.

The Lie algebra of divergence-free vector fields on $\CC^2$ also admits a central extension:
\beqn\label{eqn:centralvect}
0 \to \CC \to \cO (\CC^2) \to \Vect_0 (\CC^2) \to 0
\eeqn
where $\cO(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form~$\d z_1 \wedge \d z_2$.
These two central extension are compatible.

%Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.

\begin{prop}
Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$. 
Then, there is an isomorphism of Lie algebras 
\[
H^\bu \big(\Hat{E(5,10)} , [\d z_1 \wedge \d z_2, -] \big) \simeq \cO(\CC^2) .
\]
\end{prop}
\begin{proof}
The only thing to check is that, in cohomology, the cocycle defining the central extension of $E(5,10)$ is the cocycle exhibiting $\cO(\CC^2)$ as the central extension of divergence-free vector fields. 
Recall that the formula \eqref{eqn:cocycle} for the cocycle is 
\[
\varphi(\mu, \mu', \alpha) = \<\mu \wedge \mu', \alpha\>|_{z=0}.
\]

In cohomology, we obtain the cocycle for divergence-free vector fields by plugging in $\alpha = \d z_1 \wedge \d z_2$. 
This gives the cocycle on $\Vect_0(\CC^2)$ 
\[
(f_i \del_{z_i}, g_j \del_{z_j}) \mapsto (f_1 g_2 - f_2 g_1)(z_1=z_2=0) .
\]
This is the cocycle defining \eqref{eqn:centralvect}, as desired. 
\end{proof}

This proposition implies that the global symmetry algebra of the non-minimal twist of 11-dimensional supergravity is the Lie algebra $\cO(\CC^2)$. 
We will see that this is compatible with the calculation of the non-minimal twist of the full BV theory.

%\brian{introduce PCS}
%Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
%\[
%\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
%\]

### 2021-09-28 omega.tex
update

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory,amsaddr}

\def\vep{\varepsilon}

\addbibresource{cfs.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\section{Localization to a 5-dimensional theory}

In the last section we described a further twist

\subsection{The superconformal deformation}

The localization of the physical 11-dimensional supergravity theory is with respect to a supercharge of the form 
\[
{\bf Q} = Q + S 
\]
where $Q$ is the supertranslation defining the holomorphic twist. 
The element $S$ does not live in the algebra of supertranslations, but rather it lives in the superconformal algebra...

We consider the holomorphic two-form
\[
S(a,b,c) = a \, w_1 \d w_2 \wedge \d w_3 + b \, w_2 \d w_3 \wedge \d w_1 + c \, w_3 \d w_1 \wedge \d w_2 .
\]
In order for $S(a,b,c)$ to be $\del$-closed we have the following constraint on the variables $a,b,c$:
\beqn\label{eqn:abc}
a + b + c = 0 .
\eeqn
Using this equation, we can eliminate a single variable. 
We reparameterize using two new variables $a = \ep$, $b=\delta$, $c = -\ep - \delta$ and denote
\[
S(\vep, \delta) \define \ep \, w_1 \d w_2 \wedge \d w_3 + \delta \, w_2 \d w_3 \wedge \d w_1 - (\ep + \delta) \, w_3 \d w_1 \wedge \d w_2 .
\]

\subsection{Localized global symmetry algebra}

Up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
From this point of view, the global symmetry algebra of the $S$-deformed theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
S(\vep, \delta) \in \Omega^{2}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

We compute the cohomology of $E(5,10)$ with respect to the differential which is bracketing with this Maurer--Cartan element. 
Recall that we are using the holomorphic coordinates $(z_1,z_2,w_1,w_2,w_3)$ on $\CC^5$.

We record the following brackets in $E(5,10)$:
\begin{align*}
[f_i \del_{z_i}, S(\vep,\delta)] & = 0 \\
[g_a \del_{w_a}, S(\vep, \delta)] & = \vep w_1 (\del g_2 \wedge \d w_3 - \del g_3 \wedge \d w_2) 
+ \delta w_2 (\del g_3 \wedge \d w_1 - \del g_1 \wedge \d w_3) \\
& - (\vep + \delta) w_3 (\del g_1 \wedge \d w_2 - \del g_2 \wedge \d w_1) \\
[h \d z_1 \wedge \d z_2 , S(\vep, \delta)] & = h \left(\vep w_1 \del_{w_1} + \delta w_2 \del_{w_2} - (\ep + \delta) w_3 \del_{w_3} \right) \\
[h^{ia} \d z_i \wedge \d w_a, S(\vep, \delta)] & = \vep \ep_{ij} h^{i1} w_1 \del_{z_j} + \delta \ep_{ij} h^{i2} w_2 \del_{z_j} - (\vep + \delta) \ep_{ij} h^{i3} w_3 \del_{z_j} .
\end{align*}

From these formulas, we can read off the elements which are in the kernel of $[S,-]$:
\begin{itemize}
\item $f_i \del_{z_i}$ where $f_i \in \cO(\CC^5)$. 
\item $\lambda_a \del_{w_a}$, where $\lambda_a$ is a constant for $a=1,2,3$.  
\end{itemize}
In other words, the annihilator of $[S,-]$ in $E(5,10)$ is, up to completions, isomorphic to 
\[
\CC[z_i, w_a] \{\del_{z_i}\} \oplus \CC\{\del_{w_a}\} .
\]

\subsection{Relationship to the $\Omega$-background}

In \cite{CostelloOmega}, Costello defines the $\Omega$-background for supergravity. 
The main example treated is a certain $\Omega$-background for the non-minimal twist of 11-dimensional supergavity on 
\[
\CC^2 \times TN_k \times \RR^3 .
\]
Here, $TN_k$ is a Taub-NUT manifold with an $A_k$-singularity at the origin. 
One treats $\CC^2$ as a manifold with holonomy in $SU(2)$ and $TN_k \times \RR^3$ as a manifold with holonomy in $G_2$.

In the language of the minimal twist on 
\[
\CC^5 \times \RR = \CC^2_{z} \times \CC^3_w \times \RR_t 
\]
recall that the {\em nonminimal} twist arises from a background where the field strength of the field $\gamma$ takes the value 
\[
\del \gamma_{nm} = \d z_1 \wedge \d z_2 .
\]
This breaks the holonomy from $SU(5)$ to $SU(2)$.
Furthermore, we have shown that this background renders the theory topological along $\CC^3_w$.

\brian{equivariant...}

Therefore, we want to find a field $\gamma(a,b,c)$ such that
\beqn\label{eqn:euler}
[\gamma_{nm} , \gamma(a,b,c)] = a w_1 \del_{w_1} + b w_2 \del _{w_2} + c w_3 \del_{w_3} .
\eeqn
Recall that this bracket only depends on the field strengths of the fields.

Using $\del \gamma_{nm} = \d z_1 \wedge \d z_2$ we can easily find a solution for the field strength of $\gamma(a,b,c)$:
\[
\del \gamma(a,b,c) = a \, w_1 \d w_2 \wedge \d w_3 + b \, w_2 \d w_3 \wedge \d w_1 + c \, w_3 \d w_1 \wedge \d w_2 .
\]
In order for the expression for $\del \gamma(a,b,c)$ to be $\del$-closed, so that such a holomorphic one-form $\gamma(a,b,c)$ exists, we have the condition
\beqn\label{eqn:abc}
a + b + c = 0 .
\eeqn
Notice that we can add to this $\gamma(a,b,c)$ any holomorphic one-form on $\CC^2_z$ and it will still satisfy \eqref{eqn:euler}.

\appendix

\section{Branes}

\subsection{$\Omega$-deformed symmetry algebra}

On flat space, we have

\subsection{M2 branes in the $\Omega$-background}

\parsec[]

In the twisted $\Omega$-background a stack of $N$ M2 branes wraps 
\beqn\label{eqn:m2omega}
\{0\} \times \RR \subset \CC^2 \times \RR .
\eeqn

The field which sources this brane is a distributional differential form $F$.
The linear equation of motion for $F$ is the distributional equation 
\[
\d^2 z \wedge \dbar F = N \delta_{z=0} 
\]
where $\delta_{z=0}$ is the $\delta$-distribution for the submanifold \eqref{eqn:m2omega}.  
In what follows we denote $\til{\delta}_{z=0}$ the distributional $(0,2)$ form defined by contracting $\delta_{z=0}$ with the Calabi--Yau form~$\d^2 z$.

The field $F$ is a smooth Dolbeault form of type $(0,1)$ away from the locus of the brane $\CC^2 \times \RR_t \setminus \{0\} \times \RR \cong (\CC^2 \setminus 0) \times \RR_t$. 
Explicitly, we can characterize it as follows.

\begin{prop}
The field $F \in \Omega^{0,1} (\CC^2 \setminus 0) \otimes \Omega^{0} (\RR) $ defined by 
\[
F = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} 
\] 
satisfies the non-linear equation of motion 
\[
\dbar F + \frac12 F \star_c F = N  \til{\delta}_{z=0} .
\]
\end{prop}
\begin{proof}
The equation $\dbar F = N  \til{\delta}_{z=0}$ characterizes the Bochner--Martinelli kernel representing the residue class in $\CC^2 \setminus 0$. 
Since $F$ is a one-form $F \star_c F = 0$ is satisfied by anti-symmetry. 
\end{proof}

\parsec[]

We can interpret $F$ geometrically in the following way. 
Let's first consider just the complex geometric situation, forgetting about the $\RR$-direction.

On any hyper K\"ahler manifold $X$ there is an exact sequence of sheaves of Lie algebras
\[
0 \to \ul\CC \to \cO^{hol}(X) \to \Vect_0^{hol} (X) \to 0
\]
where $\Vect^{hol}_0(X)$ is the Lie algebra of holomorphic divergence-free vector fields and $\cO^{hol}(X)$ is equipped with the Poisson bracket induced by the holomorphic symplectic form. 
The map $\cO^{hol}(X) \to \Vect_0(X)$ is given by the holomorphic de Rham operator $\del \colon \cO^{hol}(X) \to \Omega^{1,hol}_{cl}(X)$ followed by the isomorphism 
$\Omega^{1,hol}_{cl} (X) \cong \Vect_0(X)$ given by the holomorphic symplectic form.

Extending this exact sequence to the level of Dolbeault resolutions, we see that we can view $F_0 \in \Omega^{0,1}(\CC^2 \setminus 0)$ as a $(0,1)$ Dolbeault valued divergence-free vector field $\til{F}_0$ on $\CC^2 \setminus 0$. 
Explicitly, if $F_0 = f^i (z,\zbar) \d \zbar_i$ then this $(0,1)$-valued vector field is
\[
\til{F}_0 = \ep_{jk} \partial_{z_j} f^i (z,\zbar) \d \zbar_i \partial_{z_k} .
\]

In the case at hand, $F \in \Omega^{0,1}(\CC^2 \setminus 0) \otimes \Omega^0(\RR)$ is given by the restriction along 
\[
(\CC^2 \setminus 0) \times \RR \to \CC^2 \setminus 0
\]
of the $(0,1)$-form
\[
F_0 = \# N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^4} .
\] 
The corresponding $(0,1)$-valued vector field on $\CC^2 \setminus 0$ is
\[
\til{F}_0 = \#' N \frac{\zbar_1 \d \zbar_2 - \zbar_2 \d \zbar_1}{\|z\|^6} \left(\zbar_1 \del_{z_2} - \zbar_2 \del_{z_1}\right) .
\]

\end{document}

### 2021-09-28 suco.tex
update

@@
 \[
-\ep^{abcd} w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\frac{1}{2} (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4 .
 \] 
@@
 \[
-\ep^{abcd} z w_c \d w_d \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
+\frac{1}{2} z (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
 \] 
@@
 Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
-To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above:
+To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
+Recall, we are using the holomorphic coordinates $(z,w_1,\ldots,w_4)$ on $\CC^5$ where $z$ is the holomorphic coordinate along the $M2$ brane. 
 \begin{itemize}
@@
 \[
-(z \d w_a  \wedge \d w_b + \ep^{abcd} w_c \d z \wedge \d w_d) , \quad a,b=1,2,3,4. 
+z \d w_a  \wedge \d w_b + \frac12 \d z \wedge (w_a \d w_b - w_b \d w_a) , \quad a,b=1,2,3,4. 
 \] 
@@
 \[
-z_i \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
+z_j \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
 \] 
@@
 \[
-\ep^{ijk} z_i w_a \d z_j \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
+\frac12 w_a (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
 \]
@@
 \end{lem}
+
+To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
+Recall, we are using the holomorphic coordinates $(z_1,z_2,z_3, w_1,w_2)$ on $\CC^5$ where $z_i$ are the holomorphic coordinates along the $M5$ brane. 
+\begin{itemize}
+\item 
+The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
+\[
+\d z_i \wedge \d w_a, \quad i=1,2,3, \quad a=1,2. 
+\] 
+\item 
+The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
+\[
+w_a \d z_i  \wedge \d z_j + \frac12 \d w_a \wedge (z_i \d z_j - z_j \d z_i) , \quad i,j=1,2,3, \quad a=1,2. 
+\] 
+\end{itemize}
 

### 2021-09-29 dfn.tex
reorganized index computation

@@
  \mu^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
-\nu_{(m_i)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
+\nu_{(m_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
 \gamma^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
@@
 We can now readily compute the characters.
-\begin{prop}
+\begin{prop}\label{prop:locchar}
 The $SU(5)$ local character of the holomorphic twist of the 11-dimensional theory on flat space is
@@
 \chi_{SU(5)} = 
-\prod_ {(m_i;n_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
+\prod_ {(m_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
 \\ 
@@
 \end{prop}
+\begin{proof}
+We compute the local character as the plethystic exponential of the character of linear local operators.
 
+Note that the linear local operators $ \nu_{(m_j)}$ and $\beta_{(m_j)}$ are of the same weight but opposite parity so contribute to the character with opposite sign.
+These contributions therefore cancel.
+Next, there is a summand of the linear local operators of the form
+\[
+\bigoplus _{(m_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\mu^{z_1}_{(m_j)}\partial_{z_1}\oplus \C\mu^{z_2}_{(m_j)}\partial_{z_2}\oplus \C\mu^{z_3}_{(m_j)}\partial_{z_3}\oplus\C\mu^{w_1}_{(m_j)}\partial_{w_1}\oplus \C\mu^{w_2}_{(m_j)}\partial_{w_2}\right).
+\] 
+This contributes 
+\[
+\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
+\] 
+Finally, there is a summand of the form 
+\[
+\bigoplus _{(m_i;n_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\gamma^{z_1}_{(m_i; n_j)}d{z_1}\oplus \C\gamma^{z_2}_{(m_i; n_j)}d{z_2}\oplus\C\gamma^{z_3}_{(m_i; n_j)}d{z_3}\oplus\C\gamma^{w_1}_{(m_i; n_j)}d{w_1}\oplus \C\gamma^{w_2}_{(m_i; n_j)}d {w_2}\right).
+\] 
+This likewise contributes 
+\[
+\sum_{(m_j)\in \Z^5_{\geq 0 }}t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right).
+\] 
+In sum, the character of linear local operators is the geometric series 
+\[
+\sum_{(m_j)\in \Z^5_{\geq 0 }}-t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right).
+\] 
+The plethystic exponential of this expression is then 
+\[
+\prod_ {(m_j)\in \Z^5_{\geq 0}}\frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
+\]
+\end{proof}
 \subsection{Component fields}

### 2021-10-06 susy.tex
linfty model and edits

@@
 \[
-\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee .
+\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee \oplus \C .
 \]
@@
 z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \d z_i \wedge \d z_j \in \Omega^{2}_{cl} (\CC^5) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \in \Vect_0(\CC^5) \\ \frac{\partial}{\partial z_j} \in L^\vee & \mapsto
-\frac{\partial}{\partial z_i} \in \Vect_0(\CC^5) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \Vect_0(\CC^5) \\ \partial z_i \in L^\vee & \mapsto
+\partial z_i \in \Vect_0(\CC^5) \\
 c \in \CC_c & \mapsto c \in \CC_{c'} .
@@
 This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
-In \cite{??} it is shown that this cocycle $\mu_2$ is
+In \cite{fiorenza2015super} it is shown that $\mu_2$ defines a nontrivial class in $H^4(\ft_{11d})$ so defines a one dimensional central extension of $\ft_{11d}$ as a lie 3-algebra.
+Instead of working with a one-dimensional central extension by $\C[2]$, we work with a central extension by the resolution $\Omega^\bullet(\R^{11})[2]$.
+There is a quasi-isomorphism $\clie^4(\ft_{11d})\to \clie^4(\ft_{11d}, \Omega^\bullet (\R^11))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\R^{11})[2]$-valued 2-cocycle we use.
 

### 2021-10-06 intro.tex
merge

%\documentclass[11pt]{amsart}
%
%\usepackage{macros-mtheory,amsaddr}
%\usepackage{array}
%
%\def\vep{\varepsilon}
%
%\addbibresource{cfs.bib}
%
%%\linespread{1.2} %for editing
%%\usepackage{mathpazo}
%
%\begin{document}

The twist of a supersymmetric field theory was first studied by Witten \cite{WittenTwist}.
Later, the notion was generalized and developed mathematically by Costello \cite{CostelloHol}. 
Generally speaking, the twist of a supersymmetric field theory is a systematic way of taking the invariants of a theory with respect to a fixed supercharge which squares to zero. 
In a supergravity theory, supertranslations are already gauged and so this notion of twisting is {\em a priori} not a sensible thing to do.

In their seminal paper, Costello and Li gave a definition of twisted supergravity: it is supergravity in a background where the bosonic ghost takes a nonzero value \cite{CLsugra}.
They have provided conjectural descriptions of many examples of 10-dimensional theories of supergravity, and have used these descriptions to rigorously construct quantizations of open-closed string field theories \cite{CLbcov1,CLtypeI}. 
A very active and promising direction is to use these twisted 10-dimensional models to formulate twisted versions of holography \cite{Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant}.

In this paper, we provide perturbative descriptions of all twists of 11-dimensional supergravity. 
By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
\begin{itemize}
\item The minimal (or holomorphic) twist. 
The resulting twisted theory is defined on $\CC^5 \times \RR$ and is holomorphic along $\CC^5$ and topological along the `time' direction~$\RR$. 
The twist is $SU(5)$ invariant and involves a fixed choice of a Calabi--Yau form on $\CC^5$. 
\item The non minimal twist. 
The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
The twist is $SU(2)$ invariant and involves a fixed choice of a hyper K\"ahler structure on $\CC^2$.  
\end{itemize}

In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.

\begin{conj}
The $11$-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge. 
\end{conj}

\brian{Ingmar, maybe you can comment on the status of this conjecture.}
In this paper we will provide evidence for this conjecture on a variety of fronts. 
In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist.

In \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity of \cite{CLsugra}.

In \S\ref{sec:ads} we propose a description of supergravity in twisted versions of both the ${\rm AdS}_7$ and ${\rm AdS}_4$ backgrounds. 
We show that the residual symmetries of supergravity in these backgrounds are present in our twisted background.

Finally, we describe the non minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
We find a match with a con \brian{finish}
%Surprisingly, at the twisted level these symmetries

Our 11-dimensional theory is defined more generally on the product of manifolds 
\[
X \times L
\]
where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented real one-dimensional manifold. 
The theory is of a holomorphic gravitational flavor as it describes ``partial'' deformations of complex structures along $X$. 
We will explain what we mean by this momentarily.

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(L) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu$ can be decomposed as Beltrami-like differential
\[
\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:component}.

Next, there are two fields 
\[
\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(L), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(L) .
\]
The field $\gamma^{1,2}$ is a component of the supergravity $3$-form $C$-field that survives in the twisted theory. 
The field $\gamma^{1,0}$ can be interpreted as a component of the one-form which is a ghost-for-a-ghost of the $C$-field.\footnote{The $C$-field has a gauge symmetry of the form $\delta C = \d B$ where $B$ is a two-form.
This ghost $B$ field has an additional gauge symmetry $\delta B = \d A$ for $A$ a one-form.
The field $\gamma^{1,0}$ is a component of $A$.}

There is a background where the equations of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields in our 11-dimensional theory read
\begin{align*}
\dbar \mu + \frac12 [\mu, \mu] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
(\dbar + \mu) \gamma^{1,0} = 
(\dbar + \mu) \gamma^{1,2} & = 0 \\
\div \mu & = 0 \\
\d_L \mu = \d_L \gamma^{1,0} = \d_L \gamma^{1,2} = & = 0 .
\end{align*}
In the last line $\d_L$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
Notice that were it not for the presence of the last term in the first equation then this would be the integrability equation for $\mu$ to determines a complex structure on $X$.
The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times L$ which further preserves the holomorphic volume form along the leaves.
We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

\subsection*{Appearance of exceptional Lie superalgebras}

The gauge symmetries of a field configuration in any theory form a Lie algebra. 
In the Batalin--Vilkovisky formalism, one combines fields of all ghost number into a single object which, together with the linear BRST operator, has the structure of a dg Lie algebra.\footnote{In some models one actually obtains an $L_\infty$ algebra.} 
From the point of view of deformation theory, this dg Lie algebra describes the formal moduli space of deformations of the particular field configuration.

The simplest field configuration in the twisted theory is the flat background which corresponds to considering to our 11-dimensional theory on $\CC^5 \times \RR$ where we equip $\CC^5$ with the flat holomorphic volume form. 
In this case we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.

\begin{thm}
The global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension of the exceptional super Lie algebra $E(5,10)$. 
\end{thm}

Given our main conjecture that the interacting 11-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.

\begin{conj} 
A central extension of the super Lie algebra $E(5,10)$ is a symmetry of supergravity on $\RR^{11}$ which preserves the background where the bosonic ghost takes value equal to a holomorphic supercharge $Q$.
\end{conj}

\subsection*{Relationship to other twists of supergravity}

Motivated by the topological string, Costello and Li formulated conjectural descriptions of certain twists of 10-dimensional theories of supergravity. 
All of the descriptions center around the theory of Kodaira--Spencer gravity, otherwise known as BCOV theory. 
This theory was introduced in \cite{BCOV} as the closed-string field theory of the topological $B$-model on Calabi--Yau three-folds.
It was further extended to all Calabi--Yau manifolds in \cite{CLbcov1}. 
It is a sort of holomorphic version of gravity which at the genus zero  describes fluctuations of the complex structure of the Calabi--Yau manifold. 
We recall relevant aspects of Kodaira--Spencer gravity in \ref{s:BCOV}.

Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{tbl:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
It means that the twist of supergravity we are considering arises from a certain subsector of a hybrid topological string which is the $B$-model into the Calabi--Yau manifold $\CC^n$ and the $A$-model into the symplectic manifold $\RR^{2m}$.

\begin{table}[]
\begin{tabular}{c|c|c|c|c|c|c|c|}
\cline{2-7}
& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
\end{tabular}
\end{table}

In \S \ref{s:su4red} we will show that the reduction along a line of the form $\{0\} \times \RR \times \{0\} \CC^4 \times \CC^\times \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity.

\subsection*{Future work}

\subsection*{Acknowledgements}

%\end{document}

### 2021-10-06 nonmin.tex

@@
 \end{thm}
+
+\parsec[sec:indexcheck]
+
+As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G2\times SU(2)$ twist.
+We will find that the local character of the latter agrees with a specialization of the local character computed in proposition \ref{prop:locchar}
+
+\begin{prop}
+The  local character of the $G2\times SU(2)$ twist of 11d supergravity on flat space is given by
+\[
+\chi_{SU(3)\times SU(2)}(\Obs_0^{\cE_{G2\times SU(2)}}) = \prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
+\] 
+This agrees with the specializaiton of the local character computed in proposition \ref{prop:locchar} at $y=1$.
+\end{prop}
+\begin{proof}
+The space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$.
+The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by
+\[
+A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
+\]
+
+The character of the linear span of these is given by the geometric series
+\[
+\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}
+\] 
+with plethystic exponential given by 
+\[
+\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
+\]
+
+For the last part, it suffices to show that the characters of linear local operators agree upon evaluating $y=1$.
+Summing the geometric series giving the character of linear local operators in the holomorphic twist yields the rational function \[\frac{\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y &+ q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right)}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\] Specializing $y=1$, the numerator cancels with the factors in the denominator involving the $t_i$.
+The result is \[\frac{1}{(1-q^{-1})(1-q)}\] which is exactly the sum of the geometric series we found
+
+\end{proof}
 

### 2021-10-09 dfn.tex
merge

@@
 %We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
-We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
+We can describe the $L_\infty$ structure on our new model $\cL_\infty$ explicitly.
 Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
@@
 \end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\[
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) .
-\]
+For $k \geq 2$ the general formula for the $k$-ary brackets are 
+\begin{align*}
+[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
+[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
+[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
+\end{align*}
 
@@
 
-We thus obtain a theory in the BV formalism on the product manifold $X \times L$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(S)$ and $\cL_\infty(X) \otimes \Omega^\bu(S)$.
+We thus obtain a theory in the BV formalism on the product manifold $X \times S$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(S)$ and $\cL_\infty(X) \otimes \Omega^\bu(S)$.
 
@@
 \deq{
-  S_{BF,\infty} =  \beta \wedge (\dbar + \d_L) \nu +  \gamma \wedge (\dbar + \d_L) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma .
+  S_{BF,\infty} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma .
 }
@@
 First off, we remark on grading issues. 
-In the original $\Z$-grading on the BF theory given in \eqref{eq:sympfields} with $n=5$, the component $\gamma^{1,i;j}$ sits in degree $-4+i+j$. 
+In the original $\Z$-grading on the BF theory given in \eqref{eq:sympfields} with $n=5$, the component 
+\[
+\gamma^{1,i;j} \in \Omega^{1,i}(X) \otimes \Omega^j(S) 
+\]
+sits in degree $-4+i+j$. 
 Thus, we see that in the original $\Z$-grading on BF theory one has
@@
 
-This is completely reasonable \brian{finish}
+This is completely reasonable from the point of view of twisting supersymmetry in 11-dimensions. 
+Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data \label{CosHol,ESW}.
 
@@
 
-\subsection{Equations of motion}
+\subsection{Equations of motion} \label{s:eom}
 
-Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + J$ is the minimal twist of $11$-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form.
+Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + g J$ is the minimal twist of $11$-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form.
 For the moment, we briefly read off the equations of motion of the general theory on $X \times S$.
@@
 \eeqn
-The last term represents the contraction of an element of $\Omega^{4,\bu}(X;S)$ with the section $\Omega^{-1} \in \PV^{5,\bu}(X;S)$ to yield an element of $\PV^{1,\bu}(X;S)$.
+The last term represents the contraction of an element of $\Omega^{4,\bu}(X;S)$ with the nonvanishing section $\Omega^{-1} \in \PV^{5,\bu}(X;S)$ to yield an element of $\PV^{1,\bu}(X;S)$. 
+If we vary the $\mu$ we obtain 
+\beqn\label{eqn:eommu}
+(\dbar + \d_S) \gamma + \del \beta + \frac{1}{1-\nu} (\mu \vee \del \gamma) = 0 .
+\eeqn
+Finally, if we vary $\nu$ we obtain
+\beqn\label{eqn:eomnu}
+(\dbar + \d_S) \beta + \frac12 \frac{1}{(1-\nu)^2} \mu^2 \vee \del \gamma = 0 .
+\eeqn
 
-Let us make the simplifying assumption that $\mu$ is divergence-free and locally constant along $S$: $\div \mu = 0$ and $\d_S \mu = 0$.
+The equation of motion must hold for any inhomogenous superfields.
+We can get a better sense of the equations if we expand in components of these fields. 
+The component fields of the 11-dimensional theory on $X \times S$ have the following form: 
+\begin{itemize}
+\item $\mu = \sum_{i,j} \mu^{i;j}$ is a superfield where
+\[
+\mu^{i;j} \in \PV^{1,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
+\]
+The component $\mu^{i;j}$ has parity $i+j+1 \mod 2$. 
+\item $\nu = \sum_{i,j} \nu^{i;j}$ is a superfield where
+\[
+\nu^{i;j} \in \PV^{0,i}(X, \T_X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
+\]
+The component $\nu^{i;j}$ has parity $i+j \mod 2$. 
+%The linear equations of motion state that $\mu$ is constant along $\RR$ and holomorphic divergence-free as a vector field on $\CC^5$. 
+\item 
+$\gamma = \sum_{i,j} \gamma^{i;j}$ is a superfield where
+\[
+\gamma^{i;j} \in \Omega^{1,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
+\]
+The component $\gamma^{i;j}$ has parity $i+j$. 
+\item 
+\item $\beta = \sum_{i,j} \beta^{i;j}$ is a superfield where
+\[
+\beta^{i;j} \in \Omega^{0,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
+\]
+The component $\beta^{i;j}$ has parity $i+j+1 \mod 2$. 
+\end{itemize}
+
+We look closely at the geometric meaning of \eqref{eqn:eombeta}. 
+Let's make the simplifying assumption that all components of $\mu$ are divergence-free that all fields are locally constant along $S$: $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
 Then, $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
-Then \eqref{eqn:eomgamma} can be written as 
+Then, there is a component of \eqref{eqn:eomgamma} which can be written as 
 \beqn\label{eqn:eomgamma1}
-\dbar \mu + \frac12 [\mu,\mu] + \frac12 (\del \gamma \wedge \del \gamma) \vee (g \Omega^{-1}) = 0 
+\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + \left(\frac12 \del \gamma^{1;0} \wedge \del \gamma^{1;0} + \del \gamma^{2;0} \wedge \del \gamma^{0;0}\right) \vee (g \Omega^{-1}) = 0 
 \eeqn
-where $[-,-]$ is the Schouten bracket.
+where now $[-,-]$ stands for the Schouten bracket.
 
-The equation of motion \eqref{eqn:eomgamma1} must hold for any inhomogenous field $\mu \in \PV^{1,\bu}(X;S)$. 
-The most geometrically relevant component is the case where 
-\[
-\mu^{1;0} \in \PV^{1,1}(X) \otimes \Omega^0(S) 
-\]
-which is an even field in our $\ZZ/2$ graded BV theory.
-The superscript denotes anti-holomorphic; de Rham form type. 
-For this component of $\mu$, the only components of $\gamma$ which appear in the above equations of motion are $\gamma^{0;0}$, $\gamma^{1;0}$, and $\gamma^{2;0}$.
-Expanding these components out, we obtain
-\beqn\label{eqn:eomgamma1}
-\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + (\del \gamma^{0;0} \wedge \del \gamma^{2;0}) \vee (g \Omega^{-1}) + \frac12 (\del \gamma^{1;0} \wedge \del \gamma^{1;0}) \vee (g \Omega^{-1}) = 0 .
-\eeqn
+%The most geometrically relevant component is the case where 
+%\[
+%\mu^{1;0} \in \PV^{1,1}(X) \otimes \Omega^0(S) 
+%\]
+%which is an even field in our $\ZZ/2$ graded BV theory.
+%The superscript denotes anti-holomorphic; de Rham form type. 
+%For this component of $\mu$, the only components of $\gamma$ which appear in the above equations of motion are $\gamma^{0;0}$, $\gamma^{1;0}$, and $\gamma^{2;0}$.
+%Expanding these components out, we obtain
+%\beqn\label{eqn:eomgamma1}
+%\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + (\del \gamma^{0;0} \wedge \del \gamma^{2;0}) \vee (g \Omega^{-1}) + \frac12 (\del \gamma^{1;0} \wedge \del \gamma^{1;0}) \vee (g \Omega^{-1}) = 0 .
+%\eeqn
 
@@
 \] 
-The plethystic exponential of this expression is then 
-\[
-\prod_ {(m_j)\in \Z^5_{\geq 0}}\frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
-\]
+The plethystic exponential returns the desired expression.
+%\[
+%\prod_ {(m_j)\in \Z^5_{\geq 0}}\frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
+%\]
 \end{proof}
-\subsection{Component fields}
+
+%The linear equations of motion for the superfield $\mu$ read 
+%\[
+%\dbar \mu^{i;j} + \d_{S} \mu^{i+1, j-1} = 0, \quad \div \mu^{i,j} = 0
+%\]
+%for all $i,j$. 
+%The operator $\dbar$ is the anti-holomorphic Dolbeault operator acting on $\CC^5$, $\d_S$ is the de Rham operator on $S$, and $\div$ is the divergence with respect to the fixed holomorphic volume form on $\CC^5$.
+%In particular, this states that $\mu^{i;0}$ is locally constant along $S$ and holomorphic divergence-free as a Dolbeault valued vector field on $\CC^5$.
 
@@
 
-Upon performing the $\Omega$-background, see \S \ref{s:omega}, the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
-Costello has shown via a cohomological argument that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory \cite{CostelloM5}. 
+Upon performing the $\Omega$-background,
+%see \S \ref{s:omega},
+In \cite{CostelloM5}, Costello argues that the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
+Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 
 We will return to the existence and uniqueness of a higher order quantization of the 11-dimensional theory in future work.

### 2021-10-09 dfn.tex
merge

@@
 
-When $c=0$, this result is actually exact
+When $g=0$, this result is actually exact
 since there are no Feynman diagrams present past one-loop in this case. 
-When $c \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge invariant perturbative quantization to higher orders in $\hbar$. 
+When $g \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge invariant perturbative quantization to higher orders in $\hbar$. 
 The presence of the functional $J = \frac16 \int \gamma \del \gamma \del \gamma$ allows one to construct Feynman graphs at arbitrary loop order.

### 2021-10-09 matrix.tex
merge

@@
-\section{Twisted BFFS matrix model}
+\section{Twisted matrix model}
 
@@
 
-Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional simple super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
+Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
 We recall the definition below.
@@
 \item 
-As a super Lie algebra, the $\delta^{(1)}$-cohomology of $\Pi\cE(\CC^5 \times \RR)$ is isomorphic to the trivial one-dimensional central extension of the super Lie algebra $E^{hol}(5,10)$.
+As a super Lie algebra, the $\delta^{(1)}$-cohomology of $\Pi\cE(\CC^5 \times \RR)$ is isomorphic to the trivial one-dimensional central extension of the super Lie algebra $E(5,10)$.
 \item 
-The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E^{hol}(5,10)$ determined by the even cocycle \eqref{eqn:cocycle}. 
+The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E(5,10)$ determined by the even cocycle \eqref{eqn:cocycle}. 
 \end{enumerate}
 \end{thm}
+
+This result implies that the action functional $S_{BF, \infty} + J$ of the 11-dimensional theory is invariant for infinite-dimensional Lie algebra $E(5,10)$.
+
 %defined by the even cocycle
 %\begin{align*}
-%E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to \CC \\
+%E(5,10) \times E(5,10) \times E(5,10) & \to \CC \\
 %(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
@@
 %The parity of the functional in the theorem is odd, but it is also trilinear. 
-%Thus, as a cocycle in the Chevalley--Eilenberg complex of $E^{hol}(5,10)$ it is of total even parity.
+%Thus, as a cocycle in the Chevalley--Eilenberg complex of $E(5,10)$ it is of total even parity.
 
-The super Lie algebra $E^{hol}(5,10)$ is very closely related to the super Lie algebra $E(5,10)$ studied by Kac; there is a dense embedding of super Lie algebras $E(5,10) \hookrightarrow E^{hol}(5,10)$.
+%The super Lie algebra $E(5,10)$ is very closely related to the super Lie algebra $E(5,10)$ studied by Kac; there is a dense embedding of super Lie algebras $E(5,10) \hookrightarrow E(5,10)$.
 
@@
 
-The even part of the super Lie algebra $E^{hol}(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
+The even part of the super Lie algebra $E(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
 \[
-E^{hol}(5,10)_+ = \Vect_0(\CC^5) ,
+E(5,10)_+ = \Vect_0(\CC^5) ,
 \]
@@
 \[
-E^{hol}(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
+E(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
 \]
@@
 
-More precisely, Kac studied a dense sub Lie algebra $E(5,10)$ of $E^{hol}(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
-It is this dense sub super Lie algebra which is simple.
+To be precise, Kac studied a more algebraic version of the algebra we have just introduced where holomorphic functions are replaced by holomorphic polynomials.
+Thus, the simple super Lie algebra classified in \cite{KacBible} is a dense sub Lie algebra of what we call $E(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
 
@@
 In this section, we use the description of the 11-dimensional theory as the deformation of the BF action $S_{BF,\infty}$ by the functional $J$ of Theorem \ref{thm:dfn}. 
+We set the coupling $g = 1$, for any other nonzero value of $g$ we will obtain an isomorphic super $L_\infty$ algebra.
+
 We will obtain the exact same results if we use the equivalent model of the 11-dimensional theory explained in \S \ref{s:altdfn}. 
@@
 We complete the proof of the first part of Theorem \ref{thm:global}. 
+For this we write down an explicit map between the cohomology computed above and the algebra $E(5,10)$.
 
@@
 induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E^{hol}(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E^{hol}(5,10)$ and the twist of 11-dimensional supergravity. 
+This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E(5,10)$ by $\alpha = \del \gamma$. 
+It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E(5,10)$ and the twist of 11-dimensional supergravity. 
 This completes the proof of part (1) of Theorem \ref{thm:global}.
@@
 \subsection{(Non)formality and homotopy transfer} 
+\label{s:ht}
 
@@
 \begin{tikzcd}
-\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E^{hol}(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
+\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
 \end{tikzcd}
@@
 
-Given this homotopy data, we can compute the homotopy transferred $L_\infty$ structure on the linearized BRST cohomology following \brian{??}. 
+Given this homotopy data, we can compute the homotopy transferred $L_\infty$ structure on the linearized BRST cohomology. 
 Since $\nu$ does not survive to cohomology and the fact that there are no nontrivial Lie brackets involving the field $\beta$, this transferred structure is easy to compute.
@@
 There is a single diagram which contributes to the transferred structure, it is given by
-\brian{do it}
+\begin{equation}
+\begin{tikzpicture}
+\begin{feynman}
+%\vertex at (-2,0) {$\mu'_3 \ = $};
+\vertex(a) at (-1,1) {$i(\mu)$};
+\vertex(b) at (-1,0) {$i([\gamma])$};
+\vertex(c) at (-1,-1) {$i(\mu')$};
+\vertex(d) at (0,0.5);
+\vertex(e) at (1,0);
+\vertex(f) at (2,0) {$q$};
+\diagram* {(a)--(d), (b)--(d), (d)--[edge label = $K$](e), (c)--(e), (f)--(e)};
+\end{feynman}
+\end{tikzpicture}
+\end{equation}
+together with a similar diagram with the $\mu$ and $\mu'$ flipped.
 
-This diagram leads to a new $3$-ary bracket on $E^{hol}(5,10) \oplus \CC_b$
+This diagram leads to a new $3$-ary bracket on $E(5,10) \oplus \CC_b$
 \[
@@
 \]
-where $\varphi \in \clie^{even} (E^{hol}(5,10))$ is the even Lie algebra cocycle defined by the formula
+where $\varphi \in \clie^{even} (E(5,10))$ is the even Lie algebra cocycle defined by the formula
 \beqn
 \begin{array}{rclr}
-\varphi \colon E^{hol}(5,10) \times E^{hol}(5,10) \times E^{hol}(5,10) & \to & \CC_b \\
+\varphi \colon E(5,10) \times E(5,10) \times E(5,10) & \to & \CC_b \\
 \varphi(\mu,\mu',\alpha) & = & \<\mu \wedge \mu', \alpha\>|_{z=0} .
@@
 \eeqn
-Since $b$ is central, this cocycle defines a central extension of $E^{hol}(5,10)$.
+Since $b$ is central, this cocycle defines a central extension of $E(5,10)$.
 

### 2021-10-09 susy.tex
merge

@@
 \beqn\label{eqn:susycoh}
-L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^2 L\right) \oplus \CC
+L \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^2 L^\vee\right) \oplus \CC
 \eeqn
@@
 \beqn\label{eqn:susy2bra}
-[\psi, \psi']_2 = \psi \wedge \psi' \in \wedge^4 L \cong L^\vee_v \\
+[\psi, \psi']_2 = \psi \wedge \psi' \in \wedge^4 L^\vee \cong L_v \\
 \eeqn
@@
 \beqn\label{eqn:susy3bra}
-[v, v', \psi]_3 = 4 \<v \wedge v', \psi\> \in \CC_c .
+[v, v', \psi]_3 = 4 \<v \wedge v', \psi\> \in \CC_b .
 \eeqn
@@
 \[
-H^\bu(\m2^Q) \oplus (L \xto{\id} \Pi L)  .
+H^\bu(\m2^Q) \oplus (L^\vee \xto{\id} \Pi L^\vee)  .
 \]
@@
 \begin{align*}
-[v,\lambda] & = \<v, \lambda\> \in \CC_c \\ 
-[v,\psi] & = \<v, \psi\> \in \Pi L_{\Tilde{\lambda}}.
+[v,\lambda] & = \<v, \lambda\> \in \CC_b \\ 
+[v,\psi] & = \<v, \psi\> \in \Pi L^\vee_{\Tilde{\lambda}}.
 \end{align*}
@@
 The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
-The element $Q$ only acts nontrivially on the summands $\wedge^4 L^\vee$ and $\wedge^5 L^\vee$ in $S$. 
-The image of $\wedge^4 L^\vee \cong L$ trivializes the antiholomorphic translations while the image of $\wedge^5 L^\vee$ trivializes the time translation.
-So, of the translations, only the holomorphic ones $L^\vee$ survive.
+The element $Q$ only acts nontrivially on the summands $\wedge^4 L$ and $\wedge^5 L$ in $S$. 
+The image of $\wedge^4 L \cong L^\vee$ trivializes the antiholomorphic translations while the image of $\wedge^5 L$ trivializes the time translation.
+So, of the translations, only the holomorphic ones, which live in $L$, survive.
 The map 
@@
 \] 
-is the projection onto $\wedge^0 L^\vee \oplus \wedge^1 L^\vee \oplus \wedge^2 L^\vee$. 
+is the projection onto $\wedge^0 L \oplus \wedge^1 L \oplus \wedge^2 L$. 
 The kernel of $[Q,-]$ is the stabilizer~${\rm Stab}(Q)$.
 
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L^\vee \cong \wedge^2 L$.
+In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$.
 This completes the calculation of the cohomology.
 
-We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L^\vee$ sit inside in the evident way.
+We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L$ sit inside in the evident way.
 The central element maps to $c \mapsto - 1 \in \Omega^0(\RR^{11})$.
@@
 There is only a single term in the $L_\infty$ structure generated by homotopy transfer. 
-It is determined by the following tree diagram. 
-\brian{do it}
-This recovers the formula in (2) of Proposition \ref{prop:susycoh}.
+It is determined by the following tree diagram
+\begin{equation}
+\begin{tikzpicture}
+\begin{feynman}
+%\vertex at (-2,0) {$\mu'_3 \ = $};
+\vertex(a) at (-1,1) {$i(v)$};
+\vertex(b) at (-1,0) {$i(\psi)$};
+\vertex(c) at (-1,-1) {$i(v)$};
+\vertex(d) at (0,0.5);
+\vertex(e) at (1,0);
+\vertex(f) at (2,0) {$q$};
+\diagram* {(a)--(d), (b)--(d), (d)--[edge label = $K$](e), (c)--(e), (f)--(e)};
+\end{feynman}
+\end{tikzpicture}
+\end{equation}
+together with a similar diagram with the $v$ and $v'$ reversed. 
+It is an immediate calculation to show that these trees recover the formula in (2) of Proposition \ref{prop:susycoh}.
 
@@
 \]
-where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q \simeq \fg$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
+%where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
+In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
 \end{prop}
@@
 \ul{even} & \ul{odd} & \ul{even} \\
- L & \wedge^2 L_2 & L^\vee \\
-\wedge^2 L_1 & & \\
-\lie{sl}(5) && \CC_c  \\
+ L^\vee & \wedge^2 L^\vee_2 & L \\
+\wedge^2 L_1^\vee & & \\
+\lie{sl}(5) && \CC_b  \\
 %L_2 \ar[r, "\id"] & L_3 \\ 
@@
 \begin{align*}
- L & \mapsto 0 \\
- \wedge^2 L_1 & \mapsto 0 \\
-z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\ \partial_{z_j} \in L^\vee & \mapsto
+ L^\vee & \mapsto 0 \\
+ \wedge^2 L_1^\vee  & \mapsto 0 \\
+z_i \wedge z_j \in \wedge^2 L^\vee_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\ \partial_{z_j} \in L & \mapsto
 \partial_{z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ %z_i \in %L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
 %z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
-1 \in \CC_c & \mapsto 1 \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
+1 \in \CC_b & \mapsto 1 \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
 \end{align*}
@@
 
-This map also preserves the bracket between odd elements in $\wedge^2 L_2$. 
+This map also preserves the bracket between odd elements in $\wedge^2 L_2^\vee$. 
 In the cohomology of $\m2^Q$ we have the bracket
@@
 \[
-L^\vee \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L^\vee\right) \oplus \CC_c \to E (5,10) \oplus \CC_{c'}
+L \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L \right) \oplus \CC_b \to E (5,10) \oplus \CC_{b'}
 \]
@@
 \begin{align*}
- L_1 & \mapsto 0 \\
- \wedge^2 L_1 & \mapsto 0 \\
+ L^\vee_1 & \mapsto 0 \\
+ \wedge^2 L^\vee_1 & \mapsto 0 \\
 z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \d z_i \wedge \d z_j \in \Omega^{2}_{cl} (\CC^5) \\
-A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \Vect_0(\CC^5) \\ \partial z_i \in L^\vee & \mapsto
-\partial z_i \in \Vect_0(\CC^5) \\
-c \in \CC_c & \mapsto c \in \CC_{c'} .
+A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \Vect_0(\CC^5) \\ \partial_{z_i} \in L & \mapsto
+\partial_{z_i} \in \Vect_0(\CC^5) \\
+b \in \CC_b & \mapsto b \in \CC_{b'} .
 \end{align*}
@@
 Instead of working with a one-dimensional central extension by $\C[2]$, we work with a central extension by the resolution $\Omega^\bullet(\R^{11})[2]$.
-There is a quasi-isomorphism $\clie^4(\ft_{11d})\to \clie^4(\ft_{11d}, \Omega^\bullet (\R^11))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\R^{11})[2]$-valued 2-cocycle we use.
+There is a quasi-isomorphism $\clie^4(\ft_{11d})\to \clie^4(\ft_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\R^{11})[2]$-valued 2-cocycle we use.
 

### 2021-10-13 dimred.tex
background on KS

@@
 
-Let $X$ be a Calabi--Yau manifold; for now it can be of arbitrary complex dimension. 
+Let $X$ be a Calabi--Yau manifold; for now it can be of arbitrary complex dimension $d$. 
 Define
@@
 
-\brian{surya, could fill these parsecs in?}
-
 \parsec[s:poisson]
-
-%describe odd poisson structure
+The original action for Kodaira-Spencer theory posited by \cite{BCOV}\surya{which reference is BCOV} has a nonlocal kinetic term.
+In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form.
+The Poisson kernel is given by the expression
+\[
+(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \Sym^2 (\PV^{\bu,\bu}(X)[[u]][2])
+.\]
+Explicitly, the above kernel pairs against the dual to 
+\[
+\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}(X)[[u]][2]
+\]
+ by the formula 
+\[
+\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
+\] 
+Here, the overlines denote the dual field in 
+\[
+(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
+\] 
+That is, further expanding the fields as 
+\[
+\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
+\] 
+the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.
 
@@
 
-%recall genus zero BCOV action.
+There is a natural local interaction which equips the above cyclic cochain complex with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
+\beqn
+I_{BCOV}(\Sigma) = \int^\Omega \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} \int^\Omega\langle\Sigma^{\otimes n}\rangle_0
+\eeqn
 
+where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
+\beqn
+\langle u^{k_1}\mu_1 \otimes \cdots \otimes u^{k_m}\mu_m\rangle_0 := \left (\int _{\overline {\cM}_{0,m}} \psi_1^{k_1}\cdots \psi_m^{k_m}\right ) \mu_1\cdots \mu_m = \binom{m-3}{ k_1,\cdots, k_m}  \mu_1\cdots \mu_m.
+\eeqn
+
+This interaction is extremely natural from the point of view of string field theory.
+Indeed, the B-model localizes to the space of constant maps into $X$, which factors as a product of $\overline{\cM}_{0,m}\times X$.
+This is in keeping with finding an interaction that factors as an integral over $X$ times an integral over $\overline{\cM}_{0,m}$.
+
+In \cite{BCOV} the authors show that the above interaction satisfies the classical master equation.
+Moreover, they show that the $L_\infty$ structure determined by the above action is equivalent to a natural dgla structure on the complex of fields with Lie bracket given by the Schouten bracket.
+Explicitly, the equivalence is given by the transcendental automorphism
+\[
+\Sigma \mapsto [u(\exp (\Sigma/u)-1)]_+
+\]
+where $[-]_+$ denotes projection onto positive powers of $u$.
 \parsec[s:minimalks]
 
-%define minimal ks
+Recall we observed in \ref[s:poisson] that the majority of fields pair to zero under the Poisson tensor.
+Physically these correspond to closed string fields that do not propogate.
+In the supergravity approximation, the fields that survive are those closed string fields that propogate.
+In terms of our description of closed string field theory in terms of Kodaira-Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor.
+This is referred to as minimal Kodaira-Spencer theory.
+
+The fields of minimal Kodaira-Spencer theory are given by the subcomplex of \label{eqn:ks1}
+\beqn
+\left (\bigoplus_{i+j\leq d -1}u^i\PV^{j,\bu}(X)[2], \dbar + u \div\right).
+\eeqn
+ It is easy to see that there is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map.
+There is a natural action functional given by pulling back the Kodaira-Spencer action.
 
@@
 The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.
-
-\brian{I've commented this out below, since we should just introduce minimal BCOV in general up above}
-
-%Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory.
-Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.
 

### 2021-10-13 dimred.tex
ks merge

--- 2021-09-28 dimred.tex
@@
 \section{Dimensional reduction and 10-dimensional supergravity}
+\label{sec:dimred}
 
@@
 \subsection{Reduction to IIA supergravity}
+\label{s:su4red}
 
@@
 
-\parsec[sec:dimred]
+\parsec[-]
 
@@
 
-To this end, we consider placing 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
+We consider placing twisted 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
 In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.
+Our 11-dimensional theory on such manifolds fits nicely into the formalism of \cite{BY,Eugene} in that it is topological in the direction transverse to the boundary.
 
@@
 
-In \cite{?} an explicit model has been given for the theory compactified along the slab for theories which are topological in the direction normal to the boundary.
-The fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
+An important thing to note is that the fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
 \[
@@
 \]
+To compute this derived intersection we must suitably resolve the boundary conditions.
 
@@
 \begin{itemize}
-\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate fields $\eta, B_{grav}$,
-\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate field $B$,
-\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate field $\psi$.
+\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate BV fields $\eta, B_{grav}$,
+\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate BV field $B$,
+\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate BV field $\psi$.
 \end{itemize}
@@
 
-Denote the full de Rham cohomology of $X$ by
+Consider the full de Rham cohomology of $X$ by
 \[
-\cA(X) = H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
+H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
 \]
@@
 The Poisson bracket $\{-,-,\}$ associated to the standard holomorphic symplectic structure on $\CC^2$ endows $\cO(\CC^2)$ with the structure of a Lie algebra. 
-In particular, we can tensor $\cO(\CC^2)$ with $\cA_X$ to obtain the structure of a graded Lie algebra on $\cA(X) \otimes \cO(\CC^2)$.
+In particular, we can tensor $\cO(\CC^2)$ with $H^\bu (X, \Omega^\bu)$ to obtain the structure of a graded Lie algebra on 
+\[
+H^\bu (X, \Omega^\bu) \otimes \cO(\CC^2) .
+\]
+Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$.
 
-The global symmetry algebra of the compactified theory is a deformation of this graded Lie algebra. 
-Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$. 
-The deformation of $\cA(X) \otimes \cO(\CC^2)$ introduces the following Lie bracket 
+The global symmetry algebra of the compactified theory along the Calabi--Yau three-fold $X$ is equivalent to a deformation of this graded Lie algebra. 
+The deformation introduces the following Lie bracket 
 \[
@@
 
-First, let's compute the global symmetry algebra of the twist of the pure gravity theory on $\CC^2 \times \RR$. 
-This arises from terms in the BV action \eqref{eqn:5daction} involving only $\alpha, \eta, A_{grav}$, and $B_{grav}$.
-
-The underlying graded vector space of the resulting Lie algebra is equivalent to
-\[
-\cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} .
-\]
-The non trivial Lie brackets are
+%\begin{proof}
+%The computation of the global symmetry algebra of the 5-dimensional theory is very similar to the computation in the 11-dimensional theory.
+%In terms of the de Rham cohomology, the generators of the linearized cohomology of the space of fields read:
+%\begin{itemize}
+%\item a holomorphic function $\alpha(z_1,z_2) \in H^0(X, \Omega^0) \otimes \cO(\CC^2)$.
+%\item a 
+%
+%First, let's compute the global symmetry algebra of the twist of the pure gravity theory on $\CC^2 \times \RR$. 
+%This arises from terms in the BV action \eqref{eqn:5daction} involving only $\alpha, \eta, A_{grav}$, and $B_{grav}$. 
+%
+%The underlying graded vector space of the resulting Lie algebra is equivalent to
+%\[
+%\cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} .
+%\]
+%The non trivial Lie brackets are
 %\begin{multline}
@@
 %\end{multline}
-\begin{align*}
-[\alpha, \alpha' + \eta + A_{grav} + B_{grav}] & = \{\alpha,  \alpha'\} + \{\alpha, \eta\} + \{\alpha, A_{grav}\} + \{\alpha, B_{grav}\} \\ & \in \cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} \\
-[B_{grav}, B'_{grav}] & = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
-\end{align*}
-Denote this Lie algebra by $\fg_{grav}$.
-
-The contribution of the vector and hypermultiplets form a module for $\fg_{grav}$. 
-As a graded vector space, this module is
-\[
-M_X = \cO(\CC^2) \otimes H^{1}(X, \Omega^1_X)_\perp [-1] \oplus \cO(\CC^2) \otimes 
-\]
+%\begin{align*}
+%[\alpha, \alpha' + \eta + A_{grav} + B_{grav}] & = \{\alpha,  \alpha'\} + \{\alpha, \eta\} + \{\alpha, A_{grav}\} + \{\alpha, B_{grav}\} \\ & \in \cO(\CC^2)_\alpha \oplus \cO(\CC^2)_\eta \oplus \cO(\CC^2)_{A_{grav}} \oplus \cO(\CC^2)_{B_{grav}} \\
+%[B_{grav}, B'_{grav}] & = \{B_{grav}, B'_{grav}\} \in \cO(\CC^2)_{A_{grav}} .
+%\end{align*}
+%Denote this Lie algebra by $\fg_{grav}$. 
+%
+%The contribution of the vector and hypermultiplets form a module for $\fg_{grav}$. 
+%As a graded vector space, this module is
+%\[
+%M_X = \cO(\CC^2) \otimes H^{1}(X, \Omega^1_X)_\perp [-1] \oplus \cO(\CC^2) \otimes 
+%\]
+%\brian{incomplete}
 
 \subsection{The $SU(5)$ twist of type IIA supergravity}
+\label{s:su5IIA}
 
@@
 
+We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
+The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}.
+
+A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
+In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following.
+
+\begin{prop}
+As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
+
+\parsec[]
+
 The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the 11-dimensional theory. 

### 2021-10-14 nonmin.tex

@@
 \[
-\dbar A + \d_{\RR^7} A + \partial_{z} A \wedge \partial_{w} A = 0 .
+\dbar A + \d_{\RR^7} A + \partial_{z_1} A \wedge \partial_{z_2} A = 0 .
 \]
@@
 \begin{thm}
+\label{thm:nonmin}
 The non-minimal twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
@@
 
-\parsec[sec:indexcheck]
+\subsection{Index matching}
+\label{sec:indexcheck}
 
 As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G2\times SU(2)$ twist.
+\brian{If we are going to say G2 we need to explain how G2 arises.
+I've been calling it the non minimal twist.}
 We will find that the local character of the latter agrees with a specialization of the local character computed in proposition \ref{prop:locchar}
@@
 According to the embedding in \S \ref{s:residual} this is the $\gamma$-field 
-\[
+\beqn\label{eqn:gammanm}
 \gamma_{nm} = \frac12 (z_1 \d z_2 - z_2 \d z_1) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) 
-\]
+\eeqn
 Notice that $\del \gamma_{nm} = \d z_1 \wedge \d z_2$ as desired.
@@
 This is the cocycle defining \eqref{eqn:centralvect}, as desired. 
-\end{proof}
+\end{proof}.
 
@@
 
+\subsection{The non-minimal twist of the 11-dimensional theory}
+
+Now, we turn to deducing the action function of the non-minimal twist and hence the proof of Theorem \ref{thm:nonmin}. 
+We will show that the eleven-dimensional theory on $\CC^5 \times \RR$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma_{nm}$ \eqref{eqn:gammanm} is equivalent to a theory with a purely Chern--Simons-like action functional that we referred to in the introduction to this section.
+
+Poisson Chern--Siimons theory is defined on any manifold of the form
+\[
+Z \times M
+\]
+where $Z$ is a hyper K\"ahler surface and $M$ is a smooth manifold of real dimension seven. 
+The fundamental field of the theory is  
+\[
+\alpha \in \Pi \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(M)  .
+\]
+Just in our original 11-dimensional theory, this theory is also only $\ZZ/2$ graded.
+
+The holomorphic symplectic form $\omega_Z^{2,0}$ on $Z$ induces a Poisson bracket define on all Dolbeault forms $\Omega^{0,\bu}(Z)$ which we denote by $\{-,-\}_{pb}$. 
+In local Darboux coordinates $(z_1,z_2)$, this bracket reads
+\[
+\{\alpha^I (z,\zbar) \d \zbar_I , \alpha'^J (z,\zbar) \d \zbar_J\}_{pb} = (\partial_{z_1} \alpha^I \partial_{z_2} \alpha^J \pm \partial_{z_2} \alpha^I \partial_{z_1} \alpha^J) \d \zbar_I \wedge \d \zbar_J .
+\]
+The action functional of Poisson Chern--Simons theory is 
+\beqn\label{eqn:pcsaction}
+    \frac12 \int_{Z \times M} (\alpha \wedge \d\alpha) \wedge \omega^{2,0}_Z  + \frac16 \int_{Z\times M} \alpha \wedge \{\alpha, \alpha\}_{pb} \wedge \omega^{2,0}_Z
+\eeqn
+where $\{-,-\}$ is the Poisson bracket induced from the symplectic form $\omega_Z$ on $Z$.
+
+For simplicity, we will work only on flat space $\CC^5 \times \RR = \CC^2_z \times (\CC^3_w \times \RR)$, where we view $Z = \CC^2_z$ as a hyper K\"ahler manifold with its standard holomorphic symplectic form $\omega^{2,0} = \d^2 z$.
+
+We will decompose the fields according to these coordinates. 
+For example, we decompose the $\mu$-field as $\mu = \mu_z + \mu_w$ where
+\begin{align*}
+\mu_z  &\in \PV^{1,\bu}(\CC^2_z) \otimes \PV^{0,\bu}(\CC^3_w) \otimes \Omega^\bu(\RR) \\
+\mu_w & \in \PV^{0,\bu}(\CC^2_z) \otimes \PV^{1,\bu}(\CC^3_w) \otimes \Omega^\bu(\RR)  .
+\end{align*}
+and similarly $\gamma = \gamma_z + \gamma_w$. 
+We will also use the notation $\del^z$ for the holomorphic de Rham differential along $\CC_z^2$ and similarly $\del^w$ for the holomorphic de Rham differential along $\CC^3_w$.
+
+To twist, we expand near the background where the field $\gamma_z$ takes value $\gamma_{nm}$ as in \eqref{eqn:gammanm}. 
+This will generate new kinetic and interacting terms. 
+%which we can extract by inserting a formal parameter $\delta$ and expressing the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.
+
+There are two types of interactions in the original theory.
+The first is
+\begin{equation}\label{eqn:int1}
+  \frac12 \int_{\CC^2 \times \CC^3 \times \RR} \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\d^2 z \wedge \d^3 w)
+\end{equation}
+and the second is
+\begin{equation} \label{eqn:int2}
+  \frac16\int_{\CC^2 \times \CC^3 \times \RR} \gamma \partial \gamma \partial \gamma .
+\end{equation}
+
+%We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.\brian{there might be some factors I'm being sloppy with here}
+Expanding \eqref{eqn:int1} around the background where $\gamma$ takes value $\gamma_{nm}$, we obtain,
+%\[
+%  \frac12 \int \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_W) + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\omega_Z \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_W) .
+%\]
+%Here, we have used the equation of motion $\partial \gamma^{1,0} = \Omega_Z$.
+%It will be convenient to further expand this into the components $\mu_W, \mu_Y, \gamma_W, \gamma_Y$:
+\begin{multline}
+ \int \frac{1}{1-\nu} \left(\frac12 \del^w \gamma_w \vee \mu_w^2  + \del^z \gamma_w \vee \mu_w \mu_z + \del^w \gamma_z \vee \mu_w\mu_z + \frac12 \del^z \gamma_z \vee \mu_z^2 \right) \wedge (\d^2 z \wedge \d^3 w)
+ \\
+  + \frac{1}{2} \int \frac{1}{1-\nu} \left(\d^2 z \vee \mu_z^2 \right) \wedge (\d^2 z \wedge \d^3 w) .
+  \label{eqn:delta1}
+\end{multline}
+
+We similarly expand (\ref{eqn:int2}),
+%\[
+%  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \omega_Z .
+%\]
+%Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
+%Again, we further expand this into holomorphic components along $X,Z$:
+\beqn
+\frac16 \int \left(\gamma_w \partial^z \gamma_w \partial^z \gamma_w +\gamma_w \partial^w \gamma_w \partial^z \gamma_z +  \gamma_w \partial^w \gamma_z \partial^w \gamma_z \right) + \frac{1}{2} \int \left(\gamma_w \partial^w \gamma_w \right) \wedge \d^2 z
+\label{eqn:delta2}
+\eeqn
+
+The new terms in the non-minimally twisted linearized BRST differential arise from the quadratic terms in the action in Equations \eqref{eqn:delta1} and \eqref{eqn:delta2}:
+\begin{equation}\label{eqn:newterms}
+  \frac{1}{2} \int (\d^2 z \vee \mu_z^2) \wedge (\d^2 z \wedge \d^3 w) + \frac{1}{2} \int \left(\gamma_w \wedge \partial^w \gamma_w \right) \wedge \d^2 z .
+\end{equation}
+The non-minimally twisted linear BRST complex thus takes the form
+\[
+  \begin{tikzcd}
+  & \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_W \ar[dr, "\div^z"] \ar[dashed, rounded corners, to path={ -- ([yshift=-2ex]\tikztostart.west) |- ([xshift=-1.5ex]\tikztotarget.west) -- (\tikztotarget)}, dddddr]\\
+  & & \PV^{0,\bu}_Z \hotimes \PV^{0,\bu}_W \\
+ & \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \ar[ur, "\div^w"'] & \\
+\;_{\cong}  & & \Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_W \ar[ul, dashed, bend left = 10, "\Omega^{-1}_W \partial^w"]\\
+ & \Omega^{0,\bu}_Z \hotimes \Omega^{0,\bu}_W \ar[ur, "\partial^w"] \ar[dr,"\partial^z"'] \\
+  & & \Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_W
+  %\ar[uuuuul, start anchor =  {[yshift = 0ex, xshift=0ex]}, end anchor = {[yshift=1.0ex, xshift=-5ex]}, bend left = 90, dotted] .
+  \end{tikzcd}
+\]
+Here, we write $Z = \CC^2_z$ and $X = \CC^3_w$ for notational simplicity.
+
+Here, the dashed arrow along the outside of the diagram corresponds to the BV antibracket with the first term in (\ref{eqn:newterms}).
+It is given by the isomorphism 
+\[
+\Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_W \xto{\omega^{2,0}_Z \otimes \id} \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_W
+\]
+induced holomorphic symplectic form on $Z$. 
+The other dashed arrow corresponds to the BV antibracket with the second term in (\ref{eqn:newterms}).
+It is given by the composition
+\[
+\Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_W \xto{\id \otimes \del^w} \Omega^{0,\bu}_Z \hotimes \Omega^{2,\bu}_W \xto{\id \otimes \Omega_W} \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_W
+\]
+given by applying the holomorphic de Rham operator along $X$ followed by contracting with the inverse holomorphic volume form along $X$. 
 %\brian{introduce PCS}
@@
 %\]
+
+We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
+Consider the complex
+\beqn
+\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L 
+%[-k] 
+\eeqn
+which is equipped with the differential $\dbar^z + \dbar^w + \del^w + \d_{\RR}$. 
+Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side.
+
+There is a map of linear BRST complexes from this one to the original one defined by the following equations 
+\begin{multline}
+\mu_z = (\del_{z_1} \wedge \del_{z_2}) \vee \del^z \alpha^0, \quad \mu_w = (\del_{w_1} \wedge \del_{w_2} \wedge \del_{w_3}) \vee \alpha^2, \quad \nu = \til{\alpha}^3 \\
+\beta = \alpha^0 , \quad \gamma_w = \alpha^1 , \quad \gamma_z = 0 .
+\label{eqn:g2map}
+\end{multline}
+In the above equation we have introduced the notation $\til{\alpha}^3 = \Omega_X^{-1} \vee \alpha^3$.
+
+The restriction of the kinetic terms $\int \gamma (\dbar + \d_{\RR}) \mu + \beta (\dbar + \d_{\RR}) \nu$ along \eqref{eqn:g2map} is
+\beqn\label{eqn:kin1}
+\int \sum_{k=0}^3 \alpha^k (\dbar + \d_{\RR}) \alpha^{3-k} 
+\eeqn
+The restriction of the kinetic term $\int \beta \div \mu$ along \eqref{eqn:g2map} is
+\beqn\label{eqn:kin2}
+\int \alpha^0 \del^w \alpha^2 . 
+\eeqn
+Finally, the restriction of the kinetic term $\gamma \del^w \gamma$ along \eqref{eqn:g2map} is 
+\beqn\label{eqn:kin3} 
+\int \frac12 \alpha^1 \del^w \alpha^1 . 
+\eeqn
+Together, \eqref{eqn:kin1}--\eqref{eqn:kin3} give the kinetic term in Poisson Chern--Simons theory.
+
+This shows that \eqref{eqn:g2map} is a map of linear BRST complexes.
+Applying the obvious contracting homotopy, we see that this map is a quasi-isomorphism.
+We will show that the full non-linear map intertwines the action functionals up to cohomologically exact terms, and hence defines an equivalence of BV theories.
+
+Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
+\begin{multline}
+\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
+\end{multline}
+
+\begin{multline}
+\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
++ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
+\end{multline}
+
+More invariantly, we can write the total BV action as
+\[
+\Tilde{I} = I_{CS} + I' 
+\]
+where $I_{CS} = \frac16 \int \alpha\{\alpha,\alpha\}$ and 
+\beqn
+I' = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha [\alpha \vee (\alpha \vee \Omega_X^{-1})] + \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} .
+\label{eqn:Iprime}
+\eeqn
+
+Consider the odd functional
+\[
+K = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] .
+\]
+
+\begin{lem}
+$Q K + \{I_{CS}, K\} = I'$ .
+\end{lem}
+
+The linear differential applied to $K$ is 
+\[
+\frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] \omega_Z .
+\]
+This is the first term in \eqref{eqn:Iprime}.
+
+Next, we compute
+\[
+\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
+\]
+which is the second term in \eqref{eqn:Iprime}.

### 2021-10-14 dimred.tex
merge refs

@@
 \subsection{Kodaira--Spencer theory}
+\label{s:BCOV}
 
@@
 \[
-(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \Sym^2 (\PV^{\bu,\bu}(X)[[u]][2])
-.\]
-Explicitly, the above kernel pairs against the dual to 
-\[
-\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}(X)[[u]][2]
+(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \left[\PV^{\bu,\bu}(X)\right]^{\hotimes 2} ,
 \]
- by the formula 
-\[
-\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
-\] 
-Here, the overlines denote the dual field in 
-\[
-(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
-\] 
-That is, further expanding the fields as 
-\[
-\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
-\] 
-the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.
+see \cite[{\S 1.4}]{CLbcov1}. 
+Here, we view the $\delta$-distribution as a polyvector field using the Calabi--Yau form. 
+Notice that the shifted Poisson tensor does not involve the parameter $u$ at all. 
+For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket. 
+%Explicitly, the above kernel pairs against the dual to 
+%\[
+%\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}%(X)[[u]][2]
+%\]
+% by the formula 
+%\[
+%\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
+%\] 
+%Here, the overlines denote the dual field in 
+%\[
+%(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
+%\] 
+%That is, further expanding the fields as 
+%\[
+%\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
+%\] 
+%the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.
 
@@
 
-There is a natural local interaction which equips the above cyclic cochain complex with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
+There is a natural local interaction which equips the complex \eqref{eqn:ks1} with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
 \beqn
-I_{BCOV}(\Sigma) = \int^\Omega \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} \int^\Omega\langle\Sigma^{\otimes n}\rangle_0
+I_{BCOV}(\Sigma) = {\rm Tr}_X \, \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} {\rm Tr}_X \, \langle\Sigma^{\otimes n}\rangle_0
 \eeqn
-
-where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
+where ${\rm Tr}_X \, \Phi = \int_X (\Phi \vee \Omega) \wedge \Omega$ and where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
 \beqn
@@
 where $[-]_+$ denotes projection onto positive powers of $u$.
+
 \parsec[s:minimalks]
 
-Recall we observed in \ref[s:poisson] that the majority of fields pair to zero under the Poisson tensor.
+We pointed out in \S\ref{s:poisson} that the majority of fields pair to zero under the Poisson tensor.
 Physically these correspond to closed string fields that do not propogate.
@@
 \eeqn
- It is easy to see that there is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map.
-There is a natural action functional given by pulling back the Kodaira-Spencer action.
+We observe that the original odd Poisson tensor lives in this subcomplex. 
+%here is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map. 
+There is a natural action functional given by restricting $I_{BCOV}$ to this space.
 
@@
 In principal, there is also a minimal, $SU(5)$ invariant, twist of type IIA supergravity but so far no description, even conjecturally, exists.
-We turn to this in Section \ref{sec:SU(5)twistIIA}.
+We turn to this in \S \ref{s:su5IIA}.
 
 Let $X$ be a Calabi-Yau manifold of complex dimension four. 
-The complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
-\brian{I have an issue with how this is organized}
+The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
 \beqn
@@
 \eeqn
-Denote this complex by $\cE_{mKS}(X)$. 
+Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
+%Denote this complex by $\cE_{mKS}(X)$. 
 The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.
 
-With this in hand the conjecture of \cite{CLSugra} takes the following form.
+With this in hand the conjecture of \cite{CLsugra} takes the following form.
 
@@
 Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA.
-However, as noted in \cite{CLSugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
+However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
 Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
@@
 
-Recall that the original fields of the IIA supergravity model on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
+The original space of fields of the twist of IIA supergravity on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
 In other words, it did not define a theory in the conventional BV formalism. 
@@
 \]
-This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$. \brian{finish}
+This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$.
 
@@
 \int^\Omega_{\CC^2 \times \RR} \left(\eta \dbar \alpha + B_{grav} \dbar A_{grav} + B \dbar A + \psi \dbar \chi \right) \\
-  \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
+  + \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
 + \frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
@@
 For any $k$, let $H^k(X, \Omega^k_X)_\perp$ denote the cohomology of the primitive elements.
-\brian{good notation?}
 
@@
 
-\parsec[]
-
-We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
-The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}.
-
-A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
-In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following.
-
-\begin{prop}
-As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
+%\parsec[]
+%
+%
+%We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
+%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
+%
+%A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
+%In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following. 
+%
+%\begin{prop}
+%As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
+%\end{prop}
 

### 2021-10-14 intro.tex
merge refs

@@
 In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
+\brian{also reference fabian and richard}
 The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
@@
 \[
-X \times L
+X \times S
 \]
-where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented real one-dimensional manifold. 
+where $X$ is a Calabi--Yau five-fold and $S$ is a smooth oriented real one-dimensional manifold. 
 The theory is of a holomorphic gravitational flavor as it describes ``partial'' deformations of complex structures along $X$. 
@@
 \[
-\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(L) 
+\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
 \]
@@
 \[
-\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(L), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(L) .
+\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(S), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(S) .
 \]
@@
 
-There is a background where the equations of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields in our 11-dimensional theory read
+There is a background where the equation of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields reads
 \begin{align*}
 \dbar \mu + \frac12 [\mu, \mu] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
-(\dbar + \mu) \gamma^{1,0} = 
-(\dbar + \mu) \gamma^{1,2} & = 0 \\
-\div \mu & = 0 \\
-\d_L \mu = \d_L \gamma^{1,0} = \d_L \gamma^{1,2} = & = 0 .
+%(\dbar + \mu) \gamma^{1,0} = 
+%(\dbar + \mu) \gamma^{1,2} & = 0 
+%\\
+%\div \mu & = 0 \\
+%\d_S \mu = \d_S \gamma^{1,0} = \d_S \gamma^{1,2} = & = 0 .
 \end{align*}
-In the last line $\d_L$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
+Additionally, there are the conditions that $\mu$ preserve the holomorphic volume form on $X$ and that all fields are locally constant along the topological direction $S$.  
+%In the last line $\d_S$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
 Notice that were it not for the presence of the last term in the first equation then this would be the integrability equation for $\mu$ to determines a complex structure on $X$.
-The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
-Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.
+%The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
+%Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.
 
 If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
-In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times L$ which further preserves the holomorphic volume form along the leaves.
+In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
 We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
@@
 
+In particular, correlation functions involving observables of the 11-dimensional theory will be constrained by the infinite-dimensional symmetry algebra $E(5,10)$. 
 Given our main conjecture that the interacting 11-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.

### 2021-10-14 matrix.tex
merge refs

@@
 
-Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacClass,KR} called $E(5,10)$.
+Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacBible,KacE510} called $E(5,10)$.
 We recall the definition below.

### 2021-10-14 intro.tex
introes

--- 2021-10-06 intro.tex
@@
 
-The twist of a supersymmetric field theory was first studied by Witten \cite{WittenTwist}.
-Later, the notion was generalized and developed mathematically by Costello \cite{CostelloHol}. 
-Generally speaking, the twist of a supersymmetric field theory is a systematic way of taking the invariants of a theory with respect to a fixed supercharge which squares to zero. 
-In a supergravity theory, supertranslations are already gauged and so this notion of twisting is {\em a priori} not a sensible thing to do.
+Twists of supersymmetric field theories have been a subject of active and fruitful study for many years. 
+The notion of twisting was introduced by Witten and dates back to the first example~\cite{WittenTwist}, in which a topological field theory related to Donaldson invariants of four-manifolds was constructed as a twist of four-dimensional $\N=2$ supersymmetric gauge theory.
+Shortly afterwards (thirty years ago), the field had expanded to include a diverse set of examples related to topological field theory~\cite{BlauThompson}.
 
-In their seminal paper, Costello and Li gave a definition of twisted supergravity: it is supergravity in a background where the bosonic ghost takes a nonzero value \cite{CLsugra}.
-They have provided conjectural descriptions of many examples of 10-dimensional theories of supergravity, and have used these descriptions to rigorously construct quantizations of open-closed string field theories \cite{CLbcov1,CLtypeI}.
-A very active and promising direction is to use these twisted 10-dimensional models to formulate twisted versions of holography \cite{Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant}.
+For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
+From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge.
+This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.
+The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}.
+The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even.
+As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially.
+Other twists can be understood as further twists of this holomorphic theory.
+The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}.
+(Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)
 
-In this paper, we provide perturbative descriptions of all twists of 11-dimensional supergravity. 
-By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
+In a supergravity theory, local supersymmetry is already gauged, so that the standard notion of twisting is {\em a priori} not a sensible operation.
+Twisted supergravity thus needs to be  understood differently.
+In their seminal paper~\cite{CLsugra}, Costello and Li gave a definition of twisted supergravity: it is supergravity in a background where the bosonic ghost field representing a twisting supercharge takes a nonzero value.
+Twisting a supersymmetric field theory, in the classical sense, can then be  understood as coupling the theory to supergravity and placing it in such a background.
+
+Using ideas related to string field theory and the topological B-model, Costello and Li provided conjectural descriptions of many examples of ten-dimensional theories of twisted supergravity.
+They used these descriptions to rigorously construct quantizations of open-closed string field theories~\cite{CLbcov1,CLtypeI}.
+A very active and promising direction of current research uses these twisted ten-dimensional models to formulate twisted versions of holography; see~\cite{Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant}, for example.
+
+In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity. 
+%By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
 Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 

### 2021-10-14 dfn.tex

@@
 
-The kernel of this map resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
-In fact, we can form the complex 
+The resulting complex of sheaves
 \beqn\label{eqn:cplx1}
@@
 \ul{0} & \ul{1} \\
-\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) .
+\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) ,
 \end{tikzcd}
 \eeqn
+resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
 The $\dbar$ operator, as always, is left implicit. 
-By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
+%By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
 
@@
 
-\subsection{Equations of motion} \label{s:eom}
+\subsection{Equations of motion of the component fields} \label{s:components}
 
@@
 where now $[-,-]$ stands for the Schouten bracket.
+
+\brian{finish}
 

### 2021-10-14 suco.tex
merge

@@
 \section{Twisted supergavity on AdS space}
+\label{sec:ads}
 
@@
 This coupling is justified by comparison with the physical theory and by dimensional reduction. 
-Indeed, as discussed in section \surya{}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
+Indeed, as discussed in section \ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
 Thus, the proposal mirrors electric couplings of $M2$ branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.
@@
 Moreover, reducing on a circle transverse to the $M2$ brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$.
-As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by
+As is shown in \cite{CLsugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by
 \[
@@
 \[
- F_{M2} = \# \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
+ F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
 \]
-Then, the background where $\mu = N F_{M2}$ 
-satisfies the above equations of motion
+Then, the background where $\mu = N F_{M2}$ and $\gamma = 0$
+satisfies the above equations of motion in the presence of a stack of $N$ $M2$ branes:
 \begin{align*}
@@
 Upon specializing $\gamma = 0$, the last term in the first equation above vanishes.
-The equation $\dbar F_{\rm{AdS}_4 \times S^7} = \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$.
-It is clear that $\div F_{\rm{AdS}_4 \times S^7} = 0$ and 
+The equation $\dbar F_{M2} = \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$.
+It is clear that $\div F_{M2} = 0$ and 
 \[
-[F_{\rm{AdS}_4 \times S^7}, F_{\rm{AdS}_4 \times S^7}] = 0
+[F_{M2}, F_{M2}] = 0
 \] 
@@
 \[
-(\wedge^2 \CC^4)_{+1} \otimes (\wedge^2 \CC^4)_{-1} .
+(\wedge^2 \CC^4)_{+1} \oplus (\wedge^2 \CC^4)_{-1} .
 \]
@@
 \[
-F_{M5} = \# N \frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
+F_{M5} = \frac{1}{(2\pi i)^3} \frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
 \]
@@
 %satisfies $\del \til F = F$. 
-Then, $F$ satisfies the $F = \del\gamma$-equations of motion in the presence of a stack of $N$ $M5$ branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
+Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ $M5$ branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
 \begin{align*}
-\dbar F + \d_{\RR} F & = N \delta_{w_1=w_2=t=0}  \\ 
-F \wedge F & = 0 .
+\dbar (NF_{M5}) + \d_{\RR} (NF_{M5}) & = N \delta_{w_1=w_2=t=0}  \\ 
+(NF_{M5}) \wedge (NF_{M5}) & = 0 .
 \end{align*}
@@
 \[
-\oint_{S^4} F = N 
+\oint_{S^4} N F = N 
 \]
@@
 
-\parsec[]
+\parsec[s:m5embedding]
 
@@
 \item 
-The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
+The fermionic summand $L \otimes R$ embeds into closed two-forms as
 \[
@@
 \item 
-The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
+The fermionic summand $\wedge^2 L \otimes R$ embeds into closed two-forms as
 \[
@@
 \label{prop:brads7}
-There exists $N$-dependent corrections to the embedding $i_{M5}$ which is compatible with the modified BRST differential $\delta^{(1)} + [N F,-]$. 
-Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F,-]$.
+There exists $N$-dependent corrections to the embedding $i_{M5}$ which is compatible with the modified BRST differential $\delta^{(1)} + [N F_{M5},-]$. 
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F_{M5},-]$.
 \end{prop}
@@
 
-The proof of the above proposition follows from an indirect cohomological argument. 
+The proof of the above proposition follows from another indirect cohomological argument. 
 Before getting to the proof, we introduce the relevant cohomology.

### 2021-10-14 intro.tex
stuff

@@
 The twist is $SU(5)$ invariant and involves a fixed choice of a Calabi--Yau form on $\CC^5$. 
-\item The non minimal twist. 
+\item The non-minimal twist. 
 The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
@@
 
-In \cite{SWspinor}, the last two authors used the formalism of pure spinors to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space.
-\brian{also reference fabian and richard}
-The resulting theory is $\ZZ/2$ graded which is inherited from the ghost grading and parity in the original, untwisted, 11-dimensional theory.
+In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space, following work of Cederwall~\cite{Ced-towards,Ced-11d}.
+In fact, the result of that paper shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
+(In separate work~\cite{EagerHahner}, the free-field limit of the non-minimal twist was derived from the component-field multiplet as used in the physics literature.)
+%\brian{also reference fabian and richard}
+The resulting theory is $\ZZ/2$ graded; the grading is inherited from the totalization of ghost number and intrinsic parity in the original, untwisted, eleven-dimensional theory.
 In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.

### 2021-10-14 intro.tex
merge

@@
 They used these descriptions to rigorously construct quantizations of open-closed string field theories~\cite{CLbcov1,CLtypeI}.
-A very active and promising direction of current research uses these twisted ten-dimensional models to formulate twisted versions of holography; see~\cite{Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant}, for example.
+A very active and promising direction of current research uses these twisted ten-dimensional models to formulate twisted versions of holography; see~\cite{CostelloM2, Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant, Gaiotto:2020vqj}, for example.
+In \cite{CostelloM5} supergravity in the $\Omega$-background has been introduced, and has been further studied in \cite{Gaiotto:2019wcc, Oh:2020hph, Oh:2021bwi}.
 
-In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity. 
+In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity (before turning on any $\Omega$-background).
 %By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
@@
 In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space, following work of Cederwall~\cite{Ced-towards,Ced-11d}.
-In fact, the result of that paper shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
+In fact, the result of \cite{SWspinor} shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
 (In separate work~\cite{EagerHahner}, the free-field limit of the non-minimal twist was derived from the component-field multiplet as used in the physics literature.)

### 2021-10-14 dfn.tex
eom

@@
 \]
-
 The resulting complex of sheaves
@@
 resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
-The $\dbar$ operator, as always, is left implicit. 
+The anti-holomorphic Dolbeault degrees and the $\dbar$ operator is left implicit. 
 %By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.
@@
 
-The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[??]{CG2}.
+The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[\S 3.1.3]{CG2}.
 This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
@@
 The natural pairing between $\PV^i(X;S)$ and~$\Omega^i(X;S)$ is of degree $-\dim_\C(X) -\dim_\R(S)$. 
-As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
+As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a degree $(-1)$ pairing, provided that we choose the shift to be given by
 \deq{
@@
 }
+The pairing is defined by the formula 
+\[
+\int^\Omega_{X \times S} \mu \vee \gamma + \int^\Omega_{X \times S} \nu \beta 
+\]
+where $\int^\Omega_{X \times S} \alpha = \int_{X \times S} \alpha \wedge \Omega$.
 
@@
 \deq{
-  S_{BF,0} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu + \frac{1}{2} [\mu,\mu] \vee \gamma +  [\mu,\nu] \beta .
+  S_{BF,0} =  \int^\Omega \bigg[\beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu +  \frac{1}{2} [\mu,\mu] \vee \gamma +  [\mu,\nu] \beta \bigg] .
 }
@@
 The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(S)$ is non polynomial. 
-(In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} 
+In fact, it is related to the BCOV action functional via dimensional reduction, see \S \ref{sec:dimred}.
 Explicitly, this action functional is
 \deq{
-  S_{BF,\infty} =  \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma .
+  S_{BF,\infty} =  \int^\Omega \bigg[ \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma \bigg] .
 }
@@
 We proceed to show that $S_{BF,\infty} + g J$ solves the classical master equation.
+For notational simplicity we will omit the integral symbol $\int^\Omega$.
+
 By apparent field type reasons, the equation \eqref{eq:2cond} is equivalent to the following two equations
@@
 
-\brian{finish}
+To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where the $(0,1)$ Dolbeault part of $\gamma$ is zero $\gamma^{1;0} = 0$. 
+Then, up the term involving 
+\[
+\alpha \define \del \gamma^{0;0},
+\]
+we find precisely the integrability equation for the complex structure determined by Beltrami differential $\mu^{1;0} \in \PV^{1,1} \otimes \Omega^0$. 
+If $\dbar \alpha = 0$, the holomorphic two-form $\alpha \in \Omega^{2,hol}(X)$ defines a map of sheaves
+\[
+\Omega^{2,hol}_X \xto{\wedge \alpha} \Omega^{4,hol}_X \cong_\Omega \cT^{hol}_X
+\]
+where $\cT^{hol}_X$ denotes the sheaf of holomorphic vector fields and the last isomorphism uses the Calabi--Yau form $\Omega$ on $X$.  
+The image of $\Omega^{2,hol}_X$ defines a subsheaf $\cF_{\alpha} \subset \cT^{hol}_X$. 
+Since $\del \alpha = 0$, this subsheaf is automatically integrable and hence determines a foliation.
 
+Summarizing, see that there is a field configuration where the Beltrami diffrential $\xi = \mu^{1;0} \in \Omega^{0,1}(X, \T_X)$ satisfies the modified integrability condition
+\[
+\dbar \xi + \frac12  [\xi , \xi] = \alpha \vee \rho
+\]
+for some $\rho \in \PV^{2,2} (X)$. 
+In other words, $\xi$ defines an integrable complex structure deformation along the leaf space associated to the foliation $\cF_\alpha$. 
+We leave a more complete exploration of the moduli space of solutions of the equations of motion for future work.
+
+In \cite{SWspinor}, the second two authors showed that the free-limit of the minimal twist of 11-dimensional supergravity agrees with the free-limit of the 11-dimensional theory that we have introduced here.
+Given this result, we can recognize many fields in the twisted theory as components of the physical fields of supergravity which remain after we twist.
+
+\begin{itemize}
+\item 
+The following components of $\mu$:
+\begin{align*}
+\mu^{1;0} & = \mu^j_i(z,\zbar,t) \d \zbar_j \partial_{z_i} \\
+\mu^{0;1} & = \mu^t_i (z,\zbar,t) \d t \partial_{z_i}
+\end{align*}
+comprise components of the metric which remain after the twist. 
+The components 
+\[
+\mu^{0;0} = \mu_i (z,\zbar,t) \partial_{z_i} 
+\]
+comprise the ghosts for infinitesimal diffeomorphisms. 
+\item 
+The following three-form fields
+\begin{multline}
+\beta^{3;0} = \beta^{ijk} (z,\zbar,t) \d \zbar_i \d \zbar_j \d \zbar_k , \quad \beta^{2;1} = \beta^{ij}_t (z,\zbar,t) \d \zbar_i \d \zbar_j \d t \\
+\gamma^{2;0} = \gamma^{ijk} (z,\zbar,t) \d z_i \d \zbar_j \d \zbar_k , \quad \gamma^{1;1} = \gamma^{ij}_t (z,\zbar,t) \d z_i \d \zbar_j \d t .
+\end{multline} 
+comprise components of the supergravity $C$-field which remain after the twist. 
+The two-form fields $\beta^{2;0}, \beta^{1;1}, \gamma^{1;0}, \gamma^{0;1}$, the one-form fields $\beta^{1;0}, \beta^{0;1}$, and the zero-form field $\beta^{0;0}$ is what remains of the ghost system (ghosts, ghosts for ghosts, etc.) for the supergravity $C$-field.
+\end{itemize}
 %The most geometrically relevant component is the case where 

### 2021-10-15 dfn.tex
merge

@@
 The contribution from the remaining BF action takes the form
-\begin{multline}
-    \left\{ \frac12 \frac{1}{1-\nu} \del\gamma \vee \mu^2, \frac16 \gamma \wedge \del\gamma \wedge \del \gamma \right\} \\ = \frac12 \frac{1}{1-\nu} \bigg[ (\del\gamma\vee\mu) \wedge \del\gamma \wedge \del \gamma \pm \del\gamma \wedge (\del\gamma\vee\mu) \wedge \del \gamma \pm \del\gamma \wedge \del \gamma \wedge (\del\gamma\vee\mu) \bigg].
-\end{multline}
+\[
+    \left\{ \frac12 \frac{1}{1-\nu} \del\gamma \vee \mu^2, \frac16 \gamma \wedge \del\gamma \wedge \del \gamma \right\} =\frac12 (\mu \vee \del \gamma) \wedge \del \gamma \wedge \del \gamma .
+\]
+
+    %\frac12 \frac{1}{1-\nu} \bigg[ (\del\gamma\vee\mu) \wedge \del\gamma \wedge \del \gamma \pm \del\gamma \wedge (\del\gamma\vee\mu) \wedge \del \gamma \pm \del\gamma \wedge \del \gamma \wedge (\del\gamma\vee\mu) \bigg].
+
 This expression is zero for symmetry reasons. 
 Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional which is cubic in this two-form. 
-We can ask whether such a  contraction exists just at the level of $\lie{sl}(5)$ representation theory by computing the decomposition of the two-form
-\ingmar{finish}
+We can ask whether such a contraction exists just at the level of $\lie{sl}(5)$ representation theory by computing the decomposition of the two-form.
 

### 2021-10-15 dfn.tex

@@
 }
-Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces the condition
+Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the pair of conditions
 \deq[eq:2cond]{
-  \{S_{BF},J\} + \frac12 \{J,J\} = 0.
+  \{S_{BF},J\} =  \{J,J\} = 0.
 }
@@
 
-By apparent field type reasons, the equation \eqref{eq:2cond} is equivalent to the following two equations
-\[
-\{S_{BF,\infty}, J\} = 0, \qquad \{J,J\} = 0.
-\] 
-It is furthermore immediate from the form of the BV bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field.
+%By apparent field type reasons, the equation \eqref{eq:2cond} is equivalent to the following two equations
+%\[
+%\{S_{BF,\infty}, J\} = 0, \qquad \{J,J\} = 0.
+%\]
 
+It is immediate from the form of the BV bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field. 
 It remains to check that $\{S_{BF,\infty},J\} = 0$. 
@@
 \]
-
     %\frac12 \frac{1}{1-\nu} \bigg[ (\del\gamma\vee\mu) \wedge \del\gamma \wedge \del \gamma \pm \del\gamma \wedge (\del\gamma\vee\mu) \wedge \del \gamma \pm \del\gamma \wedge \del \gamma \wedge (\del\gamma\vee\mu) \bigg].
-
 This expression is zero for symmetry reasons. 
 Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional which is cubic in this two-form.
-We can ask whether such a contraction exists just at the level of $\lie{sl}(5)$ representation theory by computing the decomposition of the two-form.
+We can ask whether such a  contraction exists just at the level of $\lie{sl}(5)$ representation theory.
+Let $\ydiagram{1}$ denote the fundamental representation of~$\lie{sl}(5)$, which we identify with constant one-forms.
+Since the term must be a scalar, the contraction $(\partial\gamma^3$ must sit in the fundamental representation again, since it is dual to a vector field.
+Computing the decomposition of the tensor cube of the two-form, we find
+\deq{
+  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}.
+}
+(In fact, the absence  of the relevant irreducible representation does not  even depend on the parity of the  field $\gamma$, since 
+  \deq{
+    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2};
+  }
+the  fundamental representation has symmetry type $\ydiagram{2,1}$.)
 

### 2021-10-15 dimred.tex
big merge

@@
 \parsec[s:poisson]
-The original action for Kodaira-Spencer theory posited by \cite{BCOV}\surya{which reference is BCOV} has a nonlocal kinetic term.
+The original action for Kodaira-Spencer theory posited by \cite{BCOV} has a nonlocal kinetic term.
 In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form.
@@
 \eeqn
+Denote this complex by $\cE_{mKS}(X)$. 
 Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
@@
 \begin{conj}
-The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields \[
-\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).\] 
+The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields 
+\beqn\label{eqn:IIAfields}. 
+\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).
+\eeqn
 The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
@@
 However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
-Since components of the $C$-field become components of $\gamma_{11d}$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
+We recalled in \S \ref{s:components} that components of the $C$-field become components of $\gamma_{11d}$ in $\cE$.
+This suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.
 
@@
 
-\brian{general background on susy. Why expect 5d $\cN=1$ susy}
+%\brian{general background on susy. Why expect 5d $\cN=1$ susy}
 
@@
 
-\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}
+%\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}
 

### 2021-10-15 intro.tex
big merge

@@
 
-\brian{Ingmar, maybe you can comment on the status of this conjecture.}
+%\brian{Ingmar, maybe you can comment on the status of this conjecture.}
 In this paper we will provide evidence for this conjecture on a variety of fronts. 
@@
 
-Finally, we describe the non minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
-We find a match with a con \brian{finish}
+Finally, we describe the non-minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
+This non-minimal twist is invariant for the group $G_2 \times SU(2)$. 
+We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in \cite{RY}. 
 %Surprisingly, at the twisted level these symmetries
+
+\subsection*{A geometric description of the model}
 
@@
 \]
-Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:component}.
+Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:components}.
 
@@
 In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
-We further unpack the equations of motion in other backgrounds in \S \ref{s:eom}.
+We further unpack the equations of motion in more general backgrounds in \S \ref{s:components}, but leave a complete study for future work.
 %The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
@@
 Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
-In Table \ref{tbl:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
+In Table \ref{table:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
 The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
@@
 \end{tabular}
+\caption{A summary of twists of 10-dimensional supergravity}
+\label{table:IIsugra}
 \end{table}
 
-In \S \ref{s:su4red} we will show that the reduction along a line of the form $\{0\} \times \RR \times \{0\} \CC^4 \times \CC^\times \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity.
+In \S \ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
 The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 

### 2021-10-15 susy.tex
merge refs
big merge

@@
 
-Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory \brian{good reference?}. 
+Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
 In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
@@
 Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-Such a supercharge defines the minimal twist of 11-dimensional supersymmetry. 
-\brian{cite \cite{SWspinor}}
+Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of 11-dimensional supersymmetry \cite{SWspinor}. 
 We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
@@
 
-In this section we compare to the work of \brian{Linfty refs}.
+In this section we compare to another description of the $M2$ brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
+Such central extensions were studied in the work \cite{BHsusyII, SSS, FSS} following \cite{CDF}.
+
 In these references, the algebra $\m2$ is defined as an $L_\infty$  
 central extension of $\lie{siso}_{11d}$. 
-
 Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
@@
 \]
-This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\ft_{11d})$. 
-In \cite{fiorenza2015super} it is shown that $\mu_2$ defines a nontrivial class in $H^4(\ft_{11d})$ so defines a one dimensional central extension of $\ft_{11d}$ as a lie 3-algebra.
-Instead of working with a one-dimensional central extension by $\C[2]$, we work with a central extension by the resolution $\Omega^\bullet(\R^{11})[2]$.
-There is a quasi-isomorphism $\clie^4(\ft_{11d})\to \clie^4(\ft_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\R^{11})[2]$-valued 2-cocycle we use.
+This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\lie{siso}_{11d})$. 
+This expression defines a nontrivial class in $H^4(\lie{siso}_{11d})$ so defines a one dimensional central extension of $\lie{siso}_{11d}$ as a Lie 3-algebra. 
+Instead of working with a one-dimensional central extension by $\CC[2]$, we work with a central extension by the resolution $\Omega^\bullet(\RR^{11})[2]$.
+There is a quasi-isomorphism $\clie^4(\lie{siso}_{11d})\to \clie^4(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\RR^{11})[2]$-valued two-cocycle we use.
 

### 2021-10-15 nonmin.tex
big merge
merge

@@
 In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.  
+This further twist is invariant for the group $G_2 \times SU(2)$ and is topological along seven directions, as opposed to just a single direction as in the $SU(5)$ twist.
 
@@
 
-As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G2\times SU(2)$ twist.
-\brian{If we are going to say G2 we need to explain how G2 arises.
+As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G_2\times SU(2)$ twist.
+%\brian{If we are going to say G2 we need to explain how G2 arises.
 I've been calling it the non minimal twist.}
@@
 \begin{prop}
-The  local character of the $G2\times SU(2)$ twist of 11d supergravity on flat space is given by
+The  local character of the $G_2\times SU(2)$-invariant twist of 11d supergravity on flat space is given by
 \[
@@
 
-Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
-\begin{multline}
-\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
-\end{multline}
-
-\begin{multline}
-\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
-+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
-\end{multline}
-
-More invariantly, we can write the total BV action as
-\[
-\Tilde{I} = I_{CS} + I' 
-\]
-where $I_{CS} = \frac16 \int \alpha\{\alpha,\alpha\}$ and 
-\beqn
-I' = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha [\alpha \vee (\alpha \vee \Omega_X^{-1})] + \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} .
-\label{eqn:Iprime}
-\eeqn
-
-Consider the odd functional
-\[
-K = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] .
-\]
-
-\begin{lem}
-$Q K + \{I_{CS}, K\} = I'$ .
-\end{lem}
-
-The linear differential applied to $K$ is 
-\[
-\frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] \omega_Z .
-\]
-This is the first term in \eqref{eqn:Iprime}.
-
-Next, we compute
-\[
-\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
-\]
-which is the second term in \eqref{eqn:Iprime}.
+%
+%Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
+%\begin{multline}
+%\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
+%\end{multline}
+%
+%\begin{multline}
+%\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
+%+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
+%\end{multline}
+%
+%More invariantly, we can write the total BV action as
+%\[
+%\Tilde{I} = I_{CS} + I' 
+%\]
+%where $I_{CS} = \frac16 \int \alpha\{\alpha,\alpha\}$ and 
+%\beqn
+%I' = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha [\alpha \vee (\alpha \vee \Omega_X^{-1})] + \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} .
+%\label{eqn:Iprime}
+%\eeqn
+%
+%Consider the odd functional
+%\[
+%K = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] .
+%\]
+%
+%\begin{lem}
+%$Q K + \{I_{CS}, K\} = I'$ .
+%\end{lem}
+%
+%The linear differential applied to $K$ is 
+%\[
+%\frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] \omega_Z .
+%\]
+%This is the first term in \eqref{eqn:Iprime}. 
+%
+%Next, we compute
+%\[
+%\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
+%\]
+%which is the second term in \eqref{eqn:Iprime}.

### 2021-10-15 suco.tex
merge

@@
 
-\brian{need to motivate osp}
+So far, we have mostly given evidence for the 11-dimensional theory as a twist of supergravity in a flat background. 
+We now turn to twisted versions of AdS backgrounds of 11-dimensional supergravity.
+
+In $M$-theory, AdS backgrounds arise from backreacting some number of branes. 
+For $M2$ branes, the backreacted geometry is ${\rm AdS}_4 \times S^7$.
+For the $M5$ branes, the backreacted geometry is ${\rm AdS}_7 \times S^4$.
+
+According to the AdS/CFT correspondence, supergravity on such backgrounds should be dual to the relevant worldvolume theory. 
+In this section, we do not directly refer to the worldvolume theories on the holomorphic twists of the $M2$ and $M5$ branes.
+Rather, we identify the fields sourcing the branes at the level of the twisted 11-dimensional theory.
+In turn, we give a proposal for the twisted AdS background. 
+We will show that the twist of the superconformal algebra is a global symmetry of this twisted background.
 
@@
 
-\begin{prop}
-The $Q$-cohomology of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-\end{prop}
+The complex form of the algebra of isometries for supergravity in both the ${\rm AdS}_4$ and ${\rm AdS}_7$ backgrounds is $\lie{osp}(8|2)$ (though, their real forms differ). 
+This agrees with the complex form of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra. 
+The bosonic part of this algebra is isomorphic to $\lie{so}(8) \oplus \lie{sp}(2) \cong \lie{so}(8) \oplus \lie{so}(5)$.
+
+The minimal supercharge $Q$ acting on 11-dimensional supersymmetry algebra is an element of this superconformal algebra. 
+In \cite{SWsuco2}, the second two authors show that the $Q$-cohomology is isomorphic to $\lie{osp}(6|1)$. 
+This super Lie algebra will play the role of the isometries in the twisted AdS background.
 
@@
 In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
-In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
+%In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 \[
-I_{M2}(\gamma) = N\int_{\C_z} \gamma
+I_{M2}(\gamma) = N\int_{\C_z} \gamma + \cdots
 \] 
-\brian{should we write $\cdots$ here? This is just the first-order piece.}
 which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
 Unlike the case of $M5$ branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
+We have only indicated the lowest order coupling, the $\cdots$ indicate higher order couplings which will explicitly involve the fields in the worldvolume theory.
 
@@
 \[
-I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma
+I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma + \cdots
 \] 
@@
 
-\brian{get the filtration straight}
+%\brian{get the filtration straight}
 
@@
 In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of 11-dimensional supergravity.
-In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
+
+%In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 
-In \cite{CLSugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
+In \cite{CLsugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
 \[
@@
 \]
-\brian{should we write $\cdots$ here? This is just the first-order piece.}
+Again, we have only explicitly indicated the first-order piece of the coupling.
 

### 2021-10-15 intro.tex
the bib is broken

@@
 From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge.
-This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.
+This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
 The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}.

### 2021-10-15 intro.tex
fix table, bib still fucked
intro

--- 2021-10-15 intro.tex
@@
 The resulting theory is $\ZZ/2$ graded; the grading is inherited from the totalization of ghost number and intrinsic parity in the original, untwisted, eleven-dimensional theory.
-In \S\ref{sec:dfn} we extend this free limit of the twist of 11-dimensional supergravity to a fully interacting theory in the Batalin--Vilkovisky (BV) formalism.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
+In \S\ref{sec:dfn} we introduce a full interacting theory in th Batalin--Vilkovisky (BV) formalism which has, as its free limit, the twist computed in \cite{SWspinor}.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
 All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
@@
 \begin{conj}
-The $11$-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge.
+The $11$-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{sec:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge.
 \end{conj}

### 2021-10-15 intro.tex

@@
 & SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
-\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
-\multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
-\end{tabular}
+\multicolumn{1}{|l|}{IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
+\multicolumn{1}{|l|}{IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
+\end{tabular} \smallskip
 \caption{A summary of twists of 10-dimensional supergravity}

### 2021-10-15 intro.tex
small typos

--- 2021-10-15 intro.tex
@@
 From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge.
-This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
+This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.
 The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}.
 The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even.
-As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially.
+As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lceil d/2\rceil$ of the translations act nontrivially.
 Other twists can be understood as further twists of this holomorphic theory.
@@
 & SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
-\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
+\multicolumn{1}{|l|}{Type IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ &  & $\RR^{10}_A$  \\ \hline
 \multicolumn{1}{|l|}{Type IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline

### 2021-10-15 intro.tex

--- 2021-10-15 intro.tex
@@
 The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even.
-As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially.
+As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lceil d/2\rceil$ of the translations act nontrivially.
 Other twists can be understood as further twists of this holomorphic theory.
@@
 Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
-In Table \ref{table:IIsugra}, we provide a summary of the conjectural twists of type IIA and type IIB supergravity. 
-The notation $\CC^n_B \times \RR^{2m}_A$ uses terminology from the topological string. 
-It means that the twist of supergravity we are considering arises from a certain subsector of a hybrid topological string which is the $B$-model into the Calabi--Yau manifold $\CC^n$ and the $A$-model into the symplectic manifold $\RR^{2m}$.
+In Table \ref{diagram}, we provide a summary of the comparisons with twists of supergravity in lower dimensions we perform.
+The squigly arrows denote further twists, and the solid arrows denote various kinds of reductions.
 
-\begin{table}[]
-\begin{tabular}{c|c|c|c|c|c|c|c|}
-\cline{2-7}
-& SU(5) twist & SU(4) twist & SU(3) twist & SU(2) twist & SU(1) twist & top twist  \\ \hline
-\multicolumn{1}{|l|}{IIA} & \S \ref{s:su5IIA} & $\CC^4_B \times \RR^2_A$ & & $\CC^2_B \times \RR^6_A$ & $\begin{matrix} \text{perturbatively} \\ \text{trivial} \end{matrix}$ & $\RR^{10}_A$  \\ \hline
-\multicolumn{1}{|l|}{IIB} & $\CC^5_B$ & & $\CC^3_B \times \RR^4_A$ & & $\CC_B \times \RR^8_A$ & \\ \hline
-\end{tabular} \smallskip
-\caption{A summary of twists of 10-dimensional supergravity}
-\label{table:IIsugra}
-\end{table}
+\begin{center}
+\begin{tikzcd}[row sep=large]
+                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
+ \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
+                                                                         &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &
+\end{tikzcd}
+\end{center}
+\label{diagram}
 
@@
 In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity.
+In \S \ref{s:Ired}, we show that the reduction along the interval $\{0\}\times [0,1]\subset \CC^5\times [0,1]$ with certain boundary conditions on the endpoints of the interval is equivalent to the twist of type I supergravity.
+We further observe in \S \ref{s:orbifold} that the twist of type I arises as the fixed points of a natural $\ZZ/2$ action on the minimal twist of IIA.
+Next, in \S \ref{s:CY3} we study the reduction along a Calabi-Yau 3 fold to obtain a conjectural description of the minimal twist of 5d $\cN=1$ supergravity.
+Finally, we show in \S \ref{s:nonmin} how the non-minimal twist of 11d supergravity arises as a further twist of our holomorphic twist.
 

### 2021-10-20 character.tex
char

\documentclass[11pt]{amsart}

\usepackage{macros-mtheory,amsaddr,tikz-feynman}

\addbibresource{references.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\subsection{Local character}

We consider the 11-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
On this background, the theory is manifestly $SU(5)$ invariant. 
In this section, we compute the corresponding character of the local operators at $0 \in \CC^5 \times \RR$.

The character is only sensitive to the free limit of the theory.
Furthermore, the linear BRST operator is an $SU(5)$-invariant deformation of the $(\dbar + \d_{\RR})$ operator. 
Therefore, to compute the character it suffices to compute the $SU(5)$-equivariant character of the $\dbar$-cohomology.

The solutions to the $(\dbar + \d_{\RR})$-equations of motion simply say that all fields are holomorphic along $\CC^5$ and constant along $\RR$. 
Thus, the solutions can be identified with 
\begin{align*}
\mu^{i}\partial_{z_i} & \in \Vect(\CC^5) \cong \oplus_i \cO(\C^5)\partial_{z_i},\quad 
\nu \in \cO (\C^5) \\
\beta & \in \cO (\C^5), \quad \gamma^{i} \d z_i \in \Omega^{1}(\CC^5) \cong \oplus_i \cO (\C^5)\d z_i 
\end{align*}
where $z_i$ is a holomorphic coordinate on $\CC^5$.

Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_j) = (m_1, m_2, m_3, m_4, m_5)\in \Z^5_{\geq 0}$; these are given by
\begin{align*}
 \mu^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
\nu_{(m_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
\gamma^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
 \beta_{(m_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\beta (0) \\
\end{align*}

It is easiest to label the Cartan subgroup of $SU(5)$ by fugacities $q_1,\ldots, q_5$ subject to the constraint that $\prod_{i=1}^5 q_i = 1$. 
The single particle index is the $SU(5)$ character of the space of linear local operators.

\begin{lem}
The single particle index is 
\[
i(q_1,\ldots,q_5) = \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i^{-1}}{\prod_{i=1}^5 (1-q_i^{-1})}
\]
where the fugacities satisfy the constraint $\prod_{i=1} q_i = 1$. 
\end{lem}
\begin{proof}
The linear local operators $ \nu_{(m_j)}$ and $\beta_{(m_j)}$ are of the same $q$-weight but opposite parity.
Thus, they do not contribute to the single particle index.

The $q$-weight of the odd local operator $\mu_{(m_j)}^i$ is 
\[
q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} .
\]
The $q$-weight of the even local operator $\gamma_{(m_j)}^i$ is 
\[
q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} .
\]

Thus, in total, the single particle index is
\[
- \frac{\sum_{i=1}^5 q_1 \cdots \Hat{q_i} \cdots q_5}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} .
\]
This simplifies to the stated expression.
\end{proof}

This single particle index for our space of local operators agrees with the one computed in \cite{NekrasovInstanton}. 
To obtain the full index of local operators we apply the plethystic exponential ${\rm PE}[i(x)] = \exp\left(\sum_n \frac1n f(x^n)\right)$.

\begin{prop}
The character of local operators of the 11-dimensional theory on $\CC^5 \times \RR$ is 
\[
\prod_{n_i \geq 0} 
\]
\end{prop}

\end{document}

### 2021-10-20 intro.tex

@@
 \begin{tikzcd}[row sep=large]
-                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
- \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
+                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" description, pos=.5] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
+ \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"]\arrow[rr, rightsquigarrow, bend right=25, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering minimal twist of type I}  &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                          &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &

### 2021-10-21 character.tex
diagram and character discussion

@@
 
-Thus, in total, the single particle index is
-\[
+Thus we find that the single particle index is given by the infinite series
+\beqn\label{infseriesindex}
+\sum_{i=1}^5\left ( \sum_{(m_i)\in \Z^5} q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} - \sum_{(m_i)\in \Z^5} q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} \right)
+\eeqn
+
+which sums to the expression
+\beqn\label{singleparticleindex}
 - \frac{\sum_{i=1}^5 q_1 \cdots \Hat{q_i} \cdots q_5}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} .
-\]
+\eeqn
+
 This simplifies to the stated expression.
@@
 \[
-\prod_{n_i \geq 0} 
+\prod_{i=1}^{5} \prod_{(m_i)\in \Z^5} \frac{1-q_1^{m_1+1}\cdots q_i^{m_i}\cdots q_5^{m_5+1}}{1-q_1^{m_1}\cdots q_i^{m_i+1}\cdots q_5^{m_5}}
 \]
 \end{prop}
+\begin{proof}
+Recall that the plethystic exponential takes sums to products and monomials to geometric series. Apply this to the infinite series \ref{infseriesindex}.
+\end{proof}
 
+In terms of these fugacities, deforming the theory in a way that breaks the $SU(5)$ symmetry to a $SU(3)\times SU(2)$ subgroup can be described by requiring that the fugacities satisfy the additional constraints \[q_1q_2q_3 = 1, \ \ \ q_4q_5=1.\]
+\begin{prop}
+After imposing the above constraints, the single particle index is
+\[
+i(q) = \frac{1}{(1-q)(1-q^{-1})}
+\]
+where $q = q_4 = q_5^{-1}$. This matches with the single particle index of the nonminimal twist.
+\end{prop}
 \end{document}

### 2021-10-21 dfn.tex
diagram and character discussion

@@
 
-\subsection{Local character}
+\subsection{Local character}\label{sec:locchar}
 
@@
 
+\iffalse
 We choose generators of the Cartan subgroup for the $SU(5)$ action with the following weights:
@@
 We can now readily compute the characters.
-\begin{prop}\label{prop:locchar}
+\begin{prop}
 The $SU(5)$ local character of the holomorphic twist of the 11-dimensional theory on flat space is
@@
 The plethystic exponential returns the desired expression.
+
+\end{proof}
+\fi
+
+It is easiest to label the Cartan subgroup of $SU(5)$ by fugacities $q_1,\ldots, q_5$ subject to the constraint that $\prod_{i=1}^5 q_i = 1$. 
+The single particle index is the $SU(5)$ character of the space of linear local operators.
+
+\begin{lem}
+The single particle index is 
+\[
+i(q_1,\ldots,q_5) = \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i^{-1}}{\prod_{i=1}^5 (1-q_i^{-1})}
+\]
+where the fugacities satisfy the constraint $\prod_{i=1} q_i = 1$. 
+\end{lem}
+\begin{proof}
+The linear local operators $ \nu_{(m_j)}$ and $\beta_{(m_j)}$ are of the same $q$-weight but opposite parity.
+Thus, they do not contribute to the single particle index.
+
+The $q$-weight of the odd local operator $\mu_{(m_j)}^i$ is 
+\[
+q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} .
+\]
+The $q$-weight of the even local operator $\gamma_{(m_j)}^i$ is 
+\[
+q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} .
+\]
+
+Thus we find that the single particle index is given by the infinite series
+\beqn\label{infseriesindex}
+\sum_{i=1}^5\left ( \sum_{(m_i)\in \Z^5} q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} - \sum_{(m_i)\in \Z^5} q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} \right)
+\eeqn
+
+which sums to the expression
+\beqn\label{singleparticleindex}
+- \frac{\sum_{i=1}^5 q_1 \cdots \Hat{q_i} \cdots q_5}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} .
+\eeqn
+
+This simplifies to the stated expression.
+\end{proof}
+
+This single particle index for our space of local operators agrees with the one computed in \cite{NekrasovInstanton}. 
+To obtain the full index of local operators we apply the plethystic exponential ${\rm PE}[i(x)] = \exp\left(\sum_n \frac1n f(x^n)\right)$.
+
+\begin{prop}\label{prop:locchar}
+The character of local operators of the 11-dimensional theory on $\CC^5 \times \RR$ is 
+\[
+\prod_{i=1}^{5} \prod_{(m_i)\in \Z^5} \frac{1-q_1^{m_1+1}\cdots q_i^{m_i}\cdots q_5^{m_5+1}}{1-q_1^{m_1}\cdots q_i^{m_i+1}\cdots q_5^{m_5}}
+\]
+\end{prop}
+\begin{proof}
+Recall that the plethystic exponential takes sums to products and monomials to geometric series. Apply this to the infinite series \ref{infseriesindex}.
+\end{proof}
 %\[
@@
 %\]
-\end{proof}
 

### 2021-10-21 intro.tex
diagram and character discussion

--- 2021-10-15 intro.tex
@@
 \begin{tikzcd}[row sep=large]
-                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
- \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
+                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{slab }" '] \arrow[d, "\text{topological }S^1" description] \arrow[rdd, "\text{CY3}" description, pos=.7, bend left = 5] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1" description] \\
+ \parbox{3cm}{\centering minimal twist of type I}  &  \parbox{3cm}{\centering minimal twist of type IIA}\arrow[l, "\text{orbifold}"]\arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                                &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                          &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &

### 2021-10-21 nonmin.tex

@@
-\section{The non-minimal twist}
+\section{The non-minimal twist}\label{s:nonmin}
 
@@
 
-\subsection{Index matching}
-\label{sec:indexcheck}
-
-As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the $G_2\times SU(2)$ twist.
-%\brian{If we are going to say G2 we need to explain how G2 arises.
-I've been calling it the non minimal twist.}
-We will find that the local character of the latter agrees with a specialization of the local character computed in proposition \ref{prop:locchar}
-
-\begin{prop}
-The  local character of the $G_2\times SU(2)$-invariant twist of 11d supergravity on flat space is given by
-\[
-\chi_{SU(3)\times SU(2)}(\Obs_0^{\cE_{G2\times SU(2)}}) = \prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
-\] 
-This agrees with the specializaiton of the local character computed in proposition \ref{prop:locchar} at $y=1$.
-\end{prop}
-\begin{proof}
-The space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$.
-The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by
-\[
-A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
-\]
-
-The character of the linear span of these is given by the geometric series
-\[
-\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}
-\] 
-with plethystic exponential given by 
-\[
-\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
-\]
-
-For the last part, it suffices to show that the characters of linear local operators agree upon evaluating $y=1$.
-Summing the geometric series giving the character of linear local operators in the holomorphic twist yields the rational function \[\frac{\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y &+ q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right)}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\] Specializing $y=1$, the numerator cancels with the factors in the denominator involving the $t_i$.
-The result is \[\frac{1}{(1-q^{-1})(1-q)}\] which is exactly the sum of the geometric series we found
-
-\end{proof}
-
-%Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
-
-%The Lie algebra of gauge symmetries of this model on flat space is 
-%\[
-%\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
-%\]
-%which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$. 
-%
-%More generally, the twist can be defined \brian{finish}
-
-\subsection{The non-minimal supercharge}
-
 From the point of view of the untwisted theory, the non-minimal twist is defined by working in a background where the fermionic ghost in the physical theory is equal to a supertranslation of the form
@@
 \]
-Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(2)$.
+Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(3) \times SU(2)$.
+
+\subsection{Index matching}
+\label{sec:indexcheck}
+
+As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the nonminimal twist.
+We will find that the local character of the latter agrees with a specialization of the local character computed in \ref{sec:locchar}
+
+\begin{prop}
+The  local character of the nonminimal twist of 11d supergravity on flat space is given by
+\[
+\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
+\] 
+This agrees with the specializaiton of the local character computed in proposition \ref{prop:locchar}.
+\end{prop}
+\begin{proof}
+The space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$.
+The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by
+\[
+A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
+\]
+
+The character of the linear span of these is given by the geometric series
+\beqn\label{nonmin:singleparticle}
+\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}
+\eeqn
+with plethystic exponential given by 
+\[
+\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
+\]
+
+For the last part, it suffices to observe the specialization at the level of single particle indices.
+A natural choice of fugacities for $SU(3)\times SU(2)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in \ref{sec:locchar} by requiring the additional constraints \[q_1q_2q_3 = 1, \ \ \ q_4q_5=1.\]
+After imposing the above constraints, the single particle index \ref{singleparticleindex} is
+\[
+i(q) = \frac{1}{(1-q)(1-q^{-1})}
+\]
+where $q = q_4=q_5^{-1}$. This is exactly the sum of the geometric series \ref{nonmin:singleparticle}
+
+\end{proof}
+
+%Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.
+
+%The Lie algebra of gauge symmetries of this model on flat space is 
+%\[
+%\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
+%\]
+%which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$. 
+%
+%More generally, the twist can be defined \brian{finish}
+
+\subsection{The non-minimal global symmetry algebra}
 

### 2021-10-21 intro.tex
intro changes

--- 2021-10-15 intro.tex
@@
 Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
-\begin{itemize}
+\begin{itemize}[leftmargin=\parindent,itemsep=\parskip]
 \item The minimal (or holomorphic) twist. 
@@
 The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
-The twist is $SU(2)$ invariant and involves a fixed choice of a hyper K\"ahler structure on $\CC^2$.  
+The twist is $SU(2)$ invariant and involves a fixed choice of a hyperk\"ahler structure on $\CC^2$.  
 \end{itemize}
 
-In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of 11-dimensional supergravity on flat space, following work of Cederwall~\cite{Ced-towards,Ced-11d}.
-In fact, the result of \cite{SWspinor} shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
+In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of eleven-dimensional supergravity on flat space, building on work of Cederwall~\cite{Ced-towards,Ced-11d} that constructed the eleven-dimensional theory in the pure spinor formalism.
+In fact, the result of~\cite{SWspinor} shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
 (In separate work~\cite{EagerHahner}, the free-field limit of the non-minimal twist was derived from the component-field multiplet as used in the physics literature.)
@@
 The resulting theory is $\ZZ/2$ graded; the grading is inherited from the totalization of ghost number and intrinsic parity in the original, untwisted, eleven-dimensional theory.
-In \S\ref{sec:dfn} we introduce a full interacting theory in th Batalin--Vilkovisky (BV) formalism which has, as its free limit, the twist computed in \cite{SWspinor}.\footnote{One subtlety is that unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the 11-dimensional theory is only $\ZZ/2$ graded.
-All odd fields can therefore be considered as ``ghosts'' in the twisted theory.}
-Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of 11-dimensional supergravity on flat space.
+In \S\ref{s:dfn} we introduce a full interacting theory in the Batalin--Vilkovisky (BV) formalism, the free limit of which is the twist computed in \cite{SWspinor}.\footnote{One subtlety is that, unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the eleven-dimensional theory is only $\ZZ/2$ graded.
+All odd fields can therefore in some sense be considered as ``ghosts'' in the twisted theory.}
+Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of eleven-dimensional supergravity on flat space.
 
 \begin{conj}
-The $11$-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{sec:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge.
+The eleven-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge.
 \end{conj}
@@
 %\brian{Ingmar, maybe you can comment on the status of this conjecture.}
-In this paper we will provide evidence for this conjecture on a variety of fronts. 
+In this paper we will provide evidence for this conjecture on a variety of fronts:
+\begin{itemize}[leftmargin=\parindent,itemsep=\parskip]
+\item
 In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist. 
-
+\item
 In \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
-For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity of \cite{CLsugra}.
-
+For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity in~\cite{CLsugra}.
+\item
 In \S\ref{sec:ads} we propose a description of supergravity in twisted versions of both the ${\rm AdS}_7$ and ${\rm AdS}_4$ backgrounds. 
 We show that the residual symmetries of supergravity in these backgrounds are present in our twisted background.
-
-Finally, we describe the non-minimal twist of 11-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
+\item
+Finally, we describe the non-minimal twist of eleven-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
 This non-minimal twist is invariant for the group $G_2 \times SU(2)$. 
-We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in \cite{RY}. 
+We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in~\cite{RY}. 
+\end{itemize}
 %Surprisingly, at the twisted level these symmetries
@@
 
-Our 11-dimensional theory is defined more generally on the product of manifolds 
+Our eleven-dimensional theory is defined more generally on the product of manifolds 
 \[
@@
 \[
-\mu \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
+\mu^{1,1} \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
 \]
 where $\T_X$ denotes the holomorphic tangent bundle on $X$.
-Locally, $\mu$ can be decomposed as Beltrami-like differential
+Locally, $\mu^{1,1}$ can be decomposed as Beltrami-like differential
 \[
-\mu = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
+\mu^{1,1} = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
 \]
-Physically speaking, $\mu$ is a component of the metric which survives in the twisted theory, see \S \ref{s:components}.
+Physically speaking, $\mu^{1,1}$ is a component of the metric which survives in the twisted theory; see~\S\ref{s:components}.
 
@@
 
-There is a background where the equation of motion involving the $\mu, \gamma^{1,0}, \gamma^{1,2}$ fields reads
+There is a background where the equation of motion involving the fields $\mu^{1,1}$, $\gamma^{1,0}$,  and~$\gamma^{1,2}$ reads
 \begin{align*}
-\dbar \mu + \frac12 [\mu, \mu] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
+\dbar \mu^{1,1} + \frac12 [\mu^{1,1}, \mu^{1,1}] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
 %(\dbar + \mu) \gamma^{1,0} = 
@@
 \end{align*}
-Additionally, there are the conditions that $\mu$ preserve the holomorphic volume form on $X$ and that all fields are locally constant along the topological direction $S$.  
+Additionally, there are the conditions that $\mu^{1,1}$ preserve the holomorphic volume form on $X$ and that all fields are locally constant along the topological direction $S$.  
 %In the last line $\d_S$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
-Notice that were it not for the presence of the last term in the first equation then this would be the integrability equation for $\mu$ to determines a complex structure on $X$.
+Notice that this would be precisely the integrability equation for $\mu^{1,1}$ to determine a complex structure on $X$, were it not for the presence of the last term in the first equation.
 %The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
@@
 
-If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero then we see that $\mu$ is exactly a deformation of complex structure along $X$. 
-In terms of the 11-dimensional geometry, this is a background which describes deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserves the holomorphic volume form along the leaves.
+If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero, then we see that $\mu^{1,1}$ is exactly a deformation of complex structure along $X$. 
+In terms of the eleven-dimensional geometry, these field configurations describe deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserve the holomorphic volume form along the leaves.
 We further unpack the equations of motion in more general backgrounds in \S \ref{s:components}, but leave a complete study for future work.
@@
 
-The simplest field configuration in the twisted theory is the flat background which corresponds to considering to our 11-dimensional theory on $\CC^5 \times \RR$ where we equip $\CC^5$ with the flat holomorphic volume form.
-In this case we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.
+The simplest field configuration in the twisted theory is the flat background; this corresponds to considering to our eleven-dimensional theory on $\CC^5 \times \RR$, where we equip $\CC^5$ with the flat holomorphic volume form.
+In this case, we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.
 
 \begin{thm}
-The global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension of the exceptional super Lie algebra $E(5,10)$. 
+The global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension of the exceptional simple super Lie algebra $E(5,10)$. 
 \end{thm}
 
-In particular, correlation functions involving observables of the 11-dimensional theory will be constrained by the infinite-dimensional symmetry algebra $E(5,10)$. 
-Given our main conjecture that the interacting 11-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.
+In particular, correlation functions involving observables of the eleven-dimensional theory will be constrained by the infinite-dimensional symmetry algebra $E(5,10)$. 
+Given our main conjecture that the interacting eleven-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.
 
@@
 
-Through the dimensional reduction of our 11-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
+Through the dimensional reduction of our eleven-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
 In Table \ref{diagram}, we provide a summary of the comparisons with twists of supergravity in lower dimensions we perform.
-The squigly arrows denote further twists, and the solid arrows denote various kinds of reductions.
+The squiggly arrows denote further twists, and the solid arrows denote various kinds of reductions.
 
+\begin{table}
 \begin{center}
-\begin{tikzcd}[row sep=large]
-                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{topological }S^1" '] \arrow[d, "\text{slab }" '] \arrow[rdd, "\text{CY3}" ' pos=.75] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1"] \\
- \parbox{3cm}{\centering minimal twist of type IIA} \arrow[r, "\text{orbifold}"] &  \parbox{3cm}{\centering minimal twist of type I} \arrow[r, rightsquigarrow, crossing over]                                                                                                                                                                                               &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
+\[
+\begin{tikzcd}[row sep=large,column sep = 3ex]
+                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{slab }" '] \arrow[d, "\text{topological }S^1" description] \arrow[rdd, "\text{CY3}" description, pos=.7, bend left = 5] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1" description] \\
+ \parbox{3cm}{\centering minimal twist of type I}  &  \parbox{3cm}{\centering minimal twist of type IIA}\arrow[l, "\text{orbifold}", start anchor={[xshift=1.5ex]west}, end anchor={[xshift=-1.5ex]east}]\arrow[r, rightsquigarrow, crossing over, end anchor = {[xshift=2ex]west}]                                                                                                                                                                                                &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow, start anchor={[xshift=-2ex]east}, end anchor={[xshift=2ex]west}] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                          &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &
 \end{tikzcd}
+\]
 \end{center}
+\caption{Relations between various twists}
 \label{diagram}
+\end{table}
 
-In \S \ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
+In \S\ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
 The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
@@
 Next, in \S \ref{s:CY3} we study the reduction along a Calabi-Yau 3 fold to obtain a conjectural description of the minimal twist of 5d $\cN=1$ supergravity.
-Finally, we show in \S \ref{s:nonmin} how the non-minimal twist of 11d supergravity arises as a further twist of our holomorphic twist.
+Finally, we show in \S \ref{s:nonmin} how the non-minimal twist of eleven-dimensional supergravity arises as a further twist of our holomorphic twist.
 
-\subsection*{Future work}
+%\subsection*{Future work}
 
 \subsection*{Acknowledgements}
+We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, O.~Gwil\-liam, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds.
+I.S.
+and B.W.
+thank the University of Heidelberg, B.W.
+thanks the Mathematisches Forschungsinstitut Oberwolfach, and I.S.
+thanks the Krameterhof for hospitality while portions of this work were being completed.
+The work of S.R.
+is supported by the Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported in part by the Government of Canada, through the Department of Innovation, Science and Economic Development Canada, and by the Province of Ontario, through the Ministry of Colleges and Universities.
+The work of I.S. is supported by the Free State of Bavaria. The work of B.W. is supported by the University of Edinburgh.
+% Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the funding agencies.
 

### 2021-10-21 dfn.tex
merge
fussnote

@@
-\section{The minimal twist of 11-dimensional supergravity} 
+\section{The minimal twist of eleven-dimensional supergravity} 
 \label{s:dfn}
@@
 
-This is completely reasonable from the point of view of twisting supersymmetry in 11-dimensions. 
+This is completely reasonable from the point of view of twisting supersymmetry in eleven dimensions. 
 Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data \label{CosHol,ESW}.
@@
 
-Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + g J$ is the minimal twist of $11$-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form.
+Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + g J$ is the minimal twist of eleven-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form.
 For the moment, we briefly read off the equations of motion of the general theory on $X \times S$.
@@
 We can get a better sense of the equations if we expand in components of these fields. 
-The component fields of the 11-dimensional theory on $X \times S$ have the following form: 
+The component fields of the eleven-dimensional theory on $X \times S$ have the following form: 
 \begin{itemize}
@@
 
-In \cite{SWspinor}, the second two authors showed that the free-limit of the minimal twist of 11-dimensional supergravity agrees with the free-limit of the 11-dimensional theory that we have introduced here.
+In \cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here.
 Given this result, we can recognize many fields in the twisted theory as components of the physical fields of supergravity which remain after we twist.
@@
 
-We consider the 11-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
+We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
 On this background, the theory is manifestly $SU(5)$ invariant. 
@@
 We are choosing the weights in this way as a matter of convenience for the later sections. 
-For instance, upon performing the further twist of the 11-dimensional theory, the $SU(5)$ symmetry is broken to an $SU(3)\times SU(2)$ symmetry; the Cartan of the unbroken symmetries corresponds to the fugacities $q, t_1, t_2$ in the above table.
+For instance, upon performing the further twist of the eleven-dimensional theory, the $SU(5)$ symmetry is broken to an $SU(3)\times SU(2)$ symmetry; the Cartan of the unbroken symmetries corresponds to the fugacities $q, t_1, t_2$ in the above table.
 
@@
 \begin{prop}
-The $SU(5)$ local character of the holomorphic twist of the 11-dimensional theory on flat space is
+The $SU(5)$ local character of the holomorphic twist of the eleven-dimensional theory on flat space is
 \begin{multline}
@@
 \begin{prop}\label{prop:locchar}
-The character of local operators of the 11-dimensional theory on $\CC^5 \times \RR$ is 
+The character of local operators of the eleven-dimensional theory on $\CC^5 \times \RR$ is 
 \[
@@
 In \cite{GRWthf} an existence result for one-loop quantizations of mixed topological-holomorphic theories was established. 
-We apply this to the 11-dimensional model at hand.
+We apply this to the eleven-dimensional model at hand.
 
-The 11-dimensional theory is a mixed topological-holomorphic theory.
+The eleven-dimensional theory is a mixed topological-holomorphic theory.
 On flat space $\CC^5_z \times \RR_t$, this means that the theory is translation invariant and that the following act homotopically trivially:
@@
 
-Recall that the action functional of the 11-dimensional theory is $S_{BF, \infty} + c J$. 
+Recall that the action functional of the eleven-dimensional theory is $S_{BF, \infty} + c J$. 
 Since the cubic and higher interactions only involve holomorphic derivatives, we obtain the following directly from the main result of \cite{GRWthf}.
@@
 \begin{thm}
-There exists a gauge fixing condition for the 11-dimensional theory on $\CC^5 \times \RR$ which renders its one-loop quantization finite and anomaly-free. 
+There exists a gauge fixing condition for the eleven-dimensional theory on $\CC^5 \times \RR$ which renders its one-loop quantization finite and anomaly-free. 
 \end{thm}
@@
 Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 
-We will return to the existence and uniqueness of a higher order quantization of the 11-dimensional theory in future work.
+We will return to the existence and uniqueness of a higher order quantization of the eleven-dimensional theory in future work.

### 2021-10-21 intro.tex
fussnote

@@
 The simplest field configuration in the twisted theory is the flat background; this corresponds to considering to our eleven-dimensional theory on $\CC^5 \times \RR$, where we equip $\CC^5$ with the flat holomorphic volume form.
-In this case, we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.
+In this case, we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.\footnote{The twist of the eleven-dimensional gravity multiplet was computed in~\cite{SWspinor} by reducing it to a particular pure spinor model based on $\Gr(2,5)$; a possible relationship between this pure spinor model and $E(5,10)$ was first pointed out by Martin Cederwall in~\cite{martinSL5}.}
 

### 2021-10-21 dfn.tex
merge

--- 2021-10-21 dfn.tex
@@
 \section{The minimal twist of 11-dimensional supergravity} 
-\label{s:dfn}
+\label{sec:dfn}
 
@@
 
-\parsec
-There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
-\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
+%\parsec
+%There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
+%\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}
 
@@
 It is easiest to label the Cartan subgroup of $SU(5)$ by fugacities $q_1,\ldots, q_5$ subject to the constraint that $\prod_{i=1}^5 q_i = 1$. 
-The single particle index is the $SU(5)$ character of the space of linear local operators.
+We first compute the single particle index.
+This is the $SU(5)$ character of the space of linear local operators.
 
@@
 This single particle index for our space of local operators agrees with the one computed in \cite{NekrasovInstanton}. 
-To obtain the full index of local operators we apply the plethystic exponential ${\rm PE}[i(x)] = \exp\left(\sum_n \frac1n f(x^n)\right)$.
+To obtain the full index of local operators we apply the plethystic exponential ${\rm PE}[f(x)] = \exp\left(\sum_n \frac1n f(x^n)\right)$.
 
@@
 \begin{proof}
-Recall that the plethystic exponential takes sums to products and monomials to geometric series. Apply this to the infinite series \ref{infseriesindex}.
+Recall that the plethystic exponential takes sums to products and monomials to geometric series. Apply this to the infinite series \eqref{infseriesindex}.
 \end{proof}

### 2021-10-21 intro.tex
merge

@@
 \item 
+In \S\ref{sec:locchar}, we show that the character of the local operators in our 11-dimensional theory agrees with the index of 11-dimensional supergravity. 
+\item
 In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist.
-\item
-In \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
-For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity in~\cite{CLsugra}.
 \item
@@
 \item
-Finally, we describe the non-minimal twist of eleven-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
+In \S\ref{s:nonmin}, we describe the non-minimal twist of eleven-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
 This non-minimal twist is invariant for the group $G_2 \times SU(2)$. 
 We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in~\cite{RY}.  
+\item Finally, in \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
+For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity in~\cite{CLsugra}.
 \end{itemize}
@@
 thank the University of Heidelberg, B.W.
-thanks the Mathematisches Forschungsinstitut Oberwolfach, and I.S.
+thanks the University of Edinburgh and the Mathematisches Forschungsinstitut Oberwolfach, and I.S.
 thanks the Krameterhof for hospitality while portions of this work were being completed.

### 2021-10-21 dfn.tex
merggg

--- 2021-10-21 dfn.tex
@@
 
-In this section we define the central theory of study, within the Batalin--Vilkovisky formalism.
-The theory will be defined on any eleven-dimensional manifold of the form $X \times L$ where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
+In this section we define the central theory of study within the Batalin--Vilkovisky formalism.
+The theory will be defined on any eleven-dimensional manifold of the form $X \times L$, where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
 
@@
 \[
-  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
+  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] , \; \dbar\right) .
 \]
@@
 resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
-The anti-holomorphic Dolbeault degrees and the $\dbar$ operator is left implicit. 
+The anti-holomorphic Dolbeault degrees and the $\dbar$ operator are left implicit. 
 %By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.

### 2021-10-21 matrix.tex

@@
 \label{s:ht}
-
-We produce the following homotopy data:
+We proceed to the proof of part (2) of Theorem \ref{thm:global}. 
+To do this, we first produce the following homotopy data:
 \begin{equation}
@@
 
-\parsec[s:altglobal]
+%\parsec[s:altglobal]
 
-In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.
+%In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.
 
-\subsection{Twisted matrix model}
+%\subsection{Twisted matrix model}

### 2021-10-21 nonmin.tex

@@
 \beqn
-\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_X \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_X \hotimes \Omega^\bu_L 
+\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_W \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_W \hotimes \Omega^\bu_L 
 %[-k] 
@@
 We will show that the full non-linear map intertwines the action functionals up to cohomologically exact terms, and hence defines an equivalence of BV theories.
+
+We first substitute the values for the fields in \eqref{eqn:g2map} into the original 11-dimensional action. 
+The terms which are at least cubic in the action in \eqref{eqn:delta1} become
+\beqn
+\int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right) .
+\eeqn
+Here, $\til \alpha^2$ denotes the element of $\Omega^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \hotimes \Omega^\bu_L$ corresponding to $\alpha^2$ determined by the Calabi--Yau form $\d^3 w$. 
+There is only one cubic term left in \eqref{eqn:delta2} when we substitute the fields according to \eqref{eqn:g2map}.
+It is
+\beqn
+\frac16 \int \alpha^1 \del^z \alpha^1 \del^z \alpha^1. 
+\eeqn
+
+Notice that the total action is of the form 
+\beqn\label{eqn:pcs1}
+S_{pCS} (\alpha) + \int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \til\alpha^3 \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \til\alpha^3 \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right)
+\eeqn
+where $S_{pCS}$ is the Poisson Chern--Simons action in \eqref{eqn:pcsaction}.
+
+We will show that the terms not appearing in $S_{pCS}(\alpha)$ are cohomologically trivial. 
+First, consider the odd local functional
+\beqn\label{eqn:triv1}
+\int \frac{1}{1 - \til \alpha^3} \alpha^2 (\til \alpha^2)^2 .
+\eeqn
+Applying the linearized BRST operator (in the non-minimal twist) this becomes 
+\[
+\int \frac{1}{1 - \til \alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 +  \int \frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2 .
+\]
+The first term in this expression agrees the first term in parentheses in \eqref{eqn:pcs1}.
+The second term is zero for symmetry reasons. 
+Thus, \eqref{eqn:triv1} trivializes the first term in parentheses in \eqref{eqn:pcs1}.
+
+It remains to trivialize the remaining terms in parentheses. 
+To do this, we fix a primitive $\eta$ of the holomorphic volume form $\d^3 w$. 
+That is, $\eta$ is a holomorphic two-form on $W$ satisfying $\del \eta = \d^3 w$. 
+Consider the (non-translation invariant) odd local functional
+\[
+\int \frac{1}{1-\til \alpha^3} \eta (\til \alpha^3)^2 \del^z \alpha^1 \del^z \alpha^0   .
+\]
+Using $\del^w \eta = \d^3 w$, we see that this functional trivializes the remaining terms in parentheses in \eqref{eqn:pcs1}.
+This completes the argument.
 

### 2021-10-25 dfn.tex
dfn

@@
 Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
-If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
-The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
+If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on~$X$ with values in $V$.
+The $\dbar$ operator $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X,V)$ defines the Dolbeault complex of $V$:
 \[
@@
 \]
-This is a free resolution for the sheaf of holomorphic sections of $V$.
+This is a free (smooth) resolution for the sheaf of holomorphic sections of $V$.
 
@@
 
-The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[\S 3.1.3]{CG2}.
-This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
+The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra~\cite[\S 3.1.3]{CG2}.
+This means that, as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle, and its differential and Lie bracket are given by differential and bidifferential operators respectively.
 
@@
 The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$. 
-The condition that the differential is square-zero $\delta_\cL \circ \delta_\cL = 0$ is equivalent to the higher Jacobi relations.
+The condition that the differential $\delta_\cL$ is square-zero is equivalent to the higher Jacobi relations.
 
@@
 \deq[eq:newbase]{
-%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
     \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
@@
 Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$.
+(Here, and in what follows, we will use the symbol $\PV^{i,\bu}$ for the Dolbeault resolution of \emph{holomorphic polyvector fields;} by definition, this is the complex $\Omega^{0,\bu}(X,\wedge^i \T_X)$.)
 The first few nonzero brackets are
@@
 The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(S)$ is non polynomial. 
-In fact, it is related to the BCOV action functional via dimensional reduction, see \S \ref{sec:dimred}.
+In fact, it is related to the BCOV action functional via dimensional reduction (see \S \ref{sec:dimred}).
 Explicitly, this action functional is
@@
 Explicitly, the automorphism is
-\begin{multline}\label{eqn:auto1}
-  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
+\begin{equation}\label{eqn:auto1}
+  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} , \qquad
   \beta \mapsto (\beta - \mu \vee \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
-\end{multline}
+\end{equation}
 
@@
 In this case, with $n = 5 + 1 - 1 = 5$ the theories described in this section are $\ZZ$-graded in the BV formalism.
-Momentarily, we consider a new term in the action which will break this grading, so this integer shift will not play an essential role.
+Momentarily, we consider a new term in the action which will break this grading; as such, this integer shift will not play an essential role.
 
@@
 We will break the $\ZZ$-grading present in BF theory discussed in the previous section to a $\ZZ/2$ grading. 
-For reference, this means that linear BRST complex of fields of the model now take the following form.
+For reference, this means that the linear cochain complex of fields of the model now takes the following form.
 
@@
 
-To define our classical field theory on $X \times S$ we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
+To define our classical field theory on $X \times S$, we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
 Such deformations are governed by the classical master equation: the parameterized family of actions 
@@
   }
-Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading.
+Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading (although it is even).
 
 This is completely reasonable from the point of view of twisting supersymmetry in eleven dimensions. 
-Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data \label{CosHol,ESW}.
-
+Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data~\label{CosHol,ESW}. 
 Nevertheless, if we break to the obvious $\ZZ/2$ grading, the functional $S_{BF} + g J$ defines an even action functional.
@@
 \deq{
-  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}.
+  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}\,.
 }
@@
   \deq{
-    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2};
+    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2}\, ;
   }
@@
 \]
-Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equations and are equivalent as~$\ZZ/2$ graded BV theories.
+Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equation, and are equivalent as~$\ZZ/2$ graded BV theories.
 
@@
 We consider the action $S_{BF, \infty} + gJ$.
-The equation of motion obtained by varying $\beta$ is especially simple, in fact linear, since it only appears in the action via a quadratic term. 
+The equation of motion obtained by varying $\beta$ is especially simple---in fact linear---since $\beta$ only appears in the action via a quadratic term. 
 It is
@@
 \]
-The component $\mu^{i;j}$ has parity $i+j+1 \mod 2$. 
+The component $\mu^{i;j}$ has parity $i+j+1 \pmod 2$. 
 \item $\nu = \sum_{i,j} \nu^{i;j}$ is a superfield where
@@
 \]
-The component $\nu^{i;j}$ has parity $i+j \mod 2$. 
+The component $\nu^{i;j}$ has parity $i+j \pmod 2$. 
 %The linear equations of motion state that $\mu$ is constant along $\RR$ and holomorphic divergence-free as a vector field on $\CC^5$. 
@@
 \]
-The component $\gamma^{i;j}$ has parity $i+j$. 
+The component $\gamma^{i;j}$ has parity $i+j\pmod 2$. 
 \item 
@@
 \]
-The component $\beta^{i;j}$ has parity $i+j+1 \mod 2$. 
+The component $\beta^{i;j}$ has parity $i+j+1 \pmod 2$. 
 \end{itemize}
@@
 We look closely at the geometric meaning of \eqref{eqn:eombeta}. 
-Let's make the simplifying assumption that all components of $\mu$ are divergence-free that all fields are locally constant along $S$: $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
-Then, $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
+Let's make the simplifying assumption that all components of $\mu$ are divergence-free, and further that all fields are locally constant along $S$: that is, $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
+Then $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
 Then, there is a component of \eqref{eqn:eomgamma} which can be written as 
@@
 
-To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where the $(0,1)$ Dolbeault part of $\gamma$ is zero $\gamma^{1;0} = 0$. 
-Then, up the term involving 
+To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where  $\gamma^{1;0}$, the $(0,1)$ Dolbeault part of $\gamma$, is zero. 
+Then, up to the term involving 
 \[
@@
 
-In \cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here.
+In~\cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here.
 Given this result, we can recognize many fields in the twisted theory as components of the physical fields of supergravity which remain after we twist.
@@
 \item 
-The following components of $\mu$:
+The components 
 \begin{align*}
@@
 \end{align*}
-comprise components of the metric which remain after the twist. 
+of $\mu$ comprise components of the metric which remain after the twist. 
 The components 
@@
 \]
-comprise the ghosts for infinitesimal diffeomorphisms. 
+comprise the ghosts for infinitesimal (holomorphic) diffeomorphisms. 
 \item 
-The following three-form fields
+The three-form fields
 \begin{multline}
@@
 
-We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
+We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$, where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
 On this background, the theory is manifestly $SU(5)$ invariant. 
@@
 This contributes 
-\[
-\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
-\] 
+\begin{multline}
+\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} \times \\
+\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
+\end{multline}
 Finally, there is a summand of the form 
@@
 
-Upon performing the $\Omega$-background,
 %see \S \ref{s:omega},
-In \cite{CostelloM5}, Costello argues that the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
+In \cite{CostelloM5}, Costello argues that, upon performing the $\Omega$-background, the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
 Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 

### 2021-10-25 dfn.tex
matrix

@@
 
-When $g=0$, this result is actually exact
-since there are no Feynman diagrams present past one-loop in this case. 
-When $g \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge invariant perturbative quantization to higher orders in $\hbar$. 
+When $g=0$, this result is actually exact,
+since there are no Feynman diagrams present past one-loop order in this case. 
+When $g \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge-invariant perturbative quantization to higher orders in $\hbar$. 
 The presence of the functional $J = \frac16 \int \gamma \del \gamma \del \gamma$ allows one to construct Feynman graphs at arbitrary loop order.

### 2021-10-25 matrix.tex
dfn
matrix

@@
-\section{Twisted matrix model}
+%\section{Twisted matrix model}
+\section{Infinite-dimensional symmetry in flat backgrounds}
+\label{s:E(5,10)}
 
@@
 In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
-More generally, after shifting the cohomological degree by one the full cohomology of states with respect to the linear BRST operator results in a graded Lie algebra. 
-If we forget the grading to a $\ZZ/2$ grading then the global symmetry algebra has the structure of a super Lie algebra.
+More generally, after shifting the cohomological degree by one, the full cohomology of states with respect to the linear BRST operator is naturally a graded Lie algebra. 
+If we forget the grading to a $\ZZ/2$ grading, then this global symmetry algebra has the structure of a super Lie algebra.
 
 In general, taking cohomology loses information. 
-If the dg Lie, or $L_\infty$ algebra, we start with is not formal then there exists higher order operations present in the linearized BRST cohomology. 
-We will refer to this as the global symmetry algebra of the theory.
+If the dg Lie (or $L_\infty$) algebra we start with is not formal, then there exist higher-order operations on the linearized BRST cohomology. 
+We will refer to this $L_\infty$ algebra as the global symmetry algebra of the theory.
 
-Before taking cohomology with respect to the linear BRST operator, we described the super $L_\infty$ structure on the parity shift of the 11-dimensional fields in the previous section. 
-This is encoded by the full BV action of the 11-dimensional theory.
+Before taking cohomology with respect to the linear BRST operator, we described the super $L_\infty$ structure on the parity shift of the eleven-dimensional fields in the previous section. 
+This is encoded by the full BV action of the eleven-dimensional theory.
 The cubic component of the full BV action induces the super Lie algebra structure present in the linearized BRST cohomology.
 
-Our main result is to relate the global symmetry algebra of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacBible,KacE510} called $E(5,10)$.
+Our main result is to relate the global symmetry algebra of the minimal twist of eleven-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacBible,KacE510} called $E(5,10)$.
 We recall the definition below.
@@
 \begin{thm}\label{thm:global}
-Let $\Pi\cE(\CC^5 \times \RR)$ be the parity shift of the fields of 11-dimensional supergravity on $\CC^5 \times \RR$ and denote by $\delta^{(1)}$ the linearized BRST operator. 
+Let $\Pi\cE(\CC^5 \times \RR)$ be the parity shift of the fields of eleven-dimensional supergravity on $\CC^5 \times \RR$ and denote by $\delta^{(1)}$ the linearized BRST operator. 
 \begin{enumerate}
@@
 \item 
-The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E(5,10)$ determined by the even cocycle \eqref{eqn:cocycle}. 
+The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E(5,10)$ determined by the even cocycle defined in~\eqref{eqn:cocycle}. 
 \end{enumerate}
@@
 
-This result implies that the action functional $S_{BF, \infty} + J$ of the 11-dimensional theory is invariant for infinite-dimensional Lie algebra $E(5,10)$.
+This result implies that the action functional $S_{BF, \infty} + J$ of the eleven-dimensional theory is invariant for the infinite-dimensional Lie algebra $E(5,10)$.
 
@@
 
-We compute the linearized BRST cohomology of 11-dimensional supergravity.
-Then, we will describe the induced structure of a super Lie algebra present in the parity shift of the cohomology thus proving part (1) of Theorem \ref{thm:global}.
+We compute the linearized BRST cohomology of eleven-dimensional supergravity.
+Then we will describe the induced structure of a super Lie algebra present in the parity shift of the cohomology, proving part (1) of Theorem~\ref{thm:global}.
 
@@
 
-First, we recall the definition of the exceptional simple super Lie algebra $E(5,10)$. 
+First we recall the definition of the exceptional simple super Lie algebra $E(5,10)$. 
 Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
-Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomoprhic $2$-forms which are closed for the holomorphic de Rham operator $\del$.
+Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomorphic $2$-forms that are closed for the holomorphic de Rham operator $\del$.
 
-The even part of the super Lie algebra $E(5,10)$ is the Lie algebra of divergence-free vector fields on $\CC^5$
+The even part of the super Lie algebra $E(5,10)$ is the Lie algebra
 \[
-E(5,10)_+ = \Vect_0(\CC^5) ,
+E(5,10)_+ = \Vect_0(\CC^5)
 \]
+of divergence-free vector fields on $\CC^5$,
 whose elements we continue to denote by $\mu$. 
@@
 \[
-E(5,10)_- = \Omega^{2}_{cl} (\CC^5) 
+E(5,10)_- = \Omega^{2}_{cl} (\CC^5),
 \]
@@
 Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
-The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$ and is defined by
+The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$, and is defined by
 \beqn\label{eqn:e510}
@@
 \eeqn
-One immediately checks that since both $\alpha, \alpha'$ are closed two-forms that the resulting vector field on the right hand side is divergence-free. 
-In coordinates, if $f^{ij} \d z_i \wedge \d z_j$, $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
+Since both $\alpha, \alpha'$ are closed two-forms,  the resulting vector field on the right hand side is divergence free. 
+In coordinates, if $f^{ij} \d z_i \wedge \d z_j$ and $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.
 
-To be precise, Kac studied a more algebraic version of the algebra we have just introduced where holomorphic functions are replaced by holomorphic polynomials.
-Thus, the simple super Lie algebra classified in \cite{KacBible} is a dense sub Lie algebra of what we call $E(5,10)$ consisting of those vector fields and two-forms which have polynomial coefficients.
+To be precise, Kac studied a more algebraic version of the algebra we have just introduced, where holomorphic functions are replaced by holomorphic polynomials.
+As such, the simple super Lie algebra that appears in the classification in~\cite{KacBible} is a dense sub Lie algebra of what we call $E(5,10)$, consisting of those vector fields and two-forms that have polynomial coefficients.
 
@@
 
-In this section, we use the description of the 11-dimensional theory as the deformation of the BF action $S_{BF,\infty}$ by the functional $J$ of Theorem \ref{thm:dfn}. 
-We set the coupling $g = 1$, for any other nonzero value of $g$ we will obtain an isomorphic super $L_\infty$ algebra.
+In this section, we use the description of the eleven-dimensional theory as the deformation of the BF action $S_{BF,\infty}$ by the functional $J$ of Theorem \ref{thm:dfn}. 
+We set the coupling $g = 1$. For any other nonzero value of $g$, we will obtain an isomorphic super $L_\infty$ algebra as explained above.
+We would also obtain equivalent  results if we used the other model of the eleven-dimensional theory explained in~\S\ref{s:altdfn}. 
+%We remark on this below. %in~\S\ref{s:altglobal}.
 
-We will obtain the exact same results if we use the equivalent model of the 11-dimensional theory explained in \S \ref{s:altdfn}. 
-We remark on this below in \S \ref{s:altglobal}.
-
-The full BRST operator is given by the BV bracket with the BV action. 
+The full differential on the cochain complex of observables of the theory is given by the BV bracket with the BV action. 
 For us, this~is 
@@
 \]
-The linear BRST operator comes only from the quadratic summands in $S_{BF,\infty}$ and is of the form
+The linear BRST operator (dual to the differential on the cochain complex of fields) comes only from the quadratic summands in $S_{BF,\infty}$, and is of the form
 \beqn\label{eqn:linearBRST}
@@
 To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$. 
-By the $\dbar$ and de Rham Poincar\'e lemmas, the cohomology of the space of fields of the 11-dimensional theory on $\CC^5 \times \RR$ with respect $\dbar + \d_{\RR}$ results in the cochain complex
+By the $\dbar$ and de Rham Poincar\'e lemmas, the cohomology of the space of fields of the eleven-dimensional theory on $\CC^5 \times \RR$ with respect $\dbar + \d_{\RR}$ results in the cochain complex
 \begin{equation}
@@
 \item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
-This is a $\beta$-type field in the 11-dimensional theory, any constant function is closed for the de Rham differential. 
+This is a $\beta$-type field in the eleven-dimensional theory, any constant function is closed for the de Rham differential. 
 This element is also a ghost in the $\ZZ/2$-graded theory. 
@@
 
-The relationship of the $\mu$-elements in $E(5,10)$ and the 11-dimensional theory is apparent.
+The relationship of the $\mu$-elements in $E(5,10)$ and the eleven-dimensional theory is apparent.
 
@@
 induced by the holomorphic de Rham differential.
-This gives the relationship between the equivalence class $[\gamma]$ in the 11-dimensional theory and a closed two-form in $E(5,10)$ by $\alpha = \del \gamma$. 
-It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E(5,10)$ and the twist of 11-dimensional supergravity. 
+This gives the relationship between the equivalence class $[\gamma]$ in the eleven-dimensional theory and a closed two-form in $E(5,10)$ by $\alpha = \del \gamma$. 
+It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E(5,10)$ and the twist of eleven-dimensional supergravity. 
 This completes the proof of part (1) of Theorem \ref{thm:global}.
@@
 \]
-where $\varphi \in \clie^{even} (E(5,10))$ is the even Lie algebra cocycle defined by the formula
+where $\varphi \in \clie^\text{even} (E(5,10))$ is the even Lie algebra cocycle defined by the formula
 \beqn
@@
 \begin{align*}
-\clie^{even} (\cL) & = \clie^{2\bu , +} (\cL) \oplus \clie^{2\bu+1, -}(\cL) \\
-\clie^{odd} (\cL) & = \clie^{2\bu , -} (\cL) \oplus \clie^{2\bu+1, +}(\cL) .
+\clie^\text{even} (\cL) & = \clie^{2\bu , +} (\cL) \oplus \clie^{2\bu+1, -}(\cL) \\
+\clie^\text{odd} (\cL) & = \clie^{2\bu , -} (\cL) \oplus \clie^{2\bu+1, +}(\cL) .
 \end{align*}
@@
 
-%In \S \ref{s:altdfn} we gave an equivalent description of the 11-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.
+%In \S \ref{s:altdfn} we gave an equivalent description of the eleven-dimensional theory as a deformation of the BF action $S_{BF,0}$ by the functional $\til J$.
 

### 2021-10-26 dfn.tex
global editing

@@
 In this section we define the central theory of study within the Batalin--Vilkovisky formalism.
-The theory will be defined on any eleven-dimensional manifold of the form $X \times L$, where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
+The theory will be defined on any eleven-dimensional manifold of the form $X \times S$, where $X$ is a Calabi--Yau five-fold and $S$ is a smooth oriented one-manifold.
 
@@
 We set up some notations and conventions in the context of complex geometry. 
-Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
+Let $V$ be a holomorphic vector bundle on a $d$ dimensional complex manifold $X$. 
 If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on~$X$ with values in $V$.
@@
 
-Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the data of a square-zero, degree $+1$ derivation $\delta_\cL$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
+Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the datum of a square-zero, degree $+1$ derivation $\delta_\cL$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$.
 The Chevalley--Eilenberg cochain complex is 
@@
 \]
-The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$. 
+The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\otimes k} \to \cL[2-k]$. 
 The condition that the differential $\delta_\cL$ is square-zero is equivalent to the higher Jacobi relations.
@@
 The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
-It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$).
+It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity.
 
@@
 We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$.
-The algebra $\cA$ will be the smooth de Rham complex $(\Omega^\bu(S) , \d_S)$ where $S$ is a smooth manifold (we will specialize the dimension of this smooth manifold shortly, but the constructions in this section make sense in any dimension).
+The algebra $\cA$ will be the smooth de Rham complex $(\Omega^\bu(S) , \d_S)$ where $S$ is a smooth manifold.
 
@@
 
-First off, we remark on grading issues. 
+Before proceeding to the proof, we remark on grading issues. 
 In the original $\Z$-grading on the BF theory given in \eqref{eq:sympfields} with $n=5$, the component 
@@
 %\] 
+\begin{proof}
 
@@
 the  fundamental representation has symmetry type $\ydiagram{2,1}$.) 
+\end{proof}
 
@@
 
-When $g = 0$ we return to BF theory for the $L_\infty$ algebra $\cL_\infty(\CC^5) \otimes \Omega^\bu(\RR)$. 
+When $g = 0$ we recover BF theory for the $L_\infty$ algebra $\cL_\infty(\CC^5) \otimes \Omega^\bu(\RR)$. 
 For any $g \ne 0$ the theories are essentially equivalent in perturbation theory. 
@@
 \begin{align*}
- \mu^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
-\nu_{(m_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
-\gamma^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
- \beta_{(m_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\beta (0) \\
+ \boldsymbol{\mu}^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
+\boldsymbol{\nu}_{(m_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
+\boldsymbol{\gamma}^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
+ \boldsymbol{\beta}_{(m_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\beta (0) \\
 \end{align*}
@@
 \begin{proof}
-The linear local operators $ \nu_{(m_j)}$ and $\beta_{(m_j)}$ are of the same $q$-weight but opposite parity.
+The linear local operators $ \boldsymbol{\nu}_{(m_j)}$ and $\boldsymbol{\beta}_{(m_j)}$ are of the same $q$-weight but opposite parity.
 Thus, they do not contribute to the single particle index.
 
-The $q$-weight of the odd local operator $\mu_{(m_j)}^i$ is 
+The $q$-weight of the odd local operator $\boldsymbol{\mu}_{(m_j)}^i$ is 
 \[
@@
 \]
-The $q$-weight of the even local operator $\gamma_{(m_j)}^i$ is 
+The $q$-weight of the even local operator $\boldsymbol{\gamma}_{(m_j)}^i$ is 
 \[
@@
 \beqn\label{infseriesindex}
-\sum_{i=1}^5\left ( \sum_{(m_i)\in \Z^5} q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} - \sum_{(m_i)\in \Z^5} q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} \right)
+\sum_{i=1}^5\left ( \sum_{(m_i)\in \Z^5_{\geq 0}} q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} - \sum_{(m_i)\in \Z^5_{\geq 0}} q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} \right)
 \eeqn
@@
 \[
-\prod_{i=1}^{5} \prod_{(m_i)\in \Z^5} \frac{1-q_1^{m_1+1}\cdots q_i^{m_i}\cdots q_5^{m_5+1}}{1-q_1^{m_1}\cdots q_i^{m_i+1}\cdots q_5^{m_5}}
+\prod_{i=1}^{5} \prod_{(m_i)\in \Z^5_{\geq 0}} \frac{1-q_1^{m_1+1}\cdots q_i^{m_i}\cdots q_5^{m_5+1}}{1-q_1^{m_1}\cdots q_i^{m_i+1}\cdots q_5^{m_5}}
 \]

### 2021-10-26 intro.tex
dfn
global editing

@@
 \item
-In \S\ref{sec:susy}, we will show that this theory has all of the residual supersymmetries present after performing the holomorphic twist.
+In \S\ref{sec:susy}, we will show that this theory has all of the expected residual supersymmetries present after performing the holomorphic twist.
 \item
@@
 It is a sort of holomorphic version of gravity which at the genus zero  describes fluctuations of the complex structure of the Calabi--Yau manifold. 
-We recall relevant aspects of Kodaira--Spencer gravity in \ref{s:BCOV}.
+We recall relevant aspects of Kodaira--Spencer gravity in \S\ref{s:BCOV}.
 

### 2021-10-26 nonmin.tex
global editing

@@
 \]
-Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(3) \times SU(2)$.
+Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(2) \times SU(3)$.
 
@@
 \[
-A_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
+\boldsymbol{A}_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
 \]
@@
 For the last part, it suffices to observe the specialization at the level of single particle indices.
-A natural choice of fugacities for $SU(3)\times SU(2)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in \ref{sec:locchar} by requiring the additional constraints \[q_1q_2q_3 = 1, \ \ \ q_4q_5=1.\]
+A natural choice of fugacities for $SU(2)\times SU(3)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in \ref{sec:locchar} by requiring the additional constraints \[q_1q_2 = 1, \ \ \ q_3q_4q_5=1.\]
 After imposing the above constraints, the single particle index \ref{singleparticleindex} is
@@
 \]
-where $q = q_4=q_5^{-1}$. This is exactly the sum of the geometric series \ref{nonmin:singleparticle}
+where $q = q_1=q_1^{-1}$. This is exactly the sum of the geometric series \ref{nonmin:singleparticle}
 
@@
 \begin{itemize}
+\item $f(z_i, w_a)dz_1\wedge dz_2$ for $f$ a holomorphic function on $\CC^5$.
 \item $f(z_i) \partial_{z_1} + g(z_i) \partial_{z_2}$ for holomorphic functions $f,g$ on $\CC_{z_1} \times \CC_{z_2}$ which satisfy 
@@
 It is immediate to check that these are the only nonzero elements in the kernel. 
-Further, any element of the second type is clearly exact by the closed two-form $\ep^{ijklm} f \d z_l \d z_m$.
+Further, any element of the first type is clearly exact and any element of the last type is clearly exact by the closed two-form $\ep^{ijklm} f \d w_l \d w_m$.
 
@@
 
-Now, we turn to deducing the action function of the non-minimal twist and hence the proof of Theorem \ref{thm:nonmin}. 
+Now, we turn to deducing the action functional of the non-minimal twist and hence the proof of Theorem \ref{thm:nonmin}. 
 We will show that the eleven-dimensional theory on $\CC^5 \times \RR$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma_{nm}$ \eqref{eqn:gammanm} is equivalent to a theory with a purely Chern--Simons-like action functional that we referred to in the introduction to this section.

### 2021-10-26 suco.tex
global editing

@@
 
-We decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
+Decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
 \[
-\CC_z \times \RR \times \CC^4_w .
+ \CC^4_w\times \CC_z \times \RR .
 \]
@@
 Unlike the case of $M5$ branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
-We have only indicated the lowest order coupling, the $\cdots$ indicate higher order couplings which will explicitly involve the fields in the worldvolume theory.
+We have only indicated the lowest order coupling, the $\cdots$ indicate higher order couplings which will be higher order in the fields of the 11d theory and explicitly involve the fields in the worldvolume theory.
 
@@
 The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-For the embedding of the bosonic subalgebra, the roles of $\lie{sl}(4)$ and $\lie{sl}(2)$ are somewhat reversed for the $M2$ brane as compared to the $M5$ brane. 
 The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
@@
 
-\begin{lem}
+\begin{lem}\label{lem:m2emb}
 These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the 11-dimensional theory on $\CC^5 \times \RR$. 
@@
 \end{lem} 
-
+\begin{proof}
 The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
@@
 \end{itemize}
-
+\end{proof}
 \parsec[]
@@
 \label{prop:brads4}
-There exists $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
+There exist $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
 Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N F_{M2},-]$.
@@
 \begin{align*}
-\CC[w_1,\ldots, w_4] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
-\CC[w_1,\ldots, w_4] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
-\CC[w_1,\ldots, w_4] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) 
+\CC[w_1,\ldots, w_4] & \hookrightarrow H^0(\CC^4 \setminus 0, \cO) \\ 
+\CC[w_1,\ldots, w_4] \{\partial_{w_i}\} & \hookrightarrow H^0(\CC^4 \setminus 0, \T) \\
+\CC[w_1,\ldots, w_4] \{\d w_i\} & \hookrightarrow H^0(\CC^4 \setminus 0, \Omega^1) 
 \end{align*}
@@
 \begin{align*}
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^\bu(\CC^4 \setminus 0, \cO) \\ 
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_i}\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \T) \\
-(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\d w_i\} & \hookrightarrow H^\bu(\CC^4 \setminus 0, \Omega^1) .
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^3(\CC^4 \setminus 0, \cO) \\ 
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_i}\} & \hookrightarrow H^3(\CC^4 \setminus 0, \T) \\
+(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\d w_i\} & \hookrightarrow H^3(\CC^4 \setminus 0, \Omega^1) .
 \end{align*}
@@
 
-The embedding of $\lie{osp}(6|1)$ we wrote down above lives in the kernel of the original BRST operator $\delta^{(1)}$. 
+The embedding of $\lie{osp}(6|1)$ we wrote down in lemma \ref{lem:m2emb} lands in the kernel of the original BRST operator $\delta^{(1)}$. 
 To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [F] , - \big]$. 
@@
 In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of 11-dimensional supergravity.
+Decompose the eleven dimensional spacetime as $\C^3_z\times \C^2_w\times \R$.
 
@@
 \[
-I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega.
+I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega +\cdots 
 \]
@@
 
-To deduce the equations of motion we deform the 11-dimensional action by the term $I_{M_5}(\mu)$.
 Varying the potential $\div^{-1} \mu$, we obtain the following equation of motion involving the field $\gamma$:
@@
 
-The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
-\[
-\lie{sl}(4) \oplus \lie{sl}(2) .
-\]
-which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-
 Recall that we have chosen coordinates of the form
@@
 
-The embedding of the bosonic piece of $\lie{osp}(6|1)$ can be described as follows. 
+The embedding of the bosonic piece of $\lie{osp}(6|1)$ can be described as follows. Recall that the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
+\[
+\lie{sl}(4) \oplus \lie{sl}(2) .
+\]
+which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
+The roles of the $\lie{sl}(4)$ and $\lie{sl}(2)$ summands are interchanged compared to the case of the $M2$ brane.
 The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
@@
 
+\begin{proof}
 To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
@@
 
+\begin{proof}[Proof of Proposition \ref{prop:brads7}]
 Let $\cL (\CC^5 \times \RR \setminus \{w_1=w_2=t=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
@@
 This completes the proof.
+\end{proof}

### 2021-10-26 susy.tex
global editing

@@
 We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the 11-dimensional theory it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
-We will see how this central extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
+In order for this to be a symmetry of the 11-dimensional theory it is necessary toconsider an extension of the 11-dimensional supersymmetry algebra corresponding to the $M2$ brane.
+We will see how this extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
 
@@
 
-\subsection{Central extensions of the supersymmetry algebra} 
+\subsection{Extensions of the supersymmetry algebra} 
 \label{sec:m2brane}
@@
 
-The $M2$ brane algebra arises as a central extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
+The $M2$ brane algebra arises as an extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
 \[
@@
 \begin{dfn}
-The algebra $\m2$ is the $\ZZ \times \ZZ/2$-graded dg Lie algebra defined by the central extension of $\lie{siso}_{11d}$ by the cocycle $c_{M2}$.  
+The algebra $\m2$ is the $\ZZ \times \ZZ/2$-graded dg Lie algebra defined by the extension of $\lie{siso}_{11d}$ by the cocycle $c_{M2}$.  
 \end{dfn}
@@
 The supercharge $Q$ is odd and of cohomological degree zero.
-Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the central summand and is even of cohomological degree $+1$.
+Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the summand $\Omega^\bu(\R^11)[2]$ and is even of cohomological degree $+1$.
 Thus, only the totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
@@
 
-We now assume that $Q$ is a rank one, or minimal, supercharge satisfying $Q^2 = 0$.
+Let $Q$ be a rank one, or minimal, supercharge satisfying $Q^2 = 0$. We first determine $H^\bullet(\m2^q)$ as a super vector space.
 
-\begin{prop}\label{prop:susycoh}
+\begin{lem}
 As a $\ZZ/2$ graded space, the cohomology of the $Q$-twist $\m2^Q$ is
@@
 whose elements we denote by $(v, m, \psi, c)$.
+\end{lem}
+\begin{proof}
+The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
+The element $Q$ only acts nontrivially on the summands $\wedge^4 L$ and $\wedge^5 L$ in $S$. 
+The image of $\wedge^4 L \cong L^\vee$ trivializes the antiholomorphic translations while the image of $\wedge^5 L$ trivializes the time translation.
+So, of the translations, only the holomorphic ones, which live in $L$, survive.
+The map 
+\[
+[Q,-] \colon \lie{so}(11,\CC) \to S 
+\] 
+is the projection onto $\wedge^0 L \oplus \wedge^1 L \oplus \wedge^2 L$. 
+The kernel of $[Q,-]$ is the stabilizer~${\rm Stab}(Q)$.
 
+In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$.
+This completes the calculation of the cohomology. 
+\end{proof}
+
+The main result of this subsection is the following:
+\begin{prop}\label{prop:susycoh}
+The cohomology of the $Q$-twist $H^\bu(\m2^Q)$ has the following structures:
 \begin{enumerate}
-\item As a super Lie algebra, the cohomology of $\m2^Q$ is the natural extension of ${\rm Stab}(Q)$ together with the bracket
+\item As a super Lie algebra, $H^\bu(\m2^Q)$ is the natural extension of ${\rm Stab}(Q)$ together with the bracket
 \beqn\label{eqn:susy2bra}
@@
 
-One outcome of this proposition is that the dg Lie algebra $\m2^Q$ is {\em not} formal; there is a 3-ary $L_\infty$ bracket present in cohomology. 
-One way to prove the proposition above is to use homotopy transfer directly to $\m2^Q$, just as we did in \S \ref{s:ht} to deduce the form of the $3$-ary bracket. 
+One way to prove the proposition above is to use homotopy transfer directly to $\m2^Q$, just as we did in the proof of Theorem \ref{thm:global} to deduce the form of the $3$-ary bracket. 
 Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition \ref{prop:susycoh}.
@@
 \begin{proof}
-
-The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
-The element $Q$ only acts nontrivially on the summands $\wedge^4 L$ and $\wedge^5 L$ in $S$. 
-The image of $\wedge^4 L \cong L^\vee$ trivializes the antiholomorphic translations while the image of $\wedge^5 L$ trivializes the time translation.
-So, of the translations, only the holomorphic ones, which live in $L$, survive.
-The map 
-\[
-[Q,-] \colon \lie{so}(11,\CC) \to S 
-\] 
-is the projection onto $\wedge^0 L \oplus \wedge^1 L \oplus \wedge^2 L$. 
-The kernel of $[Q,-]$ is the stabilizer~${\rm Stab}(Q)$.
-
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$.
-This completes the calculation of the cohomology.
-
 We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L$ sit inside in the evident way.
@@
 \parsec[]
+We now proceed to the proof of proposition \ref{prop:susycoh}
 
+\begin{proof}[Proof of Proposition \ref{prop:susycoh}]
 Using the model $\fg$ the first part of Proposition \ref{prop:susycoh} follows immediately. 
@@
 It is an immediate calculation to show that these trees recover the formula in (2) of Proposition \ref{prop:susycoh}.
+\end{proof}
 
@@
 arising from the cubic term in $\frac12 \int \frac{1}{1-\nu} \mu^2 \del \gamma$. 
-To remedy the failure for $\Phi^{(1)}$ to preserve the brackets, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \times \fg \to \Pi \cL$ defined by 
+To remedy the failure for $\Phi^{(1)}$ to preserve the brackets, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \otimes \fg \to \Pi \cL$ defined by 
 \beqn\label{eqn:phi2}
@@
 
-\parsec[]
-
+\parsec[] From the previous proposition we can readily compare the super $L_\infty$ algebra $H^\bu(\m2^Q)$ with the global symmetry algebra of our theory.
+\begin{cor}
+There is a map of super $L_\infty$ algebras 
+\[
+H^\bu(\m2^Q)\to \Hat{E(5,10)}
+\]
+where $\Hat{E(5,10)}$ is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}
+\end{cor}
+\begin{proof}
 Because this map preserves differentials, it descends to a map in cohomology. 
@@
 Recall, that the linear BRST cohomology of the parity shift of the fields of the 11-dimensional theory is equivalent to the super $L_\infty$ 
-algebra $\Hat{E(5,10)}$ which is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}.
+algebra $\Hat{E(5,10)}$.
 Also, we described the $L_\infty$ structure present in the cohomology of $\m2^Q$ in part (2) of Proposition \ref{prop:susycoh}. 
 Each of these $L_\infty$ structure involved introducing a single new $3$-ary bracket, which are easily seen to be compatible. 
-
+\end{proof}
 \parsec[]

### 2021-10-26 susy.tex
whatever

--- 2021-10-15 susy.tex
@@
 \label{sec:susy}
-%m2brane
 
-In this section we consider the minimal twist of 11-dimensinoal supersymmetry explicitly. 
-We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the 11-dimensional theory it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
+In this section we consider the minimal twist of eleven-dimensinoal supersymmetry explicitly. 
+We compute the residual supersymmetry algebra given by taking the cohomology of the eleven-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
+In order for this to be a symmetry of the eleven-dimensional theory it is necessary to perform a central extension of the eleven-dimensional supersymmetry algebra by the $M2$ brane.
 We will see how this central extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
 
-\subsection{Supersymmetry in 11 dimensions}
+\subsection{Supersymmetry in eleven dimensions}
 \label{sec:11dsusy}
@@
 \]
-The $R$-symmetry is trivial in 11-dimensional supersymmetry.
+The $R$-symmetry is trivial in eleven-dimensional supersymmetry.
 
@@
 Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
-In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
+In eleven-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
 We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
@@
 Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of 11-dimensional supersymmetry \cite{SWspinor}. 
+Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of eleven-dimensional supersymmetry \cite{SWspinor}. 
 We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
@@
 Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition \ref{prop:susycoh}.
-This minimal model also has the advantage of being more directly related to the 11-dimensional supergravity theory.
+This minimal model also has the advantage of being more directly related to the eleven-dimensional supergravity theory.
 
@@
 
-\subsection{Embedding supersymmetry into the 11-dimensional theory} \label{s:residual}
+\subsection{Embedding supersymmetry into the eleven-dimensional theory} \label{s:residual}
 
@@
 \begin{prop}
-Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying 11-dimensional supergravity on $\CC^5 \times \RR$.
+Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying eleven-dimensional supergravity on $\CC^5 \times \RR$.
 There is a map of super $L_\infty$ algebras 
@@
 %where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
+In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
 \end{prop}
@@
 
-The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
+The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted eleven-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
 
@@
 This map does not preserve all of the brackets, however. 
-Indeed, in the 11-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
+Indeed, in the eleven-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
 \[
@@
 The relationship between the transferred $L_\infty$ structures can be described as follows. 
-Recall, that the linear BRST cohomology of the parity shift of the fields of the 11-dimensional theory is equivalent to the super $L_\infty$ 
+Recall, that the linear BRST cohomology of the parity shift of the fields of the eleven-dimensional theory is equivalent to the super $L_\infty$ 
 algebra $\Hat{E(5,10)}$ which is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}.

### 2021-10-26 susy.tex

--- 2021-10-26 susy.tex
@@
 \label{sec:susy}
-%m2brane
 
-In this section we consider the minimal twist of 11-dimensinoal supersymmetry explicitly. 
-We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the 11-dimensional theory it is necessary toconsider an extension of the 11-dimensional supersymmetry algebra corresponding to the $M2$ brane.
+In this section we consider the minimal twist of eleven-dimensional supersymmetry explicitly. 
+We compute the residual supersymmetry algebra given by taking the cohomology of the eleven-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
+In order for this to be a symmetry of the eleven-dimensional theory it is necessary to consider an extension of the eleven-dimensional supersymmetry algebra corresponding to the $M2$ brane.
 We will see how this extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
 
-\subsection{Supersymmetry in 11 dimensions}
+\subsection{Supersymmetry in eleven dimensions}
 \label{sec:11dsusy}
@@
 The relationship between the transferred $L_\infty$ structures can be described as follows. 
-Recall, that the linear BRST cohomology of the parity shift of the fields of the 11-dimensional theory is equivalent to the super $L_\infty$ 
+Recall that the linear BRST cohomology of the parity shift of the fields of the eleven-dimensional theory is equivalent to the super $L_\infty$ 
 algebra $\Hat{E(5,10)}$.

### 2021-10-26 draft.tex
reorganized index computation
merge
fixes?
draft merge
introes
big merge
reorganizing
abstract

@@
 
-\usepackage{macros-mtheory,amsaddr}
+\usepackage{macros-mtheory,amsaddr,tikz-feynman}
 
-\addbibresource{cfs.bib}
+\addbibresource{references.bib}
 
@@
 
-\title{Twisted 11-dimensional supergravity, I}
+\title{Twisted eleven-dimensional supergravity}
 \author{Surya Raghavendran}
@@
 Waterloo, Ontario N2L 2Y5\\ Canada}
-\email{??}
+\email{sraghavendran@perimeterinstitute.ca}
 \author{Ingmar Saberi}
@@
 \begin{abstract}
-to do
+We construct a fully interacting holomorphic theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds.
+The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold.
+Its field content matches the holomorphic twist of the free eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions  correctly  describe interacting twisted eleven-dimensional supergravity at the perturbative level.
+We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model.
+Twists of superconformal algebras map to the fields of our model on the complement of the support of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
 \end{abstract}
@@
 
+\vfill\eject
+
+\setcounter{tocdepth}{1}
 \tableofcontents
 
-\newpage
+\input{intro}
 
@@
 
+\input{nonmin}
+
 \input{dimred}
@@
 
-\input{index}
+%\input{index}
 
-\input{nonmin}
+\printbibliography
 

### 2021-10-26 dfn.tex
merge

--- 2021-10-25 dfn.tex
@@
 
-In this section we define the central theory of study within the Batalin--Vilkovisky formalism.
+In this section we define the central theory of study within the Batalin--Vilkovisky (BV) formalism. 
 The theory will be defined on any eleven-dimensional manifold of the form $X \times L$, where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
+
+In \cite{SWspinor}, we showed that the underlying free limit of the theory we consider here is the free limit of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$. 
+The goal of this section is to introduce interactions at the level of the minimal twist. 
+The main result is Theorem \ref{thm:dfn} where we show that the theory is consistent within the BV formalism.
+
+In the remainder of the paper we discuss further consistency with supersymmetry and string theory, but in this section we focus mostly on the theory as a partially holomorphic, partially topological, theory of gravity.
+Nevertheless, we do provide some preliminary justification towards the relationship to physical supergravity including a matching of indices in \S \ref{sec:locchar}.
 
@@
 Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
-If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on~$X$ with values in $V$.
-The $\dbar$ operator $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X,V)$ defines the Dolbeault complex of $V$:
+If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
+The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
 \[
@@
 \]
-This is a free (smooth) resolution for the sheaf of holomorphic sections of $V$.
+This is a free resolution for the sheaf of holomorphic sections of $V$.
 
@@
 
-The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra~\cite[\S 3.1.3]{CG2}.
-This means that, as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle, and its differential and Lie bracket are given by differential and bidifferential operators respectively.
+The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra, see see \cite[\S 3.1.3]{CG2}.
+This means that as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle and the differential and Lie bracket are given by differential and bidifferential operators, respectively.
 
@@
 The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\times k} \to \cL[2-k]$. 
-The condition that the differential $\delta_\cL$ is square-zero is equivalent to the higher Jacobi relations.
+The condition that the differential is square-zero $\delta_\cL \circ \delta_\cL = 0$ is equivalent to the higher Jacobi relations.
 
@@
 \deq[eq:newbase]{
+%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
     \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
@@
 Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
-(Here, and in what follows, we will use the symbol $\PV^{i,\bu}$ for the Dolbeault resolution of \emph{holomorphic polyvector fields;} by definition, this is the complex $\Omega^{0,\bu}(X,\wedge^i \T_X)$.)
 The first few nonzero brackets are
@@
 The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(S)$ is non polynomial. 
-In fact, it is related to the BCOV action functional via dimensional reduction (see \S \ref{sec:dimred}).
+In fact, it is related to the BCOV action functional via dimensional reduction, see \S \ref{sec:dimred}.
 Explicitly, this action functional is
@@
 Explicitly, the automorphism is
-\begin{equation}\label{eqn:auto1}
-  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} , \qquad
+\begin{multline}\label{eqn:auto1}
+  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} \\
   \beta \mapsto (\beta - \mu \vee \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
-\end{equation}
+\end{multline}
 
@@
 In this case, with $n = 5 + 1 - 1 = 5$ the theories described in this section are $\ZZ$-graded in the BV formalism.
-Momentarily, we consider a new term in the action which will break this grading; as such, this integer shift will not play an essential role.
+Momentarily, we consider a new term in the action which will break this grading, so this integer shift will not play an essential role.
 
@@
 We will break the $\ZZ$-grading present in BF theory discussed in the previous section to a $\ZZ/2$ grading. 
-For reference, this means that the linear cochain complex of fields of the model now takes the following form.
+For reference, this means that linear BRST complex of fields of the model now take the following form.
 
@@
 
-To define our classical field theory on $X \times S$, we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
+To define our classical field theory on $X \times S$ we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
 Such deformations are governed by the classical master equation: the parameterized family of actions 
@@
   }
-Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading (although it is even).
+Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading.
 
 This is completely reasonable from the point of view of twisting supersymmetry in eleven dimensions. 
-Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data~\label{CosHol,ESW}. 
+Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data \label{CosHol,ESW}.
+
 Nevertheless, if we break to the obvious $\ZZ/2$ grading, the functional $S_{BF} + g J$ defines an even action functional.
@@
 \deq{
-  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}\,.
+  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}.
 }
@@
   \deq{
-    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2}\, ;
+    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2};
   }
@@
 \]
-Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equation, and are equivalent as~$\ZZ/2$ graded BV theories.
+Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equations and are equivalent as~$\ZZ/2$ graded BV theories.
 
@@
 We consider the action $S_{BF, \infty} + gJ$.
-The equation of motion obtained by varying $\beta$ is especially simple---in fact linear---since $\beta$ only appears in the action via a quadratic term. 
+The equation of motion obtained by varying $\beta$ is especially simple, in fact linear, since it only appears in the action via a quadratic term. 
 It is
@@
 \]
-The component $\mu^{i;j}$ has parity $i+j+1 \pmod 2$. 
+The component $\mu^{i;j}$ has parity $i+j+1 \mod 2$. 
 \item $\nu = \sum_{i,j} \nu^{i;j}$ is a superfield where
@@
 \]
-The component $\nu^{i;j}$ has parity $i+j \pmod 2$. 
+The component $\nu^{i;j}$ has parity $i+j \mod 2$. 
 %The linear equations of motion state that $\mu$ is constant along $\RR$ and holomorphic divergence-free as a vector field on $\CC^5$. 
@@
 \]
-The component $\gamma^{i;j}$ has parity $i+j\pmod 2$. 
+The component $\gamma^{i;j}$ has parity $i+j$. 
 \item 
@@
 \]
-The component $\beta^{i;j}$ has parity $i+j+1 \pmod 2$. 
+The component $\beta^{i;j}$ has parity $i+j+1 \mod 2$. 
 \end{itemize}
@@
 We look closely at the geometric meaning of \eqref{eqn:eombeta}. 
-Let's make the simplifying assumption that all components of $\mu$ are divergence-free, and further that all fields are locally constant along $S$: that is, $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
-Then $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
+Let's make the simplifying assumption that all components of $\mu$ are divergence-free that all fields are locally constant along $S$: $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
+Then, $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
 Then, there is a component of \eqref{eqn:eomgamma} which can be written as 
@@
 
-To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where  $\gamma^{1;0}$, the $(0,1)$ Dolbeault part of $\gamma$, is zero. 
-Then, up to the term involving 
+To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where the $(0,1)$ Dolbeault part of $\gamma$ is zero $\gamma^{1;0} = 0$. 
+Then, up the term involving 
 \[
@@
 
-In~\cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here.
+In \cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here.
 Given this result, we can recognize many fields in the twisted theory as components of the physical fields of supergravity which remain after we twist.
@@
 \item 
-The components 
+The following components of $\mu$:
 \begin{align*}
@@
 \end{align*}
-of $\mu$ comprise components of the metric which remain after the twist. 
+comprise components of the metric which remain after the twist. 
 The components 
@@
 \]
-comprise the ghosts for infinitesimal (holomorphic) diffeomorphisms. 
+comprise the ghosts for infinitesimal diffeomorphisms. 
 \item 
-The three-form fields
+The following three-form fields
 \begin{multline}
@@
 
-We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$, where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
+We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$ where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
 On this background, the theory is manifestly $SU(5)$ invariant. 
@@
 This contributes 
-\begin{multline}
-\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} \times \\
-\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
-\end{multline}
+\[
+\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
+\] 
 Finally, there is a summand of the form 
@@
 
+Upon performing the $\Omega$-background,
 %see \S \ref{s:omega},
-In \cite{CostelloM5}, Costello argues that, upon performing the $\Omega$-background, the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
+In \cite{CostelloM5}, Costello argues that the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
 Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 

### 2021-10-26 susy.tex
merge

--- 2021-10-26 susy.tex
@@
 \label{sec:susy}
+%m2brane
 
-In this section we consider the minimal twist of eleven-dimensinoal supersymmetry explicitly. 
-We compute the residual supersymmetry algebra given by taking the cohomology of the eleven-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the eleven-dimensional theory it is necessary to perform a central extension of the eleven-dimensional supersymmetry algebra by the $M2$ brane.
+In this section we consider the minimal twist of 11-dimensional supersymmetry explicitly. 
+We compute the residual supersymmetry algebra given by taking the cohomology of the 11-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
+In order for this to be a symmetry of the 11-dimensional theory it is necessary to perform a central extension of the 11-dimensional supersymmetry algebra by the $M2$ brane.
 We will see how this central extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
 
-\subsection{Supersymmetry in eleven dimensions}
+\subsection{Supersymmetry in 11 dimensions}
 \label{sec:11dsusy}
@@
 \]
-The $R$-symmetry is trivial in eleven-dimensional supersymmetry.
+The $R$-symmetry is trivial in 11-dimensional supersymmetry.
 
@@
 Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
-In eleven-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
+In 11-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
 We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
@@
 Our model for the $M2$ brane algebra is a dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+
 Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
-
-The $M2$ brane algebra arises as a central extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
+The $M2$ brane algebra arises as a central extension of $\lie{siso}_{11d}$ by $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
 \[
@@
 Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
-Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of eleven-dimensional supersymmetry \cite{SWspinor}. 
+Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of 11-dimensional supersymmetry \cite{SWspinor}. 
 We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.
@@
 Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition \ref{prop:susycoh}.
-This minimal model also has the advantage of being more directly related to the eleven-dimensional supergravity theory.
+This minimal model also has the advantage of being more directly related to the 11-dimensional supergravity theory.
 
@@
 
-\subsection{Embedding supersymmetry into the eleven-dimensional theory} \label{s:residual}
+\subsection{Embedding supersymmetry into the 11-dimensional theory} \label{s:residual}
 
@@
 \begin{prop}
-Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying eleven-dimensional supergravity on $\CC^5 \times \RR$.
+Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying 11-dimensional supergravity on $\CC^5 \times \RR$.
 There is a map of super $L_\infty$ algebras 
@@
 %where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
-In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
+In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of 11-dimensional theory on $\CC^5 \times \RR$. 
 \end{prop}
@@
 
-The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted eleven-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
+The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted $11$-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
 
@@
 This map does not preserve all of the brackets, however. 
-Indeed, in the eleven-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
+Indeed, in the 11-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
 \[
@@
 The relationship between the transferred $L_\infty$ structures can be described as follows. 
-Recall, that the linear BRST cohomology of the parity shift of the fields of the eleven-dimensional theory is equivalent to the super $L_\infty$ 
+Recall, that the linear BRST cohomology of the parity shift of the fields of the 11-dimensional theory is equivalent to the super $L_\infty$ 
 algebra $\Hat{E(5,10)}$ which is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}.

### 2021-10-26 dfn.tex

--- 2021-10-26 dfn.tex
@@
 
-In this section we define the central theory of study within the Batalin--Vilkovisky formalism.
-The theory will be defined on any eleven-dimensional manifold of the form $X \times S$, where $X$ is a Calabi--Yau five-fold and $S$ is a smooth oriented one-manifold.
+In this section we define the central theory of study within the Batalin--Vilkovisky (BV) formalism. 
+The theory will be defined on any eleven-dimensional manifold of the form $X \times L$, where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.
+
+In \cite{SWspinor}, we showed that the underlying free limit of the theory we consider here is the free limit of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$. 
+The goal of this section is to introduce interactions at the level of the minimal twist. 
+The main result is Theorem \ref{thm:dfn} where we show that the theory is consistent within the BV formalism.
+
+In the remainder of the paper we discuss further consistency with supersymmetry and string theory, but in this section we focus mostly on the theory as a partially holomorphic, partially topological, theory of gravity.
+Nevertheless, we do provide some preliminary justification towards the relationship to physical supergravity including a matching of indices in \S \ref{sec:locchar}.
 

### 2021-10-26 dimred.tex
merge
reorganizing

@@
 \begin{tikzcd}
+- & + & - & + \\ \hline
                         &                          &                                     & {\PV^{0,\bu}}    \\
@@
 The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields 
-\beqn\label{eqn:IIAfields}. 
+\beqn\label{eqn:IIAfields}
 \alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).
 \eeqn
-The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
+The classical interaction takes the form \[I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + \cdots\]
 %The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
@@
 
-In fact, we might as well assume that $M$ is a point and that the space of fields is of the form $\Omega^{0,\bu}(V) \otimes W$ for $W$ some graded vector space. 
+For illustrative purposes, let us first assume that $M$ is a point and that the space of fields is of the form $\Omega^{0,\bu}(V) \otimes W$ for $W$ some graded vector space. 
 As properly formulated in \cite{ESW}, it is shown that the dimensional reduction along $V \to V_\RR$ is equivalent to the theory whose fields are $\Omega^\bu(V_\RR) \otimes W$. 
@@
 The first term in this equation agrees precisely with the second term in \eqref{eqn:IIAactionpot}. 
-The final term is cohomological trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
+The final term is cohomologically trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
 %
@@
 We now turn to a different type of redution of the 11-dimensional theory, this time involving type I supergravity. 
-In this section, we briefly recall the description of type I supergravity following \cite{CLtypeI} which was motivated by the unoriented $B$-model. 
+We begin by briefly recalling the description of type I supergravity following \cite{CLtypeI} which was motivated by the unoriented $B$-model. 
 In \cite{SWspinor}, the second two authors verified the conjectural description of the space of fields recalled below using the pure spinor formalism. 
@@
 
-\subsection{Slab compactification}
+\subsection{Slab compactification}\label{s:Ired}
 
@@
 \]
-Moreover, these boundary conditions carry non linear BRST endowing their parity shifts $\Pi \cM_{t=0} , \Pi\cM_{t=1}$ with the structures of $L_\infty$ algebras. 
+Moreover, these boundary conditions carry non linear BRST operators endowing their parity shifts $\Pi \cM_{t=0} , \Pi\cM_{t=1}$ with the structures of $L_\infty$ algebras. 
 These $L_\infty$ structures must be compatible with the one on the phase space.
@@
 \]
-To place the theory on $\CC^5 \times [0,1]$ we take the same boundary condition at $t=1$:
+We will place the theory on $\CC^5 \times [0,1]$ by imposing the same boundary condition at $t=1$:
 \[
@@
 \begin{prop}
-With these boundary conditions of the classical 11-dimensional theory on $\CC^5 \times [0,1]$, the compactification along 
+With these boundary conditions for the classical 11-dimensional theory on $\CC^5 \times [0,1]$, the dimensional reduction along 
 \[
@@
 
-\subsection{Compactification along a CY3}
+\subsection{The $SU(5)$ twist of type IIA supergravity}
+\label{s:su5IIA}
+
+%\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}
+
+Thus, given that our 11-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction.
+This results in a $SU(5)$ invariant, holomorphic, theory on $\CC^5$.
+
+Let us briefly spell out the fields present in this dimensional reduction. 
+The reduction is obtained by replacing $\Omega^\bu(\RR)$ with its translation invariant subalgebra $\CC[\ep] = \CC[\d t]$. 
+Here, $\ep$ is an odd parameter playing the role of the translation invariant one-form $\d t \in \Omega^1(\RR)$. 
+Equivalently, we are compactifying the theory along 
+\[
+\CC^5 \times S^1 \to \CC^5 .
+\]
+
+The 11-dimensional the field $\mu_{11d}$ is replaced by the field 
+\[
+\mu + \ep \mu' \in \Pi \PV^{1,\bu}(\CC^5) [\ep] .
+\]
+Notice that the lowest component of $\mu$ is odd (just like $\mu_{11d})$, but the lowest component of $\mu'$ is now even. 
+Completely similarly, the remaining fields reduce as $\nu + \ep \nu'$, $\gamma + \ep \gamma'$, and $\beta + \ep \beta'$.
+
+In summary, the linear complex of fields of the dimensionally reduced theory on $\CC^5$ is
+\begin{equation}
+  \label{eqn:IIAsu5} 
+  \begin{tikzcd}[row sep = 1 ex]
+    {\rm odd} & {\rm even} & {\rm even} & {\rm odd} \\ \hline
+    \PV^{1,\bu}(\CC^5)_{\mu} \ar[r, "\del"] & \PV^{0,\bu}(\CC^5)_\nu & \\ 
+     & \ep\Omega^{0,\bu}(\CC^5)_{\beta'} \ar[r, "\div"] & \ep\Omega^{1,\bu}(\CC^5)_{\gamma'} . \\
+     &  \ep \PV^{1,\bu}(\CC^5)_{\mu'} \ar[r, "\div"] & \ep \PV^{0,\bu}(\CC^5)_{\nu'} \\
+     & & \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\div"] & \Omega^{1,\bu}(\CC^5)_\gamma.
+\end{tikzcd}
+\end{equation}
+
+We can compute the dimensional reduction of the 11-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
+We arrive at the action functional described below.
+
+\begin{conj}
+\label{conj:IIAsu5}
+The $SU(5)$ twist of type IIA supergravity on $\CC^5$ is equivalent to the theory whose linear BRST complex of fields is displayed in \eqref{eqn:IIAsu5}. 
+The full action functional is 
+\begin{multline}
+\label{eqn:su5action}
+\int^\Omega_{\CC^5}\bigg(\beta' \wedge \dbar \nu + \beta \wedge \dbar \nu' + \gamma' \wedge \dbar \mu + \gamma \wedge \dbar \mu' +  \beta' \wedge \div \mu + \beta \wedge \div \mu' \bigg) \\
++ \int^\Omega_{\CC^5} \bigg( \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma' +  \frac{1}{1-\nu} (\mu \wedge \mu') \vee \del \gamma' + \frac12 \frac{\nu'}{(1-\nu)^2} \mu^2 \vee \del \gamma \bigg) \\
++ \frac12 \int_{\CC^5} \gamma' \wedge \del \gamma \wedge \del \gamma .
+\end{multline} 
+\end{conj}
+
+The first two lines in \eqref{eqn:su5action} arise from the reduction of the BF action $S_{BF,\infty}$. 
+The final line arises from the reduction of $J = \frac16 \int \gamma_{11d} \del \gamma_{11d} \del \gamma_{11d}$.
+
+%\parsec[]
+%
+%
+%We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
+%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
+%
+%A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
+%In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following. 
+%
+%\begin{prop}
+%As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
+%\end{prop}
+
+\parsec[]\label{s:orbifold}
+
+The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the 11-dimensional theory. 
+We offer another point of view of this $S^1 / \ZZ/2$ reduction.
+
+First off, there is the following $\ZZ/2$ action on the 11-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
+We obtain it by the following tensor product of $\ZZ/2$ actions. 
+First, $\ZZ/2$ acts on $\Omega^\bu(S^1)$ by orientation reversing diffeomorphisms. 
+Second, we declare that the eigenvalue of the $\ZZ/2$ action on $\PV^{k,\bu}(\CC^5)$, for $k=0,1$ is $+1$ and the eigenvalue of the $\ZZ/2$ action on $\Omega^{k,\bu}(\CC^5)$ for $k=0,1$ is $-1$. 
+This determines a $\ZZ/2$ action on the full space of fields of the 11-dimensional theory.
+
+Upon $S^1$ compactification the $\ZZ/2$ action is easy to describe: $\mu,\nu$ both have eigenvalue $+1$, $\mu',\nu'$ both have eigenvalue $-1$, $\gamma,\beta$ both have eigenvalue $-1$, and $\gamma',\beta'$ both have eigenvalue $+1$.
+In particular, we see that the $\ZZ/2$ fixed points simply pick out the $\mu, \nu, \gamma', \beta'$ fields; this comprises the first two lines of \eqref{eqn:IIAsu5}.
+
+The fields match precisely with the fields in the twist of type I supergravity that we recalled in \S \ref{s:typeIpot} (Under the relabeling $\gamma' \leftrightarrow \til \gamma, \beta' \leftrightarrow \til \beta$).
+Furthermore, restricting the action in the above conjecture agrees precisely with the action of this twisted type I model.
+
+\subsection{Compactification along a CY3}\label{s:CY3}
 
@@
 The twist of the gravity multiplet is less clear. 
-A thorough computation of the twist has yet to appear, though some checks have been established by Elliott and the last author in \cite{EWpois}. 
+A thorough computation of the twist has yet to appear, though some checks have been established by Elliott and the last author in \cite{EWpoisson}. 
 We give a description of the twist now, but leave a detailed computation from first principles to future work.
@@
 The gravity multiplet, see \cite{CCDF} for instance, consists of a graviton $e$, a gravitino $\psi$, and a one-form gauge field $\cA_{grav}$.
-After twisting, the graviton and components of gravitino decompose into two Dolbeault-de Rham valued fields 
+After twisting, the graviton and components of the gravitino decompose into two Dolbeault-de Rham valued fields 
 \[
@@
 
+\begin{proof}
 Consider the 11-dimensional field $\nu_{11d}$. 
@@
 This completes the proof. 
+\end{proof}
 
@@
 %\brian{incomplete}
-
-\subsection{The $SU(5)$ twist of type IIA supergravity}
-\label{s:su5IIA}
-
-%\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}
-
-Thus, given that our 11-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction.
-This results in a $SU(5)$ invariant, holomorphic, theory on $\CC^5$.
-
-Let us briefly spell out the fields present in this dimensional reduction. 
-The reduction is obtained by replacing $\Omega^\bu(\RR)$ with its translation invariant subalgebra $\CC[\ep] = \CC[\d t]$. 
-Here, $\ep$ is an odd parameter playing the role of the translation invariant one-form $\d t \in \Omega^1(\RR)$. 
-Equivalently, we are compactifying the theory along 
-\[
-\CC^5 \times S^1 \to \CC^5 .
-\]
-
-The 11-dimensional the field $\mu_{11d}$ is replaced by the field 
-\[
-\mu + \ep \mu' \in \Pi \PV^{1,\bu}(\CC^5) [\ep] .
-\]
-Notice that the lowest component of $\mu$ is odd (just like $\mu_{11d})$, but the lowest component of $\mu'$ is now even. 
-Completely similarly, the remaining fields reduce as $\nu + \ep \nu'$, $\gamma + \ep \gamma'$, and $\beta + \ep \beta'$.
-
-In summary, the linear complex of fields of the dimensionally reduced theory on $\CC^5$ is
-\begin{equation}
-  \label{eqn:IIAsu5} 
-  \begin{tikzcd}[row sep = 1 ex]
-    {\rm odd} & {\rm even} & {\rm even} & {\rm odd} \\ \hline
-    \PV^{1,\bu}(\CC^5)_{\mu} \ar[r, "\del"] & \PV^{0,\bu}(\CC^5)_\nu & \\ 
-     & \ep\Omega^{0,\bu}(\CC^5)_{\beta'} \ar[r, "\div"] & \ep\Omega^{1,\bu}(\CC^5)_{\gamma'} . \\
-     &  \ep \PV^{1,\bu}(\CC^5)_{\mu'} \ar[r, "\div"] & \ep \PV^{0,\bu}(\CC^5)_{\nu'} \\
-     & & \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\div"] & \Omega^{1,\bu}(\CC^5)_\gamma.
-\end{tikzcd}
-\end{equation}
-
-We can compute the dimensional reduction of the 11-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
-We arrive at the action functional described below.
-
-\begin{conj}
-\label{conj:IIAsu5}
-The $SU(5)$ twist of type IIA supergravity on $\CC^5$ is equivalent to the theory whose linear BRST complex of fields is displayed in \eqref{eqn:IIAsu5}. 
-The full action functional is 
-\begin{multline}
-\label{eqn:su5action}
-\int^\Omega_{\CC^5}\bigg(\beta' \wedge \dbar \nu + \beta \wedge \dbar \nu' + \gamma' \wedge \dbar \mu + \gamma \wedge \dbar \mu' +  \beta' \wedge \div \mu + \beta \wedge \div \mu' \bigg) \\
-+ \int^\Omega_{\CC^5} \bigg( \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma' +  \frac{1}{1-\nu} (\mu \wedge \mu') \vee \del \gamma' + \frac12 \frac{\nu'}{(1-\nu)^2} \mu^2 \vee \del \gamma \bigg) \\
-+ \frac12 \int_{\CC^5} \gamma' \wedge \del \gamma \wedge \del \gamma .
-\end{multline} 
-\end{conj}
-
-The first two lines in \eqref{eqn:su5action} arise from the reduction of the BF action $S_{BF,\infty}$. 
-The final line arises from the reduction of $J = \frac16 \int \gamma_{11d} \del \gamma_{11d} \del \gamma_{11d}$.
-
-%\parsec[]
-%
-%
-%We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
-%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
-%
-%A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
-%In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following. 
-%
-%\begin{prop}
-%As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
-%\end{prop}
-
-\parsec[]
-
-The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the 11-dimensional theory. 
-We offer another point of view of this $S^1 / \ZZ/2$ reduction.
-
-First off, there is the following $\ZZ/2$ action on the 11-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
-We obtain it by the following tensor product of $\ZZ/2$ actions. 
-First, $\ZZ/2$ acts on $\Omega^\bu(S^1)$ by orientation reversing diffeomorphisms. 
-Second, we declare that the eigenvalue of the $\ZZ/2$ action on $\PV^{k,\bu}(\CC^5)$, for $k=0,1$ is $+1$ and the eigenvalue of the $\ZZ/2$ action on $\Omega^{k,\bu}(\CC^5)$ for $k=0,1$ is $-1$. 
-This determines a $\ZZ/2$ action on the full space of fields of the 11-dimensional theory.
-
-Upon $S^1$ compactification the $\ZZ/2$ action is easy to describe: $\mu,\nu$ both have eigenvalue $+1$, $\mu',\nu'$ both have eigenvalue $-1$, $\gamma,\beta$ both have eigenvalue $-1$, and $\gamma',\beta'$ both have eigenvalue $+1$.
-In particular, we see that the $\ZZ/2$ fixed points simply pick out the $\mu, \nu, \gamma', \beta'$ fields; this comprises the first two lines of \eqref{eqn:IIAsu5}.
-
-The fields match precisely with the fields in the twist of type I supergravity that we recalled in \S \ref{s:typeIpot} (Under the relabeling $\gamma' \leftrightarrow \til \gamma, \beta' \leftrightarrow \til \beta$).
-Furthermore, restricting the action in the above conjecture agrees precisely with the action of this twisted type I model.

### 2021-10-26 intro.tex

@@
 \begin{conj}
-The eleven-dimensional partially holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$ where the bosonic ghost takes value the holomorphic supercharge.
+The eleven-dimensional  holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$, where the bosonic ghost takes a value corresponding to a holomorphic supercharge.
 \end{conj}
@@
 In \S\ref{sec:susy}, we will show that this theory has all of the expected residual supersymmetries present after performing the holomorphic twist.
-\item
-In \S\ref{sec:ads} we propose a description of supergravity in twisted versions of both the ${\rm AdS}_7$ and ${\rm AdS}_4$ backgrounds. 
-We show that the residual symmetries of supergravity in these backgrounds are present in our twisted background.
+
 \item
@@
 We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in~\cite{RY}.  
-\item Finally, in \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
+\item In \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
 For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity in~\cite{CLsugra}.
+\item
+Finally, in \S\ref{sec:ads}, we propose a description of supergravity in twisted versions of both the ${\rm AdS}_7$ and ${\rm AdS}_4$ backgrounds. 
+We show that the residual symmetries of supergravity in these backgrounds are present in our twisted background.
 \end{itemize}

### 2021-10-26 matrix.tex

@@
 whose elements we denote by $\alpha$. 
-Besides the natural module structure, there is an odd $\times$ odd $\to$ even bracket. 
+Besides the natural module structure, there is odd bracket $ E(5,10)_-\otimes E(5,10)_\to E(5,10)_+$
 The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$, and is defined by
@@
 
-We complete the proof of the first part of Theorem \ref{thm:global}. 
-For this we write down an explicit map between the cohomology computed above and the algebra $E(5,10)$.
+Having described the linearized BRST cohomology as a super vector space, we turn to the proof of Theorem \ref{thm:global}.
+
+\begin{proof}[Proof of Theorem \ref{thm:global}]
+For the first part, we write down an explicit map between the cohomology computed above and the algebra $E(5,10)$.
 
@@
 It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E(5,10)$ and the twist of eleven-dimensional supergravity. 
-This completes the proof of part (1) of Theorem \ref{thm:global}.
+This completes the proof of part (1).
 
-\subsection{(Non)formality and homotopy transfer} 
-\label{s:ht}
-We proceed to the proof of part (2) of Theorem \ref{thm:global}. 
-To do this, we first produce the following homotopy data:
+For part (2), we first produce the following homotopy data:
 \begin{equation}
@@
 \begin{itemize}
-\item On the $\nu$'s we take $K$ be any operator $K \colon \cO \to \Vect$ such that $\div K \nu = \nu$. 
-On the $\gamma$'s we take $K$ be any operator $K \colon \Omega^1 \to \Omega^0$ such that $\del K(\gamma) = \gamma$. 
+\item On the $\nu$'s we take $K$ to be any operator $K \colon \cO \to \Vect$ such that $\div K \nu = \nu$. 
+On the $\gamma$'s we take $K$ to be any operator $K \colon \Omega^1 \to \Omega^0$ such that $\del K(\gamma) = \gamma$. 
 Also, introduce the auxiliary operator $\til{K} \colon \Omega^2_{cl} \to \Omega^1$ which satisfies the homotopy relation
@@
 Since $b$ is central, this cocycle defines a central extension of $E(5,10)$.
+\end{proof}
 

### 2021-10-26 draft.tex
merge

@@
 \begin{abstract}
-We construct a fully interacting holomorphic theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds.
-The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold.
-Its field content matches the holomorphic twist of the free eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions  correctly  describe interacting twisted eleven-dimensional supergravity at the perturbative level.
+We construct a fully interacting partially holomorphic, partially topological, theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
+%The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
+The theory describes, in part, a particular deformation of the moduli space of complex structures on the fivefold.
+Its field content matches the holomorphic (or minimal) twist of the 
+%free 
+eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions  correctly  describe interacting twisted eleven-dimensional supergravity at the perturbative level.
 We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model.
@@
 
-%\input{index}
-
 \printbibliography
@@
 
-\appendix
-
-\section{An alternative description of the 11-dimensional theory} 
-In \S \ref{s:dfn} we have described a family of BV theories on $X \times L$ where $X$ is an odd-dimensional Calabi--Yau manifold and $L$ is an odd-dimensional smooth manifold. 
-The space of fields \eqref{eq:sympfields} is equipped with an odd symplectic pairing.
-
-There is a related, alternative description of this formal moduli space which is almost equivalent. 
-Consider the resolution of holomorphic closed two-forms 
-\beqn\label{eqn:twoform}
-\Omega_{cl}^{2,hol}(X) \simeq \Omega^{2,\bu}(X) \xto{\del} \Omega^{3,\bu}(X)[-1] \to \cdots 
-\eeqn
-where we have left the $\dbar$-differential implicit, as always.
-
-There is a map from the two-term complex 
-\[
-\Omega^{0,\bu}(X)[1] \to \Omega^{1,\bu}(X)
-\]
-to the resolution \eqref{eqn:twoform} defined by the holomorphic de Rham operator $\del$. 
-This map is almost a quasi-isomorphism of sheaves; it differs by copy of constant functions $\CC[1]$ in cohomological degree $-1$.
-
-Similarly, we can tensor with the dg algebra of de Rham forms on $L$ to obtain a map of $\ZZ/2$-graded cochain complexes
-\[
-\bigg(\Pi \Omega^{0,\bu}(X;L) \xto{\del} \Omega^{1,\bu}(X;L) \bigg) \xto{\del} \bigg(\Omega^{2,\bu}(X;L) \xto{\del} \Pi \Omega^{3,\bu}(X;L) \to \cdots \bigg) .
-\]
-Again, this map is a quasi-isomorphism up to a copy of $\Pi \CC$.
-The left-hand side contains the fields $(\beta, \gamma)$. 
-This map has the effect of sending $\beta \mapsto 0$ and $\gamma \mapsto \partial \gamma \in \Omega^{2,\bu}(X;L)$.
-
-The basic idea is to replace the complex where $(\beta,\gamma)$ live by this resolution of closed two-forms. 
-The new space of fields is 
-\begin{equation}
-  \label{eq:poissfields} 
-  \begin{tikzcd}[row sep = 1 ex]
-     - & + & - & + \\ \hline
-     \PV^{1,\bu}(X; L) \ar[r, "\div"] & \PV^{0,\bu}(X; L) \\
-     & \Omega^{2,\bu}(X;L) \ar[r, "\del"] & \Omega^{3,\bu}(X;L) \ar[r] & \cdots 
-\end{tikzcd}
-\end{equation}
-
-It may seem that this description of the fields of the 11-dimensional theory is not much different than the original formulation---at the level of the free theory they only differ by a copy of constant functions in odd cohomological degree.
-We'd like to point out two main differences:
-\begin{itemize}
-\item This new description does not have the structure of a BV theory in the usual sense; there is no odd symplectic pairing on the fields. 
-Nevertheless, there is still an odd Poisson bracket acting on functionals of the fields which we will describe momentarily. 
-For this reason, we will refer to the theory as a ``Poisson BV theory''. 
-\item With the existence of the odd Poisson bracket one might be optimistic to formulate the CME for this Poisson BV theory.
-However, there is no local interaction which is consistent with the local interaction present in the original BV theory. 
-Nevertheless, the (shift of the) fields is equipped with an $L_\infty$ structure which is compatible with the odd Poisson bracket. 
-\end{itemize}
-
-\begin{prop}
-The complex \eqref{eq:poissfields} is equipped with the structure of an interacting Poisson BV theory.
-Let $\cG = \cG(X \times L)$ be the resulting $L_\infty$ algebra...
-\end{prop}
-
-Heuristically, we can write the action in the following non-local form
-\[
-\frac{1}{1-\nu} \mu^2 \eta + (\del^{-1} \eta) \eta^2 .
-\]
-\brian{are there more terms involving higher forms?}
-
-The first few nonzero brackets are
-\begin{align*}
-[\mu]_1 & = \dbar \mu + \div \mu \\
-[\eta]_1 & = \dbar \eta + \del \eta \\ 
-[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
-[\mu, \eta]_2 & = \mu \vee \del \eta \\
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
-[\nu, \mu,\eta]_3 & = \nu \mu \del \eta
-\end{align*}
-\brian{coefficients}
-For $k \geq 2$ the general formula for the $k$-ary bracket is 
-\begin{align*}
-[\eta_1,\eta_2]_2 & = \# \Omega^{-1} \vee (\eta_1 \wedge \eta_2)  \\
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \# \div(\nu_1 \cdots \nu_{k-2} \mu_1 \wedge \mu_2) \\ 
-[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu,\eta]_{k} & = \# \nu_1 \cdots \nu_{k-2} (\mu \vee \del \eta) .
-\end{align*}
-
-\parsec[]
-Consider the theory on $\CC^3 \times \RR$. 
-There is a quasi-isomorphism of $L_\infty$ Lie algebras $\CC \simeq \cG (\CC^3 \times \RR)$.
-
-\parsec[]
-Consider the theory on $\CC^5 \times \RR$.
-
-\begin{prop}
-There is a quasi-isomorphism of super $L_\infty$ algebras 
-\[
-E(5,10) \xto{\simeq} \cG(\CC^5 \times \RR) .
-\]
-This lifts to map of super $L_\infty$ algebras $E(5,10) \to \cL(\CC^5 \times \RR)$ whose kernel is $\CC$.
-\end{prop}
-
-\section{BCOV stuff}
-
-\subsection{Relation to BCOV theory}
-
-\parsec[sec:pv] 
-\ingmar{a section defining polyvector fields; not sure where this belong}
-Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
-\deq{
-  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
-}
-\ingmar{Wedges look super fucked up}
-The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$.
-Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex.
-We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.
-
-\subsubsection{}
-It will be convenient for us to cast this dg Lie algebra in a slightly different way.
-We construct a different model for the Lie algebra of divergence-free vector fields whose underlying cochain complex is the same as \eqref{eqn:cplx1}. 
-The distinguishing feature is that this model is no longer a dg Lie algebra, but an $L_\infty$ algebra.
-
-The model we use is motivated by the topological string, specifically the description of the closed topological string in terms of Kodaira--Spencer theory \cite{BCOV}.
-We recall the requisite background, but refer to \cite{CLbcov1,CLbcov2,CLtypeI} for more details.
-
-Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
-Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
-In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
-With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.
-
-Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
-\beqn\label{eqn:pv1}
-\PV^{\bu,\bu} [[u]] [1]
-\eeqn
-with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
-With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.
-
-The Schouten--Nijenhuis bracket 
-\[
-[-,-] \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
-\]
-extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
-We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
-We refer to the further cohomological shift 
-\[
-\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
-\]
-as the space of fields of Kodaira--Spencer theory.
-
-Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.
-
-\subsubsection{}
-
-\brian{bv bracket}
-
-\subsubsection{}
-
-Together with the linear BRST differential $Q_{KS}$, the bracket $\{-,-\}_{KS}$ induces the structure of a dg Lie algebra the cohomological shift of the space of local functionals $\oloc(\cE_{KS})[-2d+5]$.
-
-\begin{thm}[\cite{CLbcov1}]
-The BCOV action 
-\[
-I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
-\]
-satisfies the classical master equation 
-\[
-Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_{KS} = 0 .
-\]
-In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
-\end{thm}
-
-This action induces the square-zero operator 
-\[
-\delta_{BCOV} = Q_{KS} + \{I_{BCOV}, -\} 
-\]
-acting on observables of the Kodaira--Spencer fields. 
-In other words, it defines a non-linear BRST operator; in turn it
-induces an $L_\infty$ structure $\{[-]_k\}_{k =1,2,3,\ldots}$ on the complex \eqref{eqn:pv1} whose linear operation is $[-]_1 = Q_{KS} = \dbar + u\div$.
-
-This $L_\infty$ structure is clearly not identical as the strict dg Lie algebra structure (it has operations of arbitrary high order). 
-Nevertheless, it is equivalent to the strict dg Lie model: there is an $L_\infty$ automorphism which exchanges the two structures.
-
-It is easiest to describe this automorphism at the level of observables.
-Use the notation $\Sigma$ for a linear observable of the Kodaira--Spencer fields $\cE_{KS}$. 
-Then, the Kodaira--Spencer dg Lie algebra structure induces the non-linear BRST operator $\delta_{KS}$ given by
-\[
-\delta_{KS} (\Sigma) = Q_{KS} \Sigma + \frac12 [\Sigma,\Sigma] .
-\]
-
-The non-linear change of coordinates relating the two structures is defined by
-\[
-\Psi \colon \Sigma \mapsto \left[u (e^{\Sigma/u} -1)\right]_+
-\]
-where $[-]_+$ projects onto the non-negative powers of $u$.
-
-\parsec[]
-
-The complex resolving the (shift of) divergence-free vector fields 
-\[
-\left(\PV^{1,\bu}[1] \oplus u \PV^{0,\bu}[2] \, , \, \dbar + u \div\right) 
-\]
-is a subcomplex of $\cE_{KS}$.
-If $d = \dim_\CC(X)=3$ then the shifted Poisson bivector $\Pi_{BCOV}$ restricts to a shifted Poisson bivector on this subcomplex. 
-In particular, the action $I_{BCOV}$ restricts to a solution to the classical master equation for this subcomplex.
-
-If $d \ne 3$ then there is the following subcomplex $\til{\cE}_{KS}\subset \cE_{KS}$ defined by:
-\beqn\label{eqn:tilks}
-\begin{tikzcd}
-\ul{-1} & \ul{0} & \cdots & \ul{d-4} & \ul{d-3} & \cdots    \\
-\PV^{1,\bu} \ar[r] & u\PV^{0,\bu} & & & & &  \\
-& & & \PV^{d-2, \bu} \ar[r] & u \PV^{d-3, \bu} \ar[r] & \cdots &   .
-\end{tikzcd}
-\eeqn
-And one can check that the shifted Poisson bivector restricts to a shifted Poisson bivector on this subcomplex. 
-Thus, we have the following.
-
-\begin{prop}
-\label{prop:tilbcov}
-The BCOV action $I_{BCOV}$ restricts to a solution of the classical master equation on $\til{\cE}_{KS}$ that we denote by $\til{I}_{BCOV}$. 
-\end{prop}
-
-\subsubsection{}
-
-Define the action by the group $\CC^\times$ on the complex $\til{\cE}_{KS}$ as follows.
-Declare the first line in \eqref{eqn:tilks} is weight zero and the second line is weight $+1$. 
-%Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
-The linear BRST operator is clearly weight zero and the shifted Poisson structure $\Pi_{KS}$ is of weight $+1$. 
-Thus, the shifted Poisson bracket $\{-,-\}_{KS}$ is of $\CC^\times$ weight $+1$.
-
-\begin{lem}
-The restricted action $\til{I}_{BCOV}$ has $\CC^\times$ weight $-1$. 
-In particular, the non-linear BRST operator 
-\beqn\label{eqn:KSbrst}
-\delta_{BCOV} = Q_{KS} + \{\til{I}_{BCOV},-\}_{KS}
-\eeqn
-is $\CC^\times$ weight zero.
-\end{lem}
-\begin{proof}
-%The map $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$ preserves $\CC^\times$ weight, so it suffices to prove that $\til{I}_{BCOV}$ is weight $+1$. 
-We will make use of two gradings on $\til{\cE}_{KS}$. 
-The first is holomorphic polyvector field type, and the second is descendant degree.
-The summand $u^l \PV^{k,\bu}$ is polyvector type $k$ and descendant degree $l$.
-
-We introduce notation in this proof that won't be used later on. 
-Let $\alpha$ denote a super field living in the first line of \eqref{eqn:tilks} and let $\beta$ denote a super field living in the second line of \eqref{eqn:tilks}.
-If a field of type $\alpha$ has polyvector type $k$ then it has descendant degree $1-k$, $k=0,1$. 
-If a field of type $\beta$ has polyvector type $l$ then it has descendant degree $d-2-l$.
-
-A homogenous polynomial degree term in the BCOV action $I_{BCOV}$ is a linear combination of functionals of the form
-\[
- \alpha_1 \wedge \cdots \wedge \alpha_m \wedge \beta_1 \wedge \cdots \wedge \beta_n  .
-\]
-Let $k_i$ be the polyvector field type of $\alpha_i$ and let $l_j$ be the polyvector field type of $\beta_j$. 
-In order for this expression to contribute nontrivially to the BCOV action two constraints must hold:
-\begin{align*}
-\sum_{i=1}^m k_i + \sum_{j=1}^n l_j & = d \\
-\sum_{i=1}^m (1-k_i) + \sum_{j=1}^n (d-2-l_j) & = m+n-3 .
-\end{align*}
-The first constraint ensures that the integrand is of top polyvector degree. 
-The second constraint is on the descendant degree, see \brian{ref above}.
-
-Simplifying these two equations, one finds the condition
-\[
-m+n-3 = m+(d-2)n - d 
-\]
-which implies $n=1$, as desired. 
-\end{proof}
-
-Consider the cochain complex $\left(\oloc(\til{\cE}_{KS}) \, , \, \delta_{KS} \right)$ of all local functionals equipped with the non-linear BRST differential \eqref{eqn:KSbrst}.  
-The $\CC^\times$ weight zero subcomplex is 
-\[
-\big(\oloc(\til\cE_{KS})^{(0)} \, , \, \delta_{KS} \big) = \big(\oloc(\cE_0) \, , \, \delta_{KS} \big) 
-\]
-where $\cE_0 = \PV^{1,\bu}[1] \oplus u \PV^{0,\bu}$ is the subcomplex of the fields $\til\cE_{KS}$ comprising the first line of \eqref{eqn:tilks}.
-
-\begin{prop}
-\label{prop:Linfty}
-The differential $\delta_{KS}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
-\[
-\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
-\]
-with $[-]_1 = \dbar + \div$. 
-Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
-\end{prop}
-
-%Applying this to the $k$th exterior power of the holomorphic tangent bundle $V = \wedge^k \T_X$, we obtain a resolution of the sheaf of $k$-linear polyvector fields which we denote by $\PV^{k,\bu} (X) = \Omega^{0,\bu}(X, \wedge^k \T_X)$.
-
-%\subsubsection{}
-%
-%Consider the following cochain complex $\cE_{pot}$:
-%\beqn\label{eqn:E}
-%\begin{tikzcd}
-%\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
-%\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
-%& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
-%\end{tikzcd}
-%\eeqn
-%We will refer to the components of the fields using the notation
-%\begin{align*}
-%(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
-%(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
-%\end{align*}
-%The expressions $\mu,\nu,\beta,\gamma$ are still super fields in the sense that they have components in all anti-holomorphic Dolbeault degree. 
-%
-%Let 
-%\[
-%\begin{array}{rccc}
-% \colon \Omega_c^{0,\bu}(X) & \to & \CC [??] \\
-%\alpha & \mapsto & \int_{X} \Omega \wedge \alpha 
-%\end{array}
-%\]
-%be integration along the holomorphic volume form. 
-%Define the pairing 
-%\[
-%\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
-%\]
-%by the formula $ \gamma \vee \mu +  \beta \nu.$
-%
-%\brian{defines Poisson bivector $\Pi$.}
-%
-%\subsubsection{}
-
-%Define the map of cochain complexes $\Phi \colon \cE_{pot} \to \til{\cE}_{KS}$
-%by the formulas
-%\[
-%\Phi (\mu,\nu) = \mu + u \, \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
-%\]
-%In the last expression we have used the isomorphism $\Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu}$
-%so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.
-%
-%\begin{prop}
-%\label{prop:pot}
-%The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
-%In particular, it defines a map of dg Lie algebras
-%\[
-%\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
-%\]
-%\end{prop}
-%
-%\begin{proof}
-%prove this
-%\end{proof}
-%
-%As a corollary of Proposition \ref{prop:tilbcov} and Proposition \ref{prop:pot} we have the following result. 
-%
-%\begin{cor}
-%The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
-%\begin{align*}
-%I_{pot} & = \Phi^* \til{I}_{BCOV} \\
-%Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
-%\end{align*} 
-%\end{cor}
-
 \end{document}

### 2021-10-26 draft.tex
abs

@@
 \begin{abstract}
-We construct a fully interacting partially holomorphic, partially topological, theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
+We construct a fully interacting holomorphic/topological theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
 %The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
-The theory describes, in part, a particular deformation of the moduli space of complex structures on the fivefold.
+The theory describes a particular deformation of the cotangent bundle to the moduli space of complex structures on the fivefold.
 Its field content matches the holomorphic (or minimal) twist of the 
@@
 We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model.
-Twists of superconformal algebras map to the fields of our model on the complement of the support of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
+Twists of superconformal algebras map to the fields of our model on the complement of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
 \end{abstract}

### 2021-10-26 dimred.tex
dimred

@@
 \begin{prop}\label{prop:dimred}
-The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is equivalent to the dimensional reduction of the 11-dimensional along  
+The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is the dimensional reduction of the 11-dimensional theory along  
 \[
@@
 \[
-\til \theta = \frac{1}{1-\nu} \theta, \quad \til \eta = (1- \nu) \eta .
+\til \theta = \frac{1}{1-\nu} \theta, \quad \til \eta = (1- \nu) \eta, \quad \til \beta = \beta + \frac{1}{1-\nu} \eta \wedge \theta .
 \]
@@
 \begin{multline}
-\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma \\ + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) .
+\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \in^{\Omega_{\CC^4}}t_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) \\ + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \frac{1}{1-\nu} (\til \eta \wedge \til \theta) \div \mu  .
 \end{multline}
-The first line agrees with the first and third terms in \eqref{eqn:IIAactionpot}.
+The first line comes from plugging in the new fields into the interactions \eqref{eqn:bfred} and \eqref{eqn:jred}.
+The second line comes from plugging in the new fields into the kinetic term $\int \beta \div \mu$, which because of the non-linear change of coordinates now contributes to the interaction. 
+We observe that the first two terms agree with the first and third terms in \eqref{eqn:IIAactionpot}.
 
-The second line is very close to the second term in \eqref{eqn:IIAactionpot}, but they are still not quite the same. 
-They are, however, cohomologous. 
-Integrating by parts and applying the BV relation, we can write the second line as
+After integrating by parts, the remaining terms can be written as 
 \[
-\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right)\wedge \div (\til\theta \wedge \mu)  = \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\til\eta \wedge \mu) \vee \partial \til \theta + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til \eta \wedge \div \mu \wedge \til \theta .
+- \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right) \div (\til\theta \mu) + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \left(\frac{1}{1-\nu} \til \eta\right) \til \theta \div \mu .
 \]
-The first term in this equation agrees precisely with the second term in \eqref{eqn:IIAactionpot}. 
-The final term is cohomologically trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
+Applying the identity $\div (\til \theta \mu) = \til \theta \div \mu + \del (\til \theta) \vee \mu$, we see that this agrees exactly with the second term in \eqref{eqn:IIAactionpot}.
+% but they are still not quite the same. 
+%They are, however, cohomologous. 
+%Integrating by parts and applying the BV relation, we can write the second line as
+%\[
+%\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right)\wedge \div (\til\theta \wedge \mu)  = \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\til\eta \wedge \mu) \vee \partial \til \theta + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til \eta \wedge \div \mu \wedge \til \theta .
+%\]
+%The first term in this equation agrees precisely with the second term in \eqref{eqn:IIAactionpot}. 
+%The final term is cohomologically trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
 %
@@
 \end{equation} 
+This space of fields is equipped with an odd non-degenerate pairing.
+Like the eleven-dimensional theory, it is a classical BV theory in the $\ZZ/2$-graded sense.
 
@@
 This is precisely the underlying cochain complex of fields for the type I model with potentials. 
+The odd non-degenerate pairing on this complex agrees with the one on this particular potential theory for the twist of type I supergravity. 
+The $L_\infty$ structure on the parity shift of this complex is compatible with the one induced from the BV action in \eqref{eqn:Iactionpot}.
 \end{proof}

### 2021-10-26 intro.tex
changes to susy

@@
 \subsection*{Acknowledgements}
-We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, O.~Gwil\-liam, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds.
+We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds.
 I.S.

### 2021-10-26 susy.tex
changes to susy

--- 2021-10-26 susy.tex
@@
 We compute the residual supersymmetry algebra given by taking the cohomology of the eleven-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
-In order for this to be a symmetry of the eleven-dimensional theory it is necessary to consider an extension of the eleven-dimensional supersymmetry algebra corresponding to the $M2$ brane.
+In order for this to map to the gauge symmetries of the eleven-dimensional theory, it is necessary to consider an extension of the eleven-dimensional supersymmetry algebra corresponding to the M2 brane.
 We will see how this extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.
@@
 Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
-In eleven-dimensional supersymmetry, there are two such extensions corresponding to the $M2$ brane and the $M5$ brane.
-We begin by describing a less standard dg Lie algebra model for the $M2$ brane algebra.
+In eleven-dimensional supersymmetry, there are two such extensions corresponding to the M2 brane and the M5 brane.
+We begin by describing a less standard dg Lie algebra model for the M2 brane algebra.
 In the next section we will explain the relationship to other descriptions in terms of $L_\infty$ algebras \cite{Basu_2005,Bagger_2007,fiorenza2015super}.
 
-Our model for the $M2$ brane algebra is a dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+Our model for the M2 brane algebra is a dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.
+
 Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
-
-The $M2$ brane algebra arises as an extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
+The M2 brane algebra arises as an extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
 \[
@@
 
-Here, we are using a bigrading by $\ZZ \times \ZZ/2$. 
-The super Poincar\'e algebra is concentrated in zero integer grading and carries is natural $\ZZ/2$ grading as a super Lie algebra.
-The complex $\Omega^{\bu}(\RR^{11})[2]$ is concentrated in integer degrees $[-2,9]$ and has even parity.
-
 \begin{dfn}
@@
 
+Here, we are using a bigrading by $\ZZ \times \ZZ/2$. 
+The super Poincar\'e algebra is concentrated in zero integer grading and carries its natural $\ZZ/2$ grading as a super Lie algebra.
+The complex $\Omega^{\bu}(\RR^{11})[2]$ is concentrated in integer degrees $[-2,9]$ and has even parity.
 The bracket in $\m2$ is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.
@@
 
-Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$.
+Fix a supercharge $Q \in S$ satisfying $Q^2 = 0$ that is in the lowest stratum of the nilpotence variety.
 Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of eleven-dimensional supersymmetry \cite{SWspinor}. 
@@
 \deq{
-  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L^\vee.
+  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L.
 }
@@
 \[
-\lie{sl}(5) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee \oplus \C .
+\lie{sl}(L) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee \oplus \C .
 \]
-Furthermore, the spinorial representation can be identified with
+Furthermore, the spin representation can be identified with
 \[
-S = \wedge^\bu (L^\vee) = \CC \oplus L^\vee \oplus \wedge^2 L^\vee \oplus \wedge^3 L^\vee \oplus \wedge^4 L^\vee \oplus \wedge^5 L^\vee .
+S = \wedge^\bu (L) = \CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \oplus \wedge^4 L \oplus \wedge^5 L .
 \]
 The element $Q$ lives in the first summand.
-Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
+Let 
+\[
+{\rm Stab}(Q) =  \lie{sl}(L) \oplus \wedge^2 L^\vee \oplus L^\vee \subset \lie{so}(11,\CC)
+\]
+ be the stabilizer of $Q$. 
 This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
@@
 The supercharge $Q$ is odd and of cohomological degree zero.
-Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the summand $\Omega^\bu(\R^11)[2]$ and is even of cohomological degree $+1$.
+Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the summand $\Omega^\bu(\R^{11})[2]$ and is even of cohomological degree $+1$.
 Thus, only the totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.
@@
 
-Let $Q$ be a rank one, or minimal, supercharge satisfying $Q^2 = 0$. We first determine $H^\bullet(\m2^q)$ as a super vector space.
+Let $Q$ be a minimal supercharge satisfying $Q^2 = 0$. We first determine $H^\bullet(\m2^q)$ as a super vector space.
 
@@
 
-In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$.
+In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$; two such elements bracket to a holomorphic translation by taking the wedge product to get an element of $\wedge^4 L^\vee \cong L$.
 This completes the calculation of the cohomology. 
@@
 One way to prove the proposition above is to use homotopy transfer directly to $\m2^Q$, just as we did in the proof of Theorem \ref{thm:global} to deduce the form of the $3$-ary bracket. 
-Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition \ref{prop:susycoh}.
+Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition~\ref{prop:susycoh}.
 This minimal model also has the advantage of being more directly related to the eleven-dimensional supergravity theory.
@@
 
-Notice that naively, $\psi \in \wedge^2 L$ is not $Q$-closed due to the presence of the central extension. 
-To embed $\wedge^2 L$ we introduce the following operator
+Notice that, at least naively, $\psi \in \wedge^2 L$ is not $Q$-closed due to the presence of the central extension. 
+To embed $\wedge^2 L$ we introduce the operator
 \[
-H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11})
+H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11}),
 \]
@@
 \parsec[]
-We now proceed to the proof of proposition \ref{prop:susycoh}
+We now proceed to the proof of proposition \ref{prop:susycoh}.
 
 \begin{proof}[Proof of Proposition \ref{prop:susycoh}]
-Using the model $\fg$ the first part of Proposition \ref{prop:susycoh} follows immediately. 
+Using the model $\fg$, the first part of Proposition \ref{prop:susycoh} follows immediately. 
 We deduce the second part using homotopy transfer.
@@
 as follows.
-\begin{itemize}
+\begin{itemize}[leftmargin=\parindent]
 \item The operator $K$ annihilates $H^\bu(\m2^Q)$ and is the identity map~$K \colon \Pi L_{\til \lambda} \to L_\lambda$. 
@@
 \begin{proof}
-Recall the cohomology of $\m2^Q$ takes the following form
+Recall that the cohomology of $\m2^Q$ takes the following form
 \beqn 
@@
 \ul{even} & \ul{odd} & \ul{even} \\
- L^\vee & \wedge^2 L^\vee_2 & L \\
-\wedge^2 L_1^\vee & & \\
-\lie{sl}(5) && \CC_b  \\
-%L_2 \ar[r, "\id"] & L_3 \\ 
- .
+ L^\vee & (\wedge^2 L^\vee)_2 & L \\
+(\wedge^2 L^\vee)_1 & & \\
+\lie{sl}(5) && \CC_b 
 \end{tikzcd}
@@
 The lefthand column is ${\rm Stab}(Q)$. 
-The subscripts in $\wedge^2 L_1, \wedge^2 L_2$ are used to distinguish between the two copies of $\wedge^2 L$.
+The subscripts are used to distinguish between the two copies of $\wedge^2 L^\vee$.
 
-The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted eleven-dimensional supergravity theory has a linear $\Phi^{(1)}$ and quadratic $\Phi^{(2)}$ piece.
-
+The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted eleven-dimensional supergravity theory has a linear piece $\Phi^{(1)}$ and a quadratic piece $\Phi^{(2)}$.
 Define the linear map $\Phi^{(1)} \colon \fg \to \cL$ as follows:
@@
 
-It is immediate to check that this is a map of cochain complexes since all elements in the image of this map lie in the kernel of the linearized BRST operator \eqref{eqn:linearBRST}.
+It is immediate to check that this is a map of cochain complexes, since all elements in the image of this map lie in the kernel of the linearized BRST operator~\eqref{eqn:linearBRST}.
 
@@
 \[
-H^\bu(\m2^Q)\to \Hat{E(5,10)}
+H^\bu(\m2^Q)\to \Hat{E(5,10)},
 \]
-where $\Hat{E(5,10)}$ is a central extension $E(5,10)$ by the cocycle \eqref{eqn:cocycle}
+where $\Hat{E(5,10)}$ is a central extension of~$E(5,10)$ by the cocycle~\eqref{eqn:cocycle}.
 \end{cor}
@@
 Because this map preserves differentials, it descends to a map in cohomology. 
-We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$, it is the trivial one-dimensional central extension of $E (5,10)$. 
-The Lie algebra structure present in the cohomology of $\m2^Q$ is described in part (1) of Proposition \ref{prop:susycoh}. 
+We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$; it is the trivial one-dimensional central extension of $E (5,10)$. 
+The Lie algebra structure present in the cohomology of $\m2^Q$ is described in part (1) of Proposition~\ref{prop:susycoh}. 
 The map
@@
 algebra $\Hat{E(5,10)}$.
-Also, we described the $L_\infty$ structure present in the cohomology of $\m2^Q$ in part (2) of Proposition \ref{prop:susycoh}. 
+Also, we described the $L_\infty$ structure present in the cohomology of $\m2^Q$ in part (2) of Proposition~\ref{prop:susycoh}. 
 Each of these $L_\infty$ structure involved introducing a single new $3$-ary bracket, which are easily seen to be compatible. 
@@
 
-In this section we compare to another description of the $M2$ brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
-Such central extensions were studied in the work \cite{BHsusyII, SSS, FSS} following \cite{CDF}.
-
+In this section we compare to another description of the M2 brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
+Such central extensions were studied in~\cite{BHsusyII, SSS, FSS}, following~\cite{CDF}. 
 In these references, the algebra $\m2$ is defined as an $L_\infty$  
 central extension of $\lie{siso}_{11d}$.
+
 Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
@@
 \]
-This expression is symmetric on the spinors and anti-symmetric on the vectors, therefore it defines an element in $\clie^4(\lie{siso}_{11d})$. 
+This expression is symmetric on the spinors and antisymmetric on the vectors, therefore it defines an element in $\clie^4(\lie{siso}_{11d})$. 
 This expression defines a nontrivial class in $H^4(\lie{siso}_{11d})$ so defines a one dimensional central extension of $\lie{siso}_{11d}$ as a Lie 3-algebra. 
@@
 There is a quasi-isomorphism $\clie^4(\lie{siso}_{11d})\to \clie^4(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\RR^{11})[2]$-valued two-cocycle we use.
-
-%For clarity we adjust notation for $\lie{sl}(5)$-representations.
-Denote by $V^{1,0} = L^\vee$ the space of holomorphic translations on $\CC^5$ and $V^{\vee 1,0}$ the translation invariant holomorphic one-forms on $\CC^5$.

### 2021-10-27 nonmin.tex
main proof in proof block
merge

@@
 We will decompose the fields according to these coordinates. 
-For example, we decompose the $\mu$-field as $\mu = \mu_z + \mu_w$ where
+\begin{proof}[Proof of Theorem \ref{thm:nonmin}]
+Decompose the $\mu$-field as $\mu = \mu_z + \mu_w$ where
 \begin{align*}
@@
 The non-minimally twisted linear BRST complex thus takes the form
-\[
+\beqn\label{eqn:twisteddiagram}
   \begin{tikzcd}
@@
   \end{tikzcd}
-\]
+\eeqn
 Here, we write $Z = \CC^2_z$ and $X = \CC^3_w$ for notational simplicity.
@@
 Consider the complex
-\beqn
+\beqn\label{eqn:zw}
 \Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_W \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_W \hotimes \Omega^\bu_L 
@@
 Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side. 
+The full Poisson Chern--Simons action $S_{pCS}$ equips this complex with the structure of a dg Lie algebra.
 
-There is a map of linear BRST complexes from this one to the original one defined by the following equations 
+Define the following non-linear map of BRST complexes from \eqref{eqn:zw} to the twisted theory \eqref{eqn:twisteddiagram}.
+It is defined by the equations
 \begin{multline}
-\mu_z = (\del_{z_1} \wedge \del_{z_2}) \vee \del^z \alpha^0, \quad \mu_w = (\del_{w_1} \wedge \del_{w_2} \wedge \del_{w_3}) \vee \alpha^2, \quad \nu = \til{\alpha}^3 \\
+\mu_z = (1-\til \alpha^3) (\del_{z_1} \wedge \del_{z_2}) \vee \del^z \alpha^0 , \quad \mu_w = (\del_{w_1} \wedge \del_{w_2} \wedge \del_{w_3}) \vee \alpha^2, \quad \nu = \til{\alpha}^3 \\
 \beta = \alpha^0 , \quad \gamma_w = \alpha^1 , \quad \gamma_z = 0 .
@@
 In the above equation we have introduced the notation $\til{\alpha}^3 = \Omega_X^{-1} \vee \alpha^3$. 
+Notice the only non-linearity appears in the definition of $\mu_z$.
 
@@
 \beqn\label{eqn:kin2}
-\int \alpha^0 \del^w \alpha^2 . 
+\int \alpha^0 \del^w \alpha^2 - \int \alpha^0 \del^z \alpha^0 \del^z \alpha^3 . 
 \eeqn
-Finally, the restriction of the kinetic term $\gamma \del^w \gamma$ along \eqref{eqn:g2map} is 
+Finally, the restriction of the kinetic term $\frac12 \int \gamma \del^w \gamma$ in \eqref{eqn:delta2} along \eqref{eqn:g2map} is 
 \beqn\label{eqn:kin3} 
@@
 
-This shows that \eqref{eqn:g2map} is a map of linear BRST complexes.
-Applying the obvious contracting homotopy, we see that this map is a quasi-isomorphism.
+The formulas above show that the linear terms in \eqref{eqn:g2map} define a map of linear BRST complexes.
+Applying the apparent contracting homotopy, we see that this map is a quasi-isomorphism.
 We will show that the full non-linear map intertwines the action functionals up to cohomologically exact terms, and hence defines an equivalence of BV theories.
 
-We first substitute the values for the fields in \eqref{eqn:g2map} into the original 11-dimensional action. 
-The terms which are at least cubic in the action in \eqref{eqn:delta1} become
-\beqn
-\int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right) .
+We substitute the values for the fields in \eqref{eqn:g2map} into the original 11-dimensional action. 
+Notice that any terms involving $\gamma_z$ can be discarded. 
+Restricting \eqref{eqn:delta1} along this map, we obtain the action functional
+\beqn\label{eqn:rest1}
+\frac12 \int \frac{1}{1-\til\alpha^3}  \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \int \alpha^2 \del^z \alpha^0 \del^z \alpha^1
++ \frac12 \int (1-\alpha^3) \del^z \alpha^0 \del^z \alpha^0 .
 \eeqn
 Here, $\til \alpha^2$ denotes the element of $\Omega^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \hotimes \Omega^\bu_L$ corresponding to $\alpha^2$ determined by the Calabi--Yau form $\d^3 w$. 
+Notice that the very last term is equivalent to the functional $-\frac12\int \alpha^3 \del^z \alpha^0 \del^z \alpha^0$ since the quadratic part is a total derivative.
+
 There is only one cubic term left in \eqref{eqn:delta2} when we substitute the fields according to \eqref{eqn:g2map}.
@@
 
-Notice that the total action is of the form 
+Combining all of these terms, we see that the total action restricted along the map \eqref{eqn:g2map} is 
 \beqn\label{eqn:pcs1}
-S_{pCS} (\alpha) + \int \frac{1}{1-\til\alpha^3} \left(\frac12 \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \til\alpha^3 \alpha^2 \del^z \alpha^1 \del^z \alpha^0 + \til\alpha^3 \alpha^3 \del^z \alpha^0 \del^z \alpha^0 \right)
+S_{pCS} (\alpha) + \int \frac12 \frac{1}{1-\til\alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z
 \eeqn
@@
 
-We will show that the terms not appearing in $S_{pCS}(\alpha)$ are cohomologically trivial. 
-First, consider the odd local functional
+We will show that the term not appearing in $S_{pCS}(\alpha)$ is cohomologically trivial. 
+Consider the odd local functional
 \beqn\label{eqn:triv1}
-\int \frac{1}{1 - \til \alpha^3} \alpha^2 (\til \alpha^2)^2 .
+\frac16 \int \frac{1}{1 - \til \alpha^3} \alpha^2 (\til \alpha^2)^2 .
 \eeqn
@@
 \[
-\int \frac{1}{1 - \til \alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 +  \int \frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2 .
+\frac12 \int \frac{1}{1 - \til \alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 + \frac16 \int \frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2 .
 \]
-The first term in this expression agrees the first term in parentheses in \eqref{eqn:pcs1}.
+The first term in this expression agrees the term in \eqref{eqn:pcs1} which is not in $S_{pCS}(\alpha)$.
 The second term is zero for symmetry reasons. 
-Thus, \eqref{eqn:triv1} trivializes the first term in parentheses in \eqref{eqn:pcs1}.
+This completes the proof that the non-minimal twist is equivalent to Poisson Chern--Simons theory.
 
-It remains to trivialize the remaining terms in parentheses. 
-To do this, we fix a primitive $\eta$ of the holomorphic volume form $\d^3 w$. 
-That is, $\eta$ is a holomorphic two-form on $W$ satisfying $\del \eta = \d^3 w$. 
-Consider the (non-translation invariant) odd local functional
-\[
-\int \frac{1}{1-\til \alpha^3} \eta (\til \alpha^3)^2 \del^z \alpha^1 \del^z \alpha^0   .
-\]
-Using $\del^w \eta = \d^3 w$, we see that this functional trivializes the remaining terms in parentheses in \eqref{eqn:pcs1}.
-This completes the argument.
-
+%It remains to trivialize the remaining terms in parentheses. 
+%To do this, we fix a primitive $\eta$ of the holomorphic volume form $\d^3 w$. 
+%That is, $\eta$ is a holomorphic two-form on $W$ satisfying $\del \eta = \d^3 w$. 
+%Consider the (non-translation invariant) odd local functional
+%\[
+%\int \frac{1}{1-\til \alpha^3} \eta (\til \alpha^3)^2 \del^z \alpha^1 \del^z \alpha^0   .
+%\]
+%Using $\del^w \eta = \d^3 w$, we see that this functional trivializes the remaining terms in parentheses in \eqref{eqn:pcs1}.
+%This completes the argument. 
+\end{proof}
 %

### 2021-10-27 nonmin.tex
random merge

--- 2021-10-26 nonmin.tex
@@
 \[
-Q_{nm} \in \wedge^2 L 
+Q_{nm} \in \wedge^2 \left(L^\vee\right)
 \]
@@
 \]
-where $q = q_1=q_1^{-1}$. This is exactly the sum of the geometric series \ref{nonmin:singleparticle}
-
+where $q = q_1=q_1^{-1}$. This is exactly the sum of the geometric series~\eqref{nonmin:singleparticle}.
 \end{proof}
@@
 This completes the argument. 
-
+\end{proof}
 %

### 2021-10-27 suco.tex
random merge

@@
-\section{Twisted supergavity on AdS space}
+\section{Twisted supergravity on AdS space}
 \label{sec:ads}
 
-So far, we have mostly given evidence for the 11-dimensional theory as a twist of supergravity in a flat background. 
-We now turn to twisted versions of AdS backgrounds of 11-dimensional supergravity.
+So far, we have mostly given evidence for the eleven-dimensional theory as a twist of supergravity in a flat background. 
+We now turn to twisted versions of AdS backgrounds of eleven-dimensional supergravity.
 
-In $M$-theory, AdS backgrounds arise from backreacting some number of branes. 
-For $M2$ branes, the backreacted geometry is ${\rm AdS}_4 \times S^7$.
-For the $M5$ branes, the backreacted geometry is ${\rm AdS}_7 \times S^4$.
+In M-theory, AdS backgrounds arise from backreacting some number $N$ of branes. 
+For M2 branes, the backreacted geometry is ${\rm AdS}_4 \times S^7$.
+For the M5 branes, the backreacted geometry is ${\rm AdS}_7 \times S^4$.
 
-According to the AdS/CFT correspondence, supergravity on such backgrounds should be dual to the relevant worldvolume theory. 
-In this section, we do not directly refer to the worldvolume theories on the holomorphic twists of the $M2$ and $M5$ branes.
-Rather, we identify the fields sourcing the branes at the level of the twisted 11-dimensional theory.
+According to the AdS/CFT correspondence, supergravity on such backgrounds should be dual to the relevant worldvolume theory in the large-$N$ limit. 
+In this section, we do not directly refer to the worldvolume theories on the holomorphic twists of the M2 and M5 branes.
+Rather, we identify the fields sourcing the branes at the level of the twisted eleven-dimensional theory.
 In turn, we give a proposal for the twisted AdS background. 
@@
 
-The minimal supercharge $Q$ acting on 11-dimensional supersymmetry algebra is an element of this superconformal algebra. 
-In \cite{SWsuco2}, the second two authors show that the $Q$-cohomology is isomorphic to $\lie{osp}(6|1)$. 
+The minimal supercharge $Q$ acting on eleven-dimensional supersymmetry algebra is an element of this superconformal algebra. 
+Its $Q$-cohomology is isomorphic to $\lie{osp}(6|1)$. (Twisted superconformal symmetry in six dimensions is studied in detail by the second  two authors  in~\cite{SWsuco2}.)
 This super Lie algebra will play the role of the isometries in the twisted AdS background.
@@
 
-In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of 11-dimensional supergravity. 
+In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of eleven-dimensional supergravity. 
 %In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
@@
 
-Decompose the 11-dimensional manifold $\CC^5 \times \RR$ as
+Decompose the eleven-dimensional manifold $\CC^5 \times \RR$ as
 \[
@@
 
-Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of $N$ $M2$ branes wrapping $\R\times \C_z$. A natural interaction to consider is 
+Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of $N$ M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
 \[
@@
 which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
-Unlike the case of $M5$ branes, the coupling does not involve choosing a primitive for a field strength - it is an electric coupling.
-We have only indicated the lowest order coupling, the $\cdots$ indicate higher order couplings which will be higher order in the fields of the 11d theory and explicitly involve the fields in the worldvolume theory.
+Unlike the case of M5 branes, the coupling does not involve choosing a primitive for a field strength---it is an electric coupling.
+We have only indicated the lowest order coupling, the $\cdots$ indicate higher-order couplings which will be higher order in the fields of the eleven-dimensional theory and explicitly involve the fields in the worldvolume theory.
 
 This coupling is justified by comparison with the physical theory and by dimensional reduction. 
-Indeed, as discussed in section \ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
-Thus, the proposal mirrors electric couplings of $M2$ branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.
+Indeed, as discussed in~\S\ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
+Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.
 
-Moreover, reducing on a circle transverse to the $M2$ brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$.
+Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$.
 As is shown in \cite{CLsugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by
@@
 
-% Based on the discussion above, it is natural to expect that there is a field of twisted 11-dimensional supergravity which sources the twist of a stack of $N$ $M2$ branes living on the submanifold $\CC_z \times \RR \cong \{w=0\} \subset \CC^5$.
-
-% The differential form which sources the brane is an element
-% \[
-% \til{F} \in \Omega^{4,3} (\CC^4_w \, \setminus \, 0) \otimes \Omega^{0,0} (\CC_z) \otimes \Omega^{0} (\RR) \subset \Omega^{\bu} \left(\CC^5 \times \RR \, \setminus \, \{w=0\}\right) .
-% \]
-% Equivalently, we can think about this as a distributional valued form $\til{F} \in \Bar{\Omega}^{4,3}(\CC^5) \otimes \Omega^0 (\RR)$ which satisfies the distributional equation
-% \[
-% \dbar \til{F} = N \delta_{w=0} 
-% \]
-% where $\delta_{w=0}$ is the Dirac $\delta$-distributional for the submanifold $\{w=0\} = \CC_z \times \RR$.
-
-% Using the Calabi--Yau form we can identify such a differential form with a field of twisted supergravity. 
-% Indeed $F = \til{F} \wedge \Omega^{-1}$ is a distributional field of type
-% \[
-% F \in \Bar{\PV}^{1,3}(\CC^5) \otimes \Omega^0 (\RR) .
-% \]
-% For $F$ to make sense as a background of twisted supergravity it must satisfies the appropriate (possibly nonlinear) equation of motion, which we now verify.
-
 \parsec[sec:m2backreact]
 
-The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$. 
-Varying the deformed action with respect to $\gamma$ 
+The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M2}(\gamma)$. 
+Varying the deformed action with respect to $\gamma$,
 we obtain the equation of motion
 \beqn\label{eqn:ads4eom1}
-\dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma = N \Omega^{-1} \delta_{w=0} \\
+\dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma = N \Omega^{-1} \delta_{w=0} .
 \eeqn
 Here $[-,-]$ is the Schouten bracket. 
-Varying $\beta$ we obtain the equation of motion
+Varying $\beta$, we obtain the equation of motion
 \beqn\label{eqn:adseom2}
@@
 \]
-Then, the background where $\mu = N F_{M2}$ and $\gamma = 0$
-satisfies the above equations of motion in the presence of a stack of $N$ $M2$ branes:
+Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
+satisfies the above equations of motion in the presence of a stack of $N$ M2 branes:
 \begin{align*}
@@
 \end{align*}
-Here, we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
+Here we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
 \end{lem}
@@
 
-To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory and those in the twisted theory.
+To provide evidence for the claim that this is the twisted analog of the AdS geometry, we will show that the twist of the symmetries present in the physical theory are witnessed in the twisted theory in this background.
 
 We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w=0\}$ which corresponds to the twist of the 3d superconformal algebra.
-We first focus on the case where the flux $N=0$, in this case the embedding can be extended to all of $\CC^5 \times \RR$.
+We will define an embedding of $\lie{osp}(6|1)$ into the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w=0\}$ which corresponds to the twist of the 3d superconformal algebra.
+We first focus on the case where the flux $N=0$, for which the embedding can be extended to all of $\CC^5 \times \RR$.
 
@@
 The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
-The Lie algebra $\lie{sl}(2)$ represents special conformal transformations in $\CC_z$; the vector fields representing these transformations are not divergence-free so must be slightly adjusted. 
+The Lie algebra $\lie{sl}(2)$ represents (holomorphic) conformal transformations in $\CC_z$, which are inherited from the natural M\"obius group action on~$P^1(\C)$; the vector fields representing these transformations are not all divergence-free, and as such must be slightly adjusted.
 The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.
 
-\begin{itemize}
+\begin{itemize}[leftmargin=\parindent]
 \item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
@@
 \]
-Notice that these vector fields are divergence-free and along $w=0$ reduce to the usual special conformal transformations.
+Notice that these vector fields are divergence-free and reduce to the usual holomorphic conformal transformations along $w=0$.
 \item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
@@
 
-\begin{itemize}
+\begin{itemize}[leftmargin=\parindent]
 \item 
@@
 \begin{lem}\label{lem:m2emb}
-These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the 11-dimensional theory on $\CC^5 \times \RR$. 
+These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the eleven-dimensional theory on $\CC^5 \times \RR$. 
 Equivalently, it defines an embedding
@@
 \begin{proof}
-The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
+The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
 Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
 To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
-Recall, we are using the holomorphic coordinates $(z,w_1,\ldots,w_4)$ on $\CC^5$ where $z$ is the holomorphic coordinate along the $M2$ brane. 
-\begin{itemize}
+Recall, we are using the holomorphic coordinates $(z,w_1,\ldots,w_4)$ on $\CC^5$ where $z$ is the holomorphic coordinate along the M2 brane. 
+\begin{itemize}[leftmargin=\parindent]
 \item 
@@
 There exist $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
-Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N F_{M2},-]$.
+Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of eleven-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N F_{M2},-]$.
 \end{prop}
@@
 \begin{proof}
-Let $\cL(\CC^5 \times \RR \setminus \{w=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory. 
+Let $\cL(\CC^5 \times \RR \setminus \{w=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the eleven-dimensional theory. 
 We make the identification 
@@
 The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
-In this description the image of the flux $F$ at this page in the spectral sequence corresponds to the following class 
+In this description the image of the flux $F$ at this page in the spectral sequence corresponds to the class 
 \[
@@
 
-In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of 11-dimensional supergravity.
+In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity.
 Decompose the eleven dimensional spacetime as $\C^3_z\times \C^2_w\times \R$.
-
-%In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 
-Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting $M5$ branes.
-To this effect, we begin by discussing how the 11d theory couples to M5 branes.
-Consider a stack of $N M5$ branes wrapping 
+Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting M5 branes.
+To this effect, we begin by discussing how the eleven-dimensional theory couples to M5 branes.
+Consider a stack of $N$ M5 branes wrapping 
 \[
-\{w_1=w_2=t=0\} \subset \C^3_z\times \C^2_w\times \R 
+\{w_1=w_2=t=0\} \subset \C^3_z\times \C^2_w\times \R.
 \] 
-
 It is natural to consider the nonlocal interaction 
@@
 
-The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory \ref{s:components}. 
-In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the hodge star of the $G$-flux and integrating it over the $M5$ worldvolume.
+The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory (\S\ref{s:components}). 
+In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the Hodge star of the $G$-flux and integrating it over the M5 worldvolume.
 Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.
@@
 We obtain a deeper justification for this coupling through dimensional reduction to type IIA supergravity. 
-Reducing on the circle along the directions the $M5$ branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.
+Reducing on the circle along the directions the M5 branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.
 
@@
 
-The backreacted geometry will be given by a solution to the equations of motion upon deforming the 11-dimensional action by the interaction $I_{M5}(\mu)$.
+The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M5}(\mu)$.
 
@@
 %satisfies $\del \til F = F$. 
-Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ $M5$ branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
+Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
 \begin{align*}
@@
 \]
-for any $4$-sphere centered at $0 \in \CC^2 \times \RR$.
+for any four-sphere centered at $0 \in \CC^2 \times \RR$.
 
@@
 
-To provide evidence for the claim that this is the twisted analog of the AdS geometry we will match the symmetries present in the physical theory on ${\rm AdS}_7 \times S^4$ and those in the twisted theory.
+To provide evidence for the claim that this is the twisted analog of the AdS geometry, we will again show that the twist of the symmetries present in the physical theory on ${\rm AdS}_7 \times S^4$ appear in the twisted theory on this background.
 
 We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
-We will define an embedding of $\lie{osp}(6|1)$ into the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$ which corresponds to the twist of the 6d superconformal algebra.
+We will define an embedding of $\lie{osp}(6|1)$ into the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$ which corresponds to the twist of the 6d superconformal algebra.
 
@@
 with $z_i, i=1,2,3$ and $w_a, a=1,2$.
-The stack of $M5$ branes wrap $w_1=w_2=t=0$.
+The stack of M5 branes wrap $w_1=w_2=t=0$.
 
@@
 which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces.
-The roles of the $\lie{sl}(4)$ and $\lie{sl}(2)$ summands are interchanged compared to the case of the $M2$ brane.
+The roles of the $\lie{sl}(4)$ and $\lie{sl}(2)$ summands are interchanged compared to the case of the M2 brane.
 The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
@@
 
-\begin{itemize}
-
+\begin{itemize}[leftmargin=\parindent]
 \item
@@
 \begin{lem}
-These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the 11-dimensional theory on $\CC^5 \times \RR$. 
+These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the eleven-dimensional theory on $\CC^5 \times \RR$. 
 Equivalently, it defines an embedding
@@
 To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
-Recall, we are using the holomorphic coordinates $(z_1,z_2,z_3, w_1,w_2)$ on $\CC^5$ where $z_i$ are the holomorphic coordinates along the $M5$ brane. 
+Recall, we are using the holomorphic coordinates $(z_1,z_2,z_3, w_1,w_2)$ on $\CC^5$ where $z_i$ are the holomorphic coordinates along the M5 brane. 
 \begin{itemize}
@@
 \label{prop:brads7}
-There exists $N$-dependent corrections to the embedding $i_{M5}$ which is compatible with the modified BRST differential $\delta^{(1)} + [N F_{M5},-]$. 
-Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of 11-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F_{M5},-]$.
+There exist $N$-dependent corrections to the embedding $i_{M5}$ which are compatible with the modified BRST differential $\delta^{(1)} + [N F_{M5},-]$. 
+Furthermore, these $N$-dependent corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of eleven-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F_{M5},-]$.
 \end{prop}
@@
 
-The 11-dimensional theory is built from fields which live in the following tensor product of complexes 
+The eleven-dimensional theory is built from fields which live in the tensor product of complexes 
 \[
@@
 \]
-Precisely, this is where the $\beta,\nu$ fields live. 
-The $\mu,\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.
+More precisely, this is where the  fields $\beta$ and~$\nu$ live. 
+The $\mu$ and~$\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.
 
@@
 
-For the M5 brane it was convenient to relabel the holomorphic coordinates on $\CC^5$ by $z_1,z_2,z_3,w_1,w_2$. 
-At the twisted level, the geometry arising from backreacting $M5$ branes is based on the manifold 
+For the M5 brane, it was convenient to rename the holomorphic coordinates on $\CC^5$ to $z_1,z_2,z_3,w_1,w_2$. 
+At the twisted level, the geometry arising from backreacting M5 branes is based on the manifold 
 \[
@@
 \]
-The $\beta,\nu$ fields of 11-dimensional theory on this submanifold of $\CC^5 \times \RR$ live in the complex 
+The $\beta$ and~$\nu$ fields of the eleven-dimensional theory on this submanifold of $\CC^5 \times \RR$ live in the complex 
 \[
@@
 \]
-The $\mu,\gamma$ fields live in similar complexes where we introduce a (trivial) vector bundle on $\CC^5 \times \RR \setminus \CC^3$.
+The $\mu$ and~$\gamma$ fields live in similar complexes, where we introduce a (trivial) vector bundle on $\CC^5 \times \RR \setminus \CC^3$.
 
@@
 Let's turn to the proof of Proposition \ref{prop:brads7}.
-We proceed completely analogously to the case of backreacted $M2$ branes as in the proof of Proposition \ref{prop:brads4}.
+We proceed completely analogously to the case of backreacted M2 branes as in the proof of Proposition \ref{prop:brads4}.
 
 \begin{proof}[Proof of Proposition \ref{prop:brads7}]
-Let $\cL (\CC^5 \times \RR \setminus \{w_1=w_2=t=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the 11-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
+Let $\cL (\CC^5 \times \RR \setminus \{w_1=w_2=t=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
 
@@
 To compute this cohomology we follow the discussion in \S \ref{s:thfcohomology}.
-Just as in the case of the $M2$ brane, we see that the $\dbar + \d_{\RR}$ cohomology is (up to completions) is the direct sum of the cohomology on flat space $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with
+Just as in the case of the M2 brane, we see that the $\dbar + \d_{\RR}$ cohomology is (up to completions) is the direct sum of the cohomology on flat space $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with
 \begin{equation}
@@
 
-The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to dotted line operators in \eqref{eqn:ads7ss2}.
+The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to the dotted-line operators in~\eqref{eqn:ads7ss2}.
 

### 2021-11-04 intro.tex
merge

--- 2021-10-26 intro.tex
@@
 Other twists can be understood as further twists of this holomorphic theory.
-The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}.
-(Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)
+
+The importance and interest of holomorphic twists of supersymmetric gauge theories was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis,BCOV}.
+Si Li pushed applications of holomorphic QFT further in his work on the higher genus B-model \cite{SiThesis} and later with Costello in \cite{CLbcov1}.
+(In the physics literature, constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)
 
@@
 \subsection*{Acknowledgements}
-We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, O.~Gwil\-liam, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds.
+We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, C.~Elliott, D.~Gaiotto, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, S.~Li, N.~Paquette, S.~R\"osch, J.~Walcher, P.~Yoo for conversation and inspiration of all kinds.
 I.S.

### 2021-11-04 nonmin.tex
merge

--- 2021-10-27 nonmin.tex
@@
 \begin{prop}
+\label{prop:ham}
 Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$. 
@@
 The first term in this expression agrees the term in \eqref{eqn:pcs1} which is not in $S_{pCS}(\alpha)$.
-The second term is zero for symmetry reasons. 
+
+The latter term $\frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2$ is of polynomial degree $\geq 4$. 
+Since this term has trivial self BV bracket it determines a cocycle for the dg Lie algebra underlying Poisson Chern--Simons theory. 
+Since it is manifestly translation invariant, it arises via descent from a cocycle in the dg Lie algebra of $\infty$-jets of fields at $0 \in\CC^2 \times \RR^7$.
+This dg Lie algebra is quasi-isomorphic to the Lie algebra $\CC[[z_1,z_2]]$ equipped with the holomorphic Poisson bracket.
+(This is the formal power series version of the Lie algebra from Proposition~\ref{prop:ham}.)
+There is a weight grading on this Lie algebra given by declaring $|z_1^{n+1} z_2^{m+1}| = n+m$ which induces a grading on the Gelfand--Fuks Lie algebra cohomology.  
+The weight of the Gelfand--Fuks class corresponding to our deformation is $+2$ since no derivatives of $z_1$ or $z_2$ appear. 
+Results from \cite{Fuks} show that there is no cohomology in this weight. 
 This completes the proof that the non-minimal twist is equivalent to Poisson Chern--Simons theory.

### 2021-11-04 susy.tex
m2

@@
 
-In this section we compare to another description of the M2 brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
+In this short section we compare to another description of the M2 brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
 Such central extensions were studied in~\cite{BHsusyII, SSS, FSS}, following~\cite{CDF}. 
@@
 This expression defines a nontrivial class in $H^4(\lie{siso}_{11d})$ so defines a one dimensional central extension of $\lie{siso}_{11d}$ as a Lie 3-algebra. 
-Instead of working with a one-dimensional central extension by $\CC[2]$, we work with a central extension by the resolution $\Omega^\bullet(\RR^{11})[2]$.
-There is a quasi-isomorphism $\clie^4(\lie{siso}_{11d})\to \clie^4(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ such that the induced map on cohomology identifies $\mu_2$ with the $\Omega^\bullet(\RR^{11})[2]$-valued two-cocycle we use.
+Instead of working with a one-dimensional central extension by $\CC[2]$, we work with a central extension by the resolution $\Omega^\bullet(\RR^{11})[2]$ determined by a cocycle $c_{M2}$, see \S \ref{sec:m2brane}.
+There is a quasi-isomorphism $\clie^\bu(\lie{siso}_{11d})\to \clie^\bu(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ induced by the embedding of constant functions into the full de Rham complex.
+The cocycles $\mu_2$ and $c_{M2}$ are cohomologous via a two-step zig-zag in the double complex $\clie^\bu(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$.

### 2021-11-04 dimred.tex
stuffed turkey

@@
 
-\section{Dimensional reduction and 10-dimensional supergravity}
+\section{Dimensional reduction and ten-dimensional supergravity}
 \label{sec:dimred}
 
-In this section we demonstrate that our proposal for the action of minimally twisted 11-dimensional supergravity agrees with conjectural descriptions of twisted type IIA and type I supergravities due to Costello and Li.
+In this section we demonstrate that our proposal for the action of minimally twisted eleven-dimensional supergravity agrees with conjectural descriptions of twisted type IIA and type I supergravities due to Costello and Li.
 
@@
 Roughly, the radius of the $M$-theory circle plays the role of this coupling constant. 
-Additionally, at low energies $M$-theory is expected to be approximated by 11-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity.
-Combining these two pictures, various checks have been made that the dimensional reduction of 11-dimensional supergravity along the $M$-theory circle is type IIA supergravity.
+Additionally, at low energies $M$-theory is expected to be approximated by eleven-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity.
+Combining these two pictures, various checks have been made that the dimensional reduction of eleven-dimensional supergravity along the $M$-theory circle is type IIA supergravity.
 
@@
 There are a few different versions of Kodaira--Spencer theory, but the shared characteristic is that they are all `gravitational' in nature; they describe fluctuations of the Calabi--Yau structure. 
-From this point of view, Kodaira--Spencer theory is at the heart of the formulation of the various flavors of twisted 10-dimensional supergravity.
+From this point of view, Kodaira--Spencer theory is at the heart of the formulation of the various flavors of twisted ten-dimensional supergravity.
 
@@
 
-We now turn back to our 11-dimensional theory. 
-The first goal is to compare the dimensional reduction of our 11-dimensional theory on $\CC^5 \times \RR$
+We now turn back to our eleven-dimensional theory. 
+The first goal is to compare the dimensional reduction of our eleven-dimensional theory on $\CC^5 \times \RR$
 %where $X$ is a Calabi-Yau 4-fold 
@@
 
-Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA.
+Recall that in the physical theory, the components of the $C$-field in eleven dimensions that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA.
 However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear.
@@
 We modify the space of fields by introducing potentials for both the $\Pi$ and $\sigma$ fields. 
-First, we introduce a field $\gamma \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi \vee \Omega = \del \gamma$ where $\Omega$ is the Calabi--Yau form on $\CC^4$.
+First, we introduce a field $\gamma \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ (not to be confused, yet, with the $\gamma$ field in our eleven-dimensional theory) which satisfies $\Pi \vee \Omega = \del \gamma$ where $\Omega$ is the Calabi--Yau form on $\CC^4$.
 This condition does not uniquely fix $\gamma$. 
@@
 
-We turn to the proof of the main result of this section that the dimensional reduction of our 11-dimensional theory agrees with the twist of IIA supergravity just introduced.
+We turn to the proof of the main result of this section that the dimensional reduction of our eleven-dimensional theory agrees with the twist of IIA supergravity just introduced.
 
@@
 \begin{prop}\label{prop:dimred}
-The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is the dimensional reduction of the 11-dimensional theory along  
+The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is the dimensional reduction of the eleven-dimensional theory along  
 \[
@@
 Let us denote the holomorphic coordinate we are reducing along by $z_5 = x + \im y$. 
-We first read off the dimensional reduction of each component field of the 11-dimensional theory. 
+We first read off the dimensional reduction of each component field of the eleven-dimensional theory. 
 Per the above discussion, this is obtained by taking all fields to be independent of $y$ and replacing $\d \zbar_5$ by $\d x$. 
-To not confuse the notations of fields in 10 and 11 dimensions, we use the notation $\alpha_{11d}$ to denote an 11-dimensional field.
+To not confuse the notations of fields in ten and eleven dimensions, we use the notation $\alpha_{11d}$ to denote an eleven-dimensional field.
 
-The reductions of the 11d fields $\nu_{11d}, \beta_{11d}$ are easy to describe. 
+The reductions of the eleven-dimensional fields $\nu_{11d}, \beta_{11d}$ are easy to describe. 
 Recall that 
@@
 \]
-The reduction of this field is a 10d $\nu$ field
+The reduction of this field is a ten-dimensional $\nu$ field
 \[
@@
 \]
-Similarly, the reduction of $\beta_{11d}$ is a 10d $\beta$ field
+Similarly, the reduction of $\beta_{11d}$ is a ten-dimensional $\beta$ field
 \[
@@
 
-The reduction of the 11d fields $\mu_{11d}$ and $\gamma_{11d}$ require a bit of massaging. 
+The reduction of the eleven-dimensional fields $\mu_{11d}$ and $\gamma_{11d}$ require a bit of massaging. 
 We break the $SU(5)$ symmetry to $SU(4)$ to write
@@
 \end{align*}
-The dimensional reduction of $\mu^0_{11d}$ is a 10d $\mu$ field
+The dimensional reduction of $\mu^0_{11d}$ is a ten-dimensional $\mu$ field
 \[
@@
 
-Finally, write the 11d field $\gamma_{11d}$ as
+Finally, write the eleven-dimensional field $\gamma_{11d}$ as
 \[
@@
 \end{align*}
-The dimensional reduction of $\gamma^0_{11d}$ is a 10d $\gamma$ field
+The dimensional reduction of $\gamma^0_{11d}$ is a ten-dimensional $\gamma$ field
 \[
@@
 
-Next, we read off the dimensional reduction of the 11d action. 
+Next, we read off the dimensional reduction of the eleven-dimensional action. 
 Let us first focus on the term present in BF theory which is
@@
 
-Next, consider the cubic term in the 11d action $J = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
+Next, consider the cubic term in the eleven-dimensional action $J = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
 Upon reduction, this becomes 
@@
 
-We now turn to a different type of redution of the 11-dimensional theory, this time involving type I supergravity. 
+We now turn to a different type of redution of the eleven-dimensional theory, this time involving type I supergravity. 
 We begin by briefly recalling the description of type I supergravity following \cite{CLtypeI} which was motivated by the unoriented $B$-model. 
@@
 
-Like in the type IIA discussion, there is a slight modification of the type I model above which is most directly related to 11-dimensional supergravity.
+Like in the type IIA discussion, there is a slight modification of the type I model above which is most directly related to eleven-dimensional supergravity.
 
@@
 
-We consider placing twisted 11-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
+We consider placing twisted eleven-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
 In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.
-Our 11-dimensional theory on such manifolds fits nicely into the formalism of \cite{BY,Eugene} in that it is topological in the direction transverse to the boundary.
+Our eleven-dimensional theory on such manifolds fits nicely into the formalism of \cite{BY,Eugene} in that it is topological in the direction transverse to the boundary.
 
@@
 
-The phase space is equipped with the restriction of the linear BRST operator of the full 11-dimensional theory. 
+The phase space is equipped with the restriction of the linear BRST operator of the full eleven-dimensional theory. 
 There is also a non linear BRST operator, just like in the bulk theory.
@@
 \parsec[s:boundary]
-At $t=0$, the boundary condition of the 11-dimensional theory is determined by declaring 
+At $t=0$, the boundary condition of the eleven-dimensional theory is determined by declaring 
 \[
@@
 \begin{prop}
-With these boundary conditions for the classical 11-dimensional theory on $\CC^5 \times [0,1]$, the dimensional reduction along 
+With these boundary conditions for the classical eleven-dimensional theory on $\CC^5 \times [0,1]$, the dimensional reduction along 
 \[
@@
 
-Thus, given that our 11-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction.
+Thus, given that our eleven-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction.
 This results in a $SU(5)$ invariant, holomorphic, theory on $\CC^5$.
@@
 
-The 11-dimensional the field $\mu_{11d}$ is replaced by the field 
+The field $\mu_{11d}$ is replaced by the field 
 \[
@@
 
-We can compute the dimensional reduction of the 11-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
+We can compute the dimensional reduction of the eleven-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
 We arrive at the action functional described below.
@@
 %We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
-%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the 10d $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
+%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the ten-dimensional $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
 %
@@
 
-The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the 11-dimensional theory. 
+The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the eleven-dimensional theory. 
 We offer another point of view of this $S^1 / \ZZ/2$ reduction.
 
-First off, there is the following $\ZZ/2$ action on the 11-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
+First off, there is the following $\ZZ/2$ action on the eleven-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
 We obtain it by the following tensor product of $\ZZ/2$ actions. 
@@
 Second, we declare that the eigenvalue of the $\ZZ/2$ action on $\PV^{k,\bu}(\CC^5)$, for $k=0,1$ is $+1$ and the eigenvalue of the $\ZZ/2$ action on $\Omega^{k,\bu}(\CC^5)$ for $k=0,1$ is $-1$. 
-This determines a $\ZZ/2$ action on the full space of fields of the 11-dimensional theory.
+This determines a $\ZZ/2$ action on the full space of fields of the eleven-dimensional theory.
 
@@
 
-In the first section we saw that the 11-dimensional theory can be defined on any manifold that is a product of a Calabi--Yau five-fold with a smooth oriented one-manifold. 
-In this section, we investigate an important compactification of the 11-dimensional theory which involves the Calabi--Yau manifold $X \times \CC^2$ where $X$ is a simply connected compact Calabi--Yau three-fold.
+In the first section we saw that the eleven-dimensional theory can be defined on any manifold that is a product of a Calabi--Yau five-fold with a smooth oriented one-manifold. 
+In this section, we investigate an important compactification of the eleven-dimensional theory which involves the Calabi--Yau manifold $X \times \CC^2$ where $X$ is a simply connected compact Calabi--Yau three-fold.
 
@@
 \label{prop:5dsugra}
-The compactification of the 11-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of 5d $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hyper multiplets.
+The compactification of the eleven-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of five-dimensional $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hyper multiplets.
 \end{prop}
@@
 
-We give a conjectural capitulation of the twist of 5d $\cN=1$ supergravity. 
-Before twisting, a general 5d $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hyper multiplets. 
+We give a conjectural capitulation of the twist of five-dimensional $\cN=1$ supergravity. 
+Before twisting, a general five-dimensional $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hyper multiplets. 
 The twist of the vector and hyper multiplet has been computed in \cite{ESW}, and we recall it below. 
@@
 \label{conj:5dsugra}
-The twist of 5d supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
+The twist of five-dimensional supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
 \begin{itemize}
@@
 
-%\brian{general background on susy. Why expect 5d $\cN=1$ susy}
+%\brian{general background on susy. Why expect five-dimensional $\cN=1$ susy}
 
@@
 Let $\Omega_X$ be the holomorphic volume form on $X$. 
-To define the $11$-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
+To define the eleven-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
 Let $\omega \in \Omega^{1,1}(X)$ be a fixed K\"ahler form on $X$.
@@
 \begin{proof}
-Consider the 11-dimensional field $\nu_{11d}$. 
+Consider the eleven-dimensional field $\nu_{11d}$. 
 Under the equivalence
@@
 
-Next, consider the 11-dimensional field $\mu_{11d}$. 
+Next, consider the eleven-dimensional field $\mu_{11d}$. 
 Under the equivalence 
@@
 
-The decomposition for the 11d fields $\gamma_{11d}$ and $\beta_{11d}$ is similar. 
+The decomposition for the eleven-dimensional fields $\gamma_{11d}$ and $\beta_{11d}$ is similar. 
 We record it here:
@@
 
-To compare most directly to the description of the twist of 5d $\cN=1$ supergravity we modestly modify the fields. 
+To compare most directly to the description of the twist of five-dimensional $\cN=1$ supergravity we modestly modify the fields. 
 Let $\del$ be the holomorphic de Rham differential along $\CC^2$. 
@@
 
-Let us plug these fields in to the 11-dimensional action.
+Let us plug these fields in to the eleven-dimensional action.
 First, consider the BF term $\frac12 \int^{\Omega} \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \gamma_{11d}$. 
@@
 \end{multline}
-This term agrees with the second line in the 5d action \eqref{eqn:5daction}.
+This term agrees with the second line in the five-dimensional action \eqref{eqn:5daction}.
 
-Finally, consider the term in the 11-dimensional action $J(\gamma_{11d}) = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
+Finally, consider the term in the eleven-dimensional action $J(\gamma_{11d}) = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
 This induces the five-dimensional Chern--Simons term 
@@
 
-In \S \ref{sec:global} we computed the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ and found a close relationship to the exceptional super Lie algebra $E(5,10)$. 
+In \S \ref{sec:global} we computed the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ and found a close relationship to the exceptional super Lie algebra $E(5,10)$. 
 In this section we deduce the form of the global symmetry algebra of the five-dimensional compactified theory on $\CC^2 \times \RR$.
@@
 %\begin{proof}
-%The computation of the global symmetry algebra of the 5-dimensional theory is very similar to the computation in the 11-dimensional theory.
+%The computation of the global symmetry algebra of the 5-dimensional theory is very similar to the computation in the eleven-dimensional theory.
 %In terms of the de Rham cohomology, the generators of the linearized cohomology of the space of fields read:

### 2021-11-04 intro.tex
stuffed turkey

--- 2021-10-26 intro.tex
@@
 The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even.
-As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lceil d/2\rceil$ of the translations act nontrivially.
+As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially.
 Other twists can be understood as further twists of this holomorphic theory.
@@
 A very active and promising direction of current research uses these twisted ten-dimensional models to formulate twisted versions of holography; see~\cite{CostelloM2, Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant, Gaiotto:2020vqj}, for example.
-In \cite{CostelloM5} supergravity in the $\Omega$-background has been introduced, and has been further studied in \cite{Gaiotto:2019wcc, Oh:2020hph, Oh:2021bwi}.
+Supergravity in the $\Omega$-background was introduced in~\cite{CostelloM5}, and has been further studied in~\cite{Gaiotto:2019wcc, Oh:2020hph, Oh:2021bwi}.
 
 In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity (before turning on any $\Omega$-background).
-%By `twists' we mean ones which arise from setting a bosonic ghost to take a nonzero value of a particular supertranslation in the 11-dimensional supersymmetry algebra. 
 Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
@@
 In \S\ref{s:dfn} we introduce a full interacting theory in the Batalin--Vilkovisky (BV) formalism, the free limit of which is the twist computed in \cite{SWspinor}.\footnote{One subtlety is that, unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the eleven-dimensional theory is only $\ZZ/2$ graded.
-All odd fields can therefore in some sense be considered as ``ghosts'' in the twisted theory.}
+As such, a division of the odd fields in the twisted theory into ``ghosts'' and ``antifields'' is not really meaningful.}
 Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of eleven-dimensional supergravity on flat space.

### 2021-11-04 nonmin.tex
stuffed turkey

--- 2021-10-27 nonmin.tex
@@
 
-We have provided numerous consistency checks that the 11-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
+We have provided numerous consistency checks that the eleven-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
 We have referred to this theory as minimal as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of 11-dimensional supergravity from the lens of the holomorphic theory.  
+In this section we characterize a further twist of eleven-dimensional supergravity from the lens of the holomorphic theory.  
 This further twist is invariant for the group $G_2 \times SU(2)$ and is topological along seven directions, as opposed to just a single direction as in the $SU(5)$ twist.
@@
 \label{thm:nonmin}
-The non-minimal twist of the 11-dimensional theory is equivalent to Poisson Chern--Simons theory on 
+The non-minimal twist of the eleven-dimensional theory is equivalent to Poisson Chern--Simons theory on 
 \[
@@
 \]
-Notice that this choice of supercharge breaks the holonomy of the 11-dimensional theory from $SU(5)$ to $SU(2) \times SU(3)$.
+Notice that this choice of supercharge breaks the holonomy of the eleven-dimensional theory from $SU(5)$ to $SU(2) \times SU(3)$.
 
@@
 As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the nonminimal twist.
-We will find that the local character of the latter agrees with a specialization of the local character computed in \ref{sec:locchar}
+We will find that the local character of the latter agrees with a specialization of the local character computed in~\S\ref{sec:locchar}
 
 \begin{prop}
-The  local character of the nonminimal twist of 11d supergravity on flat space is given by
+The  local character of the nonminimal twist of eleven-dimensional supergravity on flat space is given by
 \[
@@
 For the last part, it suffices to observe the specialization at the level of single particle indices.
-A natural choice of fugacities for $SU(2)\times SU(3)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in \ref{sec:locchar} by requiring the additional constraints \[q_1q_2 = 1, \ \ \ q_3q_4q_5=1.\]
-After imposing the above constraints, the single particle index \ref{singleparticleindex} is
+A natural choice of fugacities for $SU(2)\times SU(3)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in~\S\ref{sec:locchar} by requiring the additional constraints \[q_1q_2 = 1, \ \ \ q_3q_4q_5=1.\]
+After imposing the above constraints, the single particle index~\eqref{singleparticleindex} is
 \[
@@
 
-We constructed an embedding of the $Q$-cohomology of the supersymmetry algebra into the fields of our 11-dimensional theory on $\CC^5 \times \RR$. 
+We constructed an embedding of the $Q$-cohomology of the supersymmetry algebra into the fields of our eleven-dimensional theory on $\CC^5 \times \RR$. 
 The further twist is obtained by working in a background where a certain field on $\CC^5 \times \RR$ takes nonzero value $Q_{nm}$. 
@@
 
-Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the 11-dimensional theory is the super Lie algebra $E(5,10)$.
+Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the eleven-dimensional theory is the super Lie algebra $E(5,10)$.
 From this point of view, the global symmetry algebra of the $Q_{nm}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
@@
 
-We proved in Theorem \ref{thm:global} that the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension $\Hat{E(5,10)}$ of the super Lie algebra~$E(5,10)$.
+We proved in Theorem \ref{thm:global} that the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension $\Hat{E(5,10)}$ of the super Lie algebra~$E(5,10)$.
 
@@
 \begin{prop}
-Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the 11-dimensional theory on $\CC^5 \times \RR$. 
+Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$. 
 Then, there is an isomorphism of Lie algebras 
@@
 
-This proposition implies that the global symmetry algebra of the non-minimal twist of 11-dimensional supergravity is the Lie algebra $\cO(\CC^2)$. 
+This proposition implies that the global symmetry algebra of the non-minimal twist of eleven-dimensional supergravity is the Lie algebra $\cO(\CC^2)$. 
 We will see that this is compatible with the calculation of the non-minimal twist of the full BV theory.
 
-\subsection{The non-minimal twist of the 11-dimensional theory}
+\subsection{The non-minimal twist of the eleven-dimensional theory}
 
@@
 \]
-Just in our original 11-dimensional theory, this theory is also only $\ZZ/2$ graded.
+Just in our original eleven-dimensional theory, this theory is also only $\ZZ/2$ graded.
 
@@
 
-We substitute the values for the fields in \eqref{eqn:g2map} into the original 11-dimensional action. 
+We substitute the values for the fields in \eqref{eqn:g2map} into the original eleven-dimensional action. 
 Notice that any terms involving $\gamma_z$ can be discarded. 

### 2021-11-04 intro.tex

@@
 Other twists can be understood as further twists of this holomorphic theory.
-The importance and interest of holomorphic twists was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite{NekThesis}.
-(Constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.)
+The importance and interest of holomorphic twists of supersymmetric gauge theories was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite[for example]{NekThesis,BCOV}.
+Si Li pushed applications of holomorphic QFT further in his work on the higher genus $B$-model (see~\cite{SiThesis}, and later \cite{CLbcov1} together with Costello). 
+In the physics literature, further constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.
 
@@
 \subsection*{Acknowledgements}
-We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, N.~Paquette, S.~R\"osch, J.~Walcher for conversation and inspiration of all kinds.
+We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, C.~Elliott, D.~Gaiotto, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, S.~Li, N.~Paquette, S.~R\"osch, J.~Walcher, P.~Yoo for conversation and inspiration of all kinds.
 I.S.

### 2021-11-04 dimred.tex
merge
bib; format; minor fixes; merge error

@@
 
-The original motivation for $M$-theory was as the strong coupling limit for type IIA string theory.
-Roughly, the radius of the $M$-theory circle plays the role of this coupling constant. 
-Additionally, at low energies $M$-theory is expected to be approximated by eleven-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity.
-Combining these two pictures, various checks have been made that the dimensional reduction of eleven-dimensional supergravity along the $M$-theory circle is type IIA supergravity.
+The original motivation for M-theory was as the strong coupling limit for type IIA string theory.
+Roughly, the radius of the M-theory circle plays the role of this coupling constant. 
+Additionally, at low energies M-theory is expected to be approximated by eleven-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity.
+Combining these two pictures, various checks have been made that the dimensional reduction of eleven-dimensional supergravity along the M-theory circle is type IIA supergravity.
 
@@
 \begin{multline}
-\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \in^{\Omega_{\CC^4}}t_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) \\ + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \frac{1}{1-\nu} (\til \eta \wedge \til \theta) \div \mu  .
+\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) \\ + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \frac{1}{1-\nu} (\til \eta \wedge \til \theta) \div \mu  .
 \end{multline}

### 2021-11-04 nonmin.tex
bib; format; minor fixes; merge error

@@
 \begin{prop}
+\label{prop:ham}
 Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$. 
-Then, there is an isomorphism of Lie algebras 
+Then there is an isomorphism of Lie algebras 
 \[
@@
 
-Poisson Chern--Siimons theory is defined on any manifold of the form
+Poisson Chern--Simons theory is defined on any manifold of the form
 \[
@@
 The first term in this expression agrees the term in \eqref{eqn:pcs1} which is not in $S_{pCS}(\alpha)$.
-The second term is zero for symmetry reasons. 
+
+The latter term $(1 - \til \alpha^3)^{-1} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2$ is of polynomial degree $\geq 4$. 
+Since this term has trivial self BV bracket, it determines a cocycle for the dg Lie algebra underlying Poisson Chern--Simons theory. 
+Since it is manifestly translation invariant, it arises via descent from a cocycle in the dg Lie algebra of $\infty$-jets of fields at $0 \in\CC^2 \times \RR^7$.
+This dg Lie algebra is quasi-isomorphic to the Lie algebra $\CC[[z_1,z_2]]$ equipped with the holomorphic Poisson bracket.
+(This is the formal power series version of the Lie algebra from Proposition~\ref{prop:ham}.)
+
+There is a weight grading on this Lie algebra, given by declaring $|z_1^{n+1} z_2^{m+1}| = n+m$; in turn, this induces a grading on the Gelfand--Fuks Lie algebra cohomology.  
+The weight of the Gelfand--Fuks class corresponding to our deformation is $+2$, since no derivatives of $z_1$ or $z_2$ appear. 
+Results from~\cite{Fuks} show that there is no cohomology in this weight. 
+As such, the cocycle must define a trivial deformation of the dg Lie algebra up to equivalence.
 This completes the proof that the non-minimal twist is equivalent to Poisson Chern--Simons theory. 
-
-%It remains to trivialize the remaining terms in parentheses. 
-%To do this, we fix a primitive $\eta$ of the holomorphic volume form $\d^3 w$. 
-%That is, $\eta$ is a holomorphic two-form on $W$ satisfying $\del \eta = \d^3 w$. 
-%Consider the (non-translation invariant) odd local functional
-%\[
-%\int \frac{1}{1-\til \alpha^3} \eta (\til \alpha^3)^2 \del^z \alpha^1 \del^z \alpha^0   .
-%\]
-%Using $\del^w \eta = \d^3 w$, we see that this functional trivializes the remaining terms in parentheses in \eqref{eqn:pcs1}.
-%This completes the argument. 
 \end{proof}
-%
-%Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
-%\begin{multline}
-%\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
-%\end{multline}
-%
-%\begin{multline}
-%\int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \left(\frac12 \del^X \alpha^1  [ \alpha^2 \vee (\alpha^2 \vee \Omega_X^{-1})] + \alpha^2 \del^Z \alpha^1 \del^Z \alpha^0\right) \\
-%+ \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^1 \partial^Z \alpha^1 \partial^Z \alpha^1 \\ + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \alpha^3 \partial^Z \alpha^0 \partial^Z \alpha^0 + \frac{\delta}{2} \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha^3} \partial^X \alpha^1 (\alpha^1 \Omega^{-1}_X \alpha^3) .
-%\end{multline}
-%
-%More invariantly, we can write the total BV action as
-%\[
-%\Tilde{I} = I_{CS} + I' 
-%\]
-%where $I_{CS} = \frac16 \int \alpha\{\alpha,\alpha\}$ and 
-%\beqn
-%I' = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha [\alpha \vee (\alpha \vee \Omega_X^{-1})] + \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} .
-%\label{eqn:Iprime}
-%\eeqn
-%
-%Consider the odd functional
-%\[
-%K = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] .
-%\]
-%
-%\begin{lem}
-%$Q K + \{I_{CS}, K\} = I'$ .
-%\end{lem}
-%
-%The linear differential applied to $K$ is 
-%\[
-%\frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} \partial^X \alpha \wedge [\alpha \vee (\alpha \vee \Omega_X^{-1})] \omega_Z .
-%\]
-%This is the first term in \eqref{eqn:Iprime}. 
-%
-%Next, we compute
-%\[
-%\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
-%\]
-%which is the second term in \eqref{eqn:Iprime}.

### 2021-11-04 nonmin.tex
G2

@@
 We have provided numerous consistency checks that the eleven-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
-We have referred to this theory as minimal as it depends on the complex structure in the maximal number of directions. 
-In this section we characterize a further twist of eleven-dimensional supergravity from the lens of the holomorphic theory.  
-This further twist is invariant for the group $G_2 \times SU(2)$ and is topological along seven directions, as opposed to just a single direction as in the $SU(5)$ twist.
+We have referred to this theory as ``minimal,'' since it renders the minimal number of translations homotopically trivial, or (slightly improperly) as ``holomorphic.''
+In this section we characterize the unique further twist of eleven-dimensional supergravity on flat space, as seen through the lens of the holomorphic theory.  
+This further twist is invariant for the group $G_2 \times SU(2)$ and is fully topological along seven directions, as opposed to just a single direction as in the minimal twist.
+This is easiest to see by decomposing the eleven-dimensional spinor as a representation of $\Spin(4) \times \Spin(7)$; from this perspective, a square-zero element is a rank-one element in the tensor product of a chiral spin representation of~$\Spin(4)$ and the spin representation of~$\Spin(7)$.
+Elements of the latter fall into two distinct orbits under the $\Spin(7)$ action, the minimal orbit---``Cartan pure spinors''---and the generic orbit~\cite{Igusa}.
+The stabilizer of an element of the generic orbit is~$G_2$, almost by definition.
 
-On flat space, the further twist is essentially unique and renders the theory topological in seven directions, rather than just one as in the holomorphic twist. 
-We will show that it is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory. 
-In the BV formalism, the theory $\ZZ/2$ graded and has fields given by
+We will show that the non-minimal twist is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument.
+This confirms a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}).
+
+In the BV formalism, the theory is $\ZZ/2$ graded, with fields given by
 \[

### 2021-11-04 nonmin.tex
eager/hahner

@@
 
-We will show that the non-minimal twist is equivalent to a theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument.
-This confirms a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}).
+We will show that the non-minimal twist is equivalent to an interacting theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument.
+This completes the confirmation of a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}); the result was checked at the level of the free theory in~\cite{EagerHahner} by computing the nonminimal twist of the eleven-dimensional multiplet directly at the component-field level.
 

### 2021-11-12 matrix.tex
fixed typos in htt

@@
 \item On the $\nu$'s we take $K$ to be any operator $K \colon \cO \to \Vect$ such that $\div K \nu = \nu$. 
-On the $\gamma$'s we take $K$ to be any operator $K \colon \Omega^1 \to \Omega^0$ such that $\del K(\gamma) = \gamma$. 
-Also, introduce the auxiliary operator $\til{K} \colon \Omega^2_{cl} \to \Omega^1$ which satisfies the homotopy relation
+On the $\gamma$'s we take $K$ to be any operator $K \colon \Omega^1 \to \Omega^0$ which satisfies the homotopy relation
 \beqn\label{eqn:htpy1}
-\til{K} \del \gamma + \del K \gamma = \gamma . 
+\til{K} \del \gamma + \del K \gamma = \gamma
 \eeqn
+for some auxiliary operator $\til{K} \colon \Omega^2_{cl} \to \Omega^1$.
+
 The precise form of each of these operators will not be needed.
@@
 Notice that $q(\mu)$ is automatically divergence-free.
-Next, $q(\gamma) = [\gamma]$, the equivalence class in $\Omega^1 / \d$. 
+Next, $q(\gamma) = \del \gamma$.
 If $\beta$ is a holomorphic function, then $q(\beta) = \beta (z=0)$.
 \item 
-The map $i$ embeds $\mu$ and $b$ in the obvious way.
-On the equivalence class $[\gamma] \in \Omega^1 / \d$ we define $i([\gamma]) = \gamma - \til{K} \del \gamma$. 
-Notice that this is independent of the choice of representative $\gamma$. 
+The map $i$ embeds $\mu$ and $b$ in the obvious way. On a closed two form $\alpha$, we have that $i(\alpha) = \til{K}\gamma$.
 \end{itemize}

### 2022-01-06 fivebranes/fivebranes.tex
fivebrane

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

%\linespread{1.2} %for editing

\addbibresource{references.bib}

\newcommand\thooft{`t Hooft\,}

\begin{document}

\title{Fivebranes}

\section{A single fivebrane}

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
In full generality, we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{\frac12}$.

There are four fundamental fields $(\omega, \eta, \phi,\psi)$ which consist of Dolbeault forms of type $(1,1)$ and $(0,2)$ on $X$
\[
\omega \in \Omega^{1,1}(X), \quad \eta \in \Omega^{0,2}(X),
\]
and sections 
\[
\phi \in \Omega^0(X , K^{\frac12}_\Sigma), \quad \psi \in \Omega^{0,2} (X , K^{\frac12}) .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\dbar \omega + \del \eta & = 0 \\
\dbar \eta = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

There is a system of gauge symmetries for the fields $\omega, \eta, \psi$. 
First, there are ghosts $A^{0,1}, A^{1,0}$ of Dolbeault type $(0,1)$ and $(1,0)$, respectively, which act by
\beqn
\label{eqn:ghost}
\begin{split}
\omega & \mapsto \omega + \dbar A^{1,0} + \del A^{0,1} \\
\eta & \mapsto \eta + \dbar A^{0,1} .
\end{split}
\eeqn
There is also a ghost $a \in \Omega^{0,1}(X, K^{\frac12})$ which acts by $\psi \mapsto \psi + \dbar a$. 
Finally, there are ghosts-for-ghosts which act on the ghosts by 
\beqn
\label{eqn:gghost}
\begin{split}
A^{1,0} & \mapsto A^{1,0} + \del \chi \\
A^{0,1} & \mapsto A^{0,1} + \dbar \chi \\
a & \mapsto a + \dbar \phi ,
\end{split}
\eeqn
where $\chi \in C^\infty(X)$ is a scalar and $\varphi \in \Gamma(X, K^{\frac12}_X)$.

This theory does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism.
For the sections $\phi$ we simply 
Rather, it is a (free) theory equipped with a presymplectic BV structure defined by the following two-form on the space of fields\brian{...}

\subsection{Local operators}

Upon applying the $\dbar$-equations of motion, the algebra of local operators of the theory are algebraically generated by the following linear local operators and their holomorphic derivatives
\begin{itemize}
\item $\cO_\chi$, $\cO_{\d z_i}$ where
\[
\cO_{\d z_i} \colon A^{1,0} = f^j (z) \d z_j \mapsto f^i (0) 
\]
for $i=1,2,3$. 
Notice that $\cO_\chi$ is of ghost degree $+2$ and $\cO_{\d z_i}$ is of ghost degree $+1$. 
\item $\cO_{\phi}$, $\cO_{\varphi}$. 
The operator $\cO_{\phi}$ is of ghost degree zero and $\cO_{\varphi}$ is of ghost degree $+2$. 
\end{itemize}
The residual classical BRST operator acts by 
\beqn
Q \cO_{\d z_i} = \del_{z_i} \cO_{\chi} 
\eeqn
and annihilates all remaining operators.

\begin{table}[htbp]
\centering
\begin{tabular}{llrrr}
 & $x$ & $y_1$ & $y_2$ & $z$ \\
$\cO_\chi$ & $x^{12}$ & 1 & 1 & 1\\
$\cO_{\d z_1}$ & $x^8$ & $y_1^{-1}$ & 1 & 1\\
$\cO_{\d z_2}$ & $x^8$ & $y_1$ & $y_2^{-1}$ & 1\\
$\cO_{\d z_3}$ & $x^8$ & $1$ & $y_2$ & 1\\
$\cO_\phi$ & x\textsuperscript{6} & 1 & 1 & $z^{\frac12}$ \\
$\cO_\varphi$ & x\textsuperscript{6} & 1 & 1 & $z^{-\frac12}$ \\
\end{tabular}
\caption{\label{tab:org156c4a5}Spectrum for a single fivebrane in the holomorphic twist}
\end{table}

\begin{prop}
The single particle index for a single fivebrane is 
\beqn
f_{five} (x,y_1,y_2,z) = \frac{x^6(z^{\frac12} + z^{-\frac12}) - x^8 (y_1^{-1} + y_1 y_2^{-1} + y_2) + x^{12}}{(1-x^4 y_1) (1-x^4 y_1^{-1} y_2) (1-x^4 y_2^{-1})} .
\eeqn
\end{prop}

\section{The $J$'s}

For $d > 1$ punctured affine space $\CC^d \setminus 0$ is not affine. 
We denote by $\sfA_3$ a particular algebraic model for the derived space of functions on punctured affine space. 
This model admits an inclusion of dg algebras 
\[
\sfA_3 \hookrightarrow \RR\Gamma(\CC^3 \setminus 0, \cO) 
\]
which is dense at the level of cohomology.

\begin{thm}
The operators $J[r,s]$ and their descendants form the dg Lie algebra
\beqn
\sfA_{3} \otimes \cO(\CC^2) 
\eeqn
where the commutator is 
\[
[F, G] = \ep_{ab} \del_{w_a} F \del_{w_b} G + \oint_{z \in S^5} \ep_{ab} \del_{w_a} F \del_{w_b} G |_{w=0}   .
\]
\end{thm}

\textbf{Notation}: 
Recall that the $\mu$-field is a section of $\PV^{1,\bu}(\CC^5)\otimes \Omega^\bu(\RR)$.
We will decompose it as
\[
\mu = \mu_{z_i} \del_{z_i} + \mu_{w_a} \del_{w_a} 
\]
so that the $\mu_{z_i}$ correspond to vector fields that point along the fivebrane and the $\mu_{w_a}$ are transverse. 
In this section we make explicit the Dolbeault-de Rham form dependence on the $\mu$-fields.
We will denote the components of the $\mu_{w_a}$-field, for instance, by
\[
\mu^{k;l}_{w_i} \del_{w_i} \in \PV^{1,k}(\CC^5) \otimes \Omega^{l} (\RR) .
\]

Introduce the differential operator
\[
D_{r,s} \define \frac{1}{r!s!} \del_{w_1}^r \del_{w_2}^r .
\]
Recall that there are bosonic operators $\til{J}_a [r,s]$ which couple to the vector fields $\mu_{w_a}$ which are normal to the fivebrane via
\beqn
\label{eqn:Ja}
\int_{\CC^3} \til{J}_a [r,s] (z) D_{r,s} \mu_{w_a}^{3;0}(z) .
\eeqn
Notice that $J_a[r,s]$ is a local (zero form) operator which couples to the Dolbeault $(0,3)$ part of $\mu_{w_a}$.

By holomorphic descent we obtain the Dolbeault valued local operator 
\beqn
\til{J}_a^\bu [r,s] (z) = \til{J}_a [r,s] + \til{J}_a^i[r,s] \d \zbar_i + \til{J}^{ij}_{a} [r,s] \d \zbar_i \d \zbar_j + \cdots .
\eeqn
This Dolbeault valued operator couples by the same formula as in \eqref{eqn:Ja}.
In this coupling other Dolbeault components of $\mu_{w_a}$ also appear,
\beqn
\label{eqn:Jb}
\int_{\CC^3} \til{J}_a [r,s] (z) D_{r,s} \mu_{w_a}^{3;0}(z) + \int_{\CC^3} \til{J}^i_a [r,s] (z) D_{r,s} \mu_{w_a}^{2;0}(z) \d \zbar_i + \int_{\CC^3} \til{J}^{ij}_a [r,s] (z) D_{r,s} \mu_{w_a}^{1;0}(z) \d \zbar_i \d \zbar_j .
\eeqn

\subsection{$\til J_1 \til J_1$}

The gauge variation of $\mu_1$ is
%\begin{align*}
%	Q \mu_1^{3;0} & = \dbar \mu^{2;0} + \mu_{w_a} \partial_{w_a} \fc_{w_1} + \mu_{z_i} \partial_{z_i} \fc_{w_1} - \fc_{w_a} \partial_{w_a} \mu_1 - \fc_{z_i} \partial_{z_i} \mu_{w_1} \\
%& + \partial_{w_2} \fc_\gamma \partial_z \alpha -  \partial_z\fc_\gamma \partial_{w_2} \alpha + \partial_{w_2} \fc_\alpha \partial_z \gamma - \partial_z \fc_\alpha \partial_{w_2} \gamma .
%\end{align*}

\end{document}

### 2022-01-06 dfn.tex
bib; format; minor fixes; merge error
merge

@@
 \]
-where $\int^\Omega_{X \times S} \alpha = \int_{X \times S} \alpha \wedge \Omega$.
+where $\int^\Omega_{X \times S} \alpha \define \int_{X \times S} \alpha \wedge \Omega$.
 
@@
   \deq{
-    J = \frac16 \gamma \wedge \del \gamma \wedge \del \gamma ,
+    J = \frac16 \int_{X \times S} \gamma \wedge \del \gamma \wedge \del \gamma ,
   }
@@
 In \cite{GRWthf} an existence result for one-loop quantizations of mixed topological-holomorphic theories was established. 
+The crucial thing is that these results apply to more than just topological-holomorphic theories arising from twists of supersymmetric gauge theories.
+They also apply to twists of supergravity theories. 
 We apply this to the eleven-dimensional model at hand.
@@
 
-Recall that the action functional of the eleven-dimensional theory is $S_{BF, \infty} + c J$. 
+Recall that the action functional of the eleven-dimensional theory is $S_{BF, \infty} + g J$. 
 Since the cubic and higher interactions only involve holomorphic derivatives, we obtain the following directly from the main result of \cite{GRWthf}.
@@
 Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 
-We will return to the existence and uniqueness of a higher order quantization of the eleven-dimensional theory in future work.
+We will return to the existence and uniqueness of a higher order quantization of the eleven-dimensional theory (before turning on the $\Omega$-background) in future work.

### 2022-01-06 dimred.tex

@@
 \parsec[s:poisson]
-The original action for Kodaira-Spencer theory posited by \cite{BCOV} has a nonlocal kinetic term.
+The original action for Kodaira--Spencer theory posited by \cite{BCOV} has a nonlocal kinetic term.
 In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form.
@@
 For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket.
-%Explicitly, the above kernel pairs against the dual to 
-%\[
-%\Sigma^1 = \sum u^k\mu^1_k, \Sigma^2 = \sum u^k\mu^2_k\in \PV^{\bu,\bu}%(X)[[u]][2]
-%\]
-% by the formula 
-%\[
-%\int \overline{\mu}_0^1\div \overline{\mu}_0^2.
-%\] 
-%Here, the overlines denote the dual field in 
-%\[
-%(\PV^{\bu,\bu}(X)[[u]][2])^*=\PV_c^{d-\bu,d-\bu}(X)[[u]][2].
-%\] 
-%That is, further expanding the fields as 
-%\[
-%\mu_k = \sum_{i,j=1}^d\mu_k^{(i,j)}\in \PV^{i,j}
-%\] 
-%the expression pairs $\overline{\mu}_0^{(i,j)}$ with $\overline{\mu}_0^{(d-1-i, d-j)}$.
 
@@
 In the supergravity approximation, the fields that survive are those closed string fields that propogate.
-In terms of our description of closed string field theory in terms of Kodaira-Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor.
-This is referred to as minimal Kodaira-Spencer theory.
+In terms of our description of closed string field theory in terms of Kodaira--Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor.
+This is referred to as minimal Kodaira--Spencer theory.
 
-The fields of minimal Kodaira-Spencer theory are given by the subcomplex of \label{eqn:ks1}
+The fields of minimal Kodaira--Spencer theory are given by the subcomplex of \label{eqn:ks1}
 \beqn
@@
 We observe that the original odd Poisson tensor lives in this subcomplex. 
-%here is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira-Spencer theory is a Poisson map. 
+%here is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira--Spencer theory is a Poisson map. 
 There is a natural action functional given by restricting $I_{BCOV}$ to this space.
@@
 
-Let $X$ be a Calabi-Yau manifold of complex dimension four. 
+Let $X$ be a Calabi--Yau manifold of complex dimension four. 
 The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
@@
 We will need a more detailed description of the classical action. 
-For the moment, let us introduce some notations for the fields of this IIA model, as always we leave the internal Dolbeault degree implicit:
+For the moment, let us introduce some notations for the fields of this IIA model. As always, we leave the internal Dolbeault degree implicit:
 \begin{multline}
@@
 \eeqn
-where the $\cdots$ denote terms involving higher order descendants.
+where the $\cdots$ denotes terms involving higher-order descendants.
 
@@
 The first goal is to compare the dimensional reduction of our eleven-dimensional theory on $\CC^5 \times \RR$
-%where $X$ is a Calabi-Yau 4-fold 
+%where $X$ is a Calabi--Yau 4-fold 
 with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times \CC^4$. 
@@
 In other words, it did not define a theory in the conventional BV formalism. 
-One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd non-degenerate pairing thus equipping it with the structure of a theory in the conventional BV formalism.
+One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd nondegenerate pairing, thus equipping it with the structure of a theory in the conventional BV formalism.
 
@@
 Concretely, the space of fields of the $SU(5)$ twist of type I supergravity is a subspace of minimal Kodaira--Spencer theory on $\CC^5$. 
-The $\ZZ/2$ graded space of field equipped with its linear BRST operator is 
+The $\ZZ/2$ graded space of fields equipped with its linear BRST operator is 
 \beqn\label{eqn:IIApot}
 \begin{tikzcd}
-- & + & - & +  \\ \hline
+- & + & - & +  \\[-1.7em] \hline
 {\PV^{1,\bu}}(\CC^5) \arrow[r, "u\div"]    & {u\PV^{0,\bu}}(\CC^5) \\
@@
 \end{equation} 
-This space of fields is equipped with an odd non-degenerate pairing.
+This space of fields is equipped with an odd nondegenerate pairing.
 Like the eleven-dimensional theory, it is a classical BV theory in the $\ZZ/2$-graded sense.
@@
 This is precisely the underlying cochain complex of fields for the type I model with potentials. 
-The odd non-degenerate pairing on this complex agrees with the one on this particular potential theory for the twist of type I supergravity. 
+The odd nondegenerate pairing on this complex agrees with the one on this particular potential theory for the twist of type I supergravity. 
 The $L_\infty$ structure on the parity shift of this complex is compatible with the one induced from the BV action in \eqref{eqn:Iactionpot}.
@@
 \label{prop:5dsugra}
-The compactification of the eleven-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of five-dimensional $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hyper multiplets.
+The compactification of the eleven-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of five-dimensional $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hypermultiplets.
 \end{prop}
@@
 We give a conjectural capitulation of the twist of five-dimensional $\cN=1$ supergravity. 
-Before twisting, a general five-dimensional $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hyper multiplets. 
-The twist of the vector and hyper multiplet has been computed in \cite{ESW}, and we recall it below. 
+Before twisting, a general five-dimensional $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hypermultiplets. 
+The twist of the vector and hypermultiplet has been computed in \cite{ESW}, and we recall it below. 
 The twist of the gravity multiplet is less clear. 

### 2022-01-06 suco.tex

@@
 In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of eleven-dimensional supergravity.
-%In the physical AdS background, the only bosonic fields which are non-zero are the metric and the \brian{finish}
 
@@
 Notice that these vector fields are divergence-free and reduce to the usual holomorphic conformal transformations along $w=0$.
-\item The bosonic summand $\lie{sl}(4)$ is mapped to the $4$-dimensional rotations: 
+\item The bosonic summand $\lie{sl}(4)$ is mapped to four-dimensional rotations: 
 \[
@@
 The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
-It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$ so that the odd part decomposes as
+It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$, so that the odd part decomposes as
 \[
@@
 \begin{proof}
-The second assertion follows from Theorem \ref{thm:global} that as a super Lie algebra the linearized BRST cohomology of the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
+The second assertion follows from Theorem \ref{thm:global}, which shows that, as a super Lie algebra, the linearized BRST cohomology of the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$.
 Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
@@
 
-Next, we turn on a nontrivial unit of flux $N \ne 0$. 
+Next, we turn on $N \ne 0$ units of nontrivial flux. 
 Since not all of the fields we wrote down above commute with the flux $N F_{M2}$, they are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$.
@@
 The remaining piece of the original BRST operator is drawn in dotted lines. 
-The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to dotted line operators.
-In this description the image of the flux $F$ at this page in the spectral sequence corresponds to the class 
+The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to the dotted-line operators.
+In this description, the image of the flux $F$ at this page in the spectral sequence corresponds to the class 
 \[
@@
 \]
-%and suppose 
-%\[
-%\til F \in \Bar{\Omega}^{1,2} (\CC^5) \otimes \Bar{\Omega}^1(\RR)
-%\]
-%satisfies $\del \til F = F$. 
 Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
@@
 \begin{proof}
-The first equation equation 
+The first equation,
 \[
-\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0}
+\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0},
 \]
-characterizes the kernel representing $N$ times the residue class for a $4$-sphere in 
+characterizes the kernel representing $N$ times the residue class for a four-sphere in 
 \[
@@
 The roles of the $\lie{sl}(4)$ and $\lie{sl}(2)$ summands are interchanged compared to the case of the M2 brane.
-The Lie algebra $\lie{sl}(4)$ represents conformal transformations along the plane $\CC^3_z$.
-Since not all such infinitesimal transformations are divergence-free, there precise formulas must be adjusted.   
-The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence free.
+The Lie algebra $\lie{sl}(4)$ represents (holomorphic) conformal transformations along the plane $\CC^3_z$, again coming from the natural action on $P^3(\C)$.
+Since not all such infinitesimal transformations are divergence-free, the precise vector fields must be adjusted.   
+The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence-free.
 In more detail, the embedding of the bosonic piece can be given by the following explicit formulas.
@@
 \item
-The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ is mapped to the translations 
+The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ of translations is mapped to the obvious vector fields 
 \[
@@
 \item
-The bosonic subalgebra $\CC \subset \lie{sl}(4)$ is mapped to the element
+The bosonic subalgebra $\CC \subset \lie{sl}(4)$ corresponding to rescaling $\C^3$ is mapped to the element
 \[
@@
 \] 
-Notice that these vector fields are divergence-free and restrict to the ordinary dilation along $w=0$. 
+Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
 \item 
@@
 \item 
-The bosonic summand $\lie{sl}(2)$ is mapped to the triple
+The bosonic summand $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
 \[
@@
 \begin{itemize} 
-\item The summand $L \otimes R$ consists of the remaining 6d superstranlsations. 
+\item The summand $L \otimes R$ consists of the remaining 6d supertranslations. 
 It is mapped to the fields 
@@
 
-Next, we turn on a nontrivial unit of flux $N \ne 0$. 
+Next, we turn on $N \ne 0$  units of nontrivial flux. 
 Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.
@@
 Consider the homogenous element $w_1^{-1} w_2^{-1}$. 
-This represents the class of the Dolbeault-de Rham $2$-form
+This represents the class of the Dolbeault-de Rham two-form
 \[
@@
 \]
-Notice that if we wedge with the volume form $\d w_1 \d w_2$ this is the unit $N=1$ flux introduced in Lemma \ref{lem:ads7flux}. 
-The homogenous element $w_1^{-n-1} w_2^{-m-1}$ represents the class of the holomorphic derivatives $\partial_{w_1}^n \partial_{w_2}^{m}$ applied to this $2$-form.
+Notice that, if we wedge with the volume form $\d w_1 \d w_2$, this is the unit  flux ($N=1$) introduced in Lemma \ref{lem:ads7flux}. 
+The homogenous element $w_1^{-n-1} w_2^{-m-1}$ represents the class of the holomorphic derivatives $\partial_{w_1}^n \partial_{w_2}^{m}$ applied to this two-form.
 
-Observe that when restricted to $\CC^5 \times \RR \setminus \CC^3$ the holomorphic tangent bundle along $\CC^5$ is still trivializable.
+Observe that, when restricted to $\CC^5 \times \RR \setminus \CC^3$, the holomorphic tangent bundle along $\CC^5$ is still trivializable.
 
@@
 
-Let's turn to the proof of Proposition \ref{prop:brads7}.
+Let's turn to the proof of Proposition~\ref{prop:brads7}.
 We proceed completely analogously to the case of backreacted M2 branes as in the proof of Proposition \ref{prop:brads4}.

### 2022-02-22 fivebranes/index.tex
began adding index file, created main

\subsection{Large $N$ Holomorphic Character}

We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of M5 branes. Let us briefly recall the proposal specialized to our situation \surya{this should go elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support. The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization envelope $\mc U(\mc L) = C_{\bullet}\left (\iota^{*}\cL)_{c} \right )$.

Since quantities like indices are deformation invariants, we need not consider such deformations for now. In fact we may replace $\cL$ with the abelian local dg Lie algebra describing the free limit. Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes

\[
\begin{tikzcd}
  &  \ul{\rm odd} & \ul{\rm even} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}& \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[l, "\del"]
\end{tikzcd}
.\]

\parsec
We begin by computing the hypercohomology of the factorization envelope. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.

We first introduce the following notation for representatives of classes in compactly supported Dolbeault cohomology. We write $\delta^{(a,b,c)}$ to denote the derivative of the delta function $\del_{z_{1}}^{a}\del_{z_{2}}^{b}\del_{z_{3}}^{c}\delta_{t=w_{a}=0}$.

\begin{lem}
  The hypercohomology of the factorization envelope is given by \[\sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2} \\
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}\\
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}

          where $a, b, c, k, l \geq 0$.
    \item $V_{\mu}$ is spanned by
          \begin{align}

          \end{align}
  \end{itemize}
\end{lem}

Here, we have introduced the notation $\delta^{(a,b,c)}$

The index we compute will have four fugacities, which we label as follows:
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the cartan of $\SU(3)$ which acts on $\C^{3}_{z}$.
  \item $r$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
  \item $q$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
\end{itemize}

A convenient choice of choice of weights is as in the following table:

\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & 1 & 0 & -1 & 0 & 0 \\
  $t_{2}$ & 0 & 1 & -1 & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & -1 \\
  $q$ & -1 & -1 & -1 & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\end{center}

### 2022-02-22 fivebranes/index.tex
Add files via upload

@@
 We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of M5 branes.
-Let us briefly recall the proposal specialized to our situation \surya{this should go elsewhere}.
-Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$.
+Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}.
+Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$.
 Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support.
-The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization envelope $\mc U(\mc L) = C_{\bullet}\left (\iota^{*}\cL)_{c} \right )$.
+The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization envelope $\cU(\iota^{*} \cL) = C_{\bullet}\left ((\iota^{*}\cL)_{c} \right )$.
 
@@
 \begin{tikzcd}
-  &  \ul{\rm odd} & \ul{\rm even} \\
+  &  \ul{\rm even} & \ul{\rm odd} \\
  \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
@@
 \begin{lem}
-  The hypercohomology of the factorization envelope is given by \[\sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
+  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \c U (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
   \begin{itemize}
@@
           \begin{align}
-            \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
-            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2} \\
+            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
+            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
              \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
-            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}\\
+            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
@@
           \begin{align}
-
+            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{1}},\
+             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l-1}\del_{z_{1}}\text{ where }a > 0, b,c,k,l \geq 0 \\
+            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,b-1,c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{2}}, \ \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(0,b-1,c)}w_{1}^{k}w_{2}^{l-1}\del_{z_{2}}\text{ where }b > 0,c,k,l \geq 0 \\
+            & \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,0,c-1)}w_{1}^{k-1}w_{2}^{l}\del_{z_{3}}, \ \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-l\delta^{(0,0,c-1)}w_{1}^{k}w_{2}^{l-1}\del_{z_{3}}\text{ where } c > 0,k,l \geq 0 \\
+            & \delta^{(0,0,0)}w_{2}^{l}\del_{w_1}, \ \delta^{(0,0,0)}w_{1}^{k}\del_{w_2}\text{ where }k,l \geq 0
           \end{align}
@@
 \end{lem}
+\begin{proof}
+  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and form degree.
+The $E_{1}$ page is the $d+\delbar$ cohomology and is given by the symmetric algebra on
+\[
+\begin{tikzcd}
+\ul{\rm even} & \ul{\rm odd} \\
+H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}}) \ar[r, "\del_{\Omega}"] & \H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] \
+H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T^{*}_{\C^{5}}) \ar[l, "\del"]
+\end{tikzcd}
+.\]
 
-Here, we have introduced the notation $\delta^{(a,b,c)}$
+\surya{...}
+
+\end{proof}
 

### 2022-02-22 fivebranes/main.tex
Add files via upload

--- 2022-01-06 fivebranes/fivebranes.tex
@@
 
-\title{Fivebranes}
+\title{}
 
-\section{A single fivebrane}
-
-The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
-In full generality, we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{\frac12}$.
-
-There are four fundamental fields $(\omega, \eta, \phi,\psi)$ which consist of Dolbeault forms of type $(1,1)$ and $(0,2)$ on $X$
-\[
-\omega \in \Omega^{1,1}(X), \quad \eta \in \Omega^{0,2}(X),
-\]
-and sections 
-\[
-\phi \in \Omega^0(X , K^{\frac12}_\Sigma), \quad \psi \in \Omega^{0,2} (X , K^{\frac12}) .
-\]
-%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
-The equations of motion read
-\beqn
-\label{eqn:eom}
-\begin{split}
-\dbar \omega + \del \eta & = 0 \\
-\dbar \eta = \dbar \phi = \dbar \psi & = 0 .
-\end{split}
-\eeqn
-
-There is a system of gauge symmetries for the fields $\omega, \eta, \psi$. 
-First, there are ghosts $A^{0,1}, A^{1,0}$ of Dolbeault type $(0,1)$ and $(1,0)$, respectively, which act by
-\beqn
-\label{eqn:ghost}
-\begin{split}
-\omega & \mapsto \omega + \dbar A^{1,0} + \del A^{0,1} \\
-\eta & \mapsto \eta + \dbar A^{0,1} .
-\end{split}
-\eeqn
-There is also a ghost $a \in \Omega^{0,1}(X, K^{\frac12})$ which acts by $\psi \mapsto \psi + \dbar a$. 
-Finally, there are ghosts-for-ghosts which act on the ghosts by 
-\beqn
-\label{eqn:gghost}
-\begin{split}
-A^{1,0} & \mapsto A^{1,0} + \del \chi \\
-A^{0,1} & \mapsto A^{0,1} + \dbar \chi \\
-a & \mapsto a + \dbar \phi ,
-\end{split}
-\eeqn
-where $\chi \in C^\infty(X)$ is a scalar and $\varphi \in \Gamma(X, K^{\frac12}_X)$.
-
-This theory does not admit a Lagrangian description. 
-However, it can still be put in a degenerate form of the BV formalism.
-For the sections $\phi$ we simply 
-Rather, it is a (free) theory equipped with a presymplectic BV structure defined by the following two-form on the space of fields\brian{...}
-
-\subsection{Local operators}
-
-Upon applying the $\dbar$-equations of motion, the algebra of local operators of the theory are algebraically generated by the following linear local operators and their holomorphic derivatives
-\begin{itemize}
-\item $\cO_\chi$, $\cO_{\d z_i}$ where
-\[
-\cO_{\d z_i} \colon A^{1,0} = f^j (z) \d z_j \mapsto f^i (0) 
-\]
-for $i=1,2,3$. 
-Notice that $\cO_\chi$ is of ghost degree $+2$ and $\cO_{\d z_i}$ is of ghost degree $+1$. 
-\item $\cO_{\phi}$, $\cO_{\varphi}$. 
-The operator $\cO_{\phi}$ is of ghost degree zero and $\cO_{\varphi}$ is of ghost degree $+2$. 
-\end{itemize}
-The residual classical BRST operator acts by 
-\beqn
-Q \cO_{\d z_i} = \del_{z_i} \cO_{\chi} 
-\eeqn
-and annihilates all remaining operators.
-
-\begin{table}[htbp]
-\centering
-\begin{tabular}{llrrr}
- & $x$ & $y_1$ & $y_2$ & $z$ \\
-$\cO_\chi$ & $x^{12}$ & 1 & 1 & 1\\
-$\cO_{\d z_1}$ & $x^8$ & $y_1^{-1}$ & 1 & 1\\
-$\cO_{\d z_2}$ & $x^8$ & $y_1$ & $y_2^{-1}$ & 1\\
-$\cO_{\d z_3}$ & $x^8$ & $1$ & $y_2$ & 1\\
-$\cO_\phi$ & x\textsuperscript{6} & 1 & 1 & $z^{\frac12}$ \\
-$\cO_\varphi$ & x\textsuperscript{6} & 1 & 1 & $z^{-\frac12}$ \\
-\end{tabular}
-\caption{\label{tab:org156c4a5}Spectrum for a single fivebrane in the holomorphic twist}
-\end{table}
-
-\begin{prop}
-The single particle index for a single fivebrane is 
-\beqn
-f_{five} (x,y_1,y_2,z) = \frac{x^6(z^{\frac12} + z^{-\frac12}) - x^8 (y_1^{-1} + y_1 y_2^{-1} + y_2) + x^{12}}{(1-x^4 y_1) (1-x^4 y_1^{-1} y_2) (1-x^4 y_2^{-1})} .
-\eeqn
-\end{prop}
-
-\section{The $J$'s}
-
-For $d > 1$ punctured affine space $\CC^d \setminus 0$ is not affine. 
-We denote by $\sfA_3$ a particular algebraic model for the derived space of functions on punctured affine space. 
-This model admits an inclusion of dg algebras 
-\[
-\sfA_3 \hookrightarrow \RR\Gamma(\CC^3 \setminus 0, \cO) 
-\]
-which is dense at the level of cohomology.
-
-\begin{thm}
-The operators $J[r,s]$ and their descendants form the dg Lie algebra
-\beqn
-\sfA_{3} \otimes \cO(\CC^2) 
-\eeqn
-where the commutator is 
-\[
-[F, G] = \ep_{ab} \del_{w_a} F \del_{w_b} G + \oint_{z \in S^5} \ep_{ab} \del_{w_a} F \del_{w_b} G |_{w=0}   .
-\]
-\end{thm}
-
-\textbf{Notation}: 
-Recall that the $\mu$-field is a section of $\PV^{1,\bu}(\CC^5)\otimes \Omega^\bu(\RR)$.
-We will decompose it as
-\[
-\mu = \mu_{z_i} \del_{z_i} + \mu_{w_a} \del_{w_a} 
-\]
-so that the $\mu_{z_i}$ correspond to vector fields that point along the fivebrane and the $\mu_{w_a}$ are transverse. 
-In this section we make explicit the Dolbeault-de Rham form dependence on the $\mu$-fields.
-We will denote the components of the $\mu_{w_a}$-field, for instance, by
-\[
-\mu^{k;l}_{w_i} \del_{w_i} \in \PV^{1,k}(\CC^5) \otimes \Omega^{l} (\RR) .
-\]
-
-Introduce the differential operator
-\[
-D_{r,s} \define \frac{1}{r!s!} \del_{w_1}^r \del_{w_2}^r .
-\]
-Recall that there are bosonic operators $\til{J}_a [r,s]$ which couple to the vector fields $\mu_{w_a}$ which are normal to the fivebrane via
-\beqn
-\label{eqn:Ja}
-\int_{\CC^3} \til{J}_a [r,s] (z) D_{r,s} \mu_{w_a}^{3;0}(z) .
-\eeqn
-Notice that $J_a[r,s]$ is a local (zero form) operator which couples to the Dolbeault $(0,3)$ part of $\mu_{w_a}$.
-
-By holomorphic descent we obtain the Dolbeault valued local operator 
-\beqn
-\til{J}_a^\bu [r,s] (z) = \til{J}_a [r,s] + \til{J}_a^i[r,s] \d \zbar_i + \til{J}^{ij}_{a} [r,s] \d \zbar_i \d \zbar_j + \cdots .
-\eeqn
-This Dolbeault valued operator couples by the same formula as in \eqref{eqn:Ja}.
-In this coupling other Dolbeault components of $\mu_{w_a}$ also appear,
-\beqn
-\label{eqn:Jb}
-\int_{\CC^3} \til{J}_a [r,s] (z) D_{r,s} \mu_{w_a}^{3;0}(z) + \int_{\CC^3} \til{J}^i_a [r,s] (z) D_{r,s} \mu_{w_a}^{2;0}(z) \d \zbar_i + \int_{\CC^3} \til{J}^{ij}_a [r,s] (z) D_{r,s} \mu_{w_a}^{1;0}(z) \d \zbar_i \d \zbar_j .
-\eeqn
-
-\subsection{$\til J_1 \til J_1$}
-
-The gauge variation of $\mu_1$ is
-%\begin{align*}
-%	Q \mu_1^{3;0} & = \dbar \mu^{2;0} + \mu_{w_a} \partial_{w_a} \fc_{w_1} + \mu_{z_i} \partial_{z_i} \fc_{w_1} - \fc_{w_a} \partial_{w_a} \mu_1 - \fc_{z_i} \partial_{z_i} \mu_{w_1} \\
-%& + \partial_{w_2} \fc_\gamma \partial_z \alpha -  \partial_z\fc_\gamma \partial_{w_2} \alpha + \partial_{w_2} \fc_\alpha \partial_z \gamma - \partial_z \fc_\alpha \partial_{w_2} \gamma .
-%\end{align*}
+\input{index}
 

### 2022-02-22 fivebranes/index.tex
fixed typos

@@
  \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
- \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}& \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[l, "\del"]
-\end{tikzcd}
+ \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
+& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
 .\]
@@
 \begin{proof}
-  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and form degree.
-The $E_{1}$ page is the $d+\delbar$ cohomology and is given by the symmetric algebra on
+  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and holomorphic form degree.
+The $E_{1}$ page is the $d+\dbar$ cohomology and is given by the symmetric algebra on
+
   \[
@@
 \ul{\rm even} & \ul{\rm odd} \\
-H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}}) \ar[r, "\del_{\Omega}"] & \H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] \
-H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T^{*}_{\C^{5}}) \ar[l, "\del"]
+H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}})) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) )\\
+H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3},  \iota^{*}T^{*}_{\C^{5}}))& H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO)) \ar[l, "\del"]
 \end{tikzcd}

### 2022-02-22 fivebranes/index.tex
edit

@@
 Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support.
-The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization envelope $\cU(\iota^{*} \cL) = C_{\bullet}\left ((\iota^{*}\cL)_{c} \right )$.
+The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization enveloping algebra
+\[
+\bU(\iota^{*} \cL) = C_{\bullet}\left( (\iota^{*}\cL)_{c} \right) .
+\]
 
-Since quantities like indices are deformation invariants, we need not consider such deformations for now.
-In fact we may replace $\cL$ with the abelian local dg Lie algebra describing the free limit.
+Since quantities like indices are deformation invariant, we need not consider such deformations for now. 
+In fact in this section we may, and will, replace the local Lie algebra $\cL$ with the abelian local dg Lie algebra which underlies the free limit of the twisted supergravity theory. 
 Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes
-
 \[
@@
   &  \ul{\rm even} & \ul{\rm odd} \\
- \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
+ \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{\C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
  \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
@@
 \parsec
-We begin by computing the hypercohomology of the factorization envelope. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.
+
+Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
+The $\mu$-field decomposes into vector field components which point along and transverse to the brane
+\[
+\mu
+\]
+%
+%is the sheaf of $\Z/2$-graded cochain complexes
+%\[
+%\begin{tikzcd}
+%  &  \ul{\rm even} & \ul{\rm odd} \\
+% \mu|_{w=t=0} \in & \PV^{1,\bullet}_{\C^{3}} \ar[r, "\del_{\Omega}"] & \PV^{0,\bullet}_{\C^{3}}\\
+% \gamma|_{w=t=0} \in & \Omega^{0,\bullet}_{\C^{3}} \ar[r, "\del"]
+%& \Omega^{1,\bullet}_{\C^{3}}\end{tikzcd}
+%.\]
+
+We begin by computing the hypercohomology of the factorization enveloping algebra. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.
 
@@
 \begin{lem}
-  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \c U (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
+  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \cU (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
   \begin{itemize}

### 2022-03-01 fivebranes/fivebranes.tex
fivebrane

@@
 
-\section{The $J$'s}
+\section{The $E(3,6)$ symmetry}
 
@@
 
+\subsection{Embedding $E(3|6)$ into twisted supergravity}
+
+\parsec[]
+First we explain how $E(3|6)$ embeds inside of $E(5|10)$. 
+We follow \cite{KacCheng}.
+
+A vector field $X = X(z) \in \Vect(\C^3)$ embeds as the vector field
+\[
+X \mapsto X(z) - \frac12 (\del X)(z) \sum_{i=1}^2 w_a \del_{w_a} .
+\]
+Here, $\del X$ is the divergence of $X$ with respect to the standard holomorphic volume form on $\C^3$. 
+The elements $e,h,f \otimes f(z) \in \lie{sl}(2) \otimes \C[z_i]$ embed as the vector fields
+\[
+f(z) w_1 \del_{w_2} , \quad f(z) (w_1 \del_{w_2} - w_2 \del_{w_1}, \quad f(z) w_2 \del_{w_1} . 
+\]
+respectively.
+
+Next, we explain how the odd summand embeds. 
+Recall, a general element in the odd part of $E(3|6)$ can be written as
+\[
+g(z) \del_{z_i}^{1/2} \otimes r_\pm .
+\]
+This element embeds into $E(5|10)$ as the following closed two-form
+\[
+\del \left((w_1-w_2) g(z) \d z_i \right) .
+\]
+\brian{check this}
+
+\subsection{The local Lie algebra}
+
+Let $\cE(5|10)$ be the following local Lie algebra on $X \times \C^2 \times \R$.
+
+Let $\pi \colon X \times \C^2 \times \RR \to X$. 
+We will give a model $\cG_{grav}$ for $\pi_* \cE(5|10)$ as a local Lie algebra on $\C^3$.
+
+First, introduce the holomorphic line bundle 
+\[
+w_1^k w_2^\ell \cO_{X} \define ??  .
+\]
+Let $\lie{s}_2$ denote the Lie algebra of polynomial vector fields in the variables $w_1,w_2$ which preserve the holomorphic volume form $\d w_1 \d w_2$.
+
+\begin{dfn}
+Let $\cG_{grav}$ be the following local Lie algebra on the complex three-fold $X$. 
+\begin{itemize}
+\item The even part is 
+\[
+\Omega^{0,\bu}(X , \T_X \otimes \cO_X [w_1,w_2]) \oplus \Omega^{0,\bu}(X , \lie{s}_2) .
+\]
+\item The odd part is 
+\[
+\Omega^{\geq 2, \bu}(X, \cO_X[w_1,w_2]) \oplus \Omega^{1,\bu}(X, w_1 \cO_X[w_1,w_2]) \oplus \Omega^{1,\bu}(X, w_2 \cO_X[w_1,w_2]) \oplus \cdots
+\]
+\end{itemize} 
+\end{dfn}
+
+\parsec
+
+Consider the following auxiliary grading on the local Lie algebra $\cG_{grav}$. 
+The variables $w_a$ are declared to have weight $+1$. 
+%The variables $\til w_a$ are declared to have weight $-1$. 
+Additionally, parity has weight $-1$.
+Thus, for example, the weight of $w_1 \d z_1 \d z_2$ is zero.
+
 \end{document}

### 2022-03-01 fivebranes/index.tex
minor edits

@@
 Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$.
-Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support.
-The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization enveloping algebra
-\[
-\bU(\iota^{*} \cL) = C_{\bullet}\left( (\iota^{*}\cL)_{c} \right) .
-\]
+Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection.
+The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$
+
+The twisted holography proposal asserts that the factorization algebra of local observables $\Obs_{M5}$ of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the Koszul dual $(\pi_{*} C^{\bullet}(\cL))^{!}$.
 
@@
 
-Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
-The $\mu$-field decomposes into vector field components which point along and transverse to the brane
-\[
-\mu
-\]
+%Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
+%The $\mu$-field decomposes into vector field components which point along and transverse to the brane
+%\[
+%\mu
+%\]
 %
@@
 
-We begin by computing the hypercohomology of the factorization enveloping algebra. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.
+We wish to count local operators, which are given by the costalk at $0\in \C^{3}$ of $\Obs_{M5}$.
+Let us first describe $\Obs_{M5}$ more explicitly.
+By the Poincare and $\dbar$ Poincare lemmas, we have quasi-isomorphisms for each $U\subset \C^{3}$ open
+\[
+\Obs_{M5}(U) = \Sym \left( \begin{tikzcd}  \end{tikzcd} \right)
+\]
+
+The local observables are given by $\lim _{U\ni 0} \Obs_{M5}(U)$.
 
@@
 \begin{lem}
-  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \cU (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
+  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0))=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
   \begin{itemize}

### 2022-03-11 fivebranes/index.tex

@@
 \begin{lem}
-  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0))=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
+  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0)\right )=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
   \begin{itemize}
@@
   \item $t_{1}, t_{2}$ denote generators for the cartan of $\SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $r$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
-  \item $q$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
+  \item $q$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
+  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
 \end{itemize}
@@
 \end{center}
+
+\begin{prop}
+  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by
+
+  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{-3/2}
+          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}q)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
+  \end{prop}

### 2022-03-14 fivebranes/index.tex
typo fixed
fixed typos
merge

@@
+\documentclass[11pt]{amsart}
+
+%\usepackage{../macros-master}
+\usepackage{macros-fivebrane}
+
+\begin{document}
+\section{Supersymmetric indices}
+
+\subsection{A single fivebrane}
+
+We recall the description of the holomorphic twist of a single fivebrane theory \cite{SWtensor}
+
+\parsec[]
+
+The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
+In full generality, we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
+
+The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
+There are four fundamental fields $(\mu, \Omega, \phi_\pm)$ which consist of even Dolbeault forms of type $(1,1)$ and $(0,2)$ on $X$:
+\[
+\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
+\]
+and a pair of even sections:
+\[
+(\phi_+,\phi_-) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
+\]
+%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
+The equations of motion read
+\beqn
+\label{eqn:eom}
+\begin{split}
+\del \mu + \dbar \Omega & = 0 \\
+\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
+\end{split}
+\eeqn
+
+There are gauge symmetries for the fields $\mu, \Omega$ determined by a ghost $b$ which is a Dolbeault form of type $(2,0)$ which acts simply by
+\beqn
+\label{eqn:ghost}
+\begin{split}
+\mu & \mapsto \mu + \dbar b  \\
+\Omega & \mapsto \Omega + \del b .
+\end{split}
+\eeqn
+
+This theory does not admit a Lagrangian description. 
+However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
+
+\begin{lem}
+The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
+\[
+\Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
+\]
+\end{lem}
+
+\parsec
+
+In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
+\brian{recall}
+
+\parsec
+
+The index we compute has four fugacities, which we label as follows:
+\begin{itemize}
+  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
+  \item $r$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
+  \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
+\end{itemize}
+These $U(1)$ weights are summarized in table \ref{tbl:weights1}.
+
+\begin{center}
+\begin{tabular}{c c c c c c}
+  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
+  \hline
+  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
+  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
+  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
+  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
+\end{tabular}
+\end{center}
+
+\parsec
+
+\begin{itemize}
+\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
+\[
+- q^3 \frac{t_1 q^{-2} + t_1^{-1} t_2 q^{-2} + t_2^{-1} q^{-2} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
+\[
+q^3 \frac{q^{-3}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators on $K^{-1/2} \otimes \C^2$ contribute
+\[
+q^3 \frac{q^{-3/2} r + q^{-3/2}r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+\]
+\end{itemize}
+
+Putting this all together we obtain the following.
+
+\begin{prop}
+The character of local operators of the holomorphic twist of the theory on a single fivebrane is given by the following plethystic exponential
+\[
+{\rm PExp} \left[f_{tensor} (t_1,t_2,q,r) \right] .
+\]
+where the single particle index is
+\[
+f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\]
+\end{prop}
+
+\parsec
+
+A remark comparing to Kac \cite{KR1}.
+
+\parsec
+
+There are various specializations of this character that one can consider. 
+One which is motivated from supersymmetry produces...
+
+\begin{itemize}
+\item The deformation $\d z_1 \otimes r_+$.
+\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
+\end{itemize}
+
+Both characters break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
+\[
+q = r^2 , \quad t_2 = 1 .
+\]
+As one can easily check, this specialization yields the following single particle index
+\[
+f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{1}{1-q} 
+\]
+which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$.
+
+\subsection{Character of E(3|6)}
+
 \subsection{Large $N$ Holomorphic Character}
 
-We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of M5 branes.
+We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of fivebranes.
 Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}.
 Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$.
-Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection.
+Consider a stack of $N$ fivebranes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection.
 The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$
@@
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the cartan of $\SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $q$ denotes a generator for the cartan of a $\SU(2)$ rotating the normal directions $\C^{2}_{w}$
+  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
+  \item $q$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
   \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
@@
 
-  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{-3/2}
-          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}q)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
+  \[ \operatorname{PExp} \left (\frac{r^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{3/2}
+          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}r)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
   \end{prop}
+
+\end{document}

### 2022-03-14 fivebranes/index.tex
plethystic
e36char

@@
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $r$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
+  \item $t_{1}, t_{2}$ denote generators for the Cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
+  \item $r$ denotes a generator for the Cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
   \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
@@
 \[
-- q^3 \frac{t_1 q^{-2} + t_1^{-1} t_2 q^{-2} + t_2^{-1} q^{-2} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
 \]
@@
 \[
-q^3 \frac{q^{-3}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
 \]
-\item Single particle operators on $K^{-1/2} \otimes \C^2$ contribute
+\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
 \[
-q^3 \frac{q^{-3/2} r + q^{-3/2}r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3/2}\frac{r + r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
@@
 \[
-f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
 \]
@@
 
-Both characters break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
-\[
+Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
+\beqn\label{eqn:special1}
 q = r^2 , \quad t_2 = 1 .
-\]
+\eeqn
 As one can easily check, this specialization yields the following single particle index
 \[
-f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{1}{1-q} 
+f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
 \]
@@
 
-\subsection{Character of E(3|6)}
+\subsection{Character of $E(3|6)$}
+
+\parsec[]
+
+Recall that the even part of $E(3|6)$ ...
+
+\begin{itemize}
+\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
+\[
+q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
+\[
+q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
+\[
+q^{3}\frac{q^{1/2} r + q^{1/2} r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+\]
+\end{itemize}
+
+\begin{conj}
+The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
+\[
+{\rm PExp} \left[f_{two} (t_1,t_2,q,r) \right] .
+\]
+where the single particle index is
+\[
+f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\]
+\end{conj}
+
+\parsec[]
+
+The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+\[
+f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
+\]
+which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
 

### 2022-03-15 fivebranes/index.tex
edited large N
typo
cleaning

@@
 The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
-In full generality, we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
+To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
 
 The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\mu, \Omega, \phi_\pm)$ which consist of even Dolbeault forms of type $(1,1)$ and $(0,2)$ on $X$:
+There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
 \[
@@
 \[
-(\phi_+,\phi_-) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
+(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
 \]
@@
 
+\parsec
+
+We now consider the case $X = \C^3$ and consider the local operators of the single fivebrane theory supported at $0 \in \C^3$.
+
 \begin{lem}
+\label{lem:single}
 The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
-\[
+\beqn\label{eqn:localfree}
 \Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
-\]
+\eeqn
 \end{lem}
@@
 In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
-\brian{recall}
+We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
+We recount how it acts on the vector space \eqref{eqn:localfree}.
+
+Recall that the even part of $E(3|6)$ consists of two summands:
+\[
+\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
+\]
+Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
+An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_1,r_2\}$ as the fundamental $\lie{sl}(2)$ representation.
 
@@
 
-The index we compute has four fugacities, which we label as follows:
+We consider the equivariant character of local operators on the holomorphic twist of a single fivebrane with respect to the following finite dimensional subalgebra of $E(3|6)$ 
+\[
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset E(3|6) 
+\]
+which embeds in the following way: 
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the Cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $r$ denotes a generator for the Cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
-  \item $q$ denotes a generator for the Cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
+\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
+where $(a_{ij}) \in \lie{sl}(3)$. 
+\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
+\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
 \end{itemize}
-These $U(1)$ weights are summarized in table \ref{tbl:weights1}.
 
+Accordingly, the equivariant character we has four fugacities, which we label as follows:
+\begin{itemize}
+  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which acts by vector fields on $\C^{3}_{z}$.
+  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_1,r_2\}$. 
+  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
+\end{itemize}
+The weights are summarized in table \ref{tbl:weights1}.
+Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.
+
+\begin{table}
 \begin{center}
 \begin{tabular}{c c c c c c}
-  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
+  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
   \hline
@@
 \end{tabular}
+\caption{Fugacities for a single fivebrane.}
 \end{center}
+\label{tbl:weights1}
+\end{table}
 
 \parsec
+
+We now move on to the computation of the character of local operators on a single fivebrane.
+According to the weights listed above and using the description of local operators in Lemma \label{lem:single} we have the following contributions to the character.
 
@@
 \[
-q^{3/2}\frac{r + r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
@@
 \[
-q^{3}\frac{q^{1/2} r + q^{1/2} r^{-1}}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
@@
 \[
-f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
 \]
@@
 
-  \[ \operatorname{PExp} \left (\frac{r^{3}\left (\begin{aligned} & t_{1}^{-1}r+t_{1}t_{2}^{-1}r+t_{2}r+q^{-1}r^{-3/2}+qr^{-3/2} \\  - & t_{1}r^{-1}-t_{1}^{-1}t_{2}r^{-1}-t_{2}^{-1}r^{-1}-qr^{3/2}-q^{-1}r^{3/2}
-          \end{aligned}\right)}{(1-t_{1}^{-1}r)(1-t_{2}r)(1-t_{1}t_{2}^{-1}r)(1-r^{3/2}q)(1-r^{3/2}q^{-1})}\right ).\]
+  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
+          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
   \end{prop}

### 2022-03-15 fivebranes/index.tex
cleaning

@@
 \begin{document}
-\section{Supersymmetric indices}
 
-\subsection{A single fivebrane}
+\section{The representation theory of local operators}
 
-We recall the description of the holomorphic twist of a single fivebrane theory \cite{SWtensor}
+operators, indices, etc..
+relationship to the $S^5$ partition function.
+
+\subsection{Local operators in a holomorphic theory}
 
@@
 
-The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
-To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
+Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
+Let $\cV$ denote its sheaf of holomorphic sections.
+The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
+\[
+\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
+\]
+where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
+Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
 
-The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
+As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
+\begin{itemize}
+\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
 \[
-\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
+[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
 \]
-and a pair of even sections:
+\end{itemize}
+A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
+
+\parsec[s:localops]
+
+\begin{eg}
+Suppose that $V$ is the trivial bundle on $\C^n$. 
+Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
 \[
-(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
+\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
 \]
-%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
-The equations of motion read
+Via the $n$-dimensional residue one can identify the algebra of local operators with 
+\[
+\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
+\]
+
+Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
+The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following `single particle index'
+\[
+\frac{1}{(1-q_1)\cdots (1-q_n)} .
+\]
+\end{eg}
+
+\subsection{Operators on a single fivebrane}
+
+We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
+This theory exists on any complex three-fold $X$. 
+To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.
+
+The theory on a single fivebrane is free and the underlying cochain complex of fields on $\C^3$ is given by 
 \beqn
-\label{eqn:eom}
-\begin{split}
-\del \mu + \dbar \Omega & = 0 \\
-\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
-\end{split}
+\begin{tikzcd}
+\ul{-1} & \ul{0} \\
+\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
+\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
+\end{tikzcd} 
 \eeqn
-
-There are gauge symmetries for the fields $\mu, \Omega$ determined by a ghost $b$ which is a Dolbeault form of type $(2,0)$ which acts simply by
-\beqn
-\label{eqn:ghost}
-\begin{split}
-\mu & \mapsto \mu + \dbar b  \\
-\Omega & \mapsto \Omega + \del b .
-\end{split}
-\eeqn
-
-This theory does not admit a Lagrangian description. 
-However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
-
-\parsec
-
-We now consider the case $X = \C^3$ and consider the local operators of the single fivebrane theory supported at $0 \in \C^3$.
+Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
 
@@
 \parsec
+
+\brian{i think I will recall some of this in the language of `fields' in Section 1, but it'd be good to say a few words about operators.}
 
@@
 which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
+Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
 
-\subsection{Character of $E(3|6)$}
+\subsection{A stack of two fivebranes}
 
@@
 
-\subsection{Large $N$ Holomorphic Character}
+\subsection{The large $N$ limit}
 

### 2022-03-16 fivebranes/index.tex
minor edits

@@
 
-The index we compute will have four fugacities, which we label as follows:
+\parsec
+
+We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra $\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)$ which embeds in the following way:
+
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $q$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
-  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
 \end{itemize}
 
-A convenient choice of choice of weights is as in the following table:
+This is the image of the subalgebra chosen in the calculation in \ref{} via under the map $E(3|6)\to E(5|10)$ discussed in \surya{earlier}
 
+The equivariant character thus has four fugacities, which we label as follows:
+\begin{itemize}
+  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
+  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w}$.
+  \item $q$ denotes a generator for the cartan of additional $\lie{gl}(1)$ acting by a divergence free vector field on $\C^{5}$ that restricts to a dilation on $\C^{3}$.
+\end{itemize}
+
+This choice of subalgebra is such that it restricts to the choice made in
+
+The convenient choice of weights is summarized in the following table:
 \begin{center}
@@
 \end{center}
+\parsec
 
 \begin{prop}
-  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by
+  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential
 
-  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
-          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
+  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]
+
+  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1}+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
 \end{prop}
 
+\parsec The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+\[
+f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q)^{2}.
+\]
+
+This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
+
+\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $\rm AdS_{7}\times S^{4}$ \surya{...}
+
 \end{document}

### 2022-03-21 fivebranes/twisted.tex
org

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

\section{Twisted eleven-dimensional supergravity}

\subsection{Observables in a holomorphic-topological theory}

\subsection{A model for twisted supergravity}

Let $X$ be a Calabi--Yau five-fold. 
In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given. 
Within the BV formalism, the theory is only $\Z/2$ graded.

In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.

\begin{thm}[\cite{RSW}]
On $X \times \R = \C^5 \times \R$ there is a quasi-isomorphism of the local observables of the minimal twist of eleven-dimensional supergravity 
\[
{\rm Ops}_{11d} \simeq \clie^\bu(\Hat{E}(5|10)) 
\]
\end{thm}

\subsection{Twisted fivebranes}

%\subsection{Twisted AdS backgrounds}

\parsec

\parsec[s:coupling]

\parsec[s:single]

An explicit characterization of the holomorphic twist of a single fivebrane theory was given in \cite{SWtensor}. 
We briefly recall this desription.

\parsec[]

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.

The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \mu + \dbar \Omega & = 0 \\
\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

There are gauge symmetries for the fields $\mu, \Omega$ determined by a ghost $b$ which is a Dolbeault form of type $(2,0)$ which acts simply by
\beqn
\label{eqn:ghost}
\begin{split}
\mu & \mapsto \mu + \dbar b  \\
\Omega & \mapsto \Omega + \del b .
\end{split}
\eeqn

This theory does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.

\parsec

\subsection{Enhanced symmetry in a flat background}

\parsec[s:e510]

The super Lie algebra $E(5|10)$.

\parsec[s:e36]

\end{document}

### 2022-03-30 fivebranes/twisted.tex
merge

@@
 
+One of the main results of \cite{CG2}.
+
+\begin{dfn} 
+Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
+The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
+\end{dfn}
+
+\parsec
+
+Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
+\[
+\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
+\]
+where $L$ is a graded holomorphic vector bundle on $X$.
+
+\begin{lem}
+\label{lem:localops}
+Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
+Then, the Taylor expansion map
+\[
+\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
+\]
+induces a quasi-isomorphism of commutative dg algebras
+\[
+\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
+\]
+\end{lem}
+
 \subsection{A model for twisted supergravity}
@@
 
-\begin{thm}[\cite{RSW}]
-On $X \times \R = \C^5 \times \R$ there is a quasi-isomorphism of the local observables of the minimal twist of eleven-dimensional supergravity 
+\parsec[s:fields]
+The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
+
+\parsec[s:e510]
+
+Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
 \[
-{\rm Ops}_{11d} \simeq \clie^\bu(\Hat{E}(5|10)) 
+\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
 \]
+
+\parsec[s:L0]
+
+For us, a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
+\[
+\ell_k \colon L^{\times k} \to \Pi^k L 
+\]
+are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
+Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
+Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
+\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
+A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}
+
+Let $L_{sugra}$ be the following $\Z/2$ graded $L_\infty$ algebra. 
+The even part is 
+\[
+\Vect (\Hat{D}^5) \oplus \cO (\Hat{D}^5) .
+\]
+We will denote even elements by $(\mu, \beta)$ according to the decomposition. 
+The odd part is 
+\[
+\cO(\Hat{D}^5) \oplus \Omega^1(\Hat{D}^5) .
+\]
+We will denote odd elements by $(\nu, \gamma)$ according to the decomposition.
+
+The $L_\infty$ structure is described as follows. 
+First, $\d = [-]_1$, the differential, is simply given by 
+\begin{align*}
+\d \beta & = \del \beta \in \Omega^1(\Hat{D}^5) \subset L_{sugra,-} \\
+\d \mu & = \div \mu \in \cO(\Hat{D}^5) \subset L_{sugra, -}
+\end{align*}
+and $\d \gamma = \d \nu = 0$.
+
+For $k \geq 2$ the general formula for the $k$-ary brackets is 
+\begin{align*}
+[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
+[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
+[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
+\end{align*}
+In \cite{RSW} it is shown that this endows $L_{sugra}$ with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+
+\parsec[s:sugraobs]
+
+By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cE_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
+
+On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
+First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
+\[
+\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
+\]
+The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
+\[
+\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
+\]
+which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$.
+
+\begin{thm}[\cite{RSW}[Theorem 2.1]]
+The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
+\[
+j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
+\]
+Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
 \end{thm}
+
+As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
+
+\begin{cor}
+Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
+There is a quasi-isomorphism of commutative dg algebras
+\[
+\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
+\]
+\end{cor}
 
@@
 %\subsection{Twisted AdS backgrounds}
-
-\parsec
 
@@
 
-The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
+The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
 There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
@@
 
-This theory does not admit a Lagrangian description. 
+This theory notoriously does not admit a Lagrangian description. 
 However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
+We describe this Poisson bivector explicitly
 
-\parsec
+\parsec[s:zz2]
+
+In the BV formalism the fields of a free theory together with the ghosts and the (partial) antifields combine to form a cochain complex.
+
+\parsec[s:singleops]
+
+\begin{prop}
+Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
+There is a quasi-isomorphism of super commutative dg algebras 
+\[
+\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
+\]
+\end{prop}
 
@@
 
-\parsec[s:e510]
-
-The super Lie algebra $E(5|10)$.
+\parsec[s:weight]
 
@@
 
+The super Lie algebra $E(3|6)$.
+
+\begin{lem} 
+The map $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
+\[
+E(3|6) \hookrightarrow \Hat{E(5|10)} .
+\]
+\end{lem}
+\begin{proof}
+It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
+Recall that the even cocycle defining this extension is 
+\[
+(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
+\]
+This is clearly zero since the image 
+\end{proof}
+
 \end{document}

### 2022-04-01 fivebranes/twisted.tex
merge

@@
 \end{prop}
+\begin{proof}
+This follows from Lemma \ref{lem:localops}.
+In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
+\beqn
+\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
+\eeqn
+and
+\beqn
+\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
+\eeqn
+The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
+The differential is zero on the odd summand.
+We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
+
+From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
+\[
+(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
+\]
+That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
+\end{proof}
 
 \subsection{Enhanced symmetry in a flat background}
+
+\parsec[s:locallieE510]
 
@@
 
+\section{Example}
+
+Consider the holomorphic local Lie algebra on $\C^n$
+\[
+\Omega^{0,\bu}(\C^n) 
+\]
+and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
+Now, we can restrict this to a factorization algebra on
+\[
+\C^n - 0 \subset \C^n
+\]
+that we denote by $\cF|_{\C^n - 0}$.
+
+Next, consider the radial projection
+\[
+r \colon \C^n - 0 \to \R .
+\]
+Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
+Nevertheless we can come up with a nice algebraic model.
+
+Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.
+
+\begin{lem}
+There is an injective map of factorization algebras on $\RR_{>0}$:
+\[
+\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
+\]
+which is dense in cohomology.
+\end{lem}
+
+This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
+
 \end{document}

### 2022-04-04 fivebranes/fivebranes.tex
index one fivebrane
local

@@
 \addbibresource{references.bib}
-
-\newcommand\thooft{`t Hooft\,}
 
@@
 
+\section{Careful index computation}
+
+Let's compute the index of a single fivebrane.
+
+\begin{table}[htbp]
+\centering
+\begin{tabular}{llrrr}
+ & $t_1$ & $t_2$ & $q$ & $r$ \\
+$z_1$ & $1$ & 0 & 0 & $-1$\\
+$z_2$ & $-1$ & $1$ & 0 & $-1$\\
+$z_3$ & $0$ & $-1$ & 0 & $-1$\\
+$w_1$ & $0$ & $0$ & $1$ & $3/2$\\
+$w_2$ & 0& 0 & $-1$ & $3/2$ \\
+\\
+\end{tabular}
+\caption{Assignment of fugacities}
+\end{table}
+
+\begin{itemize}
+\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
+\[
+- r^3 \frac{t_1 r^{-1} + t_1^{-1} t_2 r^{-1} + t_2^{-1} r^{-1} }{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
+\]
+\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
+\[
+r^3 \frac{1}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
+\]
+\item Single particle operators on $K^{-1/2} \otimes \C^2$ contribute
+\[
+f_{single} (t_1,t_2,q,r) = r^{\frac32} \frac{q + q^{-1}}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)}
+\]
+\end{itemize}
+
+Putting this all together we get 
+\[
+f_{tensor} (t_1,t_2,q,r) = \frac{(q + q^{-1})r^{\frac32} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )r^2 + r^3}{(1-t_1^{-1}r) (1-t_1 t_2^{-1} r) (1-t_2 r)} 
+\]
+
+The specialization $t_1=t_2$ and $q=r=1$ is
+\[
+f_{tensor}(t_1,t_2=t_1, q=1,r=1) = \frac1{1-t_1} .
+\]
+
+\section{random}
+
+The non minimal twist of the tensor is $\Omega^\bu(\R^4) \otimes \Omega^{1,\bu}(\C_z)$.
+Omega-background in one $\R^2$ gives $\Omega^\bu(\R^2) \otimes \Omega^{1,\bu}(\C_z)$.
+Looks like a deformation of $\Omega^{0,\bu}(\C_w) \otimes \Omega^{1,\bu}(\C_z) [\ep]$ by the Kapustin twist $\ep \frac{\del}{\del w}$.
+
 \end{document}

### 2022-04-04 fivebranes/twisted.tex
update?

@@
 
-By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cE_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
+By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
 
@@
 \begin{cor}
+\label{cor:sugraops}
 Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
@@
 
-\parsec[s:locallieE510]
+\parsec[s:e36]
+
+We recall the definition of the exceptional super Lie algebra $E(3|6)$. 
+We follow \cite{Kac_class, KacRudakov}.
+
+The even part of the super Lie algebra $E(3|6)$ is 
+\[
+\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
+\]
+The Lie bracket is determined by the obvious commutators and the action of vector fields on functions.
+
+The odd part is of the form
+\[
+\Omega^{-1/2}(\Hat{D}^3) \otimes \C^2 .
+\]
+where $\Omega^{-1/2}(\Hat{D}^3)$ is the space of formal power series sections of the bundle
+\[
+\T_{\Hat{D}^3}^{*} \otimes K_{\Hat{D}^3}^{-1/2}
+\]
+where $K_{\Hat{D}^3}^{-1/2}$ is the negative square-root of the canonical bundle on $\Hat{D}^3$. 
+We will write a general element of this module as 
+\[
+\alpha = \sum_i g^i \d z_i^{-1/2} 
+\]
+where $g^i \in \cO(\Hat{D}^3)$. 
+The action by the even part of the super Lie algebra is by Lie derivative and by the fundamental $\lie{sl}(2)$ action on $\C^2$.
+We will write $r \in \C^2$ for a vector in the fundamental representation.
+Finally, there is a bracket 
+\[
+E(3|6)_- \times E(3|6)_- \to E(3|6)_+
+\]
+defined by
+\[
+[\alpha_1 \otimes r_1, \alpha_2 \otimes r_2] = - (\alpha_1 \wedge \alpha_2) \otimes (r_1 \wedge r_2) - (\d \alpha_1 \otimes \alpha_2 + \alpha_1 \otimes \d \alpha_2) \otimes (r_1 \odot r_2) .
+\]
+%The first term in the above equation arises from the composition 
+%\[
+%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{\wedge \otimes \wedge} \Hat{\Omega}_3^{-1} \otimes \wedge^2 R \cong \fw_3 .
+%\] 
+%The second term uses the composition 
+%\[
+%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{(\d \otimes \id) \otimes \odot} (\Hat{\Omega}_3^{1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes \Sym^2 (R) \cong \lie{sl}(2) \otimes \Hat{\cO}_3 .
+%\]
+
+\brian{suca enhancement following \cite{SWsuca6d}}
 
@@
 
-\parsec[s:e36]
+In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$.
 
-The super Lie algebra $E(3|6)$.
+We first split the coordinates on the formal five-disk as
+\[
+(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
+\]
+In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.
+
+Assign the following weights to the super Lie algebra $E(5|10)$. 
+\begin{itemize} 
+\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
+\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
+\item the parity of an element carries an additional weight of $-1$. 
+Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
+\end{itemize} 
+The weight grading is concentrated in degrees $\geq -1$. 
+In particular, there is a decomposition of super vector spaces
+\beqn\label{eqn:decomp1}
+E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
+\eeqn
+with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
+It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
+In particular 
+\beqn 
+\label{eqn:e36iso}
+E(3|6) \cong V_0 \subset E(5|10)
+\eeqn
+is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.
+
+We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
+In this way, we get a related decomposition of super vector spaces
+\beqn\label{eqn:decomp1}
+E(5|10) = \prod_{n \geq -1} V_n
+\eeqn
+Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
+Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
+In particular, we have the following.
 
 \begin{lem} 
-The map $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
+The embedding $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
 \[
@@
 \end{lem}
-\begin{proof}
-It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
-Recall that the even cocycle defining this extension is 
+%\begin{proof}
+%It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
+%Recall that the even cocycle defining this extension is 
+%\[
+%(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
+%\]
+%This is clearly zero since the image 
+%\end{proof}
+
+Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
+By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
+\begin{align*}
+\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
+& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
+\end{align*}
+The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
+$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
 \[
-(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
+Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
 \]
-This is clearly zero since the image 
-\end{proof}
+and $\Hat{Q}$ acts on linear generators via
+\[
+\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
+\]
+
+\parsec[s:locallieE510]
+
+We have recollected how the super Lie algebra $E(5|10)$ (and its central extension) decomposes as a module for the super Lie algebra $E(3|6)$. 
+We now wish to lift this to a decomposition of factorization algebras on $\C^3$, or more generally, factorization algebras on any complex three-fold $Z$.
+
+We outline an approach to constructing the factorization algebras via enveloping factorization algebras of certain (infinite rank) local Lie algebras on the three-fold $X$. 
+For another approach \brian{pointer}.
+
+We have already discussed the local Lie algebra $\cL_{sugra}$ on $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a smooth one-manifold. 
+We take $X = Z \times \C^2$ and $S = \R$. 
+and view $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ as a factorization algebra on $Z \times \C^2 \times \R$. 
+Then, we can consider the pushforward of $\Obs_{sugra}$ along the map
+\[
+\pi \colon Z \times \C^2 \times \R \to Z 
+\]
+which leads to a factorization algebra $\pi_* \Obs_{sugra}$ on the three-fold $Z$.
+
+Since $\pi$ is not a proper map (the fibers are not compact) we cannot exhibit $\pi_*\Obs_{sugra}$ as the Chevalley--Eilenberg complex of some ordinary local Lie algebra on $Z$. 
+Nevertheless we will find a pro local Lie algebra $\cL_{sugra,\pi}$ on $Z$ which is a particularly nice `small model' for this pushforward factorization algebra.
+
+A local Lie algebra enhancement for $E(3|6)$ has been given in \cite{SWsuca6d} \brian{finish}
+
+\begin{prop}
+Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
+There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
+\begin{itemize}
+\item[(1)] there is a map of factorization algebras
+\[
+\clie^\bu(\cL_{\pi,sugra}) \to \pi_* \Obs_{sugra}
+\]
+which is dense in cohomology. 
+\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
+\beqn\label{eqn:decomp3}
+\cL_{\pi,sugra} = \prod_{n \geq -1} \cV_{n} 
+\eeqn
+\item[(3)]
+In weight zero, there is an equivalence of local Lie algebras on $Z$ 
+\[
+\cV_0 \simeq \cE(3|6)|Z .
+\]
+\end{itemize}
+\end{prop}
 

### 2022-04-05 fivebranes/boundary.tex
boundary stuff

\subsection{Defects in Holomorphic-Topological Field Theories}

\parsec

Consider a $\Z/2$-graded holomorphic-topological field theory on a split THF manifold $X\times M$ where $X$ is a complex manifold and $M$ is a smooth manifold, and let $\cL$ denote the underlying holomorphic-topological local Lie algebra. Suppose in addition, we have a  defect supported along the image of a closed embedding \[\iota : N\subset X\times M.\]

\parsec

Following \cite{PW}, the algebra of local operators on the defect is naturally a quotient of the koszul dual

\parsec

We give an operational description of the algebra of local operators on the defect. The description is meant to codify the idea that the algebra can be computed as an algebra of boundary observables for the theory compactified on the link of the defect.

Consider the normal bundle $T_{(X\times M)/N}$ and choose a fiberwise metric $h$. There is a natural surjection

\[r = (\pi, \|-\|^{2}): T_{(X\times M)/N}\to N \times \R_{\geq 0}\]

where the first component is the natural projection, and the second component is the norm squared with respect to $h$. This equips the normal bundle with the structure of a stratified vector bundle over $N\times \R_{\geq 0}$.

We wish to consider the pushforward $r_{*}\cL$. Note that away from the zero section, the restriction of $r$ gives us the structure of a sphere bundle over $N\times \R_{>0}$. Moreover, the fiber spheres are equipped with canonical foliations given by

\[\]

Let's describe its sections explicitly.

\begin{itemize}
  \item For an open set
  \item
\end{itemize}

### 2022-05-17 fivebranes/index.tex
changes

--- 2022-03-15 fivebranes/index.tex
@@
 
-\subsection{Local operators in a holomorphic theory}
+\subsection{Local operators in a holomorphic-topological theory}
+
+\begin{dfn} 
+Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
+The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
+\end{dfn}
+
+\parsec
+
+Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
+\[
+\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
+\]
+where $L$ is a graded holomorphic vector bundle on $X$.
+
+\begin{lem}
+\label{lem:localops}
+Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
+Then, the Taylor expansion map
+\[
+\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
+\]
+induces a quasi-isomorphism of commutative dg algebras
+\[
+\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
+\]
+\end{lem}
 
@@
 
+%\parsec[s:sugraops]
+%
+%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
+%
+%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
+%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
+%\[
+%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
+%\]
+%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
+%\[
+%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
+%\]
+%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
+%
+%\begin{thm}[\cite{RSW}[Theorem 2.1]]
+%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
+%\[
+%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
+%\]
+%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
+%\end{thm} 
+%
+%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
+%
+%\begin{cor}
+%\label{cor:sugraops}
+%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
+%There is a quasi-isomorphism of commutative dg algebras
+%\[
+%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
+%\]
+%\end{cor}
+
 \subsection{Operators on a single fivebrane}
@@
 Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
-An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_1,r_2\}$ as the fundamental $\lie{sl}(2)$ representation.
+An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.
 
@@
 
-Accordingly, the equivariant character we has four fugacities, which we label as follows:
+\begin{rmk}
+In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
+\cite{KacClass}.
+\end{rmk}
+
+The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
+We choose these explicitly as follows:
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which acts by vector fields on $\C^{3}_{z}$.
-  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_1,r_2\}$. 
+  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
+  \beqn
+  z_1 \del_{z_1} - z_2 \del_{z_2} , \quad z_2 \del_{z_2} - z_3 \del_{z_3}
+  \eeqn
+  on~$\C^{3}_{z}$.
+  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_+,r_-\}$. 
   \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
@@
 
-A remark comparing to Kac \cite{KR1}.
+A degeneration of this character was computed in \cite{KR1}. 
+They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
+In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
+\[
+\frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3}
+\]
+which agrees with our direct analysis above.
 
@@
 Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
+
+%\parsec[s:singleops]
+%
+%\begin{prop}
+%Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
+%There is a quasi-isomorphism of super commutative dg algebras 
+%\[
+%\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
+%\]
+%\end{prop}
+%\begin{proof}
+%This follows from Lemma \ref{lem:localops}.
+%In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
+%\beqn
+%\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
+%\eeqn
+%and
+%\beqn
+%\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
+%\eeqn
+%The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
+%The differential is zero on the odd summand.
+%We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
+%
+%From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
+%\[
+%(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
+%\]
+%That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
+%\end{proof}
 
@@
 
-The specialization of this index in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+The specialization of this index $t_1=t_2=r=1$ yields the single particle index
+\[
+\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
+\]
+
+\parsec[]
+
+The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
 \[
@@
 
-We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of fivebranes.
+We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
+Unlike the analysis above, we will the twisted holography proposal to compute this character.
+
 Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}.
@@
 
-The index we compute will have four fugacities, which we label as follows:
+\parsec
+
+We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra 
+\[
+\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
+\]
+which embeds in the following way:
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the cartan of $SU(3)$ which acts on $\C^{3}_{z}$.
-  \item $q$ denotes a generator for the cartan of a $SU(2)$ rotating the normal directions $\C^{2}_{w}$
-  \item $r$ denotes a generator for the cartan of an additional $U(1)$ acting on $\C^{5}$ preserving the volume form
+\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
+where $(a_{ij}) \in \lie{sl}(3)$. 
+\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
+\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
+\beqn\label{vf1}
+\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
+\eeqn
 \end{itemize}
 
-A convenient choice of choice of weights is as in the following table:
+Correspondingly, the equivariant character thus has four fugacities, which we label as follows:
+\begin{itemize}
+  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
+  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w_1} \times \C_{w_2}$.
+  \item $q$ denotes a generator for the Cartan of additional $\lie{gl}(1)$ generated by the divergence-free vector field \eqref{vf1}. 
+\end{itemize}
 
+This choice of weights is summarized in Table \ref{tbl:sugra}.
+
+\begin{table}
 \begin{center}
@@
   \hline
-  $t_{1}$ & 1 & 0 & -1 & 0 & 0 \\
-  $t_{2}$ & 0 & 1 & -1 & 0 & 0 \\
-  $r$ & 0 & 0 & 0 & 1 & -1 \\
-  $q$ & -1 & -1 & -1 & $\frac{3}{2}$ & $\frac{3}{2}$
+  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
+  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
+  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
+  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
 \end{tabular}
+\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity.}
+\label{tbl:sugra}
 \end{center}
+\end{table}
+
+\parsec
 
 \begin{prop}
-  The $\SU(3)\times \SU(2)\times U(1)$ character of the large $N$ local operators of the M5 brane theory is given by
+  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential
 
-  \[ \operatorname{PExp} \left (\frac{q^{3}\left (\begin{aligned} & t_{1}^{-1}q+t_{1}t_{2}^{-1}q+t_{2}q+r^{-1}q^{-3/2}+rq^{-3/2} \\  - & t_{1}q^{-1}-t_{1}^{-1}t_{2}q^{-1}-t_{2}^{-1}q^{-1}-rq^{3/2}-r^{-1}q^{3/2}
-          \end{aligned}\right)}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}\right ).\]
+  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]
+
+  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
 \end{prop}
 
+\parsec
+
+The specialization $t_1=t_2=r=1$ yields the single particle index
+\[
+\frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
+\]
+
+\parsec 
+The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+\[
+f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{(1-q)^2}
+\]
+
+This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
+
+\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...}
+
 \end{document}

### 2022-05-17 fivebranes/twisted.tex
changes

@@
 
-\subsection{Observables in a holomorphic-topological theory}
-
-One of the main results of \cite{CG2}.
-
-\begin{dfn} 
-Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
-The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-\end{dfn}
-
-\parsec
-
-Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
-\[
-\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
-\]
-where $L$ is a graded holomorphic vector bundle on $X$.
-
-\begin{lem}
-\label{lem:localops}
-Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
-Then, the Taylor expansion map
-\[
-\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
-\]
-induces a quasi-isomorphism of commutative dg algebras
-\[
-\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
-\]
-\end{lem}
-
 \subsection{A model for twisted supergravity}
 
-Let $X$ be a Calabi--Yau five-fold. 
 In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given.
 Within the BV formalism, the theory is only $\Z/2$ graded.
+In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory which we recall here.
 
-In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.
-
-\parsec[s:fields]
 The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
 
-\parsec[s:e510]
+%\parsec[s:e510]
+%
+%Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
+%\[
+%\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
+%\]
 
-Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
-\[
-\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
-\]
+\parsec[s:Lsugra]
 
-\parsec[s:L0]
-
-For us, a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
+In this paper a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
 \[
@@
 
-Let $L_{sugra}$ be the following $\Z/2$ graded $L_\infty$ algebra. 
-The even part is 
+Let $L_X$ be the following sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau five-fold $X$.
+As a sheaf of super vector spaces, $L_X$ is given as the holomorphic sections of a super vector bundle. 
+The even part of this super vector bundle is
 \[
-\Vect (\Hat{D}^5) \oplus \cO (\Hat{D}^5) .
+\T_X \oplus \C_X 
 \]
-We will denote even elements by $(\mu, \beta)$ according to the decomposition. 
+where $\T_X$ is the holomorphic tangent bundle and $\C_X$ is the trivial bundle.
+We will denote even sections by $(\mu, \beta)$ according to the decomposition. 
 The odd part is 
 \[
-\cO(\Hat{D}^5) \oplus \Omega^1(\Hat{D}^5) .
+\C_X \oplus \T^*_X .
 \]
@@
 \begin{align*}
-\d \beta & = \del \beta \in \Omega^1(\Hat{D}^5) \subset L_{sugra,-} \\
-\d \mu & = \div \mu \in \cO(\Hat{D}^5) \subset L_{sugra, -}
+\d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
+\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
 \end{align*}
 and $\d \gamma = \d \nu = 0$. 
-
 For $k \geq 2$ the general formula for the $k$-ary brackets is 
@@
 \end{align*}
-In \cite{RSW} it is shown that this endows $L_{sugra}$ with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
+
+As all operations above are given in terms of holomorphic polydifferential operators, the $L_\infty$ algebra structure above induces a $\Z/2$ graded $L_\infty$ algebra structure on the Dolbeault resolution $\Omega^{0,\bu}(X,L_X)$ of the holomorphic vector bundle $L_X$.
+
+Finally, to obtain a local $L_\infty$ algebra on $X \times S$, where $S$ denotes an arbitrary real oriented smooth one-manifold, we simply tensor with the de Rham complex along~$S$.
+We denote by $\cL_{sugra}$ the following local $\Z/2$ graded $L_\infty$ algebra on $X \times S$
+\beqn
+\cL_{sugra} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(X,L_X) .
+\eeqn
+
+\parsec[s:rsw]
+It is shown in \cite{RSW} that $\cL_{sugra}$ is equipped with a non-degenerate odd pairing which is compatible with the $L_\infty$ structure above. 
+All together, this data prescribes the structure of a $\Z/2$ graded theory in the BV formalism. 
+On $X \times S = \C^5 \times \R$ it is furthermore argued in \cite{RSW} that this BV theory is equivalent to the holomorphic (or minimal) twist of perturbative eleven-dimensional supergravity.
 
@@
 
-By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
-
-On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
-First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
+The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
 \[
-\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
+U \subset S \times X 
 \]
-The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
+the cochain complex
 \[
-\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
+\clie^\bu\left(\cL_{sugra}(U)\right) .
 \]
-which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$.
-
-\begin{thm}[\cite{RSW}[Theorem 2.1]]
-The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
-\[
-j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
-\]
-Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
-\end{thm}
-
-As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
-
-\begin{cor}
-\label{cor:sugraops}
-Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
-There is a quasi-isomorphism of commutative dg algebras
-\[
-\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
-\]
-\end{cor}
 
@@
 %\subsection{Twisted AdS backgrounds}
-
-\parsec[s:coupling]
 
@@
 
-\parsec[]
-
-The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
-To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
+The holomorphic twist of the fivebrane theory is defined on any complex three-fold $Z$ (which is not necessarily equipped with a Calabi--Yau structure).
+In the particular twist we will use we must assume, however, that $Z$ is equipped with a square-root of the canonical bundle $K_Z^{1/2}$.
 
 The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
+There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
 \[
-\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
+\alpha \in \Omega^{2,1}(X), \quad \omega \in \Omega^{3,0}(X),
 \]
@@
 \begin{split}
-\del \mu + \dbar \Omega & = 0 \\
-\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
+\del \alpha + \dbar \omega & = 0 \\
+\dbar \alpha = \dbar \phi_i & = 0 .
 \end{split}
@@
 
-\parsec[s:zz2]
+In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\ZZ/2$ graded local Lie algebra on $Z$ which is of the form 
+\[
+\cL_{single} = \Omega^{\leq 1, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
+\]
+The full space of BV fields is simply $\Pi \cL_{single}$.
 
-In the BV formalism the fields of a free theory together with the ghosts and the (partial) antifields combine to form a cochain complex.
+\parsec[s:singleobs]
 
-\parsec[s:singleops]
+The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
+\[
+U \subset Z
+\]
+the cochain complex
+\[
+\clie^\bu\left(\cL_{single}(U)\right) .
+\]
+
+\parsec[s:coupling]
+
+The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting some number of fivebranes \brian{references}. 
+In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting some number of holomorphically twisted fivebranes. 
+We briefly recall the relevant setup here.
+
+As above, let $Z$ be a three-fold equipped with $K^{1/2}_Z$.
+Consider the rank two vector bundle $K^{1/2}_Z \otimes \C^2$ on $Z$. 
+Via the linear holomorphic symplectic form on $\C^2$, the total space of this vector bundle ${\rm Tot}(K^{1/2}_Z \otimes \C^2)$ is equipped with a Calabi--Yau structure. 
+We consider the eleven-dimensional theory on 
+\[
+\R \times {\rm Tot}(K^{1/2}_Z) 
+\]
+with a stack of fivebranes supported at $0 \in \R$ and along the zero section in the total space of the vector bundle
+\[
+0 \times Z \subset \R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)  .
+\]
+Let us denote $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$.
+
+It was argued in \cite{RSW} that to leading order the coupling of a stack of twisted fivebranes to the eleven-dimensional theory is given by the nonlocal interaction 
+\beqn\label{eqn:br1}
+I_{M5} = N\int_{Z} \div^{-1}\mu \vee \Omega +\cdots 
+\eeqn
+where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.
+
+\subsection{Supergravity at the boundary of AdS}
+
+Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\RR \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
+We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
+If we remove this locus we obtain the following manifold 
+\[
+\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
+\]
+where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.
+
+\parsec[s:flat]
+
+%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
+%\[
+%\C^3 \times (\R \times \C^2 - 0) .
+%\]
+%
+%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
+%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
+
+In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.
+
+Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
+Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
+\[
+\pi_* \Obs_{sugra} 
+\]
+on $\C^3$.
+This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
+Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+
+For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
+\begin{itemize}
+\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \mu(t;w,z) = \mu(t;\lambda w , z).
+\]
+\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \nu(t;w,z) = \nu(t;\lambda w , z).
+\]
+\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(t;\lambda w , z).
+\]
+\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(t;\lambda w , z).
+\]
+\end{itemize}
+
+For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
+\[
+\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
+\]
+be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
+The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
+Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
+\[
+(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+\]
+is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+In this way, the assignment 
+\[
+\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
+\]
+defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
 
 \begin{prop}
-Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
-There is a quasi-isomorphism of super commutative dg algebras 
+For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
 \[
-\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
+\Omega^{0,\bu}(U, \cV^{(n)})
 \]
+for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$. 
+In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
 \end{prop}
-\begin{proof}
-This follows from Lemma \ref{lem:localops}.
-In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
-\beqn
-\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
-\eeqn
-and
-\beqn
-\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
-\eeqn
-The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
-The differential is zero on the odd summand.
-We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
 
-From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
+Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
 \[
-(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
+U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
 \]
-That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
-\end{proof}
+has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
+
+\begin{prop}
+There is a natural inclusion of of factorization algebras 
+\[
+\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
+\]
+which is dense at the level of cohomology. 
+\end{prop}
+
+We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
+
+\brian{old below}
 

### 2022-05-24 fivebranes/kr.tex
kr

--- 2022-04-01 fivebranes/twisted.tex
@@
 
-\section{Twisted eleven-dimensional supergravity}
+\section{Kac-Rudokov}
 
-\subsection{Observables in a holomorphic-topological theory}
+In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$.
 
-One of the main results of \cite{CG2}.
+We first split the coordinates on the formal five-disk as
+\[
+(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
+\]
+In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.
 
-\begin{dfn} 
-Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
-The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-\end{dfn}
+Assign the following weights to the super Lie algebra $E(5|10)$. 
+\begin{itemize} 
+\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
+\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
+\item the parity of an element carries an additional weight of $-1$. 
+Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
+\end{itemize} 
+The weight grading is concentrated in degrees $\geq -1$. 
+In particular, there is a decomposition of super vector spaces
+\beqn\label{eqn:decomp1}
+E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
+\eeqn
+with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
+It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
+In particular 
+\beqn 
+\label{eqn:e36iso}
+E(3|6) \cong V_0 \subset E(5|10)
+\eeqn
+is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.
 
-\parsec
+\parsec[s:e510central]
 
-Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
-\[
-\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
-\]
-where $L$ is a graded holomorphic vector bundle on $X$.
+The central extension of $E(5|10)$ is defined by the (totally even) cocycle
+\beqn\label{eqn:e510central}
+(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} .
+\eeqn
+
+We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
+In this way, we get a related decomposition of super vector spaces
+\beqn\label{eqn:decomp1}
+E(5|10) = \prod_{n \geq -1} V_n
+\eeqn
+Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
+Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
+In particular, we have the following.
 
 \begin{lem} 
-\label{lem:localops}
-Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
-Then, the Taylor expansion map
-\[
-\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
-\]
-induces a quasi-isomorphism of commutative dg algebras
-\[
-\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
-\]
-\end{lem}
-
-\subsection{A model for twisted supergravity}
-
-Let $X$ be a Calabi--Yau five-fold. 
-In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given. 
-Within the BV formalism, the theory is only $\Z/2$ graded.
-
-In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.
-
-\parsec[s:fields]
-The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
-
-\parsec[s:e510]
-
-Let $\Hat{D}^5$ denote the formal five-disk whose algebra of functions is 
-\[
-\cO(\Hat{D}^5) = \C[[z_1,\ldots,z_5]] .
-\]
-
-\parsec[s:L0]
-
-For us, a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
-\[
-\ell_k \colon L^{\times k} \to \Pi^k L 
-\]
-are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
-Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
-Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
-\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
-A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}
-
-Let $L_{sugra}$ be the following $\Z/2$ graded $L_\infty$ algebra. 
-The even part is 
-\[
-\Vect (\Hat{D}^5) \oplus \cO (\Hat{D}^5) .
-\]
-We will denote even elements by $(\mu, \beta)$ according to the decomposition. 
-The odd part is 
-\[
-\cO(\Hat{D}^5) \oplus \Omega^1(\Hat{D}^5) .
-\]
-We will denote odd elements by $(\nu, \gamma)$ according to the decomposition.
-
-The $L_\infty$ structure is described as follows. 
-First, $\d = [-]_1$, the differential, is simply given by 
-\begin{align*}
-\d \beta & = \del \beta \in \Omega^1(\Hat{D}^5) \subset L_{sugra,-} \\
-\d \mu & = \div \mu \in \cO(\Hat{D}^5) \subset L_{sugra, -}
-\end{align*}
-and $\d \gamma = \d \nu = 0$.
-
-For $k \geq 2$ the general formula for the $k$-ary brackets is 
-\begin{align*}
-[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
-[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
-[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
-\end{align*}
-In \cite{RSW} it is shown that this endows $L_{sugra}$ with the structure of a $\Z/2$ graded $L_\infty$ algebra.
-
-\parsec[s:sugraobs]
-
-By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cE_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
-
-On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
-First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
-\[
-\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
-\]
-The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
-\[
-\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
-\]
-which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$.
-
-\begin{thm}[\cite{RSW}[Theorem 2.1]]
-The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
-\[
-j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
-\]
-Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
-\end{thm}
-
-As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
-
-\begin{cor}
-Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
-There is a quasi-isomorphism of commutative dg algebras
-\[
-\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
-\]
-\end{cor}
-
-\subsection{Twisted fivebranes}
-
-%\subsection{Twisted AdS backgrounds}
-
-\parsec[s:coupling]
-
-\parsec[s:single]
-
-An explicit characterization of the holomorphic twist of a single fivebrane theory was given in \cite{SWtensor}. 
-We briefly recall this desription.
-
-\parsec[]
-
-The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
-To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.
-
-The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
-\[
-\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
-\]
-and a pair of even sections:
-\[
-(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
-\]
-%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
-The equations of motion read
-\beqn
-\label{eqn:eom}
-\begin{split}
-\del \mu + \dbar \Omega & = 0 \\
-\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
-\end{split}
-\eeqn
-
-There are gauge symmetries for the fields $\mu, \Omega$ determined by a ghost $b$ which is a Dolbeault form of type $(2,0)$ which acts simply by
-\beqn
-\label{eqn:ghost}
-\begin{split}
-\mu & \mapsto \mu + \dbar b  \\
-\Omega & \mapsto \Omega + \del b .
-\end{split}
-\eeqn
-
-This theory notoriously does not admit a Lagrangian description. 
-However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
-We describe this Poisson bivector explicitly
-
-\parsec[s:zz2]
-
-In the BV formalism the fields of a free theory together with the ghosts and the (partial) antifields combine to form a cochain complex.
-
-\parsec[s:singleops]
-
-\begin{prop}
-Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
-There is a quasi-isomorphism of super commutative dg algebras 
-\[
-\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
-\]
-\end{prop}
-\begin{proof}
-This follows from Lemma \ref{lem:localops}.
-In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
-\beqn
-\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
-\eeqn
-and
-\beqn
-\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
-\eeqn
-The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
-The differential is zero on the odd summand.
-We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
-
-From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
-\[
-(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
-\]
-That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
-\end{proof}
-
-\subsection{Enhanced symmetry in a flat background}
-
-\parsec[s:locallieE510]
-
-\parsec[s:weight]
-
-\parsec[s:e36]
-
-The super Lie algebra $E(3|6)$.
-
-\begin{lem} 
-The map $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
+The embedding $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
 \[
@@
 \end{lem}
-\begin{proof}
-It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
-Recall that the even cocycle defining this extension is 
+%\begin{proof}
+%It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
+%Recall that the even cocycle defining this extension is 
+%\[
+%(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
+%\]
+%This is clearly zero since the image 
+%\end{proof}
+
+\parsec[s:localopsdecompose]
+Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
+By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
+\begin{align*}
+\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
+& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
+\end{align*}
+The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
+$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
 \[
-(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
+Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
 \]
-This is clearly zero since the image 
-\end{proof}
+and $\Hat{Q}$ acts on linear generators via
+\[
+\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
+\]
 
-\section{Example}
+\parsec[s:e510grading]
 
-Consider the holomorphic local Lie algebra on $\C^n$
+The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
+\begin{itemize}
+\item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
+\item $\deg \d z_i = \deg \d w_a = -1/2$.
+\end{itemize}
+This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$.
+
+\subsection{Irreducible representations of $E(3|6)$}
+Thinking of the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ (or even before centrally extending) then it carries an induced consistent $\Z$-grading. 
+Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
+In particular, as a super vector space
 \[
-\Omega^{0,\bu}(\C^n) 
+E(3|6) = \oplus_{j \geq -2} \fg_j
 \]
-and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
-Now, we can restrict this to a factorization algebra on
+where
+\begin{itemize}
+\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is completely even. 
+\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is completely odd. 
+\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is completely even. 
+Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
 \[
-\C^n - 0 \subset \C^n
+h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
 \]
-that we denote by $\cF|_{\C^n - 0}$.
+The Cartan of $\lie{sl}(2)$ is spanned by
+\[
+h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
+\]
+The Cartan of $\lie{gl}(1)$ is spanned by
+\[
+Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
+\]
+\end{itemize}
 
-Next, consider the radial projection
+\parsec[s:vermas]
+
+Denote by $\fg = E(3|6)$ and let 
 \[
-r \colon \C^n - 0 \to \R .
+\fg_{<0} = \fg_{-2} \oplus \fg_{-1} , \quad \lie{g}_{>0} = \oplus_{j>0} \fg_j 
 \]
-Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
-Nevertheless we can come up with a nice algebraic model.
+so that $\fg = \fg_{<0} \oplus \fg_0 \oplus \fg_{>0}$. 
+Given a $\fg_0$-module $V$ let 
+\[
+M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
+\]
+be the induced $\fg$-module. 
+Notice that as super vector spaces 
+\[
+M(V) = \Sym(\fg_{<0}) \otimes_\C V .
+\]
 
-Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.
+We will be interested in Verma modules associated to two particular types of $\fg_0$-modules
+\begin{align*}
+V_A & = \C[z_i, w_a] \\
+V_B & = \C[z_i, \del_{w_a}]_{[2]} .
+\end{align*}
+Here, the subscript $[2]$ means that we shift $\lie{gl}(1)$ to act by the differential operator 
+\[
+Y_{[2]} = Y + 2 \id_{V_B} .
+\]
+For $X = A,B$ we let 
+\[
+V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} 
+\]
+so that $V_X = \sum_{m,n} V_X^{m,n}$. 
+There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.
+
+An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ which we denote by
+\begin{align*}
+\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
+ y & = \lambda(Y)\in \C . 
+\end{align*}
+There is an isomorphism of $\fg_0$-modules
+\begin{align*}
+V_A^{p,r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
+V_B^{p,-r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2) .
+\end{align*}
+
+\subsection{Character computations}
+
+Define the (super) character of an $E(3|6)$-module $M$ by the formula
+\[
+\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
+\]
+As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
+\[
+M(V) = \Sym(\lie{g}_{<0}) \otimes V .
+\]
+We have $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where we recall that $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
+
+Given this description, there is a simple expression for the character 
+\[
+\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
+\]
+where $R = \ch \Sym(\fg_{<0})$.
 
 \begin{lem}
-There is an injective map of factorization algebras on $\RR_{>0}$:
-\[
-\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
-\]
-which is dense in cohomology.
+We have
+\beqn
+R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+\eeqn
 \end{lem}
 
-This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
+\parsec[s:typeA]
+
+There is a cohomological description of the irreducible modules of type $A$
+\[
+I(p,0;r;\frac23 p - r) .
+\]
+In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\[
+0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(p, 0 ; r;\frac23 p - r) \leftarrow M(p+1, 0;r+1;\frac23 p - r - \frac13) \leftarrow \cdots 
+\]
+which is
+\[
+0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
+\]
+
+84rPqzleGThz
 

### 2022-05-26 fivebranes/kr.tex
unrefined

@@
 \[
-\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
+\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-\frac32 y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
 \]
@@
 
-\parsec[s:typeA]
+For notational simplicity, we will set $q = t^2$.
+
+\subsection{Characters for degenerate modules of type A} \label{s:typeA}
 
@@
 \[
-I(p,0;r;\frac23 p - r) .
+I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
 \]
 In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\beqn\label{eqn:les1}
+0 \leftarrow I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1+1,0,\lambda_3+1;\frac23 \lambda_1 - \lambda_3-\frac13) \leftarrow \cdots .
+\eeqn
+%which is
+%\[
+%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
+%\]
+
+\parsec[s:typeAunrefinedKR]
+In this section we compute the {\em unrefined} character of the type A modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
+From the long exact sequence \eqref{eqn:les1} we have the following expression 
 \[
-0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(p, 0 ; r;\frac23 p - r) \leftarrow M(p+1, 0;r+1;\frac23 p - r - \frac13) \leftarrow \cdots 
-\]
-which is
-\[
-0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
+\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
 \]
 
-84rPqzleGThz
+Let $M_j$ be the $j$th Verma module appearing in the sum above. 
+Then
+\beqn
+\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
+\eeqn
+Notice that 
+\[
+r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
+\]
+so the above expression for $\ch M_j$ reduces to
+\[
+\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
+\]
+Observe the formal identity 
+\[
+\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
+\]
+where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.
+
+Using this identity, we evaluate
+\begin{align*}
+\ch I_A(\lambda_1,\lambda_3) & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\ 
+& = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
+\end{align*}
+
+Finally, we specialize further $t=r$ and substitute $q = t^2$ to obtain
+\[
+\ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
+\]
+
+\subsection{Characters for degenerate modules of type B} \label{s:typeB}
+
+There is a cohomological description of the irreducible modules of type $B$ similar to the type A case above.
+Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
+We are only interested in the case $\lambda_1 = 0$.  
+In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\begin{multline}\label{eqn:les1}
+0 \leftarrow  I_B(0,\lambda_3) \leftarrow \\ \leftarrow M(0,0,\lambda_3;\lambda_3 + 2) \leftarrow  M(1,0,\lambda_3-1;\frac{11}{3} - \lambda_3)  \leftarrow \cdots \leftarrow M(\lambda_3, 0, 0;\frac23 \lambda_3 +2) \leftarrow \\
+ \leftarrow M(\lambda_3+2, 0, 0; \frac23 \lambda_3 + \frac43) \leftarrow M(\lambda_3+3, 0, 1; \frac23 \lambda_3 + 2) \leftarrow \cdots .
+\end{multline}
+There are $\lambda_3+1$ terms in the second line above .
+
+\parsec[s:typeBunrefinedKR]
 

### 2022-05-30 fivebranes/kr.tex
merge

@@
 In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
-
 We first split the coordinates on the formal five-disk as
@@
 
+\parsec[s:e510weight]
 Assign the following weights to the super Lie algebra $E(5|10)$. 
@@
 \beqn\label{eqn:decomp1}
-E(5|10) = \prod_{n \geq -1} V_n
+\Hat{E(5|10)} = \prod_{n \geq -1} V_n
 \eeqn
@@
 This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$. 
+Note that this is different from the weight grading we recalled in \S \ref{s:e510weight}.
 
@@
 \]
-where
+where for small values of $j$ we have:
 \begin{itemize}
@@
 \[
-V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} 
+V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} \subset V_X
 \]
-so that $V_X = \sum_{m,n} V_X^{m,n}$. 
+so that $V_X = \oplus_{m,n} V_X^{m,n}$. 
 There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.
 
-An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ which we denote by
+An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ whose components we denote by
 \begin{align*}
@@
 \end{align*} 
+Note for type $A,B$ we have $\lambda_2 = 0$. 
+To simplify notation we will write 
+\begin{align*}
+F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
+F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
+\end{align*}
+and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules.
 
@@
 \]
-We have $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where we recall that $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
+
+Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
 
@@
 
-\subsection{Characters for degenerate modules of type A} \label{s:typeA}
+\subsection{Characters for degenerate modules of type $A$} \label{s:typeA}
 
@@
 \[
-I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
+I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
 \]
@@
 \beqn\label{eqn:les1}
-0 \leftarrow I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) \leftarrow M(\lambda_1+1,0,\lambda_3+1;\frac23 \lambda_1 - \lambda_3-\frac13) \leftarrow \cdots .
+0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
 \eeqn
@@
 \parsec[s:typeAunrefinedKR]
-In this section we compute the {\em unrefined} character of the type A modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
+In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
 From the long exact sequence \eqref{eqn:les1} we have the following expression 
@@
 
-There is a cohomological description of the irreducible modules of type $B$ similar to the type A case above.
+There is a cohomological description of the irreducible modules of type B similar to the type A case above.
 Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
-We are only interested in the case $\lambda_1 = 0$.  
+We are only interested in the case $\lambda_1 = 0$ with $\lambda_3=0,1,\ldots$.  
 In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed

### 2022-05-30 fivebranes/twisted.tex
merge

@@
 Within the BV formalism, the theory is only $\Z/2$ graded.
-In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory which we recall here.
+In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.
+We recall this description here.
 
 The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold. 
+We opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
+The additional data of a theory in the BV formalism is a graded skew-symmetric pairing on this sheaf.
 
@@
 
-In this paper a $\Z/2$ graded $L_\infty$ algebra is a $\Z/2$ graded vector space $L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
+In this paper $\Z/2$ graded $L_\infty$ algebra means a $\Z/2$ graded vector space~$L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
 \[
@@
 In \cite{RSW} it is shown that this endows $L_{X}$ with the structure of a sheaf of $\Z/2$ graded $L_\infty$ algebras.
+There is a sub sheaf given by the sections $\mu$ and $\nu$ which is $L_\infty$-equivalent to the sheaf of holomorphic divergence-free vector fields on $X$.
 
@@
 
-The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
-\[
-U \subset S \times X 
-\]
-the cochain complex
+In the BV formalism, the sheaf of fields of the eleven-dimensional theory is $\Pi \cL_{sugra}$. 
+As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
+The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
+In other words, as a $\Z/2$ graded commutative dg algebra, the classical observables of the eleven-dimensional theory supported on an open set $U \subset X \times S$ is 
 \[
@@
 
+Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
+\begin{itemize}
+\item 
+The holomorphic, or minimal, twist. 
+This twist leaves three real directions invariant. 
+The holomorphic twist of any $\cN=(2,0)$ theory can be defined on any complex three-fold $Z$ equipped with a square-root of its canonical bundle. 
+\item 
+The non-minimal twist. 
+This twist leaves five real directions invariant.
+The non-minimal twist of any $\cN=(2,0)$ theory can be defined on a six-manifold of the form $M^4 \times \Sigma$ where $M^4$ is a smooth four-manifold and $\Sigma$ is a Riemann surface. 
+\end{itemize}
+
+By standard arguments, the theory on a stack of $N$ fivebranes in flat space is a theory with $\cN=(2,0)$ supersymmetry. 
+In later sections we provide arguments using the technology of twisted holography developed by Costello, Gaiotto, Li, and Paquette \cite{??} to provide a conjectural description of the twist of the theory for general $N > 1$.
+An explicit characterization of the holomorphic and non-minimal twists of a single fivebrane theory has been given in \cite{SWtensor}. 
+We briefly recall this description.
+
 \parsec[s:single]
-
-An explicit characterization of the holomorphic twist of a single fivebrane theory was given in \cite{SWtensor}. 
-We briefly recall this desription.
 
@@
 The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
+There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $Z$:
 \[
-\alpha \in \Omega^{2,1}(X), \quad \omega \in \Omega^{3,0}(X),
+\alpha \in \Omega^{2,1}(Z), \quad \omega \in \Omega^{3,0}(Z),
 \]
@@
 \[
-(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
+(\phi_1,\phi_2) \in \Omega^0(Z , K^{1/2}_Z) \otimes \C^2 .
 \]
@@
 
-In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\ZZ/2$ graded local Lie algebra on $Z$ which is of the form 
+In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z/2$ graded local Lie algebra on $Z$ which is of the form 
 \[
@@
 
-The factorization algebra of classical observables of the eleven-dimensional theory assigns to an open set 
-\[
-U \subset Z
-\]
+The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
 the cochain complex
@@
 
-The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting some number of fivebranes \brian{references}. 
-In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting some number of holomorphically twisted fivebranes. 
+The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting a number of fivebranes \brian{references}. 
+In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting a number of holomorphically twisted fivebranes. 
 We briefly recall the relevant setup here.
@@
 
-Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\RR \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
+Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\R \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
 We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
@@
 \[
-\lambda \cdot \mu(t;w,z) = \mu(t;\lambda w , z).
+\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
 \]
@@
 \[
-\lambda \cdot \nu(t;w,z) = \nu(t;\lambda w , z).
+\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
 \]
@@
 \[
-\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(t;\lambda w , z).
+\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
 \]
@@
 \[
-\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(t;\lambda w , z).
+\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
 \]
@@
 
-In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$.
-
-We first split the coordinates on the formal five-disk as
-\[
-(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
-\]
-In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.
-
-Assign the following weights to the super Lie algebra $E(5|10)$. 
-\begin{itemize} 
-\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
-\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
-\item the parity of an element carries an additional weight of $-1$. 
-Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
-\end{itemize} 
-The weight grading is concentrated in degrees $\geq -1$. 
-In particular, there is a decomposition of super vector spaces
-\beqn\label{eqn:decomp1}
-E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
-\eeqn
-with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
-It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
-In particular 
-\beqn 
-\label{eqn:e36iso}
-E(3|6) \cong V_0 \subset E(5|10)
-\eeqn
-is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.
-
-We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
-In this way, we get a related decomposition of super vector spaces
-\beqn\label{eqn:decomp1}
-E(5|10) = \prod_{n \geq -1} V_n
-\eeqn
-Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
-Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
-In particular, we have the following.
-
-\begin{lem} 
-The embedding $E(3|6) \hookrightarrow E(5|10)$ lifts to a map of super $L_\infty$ algebras 
-\[
-E(3|6) \hookrightarrow \Hat{E(5|10)} .
-\]
-\end{lem}
-%\begin{proof}
-%It suffices to show that the central extension of $E(5|10)$ splits when restricted to the subalgebra $E(3|6)$. 
-%Recall that the even cocycle defining this extension is 
-%\[
-%(\mu, \mu', \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>|_{z=0} .
-%\]
-%This is clearly zero since the image 
-%\end{proof}
-
-Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
-By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
-\begin{align*}
-\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
-& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
-\end{align*}
-The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
-$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
-\[
-Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
-\]
-and $\Hat{Q}$ acts on linear generators via
-\[
-\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
-\]
-
 \parsec[s:locallieE510]

### 2022-06-03 fivebranes/index.tex
outline

@@
 
-\parsec
+\parsec[]
 
-Without loss of generality we will assume our holomorphic-topological local Lie algebra on $M \times X$ is of the form
+In this paper we are interested in theories obtained from twists of supersymmetric theories. 
+Generally speaking, such twists have a mixed holomorphic and topological behavior.
+%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
+%Let $\cV$ denote its sheaf of holomorphic sections.
+%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
+%\[
+%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
+%\]
+%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
+%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
+%
+%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
+%\begin{itemize}
+%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
+%\[
+%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
+%\]
+%\end{itemize}
+%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
+%
+%\parsec
+
+Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
+\beqn\label{eqn:cL}
+\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
+\eeqn
+where $L$ is a graded holomorphic vector bundle on $X$.
+The structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
+For more details we refer to the definitions in \cite{GRWthf}.
+
+In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra. 
+The factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochain on the $L_\infty$ algebra $\cL(U)$. 
+We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.
+
+Suppose that $M \times X = \R^m \times \C^n$ and suppose that the bundle $L \to \C^n$ is translation invariant with fiber $L_0$ over $0 \in \R^m \times \C^n$.
+We also assume that all structure maps of the $L_\infty$ algebra are translation invariant.
+The jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras
 \[
-\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
+\cL(\C^n \times \R^m) \to L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
 \]
-where $L$ is a graded holomorphic vector bundle on $X$.
+The differential, or one-ary, operation of the $L_\infty$ algebra on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
+Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
+\[
+L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} L_0 [[z_j]] 
+\]
+is a quasi-isomorphism. 
+The only remaining differential on the right hand side is~$Q^{hol}$. 
+In total, the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.
 
@@
 \]
+Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
+\[
+\Obs(0) \simeq \cO \left( L_0[[z_1,\ldots,z_n]][1] \right) 
+\]
+where the right hand side is equipped with the differential $Q^{hol}$. 
 \end{lem}
 
-\parsec[]
+We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
+if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
+The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.
 
-Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
-Let $\cV$ denote its sheaf of holomorphic sections.
-The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
-\[
-\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
-\]
-where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
-Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
+\parsec[s:pexp]
 
-As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
-\begin{itemize}
-\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
-\[
-[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
-\]
-\end{itemize}
-A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
+\brian{characters, plethystic, etc.}
 
@@
 
+We present some simple examples.
+
 \begin{eg}
-Suppose that $V$ is the trivial bundle on $\C^n$. 
+Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
+\[
+\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(X) [-1]
+\]
+where the differential is just $\d_{dR} + \dbar$. 
+Notice that with the shift functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
 Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
@@
 Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following `single particle index'
+The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
 \[
@@
 
-\subsection{Operators on a single fivebrane}
-
-We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
-This theory exists on any complex three-fold $X$. 
-To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.
-
-The theory on a single fivebrane is free and the underlying cochain complex of fields on $\C^3$ is given by 
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
-\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
-
-\begin{lem}
-\label{lem:single}
-The $\Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
-\beqn\label{eqn:localfree}
-\Pi \Omega^{2,hol}_{cl} (\Hat{D}^3) \oplus \Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2 .
-\eeqn
-\end{lem}
-
-\parsec
+\subsection{Twisted global symmetry}
 
@@
 
-In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
-We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
-We recount how it acts on the vector space \eqref{eqn:localfree}.
+%In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
+%We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
+%We recount how it acts on the vector space \eqref{eqn:localfree}.
+% 
+%Recall that the even part of $E(3|6)$ consists of two summands:
+%\[
+%\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
+%\]
+%Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
+%An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.
 
-Recall that the even part of $E(3|6)$ consists of two summands:
+After complexification, the six-dimensional superconformal algebra is $\lie{osp}(8|4)$. 
+The holomorphic supercharge is a supertranslation 
 \[
-\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
+Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
 \]
-Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
-An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.
+which has the properties that $Q^2 = 0$ and that its image
+\[
+{\rm Im}\left(Q|_{\Pi S_+ \otimes \C^4} \right) \subset \R^6 \otimes_\R \C \cong \C^6
+\]
+is three-dimensional (spanned by the anti-holomorphic translations). 
+The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator, and its cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
+This cohomology can be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.
 
-\parsec
+We consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
+\[
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
+\]
 
-We consider the equivariant character of local operators on the holomorphic twist of a single fivebrane with respect to the following finite dimensional subalgebra of $E(3|6)$ 
-\[
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset E(3|6) 
-\]
-which embeds in the following way: 
+which acts in the following way: 
 \begin{itemize}
@@
 \end{table}
+
+\subsection{Operators on a single fivebrane}
+
+We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
+This theory exists on any complex three-fold $X$. 
+To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.
+
+The theory on a single fivebrane is free and the underlying cochain complex of the abelian holomorphic local Lie algebra on $\C^3$ is given by 
+\beqn
+\begin{tikzcd}
+\ul{-1} & \ul{0} \\
+\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
+\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
+\end{tikzcd} 
+\eeqn
+Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
+
+\begin{lem}
+\label{lem:single}
+The $\Z \times \Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
+\beqn\label{eqn:localfree}
+\Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
+\eeqn
+\end{lem}
+
+\begin{proof}
+The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
+\beqn
+\begin{tikzcd}
+\ul{-1} & \ul{0} \\
+\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
+\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
+\end{tikzcd} 
+\eeqn
+On the formal disk all closed two-forms are automatically exact, which implies the lemma.
+\end{proof}
 

### 2022-06-06 fivebranes/fact.tex
all around

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

\section{Factorization algebras in twisted $M$ theory}

The observables of any theory in the BV formalism enhance to the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of classical observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the $L_\infty$ structure maps.

The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
From the data of a factorization algebra, one can recover local operators by the following formal construction.

\begin{dfn} 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
\end{dfn}

Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures \brian{difference between limit and homotopy limit}

\subsection{The factorization algebra associated to twisted supergravity}

\parsec[s:sugraobs]

As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $X \times S$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]
We will denote the entire factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.

\parsec[s:singleobs]

Let $Z$ be a complex threefold. 
In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\cL_{single}$ on $Z$. 
The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
the cochain complex
\[
\clie^\bu\left(\cL_{single}(U)\right) .
\]
We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bu(\cL_{single})$.

\end{document}

### 2022-06-06 fivebranes/index.tex
all around

@@
 
-\section{The representation theory of local operators}
+\section{Twisted supergravity states}
 
@@
 
-\begin{dfn} 
-Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
-The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-\end{dfn}
+Generally speaking, twists of supersymmetric theories have a mixed holomorphic and topological behavior.
 
@@
 
-In this paper we are interested in theories obtained from twists of supersymmetric theories. 
-Generally speaking, such twists have a mixed holomorphic and topological behavior.
 %Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
@@
 %\parsec
-
+In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra $\cL$.
 Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
@@
 where $L$ is a graded holomorphic vector bundle on $X$.
-The structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
+The differential is required to be of the form
+\[
+\d_{dR} + \dbar + Q^{hol}
+\]
+where $\d_{dR}$ is the de Rham differential acting on $M$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon L \to L[1]$ is a holomorphic differential operator of cohomological degree $+1$.
+The higher $L_\infty$ structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
 For more details we refer to the definitions in \cite{GRWthf}.
 
-In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra. 
-The factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochain on the $L_\infty$ algebra $\cL(U)$. 
+In this situation, the factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
 We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.
@@
 \]
-The differential, or one-ary, operation of the $L_\infty$ algebra on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
+The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
 Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
@@
 \]
-is a quasi-isomorphism. 
+which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
 The only remaining differential on the right hand side is~$Q^{hol}$. 
-In total, the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.
+In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.
 
@@
 
-\begin{eg}
 Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
 \[
-\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(X) [-1]
+\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) [-1]
 \]
 where the differential is just $\d_{dR} + \dbar$. 
-Notice that with the shift functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
+Notice that with the shift, functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
 Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
@@
 \]
-\end{eg}
 
@@
 
-\subsection{Twisted global symmetry}
-
-\brian{i think I will recall some of this in the language of `fields' in Section 1, but it'd be good to say a few words about operators.}
+\subsection{Global symmetry for twisted fivebranes}
 
@@
 
-After complexification, the six-dimensional superconformal algebra is $\lie{osp}(8|4)$. 
+After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
+This algebra contains the $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
 The holomorphic supercharge is a supertranslation 
@@
 \]
-which has the properties that $Q^2 = 0$ and that its image
+which is characterized (up to equivalence) by the properties that $Q^2 = 0$ and that its image
 \[
@@
 is three-dimensional (spanned by the anti-holomorphic translations). 
-The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator, and its cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
-This cohomology can be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.
+The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
+This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.
 
-We consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra 
+To compute characters of local operators the fivebrane worldvolume theory we will consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra
+\beqn\label{eqn:bosonic1}
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
+\eeqn
+We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.
+
+In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
+Geometrically, this background is $AdS_7 \times S^4$. 
+In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.
+
+We recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
+This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory.
+
+For convenience we choose coordinates on the eleven manifold as
 \[
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
+\C^5 \times \R = \C_z^3 \times \C_w^2 \times \R_t
 \]
+with $z_i, i=1,2,3$ and $w_a, a=1,2$.
+The stack of fivebranes wrap $w_1=w_2=t=0$. 
+Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.
 
-which acts in the following way: 
 \begin{itemize}
-\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect(\Hat{D}^3)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
-where $(a_{ij}) \in \lie{sl}(3)$. 
-\item The Lie algebra $\lie{sl}(2)$ is the subalgebra of $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$ consisting of constant formal series. 
-\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by Euler vector field $\sum_i z_i \frac{\del}{\del z_i} \in \Vect(\Hat{D}^3).$
+\item
+The subalgebra $\lie{sl}(3)$ embeds as vector fields
+\[
+\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
+\]
+\item
+The subalgebra $\lie{gl}(1)$ is mapped to the element
+\[
+\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
+\] 
+Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
+\item 
+The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
+\[
+w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+\]
 \end{itemize}

### 2022-06-06 fivebranes/twisted.tex
outline
all around

@@
 
-\subsection{A model for twisted supergravity}
+\subsection{A model for holomorphically twisted supergravity}
 
@@
 The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
-We opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
-The additional data of a theory in the BV formalism is a graded skew-symmetric pairing on this sheaf.
+In the first few sections we describe the fields and equations of motion of the eleven-dimensional theory.
 
@@
 
+\parsec[s:sugrafields]
+
 \parsec[s:Lsugra]
+
+We move on to give a complete description of our eleven-dimensional model.
+In the BV formalism one introduces antifields and antighosts to the fields and ghosts that we have just described.
+It is then fundamental to consider a graded skew-symmetric pairing between fields and antifields (ghosts and antighosts). 
+Once such a pairing is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
 
@@
 On $X \times S = \C^5 \times \R$ it is furthermore argued in \cite{RSW} that this BV theory is equivalent to the holomorphic (or minimal) twist of perturbative eleven-dimensional supergravity.
-
-\parsec[s:sugraobs]
-
-In the BV formalism, the sheaf of fields of the eleven-dimensional theory is $\Pi \cL_{sugra}$. 
-As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
-The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
-In other words, as a $\Z/2$ graded commutative dg algebra, the classical observables of the eleven-dimensional theory supported on an open set $U \subset X \times S$ is 
-\[
-\clie^\bu\left(\cL_{sugra}(U)\right) .
-\]
 
@@
 The full space of BV fields is simply $\Pi \cL_{single}$.
-
-\parsec[s:singleobs]
-
-The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
-the cochain complex
-\[
-\clie^\bu\left(\cL_{single}(U)\right) .
-\]
 
@@
 \begin{prop}
-There is a natural inclusion of of factorization algebras 
+Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
+There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
+\begin{itemize}
+\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
 \[
@@
 which is dense at the level of cohomology. 
+\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
+\beqn\label{eqn:decomp3}
+\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
+\eeqn
+\item[(3)]
+In weight zero, there is an equivalence of local Lie algebras on $Z$ 
+\[
+\cV_0 \simeq \cE(3|6)|Z .
+\]
+\end{itemize}
 \end{prop}
 
-We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
+%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
 
-\brian{old below}
+\parsec
+
+\begin{prop}
+On flat space 
+\end{prop}
+
+\appendix
 
@@
 
-\begin{prop}
-Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
-There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
-\begin{itemize}
-\item[(1)] there is a map of factorization algebras
-\[
-\clie^\bu(\cL_{\pi,sugra}) \to \pi_* \Obs_{sugra}
-\]
-which is dense in cohomology. 
-\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
-\beqn\label{eqn:decomp3}
-\cL_{\pi,sugra} = \prod_{n \geq -1} \cV_{n} 
-\eeqn
-\item[(3)]
-In weight zero, there is an equivalence of local Lie algebras on $Z$ 
-\[
-\cV_0 \simeq \cE(3|6)|Z .
-\]
-\end{itemize}
-\end{prop}
-
 \section{Example}

### 2022-06-07 fivebranes/fact.tex
kd

@@
 
+\begin{rmk}
 The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
@@
 
-\begin{dfn} 
 Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
 The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-\end{dfn}
 
 Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures \brian{difference between limit and homotopy limit}
+\end{rmk}
+
+At the quantum level this Chevellay--Eilenberg complex is deformed.
+The BV formalism ...
+Even in perturbation theory the full quantum behavior of the holomorphical-topological eleven-dimensional theory is an open question. 
+We leave the problem to characterize the quantization to future work.
 
@@
 \]
-We will denote the entire factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.
+We will denote the entire classical factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.
 
-\parsec[s:singleobs]
+\parsec[s:membraneobs]
+
+\parsec[s:fivebraneobs]
 
@@
 
+\subsection{Koszul duality for factorization algebras: an ansatz}
+
+In quantum field theory Koszul duality naturally appears in the problem of coupling topological line operators to some ambient bulk theory. 
+More generally, for higher dimensional topological defects, this problem is encoded by Koszul duality for the theory of $\EE_n$ algebras \cite{??}.
+
+More generally, we anticipate a general theory of Koszul duality for factorization algebras which should encode the problem of coupling arbitrary defects (without the condition of being topological).
+Even for factorization algebras of holomorphic-topological nature this theory has not been studied in mathematics. 
+Nevertheless, we will emphasize features that we expect this general form of Koszul duality to possess which will allow us to nail down its behavior on a rather general class of factorization algebras.
+
+In this first part of this subsection we briefly recall how Koszul duality enters in the problem of coupling line operators. 
+We refer~\cite[\S 6]{CP1},~\cite[\S ??]{CG1}, or the review~\cite{PWkoszul} for more details. 
+Then, we give an ansatz for Koszul duality for factorization algebras of the form $\clie^\bu(\cL)$ where $\cL$ is some local Lie algebra. 
+From the point of view of the BV formalism this is not much of a condition, all such factorization algebras of classical observables can be cast in this form.
+
+\parsec[s:lines]
+Suppose that we have a bulk theory living on a spacetime of the form 
+\[
+\R \times M 
+\]
+where $M$ is some smooth manifold. 
+Denote by $\cA$ the corresponding factorization algebra on $\R \times M$. 
+The theory could have arbitrary behavior along $M$, but we assume that the theory is topological along $\R$. 
+This means that when viewed as a factorization algebra on $\R$ that $\cA$ is locally constant and is hence equivalent to the data of an $\EE_1$ or $A_\infty$ algebra.
+
+Next, assume that $\cB$ is another $\EE_1$ algebra, which we think of as being associated to some quantum mechanical system along the real line.
+This is a local model for the desired line operator that we are attempting to couple to the bulk theory.
+Koszul duality enters in the problem of coupling the two quantum mechanical systems $\cA$ and $\cB$---where we view $\cA$ simply as an $\EE_1$ algebra.
+
+A coupling of the two systems is Maurer--Cartan element in the algebra
+\[
+\alpha \in \cA \otimes \cB .
+\]
+That is, $\alpha$ is an element of ghost degree one which satisfies the Maurer--Cartan equation
+\[
+\delta \alpha + \alpha \star \alpha = 0 .
+\]
+Given such an $\alpha$ we can deform the algebra $\cA \otimes \cB$ by adding the term $[\alpha,-]$ to the differential. 
+In other words, at the cochain level only the differential, not the product structure, is modified.
+
+In principle, there are more general ways to `couple' two $\EE_1$ algebras; generally this is controlled by the Hochschild cohomology which governs algebra deformations of $\cA \otimes \cB$. 
+we will elaborate further on this definition. 
+In \cite{CG1} (see also \cite{PWkoszul}) it is shown how this notion relates to the physicists description of coupling in terms of local Lagrangians.
+
+To see Koszul duality, the key observation is that the data of the Maurer--Cartan element $\alpha$ is equivalent to the data of a map of $\EE_1$ algebras
+\[
+\alpha \colon \cA^! \to \cB 
+\]
+where $\cA^!$ is Koszul dual to the algebra $\cA$. 
+We then have the following slogan: the Koszul dual of the algebra of observables of the bulk theory $\cA^!$ is the algebra of operators on the {\em universal} line defect supported on $\RR \times \{x\}$, where $x \in M$.
+
+\parsec[s:celine]
+
+Before moving towards our definition of Koszul duality for a general class of factorization algebras, we briefly recast the case of duality for $\EE_1$ algebras in terms of factorization algebras.
+
+We will focus on a slight generalization of the standard Koszul duality between the exterior and symmetric algebras.
+
+\begin{prop}
+Let $\lie{g}$ be a Lie algebra and equip the associative dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological Lie map $0 \to \lie{g}$.
+The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
+\end{prop}
+
+There are explicit models for the associative dg algebras $\clie^\bu(\lie{g})$ and $U \lie{g}$ as locally constant factorization algebras on $\R$.
+First, observe that we can tensor $\fg$ with the commutative dg algebra of de Rham forms to obtain a dg Lie algebra $\fg \otimes \Omega^\bu(\R)$. 
+This has a natural enhancement to a local dg Lie algebra as this is simply the smooth sections of the bundle of Lie algebras $\fg \otimes \wedge^\bu \T^*_\RR$ equipped with the de Rham operator.
+
+Using this local Lie algebra, we obtain a model for the associative (and commutative) dg algebra $\clie^\bu(\fg)$ as the factorization algebra
+\[
+\clie^\bu(\fg \otimes \Omega^\bu_\R).
+\]
+To an open set $U \subset \R$ this produces the Chevellay--Eilenberg complex computing the Lie algebra {\em cohomology} of the dg Lie algebra $\fg \otimes \Omega^\bu(U)$---the $\fg$-valued de Rham forms on $U$.
+
+Similarly, a model for $U \fg$ is the locally constant factorization algebra
+\[
+\clie_\bu(\fg \otimes \Omega^\bu_{\R,c}).
+\]
+To an open set $U \subset \R$ this produces the Chevellay--Eilenberg complex computing the Lie algebra {\em homology} of the dg Lie algebra $\fg \otimes \Omega^\bu_c(U)$---the $\fg$-valued compactly supported de Rham forms on $U$.
+
+\parsec[s:generalkoszul]
+
+\begin{dfn}
+Let $\cL$ be a local $L_\infty$ algebra on a manifold $M$ and consider the factorization algebra $\clie^\bu(\cL)$ which assigns to an open set $U \subset M$ the cochain complex $\clie^\bu(\cL(U))$. 
+The \defterm{Koszul dual factorization algebra} is 
+\[
+\clie^\bu(\cL(U))^! \define \clie_\bu (\cL_{c}(U)) .
+\]
+In other words, the Koszul dual factorization algebra of $\clie^\bu(\cL)$ is the (untwisted) factorization enveloping algebra of the local Lie algebra $\cL$. 
+\end{dfn}
+
+\subsection{The restricted factorization algebra}
+
+For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
+\[
+0 \times 0 \times \C^3 \subset \C^5 .
+\]
+The general prescription of twisted holography is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra
+
+\parsec[s:flat]
+
+%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
+%\[
+%\C^3 \times (\R \times \C^2 - 0) .
+%\]
+%
+%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
+%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
+
+In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.
+
+Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
+Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
+\[
+\pi_* \Obs_{sugra} 
+\]
+on $\C^3$.
+This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
+Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+
+For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
+\begin{itemize}
+\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
+\]
+\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
+\]
+\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
+\]
+\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
+\]
+\end{itemize}
+
+For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
+\[
+\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
+\]
+be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
+The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
+Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
+\[
+(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+\]
+is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+In this way, the assignment 
+\[
+\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
+\]
+defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
+
+\begin{prop}
+For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
+\[
+\Omega^{0,\bu}(U, \cV^{(n)})
+\]
+for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$. 
+In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
+\end{prop}
+
+Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
+\[
+U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
+\]
+has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
+
+\begin{prop}
+Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
+There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
+\begin{itemize}
+\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
+\[
+\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
+\]
+which is dense at the level of cohomology. 
+\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
+\beqn\label{eqn:decomp3}
+\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
+\eeqn
+\item[(3)]
+In weight zero, there is an equivalence of local Lie algebras on $Z$ 
+\[
+\cV_0 \simeq \cE(3|6)|Z .
+\]
+\end{itemize}
+\end{prop}
+
+%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
+
+\parsec
+
+\begin{prop}
+On flat space 
+\end{prop}
+
 \end{document}

### 2022-06-07 fivebranes/twisted.tex
removed preambles in included files, formatting
merge

@@
 
-\parsec[s:flat]
-
-%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
-%\[
-%\C^3 \times (\R \times \C^2 - 0) .
-%\]
-%
-%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
-%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
-
-In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.
-
-Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
-Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
-\[
-\pi_* \Obs_{sugra} 
-\]
-on $\C^3$.
-This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
-Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
-
-For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
-\begin{itemize}
-\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
-\]
-\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
-\]
-\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
-\]
-\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
-\]
-\end{itemize}
-
-For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
-\[
-\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
-\]
-be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
-The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
-Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
-\[
-(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
-\]
-is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
-In this way, the assignment 
-\[
-\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
-\]
-defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
-
-\begin{prop}
-For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
-\[
-\Omega^{0,\bu}(U, \cV^{(n)})
-\]
-for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$. 
-In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
-\end{prop}
-
-Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
-\[
-U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
-\]
-has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
-
-\begin{prop}
-Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
-There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
-\begin{itemize}
-\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
-\[
-\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
-\]
-which is dense at the level of cohomology. 
-\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
-\beqn\label{eqn:decomp3}
-\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
-\eeqn
-\item[(3)]
-In weight zero, there is an equivalence of local Lie algebras on $Z$ 
-\[
-\cV_0 \simeq \cE(3|6)|Z .
-\]
-\end{itemize}
-\end{prop}
-
-%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
-
-\parsec
-
-\begin{prop}
-On flat space 
-\end{prop}
-
 \appendix

### 2022-06-07 fivebranes/twisted.tex
fivebrane

@@
-\documentclass[11pt]{amsart}
+%\documentclass[11pt]{amsart}%
 
 %\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-%%fivebrane}
 
-\begin{document}
+%%\begin{document}
 
 \section{Twisted eleven-dimensional supergravity}
-
+%
 \subsection{A model for holomorphically twisted supergravity}
@@
 
-The theory is $\Z \times \Z/2$ graded but at first pass we recall its totalization as a $\Z/2$ graded theory. 
-There are four fundamental fields $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $Z$:
+The theory is $\Z \times \Z/2$ graded where $\Z$ is the ghost number (or cohomological degree) and $\Z/2$ is parity. 
+There are four fundamental fields of ghost number zero $(\alpha, \omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $Z$:
 \[
@@
 \]
-and a pair of even sections:
+and a pair of odd $(0,1)$ forms twisted by the line bundle $K^{1/2}_Z$:
 \[
-(\phi_1,\phi_2) \in \Omega^0(Z , K^{1/2}_Z) \otimes \C^2 .
+(\phi_1,\phi_2) \in \Pi \Omega^{0,1}(Z , K^{1/2}_Z) \otimes \C^2 .
 \]
@@
 \eeqn
+There are also odd gauge symmetries for the odd fields $\phi_i$ given by
+\beqn
+\phi_i \mapsto \phi_i + \dbar \chi 
+\eeqn
+where $\chi \in \Omega^0(Z, K_{Z}^{1/2}) \otimes \C^2$.
 
@@
 
-In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z/2$ graded local Lie algebra on $Z$ which is of the form 
+In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
 \[
-\cL_{single} = \Omega^{\leq 1, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
+\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
 \]
@@
 where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.
-
-\appendix
 
@@
 
-\end{document}
+%\end{document}

### 2022-06-07 fivebranes/fact.tex
merge

@@
-\documentclass[11pt]{amsart}
+%\documentclass[11pt]{amsart}
 
 %\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-fivebrane}
 
-\begin{document}
+%\begin{document}
 
@@
 
+In analogy with the case of $\EE_1$, or locally constant factorization, algebras above we make the following definition.
+
 \begin{dfn}
 Let $\cL$ be a local $L_\infty$ algebra on a manifold $M$ and consider the factorization algebra $\clie^\bu(\cL)$ which assigns to an open set $U \subset M$ the cochain complex $\clie^\bu(\cL(U))$. 
-The \defterm{Koszul dual factorization algebra} is 
+The \defterm{$!$-dual factorization algebra} is 
 \[
-\clie^\bu(\cL(U))^! \define \clie_\bu (\cL_{c}(U)) .
+\clie^\bu(\cL)^! \define \clie_\bu (\cL_{c}) 
 \]
-In other words, the Koszul dual factorization algebra of $\clie^\bu(\cL)$ is the (untwisted) factorization enveloping algebra of the local Lie algebra $\cL$. 
+where $\clie_\bu(\cL_c)$ assigns to an open set $U \subset M$ the cochain complex $\clie_\bu(\cL_c(U))$.
+In other words, the $!$-dual factorization algebra of $\clie^\bu(\cL)$ is the (untwisted) factorization enveloping algebra of the local Lie algebra $\cL$. 
 \end{dfn}
+
+There are many things lacking in this definition. 
+First off we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
+Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
+From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie,...}}
+
+With an eye towards couplings, we do point out a universality that is satisfied by $!$-duality. 
+In \cite[Chapter ??]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
+The general context is the following: 
+\begin{itemize}
+\item $\Obs$ is the factorization algebra of classical observables of a theory in the BV formalism on a manifold $M$.
+\item $\cG$ is a local Lie algebra on $M$ which acs on the theory by local symmetries. 
+\end{itemize}
+Then, the classical version of Noether's theorem for factorization algebras produces a map of factorization algebras 
+\[
+\clie_\bu(\cG_c) \to \Obs .
+\]
+
+We arrive at $!$-duality in our situation above in the case that $\Obs$ is a factorization algebra of the form $\clie^\bu(\cL)$ where $\cL$ is another local $L_\infty$ algebra on $M$. 
+This is always possible in the BV formalism: on an open set $U$ the space of Maurer--Cartan elements in the $L_\infty$ algebra $\cL(U)$ is the space of solutions to the equations of motion on $U$.
+Thus, tautologically, the local Lie algebra $\cL$ is a symmetry of the classical theory.
 
@@
 \]
-\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
+\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
 \[
@@
 \begin{prop}
-For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
+For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
 \[
@@
 for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
+For each $n$, the differential is of the form $\dbar + Q^{hol}$.
 In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
 \end{prop}
+
+\parsec[s:weight-1]
+
+As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
+We will show that 
+\[
+\cV^{(-1)} = K^{-1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
+\]
+whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
+
+Explicitly weight zero summand $\cV^{(0)}$ consists of:
+\begin{itemize}
+\item 
+Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
+Notice that these vector fields are automatically divergence-free.
+Since $\del_{w_a}$ is treated as a section of $K^{-1/2}_Z$ we see that these are local sections of $K^{-1/2}_Z \otimes \C^2$. 
+\item 
+Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
+Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
+\[
+\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
+\]
+\end{itemize}
+
+\parsec[s:weight0]
+
+Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
+When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
+In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
+
+As a holomorphic vector bundle, we will see that
+\[
+\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\]
+The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.
+
+Explicitly, we enumerate all weight zero holomorphic sections:
+\begin{itemize}
+\item Vector fields which are locally of the form $\mu = f^i(z) \del_{z_i}$ or $\mu = g(z) A^{ab} w_a \del_{w_b}$ where $(A^{ab}) \in \lie{sl}(2)$.
+\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
+Since $\del$ is weight zero, such sections are equipped with a differential 
+\[
+\Gamma^{hol}(Z, K^{1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{1/2}) 
+\]
+which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
+The $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{1/2})$. 
+\end{itemize}
+
+\parsec[s:??]
 
@@
 Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
-There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
+There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
 \begin{itemize}
@@
 \[
-\cV_0 \simeq \cE(3|6)|Z .
+\cV_0 \simeq \cE(3|6)|Z 
 \]
+where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
 \end{itemize}
@@
 
+\parsec[s:e36]
+The exceptional super Lie algebra $E(3|6)$
+
+Let $Z$ be a complex manifold of complex dimension three equipped with a square-root of the canonical bundle.
+To freely resolve the space of holomorphic sections
+we employ the Dolbeault complex of the appropriate holomorphic vector bundle. 
+For holomorphic vector fields we introduce the dg Lie algebra
+\[
+\Omega^{0,\bu}(X , \T_X)
+\]
+of $(0,\bu)$ Dolbeault forms with values in the holomorphic tangent bundle. 
+Also, for any holomorphic vector bundle $V$ let
+\[
+\Omega^{-1/2 , \bu}(X, V) = \Omega^{0,\bu}(X , V \otimes \T_X^* \otimes \sigma^{-1}) .
+\]
+
 \parsec
 
-\begin{prop}
-On flat space 
-\end{prop}
+We define a super dg Lie algebra to be a $\Z \times \Z/2$ graded Lie algebra $\fg = \fg_+^\bu \oplus \Pi \fg_-^\bu$ which satisfies totalized graded skew symmetry and is equipped with a differential $\d$ of bidegree $(1,+)$ that is square zero and a derivation for the bracket.
+For more details see \cite[Section 2]{EHSW}.
 
-\end{document}
+\begin{dfn}
+Let $\sigma$ and $P$ be as above. 
+Define the following local super Lie algebra $\cE_{P,\sigma}$ on $X$ whose even and odd parts are
+\begin{align*}
+\cE_{P,\sigma,+} & = \Omega^{0,\bu}(X , \T_X) \oplus \Omega^{0,\bu}(X , \ad P)\\
+\cE_{P,\sigma,-} & = \Omega^{1 , \bu}(X, R_X \otimes \sigma^{-1}) .
+\end{align*}
+The differential is given by the natural $\dbar$-operator whenever it makes sense.
+The bracket is defined analogously as in formulas \brian{ref}. 
+\end{dfn}
+
+On $X = \C^3$ there is a natural choice for $\sigma = K^{1/2}_{\CC^3}$, and we can take $P$ to be the trivial $SL(2)$ bundle. 
+With these choices we have the following easy lemma.
+
+%\end{document}

### 2022-06-07 fivebranes/membrane.tex
merge

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

\section{membrane}

In this section we provide a description of the holomorphic, or minimal, twist of the worldvolume theory on a single membrane. 
It is defined on any three-manifold of the form $L \times \Sigma$ where $L$ is a real oriented one-manifold and $\Sigma$ is a Riemann surface equipped with a fourth root of the canonical bundle $K^{1/4}_\Sigma$.

The theory is $\Z/2$ graded which combines the cohomological $\Z$ and parity $\Z/2$ gradings present in the untwisted theory.
In the BV formalism the fields of the theory are
\[
\Omega^\bu(L) \otimes \Omega^{0,\bu}(\Sigma, K^{1/4}_\Sigma \otimes \C^4 \oplus \Pi K^{3/4} \otimes \C^4) .
\]
We denote fields according to the direct sum above by pairs $(\phi_a,\chi_a)$ where $a=1,\ldots 4$. 
The full BV action is 
\[
\int_{L \times \Sigma} \ep^{ab} \phi_a \d_{dR} \chi_b + \int_{L \times \Sigma} \ep^{ab} \phi_a \dbar \chi_b .
\]
The equations of motion are simply 
\[
\d_{dR} \phi_a + \dbar \phi_a = \d_{dR} \chi_a + \dbar \chi_a = 0
\]
for $a=1,\ldots, 4$.

In the (degenerate) BV formalism, this free theory can be packaged into the data of the abelian $\Z/2$ graded local Lie algebra on $L \times \Sigma$ 
\[
\cL_{membrane} = \Pi \Omega^\bu(L) \otimes \Omega^{0,\bu}(\Sigma, K^{1/4}_\Sigma \otimes \C^4 \oplus K^{3/4} \otimes \C^4)
\]
where the $\Pi$ denoted parity shift.

\section{$E(1|6)$}

\end{document}

### 2022-06-08 fivebranes/twisted.tex
backreactions setup

@@
 
-\parsec[s:coupling]
+\subsection{Twisted Backreactions}
 
-The holographic description of the ${\rm AdS}_7 \times S^4$ background in eleven-dimensional supergravity is obtained by backreacting a number of fivebranes \brian{references}. 
-In \cite{RSW} we gave a description of the twisted avatar of this background and described how it arises by backreacting a number of holomorphically twisted fivebranes. 
-We briefly recall the relevant setup here.
+In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \brian{references}.
 
-As above, let $Z$ be a three-fold equipped with $K^{1/2}_Z$.
-Consider the rank two vector bundle $K^{1/2}_Z \otimes \C^2$ on $Z$. 
-Via the linear holomorphic symplectic form on $\C^2$, the total space of this vector bundle ${\rm Tot}(K^{1/2}_Z \otimes \C^2)$ is equipped with a Calabi--Yau structure. 
-We consider the eleven-dimensional theory on 
-\[
-\R \times {\rm Tot}(K^{1/2}_Z) 
-\]
-with a stack of fivebranes supported at $0 \in \R$ and along the zero section in the total space of the vector bundle
-\[
-0 \times Z \subset \R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)  .
-\]
-Let us denote $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$.
+In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We recall the results therein, adapted to our situation.
+
+\parsec
+
+As above, let $Z$ be a three-fold, $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = {\rm Tot}V$.
+The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold - in the main body of the paper we will restrict ourselves to $V = K_{Z}^{1/2}\otimes \C^{2}$.
+We will view $\R\times X = {\rm Tot}(\R\oplus V)$, and consider a stack of N fivebranes wrapping the zero section in $\R\oplus V$.
+
+The theory in the backreacted geometry will be defineed to be a deformation of the 11d theory placed on the complement of the zero section.
+The complement of the zero section admits additional structures inherited from the obvious THF structure on $\R \times X$.
+Note that $\R\oplus V$ has an obvious rank 1 subbundle together with a complex structure on the quotient.
+Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$.
+Explicitly, the corresponding norm is given by
+\begin{align*}
+ \pi:  \R\times X & \to \R_{+} \\
+  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
+\end{align*}
+Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The fiber spheres have a canonical foliation
 
@@
 where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.
+
+\parsec
+Let $C$ be a curve, and let $V\to C$ be a rank 4-holomorphic vector bundle over $C$ such that $\wedge^{4} V = K_{C}$.
+This condition again ensures that $X = {\rm Tot} V$ is a Calabi-Yau five-fold - in the main body of the paper, we will take $V = K^{1/2}_{C}\otimes \C^{4}$.
+Abusively letting $V$ also denote its pullback along the canonical projection $\R\times C \to C$, we may view $\R\times X$ as the total space of $V$ on $\R\times C$.
+As before we will consider wrapping a stack of $N$ membranes along the zero section.
+
+Since $V$ is a complex vector bundle, we may choose a fiberwise hermitian metric, and as before, we may view $\R\times X \setminus \R\times C$ as an $S^{7}$-bundle over $\R_{>0}\times \R\times C$.
 

### 2022-06-13 fivebranes/fact.tex
merge

@@
-%\documentclass[11pt]{amsart}
+\documentclass[11pt]{amsart}
 
 %\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
+\usepackage{macros-fivebrane}
 
-%\begin{document}
+\begin{document}
 
@@
 
+In this section we consider the classical factorization algebra of observables of our prototype for the holomorphic twist of eleven-dimensional supergravity.
+
 \parsec[s:sugraobs]
@@
 As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
-In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $X \times S$. 
+In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
 The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
@@
 %The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.
+
 The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
@@
 
-\parsec[s:membraneobs]
+%\parsec[s:membraneobs]
+%
+%
+%\parsec[s:fivebraneobs]
+%
+%Let $Z$ be a complex threefold. 
+%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\cL_{single}$ on $Z$.
+%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
+%the cochain complex
+%\[
+%\clie^\bu\left(\cL_{single}(U)\right) .
+%\]
+%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bu(\cL_{single})$.
 
-\parsec[s:fivebraneobs]
+\parsec[s:restricted]
 
-Let $Z$ be a complex threefold. 
-In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\cL_{single}$ on $Z$.
-The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
-the cochain complex
+With an eye towards holography for fivebranes we fix a complex three-fold $Z$ where the fivebranes will be supported and consider the eleven-dimensional theory on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
 \[
-\clie^\bu\left(\cL_{single}(U)\right) .
+X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2),
 \]
-We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bu(\cL_{single})$.
+the total space of the rank two bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
+Here the holomorphic volume form
+One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
+Let 
+\[
+\pi \colon \R \times X_Z \to Z 
+\]
+be the map which projects out the real factor followed by the projection to the base of the total space of the complex rank two bundle $p \colon X_Z \to Z$.
+
+Like sheaves, factorization algebras can be pushed forward; thus from the factorization algebra $\Obs_{sugra}$ on $\R \times X_Z$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ on $Z$. 
+To an open set $U \subset Z$ the value of this factorization algebra is
+\begin{align*}
+(\pi_* \Obs_{sugra}) (U) & = \Obs_{sugra} \left(\pi^{-1} U\right) \\
+& = \Obs_{sugra}(\R \times p^{-1}U) .
+\end{align*}
+
+This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
+Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+This grading is determined by a $\C^\times$ action on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.
+
+\parsec[s:gradingfivebrane]
+
+In a local chart $U \subset Z$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;w,z)$ where $t \in \R$ is the real coordinate, $w=(w_1,w_2)$ is the holomorphic fiber coordinate of the rank two bundle $X_Z$ over $Z$, and $z = (z_1,z_2,z_3)$ is a local holomorphic coordinate for $U \subset Z$.
+
+%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
+%\[
+%0 \times 0 \times \C^3 \subset \C^5 .
+%\]
+%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
+%
+%\parsec[s:flatdecomp]
+%
+%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
+%%\[
+%%\C^3 \times (\R \times \C^2 - 0) .
+%%\]
+%%
+%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
+%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
+%
+%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
+%
+%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
+%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
+%\[
+%\pi_* \Obs_{sugra} 
+%\]
+%on $\C^3$.
+%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
+%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+
+With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
+\begin{itemize}
+\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
+\]
+\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
+\]
+\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
+\]
+\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
+\[
+\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
+\]
+\end{itemize}
+
+The main result of this section is the following.
+
+\begin{prop}
+\end{prop}
+
+For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
+\[
+\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
+\]
+be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
+The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
+Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
+\[
+(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+\]
+is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+In this way, the assignment 
+\[
+\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
+\]
+defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
+
+\begin{prop}
+For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
+\[
+\Omega^{0,\bu}(U, \cV^{(n)})
+\]
+for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
+For each $n$, the differential is of the form $\dbar + Q^{hol}$.
+In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
+\end{prop}
+
+We explicitly describe the first homogenous weights of $\Bar{\pi}_* \cL_{sugra}$.
+
+\parsec[s:weight-1]
+
+As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
+We will show that 
+\[
+\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
+\]
+whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
+
+Explicitly weight zero summand $\cV^{(0)}$ consists of:
+\begin{itemize}
+\item 
+Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
+Notice that these vector fields are automatically divergence-free.
+Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
+\item 
+Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
+Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
+\[
+\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
+\]
+\end{itemize}
+
+\parsec[s:weight0]
+
+Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
+When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
+In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
+
+As a holomorphic vector bundle, we will see that $\cV^{(0)}$ is 
+\[
+\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\]
+The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.
+
+Explicitly, we enumerate all weight zero holomorphic sections:
+\begin{itemize}
+\item Vector fields which are locally of the form 
+\[
+\mu = f^i(z) \del_{z_i} - \frac12 \del_{z_i} f^i(z) w_a \del_{w_a}
+\]
+and vector fields which are locally of the form
+\[
+\mu = g(z) A^{ab} w_a \del_{w_b}.
+\]
+The condition that $\mu$ be divergence-free implies that $(A^{ab}) \in \lie{sl}(2)$.
+We will identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
+\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
+Since $\del$ is weight zero, such sections are equipped with a differential 
+\[
+\Gamma^{hol}(Z, K^{-1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}) 
+\]
+which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
+This $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2})$. 
+\end{itemize}
+
+The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV^{(0)})$. 
+The differential is simply $\dbar$. 
+The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
+\begin{itemize}
+\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
+This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
+\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
+This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
+\item Finally, and most interestingly, there is a bracket of the form
+\[
+\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
+\]
+given in coordinates by
+\[
+[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right).
+\]
+\end{itemize}
+
+\parsec[s:mainfact]
+
+Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
+\[
+U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
+\]
+has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
+
+\begin{prop}
+Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
+There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
+\begin{itemize}
+\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
+\[
+\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
+\]
+which is dense at the level of cohomology. 
+\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
+\beqn\label{eqn:decomp3}
+\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
+\eeqn
+\item[(3)]
+In weight zero, there is an equivalence of local Lie algebras on $Z$ 
+\[
+\cV_0 \simeq \cE(3|6)|Z 
+\]
+where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
+\end{itemize}
+\end{prop}
+
+%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
 
@@
 
-\subsection{The restricted factorization algebra}
-
-For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
-\[
-0 \times 0 \times \C^3 \subset \C^5 .
-\]
-The general prescription of twisted holography is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra
-
-\parsec[s:flat]
-
-%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
-%\[
-%\C^3 \times (\R \times \C^2 - 0) .
-%\]
-%
-%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
-%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
-
-In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$.
-
-Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
-Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
-\[
-\pi_* \Obs_{sugra} 
-\]
-on $\C^3$.
-This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
-Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
-
-For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
-\begin{itemize}
-\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
-\]
-\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
-\]
-\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
-\]
-\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
-\[
-\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
-\]
-\end{itemize}
-
-For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
-\[
-\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\R \times \C^2 \times U)
-\]
-be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
-The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
-Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
-\[
-(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
-\]
-is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
-In this way, the assignment 
-\[
-\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
-\]
-defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
-
-\begin{prop}
-For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
-\[
-\Omega^{0,\bu}(U, \cV^{(n)})
-\]
-for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
-For each $n$, the differential is of the form $\dbar + Q^{hol}$.
-In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
-\end{prop}
-
-\parsec[s:weight-1]
-
-As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
-We will show that 
-\[
-\cV^{(-1)} = K^{-1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
-\]
-whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
-
-Explicitly weight zero summand $\cV^{(0)}$ consists of:
-\begin{itemize}
-\item 
-Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
-Notice that these vector fields are automatically divergence-free.
-Since $\del_{w_a}$ is treated as a section of $K^{-1/2}_Z$ we see that these are local sections of $K^{-1/2}_Z \otimes \C^2$. 
-\item 
-Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
-Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
-\[
-\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
-\]
-\end{itemize}
-
-\parsec[s:weight0]
-
-Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
-When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
-In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
-
-As a holomorphic vector bundle, we will see that
-\[
-\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
-\]
-The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.
-
-Explicitly, we enumerate all weight zero holomorphic sections:
-\begin{itemize}
-\item Vector fields which are locally of the form $\mu = f^i(z) \del_{z_i}$ or $\mu = g(z) A^{ab} w_a \del_{w_b}$ where $(A^{ab}) \in \lie{sl}(2)$.
-\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
-Since $\del$ is weight zero, such sections are equipped with a differential 
-\[
-\Gamma^{hol}(Z, K^{1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{1/2}) 
-\]
-which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
-The $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{1/2})$. 
-\end{itemize}
-
-\parsec[s:??]
-
-Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
-\[
-U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
-\]
-has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
-
-\begin{prop}
-Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
-There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
-\begin{itemize}
-\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
-\[
-\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
-\]
-which is dense at the level of cohomology. 
-\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
-\beqn\label{eqn:decomp3}
-\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
-\eeqn
-\item[(3)]
-In weight zero, there is an equivalence of local Lie algebras on $Z$ 
-\[
-\cV_0 \simeq \cE(3|6)|Z 
-\]
-where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
-\end{itemize}
-\end{prop}
-
-%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.
-
-\parsec[s:e36]
-The exceptional super Lie algebra $E(3|6)$
-
-Let $Z$ be a complex manifold of complex dimension three equipped with a square-root of the canonical bundle.
-To freely resolve the space of holomorphic sections
-we employ the Dolbeault complex of the appropriate holomorphic vector bundle. 
-For holomorphic vector fields we introduce the dg Lie algebra
-\[
-\Omega^{0,\bu}(X , \T_X)
-\]
-of $(0,\bu)$ Dolbeault forms with values in the holomorphic tangent bundle. 
-Also, for any holomorphic vector bundle $V$ let
-\[
-\Omega^{-1/2 , \bu}(X, V) = \Omega^{0,\bu}(X , V \otimes \T_X^* \otimes \sigma^{-1}) .
-\]
-
-\parsec
-
-We define a super dg Lie algebra to be a $\Z \times \Z/2$ graded Lie algebra $\fg = \fg_+^\bu \oplus \Pi \fg_-^\bu$ which satisfies totalized graded skew symmetry and is equipped with a differential $\d$ of bidegree $(1,+)$ that is square zero and a derivation for the bracket.
-For more details see \cite[Section 2]{EHSW}.
-
-\begin{dfn}
-Let $\sigma$ and $P$ be as above. 
-Define the following local super Lie algebra $\cE_{P,\sigma}$ on $X$ whose even and odd parts are
-\begin{align*}
-\cE_{P,\sigma,+} & = \Omega^{0,\bu}(X , \T_X) \oplus \Omega^{0,\bu}(X , \ad P)\\
-\cE_{P,\sigma,-} & = \Omega^{1 , \bu}(X, R_X \otimes \sigma^{-1}) .
-\end{align*}
-The differential is given by the natural $\dbar$-operator whenever it makes sense.
-The bracket is defined analogously as in formulas \brian{ref}. 
-\end{dfn}
-
-On $X = \C^3$ there is a natural choice for $\sigma = K^{1/2}_{\CC^3}$, and we can take $P$ to be the trivial $SL(2)$ bundle. 
-With these choices we have the following easy lemma.
-
-%\end{document}
+\end{document}

### 2022-06-13 fivebranes/fact.tex
weights

@@
 \begin{prop}
+The $L_\infty$ structure on $\cL_{sugra}$ equivariant for this $\C^\times$ action. 
+The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
 \end{prop}
+\begin{proof}
+The only nontrivial bracket to check compatibility with the $\C^\times$ action is the one which takes two $\gamma$-type sections to a $\mu$-type section of the form
+\[
+[\gamma_1, \gamma_2] = \Omega^{-1} \vee (\del \gamma_1 \wedge \del \gamma_2) 
+\]
+where $\Omega \vee (-)$ is the operation which takes a four-form
 
-For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
+It suffices to check equivariance in local coordinates; there are three cases.
+Suppose $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^j(t;w,z) \d z_j$where $f^i,g^j$ are de Rham--Dolbeault forms for $i,j=1,2,3$. 
+Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = \lambda^{-1} g^j(\lambda t;\lambda w, z) \d z_j$. 
+Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
+\beqn
+\begin{array}{llll}
+\label{eqn:lambda1} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
+\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a} .
+\end{array}
+\eeqn
+We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
+\begin{multline}
+\del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z) \d w_a \d z_i \d z_l \d z_j + \del_{z_k} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d z_k \d z_i \d w_b \d z_j \\  + \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d w_a \d z_i \d w_b \d z_j .
+\end{multline}
+Thus in the notation above we have 
+\begin{align*}
+F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \\
+G^a(t;w,z) & = \ep_{ilj} \ep_{ab} \del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z)
++ \ep_{kij} \ep_{ab} \del_{z_k} f^i(t;w,z) \del_{w_a} g^j(t;w,z)  .
+\end{align*}
+We compute the action of $\lambda \in \C^\times$ on $\mu = F^k \del_{z_k}$
+\[
+\lambda \cdot \left(F^k \del_{z_k} \right) = \ep_{ab} \ep_{ijk} \lambda^{-1} \del_{w_a} f^i(\lambda t;\lambda w,z) \lambda^{-1} \del_{w_b} g^j(\lambda t;\lambda w,z) \del_{z_k} .
+\]
+Thus the first part of \eqref{eqn:lambda1} is satisfied. 
+Similarly we observe that $\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right)  = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a}$.
+
+The next case is when $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^a(t;w,z) \d w_a$where $f^i,g^a$ are de Rham--Dolbeault forms for $i=1,2,3$ and $a=1,2$. 
+Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = g^a(\lambda t;\lambda w, z) \d w_a$. 
+Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
+\beqn
+\begin{array}{llll}
+\label{eqn:lambda2} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-1} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
+\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-1} G^a(\lambda t;\lambda w,z) \del_{w_a} .
+\end{array}
+\eeqn
+We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
+\begin{multline}
+\del_{w_b} f^i(t;w,z) \del_{z_j} g^a(t;w,z) \d w_b \d z_i \d z_j \d w_a + \del_{z_k} f^i(t;w,z) \del_{w_b} g^a(t;w,z) \d z_k \d z_i \d w_b \d w_a \\  + \del_{z_j} f^i(t;w,z) \del_{z_k} g^a(t;w,z) \d z_j \d z_i \d z_k \d w_a .
+\end{multline}
+Thus in the notation above we have 
+\begin{align*}
+F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{z_l} g^b(t;w,z) + \ep_{ab} \ep_{kij} \del_{z_k} f^i(t;w,z) \del_{w_a} g^b(t;w,z) \\
+G^a(t;w,z) & = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) .
+\end{align*}
+We compute the action of $\lambda \in \C^\times$ on $\mu = G^a \del_{z_a}$
+\[
+\lambda \cdot \left(G^a \del_{w_a} \right) = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) \lambda^{-1} \del_{w_a} .
+\]
+Thus the second part of \eqref{eqn:lambda2} is satisfied. 
+Similarly we observe that $\lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right)  = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k}$.
+
+The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
+The argument is nearly identical so we omit the details.
+
+\end{proof}
+
+For each $n \in \ZZ$ and open set $U \subset Z$, let 
 \[
@@
 be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
-The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
+%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
 Since the $n$th eigenspace is trivial when $n < -1$, we see that the product

### 2022-06-14 fivebranes/twisted.tex
merge error
progress

@@
-%\documentclass[11pt]{amsart}%
+\documentclass[11pt]{amsart}%
 
 %\usepackage{../macros-master}
-%\usepackage{macros-%%fivebrane}
+\usepackage{macros-fivebrane}
 
-%%\begin{document}
+\begin{document}
 
@@
 %
-\subsection{A model for holomorphically twisted supergravity}
+\subsection{A model for minimally twisted supergravity}
 
@@
 Within the BV formalism, the theory is only $\Z/2$ graded.
-In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory.
-We recall this description here.
+In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
+As such, the eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
 
-The eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
 In the first few sections we describe the fields and equations of motion of the eleven-dimensional theory.
@@
 
+To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
+The theory utilizes the complex structure on the Calabi--Yau fivefold $X$.
+We let $\T_X$ stand for the holomorphic tangent bundle of $X$ and $\Bar{\T}_X$ its complex conjugate.
+Thus, the complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
+\[
+\T_S \oplus \T_X \oplus \Bar{\T}_X 
+\]
+where $\T_S$ is the complexified tangent bundle of the smooth one-manifold $S$.
+Locally, we choose coordinates $(t;z,\zbar)$ where $t$ is a smooth coordinate for $S$ and $z$ is a holomorphic coordinate for $X$.
+
+Before giving a rigorous description of the fields and equations of motion, we focus on bosonic fields in our model which have an obvious analog in the untwisted theory. 
+One of the primary fields of eleven-dimensional supergravity describes deformations of the metric $g$.
+Since we work in a background which has $SU(5)$ holonomy we can take the background metric on $S \times X$ to be the product of the flat metric on $S$ with a Calabi--Yau metric $g_{CY}$ on $X$.
+
+Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
+\[
+\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* 
+\]
+which we will denote by $\mu$. 
+In local holomorphic coordinates $\mu$ admits a description like
+\[
+\mu = \mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_i} .
+\]
+
+One of the other bosonic fields of eleven-dimensional supergravity is a three-form which is usually denoted by~$C$. 
+On $S \times X$ the space of complex-valued three-forms decomposes into de Rham--Dolbeault forms as in
+\[
+\oplus_{k+p+q=3} \Omega^k(S) \otimes \Omega^{p,q}(X) .
+\]
+We denote the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
+\[
+\sum_{P,Q} f_{PQ} (t;z,\zbar) \d z_P \d \zbar_Q + \sum_{P',Q'} g_{P'Q'}(t;z,\zbar) \d t \d z_{P'}\d \zbar_{Q'} 
+\]
+where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ such that $\sum_i (p_i + q_i) = 3$, $0 \leq p_i,q_i \leq 3$.
+The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.
+
+In the minimal twist only forms with $p_i ,p_i'\leq 1$ survive. 
+Thus, the components of the three-form which survive live in
+\[
+\left(\oplus_{k+q = 3} \Omega^k(S) \otimes \Omega^{0,q}(X)\right) \oplus 
+\left(\oplus_{k+q = 2} \Omega^k(S) \otimes \Omega^{1,q}(X)\right) .
+\]
+We denote a general (non-homogenous) element in the first summand by $\beta$ and an element in the second summand by $\gamma$.
+When we want to be specific by the form type we use the notation $\beta^{k;q}$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}$ for the $(k;1,q)$ component of the three-form.
+
 \parsec[s:Lsugra]
 
-We move on to give a complete description of our eleven-dimensional model.
-In the BV formalism one introduces antifields and antighosts to the fields and ghosts that we have just described.
-It is then fundamental to consider a graded skew-symmetric pairing between fields and antifields (ghosts and antighosts). 
-Once such a pairing is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
+We move on to give a complete description of our eleven-dimensional model within the Batalin--Vilkovisky (BV) formalism.
+This amounts to introducing antifields and antighosts to the fields and ghosts that we have just described.
+One of the key structures is the graded skew-symmetric pairing between fields and antifields (ghosts and antighosts).
+Once such a pairing $\omega_{BV}$ is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
 
-In this paper $\Z/2$ graded $L_\infty$ algebra means a $\Z/2$ graded vector space~$L$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
+An $L_\infty$ algebra is a graded vector space~$L=\oplus_{p\in \Z} L^p$ equipped with a collection of operations $\{[-]_k\}_{k = 1,2,\ldots}$ where 
 \[
-\ell_k \colon L^{\times k} \to \Pi^k L 
+[-]_k \colon L^{\times k} \to L[2-k] 
 \]
 are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
-Here, $\Pi^k L = L$ if $k$ is even and $\Pi^k L = \Pi L$ if $k$ is odd. 
-Thus, $\ell_k$ is an even operation if $k$ is even and an odd operation if $k$ is odd. 
-\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
+The shift $[2-k]$ means that $[-]_k$ is of cohomological degree $k-2$.
+
+The BV fields arise as the sections of a sheaf of $L_\infty$ algebras $\cL$ over the spacetime manifold $M$.
+There is an overall shift in the relationship between the cohomological grading of $\cL$ and the ghost number in physics terminology. 
+In cohomological degree zero sit the ghosts, in cohomological degree zero sit the fields, etc..
+In this sense it is more accurate to refer to the BV fields as sections of the shift of the sheaf of $L_\infty$ algebras $\cL[1]$. 
+Together with the skew symmetric pairing $\omega_{BV}$ on the fields structure maps $[-]_k$ organize together to define the full BV action which takes the general form
+\[
+S(\Phi) = \sum_{k \geq 1} \omega_{BV} \left(\Phi , [\Phi,\ldots,\Phi]_{k}\right) .
+\]
+
+One feature of our proposal for the minimal twist of eleven-dimensional supergravity is that it only carries an overall $\Z/2$ grading. 
+This $\Z/2$ grading totalizes the original ghost grading (which is by the group $\Z$) and the fermion number which is present in the untwisted theory.
+We thus make use of $\Z/2$ graded versions of the usual BV formalism.
+In this paper $\Z/2$ graded $L_\infty$ algebra means that we just have a $\Z/2$ graded vector space.
+There are operations $\{[-]_k\}_{k = 1,2,\ldots}$ which satisfy the same higher Jacobi identities.
+The operation $[-]_k$ is even if $k$ is even and odd if $k$ is odd.\footnote{This is not to be confused with a super $L_\infty$ algebra which is an $L_\infty$ algebra internal to the category of super vector spaces.
 A $\Z/2$ graded $L_\infty$ algebra is simply what one gets when they apply the forgetful function from $\Z$ graded vector spaces to $\Z/2$ graded vector spaces.}
 
-Let $L_X$ be the following sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau five-fold $X$.
-As a sheaf of super vector spaces, $L_X$ is given as the holomorphic sections of a super vector bundle. 
+We introduce a sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau five-fold $X$.
+As a sheaf of super vector spaces, it will be given as the holomorphic sections of a super vector bundle that we denote by $L_X$. 
 The even part of this super vector bundle is
@@
 
-The $L_\infty$ structure is described as follows. 
+The $L_\infty$ structure on the sheaf of holomorphic sections of $L_X$ is described as follows. 
 First, $\d = [-]_1$, the differential, is simply given by 
@@
 [\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
-[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
-[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
+[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma \\
+[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma \\
+[\gamma_1,\gamma_2]_2 & = \Omega^{-1} \left(\del \gamma_1 \wedge \del \gamma_2 \right) .
 \end{align*}
@@
 
-%\end{document}
+\end{document}

### 2022-06-14 fivebranes/twisted.tex
updates to twisted

@@
 [\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
-[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma \\
-[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma \\
-[\gamma_1,\gamma_2]_2 & = \Omega^{-1} \left(\del \gamma_1 \wedge \del \gamma_2 \right) .
+[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
+[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
 \end{align*}
@@
 
-In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We recall the results therein, adapted to our situation.
+In \cite{RSW} we gave descriptions of twisted versions of these backgrounds.
+We recall this construction, adapted to a slightly more global situation.
+We will consider the eleven-dimensional theory on 11-manifolds that arise as total spaces of vector bundles.
+Placing the theory in the backreacted geometry is a 3-step procedure:
+
+\begin{itemize}
+  \item Place the eleven dimensional theory on the complement of the zero section.
+To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.
+
+  \item Deform the theory on the complement of the zero section by a certain maurer-cartan element. The Maurer-Cartan element is thought of as the flux sourced by branes wrapping the zero section.
+
+  \item The complement of the zero section is a manifold with boundary - we impose a natural boundary condition.
+
+\end{itemize}
 
@@
 
-The theory in the backreacted geometry will be defineed to be a deformation of the 11d theory placed on the complement of the zero section.
-The complement of the zero section admits additional structures inherited from the obvious THF structure on $\R \times X$.
-Note that $\R\oplus V$ has an obvious rank 1 subbundle together with a complex structure on the quotient.
+We begin by describing the complement of the zero section
+\[
+\R\oplus V \setminus 0\times Z
+\].
+Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation.
+That is, there is a rank 1 subbundle $\R\subset \R\oplus V$ together with a complex structure on the quotient.
 Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$.
@@
 \end{align*}
-Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The fiber spheres have a canonical foliation
+Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$.
+The vertical tangent bundle of this $S^{4}$ bundle inherits a natural subbundle coming from the THF structure of the ambient manifold; the fibers of this subbundle equip
 

### 2022-06-14 fivebranes/twisted.tex
update

--- 2022-06-14 fivebranes/twisted.tex
@@
 
-In \cite{SWspinor} a complete description of the free limit of the holomorphic twist of eleven-dimensional supergravity is given.
-Within the BV formalism, the theory is only $\Z/2$ graded.
+Eleven-dimensional supergravity is the unique...
+Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
+\begin{itemize}
+\item 
+The minimal twist. 
+This twist leaves six real directions invariant and is preserved by the subgroup $SU(5)$ of the Lorentz group. 
+\item 
+The non-minimal twist. 
+This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
+\end{itemize}
+
+In this paper we will focus primarily on the minimal twist. 
+In \cite{SWspinor} a complete description of the free limit of this twist of eleven-dimensional supergravity is given.
+Within the BV formalism, the theory is only $\Z/2$ graded, a point we will elaborate on further soon. 
 In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
-As such, the eleven-dimensional theory exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a real oriented smooth one-dimensional manifold.
+Globally, the eleven-dimensional theory exists on any manifold of the form $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
 
@@
 
-We introduce a sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau five-fold $X$.
+To build the $L_\infty$ algebra associated to the eleven-dimensional theory, we first introduce a sheaf of $\Z/2$ graded $L_\infty$ algebras on the Calabi--Yau fivefold $X$.
 As a sheaf of super vector spaces, it will be given as the holomorphic sections of a super vector bundle that we denote by $L_X$. 
@@
 On $X \times S = \C^5 \times \R$ it is furthermore argued in \cite{RSW} that this BV theory is equivalent to the holomorphic (or minimal) twist of perturbative eleven-dimensional supergravity.
+
+Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.
+\brian{elaborate gauge symmetries, write action, etc.}
 
@@
 \]
-The full space of BV fields is simply $\Pi \cL_{single}$.
+The full space of BV fields of the holomorphic twist is the sections of the $\Z \times \Z/2$ graded sheaf $\cL_{single}[1]$.
 
@@
 
-\subsection{Supergravity at the boundary of AdS}
-
-Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\R \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
-We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
-If we remove this locus we obtain the following manifold 
-\[
-\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
-\]
-where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.
-
-\subsection{Enhanced symmetry in a flat background}
-
-\parsec[s:e36]
-
-We recall the definition of the exceptional super Lie algebra $E(3|6)$. 
-We follow \cite{Kac_class, KacRudakov}.
-
-The even part of the super Lie algebra $E(3|6)$ is 
-\[
-\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
-\]
-The Lie bracket is determined by the obvious commutators and the action of vector fields on functions.
-
-The odd part is of the form
-\[
-\Omega^{-1/2}(\Hat{D}^3) \otimes \C^2 .
-\]
-where $\Omega^{-1/2}(\Hat{D}^3)$ is the space of formal power series sections of the bundle
-\[
-\T_{\Hat{D}^3}^{*} \otimes K_{\Hat{D}^3}^{-1/2}
-\]
-where $K_{\Hat{D}^3}^{-1/2}$ is the negative square-root of the canonical bundle on $\Hat{D}^3$. 
-We will write a general element of this module as 
-\[
-\alpha = \sum_i g^i \d z_i^{-1/2} 
-\]
-where $g^i \in \cO(\Hat{D}^3)$. 
-The action by the even part of the super Lie algebra is by Lie derivative and by the fundamental $\lie{sl}(2)$ action on $\C^2$.
-We will write $r \in \C^2$ for a vector in the fundamental representation.
-Finally, there is a bracket 
-\[
-E(3|6)_- \times E(3|6)_- \to E(3|6)_+
-\]
-defined by
-\[
-[\alpha_1 \otimes r_1, \alpha_2 \otimes r_2] = - (\alpha_1 \wedge \alpha_2) \otimes (r_1 \wedge r_2) - (\d \alpha_1 \otimes \alpha_2 + \alpha_1 \otimes \d \alpha_2) \otimes (r_1 \odot r_2) .
-\]
-%The first term in the above equation arises from the composition 
+%\subsection{Supergravity at the boundary of AdS}
+%
+%Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\R \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
+%We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
+%If we remove this locus we obtain the following manifold 
 %\[
-%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{\wedge \otimes \wedge} \Hat{\Omega}_3^{-1} \otimes \wedge^2 R \cong \fw_3 .
+%\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
 %\]
-%The second term uses the composition 
+%where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.
+%
+%
+%\subsection{Enhanced symmetry in a flat background}
+%
+%\parsec[s:e36]
+%
+%We recall the definition of the exceptional super Lie algebra $E(3|6)$. 
+%We follow \cite{Kac_class, KacRudakov}.
+%
+%The even part of the super Lie algebra $E(3|6)$ is 
 %\[
-%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{(\d \otimes \id) \otimes \odot} (\Hat{\Omega}_3^{1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes \Sym^2 (R) \cong \lie{sl}(2) \otimes \Hat{\cO}_3 .
+%\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
 %\]
-
-\brian{suca enhancement following \cite{SWsuca6d}}
-
-\parsec[s:weight]
-
-\parsec[s:locallieE510]
-
-We have recollected how the super Lie algebra $E(5|10)$ (and its central extension) decomposes as a module for the super Lie algebra $E(3|6)$. 
-We now wish to lift this to a decomposition of factorization algebras on $\C^3$, or more generally, factorization algebras on any complex three-fold $Z$.
-
-We outline an approach to constructing the factorization algebras via enveloping factorization algebras of certain (infinite rank) local Lie algebras on the three-fold $X$. 
-For another approach \brian{pointer}.
-
-We have already discussed the local Lie algebra $\cL_{sugra}$ on $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a smooth one-manifold. 
-We take $X = Z \times \C^2$ and $S = \R$. 
-and view $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ as a factorization algebra on $Z \times \C^2 \times \R$. 
-Then, we can consider the pushforward of $\Obs_{sugra}$ along the map
-\[
-\pi \colon Z \times \C^2 \times \R \to Z 
-\]
-which leads to a factorization algebra $\pi_* \Obs_{sugra}$ on the three-fold $Z$.
-
-Since $\pi$ is not a proper map (the fibers are not compact) we cannot exhibit $\pi_*\Obs_{sugra}$ as the Chevalley--Eilenberg complex of some ordinary local Lie algebra on $Z$. 
-Nevertheless we will find a pro local Lie algebra $\cL_{sugra,\pi}$ on $Z$ which is a particularly nice `small model' for this pushforward factorization algebra.
-
-A local Lie algebra enhancement for $E(3|6)$ has been given in \cite{SWsuca6d} \brian{finish}
-
-\section{Example}
-
-Consider the holomorphic local Lie algebra on $\C^n$
-\[
-\Omega^{0,\bu}(\C^n) 
-\]
-and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
-Now, we can restrict this to a factorization algebra on
-\[
-\C^n - 0 \subset \C^n
-\]
-that we denote by $\cF|_{\C^n - 0}$.
-
-Next, consider the radial projection
-\[
-r \colon \C^n - 0 \to \R .
-\]
-Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
-Nevertheless we can come up with a nice algebraic model.
-
-Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.
-
-\begin{lem}
-There is an injective map of factorization algebras on $\RR_{>0}$:
-\[
-\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
-\]
-which is dense in cohomology.
-\end{lem}
-
-This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
+%The Lie bracket is determined by the obvious commutators and the action of vector fields on functions. 
+%
+%The odd part is of the form
+%\[
+%\Omega^{-1/2}(\Hat{D}^3) \otimes \C^2 .
+%\]
+%where $\Omega^{-1/2}(\Hat{D}^3)$ is the space of formal power series sections of the bundle
+%\[
+%\T_{\Hat{D}^3}^{*} \otimes K_{\Hat{D}^3}^{-1/2}
+%\]
+%where $K_{\Hat{D}^3}^{-1/2}$ is the negative square-root of the canonical bundle on $\Hat{D}^3$. 
+%We will write a general element of this module as 
+%\[
+%\alpha = \sum_i g^i \d z_i^{-1/2} 
+%\]
+%where $g^i \in \cO(\Hat{D}^3)$. 
+%The action by the even part of the super Lie algebra is by Lie derivative and by the fundamental $\lie{sl}(2)$ action on $\C^2$.
+%We will write $r \in \C^2$ for a vector in the fundamental representation.
+%Finally, there is a bracket 
+%\[
+%E(3|6)_- \times E(3|6)_- \to E(3|6)_+
+%\]
+%defined by
+%\[
+%[\alpha_1 \otimes r_1, \alpha_2 \otimes r_2] = - (\alpha_1 \wedge \alpha_2) \otimes (r_1 \wedge r_2) - (\d \alpha_1 \otimes \alpha_2 + \alpha_1 \otimes \d \alpha_2) \otimes (r_1 \odot r_2) .
+%\]
+%%The first term in the above equation arises from the composition 
+%%\[
+%%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{\wedge \otimes \wedge} \Hat{\Omega}_3^{-1} \otimes \wedge^2 R \cong \fw_3 .
+%%\] 
+%%The second term uses the composition 
+%%\[
+%%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{(\d \otimes \id) \otimes \odot} (\Hat{\Omega}_3^{1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes \Sym^2 (R) \cong \lie{sl}(2) \otimes \Hat{\cO}_3 .
+%%\] 
+%
+%\brian{suca enhancement following \cite{SWsuca6d}}
+%
+%\parsec[s:weight]
+%
+%
+%\parsec[s:locallieE510]
+%
+%We have recollected how the super Lie algebra $E(5|10)$ (and its central extension) decomposes as a module for the super Lie algebra $E(3|6)$. 
+%We now wish to lift this to a decomposition of factorization algebras on $\C^3$, or more generally, factorization algebras on any complex three-fold $Z$. 
+%
+%We outline an approach to constructing the factorization algebras via enveloping factorization algebras of certain (infinite rank) local Lie algebras on the three-fold $X$. 
+%For another approach \brian{pointer}. 
+%
+%We have already discussed the local Lie algebra $\cL_{sugra}$ on $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a smooth one-manifold. 
+%We take $X = Z \times \C^2$ and $S = \R$. 
+%and view $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ as a factorization algebra on $Z \times \C^2 \times \R$. 
+%Then, we can consider the pushforward of $\Obs_{sugra}$ along the map
+%\[
+%\pi \colon Z \times \C^2 \times \R \to Z 
+%\]
+%which leads to a factorization algebra $\pi_* \Obs_{sugra}$ on the three-fold $Z$. 
+%
+%Since $\pi$ is not a proper map (the fibers are not compact) we cannot exhibit $\pi_*\Obs_{sugra}$ as the Chevalley--Eilenberg complex of some ordinary local Lie algebra on $Z$. 
+%Nevertheless we will find a pro local Lie algebra $\cL_{sugra,\pi}$ on $Z$ which is a particularly nice `small model' for this pushforward factorization algebra.
+%
+%A local Lie algebra enhancement for $E(3|6)$ has been given in \cite{SWsuca6d} \brian{finish}
+%
+%
+%
+%
+%
+%
+%
+%\section{Example} 
+%
+%Consider the holomorphic local Lie algebra on $\C^n$
+%\[
+%\Omega^{0,\bu}(\C^n) 
+%\]
+%and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
+%Now, we can restrict this to a factorization algebra on
+%\[
+%\C^n - 0 \subset \C^n
+%\]
+%that we denote by $\cF|_{\C^n - 0}$. 
+%
+%Next, consider the radial projection
+%\[
+%r \colon \C^n - 0 \to \R .
+%\]
+%Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
+%Nevertheless we can come up with a nice algebraic model.  
+%
+%Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.
+%
+%\begin{lem}
+%There is an injective map of factorization algebras on $\RR_{>0}$:
+%\[
+%\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
+%\]
+%which is dense in cohomology.
+%\end{lem}
+%
+%This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
 

### 2022-06-15 fivebranes/twisted.tex
updated sugra at boundary of ads

--- 2022-06-14 fivebranes/twisted.tex
@@
-\documentclass[11pt]{amsart}%
+%\documentclass[11pt]{amsart}%
 
 %\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-fivebrane}
 
-\begin{document}
+%\begin{document}
 
@@
 
+\subsection{Twisted Membranes}
+\surya{add}
+
 \subsection{Twisted Backreactions}
@@
 \[
-\R\oplus V \setminus 0\times Z
-\].
-Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation.
-That is, there is a rank 1 subbundle $\R\subset \R\oplus V$ together with a complex structure on the quotient.
+M = \R\oplus V \setminus 0\times Z.
+\]
+
+Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$.
 Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$.
@@
 Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$.
-The vertical tangent bundle of this $S^{4}$ bundle inherits a natural subbundle coming from the THF structure of the ambient manifold; the fibers of this subbundle equip
+Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$.
+The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure.
+Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
+\[
+  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
+\]
+
+The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure.
+\surya{CITE}
+
+We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by
+
+\[
+\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
+\ul{\rm even} & \ul{\rm odd} \\
+\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
+\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
+\end{tikzcd}
+ \right ) \otimes CR (S^{4}).
+\]
+
+Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure.
+Its computation is facilitated by the following lemma:
+
+\begin{lem}
+  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric.
+Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure.
+Then there is a quasi-isomorphism
+
+  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]
+
+  where the right-hand-side denotes the Dolbeault-deRham complex.
+\end{lem}
+
+The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
 

### 2022-06-15 fivebranes/fact.tex

@@
 The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
-From the data of a factorization algebra, one can recover local operators by the following formal construction.
-
+Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
 Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
 The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-
-Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures \brian{difference between limit and homotopy limit}
+Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
+For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point \cite{CG2}.
 \end{rmk}
@@
 We leave the problem to characterize the quantization to future work. 
+\brian{add discussion}
 
-\subsection{The factorization algebra associated to twisted supergravity}
-
-In this section we consider the classical factorization algebra of observables of our prototype for the holomorphic twist of eleven-dimensional supergravity.
-
-\parsec[s:sugraobs]
-
-As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
-In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
+In this section we will consider the classical factorization algebra of observables of our prototype for the minimal twist of eleven-dimensional supergravity given in \S \ref{s:twisted} which is defined on $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold.
+%In the \S \ref{s:twisted} we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
 The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
@@
 
-The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
+In terms of this local $L_\infty$ algebra, the $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset S \times X$ is 
 \[
@@
 \]
-We will denote the entire classical factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.
+We will denote the entire classical factorization algebra on $S \times X$ of classical observables by~$\Obs_{sugra}$.
 
@@
 
-\parsec[s:restricted]
+\subsection{The fivebrane decomposition}\label{s:resm5}
 
@@
 \]
-the total space of the rank two bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
-Here the holomorphic volume form
+the total space of the rank two holomorphic vector bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
+%In the remainder of this section we denote by $V \to Z$ this rank two holomorphic vector bundle. 
 One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
@@
 This grading is determined by a $\C^\times$ action on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.
-
-\parsec[s:gradingfivebrane]
 
@@
 The argument is nearly identical so we omit the details. 
-
 \end{proof}
 
-For each $n \in \ZZ$ and open set $U \subset Z$, let 
+For each $n \in \Z$ and open set $U \subset Z$, let 
 \[
@@
 \]
-defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
+defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.
 
-\begin{prop}
+\begin{lem}
+\label{lem:technical}
 For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
 \[
-\Omega^{0,\bu}(U, \cV^{(n)})
+\Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
 \]
-for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
+for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
 For each $n$, the differential is of the form $\dbar + Q^{hol}$.
-In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
-\end{prop}
+In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
+\end{lem}
 
-We explicitly describe the first homogenous weights of $\Bar{\pi}_* \cL_{sugra}$.
+\begin{proof}
+In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure.
+Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
+For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
+\[
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
+\]
+where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
+The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$.
+
+Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
+\[
+\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
+\]
+for every $U \subset Z$. 
+Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
+\[
+L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
+\]
+where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
+Then, we can further identify this with a Dolbeault complex of the form
+\[
+\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
+\]
+By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
+\[
+\Omega^{0,\bu} \left(U, L' \otimes M\right) 
+\]
+where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
+the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.
+
+With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
+%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
+\end{proof}
+
+We explicitly describe the first few homogenous eigenspaces of $\Bar{\pi}_* \cL_{sugra}$.
 
@@
 
-As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
+As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(-1)})$. 
 We will show that 
 \[
-\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
+\cV_{fivebrane}^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
 \]
@@
 
-Explicitly weight zero summand $\cV^{(0)}$ consists of:
+Explicitly weight zero summand $\cV_{fivebrane}^{(0)}$ consists of:
 \begin{itemize}
@@
 
-Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
-When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
-In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
+Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
+When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
+%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
 
-As a holomorphic vector bundle, we will see that $\cV^{(0)}$ is 
+As a holomorphic vector bundle, we will see that $\cV_{fivebrane}^{(0)}$ is 
 \[
-\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\cV_{fivebrane}^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
 \]
@@
 
-The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV^{(0)})$. 
+The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$. 
 The differential is simply $\dbar$. 
-The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
+The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV_{fivebrane}^{(0)}$ which we can describe as follows:
 \begin{itemize}
@@
 \[
-[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right).
+[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right) 
 \]
+\brian{finish}
 \end{itemize}
@@
 
-Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
+Since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
 \[
-U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
+U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
 \]
-has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.
+has the structure of a factorization algebra on the three-fold $Z$. 
+We denote this factorization algebra by $\Bar{\pi}_* \Obs_{sugra}$.
 
-\begin{prop}
-Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
-There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
-\begin{itemize}
-\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
-\[
-\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
-\]
-which is dense at the level of cohomology. 
-\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
-\beqn\label{eqn:decomp3}
-\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
-\eeqn
-\item[(3)]
-In weight zero, there is an equivalence of local Lie algebras on $Z$ 
-\[
-\cV_0 \simeq \cE(3|6)|Z 
-\]
-where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
-\end{itemize}
-\end{prop}
+%\begin{prop}
+%Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
+%There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
+%\begin{itemize}
+%\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
+%\[
+%\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
+%\]
+%which is dense at the level of cohomology. 
+%\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
+%\beqn\label{eqn:decomp3}
+%\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
+%\eeqn
+%\item[(3)]
+%In weight zero, there is an equivalence of local Lie algebras on $Z$ 
+%\[
+%\cV_0 \simeq \cE(3|6)|Z 
+%\]
+%where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
+%\end{itemize}
+%\end{prop}
 
@@
 
+\subsection{The membrane decomposition}
+
+We briefly go through an analogous decomposition for membranes. 
+For this, we fix a Riemann surface $C$ and consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
+\[
+X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
+\]
+the total space of the rank four bundle $K_C^{1/4} \otimes \C^2$ over $C$.
+Denote by 
+\[
+\pi \colon V \to \R \times C
+\] 
+the pullback of this vector bundle along the projection $\R \times C \to C$.
+We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
+In this description, the twisted membranes will be supported along the zero section of $V$. 
+The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.
+
+As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
+Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+This grading is determined by a (different) $\C^\times$ action on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$ which we now describe.
+
+In a local THF chart $U \subset \R \times C$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;z,w)$ where $(t;z) \in U \subset\R \times C$ is THF coordinate and $w=(w_1,w_2,w_3,w_4)$ is the holomorphic fiber coordinate of the rank four bundle $V$.
+
+%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
+%\[
+%0 \times 0 \times \C^3 \subset \C^5 .
+%\]
+%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
+%
+%\parsec[s:flatdecomp]
+%
+%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
+%%\[
+%%\C^3 \times (\R \times \C^2 - 0) .
+%%\]
+%%
+%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
+%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
+%
+%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
+%
+%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
+%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
+%\[
+%\pi_* \Obs_{sugra} 
+%\]
+%on $\C^3$.
+%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
+%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+
+With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
+\begin{itemize}
+\item On the fields $\mu(t;w,z)$ the action is
+\[
+\lambda \cdot \mu(t;z,w) = \mu(t; z , \lambda w).
+\]
+\item On the fields $\nu(t;w,z)$ the action is
+\[
+\lambda \cdot \nu(t;z,w) = \nu(t;z ,\lambda w).
+\]
+\item On the fields $\beta(t;w,z)$ the action is
+\[
+\lambda \cdot \beta(t;z,w) = \lambda^{-1} \beta(t; z, \lambda w).
+\]
+\item On the fields $\gamma(t;w,z)$ the action is
+\[
+\lambda \cdot \gamma(t;z,w) = \lambda^{-1} \gamma(t; z ,\lambda w).
+\]
+\end{itemize}
+
+\begin{prop}
+The $L_\infty$ structure on $\pi_* \cL_{sugra}$ is equivariant for this $\C^\times$ action. 
+%The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
+\end{prop}
+
+As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\pi_* \cL_{sugra}$ into eigenspaces. 
+Similarly to the proof of Lemma \ref{lem:technical} one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
+\[
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV_{membrane}^{(n)}\right)
+\]
+where $\cV^{(n)}_{membrane}$ is a holomorphic super vector bundle on $C$.
+
+We will state explicit descriptions of the first few eigenspaces without details of the proof. 
+The first nontrivial eigenspace is, as in the fivebrane case, $n=-1$. 
+Here, one can see that 
+\[
+\cV^{(-1)}_{membrane} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
+\]
+For $n=0$ one has 
+\[
+\cV^{(0)}_{membrane} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
+\]
 \subsection{Koszul duality for factorization algebras: an ansatz}

### 2022-06-15 fivebranes/twisted.tex

--- 2022-06-14 fivebranes/twisted.tex
@@
 \]
-The full space of BV fields of the holomorphic twist is the sections of the $\Z \times \Z/2$ graded sheaf $\cL_{single}[1]$.
 
@@
 
-The theory in the backreacted geometry will be defineed to be a deformation of the 11d theory placed on the complement of the zero section.
-The complement of the zero section admits additional structures inherited from the obvious THF structure on $\R \times X$.
-Note that $\R\oplus V$ has an obvious rank 1 subbundle together with a complex structure on the quotient.
+We begin by describing the complement of the zero section
+\[
+M = \R\oplus V \setminus 0\times Z.
+\]
+
+Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$.
 Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$.
@@
 \end{align*}
-Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The fiber spheres have a canonical foliation
+Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$.
+Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$.
+The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure.
+Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
+\[
+  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
+\]
+
+The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure.
+\surya{CITE}
+
+We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by
+
+\[
+\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
+\ul{\rm even} & \ul{\rm odd} \\
+\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
+\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
+\end{tikzcd}
+ \right ) \otimes CR (S^{4}).
+\]
+
+Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure.
+Its computation is facilitated by the following lemma:
+
+\begin{lem}
+  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric.
+Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure.
+Then there is a quasi-isomorphism
+
+  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]
+
+  where the right-hand-side denotes the Dolbeault-deRham complex.
+\end{lem}
+
+The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
 

### 2022-06-15 fivebranes/twisted.tex
boundary

@@
-%\documentclass[11pt]{amsart}%
+\documentclass[11pt]{amsart}%
 
 %\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
+\usepackage{macros-fivebrane}
+\newcommand{\thfd}{\Bar{D}}
+\newcommand{\thfdel}{D}
 
-%\begin{document}
+\begin{document}
 
@@
 
-  \item Deform the theory on the complement of the zero section by a certain maurer-cartan element. The Maurer-Cartan element is thought of as the flux sourced by branes wrapping the zero section.
+  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element. 
+  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
 
-  \item The complement of the zero section is a manifold with boundary - we impose a natural boundary condition.
+  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.
 
@@
 
-\parsec
+\parsec[s:brfive]
 
-As above, let $Z$ be a three-fold, $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = {\rm Tot}V$.
-The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold - in the main body of the paper we will restrict ourselves to $V = K_{Z}^{1/2}\otimes \C^{2}$.
-We will view $\R\times X = {\rm Tot}(\R\oplus V)$, and consider a stack of N fivebranes wrapping the zero section in $\R\oplus V$.
+We first consider the situation of backreacting some number of (twisted) fivebrans.
+Let $Z$ be a three-fold that the fivebranes wrap. 
+Let $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
+The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 
+The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
 
-We begin by describing the complement of the zero section
+We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus V$.
+Denote the complement of the zero section by
 \[
-M = \R\oplus V \setminus 0\times Z.
+M_V = \text{Tot}(\R\oplus V) - 0(Z).
 \]
+Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
+The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
 
-Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$.
-Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$.
-Explicitly, the corresponding norm is given by
+A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$. 
+We will say that $F$ equips $M$ with the a THF structure. 
+%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
+The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection. 
+Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
+The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s. 
+(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
+
+Any submanifold of a THF manifold is itself a THF manifold. 
+We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
+
+We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology. 
+Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex 
+\beqn\label{eqn:drdol}
+\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
+\eeqn
+As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
+More generally, there is a natural cohomology associated to a THF structure.
+Suppose $(M,F)$ is a THF structure and 
+denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
+For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$. 
+The derivative along the leaves of the foliation defined by $V$ defines a map 
+\[
+\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
+\]
+By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$. 
+Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$. 
+There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$. 
+The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows 
+\[
+\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right) 
+\]
+with the structure of a bigraded commutative dg algebra.
+This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes. 
+For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra 
+\beqn\label{thfcoh1}
+\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
+\eeqn
+We leave the $\thfd$ operator implicit in the presentation on the right hand side.
+When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
+There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
+
+%Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
+With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes. 
+We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus V$ over $Z$ and a fiberwise partially hermitian metric. 
+Explicitly, the corresponding norm defines a map
 \begin{align*}
- \pi:  \R\times X & \to \R_{+} \\
+ h \colon  \R\times X & \to \R_{+} \\
   (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
 \end{align*}
-Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$.
-Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$.
-The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure.
-Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
+Letting $\pi \colon \R\times X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle 
+\[
+p \define (h,\pi) \colon \R \times X \to \R_{+}\times Z 
+\] 
+which restricts to an $S^4$ bundle $p|M \colon M \to \R_{>0} \times Z$.
+These embeddings and projections fit inside of the following commutative diagram
+\[
+\begin{tikzcd} 
+M \ar[d,"p|M"'] \ar[r,hook] & \R \times X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
+\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
+\end{tikzcd}
+\]
+The inclusions on the left are the natural embeddings. 
+The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = \R \times X$ and the bottom right inclusion is the embedding at radius $r = 0$.
+
+As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$. 
+Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|M$.
+The resulting sheaf of $L_\infty$ algebras $(p|M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
+
+The theory on $M$ extends to a theory on the manifold obtained by filling in the zero section of $\R \times V$; in other words, we know that the theory is defined on the entire space $\R \times X$.
+This means that there is a natural way to extend the theory on $\R_{>0} \times Z$ to the seven-manifold with boundary $\R_{+} \times Z$. 
+The restriction of this theory to the six-dimensional boundary plays the most important role for us.
+
+\brian{trying to incorporate below}
+%To do this we will make use of the natural foliated geometric structures which we have around.
+
+Let $V_{M}$ denote the vertical tangent bundle to $(h, \pi)$, which we view as a subbundle of the real tangent bundle $T_{M}$. 
+The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, if $\iota \colon M \to \R\times X$ is inclusion, then we consider the pair
 \[
@@
 
-We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by
+ The underlying sheaf of cochain complexes is given by
 

### 2022-06-15 fivebranes/twisted.tex
states

@@
 
+\parsec[s:twistedsugra]
+
+In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze `twisted $M$ theory'. 
+This theory is obtained from \brian{finish}
+
 \subsection{Twisted fivebranes}
@@
 \end{itemize}
+
+\parsec[s:brkevin]
+
+As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface, with some number of twisted `fivebranes' wrapping
+\[
+0 \times 0 \times C \subset \R \times \C \times C .
+\]
+It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
+Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
+We proceed to describe the twisted version of states at the boundary of this version of $AdS$. 
+We first proceed before turning on the backreaction.
+
+If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection ${\rm Tot}(\R \oplus K_C) \to \R_+ \times C$ which combines the fiberwise norm with the natural bundle projection.
+Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate. 
+The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
+
+Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
+We will elaborate on the appearance of this sort of cohomology momentarily.
+The theory admits a natural `vacuum' boundary condition at $r=0$.
+In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.
+
+The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point. 
+The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$. 
+Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.
+
+Modifications of the boundary condition at the point $z = 0$ on the boundary take the form
+\[
+\alpha = f(w) \delta^{(r)}_{z=0} 
+\]
+where $f$ is some holomorphic function. 
+Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
+It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
+\[
+\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
+\]
+
+\brian{finish}
 

### 2022-06-16 fivebranes/twisted.tex
lag

@@
 
-As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface, with some number of twisted `fivebranes' wrapping
+As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping
 \[
@@
 It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
+Denote by $(t,w)$ the fiber coordinates.
 Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
@@
 
-Modifications of the boundary condition at the point $z = 0$ on the boundary take the form
+Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
 \[
@@
 
+The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
+The phase space at the boundary $C$ can be identified with the following cohomology
+\[
+\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
+\]
+where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation. 
+We refer to the section below for a reminder on this geometric structure.
+
+The phase space is equipped with a natural symplectic form given by
+\[
+\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
+\]
+There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C \setminus 0$ which extends to zero.
+The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
+
 \brian{finish}
@@
 
-We first consider the situation of backreacting some number of (twisted) fivebrans.
+We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
 Let $Z$ be a three-fold that the fivebranes wrap. 
-Let $V\to Z$ a rank 2 holomorphic vector bundle such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
+We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
 The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 

### 2022-06-16 fivebranes/index.tex
cleaned up

@@
 Unlike the analysis above, we will the twisted holography proposal to compute this character.
-
-Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}.
-Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$.
-Consider a stack of $N$ fivebranes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection.
-The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$
-
-The twisted holography proposal asserts that the factorization algebra of local observables $\Obs_{M5}$ of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the Koszul dual $(\pi_{*} C^{\bullet}(\cL))^{!}$.
-
-Since quantities like indices are deformation invariant, we need not consider such deformations for now.
-In fact in this section we may, and will, replace the local Lie algebra $\cL$ with the abelian local dg Lie algebra which underlies the free limit of the twisted supergravity theory.
-Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes
-\[
-\begin{tikzcd}
-  &  \ul{\rm even} & \ul{\rm odd} \\
- \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{\C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
- \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
-& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
-.\]
-
-\parsec
-
-%Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
-%The $\mu$-field decomposes into vector field components which point along and transverse to the brane
-%\[
-%\mu
-%\]
-%
-%is the sheaf of $\Z/2$-graded cochain complexes
-%\[
-%\begin{tikzcd}
-%  &  \ul{\rm even} & \ul{\rm odd} \\
-% \mu|_{w=t=0} \in & \PV^{1,\bullet}_{\C^{3}} \ar[r, "\del_{\Omega}"] & \PV^{0,\bullet}_{\C^{3}}\\
-% \gamma|_{w=t=0} \in & \Omega^{0,\bullet}_{\C^{3}} \ar[r, "\del"]
-%& \Omega^{1,\bullet}_{\C^{3}}\end{tikzcd}
-%.\]
-
-We wish to count local operators, which are given by the costalk at $0\in \C^{3}$ of $\Obs_{M5}$.
-Let us first describe $\Obs_{M5}$ more explicitly.
-By the Poincare and $\dbar$ Poincare lemmas, we have quasi-isomorphisms for each $U\subset \C^{3}$ open
-\[
-\Obs_{M5}(U) = \Sym \left( \begin{tikzcd}  \end{tikzcd} \right)
-\]
-
-The local observables are given by $\lim _{U\ni 0} \Obs_{M5}(U)$.
-
-We first introduce the following notation for representatives of classes in compactly supported Dolbeault cohomology.
-We write $\delta^{(a,b,c)}$ to denote the derivative of the delta function $\del_{z_{1}}^{a}\del_{z_{2}}^{b}\del_{z_{3}}^{c}\delta_{t=w_{a}=0}$.
-
-\begin{lem}
-  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0)\right )=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
-  \begin{itemize}
-    \item $V_{\gamma}$ is spanned by
-          \begin{align}
-            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
-            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
-             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
-            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
-            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
-          \end{align}
-
-          where $a, b, c, k, l \geq 0$.
-    \item $V_{\mu}$ is spanned by
-          \begin{align}
-            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{1}},\
-             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l-1}\del_{z_{1}}\text{ where }a > 0, b,c,k,l \geq 0 \\
-            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,b-1,c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{2}}, \ \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(0,b-1,c)}w_{1}^{k}w_{2}^{l-1}\del_{z_{2}}\text{ where }b > 0,c,k,l \geq 0 \\
-            & \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,0,c-1)}w_{1}^{k-1}w_{2}^{l}\del_{z_{3}}, \ \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-l\delta^{(0,0,c-1)}w_{1}^{k}w_{2}^{l-1}\del_{z_{3}}\text{ where } c > 0,k,l \geq 0 \\
-            & \delta^{(0,0,0)}w_{2}^{l}\del_{w_1}, \ \delta^{(0,0,0)}w_{1}^{k}\del_{w_2}\text{ where }k,l \geq 0
-          \end{align}
-  \end{itemize}
-\end{lem}
-\begin{proof}
-  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and holomorphic form degree.
-The $E_{1}$ page is the $d+\dbar$ cohomology and is given by the symmetric algebra on
-
-  \[
-\begin{tikzcd}
-\ul{\rm even} & \ul{\rm odd} \\
-H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}})) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) )\\
-H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3},  \iota^{*}T^{*}_{\C^{5}}))& H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO)) \ar[l, "\del"]
-\end{tikzcd}
-.\]
-
-\surya{...}
-
-\end{proof}
-
-\parsec
-
 We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra

### 2022-06-29 fivebranes/fact.tex
all around

@@
 
-The observables of any theory in the BV formalism enhance to the structure of a factorization algebra on spacetime \cite{CG2}. 
-Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of classical observables assigns the cochain complex
+The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
+Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
 \[
@@
 
-\begin{rmk}
-The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
-Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
-Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
-The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
-Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
-For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point \cite{CG2}.
-\end{rmk}
+At the quantum level the factorization algebra of classical observables is deformed.
+Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
+Even in perturbation theory, the full quantum behavior of the holomorphic-topological eleven-dimensional theory is an open question. 
+We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.
 
-At the quantum level this Chevellay--Eilenberg complex is deformed.
-The BV formalism ...
-Even in perturbation theory the full quantum behavior of the holomorphical-topological eleven-dimensional theory is an open question. 
-We leave the problem to characterize the quantization to future work. 
-\brian{add discussion}
-
-In this section we will consider the classical factorization algebra of observables of our prototype for the minimal twist of eleven-dimensional supergravity given in \S \ref{s:twisted} which is defined on $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold.
+In this section we focus on the factorization algebra of classical observables of our prototype for the minimal twist of eleven-dimensional supergravity which we recalled in \S \ref{s:twisted}. 
+This model is defined on any eleven-manifold $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
 %In the \S \ref{s:twisted} we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
@@
 
-\subsection{The fivebrane decomposition}\label{s:resm5}
+\subsection{The fivebrane decomposition of twisted supergravity}\label{s:resm5}
 
@@
 This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
-Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
-This grading is determined by a $\C^\times$ action on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.
+Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such. 
+This grading is determined by looking at an eigenspace decomposition of a certain compact abelian group acting on the fields of the eleven-dimensional theory on $\R \times X_Z$ which we now describe.
 
+One of the primary features of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is that it is of the form $\clie^\bu(\cG)$ where $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of a pro vector bundle.
+To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler construction related to branes in five-dimensional Chern--Simons theory.
+
+\parsec[]
+
+As we recalled in~\S \ref{??}, Costello's five-dimensional Chern--Simons theory is the result of applying the $\Omega$-background to $M$ theory on a Taub--NUT space.
+In this setting, fivebranes which hit the tip of the Taub--NUT become chiral defects supported along a Riemann surface $C$ in the five-manifold. 
+In analogy with the situation above, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the fivebranes wrapping the zero section.
+Denote by $\Obs_{CS}$ the observables of five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
+Let $\pi \colon \R \times {\rm Tot}(K_C) \to C$ be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.
+
+Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
+Using this we can look at the subfactorization algebra 
+\beqn\label{eqn:taylor1a}
+\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
+\eeqn
+which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.
+
+For the rank one abelian gauge group, the space of fields of non-commutative Chern--Simons theory on $\R \times {\rm Tot}(K_C)$ is
+\[
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
+\]
+The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
+%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
+For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
+\[
+(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
+\]
+where $p \colon K_C \to C$.
+If, moreover, $U$ is a trivializing cover then
+\[
+(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
+\]
+On the other hand, we have
+\[
+(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
+\]
+Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
+Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO^{hol}(\C) \to \C[[w]]$.
+
+\parsec[]
+
+Let us return to the situation of a three-fold $Z$ in the eleven-manifold $\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
+The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory.
+
+This time we consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
+Using this we can define the subfactorization algebra 
+\beqn\label{eqn:taylor1b}
+\Bar{\pi}_* \Obs_{sugra} \subset \pi_* \Obs_{sugra}
+\eeqn
+which to an open set~$U \subset Z$ assigns the subcomplex of observables in~$\Obs_{sugra} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1) \times U(1)$ action.
+
+By construction, the restricted factorization algebra is of the form
+\[
+\pi_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
+\]
+where $\cG_Z$ is an infinite-rank local $L_\infty$ algebra on $Z$. 
+Just as in the case of five-dimensional Chern--Simons theory, the embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
+\[
+\pi_* \cL_{sugra} \to \cG_Z .
+\]
+
+\parsec[s:cstarfive]
+
+We now consider a particular decomposition of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$. 
 In a local chart $U \subset Z$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;w,z)$ where $t \in \R$ is the real coordinate, $w=(w_1,w_2)$ is the holomorphic fiber coordinate of the rank two bundle $X_Z$ over $Z$, and $z = (z_1,z_2,z_3)$ is a local holomorphic coordinate for $U \subset Z$.
@@
 
-The main result of this section is the following.
+The following proposition summarizes that this $\C^\times$-action is compatible with the $L_\infty$ structure on $\cL_{sugra}$.
 
@@
 
+We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
+Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
 For each $n \in \Z$ and open set $U \subset Z$, let 
 \[
-\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
+\cG_Z(U)^{(n)}\subset \cG_Z(U)
 \]
 be the weight $n$ eigenspace with respect to this $\C^\times$ action.
+As a corollary of the proposition, we get a product decomposition 
+\[
+\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
+\]
+In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
+Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.
+
+We turn to explicitly describing the first few homogenous $\C^\times$-weights of~$\cG_Z$.
+
 %The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
-Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
-\[
-(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
-\]
-is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
-In this way, the assignment 
-\[
-\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
-\]
-defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.
+%Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
+%\[
+%\cG_Z (U)  \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+%\]
+%is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
+%In this way, the assignment 
+%\[
+%\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
+%\]
+%defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.
 
-\begin{lem}
-\label{lem:technical}
-For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
-\[
-\Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
-\]
-for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
-For each $n$, the differential is of the form $\dbar + Q^{hol}$.
-In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
-\end{lem}
-
-\begin{proof}
-In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure.
-Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
-For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
-\[
-\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
-\]
-where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
-The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$.
-
-Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
-\[
-\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
-\]
-for every $U \subset Z$. 
-Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
-\[
-L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
-\]
-where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
-Then, we can further identify this with a Dolbeault complex of the form
-\[
-\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
-\]
-By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
-\[
-\Omega^{0,\bu} \left(U, L' \otimes M\right) 
-\]
-where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
-the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.
-
-With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
-%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
-\end{proof}
-
-We explicitly describe the first few homogenous eigenspaces of $\Bar{\pi}_* \cL_{sugra}$.
+%\begin{lem}
+%\label{lem:technical}
+%For each $n$, $\cG
+%\[
+%U \mapsto \Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
+%\]
+%for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
+%For each $n$, the differential is of the form $\dbar + Q^{hol}$.
+%In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
+%\end{lem}
+%
+%\begin{proof}
+%In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure.
+%Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
+%For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
+%\[
+%\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
+%\]
+%where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
+%The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$. 
+%
+%Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
+%\[
+%\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
+%\]
+%for every $U \subset Z$. 
+%Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
+%\[
+%L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
+%\]
+%where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
+%Then, we can further identify this with a Dolbeault complex of the form
+%\[
+%\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
+%\]
+%By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
+%\[
+%\Omega^{0,\bu} \left(U, L' \otimes M\right) 
+%\]
+%where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
+%the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.
+%
+%With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
+%%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
+%\end{proof}
 
@@
 
-As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(-1)})$. 
+The first non trivial case is the weight $(-1)$ piece $\cG_Z^{(-1)}$.
 We will show that
+$\cG_Z^{(-1)}$ is equivalent as an abelian local Lie algebra to one of the form $\Omega^{0,\bu}(Z, \cV^{(-1)})$ where $\cV^{(-1)}$ is the holomorphic vector bundle
 \[
-\cV_{fivebrane}^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
+\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z .
 \]
-whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
+The Dolbeault forms are equipped with the natural $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
 
-Explicitly weight zero summand $\cV_{fivebrane}^{(0)}$ consists of:
+Explicitly weight $(-1)$ summand $\cV^{(-1)}$ consists of:
 \begin{itemize}
 \item 
-Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
+Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $Z$.
 Notice that these vector fields are automatically divergence-free.
@@
 
-Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
+Particularly important for us will be the weight zero summand $\cG_Z^{(0)}$.
+Again, as a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
 When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
@@
 
-As a holomorphic vector bundle, we will see that $\cV_{fivebrane}^{(0)}$ is 
+The holomorphic vector bundle $\cV^{(0)}$ is 
 \[
-\cV_{fivebrane}^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
 \]
-The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.
+The local $L_\infty$ structure of $\cL_{sugra}$ endows the Dolbeault complex of this holomorphic vector bundle with a local Lie algebra structure.
+The differential turns out to be the natural $\dbar$ operator.
+We describe the bracket below.
 
-Explicitly, we enumerate all weight zero holomorphic sections:
+Explicitly, we enumerate all holomorphic sections of $\cV^{(0)}$:
 \begin{itemize}
@@
 The condition that $\mu$ be divergence-free implies that $(A^{ab}) \in \lie{sl}(2)$.
-We will identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
+We identify the first such vector fields with sections of $\T_Z$ and the second such vector fields with sections of $\lie{sl}(2) \otimes \cO_Z$. 
 \item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
@@
 \[
-\Gamma^{hol}(Z, K^{-1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}) 
+\Gamma^{hol}(Z, K^{-1/2}\otimes \C^2) \xto{D} \Pi \Gamma^{hol}(Z, K^{-1/2} \otimes \C^2) \oplus \Pi\Omega^{1,hol}(Z, K^{-1/2}\otimes \C^2) 
 \]
 which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
-This $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2})$. 
+This $\Z/2$ graded complex of sheaves is equivalent to $\Pi\Omega^{1,hol}(Z, K^{-1/2}\otimes \C^2)$. 
 \end{itemize}
 
-The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$. 
-The differential is simply $\dbar$. 
-The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV_{fivebrane}^{(0)}$ which we can describe as follows:
+The Lie bracket on $\cG_Z^{(0)}$ is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
 \begin{itemize}
@@
 given in coordinates by
-\[
-[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right) 
-\]
-\brian{finish}
+\begin{multline}
+[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
+\end{multline}
+The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
 \end{itemize}
 
-\parsec[s:mainfact]
-
-Since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
-\[
-U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
-\]
-has the structure of a factorization algebra on the three-fold $Z$. 
-We denote this factorization algebra by $\Bar{\pi}_* \Obs_{sugra}$.
+%\parsec[s:mainfact]
+%
+%Since $\cG_Z$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
+%\[
+%U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
+%\]
+%has the structure of a factorization algebra on the three-fold $Z$. 
+%We denote this factorization algebra on $Z$ by $\Obs_{sugra}|_Z$.
 
@@
 
-We briefly go through an analogous decomposition for membranes. 
-For this, we fix a Riemann surface $C$ and consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
+We briefly highlight an analogous construction of the restricted factorization algebra which is natural from the point of view of membranes.
+Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.
+
+We consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
 \[
@@
 \]
-the total space of the rank four bundle $K_C^{1/4} \otimes \C^2$ over $C$.
+the total space of the rank four bundle $K_C^{1/4} \otimes \C^4$ over $C$.
 Denote by 
@@
 As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
-Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
-This grading is determined by a (different) $\C^\times$ action on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$ which we now describe.
+Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such.
+
+To construct this factorization algebra we consider the action of the compact torus $U(1)^{\times 4}$ which rotates the fibers of the bundle $K_C^{1/4} \otimes \C^4$.
+We let $\Bar{\pi}_* \Obs_{sugra}$ be the factorization algebra on $\R \times C$ consisting of observables which are finite sums of integral eigenvectors for this group action.
+Again, we find that $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG_{\R \times C})$ for some $\infty$ sheaf of $L_\infty$ algebras $\cG_{\R \times C}$ on $\R \times C$ which is the sections of a pro vector bundle.
+
+Analogous to the decomposition determined by the $\C^\times$ action considered in \ref{s:cstarfive}, there is a decomposition of $\cG_{\R \times C}$ determined by a (different) $\C^\times$ acting on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$.
 
@@
 \[
-\lambda \cdot \beta(t;z,w) = \lambda^{-1} \beta(t; z, \lambda w).
+\lambda \cdot \beta(t;z,w) = \lambda^{-2} \beta(t; z, \lambda w).
 \]
@@
 \[
-\lambda \cdot \gamma(t;z,w) = \lambda^{-1} \gamma(t; z ,\lambda w).
+\lambda \cdot \gamma(t;z,w) = \lambda^{-2} \gamma(t; z ,\lambda w).
 \]
@@
 \begin{prop}
-The $L_\infty$ structure on $\pi_* \cL_{sugra}$ is equivariant for this $\C^\times$ action. 
+The $L_\infty$ structure on $\cL_{sugra}$ is equivariant for this $\C^\times$ action. 
 %The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
@@
 
-As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\pi_* \cL_{sugra}$ into eigenspaces. 
+As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
 Similarly to the proof of Lemma \ref{lem:technical} one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
 \[
-\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV_{membrane}^{(n)}\right)
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
 \]
-where $\cV^{(n)}_{membrane}$ is a holomorphic super vector bundle on $C$.
+where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.
 
@@
 \[
-\cV^{(-1)}_{membrane} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
+\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
 \]
@@
 \[
-\cV^{(0)}_{membrane} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
+\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
 \]
+
 \subsection{Koszul duality for factorization algebras: an ansatz}
@@
 \begin{prop}
-Let $\lie{g}$ be a Lie algebra and equip the associative dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological Lie map $0 \to \lie{g}$.
+Let $\lie{g}$ be a Lie algebra and equip the associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
 The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
@@
 There are many things lacking in this definition. 
-First off we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
+First, we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
 Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
@@
 
-With an eye towards couplings, we do point out a universality that is satisfied by $!$-duality. 
+\parsec[s:noether]
+
+While we don't prove that the factorization algebra $\clie^\bu(\cL)^!$ satisfies any sort of categorical duality, we point out a universality that is satisfied with reference to couplings.
 In \cite[Chapter ??]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
@@
 \begin{itemize}
-\item $\Obs$ is the factorization algebra of classical observables of a theory in the BV formalism on a manifold $M$.
-\item $\cG$ is a local Lie algebra on $M$ which acs on the theory by local symmetries. 
+\item $\cB$ is the factorization algebra on spacetime $M$ of classical observables for some auxiliary theory in the BV formalism.
+\item $\cL$ is a local Lie algebra on $M$ which acts on the theory by local symmetries. 
 \end{itemize}
@@
 \[
-\clie_\bu(\cG_c) \to \Obs .
+\clie_\bu(\cL_c) \to \cB .
 \]
 
-We arrive at $!$-duality in our situation above in the case that $\Obs$ is a factorization algebra of the form $\clie^\bu(\cL)$ where $\cL$ is another local $L_\infty$ algebra on $M$. 
-This is always possible in the BV formalism: on an open set $U$ the space of Maurer--Cartan elements in the $L_\infty$ algebra $\cL(U)$ is the space of solutions to the equations of motion on $U$.
-Thus, tautologically, the local Lie algebra $\cL$ is a symmetry of the classical theory.
+In our context, we imagine that the local Lie algebra $\cL$ describes a theory in the BV formalism.
+The factorization algebra of classical observables is $\Obs = \clie^\bu(\cL)$. 
+A natural way to couple the factorization algebras $\Obs$ and $\cB$ is to ask that $\cL$ act on $\cB$ as above.
+Then, this result produces a map of factorization algebras $\Obs^! \to \cB$.
+In this sense, $\Obs^!$ is the universal factorization algebra which couples to $\Obs$.
+
+\subsection{Summary}
 

### 2022-06-29 fivebranes/index.tex
all around

--- 2022-06-06 fivebranes/index.tex
@@
 
-\subsection{Local operators in a holomorphic-topological theory}
+\subsection{Counting supergravity states}
 
@@
 
-%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
-%Let $\cV$ denote its sheaf of holomorphic sections.
-%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
-%\[
-%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
-%\]
-%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
-%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
-%
-%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
-%\begin{itemize}
-%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
-%\[
-%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
-%\]
-%\end{itemize}
-%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
-%
-%\parsec
-In part, the data of a holomorphic-topological theory in the BV formalism is prescribed by a holomorphic-topological local $L_\infty$ algebra $\cL$.
-Without loss of generality we will assume our holomorphic-topological local $L_\infty$ algebra on $M \times X$ is of the form
-\beqn\label{eqn:cL}
-\cL = \Omega^\bu (M) \hotimes \Omega^{0,\bu}(X, L) 
-\eeqn
-where $L$ is a graded holomorphic vector bundle on $X$.
-The differential is required to be of the form
-\[
-\d_{dR} + \dbar + Q^{hol}
-\]
-where $\d_{dR}$ is the de Rham differential acting on $M$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon L \to L[1]$ is a holomorphic differential operator of cohomological degree $+1$.
-The higher $L_\infty$ structure maps of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators. 
-For more details we refer to the definitions in \cite{GRWthf}.
-
-In this situation, the factorization algebra of classical observables supported on an open set $U \subset M \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
-We will give a concise presentation for the {\em local} operators in a topological-holomorphic theory.
-
-Suppose that $M \times X = \R^m \times \C^n$ and suppose that the bundle $L \to \C^n$ is translation invariant with fiber $L_0$ over $0 \in \R^m \times \C^n$.
-We also assume that all structure maps of the $L_\infty$ algebra are translation invariant.
-The jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras
-\[
-\cL(\C^n \times \R^m) \to L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
-\]
-The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
-Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
-\[
-L_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} L_0 [[z_j]] 
-\]
-which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
-The only remaining differential on the right hand side is~$Q^{hol}$. 
-In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of $L_\infty$ algebras $\cL(\R^m \times \C^n) \to L_0[[z_j]]$.
-
-\begin{lem}
-\label{lem:localops}
-Suppose that $\cL$ is a holomorphic-topological local Lie algebra on $\R^m \times \C^n$ and consider the factorization algebra $\Obs = \clie^\bu (\cL)$. 
-Then, the Taylor expansion map
-\[
-\cL(\C^n \times \R^m) \to L_0[[z_0,\ldots,z_n]]
-\]
-induces a quasi-isomorphism of commutative dg algebras
-\[
-\Obs(0) \simeq \clie^\bu \left( L_0[[z_1,\ldots,z_n]] \right) .
-\]
-Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
-\[
-\Obs(0) \simeq \cO \left( L_0[[z_1,\ldots,z_n]][1] \right) 
-\]
-where the right hand side is equipped with the differential $Q^{hol}$. 
-\end{lem}
-
-We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
-if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
-The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.
-
 \parsec[s:pexp]
@@
 \brian{characters, plethystic, etc.}
-
-\parsec[s:localops]
-
-We present some simple examples.
-
-Suppose that $L$ is the trivial bundle on $\C^n$ and consider the abelian holomorphic-topological local Lie algebra 
-\[
-\Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) [-1]
-\]
-where the differential is just $\d_{dR} + \dbar$. 
-Notice that with the shift, functions on $\R^m \times \C^n$ are in cohomological degree $+1$.
-Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
-\[
-\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
-\]
-Via the $n$-dimensional residue one can identify the algebra of local operators with 
-\[
-\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
-\]
-
-Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
-\[
-\frac{1}{(1-q_1)\cdots (1-q_n)} .
-\]
 

### 2022-06-29 fivebranes/kr.tex
removed preambles in included files, formatting
all around

@@
 
-In \cite{KacRudakov} an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
-We first split the coordinates on the formal five-disk as
-\[
-(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
-\]
-In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.
+A result of \cite{RSW} relates the global sections of the $L_\infty$ algebra $\cL_{sugra}$ describing the minimal twist of eleven-dimensional supergravity on $\R \times \C^5$ with a central ($L_\infty$) extension of the exceptional super Lie algebra $E(5|10)$.
+From the point of view of (twisted) extended objects in $M$ theory like membranes and fivebranes there are two very important subalgebras of $E(5|10)$: the exceptional super Lie algebras $E(1|6)$ and $E(3|6)$.
+
+The exceptional super Lie algebras $E(1|6)$ and $E(3|6)$ play the role of infinite-dimensional `enhanced' superconformal algebras---we expect that they act on the holomorphic twist of any superconformal field theory in dimensions three and six, respectively.
+From the point of view of $M$ theory these super Lie algebras act as symmetries of supergravity backgrounds which are twisted analogs of $AdS_4 \times S^7$ and $AdS_7 \times S^4$, respectively---these arise from backreacting, in flat space, some number of twisted membranes and fivebranes, respectively.
+
+In \cite{KR1}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
+In this section we compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR1}.
+
+Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
+Following the description of these irreducible modules given in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.
+
+There is a different decomposition of $E(5|10)$ (and its central extension) which has as its weight zero piece the subalgebra $E(1|6)$; this decomposition is natural from the point of view of membranes.
+
+%an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
+%We first split the coordinates on the formal five-disk as
+%\[
+%(z_i ; w_a) \in \Hat{D}^3 \times \Hat{D}^2 .
+%\]
+%In the fivebrane picture, the coordinates $z_i$ parameterize the holomorphic directions along the brane and the coordinates $w_a$ are the holomorphic coordinates transverse to the brane.
+
+\subsection{The fivebrane decomposition of $E(5|10)$}
+
+%Following the prescription of twisted holography our ansatz for
+
+We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR1}.
+In \S \ref{s:m5localops} we return to fivebranes and use this algebraic decomposition to characterize local operators of the twisted theory.
 
 \parsec[s:e510weight]
+
+As above, we denote by $\{z_i\}$ the local coordinates along the fivebrane $Z=\C^3$ and $\{w_a\}$ the transverse holomorphic coordinates to the zero section in the fivefold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
+
+The even part of the super Lie algebra $E(5|10)$ is formal vector fields on the formal disk $\Hat{D}^3_z \times \Hat{D}^2_w$, whose elements we denote by $\mu$. 
+The odd part is given by the space of closed two-forms on the formal disk, whose elements we denote by $\alpha$.
+Equivalently, we can think of the space of closed two-forms as the space of equivalence classes of one-forms $\Omega^1(\Hat{D}^3_z \times \Hat{D}^2) / \text{Im}(\del)$.
+
 Assign the following weights to the super Lie algebra $E(5|10)$. 
@@
 Thus, for example, the odd element $[w_1 \d z_1] \in \Pi \Omega^1(\Hat{D}^5)/{\rm Im}(\del)$ carries weight $+1 - 1 = 0$. 
+(If we think about the odd part as the space of closed two-forms then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.)
 \end{itemize} 
@@
 It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. 
-In particular 
+In weight zero, $V_0$ is isomorphic to the super Lie algebra $E(3|6)$.
+In particular, 
 \beqn 
@@
 \eeqn
-is a sub super Lie algebra and each $V_n$ is a module for $E(3|6)$.
+is a sub super Lie algebra and each $\til{V}_{-1}, V_n, n \geq 0$ is a module for $E(3|6)$.
 
@@
 
-The central extension of $E(5|10)$ is defined by the (totally even) cocycle
+As we will recall momentarily, our eleven-dimensional model is more closely related to an $L_\infty$ central extension $\Hat{E(5|10)}$ of $E(5|10)$\cite[\S 3]{RSW}. 
+The central extension of $E(5|10)$ is defined by the (totally even) three-linear cocycle
 \beqn\label{eqn:e510central}
-(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} .
+(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} \in \C .
 \eeqn
@@
 \eeqn
+We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
 Here $V_{-1}$ is a $\C$-extension of the module $\til V_{-1}$ defined in the decomposition above.
@@
 
-\parsec[s:localopsdecompose]
-Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
-By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
-\begin{align*}
-\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
-& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
-\end{align*}
-The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
-$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
-\[
-Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
-\]
-and $\Hat{Q}$ acts on linear generators via
-\[
-\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
-\]
+%\parsec[s:localopsdecompose]
+%Notice that as a consequence of this decomposition there is a corresponding decomposition of local operators of the eleven-dimensional theory on $\C^5 \times \R$. 
+%By corollary \ref{cor:sugraops} there is a decomposition of $\Z/2$-graded cochain complexes 
+%\begin{align*}
+%\Obs_{sugra} (0) & = \clie^\bu \left( \Hat{V}_{-1} \times \prod_{n \geq 0} V_n \right) \\
+%& = \Sym(\Pi \Hat{V}^*_{-1}) \otimes \bigotimes_{n \geq 0} \Sym\left(\Pi V^*_n\right) .
+%\end{align*}
+%The differential $Q$, which is defined using the Lie bracket on $\Hat{E(5|10)}$ is of the form
+%$Q = Q_0 + \Hat{Q}$ where $Q_0$ acts on linear generators via
+%\[
+%Q_0 \colon V^*_n \to \oplus_{m + \ell = n} V^*_m \otimes V^*_\ell
+%\]
+%and $\Hat{Q}$ acts on linear generators via
+%\[
+%\Hat{Q} \colon \CC \to \oplus_{m + \ell + n = -1} V^*_m \otimes V^*_\ell \otimes V^*_n .
+%\]
 
@@
 
+There is another auxiliary grading that we will make use of which is also defined in \cite{KR,KacClass}. 
 The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
@@
 \item $\deg z_i = \deg w_a = 2$, so that $\deg \del_{z_i} = \deg \del_{w_a} = -2$. 
-\item $\deg \d z_i = \deg \d w_a = -1/2$.
+\item Parity carries an additional degree of $-3/2$, so that $\deg \d z_i = \deg \d w_a = -1/2$.
 \end{itemize}
 This consistent $\Z$-grading extends to the central extension of $E(5|10)$ by declaring that the central term has degree $-5$. 
-Note that this is different from the weight grading we recalled in \S \ref{s:e510weight}.
+To distinguish this from the `weight' grading above, we will refer to this grading as `degree'.
 
 \subsection{Irreducible representations of $E(3|6)$}
-Thinking of the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ (or even before centrally extending) then it carries an induced consistent $\Z$-grading. 
+We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
+Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ we then see that it carries an induced consistent $\Z$-grading by degree. 
 Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
-In particular, as a super vector space
+One can check that the algebra is supported in degrees $j \geq -2$ so that as a super vector space
 \[
-E(3|6) = \oplus_{j \geq -2} \fg_j
+E(3|6) = \prod_{j \geq -2} \fg_j
 \]
@@
 \begin{itemize}
-\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is completely even. 
-\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is completely odd. 
-\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is completely even. 
+\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is a completely even super vector space. 
+\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is a completely odd super vector space.
+\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is a completely even super vector space.
 Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
@@
 
+The irreducible modules that we consider are constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
 Denote by $\fg = E(3|6)$ and let 
@@
 Given a $\fg_0$-module $V$ let 
-\[
+\beqn\label{eqn:verma1}
 M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
-\]
+\eeqn
 be the induced $\fg$-module. 
-Notice that as super vector spaces 
-\[
-M(V) = \Sym(\fg_{<0}) \otimes_\C V .
-\]
+Notice that as super vector spaces~$M(V) = \Sym(\fg_{<0}) \otimes_\C V$.
 
@@
 
-An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda$ whose components we denote by
+An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
 \begin{align*}
@@
 \end{align*}
-and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules.
+and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules \eqref{eqn:verma1}.
+
+One of the main results of \cite{KR1} characterizes the irreducible quotients of these Verma modules. 
+\begin{thm}[\cite{KR1}]
+The Verma modules $M_A(\lambda_1,\lambda_3)$ and $M_A(\lambda_1,\lambda_3)$ have unique irreducible quotients denoted by $I_A(\lambda_1,\lambda_3)$ and $I_B(\lambda_1,\lambda_3)$, respectively. 
+Furthermore, for any $\lambda_1,\lambda_3 \in \Z_+$ one has $M_A(\lambda_1,\lambda_3) \ne I_A(\lambda_1,\lambda_3)$ and $M_B(\lambda_1,\lambda_3) \ne I_B(\lambda_1,\lambda_3)$.
+\end{thm}
+
+\parsec[]
+
+The last bit of algebraic input we need is a result of \cite{KR2} which uses these irreducible quotients $I_A(\lambda_1,\lambda_3)$ and $I_{B} (\lambda_1,\lambda_3)$ to characterize the $E(3|6)$-representations which appear in the decomposition of $E(5|10)$.
+
+\begin{thm}[\cite{KR2}]
+Consider the decomposition \eqref{eqn:decomp1} of the super Lie algebra
+\beqn
+E(5|10) = \til V_{-1} \times \prod_{i \geq -1} V_n
+\eeqn
+where $V_0 \simeq E(3|6)$. 
+Then, as $E(3|6)$-modules there are isomorphisms 
+\begin{align*}
+\til V_{-1}^* & \simeq I_A(0,1) \\
+E(3|6)^* = V_0^* & \simeq I_A(1,0) \\
+V_j^* & \simeq I_B(0,j-1), \quad j \geq 1
+\end{align*}
+where $(-)^*$ denotes the topological dual.
+\end{thm}
+
+For the centrally extension of $E(5|10)$ we need to adjust things slightly. 
+The decomposition of the central extension is $\prod_{j \geq -1} V_j$, where only $V_{-1}$ differs from the weight $(-1)$ part $\til V_{-1}$ of $E(5|10)$.
+It is easy to see that as $E(3|6)$-modules $V_{-1}^*$ is a direct sum 
+\[
+V_{-1}^* = \til V_{-1}^* \oplus \C = I_A(0,1) \oplus \C
+\]
+with $\C$ the trivial module. 
+(In \cite[\S 5]{KR2} they refer to the module $V_{-1}^*$ as~$P$.)
+
+\subsection{Decomposing fivebrane local operators}
+
+The factorization algebra of classical observables for our model of twisted supergravity is $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ where $\cL_{sugra}$ is the local $L_\infty$ algebra of \S\ref{s:sugraL}.
+As in \S\ref{s:fact}, let us take the eleven-manifold that this theory is defined on to be $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)$ where $Z$ is a complex three-fold.
+In \S\ref{s:??}, we defined the restriction $\Obs_{sugra}|_{Z}$ of the factorization algebra of twisted supergravity observables to the submanifold~$Z$.
+%is a dense subfactorization algebra of the pushforward of $\clie^\bu(\cL_{sugra})$ along the obvious projection.
+
+The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
+As a factorization algebra on the three-fold $Z$ the $!$-dual factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\Bar{\pi}_* \cL_{sugra,c})$ where $\Bar{\pi}_* \cL_{sugra}$ is an infinite-dimensional local Lie algebra on $Z$ which admits a (non-cohomological) weight grading
+\beqn\label{eqn:decomp2a}
+\Bar{\pi}_* \cL_{sugra} = \bigoplus_{n \geq -1} \Omega^{0,\bu}(Z, \cV^{(n)}) 
+\eeqn
+where $\cV^{(n)}$ is some holomorphic vector bundle on $Z$.
+
+For the remainder of this section we focus on the case $Z = \C^3$. 
+Our goal is to relate this decomposition to the purely algebraic one of \cite{KR1} that we just recalled.
+In turn, this will give us a description of fivebrane local operators supported at $0 \in \C^3$ in terms of irreducible representations of the super Lie algebra $E(3|6)$.
+
+\parsec[]
+
+First, we recall the precise relationship between the central extension of the super Lie algebra $E(5|10)$ and the local Lie algebra~$\cL_{sugra}$ on~$\R \times \C^5$.
+The local $L_\infty$ algebra $\cL_{sugra}$ on $\R \times \C^5$ can be written as 
+\[
+\cL_{sugra} = \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5, L) \simeq \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5) \otimes L_0 ,
+\]
+where $L$ is a translation invariant holomorphic vector bundle and~$L_0$ its fiber over~$0 \in \C^5$.
+As in \S \ref{s:interacting}, the local $L_\infty$ algebra structure on $\cL_{sugra}$ induces an $L_\infty$ structure on the $\infty$-jets at~$0 \in \R \times \C^5$ of $\cL_{sugra}$, which we can identify using the Poincar\'e lemma with~$L_0[[z_1,\ldots,z_5]]$.
+Furthermore, the Taylor expansion map at $0 \in \R \times \C^5$ defines an $L_\infty$ map
+\[
+\cL_{sugra}(\R \times \C^5) \to L_0[[z_1,\ldots,z_5]] .
+\]
+
+In~\cite{RSW} it is shown that $L_0[[z_1,\ldots,z_5]]$ is equivalent to the super Lie algebra $\Hat{E(5|10)}$ which is the central extension of $E(5|10)$ by the cocycle in \brian{finish}. 
+There is a similar result for the restricted local $L_\infty$ algebra $\Bar{\pi}_*\cL_{sugra}$.
+
+If we take the threefold $Z = \C^3$ then of course $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2) \simeq \R \times \C^5$.
+
+%First, we will see how to relate the decomposition at the level of global sections of~$\cL_{sugra}$ over~$Z = \C^3$.
+
+%In the decomposition \eqref{eqn:decomp2a} the
 

### 2022-06-29 fivebranes/twisted.tex
all around

@@
 
-Eleven-dimensional supergravity is the unique...
+Eleven-dimensional supergravity is the unique supersymmetric theory in eleven dimensions.
+It plays an important role as the low energy limit of $M$ theory.
+
+Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
+In any theory of supergravity, there is an collection of bosonic ghosts which, in part, incorporate local supersymmetry.
+By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.
+
 Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
@@
 In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
-Globally, the eleven-dimensional theory exists on any manifold of the form $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
+Globally, the eleven-dimensional theory exists on any manifold of the form 
+\[
+S \times X 
+\] 
+where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
 
@@
 \]
+Part of the equations of motion for $\mu$ dictate that it be locally constant along~$S$.
+Ordinarily, for $\mu$ to describe a deformation of complex structure in the $X$ direction we would require that it satisfy the Muarer--Cartan equation.
+For twisted supergravity, however, we find a modification of this equation which involves the twisted analog of another familiar field.
 
-One of the other bosonic fields of eleven-dimensional supergravity is a three-form which is usually denoted by~$C$. 
+One of the other bosonic fields of eleven-dimensional supergravity is a three-form that we denote by~$\sf C$. 
 On $S \times X$ the space of complex-valued three-forms decomposes into de Rham--Dolbeault forms as in
@@
 When we want to be specific by the form type we use the notation $\beta^{k;q}$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}$ for the $(k;1,q)$ component of the three-form.
+
+Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
+Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.
 
@@
 \]
-There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C \setminus 0$ which extends to zero.
+There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
 The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.

### 2022-06-29 fivebranes/fact.tex
merge

@@
-\documentclass[11pt]{amsart}
-
-%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
-
-\begin{document}
+%\documentclass[11pt]{amsart}
+%
+%%\usepackage{../macros-master}
+%\usepackage{macros-fivebrane}
+%
+%\begin{document}
 
@@
 
-\end{document}
+We summarize the key points of this section.
+In both the fivebrane and membrane case, we have described a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables restricted to the worldvolume of the fivebrane or membrane.
+This factorization algebra is of the form 
+\[
+\pi_*\Obs_{sugra} = \clie^\bu(\cG)
+\]
+where $\cG$ is a sheaf of $L_\infty$ algebras on the worldvolume of the fivebrane or membrane.
+While $\infty$ rank, $\cG$ is still well-behaved geometrically. 
+It is given as the sheaf of sections of a pro vector bundle.
+
+This local $L_\infty$ algebra came with a natural decomposition 
+\[
+\cG = \oplus_{j \geq -1} \cG^{(j)} .
+\]
+The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
+This sequence of ideals induces a limit diagram of vector bundles
+\beqn\label{eqn:lim}
+0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
+\eeqn
+where $0$ is the zero vector bundle.
+For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
+For $N > 0$, we define 
+\beqn
+\til \cG_N \define \cG / \cG^{(\geq N-1)} 
+\eeqn
+which has the induced structure of a local $L_\infty$ algebra on the worldvolume.
+
+The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
+\beqn\label{eqn:colim}
+\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\cG_2) \to \cdots ,
+\eeqn
+whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
+Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
+There is a similar diagram upon applying~$!$-duals
+\beqn
+\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots ,
+\eeqn 
+whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$.
+
+%\end{document}

### 2022-06-29 fivebranes/index.tex
merge

@@
 relationship to the $S^5$ partition function.
-
-\subsection{Counting supergravity states}
-
-Generally speaking, twists of supersymmetric theories have a mixed holomorphic and topological behavior.
-
-\parsec[]
-
-\parsec[s:pexp]
-
-\brian{characters, plethystic, etc.}
 
@@
 
-%In \cite{SW6d} a symmetry by the exceptional super Lie algebra $E(3|6)$ on the holomorphic twist of the free tensor multiplet was constructed.
-%We recall the action of its even part on local operators of the holomorphic twist of the free tensor multiplet. 
-%We recount how it acts on the vector space \eqref{eqn:localfree}.
-% 
-%Recall that the even part of $E(3|6)$ consists of two summands:
-%\[
-%\Vect(\Hat{D}^3) \times \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
-%\]
-%Formal vector fields act naturally by Lie derivative on both summands in \eqref{eqn:localfree}. 
-%An $\lie{sl}(2)$-valued function acts on $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$ where we view $\C^2 = {\rm span}\{r_+,r_-\}$ as the fundamental $\lie{sl}(2)$ representation.
-
 After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
-This algebra contains the $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
+This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
 The holomorphic supercharge is a supertranslation 
@@
 
-To compute characters of local operators the fivebrane worldvolume theory we will consider the symmetry of the holomorphic twist of a six-dimensional superconormal theory with respect to the even subalgebra
+In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
+Geometrically, this background is $AdS_7 \times S^4$. 
+In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.
+
+In this section we will compute characters of the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes.
+Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
+We will enumerate states via considering a Cartan in the even subalgebra
 \beqn\label{eqn:bosonic1}
@@
 \eeqn
-We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.
-
-In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
-Geometrically, this background is $AdS_7 \times S^4$. 
-In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.
+%We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.
 
@@
 \[
-\C^5 \times \R = \C_z^3 \times \C_w^2 \times \R_t
+\R \times \C^5 = \R_t \times \C^2_w \times \C_z^3 
 \]
-with $z_i, i=1,2,3$ and $w_a, a=1,2$.
+with $z = (z_i), i=1,2,3$ and $w = (w_a), a=1,2$.
 The stack of fivebranes wrap $w_1=w_2=t=0$. 
@@
 The subalgebra $\lie{sl}(3)$ embeds as vector fields
-\[
+\beqn
 \sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
-\]
+\eeqn
+By definition, these vector fields are automatically divergence-free.
 \item
-The subalgebra $\lie{gl}(1)$ is mapped to the element
-\[
-\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
-\] 
-Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
+The generator of the subalgebra $\lie{gl}(1)$ is mapped to the element
+\beqn\label{eqn:Y}
+Y = \sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
+\eeqn 
+Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $t=w=0$. 
 \item 
 The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
-\[
+\beqn
 w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
-\]
+\eeqn
 \end{itemize}
@@
   \beqn
-  z_1 \del_{z_1} - z_2 \del_{z_2} , \quad z_2 \del_{z_2} - z_3 \del_{z_3}
+  h_1 = z_1 \del_{z_1} - z_2 \del_{z_2} , \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3}.
   \eeqn
-  on~$\C^{3}_{z}$.
-  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on $\C^{2} = {\rm span}\{r_+,r_-\}$. 
-  \item $q$ denotes a generator for the Cartan of an additional $\lie{gl}(1)$ which acts by dilations on $\C^3$. 
+   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element~$\eqref{eqn:Y}$. 
+  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
+  \beqn
+  h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
+  \eeqn
 \end{itemize}
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c}
-  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
-  \hline
-  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
-  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
-  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
-  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
-\end{tabular}
-\caption{Fugacities for a single fivebrane.}
-\end{center}
-\label{tbl:weights1}
-\end{table}
+%\begin{table}
+%\begin{center}
+%\begin{tabular}{c c c c c c}
+%  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
+%  \hline
+%  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
+%  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
+%  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
+%  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
+%\end{tabular}
+%\caption{Fugacities for a single fivebrane.}
+%\end{center}
+%\label{tbl:weights1}
+%\end{table}
 
-\subsection{Operators on a single fivebrane}
+\subsection{Global symmetry for twisted membranes}
 
-We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
-This theory exists on any complex three-fold $X$. 
-To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.
+\subsection{Counting supergravity states}
 
-The theory on a single fivebrane is free and the underlying cochain complex of the abelian holomorphic local Lie algebra on $\C^3$ is given by 
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
-\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
+We enumerate single particle supergravity states via computing the super trace of the operator $t_1^{h_1} t_2^{h_2} q^Y r^h$. 
+The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
 
-\begin{lem}
-\label{lem:single}
-The $\Z \times \Z/2$ algebra of local operators of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
-\beqn\label{eqn:localfree}
-\Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
-\eeqn
-\end{lem}
+\parsec[s:pexp]
 
-\begin{proof}
-The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
-\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-On the formal disk all closed two-forms are automatically exact, which implies the lemma.
-\end{proof}
-
-\parsec
-
-We now move on to the computation of the character of local operators on a single fivebrane.
-According to the weights listed above and using the description of local operators in Lemma \label{lem:single} we have the following contributions to the character.
-
-\begin{itemize}
-\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
-\[
-- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
-\[
-q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
-\[
-q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-\end{itemize}
-
-Putting this all together we obtain the following.
-
-\begin{prop}
-The character of local operators of the holomorphic twist of the theory on a single fivebrane is given by the following plethystic exponential
-\[
-{\rm PExp} \left[f_{tensor} (t_1,t_2,q,r) \right] .
-\]
-where the single particle index is
-\[
-f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
-\end{prop}
-
-\parsec
-
-A degeneration of this character was computed in \cite{KR1}. 
-They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
-In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
-\[
-\frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3}
-\]
-which agrees with our direct analysis above.
-
-\parsec
-
-There are various specializations of this character that one can consider. 
-One which is motivated from supersymmetry produces...
-
-\begin{itemize}
-\item The deformation $\d z_1 \otimes r_+$.
-\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
-\end{itemize}
-
-Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
-\beqn\label{eqn:special1}
-q = r^2 , \quad t_2 = 1 .
-\eeqn
-As one can easily check, this specialization yields the following single particle index
-\[
-f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
-\]
-which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
-Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
+\brian{characters, plethystic, etc.}
 

### 2022-06-29 fivebranes/ops.tex
merge

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

\section{Local operators in twisted $M$ theory}

The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
Let $\Obs$ be the factorization algebra of observables of some theory defined on a smooth manifold $M$.
The space of \defterm{local operators} at point $p \in M$ is, in a precise sense, the limiting behavior of the factorization algebra evaluated on the system of open sets which contain the point~$p$.

Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point.

In this section we recall the essentials of the theory of local operators for holomorphic-topological theories.

\subsection{The definition of local operators}

A factorization algebra encodes the many ways to combine observables supported on arbitrary open sets. 
Local operators, on the other hand, exist just at a point in spacetime.
From the factorization algebra perspective one can recover local operators by looking at observables which are supported on \text{every} open set which contains the given point; mathematically this is computed by a limit.

Precisely, in \cite[Definition 10.1.0.1]{CG2} the space of local operators of a factorization algebra $\cF$ at a point $p \in M$ is defined by the limit $\cF(p) = \lim_{U \ni p} \cF(U)$ which runs over open sets $U \subset M$ containing~$p$.

We will only consider local operators on affine space $\R^d$. 
In this case, we will have the additional property that the factorization algebras are translation invariant.
At the level of local operators this means that the translation map $\tau_{p \to p'}$ induces an isomorphism $\cF(p) \simeq \cF(p')$. 
Without loss of generality, we will consider expressions for local operators at $0 \in \R^d$.

For topological-holomorphic theories the local operators take a very familiar form.
As an algebra they are generated by holomorphic derivatives of the fields evaluated at the specified point. 
In this section we carefully formulate this result and give some examples.

\parsec[s:free]

%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
%Let $\cV$ denote its sheaf of holomorphic sections.
%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
%\[
%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
%\]
%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
%
%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
%\begin{itemize}
%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
%\[
%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
%\]
%\end{itemize}
%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
%
%\parsec
A topological-holomorphic theory exists on spacetimes of the form $S \times X$ where $S$ is a smooth manifold and $X$ is a complex manifold (possibly equipped with some auxiliary geometric structures). 
The typical space of fields of a holomorphic-topological theory in the BV formalism is
\beqn\label{eqn:cE}
\cE = \Omega^\bu (S) \hotimes \Omega^{0,\bu}(X, V) 
\eeqn
where $V$ is a graded holomorphic vector bundle on $X$.
The underlying free theory is described by a differential on the space of fields of the form
\[
\d_{dR} + \dbar + Q^{hol} .
\]
Here $\d_{dR}$ is the de Rham differential acting on $S$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon V \to V[1]$ is a holomorphic differential operator of cohomological degree~$+1$.
This means that the free, linear equations of motion for a field $\varphi$ take the form
\[
\d_{dR} \varphi + \dbar \varphi + Q^{hol} \varphi = 0 .
\]
Taking into account linear gauge symmetries corresponds to cohomology---solutions to the equations of motion modulo the image of $\d_{dR} + \dbar + Q^{hol}$.

Notice that $\cE$ is a sheaf of cochain complexes---it makes sense to restrict the fields to any open set $U \subset S \times X$. 
The factorization algebra of observables of the free theory whose fields are as above assigns to an open set $U \subset S \times X$ the cochain complex
\[
\Obs \colon U \mapsto \cO(\cE(U)) = \Sym \left(\cE(U)^\vee \right) 
\]
equipped with the induced differential.
Here $\cE(U)^\vee$ denotes the {\em topological} dual of the graded vector space $\cE(U)$. 
As a graded vector space one has an isomorphism $\cE(U)^\vee \simeq \overline{\cE}^!_c(U)$ where the bar denotes distributional sections and $!$ is the Serre dual. 
Explicitly, if $U = U' \times U'' \subset S \times X$ then 
\[
\overline{\cE}^!_c(U' \times U'') \simeq \overline{\Omega}^\bu(U') \otimes \overline{\Omega}^{n,\bu}(U'',V^*)[n+m] 
\]
where $\dim_\C (X) = n$ and $\dim_\R (S) = m$.

Let's restrict to the case that $S \times X = \R^m \times \C^n$ and suppose that the bundle $V \to \C^n$ is translation invariant with fiber $V_0$ over $0 \in \R^m \times \C^n$.
We also assume that the operator $Q^{hol}$ is translation invariant. 
The jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes
\[
\cE(\C^n \times \R^m) \to V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
\]
The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables. 
Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
\[
V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} V_0 [[z_j]] 
\]
which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
The only remaining differential on the right hand side is~$Q^{hol}$. 
In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes $\cE(\R^m \times \C^n) \to V_0[[z_j]]$.

\begin{lem}
\label{lem:taylor}
Suppose that $\cE$ is the sheaf of cochain complexes representing the free topological-holomorphic theory on $S \times X = \R^m \times \C^n$ and consider the factorization algebra of observables~$\Obs = \cO (\cE)$. 
Then, the Taylor expansion map
\beqn\label{eqn:taylor}
\cE(\C^n \times \R^m) \to V_0[[z_0,\ldots,z_n]]
\eeqn
induces a quasi-isomorphism of commutative dg algebras
\[
\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]] \right) .
\]
%Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
%\[
%\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]][1] \right) 
%\]
%where the right hand side is equipped with the differential $Q^{hol}$. 
\end{lem}
\begin{proof}
Suppose that $D_\R \times D_\C \subset \R^m \times \C^n$ is a product of a real $m$-disk times a complex $n$-disk containing the origin.
The algebra of observables supported on $D_\R \times D_\C$ is quasi-isomorphic to 
\[
\cO\left( \cO^{hol}(D_\C) \otimes V_0 \right) .
\]

Observe that there is a canonical map on fields 
\[
\cO^{hol}(D_\C) \otimes V_0 \to V_0[[z_1,\ldots,z_n]]
\]
given by taking the power series expansion at $0 \in D_\R \times D_\C$. 
If an observables on $D_\R \times D_\C$ depends on only the value of the field and its derivatives at $0 \in D_\R \times D_\C$ then it automatically factors through this map. 
In particular, this means that there is a quasi-isomorphism of local operators with functions on $V_0[[z_1,\ldots,z_n]]$,
\[
\Obs(0) \simeq \cO(V_0 [[z_1,\ldots,z_n]] .
\] 
\end{proof}

Let's unpack this result explicitly. 
Using the $n$-dimensional residue, we can identify the topological dual of $V_0[[z_1,\ldots,z_n]]$ with the vector space
\beqn
\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n} V_0^* [z_0^{-1}, \ldots,z_n^{-1}] .
\eeqn
This is the space of linear local operators.

Suppose that $\chi \colon V_0 \to \C$ is a dual vector in~$V_0^*$. 
Then, we obtain a linear local operator at $0 \in \R^m \times \C^n$ on the space of fields by the assignment
\[
\varphi \mapsto \del_{z_1}^{k_1} \cdots \del_{z_n}^{k_n} \<\chi,\varphi\> (0) 
\]
where $k_i \geq 0$. 
Under the quasi-isomorphism of the lemma above, this corresponds to the linear local operator 
\[
\frac{\d z_1}{z_1^{k_1+1}} \cdots \frac{\d z_n}{z_n^{k_n+1}} \chi .
\]

\parsec[s:interaction]

It is not hard to turn on interactions in the description above. 
An interacting theory in the BV formalism is described by a local $L_\infty$ algebra structure on $\cL = \cE[-1]$, where $\cE$ is the sheaf of fields.
For a topological-holomorphic theory the higher $L_\infty$ structure maps $[\cdot]_k$ of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators and $[\cdot]_1 = \d_{dR} + \dbar + Q^{hol}$.  
For more details we refer to the definitions in \cite{GRWthf}.

In this situation, the factorization algebra of classical observables supported on an open set $U \subset S \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
This defines a factorization algebra 
\[
\Obs \colon U \mapsto \clie^\bu(\cL(U)) .
\]
We will now give a concise presentation for the {\em local} operators in a topological-holomorphic theory.

On $S \times X = \R^m \times \C^n$ we can also ask that all $L_\infty$ structure maps be translation invariant. 
If this is the case, one obtains the induced structure of an $L_\infty$ algebra on the (shift of the) jets of the fields supported at $0 \in \R^m \times \C^n$
\[
V_0 [[z_1,\ldots,z_n]] [1] .
\]
The $[\cdot]_1$ operation is precisely $Q^{hol}$ as above.
The Taylor expansion map \eqref{eqn:taylor} is a map of $L_\infty$ algebras. 
Combining this with Lemma \ref{lem:taylor}, one gets a quasi-isomorphism of cochain complexes between the local operators of an interacting topological-holomorphic theory in terms of Lie algebra cohomology
\[
\Obs(0) \simeq \clie^\bu\left(V_0[[z_1,\ldots,z_n]][1]\right) .
\]

%We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
%if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
%The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.

\parsec[s:envelope]

There is another way that observables are presented in a degenerate version of the BV formalism. 
Suppose that $\cL$ is a local Lie algebra on a manifold $M$. 
Then, one can consider the factorization algebra
\[
\cF = \clie_\bu(\cL_c)
\]
which assigns to an open set $U$ the cochain complex $\clie_\bu(\cL_c(U))$.
This is the $!$-dual of the factorization algebra $\clie^\bu(\cL)$.
For topological-holomorphic local Lie algebras there is still an algorithm for computing $\cF(p)$ for a point~$p \in M$.

We will assume that $\cL$ is a translation invariant topological-holomorphic local Lie algebra whose underlying sheaf of cochain complexes is
\[
\cL = \Omega^\bu (\R^m) \hotimes \Omega^{0,\bu}(\C^n, L)
\]
Here $L$ is a translation invariant holomorphic vector bundle on $\C^n$ and the differential in the complex is $\d_{dR} + \dbar + Q^{hol}$ as above.

\begin{lem}
\label{lem:envelope}
Suppose that $\cL$ is a topological-holomorphic local Lie algebra on $S \times X = \R^m \times \C^n$ and let $\cF$ be the factorization algebra $\clie_\bu(\cL_c)$.
Moreover, assume that $Q^{hol}$ is an elliptic holomorphic differential operator. 
Then, there is a spectral sequence converging to $H^\bu(\cF(0))$ whose first page is the $Q^{hol}$ cohomology of
\[
\cO \left(\d^n z L_0^*[[z_1,\ldots,z_n]] [n+m-1] \right) .
\]
\end{lem}
\begin{proof}
First, notice that as graded topological vector spaces one has an isomorphism for any open set $U \subset M$ 
\beqn\label{eqn:dist}
\left(\overline{\cL}^!(U)\right)^\vee \simeq \cL_c(U) 
\eeqn

We use the spectral sequence induced by the filtration by the homogenous degree of a local operator.
The first page is the cohomology of 
\[
\lim_{0 \ni U} \Sym(\cL_c(U)[1]) 
\]
with respect to the linear differential $\d_{dR} + \dbar + Q^{hol}$ which acts on $\cL_c(U)$ and extends to the symmetric algebra by the rule that it is a derivation.

Using the isomorphism \eqref{eqn:dist}, we have an isomorphism 
\[
\Sym(\cL_c(U)[1]) \simeq \cO\left(\overline{\cL}^!(U)[-1]\right) 
\]
for any open set $U$.
By assumption, the linear differential $[\cdot]_1$ is elliptic, in particular the embedding of smooth sections into distributional sections
\[
\cL^!(U) \hookrightarrow \overline{\cL}^! (U)
\]
is a quasi-isomorphism for any open set~$U$.

Explicitly, we can assume that $U$ is an open set of the form $U' \times U'' \subset \R^m \times \C^n$ with $U' \subset \R^m$ contractible and $U''\subset \C^n$ Stein.
Then we have a sequence of quasi-isomorphisms
\begin{align*}
\overline{\cL}^! (U) [-1] & \simeq \cL^!(U) [-1] \\ & \simeq \Omega^\bu(U') \otimes \Omega^{0,\bu}(U'',K_{\C^n} \otimes L^*)[n+m-1] . 
\end{align*}
Thus, the first page of this spectral sequence is isomorphic to the cohomology of the local operators $\Obs(0)$ of the free theory whose underlying cochain complex of fields is 
\[
\cE = \Omega^\bu(\R^m) \hotimes \Omega^{0,\bu}(\C^n , K_{\C^n} \otimes L^*[n+m-1]).
\]
In the notation of Equation \eqref{eqn:cE}, the holomorphic vector bundle $V$ is 
\[
K_{\C^n} \otimes L^*[n+m-1] .
\]
The result now follows from Lemma~\ref{lem:taylor} where we have used $\d^n z$ for basis for the line $K_{\C^n}|_0$. 
\end{proof}

\parsec[s:examples]

We present some simple examples.

\begin{eg}
Suppose that $V$ is the trivial bundle on $\C^n$ and consider the theory whose fields are
\[
\cE = \Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) 
\]
where the differential is just $\d_{dR} + \dbar$. 
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
\end{eg}

\begin{eg}
Consider the abelian local Lie algebra on $X = \C$ whose sheaf of cochain complexes is 
\[
\cL = \Omega^{0,\bu}\left(\C, K_{\C}^{\otimes r}\right),
\]
where $r \in \Z$. 
Then, we have the factorization algebra which assigns to $U \subset \C$ the complex
\[
\cF(U) = \clie_\bu(\cL_c(U)) = \Sym\left(\Omega^{0,\bu}_c\left(U, K_U^{\otimes r}\right)\right)
\]
where the differential is $\dbar$. 
By Lemma \ref{lem:envelope} we see that the local operators $\cF(0)$ is identified with the vector space
\[
\cO\left(\d z^{\otimes (r + 1)} \C[[z]] \right) .
\]
In particular, the single particle index of local operators is 
\[
\frac{q^{r+1}}{1-q} 
\]
where $q$ represents the fugacity for the standard $\C^\times$ action on $\C$.
\end{eg}

\subsection{Comparison to `states'}

\subsection{Operators on a single fivebrane}

We recalled the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables~$\Obs_{single}$ on $Z$.
We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs_{single}(0)$ supported at~$0 \in \C^3$.

The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{single}$ with linear BRST differential is
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

Before moving on to characterizing local operators we take a brief moment to comment on the holographic appearance of the theory on a single fivebrane.

\parsec[s:fiverelatesingle]

In \eqref{eqn:lim2} we presented the universal factorization algebra of classical observables on the fivebrane 
\[
(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) 
\]
as a limit.
The first nonzero term in this limit diagram is 
\[
\clie_\bu(\cG_{1,c})
\]
where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$.

\begin{prop}
There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
\[
\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{single} .
\]
\end{prop}

\begin{proof}
In weight $(-1)$ the abelian local Lie algebra takes the form
\[
\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
\]
where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
\beqn\label{eqn:weight-1a}
\begin{tikzcd}
\ul{odd} & \ul{even}\\
\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
\end{tikzcd}
\eeqn
On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
\[
\cO(\cE_{single}(U)) = \Sym(\Pi \overline{\cE}_{single,c}^!(U)) .
\]
It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
The result then follows by applying ellipticity.
\end{proof}

We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
However, when $\lie{g}$ is abelian (so, a cochain complex) we can simply identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.

\parsec[]

We move on to characterizing the character of the holomorphic twist of the theory on a single fivebrane.
By the previous result we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.

\begin{lem}
\label{lem:single}
The $\Z \times \Z/2$ graded algebra of local operators $\Obs_{single}(0)$ of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
\beqn\label{eqn:localfree}
V_0[[z_1,z_2,z_3]] \simeq \Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
\eeqn
\end{lem}

\begin{proof}
The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
On the formal disk all closed two-forms are automatically exact, which implies the lemma.
\end{proof}

\parsec

We move on to the straightforward computation of the character of local operators on a single fivebrane which we will present as the plethystic exponential of the character of linear local operators
\beqn
\chi_{single} (t_1,t_2,q,r) = {\rm PExp} \big[f_{single}(t_1,t_2,q,r) \big] .
\eeqn
According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{single}$.

\begin{itemize}
\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
\[
- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
\]
\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
\[
q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
\]
\end{itemize}

Putting this all together we obtain the following.

\begin{prop}
The character $\chi_{single}(t_1,t_2,q,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of
\[
f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\]
\end{prop}

\parsec

There are various degenerations, or specializations, of this character which are interesting to consider.
These specializations involve restricting the character above to a subalgebra of the full Cartan that we considered above.

One degeneration of this character involves specializing $t_1=t_2=r=1$:
%They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
%In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
\[
\chi_{single} (q,t_1=t_2=r=1) = \frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3} .
\]
In \S \ref{s:kr} we will compare this to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.

\parsec

Another specialization is related to the superconformal algebra.

\begin{itemize}
\item The deformation $\d z_1 \otimes r_+$.
\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
\end{itemize}

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.

%\subsection{Categorifying the index for free theories}
%
%In the case of both membranes and fivebranes we constructed a particular restriction of the local $L_\infty$ algebra $\cL_{sugra}$ to the respective worldvolume theories which we denoted by $\Bar{\pi}_* \cL_{sugra}$. 
%There are two important sub local $L_\infty$ algebras 
%\[
%\begin{tikzcd}
%& \Bar{\pi}_*\cL_{sugra} & \\
%\Bar{\pi}_*\cL_{sugra}^{(-1)} \ar[ur] & & \Bar{\pi}_*\cL_{sugra}^{(0)} \ar[ul] .
%\end{tikzcd}
%\]
%This diagram induces a diagram of factorization algebras
%\[
%\begin{tikzcd}
%& \left(\Obs_{sugra}|_Z\right)^! & \\
%\clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(-1)}) \ar[ur] & & \clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(0)}) \ar[ul].
%\end{tikzcd}
%\]

%\parsec[s:sugraops]
%
%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra. 
%
%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
%\[
%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
%\]
%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
%\[
%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
%\]
%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
%
%\begin{thm}[\cite{RSW}[Theorem 2.1]]
%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
%\[
%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
%\]
%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
%\end{thm} 
%
%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
%
%\begin{cor}
%\label{cor:sugraops}
%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
%There is a quasi-isomorphism of commutative dg algebras
%\[
%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
%\]
%\end{cor}

\subsection{Operators on a single membrane}

%\end{document}

### 2022-07-06 fivebranes/kr.tex
merge

@@
 \documentclass[11pt]{amsart}
-
-%\usepackage{../macros-master}
+%
+%%\usepackage{../macros-master}
 \usepackage{macros-fivebrane}
-
+%
 \begin{document}
 
-\section{Kac-Rudokov}
+\section{A series of finite $N$ conjectures}
 
@@
 
-\subsection{The fivebrane decomposition of $E(5|10)$}
+\subsection{The fivebrane decomposition of $\Hat{E(5|10)}$}
 
@@
 
-As above, we denote by $\{z_i\}$ the local coordinates along the fivebrane $Z=\C^3$ and $\{w_a\}$ the transverse holomorphic coordinates to the zero section in the fivefold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
+As above, we denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
 
@@
 
+\subsection{Decomposing fivebrane local operators}
+
+The factorization algebra of classical observables for our model of twisted supergravity is $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ where $\cL_{sugra}$ is the local $L_\infty$ algebra of \S\ref{s:sugraL}.
+As in \S\ref{s:fact}, let us take the eleven-manifold that this theory is defined on to be $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)$ where $Z$ is a complex three-fold.
+In \S\ref{s:??}, we defined the restriction $\Obs_{sugra}|_{Z}$ of the factorization algebra of twisted supergravity observables to the submanifold~$Z$.
+%is a dense subfactorization algebra of the pushforward of $\clie^\bu(\cL_{sugra})$ along the obvious projection.
+
+The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
+The $!$-dual of the factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\cG_c)$ where $\cG$ is an infinite-dimensional local $L_\infty$ algebra on $Z$.
+In \S \ref{s:weight1} we defined a $\C^\times$ action on $\cG$ which determines a (non-cohomological) weight grading
+\beqn\label{eqn:decomp2a}
+\cG = \bigoplus_{n \geq -1} \Omega^{0,\bu}(Z, \cV^{(n)}) 
+\eeqn
+where $\cV^{(n)}$ is some holomorphic vector bundle on $Z$.
+
+For the remainder of this section we focus on the case $Z = \C^3$. 
+Our goal is to show that this weight grading is compatible with the one on the central extension of $E(5|10)$ that we recalled in \S \ref{s:e510central}. 
+In turn, this will give us a description of fivebrane local operators supported at $0 \in \C^3$ in terms of irreducible representations of the super Lie algebra $E(3|6)$.
+
+\parsec[]
+
+First, we recall the precise relationship between the central extension of the super Lie algebra $E(5|10)$ and the local Lie algebra~$\cL_{sugra}$ on~$\R \times \C^5$.
+The local $L_\infty$ algebra $\cL_{sugra}$ on $\R \times \C^5$ can be written as 
+\[
+\cL_{sugra} = \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5, L) \simeq \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5) \otimes L_0 ,
+\]
+where $L$ is a translation invariant holomorphic vector bundle and~$L_0$ its fiber over~$0 \in \C^5$.
+As in \S \ref{s:interacting}, the local $L_\infty$ algebra structure on $\cL_{sugra}$ induces an $L_\infty$ structure on the $\infty$-jets at~$0 \in \R \times \C^5$ of $\cL_{sugra}$, which we can identify using the Poincar\'e lemma with~$L_0[[z_1,\ldots,z_5]]$.
+Furthermore, the Taylor expansion map at $0 \in \R \times \C^5$ defines an $L_\infty$ map
+\beqn
+T_0 \colon \cL_{sugra}(\R \times \C^5) \to L_0[[w_1,w_2, z_1,z_2,z_3]] 
+\eeqn
+where we recall that we have used $\{z_i\}$ for the coordinates along the directions the fivebrane wraps in 
+\[
+\C^5 \simeq {\rm Tot}(K^{1/2}_Z \otimes \C^2)
+\]
+and $\{w_a\}$ for the transverse holomorphic coordinates.
+
+In~\cite{RSW} it is shown that $L_0[[w_1,w_2, z_1,z_2,z_3]]$ is equivalent to the super Lie algebra $\Hat{E(5|10)}$ which is the central extension of $E(5|10)$ by the cocycle in \brian{finish}. 
+The restricted local $L_\infty$ algebra $\cG$ sits somewhere in-between $\cL_{sugra}(\R \times \C^5)$ and $\Hat{E(5,10)}$.
+
+The sheaf of local $L_\infty$ algebras $\cG$ on $\C^3$ is the smooth sections of a holomorphic translation invariant pro vector bundle $G$. 
+Let $G_0$ be the fiber over $0 \in \C^3$. 
+Similarly as above, since the space $G_0[[z_1,z_2,z_3]]$ is the $\infty$-jets of $\cG$ at $0 \in \C^3$ it is equipped with the structure of an $L_\infty$ algebra and the Taylor expansion map 
+\[
+T_0^{\C^3} \colon \cG(\C^3) \to G_0[[z_1,z_2,z_3]] 
+\]
+is a map of $L_\infty$ algebras.
+
+\begin{lem}
+\begin{itemize}
+\item[(1)]
+There is an equivalence of $L_\infty$ algebras
+\[
+\Hat{E(5|10)} \simeq G_0 [[z_1,z_2,z_3]] .
+\]
+\item[(2)]The partial Taylor expansion of sections of $\cL_{sugra}(\R \times \C^5)$ at $w_1=w_2 = 0$ defines a map of $L_\infty$ algebras 
+\[
+\cL_{sugra}(\R \times \C^5) \to \cG(\C^3) ,
+\]
+and makes the following diagram commute
+\[
+\begin{tikzcd}
+\cL_{sugra}(\R \times \C^5) \ar[dr,dotted] \ar[rr,"T_0^{\R \times \C^5}"] & &  \Hat{E(5|10)} \\ 
+& \cG(\C^3) \ar[ur,"T_0^{\C^3}"'] & .
+\end{tikzcd} 
+\]
+\item[(3)] 
+The Taylor expansion map $T_0^{\C^3}$ is $\C^\times$-equivariant. 
+\end{itemize}
+\end{lem}
+%First, we will see how to relate the decomposition at the level of global sections of~$\cL_{sugra}$ over~$Z = \C^3$.
+
+%In the decomposition \eqref{eqn:decomp2a} the
+
+In \S \ref{s:}. \brian{finish}
+
 \subsection{Irreducible representations of $E(3|6)$}
 We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
-Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of $\Hat{E(5|10)}$ we then see that it carries an induced consistent $\Z$-grading by degree. 
+Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of the central extension of $E(5|10)$ we see that it carries an induced consistent $\Z$-grading by degree. 
 Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
@@
 
-The irreducible modules that we consider are constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
+We are interested in a class of irreducible modules for $E(3|6)$ that can be constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
 Denote by $\fg = E(3|6)$ and let 
@@
 
-An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2;\lambda_3;y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
+An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2,\lambda_3,y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
 \begin{align*}
@@
 \end{align*}
-There is an isomorphism of $\fg_0$-modules
+Actually, for the remainder of this section we will be interested in the case $\lambda_2 = 0$; the modules with $\lambda_2 \ne 0$ will play no role.
+
+For $\lambda_1,\lambda_3 \geq 0$ there are isomorphisms of $\fg_0$-modules
 \begin{align*}
-V_A^{p,r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
-V_B^{p,-r} & \simeq F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2) .
+V_A^{\lambda_1,\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 - \lambda_3) \\
+V_B^{\lambda_1,-\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 + \lambda_3 +2) .
 \end{align*} 
-Note for type $A,B$ we have $\lambda_2 = 0$. 
-To simplify notation we will write 
+To simplify notation we will get rid of the dependence on $\lambda_2$ and write 
 \begin{align*}
@@
 
+In \textit{loc. cit.} they refer to such irreducible modules $I_A,I_B$ as `degenerate'.
+
 \parsec[]
@@
 where $V_0 \simeq E(3|6)$. 
-Then, as $E(3|6)$-modules there are isomorphisms 
+Then, there are isomorphisms of $E(3|6)$-modules
 \begin{align*}
@@
 
-\subsection{Decomposing fivebrane local operators}
+\subsection{Characters for degenerate modules of type $A$} \label{s:typeA}
 
-The factorization algebra of classical observables for our model of twisted supergravity is $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ where $\cL_{sugra}$ is the local $L_\infty$ algebra of \S\ref{s:sugraL}.
-As in \S\ref{s:fact}, let us take the eleven-manifold that this theory is defined on to be $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2)$ where $Z$ is a complex three-fold.
-In \S\ref{s:??}, we defined the restriction $\Obs_{sugra}|_{Z}$ of the factorization algebra of twisted supergravity observables to the submanifold~$Z$.
-%is a dense subfactorization algebra of the pushforward of $\clie^\bu(\cL_{sugra})$ along the obvious projection.
-
-The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
-As a factorization algebra on the three-fold $Z$ the $!$-dual factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\Bar{\pi}_* \cL_{sugra,c})$ where $\Bar{\pi}_* \cL_{sugra}$ is an infinite-dimensional local Lie algebra on $Z$ which admits a (non-cohomological) weight grading
-\beqn\label{eqn:decomp2a}
-\Bar{\pi}_* \cL_{sugra} = \bigoplus_{n \geq -1} \Omega^{0,\bu}(Z, \cV^{(n)}) 
-\eeqn
-where $\cV^{(n)}$ is some holomorphic vector bundle on $Z$.
-
-For the remainder of this section we focus on the case $Z = \C^3$. 
-Our goal is to relate this decomposition to the purely algebraic one of \cite{KR1} that we just recalled.
-In turn, this will give us a description of fivebrane local operators supported at $0 \in \C^3$ in terms of irreducible representations of the super Lie algebra $E(3|6)$.
-
-\parsec[]
-
-First, we recall the precise relationship between the central extension of the super Lie algebra $E(5|10)$ and the local Lie algebra~$\cL_{sugra}$ on~$\R \times \C^5$.
-The local $L_\infty$ algebra $\cL_{sugra}$ on $\R \times \C^5$ can be written as 
-\[
-\cL_{sugra} = \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5, L) \simeq \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^5) \otimes L_0 ,
-\]
-where $L$ is a translation invariant holomorphic vector bundle and~$L_0$ its fiber over~$0 \in \C^5$.
-As in \S \ref{s:interacting}, the local $L_\infty$ algebra structure on $\cL_{sugra}$ induces an $L_\infty$ structure on the $\infty$-jets at~$0 \in \R \times \C^5$ of $\cL_{sugra}$, which we can identify using the Poincar\'e lemma with~$L_0[[z_1,\ldots,z_5]]$.
-Furthermore, the Taylor expansion map at $0 \in \R \times \C^5$ defines an $L_\infty$ map
-\[
-\cL_{sugra}(\R \times \C^5) \to L_0[[z_1,\ldots,z_5]] .
-\]
-
-In~\cite{RSW} it is shown that $L_0[[z_1,\ldots,z_5]]$ is equivalent to the super Lie algebra $\Hat{E(5|10)}$ which is the central extension of $E(5|10)$ by the cocycle in \brian{finish}. 
-There is a similar result for the restricted local $L_\infty$ algebra $\Bar{\pi}_*\cL_{sugra}$.
-
-If we take the threefold $Z = \C^3$ then of course $\R \times {\rm Tot}(K^{1/2}_Z \otimes \C^2) \simeq \R \times \C^5$.
-
-%First, we will see how to relate the decomposition at the level of global sections of~$\cL_{sugra}$ over~$Z = \C^3$.
-
-%In the decomposition \eqref{eqn:decomp2a} the
-
-\subsection{Character computations}
-
-Define the (super) character of an $E(3|6)$-module $M$ by the formula
+The (super) character of an $E(3|6)$-module $M$ is given by the formula
 \[
@@
 \]
+Our goal in this section is to compute the explicit formula for the character of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$.
+
 As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
@@
 
-Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
+%Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
 
-Given this description, there is a simple expression for the character 
+For type $A$ degenerate modules we start with the $\fg_0$-module 
 \[
-\ch\, {M(F(\lambda_1,\lambda_2;\lambda_3;y))} = q^{-\frac32 y} t_1^{\lambda_1}t_2^{\lambda_2} r^{\lambda_3} R(q,t_1,t_2,r) \cdot {\rm sdim}( V )
+V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
 \] 
-where $R = \ch \Sym(\fg_{<0})$.
+given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
+There is thus a simple expression for the character 
+\beqn\label{eqn:MA}
+\ch\, {M_A(\lambda_1,\lambda_3)} = q^{-\frac32 y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) 
+\eeqn
+where $R = \ch \Sym(\fg_{<0})$ and 
+\[
+\ch(V_A^{\lambda_1,\lambda_3}) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
+\]
+is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
+In this expression $\ch_{SU(3)}^{\lambda_1}$ is the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.
 
@@
 
-For notational simplicity, we will set $q = t^2$.
+Before moving on, we point out that in the formula for $R$ if we specialize $t_1=t_2=1$we obtain
+\[
+R(q,r) = \frac{(1-q^{1/2}r)^3 (1-q^{1/2} r^{-1})^3}{(1-q)^3} .
+\]
+Finally, in the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.
 
-\subsection{Characters for degenerate modules of type $A$} \label{s:typeA}
-
-There is a cohomological description of the irreducible modules of type $A$
+To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
 \[
@@
 From the long exact sequence \eqref{eqn:les1} we have the following expression 
-\[
-\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} = \sum_{j \geq 0} \ch M(\lambda_1+j,0,\lambda_3+j;\frac23 \lambda_1 - \lambda_3 - \frac{j}{3}) .
-\]
+\beqn
+\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
+\eeqn 
+We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
+\beqn
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
+\eeqn
 
-Let $M_j$ be the $j$th Verma module appearing in the sum above. 
-Then
+Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
+\begin{align*}
+\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{-\lambda_1-j} t_2^{\lambda_1 + j} \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
+%\\ 
+%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
+\end{align*}
+and $SU(2)$ character
+\begin{align*}
+\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
+\end{align*}
+
+Given these formulas we see that we need to compute the sum
+\begin{multline}
+\sum_{j \geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+= \frac{1}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
+= \sum_{k=0}^{\lambda_1+j} \sum_{l=0}^k 
+\end{multline}
+
+Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
+\begin{multline} 
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
+\end{multline}
+
+\parsec
+
 \beqn
@@
 \begin{align*}
-\ch I_A(\lambda_1,\lambda_3) & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\ 
+\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\
 & = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
 \end{align*}
+
+In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character specializes to
+\[
+\ch I_A(1,0)|_{t_1=t_2=1} = \frac{r^2}{(1-t^2)^3} \left[ t^2 (r^2 + r^{-2} + 1) - 3 t (r + r^{-1}) + 3 \right] .
+\]
 

### 2022-07-06 fivebranes/twisted.tex
merge

@@
-\documentclass[11pt]{amsart}%
+%\documentclass[11pt]{amsart}%
+%
+%%\usepackage{../macros-master}
+%\usepackage{macros-fivebrane}
 
-%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%
+%\begin{document}
+%
+
 \newcommand{\thfd}{\Bar{D}}
@@
 
-\begin{document}
+\section{Twisted eleven-dimensional supergravity}
 
-\section{Twisted eleven-dimensional supergravity}
-%
 \subsection{A model for minimally twisted supergravity}
@@
 
-In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze `twisted $M$ theory'. 
-This theory is obtained from \brian{finish}
+In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze twists of $M$ theory, starting with an $\Omega$-deformation of the nonminimal twist of eleven-dimensional supergravity.
+Using a type IIA description, the theory was shown to admit a description in terms of a holomorphic-topological gauge theory in five dimensions with a well-behaved quantization.
+
+The five-dimensional theory is also a $\Z/2$-graded within the BV formalism and exists on any manifold of the form
+\[
+  S\times Y
+\]
+
+where $Y$ is a holomorphic-symplectic surface and $S$ is a real oriented smooth one-dimensional manifold.
+
+The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
+\beqn
+\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
+\eeq.
+
+The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket.
+This can be extended in a graded way to the entire Dolbeault complex; \cL_{5d} is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
+The five-dimensional theory
 
@@
 
-\subsection{Twisted Backreactions}
+\subsection{States in twisted supergravity}
 
@@
 \]
+Linear combinations of such states form a dense subspace of all possible modifications at the boundary.
 
@@
 The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
-
-\brian{finish}
 

### 2022-07-06 fivebranes/kr.tex
update

@@
 \parsec[s:typeAunrefinedKR]
-In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
 From the long exact sequence \eqref{eqn:les1} we have the following expression 
@@
 We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
-\beqn
+\beqn\label{eqn:chA1}
 \ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
@@
 
-Given these formulas we see that we need to compute the sum
+We proceed to evaluate the sum in \eqref{eqn:chA1}
 \begin{multline}
-\sum_{j \geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
-= \frac{1}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
-= \sum_{k=0}^{\lambda_1+j} \sum_{l=0}^k 
+t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
+\\ \left.
+- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
 \end{multline}
@@
 \parsec
-
+In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
 \beqn

### 2022-07-07 fivebranes/kr.tex
merge

--- 2022-07-06 fivebranes/kr.tex
@@
 \begin{lem}
+\label{lem:R}
 We have
@@
 \end{lem}
+%which is
+%\[
+%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
+%\]
 
-Before moving on, we point out that in the formula for $R$ if we specialize $t_1=t_2=1$we obtain
-\[
-R(q,r) = \frac{(1-q^{1/2}r)^3 (1-q^{1/2} r^{-1})^3}{(1-q)^3} .
-\]
-Finally, in the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.
+In the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.
 
+\parsec[s:typeAunrefinedKR]
 To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
@@
 \eeqn 
-%which is
-%\[
-%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
-%\]
-
-\parsec[s:typeAunrefinedKR]
-In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
-From the long exact sequence \eqref{eqn:les1} we have the following expression 
+From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
 \beqn
@@
 \begin{align*}
-\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{-\lambda_1-j} t_2^{\lambda_1 + j} \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
+\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
 %\\ 
@@
 
-Given these formulas we see that we need to compute the sum
+We proceed to evaluate the sum in \eqref{eqn:chA1}
 \begin{multline}
-\sum_{j \geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
-= \frac{1}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
-= \sum_{k=0}^{\lambda_1+j} \sum_{l=0}^k 
+t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
+\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\
+\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
+%
+%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
+\\ \left.
+- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
 \end{multline}
+
+We split the sum $\sum_{j \geq 0}$ into four terms
+\begin{itemize}
+\item the first term is 
+\beqn
+(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
+\eeqn
+Evaluating the infinite series this becomes
+\begin{multline} 
+r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
+\end{multline}
+\item the second term is
+\beqn
+t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
+\eeqn
+\end{itemize}
 
@@
 \parsec
+In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$. 
+In this specialization it is easy to see that 
+\[
+\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
+\]
+which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.
 
-\beqn
-\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
+We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:IA1}:
+\beqn\label{eqn:chA1}
+\ch M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
 \eeqn
-Notice that 
+where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
+\[
+R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
+\]
+which we read off readily from Lemma \ref{lem:R}
+In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
 \[
@@
 \]
-so the above expression for $\ch M_j$ reduces to
-\[
-\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
-\]
-Observe the formal identity 
+
+Now, observe the formal identity 
 \[
@@
 
-In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character specializes to
-\[
-\ch I_A(1,0)|_{t_1=t_2=1} = \frac{r^2}{(1-t^2)^3} \left[ t^2 (r^2 + r^{-2} + 1) - 3 t (r + r^{-1}) + 3 \right] .
-\]
+In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
+\beqn
+\ch I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + t^6 - 3 t^4}{(1-t^2)^3} .
+\eeqn
 
-Finally, we specialize further $t=r$ and substitute $q = t^2$ to obtain
-\[
+In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
+\beqn
+\ch I_A(1,0)|_{t_1=t_2=1} = \frac{(r^2 + r^{-2} + 1) - 3 t^{-1} (r + r^{-1}) + 3t^{-2} }{(1-t^2)^3} .
+\eeqn
+\brian{The $(1,0)$ character differs from $N=2$ index by a factor of $t^6 = q^3$ as expected.}
+
+Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
+\beqn
 \ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
-\]
+\eeqn
 

### 2022-07-08 fivebranes/kr.tex
kr update

@@
 \begin{thm}[\cite{KR1}]
-The Verma modules $M_A(\lambda_1,\lambda_3)$ and $M_A(\lambda_1,\lambda_3)$ have unique irreducible quotients denoted by $I_A(\lambda_1,\lambda_3)$ and $I_B(\lambda_1,\lambda_3)$, respectively. 
+The Verma modules $M_A(\lambda_1,\lambda_3)$ and $M_A(\lambda_1,\lambda_3)$ have unique irreducible quotients denoted by 
+\beqn
+I_A(\lambda_1,\lambda_3), \quad \text{and} \quad I_B(\lambda_1,\lambda_3)
+\eeqn
+respectively. 
 Furthermore, for any $\lambda_1,\lambda_3 \in \Z_+$ one has $M_A(\lambda_1,\lambda_3) \ne I_A(\lambda_1,\lambda_3)$ and $M_B(\lambda_1,\lambda_3) \ne I_B(\lambda_1,\lambda_3)$.
@@
 
-\subsection{Characters for degenerate modules of type $A$} \label{s:typeA}
+\subsection{Modified characters for degenerate modules of type $A$} \label{s:typeA}
 
@@
 \[
-\ch \, M  \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
+\ch (M) \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
 \]
-Our goal in this section is to compute the explicit formula for the character of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$.
+Our goal in this section is to compute the explicit formula for a modified version of this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$.
 
@@
 \]
-
+We define the modified character of a Verma module by the formula
+\[
+\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
+\]
+Define
+\[
+R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
+\]
+so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the $\fg_0$ representation $V$.
 %Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
 
-For type $A$ degenerate modules we start with the $\fg_0$-module 
+Our definition of the modified character relies on a cohomological description of the irreducible modules $I_A(\lambda_1,\lambda_3)$ of type~$A$.
+%\[
+%I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
+%\]
+In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\beqn\label{eqn:les1}
+0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
+\eeqn 
+From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
+\beqn
+\label{eqn:chA1}
+\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
+\eeqn 
+Like the Verma modules, we can defined a modified version of this character by the formula
+\beqn
+\label{eqn:chA2}
+\til \ch \, I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \til\ch \, M_A(\lambda_1+j,\lambda_3+j)  .
+\eeqn
+
+We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term the sum in \eqref{eqn:chA1}
+\beqn\label{eqn:chA3}
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
+\eeqn
+And similarly for the sum in \eqref{eqn:chA2}.
+
+The first ingredient in determining an explicit formula for the modified character of type $A$ Verma modules is a direct calculation.
+\begin{lem}
+\label{lem:R}
+Then
+%\beqn
+%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+%\eeqn
+\beqn
+R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+\eeqn
+\end{lem}
+
+Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
 \[
@@
 given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
-There is thus a simple expression for the character 
+Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
+\begin{prop}
+One has
 \beqn\label{eqn:MA}
-\ch\, {M_A(\lambda_1,\lambda_3)} = q^{-\frac32 y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) 
+\til \ch \, {M_A(\lambda_1,\lambda_3)} = q^{y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r^{-1})
 \eeqn
-where $R = \ch \Sym(\fg_{<0})$ and 
-\[
+where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
+\beqn\label{eqn:su}
 \ch(V_A^{\lambda_1,\lambda_3}) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
-\]
+\eeqn
 is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
-In this expression $\ch_{SU(3)}^{\lambda_1}$ is the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.
+\end{prop}
 
-\begin{lem}
-\label{lem:R}
-We have
-\beqn
-R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
-\eeqn
-\end{lem}
+In expression \eqref{eqn:su}, $\ch_{SU(3)}^{\lambda_1}$ denotes the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.
+
 %which is
@@
 In the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.
-
-\parsec[s:typeAunrefinedKR]
-To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
-\[
-I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
-\]
-In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
-\beqn\label{eqn:les1}
-0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
-\eeqn 
-From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
-\beqn
-\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
-\eeqn 
-We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
-\beqn\label{eqn:chA1}
-\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
-\eeqn
 
@@
 In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.
+
+\begin{prop}
+\label{prop:chA}
+Let $\lambda_1,\lambda_3 \geq 0$. 
+The $t_1=t_2=1$ specialization of the modified character $\til \ch \, I_A(\lambda_1,\lambda_3)$ is given by the expression
+\beqn
+\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
+\eeqn
+where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
+\end{prop}
+
+\begin{proof}
 In this specialization it is easy to see that 
@@
 
-We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:IA1}:
-\beqn\label{eqn:chA1}
-\ch M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
+We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
+\beqn
+\til\ch M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^{-j} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
 \eeqn
@@
 \]
-which we read off readily from Lemma \ref{lem:R}
+which we read off from Lemma \ref{lem:R}.
 In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
@@
 \[
-\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
+\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
 \]
-where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.
-
+where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
 Using this identity, we evaluate
 \begin{align*}
-\ch I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{3 \lambda_3 - 2 \lambda_1}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p(tr)}{(1-tr)^3} - \frac{r^{-\lambda_3-2}p(tr^{-1})}{(1-tr^{-1})^3} \right) \\
-& = \frac{t^{3 \lambda_3-2\lambda_1}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p(tr) (1-tr^{-1})^3 - r^{-\lambda_3-2} p(tr^{-1})(1-tr)^3 \right) .
+\til \ch \, I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\
+& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
 \end{align*}
+This completes the proof
+\end{proof}
 
@@
 \beqn
-\ch I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + t^6 - 3 t^4}{(1-t^2)^3} .
+\til \ch \, I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
 \eeqn
@@
 \beqn
-\ch I_A(1,0)|_{t_1=t_2=1} = \frac{(r^2 + r^{-2} + 1) - 3 t^{-1} (r + r^{-1}) + 3t^{-2} }{(1-t^2)^3} .
+\til \ch \, I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
 \eeqn
-\brian{The $(1,0)$ character differs from $N=2$ index by a factor of $t^6 = q^3$ as expected.}
 
@@
 \beqn
-\ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
+\til \ch \, I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
 \eeqn
@@
 There is a cohomological description of the irreducible modules of type B similar to the type A case above.
-Let $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
-We are only interested in the case $\lambda_1 = 0$ with $\lambda_3=0,1,\ldots$.  
+Recall that the degenerate module of type $B$ is $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
+We are only interested in the case $\lambda_1 = 0$ with $\lambda_3\geq 0$.  
 In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
 \begin{multline}\label{eqn:les1}
-0 \leftarrow  I_B(0,\lambda_3) \leftarrow \\ \leftarrow M(0,0,\lambda_3;\lambda_3 + 2) \leftarrow  M(1,0,\lambda_3-1;\frac{11}{3} - \lambda_3)  \leftarrow \cdots \leftarrow M(\lambda_3, 0, 0;\frac23 \lambda_3 +2) \leftarrow \\
- \leftarrow M(\lambda_3+2, 0, 0; \frac23 \lambda_3 + \frac43) \leftarrow M(\lambda_3+3, 0, 1; \frac23 \lambda_3 + 2) \leftarrow \cdots .
+0 \leftarrow  I_B(0,\lambda_3) \\ \leftarrow M_B(0,\lambda_3) \leftarrow  M_B(1,\lambda_3-1)  \leftarrow \cdots \leftarrow M(\lambda_3, 0) \\
+ \leftarrow M_A(\lambda_3+2, 0) \leftarrow M_A(\lambda_3+3,1) \leftarrow \cdots .
 \end{multline}
 There are $\lambda_3+1$ terms in the second line above .  
+Notice that the bottom line is simply the resolution for the module $I(\lambda_3+2, 0)$ of type $A$. 
+Using this long exact sequence we obtain a simple formula for the character of type $B$ modules
+\beqn\label{eqn:chB1}
+\ch I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3} \ch M_B(k, \lambda_3-k) + \ch I_A(\lambda_3+2,0) .
+\eeqn
+And similarly we have the following formula for the modified character
+\beqn\label{eqn:chB2}
+\til \ch \, I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3}\til \ch\, M_B(k, \lambda_3-k) + \til \ch \, I_A(\lambda_3+2,0) .
+\eeqn
+
+\begin{prop}
+\label{prop:chB}
+The modified character $\til \ch \, I_B(0,\lambda_3)$ is given by the expression
+\begin{multline}
+t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+\end{multline}
+where $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chA}. 
+\end{prop}
+
+\begin{proof}
+We have already computed $\til \ch \, I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ above. 
+Thus, it suffices to compute the modified character of the type $B$ Verma modules.
+
+As above, the modified character for the Verma module $M_B(k,\lambda_3-k)$, for $0 \leq k \leq \lambda_3$ is given by
+\[
+\til \ch \, M_B(k,\lambda_3-k)|_{t_1=t_2=1} = t^{3 \lambda_3 - k + 6} R(t,r) .
+\]
+Thus, \eqref{eqn:chB2} simplifies to 
+\[
+\til \ch \, I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \til \ch \, I_{A}(\lambda_3+2,0) .
+\]
+The result now follows from Proposition \ref{prop:chA}.
+\end{proof}
 
@@
 
+For integer $N$ let 
+\[
+p_{N}(x) = \frac12 \left(N^2 x^2 + N x^2 - 2N^2x -4 N x + N^2 + 3N +2\right) .
+\]
+Then the index for $N > 2$ fivebranes after specializing the $SU(3)$ fugacities is
+\begin{multline}
+t^{2 N} \frac{(1-tr)^3 (1-tr^{-1})^3 (1-t^{\lambda_3+1})}{(1-t^2)^3(1 - t)} \\ + \frac{t^{2N + 4}}{(1-t^2)^3 (1-r^{-2})} \left(p_{N-1} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{N-1}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+\end{multline}
+
 \end{document}

### 2022-07-08 fivebranes/intro.tex
merge

\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
\usepackage{macros-fivebrane}
%
\begin{document}

\section{Introduction}

The six-dimensional $\cN=(2,0)$ supersymmetric theory

In this paper we apply the proposal of \textit{twisted holography} introduced by Costello and Li in \cite{CLsugra} to access the worldvolume theory on a stack of fivebranes in minimally twisted eleven-dimensional supergravity.
Twisted holography shares, in many ways, the spirit of familiar gauge-gravity dualities such as the AdS/CFT correspondence. 
The heart of the program relates the algebra of observables of the bulk gravity theory, which lives on a twisted version of AdS space, to the observables of the worldvolume theory living on a defect, which plays the role of the CFT.

\end{document}

### 2022-07-09 fivebranes/twisted.tex
twisted membranes

@@
 Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
-In any theory of supergravity, there is an collection of bosonic ghosts which, in part, incorporate local supersymmetry.
+In any theory of supergravity, the action of supersymmetry is gauged.
+When one treats the theory in the BRST formalism, the fields then include a collection of bosonic ghosts which homologically enforce invariance under the odd gauge symmetries.
+
 By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.
@@
 \cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
-\eeq.
+\eeq
 
-The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket.
-This can be extended in a graded way to the entire Dolbeault complex; \cL_{5d} is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
-The five-dimensional theory
+The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket $\{-,-\}_{Y}$.
+This can be extended in a graded way to the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
+
+Wedging and integrating against the holomorphic volume form on $Y$ defines an odd pairing on $\cL_{5d}$; together with the above, this equips $\cL_{5d}$ with the structure of a $\Z/2$-graded BV theory.
+
+The equations of motion of $\cL_{5d}$ describe locally-constant families of deformations of the fixed holomorphic Poisson structure on $Y$.
 
@@
 \cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
+\]
+
+\subsection{Twisted membranes}
+
+The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory - a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{} For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect.
+\cite{}
+
+Twists of $\cN=8$ gauge theories in 3d were classified in \cite{}.
+Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{}.
+Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:
+
+\begin{itemize}
+  \item The minimal twist.
+This twist leaves 2 real directions invariant.
+The theory can be defined on a 3-manifold of the form $S\times \Sigma$ where $S$ is a smooth oriented one-manifold and $\Sigma$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
+
+  \item The nonminimal twists. There are two such twists, both of which leave 3 real directions invariant, and are permuted under 3d mirror symmetry.
+\end{itemize}
+
+\parsec
+
+We briefly recall the description of the minimal twist of the ABJM theory for $N=1$.
+
+\surya{fields, gauge symmetries, etc}
+
+In the BV formalism, this free theory can be packaged into the data of an abelian $\Z$ graded local Lie algebra on $\Sigma$ which takes the form
+\[
+\Omega^{\bu}(S)\times \left (\Omega^{0,\bu}(\Sigma) \oplus \Pi \Omega^{0,\bu} (\Sigma )\right ) \otimes \C^{4}.
 \]

### 2022-07-09 fivebranes/index.tex
reorganizing

@@
 
-operators, indices, etc..
-relationship to the $S^5$ partition function.
+\subsection{States in twisted supergravity}
+
+In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \brian{references}.
+
+In \cite{RSW} we gave descriptions of twisted versions of these backgrounds.
+We recall this construction, adapted to a slightly more global situation.
+We will consider the eleven-dimensional theory on 11-manifolds that arise as total spaces of vector bundles.
+Placing the theory in the backreacted geometry is a 3-step procedure:
+
+\begin{itemize}
+  \item Place the eleven dimensional theory on the complement of the zero section.
+To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.
+
+  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element.
+  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
+
+  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.
+
+\end{itemize}
+
+\parsec[s:brkevin]
+
+As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping
+\[
+0 \times 0 \times C \subset \R \times \C \times C .
+\]
+It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$.
+Denote by $(t,w)$ the fiber coordinates.
+Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background.
+We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
+We first proceed before turning on the backreaction.
+
+If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection ${\rm Tot}(\R \oplus K_C) \to \R_+ \times C$ which combines the fiberwise norm with the natural bundle projection.
+Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
+The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
+
+Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
+We will elaborate on the appearance of this sort of cohomology momentarily.
+The theory admits a natural `vacuum' boundary condition at $r=0$.
+In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.
+
+The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
+The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
+Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.
+
+Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
+\[
+\alpha = f(w) \delta^{(r)}_{z=0}
+\]
+where $f$ is some holomorphic function.
+Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
+It is convenient to parameterize such boundary modifications algebraically by expressions of the form
+\[
+\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
+\]
+Linear combinations of such states form a dense subspace of all possible modifications at the boundary.
+
+The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
+The phase space at the boundary $C$ can be identified with the following cohomology
+\[
+\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
+\]
+where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation.
+We refer to the section below for a reminder on this geometric structure.
+
+The phase space is equipped with a natural symplectic form given by
+\[
+\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
+\]
+There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
+The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
+
+\parsec[s:brfive]
+
+We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
+Let $Z$ be a three-fold that the fivebranes wrap.
+We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$.
+The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.
+The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
+
+We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus V$.
+Denote the complement of the zero section by
+\[
+M_V = \text{Tot}(\R\oplus V) - 0(Z).
+\]
+Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
+The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
+
+A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
+We will say that $F$ equips $M$ with the a THF structure.
+%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
+The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection.
+Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
+The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s.
+(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
+
+Any submanifold of a THF manifold is itself a THF manifold.
+We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
+
+We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
+Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex
+\beqn\label{eqn:drdol}
+\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
+\eeqn
+As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
+More generally, there is a natural cohomology associated to a THF structure.
+Suppose $(M,F)$ is a THF structure and
+denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
+For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
+The derivative along the leaves of the foliation defined by $V$ defines a map
+\[
+\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
+\]
+By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
+Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
+There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
+The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
+\[
+\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
+\]
+with the structure of a bigraded commutative dg algebra.
+This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
+For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
+\beqn\label{thfcoh1}
+\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
+\eeqn
+We leave the $\thfd$ operator implicit in the presentation on the right hand side.
+When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
+There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
+
+%Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
+With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes.
+We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus V$ over $Z$ and a fiberwise partially hermitian metric.
+Explicitly, the corresponding norm defines a map
+\begin{align*}
+ h \colon  \R\times X & \to \R_{+} \\
+  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
+\end{align*}
+Letting $\pi \colon \R\times X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
+\[
+p \define (h,\pi) \colon \R \times X \to \R_{+}\times Z
+\]
+which restricts to an $S^4$ bundle $p|M \colon M \to \R_{>0} \times Z$.
+These embeddings and projections fit inside of the following commutative diagram
+\[
+\begin{tikzcd}
+M \ar[d,"p|M"'] \ar[r,hook] & \R \times X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
+\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
+\end{tikzcd}
+\]
+The inclusions on the left are the natural embeddings.
+The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = \R \times X$ and the bottom right inclusion is the embedding at radius $r = 0$.
+
+As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$.
+Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|M$.
+The resulting sheaf of $L_\infty$ algebras $(p|M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
+
+The theory on $M$ extends to a theory on the manifold obtained by filling in the zero section of $\R \times V$; in other words, we know that the theory is defined on the entire space $\R \times X$.
+This means that there is a natural way to extend the theory on $\R_{>0} \times Z$ to the seven-manifold with boundary $\R_{+} \times Z$.
+The restriction of this theory to the six-dimensional boundary plays the most important role for us.
+
+\brian{trying to incorporate below}
+%To do this we will make use of the natural foliated geometric structures which we have around.
+
+Let $V_{M}$ denote the vertical tangent bundle to $(h, \pi)$, which we view as a subbundle of the real tangent bundle $T_{M}$.
+The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, if $\iota \colon M \to \R\times X$ is inclusion, then we consider the pair
+\[
+  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
+\]
+
+The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure.
+\surya{CITE}
+
+ The underlying sheaf of cochain complexes is given by
+
+\[
+\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
+\ul{\rm even} & \ul{\rm odd} \\
+\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
+\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
+\end{tikzcd}
+ \right ) \otimes CR (S^{4}).
+\]
+
+Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure.
+Its computation is facilitated by the following lemma:
+
+\begin{lem}
+  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric.
+Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure.
+Then there is a quasi-isomorphism
+
+  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]
+
+  where the right-hand-side denotes the Dolbeault-deRham complex.
+\end{lem}
+
+The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
+
+It was argued in \cite{RSW} that to leading order the coupling of a stack of twisted fivebranes to the eleven-dimensional theory is given by the nonlocal interaction
+\beqn\label{eqn:br1}
+I_{M5} = N\int_{Z} \div^{-1}\mu \vee \Omega +\cdots
+\eeqn
+where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.
+
+\parsec
+Let $C$ be a curve, and let $V\to C$ be a rank 4-holomorphic vector bundle over $C$ such that $\wedge^{4} V = K_{C}$.
+This condition again ensures that $X = {\rm Tot} V$ is a Calabi-Yau five-fold - in the main body of the paper, we will take $V = K^{1/2}_{C}\otimes \C^{4}$.
+Abusively letting $V$ also denote its pullback along the canonical projection $\R\times C \to C$, we may view $\R\times X$ as the total space of $V$ on $\R\times C$.
+As before we will consider wrapping a stack of $N$ membranes along the zero section.
+
+Since $V$ is a complex vector bundle, we may choose a fiberwise hermitian metric, and as before, we may view $\R\times X \setminus \R\times C$ as an $S^{7}$-bundle over $\R_{>0}\times \R\times C$.
 

### 2022-07-09 fivebranes/twisted.tex
reorganizing

@@
 
-\section{Twisted eleven-dimensional supergravity}
+\section{Twists in dimensions three, six, and eleven}
 
@@
 
+It is expected that the theory on a stack of $N$ fivebranes in flat space has $\cN=(2,0)$ superconformal symmetry.
 Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
@@
 
-By standard arguments, the theory on a stack of $N$ fivebranes in flat space is a theory with $\cN=(2,0)$ supersymmetry. 
-In later sections we provide arguments using the technology of twisted holography developed by Costello, Gaiotto, Li, and Paquette \cite{??} to provide a conjectural description of the twist of the theory for general $N > 1$.
-An explicit characterization of the holomorphic and non-minimal twists of a single fivebrane theory has been given in \cite{SWtensor}. 
-We briefly recall this description.
+An explicit characterization of these twists for $N=1$ has been given in \cite{SWtensor}; we recall the description of the minimal twist.
 
@@
 \]
-
-\subsection{States in twisted supergravity}
-
-In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \brian{references}.
-
-In \cite{RSW} we gave descriptions of twisted versions of these backgrounds.
-We recall this construction, adapted to a slightly more global situation.
-We will consider the eleven-dimensional theory on 11-manifolds that arise as total spaces of vector bundles.
-Placing the theory in the backreacted geometry is a 3-step procedure:
-
-\begin{itemize}
-  \item Place the eleven dimensional theory on the complement of the zero section.
-To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.
-
-  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element. 
-  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
-
-  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.
-
-\end{itemize}
-
-\parsec[s:brkevin]
-
-As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping
-\[
-0 \times 0 \times C \subset \R \times \C \times C .
-\]
-It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$. 
-Denote by $(t,w)$ the fiber coordinates.
-Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background. 
-We proceed to describe the twisted version of states at the boundary of this version of $AdS$. 
-We first proceed before turning on the backreaction.
-
-If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection ${\rm Tot}(\R \oplus K_C) \to \R_+ \times C$ which combines the fiberwise norm with the natural bundle projection.
-Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate. 
-The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
-
-Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
-We will elaborate on the appearance of this sort of cohomology momentarily.
-The theory admits a natural `vacuum' boundary condition at $r=0$.
-In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.
-
-The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point. 
-The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$. 
-Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.
-
-Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
-\[
-\alpha = f(w) \delta^{(r)}_{z=0} 
-\]
-where $f$ is some holomorphic function. 
-Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$. 
-It is convenient to parameterize such boundary modifications algebraically by expressions of the form 
-\[
-\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
-\]
-Linear combinations of such states form a dense subspace of all possible modifications at the boundary.
-
-The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
-The phase space at the boundary $C$ can be identified with the following cohomology
-\[
-\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
-\]
-where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation. 
-We refer to the section below for a reminder on this geometric structure.
-
-The phase space is equipped with a natural symplectic form given by
-\[
-\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
-\]
-There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
-The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
-
-\parsec[s:brfive]
-
-We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
-Let $Z$ be a three-fold that the fivebranes wrap. 
-We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$. 
-The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$. 
-The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
-
-We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus V$.
-Denote the complement of the zero section by
-\[
-M_V = \text{Tot}(\R\oplus V) - 0(Z).
-\]
-Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
-The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
-
-A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$. 
-We will say that $F$ equips $M$ with the a THF structure. 
-%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
-The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection. 
-Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
-The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s. 
-(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
-
-Any submanifold of a THF manifold is itself a THF manifold. 
-We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
-
-We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology. 
-Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex 
-\beqn\label{eqn:drdol}
-\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
-\eeqn
-As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
-More generally, there is a natural cohomology associated to a THF structure.
-Suppose $(M,F)$ is a THF structure and 
-denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
-For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$. 
-The derivative along the leaves of the foliation defined by $V$ defines a map 
-\[
-\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
-\]
-By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$. 
-Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$. 
-There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$. 
-The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows 
-\[
-\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right) 
-\]
-with the structure of a bigraded commutative dg algebra.
-This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes. 
-For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra 
-\beqn\label{thfcoh1}
-\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
-\eeqn
-We leave the $\thfd$ operator implicit in the presentation on the right hand side.
-When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
-There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
-
-%Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
-With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes. 
-We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus V$ over $Z$ and a fiberwise partially hermitian metric. 
-Explicitly, the corresponding norm defines a map
-\begin{align*}
- h \colon  \R\times X & \to \R_{+} \\
-  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
-\end{align*}
-Letting $\pi \colon \R\times X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle 
-\[
-p \define (h,\pi) \colon \R \times X \to \R_{+}\times Z 
-\] 
-which restricts to an $S^4$ bundle $p|M \colon M \to \R_{>0} \times Z$.
-These embeddings and projections fit inside of the following commutative diagram
-\[
-\begin{tikzcd} 
-M \ar[d,"p|M"'] \ar[r,hook] & \R \times X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
-\R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
-\end{tikzcd}
-\]
-The inclusions on the left are the natural embeddings. 
-The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = \R \times X$ and the bottom right inclusion is the embedding at radius $r = 0$.
-
-As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$. 
-Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|M$.
-The resulting sheaf of $L_\infty$ algebras $(p|M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
-
-The theory on $M$ extends to a theory on the manifold obtained by filling in the zero section of $\R \times V$; in other words, we know that the theory is defined on the entire space $\R \times X$.
-This means that there is a natural way to extend the theory on $\R_{>0} \times Z$ to the seven-manifold with boundary $\R_{+} \times Z$. 
-The restriction of this theory to the six-dimensional boundary plays the most important role for us.
-
-\brian{trying to incorporate below}
-%To do this we will make use of the natural foliated geometric structures which we have around.
-
-Let $V_{M}$ denote the vertical tangent bundle to $(h, \pi)$, which we view as a subbundle of the real tangent bundle $T_{M}$. 
-The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, if $\iota \colon M \to \R\times X$ is inclusion, then we consider the pair
-\[
-  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
-\]
-
-The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure.
-\surya{CITE}
-
- The underlying sheaf of cochain complexes is given by
-
-\[
-\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
-\ul{\rm even} & \ul{\rm odd} \\
-\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
-\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
-\end{tikzcd}
- \right ) \otimes CR (S^{4}).
-\]
-
-Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure.
-Its computation is facilitated by the following lemma:
-
-\begin{lem}
-  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric.
-Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure.
-Then there is a quasi-isomorphism
-
-  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]
-
-  where the right-hand-side denotes the Dolbeault-deRham complex.
-\end{lem}
-
-The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
-
-It was argued in \cite{RSW} that to leading order the coupling of a stack of twisted fivebranes to the eleven-dimensional theory is given by the nonlocal interaction 
-\beqn\label{eqn:br1}
-I_{M5} = N\int_{Z} \div^{-1}\mu \vee \Omega +\cdots 
-\eeqn
-where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.
-
-\parsec
-Let $C$ be a curve, and let $V\to C$ be a rank 4-holomorphic vector bundle over $C$ such that $\wedge^{4} V = K_{C}$.
-This condition again ensures that $X = {\rm Tot} V$ is a Calabi-Yau five-fold - in the main body of the paper, we will take $V = K^{1/2}_{C}\otimes \C^{4}$.
-Abusively letting $V$ also denote its pullback along the canonical projection $\R\times C \to C$, we may view $\R\times X$ as the total space of $V$ on $\R\times C$.
-As before we will consider wrapping a stack of $N$ membranes along the zero section.
-
-Since $V$ is a complex vector bundle, we may choose a fiberwise hermitian metric, and as before, we may view $\R\times X \setminus \R\times C$ as an $S^{7}$-bundle over $\R_{>0}\times \R\times C$.
 

### 2022-07-11 fivebranes/twisted.tex

@@
 
-\section{Twists in dimensions three, six, and eleven}
+\section{Twists in dimensions eleven, six, and three}
 
@@
 
-By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a twisting supercharge.
+By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge.
+Such backgrounds have the feature that the worldvolume theories of branes in their presence are twisted.
 
-Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
+Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of $Q$.
 \begin{itemize}
@@
 
-In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze twists of $M$ theory, starting with an $\Omega$-deformation of the nonminimal twist of eleven-dimensional supergravity.
-Using a type IIA description, the theory was shown to admit a description in terms of a holomorphic-topological gauge theory in five dimensions with a well-behaved quantization.
+\surya{ FINISH }
 
-The five-dimensional theory is also a $\Z/2$-graded within the BV formalism and exists on any manifold of the form
+In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists.
+
+The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
+
+The five-dimensional theory is $\Z$-graded within the BV formalism and exists on any manifold of the form
 \[
@@
 
-The fields of the theory are given by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
+As a gauge theory, the fundamental field is a one-form. The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
+\[
+\oplus_{k+p+q=1}\Omega^{k}(S)\otimes \Omega^{p,q}(Y).
+\]
+
+and we continue to label elements of the homogeneous pieces as $(k;p,q)$ forms.
+The fields of ghost number zero are those one-forms with $p=0$.
+We will use the notation $\alpha^{k;q}$ with $k+q=1$ for the corresponding component of the one-form.
+
+These fields are subject to the equations of motion
+
+\beqn
+0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y
+0 = d\alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
+\eeqn
+
+where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$.
+
+We may get a better feeling for these equations upon giving $\alpha^{{1;0}}$ a VEV such that $\dbar\alpha^{{1;0}}=0$. The secnod equation then reads
+
+\beqn
+0 = d\alpha^{0;1} + \{\alpha^{1;0}, \alpha^{0;1}\}
+\eqn
+
+The fields $\alpha^{{k;q}}$ have a gauge symmetry determined by a ghost $b \in \Omega^{0}(S\times Y)$. Explicitly, the corresponding infinitessimal gauge transformation is given by
+\[
+\alpha^{k;q}\mapsto \alpha^{k;q} + db+\dbar b + \{b, \alpha^{k;q}\}_{Y}
+\].
+
+In the BV formalism, the fields are described by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
+
 \beqn
 \cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
-\eeq
+\eeqn
 
-The sheaf of holomorphic functions on $Y$ has a natural lie bracket given by the holomorphic poisson bracket $\{-,-\}_{Y}$.
-This can be extended in a graded way to the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
+The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a lie bracket on the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
 
 Wedging and integrating against the holomorphic volume form on $Y$ defines an odd pairing on $\cL_{5d}$; together with the above, this equips $\cL_{5d}$ with the structure of a $\Z/2$-graded BV theory.
-
-The equations of motion of $\cL_{5d}$ describe locally-constant families of deformations of the fixed holomorphic Poisson structure on $Y$.
 
@@
 We describe this Poisson bivector explicitly
-
+\surya{ FINISH }
 In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 

### 2022-07-18 fivebranes/twisted.tex
merge

@@
-%\documentclass[11pt]{amsart}%
+\documentclass[11pt]{amsart}%
 %
 %%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
+\usepackage{macros-fivebrane}
 
 %
-%\begin{document}
+\begin{document}
 %
-
-\newcommand{\thfd}{\Bar{D}}
-\newcommand{\thfdel}{D}
 
@@
 
-Eleven-dimensional supergravity is the unique supersymmetric theory in eleven dimensions.
-It plays an important role as the low energy limit of $M$ theory.
+%Eleven-dimensional supergravity is the unique supersymmetric theory in eleven dimensions.
+%It plays an important role as the low energy limit of $M$-theory.
 
 Recently in \cite{CLsugra}, Costello and Li gave a rigorous definition of twisted supergravity.
+The idea is roughly the following.
 In any theory of supergravity, the action of supersymmetry is gauged. 
 When one treats the theory in the BRST formalism, the fields then include a collection of bosonic ghosts which homologically enforce invariance under the odd gauge symmetries.
-
 By definition, twisted supergravity is supergravity in the background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge. 
-Such backgrounds have the feature that the worldvolume theories of branes in their presence are twisted.
+Such backgrounds have the feature that the worldvolume theories of branes in their presence are twisted in a way that is compatible with the usual notion of twisting supersymmetric gauge theories.
 
@@
 In \cite{RSW} we have given a proposal for the minimal twist of fully interacting eleven-dimensional supergravity as a $\Z/2$ graded interacting BV theory in a background with global symmetry group $SU(5)$.
-Globally, the eleven-dimensional theory exists on any manifold of the form 
+
+The eleven-dimensional theory exists on any manifold which is locally of the form 
 \[
@@
 where $X$ is a Calabi--Yau fivefold and $S$ is a real oriented smooth one-dimensional manifold.
+More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
 
-In the first few sections we describe the fields and equations of motion of the eleven-dimensional theory.
+In the first few sections we recall the fields and equations of motion of this eleven-dimensional theory.
 
@@
 To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
-The theory utilizes the complex structure on the Calabi--Yau fivefold $X$.
+Let's first consider the case that the eleven-dimensional manifold is of the form $S \times X$, where $X$ is a Calabi--Yau fivefold.
 We let $\T_X$ stand for the holomorphic tangent bundle of $X$ and $\Bar{\T}_X$ its complex conjugate.
-Thus, the complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
+The complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
 \[
@@
 \]
-are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra \cite{??}. 
+are multilinear maps which satisfy the ordinary higher Jacobi relations defining an $L_\infty$ algebra.
 The shift $[2-k]$ means that $[-]_k$ is of cohomological degree $k-2$.
@@
 There is an overall shift in the relationship between the cohomological grading of $\cL$ and the ghost number in physics terminology. 
-In cohomological degree zero sit the ghosts, in cohomological degree zero sit the fields, etc..
+In cohomological degree zero of $\cL$ sit the ghosts, in cohomological degree one sit the fields, etc..
 In this sense it is more accurate to refer to the BV fields as sections of the shift of the sheaf of $L_\infty$ algebras $\cL[1]$. 
-Together with the skew symmetric pairing $\omega_{BV}$ on the fields structure maps $[-]_k$ organize together to define the full BV action which takes the general form
-\[
-S(\Phi) = \sum_{k \geq 1} \omega_{BV} \left(\Phi , [\Phi,\ldots,\Phi]_{k}\right) .
-\]
+We refer to \cite{CG2,ESW} for a further review of these conventions.
+Together with the skew symmetric pairing $\omega_{BV}$ of cohomological degree $-1$ on $\cL[1]$, the structure maps $[-]_k$ organize together to define the full BV action which takes the general form
+\beqn
+\label{eqn:Sbv}
+S(\Phi) = \sum_{k \geq 1} \omega_{BV} \left(\Phi , [\Phi,\ldots,\Phi]_{k}\right) ,
+\eeqn
+which we can think of as a functional on $\cL[1]$ of cohomological degree zero.
 
@@
 
-Finally, to obtain a local $L_\infty$ algebra on $X \times S$, where $S$ denotes an arbitrary real oriented smooth one-manifold, we simply tensor with the de Rham complex along~$S$.
+Finally, to obtain a local $L_\infty$ algebra on $S \times X$, where $S$ denotes a real oriented smooth one-manifold, we simply tensor with the de Rham complex along~$S$.
 We denote by $\cL_{sugra}$ the following local $\Z/2$ graded $L_\infty$ algebra on $X \times S$
@@
 
-\parsec[s:rsw]
-It is shown in \cite{RSW} that $\cL_{sugra}$ is equipped with a non-degenerate odd pairing which is compatible with the $L_\infty$ structure above. 
-All together, this data prescribes the structure of a $\Z/2$ graded theory in the BV formalism. 
-On $X \times S = \C^5 \times \R$ it is furthermore argued in \cite{RSW} that this BV theory is equivalent to the holomorphic (or minimal) twist of perturbative eleven-dimensional supergravity.
+It is shown in \cite{RSW} that $\cL_{sugra}$ is equipped with a non-degenerate skew symmetric odd pairing $\omega_{BV,sugra}$ which is compatible with the $L_\infty$ structure above. 
+All together, this data prescribes the structure of a $\Z/2$ graded theory in the BV formalism where the BV action is as in \eqref{eqn:Sbv}.
 
 Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.
-\brian{elaborate gauge symmetries, write action, etc.}
 
@@
 
-\surya{ FINISH }
+Before proceeding with the appearance of extended objects such as membranes and fivebranes in the minimal twist of eleven-dimensional supergravity we discuss a related, but simpler, five-dimensional theory.
+This five-dimensional theory, as argued by Costello \cite{CostelloM5}, arises from placing eleven-dimensional supergravity in the so-called `twisted $\Omega$-background'.
+We will use this theory for the sake of highlighting more accessible examples of the constructions later on in the paper.
 
-In \cite{CostelloM5,CostelloM2}, Costello introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists.
-
+In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists defined on multi Taub--NUT spaces.
 The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
 
-The five-dimensional theory is $\Z$-graded within the BV formalism and exists on any manifold of the form
+The five-dimensional theory exists on any manifold of the form
 \[
@@
 \]
+where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.
 
-where $Y$ is a holomorphic-symplectic surface and $S$ is a real oriented smooth one-dimensional manifold.
-
-As a gauge theory, the fundamental field is a one-form. The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
+The fundamental field of the five-dimensional theory is a one-form. 
+The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
 \[
@@
 \]
-
-and we continue to label elements of the homogeneous pieces as $(k;p,q)$ forms.
+We continue to label elements of the homogeneous pieces as $(k;p,q)$ forms. 
 The fields of ghost number zero are those one-forms with $p=0$. 
@@
 
+\brian{this is just the `semi-classical' limit of what Kevin looks at?}
 These fields are subject to the equations of motion
+\beqn
+0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y , \qquad
+0 = \d \alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
+\eeqn
+where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
 
-\beqn
-0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y
-0 = d\alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
-\eeqn
+%We may get a better feeling for these equations after assuming that $\alpha^{1;0}$ is holomorphic $\alpha^{{1;0}}$ a VEV such that $\dbar\alpha^{{1;0}}=0$. 
+%The second equation then reads
+%
+%\beqn
+%0 = d\alpha^{0;1} + \{\alpha^{1;0}, \alpha^{0;1}\}
+%\eeqn
 
-where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$.
-
-We may get a better feeling for these equations upon giving $\alpha^{{1;0}}$ a VEV such that $\dbar\alpha^{{1;0}}=0$. The secnod equation then reads
-
-\beqn
-0 = d\alpha^{0;1} + \{\alpha^{1;0}, \alpha^{0;1}\}
-\eqn
-
-The fields $\alpha^{{k;q}}$ have a gauge symmetry determined by a ghost $b \in \Omega^{0}(S\times Y)$. Explicitly, the corresponding infinitessimal gauge transformation is given by
+There is a non-linear gauge symmetry determined by a ghost $b \in C^\infty (S\times Y)$. 
+Explicitly, the corresponding infinitesimal gauge transformation is given by
 \[
 \alpha^{k;q}\mapsto \alpha^{k;q} + db+\dbar b + \{b, \alpha^{k;q}\}_{Y}
-\].
+\]
 
-In the BV formalism, the fields are described by a local dg-lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
-
+In the BV formalism, the full space of BV fields together with equations of motion and gauge symmetries can described by a local dg Lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
 \beqn
-\cL_{5d} \define \Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
+\Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
 \eeqn
-
-The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a lie bracket on the entire Dolbeault complex; $\cL_{5d}$ is then the tensor product of a commutative algebra and a lie algebra so is canonically a local dg-lie algebra.
-
-Wedging and integrating against the holomorphic volume form on $Y$ defines an odd pairing on $\cL_{5d}$; together with the above, this equips $\cL_{5d}$ with the structure of a $\Z/2$-graded BV theory.
+The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a Lie bracket on the entire Dolbeault complex $\Omega^{0,\bu}(Y)$.
+The dg lie algebra structure is then obtained by the tensor product with the commutative dg algebra $\Omega^\bu(S)$. 
+The BV pairing is given by integrating against the holomorphic volume form on $Y$.
 
@@
 
-It is expected that the theory on a stack of $N$ fivebranes in flat space has $\cN=(2,0)$ superconformal symmetry.
+It is expected that the worldvolume theory of fivebranes in $M$-theory on flat space is equipped with $\cN=(2,0)$ superconformal symmetry. 
 Six-dimensional $\cN=(2,0)$ supersymmetry admits two inequivalent classes of twists characterized by the number of directions which are left invariant:
@@
 
-An explicit characterization of these twists for $N=1$ has been given in \cite{SWtensor}; we recall the description of the minimal twist.
+An explicit characterization of these twists in the case of the stack of a single fivebrane has been given in \cite{SWtensor}.
+We recall the description of the minimal twist.
 
@@
 \[
-\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
+\cL_{N=1} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
 \]

### 2022-07-18 fivebranes/twisted.tex
merge

@@
 
-Before giving a rigorous description of the fields and equations of motion, we focus on bosonic fields in our model which have an obvious analog in the untwisted theory. 
+Before giving a full description of the fields and equations of motion wrapped up into the BV formalism, we give an explicit description of the equations of motion and gauge symmetries.
+
 One of the primary fields of eleven-dimensional supergravity describes deformations of the metric $g$.
@@
 \[
-\mu = \mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_i} .
+\mu^{\Bar{i}}_j (t;z,\zbar) \d \zbar_{\Bar{i}} \otimes \del_{z_j} .
 \]
-Part of the equations of motion for $\mu$ dictate that it be locally constant along~$S$.
-Ordinarily, for $\mu$ to describe a deformation of complex structure in the $X$ direction we would require that it satisfy the Muarer--Cartan equation.
+More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms of arbitrary Dolbeault type, which we can write in superfield notation as
+\[
+\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j}
+\]
+where there is a sum over the multi-index $\Bar{I}$. 
+In this notation, the component of the field $\mu$ is {\em odd} if $|I|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
+In particular we have odd fields $\mu_j(t;z,\zbar) \del_{z_j}$ which play the role of ghosts for infinitesimal changes of coordinates.
+We will see that the equations of motion dictate that we only see changes of holomorphic coordinates.
+
+The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$. 
+This means that it is required to satisfy the condition 
+\beqn
+\div \mu = 0
+\eeqn
+where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
+In the BV formalism one can encode this by introducing another field, but for the sake of discussion we omit that approach for now.
+Another piece of the equations of motion for~$\mu$ dictate that it be locally constant along~$S$.
+
+Ordinarily, for $\mu$ to describe a deformation of complex structure in the $X$ direction we would require that it satisfy the Maurer--Cartan equation.
 For twisted supergravity, however, we find a modification of this equation which involves the twisted analog of another familiar field.
@@
 One of the other bosonic fields of eleven-dimensional supergravity is a three-form that we denote by~$\sf C$.
-On $S \times X$ the space of complex-valued three-forms decomposes into de Rham--Dolbeault forms as in
+In the BV formalism we see all types of differential forms corresponding to a tower of ghosts for this $C$-field together with antifields and antighosts.
+
+On $S \times X$ the space of complex-valued differential forms decomposes into de Rham--Dolbeault forms as in
 \[
-\oplus_{k+p+q=3} \Omega^k(S) \otimes \Omega^{p,q}(X) .
+\oplus_{k,p,q} \Omega^k(S) \otimes \Omega^{p,q}(X) .
 \]
-We denote the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
+We refer to the homogenous pieces as the space of $(k;p,q)$ forms, these admit local presentations as
 \[
@@
 \]
-where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ such that $\sum_i (p_i + q_i) = 3$, $0 \leq p_i,q_i \leq 3$.
-The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.
+where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$.
+%The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.
 
 In the minimal twist only forms with $p_i ,p_i'\leq 1$ survive. 
-Thus, the components of the three-form which survive live in
+Thus, we have as part of the complex of fields in the twisted theory
 \[
-\left(\oplus_{k+q = 3} \Omega^k(S) \otimes \Omega^{0,q}(X)\right) \oplus 
-\left(\oplus_{k+q = 2} \Omega^k(S) \otimes \Omega^{1,q}(X)\right) .
+\left(\oplus_{k,q} \Omega^k(S) \otimes \Omega^{0,q}(X)\right) \oplus 
+\left(\oplus_{k',q'} \Omega^{k'}(S) \otimes \Omega^{1,q'}(X)\right) .
 \]
 We denote a general (non-homogenous) element in the first summand by $\beta$ and an element in the second summand by $\gamma$.
-When we want to be specific by the form type we use the notation $\beta^{k;q}$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}$ for the $(k;1,q)$ component of the three-form.
+When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
+Fields $\beta^{k;q}$ with $k+q = $even are {\em odd} and fields $\gamma^{k;q}$ with $k+q = $odd are {\em even} fields.
 
-Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
-Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.
+The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
+When $\div \mu = 0$ it takes the form
+\beqn\label{eqn:eom2}
+\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
+\eeqn
+
+The theory also enjoys the following gauge symmetries.
+First, for any 
+\brian{finish}
+%Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
+%Thus, locally we can assume that the $\Omega^1(S)$ components are exact and the $\Omega^0(S)$ components are locally constant.
 

### 2022-07-18 fivebranes/intro.tex
updates

@@
-\documentclass[11pt]{amsart}
+%\documentclass[11pt]{amsart}
 %
 %%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-fivebrane}
 %
-\begin{document}
+%\begin{document}
 
 \section{Introduction}
+Superconformal field theories admit a plethora of exactly computable, protected quantities, giving them a distinguished role in supersymmetric physics.
+Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories.
+Examples of such a quantities are superconformal indices, which are generating functions for the R-charges of BPS local operators.
+Crucial steps towards a more microscopic understanding of superconformal indices were taken in \cite{}, articulated through the construction of twisting.
+
+Introduced by Witten \cite{} and further developed by Costello \cite{}, twisting refers to a fixed-point construction for field theories equipped with the action of a supersymmetry algebra.
+Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge - the result is a theory on which the translations in the image of the supercharge act homotopically trivially.
+Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.
+One of the insights of \cite{} was that superconformal indices counts exactly local operators in the minimal twist.
 

### 2022-07-19 fivebranes/twisted.tex
cs

@@
 \eeqn
+Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.
 
@@
 
-In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists defined on multi Taub--NUT spaces.
+In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of the nonminimal twist defined on multi Taub--NUT spaces.
 The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
 
-The five-dimensional theory exists on any manifold of the form
+This five-dimensional theory is formally similar to a non-commutative version of Chern--Simons theory.
+It exists on any manifold of the form
 \[
@@
 where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.
+We denote the corresponding holomorphic two-form on $Y$ by $\Omega_Y$.
 
-The fundamental field of the five-dimensional theory is a one-form. 
-The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
+There are two parameters in this theory which Costello calls $\delta$ and $\ep$.
+The parameter $\delta$ controls the Chern--Simons type coupling, which in this section and going forward we will simply set to be the unit. 
+The parameter $\ep$ measures the non-commutativity. 
+It appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star$.
+
+We consider the following subalgebra of complex-valued forms on $S\times Y$:
 \[
-\oplus_{k+p+q=1}\Omega^{k}(S)\otimes \Omega^{p,q}(Y).
+\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
 \]
-We continue to label elements of the homogeneous pieces as $(k;p,q)$ forms. 
-The fields of ghost number zero are those one-forms with $p=0$. 
-We will use the notation $\alpha^{k;q}$ with $k+q=1$ for the corresponding component of the one-form.
+We continue to label elements of the homogeneous pieces as $(k;q)$ forms.
+We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
+Not only is $\cL_{5d}$ a dg algebra, if we adjoin formal parameter then $\cL_{5d}[[\ep]]$ is a dg Lie algebra with respect to the Moyal commutator $[-,-]_\star$.
 
-\brian{this is just the `semi-classical' limit of what Kevin looks at?}
-These fields are subject to the equations of motion
+In the BV formalism the space of fields of the five-dimensional theory is $\cL_{5d}[[\ep]] [1]$. 
+The fundamental field of the five-dimensional theory is a $\C[[\ep]]$ one-form on~$S \times Y$, which is a degree $0$ element in $\cL_{5d}[[\ep]] [1]$.
+
+We can take a gauge condition where $\alpha^{1;0}$ vanishes.
+In this case the equations of motion for the one-form field simply reads
 \beqn
-0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y , \qquad
-0 = \d \alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
+\dbar \alpha^{0;1} + \alpha^{0;1} \star \alpha^{0;1} = 0,
 \eeqn
-where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
+together with the condition that $\d_S \alpha^{0;1} = 0$.
+Here $\star$ denotes the holomorphic Moyal product on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
 
@@
 
-There is a non-linear gauge symmetry determined by a ghost $b \in C^\infty (S\times Y)$. 
-Explicitly, the corresponding infinitesimal gauge transformation is given by
+Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $\alpha^{0;0} \in C^\infty (S\times Y)[[\ep]]$. 
+Explicitly, the corresponding infinitesimal gauge transformation is given in components by
 \[
-\alpha^{k;q}\mapsto \alpha^{k;q} + db+\dbar b + \{b, \alpha^{k;q}\}_{Y}
+\alpha^{k;q}\mapsto \alpha^{k;q} + \d_S \alpha^{0;0} +\dbar \alpha^{0;0} + \{\alpha^{0;0}, \alpha^{k;q}\}_{Y}
 \]
 
-In the BV formalism, the full space of BV fields together with equations of motion and gauge symmetries can described by a local dg Lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
+The full BV action functional describing this model is the non-commutative Chern--Simons action
 \beqn
-\Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
+S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star \alpha \star \alpha \right) \wedge \Omega_Y .
 \eeqn
-The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a Lie bracket on the entire Dolbeault complex $\Omega^{0,\bu}(Y)$.
-The dg lie algebra structure is then obtained by the tensor product with the commutative dg algebra $\Omega^\bu(S)$. 
-The BV pairing is given by integrating against the holomorphic volume form on $Y$.
+Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$.
+
+%In the BV formalism, the full space of BV fields together with equations of motion and gauge symmetries can described by a local dg Lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
+%\beqn
+%\Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
+%\eeqn
+%The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a Lie bracket on the entire Dolbeault complex $\Omega^{0,\bu}(Y)$.
+%The dg lie algebra structure is then obtained by the tensor product with the commutative dg algebra $\Omega^\bu(S)$. 
+%The BV pairing is given by integrating against the holomorphic volume form on $Y$.
 

### 2022-07-19 fivebranes/fact.tex
merge

@@
-%\documentclass[11pt]{amsart}
+\documentclass[11pt]{amsart}
 %
 %%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
+\usepackage{macros-fivebrane}
 %
-%\begin{document}
+\begin{document}
 
 \section{Factorization algebras in twisted $M$ theory}
+
+In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting). 
+Our ansatz relies on a proposal for twisted holography developed by \brian{cites}.
 
@@
 which computes the Lie algebra cohomology of $\cL(U)$. 
-The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the $L_\infty$ structure maps.
+The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the~$L_\infty$ structure maps.
 
@@
 Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
-Even in perturbation theory, the full quantum behavior of the holomorphic-topological eleven-dimensional theory is an open question. 
+Even in perturbation theory, the full quantum behavior of our proposal for the minimal twist of eleven-dimensional theory is an open question. 
 We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.
 
-In this section we focus on the factorization algebra of classical observables of our prototype for the minimal twist of eleven-dimensional supergravity which we recalled in \S \ref{s:twisted}. 
+We start with the factorization algebra of classical observables of our prototype for the minimal twist of eleven-dimensional supergravity which we recalled in \S \ref{s:twisted}. 
 This model is defined on any eleven-manifold $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
@@
 %The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential. 
-
 In terms of this local $L_\infty$ algebra, the $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset S \times X$ is 
@@
 \]
-We will denote the entire classical factorization algebra on $S \times X$ of classical observables by~$\Obs_{sugra}$.
+We will denote the classical factorization algebra on $S \times X$ of classical observables by~$\Obs_{sugra}$.
 
@@
 
-Like sheaves, factorization algebras can be pushed forward; thus from the factorization algebra $\Obs_{sugra}$ on $\R \times X_Z$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ on $Z$. 
-To an open set $U \subset Z$ the value of this factorization algebra is
+Like sheaves, factorization algebras can be pushed forward.
+Thus, from the factorization algebra $\Obs_{sugra}$ on $\R \times X_Z$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ defined on the three-fold $Z$.
+Explicitly, to an open set $U \subset Z$ the factorization assigns the cochain complex
 \begin{align*}
@@
 
-One of the primary features of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is that it is of the form $\clie^\bu(\cG)$ where $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of a pro vector bundle.
-To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler construction related to branes in five-dimensional Chern--Simons theory.
+One of the primary features of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is that it is of the form $\clie^\bu(\cG)$ where $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
+To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.
 
@@
 As we recalled in~\S \ref{??}, Costello's five-dimensional Chern--Simons theory is the result of applying the $\Omega$-background to $M$ theory on a Taub--NUT space.
-In this setting, fivebranes which hit the tip of the Taub--NUT become chiral defects supported along a Riemann surface $C$ in the five-manifold. 
-In analogy with the situation above, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the fivebranes wrapping the zero section.
-Denote by $\Obs_{CS}$ the observables of five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
-Let $\pi \colon \R \times {\rm Tot}(K_C) \to C$ be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.
+In this setting, fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
+In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
+Denote by $\Obs_{CS}$ the observables of the semi-classical limit of non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
+Let 
+\[\pi \colon \R \times {\rm Tot}(K_C) \to C
+\]
+be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.
 
@@
 
-For the rank one abelian gauge group, the space of fields of non-commutative Chern--Simons theory on $\R \times {\rm Tot}(K_C)$ is
+For the rank one abelian gauge group, the space of fields of the five-dimensional theory on $\R \times {\rm Tot}(K_C)$ is
 \[
@@
 where $p \colon K_C \to C$.
-If, moreover, $U$ is a trivializing cover then
+The Chevalley--Eilenberg complex is taken with respect to the dg Lie algebra structure coming from the holomorphic Poisson structure on the total space of~$K_C$. 
+If $U$ is a trivializing cover then
 \[
@@
 Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
-Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO^{hol}(\C) \to \C[[w]]$.
+Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
+The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is similar to the non-formal case---it is the natural one if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in $K_C$.
+
+%The differential is simply $\dbar$ in the direction of the curve $C$. 
+%If we write an arbitrary element of this complex as $w^k \alpha$, where $\alpha \in \Omega^{0,\bu}(C)$, then the Lie bracket is
+%\[
+%[w^k \alpha, w^l \beta]
 
@@
 \subsection{Summary}
+\label{sec:factsummary}
 
@@
 For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
-For $N > 0$, we define 
+
+Define 
 \beqn
-\til \cG_N \define \cG / \cG^{(\geq N-1)} 
+\cG_1 \define \cG / \cG^{(\geq 0)} 
 \eeqn
-which has the induced structure of a local $L_\infty$ algebra on the worldvolume.
+and for $N > 1$
+\beqn
+\til \cG_N \define \cG / \cG^{(\geq N-1)} , \quad \cG_N \define \cG^{\geq 0} / \cG^{(\geq N-1)} .
+\eeqn
+Each of $\cG_1, \cG_{N}, \til \cG_N$ has the induced structure of a local $L_\infty$ algebra on the worldvolume.
+Notice that as factorization algebras of graded vector spaces one has
+\[
+\til \cG_N = \cG_N \otimes \cG_1
+\]
+for $N > 1$.
 
@@
 \beqn\label{eqn:colim}
-\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\cG_2) \to \cdots ,
+\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
 \eeqn
@@
 Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
-There is a similar diagram upon applying~$!$-duals
+Applying~$!$-duals we obtain a sequence
 \beqn
-\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots ,
+\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
 \eeqn 
 whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
+We also point out that there is a similar diagram of the form
+\beqn
+\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
+\eeqn
 
-%\end{document}
+\end{document}

### 2022-07-19 fivebranes/index.tex
merge

@@
-%\documentclass[11pt]{amsart}
+\documentclass[11pt]{amsart}
 %
 %%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
+\usepackage{macros-fivebrane}
 %
-%\begin{document}
+\begin{document}
 
@@
 
-In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \brian{references}.
+In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
+In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \textit{loc. cit.}.
 
-In \cite{RSW} we gave descriptions of twisted versions of these backgrounds.
-We recall this construction, adapted to a slightly more global situation.
-We will consider the eleven-dimensional theory on 11-manifolds that arise as total spaces of vector bundles.
-Placing the theory in the backreacted geometry is a 3-step procedure:
+We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 3-step procedure:
 
 \begin{itemize}
-  \item Place the eleven dimensional theory on the complement of the zero section.
+  \item Place the eleven-dimensional theory on the complement of the zero section.
 To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.
@@
 
-As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \C \times C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping
+As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \T^* C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping the zero section
 \[
-0 \times 0 \times C \subset \R \times \C \times C .
+0 \times C \subset \R \times \T^* C .
 \]
-It will be convenient to view $\R \times \C \times C$ as the total space of the real rank two bundle $\R \oplus K_C$ over $C$.
-Denote by $(t,w)$ the fiber coordinates.
-Removing the zero section and deforming by the backreaction associated to $C$ corresponds to the twisted version of the $S^2 \times AdS_3$ background.
+Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$.
+If we remove the defect we obtain the manifold 
+\[
+\left(\R \times \T^* C\right) - C \simeq C \times \R_{>0} \times S^2 
+\]
+where this identification requires the choice of a fiberwise partially hermitian metric.  
+This manifold is equipped with the natural structure of a transversely holomorphic foliation (THF).
+We will see that the including the backreaction corresponds to deforming this tructure. 
+For sake of analogy, we think of as being a twisted version of $AdS_3 \times S^2$.
+\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
 We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
@@
 
-If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection ${\rm Tot}(\R \oplus K_C) \to \R_+ \times C$ which combines the fiberwise norm with the natural bundle projection.
+If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{>0} \times C$ which combines the fiberwise norm with the natural bundle projection.
 Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
@@
 \subsection{Global symmetry for twisted fivebranes}
+\label{s:global1}
 
@@
 
-\subsection{A stack of two fivebranes}
-
-\parsec[]
-
-Recall that the even part of $E(3|6)$ ...
-
-\begin{itemize}
-\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
-\[
-q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
-\[
-q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
-\[
-q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-\end{itemize}
-
-\begin{conj}
-The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
-\[
-{\rm PExp} \left[f_{two} (t_1,t_2,q,r) \right] .
-\]
-where the single particle index is
-\[
-f_{two} (t_1,t_2,q,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
-\end{conj}
-
-\parsec[]
-
-The specialization of this index $t_1=t_2=r=1$ yields the single particle index
-\[
-\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
-\]
-
-\parsec[]
-
-The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
-\[
-f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
-\]
-which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
-
 \subsection{The large $N$ limit}

### 2022-07-19 fivebranes/ops.tex
merge

@@
 
-The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
-Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
+The notion of a factorization algebra captures both the local operators of a theory together with the non-local operators that on can define from the local ones via descent.
+From the data of a factorization algebra, one can recover local operators by the following formal construction. 
 Let $\Obs$ be the factorization algebra of observables of some theory defined on a smooth manifold $M$.
-The space of \defterm{local operators} at point $p \in M$ is, in a precise sense, the limiting behavior of the factorization algebra evaluated on the system of open sets which contain the point~$p$.
+The space of local operators at point $p \in M$ is, in a precise sense, the limiting behavior of the factorization algebra evaluated on the system of open sets which contain the point~$p$.
 
@@
 
-\subsection{The definition of local operators}
+\subsection{Local operators in topological-holomorphic theories}
 
@@
 For topological-holomorphic theories the local operators take a very familiar form.
-As an algebra they are generated by holomorphic derivatives of the fields evaluated at the specified point. 
+As an algebra they are generated by (holomorphic) derivatives of the fields evaluated at the specified point. 
+More precisely, the local operators depend only on the $\infty$-jets of the fields at a point.
 In this section we carefully formulate this result and give some examples.
@@
 equipped with the induced differential.
-Here $\cE(U)^\vee$ denotes the {\em topological} dual of the graded vector space $\cE(U)$. 
-As a graded vector space one has an isomorphism $\cE(U)^\vee \simeq \overline{\cE}^!_c(U)$ where the bar denotes distributional sections and $!$ is the Serre dual. 
+
+Some remarks are in order:
+\begin{itemize}
+\item If $V$ is a topological vector space then $\cO(V) = \Sym(V^\vee)$ denotes the algebra of polynomials on~$V$.
+Here~$V^\vee$ is the topological dual.
+\item The topological dual of $\cE(U)$ is $\cE(U)^\vee \simeq \overline{\cE}^!_c(U)$ where the bar denotes distributional sections, the subscript $c$ denotes compact support, and $!$ denotes the Serre dual.
 Explicitly, if $U = U' \times U'' \subset S \times X$ then 
@@
 where $\dim_\C (X) = n$ and $\dim_\R (S) = m$. 
+\end{itemize}
 
@@
 We also assume that the operator $Q^{hol}$ is translation invariant.
+
+Given a vector bundle $E \to M$, the bundle of $\infty$-jets $J^\infty E \to M$ is a $\infty$-dimensional pro vector bundle whose fiber over a point $p \in M$ is 
+If $M = \R^d$ and $E$ is translation invariant, then the bundle of $\infty$-jets can be identified with $E_0 \times \C[[x_i]]$ where
+
 The jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes
@@
 \[
-\Obs(0) \simeq \cO(V_0 [[z_1,\ldots,z_n]] .
+\Obs(0) \simeq \cO\left(V_0 [[z_1,\ldots,z_n]]\right).
 \] 
@@
 This is the space of linear local operators. 
-
-Suppose that $\chi \colon V_0 \to \C$ is a dual vector in~$V_0^*$. 
-Then, we obtain a linear local operator at $0 \in \R^m \times \C^n$ on the space of fields by the assignment
+If $\chi \colon V_0 \to \C$ is a dual vector in~$V_0^*$
+then we obtain a linear local operator at $0 \in \R^m \times \C^n$ on the space of fields by the assignment
 \[
@@
 \[
-V_0 [[z_1,\ldots,z_n]] [1] .
+V_0 [[z_1,\ldots,z_n]] [-1] .
 \]
@@
 \[
-\Obs(0) \simeq \clie^\bu\left(V_0[[z_1,\ldots,z_n]][1]\right) .
+\Obs(0) \simeq \clie^\bu\left(V_0[[z_1,\ldots,z_n]][-1]\right) .
 \]
@@
 There is another way that observables are presented in a degenerate version of the BV formalism.
-Suppose that $\cL$ is a local Lie algebra on a manifold $M$. 
-Then, one can consider the factorization algebra
+Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
+We have seen that the observables~$\cO(\cE) = \Sym(\cE^\vee)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
+That is, we consider the factorization algebra 
 \[
-\cF = \clie_\bu(\cL_c)
+U \subset M \mapsto \Sym \left(\cE_c(U) \right) 
 \]
-which assigns to an open set $U$ the cochain complex $\clie_\bu(\cL_c(U))$.
-This is the $!$-dual of the factorization algebra $\clie^\bu(\cL)$.
-For topological-holomorphic local Lie algebras there is still an algorithm for computing $\cF(p)$ for a point~$p \in M$.
+where $U \to \cE_c(U)$ is the cosheaf of compactly supported sections of the bundle~$E$.
 
-We will assume that $\cL$ is a translation invariant topological-holomorphic local Lie algebra whose underlying sheaf of cochain complexes is
-\[
-\cL = \Omega^\bu (\R^m) \hotimes \Omega^{0,\bu}(\C^n, L)
-\]
-Here $L$ is a translation invariant holomorphic vector bundle on $\C^n$ and the differential in the complex is $\d_{dR} + \dbar + Q^{hol}$ as above.
+%Suppose that $\cL$ is a local Lie algebra on a manifold $M$. 
+%Then, one can consider the factorization algebra
+%\[
+%\cF = \clie_\bu(\cL_c)
+%\]
+%which assigns to an open set $U$ the cochain complex $\clie_\bu(\cL_c(U))$.
+%This is the $!$-dual of the factorization algebra $\clie^\bu(\cL)$.
+%For topological-holomorphic local Lie algebras there is still an algorithm for computing $\cF(p)$ for a point~$p \in M$.
+%
+%We will assume that $\cL$ is a translation invariant topological-holomorphic local Lie algebra whose underlying sheaf of cochain complexes is
+%\[
+%\cL = \Omega^\bu (\R^m) \hotimes \Omega^{0,\bu}(\C^n, L)
+%\]
+%Here $L$ is a translation invariant holomorphic vector bundle on $\C^n$ and the differential in the complex is $\d_{dR} + \dbar + Q^{hol}$ as above.
 
@@
 \label{lem:envelope}
-Suppose that $\cL$ is a topological-holomorphic local Lie algebra on $S \times X = \R^m \times \C^n$ and let $\cF$ be the factorization algebra $\clie_\bu(\cL_c)$.
-Moreover, assume that $Q^{hol}$ is an elliptic holomorphic differential operator. 
-Then, there is a spectral sequence converging to $H^\bu(\cF(0))$ whose first page is the $Q^{hol}$ cohomology of
-\[
-\cO \left(\d^n z L_0^*[[z_1,\ldots,z_n]] [n+m-1] \right) .
-\]
+Suppose that $\cE$ is the sheaf of fields of a free holomorphic theory as in~\eqref{eqn:cE} and consider the factorization algebra~$\cF = \Sym(\cE_c)$. 
+Then, the algebra of classical local operators at~$0 \in \C^n$ of the factorization algebra~$\cF$ is quasi-isomorphic to 
+\begin{align*}
+\cF(0) & \simeq {\rm Sym} \left(\Omega^{n,hol}(\Hat{D}^n,V_0^*)^\vee [-n]\right) \\ & \cong \cO\left(\Omega^{n,hol}(\Hat{D}^n,V_0^*) [n] \right) 
+\end{align*}
+where the differential on the right hand side is~$Q^{hol}$.
 \end{lem}
+
+%\begin{lem}
+%\label{lem:envelope}
+%Suppose that $\cL$ is a topological-holomorphic local Lie algebra on $S \times X = \R^m \times \C^n$ and let $\cF$ be the factorization algebra $\clie_\bu(\cL_c)$.
+%Moreover, assume that $Q^{hol}$ is an elliptic holomorphic differential operator. 
+%Then, there is a spectral sequence converging to $H^\bu(\cF(0))$ whose first page is the $Q^{hol}$ cohomology of
+%\[
+%\cO \left(\d^n z L_0^*[[z_1,\ldots,z_n]] [n+m-1] \right) .
+%\]
+%\end{lem}
 \begin{proof}
@@
 \beqn\label{eqn:dist}
-\left(\overline{\cL}^!(U)\right)^\vee \simeq \cL_c(U) 
+\left(\overline{\cE}^!(U)\right)^\vee \simeq \cE_c(U) 
 \eeqn
-
-We use the spectral sequence induced by the filtration by the homogenous degree of a local operator.
-The first page is the cohomology of 
-\[
-\lim_{0 \ni U} \Sym(\cL_c(U)[1]) 
-\]
-with respect to the linear differential $\d_{dR} + \dbar + Q^{hol}$ which acts on $\cL_c(U)$ and extends to the symmetric algebra by the rule that it is a derivation.
-
-Using the isomorphism \eqref{eqn:dist}, we have an isomorphism 
-\[
-\Sym(\cL_c(U)[1]) \simeq \cO\left(\overline{\cL}^!(U)[-1]\right) 
-\]
+%
+%We use the spectral sequence induced by the filtration by the homogenous degree of a local operator.
+%The first page is the cohomology of 
+%\[
+%\lim_{U \ni 0} \Sym(\cL_c(U)[1]) 
+%\]
+%with respect to the linear differential $\d_{dR} + \dbar + Q^{hol}$ which acts on $\cL_c(U)$ and extends to the symmetric algebra by the rule that it is a derivation.
+This implies there is an isomorphism
+\beqn\label{eqn:dist2}
+\Sym(\cE_c(U)) \simeq \cO\left(\overline{\cE}^!(U)\right) 
+\eeqn
 for any open set $U$.
 By assumption, the linear differential $[\cdot]_1$ is elliptic, in particular the embedding of smooth sections into distributional sections
-\[
-\cL^!(U) \hookrightarrow \overline{\cL}^! (U)
-\]
+\beqn\label{eqn:dist3}
+\cE^!(U) \hookrightarrow \overline{\cE}^! (U)
+\eeqn
 is a quasi-isomorphism for any open set~$U$.
 
-Explicitly, we can assume that $U$ is an open set of the form $U' \times U'' \subset \R^m \times \C^n$ with $U' \subset \R^m$ contractible and $U''\subset \C^n$ Stein.
+We can assume that $U \subset \C^n$ is a Stein open set containing~$0 \in \C^n$.
+%of the form $U' \times U'' \subset \R^m \times \C^n$ with $U' \subset \R^m$ contractible and $U''\subset \C^n$ Stein.
 Then we have a sequence of quasi-isomorphisms
 \begin{align*}
-\overline{\cL}^! (U) [-1] & \simeq \cL^!(U) [-1] \\ & \simeq \Omega^\bu(U') \otimes \Omega^{0,\bu}(U'',K_{\C^n} \otimes L^*)[n+m-1] . 
+\overline{\cE}^! (U) & \simeq \cE^!(U) \\ & \simeq \Omega^{n,\bu}(U, V^*)[n].
 \end{align*}
-Thus, the first page of this spectral sequence is isomorphic to the cohomology of the local operators $\Obs(0)$ of the free theory whose underlying cochain complex of fields is 
-\[
-\cE = \Omega^\bu(\R^m) \hotimes \Omega^{0,\bu}(\C^n , K_{\C^n} \otimes L^*[n+m-1]).
-\]
-In the notation of Equation \eqref{eqn:cE}, the holomorphic vector bundle $V$ is 
-\[
-K_{\C^n} \otimes L^*[n+m-1] .
-\]
-The result now follows from Lemma~\ref{lem:taylor} where we have used $\d^n z$ for basis for the line $K_{\C^n}|_0$. 
+The result now follows from Lemma~\ref{lem:taylor}.
+
+%Thus, the first page of this spectral sequence is isomorphic to the cohomology of the local operators $\Obs(0)$ of the free theory whose underlying cochain complex of fields is 
+%\[
+%\cE = \Omega^\bu(\R^m) \hotimes \Omega^{0,\bu}(\C^n , K_{\C^n} \otimes L^*[n+m-1]).
+%\]
+%In the notation of Equation \eqref{eqn:cE}, the holomorphic vector bundle $V$ is 
+%\[
+%K_{\C^n} \otimes L^*[n+m-1] .
+%\]
+%The result now follows from Lemma~\ref{lem:taylor} where we have used $\d^n z$ for basis for the line $K_{\C^n}|_0$. 
 \end{proof}
@@
 Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following single particle index
+We would like to observe that the equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the single particle index which is immediate to compute:
 \[
@@
 \]
+However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
+This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$. 
+One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
+\[
+\frac{y}{(1-q_1)\cdots (1-q_n)} .
+\]
+The plethystic exponential of such an expression is
+\[
+\prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
+\]
+which now makes sense as a power series in the variables $y,q_1,\ldots,q_n$.
 \end{eg}
 
+Its instructive to see how local operators differ between $!$-dual factorization algebras.
+Let us first point out a simple example. 
 \begin{eg}
-Consider the abelian local Lie algebra on $X = \C$ whose sheaf of cochain complexes is 
+Consider the sheaf of cochain complexes
 \[
-\cL = \Omega^{0,\bu}\left(\C, K_{\C}^{\otimes r}\right),
+\cE = \Omega^{0,\bu}\left(\C, K_{\C}^{\otimes r}\right),
 \]
-where $r \in \Z$. 
-Then, we have the factorization algebra which assigns to $U \subset \C$ the complex
+where $r \in \Z$ and the differential is~$\dbar$. 
+Then, we can consider both the factorization algebra $\Obs = \cO(\cE)$ and its $!$-dual $\Obs^! = \Sym(\cE_c)$.
+
+The $\infty$-jets at $0 \in \C$ of $\cE$ is quasi-isomorphic to $\Gamma(\Hat{D}^n, K^{\otimes r}) = \d z^{\otimes r} \C[[z]]$. 
+Thus the algebra of local operators $\Obs(0)$ is quasi-isomorphic to 
 \[
-\cF(U) = \clie_\bu(\cL_c(U)) = \Sym\left(\Omega^{0,\bu}_c\left(U, K_U^{\otimes r}\right)\right)
+\Obs(0) \simeq \cO \left(\Gamma(\Hat{D}, K^{\otimes r})\right) .
 \]
-where the differential is $\dbar$. 
-By Lemma \ref{lem:envelope} we see that the local operators $\cF(0)$ is identified with the vector space
+In particular, the character of local operators $\Obs(0)$ is the plethystic exponential of
 \[
-\cO\left(\d z^{\otimes (r + 1)} \C[[z]] \right) .
+\frac{q^{r}}{1-q} 
 \]
-In particular, the single particle index of local operators is 
+where $q$ represents the fugacity for the standard~$\C^\times$ action on~$\C$.
+Notice that when $r = 0$ we run into a similar problem as in the previous example. 
+It is therefore convenient to introduce an extra fugacity $y$ which enters the single particle character as
 \[
-\frac{q^{r+1}}{1-q} 
+\frac{y q^{r}}{1-q}  .
+\]
+
+%Then, we have the factorization algebra which assigns to $U \subset \C$ the complex
+%\begin{align*}
+%\cF(U) & = \clie_\bu(\cL_c(U)) \\ & = \Sym\left(\Omega^{0,\bu}_c\left(U, K_U^{\otimes r}\right) [1] \right)
+%\end{align*}
+%where the differential is $\dbar$.
+
+%Serre duality induces an isomorphism
+%\begin{align*}
+%\Omega^{0,\bu}_c(\C, K_\C^{\otimes r}) \cong \left( \Gamma^{hol} (\C , K_\C \otimes K_\C^{-r})\right)^* \\
+%= \left( \Gamma^{hol} (\C , K_\C^{1-r})\right)^* .
+%\end{align*}
+
+On the other hand, by Lemma \ref{lem:envelope} we see that the local operators associated to the $!$-dual $\Obs^!(0)$ is identified with the vector space
+\[
+\cO\left(\Gamma(\Hat{D}, K^{1-r})[1]\right) .
+\]
+In particular, the character of local operators $\Obs^!(0)$ is the plethystic exponential of
+\[
+-\frac{q^{1-r}}{1-q} 
 \]
 where $q$ represents the fugacity for the standard $\C^\times$ action on $\C$.
+This time, when $r=1$ there is a problem with defining the plethystic exponential. 
+To get an expression that makes sense for all $r$ we can again introduce a variable $y$ which enters the single particle character as
+\[
+- \frac{y q^{1-r}}{1-q} .
+\]
 \end{eg}
+
+\subsection{A relationship to the supersymmetric index}
 
@@
 We recalled the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
-This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables~$\Obs_{single}$ on $Z$.
-We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs_{single}(0)$ supported at~$0 \in \C^3$.
+This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables~$\Obs^{6d}_{\lie{u}(1)}$ on $Z$.
+We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs^{6d}_{\lie{u}(1)}(0)$ supported at~$0 \in \C^3$.
 
-The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{single}$ with linear BRST differential is
+The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{\lie{u}(1)}$ with linear BRST differential is
 \beqn
@@
 \[
-\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{single} .
+\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{\lie{u}(1)} .
 \]
@@
 \[
-\cO(\cE_{single}(U)) = \Sym(\Pi \overline{\cE}_{single,c}^!(U)) .
+\cO(\cE_{\lie{u}(1)}(U)) = \Sym(\Pi \overline{\cE}_{\lie{u}(1),c}^!(U)) .
 \]
@@
 We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
-However, when $\lie{g}$ is abelian (so, a cochain complex) we can simply identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
+However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
 
@@
 \label{lem:single}
-The $\Z \times \Z/2$ graded algebra of local operators $\Obs_{single}(0)$ of the holomorphic single fivebrane theory is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
+The $\Z \times \Z/2$ graded algebra of local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
 \beqn\label{eqn:localfree}
@@
 \begin{proof}
-The jet expansion at $0 \in \C^3$ determines a map from the section of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
+The jet expansion at $0 \in \C^3$ determines a map from the sections of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
 \beqn
@@
 \beqn
-\chi_{single} (t_1,t_2,q,r) = {\rm PExp} \big[f_{single}(t_1,t_2,q,r) \big] .
+\chi^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = {\rm PExp} \big[f^{6d}_{\lie{u}(1)}(t_1,t_2,q,r) \big] .
 \eeqn
@@
 \begin{prop}
-The character $\chi_{single}(t_1,t_2,q,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of
+The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
 \[
-f_{tensor} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
 \]
@@
 
-One degeneration of this character involves specializing $t_1=t_2=r=1$:
+One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
+\beqn
+f_{u(1)}(t,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
+\eeqn
 %They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
 %In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
-\[
-\chi_{single} (q,t_1=t_2=r=1) = \frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3} .
-\]
+%\[
+%\chi_{u(1)} (q,t_1=t_2=r=1) = \frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3} .
+%\]
 In \S \ref{s:kr} we will compare this to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.
@@
 
-Another specialization is related to the superconformal algebra.
+Another specialization is related to a particular deformations by elements in the (twisted) superconformal algebra.
+Recall that after performing the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry, the residual superconformal algebra is~$\lie{osp}(6|2)$. 
+We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.
+
+There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
+The odd part of~$\lie{osp}(6|2)$ can be identified with 
+\[
+\C^3 \otimes \C^2 \oplus \Sym^2(\C^3) \otimes \C^2 
+\]
+where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations.
 
 \begin{itemize}
-\item The deformation $\d z_1 \otimes r_+$.
+\item The space $\C^3 \otimes \C^2$ is spanned by twisted supergravity fields of the form $\gamma = w_a \d z_i$. 
 \item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
@@
 
+\subsection{A conjectural description of a stack of two fivebranes}
+
+In \S\ref{fact:summary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
+\[
+\clie_{\bu}(\cG_{1,c}) \leftarrow \clie_{\bu}(\til \cG_{2,c}) \leftarrow \cdots .
+\]
+We now turn to the factorization algebra $\clie_{\bu}(\til \cG_{2,c})$.
+
+Recall that $\til \cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\til \cG_{2} = \cG / \cG^{\geq 1}$. 
+Since $\cG$ is concentrated in weights $\geq -1$ we see that $\til \cG_{2}$ is of the form
+\[
+\til \cG_2 = \cG_2 \ltimes \cG_1 
+\]
+where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
+We focus mostly on the factorization algebra $\clie_\bu(\cG_{2,c})$.
+
+We have already characterized the local dg Lie algebra $\cG_{2}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
+We deduce that $\cG_2$ can be given a $\Z \times \Z/2$ grading where, as usual, we refer to $\Z$ as the cohomological grading and $\Z/2$ as the parity. 
+With this lift to a $\Z \times \Z/2$ grading, the even part of $\cG_2$ is
+\[
+\Omega^{0,\bu}(Z, \T_Z) \oplus \Omega^{0,\bu}(Z) \otimes \lie{sl}(2) 
+\]
+with its natural cohomological grading by Dolbeault form type. 
+The odd part of $\cG_2$ is
+\[
+\Omega^{1,\bu}(Z, K_Z^{-1/2}) \otimes \C^2 .
+\]
+The differential is $\dbar$ and the Lie bracket has been described in \S\ref{s:weight0}.
+
+On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{s:KacClass}. 
+Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+
+\parsec
+
+We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$.
+
+\begin{itemize}
+\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
+\[
+q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
+\[
+q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\]
+\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
+\[
+q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+\]
+\end{itemize}
+
+\begin{conj}
+The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
+\[
+\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
+\]
+where the single particle index is
+\[
+f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\]
+\end{conj}
+
+Following the general relationship between characters of holomorphic twists of supersymmetric theories and supersymmetric indices, this our conjecture for the supersymmetric index of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(2)$.
+Similarly, the index associated to the $\lie{gl}(2)$ theory is conjectured to be simply the product 
+\[
+\chi_{\lie{gl}(2)}^{6d} (q,t_1,t_2,r) = \chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) \cdot \chi_{\lie{u}(1)}^{6d}(q,t_1,t_2,r)
+\]
+where the index for the $\lie{u}(1)$ theory is given in the previous section. 
+As a factorization algebra \brian{finish}
+
+\parsec[]
+
+The specialization of this index $t_1=t_2=r=1$ yields the single particle index
+\[
+\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
+\]
+
+\parsec[]
+
+The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+\[
+f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
+\]
+which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
+
 \subsection{Operators on a single membrane}
 
-%\end{document}
+\end{document}

### 2022-07-19 fivebranes/intro.tex
updated intro

@@
 Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.
-One of the insights of \cite{} was that superconformal indices counts exactly local operators in the minimal twist.
 
-The six-dimensional $\cN=(2,0)$ supersymmetric theory
+One of the insights of \cite{} was that superconformal indices count exactly local operators in the minimal twist - accordingly, we may think of the algebra of local operators in the minimal twist as \textit{categorifying} the superconformal index.
+Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}.
+Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set.
 
-In this paper we apply the proposal of \textit{twisted holography} introduced by Costello and Li in \cite{CLsugra} to access the worldvolume theory on a stack of fivebranes in minimally twisted eleven-dimensional supergravity.
-Twisted holography shares, in many ways, the spirit of familiar gauge-gravity dualities such as the AdS/CFT correspondence. 
-The heart of the program relates the algebra of observables of the bulk gravity theory, which lives on a twisted version of AdS space, to the observables of the worldvolume theory living on a defect, which plays the role of the CFT.
+A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\mc N=(2,0)$ and three-dimensional $\mc N=8$ superconformal field theories.
+However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization.
+In light of this, we propose to access the minimal twist and its local operators via \textit{twisted holography}.
+
+\subsection{Twisted Holography}
+Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of twists.
+The main objects involved are factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes therein.
+
+A more concrete, albeit informal, statement is as follows.
+Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory.
+Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\into X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.
+
+\begin{}[Twisted Holographic Principle]
+  There is a map of factorization algebras
+  \[
+        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
+  \]
+
+      that becomes an equivalence in the large $N$ limit.
+    \end{}
+
+    This statement has been tested in many examples \cite{}.
+
+\subsection{Infinite dimensional symmetry enhancement by exceptional simple lie superalgebras}
+
+\subsection{Outline}
+
+The paper is organized as follows. The first section is the present introduction.
+
+In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\mc N=(2,0)$ \cite{} and three-dimensional $\mc N=8$ \cite{} superconformal field theories.
 

### 2022-07-19 fivebranes/kr.tex
allinone
merge

@@
 
+Given this elegant relationship between twisted supergravity and these exceptional super Lie algebras, we ask the natural question of the consequences of the representation theory of such exceptional algebras to $M$-theory.
+The goal in this section is to relate a particular decomposition of the central extension of $E(5|10)$ to local operators on a stack of membranes and fivebranes.
+
 In \cite{KR1}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
-In this section we compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR1}.
-
+We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR1}.
 Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
@@
 There is a different decomposition of $E(5|10)$ (and its central extension) which has as its weight zero piece the subalgebra $E(1|6)$; this decomposition is natural from the point of view of membranes.
-
+We comment on this in \S \ref{sec:membraneindex}.
 %an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
@@
 We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR1}.
-In \S \ref{s:m5localops} we return to fivebranes and use this algebraic decomposition to characterize local operators of the twisted theory.
+In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.
 
@@
 
-As above, we denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
+As above, we denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in the five-fold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
 
 The even part of the super Lie algebra $E(5|10)$ is formal vector fields on the formal disk $\Hat{D}^3_z \times \Hat{D}^2_w$, whose elements we denote by $\mu$. 
-The odd part is given by the space of closed two-forms on the formal disk, whose elements we denote by $\alpha$.
-Equivalently, we can think of the space of closed two-forms as the space of equivalence classes of one-forms $\Omega^1(\Hat{D}^3_z \times \Hat{D}^2) / \text{Im}(\del)$.
+The odd part is given by the space of closed two-forms on the formal disk, whose elements we denote by~$\alpha$.
+Equivalently, by the formal Poincar\'e lemma we can think of the space of closed two-forms as the space of equivalence classes of one-forms $\Omega^1(\Hat{D}^3_z \times \Hat{D}^2) / \text{Im}(\del)$.
 
@@
 \eeqn
-is a sub super Lie algebra and each $\til{V}_{-1}, V_n, n \geq 0$ is a module for $E(3|6)$.
+is a sub super Lie algebra and $\til{V}_{-1}, V_n, n \geq 0$ is a module for $E(3|6)$.
 
@@
 
-As we will recall momentarily, our eleven-dimensional model is more closely related to an $L_\infty$ central extension $\Hat{E(5|10)}$ of $E(5|10)$\cite[\S 3]{RSW}. 
-The central extension of $E(5|10)$ is defined by the (totally even) three-linear cocycle
+The twist of eleven-dimensional supergravity is more closely related to an $L_\infty$ central extension of $E(5|10)$ of the form
+\[
+0 \to \C \to \Hat{E(5|10)} \to E(5|10) \to 0 .
+\]
+See \cite[\S 3]{RSW}. 
+The central extension is defined by the (totally even) three-linear cocycle
 \beqn\label{eqn:e510central}
@@
 \eeqn
+Since this is a three-linear functional the model we use for the central extension is a super $L_\infty$ algebra (with zero one-ary operation) rather than just a super Lie algebra.
 
-We can extend the weight grading of $E(5|10)$ to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
-In this way, we get a related decomposition of super vector spaces
+We can extend the weight grading of $E(5|10)$ from \S \ref{s:e510weight} to a weight grading of the central extension $\Hat{E(5|10)}$ by declaring that the central term have weight $-1$.
+In this way, we get a related decomposition of super $L_\infty$ algebras
 \beqn\label{eqn:decomp1}
@@
 
+\subsection{Irreducible representations of $E(3|6)$}
+We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
+The main goal of this section is to deduce explicit formulas for certain irreducible modules which we will, in turn, relate to indices of local operators of the twisted fivebrane theory.
+
+Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of the central extension of $E(5|10)$ we see that it carries an induced consistent $\Z$-grading by degree. 
+Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
+One can check that the algebra is supported in degrees $j \geq -2$ so that as a super vector space
+\[
+E(3|6) = \prod_{j \geq -2} \fg_j
+\]
+where for small values of $j$ we have:
+\begin{itemize}
+\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is a completely even super vector space. 
+\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is a completely odd super vector space.
+\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is a completely even super vector space.
+Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
+\[
+h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
+\]
+The Cartan of $\lie{sl}(2)$ is spanned by
+\[
+h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
+\]
+The Cartan of $\lie{gl}(1)$ is spanned by
+\[
+Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
+\]
+\end{itemize}
+
+\parsec[s:vermas]
+
+We are interested in a class of irreducible modules for $E(3|6)$ that can be constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
+Denote by $\fg = E(3|6)$ and let 
+\[
+\fg_{<0} = \fg_{-2} \oplus \fg_{-1} , \quad \lie{g}_{>0} = \oplus_{j>0} \fg_j 
+\]
+so that $\fg = \fg_{<0} \oplus \fg_0 \oplus \fg_{>0}$. 
+Given a $\fg_0$-module $V$ let 
+\beqn\label{eqn:verma1}
+M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
+\eeqn
+be the induced $\fg$-module. 
+Notice that as super vector spaces we have 
+\beqn
+M(V) = \Sym(\fg_{<0}) \otimes_\C V .
+\eeqn
+
+We will be interested in Verma modules associated to two particular types of $\fg_0$-modules
+\begin{align*}
+V_A & = \C[z_i, w_a] \\
+V_B & = \C[z_i, \del_{w_a}]_{[2]} .
+\end{align*}
+Here, the subscript $[2]$ means that we shift $\lie{gl}(1)$ to act by the differential operator 
+\[
+Y_{[2]} = Y + 2 \id_{V_B} .
+\]
+For $X = A,B$ we let 
+\[
+V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} \subset V_X
+\]
+so that $V_X = \oplus_{m,n} V_X^{m,n}$. 
+There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.
+
+An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2,\lambda_3,y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
+\begin{align*}
+\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
+ y & = \lambda(Y)\in \C . 
+\end{align*}
+Actually, for the remainder of this section we will be interested in the case $\lambda_2 = 0$; the modules with $\lambda_2 \ne 0$ will play no role.
+
+For $\lambda_1,\lambda_3 \geq 0$ there are isomorphisms of $\fg_0$-modules
+\begin{align*}
+V_A^{\lambda_1,\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 - \lambda_3) \\
+V_B^{\lambda_1,-\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 + \lambda_3 +2) .
+\end{align*} 
+To simplify notation we will get rid of the dependence on $\lambda_2$ and write 
+\begin{align*}
+F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
+F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
+\end{align*}
+and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules \eqref{eqn:verma1}.
+
+Particularly important for us will be Verma modules associated with the linear duals of the above $\fg_0$-modules.
+We let 
+\begin{align*}
+\til{M}_A(\lambda_1,\lambda_3) &\define M \left( (V_A^{\lambda_1,\lambda_3})^* \right) \\
+\til{M}_B(\lambda_1,\lambda_3) &\define M \left( (V_B^{\lambda_1,\lambda_3})^* \right) .
+\end{align*}
+As supervector spaces one has, for example
+\beqn
+\til{M}_A(\lambda_1,\lambda_3) = \Sym(\fg_{<0}) \otimes_\C (V_A^{\lambda_1,\lambda_3})^* .
+\eeqn
+We will refer to $\til{M}_A(\lambda_1,\lambda_3)$ and $\til{M}_A (\lambda_1,\lambda_3)$ as `modified' Verma modules to decipher them from $M_A(\lambda_1,\lambda_3)$ and $M_B(\lambda_1,\lambda_3)$.
+
+One of the main results of \cite{KR1} characterizes the irreducible quotients of these Verma modules. 
+\begin{thm}[\cite{KR1}]
+The Verma modules $M_A(\lambda_1,\lambda_3)$ and $M_A(\lambda_1,\lambda_3)$ have unique irreducible quotients denoted by 
+\beqn
+I_A(\lambda_1,\lambda_3), \quad \text{and} \quad I_B(\lambda_1,\lambda_3)
+\eeqn
+respectively. 
+Furthermore, for any $\lambda_1,\lambda_3 \in \Z_+$ one has $M_A(\lambda_1,\lambda_3) \ne I_A(\lambda_1,\lambda_3)$ and $M_B(\lambda_1,\lambda_3) \ne I_B(\lambda_1,\lambda_3)$.
+\end{thm}
+
+In \textit{loc. cit.} they refer to such irreducible modules $I_A,I_B$ as `degenerate'.
+Similarly, the modified Verma modules have irreducible quotients that we will denote by 
+\beqn
+\til{I}_A(\lambda_1,\lambda_3), \quad \text{and} \quad \til{I}_B(\lambda_1,\lambda_3) .
+\eeqn
+
+\parsec[]
+
+The last bit of algebraic input we need is a result of \cite{KR2} which uses these irreducible quotients $I_A(\lambda_1,\lambda_3)$ and $I_{B} (\lambda_1,\lambda_3)$ to characterize the $E(3|6)$-representations which appear in the decomposition of $E(5|10)$.
+
+\begin{thm}[\cite{KR2}]
+Consider the decomposition \eqref{eqn:decomp1} of the super Lie algebra
+\beqn
+E(5|10) = \til V_{-1} \times \prod_{i \geq -1} V_n
+\eeqn
+where $V_0 \simeq E(3|6)$. 
+Then, there are isomorphisms of $E(3|6)$-modules
+\begin{align*}
+\til V_{-1}^* & \simeq I_A(0,1) \\
+E(3|6)^* = V_0^* & \simeq I_A(1,0) \\
+V_j^* & \simeq I_B(0,j-1), \quad j \geq 1
+\end{align*}
+where $(-)^*$ denotes the topological dual.
+\end{thm}
+
+For the centrally extension of $E(5|10)$ we need to adjust things slightly. 
+The decomposition of the central extension is $\prod_{j \geq -1} V_j$, where only $V_{-1}$ differs from the weight $(-1)$ part $\til V_{-1}$ of $E(5|10)$.
+It is easy to see that as $E(3|6)$-modules $V_{-1}^*$ is a direct sum 
+\[
+V_{-1}^* = \til V_{-1}^* \oplus \C = I_A(0,1) \oplus \C
+\]
+with $\C$ the trivial module. 
+(In \cite[\S 5]{KR2} they refer to the module $V_{-1}^*$ as~$P$.)
+
+\subsection{Modified characters for degenerate modules of type $A$} \label{s:typeA}
+
+The (super) character of an $E(3|6)$-module $M$ is given by the formula
+\[
+\ch (M) \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
+\]
+Our goal in this section is to compute the explicit formula for this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ (and its modified version $\til I_A(\lambda_1,\lambda_3)$) which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$ (respectively, $\til M_A(\lambda_1,\lambda_3)$).
+
+As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
+\[
+M(V) = \Sym(\lie{g}_{<0}) \otimes V .
+\]
+%We define the modified character of a Verma module by the formula
+%\[
+%\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
+%\]
+Define
+\[
+R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
+\]
+so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the finite-dimensional $\fg_0$-representation $V$.
+In the computations of the sections that follow we will make the substitution $\boxed{q = t^2}$ for notational simplicity.
+
+%Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
+
+Our computation of the character relies on a cohomological description of the irreducible modules $I_A(\lambda_1,\lambda_3)$ of type~$A$.
+%\[
+%I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
+%\]
+In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\beqn\label{eqn:les1}
+0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
+\eeqn 
+From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
+\beqn
+\label{eqn:chA1}
+\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
+\eeqn 
+There is a similar formula for the module $\til{I}_A(\lambda_1,\lambda_3)$ in terms of the modified Verma modules
+\beqn
+\label{eqn:chA2}
+\ch \, \til I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch \, \til M_A(\lambda_1+j,\lambda_3+j)  .
+\eeqn
+
+We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term the sum in \eqref{eqn:chA1}
+\beqn\label{eqn:chA3}
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
+\eeqn
+And similarly for the sum in \eqref{eqn:chA2}---the $SU(2)$ part of the character remains the same and the $SU(3)$ part is related by $t_i\leftrightarrow t_i^{-1}$.
+
+The first ingredient in determining an explicit formula for the modified character of type $A$ Verma modules is a direct calculation.
+\begin{lem}
+\label{lem:R}
+The explicit formula for $R = R(t,t_1,t_2,r)$ is
+%\beqn
+%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+%\eeqn
+\beqn
+R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+\eeqn
+\end{lem}
+
+Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
+\[
+V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
+\] 
+given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
+Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
+\begin{prop}
+One has
+\beqn\label{eqn:MA}
+\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
+\eeqn
+where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
+\beqn\label{eqn:su}
+\ch(V_A^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
+\eeqn
+is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
+\end{prop}
+
+In expression \eqref{eqn:su}, $\ch_{SU(3)}^{\lambda_1}$ denotes the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.
+
+%which is
+%\[
+%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
+%\]
+Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
+\begin{align*}
+\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
+%\\ 
+%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
+\end{align*}
+and $SU(2)$ character
+\begin{align*}
+\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
+\end{align*}
+
+We proceed to evaluate the sum in \eqref{eqn:chA1}
+\begin{multline}
+t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
+= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
+\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\
+\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
+%
+%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
+\\ \left.
+- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
+\end{multline}
+
+We split the sum $\sum_{j \geq 0}$ into four terms
+\begin{itemize}
+\item the first term is 
+\beqn
+(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
+\eeqn
+Evaluating the infinite series this becomes
+\begin{multline} 
+r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
+\end{multline}
+\item the second term is
+\beqn
+t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
+\eeqn
+\end{itemize}
+
+Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
+\begin{multline} 
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
+\end{multline}
+
+\parsec
+In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.
+
+\begin{prop}
+\label{prop:chA}
+Let $\lambda_1,\lambda_3 \geq 0$. 
+The $t_1=t_2=1$ specialization of $\ch \, \til I_A(\lambda_1,\lambda_3)$ is given by the expression
+\beqn
+\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
+\eeqn
+where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
+\end{prop}
+
+\begin{proof}
+In this specialization it is easy to see that 
+\[
+\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
+\]
+which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.
+
+We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
+\beqn
+\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^{-j} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
+\eeqn
+where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
+\[
+R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
+\]
+which we read off from Lemma \ref{lem:R}.
+In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
+\[
+r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
+\]
+
+Now, observe the formal identity 
+\[
+\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
+\]
+where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
+Using this identity, we evaluate
+\begin{align*}
+\ch \til I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\
+& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
+\end{align*}
+This completes the proof
+\end{proof}
+
+In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
+\beqn
+\ch \til I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
+\eeqn
+
+In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
+\beqn
+ \ch \til I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
+\eeqn
+
+Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
+\beqn
+\ch \til I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
+\eeqn
+
+\subsection{Characters for degenerate modules of type B} \label{s:typeB}
+
+There is a cohomological description of the irreducible modules of type B similar to the type A case above.
+Recall that the degenerate module of type $B$ is $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
+We are only interested in the case $\lambda_1 = 0$ with $\lambda_3\geq 0$.  
+In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
+\begin{multline}\label{eqn:les1}
+0 \leftarrow  I_B(0,\lambda_3) \\ \leftarrow M_B(0,\lambda_3) \leftarrow  M_B(1,\lambda_3-1)  \leftarrow \cdots \leftarrow M(\lambda_3, 0) \\
+ \leftarrow M_A(\lambda_3+2, 0) \leftarrow M_A(\lambda_3+3,1) \leftarrow \cdots .
+\end{multline}
+There are $\lambda_3+1$ terms in the second line above .  
+Notice that the bottom line is simply the resolution for the module $I(\lambda_3+2, 0)$ of type $A$. 
+Using this long exact sequence we obtain a simple formula for the character of type $B$ modules
+\beqn\label{eqn:chB1}
+\ch I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3} \ch M_B(k, \lambda_3-k) + \ch I_A(\lambda_3+2,0) .
+\eeqn
+And similarly we have the following formula for character of the module $\til I_B(0,\lambda_3)$ as
+\beqn\label{eqn:chB2}
+ \ch \til I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3} \ch \til M_B(k, \lambda_3-k) + \ch \til I_A(\lambda_3+2,0) .
+\eeqn
+
+\begin{prop}
+\label{prop:chB}
+For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ specialized at $t_1=t_2=1$ is given by the expression
+\begin{multline}
+\label{eqn:chB3}
+t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+\end{multline}
+where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chB}. 
+\end{prop}
+
+\begin{proof}
+We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in \S \ref{s:typA}.
+Thus, it suffices to compute the modified character of the type $B$ Verma modules 
+\[
+\til M_{B}(k,\lambda_3-k) .
+\]
+
+The character of the Verma module $\til M_B(k,\lambda_3-k)$, for $0 \leq k \leq \lambda_3$, is given by
+\[
+\ch \til M_B(k,\lambda_3-k)|_{t_1=t_2=1} = t^{3 \lambda_3 - k + 6} R(t,r) .
+\]
+Thus, \eqref{eqn:chB2} simplifies to 
+\[
+\ch \til I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \ch \til I_{A}(\lambda_3+2,0) .
+\]
+The result now follows from the formula for $\ch \til I_A(\lambda_3+2,0)$ given in Proposition~\ref{prop:chA}.
+\end{proof}
+
+Notice that since $R(t=r) = 0$ it follows that if we further specialize at $t = r$ and substitute $q = t^2$ then the first line of \eqref{eqn:chB3} vanishes so that
+\beqn
+\ch \til I_B(0,\lambda_3)|_{t=r, t_i=1} = \ch \til I_A(\lambda_3+2,0)|_{t=r, t_i=1} = \frac{q^{\lambda_3 + 1}}{1 - q} .
+\eeqn
+
+\parsec[s:typeBunrefinedKR]
+
+For integer $N$ let 
+\[
+p_{N}(x) = \frac12 \left(N^2 x^2 + N x^2 - 2N^2x -4 N x + N^2 + 3N +2\right) .
+\]
+Then the index for $N > 2$ fivebranes after specializing the $SU(3)$ fugacities is
+\begin{multline}
+t^{2 N} \frac{(1-tr)^3 (1-tr^{-1})^3 (1-t^{N+2})}{(1-t^2)^3(1 - t)} \\ + \frac{t^{2N + 4}}{(1-t^2)^3 (1-r^{-2})} \left(p_{N-1} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{N-1}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+\end{multline}
+
 \subsection{Decomposing fivebrane local operators}
@@
 
-The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory.
+The general prescription of twisted holography is that the $!$-dual of $\Obs_{sugra}|_Z$ is the factorization algebra of the universal defect supported along $Z$ in the eleven-dimensional theory---this is our ansatz for the large $N$ limit of local operators along the brane.
 The $!$-dual of the factorization algebra $\Obs_{sugra}|_Z$ is of the form $\clie_\bu (\cG_c)$ where $\cG$ is an infinite-dimensional local $L_\infty$ algebra on $Z$.
@@
 
-For the remainder of this section we focus on the case $Z = \C^3$. 
+For the remainder of this section we focus on the case $Z = \C^3$ and local operators at~$0 \in \C^3$. 
 Our goal is to show that this weight grading is compatible with the one on the central extension of $E(5|10)$ that we recalled in \S \ref{s:e510central}. 
@@
 
-\subsection{Irreducible representations of $E(3|6)$}
-We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
-Since we have realized the super Lie algebra $E(3|6)$ as the weight zero subalgebra of the central extension of $E(5|10)$ we see that it carries an induced consistent $\Z$-grading by degree. 
-Denote by $\fg_j$ the degree $j$ super subspace of $E(3|6)$.
-One can check that the algebra is supported in degrees $j \geq -2$ so that as a super vector space
-\[
-E(3|6) = \prod_{j \geq -2} \fg_j
-\]
-where for small values of $j$ we have:
-\begin{itemize}
-\item $\fg_{-2} = {\rm span}\{\del_{z_i}\; | \; {i=1,2,3}\}$ which is a completely even super vector space. 
-\item $\fg_{-1} = {\rm span}\{\d z_i \wedge \d w_a \; | \; i=1,2,3, a=1,2\}$ which is a completely odd super vector space.
-\item $\fg_0 \cong \lie{sl}(3) \oplus \lie{sl}(2) \oplus \lie{gl}(1)$ which is a completely even super vector space.
-Explicitly, the Cartan of $\lie{sl}(3)$ is spanned by 
-\[
-h_1 = z_1 \del_{z_1} - z_2 \del_{z_2}, \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3} .
-\]
-The Cartan of $\lie{sl}(2)$ is spanned by
-\[
-h_3 = w_1 \del_{w_1} - w_2 \del_{w_2} .
-\]
-The Cartan of $\lie{gl}(1)$ is spanned by
-\[
-Y = \frac23 \sum_{i=1,2,3} z_i \del_{z_i} - \sum_{a=1,2} w_a \del_{w_a} .
-\]
-\end{itemize}
-
-\parsec[s:vermas]
-
-We are interested in a class of irreducible modules for $E(3|6)$ that can be constructed via resolutions of particular Verma modules \cite{KR2} that we now recall.
-Denote by $\fg = E(3|6)$ and let 
-\[
-\fg_{<0} = \fg_{-2} \oplus \fg_{-1} , \quad \lie{g}_{>0} = \oplus_{j>0} \fg_j 
-\]
-so that $\fg = \fg_{<0} \oplus \fg_0 \oplus \fg_{>0}$. 
-Given a $\fg_0$-module $V$ let 
-\beqn\label{eqn:verma1}
-M (V) \define U(\fg) \otimes_{U(\fg_{\geq 0})} V 
-\eeqn
-be the induced $\fg$-module. 
-Notice that as super vector spaces~$M(V) = \Sym(\fg_{<0}) \otimes_\C V$.
-
-We will be interested in Verma modules associated to two particular types of $\fg_0$-modules
-\begin{align*}
-V_A & = \C[z_i, w_a] \\
-V_B & = \C[z_i, \del_{w_a}]_{[2]} .
-\end{align*}
-Here, the subscript $[2]$ means that we shift $\lie{gl}(1)$ to act by the differential operator 
-\[
-Y_{[2]} = Y + 2 \id_{V_B} .
-\]
-For $X = A,B$ we let 
-\[
-V_X^{m,n} = \{f \in V_X \; | \; \sum z_i \del_{z_i} f = m f , \quad \sum w_a \del_{w_a} f = n f.\} \subset V_X
-\]
-so that $V_X = \oplus_{m,n} V_X^{m,n}$. 
-There is a similar decomposition of the resulting Verma modules $M(V_X)$ in terms of the Verma modules $M(V_{X}^{m,n})$.
-
-An irreducible $\fg_0$-module $F(\lambda_1,\lambda_2,\lambda_3,y)$ is characterized by a highest weight $\lambda = (\lambda_1,\lambda_2,\lambda_3,y)$ whose components we denote by
-\begin{align*}
-\lambda_i & = \lambda (h_i) \in \Z_{\geq 0}, \\
- y & = \lambda(Y)\in \C . 
-\end{align*}
-Actually, for the remainder of this section we will be interested in the case $\lambda_2 = 0$; the modules with $\lambda_2 \ne 0$ will play no role.
-
-For $\lambda_1,\lambda_3 \geq 0$ there are isomorphisms of $\fg_0$-modules
-\begin{align*}
-V_A^{\lambda_1,\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 - \lambda_3) \\
-V_B^{\lambda_1,-\lambda_3} & \simeq F(\lambda_1,0,\lambda_3,\frac23 \lambda_1 + \lambda_3 +2) .
-\end{align*} 
-To simplify notation we will get rid of the dependence on $\lambda_2$ and write 
-\begin{align*}
-F_A(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 - \lambda_3) \\
-F_B(\lambda_1,\lambda_3) & \define F(\lambda_1,0;\lambda_3;\frac23 \lambda_1 + \lambda_3 +2)  
-\end{align*}
-and similarly $M_A(\lambda_1,\lambda_3)$, $M_B(\lambda_1,\lambda_3)$ for the associated Verma modules \eqref{eqn:verma1}.
-
-One of the main results of \cite{KR1} characterizes the irreducible quotients of these Verma modules. 
-\begin{thm}[\cite{KR1}]
-The Verma modules $M_A(\lambda_1,\lambda_3)$ and $M_A(\lambda_1,\lambda_3)$ have unique irreducible quotients denoted by 
-\beqn
-I_A(\lambda_1,\lambda_3), \quad \text{and} \quad I_B(\lambda_1,\lambda_3)
-\eeqn
-respectively. 
-Furthermore, for any $\lambda_1,\lambda_3 \in \Z_+$ one has $M_A(\lambda_1,\lambda_3) \ne I_A(\lambda_1,\lambda_3)$ and $M_B(\lambda_1,\lambda_3) \ne I_B(\lambda_1,\lambda_3)$.
-\end{thm}
-
-In \textit{loc. cit.} they refer to such irreducible modules $I_A,I_B$ as `degenerate'.
-
-\parsec[]
-
-The last bit of algebraic input we need is a result of \cite{KR2} which uses these irreducible quotients $I_A(\lambda_1,\lambda_3)$ and $I_{B} (\lambda_1,\lambda_3)$ to characterize the $E(3|6)$-representations which appear in the decomposition of $E(5|10)$.
-
-\begin{thm}[\cite{KR2}]
-Consider the decomposition \eqref{eqn:decomp1} of the super Lie algebra
-\beqn
-E(5|10) = \til V_{-1} \times \prod_{i \geq -1} V_n
-\eeqn
-where $V_0 \simeq E(3|6)$. 
-Then, there are isomorphisms of $E(3|6)$-modules
-\begin{align*}
-\til V_{-1}^* & \simeq I_A(0,1) \\
-E(3|6)^* = V_0^* & \simeq I_A(1,0) \\
-V_j^* & \simeq I_B(0,j-1), \quad j \geq 1
-\end{align*}
-where $(-)^*$ denotes the topological dual.
-\end{thm}
-
-For the centrally extension of $E(5|10)$ we need to adjust things slightly. 
-The decomposition of the central extension is $\prod_{j \geq -1} V_j$, where only $V_{-1}$ differs from the weight $(-1)$ part $\til V_{-1}$ of $E(5|10)$.
-It is easy to see that as $E(3|6)$-modules $V_{-1}^*$ is a direct sum 
-\[
-V_{-1}^* = \til V_{-1}^* \oplus \C = I_A(0,1) \oplus \C
-\]
-with $\C$ the trivial module. 
-(In \cite[\S 5]{KR2} they refer to the module $V_{-1}^*$ as~$P$.)
-
-\subsection{Modified characters for degenerate modules of type $A$} \label{s:typeA}
-
-The (super) character of an $E(3|6)$-module $M$ is given by the formula
-\[
-\ch (M) \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
-\]
-Our goal in this section is to compute the explicit formula for a modified version of this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$.
-
-As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
-\[
-M(V) = \Sym(\lie{g}_{<0}) \otimes V .
-\]
-We define the modified character of a Verma module by the formula
-\[
-\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
-\]
-Define
-\[
-R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
-\]
-so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the $\fg_0$ representation $V$.
-%Recall that $\lie{g}_{<0} = \lie{g}_{-2} \oplus \lie{g}_{-1}$ where $\lie{g}_{-2} \cong \C^3$ spanned by $\del_{z_i}$ and $\lie{g}_{-1} \cong \Pi \C^6$ spanned by the odd elements $r_a \d z_i$ for $a=1,2$ and $i=1,2,3$.
-
-Our definition of the modified character relies on a cohomological description of the irreducible modules $I_A(\lambda_1,\lambda_3)$ of type~$A$.
-%\[
-%I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
-%\]
-In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
-\beqn\label{eqn:les1}
-0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
-\eeqn 
-From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
-\beqn
-\label{eqn:chA1}
-\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
-\eeqn 
-Like the Verma modules, we can defined a modified version of this character by the formula
-\beqn
-\label{eqn:chA2}
-\til \ch \, I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \til\ch \, M_A(\lambda_1+j,\lambda_3+j)  .
-\eeqn
-
-We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term the sum in \eqref{eqn:chA1}
-\beqn\label{eqn:chA3}
-\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
-\eeqn
-And similarly for the sum in \eqref{eqn:chA2}.
-
-The first ingredient in determining an explicit formula for the modified character of type $A$ Verma modules is a direct calculation.
-\begin{lem}
-\label{lem:R}
-Then
-%\beqn
-%R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
-%\eeqn
-\beqn
-R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
-\eeqn
-\end{lem}
-
-Recall that the type $A$ degenerate modules are defined by induction from the $\fg_0$-module 
-\[
-V = V^{\lambda_1,\lambda_3}_A \subset \C[z_i,w_a]
-\] 
-given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,w_a$ respectively.
-Thus, we have the following explicit presentation for the modified character of type $A$ modules. 
-\begin{prop}
-One has
-\beqn\label{eqn:MA}
-\til \ch \, {M_A(\lambda_1,\lambda_3)} = q^{y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r^{-1})
-\eeqn
-where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
-\beqn\label{eqn:su}
-\ch(V_A^{\lambda_1,\lambda_3}) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
-\eeqn
-is the $SU(3) \times SU(2)$ character of the representation $V_A^{\lambda_1,\lambda_3}$. 
-\end{prop}
-
-In expression \eqref{eqn:su}, $\ch_{SU(3)}^{\lambda_1}$ denotes the character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1,0)$ and $\ch^{\lambda_3}_{SU(2)}$ is the character of the irreducible $SU(2)$ representation of highest weight $\lambda_3$.
-
-%which is
-%\[
-%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
-%\]
-
-In the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.
-
-Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
-\begin{align*}
-\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
-%\\ 
-%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
-\end{align*}
-and $SU(2)$ character
-\begin{align*}
-\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
-\end{align*}
-
-We proceed to evaluate the sum in \eqref{eqn:chA1}
-\begin{multline}
-t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
-= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
-= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
-\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\
-\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
-%
-%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
-\\ \left.
-- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
-\end{multline}
-
-We split the sum $\sum_{j \geq 0}$ into four terms
-\begin{itemize}
-\item the first term is 
-\beqn
-(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
-\eeqn
-Evaluating the infinite series this becomes
-\begin{multline} 
-r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
-\end{multline}
-\item the second term is
-\beqn
-t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
-\eeqn
-\end{itemize}
-
-Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
-\begin{multline} 
-\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
-\end{multline}
-
-\parsec
-In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.
-
-\begin{prop}
-\label{prop:chA}
-Let $\lambda_1,\lambda_3 \geq 0$. 
-The $t_1=t_2=1$ specialization of the modified character $\til \ch \, I_A(\lambda_1,\lambda_3)$ is given by the expression
-\beqn
-\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
-\eeqn
-where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
-\end{prop}
-
-\begin{proof}
-In this specialization it is easy to see that 
-\[
-\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
-\]
-which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.
-
-We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
-\beqn
-\til\ch M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^{-j} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
-\eeqn
-where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
-\[
-R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
-\]
-which we read off from Lemma \ref{lem:R}.
-In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
-\[
-r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
-\]
-
-Now, observe the formal identity 
-\[
-\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
-\]
-where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
-Using this identity, we evaluate
-\begin{align*}
-\til \ch \, I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\
-& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
-\end{align*}
-This completes the proof
-\end{proof}
-
-In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
-\beqn
-\til \ch \, I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
-\eeqn
-
-In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
-\beqn
-\til \ch \, I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
-\eeqn
-
-Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
-\beqn
-\til \ch \, I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
-\eeqn
-
-\subsection{Characters for degenerate modules of type B} \label{s:typeB}
-
-There is a cohomological description of the irreducible modules of type B similar to the type A case above.
-Recall that the degenerate module of type $B$ is $I_B(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3+2)$. 
-We are only interested in the case $\lambda_1 = 0$ with $\lambda_3\geq 0$.  
-In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
-\begin{multline}\label{eqn:les1}
-0 \leftarrow  I_B(0,\lambda_3) \\ \leftarrow M_B(0,\lambda_3) \leftarrow  M_B(1,\lambda_3-1)  \leftarrow \cdots \leftarrow M(\lambda_3, 0) \\
- \leftarrow M_A(\lambda_3+2, 0) \leftarrow M_A(\lambda_3+3,1) \leftarrow \cdots .
-\end{multline}
-There are $\lambda_3+1$ terms in the second line above .  
-Notice that the bottom line is simply the resolution for the module $I(\lambda_3+2, 0)$ of type $A$. 
-Using this long exact sequence we obtain a simple formula for the character of type $B$ modules
-\beqn\label{eqn:chB1}
-\ch I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3} \ch M_B(k, \lambda_3-k) + \ch I_A(\lambda_3+2,0) .
-\eeqn
-And similarly we have the following formula for the modified character
-\beqn\label{eqn:chB2}
-\til \ch \, I_B(0,\lambda_3) = \sum_{k=0}^{\lambda_3}\til \ch\, M_B(k, \lambda_3-k) + \til \ch \, I_A(\lambda_3+2,0) .
-\eeqn
-
-\begin{prop}
-\label{prop:chB}
-The modified character $\til \ch \, I_B(0,\lambda_3)$ is given by the expression
-\begin{multline}
-t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
-\end{multline}
-where $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chA}. 
-\end{prop}
-
-\begin{proof}
-We have already computed $\til \ch \, I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ above. 
-Thus, it suffices to compute the modified character of the type $B$ Verma modules.
-
-As above, the modified character for the Verma module $M_B(k,\lambda_3-k)$, for $0 \leq k \leq \lambda_3$ is given by
-\[
-\til \ch \, M_B(k,\lambda_3-k)|_{t_1=t_2=1} = t^{3 \lambda_3 - k + 6} R(t,r) .
-\]
-Thus, \eqref{eqn:chB2} simplifies to 
-\[
-\til \ch \, I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \til \ch \, I_{A}(\lambda_3+2,0) .
-\]
-The result now follows from Proposition \ref{prop:chA}.
-\end{proof}
-
-\parsec[s:typeBunrefinedKR]
-
-For integer $N$ let 
-\[
-p_{N}(x) = \frac12 \left(N^2 x^2 + N x^2 - 2N^2x -4 N x + N^2 + 3N +2\right) .
-\]
-Then the index for $N > 2$ fivebranes after specializing the $SU(3)$ fugacities is
-\begin{multline}
-t^{2 N} \frac{(1-tr)^3 (1-tr^{-1})^3 (1-t^{\lambda_3+1})}{(1-t^2)^3(1 - t)} \\ + \frac{t^{2N + 4}}{(1-t^2)^3 (1-r^{-2})} \left(p_{N-1} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{N-1}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
-\end{multline}
-
 \end{document}

### 2022-07-19 fivebranes/intro.tex

@@
 
-A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\mc N=(2,0)$ and three-dimensional $\mc N=8$ superconformal field theories.
+A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\cN=(2,0)$ and three-dimensional $\cN=8$ superconformal field theories.
 However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization.
@@
 
-In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\mc N=(2,0)$ \cite{} and three-dimensional $\mc N=8$ \cite{} superconformal field theories.
+In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\cN=(2,0)$ \cite{} and three-dimensional $\cN=8$ \cite{} superconformal field theories.
 

### 2022-07-19 fivebranes/intro.tex
macros

@@
 Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory.
-Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\into X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.
+Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\to X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.
 
-\begin{}[Twisted Holographic Principle]
+\begin{slogan}[Twisted Holographic Principle]
   There is a map of factorization algebras
@@
       that becomes an equivalence in the large $N$ limit.
-    \end{}
+\end{slogan}
 

### 2022-07-20 fivebranes/kr.tex
merge

@@
-\documentclass[11pt]{amsart}
+%\documentclass[11pt]{amsart}
 %
 %%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-fivebrane}
 %
-\begin{document}
+%\begin{document}
 
@@
 \[
-\ch (M) \define {\rm tr}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
+\ch (M) \define {\rm str}_M q^{Y} t_1^{h_1} t_2^{h_2} r^{h_3} .
 \]
 Our goal in this section is to compute the explicit formula for this character in the case of the degenerate modules $I_A(\lambda_1,\lambda_3)$ of type $A$ (and its modified version $\til I_A(\lambda_1,\lambda_3)$) which are irreducible quotients of the Verma modules $M_A(\lambda_1,\lambda_3)$ (respectively, $\til M_A(\lambda_1,\lambda_3)$).
-
-As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
-\[
-M(V) = \Sym(\lie{g}_{<0}) \otimes V .
-\]
-%We define the modified character of a Verma module by the formula
-%\[
-%\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
-%\]
-Define
-\[
-R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
-\]
-so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the finite-dimensional $\fg_0$-representation $V$.
-In the computations of the sections that follow we will make the substitution $\boxed{q = t^2}$ for notational simplicity.
 
@@
 
-We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term the sum in \eqref{eqn:chA1}
-\beqn\label{eqn:chA3}
-\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
-\eeqn
-And similarly for the sum in \eqref{eqn:chA2}---the $SU(2)$ part of the character remains the same and the $SU(3)$ part is related by $t_i\leftrightarrow t_i^{-1}$.
+As a super vector space, the Verma module $M(V)$ associated to a $\fg_0$-module $V$ is 
+\[
+M(V) = \Sym(\lie{g}_{<0}) \otimes V .
+\]
+%We define the modified character of a Verma module by the formula
+%\[
+%\til{\ch} \, M(V) = \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) \cdot \ch (V) \left(q^{-1}, t_1^{-1}, t_2^{-1}, r^{-1} \right)  .
+%\]
+Define
+\[
+R(q,t_1,t_2,r) \define \ch \left(\Sym(\lie{g}_{<0}) \right)(q, t_1,t_2,r) ,
+\]
+so that the character of the Verma module $M(V)$ is a product of $R$ with the character of the finite-dimensional $\fg_0$-representation $V$
+\[
+\ch M(V) (q,t_1,t_2,r) = R(q,t_1,t_2,r) \cdot \ch (V) (q,t_1,t_2,r).
+\]
+In the computations of the sections that follow we will make the substitution $\boxed{q = t^2}$ for notational simplicity.
 
-The first ingredient in determining an explicit formula for the modified character of type $A$ Verma modules is a direct calculation.
+The first ingredient in determining an explicit formula for Verma modules is a direct calculation.
 \begin{lem}
@@
 \beqn\label{eqn:MA}
-\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(q,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
+\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
 \eeqn
@@
 
-We proceed to evaluate the sum in \eqref{eqn:chA1}
-\begin{multline}
-t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
-= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
-= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
-\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\
-\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
-%
-%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
-\\ \left.
-- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
-\end{multline}
+We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term the sum in \eqref{eqn:chA1}
+\beqn\label{eqn:chA3}
+\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
+\eeqn
+And similarly for the sum in \eqref{eqn:chA2}---the $SU(2)$ part of the character remains the same and the $SU(3)$ part is related by $t_i\leftrightarrow t_i^{-1}$.
 
-We split the sum $\sum_{j \geq 0}$ into four terms
-\begin{itemize}
-\item the first term is 
-\beqn
-(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
-\eeqn
-Evaluating the infinite series this becomes
-\begin{multline} 
-r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
-\end{multline}
-\item the second term is
-\beqn
-t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
-\eeqn
-\end{itemize}
+\parsec[s:unrefinedA]
 
-Combining with the formula for $R(t,r,t_1,t_2)$ we arrive at the formula
-\begin{multline} 
-\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} 
-\end{multline}
-
-\parsec
 In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.
@@
 \begin{proof}
-In this specialization it is easy to see that 
+In this specialization we just see the dimension of the highest weight $SU(3)$ representations
 \[
-\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
+\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
 \]
-which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.
 
 We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
-\beqn
-\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^{-j} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
+\beqn\label{eqn:MA2}
+\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
 \eeqn
-where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
+where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
 \[
-R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
+R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
 \]
-which we read off from Lemma \ref{lem:R}.
-In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
-\[
-r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
-\]
+In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
+%\[
+%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
+%\]
 
@@
 \beqn
-\ch \til I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
+\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
 \eeqn
 
+\parsec[s:refinedA]
+
+We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$, before specializing $t_1=t_2=1$.
+The character will be given in terms of a generating function for highest weight $SU(3)$ representations.
+
+Our first aim is to deduce a closed formula for the following generating function
+\beqn
+\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
+\eeqn
+where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$. 
+It will be convenient to define the polynomial 
+\beqn\label{eqn:h1}
+h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
+\eeqn
+
+\begin{lem}
+One has
+\beqn
+\til p_{\lambda_1} (x,t_1,t_2) = \frac{p_{\lambda_1}(x,t_1,t_2)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
+\eeqn
+where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by
+\beqn
+p_{\lambda_1}(x,t_1,t_2) = 1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)
+\eeqn 
+\end{lem} 
+\begin{proof}
+\begin{multline}
+t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \sum_{k=0}^{\lambda_1 + j} t_1^{j-k} t_2^{-j+2k} x^j \left(1 - t_1^{-k-1} t_2^{-k-1}\right) \\ 
+= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{1-t_1^{-1} t_2^{-1}} \sum_{j \geq 0} \left(t_1^j t_2^{-j} \frac{1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}}{1-t_1^{-1} t_2^{2}} - t_1^{j-1} t_2^{-j-1} \frac{1 - (t_1^{-2} t_2)^{\lambda_1+j+1}}{1 - t_1^{-2} t_2} \right) x^j  \\
+%= \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{2})} \sum_{j \geq 0} \left( t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1})(1 - t_1^{-2} t_2) \right.
+\\ \left.
+- t_1^{j-1} t_2^{-j-1} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1})(1-t_1^{-1} t_2^{2}) \right) x^j \\
+= F(t_1,t_2) \left( G_1 (t_1,t_2,x) - t_1^{-1} t_2^{-1} G_2 (t_1,t_2,x)\right) .
+\end{multline}
+
+Where
+\begin{itemize}
+\item $F(t_1,t_2) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{(1-t_1^{-1} t_2^{-1}) (1-t_1^{-1} t_2^{2}) (1 - t_1^{-2} t_2)}$. 
+\item $G_1(t_1,t_2,x) = \frac{1}{1 - t_1^{-1} t_2^2} \sum_{j \geq 0}  t_1^j t_2^{-j} (1-(t_1^{-1} t_2^{2})^{\lambda_1+j+1}) x^j$. 
+\item $G_2(t_1,t_2,x) = \frac{1}{1 - t_1^{-2} t_2}\sum_{j \geq 0} t_1^{j} t_2^{-j} (1 - (t_1^{-2} t_2)^{\lambda_1+j+1}) x^j$. 
+\end{itemize}
+%
+%Directly, we compute
+%\begin{align*}
+%G_1(t_1,t_2,x) & = \frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \\
+%G_2(t_1,t_2,x) & = \frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}
+%\end{align*}
+We state an intermediate lemma.
+\begin{lem}
+One has
+\begin{align*}
+G_1(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_2 x)} \big(1 + h(t_1,t_2,x) \big) \\
+G_2(t_1,t_2,x) & = \frac{1}{(1 - t_1 t_2^{-1} x)(1-t_1^{-1} x)} \left(1 + t_1^{-1} t_2^{-1} h(t_1,t_2,x) \right) .
+\end{align*}
+where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h}. 
+\end{lem}
+
+\begin{proof}
+Formally evaluating the sum over $j$ we obtain
+\begin{align*}
+G_1(t_1,t_2,x) & = \frac{1}{1 - t_1^{-1} t_2^2} \left(\frac{1}{1 - t_1 t_2^{-1} x} - \frac{t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2}}{1 - t_2 x} \right) \\
+G_2(t_1,t_2,x) & = \frac{1}{1 - t_1^{-2} t_2} \left(\frac{1}{1-t_1 t_2^{-1} x} - \frac{t_1^{-2\lambda_1-2}t_2^{\lambda_1+1}}{1-t_1^{-1}x}\right) .
+\end{align*}
+
+Write $G_1 = g_1 / (1- t_1^{-1} t_2^2)$ and consider the polynomial
+\beqn
+\label{eqn:h2}
+ (1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)
+= 1 - t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
+\eeqn
+This polynomial is clearly divisible by $1-t_1^{-1} t_2^2$ so we can define the polynomial
+\beqn
+\til h_{\lambda_1}(t_1,t_2,x) = \frac{(1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)}{1-t_1^{-1} t_2^2} 
+\eeqn
+By definition we have
+\beqn
+G_1(t_1,t_2,x) = \frac{\til h (t_1, t_2,x)}{(1-t_2 x)(1-t_1 t_2^{-1} x)} .
+\eeqn
+
+We are interested in the polynomial $h_{\lambda_1} = \til h_{\lambda_1} - 1$. 
+By equation \eqref{eqn:h2} we see that 
+\beqn
+h_{\lambda_1} (t_1,t_2,x) = \frac{t_2 (t_1^{-1} t_2 - x) (1-t_1^{-\lambda_1} t_2^{2\lambda_1})}{1-t_1^{-1} t_2^2} .
+\eeqn
+The lemma immediately follows.
+%\beqn
+%h(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
+%\eeqn
+\end{proof}
+
+From this lemma we conclude that
+\beqn
+\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)\right)
+\eeqn
+and the result follows.
+\end{proof}
+
+%\begin{multline}
+%t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
+%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
+%= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
+%\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\
+%\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
+%%
+%%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right.
+\\ \left.
+- t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
+%\end{multline}
+%
+%We split the sum $\sum_{j \geq 0}$ into four terms
+%\begin{itemize}
+%\item the first term is 
+%\beqn
+%(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
+%\eeqn
+%Evaluating the infinite series this becomes
+%\begin{multline} 
+%r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
+%\end{multline}
+%\item the second term is
+%\beqn
+%t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
+%\eeqn
+%\end{itemize}
 \subsection{Characters for degenerate modules of type B} \label{s:typeB}

### 2022-07-21 fivebranes/kr.tex
small error
merge

@@
 \beqn
-R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
+R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1 q^{1/2} r^a)(1-t_1^{-1} t_2 q^{1/2} r^a)(1-t_2^{-1} q^{1/2} r^a)
 \eeqn
@@
 
-\parsec[s:unrefinedA]
-
-In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$.
-
-\begin{prop}
-\label{prop:chA}
-Let $\lambda_1,\lambda_3 \geq 0$. 
-The $t_1=t_2=1$ specialization of $\ch \, \til I_A(\lambda_1,\lambda_3)$ is given by the expression
-\beqn
-\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
-\eeqn
-where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
-\end{prop}
-
-\begin{proof}
-In this specialization we just see the dimension of the highest weight $SU(3)$ representations
-\[
-\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
-\]
-
-We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
-\beqn\label{eqn:MA2}
-\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
-\eeqn
-where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
-\[
-R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
-\]
-In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
+%\parsec[s:unrefinedA]
+%
+%In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$. 
+%
+%\begin{prop}
+%\label{prop:chA}
+%Let $\lambda_1,\lambda_3 \geq 0$. 
+%The $t_1=t_2=1$ specialization of $\ch \, \til I_A(\lambda_1,\lambda_3)$ is given by the expression
+%\beqn
+%\frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) 
+%\eeqn
+%where $p_{\lambda_1}(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$. 
+%\end{prop}
+%
+%\begin{proof}
+%In this specialization we just see the dimension of the highest weight $SU(3)$ representations
 %\[
-%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
+%\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} .
 %\]
-
-Now, observe the formal identity 
-\[
-\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
-\]
-where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
-Using this identity, we evaluate
-\begin{align*}
-\ch \til I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\
-& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 - r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
-\end{align*}
-This completes the proof
-\end{proof}
-
-In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
-\beqn
-\ch \til I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
-\eeqn
-
-In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
-\beqn
- \ch \til I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
-\eeqn
-
-Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
-\beqn
-\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
-\eeqn
+%
+%We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:chA2}:
+%\beqn\label{eqn:MA2}
+%\ch \til M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{2 \lambda_1-3\lambda_3-j} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
+%\eeqn
+%where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$ from Lemma \ref{lem:R}:
+%\[
+%R(t,r) = R|_{t_1=t_2=1} = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} .
+%\]
+%In equation \eqref{eqn:MA2} we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$. 
+%%\[
+%%r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
+%%\]
+%
+%Now, observe the formal identity 
+%\[
+%\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p_{\lambda_1}(x)}{(1-x)^3}  
+%\]
+%where $p_{\lambda_1}(x)$ is as in the statement of the proposition.
+%Using this identity, we evaluate
+%\begin{align*}
+%\ch \til I_A(\lambda_1,\lambda_3)|_{t_1=t_2=1} & = \frac{R(r,t) t^{2 \lambda_1-3 \lambda_3}}{1-r^{-2}} \left(\frac{r^{\lambda_3} p_{\lambda_1}(t^{-1}r)}{(1-t^{-1}r)^3} - \frac{r^{-\lambda_3-2}p_{\lambda_1}(t^{-1}r^{-1})}{(1-t^{-1}r^{-1})^3} \right) \\
+%& = \frac{t^{2\lambda_1-3 \lambda_3+6}}{(1-t^2)^3(1-r^{-2})} \left(r^{\lambda_3} p_{\lambda_1}(t^{-1}r) (1-t^{-1}r^{-1})^3 \right.
+\\ & \left.
+- r^{-\lambda_3-2} p_{\lambda_1}(t^{-1}r^{-1})(1-t^{-1}r)^3 \right) .
+%\end{align*}
+%This completes the proof
+%\end{proof}
+%
+%In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
+%\beqn
+%\ch \til I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + 1 - 3 t^2}{(1-t^2)^3} .
+%\eeqn
+%
+%In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
+%\beqn
+% \ch \til I_A(1,0)|_{t_1=t_2=1} = \frac{t^6(r^2 + r^{-2} + 1) - 3 t^7 (r + r^{-1}) + 3t^8 }{(1-t^2)^3} .
+%\eeqn
+%
+%Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
+%\beqn
+%\ch \til I_A(\lambda_1,\lambda_3) = \frac{t^{2 \lambda_1 - 2 \lambda_3 + 2}}{1 - t^2} = \frac{q^{\lambda_1-\lambda_3+1}}{1-q} .
+%\eeqn
 
@@
 
-We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$, before specializing $t_1=t_2=1$.
-The character will be given in terms of a generating function for highest weight $SU(3)$ representations.
+We now turn to the formula for the totally unrefined character of $\til I_A(\lambda_1,\lambda_3)$ as a function of the fugacities $t,t_1,t_2,r$.
+To state the result we introduce some notation.
 
-Our first aim is to deduce a closed formula for the following generating function
+For $\lambda_1 \geq 0$ define the polynomial in the variables $t_i^{\pm 1}$ and an auxiliary variable $x$
+\beqn\label{eqn:p}
+p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h(t_1,t_2,x)\right) 
+\eeqn
+where for $\lambda_1 > 0$
+\beqn\label{eqn:h1}
+h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  
+\eeqn
+and for $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.
+
+Our main result of this section is the following.
+\begin{thm}
+\label{thm:refinedA}
+For any $\lambda_1,\lambda_3 \geq 0$ the character of $\til I_A(\lambda_1,\lambda_3)$ is given by the following expression
+\begin{multline}
+\frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
+\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
+\\
+- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
+\end{multline}
+\end{thm}
+
+Recall that the character is given by the infinite sum
+\beqn
+\ch \til I_A (\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch \til M_A(\lambda_1+j, \lambda_3+j)
+\eeqn
+For each $j \geq 0$ we have
+\begin{multline}
+\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j} \cdot \ch^{\lambda_3+j}_{SU(2)} \\ =
+\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
+\end{multline}
+
+The first step is to deduce a closed formula for the following generating function
 \beqn
@@
 where we recall that $\ch_{SU(3)}^{\lambda_3+j} (t_1,t_2)$ is the $SU(3)$ character of the irreducible $SU(3)$ representation of highest weight $(\lambda_1+j,0)$.
-It will be convenient to define the polynomial 
-\beqn\label{eqn:h1}
-h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  .
-\eeqn
 
 \begin{lem}
+\label{lem:generating}
 One has
 \beqn
-\til p_{\lambda_1} (x,t_1,t_2) = \frac{p_{\lambda_1}(x,t_1,t_2)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
+\til p_{\lambda_1} (t_1,t_2,x) = \frac{p_{\lambda_1}(t_1,t_2,x)}{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)} .
 \eeqn
-where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by
-\beqn
-p_{\lambda_1}(x,t_1,t_2) = 1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)
-\eeqn 
+where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by equation \eqref{eqn:p}.
+
 \end{lem} 
@@
  (1-t_2 x)(1-t_1 t_2^{-1} x) g_1(t_1,t_2,x)
-= 1 - t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
+= 1 - t_1^{-\lambda_1-1} t_2^{2 \lambda_1 + 2} - t_2 x + t_1^{-\lambda_1} t_2^{2 \lambda_1 + 1} x .
 \eeqn
@@
 
-From this lemma we conclude that
+From this intermediate lemma we conclude that
 \beqn
-\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1+t_1 t_2 - t_2 x) h(t_1,t_2,x)\right)
+\til{p}_{\lambda_1}(t_1,t_2,x) = \frac{t_1^{\lambda_1} t_2^{-\lambda_1}}{{(1-t_1^{-1} x)(1-t_1t_2^{-1} x)(1-t_2 x)}} \left(1 + (1 +t_1^{-1}t_2^{-1}- t_1^{-1} x) h(t_1,t_2,x)\right)
 \eeqn
-and the result follows.
+Which completes the proof of Lemma \ref{lem:generating}. 
 \end{proof}
+
+Now, the proof of Theorem \ref{thm:refinedA} is an immediate computation. 
+\begin{multline}
+\ch \til I_A(\lambda_1,\lambda_2) = \frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \left(r^{\lambda_3} \frac{p_{\lambda_1}(t_1,t_2,r t^{-1})}{(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1})}  \right.
+\\ \left.
+- r^{-\lambda_3-2} \frac{p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})}{(1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1})}\right) \\
+= \frac{t^{2 \lambda_1 - 3 \lambda_3+6}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
+\left(r^{\lambda_3} p_{\lambda_1}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
+\\
+- \left. r^{-\lambda_3 - 2} p_{\lambda_1}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right) .
+\end{multline}
+
+\parsec[s:tests]
+
+We can greatly simplify expressions for the character of $\til I_A(\lambda_1,\lambda_3)$ for small values of $\lambda_1,\lambda_3$. 
+The following corollaries are immediate computations.
+
+\begin{cor} 
+\label{cor:6dtest1}
+When $(\lambda_1,\lambda_3) = (0,1)$ one has 
+\beqn\label{eqn:6doneTest}
+\ch \til I_A(0,1) = \frac{(r + r^{-1})t^{3} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )t^4 + t^6}{(1-t_1^{-1}t^2) (1-t_1 t_2^{-1} t^2) (1-t_2 t^2)} .
+\eeqn
+\end{cor}
+
+Note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of the six-dimensional theory abelian superconformal theory from Proposition \ref{prop:6done}.
+
+The next easy case is the following.
+\begin{cor}
+\label{cor:6dtest2}
+When $(\lambda_1,\lambda_3) = (1,0)$ one has  
+\beqn\label{eqn:6dtwo}
+\ch \til I_A(1,0) = \frac{t^8(t_1^{-1} + t_1 t_2^{-1}  + t_2) + t^6 (r^2 + r^{-2} + 1) - t^{7} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}t^2) (1-t_1 t_2^{-1} t^2) (1-t_2 t^2)} .
+\eeqn
+\end{cor}
+
+Again, we note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ which we computed in Proposition \ref{prop:6dtwo}.
 

### 2022-07-21 fivebranes/ops.tex
allinone
merge

@@
 \begin{prop}
+\label{prop:6done}
 The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
-\[
+\beqn\label{eqn:6done}
 f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
+\eeqn
 \end{prop}
@@
 \[
-q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
@@
 
-\begin{conj}
+Combining these expressions we obtain the following.
+
+\begin{prop} \label{prop:6dtwo}
+The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
+\beqn\label{eqn:6dtwo1}
+\frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\eeqn
+\end{prop}
+
+Based on our discussion above we are led to the following conjecture.
+\begin{conj}\label{conj:6dtwo}
 The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
@@
 where the single particle index is
-\[
-f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
+\beqn\label{eqn:6dtwo}
+f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\eeqn
 \end{conj}

### 2022-07-21 fivebranes/index.tex

@@
 
-\subsection{States in twisted supergravity}
+The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT \cite{}.
+The goal of this section is to provide constructions of spaces of supergravity states in our eleven-dimensional model, via geometric quantization.
+The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property - they are naturally modules for certain infinite dimensional exceptional lie superalgebras.
+We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
 
+Before proceeding with the construction, let us first give some feel for the situation we hope to describe.
+Suppose we consider a gravitational theory on $AdS_{d+1}\times S^{d^{\prime}}$, which we compactify to view as a theory on $AdS_{d+1}$ with all Kaluza-Klein harmonics included.
+Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$.
+A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{}.
+Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values.
+Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.
+
+\subsection{Twisted Backreactions}
+We begin by describing the relevant backgrounds.
 In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
-In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \textit{loc. cit.}.
+In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.
 
@@
   The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
-
-  \item The complement of the zero section is a manifold with boundary---we impose a natural boundary condition.
-
 \end{itemize}
@@
 \parsec[s:brkevin]
-
 As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \T^* C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping the zero section
@@
 Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$.
+
 If we remove the defect we obtain the manifold
@@
 \]
-where this identification requires the choice of a fiberwise partially hermitian metric.  
+
 This manifold is equipped with the natural structure of a transversely holomorphic foliation (THF).
-We will see that the including the backreaction corresponds to deforming this tructure. 
-For sake of analogy, we think of as being a twisted version of $AdS_3 \times S^2$.
+
+If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
+Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
+
+The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
+Moreover, they come equipped with a canonical complexified foliation of rank 1.
+Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the  Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
+
+We will see that the including the backreaction corresponds to deforming this structure.
+For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.
 \footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
 We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
-We first proceed before turning on the backreaction.
+We first proceed before turning on the flux sourced by the brane.
 
-If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{>0} \times C$ which combines the fiberwise norm with the natural bundle projection.
-Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
-The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
-
-Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
-We will elaborate on the appearance of this sort of cohomology momentarily.
 The theory admits a natural `vacuum' boundary condition at $r=0$.
@@
 There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
-The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$.
+The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
 

### 2022-07-21 fivebranes/intro.tex
intro and index

@@
 
-\begin{slogan}[Twisted Holographic Principle]
+\begin{expect}[Twisted Holographic Principle]
   There is a map of factorization algebras
   \[
-        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
+        (\Obs_{grav}|_{Y})^{!}\to \Obs^{N}_{brane}
   \]
@@
       that becomes an equivalence in the large $N$ limit.
-\end{slogan}
+\end{expect}
 
-    This statement has been tested in many examples \cite{}.
+Nonetheless, the above expectation has been tested in many examples \cite{}.
 

### 2022-08-01 fivebranes/index.tex
intro index twisted

@@
 \parsec[s:brkevin]
-As a way to highlight the key aspects of the construction, we consider the simplified model of Costello's twisted $M$ theory on $\R \times \T^* C$, where $C$ is a Riemann surface equipped with a nonvanishing holomorphic one-form $\d z$, with some number of twisted `fivebranes' wrapping the zero section
+As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory.
+The relevant local calculation can be found in the appendix of \cite{}; our goal here is to simply identify the salient global features that allow one to reduce to said local calculation.
+
+We consider the theory on $X = Tot (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
 \[
@@
 \]
-Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$.
+Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $M = X - 0 \times C$.
 
-If we remove the defect we obtain the manifold
-\[
-\left(\R \times \T^* C\right) - C \simeq C \times \R_{>0} \times S^2
-\]
+Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF).
 
-This manifold is equipped with the natural structure of a transversely holomorphic foliation (THF).
+If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
+The restriction $p|M$ equips $M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$.
+Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $M$.
+As part of this data, each of the fiber spheres is equipped with a complex foliation of rank 1.
 
-If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $\R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
-Denote by $r$ a coordinate for the direction $\R_+$ normal to the brane and let $z \in C$ be a local holomorphic coordinate.
+Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p|M$.
+The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres.
+In the holomorphic-topological setting, the Kaluza-Klein modes will be modeled by a variant of Cauchy-Riemann cohomology.
 
-The fibers of this projection away from $r = 0$ are all homeomorphic to the two-sphere.
-Moreover, they come equipped with a canonical complexified foliation of rank 1.
-Compactification along this projection results in a theory with infinitely many Kaluza--Klein modes roughly parametrized by the  Cauchy--Riemann cohomology of the two sphere as a hypersurface in $\R \oplus K_C|_z \simeq \R \times \C$.
+Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to 3d Chern-Simons.
 
-We will see that the including the backreaction corresponds to deforming this structure.
 For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.
@@
 Let $Z$ be a three-fold that the fivebranes wrap.
-We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$, and let $X = \text{Tot}(V)$.
-The condition on $V$ ensures that $X$ is a Calabi-Yau five-fold---in the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.
-The eleven-manifold we place our theory on is $\R\times X_V$, which we can view as the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
+We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$;
+this condition ensures that the total space of $V$ is a Calabi-Yau five-fold. In the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.
+
+Consider the bundle $\R\oplus V$; this bundle has a canonical partially flat connection.
+We wish to consider our eleven dimensional model on $X = Tot (\R\oplus V)$ which is the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
+The partially flat connection on $\R\oplus V$ equips $X$ with a canonical THF structure.
 
@@
 \begin{align*}
- h \colon  \R\times X & \to \R_{+} \\
+ h \colon  X & \to \R_{+} \\
   (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
 \end{align*}
-Letting $\pi \colon \R\times X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
+Letting $\pi \colon X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
 \[
@@
 \begin{tikzcd}
-M \ar[d,"p|M"'] \ar[r,hook] & \R \times X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
+M \ar[d,"p|M"'] \ar[r,hook] & X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
 \R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
@@
 The inclusions on the left are the natural embeddings.
-The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = \R \times X$ and the bottom right inclusion is the embedding at radius $r = 0$.
+The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = X$ and the bottom right inclusion is the embedding at radius $r = 0$.
 

### 2022-08-02 fivebranes/fact.tex
update

@@
 In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting).
-Our ansatz relies on a proposal for twisted holography developed by \brian{cites}.
+For the case at hand, our expectation for universal can be understood as the theory on a large number of membranes and fivebranes. 
+We will see how this interpretation is supported by the supergravity index calculations presented in the last section.
 
+Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloOmega,costello2021twisted,CP}.
+The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
+Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}. \brian{surya add more?}
+
+It is absolutely crucial for this proposal that we work in a derived setting using the BV formalism. 
 The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
@@
 
-We briefly highlight an analogous construction of the restricted factorization algebra which is natural from the point of view of membranes.
+We briefly highlight an analogous construction of the restricted factorization algebra describing membranes.
 Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.
@@
 As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
-Similarly to the proof of Lemma \ref{lem:technical} one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
+Similarly as above one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
 \[
@@
 \]
+As in the case of fivebranes, the $n=0$ eigenspace is equipped with the structure of a super Lie algebra whose exact form we do not state now.
 
@@
 In quantum field theory Koszul duality naturally appears in the problem of coupling topological line operators to some ambient bulk theory. 
-More generally, for higher dimensional topological defects, this problem is encoded by Koszul duality for the theory of $\EE_n$ algebras \cite{??}.
+More generally, for higher dimensional topological defects, this problem is encoded by Koszul duality for the theory of $\EE_n$ algebras \cite{FrancisGaitsgory} \cite[\S 5.2]{LurieHA}.
 
@@
 In this first part of this subsection we briefly recall how Koszul duality enters in the problem of coupling line operators. 
-We refer~\cite[\S 6]{CP1},~\cite[\S ??]{CG1}, or the review~\cite{PWkoszul} for more details. 
+We refer~\cite[\S 6]{CP1},~\cite[\S 8]{CG1}, or the review~\cite{PWkoszul} for more details. 
 Then, we give an ansatz for Koszul duality for factorization algebras of the form $\clie^\bu(\cL)$ where $\cL$ is some local Lie algebra. 
-From the point of view of the BV formalism this is not much of a condition, all such factorization algebras of classical observables can be cast in this form.
+From the point of view of the perturbative BV formalism this is not much of a restriction, all such factorization algebras of classical observables can be cast in this form.
 
@@
 \begin{prop}
-Let $\lie{g}$ be a Lie algebra and equip the associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
+Let $\lie{g}$ be a Lie algebra and equip the filtered associative (and commutative) dg algebra $\clie^\bu(\fg)$ with the augmentation induced by the tautological homomorphism $0 \to \lie{g}$.
 The Koszul dual of $\clie^\bu(\lie{g})$ with respect to this augmentation is equivalent to the universal enveloping algebra $U \fg$. 
@@
 \[
-\clie_\bu(\fg \otimes \Omega^\bu_{\R,c}).
+\clie_\bu(\fg \otimes \Omega^\bu_{\R,c}),
 \]
+see \cite[\S 3.4]{CG1}.
 To an open set $U \subset \R$ this produces the Chevellay--Eilenberg complex computing the Lie algebra {\em homology} of the dg Lie algebra $\fg \otimes \Omega^\bu_c(U)$---the $\fg$-valued compactly supported de Rham forms on $U$.
@@
 While we don't prove that the factorization algebra $\clie^\bu(\cL)^!$ satisfies any sort of categorical duality, we point out a universality that is satisfied with reference to couplings.
-In \cite[Chapter ??]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
+In \cite[Part 3]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
 The general context is the following: 
@@
 We also point out that there is a similar diagram of the form
-\beqn
+\beqn\label{eqn:limit2}
 \clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .

### 2022-08-02 fivebranes/index.tex
update

@@
 \section{Twisted supergravity states}
+\label{sec:states}
 
-The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT \cite{}.
-The goal of this section is to provide constructions of spaces of supergravity states in our eleven-dimensional model, via geometric quantization.
-The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property - they are naturally modules for certain infinite dimensional exceptional lie superalgebras.
+The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT. 
+The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization.
+The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras.
 We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
@@
 We begin by describing the relevant backgrounds.
-In eleven-dimensional supergravity, the ${\rm AdS}_7 \times S^4$ and ${\rm AdS}_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
+In eleven-dimensional supergravity, the $AdS_7 \times S^4$ and $AdS_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
 In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.
@@
 
-We consider the theory on $X = Tot (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
+We consider the theory on $X = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
 \[
@@
 
-Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF).
+Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.
 
@@
 \]
-where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation.
+where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
 We refer to the section below for a reminder on this geometric structure.
@@
 
-\subsection{Global symmetry for twisted fivebranes}
+\subsection{Global symmetry for twisted $AdS$}
 \label{s:global1}
 
-After complexification, the~six-dimensional superconformal algebra is $\lie{osp}(8|4)$ whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
-This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
-The holomorphic supercharge is a supertranslation 
+After complexification, the~six-dimensional and three-dimensional superconformal algebras are isomorphic to $\lie{osp}(8|4)$.
+The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
+This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
+It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
+
+In the six-dimensional case, the holomorphic supercharge is a supertranslation 
 \[
-Q \in \Pi S_+ \otimes \C^4 \subset \lie{osp}(8|4)
+Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \lie{osp}(8|4)
 \]
@@
 
+Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
+The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.
+
 In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
 Geometrically, this background is $AdS_7 \times S^4$. 
-In \cite{RSW} we have proposed a twisted analog of the AdS background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twisted superconformal algebra.
+Similarly, for backreacting membranes the background is $AdS_4 \times S^7$. 
+In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.
 
-In this section we will compute characters of the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes.
+We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
 Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
-We will enumerate states via considering a Cartan in the even subalgebra
+We will enumerate states via choosing a Cartan in the following subalgebra of the twisted superconformal algebra
 \beqn\label{eqn:bosonic1}
@@
 
-We recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
+We will first recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
 This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory. 
+The embedding is distinct for fivebranes and membranes.
+We turn first to the fivebrane case.
+
+\subsection{Supergravity states for twisted $AdS_7$}
 
@@
 
-\begin{rmk}
-In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
-\cite{KacClass}.
-\end{rmk}
+%\begin{rmk}
+%In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of the exceptional Lie algebra $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
+%\cite{KacClass}.
+%We will make use of this grading in \S \ref{s:kr}.
+%\end{rmk}
 
-The dimension of a Cartan subalgebra is four and accordingly, the equivariant character we study has four fugacities.
+The dimension of a Cartan subalgebra of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$ is four and accordingly, the equivariant character we study has four fugacities.
 We choose these explicitly as follows:
@@
   \beqn
-  h_1 = z_1 \del_{z_1} - z_2 \del_{z_2} , \quad h_2 = z_2 \del_{z_2} - z_3 \del_{z_3}.
+  h_1 = z_1 \frac{\del}{\del {z_1}} - z_2 \frac{\del}{\del{z_2}} , \quad h_2 = z_2 \frac{\del}{\del{z_2}} - z_3 \frac{\del}{\del{z_3}}.
   \eeqn
-   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element~$\eqref{eqn:Y}$. 
+   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element $Y$ from equation~$\eqref{eqn:Y}$. 
   \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
@@
 \end{itemize}
-The weights are summarized in table \ref{tbl:weights1}.
-Recall that the coordinates $(r_1,r_2)$ are used to label the basis of $\C^2$ in the space of fields $\Gamma^{hol}(\Hat{D}^3, K^{1/2}) \otimes \C^2$.
+
+The twisted supergravity states $\cH_{sugra}^{6d}$ form a representation for $\lie{osp}(6|2)$. 
+The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
+These are summarized in table \ref{tbl:sugraM5}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c}
+  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
+  \hline
+  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
+  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
+  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
+  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
+\end{tabular}
+\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \C^3$.}
+\label{tbl:sugraM5}
+\end{center}
+\end{table}
+
+We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{6d}_{sugra}$:
+\beqn
+f^{6d}_{sugra}(q,t_1,t_2,r) = \Tr_{\cH_{sugra}^{6d}} (-1)^F q^Y t_1^{h_1} t_2^{h_2} r^h .
+\eeqn
+The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace. 
+That is, we compute the expression
+
+\begin{prop}
+The single particle index of the space of twisted supergravity states $\cH_{sugra}^{6d}$ is given by the following expression
+\beqn
+f_{sugra}^{6d} (q, t_{1}, t_{2}, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
+\eeqn
+\end{prop}
+
+We record a few specializations of this index which we will remark on further in \S \ref{s:??}.
+\parsec 
+The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+\[
+f_{sugra}^{6d}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
+\]
+
+This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
+
+\parsec
+
+The specialization $t_1=t_2=r=1$ yields the single particle index
+\[
+f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
+\]
+
+\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...} \brian{not sure where this was supposed to go?}
+
+\subsection{Supergravity states for twisted $AdS_4$}
 
@@
 
-\subsection{Global symmetry for twisted membranes}
-
-\subsection{Counting supergravity states}
-
-We enumerate single particle supergravity states via computing the super trace of the operator $t_1^{h_1} t_2^{h_2} q^Y r^h$. 
-The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
-
-\parsec[s:pexp]
-
-\brian{characters, plethystic, etc.}
-
-%\parsec[s:singleops]
-%
-%\begin{prop}
-%Let $\Obs_{fivebrane}$ be the observables of the theory on a single fivebrane on $\C^3$ after performing the holomorphic twist.
-%There is a quasi-isomorphism of super commutative dg algebras 
-%\[
-%\Obs_{fivebrane} (0) \simeq \Sym \left( I(0,0;1;-1)^* \right) .
-%\]
-%\end{prop}
-%\begin{proof}
-%This follows from Lemma \ref{lem:localops}.
-%In \cite{SWsuca6d} a dg lift of Kac's module $I(0,0;1;-1)$ was defined with the following bigraded pieces:
-%\beqn
-%\text{bidegree} (-1,+)\colon \quad \Hat{\Omega}_3^{2} , \qquad \text{bidegree} (0,+)\colon \quad \Hat{\Omega}^{3}_3
-%\eeqn
-%and
-%\beqn
-%\text{bidegree} (-1, -)\colon \quad \Hat{\Omega}^{3/2}_{3} \otimes R .
-%\eeqn
-%The differential is the (algebraic) de Rham differential $\del \colon \Hat{\Omega}^2 \to \Hat{\Omega}^3$. 
-%The differential is zero on the odd summand.
-%We will call this cochain complex $(E_{fivebrane}(\Hat{D}^3), \del)$.
-%
-%From the description of the fields of the holomorphic twist of the single fivebrane it is easy to see that the Taylor expansion at $0 \in \C^3$ defines a cochain map
-%\[
-%(\cE_{fivebrane} (\C^3), Q) \to (E_{fivebrane}(\Hat{D}^3), \del) 
-%\]
-%That this induces a quasi-isomorphism $J_0^\infty \cE_{fivebrane} \simeq E (\Hat{D}^3)$ follows from the Dolbeault Poincar\'e lemma.
-%\end{proof}
-
-\subsection{The large $N$ limit}
-
-We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
-Unlike the analysis above, we will the twisted holography proposal to compute this character.
-We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra
-\[
-\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
-\]
-which embeds in the following way:
-\begin{itemize}
-\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
-where $(a_{ij}) \in \lie{sl}(3)$. 
-\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
-\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
-\beqn\label{vf1}
-\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
-\eeqn
-\end{itemize}
-
-Correspondingly, the equivariant character thus has four fugacities, which we label as follows:
-\begin{itemize}
-  \item $t_{1}, t_{2}$ again denote generators for the Cartan of $\lie{sl}(3)$ acting by vector fields on $\C^{3}_{z}$.
-  \item $r$ denotes a generators for the Cartan of a $\lie{sl}(2)$ acting by the fundamental representation on the normal directions $\C_{w_1} \times \C_{w_2}$.
-  \item $q$ denotes a generator for the Cartan of additional $\lie{gl}(1)$ generated by the divergence-free vector field \eqref{vf1}. 
-\end{itemize}
-
-This choice of weights is summarized in Table \ref{tbl:sugra}.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c}
-  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
-  \hline
-  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
-  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
-  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
-  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
-\end{tabular}
-\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity.}
-\label{tbl:sugra}
-\end{center}
-\end{table}
-
-\parsec
-
-\begin{prop}
-  The character of local operators of the holomorphic twist of the theory on a large number of fivebranes is given by the following plethystic exponential
-
-  \[ \rm PExp [f_{large N}(t_{1}, t_{2}, q, r)] \]
-
-  where the single particle index is \[f_{large N}(t_{1}, t_{2}, q, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
-\end{prop}
-
-\parsec
-
-The specialization $t_1=t_2=r=1$ yields the single particle index
-\[
-\frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
-\]
-
-\parsec 
-The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
-\[
-f_{two}(t_1, 1, q, q^{1/2}) = \frac{q}{(1-q)^2}
-\]
-
-This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
-
-\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...}
-
 %\end{document}

### 2022-08-02 fivebranes/kr.tex
update

@@
 \section{A series of finite $N$ conjectures}
+\label{s:kr}
 
@@
 
-In \cite{KR1}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
-We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR1}.
+In \cite{KR2}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
+We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR2}.
 Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
-Following the description of these irreducible modules given in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.
+Following the description of these irreducible modules constructed in \cite{KR1,KR2} we compute (un)refined characters and proceed to give a conjectural procedure for computing (un)refined fivebrane indices.
 
@@
 
-We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR1}.
+We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR2}.
 In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.
@@
 \subsection{Irreducible representations of $E(3|6)$}
-We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in \cite{KR1,KR2,KR3}.
+We recall the requisite knowledge of irreducible representations of $E(3|6)$ as characterized in~\cite{KR1,KR2,KR3}.
 The main goal of this section is to deduce explicit formulas for certain irreducible modules which we will, in turn, relate to indices of local operators of the twisted fivebrane theory.
@@
 
-\subsection{Modified characters for degenerate modules of type $A$} \label{s:typeA}
+\subsection{Character of modified type $A$ modules} \label{s:typeA}
 
@@
 \beqn\label{eqn:MA}
-\ch \, \til M_A(\lambda_1,\lambda_3) = q^{y} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
+\ch \, \til M_A(\lambda_1,\lambda_3) = t^{y_A} R(t,r,t_1,t_2) \cdot \ch (V_A^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
 \eeqn
-where $y = \lambda_1 - \frac32 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
+where $y_A = 2\lambda_1 - 3 \lambda_3$, $R$ is as in Lemma \ref{lem:R} and 
 \beqn\label{eqn:su}
@@
 \begin{align*}
-\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
+\ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
 %\\ 
@@
 \begin{multline}
-\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j} \cdot \ch^{\lambda_3+j}_{SU(2)} \\ =
-\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
+\ch \til M_A(\lambda_1+j, \lambda_3+j) = R \cdot t^{2 \lambda_1-3 \lambda_3-j} \cdot \ch_{SU(3)}^{\lambda_1+j}(t_1^{-1},t_2^{-1}) \cdot \ch^{\lambda_3+j}_{SU(2)}(r) \\ =
+\frac{t^{2 \lambda_1 - 3 \lambda_3} R}{1-r^{-2}} \ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) t^{-j} (r^{\lambda_3 + j} - r^{-\lambda_3 - j - 2}).
 \end{multline}
@@
 \beqn
-\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_3+j} (t_1^{-1},t_2^{-1}) x^j .
+\til p^{\lambda_1} (x,t_1,t_2) = \sum_{j \geq 0} \ch_{SU(3)}^{\lambda_1+j} (t_1^{-1},t_2^{-1}) x^j .
 \eeqn
@@
 \begin{proof}
+We start by expanding the expression for the generating function $\til p_{\lambda_1}(t_1,t_2,x)$:
 \begin{multline}
@@
 
-Where
+Here, we have introduced the following functions
 \begin{itemize}
@@
 \end{align*}
-where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h}. 
+where $h_{\lambda_1}(t_1,t_2,x)$ is as in equation \eqref{eqn:h1}. 
 \end{lem}
@@
 %\end{itemize}
-\subsection{Characters for degenerate modules of type B} \label{s:typeB}
+
+\subsection{Character of modified type $B$ modules} \label{s:typeB}
 
@@
 
-\begin{prop}
-\label{prop:chB}
-For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ specialized at $t_1=t_2=1$ is given by the expression
+Recall that the type $B$ degenerate modules are defined by induction from the $\fg_0$-module 
+\[
+V = V^{\lambda_1,\lambda_3}_B \subset \C[z_i,\del_{w_a}]
+\] 
+given by polynomials of homogenous degree $\lambda_1,\lambda_3$ in the variables $z_i,\del_{w_a}$ respectively.
+As in the type $A$ case, we have the following expression for the character of the modified type $B$ module.
+
+%\begin{prop}
+%One has
+%\beqn\label{eqn:MA}
+%\ch \, \til M_B(\lambda_1,\lambda_3) = t^{y_B} R(t,r,t_1,t_2) \cdot \ch (V_B^{\lambda_1,\lambda_3}) (t_1^{-1},t_2^{-1},r)
+%\eeqn
+%where $y_B = 2\lambda_1 + 3 \lambda_3+6$, $R$ is as in Lemma \ref{lem:R} and
+%\beqn\label{eqn:suB}
+%\ch(V_B^{\lambda_1,\lambda_3})(t_1,t_2,r) = \ch_{SU(3)}^{\lambda_1}(t_1,t_2) \ch_{SU(2)}^{\lambda_3} (r) 
+%\eeqn
+%is the $SU(3) \times SU(2)$ character of the representation $V_B^{\lambda_1,\lambda_3}$.
+%\end{prop}
+
+Just as in the type A case we can compute the character of the Verma module $\til M_B(l,\lambda_3-l)$, for $0 \leq l \leq \lambda_3$ by the formula
+\beqn\label{eqn:chMB}
+\ch \til M_B(l,\lambda_3-l) = t^{3 \lambda_3 - l + 6} R(t,t_1,t_2,r) \ch_{SU(3)}^{l}(t_1^{-1},t_2^{-1}) \ch_{SU(2)}^{\lambda_3-l} (r)  .
+\eeqn
+Introduce the generating function
+\beqn
+\til q_{\lambda_3} (t_1,t_2,x) = \sum_{l=0}^{\lambda_3} \ch^l_{SU(3)} (t_1^{-1},t_2^{-1}) x^l 
+\eeqn
+
+%\begin{prop}
+%\label{prop:chB}
+%For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ specialized at $t_1=t_2=1$ is given by the expression
+%\begin{multline}
+%\label{eqn:chB3}
+%t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+%\end{multline}
+%where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chB}. 
+%\end{prop}
+
+\begin{thm}
+\label{thm:chB}
+For $\lambda_3 \geq 0$ the character $\ch \til I_B(0,\lambda_3)$ is given by the expression
 \begin{multline}
 \label{eqn:chB3}
-t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} \\ + \frac{t^{2\lambda_3 + 10}}{(1-t^2)^3 (1-r^{-2})} \left(p_{\lambda_3+2} (t^{-1} r) (1 - t^{-1} r^{-1})^3 - r^{-2} p_{\lambda_3}(t^{-1} r^{-1})(1-t^{-1}r)^3 \right)
+\frac{t^{2 \lambda_3 + 6} R(t,t_1,t_2,r)}{1-r^{-2}} \left(r^{\lambda_3} \til q_{\lambda_3} (t_1,t_2,t^{-1}r^{-1}) - r^{-\lambda_3-2} \til q_{\lambda_3} (t_1,t_2,t^{-1}r) \right) \\ + \frac{t^{2 \lambda_3+10}}{(1-t_1^{-1} t^2)(1-t_1t_2^{-1}t^2)(1-t_2 t^2)(1-r^{-2})} \times \\
+\left(p_{\lambda_3+2}(t_1,t_2,t^{-1} r) (1-t_1^{-1} r^{-1} t^{-1})(1-t_1t_2^{-1} r^{-1} t^{-1})(1-t_2 r^{-1} t^{-1}) \right.
+\\
+- \left. r^{-2} p_{\lambda_3+2}(t_1,t_2,r^{-1} t^{-1})(1-t_1^{-1} r t^{-1})(1-t_1t_2^{-1} r t^{-1})(1-t_2 r t^{-1}) \right)
 \end{multline}
-where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Proposition \ref{prop:chB}. 
-\end{prop}
+where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedA}.
+\end{thm}
 
 \begin{proof}
-We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in \S \ref{s:typA}.
-Thus, it suffices to compute the modified character of the type $B$ Verma modules 
+We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in Theorem~\ref{thm:refinedA}.
+The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last two lines in the stated formula.
+
+It suffices to compute the character of the modified type $B$ Verma modules 
 \[
@@
 
-The character of the Verma module $\til M_B(k,\lambda_3-k)$, for $0 \leq k \leq \lambda_3$, is given by
-\[
-\ch \til M_B(k,\lambda_3-k)|_{t_1=t_2=1} = t^{3 \lambda_3 - k + 6} R(t,r) .
-\]
-Thus, \eqref{eqn:chB2} simplifies to 
-\[
-\ch \til I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \ch \til I_{A}(\lambda_3+2,0) .
-\]
-The result now follows from the formula for $\ch \til I_A(\lambda_3+2,0)$ given in Proposition~\ref{prop:chA}.
+%Thus, \eqref{eqn:chB2} simplifies to 
+%\[
+%\ch \til I_B(0,\lambda_3) = t^{2 \lambda_3 + 6} R(t,r) \frac{1-t^{\lambda_3+1}}{1 - t} + \ch \til I_{A}(\lambda_3+2,0) .
+%\]
+%The result now follows from the formula for $\ch \til I_A(\lambda_3+2,0)$ given in Proposition~\ref{prop:chA}.
 \end{proof}
@@
 \eeqn
+
+\parsec[s:firstcase]
+
+Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$.
 

### 2022-08-02 fivebranes/twisted.tex
update

@@
-\documentclass[11pt]{amsart}%
+%\documentclass[11pt]{amsart}%
 %
 %%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
+%\usepackage{macros-fivebrane}
 
 %
-\begin{document}
+%\begin{document}
 %
@@
 \section{Twists in dimensions eleven, six, and three}
+\label{s:twisted}
+
+In this section we review the descriptions of twists of the key players in $M$-theory including eleven-dimensional supergravity as well as the three and six-dimensional superconformal field theories associated to the abelian Lie algebra~$\lie{gl}(1)$.
 
@@
 
-Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of $Q$.
+Eleven-dimensional supersymmetry admits two inequivalent classes of twists characterized by the dimension of the subspace of translations spanned by the image of bracketing with the twisting supercharge.
 \begin{itemize}
@@
 
-The eleven-dimensional theory exists on any manifold which is locally of the form 
+The eleven-dimensional theory described in \cite{RSW} exists on any manifold which is locally of the form 
 \[
@@
 More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
+We will elaborate on this further in \S \ref{sec:states}.
 
-In the first few sections we recall the fields and equations of motion of this eleven-dimensional theory.
+We recall the fields and equations of motion of this eleven-dimensional theory.
 
@@
 
-To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
-Let's first consider the case that the eleven-dimensional manifold is of the form $S \times X$, where $X$ is a Calabi--Yau fivefold.
-We let $\T_X$ stand for the holomorphic tangent bundle of $X$ and $\Bar{\T}_X$ its complex conjugate.
+%To begin this section we highlight some of the important features of the eleven-dimensional model considered in \cite{RSW}. 
+%Let's first consider the case that the eleven-dimensional manifold is of the form $S \times X$, where $X$ is a Calabi--Yau fivefold.
+Let $\T_X$ stand for the holomorphic tangent bundle of the Calabi--Yau fivefold $X$ and $\Bar{\T}_X$ its complex conjugate.
 The complexified tangent bundle of the eleven-manifold $S \times X$ decomposes as
@@
 
-Before giving a full description of the fields and equations of motion wrapped up into the BV formalism, we give an explicit description of the equations of motion and gauge symmetries.
+Momentarily we will give a full presentation of the fields and equations of motion within the Batalin--Vilkovisky (BV) formalism.
+But first, we will give a more direct description of the equations of motion and gauge symmetries of the model.
 
 One of the primary fields of eleven-dimensional supergravity describes deformations of the metric $g$.
-Since we work in a background which has $SU(5)$ holonomy we can take the background metric on $S \times X$ to be the product of the flat metric on $S$ with a Calabi--Yau metric $g_{CY}$ on $X$.
+Since we work in a background which has $SU(5)$ holonomy we can take the background metric on $S \times X$ to be the product of the flat metric on $S$ with a Calabi--Yau metric $g_{X}$ on $X$.
 
@@
 \[
-\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* 
+\Bar{\T}_X^* \otimes \T_X \cong \Bar{\T}^*_X \otimes \Bar{\T}_X^* . 
 \]
-which we will denote by $\mu$. 
+Here, we have used the isomorphism granted by the K\"ahler metric $g_{X}$.
 In local holomorphic coordinates $\mu$ admits a description like
@@
 \]
-More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms of arbitrary Dolbeault type, which we can write in superfield notation as
+More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms on $X$ of arbitrary Dolbeault type and de Rham forms on $S$, which we can write in superfield notation as
 \[
-\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j}
+\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j} + \mu^{\Bar{I}}_{t,j} (t;z,\zbar) \d t \d \zbar_{\Bar{I}} \otimes \del_{z_j}
 \]
-where there is a sum over the multi-index $\Bar{I}$. 
-In this notation, the component of the field $\mu$ is {\em odd} if $|I|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
+where there is a sum over the multi-index $\Bar{I}$ as it ranges over subsets of $\{1,\ldots,5\}$.
+In this notation, the component $\mu^{\Bar{I}}_j$ is {\em odd} if $|\Bar{I}|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
+Similarly, the component $\mu^{\Bar{I}}_{t,j}$ is {\em even} if $|\Bar{I}|=0,2,4$ is even and {\em odd} if $|I| = 1,3,5$ is odd.
 In particular we have odd fields $\mu_j(t;z,\zbar) \del_{z_j}$ which play the role of ghosts for infinitesimal changes of coordinates.
@@
 The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$.
-This means that it is required to satisfy the condition 
+This means that it is required to satisfy the equation
 \beqn
@@
 where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
-In the BV formalism one can encode this by introducing another field, but for the sake of discussion we omit that approach for now.
+By including the full space of BV fields, this condition does arise from an action functional principle---it is not an additional constraint like the one present in the six-dimensional superconformal theory.
+The field to add in this situation is a Dolbeault form $\nu \in \Omega^{0,\bu}(X)$ which imposes the equation above upon setting $\nu = 0$.
 Another piece of the equations of motion for~$\mu$ dictate that it be locally constant along~$S$.
@@
 
-One of the other bosonic fields of eleven-dimensional supergravity is a three-form that we denote by~$\sf C$.
-In the BV formalism we see all types of differential forms corresponding to a tower of ghosts for this $C$-field together with antifields and antighosts.
+The other primary bosonic field of eleven-dimensional supergravity is a three-form.
+In the BV formalism we see all types of differential forms corresponding to a tower of ghosts for this higher gauge field together with antifields and antighosts.
 
@@
 \]
-where the first sum is over tuples $P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$.
-%The second sum is over tuples $P',Q'$ such that $\sum_i (p_i'+q_i') = 2$.
+where the first sum is over tuples~$P=(p_1,p_2,p_3),Q=(q_1,q_2,q_3)$ and
+the second sum is over tuples~$P'=(p'_1,p'_2,p'_3),Q=(q'_1,q'_2,q'_3)$
 
 In the minimal twist only forms with $p_i ,p_i'\leq 1$ survive. 
-Thus, we have as part of the complex of fields in the twisted theory
+Thus, we have as part of the complex of fields in the twisted theory the space of forms
 \[
@@
 We denote a general (non-homogenous) element in the first summand by $\beta$ and an element in the second summand by $\gamma$.
-When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
-Fields $\beta^{k;q}$ with $k+q = $even are {\em odd} and fields $\gamma^{k;q}$ with $k+q = $odd are {\em even} fields.
+As above we can expand such fields in local coordinates using multi-indices by 
+\begin{align*}
+\beta & = \beta^{\Bar{I}} \d \zbar_{\Bar{I}} + \beta_t^{\Bar{J}} \d t \d \zbar_{\Bar{J}}\\
+\gamma & = \gamma^{i \Bar{I}} \d z_i \d \zbar_{\Bar{I}} + \gamma_t^{j \Bar{J}} \d t \d z_j \d \zbar_{\Bar{J}}.
+\end{align*}
+%When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
+Fields $\beta^{\Bar{I}}, \gamma_t^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp.
+even) are {\em even} (resp.
+{\em odd}) and fields $\beta_t^{\Bar{I}}, \gamma^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp.
+even) are {\em odd} (resp.
+{\em even}).
 
@@
 Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.
+On the left hand side we are implicitly using an identification between the holomorphic tangent bundle $\T_X$ and the bundle $\wedge^4 \T^*_X$ granted by the holomorphic volume form on $X$.
+This allows us to view this equation as taking place entirely in the graded space $\Omega^\bu(S) \hotimes \Omega^{4,\bu}(X)$. 
+In particular, this equation is inhomogenous in form type.
+As an example of the homogenous form type $(0;4,2)$ piece of this equation we have 
+\[
+\ep^{ijklm} \del_{\zbar_{\bar{j}}} \mu_m^{\bar{i}} + \ep^{ijkmn} \del_{z_l} (\mu_{m} \mu_{n}) =\del_{z_i} \gamma^{j \bar{i}} \del_{z_k} \gamma^{l \bar{j}} 
+\]
 
-The theory also enjoys the following gauge symmetries.
-First, for any 
-\brian{finish}
 %Along $S$, $\beta$ and $\gamma$ behave like abelian gauge fields.
@@
 We move on to give a complete description of our eleven-dimensional model within the Batalin--Vilkovisky (BV) formalism.
-This amounts to introducing antifields and antighosts to the fields and ghosts that we have just described.
-One of the key structures is the graded skew-symmetric pairing between fields and antifields (ghosts and antighosts).
+In the superfield notation above we have implicitly provided all components of the ghosts, fields, anti-fields, and anti-ghosts.
+One of the key structures in the BV formalism is the graded skew-symmetric pairing between fields and antifields (ghosts and antighosts).
 Once such a pairing $\omega_{BV}$ is introduced, one can opt to describe solutions to the equations of motion as Maurer--Cartan elements of a certain sheaf of ($\Z/2$-graded) $L_\infty$ algebras on $X \times S$.
@@
 \d \beta & = \del \beta \in \Omega^1_X \subset L_{X,-} \\
-\d \mu & = \div \mu \in \cO_X \subset L_{X, -}
+\d \mu & = \div \mu \in \cO_{X,\nu} \subset L_{X, -}
 \end{align*}
@@
 \begin{align*}
-[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
-[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
-[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
+[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \in \PV^1_X \\
+[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma \in \cO_{X,\beta} .\\
+[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma \in \Omega^1_X \\
+[\gamma_1,\gamma_2] & = \Omega_X \vee (\del \gamma_1 \wedge \del \gamma_2) \in \PV^1_X .
 \end{align*}
@@
 
-Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.
+The free part of the BV action is easy to describe
+\beqn
+\int_{S \times X} \left(\gamma \d \mu\right) \Omega_X + \int_{S \times X} (\beta \dbar \nu) \Omega_X + \int_{S \times X} (\beta \div \mu) \Omega_X ,
+\eeqn
+where $\Omega_X$ is the holomorphic volume form on~$X$.
+Notice that in the first two terms no holomorphic derivatives appear in the direction of $X$ due to the presence of this holomorphic volume form.
+
+The interacting part of the action is more complicated, partly for the reason that in our presentation above it is given by a formal series in the space of fields, rather than just a polynomial in the fields.
+Explicitly, the interaction can be written as
+\beqn
+\frac12 \int_{S \times X} (\mu^2 \del \gamma) \frac{\Omega_X}{1- \nu} + \frac16 \int_{S \times X} \gamma \del \gamma \del \gamma .
+\eeqn
+%
+%Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.
 
@@
 
-In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of the nonminimal twist defined on multi Taub--NUT spaces.
-The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
+In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
+The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
 
@@
 
-There are two parameters in this theory which Costello calls $\delta$ and $\ep$.
-The parameter $\delta$ controls the Chern--Simons type coupling, which in this section and going forward we will simply set to be the unit. 
-The parameter $\ep$ measures the non-commutativity. 
-It appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star$.
+There are two parameters in this theory $\delta$ and $\ep$, see \textit{loc. cit.}.
+The parameter $\delta$ controls the coupling of the Chern--Simons action, which in this section and going forward we will simply set to be the unit. 
+The parameter $\ep$ measures the non-commutativity---
+it appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star_\ep$.
 
@@
 \]
-We continue to label elements of the homogeneous pieces as $(k;q)$ forms.
-We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
-Not only is $\cL_{5d}$ a dg algebra, if we adjoin formal parameter then $\cL_{5d}[[\ep]]$ is a dg Lie algebra with respect to the Moyal commutator $[-,-]_\star$.
+In local coordinates a general differential form in $\cL_{5d}$ admits a decomposition as
+\[
+\alpha = \alpha^{\Bar I} \d \zbar_{\Bar I} + \alpha^{\Bar I}_t \d t \d \zbar_{\Bar I} .
+\]
+%We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
+We can understand the Moyal product along the holomorphic symplectic surface $Y$ as endowing $\cL_{5d}[[\ep]]$ with the structure of a dg algebra. 
+Of course, we can forget down to a dg Lie algebra structure with respect to the Moyal commutator $[-,-]_{\star_{\ep}}$.
 
@@
 
-We can take a gauge condition where $\alpha^{1;0}$ vanishes.
-In this case the equations of motion for the one-form field simply reads
+We can take a gauge condition where the $\d t$ component of the one-form $\alpha_t$ vanishes.
+In this case the equations of motion for the one-form field, in components, simply reads
 \beqn
-\dbar \alpha^{0;1} + \alpha^{0;1} \star \alpha^{0;1} = 0,
+\del_{\zbar_{\Bar{i}}} \alpha^{\Bar{j}} + \alpha^{\Bar{i}} \star_\ep \alpha^{\Bar{j}} = 0,
 \eeqn
-together with the condition that $\d_S \alpha^{0;1} = 0$.
-Here $\star$ denotes the holomorphic Moyal product on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
+together with the condition that $\del_t \alpha^{\Bar{i}} = 0$ for all $\Bar{i}, \Bar{j}$.
+%Here $\star_{\ep}$ denotes the holomorphic Moyal product on $Y$ and $\del_t$, $$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
 
@@
 
-Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $\alpha^{0;0} \in C^\infty (S\times Y)[[\ep]]$. 
-Explicitly, the corresponding infinitesimal gauge transformation is given in components by
+Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $f \in C^\infty (S\times Y)[[\ep]]$. 
+Explicitly, the corresponding infinitesimal gauge transformation for the one-form component of $\alpha$ is given by
 \[
-\alpha^{k;q}\mapsto \alpha^{k;q} + \d_S \alpha^{0;0} +\dbar \alpha^{0;0} + \{\alpha^{0;0}, \alpha^{k;q}\}_{Y}
+\alpha \mapsto \alpha + \del_t f \d t +\del_{\zbar_{\Bar{i}}} f \d \zbar_{\Bar{i}} + [f, \alpha]_{\star_\ep} .
 \]
+Here, $[-,-]_{\star_{\ep}}$ is the commutator with respect to the Moyal product $\star_\ep$.
 
@@
 \beqn
-S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star \alpha \star \alpha \right) \wedge \Omega_Y .
+S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star_\ep \alpha \star_\ep \alpha \right) \wedge \Omega_Y .
 \eeqn
-Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$.
+Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$ (notice that that no holomorphic derivatives appear in the kinetic term due to the appearance of $\Omega_Y$).
 
@@
 The holomorphic, or minimal, twist. 
-This twist leaves three real directions invariant. 
+This twist leaves three real directions invariant and is stabilized by the double cover of the group $U(3)$. 
 The holomorphic twist of any $\cN=(2,0)$ theory can be defined on any complex three-fold $Z$ equipped with a square-root of its canonical bundle. 
@@
 The non-minimal twist. 
-This twist leaves five real directions invariant.
+This twist leaves five real directions invariant and is stabilized by the group $SO(4) \times U(1)$. 
 The non-minimal twist of any $\cN=(2,0)$ theory can be defined on a six-manifold of the form $M^4 \times \Sigma$ where $M^4$ is a smooth four-manifold and $\Sigma$ is a Riemann surface. 
@@
 However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.
-We describe this Poisson bivector explicitly
-\surya{ FINISH }
-In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
-\[
-\cL_{N=1} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
-\]
+In the (degenerate) BV formalism, the space of fields of the theory is
+\beqn
+\cE^{6d}_{\lie{u}(1)} = \Omega^{\geq 2, \bu}(Z)[1] \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 [1] ,
+\eeqn
+and the linear BRST differential is described by the following diagram
+\beqn\label{eqn:weight-1a}
+\begin{tikzcd}
+\ul{-1} & \ul{0}\\
+\Pi \Omega^{0,\bu}(Z, K_Z^{1/2} \otimes \C^2) & \\
+\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) ,
+\end{tikzcd}
+\eeqn
+where the $\dbar$ operator acts implicitly on each summand.
 
@@
 
-The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory - a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{} For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect.
-\cite{}
+The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory---a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{Aharony:2008ug}.
+For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect \cite{Bagger:2007jr,Gustavsson:2007vu}.
 
-Twists of $\cN=8$ gauge theories in 3d were classified in \cite{}.
-Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{}.
+Twists of three-dimensional $\cN=8$ supersymmetric gauge theories were classified and characterized in \cite{ESsusy,ESW,Garner:2022vds}. 
+Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{Aganagic:2017tvx}. 
 Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:
@@
 This twist leaves 2 real directions invariant.
-The theory can be defined on a 3-manifold of the form $S\times \Sigma$ where $S$ is a smooth oriented one-manifold and $\Sigma$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
+The theory can be defined on a 3-manifold of the form $S\times C$ where $S$ is a smooth oriented one-manifold and $C$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
 
@@
 
-We briefly recall the description of the minimal twist of the ABJM theory for $N=1$.
-
-\surya{fields, gauge symmetries, etc}
-
-In the BV formalism, this free theory can be packaged into the data of an abelian $\Z$ graded local Lie algebra on $\Sigma$ which takes the form
+We briefly recall the description of the minimal twist of the ABJM theory associated to the single membrane theory.
+Let $K^{1/4}_C$ be a fourth-root of the canonical bundle of $C$. 
+In the BV formalism, this free theory has underlying space of fields
 \[
-\Omega^{\bu}(S)\times \left (\Omega^{0,\bu}(\Sigma) \oplus \Pi \Omega^{0,\bu} (\Sigma )\right ) \otimes \C^{4}.
+\Omega^{\bu}(S) \hotimes \left[ \Omega^{0,\bu}(C, K^{1/4}_C \otimes \C^4) \oplus \Pi \Omega^{0,\bu} (C,K^{3/4}_C \otimes \C^4) \right] .
 \]
+The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
+If we split the fields according to the direct sum above by $X, \Psi$ then the action is simply
+\[
+\int_{S \times C} \Psi \d_S X + \int_{S \times C} \Psi \dbar_\Sigma X .
+\]
+Here, we have implicitly chosen a non-degenerate symmetric pairing on $\C^4$.
 

### 2022-08-05 fivebranes/kr.tex
merge

@@
 In \cite{KR2}, a $\Z$-graded decomposition of $E(5|10)$ is defined which has the property that the weight zero subalgebra is isomorphic to the exceptional super Lie algebra $E(3|6)$.
-We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:flatdecomp}, to this decomposition considered in \cite{KR2}.
+We compare our decomposition of the $!$-dual factorization algebra of $\clie^\bu(\cL_{sugra})$ on the complex three-fold $Z = \C^3$, see \S \ref{s:fact}, to this decomposition considered in \cite{KR2}.
 Naturally, every other graded summand appearing in the decomposition of $E(5|10)$ is a module for $E(3|6)$---it turns out that every module that appears in this way is irreducible.
@@
 There is a different decomposition of $E(5|10)$ (and its central extension) which has as its weight zero piece the subalgebra $E(1|6)$; this decomposition is natural from the point of view of membranes.
-We comment on this in \S \ref{sec:membraneindex}.
+We comment on this in \S \ref{sec:kacmembrane}.
 %an embedding of $E(3|6)$ into $E(5|10)$ is constructed by considering the following auxiliary weight grading on the super Lie algebra $E(5|10)$. 
@@
 We begin by turning to the algebraic side of things and start by recalling the weight decomposition of $E(5|10)$ constructed in \cite{KR2}.
-In \S \ref{s:m5localops} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.
+In \S \ref{s:kacfivebrane} we return to fivebranes and use this to give a  characterization of local operators of the twisted theory.
 
@@
 \]
-See \cite[\S 3]{RSW}. 
+See \cite[\S 3]{RSW}, and \S \ref{s:kacfivebrane}.
 The central extension is defined by the (totally even) three-linear cocycle
@@
 
-There is another auxiliary grading that we will make use of which is also defined in \cite{KR,KacClass}. 
+There is another auxiliary grading that we will make use of which is also defined in \cite{KR2,KacClass}. 
 The super Lie algebra $E(5|10)$ carries a (non-cohomological) consistent $\Z$-grading by declaring 
@@
 \beqn\label{eqn:p}
-p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h(t_1,t_2,x)\right) 
+p_{\lambda_1}(t_1,t_2,x) = t_1^{\lambda_1} t_2^{-\lambda_1} \left(1 + (1+t_1^{-1} t_2^{-1} - t_1^{-1} x) h_{\lambda_1}(t_1,t_2,x)\right) 
 \eeqn
@@
 \beqn\label{eqn:h1}
-h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_2 -2}\right)  
+h_{\lambda_1}(t_1,t_2,x) = t_2 (t_1^{-1} t_2 - x) \left(1 + t_1^{-1} t_2^2 + \cdots + t_1^{-\lambda_1+1} t_2^{2 \lambda_1 -2}\right)  
 \eeqn
-and for $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.
+where the sum in parentheses has $\lambda_1$ terms.
+For $\lambda_1 = 0$ we set $h_0 (t_1,t_2,x) = 0$.
 
@@
 \label{thm:refinedA}
-For any $\lambda_1,\lambda_3 \geq 0$ the character of $\til I_A(\lambda_1,\lambda_3)$ is given by the following expression
+For any $\lambda_1,\lambda_3 \geq 0$ the character of $\ch \til I_A(\lambda_1,\lambda_3)$ is given by the following expression
 \begin{multline}
@@
 \end{multline}
+where $p_{\lambda_1}$ is as in equation \eqref{eqn:p}.
 \end{thm}
@@
 \eeqn
-where the polynomial $p_{\lambda_1}(x,t_1,t_2)$ is given by equation \eqref{eqn:p}.
+where the polynomial $p_{\lambda_1}(t_1,t_2,x)$ is given by equation \eqref{eqn:p}.
 
@@
 \begin{multline}
+\label{eqn:long}
 t_1^{\lambda_1} t_2^{-\lambda_1} \sum_{j \geq 0} t_1^{j} t_2^{-j} x^j \sum_{k=0}^{\lambda_1 + j}t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
@@
 
-Now, the proof of Theorem \ref{thm:refinedA} is an immediate computation. 
+Now, we plug these expressions into \eqref{eqn:long} and simplify to obtain
 \begin{multline}
@@
 \end{multline} 
+This completes the proof of Theorem \ref{thm:refinedA}.
 
@@
 
-Note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of the six-dimensional theory abelian superconformal theory from Proposition \ref{prop:6done}.
+We note that upon substituting $q = t^2$ this agrees with $\chi_{\lie{u}(1)}^{6d}(t_1,t_2,q,r)$---the character of local operators on the holomorphic twist of the abelian six-dimensional superconformal theory, see Proposition \ref{prop:6done}.
 
@@
 
-Again, we note that upon substituting $q = t^2$ this agrees with the our direct computation of the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ which we computed in Proposition \ref{prop:6dtwo}.
+Again, we note that upon substituting $q = t^2$ this agrees with $\chi_{\lie{sl}(2)}^{6d}(t_1,t_2,q,r)$---the character of local operators on the holomorphic twist of our conjectural description of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$, see Proposition \ref{prop:6dtwo}.
+
+We will see how these agreements for small values of $\lambda_1,\lambda_3$ fit into a more general relationship between the irreducible modules $\til I_A(\lambda_1,\lambda_3)$ and $\til I_{B} (\lambda_1,\lambda_3)$ and local operators of the universal fivebrane theory in \S \ref{s:kacfivebrane}.
 
@@
 \end{multline}
-where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedA}.
+where the polynomial $p_{\lambda_3 + 2}(x)$ is as in Theorem \ref{thm:refinedB}.
 \end{thm}
@@
 We have already computed $\ch\til I_A(\lambda_1,\lambda_3)$ for any pair $(\lambda_1,\lambda_3)$ in Theorem~\ref{thm:refinedA}.
-The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last two lines in the stated formula.
+The formula for $\ch \til I_A(\lambda_3+2,0)$ accounts for the last three lines equation \eqref{eqn:chB3}.
 
@@
 \[
-\til M_{B}(k,\lambda_3-k) .
+\til M_{B}(l,\lambda_3-l) ,
 \]
+and to sum from $l = 0$ to $l = \lambda_3$. 
+This is precisely the first line of \eqref{eqn:chB3}.
 
@@
 
-Notice that since $R(t=r) = 0$ it follows that if we further specialize at $t = r$ and substitute $q = t^2$ then the first line of \eqref{eqn:chB3} vanishes so that
+Notice that since $R(t=r) = 0$ and that $\ch \til M_B$ is regular along $t=r$ it follows that if we specialize at $t = r$ and substitute $q = t^2$ then the first line of \eqref{eqn:chB3} vanishes so that
 \beqn
@@
 
-\parsec[s:firstcase]
+\parsec[s:Bfirstcase]
 
-Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$.
+Let's unpack the character of the simplest module of type $B$, namely $\til I_B(0,0)$, that is $\lambda_3 = 0$ in equation \ref{eqn:chB2}.
+Notice that $\til q_0 (t_1,t_2,x) = 1$, thus
+\beqn
+\ch \til M_B(0,0) = t^6 R(t_1,t_2,t,r) .
+\eeqn
+
+Next we need to compute \ch \til I_A(2, 0)$.
+For this we refer to Theorem \ref{thm:refinedA}.
+Notice that 
+\[
+p_
 
@@
 \subsection{Decomposing fivebrane local operators}
+\label{s:kacfivebrane}
 

### 2022-08-05 fivebranes/ops.tex
merge

@@
 In this section we recall the essentials of the theory of local operators for holomorphic-topological theories. 
+We consider a way of counting operators in a topological-holomorphic theory, called the `local character' of a holomorphic-topological theory \cite{SWchar}, and compare it to the superconformal index.
+We will then present a few examples including expressions for the local character on the twists of a theory on a single membrane and fivebrane and will find the expected match with the physics literature.
 
@@
 
+\parsec[s:localchar]
+
+Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
+The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
+The particular group of symmetries depends on the theory, so we will present some examples.
+
+The holomorphic twist of the superconformal algebra in dimensions three and six is $\lie{osp}(6|2)$. 
+So , in the case of the holomorphic twist of three and six-dimensional superconformal theories we consider the local character of operators with respect to the Lie algebra 
+\beqn\label{eqn:cartan2}
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
+\eeqn
+and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.
+
+Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character.
+That is, the character of linear local operators.
+
 \parsec[s:examples]
@@
 Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-We would like to observe that the equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the single particle index which is immediate to compute:
+We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index which is immediate to compute:
 \[
@@
 However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
-This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$. 
+This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$, so counting local operators in this way is ill-defined. 
 One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
@@
 \]
-The plethystic exponential of such an expression is
+The plethystic exponential of such an expression returns the local character
 \[
-\prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
+\chi(q_1,\ldots,q_n,y) = \prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
 \]
@@
 
-\subsection{A relationship to the supersymmetric index}
+\subsection{A relationship to the superconformal index}
+
+We will turn to computing the local character for twists of the single membrane and fivebrane theories momentarily and comment on the relationship to known formulas in the physics literature. 
+First, we point out a general relationship between the local character as we've defined it and the superconformal index.
+
+The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
+Explicitly, if the theory lives in a $d$-dimensional space time and $\cH$ denotes the Hilbert space on $S^{d-1}$, then the index is
+\beqn
+\cI(q,x_1,\ldots,x_n) = \Tr_{\cH} (-1)^F q^{\delta} x_1^{G_1} \cdots x_n^{G_n} 
+\eeqn
+where $\{G_i\}$ are a collection of charges that commute with a particular subset of elements of the superconformal algebra. 
+We can choose that each $G_i$ commute with a minimal supercharge $Q$ and its adjoint $Q^{\dagger}$ in the superconformal algebra.
+Necessarily the $G_i$ also commute with $\delta = [Q,Q^{\dagger}]$.
+After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{d-1} \times S^1$.
+
+The Witten index is protected under twisting---in our setup the index $\cI(q,x_1,\ldots,x_n)$ can be computed in the minimal twist of the superconformal theory we start with.
+Let us specialize to the case of the six-dimensional superconformal index. 
+In this case, we choose our fugacities to be $x_1 = t_1, x_2 = t_2$ and $x_3 = r$ as generators for the Cartan in the twisted superconformal algebra, see equation \eqref{eqn:cartan2}.
+
+The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$ \cite{SWchar}. 
+Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.
+
+%\[
+%(\C^3 - 0) / \sim  \; \simeq \; S^5 \times S^1 .
+%\]
+%The perspective of the holomorphic twist allows us to holomorphic theory agrees with the partition function on the product of spheres is basically goes by the process of `radial quantization'. 
+%Consider the restriction of the theory to $\C^3 - 0 \subset \C^3$ and its dimensional reduction to quantum mechanics along
+%\[
+%|-| \colon \C^3 - 0 \to \RR_{>0} .
+%\]
+%The fiber of this map over a point is $S^5$. 
+%By the nature of holomorphic QFT, we can extract from the OPE in the radial direction a canonical associative ($A_\infty$) algebra $\cA_{\lie{u}(1)} = \int_{\C^3 - 0} \Obs$ which is roughly the value of the theory on $S^5$.
+%There is a canonical boundary condition of the quantum mechanics theory at radius $r = 0$ given by the local operators $\Obs(0)$ at $0 \in \C^3$ which, in turn, has the structure of a $\cA$-module. 
+%By standard arguments placing this quantum mechanics theory on circle $S^1$ results in the trace of the $\cA$-module $\Obs(0)$ 
+%\[
+%Z(S^{5} \times S^1) = {\rm Tr}_{\cA} (\Obs(0)) .
+%\]
+%From the trace on the right-hand side we can recover the character as defined above. 
+%Indeed, the $E(3|6)$-module structure on local operators factors through a map 
+%$E(3|6) \to \cA$ since we wrote down the explicit Hamiltonians above in \eqref{eq:ham1}, for instance.
 
@@
 
-We recalled the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
-This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables~$\Obs^{6d}_{\lie{u}(1)}$ on $Z$.
+We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
+This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables
+\[
+\Obs^{6d}_{\lie{u}(1)} 
+\]
+on $Z$.
 We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs^{6d}_{\lie{u}(1)}(0)$ supported at~$0 \in \C^3$.
@@
 
-In \eqref{eqn:lim2} we presented the universal factorization algebra of classical observables on the fivebrane 
+In equation \eqref{eqn:limit2} we presented the universal factorization algebra of classical observables on the fivebrane 
 \[
@@
 \[
-\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{\lie{u}(1)} .
+\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs^{6d}_{\lie{u}(1)} .
 \]
@@
 
-We move on to characterizing the character of the holomorphic twist of the theory on a single fivebrane.
+We know deduce the character of the holomorphic twist of the theory on a single fivebrane.
 By the previous result we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
@@
 \label{prop:6done}
-The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
+The local character $\chi_{\lie{u}(1)}(q,t_1,t_2,r)$ of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
 \beqn\label{eqn:6done}
-f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+f^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
 \eeqn
 \end{prop}
+
+Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
+In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
+For the case of the single fivebrane theory, this implies that the local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ form a representation for $E(3|6)$.
+
+This fact also follows from our holographic analysis. 
+In \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$.
+Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
+In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs_{\lie{u}(1)}^{6d}$.
+On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+Combining these facts we see that $\Obs_{\lie{u}(1)}^{6d}(0)$ is a module for $E(3|6)$.
+
+In \S \ref{s:kr} we will express this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.
 
@@
 \beqn
-f_{u(1)}(t,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
+f^{6d}_{\lie{u}(1)}(q,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
 \eeqn
@@
 %\]
-In \S \ref{s:kr} we will compare this to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.
 
@@
 \[
-f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
+f_{\lie{u}(1)}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
 \]
@@
 
-In \S\ref{fact:summary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
+In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
 \[
@@
 
-On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{s:KacClass}. 
+On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
 Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
@@
 \[
-f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
+f^{6d}_{\lie{sl}(2)}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
 \]

### 2022-08-05 fivebranes/index.tex

@@
 We wish to consider our eleven dimensional model on $X = Tot (\R\oplus V)$ which is the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
-The partially flat connection on $\R\oplus V$ equips $X$ with a canonical THF structure.
+The partially flat connection on $\R\oplus V$ equips $X$ with a canonical THF structure $F_{X}\subset T_{X}$.
 
@@
 
-Let $V_{M}$ denote the vertical tangent bundle to $(h, \pi)$, which we view as a subbundle of the real tangent bundle $T_{M}$.
-The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, if $\iota \colon M \to \R\times X$ is inclusion, then we consider the pair
+Recall that we have a THF structure on $X$ induced from a partially flat conneciton on $\R\oplus V$; this is codified by saying that there is a splitting of the exact sequence
+
 \[
-  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
-\]
+0 \to \ker \to F_{X}\to \pi^{*}T^{1,0}_{Z}\to 0
+.\]
+
+Both $F_{X}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that that the splitting preserves the lie brackets on sections.
+
+Consider the relevant tangent sequence of the map
 
@@
 We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
-Such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$. 
-We will enumerate states via choosing a Cartan in the following subalgebra of the twisted superconformal algebra
-\beqn\label{eqn:bosonic1}
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) .
-\eeqn
-%We will understand how the twisted superconformal algebra acts on fivebranes via holographic principles.
-
-We will first recall how the bosonic subalgebra \eqref{eqn:bosonic1} of this twisted superconformal algebra embeds as symmetries of the eleven-dimensional theory in this twisted background. 
+As recalled above, such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$.
+We will enumerate states via choosing a Cartan in the bosonic subalgebra of the twisted superconformal algebra.
+Let us recall how the bosonic subalgebra embeds as symmetries of the eleven-dimensional theory in this twisted background.
 This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory. 
@@
 By definition, these vector fields are automatically divergence-free.
+
 \item
         The generator of the subalgebra $\lie{gl}(1)$ is mapped to the element
-\beqn\label{eqn:Y}
-Y = \sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
+        \beqn
+        Y = \sum_{i=1}^3 z_i\frac{\del}{\del z_i} - \frac 32\sum_{a=1}^2 w_a\frac{\del}{del w_a}\in \PV^{1,0}(\C^5)\otimes \Omega^0 (\R).
         \eeqn
-Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $t=w=0$. 
+    Notice that this vector field is divergence-free and restricts to the Euler vector field along $t=w_{a} = 0$.
 \item 
@@
 \beqn
-w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+ w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del 1}, \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
 \eeqn
@@
 \subsection{Supergravity states for twisted $AdS_4$}
+For convenience we choose coordinates on the eleven manifold as
+\[
+\R \times \C^5 = \R_t \times \C^4_w \times \C_z^
+\]
+with $w = (w_a), a=1,2,3,4$.
+The stack of membranes wrap $w_1=w_2=w_{3}=w_{4} = 0$.
 
-%\begin{table}
-%\begin{center}
-%\begin{tabular}{c c c c c c}
-%  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $r_{1}$ & $r_{2}$ \\
-%  \hline
-%  $t_{1}$ & $1$ & $-1$ & $0$ & $0$ & $0$ \\
-%  $t_{2}$ & $0$ & $1$ & $-1$ & $0$ & $0$ \\
-%  $r$ & $0$ & $0$ & $0$ & $1$ & $-1$ \\
-%  $q$ & $-1$ & $-1$ & $-1$ & $0$ & $0$
-%\end{tabular}
-%\caption{Fugacities for a single fivebrane.}
-%\end{center}
-%\label{tbl:weights1}
-%\end{table}
+\begin{itemize}
+\item
+The subalgebra $\lie{sl}(4)$ ($R$-symmetry) embeds as vector fields
+\beqn
+\sum_{ab} A_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ab}) \in \lie{sl}(4) .
+\eeqn
+By definition, these vector fields are automatically divergence-free.
 
-%\end{document}
+\item
+The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
+\beqn
+ \frac{\del}{\del z}, z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+\eeqn
+\end{itemize}
+
+%\begin{rmk}
+%In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of the exceptional Lie algebra $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
+%\cite{KacClass}.
+%We will make use of this grading in \S \ref{s:kr}.
+%\end{rmk}
+The equivariant character again has four fugacities, which we explicitly choose as follows:
+\begin{itemize}
+  \item $t_{1}, t_{2}, t_{3}$ denote generators for the Cartan of $\lie{sl}(4)$ which is generated by the vector fields
+  \beqn
+  h_1 = w_1 \frac{\del}{\del {w_1}} - w_4 \frac{\del}{\del{w_4}} , \quad h_2 = w_2 \frac{\del}{\del{w_2}} - w_4 \frac{\del}{\del{w_4}} , \quad h_3 = w_3\frac{\del}{\del w_3}-w_4\frac{\del}{\del w_4}.
+  \eeqn
+  \item $q$ denotes a generator for the Cartan of the $\lie{sl}(2)$ which is generated by the vector field
+        \beqn
+        T =  z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}
+        \eeqn
+\end{itemize}
+
+Once again, the twisted spergravity states $\cH_{sugra}^{3d}$ form a representation for $\lie{osp}(6|2)$.
+The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^4_w \times \C_z$.
+These are summarized in table \ref{tbl:sugraM5}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c}
+  & $z$ & $w_{1}$ & $w_{2}$ & $w_{3}$ & $w_{4}$ \\
+  \hline
+  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
+  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
+  $t_{3}$ & 0 & 0 & 0 & 1 & $-1$ \\
+  $q$ & $-1$ & $\frac 14$ & $\frac 14$ & $\frac{1}{4}$ & $\frac{1}{4}$
+\end{tabular}
+\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \R\times \C$.}
+\label{tbl:sugraM5}
+\end{center}
+\end{table}
+
+We enumerate single particle supergravity states via computing the super trace of the operator $q^T t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{3d}_{sugra}$:
+\beqn
+f^{3d}_{sugra}(q,t_1,t_2,t_3) = \Tr_{\cH_{sugra}^{3d}} (-1)^F q^T t_1^{h_1} t_2^{h_2} t_3^{h_3} .
+\eeqn
+The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
+That is, we compute the expression
+
+\begin{prop}
+The single particle index of the space of twisted supergravity states $\cH_{sugra}^{3d}$ is given by the following expression
+\beqn
+f_{sugra}^{3d} (q, t_{1}, t_{2}, t_3) = \frac{\left(\begin{aligned}
+        & -q^{-7/4}(t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) +q^{1/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) \\
+        & +q^{1/2}(1-q)(t_{1}t_{2}+t_{1}t_{3}+t_{2}t_{3}+t_{1}^{-1}t_{2}^{-1}+t_{1}^{-1}t_{3}^{-1}+t_{2}^{-1}t_{3}^{-1})\end{aligned}\right)}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})}.
+\eeqn
+\end{prop}
+
+\parsec Upon performing the change of variables
+
+\beqn
+q= x^{2} , \quad t_1 = (y_{2}y_{3})^{1/2}/y_1^{1/2} , \quad t_2 = (y_{1}y_3)^{1/2}/ y_2^{1/2} , \quad t_3 = (y_1 y_2)^{1/2}/y_{3}^{1/2}
+\eeqn
+
+the result agrees with previously computed indices for single particle states for supergravity on $AdS_{4}\times S^{7}$ \cite{}

### 2022-08-09 fivebranes/twisted.tex
thf

@@
 \beqn
-\int_{S \times X} \left(\gamma \d \mu\right) \Omega_X + \int_{S \times X} (\beta \dbar \nu) \Omega_X + \int_{S \times X} (\beta \div \mu) \Omega_X ,
+\label{eqn:free}
+\int_{S \times X} \left(\gamma (\d_{dR} + \dbar) \mu\right) \Omega_X + \int_{S \times X} (\beta (\d_{dR} + \dbar) \nu) \Omega_X + \int_{S \times X} (\beta \div \mu) \Omega_X ,
 \eeqn
@@
 \beqn
+\label{eqn:int}
 \frac12 \int_{S \times X} (\mu^2 \del \gamma) \frac{\Omega_X}{1- \nu} + \frac16 \int_{S \times X} \gamma \del \gamma \del \gamma .
@@
 
+\brian{non BV setup}
+
 The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory---a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{Aharony:2008ug}.
@@
 Twists of three-dimensional $\cN=8$ supersymmetric gauge theories were classified and characterized in \cite{ESsusy,ESW,Garner:2022vds}. 
-Moreover, the ABJM theories are examples of 3d $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{Aganagic:2017tvx}. 
+Moreover, the ABJM theories are examples of three-dimensional $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{Aganagic:2017tvx}. 
 Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:
@@
   \item The minimal twist.
-This twist leaves 2 real directions invariant.
-The theory can be defined on a 3-manifold of the form $S\times C$ where $S$ is a smooth oriented one-manifold and $C$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
+This twist leaves two real directions invariant.
+The theory can be defined on a three-manifold of the form $S\times C$ where $S$ is a smooth oriented one-manifold and $C$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
 
-  \item The nonminimal twists. There are two such twists, both of which leave 3 real directions invariant, and are permuted under 3d mirror symmetry.
+  \item The nonminimal twists. There are two such twists, both of which leave three real directions invariant, and are permuted under three-dimensional mirror symmetry.
 \end{itemize}
@@
 
-%\subsection{Supergravity at the boundary of AdS}
+\subsection{A more general background}
+
+The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.
+More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.
+
+A THF structure on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
+Equivalently, this allows you to choose an atlas of coordinates $(t_i, z_j)$ on $M$ which transform smoothly in the $t_i$-variables and holomorphically in the $z_j$-variables. 
+So, locally we may take a local patch in a THF manifold to be of the form $\R^m \times \C^n$. 
+%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
+%he product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $M$ along the projection.
+%Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
+The bundle $F$ is locally spanned by the vector fields $\partial / \partial t_i$'s and $\del/\del \zbar_j$'s.
+(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
+We will say that $M$ is of dimension $(m,n)$ (so it is a manifold of real dimension $m + 2n$).
+
+We will assume in addition to having a THF structure that $M$ is equipped with the data of a bundle isomorphism $\wedge^{n} (\T_M \otimes \C / F)^* \cong \C$ which we will denote by~$\Omega_F$. 
+If $F \cap \Bar{F} = 0$ then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
+
+There is a notion of the sheaf of `holomorphic functions' $\cO_F$ on any manifold $M$ equipped with a THF~$F$---in the language of foliations these are the functions on $M$ which are constant along the leaves of $F$.
+Locally, on a coordinate patch it is given by functions which only depend on the holomorphic variables $z_i$.
+There is a resolution $\cA^\bu_F$ for $\cO_F$ by locally free sheaves on $M$ which is the THF analog of the de Rham and Dolbeault complexes. 
+In degree zero $\cA^0_F$ is just the sheaf of smooth functions on $M$.
+In degree $k$ one takes $\cA^k_F$ the sheaf of sections of the bundle $\wedge^\bu F^*$.
+The derivative along the leaves of the foliation defined by $F$ defines a map of sheaves
+\[
+\thfd \colon \cA^{q}_F \to \cA^{q+1}_F  .
+\]
+By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and one can show that the natural map $\cO_F \xto{\simeq} \cA^\bu_F$ provides a resolution.
+% and so $\thfd$ equips $\cA^{\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
+Locally in a split THF structure like $\R^m \times \C^n$ the operator $\thfd$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
+
+There is also the notion of the sheaf of `holomorphic vector fields' $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$. 
+Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
+Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
+$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
+Then we obtain a resolution
+\beqn
+\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
+\eeqn
+Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
+Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.
+
+We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
+Let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
+\beqn\label{eqn:drdol}
+\Omega^{\bu}(S) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(S) \otimes \Omega^{1,\bu}(X) .
+\eeqn
+As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
+There is an analog of this operator $1 \otimes \del$ on a manifold $M$ equipped with a THF~$F$.
+It is a differential operator 
+\beqn
+D \colon \cA^{p,\bu}_F \to \cA^{p+1,\bu}_F
+\eeqn
+which locally is just the holomorphic de Rham operator. 
+This operator commutes with $\thfd$.
+The generalized $\beta$ and $\gamma$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F \xto{D} \cA^{1,\bu}_F$.
+
+\newcommand\Div{D_\Omega}
+
+Next we should say where the generalized $\mu$ and $\nu$ fields live. 
+The volume form $\Omega_F \colon \C \cong \wedge^n \theta_F^*$ determines an isomorphism $\cA^{p,q}_F \cong \cA^{n-p,q}_F$ for each $p,q$.
+Via this isomorphism we can identify $D \colon \cA^{n-1,\bu}_F \to \cA^{n,\bu}_F$ with a differential operator
+\beqn
+\Div \colon \cA_F^{\bu}(\theta_F) \to \cA^\bu_F .
+\eeqn
+The $\mu$ and $\nu$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F(\theta_F) \xto{\Div} \cA^\bu_F$. 
+This resolves the THF version of the sheaf of holomorphic vector fields on $M$ which preserve the form $\Omega_F$.
+
+Now we are in a place to describe a BV theory defined on an eleven-manifold $M$ equipped with a THF $F$ and a volume form $\Omega_F$ on the leaf space.
+The space of fields of the theory consist of fields $\beta,\gamma, \mu, \nu$ as before but where
+\beqn
+\beta \in \Pi \cA_F^\bu, \quad \gamma \in \cA^{1,\bu}_F, \quad \mu \in \Pi \cA^\bu_F(\theta_F), \quad \nu \in \cA_F^\bu  .
+\eeqn
+Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$. 
+The free part of the action functional (cf. \eqref{eqn:free}) is 
+\beqn
+\int_M (\gamma \thfd \mu) \Omega_F + \int_M (\beta \thfd \gamma) \Omega_F + \int_M (\beta \Div \mu) \Omega_F .
+\eeqn
+The interaction (cf. \eqref{eqn:int}) is
+\beqn
+\label{eqn:int}
+\frac12 \int_{M} (\mu^2 D \gamma) \frac{\Omega_F}{1- \nu} + \frac16 \int_{M} \gamma D \gamma D \gamma .
+\eeqn
+
+%More generally, there is a natural cohomology associated to a THF structure.
+%Suppose $(M,F)$ is a THF structure and
+%denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
+%For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
+%The derivative along the leaves of the foliation defined by $V$ defines a map
+%\[
+%\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
+%\]
+%By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
+%Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
+%There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
+%The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
+%\[
+%\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
+%\]
+%with the structure of a bigraded commutative dg algebra.
+%This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
+%For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
+%\beqn\label{thfcoh1}
+%\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
+%\eeqn
+%We leave the $\thfd$ operator implicit in the presentation on the right hand side.
+%When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
+%There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
 %
-%Suppose we are in the situation in the last section where we place the eleven-dimensional theory on $\R \times X$ where $X = {\rm Tot}(K^{1/2}_Z \otimes \C^2)$. 
-%We are furthermore placing some number of fivebranes along the locus $Z$ cut out by the zero section. 
-%If we remove this locus we obtain the following manifold 
-%\[
-%\R \times X - \left(0 \times Z\right) \simeq Z \times \left({\rm Tot}(N_Z) - 0\right) 
-%\]
-%where on the right hand side ${\rm Tot}(N_Z) - 0$ is the total space of the normal bundle to $Z$ in $\R \times X$ minus the zero section.
+%Any submanifold of a THF manifold is itself a THF manifold.
+%We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
 %
-%
-%\subsection{Enhanced symmetry in a flat background}
-%
-%\parsec[s:e36]
-%
-%We recall the definition of the exceptional super Lie algebra $E(3|6)$. 
-%We follow \cite{Kac_class, KacRudakov}.
-%
-%The even part of the super Lie algebra $E(3|6)$ is 
-%\[
-%\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) .
-%\]
-%The Lie bracket is determined by the obvious commutators and the action of vector fields on functions. 
-%
-%The odd part is of the form
-%\[
-%\Omega^{-1/2}(\Hat{D}^3) \otimes \C^2 .
-%\]
-%where $\Omega^{-1/2}(\Hat{D}^3)$ is the space of formal power series sections of the bundle
-%\[
-%\T_{\Hat{D}^3}^{*} \otimes K_{\Hat{D}^3}^{-1/2}
-%\]
-%where $K_{\Hat{D}^3}^{-1/2}$ is the negative square-root of the canonical bundle on $\Hat{D}^3$. 
-%We will write a general element of this module as 
-%\[
-%\alpha = \sum_i g^i \d z_i^{-1/2} 
-%\]
-%where $g^i \in \cO(\Hat{D}^3)$. 
-%The action by the even part of the super Lie algebra is by Lie derivative and by the fundamental $\lie{sl}(2)$ action on $\C^2$.
-%We will write $r \in \C^2$ for a vector in the fundamental representation.
-%Finally, there is a bracket 
-%\[
-%E(3|6)_- \times E(3|6)_- \to E(3|6)_+
-%\]
-%defined by
-%\[
-%[\alpha_1 \otimes r_1, \alpha_2 \otimes r_2] = - (\alpha_1 \wedge \alpha_2) \otimes (r_1 \wedge r_2) - (\d \alpha_1 \otimes \alpha_2 + \alpha_1 \otimes \d \alpha_2) \otimes (r_1 \odot r_2) .
-%\]
-%%The first term in the above equation arises from the composition 
-%%\[
-%%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{\wedge \otimes \wedge} \Hat{\Omega}_3^{-1} \otimes \wedge^2 R \cong \fw_3 .
-%%\] 
-%%The second term uses the composition 
-%%\[
-%%(\Hat{\Omega}_3^{-1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes (R \otimes R) \xto{(\d \otimes \id) \otimes \odot} (\Hat{\Omega}_3^{1/2} \otimes \Hat{\Omega}_3^{-1/2}) \otimes \Sym^2 (R) \cong \lie{sl}(2) \otimes \Hat{\cO}_3 .
-%%\] 
-%
-%\brian{suca enhancement following \cite{SWsuca6d}}
-%
-%\parsec[s:weight]
-%
-%
-%\parsec[s:locallieE510]
-%
-%We have recollected how the super Lie algebra $E(5|10)$ (and its central extension) decomposes as a module for the super Lie algebra $E(3|6)$. 
-%We now wish to lift this to a decomposition of factorization algebras on $\C^3$, or more generally, factorization algebras on any complex three-fold $Z$. 
-%
-%We outline an approach to constructing the factorization algebras via enveloping factorization algebras of certain (infinite rank) local Lie algebras on the three-fold $X$. 
-%For another approach \brian{pointer}. 
-%
-%We have already discussed the local Lie algebra $\cL_{sugra}$ on $X \times S$ where $X$ is a Calabi--Yau five-fold and $S$ is a smooth one-manifold. 
-%We take $X = Z \times \C^2$ and $S = \R$. 
-%and view $\Obs_{sugra} = \clie^\bu(\cL_{sugra})$ as a factorization algebra on $Z \times \C^2 \times \R$. 
-%Then, we can consider the pushforward of $\Obs_{sugra}$ along the map
-%\[
-%\pi \colon Z \times \C^2 \times \R \to Z 
-%\]
-%which leads to a factorization algebra $\pi_* \Obs_{sugra}$ on the three-fold $Z$. 
-%
-%Since $\pi$ is not a proper map (the fibers are not compact) we cannot exhibit $\pi_*\Obs_{sugra}$ as the Chevalley--Eilenberg complex of some ordinary local Lie algebra on $Z$. 
-%Nevertheless we will find a pro local Lie algebra $\cL_{sugra,\pi}$ on $Z$ which is a particularly nice `small model' for this pushforward factorization algebra.
-%
-%A local Lie algebra enhancement for $E(3|6)$ has been given in \cite{SWsuca6d} \brian{finish}
-%
-%
-%
-%
-%
-%
-%
-%\section{Example} 
-%
-%Consider the holomorphic local Lie algebra on $\C^n$
-%\[
-%\Omega^{0,\bu}(\C^n) 
-%\]
-%and corresponding factorization algebra $\cF = \clie^\bu(\Omega^{0,\bu}(\C^n))$. 
-%Now, we can restrict this to a factorization algebra on
-%\[
-%\C^n - 0 \subset \C^n
-%\]
-%that we denote by $\cF|_{\C^n - 0}$. 
-%
-%Next, consider the radial projection
-%\[
-%r \colon \C^n - 0 \to \R .
-%\]
-%Notice that $r_* (\cF|_{\C^n - 0})$ will not be the observables of any ordinary local Lie algebra.
-%Nevertheless we can come up with a nice algebraic model.  
-%
-%Let $A_n$ be the usual dg model for the formal punctured disk $\Hat{D}^n - 0$ as defined in \cite{FHK,GWkm}.
-%
-%\begin{lem}
-%There is an injective map of factorization algebras on $\RR_{>0}$:
-%\[
-%\clie^\bu(\Omega^\bu(\RR_{>0}) \otimes A_n) \to r_* (\cF|_{\C^n - 0}) 
-%\]
-%which is dense in cohomology.
-%\end{lem}
-%
-%This tells us that the correct `fields' of the dimensionally reduced theory on $\RR_{>0}$ is $\Omega^\bu(\R_{>0}) \otimes A_n$.
-
 %\end{document}

### 2022-08-09 fivebranes/index.tex
table fixed
merge
notational changes and compactification

@@
 
-We consider the theory on $X = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
+We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
 \[
@@
 \]
-Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $M = X - 0 \times C$.
+Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.
 
-Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $X$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.
+Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.
 
 If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
-The restriction $p|M$ equips $M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$.
-Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $M$.
+The restriction $p| \mathring M$ equips $\mathring M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$.
+Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $\mathring M$.
 As part of this data, each of the fiber spheres is equipped with a complex foliation of rank 1.
 
-Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p|M$.
+Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$.
 The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres.
@@
 Let $Z$ be a three-fold that the fivebranes wrap.
-We also fix a rank 2 holomorphic vector bundle $V\to Z$ such that $\wedge^{2} V \cong K_{Z}$;
-this condition ensures that the total space of $V$ is a Calabi-Yau five-fold. In the main body of the paper we will choose $V$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.
+We also fix a rank 2 holomorphic vector bundle $W\to Z$ such that $\wedge^{2} W \cong K_{Z}$;
+this condition ensures that the total space of $W$ is a Calabi-Yau five-fold. In the main body of the paper we will choose $W$ to be the bundle $K_{Z}^{1/2}\otimes \C^{2}$.
 
-Consider the bundle $\R\oplus V$; this bundle has a canonical partially flat connection.
-We wish to consider our eleven dimensional model on $X = Tot (\R\oplus V)$ which is the total space of the \textit{real} rank five bundle $\R\oplus V$ over $Z$.
-The partially flat connection on $\R\oplus V$ equips $X$ with a canonical THF structure $F_{X}\subset T_{X}$.
+Consider the bundle $\R\oplus W$; this bundle has a canonical partially flat connection.
+We wish to consider our eleven dimensional model on $M = Tot (\R\oplus W)$ which is the total space of the \textit{real} rank five bundle $\R\oplus W$ over $Z$.
+The partially flat connection on $\R\oplus W$ equips $M$ with a canonical THF structure $F_{M}\subset T_{M}^{\C}$.
 
-We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus V$.
+We place a stack of $N$ fivebranes wrapping the zero section in $\R\oplus W$.
 Denote the complement of the zero section by
 \[
-M_V = \text{Tot}(\R\oplus V) - 0(Z).
+\mathring{M} = \text{Tot}(\R\oplus W) - 0(Z).
 \]
-Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
-The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
 
-A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
-We will say that $F$ equips $M$ with the a THF structure.
+%Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
+%The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
+
+%A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
+%We will say that $F$ equips $M$ with the a THF structure.
 %Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
-The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection.
-Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
-The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s.
-(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
+%The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection.
+%Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
+%The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s.
+%(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
 
-Any submanifold of a THF manifold is itself a THF manifold.
-We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
+%Any submanifold of a THF manifold is itself a THF manifold.
+%We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
 
-We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex
-\beqn\label{eqn:drdol}
-\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
-\eeqn
-As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
-More generally, there is a natural cohomology associated to a THF structure.
-Suppose $(M,F)$ is a THF structure and
-denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
-For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
-The derivative along the leaves of the foliation defined by $V$ defines a map
-\[
-\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
-\]
-By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
-Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
-There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
-The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
-\[
-\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
-\]
-with the structure of a bigraded commutative dg algebra.
-This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
-For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
-\beqn\label{thfcoh1}
-\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
-\eeqn
-We leave the $\thfd$ operator implicit in the presentation on the right hand side.
-When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
-There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
+%We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
+%Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex
+%\beqn\label{eqn:drdol}
+%\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
+%\eeqn
+%As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
+%More generally, there is a natural cohomology associated to a THF structure.
+%Suppose $(M,F)$ is a THF structure and
+%denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
+%For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
+%The derivative along the leaves of the foliation defined by $V$ defines a map
+%\[
+%\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
+%\]
+%By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
+%Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
+%There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
+%The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
+%\[
+%\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
+%\]
+%with the structure of a bigraded commutative dg algebra.
+%This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
+%For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
+%\beqn\label{thfcoh1}
+%\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
+%\eeqn
+%We leave the $\thfd$ operator implicit in the presentation on the right hand side.
+%When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
+%There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
 
 %Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
-With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes.
-We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus V$ over $Z$ and a fiberwise partially hermitian metric.
+
+%With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes.
+
+We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus W$ over $Z$ and a fiberwise partially hermitian metric.
+
 Explicitly, the corresponding norm defines a map
 \begin{align*}
- h \colon  X & \to \R_{+} \\
+ h \colon  M & \to \R_{+} \\
   (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
 \end{align*}
-Letting $\pi \colon X \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
+Letting $\pi \colon M \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
 \[
-p \define (h,\pi) \colon \R \times X \to \R_{+}\times Z
+p \define (h,\pi) \colon M \to \R_{+}\times Z
 \]
-which restricts to an $S^4$ bundle $p|M \colon M \to \R_{>0} \times Z$.
+which restricts to an $S^4$ bundle $p|\mathring {M} \colon \mathring{M} \to \R_{>0} \times Z$.
 These embeddings and projections fit inside of the following commutative diagram
@@
 \begin{tikzcd}
-M \ar[d,"p|M"'] \ar[r,hook] & X \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
+M \ar[d,"p|\mathring M"'] \ar[r,hook] & \mathring{M} \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
 \R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
@@
 As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$.
-Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|M$.
-The resulting sheaf of $L_\infty$ algebras $(p|M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
+Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$.
+The resulting sheaf of $L_\infty$ algebras $(p|\mathring M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
 
@@
 
-\brian{trying to incorporate below}
-%To do this we will make use of the natural foliated geometric structures which we have around.
-
-Recall that we have a THF structure on $X$ induced from a partially flat conneciton on $\R\oplus V$; this is codified by saying that there is a splitting of the exact sequence
+Recall that we have a THF structure on $M$ induced from a partially flat conneciton on $\R\oplus W$. The partial connection amounts to a splitting of the exact sequence
 
 \[
-0 \to \ker \to F_{X}\to \pi^{*}T^{1,0}_{Z}\to 0
+  0 \to F_{X}\cap T_{M/Z}^{\C}\to F_{X}\to \pi^{*}T^{1,0}_{Z}\to 0
 .\]
@@
 Both $F_{X}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that that the splitting preserves the lie brackets on sections.
-
-Consider the relevant tangent sequence of the map
-
-The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure.
-\surya{CITE}
-
- The underlying sheaf of cochain complexes is given by
-
-\[
-\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
-\ul{\rm even} & \ul{\rm odd} \\
-\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
-\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
-\end{tikzcd}
- \right ) \otimes CR (S^{4}).
-\]
-
-Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure.
-Its computation is facilitated by the following lemma:
-
-\begin{lem}
-  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric.
-Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure.
-Then there is a quasi-isomorphism
-
-  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]
-
-  where the right-hand-side denotes the Dolbeault-deRham complex.
-\end{lem}
-
-The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
 
@@
 \beqn
- w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del 1}, \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+ w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del 1}, \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
 \eeqn
@@
 \[
-\R \times \C^5 = \R_t \times \C^4_w \times \C_z^
+\R \times \C^5 = \R_t \times \C^4_w \times \C_z
 \]
@@
 The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^4_w \times \C_z$.
-These are summarized in table \ref{tbl:sugraM5}.
+These are summarized in table \ref{tbl:sugraM2}.
 
@@
   \hline
-  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
-  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
+  $t_{1}$ & 0 & 1 & 0 & 0 & $-1$ \\
+  $t_{2}$ & 0 & 0 & 1 & 0 & $-1$ \\
   $t_{3}$ & 0 & 0 & 0 & 1 & $-1$ \\

### 2022-08-09 fivebranes/index.tex
merge

--- 2022-08-05 fivebranes/index.tex
@@
 
-Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to 3d Chern-Simons.
+Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.
 
@@
 The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
-
-A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
-We will say that $F$ equips $M$ with the a THF structure.
-%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
-The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection.
-Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
-The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s.
-(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
-
-Any submanifold of a THF manifold is itself a THF manifold.
-We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
-
-We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex
-\beqn\label{eqn:drdol}
-\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
-\eeqn
-As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
-More generally, there is a natural cohomology associated to a THF structure.
-Suppose $(M,F)$ is a THF structure and
-denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
-For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
-The derivative along the leaves of the foliation defined by $V$ defines a map
-\[
-\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
-\]
-By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
-Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
-There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
-The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
-\[
-\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
-\]
-with the structure of a bigraded commutative dg algebra.
-This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
-For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
-\beqn\label{thfcoh1}
-\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
-\eeqn
-We leave the $\thfd$ operator implicit in the presentation on the right hand side.
-When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
-There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
 

### 2022-08-22 fivebranes/fact.tex
merge
update

@@
 \section{Factorization algebras in twisted $M$ theory}
+\label{s:fact}
 
@@
 
-It is absolutely crucial for this proposal that we work in a derived setting using the BV formalism. 
+It is absolutely crucial for this proposal that we work in a derived setting using the Batalin--Vilkovisky (BV) formalism. 
 The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
@@
 which computes the Lie algebra cohomology of $\cL(U)$. 
-The differential on this cochain complex is precisely the Chevellay--Eilenberg differential associated to the~$L_\infty$ structure maps.
+The differential on this cochain complex is precisely the Chevalley--Eilenberg differential associated to the~$L_\infty$ structure maps.
 
@@
 In terms of this local $L_\infty$ algebra, the $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset S \times X$ is 
-\[
+\beqn\label{eqn:sugraobs}
 \clie^\bu\left(\cL_{sugra}(U)\right) .
-\]
+\eeqn
 We will denote the classical factorization algebra on $S \times X$ of classical observables by~$\Obs_{sugra}$.
@@
 
-With an eye towards holography for fivebranes we fix a complex three-fold $Z$ where the fivebranes will be supported and consider the eleven-dimensional theory on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
-\[
-X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2),
-\]
-the total space of the rank two holomorphic vector bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
+Fix a complex three-fold $Z$, where the fivebranes will be supported, and assume that it is equipped with a sqaure-root of its canonical bundle $K^{1/2}_Z$.
+We consider the eleven-dimensional theory that we introduced in \S \ref{s:twisted} on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
+\beqn
+X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2).
+\eeqn
+This is the total space of the rank two holomorphic vector bundle $K_Z^{1/2} \otimes \C^2$ over~$Z$. 
 %In the remainder of this section we denote by $V \to Z$ this rank two holomorphic vector bundle. 
-One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
+One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over~$Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
 Let 
-\[
+\beqn
 \pi \colon \R \times X_Z \to Z 
-\]
+\eeqn
 be the map which projects out the real factor followed by the projection to the base of the total space of the complex rank two bundle $p \colon X_Z \to Z$.
 
+The classical observables of the eleven-dimensional theory form a factorization algebra on $\R \times X_Z$ that we have denoted by $\Obs_{sugra}$.
 Like sheaves, factorization algebras can be pushed forward.
-Thus, from the factorization algebra $\Obs_{sugra}$ on $\R \times X_Z$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ defined on the three-fold $Z$.
+Thus, using $\pi$ we obtain a factorization algebra $\pi_* \Obs_{sugra}$ defined on the three-fold~$Z$.
 Explicitly, to an open set $U \subset Z$ the factorization assigns the cochain complex
@@
 This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $Z$.
+In physics terminology this feature is due to the presence of an infinite tower of so-called Kaluza--Klein modes which means that the space of fields is not given as the sections of a finite rank vector bundle on~$Z$.
+Mathematically, this is due to the fact that the map $\pi$ is not proper.
 Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such. 
@@
 
-One of the primary features of the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is that it is of the form $\clie^\bu(\cG)$ where $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
+Like $\Obs_{sugra}$ in equation \eqref{eqn:sugraobs}, the factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG)$.
+Here, $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
 To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.
@@
 
-As we recalled in~\S \ref{??}, Costello's five-dimensional Chern--Simons theory is the result of applying the $\Omega$-background to $M$ theory on a Taub--NUT space.
-In this setting, fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
+In~\S \ref{s:twistedsugra} we recalled some features of a five-dimensional Chern--Simons type theory that Costello has shown to be the result of applying the $\Omega$-background to $M$-theory on a Taub--NUT space \cite{CostelloM5}.
+In this setting fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
 In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
-Denote by $\Obs_{CS}$ the observables of the semi-classical limit of non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
+Denote by $\Obs_{CS}$ the classical observables\footnote{We treat the theory classically as a perturbative theory on $\R \times {\rm Tot}(K_C)$.
+We note that the theory is defined in terms of two parameters $\ep, \delta$ where $\delta$ is the Chern--Simons coupling and $\ep$ is the non-commutative parameter controlling the deformation quantization of the holomorphic symplectic manifold ${\rm Tot}(K_C)$.
+For convenience we set both $\ep, \delta$ to be one.}
+of the non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
 Let 
-\[\pi \colon \R \times {\rm Tot}(K_C) \to C
-\]
+\beqn
+\pi \colon \R \times {\rm Tot}(K_C) \to C
+\eeqn
 be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.
@@
 Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
-The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is similar to the non-formal case---it is the natural one if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in $K_C$.
+The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is given by the Moyal commutator. 
+This is similar to the non-formal case---it is the natural bracket if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in~$K_C$.
 
@@
 
-Let us return to the situation of a three-fold $Z$ in the eleven-manifold $\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
-The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory.
+Let us return to the situation of a complex three-fold $Z$ as submanifold the eleven-manifold~$\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
+The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory as we just discussed.
 
@@
 
+\brian{make precise statement using $E(3|6)$.}
+
 Particularly important for us will be the weight zero summand $\cG_Z^{(0)}$.
 Again, as a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
+Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
 When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
@@
 
-\subsection{The membrane decomposition}
+\parsec[s:general_decomp]
 
-We briefly highlight an analogous construction of the restricted factorization algebra describing membranes.
-Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.
-
-We consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
-\[
-X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
-\]
-the total space of the rank four bundle $K_C^{1/4} \otimes \C^4$ over $C$.
-Denote by 
-\[
-\pi \colon V \to \R \times C
-\] 
-the pullback of this vector bundle along the projection $\R \times C \to C$.
-We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
-In this description, the twisted membranes will be supported along the zero section of $V$. 
-The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.
-
-As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
-Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such.
-
-To construct this factorization algebra we consider the action of the compact torus $U(1)^{\times 4}$ which rotates the fibers of the bundle $K_C^{1/4} \otimes \C^4$.
-We let $\Bar{\pi}_* \Obs_{sugra}$ be the factorization algebra on $\R \times C$ consisting of observables which are finite sums of integral eigenvectors for this group action.
-Again, we find that $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG_{\R \times C})$ for some $\infty$ sheaf of $L_\infty$ algebras $\cG_{\R \times C}$ on $\R \times C$ which is the sections of a pro vector bundle.
-
-Analogous to the decomposition determined by the $\C^\times$ action considered in \ref{s:cstarfive}, there is a decomposition of $\cG_{\R \times C}$ determined by a (different) $\C^\times$ acting on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$.
-
-In a local THF chart $U \subset \R \times C$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;z,w)$ where $(t;z) \in U \subset\R \times C$ is THF coordinate and $w=(w_1,w_2,w_3,w_4)$ is the holomorphic fiber coordinate of the rank four bundle $V$.
-
-%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
-%\[
-%0 \times 0 \times \C^3 \subset \C^5 .
-%\]
-%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
-%
-%\parsec[s:flatdecomp]
-%
-%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
-%%\[
-%%\C^3 \times (\R \times \C^2 - 0) .
-%%\]
-%%
-%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
-%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
-%
-%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
-%
-%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
-%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
-%\[
-%\pi_* \Obs_{sugra} 
-%\]
-%on $\C^3$.
-%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
-%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
-
-With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
-\begin{itemize}
-\item On the fields $\mu(t;w,z)$ the action is
-\[
-\lambda \cdot \mu(t;z,w) = \mu(t; z , \lambda w).
-\]
-\item On the fields $\nu(t;w,z)$ the action is
-\[
-\lambda \cdot \nu(t;z,w) = \nu(t;z ,\lambda w).
-\]
-\item On the fields $\beta(t;w,z)$ the action is
-\[
-\lambda \cdot \beta(t;z,w) = \lambda^{-2} \beta(t; z, \lambda w).
-\]
-\item On the fields $\gamma(t;w,z)$ the action is
-\[
-\lambda \cdot \gamma(t;z,w) = \lambda^{-2} \gamma(t; z ,\lambda w).
-\]
-\end{itemize}
+\brian{mention $E(3|6)$ module structure}
 
 \begin{prop}
-The $L_\infty$ structure on $\cL_{sugra}$ is equivariant for this $\C^\times$ action. 
-%The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
+Let $j \geq 1$. 
+The complex of vector bundles $\cG^{(j)}$ is quasi-isomorphic to
+\beqn
+\Omega^{0,\bu}(Z, \cV^{(j)}) 
+\eeqn
+where $\cV^{(j)}$ is the super holomorphic vector bundle 
+\beqn
+\begin{tikzcd}
+\ul{even} & \ul{odd} \\
+S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z & S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z \\
+S^{j+2}(\C^2) \otimes K^{-j/2}_Z & S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z .
+\end{tikzcd}
+\eeqn
 \end{prop}
 
-As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
-Similarly as above one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
-\[
-\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
-\]
-where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.
+\begin{proof}
 
-We will state explicit descriptions of the first few eigenspaces without details of the proof. 
-The first nontrivial eigenspace is, as in the fivebrane case, $n=-1$. 
-Here, one can see that 
-\[
-\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
-\]
-For $n=0$ one has 
-\[
-\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
-\]
-As in the case of fivebranes, the $n=0$ eigenspace is equipped with the structure of a super Lie algebra whose exact form we do not state now.
+\begin{itemize}
+\item Let $f(w) \in \C[w_1,w_2]_j$ be a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and suppose that $g(z) \del_{z_i}$ is a holomorphic vector field on $Z$. 
+Define the $\mu$-type field
+\beqn
+f(w) g(z) \del_{z_i} + \cdots
+\eeqn
+\item Let $f(w) \in \C[w_1,w_2]_{j+2}$ be a homogenous degree $j+2$ polynomial and consider the one-form $\del f(w) = \del_{w_1} f(w)\d w_1 + \del_{w_2} f(w) \d w_2$.
+Using the holomorphic symplectic form we obtain the vector field
+\beqn
+g(z) \left(\del_{w_1} f(w) \del_{w_2} - \del_{w_2} f(w) \del_{w_1}\right) .
+\eeqn
+\end{itemize}
+\end{proof}
 

### 2022-08-22 fivebranes/index.tex
update

--- 2022-08-09 fivebranes/index.tex
@@
 \]
-
-%Notice that in \S \ref{s:Lsugra} we have only defined the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on a product of a smooth one-manifold times a Calabi--Yau five-fold.
-%The eleven-manifold $M_V$ is not of this form, nevertheless there is a generalization of $\cL_{sugra}$ which one can define using the natural geometric structure present in our situation.
-
-%A transversely holomorphic foliation (THF) on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
-%We will say that $F$ equips $M$ with the a THF structure.
-%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
-%The product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $N$ along the projection.
-%Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
-%The bundle $F$ is locally spanned by the vector fields $\partial / \partial x_i$'s and $\del/\del \zbar_j$'s.
-%(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
-
-%Any submanifold of a THF manifold is itself a THF manifold.
-%We are most interested in the submanifold $M_V \subset {\rm Tot}(\R \oplus V) = \R \times X$ where we equip $\R \times X$ with its standard split THF structure.
-
-%We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-%Let us focus on the fields $\beta,\gamma$ which on $\R \times X$ combine to form the complex
-%\beqn\label{eqn:drdol}
-%\Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(\R) \otimes \Omega^{1,\bu}(X) .
-%\eeqn
-%As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
-%More generally, there is a natural cohomology associated to a THF structure.
-%Suppose $(M,F)$ is a THF structure and
-%denote by $Q$ the (complex) quotient bundle $\T_\C M / F$.
-%For each $p,q$ denote by $\cA^{p;q}$ smooth sections of the bundle $\wedge^p Q^\vee \otimes \wedge^q F^\vee$.
-%The derivative along the leaves of the foliation defined by $V$ defines a map
-%\[
-%\thfd \colon \cA^{p;q} \to \cA^{p;q+1}  .
-%\]
-%By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and so $\thfd$ equips $\cA^{p;\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
-%Locally in a split THF structure the operator $D$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
-%There is also an analog of the holomorphic $\del$ operator which takes the form $\thfdel \colon \cA^{p;q} \to \cA^{p+1;q}$.
-%The obvious exterior product $\cA^{p;q} \times \cA^{r;s} \to \cA^{p+r;q+s}$ further endows
-%\[
-%\left(\cA^{\bu;\bu} (M), \thfd + \thfdel\right) = \left(\oplus_p \cA^{p;\bu}[-p] , \thfd + \thfdel \right)
-%\]
-%with the structure of a bigraded commutative dg algebra.
-%This complex is simply isomorphic to the de Rham complex of $M$, but this presentation lends itself to more interesting quotient complexes.
-%For example, the forms of type $(p,\bu)$ with $p \geq 2$ form an ideal inside of this dg algebra; hence we get a quotient dg algebra
-%\beqn\label{thfcoh1}
-%\left(\cA^{\leq 1;\bu}(M), \thfd + \thfdel\right) = \quad \cA^{0;\bu} \xto{\thfdel} \cA^{1;\bu} .
-%\eeqn
-%We leave the $\thfd$ operator implicit in the presentation on the right hand side.
-%When $M = M_V$, it is this complex that is the THF generalization of the truncated de Rham--Dolbeault complex in \eqref{eqn:drdol}---it is easy to see that it agrees with this complex in the case of a split THF manifold.
-%There is a similar THF description for the fields $\mu,\nu$ in the eleven-dimensional theory.
-
-%Note that the eleven-manifold $\R \times X$ is equipped with a natural transverseley--holomorphic foliation (THF)---the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \Bar{T}_{Z}$.
-
-%With this THF cohomological description of the eleven-dimensional theory in place we proceed to describe the boundary condition obtained by removing the location of the branes.
 
@@
 We will enumerate states via choosing a Cartan in the bosonic subalgebra of the twisted superconformal algebra. 
-Let us recall how the bosonic subalgebra embeds as symmetries of the eleven-dimensional theory in this twisted background.
-This manifests as an embedding of this bosonic subalgebra into the ghosts of the eleven-dimensional theory. 
+We recall below how the bosonic piece of the algebra
+\beqn
+\label{eqn:gut}
+\lie{sl}(4) \times \lie{sl}(2) \subset \lie{osp}(6|2) 
+\eeqn
+embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.
 The embedding is distinct for fivebranes and membranes.
 We turn first to the fivebrane case.
+
+\brian{enhance to E(3|6)}.
 
@@
 with $z = (z_i), i=1,2,3$ and $w = (w_a), a=1,2$.
-The stack of fivebranes wrap $w_1=w_2=t=0$. 
+The stack of fivebranes wrap 
+\beqn
+w_1=w_2=t=0 .
+\eeqn
 Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.
 
+The subalgebra \eqref{eqn:gut} of the twisted superconformal algebra $\lie{osp}(6|2)$ embeds as ghosts in our eleven-dimensional model as follows.
 \begin{itemize}
 \item
-The subalgebra $\lie{sl}(3)$ embeds as vector fields
+The subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ embeds as vector fields rotating the plane $\C^3_z$
 \beqn
@@
 By definition, these vector fields are automatically divergence-free.
-
-\item
-        The generator of the subalgebra $\lie{gl}(1)$ is mapped to the element
-        \beqn
-        Y = \sum_{i=1}^3 z_i\frac{\del}{\del z_i} - \frac 32\sum_{a=1}^2 w_a\frac{\del}{del w_a}\in \PV^{1,0}(\C^5)\otimes \Omega^0 (\R).
-        \eeqn
 Notice that this vector field is divergence-free and restricts to the Euler vector field along $t=w_{a} = 0$.
@@
 \beqn
- w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del 1}, \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+ w_1 \frac{\del}{\del w_2}, \quad w_2 \frac{\del}{\del w_1}, \quad \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+\eeqn
+\item Scaling on the plane $\C^3$ embeds as the vector field
+\beqn\label{eqn:Delta}
+        \Delta = \sum_{i=1}^3 z_i\frac{\del}{\del z_i} - \frac 32\sum_{a=1}^2 w_a\frac{\del}{\del w_a}\in \PV^{1,0}(\C^5)\otimes \Omega^0 (\R).
 \eeqn
@@
 %\end{rmk}
-
+This describes an embedding of the algebra 
+\beqn\label{eqn:gut2}
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{sl}(4) \times \lie{sl}(2) 
+\eeqn
+into the ghosts of our model.
 The dimension of a Cartan subalgebra of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$ is four and accordingly, the equivariant character we study has four fugacities.
@@
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is generated by the vector fields
+  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is spanned by the vector fields
   \beqn
@@
   \eeqn
-   \item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element $Y$ from equation~$\eqref{eqn:Y}$. 
   \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
   \beqn
+  \label{eqn:hCartan}
   h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
   \eeqn
+\item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element $\Delta$ from equation~$\eqref{eqn:Delta}$. 
 \end{itemize}
@@
 \beqn
-f^{6d}_{sugra}(q,t_1,t_2,r) = \Tr_{\cH_{sugra}^{6d}} (-1)^F q^Y t_1^{h_1} t_2^{h_2} r^h .
+f^{6d}_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}^{6d}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
 \eeqn
@@
 \begin{prop}
-The single particle index of the space of twisted supergravity states $\cH_{sugra}^{6d}$ is given by the following expression
+The single particle index of the space of twisted supergravity states~$\cH_{sugra}^{6d}$ is given by the following expression
 \beqn
-f_{sugra}^{6d} (q, t_{1}, t_{2}, r) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
+\label{eqn:sugra_index}
+f_{sugra}^{6d} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
+\eeqn
+The full (multiparticle) index is defined to be the plethystic exponential 
+\beqn
+{\rm PExp}\left[f_{sugra}^{6d}(t_1,t_2,r,q)\right] .
 \eeqn
@@
 
-We record a few specializations of this index which we will remark on further in \S \ref{s:??}.
+To simplify the form of this index we can introduce a different parametrization of the Cartan of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$.
+First, we can parameterize the Cartan of $\lie{sl}(3)$ by the vector fields
+  \beqn\label{eqn:ys}
+  -(\log y_1) z_1 \frac{\del}{\del {z_1}} - (\log y_2) z_2 \frac{\del}{\del{z_2}} - (\log y_3) z_3 \frac{\del}{\del{z_3}} .
+  \eeqn
+where $y_1,y_2,y_3$ are parameters which satisfy the single constraint
+\beqn
+y_1 y_2 y_3 = 1 .
+\eeqn
+In terms of the variables $t_1,t_2$ used above we have
+\beqn
+y_1 = t_1^{-1},\quad y_2 = t_1 t_2^{-1}, \quad y_3 = t_2 .
+\eeqn
+Second, we can parametrize the Cartan of the remaining subalgebra $\lie{sl}(2) \times \lie{gl}(1)$ by the two vector fields
+\beqn
+\til{h} = h + \frac12 \Delta \quad \text{and} \quad \Delta
+\eeqn
+where $\Delta$ is as in equation \eqref{eqn:Delta} and $h$ is as in \eqref{eqn:hCartan}.
+We denote by $y$ the generator of the Cartan corresponding to the vector field $\til{h}$ and by $q$ (as above) the generator corresponding to~$\Delta$.
+In terms of the variable~$r$ used above we have 
+\beqn
+y = q^{1/2} r .
+\eeqn
+
+Using the paramterization fo the Cartan given by the variables $y_i,y,\Delta$ we obtain the equivalent expression for the index \eqref{eqn:sugra_index} as 
+\beqn
+\label{eqn:Kim_sugra}
+f_{sugra}^{6d} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
+\eeqn
+We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
+%\beqn
+%t_1 = y_1^{-1} , \quad t_2 = y_3, \quad r = q^{-1/2} y 
+%\eeqn
+
+Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
+\beqn
+q = x^4, \quad t_1 = y_2, \quad t_2 = y_1, \quad r^2 = z .
+\eeqn
+(Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
+We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.
+
 \parsec 
@@
 with $w = (w_a), a=1,2,3,4$.
-The stack of membranes wrap $w_1=w_2=w_{3}=w_{4} = 0$.
+The stack of membranes wrap 
+\beqn
+w_1=w_2=w_{3}=w_{4} = 0 .
+\eeqn
 
+The bosonic subalgebra \lie{eqn:gut} of the twisted superconformal algebra embeds, in this case, as the following ghosts of the eleven-dimensional model.
 \begin{itemize}
@@
 \beqn
- \frac{\del}{\del z}, z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
+ \frac{\del}{\del z}, \quad z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}, \quad \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
 \eeqn
@@
         \beqn
-        T =  z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}
+        L_0 =  z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}
         \eeqn
@@
 \caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \R\times \C$.}
-\label{tbl:sugraM5}
+\label{tbl:sugraM2}
 \end{center}
@@
 
-We enumerate single particle supergravity states via computing the super trace of the operator $q^T t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{3d}_{sugra}$:
+We enumerate single particle supergravity states via computing the super trace of the operator $q^T t_1^{h_1} t_2^{h_2} t_3^{h_3}$ acting on $\cH^{3d}_{sugra}$:
 \beqn
@@
 \eeqn
-The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
-That is, we compute the expression
 
@@
 \beqn
-f_{sugra}^{3d} (q, t_{1}, t_{2}, t_3) = \frac{\left(\begin{aligned}
-        & -q^{-7/4}(t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) +q^{1/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) \\
-        & +q^{1/2}(1-q)(t_{1}t_{2}+t_{1}t_{3}+t_{2}t_{3}+t_{1}^{-1}t_{2}^{-1}+t_{1}^{-1}t_{3}^{-1}+t_{2}^{-1}t_{3}^{-1})\end{aligned}\right)}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})}.
+f_{sugra}^{3d} (q,t_1,t_2,t_3) = \frac{1 + q^{5/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) - q^{3/4} (t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) - q^2}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})} .
 \eeqn
@@
 
-\parsec Upon performing the change of variables
-
+This result is in close agreement with previously computed indices for supergravity on $AdS_{4}\times S^{7}$
+For example, our formula differs slightly from the expression found in \cite[Eq. (2.17)]{Bhattacharya:2008zy}. 
+To obtain an exact match we simply subtract one single particle state
 \beqn
-q= x^{2} , \quad t_1 = (y_{2}y_{3})^{1/2}/y_1^{1/2} , \quad t_2 = (y_{1}y_3)^{1/2}/ y_2^{1/2} , \quad t_3 = (y_1 y_2)^{1/2}/y_{3}^{1/2}
+f_{sugra}^{3d} (q, t_{1}, t_{2}, t_3) - 1 = \frac{\left(\begin{aligned}
+        & -q^{7/4}(t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) +q^{1/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) \\
+        & +q^{1/2}(1-q)(t_{1}t_{2}+t_{1}t_{3}+t_{2}t_{3}+t_{1}^{-1}t_{2}^{-1}+t_{1}^{-1}t_{3}^{-1}+t_{2}^{-1}t_{3}^{-1})\end{aligned}\right)}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})}.
 \eeqn
-
-the result agrees with previously computed indices for single particle states for supergravity on $AdS_{4}\times S^{7}$ \cite{}
+To compare exactly to \cite{Bhattacharya:2008zy} we note the change of variables
+\beqn
+q= x^{2} , \quad t_1 = (y_{2}y_{3})^{1/2}/y_1^{1/2} , \quad t_2 = (y_{1}y_3)^{1/2}/ y_2^{1/2} , \quad t_3 = (y_1 y_2)^{1/2}/y_{3}^{1/2} .
+\eeqn

### 2022-08-22 fivebranes/twisted.tex
update

@@
 \eeqn
+Notice that upon varying the field $\gamma$ and assuming that $\d_{dR} \mu = 0$ and $\nu = \div \mu = 0$ we recover the equation of motion \eqref{eqn:eom2} from this action functional. 
 %
@@
 The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
+We do not recall the precise relationship between this five-dimensional theory and eleven-dimensional supergravity, but it will be helpful to recall some features of the five-dimensional theory.
 
@@
 
-\brian{non BV setup}
-
 The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory---a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{Aharony:2008ug}.
@@
 \[
-\Omega^{\bu}(S) \hotimes \left[ \Omega^{0,\bu}(C, K^{1/4}_C \otimes \C^4) \oplus \Pi \Omega^{0,\bu} (C,K^{3/4}_C \otimes \C^4) \right] .
+\Omega^{\bu}(S) \hotimes \left[ \Pi \Omega^{0,\bu}(C, K^{1/4}_C \otimes U) \oplus \Omega^{0,\bu} (C,K^{3/4}_C \otimes U^*) \right] 
 \]
+where $W\cong \C^4$ is the fundamental $\lie{sl}(4)$ representation.
 The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
@@
 More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.
+For general background on the theory of THFs we refer the reader to \cite{DuchampKalka,Rawnsley}.
 
@@
 If $F \cap \Bar{F} = 0$ then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
+For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure.
 
@@
 \eeqn
+The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.
+
 Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
@@
 \beqn
-\beta \in \Pi \cA_F^\bu, \quad \gamma \in \cA^{1,\bu}_F, \quad \mu \in \Pi \cA^\bu_F(\theta_F), \quad \nu \in \cA_F^\bu  .
+\beta \in \Pi \cA_F^\bu (M) , \quad \gamma \in \cA^{1,\bu}_F (M) , \quad \mu \in \Pi \cA^\bu_F(M, \theta_F), \quad \nu \in \cA_F^\bu (M)  .
 \eeqn
@@
 \eeqn
+If we assume that $\nu = \Div \mu = 0$ we recover the following equation of motion upon varying $\gamma$
+\beqn
+\thfd \mu + \frac12 [\mu,\mu] = D \gamma D \gamma .
+\eeqn
+This is a generalization of equation \eqref{eqn:eom2} for a general THF $F$ on the eleven-manifold~$M$.
 

### 2022-08-22 fivebranes/fact.tex
end of day

@@
 
-\subsection{Summary}
+\subsection{A finite $N$ conjecture}
 \label{sec:factsummary}
 
-We summarize the key points of this section.
-In both the fivebrane and membrane case, we have described a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables restricted to the worldvolume of the fivebrane or membrane.
+We summarize the key points of this section which will lead to a general conjecture for the factorization algebra of observables for the worldvolume theory on a finite number of fivebranes in the holomorphic twist.
+In the beginning of this section we defined a factorization algebra $\Bar{\pi}_*\Obs_{sugra}$ which we think about as being the factorization algebra of observables of twisted supergravity restricted to the worldvolume of the fivebrane or membrane.
 This factorization algebra is of the form 
 \[
-\pi_*\Obs_{sugra} = \clie^\bu(\cG)
+\Bar{\pi}_*\Obs_{sugra} = \clie^\bu(\cG)
 \]
-where $\cG$ is a sheaf of $L_\infty$ algebras on the worldvolume of the fivebrane or membrane.
-While $\infty$ rank, $\cG$ is still well-behaved geometrically. 
-It is given as the sheaf of sections of a pro vector bundle.
+where $\cG = \cG_Z$ is a sheaf of $L_\infty$ algebras on the worldvolume~$Z$ of the fivebrane.
 
-This local $L_\infty$ algebra came with a natural decomposition 
+We have seen that $\cG$ is given as the sheaf of sections of a pro vector bundle. 
+In fact, the local $L_\infty$ algebra $\cG$ came with a natural decomposition 
 \[
@@
 Applying~$!$-duals we obtain a sequence
-\beqn
+\beqn\label{eqn:limit1}
 \ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
@@
 \eeqn 
+whose limit is the universal factorization algebra of classical observables on the fivebrane 
+\[
+(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) .
+\]
+
+The first nonzero term in this limit diagram \eqref{eqn:limit1} is 
+\[
+\clie_\bu(\cG_{1,c})
+\]
+where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$. 
+In \cite{SWtensor}, Saberi and the second author have given an explicit description of the holomorphic twist of the worldvolume theory on a single fivebrane, that is, the six-dimensional superconformal theory associated to the abelian Lie algebra~$\lie{gl}(1)$.
+We denote the corresponding factorization algebra on the three-fold~$Z$ by~$\Obs_1$.
+
+We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
+This is a free theory and the underlying $\Z \times \Z/2$ graded cochain complex of fields $\cE_{1}$ with linear BRST differential is
+\beqn
+\begin{tikzcd}
+\ul{-1} & \ul{0} \\
+\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
+\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
+\end{tikzcd} 
+\eeqn
+Here we recall in the $\Z \times \Z/2$ bigrading the differential has bidegree $(1,0)$. 
+The factorization algebra $\Obs_1$ is given by~$\cO(\cE_1)$.
+
+\begin{prop}
+\label{prop:factabelian}
+There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
+\[
+\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{1} .
+\]
+\end{prop}
+
+\begin{proof}
+In weight $(-1)$ the abelian local Lie algebra takes the form
+\[
+\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
+\]
+where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
+As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
+\beqn\label{eqn:weight-1a}
+\begin{tikzcd}
+\ul{odd} & \ul{even}\\
+\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
+\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
+\end{tikzcd}
+\eeqn
+On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
+\[
+\cO(\cE_{1}(U)) = \Sym(\Pi \overline{\cE}_{1,c}^!(U)) .
+\]
+It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
+The result then follows by applying ellipticity.
+\end{proof}
+
+We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
+However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
+
+We now formulate a general conjecture about the worldvolume theory on a stack of holomorphically twisted fivebranes.
+Recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
+In this form of the conjecture we focus only on the six-dimensional superconformal theories associated to Lie algebras of type $A$.
+
+\begin{conj}
+\label{conj:fact}
+For $N > 1$, let $\Obs_N$ be the factorization algebra on $Z$ of classical observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$.
+Then, there is an equivalence of factorization algebras on~$Z$:
+\beqn
+\Obs_{N} \simeq \clie_\bu(\cG_{N,c}) .
+\eeqn 
+\end{conj}
 

### 2022-08-22 fivebranes/finite.tex
end of day

--- 2022-07-19 fivebranes/ops.tex
@@
-\documentclass[11pt]{amsart}
-%
-%%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
-%
-\begin{document}
+\section{Operators on a finite number of fivebranes}
 
-\section{Local operators in twisted $M$ theory}
+In conjecture \ref{conj:fact} we have formulated a conjectural description of the factorization algebra of classical observables $\Obs_{N}$ associated to the worldvolume theory on a stack of $N$ fivebranes in the holomorphic twist.
+Concretely, for each $N$ we have constructed a local Lie algebra $\cG_N$ on the worldvolume three-fold $Z$. 
+Our conjecture is that the factorization algebra associated to a stack of $N$ holomorphically twisted fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{N,c})$, where $\cG_{N,c}$ denotes the cosheaf of compactly supported sections.
+The main goal of this section is to extract the algebra of local operators from this factorization algebra and to then deduce explicit formulas for  local characters.
 
-The notion of a factorization algebra captures both the local operators of a theory together with the non-local operators that on can define from the local ones via descent.
-From the data of a factorization algebra, one can recover local operators by the following formal construction. 
-Let $\Obs$ be the factorization algebra of observables of some theory defined on a smooth manifold $M$.
-The space of local operators at point $p \in M$ is, in a precise sense, the limiting behavior of the factorization algebra evaluated on the system of open sets which contain the point~$p$.
+For a stack of $N=1$ fivebranes, which corresponds to the abelian six-dimensional superconformal field theory, we find that our local character matches exactly with the expressions in the literature. 
+This is not a surprise as we have shown that even at the level of factorization algebras $\clie_\bu(\cG_{1,c})$ is quasi-isomorphic to~$\Obs_1$, see Proposition~\ref{prop:factabelian}.
 
-Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
-For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point.
+The main result of this section is a closed formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
+Following conjecture \ref{conj:fact} and the general discussion of \S \ref{sec:sucaindex} we are led to hypothesize a closed formula for the superconformal index for the theory on a finite number of fivebranes (in flat space).
+As far as the authors are aware of there is no closed formula for the refined superconformal index (with four independent fugacities) for the theory on a stack of $N > 1$ fivebranes.
+For small values of $N$ we expand our closed formulas to low orders in the fugacity $q$ (which roughly counts instanton charge) to match exactly with expressions in the literature.
 
-In this section we recall the essentials of the theory of local operators for holomorphic-topological theories.
+\subsection{Local characters for twisted superconformal theories}\label{s:localchar}
 
-\subsection{Local operators in topological-holomorphic theories}
+Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
+The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
+The particular group of symmetries depends on the theory, so we will present some examples.
 
-A factorization algebra encodes the many ways to combine observables supported on arbitrary open sets. 
-Local operators, on the other hand, exist just at a point in spacetime.
-From the factorization algebra perspective one can recover local operators by looking at observables which are supported on \text{every} open set which contains the given point; mathematically this is computed by a limit.
+The holomorphic twist of the superconformal algebra in dimension six is $\lie{osp}(6|2)$. 
+In the case of the holomorphic twist of a six-dimensional superconformal theory we will consider the local character of operators with respect to the subalgebra 
+\beqn\label{eqn:cartan2}
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
+\eeqn
+and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.
+We recalled in \S \ref{sec:states} an alternative parametrization of the fugacities in terms of the parameters $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$.
+These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$.
 
-Precisely, in \cite[Definition 10.1.0.1]{CG2} the space of local operators of a factorization algebra $\cF$ at a point $p \in M$ is defined by the limit $\cF(p) = \lim_{U \ni p} \cF(U)$ which runs over open sets $U \subset M$ containing~$p$.
-
-We will only consider local operators on affine space $\R^d$. 
-In this case, we will have the additional property that the factorization algebras are translation invariant.
-At the level of local operators this means that the translation map $\tau_{p \to p'}$ induces an isomorphism $\cF(p) \simeq \cF(p')$. 
-Without loss of generality, we will consider expressions for local operators at $0 \in \R^d$.
-
-For topological-holomorphic theories the local operators take a very familiar form.
-As an algebra they are generated by (holomorphic) derivatives of the fields evaluated at the specified point. 
-More precisely, the local operators depend only on the $\infty$-jets of the fields at a point.
-In this section we carefully formulate this result and give some examples.
-
-\parsec[s:free]
-
-%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
-%Let $\cV$ denote its sheaf of holomorphic sections.
-%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
-%\[
-%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
-%\]
-%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
-%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
-%
-%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
-%\begin{itemize}
-%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
-%\[
-%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
-%\]
-%\end{itemize}
-%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
-%
-%\parsec
-A topological-holomorphic theory exists on spacetimes of the form $S \times X$ where $S$ is a smooth manifold and $X$ is a complex manifold (possibly equipped with some auxiliary geometric structures).
-The typical space of fields of a holomorphic-topological theory in the BV formalism is
-\beqn\label{eqn:cE}
-\cE = \Omega^\bu (S) \hotimes \Omega^{0,\bu}(X, V) 
-\eeqn
-where $V$ is a graded holomorphic vector bundle on $X$.
-The underlying free theory is described by a differential on the space of fields of the form
-\[
-\d_{dR} + \dbar + Q^{hol} .
-\]
-Here $\d_{dR}$ is the de Rham differential acting on $S$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon V \to V[1]$ is a holomorphic differential operator of cohomological degree~$+1$.
-This means that the free, linear equations of motion for a field $\varphi$ take the form
-\[
-\d_{dR} \varphi + \dbar \varphi + Q^{hol} \varphi = 0 .
-\]
-Taking into account linear gauge symmetries corresponds to cohomology---solutions to the equations of motion modulo the image of $\d_{dR} + \dbar + Q^{hol}$.
-
-Notice that $\cE$ is a sheaf of cochain complexes---it makes sense to restrict the fields to any open set $U \subset S \times X$. 
-The factorization algebra of observables of the free theory whose fields are as above assigns to an open set $U \subset S \times X$ the cochain complex
-\[
-\Obs \colon U \mapsto \cO(\cE(U)) = \Sym \left(\cE(U)^\vee \right) 
-\]
-equipped with the induced differential.
-
-Some remarks are in order:
-\begin{itemize}
-\item If $V$ is a topological vector space then $\cO(V) = \Sym(V^\vee)$ denotes the algebra of polynomials on~$V$.
-Here~$V^\vee$ is the topological dual.
-\item The topological dual of $\cE(U)$ is $\cE(U)^\vee \simeq \overline{\cE}^!_c(U)$ where the bar denotes distributional sections, the subscript $c$ denotes compact support, and $!$ denotes the Serre dual.
-Explicitly, if $U = U' \times U'' \subset S \times X$ then 
-\[
-\overline{\cE}^!_c(U' \times U'') \simeq \overline{\Omega}^\bu(U') \otimes \overline{\Omega}^{n,\bu}(U'',V^*)[n+m] 
-\]
-where $\dim_\C (X) = n$ and $\dim_\R (S) = m$. 
-\end{itemize}
-
-Let's restrict to the case that $S \times X = \R^m \times \C^n$ and suppose that the bundle $V \to \C^n$ is translation invariant with fiber $V_0$ over $0 \in \R^m \times \C^n$.
-We also assume that the operator $Q^{hol}$ is translation invariant.
-
-Given a vector bundle $E \to M$, the bundle of $\infty$-jets $J^\infty E \to M$ is a $\infty$-dimensional pro vector bundle whose fiber over a point $p \in M$ is 
-If $M = \R^d$ and $E$ is translation invariant, then the bundle of $\infty$-jets can be identified with $E_0 \times \C[[x_i]]$ where
-
-The jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes
-\[
-\cE(\C^n \times \R^m) \to V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
-\]
-The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
-Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
-\[
-V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} V_0 [[z_j]] 
-\]
-which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
-The only remaining differential on the right hand side is~$Q^{hol}$. 
-In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes $\cE(\R^m \times \C^n) \to V_0[[z_j]]$.
-
-\begin{lem}
-\label{lem:taylor}
-Suppose that $\cE$ is the sheaf of cochain complexes representing the free topological-holomorphic theory on $S \times X = \R^m \times \C^n$ and consider the factorization algebra of observables~$\Obs = \cO (\cE)$.
-Then, the Taylor expansion map
-\beqn\label{eqn:taylor}
-\cE(\C^n \times \R^m) \to V_0[[z_0,\ldots,z_n]]
-\eeqn
-induces a quasi-isomorphism of commutative dg algebras
-\[
-\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]] \right) .
-\]
-%Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
-%\[
-%\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]][1] \right) 
-%\]
-%where the right hand side is equipped with the differential $Q^{hol}$. 
-\end{lem}
-\begin{proof}
-Suppose that $D_\R \times D_\C \subset \R^m \times \C^n$ is a product of a real $m$-disk times a complex $n$-disk containing the origin.
-The algebra of observables supported on $D_\R \times D_\C$ is quasi-isomorphic to 
-\[
-\cO\left( \cO^{hol}(D_\C) \otimes V_0 \right) .
-\]
-
-Observe that there is a canonical map on fields 
-\[
-\cO^{hol}(D_\C) \otimes V_0 \to V_0[[z_1,\ldots,z_n]]
-\]
-given by taking the power series expansion at $0 \in D_\R \times D_\C$. 
-If an observables on $D_\R \times D_\C$ depends on only the value of the field and its derivatives at $0 \in D_\R \times D_\C$ then it automatically factors through this map. 
-In particular, this means that there is a quasi-isomorphism of local operators with functions on $V_0[[z_1,\ldots,z_n]]$,
-\[
-\Obs(0) \simeq \cO\left(V_0 [[z_1,\ldots,z_n]]\right).
-\] 
-\end{proof}
-
-Let's unpack this result explicitly. 
-Using the $n$-dimensional residue, we can identify the topological dual of $V_0[[z_1,\ldots,z_n]]$ with the vector space
-\beqn
-\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n} V_0^* [z_0^{-1}, \ldots,z_n^{-1}] .
-\eeqn
-This is the space of linear local operators. 
-If $\chi \colon V_0 \to \C$ is a dual vector in~$V_0^*$
-then we obtain a linear local operator at $0 \in \R^m \times \C^n$ on the space of fields by the assignment
-\[
-\varphi \mapsto \del_{z_1}^{k_1} \cdots \del_{z_n}^{k_n} \<\chi,\varphi\> (0) 
-\]
-where $k_i \geq 0$. 
-Under the quasi-isomorphism of the lemma above, this corresponds to the linear local operator 
-\[
-\frac{\d z_1}{z_1^{k_1+1}} \cdots \frac{\d z_n}{z_n^{k_n+1}} \chi .
-\]
-
-\parsec[s:interaction]
-
-It is not hard to turn on interactions in the description above. 
-An interacting theory in the BV formalism is described by a local $L_\infty$ algebra structure on $\cL = \cE[-1]$, where $\cE$ is the sheaf of fields.
-For a topological-holomorphic theory the higher $L_\infty$ structure maps $[\cdot]_k$ of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators and $[\cdot]_1 = \d_{dR} + \dbar + Q^{hol}$.
-For more details we refer to the definitions in \cite{GRWthf}.
-
-In this situation, the factorization algebra of classical observables supported on an open set $U \subset S \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
-This defines a factorization algebra 
-\[
-\Obs \colon U \mapsto \clie^\bu(\cL(U)) .
-\]
-We will now give a concise presentation for the {\em local} operators in a topological-holomorphic theory.
-
-On $S \times X = \R^m \times \C^n$ we can also ask that all $L_\infty$ structure maps be translation invariant. 
-If this is the case, one obtains the induced structure of an $L_\infty$ algebra on the (shift of the) jets of the fields supported at $0 \in \R^m \times \C^n$
-\[
-V_0 [[z_1,\ldots,z_n]] [-1] .
-\]
-The $[\cdot]_1$ operation is precisely $Q^{hol}$ as above.
-The Taylor expansion map \eqref{eqn:taylor} is a map of $L_\infty$ algebras. 
-Combining this with Lemma \ref{lem:taylor}, one gets a quasi-isomorphism of cochain complexes between the local operators of an interacting topological-holomorphic theory in terms of Lie algebra cohomology
-\[
-\Obs(0) \simeq \clie^\bu\left(V_0[[z_1,\ldots,z_n]][-1]\right) .
-\]
-
-%We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
-%if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
-%The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.
-
-\parsec[s:envelope]
-
-There is another way that observables are presented in a degenerate version of the BV formalism.
-Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
-We have seen that the observables~$\cO(\cE) = \Sym(\cE^\vee)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
-That is, we consider the factorization algebra 
-\[
-U \subset M \mapsto \Sym \left(\cE_c(U) \right) 
-\]
-where $U \to \cE_c(U)$ is the cosheaf of compactly supported sections of the bundle~$E$.
-
-%Suppose that $\cL$ is a local Lie algebra on a manifold $M$. 
-%Then, one can consider the factorization algebra
-%\[
-%\cF = \clie_\bu(\cL_c)
-%\]
-%which assigns to an open set $U$ the cochain complex $\clie_\bu(\cL_c(U))$.
-%This is the $!$-dual of the factorization algebra $\clie^\bu(\cL)$.
-%For topological-holomorphic local Lie algebras there is still an algorithm for computing $\cF(p)$ for a point~$p \in M$.
-%
-%We will assume that $\cL$ is a translation invariant topological-holomorphic local Lie algebra whose underlying sheaf of cochain complexes is
-%\[
-%\cL = \Omega^\bu (\R^m) \hotimes \Omega^{0,\bu}(\C^n, L)
-%\]
-%Here $L$ is a translation invariant holomorphic vector bundle on $\C^n$ and the differential in the complex is $\d_{dR} + \dbar + Q^{hol}$ as above.
-
-\begin{lem}
-\label{lem:envelope}
-Suppose that $\cE$ is the sheaf of fields of a free holomorphic theory as in~\eqref{eqn:cE} and consider the factorization algebra~$\cF = \Sym(\cE_c)$. 
-Then, the algebra of classical local operators at~$0 \in \C^n$ of the factorization algebra~$\cF$ is quasi-isomorphic to 
-\begin{align*}
-\cF(0) & \simeq {\rm Sym} \left(\Omega^{n,hol}(\Hat{D}^n,V_0^*)^\vee [-n]\right) \\ & \cong \cO\left(\Omega^{n,hol}(\Hat{D}^n,V_0^*) [n] \right) 
-\end{align*}
-where the differential on the right hand side is~$Q^{hol}$.
-\end{lem}
-
-%\begin{lem}
-%\label{lem:envelope}
-%Suppose that $\cL$ is a topological-holomorphic local Lie algebra on $S \times X = \R^m \times \C^n$ and let $\cF$ be the factorization algebra $\clie_\bu(\cL_c)$.
-%Moreover, assume that $Q^{hol}$ is an elliptic holomorphic differential operator. 
-%Then, there is a spectral sequence converging to $H^\bu(\cF(0))$ whose first page is the $Q^{hol}$ cohomology of
-%\[
-%\cO \left(\d^n z L_0^*[[z_1,\ldots,z_n]] [n+m-1] \right) .
-%\]
-%\end{lem}
-\begin{proof}
-First, notice that as graded topological vector spaces one has an isomorphism for any open set $U \subset M$ 
-\beqn\label{eqn:dist}
-\left(\overline{\cE}^!(U)\right)^\vee \simeq \cE_c(U) 
-\eeqn
-%
-%We use the spectral sequence induced by the filtration by the homogenous degree of a local operator.
-%The first page is the cohomology of 
-%\[
-%\lim_{U \ni 0} \Sym(\cL_c(U)[1]) 
-%\]
-%with respect to the linear differential $\d_{dR} + \dbar + Q^{hol}$ which acts on $\cL_c(U)$ and extends to the symmetric algebra by the rule that it is a derivation.
-This implies there is an isomorphism
-\beqn\label{eqn:dist2}
-\Sym(\cE_c(U)) \simeq \cO\left(\overline{\cE}^!(U)\right) 
-\eeqn
-for any open set $U$.
-By assumption, the linear differential $[\cdot]_1$ is elliptic, in particular the embedding of smooth sections into distributional sections
-\beqn\label{eqn:dist3}
-\cE^!(U) \hookrightarrow \overline{\cE}^! (U)
-\eeqn
-is a quasi-isomorphism for any open set~$U$.
-
-We can assume that $U \subset \C^n$ is a Stein open set containing~$0 \in \C^n$.
-%of the form $U' \times U'' \subset \R^m \times \C^n$ with $U' \subset \R^m$ contractible and $U''\subset \C^n$ Stein.
-Then we have a sequence of quasi-isomorphisms
-\begin{align*}
-\overline{\cE}^! (U) & \simeq \cE^!(U) \\ & \simeq \Omega^{n,\bu}(U, V^*)[n].
-\end{align*}
-The result now follows from Lemma~\ref{lem:taylor}.
-
-%Thus, the first page of this spectral sequence is isomorphic to the cohomology of the local operators $\Obs(0)$ of the free theory whose underlying cochain complex of fields is 
-%\[
-%\cE = \Omega^\bu(\R^m) \hotimes \Omega^{0,\bu}(\C^n , K_{\C^n} \otimes L^*[n+m-1]).
-%\]
-%In the notation of Equation \eqref{eqn:cE}, the holomorphic vector bundle $V$ is 
-%\[
-%K_{\C^n} \otimes L^*[n+m-1] .
-%\]
-%The result now follows from Lemma~\ref{lem:taylor} where we have used $\d^n z$ for basis for the line $K_{\C^n}|_0$. 
-\end{proof}
-
-\parsec[s:examples]
-
-We present some simple examples.
-
-\begin{eg}
-Suppose that $V$ is the trivial bundle on $\C^n$ and consider the theory whose fields are
-\[
-\cE = \Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) 
-\]
-where the differential is just $\d_{dR} + \dbar$. 
-Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
-\[
-\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
-\]
-Via the $n$-dimensional residue one can identify the algebra of local operators with 
-\[
-\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
-\]
-
-Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-We would like to observe that the equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the single particle index which is immediate to compute:
-\[
-\frac{1}{(1-q_1)\cdots (1-q_n)} .
-\]
-However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
-This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$. 
-One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
-\[
-\frac{y}{(1-q_1)\cdots (1-q_n)} .
-\]
-The plethystic exponential of such an expression is
-\[
-\prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
-\]
-which now makes sense as a power series in the variables $y,q_1,\ldots,q_n$.
-\end{eg}
-
-Its instructive to see how local operators differ between $!$-dual factorization algebras.
-Let us first point out a simple example. 
-\begin{eg}
-Consider the sheaf of cochain complexes
-\[
-\cE = \Omega^{0,\bu}\left(\C, K_{\C}^{\otimes r}\right),
-\]
-where $r \in \Z$ and the differential is~$\dbar$. 
-Then, we can consider both the factorization algebra $\Obs = \cO(\cE)$ and its $!$-dual $\Obs^! = \Sym(\cE_c)$.
-
-The $\infty$-jets at $0 \in \C$ of $\cE$ is quasi-isomorphic to $\Gamma(\Hat{D}^n, K^{\otimes r}) = \d z^{\otimes r} \C[[z]]$. 
-Thus the algebra of local operators $\Obs(0)$ is quasi-isomorphic to 
-\[
-\Obs(0) \simeq \cO \left(\Gamma(\Hat{D}, K^{\otimes r})\right) .
-\]
-In particular, the character of local operators $\Obs(0)$ is the plethystic exponential of
-\[
-\frac{q^{r}}{1-q} 
-\]
-where $q$ represents the fugacity for the standard~$\C^\times$ action on~$\C$.
-Notice that when $r = 0$ we run into a similar problem as in the previous example. 
-It is therefore convenient to introduce an extra fugacity $y$ which enters the single particle character as
-\[
-\frac{y q^{r}}{1-q}  .
-\]
-
-%Then, we have the factorization algebra which assigns to $U \subset \C$ the complex
-%\begin{align*}
-%\cF(U) & = \clie_\bu(\cL_c(U)) \\ & = \Sym\left(\Omega^{0,\bu}_c\left(U, K_U^{\otimes r}\right) [1] \right)
-%\end{align*}
-%where the differential is $\dbar$.
-
-%Serre duality induces an isomorphism
-%\begin{align*}
-%\Omega^{0,\bu}_c(\C, K_\C^{\otimes r}) \cong \left( \Gamma^{hol} (\C , K_\C \otimes K_\C^{-r})\right)^* \\
-%= \left( \Gamma^{hol} (\C , K_\C^{1-r})\right)^* .
-%\end{align*}
-
-On the other hand, by Lemma \ref{lem:envelope} we see that the local operators associated to the $!$-dual $\Obs^!(0)$ is identified with the vector space
-\[
-\cO\left(\Gamma(\Hat{D}, K^{1-r})[1]\right) .
-\]
-In particular, the character of local operators $\Obs^!(0)$ is the plethystic exponential of
-\[
--\frac{q^{1-r}}{1-q} 
-\]
-where $q$ represents the fugacity for the standard $\C^\times$ action on $\C$.
-This time, when $r=1$ there is a problem with defining the plethystic exponential. 
-To get an expression that makes sense for all $r$ we can again introduce a variable $y$ which enters the single particle character as
-\[
-- \frac{y q^{1-r}}{1-q} .
-\]
-\end{eg}
-
-\subsection{A relationship to the supersymmetric index}
-
-\subsection{Comparison to `states'}
+Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character.
+That is, the character of linear local operators.
 
@@
 
-We recalled the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
-This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables~$\Obs^{6d}_{\lie{u}(1)}$ on $Z$.
-We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs^{6d}_{\lie{u}(1)}(0)$ supported at~$0 \in \C^3$.
-
-The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{\lie{u}(1)}$ with linear BRST differential is
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
-\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
-
-Before moving on to characterizing local operators we take a brief moment to comment on the holographic appearance of the theory on a single fivebrane.
-
-\parsec[s:fiverelatesingle]
-
-In \eqref{eqn:lim2} we presented the universal factorization algebra of classical observables on the fivebrane 
-\[
-(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) 
-\]
-as a limit.
-The first nonzero term in this limit diagram is 
-\[
-\clie_\bu(\cG_{1,c})
-\]
-where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$.
-
-\begin{prop}
-There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
-\[
-\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{\lie{u}(1)} .
-\]
-\end{prop}
-
-\begin{proof}
-In weight $(-1)$ the abelian local Lie algebra takes the form
-\[
-\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
-\]
-where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
-As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
-\beqn\label{eqn:weight-1a}
-\begin{tikzcd}
-\ul{odd} & \ul{even}\\
-\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
-\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
-\end{tikzcd}
-\eeqn
-On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
-\[
-\cO(\cE_{\lie{u}(1)}(U)) = \Sym(\Pi \overline{\cE}_{\lie{u}(1),c}^!(U)) .
-\]
-It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
-The result then follows by applying ellipticity.
-\end{proof}
-
-We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
-However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
-
-\parsec[]
-
-We move on to characterizing the character of the holomorphic twist of the theory on a single fivebrane.
-By the previous result we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
+We deduce the character of the holomorphic twist of the theory on a single fivebrane and will find an exact match with the index of the six-dimensional superconformal theory for the abelian Lie algebra $\lie{gl}(1)$.
+By the proposition \ref{prop:factabelian} we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
 
@@
 \label{lem:single}
-The $\Z \times \Z/2$ graded algebra of local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
+The $\Z \times \Z/2$ graded algebra of local operators $\Obs_{1}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
 \beqn\label{eqn:localfree}
@@
 
-\parsec
-
-We move on to the straightforward computation of the character of local operators on a single fivebrane which we will present as the plethystic exponential of the character of linear local operators
+We present the character of $\Obs_1(0)$ as the plethystic exponential of the character $f_1(t_1,t_2,r,q)$ of the space of linear local operators
 \beqn
-\chi^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = {\rm PExp} \big[f^{6d}_{\lie{u}(1)}(t_1,t_2,q,r) \big] .
+\chi_{1} (t_1,t_2,r,q) = {\rm PExp} \big[f_1(t_1,t_2,r,q) \big] .
 \eeqn
-According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{single}$.
+According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{1}(t_1,t_2,r,q)$.
 
@@
 \begin{prop}
-The character $\chi_{u(1)}(q,t_1,t_2,r)$ of local operators of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
-\[
-f^{6d}_{u(1)} (q,t_1,t_2,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
+\label{prop:6done}
+The local character $\chi_{1}(t_1,t_2,r,q)$ of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle character
+\beqn\label{eqn:6done}
+f_{1} (t_1,t_2,r,q) = \frac{q^{3/2}(r + r^{-1}) - q^2(t_1 + t_1^{-1} t_2 + t_2^{-1} ) + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+\eeqn
 \end{prop}
 
-\parsec
+In terms of the parameters $y_1,y_2,y_3,y,q$ this single particle character reads
+\beqn
+f_{1} (y_i,y,q) = \frac{qy + q^2y^{-1} - q^2(y_1+y_2+y_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
+\eeqn
+The expression matches exactly with the index of the abelian six-dimensional superconformal theory.
+For example, compare with \cite[Eq. (3.1)]{Kim:2013nva} or \cite[Eq. (3.35)]{Bhattacharya:2008zy}.
+From now on, we will give all formulas for the index in terms of the parameters $y_1,y_2,y_3,y,q$.
 
-There are various degenerations, or specializations, of this character which are interesting to consider.
-These specializations involve restricting the character above to a subalgebra of the full Cartan that we considered above.
+Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
+In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
+For the case of the single fivebrane theory, this implies that the local operators $\Obs_{1}(0)$ form a representation for $E(3|6)$.
 
-One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
-\beqn
-f_{u(1)}(t,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
-\eeqn
+This fact also follows from our holographic analysis. 
+In \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$.
+Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
+In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs_{1}$.
+On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+Combining these facts we see that $\Obs_{1}(0)$ is a module for $E(3|6)$.
+
+In \S \ref{s:kr} we will express this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
+
+%\parsec
+%
+%There are various degenerations, or specializations, of this character which are interesting to consider.
+%These specializations involve restricting the character above to a subalgebra of the full Cartan that we considered above.
+%
+%One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
+%\beqn
+%f_{1}(r,q) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
+%\eeqn
 %They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
@@
 %\]
-In \S \ref{s:kr} we will compare this to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.
 
 \parsec
-
-Another specialization is related to a particular deformations by elements in the (twisted) superconformal algebra.
+There are various degenerations, or specializations, of this character which are interesting to consider.
+A particularly meaningful one is related to two deformations of the theory by elements in the (twisted) superconformal algebra.
 Recall that after performing the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry, the residual superconformal algebra is~$\lie{osp}(6|2)$. 
@@
 \]
-where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations.
+where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations, respectively.
 
@@
 
-Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
+Both deformations break the global Cartan subalgebra down to $\lie{gl}(1) \times \lie{gl}(1)$ according to the specializations
 \beqn\label{eqn:special1}
-q = r^2 , \quad t_2 = 1 .
+y=1 , \quad y_3 = 1 .
 \eeqn
+Notice that due to the constraint $y_1y_2y_3=1$ this forces $y_1 = y_2^{-1}$.
 As one can easily check, this specialization yields the following single particle index
 \[
-f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
+f_{1}(y_1, y_1^{-1},y_3=1, y=1, q) = \frac{q}{1-q} 
 \]
 which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
-Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
+Notice that the dependence on the parameter $y_1$ has completely dropped out even though we have not specialized it to any value.
+%Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
 
-%\subsection{Categorifying the index for free theories}
-%
-%In the case of both membranes and fivebranes we constructed a particular restriction of the local $L_\infty$ algebra $\cL_{sugra}$ to the respective worldvolume theories which we denoted by $\Bar{\pi}_* \cL_{sugra}$.
-%There are two important sub local $L_\infty$ algebras 
-%\[
-%\begin{tikzcd}
-%& \Bar{\pi}_*\cL_{sugra} & \\
-%\Bar{\pi}_*\cL_{sugra}^{(-1)} \ar[ur] & & \Bar{\pi}_*\cL_{sugra}^{(0)} \ar[ul] .
-%\end{tikzcd}
-%\]
-%This diagram induces a diagram of factorization algebras
-%\[
-%\begin{tikzcd}
-%& \left(\Obs_{sugra}|_Z\right)^! & \\
-%\clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(-1)}) \ar[ur] & & \clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(0)}) \ar[ul].
-%\end{tikzcd}
-%\]
+\subsection{A conjectural description of operators on a stack of two fivebranes}
 
-%\parsec[s:sugraops]
-%
-%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
-%
-%On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
-%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
-%\[
-%\Vect_0 (\C^5) = \{X \in \Vect(\C^5) \; | \; \div X = 0\} .
-%\]
-%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
-%\[
-%\Omega^{1,hol}(\C^5) / {\rm Im}(\del) 
-%\]
-%which is, of course, equivalent to the space of closed holomorphic two-forms $\Omega^{2,hol}_{cl}(\C^5)$. 
-%
-%\begin{thm}[\cite{RSW}[Theorem 2.1]]
-%The Taylor expansion map determines a map of $\Z/2$ graded $L_\infty$ algebras
-%\[
-%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
-%\]
-%Furthermore, $L_{sugra}$ is equivalent as a $\Z/2$ graded $L_\infty$ algebra to $\Hat{E(5|10)}$. 
-%\end{thm} 
-%
-%As an immediate corollary of this result we obtain by Lemma \ref{lem:localops} the following.
-%
-%\begin{cor}
-%\label{cor:sugraops}
-%Let $\Obs_{sugra}$ be the factorization algebra on $\C^5 \times \R$ of classical observables of the minimal twist of eleven-dimensional supergravity.
-%There is a quasi-isomorphism of commutative dg algebras
-%\[
-%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
-%\]
-%\end{cor}
-
-\subsection{A conjectural description of a stack of two fivebranes}
-
-In \S\ref{fact:summary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
+In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
 \[
@@
 \[
-q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+q^3 \frac{y_1 q + y_2 q + y_3 q }{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
 \]
@@
 \[
-q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+\frac{q^2 y^2 + q^3 + q^4 y^{-2}}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
 \]
+%\[
+%q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+%\]
 \item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
 \[
-q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3}\frac{(y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
 \]
@@
 
-\begin{conj}
+Combining these expressions we obtain the following.
+
+\begin{prop} \label{prop:6dtwo}
+The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the plethystic exponential of the following expression
+\beqn\label{eqn:6dtwo}
+f_{2} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
+\eeqn
+%\beqn\label{eqn:6dtwo}
+%f_{2} (t_1,t_2,r,q) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
+%\eeqn
+\end{prop}
+
+\brian{add some better transition} 
+Based on our discussion above we are led to the following conjecture.
+\begin{conj}\label{conj:6dtwo}
 The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
 \[
-\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
+\chi_{2} (t_1,t_2,r,q) = {\rm PExp} \left[f_2(t_1,t_2,r,q) \right] .
 \]
-where the single particle index is
-\[
-f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1^{-1} + t_1t_2^{-1} + t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\]
+where the single particle index is as in \eqref{eqn:6dtwo}.
 \end{conj}
@@
 \[
-\chi_{\lie{gl}(2)}^{6d} (q,t_1,t_2,r) = \chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) \cdot \chi_{\lie{u}(1)}^{6d}(q,t_1,t_2,r)
+\til \chi_{2} (y_i,y,q) = \chi_{2} (y_i,y,q) \cdot \chi_{1}(y_i,y,q)
 \]
-where the index for the $\lie{u}(1)$ theory is given in the previous section. 
+where the character $\chi_{1}$ for the $\lie{gl}(1)$ theory is given in the previous section. 
 As a factorization algebra \brian{finish}
+
+%\parsec[]
+%
+%The specialization of this index $t_1=t_2=r=1$ yields the single particle index
+%\[
+%\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
+%\]
 
@@
 
-The specialization of this index $t_1=t_2=r=1$ yields the single particle index
+The specialization of this index $y=1, y_3=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
 \[
-\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
-\]
-
-\parsec[]
-
-The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
-\[
-f_{two}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
+f_{2}(y_1, y_2, y_3=1, y=1, q) = \frac{q^2}{1-q} 
 \]
@@
 
-\subsection{Operators on a single membrane}
+\subsection{Finite $N$ index}
 
-\end{document}
+For $k \geq 3$ let
+\begin{align*}
+f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
+& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+\end{align*}
+
+%\begin{align*}
+%f_k (y_1,y_2,y_3,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi_k(q^{-1/2} y) \right. \\
+%& \left.  - q^{3(k-1)/2} \chi_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+%\end{align*}
+
+\begin{thm}
+\label{thm:finite}
+The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ on $Z=\C^3$ is 
+\beqn
+\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=2}^N f_k(y_1,y_2,y_3,y,q)\right].
+\eeqn
+\end{thm}
+
+We thus arrive at the following conjecture for the index of the worldvolume theory on a stack of a finite number of fivebranes which we phrase in terms of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$.
+
+\begin{conj} 
+The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$ is $\chi_{N}(y_1,y_2,y_3,y,q)$. 
+\end{conj}

### 2022-08-22 fivebranes/ops.tex
end of day

@@
 Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
-We have seen that the observables~$\cO(\cE) = \Sym(\cE^\vee)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
+We have seen that the observables~$\cO(\cE) = \Sym(\cE^*)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
 That is, we consider the factorization algebra 
@@
 
-\parsec[s:localchar]
+\subsection{Local characters for topological-holomorphic theories}\label{s:localchar}
 
 Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
-The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
-The particular group of symmetries depends on the theory, so we will present some examples.
+We will restrict our attention to cases where $\cF$, as a graded vector space, is of the form $\Sym(\cE^*)$ or $\Sym(\cE_c)$ where $\cE$ is of the form \eqref{eqn:cE}.
 
-The holomorphic twist of the superconformal algebra in dimensions three and six is $\lie{osp}(6|2)$. 
-So , in the case of the holomorphic twist of three and six-dimensional superconformal theories we consider the local character of operators with respect to the Lie algebra 
-\beqn\label{eqn:cartan2}
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
+The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries $H$, see \cite{SWchar}.
+The particular group of symmetries depends on the theory, and we will present some examples momentarily.
+
+By assumption, as a graded algebra, the algebra of local operators $\cF(0)$ of a topological-holomorphic theory is of the form
+\beqn
+\cF(0) = \Sym (\lie{s})
 \eeqn
-and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.
+where $\lie{s}$ is a graded topological vector space which we interpret as the linear local operators.
 
-Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character.
-That is, the character of linear local operators.
+We will also assume that the group of symmetries $H$ acting on $\cF(0)$ arises from an action of $H$ on the linear local operators $\lie{s}$. 
+Denote by $f_{\cF}({\bf q})$ the character of $\lie{s}$ with respect to this group action---this is the so-called `single particle' character. 
+The full character of $\cF(0)$ is then given as the plethystic exponential of this single particle character
+\beqn
+\chi_{\cF}({\bf q}) = {\rm PExp}\left[f_{\cF}({\bf q}) \right] .
+\eeqn
 
-\parsec[s:examples]
+\subsection{Examples}
 
@@
 \[
-\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
+\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) ,
 \]
+where $\lie{s} \simeq \frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]$ is (equivalent to) the space of linear local operators.
 
-Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
-We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index which is immediate to compute:
+Consider the standard torus action $\C^\times \times \cdots \times \C^\times$ on $\C^n$. 
+We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index (the character of the space of linear local operators) which is immediate to compute:
 \[
@@
 
-The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$ \cite{SWchar}. 
+The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
 Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.
@@
 \subsection{Comparison to `states'}
-
-\subsection{Operators on a single fivebrane}
-
-We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
-This theory exists on any complex three-fold~$Z$ and hence we get a factorization algebra of classical observables
-\[
-\Obs^{6d}_{\lie{u}(1)} 
-\]
-on $Z$.
-We will specialize to~$Z=\C^3$ to characterize local operators~$\Obs^{6d}_{\lie{u}(1)}(0)$ supported at~$0 \in \C^3$.
-
-The theory on a single fivebrane is free and the underlying cochain complex of fields $\cE_{\lie{u}(1)}$ with linear BRST differential is
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2,\bu}(Z) \ar[r,"\del"] & \Omega^{3,\bu}(Z) \\
-\Pi \Omega^{0,\bu}(Z, K_{Z}^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.
-
-Before moving on to characterizing local operators we take a brief moment to comment on the holographic appearance of the theory on a single fivebrane.
-
-\parsec[s:fiverelatesingle]
-
-In equation \eqref{eqn:limit2} we presented the universal factorization algebra of classical observables on the fivebrane 
-\[
-(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) 
-\]
-as a limit.
-The first nonzero term in this limit diagram is 
-\[
-\clie_\bu(\cG_{1,c})
-\]
-where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$.
-
-\begin{prop}
-There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on the three-fold~$Z$
-\[
-\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs^{6d}_{\lie{u}(1)} .
-\]
-\end{prop}
-
-\begin{proof}
-In weight $(-1)$ the abelian local Lie algebra takes the form
-\[
-\cG_Z^{(-1)} \simeq \Omega^{0,\bu}(Z,\cV^{(-1)}) 
-\]
-where $\cV^{(-1)}$ was defined in \ref{s:weight-1}.
-As a sheaf of $\Z/2$ gradedcochain complexes the factorization algebra $\clie_\bu(\cG_Z^{(-1)})$ assigns to an open set $U\subset Z$ the graded symmetric algebra on the complex
-\beqn\label{eqn:weight-1a}
-\begin{tikzcd}
-\ul{odd} & \ul{even}\\
-\Omega_c^{0,\bu}(U, K_Z^{1/2} \otimes \C^2) & \\
-\Omega_c^{0,\bu}(U) \ar[r,"\del"] & \Omega_c^{1,\bu}(U) .
-\end{tikzcd}
-\eeqn
-On the other hand, as a $\Z/2$ graded cochain complex, the factorization algebra of observables of the theory on a single fivebrane is of the form 
-\[
-\cO(\cE_{\lie{u}(1)}(U)) = \Sym(\Pi \overline{\cE}_{\lie{u}(1),c}^!(U)) .
-\]
-It is immediate to see that as a $\Z/2$ graded cochain complex $\cE_c^!(U)$ is exactly \eqref{eqn:weight-1a}.
-The result then follows by applying ellipticity.
-\end{proof}
-
-We remark that the Chevalley--Eilenberg complex of an $L_\infty$ algebra $\clie_\bu(\lie{g})$ does not have the structure of a commutative dg algebra.
-However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
-
-\parsec[]
-
-We know deduce the character of the holomorphic twist of the theory on a single fivebrane.
-By the previous result we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
-
-\begin{lem}
-\label{lem:single}
-The $\Z \times \Z/2$ graded algebra of local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
-\beqn\label{eqn:localfree}
-V_0[[z_1,z_2,z_3]] \simeq \Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
-\eeqn
-\end{lem}
-
-\begin{proof}
-The jet expansion at $0 \in \C^3$ determines a map from the sections of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
-\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-On the formal disk all closed two-forms are automatically exact, which implies the lemma.
-\end{proof}
-
-\parsec
-
-We move on to the straightforward computation of the character of local operators on a single fivebrane which we will present as the plethystic exponential of the character of linear local operators
-\beqn
-\chi^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = {\rm PExp} \big[f^{6d}_{\lie{u}(1)}(t_1,t_2,q,r) \big] .
-\eeqn
-According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{single}$.
-
-\begin{itemize}
-\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
-\[
-- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
-\[
-q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
-\[
-q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-\end{itemize}
-
-Putting this all together we obtain the following.
-
-\begin{prop}
-\label{prop:6done}
-The local character $\chi_{\lie{u}(1)}(q,t_1,t_2,r)$ of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle index
-\beqn\label{eqn:6done}
-f^{6d}_{\lie{u}(1)} (t_1,t_2,q,r) = \frac{(r + r^{-1})q^{3/2} - (t_1 + t_1^{-1} t_2 + t_2^{-1} )q^2 + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\eeqn
-\end{prop}
-
-Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
-In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
-For the case of the single fivebrane theory, this implies that the local operators $\Obs^{6d}_{\lie{u}(1)}(0)$ form a representation for $E(3|6)$.
-
-This fact also follows from our holographic analysis. 
-In \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$.
-Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
-In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs_{\lie{u}(1)}^{6d}$.
-On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
-Combining these facts we see that $\Obs_{\lie{u}(1)}^{6d}(0)$ is a module for $E(3|6)$.
-
-In \S \ref{s:kr} we will express this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in \cite{KR2}.
-
-\parsec
-
-There are various degenerations, or specializations, of this character which are interesting to consider.
-These specializations involve restricting the character above to a subalgebra of the full Cartan that we considered above.
-
-One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
-\beqn
-f^{6d}_{\lie{u}(1)}(q,r) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
-\eeqn
-%They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
-%In a similar method to the one used in \cite{KR1}, one can compute the specialized (super) character of $I(0,0;1;-1)$ to find
-%\[
-%\chi_{u(1)} (q,t_1=t_2=r=1) = \frac{2 q^{3/2} - 3 q^2 + q^3}{(1-q)^3} .
-%\]
-
-\parsec
-
-Another specialization is related to a particular deformations by elements in the (twisted) superconformal algebra.
-Recall that after performing the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry, the residual superconformal algebra is~$\lie{osp}(6|2)$. 
-We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.
-
-There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
-The odd part of~$\lie{osp}(6|2)$ can be identified with 
-\[
-\C^3 \otimes \C^2 \oplus \Sym^2(\C^3) \otimes \C^2 
-\]
-where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations.
-
-\begin{itemize}
-\item The space $\C^3 \otimes \C^2$ is spanned by twisted supergravity fields of the form $\gamma = w_a \d z_i$. 
-\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
-\end{itemize}
-
-Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
-\beqn\label{eqn:special1}
-q = r^2 , \quad t_2 = 1 .
-\eeqn
-As one can easily check, this specialization yields the following single particle index
-\[
-f_{\lie{u}(1)}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
-\]
-which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
-Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.
 
@@
 
-\subsection{A conjectural description of a stack of two fivebranes}
-
-In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
-\[
-\clie_{\bu}(\cG_{1,c}) \leftarrow \clie_{\bu}(\til \cG_{2,c}) \leftarrow \cdots .
-\]
-We now turn to the factorization algebra $\clie_{\bu}(\til \cG_{2,c})$.
-
-Recall that $\til \cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\til \cG_{2} = \cG / \cG^{\geq 1}$. 
-Since $\cG$ is concentrated in weights $\geq -1$ we see that $\til \cG_{2}$ is of the form
-\[
-\til \cG_2 = \cG_2 \ltimes \cG_1 
-\]
-where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
-We focus mostly on the factorization algebra $\clie_\bu(\cG_{2,c})$.
-
-We have already characterized the local dg Lie algebra $\cG_{2}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
-We deduce that $\cG_2$ can be given a $\Z \times \Z/2$ grading where, as usual, we refer to $\Z$ as the cohomological grading and $\Z/2$ as the parity. 
-With this lift to a $\Z \times \Z/2$ grading, the even part of $\cG_2$ is
-\[
-\Omega^{0,\bu}(Z, \T_Z) \oplus \Omega^{0,\bu}(Z) \otimes \lie{sl}(2) 
-\]
-with its natural cohomological grading by Dolbeault form type. 
-The odd part of $\cG_2$ is
-\[
-\Omega^{1,\bu}(Z, K_Z^{-1/2}) \otimes \C^2 .
-\]
-The differential is $\dbar$ and the Lie bracket has been described in \S\ref{s:weight0}.
-
-On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
-Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
-
-\parsec
-
-We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$.
-
-\begin{itemize}
-\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
-\[
-q^3 \frac{t_1^{-1} q + t_1 t_2^{-1} q + t_2 q }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
-\[
-q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
-\[
-q^{3}\frac{(q^{1/2} r + q^{1/2} r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-\end{itemize}
-
-Combining these expressions we obtain the following.
-
-\begin{prop} \label{prop:6dtwo}
-The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
-\beqn\label{eqn:6dtwo1}
-\frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\eeqn
-\end{prop}
-
-Based on our discussion above we are led to the following conjecture.
-\begin{conj}\label{conj:6dtwo}
-The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
-\[
-\chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) = {\rm PExp} \left[f_{\lie{sl}(2)}^{6d} (t_1,t_2,q,r) \right] .
-\]
-where the single particle index is
-\beqn\label{eqn:6dtwo}
-f_{\lie{sl}(2)}^{6d} (q, t_1,t_2,r) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\eeqn
-\end{conj}
-
-Following the general relationship between characters of holomorphic twists of supersymmetric theories and supersymmetric indices, this our conjecture for the supersymmetric index of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(2)$.
-Similarly, the index associated to the $\lie{gl}(2)$ theory is conjectured to be simply the product 
-\[
-\chi_{\lie{gl}(2)}^{6d} (q,t_1,t_2,r) = \chi_{\lie{sl}(2)}^{6d} (q,t_1,t_2,r) \cdot \chi_{\lie{u}(1)}^{6d}(q,t_1,t_2,r)
-\]
-where the index for the $\lie{u}(1)$ theory is given in the previous section. 
-As a factorization algebra \brian{finish}
-
-\parsec[]
-
-The specialization of this index $t_1=t_2=r=1$ yields the single particle index
-\[
-\frac{3q^4 + 3 q^3 - 6 q^{7/2}}{(1-q)^3}. 
-\]
-
-\parsec[]
-
-The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
-\[
-f^{6d}_{\lie{sl}(2)}(t_1, 1, q, q^{1/2}) = \frac{q^2}{1-q} 
-\]
-which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
-
-\subsection{Operators on a single membrane}
-
 %\end{document}

### 2022-08-24 fivebranes/finite.tex
merger

@@
-\section{Operators on a finite number of fivebranes}
+\section{Conjectures for operators on a finite number of fivebranes}
 
 In conjecture \ref{conj:fact} we have formulated a conjectural description of the factorization algebra of classical observables $\Obs_{N}$ associated to the worldvolume theory on a stack of $N$ fivebranes in the holomorphic twist.
-Concretely, for each $N$ we have constructed a local Lie algebra $\cG_N$ on the worldvolume three-fold $Z$. 
+In this section we begin to provide some evidence for this description at the level of local operators, which is just a small piece of the factorization algebra.
+
+For each $N$ we have constructed a local Lie algebra $\cG_N$ on the worldvolume three-fold $Z$. 
 Our conjecture is that the factorization algebra associated to a stack of $N$ holomorphically twisted fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{N,c})$, where $\cG_{N,c}$ denotes the cosheaf of compactly supported sections.
@@
 
-The main result of this section is a closed formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
+The main computation of this section is a closed formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
 Following conjecture \ref{conj:fact} and the general discussion of \S \ref{sec:sucaindex} we are led to hypothesize a closed formula for the superconformal index for the theory on a finite number of fivebranes (in flat space).
@@
 
-In \S \ref{s:kr} we will express this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
+In appendix \S \ref{s:kr} we will describe this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
 
@@
 There are various degenerations, or specializations, of this character which are interesting to consider.
-A particularly meaningful one is related to two deformations of the theory by elements in the (twisted) superconformal algebra.
-Recall that after performing the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry, the residual superconformal algebra is~$\lie{osp}(6|2)$. 
+A particularly meaningful one is related to two different deformations of the theory by elements in the (twisted) superconformal algebra.
+Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
 We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.
@@
 \[
-\C^3 \otimes \C^2 \oplus \Sym^2(\C^3) \otimes \C^2 
+\C^3 \otimes \C^2 \oplus \wedge^2(\C^3) \otimes \C^2 
 \]
-where $\C^3, \C^2$ are the fundamental $SU(3)$ and $SU(2)$ representations, respectively.
+where $\C^3, \C^2$ are the fundamental $\lie{sl}(3)$ and $\lie{sl}(2)$ representations, respectively.
 
 \begin{itemize}
-\item The space $\C^3 \otimes \C^2$ is spanned by twisted supergravity fields of the form $\gamma = w_a \d z_i$. 
-\item The deformation $(z_2 \d z_3 - z_3 \d z_2) \otimes r_-$. 
+\item The summand $\C^3 \otimes \C^2$ embeds into the ghosts of twisted supergravity via the $\gamma$-type fields which satisfy
+\[
+\del \gamma = \d w_a \d z_i .
+\]
+where $i=1,2,3$ and $a = 1,2$.
+Note that $\gamma$ appears to be ambiguous up to a closed holomorphic one-form, but since there is a linear gauge symmetry which sends $\beta \mapsto \del \beta$, it implies that $\gamma$ is unique up to a BRST exact term.
+Since in our model all closed one-forms are rendered trivial in cohomology
+\item The summand $\wedge^2(\C^3) \otimes \C^2$ embeds as another $\gamma$-type field which satisfies 
+\[
+\del \gamma = w_a \d z_i \d z_j .
+\]
 \end{itemize}

### 2022-08-24 fivebranes/ops.tex
merger

@@
 \subsection{A relationship to the superconformal index}
-
+\label{sec:sucaindex}
 We will turn to computing the local character for twists of the single membrane and fivebrane theories momentarily and comment on the relationship to known formulas in the physics literature. 

### 2022-08-24 fivebranes/finite.tex
merge

@@
 For small values of $N$ we expand our closed formulas to low orders in the fugacity $q$ (which roughly counts instanton charge) to match exactly with expressions in the literature.
-
-\subsection{Local characters for twisted superconformal theories}\label{s:localchar}
-
-Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
-The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
-The particular group of symmetries depends on the theory, so we will present some examples.
-
-The holomorphic twist of the superconformal algebra in dimension six is $\lie{osp}(6|2)$. 
-In the case of the holomorphic twist of a six-dimensional superconformal theory we will consider the local character of operators with respect to the subalgebra 
-\beqn\label{eqn:cartan2}
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2) 
-\eeqn
-and denote the corresponding fugacities by $t_1,t_2,r,q$ just as in \S \ref{sec:states} in our computation of the index of twisted supergravity states.
-We recalled in \S \ref{sec:states} an alternative parametrization of the fugacities in terms of the parameters $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$.
-These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$.
-
-Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character.
-That is, the character of linear local operators.
 
@@
 Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
-We have recalled in \ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.
+We have recalled in \S\ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory.
 
 There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
-The odd part of~$\lie{osp}(6|2)$ can be identified with 
+The odd part of~$\lie{osp}(6|2)$ can be identified with the twelve-dimensional space
 \[
@@
 where $\C^3, \C^2$ are the fundamental $\lie{sl}(3)$ and $\lie{sl}(2)$ representations, respectively. 
+The $\lie{gl}(1)$ factor in the bosonic part of $\lie{osp}(6|2)$ acts with weight $1/2$ on both summands.
 

### 2022-08-24 fivebranes/ops.tex
merge

--- 2022-08-22 fivebranes/ops.tex
@@
 We consider a way of counting operators in a topological-holomorphic theory, called the `local character' of a holomorphic-topological theory \cite{SWchar}, and compare it to the superconformal index.
-We will then present a few examples including expressions for the local character on the twists of a theory on a single membrane and fivebrane and will find the expected match with the physics literature.
+We then present a few simple examples and then go on to set up the theory of local operators associated to factorization algebras~$\clie_\bu(\cG_{N,c})$ we constructed in \S \ref{s:fact}.
 
@@
 
+\subsection{Local characters for twisted superconformal theories}\label{s:localchar}
+
+Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
+The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
+The particular group of symmetries depends on the theory.
+In this section we focus on local characters of factorization algebras that arise as twists of six-dimensional $\cN=(2,0)$ supersymmetric theories.
+
+The (complexified) superconformal algebra in dimension six is $\lie{osp}(8|4)$. 
+The holomorphic twist of this superconformal algebra is $\lie{osp}(6|2)$. 
+We will consider the symmetry by the bosonic subalgebra
+\beqn\label{eqn:cartan3}
+\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2)  .
+\eeqn
+The corresponding generators of the Cartan, as in \S \ref{sec:states}, were denoted $h_1,h_2,h,$ and $\Delta$ and the respective fugacities $t_1,t_2,r,q$.
+
+We have described how this subalgebra embeds as fields in the twist of eleven-dimensional supergravity in \S \ref{s:ads7}. 
+In particular, the holomorphic twist of any six-dimensional superconformal theory will have as a symmetry the subalgebra \eqref{eqn:cartan3}.
+If the corresponding factorization algebra is $\cF$, and the local operators $\cF(0)$, the local character is then defined by the formal expression
+\beqn
+\chi_{\cF}(t_1,t_2,r,q) = {\rm Tr}_{\cF(0)} \left((-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta\right) .
+\eeqn
+In the next section we will compute these characters in the case that the factorization algebra $\cF$ is $\clie_\bu(\cG_{N,c})$ where $N = 1,2,\ldots$.
+
+We pointed out in \S \ref{sec:states} an alternative parametrization of the fugacities in terms of the parameters $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$.
+These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$. 
+We will also consider formulas for the local character in terms of these variables.
+
+%Note that for local operators which are the symmetric algebra of some graded vector space we can compute, as usual, the character as the plethystic exponential of a the single particle local character.
+%That is, the character of linear local operators.
+
 \subsection{A relationship to the superconformal index}
-
-We will turn to computing the local character for twists of the single membrane and fivebrane theories momentarily and comment on the relationship to known formulas in the physics literature. 
-First, we point out a general relationship between the local character as we've defined it and the superconformal index.
+\label{sec:sucaindex}
+There is a general relationship between the local character for the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetric theories and the more well-studied superconformal index.
 
 The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
-Explicitly, if the theory lives in a $d$-dimensional space time and $\cH$ denotes the Hilbert space on $S^{d-1}$, then the index is
+In our situation we look at the Hilbert space $\cH$ of the theory on $S^{5}$ and consider the index heuristically of the form
 \beqn
-\cI(q,x_1,\ldots,x_n) = \Tr_{\cH} (-1)^F q^{\delta} x_1^{G_1} \cdots x_n^{G_n} 
+\Tr_{\cH} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
 \eeqn
-where $\{G_i\}$ are a collection of charges that commute with a particular subset of elements of the superconformal algebra. 
-We can choose that each $G_i$ commute with a minimal supercharge $Q$ and its adjoint $Q^{\dagger}$ in the superconformal algebra.
-Necessarily the $G_i$ also commute with $\delta = [Q,Q^{\dagger}]$.
-After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{d-1} \times S^1$.
+where $\{G_i\}$ are a collection of charges that commute with the holomorphic supercharge $Q$ and its superconformal adjoint $S = Q^\dagger$. 
+Here, $\Delta = [Q,S]$.
+We choose three elements $G_1,G_2,G_3$ in such a way that they become the elements $h_1,h_2,h$ upon taking $Q$-cohomology (and so automatically commute with $Q$ and $S$). 
+Thus we consider the following index
+\beqn
+\cI (t_1,t_2,r,q) \define \Tr_{\cH} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
+\eeqn
+After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.
 
-The Witten index is protected under twisting---in our setup the index $\cI(q,x_1,\ldots,x_n)$ can be computed in the minimal twist of the superconformal theory we start with.
-Let us specialize to the case of the six-dimensional superconformal index. 
-In this case, we choose our fugacities to be $x_1 = t_1, x_2 = t_2$ and $x_3 = r$ as generators for the Cartan in the twisted superconformal algebra, see equation \eqref{eqn:cartan2}.
-
+The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
 The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
-Thus, the index $\cI(q,t_1,t_2,r)$ agrees with the holomorphic character $\chi(q,t_1,t_2,r)$.
+Thus, the index $\cI(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
 

### 2022-08-24 fivebranes/finite.tex
N=1
minor change
finite

@@
 \end{prop}
+testing
 
@@
 \beqn
-f_{1} (y_i,y,q) = \frac{qy + q^2y^{-1} - q^2(y_1+y_2+y_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
+\label{eqn:6done1}
+f_{1} (y_i,y,q) = \frac{qy + q^2y^{-1} - q^2(y^{-1}_1+y^{-1}_2+y^{-1}_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
 \eeqn
@@
 
+Define
+\beqn
+d(y_i,y,q) = (1-y_1 q)(1-y_2q)(1-y_3q) .
+\eeqn 
 For $k \geq 3$ let
+%\begin{align*}
+%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
+%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+%\end{align*}
 \begin{align*}
-f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
-& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi_k(q^{-1/2} y) \right. \\
+& \frac{\left.  - q^{3(k-1)/2} \chi_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
 \end{align*}
 
-%\begin{align*}
-%f_k (y_1,y_2,y_3,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi_k(q^{-1/2} y) \right. \\
-%& \left.  - q^{3(k-1)/2} \chi_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
-%\end{align*}
+To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory by 
+\beqn
+g_1 (y_i,y,q) = f_1(y_i,y,q)
+\eeqn
+where $f_1(y_i,y,q)$ is as in equation \eqref{eqn:6done1} and also denote by 
+\beqn
+g_2 (y_i,y,q) = f_2(y_i,y,q)
+\eeqn
+where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
+Thus $g_2$ is the single particle local character of $\clie_\bu(\cG_{2,c})$ and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.
 
@@
 \beqn
-\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=2}^N f_k(y_1,y_2,y_3,y,q)\right].
+\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=2}^N g_k(y_1,y_2,y_3,y,q)\right].
+\eeqn
+Similarly, the local character of the factorization algebra $\clie_\bu(\til{\cG}_{N,c})$ is 
+\beqn
+\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=1}^N g_k(y_1,y_2,y_3,y,q)\right].
 \eeqn
@@
 \end{conj}
+
+\begin{prop}
+One has
+\beqn
+\chi_{sugra}(y_i, y, q) = \lim_{N \to \infty} \til{\chi}_N(y_i,y,q)
+\eeqn
+\end{prop}
+
+\begin{proof}
+It suffices to show that at the level of single particle indices one has
+\beqn
+f_{sugra}(y_i, y, q) = \lim_{N \to \infty} f_N(y_i,y,q) ,
+\eeqn
+where $f_N = \sum_{k = 1}^N g_k$.
+
+We will use the following identity 
+\beqn
+\sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\lie{sl}(2)}(q^{-1/2}y) = \frac{1}{(1-q y)(1-q^2 y^{-1})} .
+\eeqn
+We will denote this expression by $S(y,q)$.
+
+From the form of $f_{sugra}$ and $g_k$, one can readily see that the result reduces to observing that
+\begin{multline}
+\left(q^4 (y_1+y_2+y_3) + 1 - q^6 - q^2 (y_1^{-1} + y_2^{-1} + y_3^{-1})\right)S(y,q) - 1 + q^3= \\
+\left(q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2) \right) S(y,q) .
+\end{multline}
+
+%\begin{itemize}
+%\item $q^4 \sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\lie{sl}(2)}(q^{-1/2} y)(y_1+y_2+y_3) = \frac{q^4(y_1+y_2+y_3)}{(1-q y)(1-q^2 y^{-1})}$. 
+%\end{itemize}
+
+\end{proof}
+
+As an immediate corollary we have the following result.
+\begin{cor}
+For any $N \geq 1$ one has
+\beqn
+\chi_{sugra}(y_i,y,q) = \til{\chi}_N(y_i,y,q) \mod q^{N+1} .
+\eeqn
+\end{cor}

### 2022-09-01 fivebranes/fact.tex
weights

@@
 
-In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting).
-For the case at hand, our expectation for universal can be understood as the theory on a large number of membranes and fivebranes. 
-We will see how this interpretation is supported by the supergravity index calculations presented in the last section.
+In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal fivebrane theory after performing the holomorphic twist.
+For the case at hand, our expectation for the universal theory can be understood as the worldvolume theory on a large number of fivebranes. 
+We will see how this relates to the description of the states in twisted supergravity as defined in the last section.
+Later, we see how our interpretation is supported by a relationship of the supergravity index to the fivebrane superconformal index.
 
@@
 The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
-Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}. \brian{surya add more?}
+Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}.
 
@@
 \]
-which computes the Lie algebra cohomology of $\cL(U)$. 
+which computes the Lie algebra cohomology of the $L_\infty$ algebra $\cL(U)$. 
 The differential on this cochain complex is precisely the Chevalley--Eilenberg differential associated to the~$L_\infty$ structure maps.
 
-At the quantum level the factorization algebra of classical observables is deformed.
+At the quantum level the factorization algebra of observables is deformed.
 Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
@@
 As a corollary of the proposition, we get a product decomposition 
-\[
+\beqn
+\label{eqn:Gdecomp}
 \cG_Z = \prod_{n \geq -1} \cG^{(n)} .
-\]
+\eeqn
 In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
 Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.
-
-We turn to explicitly describing the first few homogenous $\C^\times$-weights of~$\cG_Z$.
 
@@
 \]
-The Dolbeault forms are equipped with the natural $\dbar$ operator and the $\del$ operator which takes functions to one-forms.
+This Dolbeault complex is equipped with the natural $\dbar$ operator and the $\del$ operator which goes from $\Omega^{0,\bu}(Z)$ to $\Omega^{1,\bu}(Z)$.
 
@@
 
-\brian{make precise statement using $E(3|6)$.}
+The weight zero summand $\cG_Z^{(0)}$ is special because it carries the induced structure of a local $L_\infty$ algebra on $Z$ inherited from the $L_\infty$ algebra $\cL_{sugra}$.
+As a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
+We will prove the following.
 
-Particularly important for us will be the weight zero summand $\cG_Z^{(0)}$.
-Again, as a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
-Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
+\begin{prop}\label{prop:v0}
+As a $\Z/2$ graded local Lie algebra on $Z$, the weight zero summand~$\cG^{(0)}_Z$ is equivalent to $\cE(3|6)$. 
+\end{prop}
+
+%Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
 When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
@@
 
-The holomorphic vector bundle $\cV^{(0)}$ is 
+To see that $\cG^{(0)}$ and $\cE(3|6)$ are equivalent as super vector bundles we must show that
 \[
-\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\cV^{(0)} \simeq \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
 \]
@@
 
-The Lie bracket on $\cG_Z^{(0)}$ is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
-\begin{itemize}
-\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
-This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
-\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
-This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
-\item Finally, and most interestingly, there is a bracket of the form
-\[
-\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
-\]
-given in coordinates by
-\begin{multline}
-[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
-\end{multline}
-The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
-\end{itemize}
+The Lie bracket on $\cG_Z^{(0)}$ is defined from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ inherited from the $L_\infty$ algebra $\cL_{sugra}$. 
+In fact, there is only a two-ary bracket, and an immediate calculation shows that it agrees with the Lie bracket on $\cE(3|6)$.
+
+%\begin{rmk}
+%In \cite{KacClass} an embedding of super Lie algebras from $E(3|6)$ into $E(5|10)$ is constructed.
+%Recall that in the case $Z = \C^3$, the $\infty$-jets at $0 \in \C^3$ of the local Lie algebra $\cE(3|6)$ is precisely the exceptional super Lie algebra $E(3|6)$.
+%Similarly, the $\infty$-jets at $0 \in \C^3$ of the local $L_\infty$ algebra $\cG_{\C^3}$ is $\Hat{E(5|10)}$.
+%The embedding of local $L_\infty$ algebras on $Z$ from $\cE(3|6)$ into $\cG_Z$ that we just described agrees with the embedding of \cite{KacClass} upon taking $\infty$-jets.
+%(Note that the central term in $\Hat{E(5|10)}$ plays no role herem since it sits in $\C^\times$-weight $-1$.)
+%\end{rmk}
+
+%\begin{itemize}
+%\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
+%This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
+%\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
+%This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
+%\item Finally, and most interestingly, there is a bracket of the form
+%\[
+%\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
+%\]
+%given in coordinates by
+%\begin{multline}
+%[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
+%\end{multline}
+%The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
+%\end{itemize}
 
@@
 
-\brian{mention $E(3|6)$ module structure}
+We move on to give the following general description of the weight $j$ component $\cG^{(j)}$.
+Since we have already described $j = -1,0$ we focus on $j \geq 1$.
 
@@
 \beqn
+\label{eqn:Vj}
 \begin{tikzcd}
@@
 \begin{proof}
+As above, let $\C^2$ stand for the fundamental $\lie{sl}(2)$ representation and so the irreducible highest weight $j$ representation is $S^j(\C^2)$.
 
+The weight $j \geq 1$ complex of vector bundles $\cG^{(j)}$ is readily seen to be of the following form
+\beqn
+\begin{tikzcd}
+\ul{even} & \ul{odd} \\
+\Omega^{0,\bu}(Z , \T_Z \otimes K^{-j/2}_Z) \otimes S^j(\C^2) \ar[dr, "D_1"] \\ & \Omega^{0,\bu}(Z, K^{-j/2}_Z) \otimes S^j(\C^2) \\ 
+\Omega^{0,\bu}(Z , K^{-j/2}_Z) \otimes S^{j+1}(\C^2) \otimes \C^2 \ar[ur, "D_2"'] & \\
+& \Omega^{1,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^{j+1}(\C^2) \\ 
+\Omega^{0,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^{j+1}(\C^2) \ar[ur, "D_3"] \ar[dr, "D_4"'] \\
+& \Omega^{0,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^j(\C^2) \otimes \C^2 . 
+\end{tikzcd}
+\eeqn
+
+Here, as usual, the $\dbar$ operator is left implicit.
+Let us describe the differentials $D_1,D_2,D_3,D_4$.
+Recall that the five-fold $X = \text{Tot}(K_Z^{1/2} \otimes \C^2)$ is equipped with a non-vanishing holomorphic volume form. 
+The corresponding divergence operator $\div$ restricted to the weight $j$ subspace is $\div = D_1 + D_2$. 
+The differential $D_2$ is given by the identity on $\Omega^{0,\bu}(Z, K^{-j/2}_Z)$ tensored with the natural $\lie{sl}(2)$-equivariant projection
+\beqn
+S^{j+1}(\C^2) \otimes \C^2 \cong S^{j+2}(\C^2) \oplus S^{j}(\C^2) \twoheadrightarrow S^{j}(\C^2) .
+\eeqn
+
+The holomorphic de Rham operator on $X$ is $\del = D_3+D_4$. 
+The differential $D_4$ is the identity on $\Omega^{0,\bu}(Z, K^{-(j+1)/2}$ tensored with the natural $\lie{sl}(2)$-equivariant inclusion
+\beqn
+S^{j+1}(\C^2) \hookrightarrow S^{j-1}(\C^2) \oplus S^{j+1}(\C^2) \cong S^j(\C^2) \otimes \C^2 .
+\eeqn
+
+There is a spectral sequence whose first term is computed by the $D_2,D_4$ cohomology. 
+This term in the spectral sequence is isomorphic the complex $\Omega^{0,\bu}(Z, \cV^{(j)})$ where $\cV^{(j)}$ is as in equation \eqref{eqn:Vj}.
+There are no further terms in the spectral sequence, so the result follows. 
+\end{proof}
+
+One can write down an explicit quasi-isomorphism
+\beqn
+\Phi \colon \Omega^{0,\bu}(Z, \cV^{(j)}) \to \cG^{(j)} 
+\eeqn 
+as follows.
 \begin{itemize}
-\item Let $f(w) \in \C[w_1,w_2]_j$ be a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and suppose that $g(z) \del_{z_i}$ is a holomorphic vector field on $Z$. 
-Define the $\mu$-type field
+\item First we describe what the map looks like on the even summands.
+Locally a section of $\Omega^{0,\bu}(Z, S^j(\C^2) \otimes T_Z \otimes K^{-j/2}_Z)$ is of the form
 \beqn
-f(w) g(z) \del_{z_i} + \cdots
+f(w) \otimes g_i(z) \del_{z_i} 
 \eeqn
-\item Let $f(w) \in \C[w_1,w_2]_{j+2}$ be a homogenous degree $j+2$ polynomial and consider the one-form $\del f(w) = \del_{w_1} f(w)\d w_1 + \del_{w_2} f(w) \d w_2$.
-Using the holomorphic symplectic form we obtain the vector field
+where $f(w) \in \C[w_1,w_2]_j$ is a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and the $g_i(z)$'s are Dolbeault forms on $Z$.
+Define the divergence-free $\mu$-type field $\Phi(f(w) \otimes g_i(z) \del_{z_i})$ by the expression
 \beqn
-g(z) \left(\del_{w_1} f(w) \del_{w_2} - \del_{w_2} f(w) \del_{w_1}\right) .
+f(w) g(z) \del_{z_i} - \frac{1}{j+2} \left(\del_{z_i} g_i(z)\right) f(w) E_w
+\eeqn
+where $E_w = w_a \del_{w_a}$ is the Euler vector field in the direction transverse to the brane. 
+\item Locally a section of $\Omega^{0,\bu}(Z, S^{j+2} \otimes K^{-j/2}_Z)$ is of the form
+\beqn
+f(w) \otimes g(z)  
+\eeqn
+where $f(w) \in \C[w_1,w_2]_{j+2}$ is a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $Z$.
+Define the divergence-free $\mu$-type field $\Phi(f(w) \otimes g(z))$ by the expression
+\beqn
+g(z)(\del_{w_1} f (w) \del_{w_2} - \del_{w_2} f(w) \del_{w_1}) 
+\eeqn
+\item Next for the odd summands.
+Locally a section of $\Omega^{0,\bu}(Z, S^{j-1} \otimes K^{-(j+1)/2}_Z)$ is of the form
+\beqn
+f(w) \otimes g(z)  
+\eeqn
+where $f(w) \in \C[w_1,w_2]_{j-1}$ is a homogenous degree $j-1$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $Z$.
+Define the $\gamma$-field $\Phi(f(w) \otimes g(z))$ by the expression
+\beqn
+\frac12 g(z)f(w)(w_1 \d w_2 - w_2 \d w_1) .
+\eeqn
+\item
+Locally a section of $\Omega^{0,\bu}(Z, S^{j+1} \otimes T^*_Z \otimes K^{-(j+1)/2}_Z)$ is of the form
+\beqn
+f(w) \otimes g^i(z)  \d z_i
+\eeqn
+where $f(w) \in \C[w_1,w_2]_{j+1}$ is a homogenous degree $j+1$ polynomial in the variables $w_1,w_2$ and the $g^i(z)$'s are Dolbeault forms on $Z$.
+Define the $\gamma$-field $\Phi(f(w) \otimes g^i(z) \d z_i)$ by the expression
+\beqn
+f(w) g^i (z) \d z_i .
 \eeqn
 \end{itemize}
-\end{proof}
+
+The complex $\cG^{(j)}$ is manifestly a local module for the local Lie algebra $\cG^{(0)}$. 
+With the identification $\cG^{(0)} \simeq \cE(3|6)$ and $\cG^{(j)} \simeq \Omega^{0,\bu}(Z, \cV^{(j)})$ we can read off this module structure completely explicitly.
+
+Recall that as a complex of vector bundles $\cE(3|6) = \Omega^{0,\bu}(Z, \cV^{(0)}$ where 
+\beqn
+\cV^{(0)} 
+\eeqn
+
+\parsec[s:kacrelation]
+
+In the case $Z = \C^3$, the product decomposition of $\cG = \cG_{\C^3}$ in equation \eqref{eqn:Gdecomp} is closely related to a decomposition of the exceptional simple super Lie algebra $E(5|10)$ studied in \cite{KR2}.
+Here, the eleven-manifold bulk is just 
+\beqn
+\R \times {\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2) \simeq \R \times \C^5 .
+\eeqn
+
+In \S \ref{s:e510} we recalled the result from \cite{RSW} that the $\infty$-jets of $\cL_{sugra}$ at $0 \in \R \times \C^5$ is quasi-isomorphic to $\Hat{E(5|10)}$, a certain central extension of $E(5|10)$.
+It follows that the $\infty$-jets of the local Lie algebra $\cG$ at $0 \in \C^3$ is also quasi-isomorphic to $\Hat{E(5|10)}$.
+
+In \cite{KR2} the following weight decomposition of $E(5|10)$ is constructed.
+Denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in the five-fold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
+Assign the following weights to the super Lie algebra $E(5|10)$. 
+\begin{itemize} 
+\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
+\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
+\item the parity of an element carries an additional weight of $-1$. 
+Thus, for example, the odd element $[\d w_1 \d z_1] \in \Omega^{2,cl}(\Hat{D}^5)$ carries weight $+1 - 1 = 0$. 
+(If we think about the odd part as the space of closed two-forms then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.)
+\end{itemize} 
+The weight grading is concentrated in degrees $\geq -1$. 
+In particular, there is a decomposition of super vector spaces
+\beqn\label{eqn:decomp1}
+E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
+\eeqn
+with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
+It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$.
+
+At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
+In this way, we get a related decomposition of super $L_\infty$ algebras
+\beqn\label{eqn:decomp2}
+\Hat{E(5|10)} = \prod_{n \geq -1} V_n
+\eeqn
+We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
+Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
+Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
+
+The decomposition in equation \eqref{eqn:decomp2} has the property that $V_0$ is isomorphic to $E(3|6)$ as super Lie algebras.
+In particular, for each $n$, $V_n$ is a module for $V_0 = E(3|6)$.
+This is compatible with our description in proposition~\ref{prop:v0} where we showed that as local Lie algebras $\cG^{(0)} \simeq \cE(3|6)$. 
+Indeed, the $\infty$-jets of the local Lie algebra $\cE(3|6)$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$. 
+By the compatibility of our decomposition with \cite{KR2} we see that $V_n$ is quasi-isomorphic to the $\infty$-jets of $\cG^{(n)}$ at $0 \in \C^3$.
 
@@
 Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
-From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie,...}}
+From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie}}
 

### 2022-09-01 fivebranes/fact.tex
e36 action

@@
 \[
-\cV^{(0)} \simeq \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
+\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
 \]
@@
 
-Recall that as a complex of vector bundles $\cE(3|6) = \Omega^{0,\bu}(Z, \cV^{(0)}$ where 
+Recall that as a complex of vector bundles $\cE(3|6) = \Omega^{0,\bu}(Z, \cV^{(0)})$ where 
 \beqn
-\cV^{(0)} 
+\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right) .
 \eeqn
+The local Lie algebra structure on $\cE(3|6)$ arises from a Lie algebra structure on the sheaf of holomorphic sections of $\cV^{(0)}$.
+Likewise, the $\cE(3|6)$-module structure on $\cG^{(j)} \simeq \Omega^{0,\bu}(Z, \cV^{(j)})$ arises from a holomorphic $\cV^{(0)}$-module structure on the holomorphic sections of $\cV^{(j)}$. 
+By holomorphic, we mean that the structure maps are all holomorphic differential operators.
+
+We describe this $\cV^{(0)}$-module structure on $\cV^{(j)}$ explicitly.
+Holomorphic sections of $\T_Z$ will act by Lie derivative on $\cV^{(j)}$.
+Holomorphic $\sl(2)$-valued functions will also act in the natural way since each component of $\cV^{(j)}$ is labeled by an irreducible $\lie{sl}(2)$ representation.
+
+Finally, we need to explain how holomorphic sections of the odd component $\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2$ of $\cV^{(0)}$ act.
+We first give a global description of this action, and then we will write down the explicit formula in local coordinates.
+For the local coordinate description recall that a general section of $\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2$ has the form $w_a g^i(z) \d z_i$ where $g^i(z)$ is a holomorphic function. 
+\begin{itemize}
+\item The odd part of $\cV^{(0)}$ acts on the component $S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z$ through the composition
+\beqn
+\begin{tikzcd}
+\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j-1}(\C^2) \oplus S^{j+1}(\C^2)\right) \otimes \left(\T_Z \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z\right) \ar[dl] \ar[d] \\
+S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z & S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z 
+\end{tikzcd}
+\eeqn
+Here, the leftmost downward arrow is the evident $\lie{sl}(2)$ projection together with the canonical pairing between sections of $\T_Z$ and $\T^*_Z$.
+The rightmost downward arrow is the other $\lie{sl}(2)$ projection together with the Lie derivative of holomorphic one-forms.  
+Given a local section $f(w) \otimes h_i(z) \del_{z_i}$ of $S^j(\C^2) \otimes \T_Z \otimes K_Z^{-j/2}$ an explicit formula for this action is
+\begin{align*}
+(w_a g^i(z) \d z_i) \cdot (f(w) \otimes h_k(z) \del_{z_k}) & = \ep_{ab} (\del_{w_b} f(w)) (g^i h_i)(z)  \\ & + w_a f(w) L_{h_k \del_{z_k}} (g^i \d z_i) .
+\end{align*}
+\item The odd part of $\cV^{(0)}$ acts on the component $S^{j+2}(\C^2) \otimes K^{-j/2}_Z$ through the composition
+\beqn
+\begin{tikzcd}
+\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j+2}(\C^2) \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j+1}(\C^2) \oplus S^{j+3}(\C^2)\right) \otimes \left(\T^*_Z \otimes K^{-(j+1)/2}_Z\right) \ar[d] \\
+& S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z
+\end{tikzcd}
+\eeqn
+where the downward arrow is induced by the evident $\lie{sl}(2)$ projection.
+\item The odd part of $\cV^{(0)}$ acts on the component $S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z$ through the composition
+\beqn
+\begin{tikzcd}
+\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j-1}(\C^2) \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j-2}(\C^2) \oplus S^{j}(\C^2)\right) \otimes \left(\T^*_Z \otimes K^{-1}_Z K^{-j/2}_Z\right) \ar[d] \\
+& S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z
+\end{tikzcd}
+\eeqn
+where the downward arrow is induced by the evident $\lie{sl}(2)$ projection together with the holomorphic de Rham operator taking holomorphic one-forms to holomorphic two-forms. 
+\item Finally, the odd part of $\cV^{(0)}$ acts on the component $S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z$ through the composition
+\beqn
+\begin{tikzcd}
+\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j}(\C^2) \oplus S^{j+2}(\C^2)\right) \otimes \left(\T^*_Z \otimes \T^*_Z \otimes K^{-1}_Z K^{-j/2}_Z\right) \ar[dl] \ar[d] \\
+S^j (\C^2) \otimes \T_Z \otimes K_Z^{-j/2} & S^{j+2}(\C^2)  \otimes K^{-j/2}_Z
+\end{tikzcd}
+\eeqn
+where the leftmost downward arrow is induced by the evident $\lie{sl}(2)$ projection.
+The rightmost downward arrow is induced by the remaining $\lie{sl}(2)$ projection together with the holomorphic de Rham operator taking holomorphic two-forms to holomorphic three-forms.
+\end{itemize}
 

### 2022-09-01 fivebranes/fact.tex
merge

@@
 In particular, for each $n$, $V_n$ is a module for $V_0 = E(3|6)$.
+In fact, each $V_n$ is an irreducible $E(3|6)$-module \cite{KR2}.
+
 This is compatible with our description in proposition~\ref{prop:v0} where we showed that as local Lie algebras $\cG^{(0)} \simeq \cE(3|6)$. 
 Indeed, the $\infty$-jets of the local Lie algebra $\cE(3|6)$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$. 
-By the compatibility of our decomposition with \cite{KR2} we see that $V_n$ is quasi-isomorphic to the $\infty$-jets of $\cG^{(n)}$ at $0 \in \C^3$.
+By the compatibility of our decomposition with \cite{KR2} we see that $V_n$ is quasi-isomorphic to the $\infty$-jets of $\cG^{(n)}$ at $0 \in \C^3$ as a module for $E(3|6)$.
 
@@
 \beqn\label{eqn:limit2}
-\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{2,c}) \leftarrow \cdots .
+\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{3,c}) \leftarrow \cdots .
 \eeqn 

### 2022-09-01 fivebranes/finite.tex
merge

@@
 In this section we begin to provide some evidence for this description at the level of local operators, which is just a small piece of the factorization algebra.
+As we reviewed just in the previous section, the space of local operators is what categorifies the specific superconformal index that we study in this paper.
+%The structure of a three-dimensional holomorphic factorization algebra induces algebraic operations on the algebra of local operators
 
@@
 Our conjecture is that the factorization algebra associated to a stack of $N$ holomorphically twisted fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{N,c})$, where $\cG_{N,c}$ denotes the cosheaf of compactly supported sections.
-The main goal of this section is to extract the algebra of local operators from this factorization algebra and to then deduce explicit formulas for local characters.
+The main goal of this section is to extract the algebra of local operators from this factorization algebra and to then deduce explicit formulas for the local character, and hence the superconformal index.
 
@@
 
-We deduce the character of the holomorphic twist of the theory on a single fivebrane and will find an exact match with the index of the six-dimensional superconformal theory for the abelian Lie algebra $\lie{gl}(1)$.
+We deduce the character of the holomorphic twist of the theory on a single fivebrane and will find an exact match with the index of the six-dimensional superconformal theory associated to the abelian Lie algebra $\lie{gl}(1)$.
 By the proposition \ref{prop:factabelian} we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
@@
 \Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
-\Pi \Omega^0(\Hat{D}^3, K^{1/2} \otimes \C^2) . 
+\Pi \Omega^0(\Hat{D}^3, K^{1/2}_{\Hat{D}^3}\otimes \C^2) . 
 \end{tikzcd} 
@@
 \[
-- q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
+- q^2 \frac{\chi^{\lie{sl}(3)}_{[0,1]}(t_1,t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = - q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
+where $\chi^{\lie{sl}(3)}_{[1,0]}(t_1,t_2)$ is the $\lie{sl}(3)$ character of highest weight $[1,0]$.
 \item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
@@
 \[
-q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
+q^{3/2} \frac{\chi_{1}^{\lie{sl}(2)} (r)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
 \]
+where $\chi_{1}^{\lie{sl}(2)} (r)$ is the $\lie{sl}(2)$ character of highest weight one.
 \end{itemize}
@@
 \end{prop}
-testing
 
@@
 
-We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$.
+We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$ using Lemma~\ref{lem:envelope}.
+For simplicity we will use the fugacities $y_i, y, q$.
 
@@
 \[
-q^3 \frac{y_1 q + y_2 q + y_3 q }{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
+q^4 \frac{\chi^{\lie{sl}(3)}_{[1,0]}(y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = q^4 \frac{y_1 + y_2 + y_3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
 \]
@@
 \[
-\frac{q^2 y^2 + q^3 + q^4 y^{-2}}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
+q^3 \frac{\chi_2^{\lie{sl}(2)} (q^{-1/2}y)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = \frac{q^2 y^2 + q^3 + q^4 y^{-2}}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
 \]
@@
 \[
-q^{3}\frac{(y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
+q^{7/2}\frac{\chi^{\lie{sl}(2)}_{1}(q^{-1/2} y) \, \chi_{[0,1]}^{\lie{sl}(3)} (y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)} = q^{3}\frac{(y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}
 \]
@@
 
-\brian{add some better transition} 
-Based on our discussion above we are led to the following conjecture.
+Recall that our conjecture for the factorization algebra associated to the holomorphic twist of the six-dimensional worldvolume theory associated to a stack of two fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{2,c})$.
+We can now state a decategorified version of conjecture \ref{conj:fact} at the level of superconformal indices, or local characters.
+
 \begin{conj}\label{conj:6dtwo}
-The character of local operators of the holomorphic twist of the theory on a stack of two fivebranes is given by the following plethystic exponential
+The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ is given by
 \[
-\chi_{2} (t_1,t_2,r,q) = {\rm PExp} \left[f_2(t_1,t_2,r,q) \right] .
+\chi_{2} (y_i,y,q) = {\rm PExp} \left[f_2(y_i,y,q) \right] .
 \]
-where the single particle index is as in \eqref{eqn:6dtwo}.
+where $f_2(y_i,y,q)$ is as in \eqref{eqn:6dtwo}.
 \end{conj}
 
-Following the general relationship between characters of holomorphic twists of supersymmetric theories and supersymmetric indices, this our conjecture for the supersymmetric index of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(2)$.
 Similarly, the index associated to the $\lie{gl}(2)$ theory is conjectured to be simply the product 
@@
 where the character $\chi_{1}$ for the $\lie{gl}(1)$ theory is given in the previous section.
-As a factorization algebra \brian{finish}
 
@@
 
-Define
+Before exhibiting the general formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ on $\C^3$ we set up some notation. 
+As above, we let $\chi_k^{\lie{sl}(2)}$ and $\chi^{\lie{sl}(3)}_{[k,l]}$ denote the highest weight $\lie{sl}(2)$ and $\lie{sl}(3)$ characters. 
+We also define the following expression which appears in the denominator in all of our characters
 \beqn
@@
 \eeqn 
-For $k \geq 3$ let
-%\begin{align*}
-%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
-%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
-%\end{align*}
-\begin{align*}
-g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi_k(q^{-1/2} y) \right. \\
-& \frac{\left.  - q^{3(k-1)/2} \chi_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
-\end{align*}
-
-To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory by 
+To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory $\Obs_1$ by 
 \beqn
@@
 where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
-Thus $g_2$ is the single particle local character of $\clie_\bu(\cG_{2,c})$ and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.
+Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c})$.
+Finally, for $k \geq 3$ let
+%\begin{align*}
+%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
+%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+%\end{align*}
+\begin{align*}
+g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
+& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
+\end{align*}
+%and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.
 
@@
 \label{thm:finite}
-The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ on $Z=\C^3$ is 
+The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ is
 \beqn
@@
 \end{thm}
+\begin{proof}
+By Lemma~\ref{lem:envelope} the character of $\clie_\bu (\cG_{N,c})$ is given by 
+\beqn
+\chi_N = \text{PExp} \left[f_N\right]
+\eeqn
+where $f_N$ is the single particle local character.
+Thus, it suffices to show that $f_N = \sum_{k = 2}^N g_k$.
+Recall that we have the following filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$ given by 
+\beqn
+\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \clie_\bu (\cG_{N,c}) .
+\eeqn
+Thus we have the following expression for the associated graded factorization algebra 
+\beqn
+\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=2}^N \clie_\bu(\cG^{(k)}.
+\eeqn
+
+Thus, it suffices to show that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG_{k,c})$, which is a direct computation.
+\end{proof}
 
@@
 \end{conj}
+
+It follows from the fact that limit of the diagram in \ref{eqn:limit1} is $(\Bar{\pi}_* \Obs_{sugra})^!
+\simeq \clie_\bu(\cG_c)$ that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in Proposition~\ref{prop:sugraindex1}.
+Alternatively, we have the following direct proof of this fact.
 
@@
 
-From the form of $f_{sugra}$ and $g_k$, one can readily see that the result reduces to observing that
+Using this identity one can directly see that the result reduces to observing that
 \begin{multline}

### 2022-09-01 fivebranes/ops.tex
merge

@@
 We also assume that the operator $Q^{hol}$ is translation invariant.
-
-Given a vector bundle $E \to M$, the bundle of $\infty$-jets $J^\infty E \to M$ is a $\infty$-dimensional pro vector bundle whose fiber over a point $p \in M$ is 
-If $M = \R^d$ and $E$ is translation invariant, then the bundle of $\infty$-jets can be identified with $E_0 \times \C[[x_i]]$ where
 
@@
 These parameters are related by $y_1=t_1^{-1}, y_2 = t_1 t_2^{-1}, y_3 = t_2$ and $y = q^{1/2} r$. 
-We will also consider formulas for the local character in terms of these variables.
+We will also consider formulas for the local character $\chi(y_i,y,q)$ in terms of these variables.
 
@@
 \label{sec:sucaindex}
-There is a general relationship between the local character for the holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetric theories and the more well-studied superconformal index.
+The local character for the holomorphic twist of a six-dimensional $\cN=(2,0)$ supersymmetric theory agrees with the well-known superconformal index.
+Generally, in any dimension, the superconformal index counts states $\cH^Q$ which are annihilated by a particular supercharge~$Q$.
+The index is defined as a function on the Cartan of a commuting subalgebra with respect to $Q$.
+For six-dimensional superconformal theories, a natural choice of a supercharge is the holomorphic twisting supercharge. 
+Then the index is sensitive to the so-called $\tfrac{1}{16}$-BPS states.
 
-The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
-In our situation we look at the Hilbert space $\cH$ of the theory on $S^{5}$ and consider the index heuristically of the form
+Recall that the odd part of the $\cN=(2,0)$ supersymmetry algebra is $S_+ \otimes R$ where $S_+$ is the positive irreducible spin representation of $\lie{so}(6)$ and $R \cong \C^4$.
+Square-zero supercharges $Q \in S_+ \otimes R$ are stratified by the rank of the corresponding map $R \to (S_+)^* \cong S_-$.
+A holomorphic supercharge $Q$ has rank one (such elements automatically square to zero). 
+Thus, the superconformal index counts precisely the states in the holomorphic twist.
+In the terminology above these states comprise the algebra of local operators $\cH^Q = \Obs(0)$ in the holomorphic twist of the six-dimensional $\cN=(2,0)$ theory.
+
+The six-dimensional superconformal algebra (before twisting) is~$\lie{osp}(8|4)$.
+The Cartan of the Lie super algebra is six-dimensional generated by elements
+\[
+H, J_1,J_2,J_3,R_1,R_2 .
+\]
+The holomorphic twisting supercharge $Q \in \lie{osp}(8|4)$ and the (super) commuting subalgebra is $\lie{osp}(6|2)$ together with the element 
+\[
+\Delta \define [Q,Q^\dagger] = H - (J_1 + J_2 + J_3) - 2 (R_1 + R_2) 
+\]
+where $Q^\dagger$ denotes the superconformal partner to the supercharge $Q$. 
+The superconformal index counts states which saturate the BPS bound $\Delta \geq 0$ as a representation for the subalgebra $\lie{osp}(6|2)$. 
+To fit with the notation used in this paper, the superconformal index can be written as
 \beqn
-\Tr_{\cH} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
+\cI(y_i,y,q) = \Tr_{\cH^Q} (-1)^F q^{H + \frac13 (J_1+J_2+J_3)} y_1^{J_1} y_2^{J_2} y_3^{J_3} y^{R_1 - R_2} .
 \eeqn
-where $\{G_i\}$ are a collection of charges that commute with the holomorphic supercharge $Q$ and its superconformal adjoint $S = Q^\dagger$. 
-Here, $\Delta = [Q,S]$.
-We choose three elements $G_1,G_2,G_3$ in such a way that they become the elements $h_1,h_2,h$ upon taking $Q$-cohomology (and so automatically commute with $Q$ and $S$). 
-Thus we consider the following index
-\beqn
-\cI (t_1,t_2,r,q) \define \Tr_{\cH} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
-\eeqn
-After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.
+This agrees precisely with the local character $\chi(y_i,y,q)$ with the evident change of coordinates for the Cartan of $\lie{osp}(6|2)$.
 
-The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
-The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
-Thus, the index $\cI(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
+%The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
+%The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
+%Thus, the index $\cI(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
+
+%The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
+%In our situation we look at the Hilbert space $\cH$ of the theory on $S^{5}$ and consider the index heuristically of the form
+%\beqn
+%\Tr_{\cH} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
+%\eeqn
+%where $\{G_i\}$ are a collection of charges that commute with the holomorphic supercharge $Q$ and its superconformal adjoint $S = Q^\dagger$. 
+%Here, $\Delta = [Q,S]$.
+%We choose three elements $G_1,G_2,G_3$ in such a way that they become the elements $h_1,h_2,h$ upon taking $Q$-cohomology (and so automatically commute with $Q$ and $S$). 
+%Thus we consider the following index
+%\beqn
+%\cI (t_1,t_2,r,q) \define \Tr_{\cH} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
+%\eeqn
+%After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.
 

### 2022-09-01 fivebranes/finite.tex
specialize

@@
 
-\subsection{Finite $N$ index}
+\subsection{A closed formula for the finite $N$ index}
 
@@
 \beqn
-g_1 (y_i,y,q) = f_1(y_i,y,q)
+g_{-1} (y_i,y,q) = f_1(y_i,y,q)
 \eeqn
@@
 \beqn
-g_2 (y_i,y,q) = f_2(y_i,y,q)
+g_0 (y_i,y,q) = f_2(y_i,y,q)
 \eeqn
 where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
-Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c})$.
-Finally, for $k \geq 3$ let
+Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c}) = \clie_{\bu}(\cG_c^{(0)})$.
+Finally, for $k \geq 1$ let
 %\begin{align*}
@@
 %\end{align*}
+%\begin{align*}
+%g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
+%& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
+%\end{align*}
 \begin{align*}
-g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
-& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
+g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
+& \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
 \end{align*}
@@
 \label{thm:finite}
+Let $N \geq 3$. 
 The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ is
 \beqn
-\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=2}^N g_k(y_1,y_2,y_3,y,q)\right].
+\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
 \eeqn
@@
 \beqn
-\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=1}^N g_k(y_1,y_2,y_3,y,q)\right].
+\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=-1}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
 \eeqn
@@
 where $f_N$ is the single particle local character.
-Thus, it suffices to show that $f_N = \sum_{k = 2}^N g_k$.
+Thus, it suffices to show that $f_N = \sum_{k = 0}^{N-2} g_k$.
 Recall that we have the following filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$ given by 
 \beqn
-\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \clie_\bu (\cG_{N,c}) .
+\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \leftarrow \clie_\bu (\cG_{N,c}) .
 \eeqn
@@
 \beqn
-\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=2}^N \clie_\bu(\cG^{(k)}.
+\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=0}^N \clie_\bu(\cG^{(k)}).
 \eeqn
 
-Thus, it suffices to show that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG_{k,c})$, which is a direct computation.
+Thus, we must see that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG^{(k)}_c)$, which is a direct observation using the description of $\cG^{(k)}$ we have given in Proposition \ref{prop:Vj}.
 \end{proof}
@@
 \end{conj}
+
+\parsec
 
@@
 \beqn
-f_{sugra}(y_i, y, q) = \lim_{N \to \infty} f_N(y_i,y,q) ,
+f_{sugra}(y_i, y, q) = \lim_{N \to \infty} \til{f}_N(y_i,y,q) ,
 \eeqn
-where $f_N = \sum_{k = 1}^N g_k$.
+where $\til{f}_N = \sum_{k = -1}^{N-2} g_k$.
 
@@
 \end{cor}
+\begin{proof}
+This follows from observing that at the level of single particle states $f_N$ is of order $q^{N}$.
+\end{proof}
+
+\parsec
+
+We can also apply the specialization $y=1, y_3=1$ to $\chi_N$.
+\begin{prop}
+Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$) one has the following single particle index
+\beqn
+f_N (y_1,y_2, y_3=1,y=1,q) = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
+\eeqn
+\end{prop}
+\begin{proof}
+By induction it suffices to show that the specialization of the single particle local character $g_k$ of the factorization algebra $\clie_\bu(\cG^{(k)})$ is $q^{k+2} / (1-q)$. 
+We have already seen this in the case $k=-1,0$, so it suffices to show this when $k \geq 1$.
+
+First observe that the denominator becomes
+\beqn
+d(y_1,y_2,y_3=1,y=1,q) = (1-y_1 q)(1-y_2q) (1-q) .
+\eeqn
+
+Next, we observe that the numerator of $g_k (y_1,y_2,y_3=1,y=1,q)$ can be factored as
+\begin{align*}
+q^{3 + 3k/2} \left(q^{-(k+2)/2} + q^{-(k-2)/2} - q^{-k/2} (y_1+y_2) \right) 
+& = q^{k+2} (1 + q^2 - q (y_1 + y_2)) \\
+& = q^{k+2} (1 - y_1 q) (1-y_2 q) 
+\end{align*}
+where in the last line we have used $y_1 y_2 = 1$.
+The result follows.
+\end{proof}

### 2022-09-02 fivebranes/fact.tex
changed conventions

@@
 \begin{prop}
+\label{prop:Vj}
 Let $j \geq 1$. 
@@
 This factorization algebra is of the form 
-\[
+\beqn
+\label{eqn:factgrad}
 \Bar{\pi}_*\Obs_{sugra} = \clie^\bu(\cG)
-\]
+\eeqn
 where $\cG = \cG_Z$ is a sheaf of $L_\infty$ algebras on the worldvolume~$Z$ of the fivebrane.
@@
 \[
-\cG = \oplus_{j \geq -1} \cG^{(j)} .
+\cG = \prod_{k \geq -1} \cG^{(k)} .
 \]
-The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
-This sequence of ideals induces a limit diagram of vector bundles
-\beqn\label{eqn:lim}
-0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
+There is a related local $L_\infty$ algebra 
+\beqn
+\til \cG \define \prod_{k \geq 0} \cG^{(k)}
 \eeqn
-where $0$ is the zero vector bundle.
-For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
+where we simply forget the weight $-1$ component.
 
-Define 
+This weight grading on $\cG$ induces a filtration on the factorization algebra \eqref{eqn:factgrad} and on its $!$-dual $\clie_\bu (\cG_{c})$. 
+For $k \geq -1$ define
 \beqn
-\cG_1 \define \cG / \cG^{(\geq 0)} 
+\cG^{(\geq k)} = \prod_{j \geq k} \cG^{(j)}  .
 \eeqn
-and for $N > 1$
+Notice that $\cG^{(\geq -1)} = \cG$.
+For $N \geq 1$ define the local $L_\infty$ algebra
 \beqn
-\til \cG_N \define \cG / \cG^{(\geq N-1)} , \quad \cG_N \define \cG^{\geq 0} / \cG^{(\geq N-1)} .
+\cG_N \define \cG / \cG^{(\geq N-1)} .
 \eeqn
-Each of $\cG_1, \cG_{N}, \til \cG_N$ has the induced structure of a local $L_\infty$ algebra on the worldvolume.
-Notice that as factorization algebras of graded vector spaces one has
-\[
-\til \cG_N = \cG_N \otimes \cG_1
-\]
-for $N > 1$.
+Similarly, for $N \geq 2$ define
+\beqn
+\til \cG_N \define \til \cG / \cG^{(N-1)} .
+\eeqn
+We have chosen a convenient chose of indexing for the constructions below.
 
-The limit diagram \eqref{eqn:lim} induces a diagram of factorization algebras
-\beqn\label{eqn:colim}
-\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
+%The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
+%This sequence of ideals induces a limit diagram of vector bundles
+%\beqn\label{eqn:lim}
+%0 = \cG / \cG^{(\geq -1)} \leftarrow \cG / \cG^{(\geq 0)} \leftarrow \cG / \cG^{(\geq 1)} \leftarrow \cdots ,
+%\eeqn
+%where $0$ is the zero vector bundle.
+%For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
+The resulting filtration of the $!$-dual
+\beqn
+\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c})
 \eeqn 
-whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
-Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set. 
-Applying~$!$-duals we obtain a sequence
-\beqn\label{eqn:limit1}
-\ul\C \leftarrow \clie_\bu(\cG_{1,c}) \leftarrow \clie_\bu (\til \cG_{2,c}) \leftarrow \cdots ,
+of the factorization algebra \eqref{eqn:factgrad} is of the form
+\beqn\label{eqn:fil1}
+\clie_\bu (\cG_{1,c}) \subset \clie_\bu (\cG_{2,c}) \subset \cdots \subset \clie_\bu(\cG_c) .
 \eeqn
-whose limit is $\clie_\bu(\cG_c) = (\Bar{\pi}_* \Obs_{sugra})^!$. 
-We also point out that there is a similar diagram of the form
-\beqn\label{eqn:limit2}
-\clie_\bu (\cG_{2,c}) \leftarrow \clie_\bu (\cG_{3,c}) \leftarrow \cdots .
+Similarly, there is a filtration on the factorization algebra $\clie_\bu (\til \cG_c)$ of the form
+\beqn
+\label{eqn:fil2}
+\clie_\bu(\til \cG_{2,c}) \subset \clie_\bu(\til \cG_{3,c}) \subset \cdots \subset \clie_\bu(\til \cG_c).
 \eeqn
-whose limit is the universal factorization algebra of classical observables on the fivebrane 
-\[
-(\Bar{\pi}_* \Obs_{sugra})^! = \clie_\bu(\cG_{Z,c}) .
-\]
+%Explicitly, the underlying super vector space of the weight $k$ component $\clie_\bu(\cG_{c})^{(k)}$ is 
+%\beqn
+%\bigoplus_{m \geq 0} \bigoplus_{\sum_{i=1}^m j_i = k} \left(\cG_c^{(j_1)} \otimes \cdots \otimes \cG_{c}^{(j_m)}\right)_{\Sigma_m} 
+%\eeqn
+%where we take coinvariants for the symmetric group $\Sigma_m$.
+%Similarly, the factorization algebra $\clie_\bu(\til \cG_c) = \oplus_{k \geq 0} \clie_\bu(\til \cG_c)^{(k)}$ is graded.
 
-The first nonzero term in this limit diagram \eqref{eqn:limit1} is 
+%Define 
+%\beqn
+%\cG_1 \define \cG / \cG^{(\geq 0)} 
+%\eeqn
+%and for $N > 1$
+%\beqn
+%\til \cG_N \define \cG / \cG^{(\geq N-1)} , \quad \cG_N \define \cG^{\geq 0} / \cG^{(\geq N-1)} .
+%\eeqn
+%Each of $\cG_1, \cG_{N}, \til \cG_N$ has the induced structure of a local $L_\infty$ algebra on the worldvolume.
+%Notice that as factorization algebras of graded vector spaces one has
+%\[
+%\til \cG_N = \cG_N \otimes \cG_1
+%\]
+%for $N > 1$.
+
+%\beqn\label{eqn:colim}
+%\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
+%\eeqn
+%whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
+%Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set.
+
+The first term in the filtration \eqref{eqn:fil1} is 
 \[
@@
 \]
-where $\cG_1$ is the abelian local Lie algebra $\cG_{1} = \cG / \cG^{(\geq 0)} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$. 
+where $\cG_1$ is the abelian local Lie algebra $\cG_{1} \cong \cG^{(-1)}$---this is just the weight $(-1)$ piece of the decomposition of $\cG$. 
 In \cite{SWtensor}, Saberi and the second author have given an explicit description of the holomorphic twist of the worldvolume theory on a single fivebrane, that is, the six-dimensional superconformal theory associated to the abelian Lie algebra~$\lie{gl}(1)$.
@@
 
-We now formulate a general conjecture about the worldvolume theory on a stack of holomorphically twisted fivebranes.
-Recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
-In this form of the conjecture we focus only on the six-dimensional superconformal theories associated to Lie algebras of type $A$.
+We now formulate a conjecture about the worldvolume theory on a stack of holomorphically twisted fivebranes.
+Evidence for this conjecture will be given in the remaining parts of this paper.
+In this conjecrture, we recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
 
@@
 \label{conj:fact}
-For $N > 1$, let $\Obs_N$ be the factorization algebra on $Z$ of classical observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$.
-Then, there is an equivalence of factorization algebras on~$Z$:
+For $N \geq 1$, let $\Obs_{N}$ be the factorization algebra of classical observables of the holomorphic twist of the worldvolume theory on a stack of $N$ fivebranes. 
+Then, there is an equivalence of factorization algebras
 \beqn
-\Obs_{N} \simeq \clie_\bu(\cG_{N,c}) .
+\Obs_N \simeq \clie_\bu(\cG_{N,c}) .
 \eeqn
+
+Similarly, for $N > 1$, let $\til \Obs_N$ be the factorization algebra of classical observables of the holomorphic twist of the worldvolume theory on a stack of $N$ fivebranes with the center of mass degrees of freedom removed.
+Then, there is an equivalence of factorization algebras
+\beqn
+\til\Obs_N \simeq \clie_\bu(\til \cG_{N,c}) .
+\eeqn
+In the language of superconformal $\cN=(2,0)$ theories our conjecture is that $\clie_\bu(\til \cG_{N,c})$ is the factorization algebra of classical observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$.
 \end{conj}

### 2022-09-02 fivebranes/finite.tex
changed conventions

@@
 
-In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a tower of factorization algebras 
+In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a filtration of the factorization algebra $\clie_\bu(\cG_c)$. 
 \[
-\clie_{\bu}(\cG_{1,c}) \leftarrow \clie_{\bu}(\til \cG_{2,c}) \leftarrow \cdots .
+\clie_{\bu}(\cG_{1,c}) \subset \clie_{\bu}(\cG_{2,c}) \subset \cdots .
 \]
-We now turn to the factorization algebra $\clie_{\bu}(\til \cG_{2,c})$.
+We now turn to the factorization algebra $\clie_{\bu}(\cG_{2,c})$.
 
-Recall that $\til \cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\til \cG_{2} = \cG / \cG^{\geq 1}$. 
+Recall that $\cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\cG_{2} = \cG / \cG^{\geq 1}$. 
 Since $\cG$ is concentrated in weights $\geq -1$ we see that $\til \cG_{2}$ is of the form
 \[
-\til \cG_2 = \cG_2 \ltimes \cG_1 
+\cG_2 = \til \cG_2 \ltimes \cG_1 
 \]
-where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
-We focus mostly on the factorization algebra $\clie_\bu(\cG_{2,c})$.
+where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\til \cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
+We focus mostly on the factorization algebra $\clie_\bu(\til \cG_{2,c})$.
 
-We have already characterized the local dg Lie algebra $\cG_{2}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
-We deduce that $\cG_2$ can be given a $\Z \times \Z/2$ grading where, as usual, we refer to $\Z$ as the cohomological grading and $\Z/2$ as the parity. 
-With this lift to a $\Z \times \Z/2$ grading, the even part of $\cG_2$ is
+We have already characterized the local dg Lie algebra $\til \cG_{2} = \cG^{(0)}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
+We have also shown that $\cG^{(0)}$ is equivalent to the local Lie algebra $\cE(3|6)$. 
+The even part of $\cE(3|6)$ is
 \[
@@
 with its natural cohomological grading by Dolbeault form type. 
-The odd part of $\cG_2$ is
+The odd part of $\cE(3|6)$ is
 \[
@@
 
-On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
-Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+%On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
+%Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
 
@@
 \begin{prop} \label{prop:6dtwo}
-The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the plethystic exponential of the following expression
+The character of local operators of the factorization algebra $\clie_\bu(\til \cG_{2,c})$ on $\C^3$ is given by the plethystic exponential of the following expression
 \beqn\label{eqn:6dtwo}
-f_{2} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
+\til f_{2} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
 \eeqn
@@
 
-Recall that our conjecture for the factorization algebra associated to the holomorphic twist of the six-dimensional worldvolume theory associated to a stack of two fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{2,c})$.
+Recall that our conjecture for the factorization algebra associated to the holomorphic twist of the six-dimensional worldvolume theory associated to a stack of two fivebranes is $\Obs_2 \simeq \clie_\bu(\cG_{2,c}) \cong \clie_\bu(\cG_{1,c}) \otimes \clie_\bu(\til \cG_{2,c})$.
+And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.
 We can now state a decategorified version of conjecture \ref{conj:fact} at the level of superconformal indices, or local characters.
@@
 \[
-\chi_{2} (y_i,y,q) = {\rm PExp} \left[f_2(y_i,y,q) \right] .
+\til \chi_{2} (y_i,y,q) = {\rm PExp} \left[\til f_2(y_i,y,q) \right] .
 \]
-where $f_2(y_i,y,q)$ is as in \eqref{eqn:6dtwo}.
+where $\til f_2(y_i,y,q)$ is as in \eqref{eqn:6dtwo}.
 \end{conj}
 
-Similarly, the index associated to the $\lie{gl}(2)$ theory is conjectured to be simply the product 
+Similarly, the index associated to the $\lie{gl}(2)$ theory, which is the local character of $\clie_\bu(\cG_{2,c})$, is conjectured to be simply the product 
 \[
-\til \chi_{2} (y_i,y,q) = \chi_{2} (y_i,y,q) \cdot \chi_{1}(y_i,y,q)
+\chi_{2} (y_i,y,q) = \chi_{2} (y_i,y,q) \cdot \chi_{1}(y_i,y,q)
 \]
-where the character $\chi_{1}$ for the $\lie{gl}(1)$ theory is given in the previous section.
+where the character $\chi_{1}$ for the $\lie{gl}(1)$ theory is given in proposition~\ref{prop:6done}
+Equivalently, $\chi_2$ is the plethystic exponential of $f_2 = f_1 + \til f_2$.
 
@@
 \[
-f_{2}(y_1, y_2, y_3=1, y=1, q) = \frac{q^2}{1-q} 
+\til f_{2}(y_1, y_2, y_3=1, y=1, q) = \frac{q^2}{1-q} 
 \]
@@
 \beqn
-g_0 (y_i,y,q) = f_2(y_i,y,q)
+g_0 (y_i,y,q) = \til f_2(y_i,y,q)
 \eeqn
-where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
-Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c}) = \clie_{\bu}(\cG_c^{(0)})$.
+where $\til f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
+Thus $g_2$ is the single particle local character of $\clie_\bu(\til \cG_{2,c}) = \clie_{\bu}(\cG_c^{(0)})$.
 Finally, for $k \geq 1$ let
@@
 \beqn
-\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
+\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=-1}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
 \eeqn
@@
 \beqn
-\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=-1}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
+\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
 \eeqn
@@
 where $f_N$ is the single particle local character.
-Thus, it suffices to show that $f_N = \sum_{k = 0}^{N-2} g_k$.
-Recall that we have the following filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$ given by 
+Thus, it suffices to show that $f_N = \sum_{k = -1}^{N-2} g_k$.
+Recall that from the filtration \eqref{eqn:fil1} we obtain a filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$:
 \beqn
-\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \leftarrow \clie_\bu (\cG_{N,c}) .
+\clie_{\bu}(\cG_{1,c}) \subset \clie_\bu(\cG_{2,c}) \subset \cdots \subset \clie_{\bu}(\cG_{N,c}) .
 \eeqn
-Thus we have the following expression for the associated graded factorization algebra 
+%\beqn
+%\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \leftarrow \clie_\bu (\cG_{N,c}) .
+%\eeqn
+associated graded factorization algebra is of the form
 \beqn
-\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=0}^N \clie_\bu(\cG^{(k)}).
+\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=-1}^N \Sym \left(\cG^{(k)}_c\right).
 \eeqn
@@
 \begin{conj} 
-The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$ is $\chi_{N}(y_1,y_2,y_3,y,q)$. 
+The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$ is $\til \chi_{N}(y_1,y_2,y_3,y,q)$. 
 \end{conj}
@@
 
-It follows from the fact that limit of the diagram in \ref{eqn:limit1} is $(\Bar{\pi}_* \Obs_{sugra})^!
-\simeq \clie_\bu(\cG_c)$ that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in Proposition~\ref{prop:sugraindex1}.
+It follows from the filtration in \eqref{eqn:fil1} that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in proposition~\ref{prop:sugraindex1}. 
 Alternatively, we have the following direct proof of this fact.
@@
 \beqn
-\chi_{sugra}(y_i, y, q) = \lim_{N \to \infty} \til{\chi}_N(y_i,y,q)
+\chi_{sugra}(y_i, y, q) = \lim_{N \to \infty} \chi_N(y_i,y,q)
 \eeqn

### 2022-09-06 fivebranes/finite.tex
imamura

@@
 %\end{align*}
-\begin{align*}
+\beqn
+\label{eqn:gk}
+\begin{array}{cccc}
 g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
 & \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
-\end{align*}
+\end{array}
+\eeqn
 %and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.
@@
 \end{proof}
+
+\subsection{Comparisons to expansions of superconformal indices}
+
+In the final section we would like to exhibit a series of direct consistency checks with our conjectural exact formula for the index of the non-abelian six-dimensional superconformal theory with a few expansions that have appeared in recent literature.
+
+\parsec
+Let us first focus on the superconformal theory associated to the Lie algebra $\lie{sl}(2)$ (so type $A_1$).
+Our conjecture for the superconformal index in this case is the plethystic exponential of $\til f_2 (y_i,y,q)$ from equation \eqref{eqn:6dtwo}.
+We expand the formal single particle index $\til f_2 (y_i, y, q)$ as a series in the variable~$q$, yielding
+\begin{align*}
+\til f_2 (y_i,y,q) & = y^2 q^2 + \left(1 - \chi_{[0,1]}(y_i) y + \chi_{[1,0]} y^2 \right) q^3 \\
+& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 \right) q^4 + O(q^5) .
+\end{align*}
+From this expression, we obtain the $q$-expansion of the index $\til \chi_2(y_i,y,q) = \text{PExp}[\til f_2]$ as 
+\begin{align*}
+\til \chi_2(y_i,y,q) & = 1 + y^2 q^2 + \left(1-\chi_{[0,1]}(y_i) y + \chi_{[1,0]}(y_i)y^2\right)q^3 \\ 
+& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 + y^4\right)q^4 + O(q^5)
+\end{align*}
+
+Similarly, for the $\lie{gl}(2)$ theory $\chi_2 = \text{PExp}[f_1 + \til f_2] = \chi_1 \cdot \til \chi_2$ we find the expansion
+\begin{align*}
+\chi_2 (y_i,y,q) & = y q + \left(y^{-1} - \chi_{[0,1]}(y_i) + \chi_{[1,0]}(y_i) y + 2y^2 \right) q^2 \\ 
+& + \left( \chi_{[1,0]}(y_i) y^{-1} - (\chi_{[1,1]}(y_i)-2) + (\chi_{[2,0]}(y_i) - 2 \chi_{[0,1]}(y_i)) y + 2 \chi_{[1,0]}(y_i) y^2 + 2y^3\right) q^3 + O(q^4) .
+\end{align*}
+
+We observe that these $q$-expansions agree precisely with the expansions in \cite{Kim:2013nva} for the $\lie{gl}(2)$ theory  
+(see equations (3.51) and (3.65) of \textit{loc. cit.}).
+
+\parsec
+
+We proceed to compare expansions of our exact expression for the $\lie{gl}(3)$ theory to those in \cite{Kim:2031nva}. 
+Recall that the conjectural $\lie{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
+\beqn
+\chi_3 (y_i,y,q) = \text{PExp}[f_3(y_i,y,q)] = \chi_2(y_i,y,q) \cdot \text{PExp}[g_3(y_i,y,q)]  .
+\eeqn
+Here, $f_3(y_i,y,q)$ is the single particle local character for the holomorphic factorization algebra $\Obs_3$ and $g_3(y_i,y,q)$ is given in equation \eqref{eqn:gk}.
+
+Since $g_3(y_i,y,q) = y^3 q^3 + O(q^4)$ we see that $\chi_3$ and $\chi_2$ agree up to order $q^2$ and the difference at order $q^3$ is simply
+\beqn
+\chi_3(y_i,y,q) - \chi_2(y_i,y,q) = y^3q^3 + O(q^4) .
+\eeqn
+This is again in exact agreement with the index for the $\lie{gl}(3)$ theory computed \cite{Kim:2013nva} up to order $q^3$ (see equation (3.79) of \textit{loc. cit.}).
+
+\parsec
+
+Next, we compare to expansions for the $\lie{sl}(N)$ theory computed in \cite{Imamura}.
+It will be convenient to change the variables $(y_i, y, q) \to (y_i,x,q)$ where 
+\beqn
+x = qy .
+\eeqn 
+We will again expand in powers of $q$.\footnote{To match precisely with the equations in \cite{Imamura} we note that it is necessary to relable the variables $y_i \leftrightarrow u_i$, $x \leftrightarrow \check{x}$, and $q \leftrightarrow y$ where the variable $y$ is distinct from the one we use in this paper!}
+
+Starting with the $\lie{sl}(2)$ theory we find that up to order $q^4$ the single particle index is
+\begin{align*}
+\til f_2 (y_i,x,q) & = x^2 + \chi_{[1,0]}(y_i) x^2 q \\
+& + \left(-\chi_{[0,1]}(y_i) x + \chi_{[2,0]}(y_i) x^2 \right) q^2 +  \left(1-x-\chi_{[1,1]}(y_i) x + \chi_{[3,0]}(y_i) x^2 \right) q^3 \\
+& + \left(2 \chi_{[1,0]}(y_i) - \chi_{[2,1]}(y_i) x + \chi_{[4,0]}(y_i)x^2 \right)q^4 + O(q^5) .
+\end{align*}
+
+It follows that the plethystic exponential $\chi_2(y_i,y,q)$ of this expression has $q$-expansion
+\begin{align*}
+\chi_2(y_i,y,q) & = \frac{1}{1-x^2} + \chi_{[1,0]}(y_i) x^2 \frac{1}{1-x^2} q \\
+& + \left(-\chi_{[0,1]}(y_i) x + \chi_{[2,0]}(y_i) x^2 (1+x^2)\right) \frac{1}{1-x^2} q^2 \\ 
+& + \left( 1 - x - x^3 + x^6 + \chi_{[1,1]}(y_i) (-x - x^3 + x^4) + \chi_{[3,0]}(y_i) (x^2 + x^4 + x^6) \right) \frac{1}{1-x^2} q^3 \\
+& + O(q^4) 
+\end{align*}
+This agrees with the expansion in \cite{Imamura} (see equation (68)) except for the $\lie{sl}(3)$-scalar term at order $q^3$. 
+We find $(1-x-x^3+x^6) / (1-x^2) = (1-x^3-x^4-x^5) / (1+x)$ whereas Imamura's result is $1 / (1+x)$. 
+It would be interesting to explain the physical or representation theoretic source of this discrepancy.

### 2022-09-09 fivebranes/finite.tex
finite edits

@@
-\section{Conjectures for operators on a finite number of fivebranes}
+\section{Conjectures for operators on fivebranes}
 
@@
 There are various degenerations, or specializations, of this character which are interesting to consider.
-A particularly meaningful one is related to two different deformations of the theory by elements in the (twisted) superconformal algebra.
+A particularly meaningful one is related to two different deformations of the theory by elements in the (twisted) superconformal algebra and is known as the Schur limit of the index.
+
 Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
 We have recalled in \S\ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory. 
-
 There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
@@
 
-The specialization of this index $y=1, y_3=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+The Schur limit $y=1, y_3=1$ of $\til f_2$ in \eqref{eqn:special1} yields 
 \[
@@
 \]
-which is the same as the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
+which is the single particle index of Virasoro vacuum module on the Riemann surface $\Sigma = \C_{z_1}$.
 
@@
 \label{eqn:gk}
-\begin{array}{cccc}
-g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
-& \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
+\begin{array}{lllll}
+g_k (y_i,y,q) \define & q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)\chi_{[1,0]}(y_i) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
+&\displaystyle \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) \chi_{[0,1]}(y_i) \right)}{d(y_i,y,q)} .
 \end{array}
@@
 \end{conj}
+
+We proceed to give some concrete evidence for this conjecture.
+First, we show that when we take the limit as $N \to \infty$ that we recover the index computed from the gravitational side.
 
@@
 
-We can also apply the specialization $y=1, y_3=1$ to $\chi_N$.
+We can also apply the Schur limit  $y,y_3\to 1$ to $\chi_N$.
 \begin{prop}
@@
 \eeqn
+The plethystic exponential of the right hand side is the vacuum character of the $W_{N}$ vertex algebra.
 \end{prop}
@@
 \chi_2 (y_i,y,q) & = y q + \left(y^{-1} - \chi_{[0,1]}(y_i) + \chi_{[1,0]}(y_i) y + 2y^2 \right) q^2 \\ 
-& + \left( \chi_{[1,0]}(y_i) y^{-1} - (\chi_{[1,1]}(y_i)-2) + (\chi_{[2,0]}(y_i) - 2 \chi_{[0,1]}(y_i)) y + 2 \chi_{[1,0]}(y_i) y^2 + 2y^3\right) q^3 + O(q^4) .
+& + \left( \chi_{[1,0]}(y_i) y^{-1} - (\chi_{[1,1]}(y_i)-2) + (\chi_{[2,0]}(y_i) - 2 \chi_{[0,1]}(y_i)) y + 2 \chi_{[1,0]}(y_i) y^2 + 2y^3\right) q^3 \\ & + O(q^4) .
 \end{align*}
@@
 
-We proceed to compare expansions of our exact expression for the $\lie{gl}(3)$ theory to those in \cite{Kim:2031nva}. 
+We proceed to compare expansions of our exact expression for the $\lie{gl}(3)$ theory to those in \cite{Kim:2013nva}. 
 Recall that the conjectural $\lie{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
@@
 
-It follows that the plethystic exponential $\chi_2(y_i,y,q)$ of this expression has $q$-expansion
+It follows that the plethystic exponential $\til \chi_2(y_i,y,q)$ of this expression has $q$-expansion
 \begin{align*}
-\chi_2(y_i,y,q) & = \frac{1}{1-x^2} + \chi_{[1,0]}(y_i) x^2 \frac{1}{1-x^2} q \\
-& + \left(-\chi_{[0,1]}(y_i) x + \chi_{[2,0]}(y_i) x^2 (1+x^2)\right) \frac{1}{1-x^2} q^2 \\ 
-& + \left( 1 - x - x^3 + x^6 + \chi_{[1,1]}(y_i) (-x - x^3 + x^4) + \chi_{[3,0]}(y_i) (x^2 + x^4 + x^6) \right) \frac{1}{1-x^2} q^3 \\
+\til \chi_2(y_i,y,q) & = \frac{1}{1-x^2} +  \frac{x^2}{1-x^2} \chi_{[1,0]}(y_i) q \\
+& + \left(- x \chi_{[0,1]}(y_i) +  x^2 (1+x^2)\chi_{[2,0]}(y_i)\right) \frac{1}{1-x^2} q^2 \\ 
+& + \left( 1 - x - x^3 + x^6 + (-x - x^3 + x^4) \chi_{[1,1]}(y_i)  + (x^2 + x^4 + x^6)\chi_{[3,0]}(y_i)  \right) \frac{1}{1-x^2} q^3 \\
 & + O(q^4) 
@@
 It would be interesting to explain the physical or representation theoretic source of this discrepancy.
+
+Similarly, we can obtain the $q$-expansions for the local character $\chi_3(y_i,x,q)$ of the factorization algebra $\Obs_3$ and compare it to the $q$-expansion for the superconformal index of the $\lie{sl}(3)$ theory in \cite{Imamura}.
+Up to order $q^3$ we have
+\begin{align*}
+\chi_3(y_i,x,q) & = \frac{1}{(1-x^2)(1-x^3)} + \frac{x^2}{(1-x)(1-x^3)} \chi_{[1,0]}(y_i) q \\
+& + \left((-x -x^2 + x^5)\chi_{[0,1]}(y_i) + (x^2 + x^3 + x^4 + x^5+ x^6) \chi_{[2,0]}(y_i) \right) \frac{1}{(1-x^2)(1-x^3)} q^2 \\
+& + 
+\end{align*}

### 2022-09-09 fivebranes/intro.tex
finite edits

@@
 Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories. 
-Examples of such a quantities are superconformal indices, which are generating functions for the R-charges of BPS local operators.
+Examples of such a quantities are superconformal indices, which are generating functions for the $R$-charges of BPS local operators. 
 Crucial steps towards a more microscopic understanding of superconformal indices were taken in \cite{}, articulated through the construction of twisting.
 
-Introduced by Witten \cite{} and further developed by Costello \cite{}, twisting refers to a fixed-point construction for field theories equipped with the action of a supersymmetry algebra.
-Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge - the result is a theory on which the translations in the image of the supercharge act homotopically trivially.
-Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.
+Introduced by Witten \cite{WittenTwist} and further developed by Costello \cite{CostelloHol}, twisting refers to a localization, or fixed-point, construction for theories equipped with an action of a supersymmetry algebra.
+Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge---the result is a theory for which the infinitesimal translations in the image of the nilpotent supercharge act homotopically trivially.
+When a twist exists (which is almost always) a supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.
 
-One of the insights of \cite{} was that superconformal indices count exactly local operators in the minimal twist - accordingly, we may think of the algebra of local operators in the minimal twist as \textit{categorifying} the superconformal index.
+One of the insights of \cite{} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
 Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. 
-Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set.
+Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set (for example, non-local operators obtained from local ones via a descent procedure).
 
-A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\cN=(2,0)$ and three-dimensional $\cN=8$ superconformal field theories.
-However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization.
-In light of this, we propose to access the minimal twist and its local operators via \textit{twisted holography}.
+A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
+%and three-dimensional $\cN=8$ superconformal field theories. 
+As is well-known, the six-dimensional~$\cN=(2,0)$ supersymmetric theory is quite elusive---it admits no known Lagrangian formulation, and outside of the abelian case, is not known to admit a field theoretic realization.
+In light of this, we propose to access the minimal twist and its local operators via the proposal of \textit{twisted holography}.
 
 \subsection{Twisted Holography}
-Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of twists.
-The main objects involved are factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes therein.
+Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of supersymmetric twists. 
+Fundamentally, it conjectures a duality between the algebra of observables of the (twisted) gravitational theory and the algebra of observables of the gauge theory.
+There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory side.
 
-A more concrete, albeit informal, statement is as follows.
-Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory.
-Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\to X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.
+As we mentioned above, the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra.
+The predicted type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
+Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to a (augmented) algebra $A$ a dual $A^!$ whose
+
+A more concrete, albeit informal, statement of twisted holography is as follows. 
+Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of the bulk gravitational theory. 
+Suppose we have, in addition, a stack of $N$ branes, wrapping a submanifold $\iota \colon Y\to X$, whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
+
+\brian{to do}
+\begin{itemize}
+\item 6d theory how ubiquitous it is. 
+\item more elaboration on twisted holography.
+\end{itemize}
 
@@
 
+\brian{to do}
+
 \subsection{Outline}

### 2022-09-16 fivebranes/fact.tex
fixed limit

@@
 \label{eqn:Gdecomp}
-\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
+\cG_Z = \bigoplus_{n \geq -1} \cG^{(n)} .
 \eeqn
@@
 %\[
-%\cG_Z (U)  \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+%\cG_Z (U)  \bigoplus_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
 %\]
@@
 %\beqn\label{eqn:decomp3}
-%\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
+%\Bar{\pi}_{*} \cL_{sugra} = \bigoplus_{n \geq -1} \cV_{n} 
 %\eeqn
@@
 \beqn\label{eqn:decomp1}
-E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
+E(5|10) = \til V_{-1} \times \bigoplus_{n \geq 0} V_n 
 \eeqn
@@
 \beqn\label{eqn:decomp2}
-\Hat{E(5|10)} = \prod_{n \geq -1} V_n
+\Hat{E(5|10)} = \bigoplus_{n \geq -1} V_n
 \eeqn
@@
 \subsection{Koszul duality for factorization algebras: an ansatz}
+\label{s:noether}
 
@@
 \[
-\cG = \prod_{k \geq -1} \cG^{(k)} .
+\cG = \bigoplus_{k \geq -1} \cG^{(k)} .
 \]
@@
 \beqn
-\til \cG \define \prod_{k \geq 0} \cG^{(k)}
+\til \cG \define \bigoplus_{k \geq 0} \cG^{(k)}
 \eeqn
 where we simply forget the weight $-1$ component. 
+These product decompositions also hold at the level of compactly supported sections.
 
-This weight grading on $\cG$ induces a filtration on the factorization algebra \eqref{eqn:factgrad} and on its $!$-dual $\clie_\bu (\cG_{c})$. 
-For $k \geq -1$ define
+This weight grading on $\cG$ induces a filtration on the factorization algebra \eqref{eqn:factgrad} and on its $!$-dual 
 \beqn
-\cG^{(\geq k)} = \prod_{j \geq k} \cG^{(j)}  .
+\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c}).
 \eeqn
-Notice that $\cG^{(\geq -1)} = \cG$.
-For $N \geq 1$ define the local $L_\infty$ algebra
+We will focus just on the $!$-dual factorization algebra.
+To construct the filtration, first consider the natural filtration on the local Lie algebra $\cG$ induced by the grading
 \beqn
-\cG_N \define \cG / \cG^{(\geq N-1)} .
+\cG = F^0 \cG \supset F^1 \cG \supset \cdots 
 \eeqn
-Similarly, for $N \geq 2$ define
+where for $N \geq 1$ we have
 \beqn
-\til \cG_N \define \til \cG / \cG^{(N-1)} .
+F^N \cG = \cG^{(\geq N-2)} = \bigoplus_{j \geq N-2} \cG^{(j)} ,
 \eeqn
-We have chosen a convenient chose of indexing for the constructions below.
+and similarly for $\til \cG$. 
+If we define 
+\beqn
+\cG_1 \define \cG / \cG^{(\geq 0)} 
+\eeqn
+and for $N > 1$
+\beqn\label{eqn:gN}
+\cG_N \define \cG / \cG^{(\geq N-1)} , \quad \til \cG_N \define \til \cG / \cG^{(\geq N-1)} ,
+\eeqn
+then the associated graded local Lie algebras $\op{Gr} \cG$ and $\op{Gr} \til{\cG}$ satisfy $\op{Gr} \cG = \op{colim} \cG_N$ and $\op{Gr} \til \cG = \op{colim} \til \cG_N$.
+These filtrations also hold at the level of compactly supported sections.
 
+The filtration on $\cG$ induces a filtration of the factorization algebra $\clie_\bu (\cG_{c})$ 
+\beqn
+\clie_\bu (\cG_c) = F^0 \clie_\bu (\cG_c) \supset F^1 \clie_\bu (\cG_c) \supset \cdots 
+\eeqn
+where $F^N \clie_\bu(\cG_c) = \clie_\bu(F^N \cG_c)$. 
+Similarly, we have a filtration on the factorization algebra $\clie_\bu(\til \cG_c)$. 
+At the level of the associated graded, we have
+\beqn
+\label{eqn:lim}
+\op{Gr} \clie_\bu (\cG_{c}) = \op{colim}_{N \geq 1} \clie_\bu(\cG_{N,c}) .
+\eeqn
+Similarly $\op{Gr} \clie_\bu (\til \cG_{c}) = \op{colim}_{N \geq 2} \clie_\bu(\til \cG_{N,c})$.
 %The subalgebra $\cG^{(\geq k)} = \oplus_{j \geq k} \cG^{(j)}$ is an ideal for every $k$. 
@@
 %For each $k$, we point out that $\cG / \cG^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
-The resulting filtration of the $!$-dual
-\beqn
-\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c})
-\eeqn 
-of the factorization algebra \eqref{eqn:factgrad} is of the form
-\beqn\label{eqn:fil1}
-\clie_\bu (\cG_{1,c}) \subset \clie_\bu (\cG_{2,c}) \subset \cdots \subset \clie_\bu(\cG_c) .
-\eeqn
-Similarly, there is a filtration on the factorization algebra $\clie_\bu (\til \cG_c)$ of the form
-\beqn
-\label{eqn:fil2}
-\clie_\bu(\til \cG_{2,c}) \subset \clie_\bu(\til \cG_{3,c}) \subset \cdots \subset \clie_\bu(\til \cG_c).
-\eeqn
-%Explicitly, the underlying super vector space of the weight $k$ component $\clie_\bu(\cG_{c})^{(k)}$ is 
+%The resulting filtration of the $!$-dual
 %\beqn
-%\bigoplus_{m \geq 0} \bigoplus_{\sum_{i=1}^m j_i = k} \left(\cG_c^{(j_1)} \otimes \cdots \otimes \cG_{c}^{(j_m)}\right)_{\Sigma_m} 
+%\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c})
 %\eeqn 
-%where we take coinvariants for the symmetric group $\Sigma_m$.
-%Similarly, the factorization algebra $\clie_\bu(\til \cG_c) = \oplus_{k \geq 0} \clie_\bu(\til \cG_c)^{(k)}$ is graded.
+%of the factorization algebra \eqref{eqn:factgrad} is of the form
+%\beqn\label{eqn:fil1}
+%\clie_\bu (\cG_{1,c}) \subset \clie_\bu (\cG_{2,c}) \subset \cdots \subset \clie_\bu(\cG_c) .
+%\eeqn
+%Similarly, there is a filtration on the factorization algebra $\clie_\bu (\til \cG_c)$ of the form
+%\beqn
+%\label{eqn:fil2}
+%\clie_\bu(\til \cG_{2,c}) \subset \clie_\bu(\til \cG_{3,c}) \subset \cdots \subset \clie_\bu(\til \cG_c).
+%\eeqn
 
-%Define 
-%\beqn
-%\cG_1 \define \cG / \cG^{(\geq 0)} 
-%\eeqn
-%and for $N > 1$
-%\beqn
-%\til \cG_N \define \cG / \cG^{(\geq N-1)} , \quad \cG_N \define \cG^{\geq 0} / \cG^{(\geq N-1)} .
-%\eeqn
-%Each of $\cG_1, \cG_{N}, \til \cG_N$ has the induced structure of a local $L_\infty$ algebra on the worldvolume.
-%Notice that as factorization algebras of graded vector spaces one has
-%\[
-%\til \cG_N = \cG_N \otimes \cG_1
-%\]
-%for $N > 1$.
-
-%\beqn\label{eqn:colim}
-%\ul\C \to \clie^\bu(\cG_1) \to \clie^\bu(\til \cG_2) \to \cdots ,
-%\eeqn
-%whose colimit is~$\Bar{\pi}_* \Obs_{sugra}$. 
-%Here $\ul\C$ is the constant factorization algebra whose value is $\C$ on every open set.
-
-The first term in the filtration \eqref{eqn:fil1} is 
+The first term in the limit \eqref{eqn:lim} is 
 \[

### 2022-09-16 fivebranes/finite.tex
fixed limit

@@
 Thus, it suffices to show that $f_N = \sum_{k = -1}^{N-2} g_k$.
-Recall that from the filtration \eqref{eqn:fil1} we obtain a filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$:
+Recall that from the description \eqref{eqn:gN} we have, as local Lie algebras:
 \beqn
-\clie_{\bu}(\cG_{1,c}) \subset \clie_\bu(\cG_{2,c}) \subset \cdots \subset \clie_{\bu}(\cG_{N,c}) .
+\cG_N = \cG / \cG^{(\geq N-2)} ,
 \eeqn 
+for $N \geq 1$. 
+In particular, as a super vector bundle on the threefold $Z = \C^3$ we have
+\[
+\cG_N = \cG^{(-1)} \oplus \cG^{(0)} \oplus \cdots \oplus \cG^{(N-2)} .
+\]
 %\beqn
@@
 %\eeqn
-associated graded factorization algebra is of the form
-\beqn
-\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=-1}^N \Sym \left(\cG^{(k)}_c\right).
-\eeqn
-
-Thus, we must see that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG^{(k)}_c)$, which is a direct observation using the description of $\cG^{(k)}$ we have given in Proposition \ref{prop:Vj}.
+So, it suffices to observe that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG^{(k)}_c)$, which is a direct observation using the description of $\cG^{(k)}$ we have given in Proposition \ref{prop:Vj}.
 \end{proof}
@@
 
-It follows from the filtration in \eqref{eqn:fil1} that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in proposition~\ref{prop:sugraindex1}. 
+It follows from the limit description in \eqref{eqn:lim} that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in proposition~\ref{prop:sugraindex1}.
 Alternatively, we have the following direct proof of this fact.

### 2022-09-16 fivebranes/index.tex
fixed limit
merge error fixed

@@
 We begin by describing the relevant backgrounds.
-In eleven-dimensional supergravity, the $AdS_7 \times S^4$ and $AdS_{4}\times S^{7}$ backgrounds are obtained by backreacting a number of fivebranes and membranes respectively in flat space \cite{Maldacena:1997re,WittenAdS}.
-In \cite{RSW} we gave descriptions of twisted versions of these backgrounds. We will recall this construction, adapted to a slightly more global situation than is considered in \cite{RSW}.
+In eleven-dimensional supergravity, the $AdS_7 \times S^4$ background is obtained by backreacting a number of fivebranes in flat space \cite{Maldacena:1997re,WittenAdS}.
+In \cite{RSW} we gave descriptions of twisted versions of this background. We will recall this construction, adapted to a slightly more global situation than considered previously.
 
-We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 3-step procedure:
+We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 2-step procedure:
 
@@
 \end{align*}
-Letting $\pi \colon M \to Z$ be the natural projection, we obtain the $S^{4}$ bundle
+Letting $\pi \colon M \to Z$ be the natural projection, we obtain the projection
 \[
@@
 \begin{tikzcd}
-M \ar[d,"p|\mathring M"'] \ar[r,hook] & \mathring{M} \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
+\mathring{M} \ar[d,"p|\mathring M"'] \ar[r,hook] & M \ar[d,"p"] & \ar[l,hook',"0"'] Z \ar[d,"="] \\
 \R_{>0} \times Z \ar[r,hook] & \R_{+} \times Z & \ar[l,hook',"0 \times \id"] Z.
@@
 The inclusions on the left are the natural embeddings.
-The top right inclusion is the zero section of ${\rm Tot}(\R \oplus V) = X$ and the bottom right inclusion is the embedding at radius $r = 0$.
+The top right inclusion is the zero section of $M = {\rm Tot}(\R \oplus V)$ and the bottom right inclusion is the embedding at radius $r = 0$.
 
-As we just elaborated, the eleven-dimensional theory is defined on the THF manifold $M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $M$.
+As we elaborated in section \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$.
 Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$.
@@
 
-The theory on $M$ extends to a theory on the manifold obtained by filling in the zero section of $\R \times V$; in other words, we know that the theory is defined on the entire space $\R \times X$.
-This means that there is a natural way to extend the theory on $\R_{>0} \times Z$ to the seven-manifold with boundary $\R_{+} \times Z$.
-The restriction of this theory to the six-dimensional boundary plays the most important role for us.
+\begin{prop}
+  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
+  \beqn
+  \eeqn
 
-Recall that we have a THF structure on $M$ induced from a partially flat conneciton on $\R\oplus W$. The partial connection amounts to a splitting of the exact sequence
+  where . The BV pairing is given by
+
+\end{prop}
+\begin{proof}
+Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
+The partial connection yields a splitting of the exact sequence
 
 \[
-  0 \to F_{X}\cap T_{M/Z}^{\C}\to F_{X}\to \pi^{*}T^{1,0}_{Z}\to 0
-.\]
+  0 \to F_{M}\cap T_{M/Z}^{\C}\to F_{M}\to \pi^{*}T^{0,1}_{Z}\to 0
+\]
 
-Both $F_{X}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that that the splitting preserves the lie brackets on sections.
+Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that that the splitting preserves the lie brackets on sections.
+\end{proof}
 
-It was argued in \cite{RSW} that to leading order the coupling of a stack of twisted fivebranes to the eleven-dimensional theory is given by the nonlocal interaction
+\parsec[s:flux]
+The second step in the construction of the backreacted geometry involves deforming the pushforward $(p| \mathring{M})_{*}\cL_{sugra}$ by a certain Maurer-Cartan element.
+The Maurer-Cartan element is determined by the lowest order term in the coupling between the eleven dimensional theory and the stack of fivebranes.
+It was argued in \cite{RSW} that the relevant coupling is given by the nonlocal interaction
 \beqn\label{eqn:br1}
-I_{M5} = N\int_{Z} \div^{-1}\mu \vee \Omega +\cdots
+I_{fivebrane} = N\int_{Z} D_\Omega^{-1}\mu \vee \Omega +\cdots
 \eeqn
-where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)$ is a component of a field in the eleven-dimensional theory which satisfies $\div \mu = 0$.
+where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(\vartheta_{F})$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.
 
-\parsec
-Let $C$ be a curve, and let $V\to C$ be a rank 4-holomorphic vector bundle over $C$ such that $\wedge^{4} V = K_{C}$.
+The relevant Maurer-Cartan element is a solution to the equations of motion for the eleven-dimensional theory deformed by this interaction.
+After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields the following equation for $\gamma$
+\beqn
+\thfd D \gamma + D_\Omega\left (\frac{\mu}{1-\nu}\right )\wedge D \gamma = N \delta_Z.
+\eeqn
+
+%\parsec
+%Let $C$ be a curve, and let $V\to C$ be a rank 4-holomorphic vector bundle over $C$ such that $\wedge^{4} V = K_{C}$.
 This condition again ensures that $X = {\rm Tot} V$ is a Calabi-Yau five-fold - in the main body of the paper, we will take $V = K^{1/2}_{C}\otimes \C^{4}$.
@@
 
-Since $V$ is a complex vector bundle, we may choose a fiberwise hermitian metric, and as before, we may view $\R\times X \setminus \R\times C$ as an $S^{7}$-bundle over $\R_{>0}\times \R\times C$.
+%Since $V$ is a complex vector bundle, we may choose a fiberwise hermitian metric, and as before, we may view $\R\times X \setminus \R\times C$ as an $S^{7}$-bundle over $\R_{>0}\times \R\times C$.
 
@@
 %\end{cor}
+\parsec[s:hilbertspace]
+The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construciton of the Hilbert space.
+The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$.
+We will construct the Hilbert space by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.
+
+Our ansatz for geometric quantization will avoid discussion of subtler aspects such as the metaplectic correction.
+We define the geometric quantization to be given by functions that are constant along the leaves of a lagrangian foliation of the phase space.
+
+The phase space at $\infty\in \R_{>0}$ is computed by restricting to a neighborhood $(a, \infty)\subset \R_{>0}$:
+\beqn
+(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}=
+\eeqn
+
+There is a symplectic pairing given by
+\beqn
+\eeqn
 
@@
 Geometrically, this background is $AdS_7 \times S^4$.
-Similarly, for backreacting membranes the background is $AdS_4 \times S^7$. 
+
 In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.
@@
 
-\subsection{Supergravity states for twisted $AdS_7$}
+\subsection{Mass Spectroscopy on twisted $AdS_7\times S^{4}$}
+\label{s:ads7}
 
@@
 \begin{prop}
+\label{prop:sugraindex1}
 The single particle index of the space of twisted supergravity states~$\cH_{sugra}^{6d}$ is given by the following expression
@@
 
-\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$ \surya{...} \brian{not sure where this was supposed to go?}
-
-\subsection{Supergravity states for twisted $AdS_4$}
-For convenience we choose coordinates on the eleven manifold as
-\[
-\R \times \C^5 = \R_t \times \C^4_w \times \C_z
-\]
-with $w = (w_a), a=1,2,3,4$.
-The stack of membranes wrap 
-\beqn
-w_1=w_2=w_{3}=w_{4} = 0 .
-\eeqn
-
-The bosonic subalgebra \lie{eqn:gut} of the twisted superconformal algebra embeds, in this case, as the following ghosts of the eleven-dimensional model.
-\begin{itemize}
-\item
-The subalgebra $\lie{sl}(4)$ ($R$-symmetry) embeds as vector fields
-\beqn
-\sum_{ab} A_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ab}) \in \lie{sl}(4) .
-\eeqn
-By definition, these vector fields are automatically divergence-free.
-
-\item
-The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
-\beqn
- \frac{\del}{\del z}, \quad z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}, \quad \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
-\eeqn
-\end{itemize}
-
-%\begin{rmk}
-%In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of the exceptional Lie algebra $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
-%\cite{KacClass}.
-%We will make use of this grading in \S \ref{s:kr}.
-%\end{rmk}
-The equivariant character again has four fugacities, which we explicitly choose as follows:
-\begin{itemize}
-  \item $t_{1}, t_{2}, t_{3}$ denote generators for the Cartan of $\lie{sl}(4)$ which is generated by the vector fields
-  \beqn
-  h_1 = w_1 \frac{\del}{\del {w_1}} - w_4 \frac{\del}{\del{w_4}} , \quad h_2 = w_2 \frac{\del}{\del{w_2}} - w_4 \frac{\del}{\del{w_4}} , \quad h_3 = w_3\frac{\del}{\del w_3}-w_4\frac{\del}{\del w_4}.
-  \eeqn
-  \item $q$ denotes a generator for the Cartan of the $\lie{sl}(2)$ which is generated by the vector field
-        \beqn
-        L_0 =  z \frac{\del}{\del z}-\frac{1}{4}\sum_{a=1}^4 w_a\frac{\del}{\del w_a}
-        \eeqn
-\end{itemize}
-
-Once again, the twisted spergravity states $\cH_{sugra}^{3d}$ form a representation for $\lie{osp}(6|2)$.
-The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^4_w \times \C_z$.
-These are summarized in table \ref{tbl:sugraM2}.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c}
-  & $z$ & $w_{1}$ & $w_{2}$ & $w_{3}$ & $w_{4}$ \\
-  \hline
-  $t_{1}$ & 0 & 1 & 0 & 0 & $-1$ \\
-  $t_{2}$ & 0 & 0 & 1 & 0 & $-1$ \\
-  $t_{3}$ & 0 & 0 & 0 & 1 & $-1$ \\
-  $q$ & $-1$ & $\frac 14$ & $\frac 14$ & $\frac{1}{4}$ & $\frac{1}{4}$
-\end{tabular}
-\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \R\times \C$.}
-\label{tbl:sugraM2}
-\end{center}
-\end{table}
-
-We enumerate single particle supergravity states via computing the super trace of the operator $q^T t_1^{h_1} t_2^{h_2} t_3^{h_3}$ acting on $\cH^{3d}_{sugra}$:
-\beqn
-f^{3d}_{sugra}(q,t_1,t_2,t_3) = \Tr_{\cH_{sugra}^{3d}} (-1)^F q^T t_1^{h_1} t_2^{h_2} t_3^{h_3} .
-\eeqn
-
-\begin{prop}
-The single particle index of the space of twisted supergravity states $\cH_{sugra}^{3d}$ is given by the following expression
-\beqn
-f_{sugra}^{3d} (q,t_1,t_2,t_3) = \frac{1 + q^{5/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) - q^{3/4} (t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) - q^2}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})} .
-\eeqn
-\end{prop}
-
-This result is in close agreement with previously computed indices for supergravity on $AdS_{4}\times S^{7}$
-For example, our formula differs slightly from the expression found in \cite[Eq. (2.17)]{Bhattacharya:2008zy}. 
-To obtain an exact match we simply subtract one single particle state
-\beqn
-f_{sugra}^{3d} (q, t_{1}, t_{2}, t_3) - 1 = \frac{\left(\begin{aligned}
-        & -q^{7/4}(t_{1}^{-1}+t_{2}^{-1}+t_{3}^{-1}+t_{1}t_{2}t_{3}) +q^{1/4}(t_{1}+t_{2}+t_{3}+t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}) \\
-        & +q^{1/2}(1-q)(t_{1}t_{2}+t_{1}t_{3}+t_{2}t_{3}+t_{1}^{-1}t_{2}^{-1}+t_{1}^{-1}t_{3}^{-1}+t_{2}^{-1}t_{3}^{-1})\end{aligned}\right)}{(1-q)(1-t_{1}q^{1/4})(1-t_{2}q^{1/4})(1-t_{3}q^{1/4})(1-t_{1}^{-1}t_{2}^{-1}t_{3}^{-1}q^{1/4})}.
-\eeqn
-To compare exactly to \cite{Bhattacharya:2008zy} we note the change of variables
-\beqn
-q= x^{2} , \quad t_1 = (y_{2}y_{3})^{1/2}/y_1^{1/2} , \quad t_2 = (y_{1}y_3)^{1/2}/ y_2^{1/2} , \quad t_3 = (y_1 y_2)^{1/2}/y_{3}^{1/2} .
-\eeqn
+\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$

### 2022-09-16 fivebranes/intro.tex
intro

@@
-%\documentclass[11pt]{amsart}
-%
-%%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
-%
-%\begin{document}
+\documentclass[11pt]{amsart}
+
+%\usepackage{../macros-master}
+\usepackage{macros-fivebrane}
+
+\begin{document}
 
@@
 Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories. 
-Examples of such a quantities are superconformal indices, which are generating functions for the $R$-charges of BPS local operators. 
-Crucial steps towards a more microscopic understanding of superconformal indices were taken in \cite{}, articulated through the construction of twisting.
+Examples of such a quantity is the superconformal index, which is a generating function for some collection of $R$-charges of certain BPS local operators. 
+Crucial steps towards a more microscopic understanding of superconformal indices were taken in \brian{surya fill in this empty citation} \cite{}, articulated through the construction of twisting.
 
@@
 
-One of the insights of \cite{} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
+One of the insights of \brian{surya fill in this empty citation} \cite{} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
 Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. 
@@
 
-A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
+A principal goal of the present paper is to initiate the study of factorization algebras associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
 %and three-dimensional $\cN=8$ superconformal field theories. 
@@
 There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory side.
+The type of twisted holography which is at play in this paper is a twisted version of the $AdS_7/CFT_6$ duality involving fivebranes inside of eleven-dimensional supergravity.
 
-As we mentioned above, the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra.
+We mentioned that the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra.
 The predicted type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
-Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to a (augmented) algebra $A$ a dual $A^!$ whose
+Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to a (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
+Following the work of \cite{CLsugra,CP1} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
+If $A$ is the algebra of operators of some bulk quantum field theory (perturbatively we can even consider a theory of gravity) then $A^!$ is the algebra of operators on the universal topological line defect.
+Universal here means that algebra of operators on any other line defect which couples to the bulk system admits a unique map of algebras from~$A^!$.
 
-A more concrete, albeit informal, statement of twisted holography is as follows. 
+The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so in this paper.
+This sort of duality would allow one to make sense of universality statements as above for higher dimensional, possibly non-topological, defects in an arbitrary bulk quantum field theory.
+Nevertheless, we can make the following ansatz for the Koszul dual $\cF^!$, which we refer to as the $!$-dual in this paper to avoid confusion, of a factorization algebra~$\cF$ of observables of some bulk quantum field theory.
+It is the universal factorization algebra, along a specified defect, which couples to the bulk quantum field theory.
+While this heuristic definition sounds natural, it does not lend itself to an explicit description.
+However, for factorization algebras of bulk quantum field theories which can be expressed in a particular way we can refer to a local version of Noether's theorem in order to get our hands on it, see~\S\ref{s:noether}.
+
+Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
 Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of the bulk gravitational theory. 
-Suppose we have, in addition, a stack of $N$ branes, wrapping a submanifold $\iota \colon Y\to X$, whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
+Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
+In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebra $\Obs_{brane}(N)$.
 
-\brian{to do}
-\begin{itemize}
-\item 6d theory how ubiquitous it is. 
-\item more elaboration on twisted holography.
-\end{itemize}
+Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{brane}(N)$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
+We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}
 
-\begin{expect}[Twisted Holographic Principle]
+\begin{expect}[Twisted holographic principle following \cite{CLsugra}]
 There is a map of factorization algebras
 \[
-        (\Obs_{grav}|_{Y})^{!}\to \Obs^{N}_{brane}
+  (\Obs_{grav}|_{Y})^{!}\to \Obs_{brane}(N)
 \]
-
 that becomes an equivalence in the large $N$ limit.
@@
 
-Nonetheless, the above expectation has been tested in many examples \cite{}.
+From the point of view of the bulk gravitational theory, one can understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the manifold $X - Y$ obtained by subtracting the brane.
+In most examples the above principle is too naive as we are forgetting a key ingredient, the so-called backreaction of the branes. 
+On one hand, this deforms the geometric structure used to define the gravitational theory on $X - Y$---concretely, it will correspond to a certain deformation of the factorization algebra $(\Obs_{grav}|_{Y})^{!}$.
 
-\subsection{Infinite dimensional symmetry enhancement by exceptional simple lie superalgebras}
+The above expectation can be tested in instances where both sides of the duality admit explicit descriptions. 
+This has been carried out in many examples including:
+\begin{itemize}
+\item $D1$ branes in the topological string on the deformed conifold \cite{costello2021twisted}.
+Here, the duality is formulated in terms of vertex algebras which are avatars of holomorphic factorization algebras on a Riemann surface.
+This is also understood as a deformed version of the physical duality between 4d $\cN=4$ supersymmetric Yang--Mills and type IIB superstring theory on $AdS_5$. 
+\item A system of twisted $D1-D5$ branes in type IIB string theory on twisted $AdS_3 \times S^3 \times T^4$ \cite{CP1}. 
+Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a supersymmetric version.
+\item Membranes and fivebranes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}.
+In the particular $\Omega$-background membranes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras (and hence ordinary Koszul duality).
+The $\Omega$-background localizes fivebranes to a complex plane and the duality can be formulated in terms of vertex algebras (one-dimensional holomorphic factorization algebras). 
+\end{itemize}
 
-\brian{to do}
+A feature of the above examples is that via some method one can understand, independently, the algebra of observables on both sides of the duality. 
+For fivebranes in $M$-theory, before turning on the $\Omega$-background, there is no known description which is robust enough to fit inside of the factorization algebra formulation of a quantum field theory.
+So, rather than prove, or test, a version of the twisted holographic principle, the objective of this paper is to \textit{use} the twisted holographic principal to obtain an explicit description of the factorization algebra associated to the worldvolume theory on a stack of fivebranes (after performing the minimal, holomorphic, twist).
+
+Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
+After taking a certain classical limit, our conjectural description arises from a presentation of the $!$-dual as
+\beqn
+(\Obs_{grav}|_{Y})^{!} \simeq \cF_{-1} \otimes \cF_0 \otimes \cdots \cF_1 \otimes \cdots 
+\eeqn
+for some factorization algebras $\cF_{-1},\cF_0, \cF_{1},\ldots$ which are defined using a certain weight decomposition of the bulk gravitational theory.
+The strange indexing conventions will be explained in \S\ref{eqn:fact}.
+
+Using this presentation, our conjecture for the factorization algebra associated to the worldvolume theory on a stack of $N$ twisted fivebranes, after taking the same classical limit, has the form
+\beqn\label{eqn:finiteTensor}
+\Obs_{brane} (N) = \cF_{-1} \otimes \cF_2 \otimes \cdots \otimes \cF_{N-2} .
+\eeqn
+In other words, we simply truncate the tensor decomposition at order $N$.
+
+A related theory is the minimal twist of the six-dimensional superconformal theory associated to a Lie algebra of type $A_{N-1}$.
+We denote the corresponding factorization algebra by $\Obs_{A_{N-1}}$ for now. 
+This is obtained from the worldvolume theory simply by throwing away the modes propagating transverse to the brane, which in our presentation above corresponds to stripping off the first factor $\cF_{-1}$.
+Thus, at the level of factorization algebras we have a similar decomposition
+\beqn
+\Obs_{A_{N-1}} = \cF_0 \otimes \cF_1 \otimes \cdots \otimes \cA_{N-1} .
+\eeqn
+
+We want to emphasize that these expressions only hold after taking this classical limit.
+This decomposition as a tensor product of factorization algebras will break down at the quantum level.
+Nevertheless, the description provides a very effective way to compute certain protected quantities like the superconformal index.
+
+As the formalism of Koszul duality and factorization algebras is rather abstract, it is useful to first indicate what our approach looks like at the level of the superconformal index. 
+On one hand, we have the index of multi-particle states of the supergravity theory on the manifold obtained by removing the location of the brane; we denote this by $\chi_{grav}({\bf x})$.
+It is a function of some number of fugacities ${\bf x}$ which we will discuss explicitly in our examples momentarily. 
+Typically, this multi-particle index can be obtained from the single-particle index $f_{grav}({\bf x})$ of gravitational states through the plethystic exponential. 
+Since the index is only really sensitive to the minimal twist, it is reasonable that we can compute the index using our formulation of twisted eleven-dimensional supergravity.
+We will obtain known formulas for the index of eleven-dimensional supergravity states on $AdS_7$ in \S\ref{s:states} using our description of twisted supergravity.
+
+While we don't need to know the precise relationship at the moment, we can point out that the data of a factorization algebra encodes, in particular, the algebra of local operators of a system.
+This is convenient from the point of view of the superconformal index since as we have already pointed out we can compute it as the index of local operators of the twisted theory.
+We will see how the descriptions above lead to a presentation for the superconformal index $\chi_N({\bf x})$ of the worldvolume theory on a finite stack of $N$ fivebranes.
+
+If we are working simply on the worldvolume $\C^3 \cong \R^6$, our description in \eqref{eqn:finiteTensor} posits that after taking the classical limit the local operators on a stack of $N$ twisted fivebranes is
+\beqn
+\cF_{-1}(0) \otimes \cdots \otimes \cF_{N-2}(0) ,
+\eeqn
+where $\cF_k(0)$ stands for the algebra of local operators associated to the factorization algebra $\cF_k$.
+Forgetting about the differentials for the time being, the local operators $\cF_k(0)$ are given as the free algebra on some vector space $V_k$ of linear local opeartors.
+Thus, to compute the index of local operators of $\Obs_{brane}(N)$ it suffices to compute the index of all of the $V_k$---this is the single particle index---and then apply the plethystic exponential.
+For now, denote by $g_k({\bf x})$ the index of the vector space $V_k$.
+
+Putting all of this together, our approach is based on the observation that we can express the single particle supergravity index as
+\beqn
+f_{grav}({\bf x}) = \sum_{k=-1}^\infty g_k({\bf x}) .
+\eeqn
+Then, the avatar of our conjectural description in \eqref{eqn:finiteTensor} at the level of the superconformal index is
+\beqn
+f_N ({\bf x}) = \sum_{k = -1}^{N-2} g_k({\bf x}) .
+\eeqn
+To obtain the superconformal index we simply apply the plethystic exponential
+\beqn
+\chi_N({\bf x}) = \prod_{k=-1}^{N-2} {\rm PExp}\left[g_k({\bf x})\right] .
+\eeqn
+This is a formula for the index on a finite stack of $N$ fivebranes. 
+A related quantity is the index of the superconformal field theory associated to the Lie algebra $A_{N-1}$. 
+To obtain this we simply through away contributions coming from a single fivebrane, which results in the expression
+\beqn
+\chi_{A_{N-1}}({\bf x}) = \prod_{k=0}^{N-2} {\rm PExp}\left[g_k({\bf x})\right] .
+\eeqn
+
+From these formulas it is manifest that the holographic relation $\chi_{grav} = \lim_{N \to \infty} \chi_N$ holds. 
+The next thing we turn to is evidence for our claim that $\chi_N({\bf x})$ really is the superconformal index associated to fivebranes. 
+In ~\S\ref{s:finite} we will show that for small values of $N$ our closed of formulas, when appropriately expanded, agree with approximations which have been found in the literature.
+Even stronger evidence would involve the factorization algebras $\Obs_{brane}(N)$, and we will briefly sketch how this should go in later sections but leave a full treatment to future work.
+
+To get an even better handle on our conjectural description we focus on the case~$N=2$.
+
+\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
+
+The first ingredient we need 
+In \S\ref{s:twisted} we will recall a description of the minimal twist of eleven-dimensional supergravity following \cite{RSW} which is
 

### 2022-09-19 fivebranes/intro.tex
agt gl(1)

@@
 \documentclass[11pt]{amsart}
+
+\linespread{1.15} %for editing
 
@@
 
-A principal goal of the present paper is to initiate the study of factorization algebras associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
+A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
+As a factorization algebra encodes, in particular, the local operators of a theory we can extract from them familiar quantities like the superconformal index.
 %and three-dimensional $\cN=8$ superconformal field theories. 
@@
 In light of this, we propose to access the minimal twist and its local operators via the proposal of \textit{twisted holography}.
+Before getting into the details of this proposal, we point out a collection of exceptional super Lie algebras which will play a pivotal role in our approach; and appear quite naturally from the point of view of twisted supergravity and twisted superconformal field theory.
 
-\subsection{Twisted Holography}
+\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
+
+In \S\ref{s:twisted} we will recall a description of the minimal twist of eleven-dimensional supergravity, the low energy limit of $M$-theory, following \cite{RSW}.
+In this twist, the theory is holomorphic in a maximal number of directions, which is five complex directions, and topological in the remaining real direction. 
+Surprisingly, there is a novel relationship between this theory and a certain exceptional simple super Lie algebra called $E(5|10)$. 
+On flat space, $\R \times \C^5$ we have shown that our description yields a presentation of the algebra of local operators which takes the following form 
+\beqn
+\clie^\bu\left(\Hat{E(5|10)}\right) .
+\eeqn
+This is the Chevalley--Eilenberg complex (computing Lie algebra cohomology) of a particular central extension of the super Lie algebra $E(5|10)$. 
+We emphasize that this statement about local operators is only interesting when one works in the Batalin--Vilkovisky formalism taking into account all ghosts, fields, anti-fields, etc..
+
+There is another exceptional super Lie algebra around when one starts to consider fivebranes inside of eleven-dimensional supergravity. 
+In this twist, fivebranes are completely holomorphic objects which, in flat space, wrap three complex directions in the eleven-dimensional bulk theory
+\beqn
+\C^3 \subset \R \times \C^5 .
+\eeqn
+An important facet of the wordvolume theory associated to a stack of fivebranes in $M$-theory is that it is a superconformal theory with $\cN=(2,0)$ supersymmetry.
+
+In six dimensions (after complexifying) the superconformal algebra is the super Lie algebra $\lie{osp}(8|4)$, whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
+Twisting involves the choice of a holomorphic supercharge $Q$ which leaves three directions invariant and breaks this super Lie algebra down to the smaller super Lie algebra $\lie{osp}(6|2)$.
+The $Q$-twist of any six-dimensional superconformal field theory has a symmetry by this super Lie algebra.
+
+As we just pointed out, the super Lie algebra $E(5|10)$ (or rather its central extension) describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist. 
+It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $E(5|10)$. 
+In fact, $\lie{osp}(6|2)$ sits inside of a small (but still infinite-dimensional) super Lie algebra called $E(3|6)$.
+
+\begin{conj}[with Ingmar Saberi]
+After the holomorphic twist, the six-dimensional superconformal symmetry algebra gets enhanced to the exceptional simple super Lie algebra $E(3|6)$.
+As a consequence, after twisting, the space of local operators of any six-dimensional superconformal theory is a representation for $E(3|6)$.
+\end{conj}
+
+A consequence of this conjecture is that we can interpret, for example, the superconformal index as a character for $E(3|6)$. 
+For reference to future formulas, we point out that we choose a Cartan for $E(3|6)$ whose basis is labeled by the standard fugacities which are typically used to count the superconformal index.
+As we turn to holography, we would like to keep in mind this proposed large symmetry algebra which exists after twisting six-dimensional $\cN=(2,0)$ supersymmetry. 
+Fitting with this conjecture, we will identify our proposed spaces of local operators associated to the worldvolume theory on stacks of fivebranes with known representations for $E(3|6)$.
+
+\subsection{Our approach via twisted holography}
 Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of supersymmetric twists. 
@@
 In most examples the above principle is too naive as we are forgetting a key ingredient, the so-called backreaction of the branes. 
-On one hand, this deforms the geometric structure used to define the gravitational theory on $X - Y$---concretely, it will correspond to a certain deformation of the factorization algebra $(\Obs_{grav}|_{Y})^{!}$.
+This deforms the geometric structure used to define the gravitational theory on $X - Y$---concretely, it will correspond to a certain deformation of the factorization algebra $(\Obs_{grav}|_{Y})^{!}$.
 
@@
 Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
-After taking a certain classical limit, our conjectural description arises from a presentation of the $!$-dual as
+After taking a certain classical limit, this argument relies on a presentation of the $!$-dual as
 \beqn
-(\Obs_{grav}|_{Y})^{!} \simeq \cF_{-1} \otimes \cF_0 \otimes \cdots \cF_1 \otimes \cdots 
+(\Obs_{grav}|_{Y})^{!} \simeq \cF_{-1} \otimes \cF_0 \otimes \cF_1 \otimes \cdots 
 \eeqn
 for some factorization algebras $\cF_{-1},\cF_0, \cF_{1},\ldots$ which are defined using a certain weight decomposition of the bulk gravitational theory.
+In fact, this decomposition is intimately related to a certain decomposition of the exceptional simple super Lie algebra $E(5|10)$ that we have already mentioned plays an important role in the minimal twist of eleven-dimensional supergravity.
 The strange indexing conventions will be explained in \S\ref{eqn:fact}.
@@
 In other words, we simply truncate the tensor decomposition at order $N$.
+The surprising part is that the factorization algebras $\cF_k$ are directly identifiable from the point of view of the gravitational theory!
 
-A related theory is the minimal twist of the six-dimensional superconformal theory associated to a Lie algebra of type $A_{N-1}$.
+A related theory is the minimal twist of the six-dimensional $\cN=(2,0)$ superconformal theory associated to a Lie algebra of type $A_{N-1}$.
 We denote the corresponding factorization algebra by $\Obs_{A_{N-1}}$ for now. 
 This is obtained from the worldvolume theory simply by throwing away the modes propagating transverse to the brane, which in our presentation above corresponds to stripping off the first factor $\cF_{-1}$.
-Thus, at the level of factorization algebras we have a similar decomposition
+Thus, at the level of factorization algebras we have a similar proposed decomposition
 \beqn
-\Obs_{A_{N-1}} = \cF_0 \otimes \cF_1 \otimes \cdots \otimes \cA_{N-1} .
+\Obs_{A_{N-1}} = \cF_0 \otimes \cF_1 \otimes \cdots \otimes \cF_{N-2} .
 \eeqn
 
-We want to emphasize that these expressions only hold after taking this classical limit.
+We want to emphasize that these expressions only hold after taking this classical limit and taking some truncation of the differential present which is present on the left-hand side.\footnote{An instructive avatar of this decomposition to keep in mind is the description of the $W_N$ vertex algebra as being generated by a collection of operators of spins $2,3,\ldots, N$.
+Only in the classical limit does the $W_N$ vertex algebra decompose as a pure tensor product.}
 This decomposition as a tensor product of factorization algebras will break down at the quantum level.
@@
 On one hand, we have the index of multi-particle states of the supergravity theory on the manifold obtained by removing the location of the brane; we denote this by $\chi_{grav}({\bf x})$.
-It is a function of some number of fugacities ${\bf x}$ which we will discuss explicitly in our examples momentarily. 
+It is a function of the fugacities ${\bf x}$ which in this setting are given by coordinate functions on the four-dimensional Cartan subalgebra of~$\lie{osp}(6|2)$.
 Typically, this multi-particle index can be obtained from the single-particle index $f_{grav}({\bf x})$ of gravitational states through the plethystic exponential. 
@@
 \beqn
-\cF_{-1}(0) \otimes \cdots \otimes \cF_{N-2}(0) ,
+\cF_{-1}(0) \otimes \cF_0(0) \otimes \cdots \otimes \cF_{N-2}(0) ,
 \eeqn
@@
 For now, denote by $g_k({\bf x})$ the index of the vector space $V_k$.
+This quantity is directly computable from the gravitational side.
 
@@
 A related quantity is the index of the superconformal field theory associated to the Lie algebra $A_{N-1}$. 
-To obtain this we simply through away contributions coming from a single fivebrane, which results in the expression
+To obtain this we simply throw away contributions coming from a single fivebrane, which results in the expression
 \beqn
@@
 In ~\S\ref{s:finite} we will show that for small values of $N$ our closed of formulas, when appropriately expanded, agree with approximations which have been found in the literature.
+We will also check that a number of specializations of the fugacities agree with certain unrefined indices which have been computed via other means.
 Even stronger evidence would involve the factorization algebras $\Obs_{brane}(N)$, and we will briefly sketch how this should go in later sections but leave a full treatment to future work.
 
-To get an even better handle on our conjectural description we focus on the case~$N=2$.
+To state some explicit results and to make concrete conjectures for these indices we will take a look at small values of~$N$.
 
-\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
+\subsection*{The abelian $\cN=(2,0)$ theory}
 
-The first ingredient we need 
-In \S\ref{s:twisted} we will recall a description of the minimal twist of eleven-dimensional supergravity following \cite{RSW} which is
+The abelian six-dimensional $\cN=(2,0)$ theory is the worldvolume theory on a single fivebrane. 
+It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
+In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given---it defines a complex three-dimensional factorization algebra that we will denote by $\Obs_1$.
+In this paper we only consider the classical limit of this factorization algebra, but there is a simple quantization of its natural shifted Poisson structure which we will use in this section.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}
+
+The superconformal index can be computed from the local character of the factorization aglebra $\Obs_1$. 
+We recover the standard formulas in the literature in terms of the five fugacities $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$, see for instance \cite{Kim:2013nva}.
+
+Let us place this factorization algebra on the threefold $\C^\times \times \C^2$ and consider the reduction along the circle $S^1 \subset \C^\times$. 
+In \cite{SWtensor} we have shown that the naive dimensional reduction (where we throw out higher Kaluza--Klein modes along $S^1 \subset \C^\times$) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of perturbative supersymmetric Yang--Mills theory for the group $U(1)$.
+If we keep track of Kaluza--Klein modes, our ansatz is that the full dimensional reduction 
+\beqn
+\oint_{S^1} \Obs_1
+\eeqn
+is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from monopole operators.
+In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.
+
+There is a nice relationship to the AGT correspondence which we can remark on in this abelian case. 
+In the notation we are using for fugacities, the so-called Schur limit of the superconformal index is simply $y_1=y=1$.
+For the abelian theory this immediately gives the function $\frac{q}{1-q}$ which is the well-known vacuum character of the Heisenberg vertex algebra. 
+Geometrically, the Schur limit corresponds to working with an equivariant version of the Hilbert space.
+In this setting, this is the equivariant cohomology of the moduli space of instantons of rank one.
+This specialization then agrees with the famous result of Nakajima which characterizes the equivariant cohomology of the moduli space of rank one instantons (also known as the Hilbert scheme of points) with the Heisenberg vacuum module.
+
+If we return to six dimensions, one can use the radial direction in $\C^\times \times \C^2$ to endow the factorization algebra $\oint_{S^1} \Obs_1$ with the structure of an (dg) associative algebra. 
+This Schur limit corresponds to a particular deformation of this algebra by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$.
+We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}.
+One can identify (though we do not do that in this paper) this deformation of $\oint_{S^1} \Obs_1$ with the Heisenberg algebra.
+
+\subsection*{The $\cN=(2,0)$ theory of type $A_1$}
+
+\begin{conj}\label{conj:6dtwo}
+The superconformal index of the six-dimensional $\cN=(2,0)$ theory of type $A_1$ is 
+\[
+\chi_{A_1} (y_i,y,q) = {\rm PExp} \left[f_{A_1}(y_i,y,q) \right] .
+\]
+where the single particle index $f_{A_1}(y_i,y,q)$ is 
+\beqn\label{eqn:A1}
+\frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
+\eeqn
+\end{conj}
 

### 2022-09-19 fivebranes/index.tex
direct image

@@
 Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
-The partial connection yields a splitting of the exact sequence
+The situation is summarized in the diagram below.
 
 \[
-  0 \to F_{M}\cap T_{M/Z}^{\C}\to F_{M}\to \pi^{*}T^{0,1}_{Z}\to 0
+  \begin{tikzcd}
+    0 \ar[r] & F_{M}\cap T_{M/Z}^{\C}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
+    0 \ar[r] & T_{M/Z}^{\C}\ar[r] & T_{M}^{\C}\ar[r] & T_{Z}^{\C}\ar[r] & 0.
+  \end{tikzcd}
 \]
 
-Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that that the splitting preserves the lie brackets on sections.
+The existence of a partially flat connection amounts to a choice of splitting \[\sigma: \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row.
+Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that $\sigma$ preserves the lie brackets on sections.
+
+We have a similar diagram expressing that the sphere bundle $\mathring M \to \R_{>0}\times Z$ is a map of THF manifolds when both the domain and codomain are equipped with the induced THF structures.
+\[
+  \begin{tikzcd}
+    0 \ar[r] & F_{\mathring M}\cap T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r]\ar[d] & F_{\mathring M}\ar[r]\ar[d]  & h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
+    0 \ar[r] & T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r] & T_{\mathring M}^{\C}\ar[r] & h^{*}T_{\R_{>o}}\oplus T_{Z}^{\C}\ar[r] & 0.
+  \end{tikzcd}
+\]
+
+We
 \end{proof}

### 2022-09-19 fivebranes/intro.tex
merge
sl2

@@
 Fitting with this conjecture, we will identify our proposed spaces of local operators associated to the worldvolume theory on stacks of fivebranes with known representations for $E(3|6)$.
+
+We will see throughout this paper that the so-called Schur limit of our superconformal index agrees with the vacuum character of well-studied vertex algebras. 
+Field theoretically, the Schur limit corresponds to a certain deformation of a six-dimensional superconformal theory \cite{Beemetal}. 
+Upon performing this deformation, the super Lie algebra $E(3|6)$ deforms to a familiar object in chiral CFT: the Lie algebra of vector fields on the (formal) disk.
+So, if we were to deform the conjecture above according to this Schur limit we would recover the familiar consequence that a chiral conformal field theory has as part of its symmetries the Lie algebra of vector fields on the formal disk.
+Of course, there is a richer algebra around---the Virasoro algebra---which extends the Lie algebra of vector fields on the {\em punctured} disk. 
+We will say more about a six-dimensional lift of this object later on in this introduction.
 
@@
 
-To state some explicit results and to make concrete conjectures for these indices we will take a look at small values of~$N$.
+One of the most attractive features of the six-dimensional theory associated to the Lie algebra of type $A_{N-1}$ is through its relationship to the famous correspondence of Alday, Gaiotto, and Tachikawa \cite{AGT}.
+On the four-dimensional side, the key player is the equivariant cohomology of the moduli space of instantons of type $A_{N-1}$. 
+The six-dimensional theory of type $A_{N-1}$ explains a powerful relationship between this object and a certain chiral conformal field theory. 
+We anticipate, though do not prove any statements in the spirit of the AGT correspondence in this paper, that our factorization algebras $\Obs_{A_{N-1}}$ have the ability to \brian{not sure what's a good way to say this.}
+To state some explicit results and to make concrete conjectures at the level of the superconformal index we will take a look at small values of~$N$.
 
@@
 One can identify (though we do not do that in this paper) this deformation of $\oint_{S^1} \Obs_1$ with the Heisenberg algebra. 
+Thus, we expect that the dg algebra $\oint_{S^1} \Obs_1$, {\em before} deforming, should act on the non-equivariant cohomology of the moduli space of instantons of rank one.
 
 \subsection*{The $\cN=(2,0)$ theory of type $A_1$}
+
+The first major conjecture that we make is for an expression for the algebra of local operators $\Obs_{A_1}(0)$, or really the factorization algebra $\Obs_{A_1}$, of the holomorphic twist of the $\cN=(2,0)$ theory associated to a Lie algebra of type $A_1$.
+At the level of the superconformal index, we can state the concrete expectation now.
 
@@
 \eeqn
+We follow the same conventions for fugacities as in \cite{Kim:2013nva}. 
 \end{conj}
+
+%In \S \ref{s:fact} we will explain a conjecture for the classical limit of $\Obs_{A_1}$ as a factorization enveloping algebra of a certain local Lie algebra enhancement of $E(3|6)$.
+
+Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactifying $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
+From our conjectural description of $\Obs_{A_1}$ (we denote this factorization algebra by $\til\Obs_2$ in the body of the paper) given in \S \ref{s:fact}, one can see that this classical limit of the associative dg algebra is of the form
+\beqn
+U \left(\cE(3|6)|_{\C^\times \times \C^2}\right) .
+\eeqn
+This is meant to indicate the enveloping algebra of a super Lie algebra $\cE(3|6)|_{\C^\times \times \C^2}$ which is a `punctured' version of the exceptional simple super Lie algebra $E(3|6)$. 
+In particular, $E(3|6)$ sits inside this super Lie algebra as the positive modes.
+Again, in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory. 
+At the quantum level, we expect that the algebra gets deformed to the enveloping algebra of a certain ($L_\infty$) central extension of this super Lie algebra.
+
+\begin{conj}
+The associative dg algebra $\oint_{S^1} \Obs_{A_1}$ (after turning on this central extension) acts on the cohomology of the moduli space of $SU(2)$-instantons on flat space~$\C^2 = \R^4$. 
+\end{conj}
+
+Let us summarize some evidence for this claim which is in line with the AGT correspondence. 
+First off, the Hilbert space of the five-dimensional theory is simply given as the space of local operators $\Obs_{A_1}(0)$.
+The Schur limit of the superconformal index, which is the character of this space of local operators, is precisely the character of the Virasoro vacuum module $\frac{q^2}{1-q}$.
+Furthermore, the algebra $\oint_{S^1} \Obs_{A_1}$ naturally acts on this space, and we expect that deforming this algebra in accordance with the Schur limit is exactly the Virasoro algebra $U(\text{Vir})$.
 
@@
 
-In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\cN=(2,0)$ \cite{} and three-dimensional $\cN=8$ \cite{} superconformal field theories.
-
 \end{document}

### 2022-09-20 fivebranes/finite.tex
minimally reduced

@@
 \begin{array}{lllll}
-g_k (y_i,y,q) \define & q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)\chi_{[1,0]}(y_i) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
-&\displaystyle \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) \chi_{[0,1]}(y_i) \right)}{d(y_i,y,q)} .
+g_k (y_i,y,q) \define & q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)\chi^{\lie{sl}(3)}_{[1,0]}(y_i) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
+&\displaystyle \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) \chi^{\lie{sl}(3)}_{[0,1]}(y_i) \right)}{d(y_i,y,q)} .
 \end{array}
@@
 
+\parsec[]
+
+We would also like to point out compatibility of our expression with a certain ``minimally reduced'' index considered in \cite{GaiottoJihoon}. 
+This minimal reduction is the result of sending certain parameters to zero while keeping some expression in the fugacities fixed.
+To consider it it is useful to make the following change of variables: 
+\beqn
+z_i = y_i q, \quad w_1 = yq, \quad w_2 = y^{-1} q^2 .
+\eeqn
+These variables satisfy the constraint $z_1 z_2 z_3 = w_1 w_2$.
+
+The limit that we consider is 
+\beqn\label{eqn:limitgaitto}
+z_3 , w_2 \to 0 .
+\eeqn
+This will result in an index which has three remaining fugacities.
+
+\begin{prop}
+\label{prop:gaiotto}
+The limit $z_3 , w_2 \to 0$ of the expression $\chi_{N}(z_i,w_a)$ is 
+\beqn
+\prod_{a=1}^N \prod_{b,c \geq 0} \frac{1-w_1^{a-1}z_1^{b+1} z_2^{c+1}}{1-w_1^a z_1^b z_2^c} .
+\eeqn
+\end{prop}
+\begin{proof}
+It is easy to see that the $z_3,w_2 \to 0$ limit of $g_{-1}$ is 
+\beqn
+g_{-1}(z_1,z_2,w_1) = \frac{w_1 - z_1 z_2}{(1-z_1)(1-z_2)} 
+\eeqn
+and the $z_3,w_2 \to 0$ limit of $g_0$ is 
+\beqn
+g_0(z_1,z_2,w_3) = w_1 g_{-1}(z_1,z_2,w_1) .
+\eeqn
+
+In the coordinates $z_i,w_a$ the expression $g_k$, for $k \geq 1$, in \eqref{eqn:gk} can be written as
+\beqn
+\label{eqn:gk}
+\begin{array}{lllll}
+g_k (z_i,w_a) \define & \left( z_1z_2z_3 p_k(w_1,w_2) (z_1+z_2+z_3) + p_{k+2}(w_1,w_2)  \right. \\
+&\displaystyle \frac{\left.  -z_1z_2z_3 p_{k-1}(w_1,w_2) - p_{k+2}(w_1,w_2) (z_1z_2+z_2z_3+z_1z_3) \right)}{(1-z_1)(1-z_2)(1-z_3)} .
+\end{array}
+\eeqn
+Here $p_k(w_1,w_2) = \sum_{i+j=k} w_1^i w_2^j$.
+
+From this expression it is easy to see that $\lim_{z_3,w_2 \to 0} g_k$ is 
+\beqn
+g_k(z_1,z_2,w_1) = w_1^{k+1} g_{-1}(z_1,z_2,w_1) .
+\eeqn
+The result follows from applying the plethystic exponential.
+\end{proof}
+
+The $z_3,w_2 \to 0$ limit of our index is quite similar, though not exactly, the index of a four-dimensional $\cN=1$ theory.
+
 \subsection{Comparisons to expansions of superconformal indices}

### 2022-09-20 fivebranes/intro.tex
abstract

@@
-\documentclass[11pt]{amsart}
+%\documentclass[11pt]{amsart}
+%
+%\linespread{1.15} %for editing
+%
+%%\usepackage{../macros-master}
+%\usepackage{macros-fivebrane}
 
-\linespread{1.15} %for editing
-
-%\usepackage{../macros-master}
-\usepackage{macros-fivebrane}
-
-\begin{document}
+%\begin{document}
 
@@
 
-Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactifying $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
+Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactify $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
 From our conjectural description of $\Obs_{A_1}$ (we denote this factorization algebra by $\til\Obs_2$ in the body of the paper) given in \S \ref{s:fact}, one can see that this classical limit of the associative dg algebra is of the form

### 2022-09-20 fivebranes/main.tex
outline
all around
removed preambles in included files, formatting
merge
main
abstract

@@
 
-%\linespread{1.2} %for editing
+\linespread{1.15} %for editing
 
@@
 
-\newcommand\thooft{`t Hooft\,}
-
 \begin{document}
 
-\title{}
+\title{A holomorphic approach to branes in twisted~$M$-theory}
+\maketitle
 
+\begin{abstract}
+We present a conjectural description of the algebra of operators on a stack of finitely many fivebranes in $M$-theory at the level of the holomorphic twist.
+Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
+From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional theories of type $A_{N-1}$.
+\end{abstract}
+
+\setcounter{tocdepth}{1}
+\tableofcontents
+
+\input{intro}
+
+\subsection*{Acknowledgements}
+We thank K.~Costello, D.~Gaiotto, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
+Special thanks are due to Ingmar Saberi for his collaborations on past, current, and future related projects.
+The work of S.R. ...
+The work of B.W. was supported by Boston University and the University of Edinburgh. 
+%Twisted supergravity
+\input{twisted}
+
+%The character of holomorphic local operators
+%%introduce local operators for hol/top theories.
+%%introduce hol characters for hol/top theories. 
+%%example of a single fivebrane
+%%example of a single membrane
+%%Large N limit.
 \input{index}
 
+%Factorization algebras in twisted M theory
+%%`Restricted' factorization algebra.
+%%Koszul duality.
+
+\input{fact}
+%A holographic decomposition of local operators
+%%E(3|6) decomposition of local operators. 
+%%character computations following KR resolutions.
+%%E(1|6) decomposition of local operators. 
+%%some finite N membrane indices??
+
+\input{ops}
+
+\input{finite}
+
+%%backreaction for single fivebrane.
+
+%%\input{??}
+
+\printbibliography
+
 \end{document}

### 2022-09-20 fivebranes/twisted.tex
direct image and general background

@@
 
-\section{Twists in dimensions eleven, six, and three}
+\section{Twists in dimensions eleven and six}
 \label{s:twisted}
@@
 
-Before proceeding with the appearance of extended objects such as membranes and fivebranes in the minimal twist of eleven-dimensional supergravity we discuss a related, but simpler, five-dimensional theory.
+Before proceeding with the appearance of fivebranes in the minimal twist of eleven-dimensional supergravity we discuss a related, but simpler, five-dimensional theory.
 This five-dimensional theory, as argued by Costello \cite{CostelloM5}, arises from placing eleven-dimensional supergravity in the so-called `twisted $\Omega$-background'.
@@
 
+\subsection{A more general background}
+
+The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.
+More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.
+For general background on the theory of THFs we refer the reader to \cite{DuchampKalka, KamberTondeur, Rawnsley}.
+
+A THF structure on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
+Equivalently, this allows you to choose an atlas of coordinates $(t_i, z_j)$ on $M$ which transform smoothly in the $t_i$-variables and holomorphically in the $z_j$-variables. 
+Accordingly, we may take a local patch in a THF manifold to be of the form $\R^m \times \C^n$.
+%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
+%he product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $M$ along the projection.
+%Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
+The bundle $F$ is locally spanned by the vector fields $\partial / \partial t_i$'s and $\del/\del \zbar_j$'s.
+(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
+We will say that $M$ is of dimension $(m,n)$ (so it is a manifold of real dimension $m + 2n$).
+
+Associated to a foliation $F$, its normal bundle is the quotient bundle $Q = T^{\C}_{M}/F$.
+We assume in addition to having a THF structure that $M$ is equipped with the data of a trivialization $\wedge^{n} Q^* \cong \C_{M}$ which we will denote by~$\Omega_F$.
+We require that the trivialization is constant along the leaves of $F$, i.e.
+that $D\Omega_{F} = 0$.
+If $F \cap \Bar{F} = 0$, then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
+For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure.
+
+There is a notion of the sheaf of `holomorphic functions' $\cO_F$ on any manifold $M$ equipped with a THF~$F$---in the language of foliations these are the functions on $M$ which are constant along the leaves of $F$.
+Locally, on a coordinate patch it is given by functions which only depend on the holomorphic variables $z_i$.
+There is a resolution $\cA^\bu_F$ for $\cO_F$ by locally free sheaves on $M$ which is the THF analog of the de Rham and Dolbeault complexes. 
+In degree zero $\cA^0_F$ is just the sheaf of smooth functions on $M$.
+In degree $k$ one takes $\cA^k_F$ the sheaf of sections of the bundle $\wedge^k F^*$.
+The derivative along the leaves of the foliation defined by $F$ defines a map of sheaves
+\[
+\thfd \colon \cA^{q}_F \to \cA^{q+1}_F  .
+\]
+By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and one can show that the natural map $\cO_F \xto{\simeq} \cA^\bu_F$ provides a resolution.
+% and so $\thfd$ equips $\cA^{\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
+Locally in a split THF structure like $\R^m \times \C^n$ the operator $\thfd$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
+
+The fields of our eleven-dimensional theory may be described as sheaves of flat sections of some natural partially flat bundles on $M$.
+First, we note that the bundle normal bundle $Q$ and its dual $Q^{*}$ admit a natural connection defined along the leaves of $F$, the so-called Bott connection \cite{KamberTondeur}.
+
+There is also the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
+Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
+Let $\theta_F$ be the bundle $T_M ^{\C} / F$ on $M$ and declare
+$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
+Then we obtain a resolution
+\beqn
+\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
+\eeqn
+The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.
+
+Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
+Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.
+
+We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
+Let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
+\beqn\label{eqn:drdol}
+\Omega^{\bu}(S) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(S) \otimes \Omega^{1,\bu}(X) .
+\eeqn
+As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
+There is an analog of this operator $1 \otimes \del$ on a manifold $M$ equipped with a THF~$F$.
+It is a differential operator 
+\beqn
+D \colon \cA^{p,\bu}_F \to \cA^{p+1,\bu}_F
+\eeqn
+which locally is just the holomorphic de Rham operator. 
+This operator commutes with $\thfd$.
+The generalized $\beta$ and $\gamma$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F \xto{D} \cA^{1,\bu}_F$.
+
+\newcommand\Div{D_\Omega}
+
+Next we should say where the generalized $\mu$ and $\nu$ fields live. 
+The volume form $\Omega_F \colon \C \cong \wedge^n \theta_F^*$ determines an isomorphism $\cA^{p,q}_F \cong \cA^{n-p,q}_F$ for each $p,q$.
+Via this isomorphism we can identify $D \colon \cA^{n-1,\bu}_F \to \cA^{n,\bu}_F$ with a differential operator
+\beqn
+\Div \colon \cA_F^{\bu}(\theta_F) \to \cA^\bu_F .
+\eeqn
+The $\mu$ and $\nu$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F(\theta_F) \xto{\Div} \cA^\bu_F$. 
+This resolves the THF version of the sheaf of holomorphic vector fields on $M$ which preserve the form $\Omega_F$.
+
+Now we are in a place to describe a BV theory defined on an eleven-manifold $M$ equipped with a THF $F$ and a volume form $\Omega_F$ on the leaf space.
+The space of fields of the theory consist of fields $\beta,\gamma, \mu, \nu$ as before but where
+\beqn
+\beta \in \Pi \cA_F^\bu (M) , \quad \gamma \in \cA^{1,\bu}_F (M) , \quad \mu \in \Pi \cA^\bu_F(M, \theta_F), \quad \nu \in \cA_F^\bu (M)  .
+\eeqn
+Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$. 
+The free part of the action functional (cf. \eqref{eqn:free}) is 
+\beqn
+\int_M (\gamma \thfd \mu) \Omega_F + \int_M (\beta \thfd \gamma) \Omega_F + \int_M (\beta \Div \mu) \Omega_F .
+\eeqn
+The interaction (cf. \eqref{eqn:int}) is
+\beqn
+\label{eqn:int}
+\frac12 \int_{M} (\mu^2 D \gamma) \frac{\Omega_F}{1- \nu} + \frac16 \int_{M} \gamma D \gamma D \gamma .
+\eeqn
+If we assume that $\nu = \Div \mu = 0$ we recover the following equation of motion upon varying $\gamma$
+\beqn
+\thfd \mu + \frac12 [\mu,\mu] = D \gamma D \gamma .
+\eeqn
+This is a generalization of equation \eqref{eqn:eom2} for a general THF $F$ on the eleven-manifold~$M$.
+
 \subsection{Twisted fivebranes}
-
-%\subsection{Twisted AdS backgrounds}
 
@@
 
-\subsection{Twisted membranes}
-
-The theory on a stack of $N$ membranes probing the origin in $\C^{4}/\Z_{k}$ is expected to be described by the ABJM theory---a 3d $\cN=6$ superconformal gauge theory with gauge group $U(N)\times U(N)$ at levels $\pm k$ respectively \cite{Aharony:2008ug}.
-For $k=1,2$ the theory witnesses an enhancement to $\cN=8$ due to a nonperturbative effect \cite{Bagger:2007jr,Gustavsson:2007vu}.
-
-Twists of three-dimensional $\cN=8$ supersymmetric gauge theories were classified and characterized in \cite{ESsusy,ESW,Garner:2022vds}. 
-Moreover, the ABJM theories are examples of three-dimensional $\cN=2$ Chern-Simons matter theories, whose twists were studied in \cite{Aganagic:2017tvx}. 
-Twists of such occur in two inequivalent classes, similarly labeled by the dimension of the subspace of translations given by the image of the twisting supercharge:
-
-\begin{itemize}
-  \item The minimal twist.
-This twist leaves two real directions invariant.
-The theory can be defined on a three-manifold of the form $S\times C$ where $S$ is a smooth oriented one-manifold and $C$ is a Riemann surface equipped with a fourth-root of its canonical bundle.
-
-  \item The nonminimal twists. There are two such twists, both of which leave three real directions invariant, and are permuted under three-dimensional mirror symmetry.
-\end{itemize}
-
-\parsec
-
-We briefly recall the description of the minimal twist of the ABJM theory associated to the single membrane theory.
-Let $K^{1/4}_C$ be a fourth-root of the canonical bundle of $C$. 
-In the BV formalism, this free theory has underlying space of fields
-\[
-\Omega^{\bu}(S) \hotimes \left[ \Pi \Omega^{0,\bu}(C, K^{1/4}_C \otimes U) \oplus \Omega^{0,\bu} (C,K^{3/4}_C \otimes U^*) \right] 
-\]
-where $W\cong \C^4$ is the fundamental $\lie{sl}(4)$ representation.
-The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
-If we split the fields according to the direct sum above by $X, \Psi$ then the action is simply
-\[
-\int_{S \times C} \Psi \d_S X + \int_{S \times C} \Psi \dbar_\Sigma X .
-\]
-Here, we have implicitly chosen a non-degenerate symmetric pairing on $\C^4$.
-
-\subsection{A more general background}
-
-The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.
-More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.
-For general background on the theory of THFs we refer the reader to \cite{DuchampKalka,Rawnsley}.
-
-A THF structure on a smooth manifold $M$ is an integrable subbundle $F \subset \T_M \otimes \C$ such that $F + \Bar{F} = \T_M \otimes \C$.
-Equivalently, this allows you to choose an atlas of coordinates $(t_i, z_j)$ on $M$ which transform smoothly in the $t_i$-variables and holomorphically in the $z_j$-variables. 
-So, locally we may take a local patch in a THF manifold to be of the form $\R^m \times \C^n$. 
-%Suppose $M$ is a manifold equipped with a THF structure and let $\cF$ be the corresponding foliation of even codimension.
-%he product $M = S \times X$, where $X$ is a complex manifold and $S$ is a smooth manifold has a natural THF structure with $F$ the restriction of the tangent bundle of $M$ along the projection.
-%Locally, any THF manifold is split of the form $\R^d \times \C^n$, whose coordinates we will denote by $(x_i ;  z_j)$.
-The bundle $F$ is locally spanned by the vector fields $\partial / \partial t_i$'s and $\del/\del \zbar_j$'s.
-(Notice that when $F \cap \Bar{F} = 0$ we are just describing an ordinary complex structure on $M$.)
-We will say that $M$ is of dimension $(m,n)$ (so it is a manifold of real dimension $m + 2n$).
-
-We will assume in addition to having a THF structure that $M$ is equipped with the data of a bundle isomorphism $\wedge^{n} (\T_M \otimes \C / F)^* \cong \C$ which we will denote by~$\Omega_F$. 
-If $F \cap \Bar{F} = 0$ then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
-For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure.
-
-There is a notion of the sheaf of `holomorphic functions' $\cO_F$ on any manifold $M$ equipped with a THF~$F$---in the language of foliations these are the functions on $M$ which are constant along the leaves of $F$.
-Locally, on a coordinate patch it is given by functions which only depend on the holomorphic variables $z_i$.
-There is a resolution $\cA^\bu_F$ for $\cO_F$ by locally free sheaves on $M$ which is the THF analog of the de Rham and Dolbeault complexes. 
-In degree zero $\cA^0_F$ is just the sheaf of smooth functions on $M$.
-In degree $k$ one takes $\cA^k_F$ the sheaf of sections of the bundle $\wedge^\bu F^*$.
-The derivative along the leaves of the foliation defined by $F$ defines a map of sheaves
-\[
-\thfd \colon \cA^{q}_F \to \cA^{q+1}_F  .
-\]
-By integrability one has $\thfd^2 = \thfd \circ \thfd = 0$ and one can show that the natural map $\cO_F \xto{\simeq} \cA^\bu_F$ provides a resolution.
-% and so $\thfd$ equips $\cA^{\bu} = \oplus_q \cA^{p;q}[-q]$ with the structure of a cochain complex for each $p$.
-Locally in a split THF structure like $\R^m \times \C^n$ the operator $\thfd$ is of the form $\d_{dR} + \dbar$ where $\d_{dR}$ is the de Rham differential along $\R^d$ and $\dbar$ is the Dolbeault operator along $\C^n$.
-
-There is also the notion of the sheaf of `holomorphic vector fields' $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$. 
-Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
-Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
-$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
-Then we obtain a resolution
-\beqn
-\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
-\eeqn
-The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.
-
-Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
-Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.
-
-We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-Let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
-\beqn\label{eqn:drdol}
-\Omega^{\bu}(S) \otimes \Omega^{0,\bu}(X) \xto{1 \otimes \del} \Omega^{\bu}(S) \otimes \Omega^{1,\bu}(X) .
-\eeqn
-As usual, we leave the $\d_{dR}$ and $\dbar$ operators implicit.
-There is an analog of this operator $1 \otimes \del$ on a manifold $M$ equipped with a THF~$F$.
-It is a differential operator 
-\beqn
-D \colon \cA^{p,\bu}_F \to \cA^{p+1,\bu}_F
-\eeqn
-which locally is just the holomorphic de Rham operator. 
-This operator commutes with $\thfd$.
-The generalized $\beta$ and $\gamma$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F \xto{D} \cA^{1,\bu}_F$.
-
-\newcommand\Div{D_\Omega}
-
-Next we should say where the generalized $\mu$ and $\nu$ fields live. 
-The volume form $\Omega_F \colon \C \cong \wedge^n \theta_F^*$ determines an isomorphism $\cA^{p,q}_F \cong \cA^{n-p,q}_F$ for each $p,q$.
-Via this isomorphism we can identify $D \colon \cA^{n-1,\bu}_F \to \cA^{n,\bu}_F$ with a differential operator
-\beqn
-\Div \colon \cA_F^{\bu}(\theta_F) \to \cA^\bu_F .
-\eeqn
-The $\mu$ and $\nu$ fields will be sections of the two-term complex of sheaves $\cA^\bu_F(\theta_F) \xto{\Div} \cA^\bu_F$. 
-This resolves the THF version of the sheaf of holomorphic vector fields on $M$ which preserve the form $\Omega_F$.
-
-Now we are in a place to describe a BV theory defined on an eleven-manifold $M$ equipped with a THF $F$ and a volume form $\Omega_F$ on the leaf space.
-The space of fields of the theory consist of fields $\beta,\gamma, \mu, \nu$ as before but where
-\beqn
-\beta \in \Pi \cA_F^\bu (M) , \quad \gamma \in \cA^{1,\bu}_F (M) , \quad \mu \in \Pi \cA^\bu_F(M, \theta_F), \quad \nu \in \cA_F^\bu (M)  .
-\eeqn
-Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$. 
-The free part of the action functional (cf. \eqref{eqn:free}) is 
-\beqn
-\int_M (\gamma \thfd \mu) \Omega_F + \int_M (\beta \thfd \gamma) \Omega_F + \int_M (\beta \Div \mu) \Omega_F .
-\eeqn
-The interaction (cf. \eqref{eqn:int}) is
-\beqn
-\label{eqn:int}
-\frac12 \int_{M} (\mu^2 D \gamma) \frac{\Omega_F}{1- \nu} + \frac16 \int_{M} \gamma D \gamma D \gamma .
-\eeqn
-If we assume that $\nu = \Div \mu = 0$ we recover the following equation of motion upon varying $\gamma$
-\beqn
-\thfd \mu + \frac12 [\mu,\mu] = D \gamma D \gamma .
-\eeqn
-This is a generalization of equation \eqref{eqn:eom2} for a general THF $F$ on the eleven-manifold~$M$.
-
 %More generally, there is a natural cohomology associated to a THF structure.

### 2022-09-20 fivebranes/twisted.tex
merge

--- 2022-08-22 fivebranes/twisted.tex
@@
 
+\parsec[s:e510]
+
+In the case that $X = \C^5$ and $S = \R$ the eleven-dimensional model we have just described bears a close relationship to the exceptional simple super Lie algebra $E(5|10)$ classified in \cite{KacClass}.
+The even part of $E(5|10)$ is the Lie algebra of divergence-free vector fields on the formal five-disk $\Hat{D}^5$. 
+The odd part of $E(5|10)$ is the space of closed two-forms $\Omega^{2,cl}(\Hat{D}^5)$ on the formal five-disk.
+There is a natural action of divergence-free vector fields on closed two forms. 
+Additionally there is a Lie bracket between two closed two-forms $\alpha,\alpha'$ which produces a divergence-free vector field via the standard holomorphic volume form on the five-disk:
+\beqn
+[\alpha,\alpha'] = \Omega_{\Hat{D}^5}^{-1} \vee ( \alpha \wedge \alpha' ) .
+\eeqn
+
+Given a vector bundle $E \to M$, the bundle of $\infty$-jets $J^\infty E \to M$ is a $\infty$-dimensional pro vector bundle whose sections consist of $\infty$-jets of sections of $E$.
+If $M = \R^d$ and $E$ is translation invariant, then the bundle of $\infty$-jets can be identified with $E_0 \times \C[[x_i]]$ where $\{x_i\}$ is a chosen coordinate on~$\R^d$. 
+The process of taking $\infty$-jets is well-behaved for local Lie algebras:
+the $\infty$-jets of a translation invariant local Lie algebra on $\R^d$ at a point carries the natural structure of a Lie algebra.
+
+In \cite{RSW} it is shown that the $\infty$-jets of $\cL_{sugra}$ at $0 \in \R \times \C^5$ is quasi-isomorphic to a central extension $\Hat{E(5|10)}$ of the super Lie algebra $E(5|10)$.
+The central extension is defined by the (totally even) three-linear cocycle
+\beqn\label{eqn:e510central}
+(\mu, \mu' , \alpha) \mapsto \<\mu \wedge \mu' , \alpha\>_{z=w=0} \in \C .
+\eeqn
+Since this is a three-linear functional the model we use for the central extension is a super $L_\infty$ algebra (with zero one-ary operation) rather than just a super Lie algebra.
+
 \parsec[s:twistedsugra]
@@
 In degree zero $\cA^0_F$ is just the sheaf of smooth functions on $M$.
-In degree $k$ one takes $\cA^k_F$ the sheaf of sections of the bundle $\wedge^\bu F^*$.
+In degree $k$ one takes $\cA^k_F$ the sheaf of sections of the bundle $\wedge^k F^*$.
 The derivative along the leaves of the foliation defined by $F$ defines a map of sheaves
@@
 Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
-$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
+$\cA^k(\theta_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^k F^* \otimes \theta_F$.
 Then we obtain a resolution

### 2022-09-20 fivebranes/index.tex

@@
 
-\begin{prop}
-  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
-  \beqn
-  \eeqn
-
-  where . The BV pairing is given by
-
-\end{prop}
-\begin{proof}
+We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}.
 Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
@@
 
-We
-\end{proof}
+\surya{conditions for top left to be a vector bundle}
+
+We claim that the splitting $\sigma$ induces a splitting $\mathring \sigma : h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}\to F_{\mathring M}$.
+\surya{is this obvious?} It is clear that $\mathring \sigma$ preserves lie brackets.
+
+For brevity, let $F_{\mathring M/\R_{>0}\times Z} = F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}$ and $p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}$.
+Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{F_{\R_{>0}\times Z}}$-module.
+
+The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
+\[
+  \cA^{\bu}_{F_{\mathring M}}(\cL)\cong \cA^{\bu}_{F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{F_{{\mathring M/ \R_{>0}\times Z}}}\otimes \cL
+\]
+
+Accordingly, the differential splits
+
+Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties.
+We may commute it past the tensor product above.
+Moreover, we may apply the functor term-wise.
+The result is that the pushforward is given by
+
+In sum, we have proven the following:
+
+\begin{prop}
+  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
+  \beqn
+  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL))\right)
+  \eeqn
+
+  The BV pairing is given by
+  \beqn
+  \int_{}
+  \eeqn
+
+\end{prop}
 

### 2022-09-20 fivebranes/twisted.tex

--- 2022-09-20 fivebranes/twisted.tex
@@
 Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
-Let $\theta_F$ be the bundle $T_M ^{\C} / F$ on $M$ and declare
-$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
+Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
+$\cA^k(\theta_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^k F^* \otimes \theta_F$.
 Then we obtain a resolution

### 2022-09-21 fivebranes/index.tex
merge error

@@
 We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}.
-Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
+Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
 The situation is summarized in the diagram below.
-
 \[
@@
 
-For brevity, let $F_{\mathring M/\R_{>0}\times Z} = F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}$ and $p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}$.
-Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{F_{\R_{>0}\times Z}}$-module.
+We wish to describe $\cA^{\bu}_{F}$-modules, for $F$ an involutive subbundle appearing in the top row of the above diagram.
+To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the directions in which the leaves lie.
+Explicitly, let $\cA_{\mathring M/\R_{>0}\times Z} = \cA_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}$, $F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}$ and $\cA_{\R_{>0}\times Z} = \cA_{\pi^{*} F _{\R_{>0}\times Z}}$.
+Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
 
@@
 \[
-  \cA^{\bu}_{F_{\mathring M}}(\cL)\cong \cA^{\bu}_{F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{F_{{\mathring M/ \R_{>0}\times Z}}}\otimes \cL
+  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}\otimes \cL
 \]
-
-Accordingly, the differential splits
 
@@
 Moreover, we may apply the functor term-wise.
-The result is that the pushforward is given by
+The result is that the pushforward is given by \surya{finish}
+
+In \cite{KormanThesis}, the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ is interpreted as defining a superconnection on the pushforward $\pi_{*}\cA^{\bu}_{\mathring M/R_{>0}\times Z}$ viewed as the sheaf of sections of a complex of pro-vector bundles on $\R_{+}\times Z$.
+
+\surya{finish}
 
@@
   \beqn
-  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL))\right)
+  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL), \thfd)\right)
   \eeqn
@@
 
+\end{prop}
+
+The model for the pushforward in the previous proposition appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KormanThesis} that converges to the cohomology with respect to the totalized differential $D+\thfd$ $H^{\bullet}(\cA_{\mathring M}(\cL), D+\thfd)$.
+In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where $M = Tot (\R\oplus \C^{2}\to \C^{3})$.
+We recall the result.
+Fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.
+
+\begin{prop}
+Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(\cL)), \thfD)$ is a direct sum of the cohomology on flat space $H^{\bu}(\gamma(\cA)$
 \end{prop}
@@
 
-After complexification, the~six-dimensional and three-dimensional superconformal algebras are isomorphic to $\lie{osp}(8|4)$.
+After complexification, the~six-dimensional superconformal algebra is isomorphic to $\lie{osp}(8|4)$.
 The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
 This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
-It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
+%It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
 
-In the six-dimensional case, the holomorphic supercharge is a supertranslation 
+The holomorphic supercharge is a supertranslation
 \[
@@
 
-Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
+%Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
 The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.
 
-In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
-Geometrically, this background is $AdS_7 \times S^4$.
+In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$.
+This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in \ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
 
-In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.
-
-We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
-As recalled above, such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$.
-We will enumerate states via choosing a Cartan in the bosonic subalgebra of the twisted superconformal algebra. 
+We will enumerate states via their weights a Cartan in the bosonic subalgebra of the twisted superconformal algebra.
 We recall below how the bosonic piece of the algebra
@@
 embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.
-The embedding is distinct for fivebranes and membranes.
-We turn first to the fivebrane case.
 
 \brian{enhance to E(3|6)}.
+However, we first note that the hilbert space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
 

### 2022-09-21 fivebranes/twisted.tex
merge error

@@
 
-There is also the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
-Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
-Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
-$\cA^k(\theta_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^k F^* \otimes \theta_F$.
-Then we obtain a resolution
+These furnish the notion of the sheaf of holomorphic vector fields $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$.
+These are the sheaves of sections of $Q$ and $Q^{*}$ that are flat with respect to the Bott connection.
+Locally, on $\R^m \times \C^n$ these are of the form $f^i \del / \del z_i$ and $f^{i}dz_{i}$ where each $f^i \in \cO_F$.
+
+Let $\cA^k(Q), \cA^{k}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have resolutions
+
 \beqn
-\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
+\vartheta_F \xto{\simeq} \cA^\bu(Q) \\
+\Omega^1_F \xto{\simeq}  \cA^\bu(Q^*)
 \eeqn
-The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.
-
-Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
-Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.
+The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(Q)$ the structure of a dg Lie algebra.
 
 We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-Let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
+focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
 \beqn\label{eqn:drdol}

### 2022-09-21 fivebranes/index.tex
prop 3.2

@@
 
+\surya{sloppy about hypercohomology}
 \begin{prop}
-Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(\cL)), \thfD)$ is a direct sum of the cohomology on flat space $H^{\bu}(\gamma(\cA)$
+  Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd)$ is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA)(L), \thfd)$ with the complex
+
+  \beeqn
+  \begin{tikzcd}[row sep = 1 ex]
+    + & - \\ \hline
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
+w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
+\end{tikzcd}
+\eeqn
 \end{prop}

### 2022-09-21 fivebranes/index.tex
ss

@@
 Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$.
-A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{}.
+A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{WittenHolography}.
 Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values.
@@
 
-We wish to describe $\cA^{\bu}_{F}$-modules, for $F$ an involutive subbundle appearing in the top row of the above diagram.
-To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the directions in which the leaves lie.
-Explicitly, let $\cA_{\mathring M/\R_{>0}\times Z} = \cA_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}$, $F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}$ and $\cA_{\R_{>0}\times Z} = \cA_{\pi^{*} F _{\R_{>0}\times Z}}$.
+For each of the involutive subbundles $F$ appearing in the top row of the above diagram, we wish to describe certain  To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the whether the leaves lie along the base or fiber of the submersion $p$.
+
+Explicitly, we set
+\begin{align*}
+  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}} \\
+  F_{\R_{>0}\times Z} &  = T_{\R_{>0}}\oplus T^{0,1}_{Z} \text{ so }p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z} \\
+  \cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}} \text{ so }p^{*}\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{p^{*}F _{\R_{>0}\times Z}}
+\end{align*}
+
 Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
@@
 \[
-  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}\otimes \cL
+  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L)
 \]
@@
 
-In \cite{KormanThesis}, the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ is interpreted as defining a superconnection on the pushforward $\pi_{*}\cA^{\bu}_{\mathring M/R_{>0}\times Z}$ viewed as the sheaf of sections of a complex of pro-vector bundles on $\R_{+}\times Z$.
-
+We now analyze the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
 \surya{finish}
@@
   \beqn
-  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL), \thfd)\right)
+  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu p_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
   \eeqn
@@
   \beqn
-  \int_{}
   \eeqn
@@
 
-The model for the pushforward in the previous proposition appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KormanThesis} that converges to the cohomology with respect to the totalized differential $D+\thfd$ $H^{\bullet}(\cA_{\mathring M}(\cL), D+\thfd)$.
-In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where $M = Tot (\R\oplus \C^{2}\to \C^{3})$.
-We recall the result.
-Fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.
+The previous result gives a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
+In particular, the result is local on $R_{>0}\times Z$.
+For computing the space of states, it will be useful to have a description of its global sections.
+For the computation of numerical invariants such as graded characters, of the space of states, a more drastic simplification is useful.
+Indeed, we may anticipate cohomological cancellations in the character and instead compute the character of any cochain complex that a spectral sequence whose first page is the global sections abuts to.
 
-\surya{sloppy about hypercohomology}
+The global sections of the sheaf in proposition \ref{dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
+\beqn
+E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q p _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
+\eeqn
+We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.
+
+In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
+\beqn
+M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
+\eeqn
+
+To recall the result, fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.
+
 \begin{prop}
-  Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd)$ is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA)(L), \thfd)$ with the complex
+  Up to completion, the cohomology
+  \beqn
+  \mathbb H^{\bu} (\cA_{\mathring M}^\bu (L) ) = H^{\bu}\left (\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd\right)
+  \eeqn
+  is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA_{M}^{\bu}(L), \thfd)$ with the complex
 

### 2022-09-21 fivebranes/index.tex
merge index

--- 2022-09-21 fivebranes/index.tex
@@
 The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization.
-The state spaces on ${\rm AdS}_{7}\times S^{4}$ and ${\rm AdS}_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras.
+The state spaces on $AdS_{7}\times S^{4}$ and $AdS_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras.
 We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
@@
 
-For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.
-\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
+For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
 We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
@@
 We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}.
-Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
+Recall that we have a THF structure on $M$, given by an involutive subsheaf $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
 The situation is summarized in the diagram below.
+
 \[
@@
 
-We wish to describe $\cA^{\bu}_{F}$-modules, for $F$ an involutive subbundle appearing in the top row of the above diagram.
-To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the directions in which the leaves lie.
-Explicitly, let $\cA_{\mathring M/\R_{>0}\times Z} = \cA_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}$, $F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}$ and $\cA_{\R_{>0}\times Z} = \cA_{\pi^{*} F _{\R_{>0}\times Z}}$.
-Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
+For brevity, let $F_{\mathring M/\R_{>0}\times Z} = F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}$ and $p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}$.
+Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{F_{\R_{>0}\times Z}}$-module.
 
@@
 \[
-  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}\otimes \cL
+  \cA^{\bu}_{F_{\mathring M}}(\cL)\cong \cA^{\bu}_{F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{F_{{\mathring M/ \R_{>0}\times Z}}}\otimes \cL
 \]
+
+Accordingly, the differential splits
 
@@
 Moreover, we may apply the functor term-wise.
-The result is that the pushforward is given by \surya{finish}
-
-In \cite{KormanThesis}, the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ is interpreted as defining a superconnection on the pushforward $\pi_{*}\cA^{\bu}_{\mathring M/R_{>0}\times Z}$ viewed as the sheaf of sections of a complex of pro-vector bundles on $\R_{+}\times Z$.
-
-\surya{finish}
+The result is that the pushforward is given by
 
@@
   \beqn
-  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL), \thfd)\right)
+  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL))\right)
   \eeqn
@@
 
-\end{prop}
-
-The model for the pushforward in the previous proposition appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KormanThesis} that converges to the cohomology with respect to the totalized differential $D+\thfd$ $H^{\bullet}(\cA_{\mathring M}(\cL), D+\thfd)$.
-In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where $M = Tot (\R\oplus \C^{2}\to \C^{3})$.
-We recall the result.
-Fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.
-
-\begin{prop}
-Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(\cL)), \thfD)$ is a direct sum of the cohomology on flat space $H^{\bu}(\gamma(\cA)$
 \end{prop}
@@
 
-After complexification, the~six-dimensional superconformal algebra is isomorphic to $\lie{osp}(8|4)$.
+After complexification, the~six-dimensional and three-dimensional superconformal algebras are isomorphic to $\lie{osp}(8|4)$.
 The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
 This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
-%It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
+It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
 
-The holomorphic supercharge is a supertranslation
+In the six-dimensional case, the holomorphic supercharge is a supertranslation 
 \[
@@
 
-%Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
+Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
 The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.
 
-In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$.
-This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in \ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
+In the untwisted situation, the symmetry of solutions to eleven-dimensional supergravity in the presence of fivebranes wrapping a six-dimensional affine subspace is exactly the superconformal algebra $\lie{osp}(8|4)$ (after complexification).
+Geometrically, this background is $AdS_7 \times S^4$.
 
-We will enumerate states via their weights a Cartan in the bosonic subalgebra of the twisted superconformal algebra.
+In \cite{RSW} we have proposed a twisted analog of the $AdS$ background and have shown that solutions to equations of motion of our eleven-dimensional theory in the presence of twisted fivebranes and membranes contains the symmetry algebra $\lie{osp}(6|2)$---which is precisely the twists of the superconformal algebras we just discussed.
+
+We will count the single-particle gravitational states in our eleven-dimensional model for the geometry resulting from backreacting twisted fivebranes and membranes.
+As recalled above, such states have a symmetry by the twisted superconformal algebra $\lie{osp}(6|2)$.
+We will enumerate states via choosing a Cartan in the bosonic subalgebra of the twisted superconformal algebra. 
 We recall below how the bosonic piece of the algebra
@@
 embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.
+The embedding is distinct for fivebranes and membranes.
+We turn first to the fivebrane case.
 
 \brian{enhance to E(3|6)}.
-However, we first note that the hilbert space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
 

### 2022-09-21 fivebranes/twisted.tex

@@
 
-Let $\cA^k(Q), \cA^{k}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have resolutions
+Let $\cA^k(Q), \cA^{k}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have fine resolutions
 
 \beqn
-\vartheta_F \xto{\simeq} \cA^\bu(Q) \\
-\Omega^1_F \xto{\simeq}  \cA^\bu(Q^*)
+\vartheta_F \xto{\simeq} \cA^\bu(Q) \ \ \ \ \ \ \ \Omega^1_F \xto{\simeq}  \cA^\bu(Q^*)
 \eeqn
 The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(Q)$ the structure of a dg Lie algebra.
+Likewise, the sheaf $\Omega^{1}_{F}$ carries the contragradient action of $\vartheta_{F}$ which likewise extends to equip $\cA^{\bu}(Q^{*})$ with the structure of a dg-module over $\cA^{\bu}(Q)$.
 
-We have expressed the fields of the eleven-dimensional theory in terms of a mixed type of de Rham and Dolbeault cohomology.
-focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
+The holomorphic derham and divergence operators also have analogues in the THF setting, which are now defined on the leaf space.
+First, for a vector bundle with  $\cA^{p,q}(Q)$ denote the sheaf of $C^{\infty}$ sections of $\wedge^{q} F^{*}\otimes \wedge^p Q$.
+The fields of the eleven-dimensional theory, which we phrased in terms of a mixed type of de Rham and Dolbeault cohomology, can now be elegantly repackaged in terms of the above.
+For illustration, let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
 \beqn\label{eqn:drdol}

### 2022-09-22 fivebranes/fact.tex
e36

@@
 \label{eqn:Gdecomp}
-\cG_Z = \bigoplus_{n \geq -1} \cG^{(n)} .
+\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
 \eeqn
@@
 %\[
-%\cG_Z (U)  \bigoplus_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
+%\cG_Z (U)  \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
 %\]
@@
 As a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
-We will prove the following.
+We will prove that it is equivalent to a local Lie algebra version of the exceptional super Lie algebra $E(3|6)$.
+
+By local version, we mean a version of $E(3|6)$ which exists as a sheaf of super Lie algebras of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$ on any complex threefold $Z$ equipped with a square-root of its canonical bundle.
+The even part of this sheaf is simply a semi-direct product 
+\beqn
+\Vect^{hol}(Z) \oplus \sl(2) \otimes \cO_Z .
+\eeqn
+Notice the similarity with the even part of $E(3|6)$ in equation \eqref{eqn:evenE36}. 
+The odd part is 
+\beqn
+\Omega^{1,hol}(Z, K^{-1/2}_Z) \otimes \C^2 
+\eeqn
+Again, we observe the similarities with the odd part of $E(3|6)$ given in equation \eqref{eqn:oddE36}. 
+The Lie bracket on this sheaf of super vector spaces is defined analogously to the bracket on $E(3|6)$. 
+In particular, the bracket operations only involve holomorphic differential operators and hence extends to a local dg super Lie algebra structure on the Dolbeault resolution of the above holomorphic vector bundles.
+We denote this local dg super Lie algebra by $\cE(3|6)$.
+
+When $Z = \C^3$ the $\infty$-jets at $0 \in \C^3$ of the local Lie algebra $\cE(3|6)$ is equivalent to the exceptional super Lie algebra $E(3|6)$.
 
@@
 %Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
-When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
 %More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.
@@
 %\beqn\label{eqn:decomp3}
-%\Bar{\pi}_{*} \cL_{sugra} = \bigoplus_{n \geq -1} \cV_{n} 
+%\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
 %\eeqn
@@
 \beqn\label{eqn:decomp1}
-E(5|10) = \til V_{-1} \times \bigoplus_{n \geq 0} V_n 
+E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
 \eeqn
@@
 \beqn\label{eqn:decomp2}
-\Hat{E(5|10)} = \bigoplus_{n \geq -1} V_n
+\Hat{E(5|10)} = \prod_{n \geq -1} V_n
 \eeqn
@@
 \[
-\cG = \bigoplus_{k \geq -1} \cG^{(k)} .
+\cG = \prod_{k \geq -1} \cG^{(k)} .
 \]
@@
 \beqn
-\til \cG \define \bigoplus_{k \geq 0} \cG^{(k)}
+\til \cG \define \prod_{k \geq 0} \cG^{(k)}
 \eeqn
@@
 \beqn
-F^N \cG = \cG^{(\geq N-2)} = \bigoplus_{j \geq N-2} \cG^{(j)} ,
+F^N \cG = \cG^{(\geq N-2)} = \prod_{j \geq N-2} \cG^{(j)} ,
 \eeqn

### 2022-09-22 fivebranes/index.tex
compilation error
index

@@
 The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. 
-The state spaces on $AdS_{7}\times S^{4}$ and $AdS_{4}\times S^{7}$ have a remarkable property---they are naturally modules for certain infinite-dimensional exceptional super Lie algebras.
+The state space on the twisted version of $AdS_{7}\times S^{4}$ has a remarkable property---it is naturally a module for a certain infinite-dimensional exceptional super Lie algebra. 
 We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
@@
 
-We now analyze the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
+We now analyze the THF differential $\thfd$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
 \surya{finish}
@@
 
-  \beeqn
+  \beqn
   \begin{tikzcd}[row sep = 1 ex]
@@
 In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$.
-This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in \ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
+This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
 
@@
 
-\brian{enhance to E(3|6)}.
-However, we first note that the hilbert space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
+However, we first note that the state space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
+
+\parsec
+Surprisingly, at the twisted level this symmetry by the super Lie algebra $\lie{osp}(6|2)$ is enhanced to a symmetry by an infinite-dimensional super Lie algebra called $E(3|6)$. 
+This is an exceptional simple super Lie algebra and was classified by Kac in \cite{KacClass}. 
+The even part $E(3|6)_{even}$ of this super Lie algebra is a semi-direct product 
+\beqn\label{eqn:evenE36}
+\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) 
+\eeqn
+where $\Vect(\Hat{D}^3)$ stands for the Lie algebra of (holomorphic) formal vector fields on the three-disk and $\cO(\Hat{D}^3)$ is the algebra of formal power series in three variables.
+The odd part $E(3|6)_{odd}$ is 
+\beqn\label{eqn:oddE36}
+\Omega^{1}(\Hat{D}^3, K^{-1/2}) \otimes \C^2  .
+\eeqn
+This is the tensor product of the fundamental $\lie{sl}(2)$ representation with the space of one-forms on the formal three-disk twisted by the line bundle $K^{-1/2}$.
+For a description of the Lie bracket we refer to \cite{KacClass}.
+%The non-obvious Lie bracket is of the form $E(3|6)_{odd} \otimes E(3|6)_{odd} \to E(3|6)_{even}$ and is defined by the composition
+
+The embedding $\lie{osp}(6|2)$ into $E(3|6)$ is described as follows.
+The even summand $\lie{sl}(4)$ simply embeds as the constant, linear, and quadratic vector fields which act on a formal neighborhood of $0 \in \C\mathbb{P}^3$.
+The even summand $\lie{sl}(2)$ embeds as the constant power series in $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$. 
+The odd summand $\C^3 \otimes \C^2$ embeds as the constant one-forms and the other odd summand embeds as the linear one-forms 
+\beqn
+\frac12 (z_i \d z_j - z_j \d z_i) \otimes w_a
+\eeqn
+where, here $i \ne j$ and the fundamental $\lie{sl}(2)$ representation is spanned by $w_1,w_2$.
+We are leaving out the twist by the $-1/2$ root of the canonical bundle for simplicity.
+
+\begin{prop}
+The state space $\cH_{sugra}$ is a representation for $E(3|6)$.
+The representation restricts to the original $\lie{osp}(6|2)$ representation under the embedding above.
+\end{prop}
+\begin{proof}
+\brian{Surya can you fill this in}
+\end{proof}
 
@@
 
-For convenience we choose coordinates on the eleven manifold as
+We move on to enumerating the state space $\cH_{sugra}$ on the twisted version of $AdS_7 \times S^4$ in terms of the index. 
+We choose coordinates on flat space as
 \[
@@
 
-The twisted supergravity states $\cH_{sugra}^{6d}$ form a representation for $\lie{osp}(6|2)$. 
+The twisted supergravity states $\cH_{sugra}$ form a representation for $\lie{osp}(6|2)$. 
 The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
@@
 
-We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH^{6d}_{sugra}$:
+We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH_{sugra}$:
 \beqn
-f^{6d}_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}^{6d}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
+f_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
 \eeqn
@@
 \label{prop:sugraindex1}
-The single particle index of the space of twisted supergravity states~$\cH_{sugra}^{6d}$ is given by the following expression
+The single particle index of the space of twisted supergravity states~$\cH_{sugra}$ is given by the following expression
 \beqn
 \label{eqn:sugra_index}
-f_{sugra}^{6d} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
+f_{sugra} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
 \eeqn
@@
 \beqn
-{\rm PExp}\left[f_{sugra}^{6d}(t_1,t_2,r,q)\right] .
+{\rm PExp}\left[f_{sugra}(t_1,t_2,r,q)\right] .
 \eeqn
@@
 \label{eqn:Kim_sugra}
-f_{sugra}^{6d} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
+f_{sugra} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
 \eeqn
@@
 (Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
-We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.
+%We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.
 
 \parsec 
-The specialization of this index $q=r^2, t_2=1$ in \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
+We consider the specialization of this index 
+\beqn
+q=r^2, t_2=1 
+\eeqn
+which is known as the Schur limit.
+Applying this limit to \eqref{eqn:special1} yields the plethystic exponential of the following single particle index
 \[
-f_{sugra}^{6d}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
+f_{sugra}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2}
 \]
+This plethystic exponential yields the MacMahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
 
-This plethystic exponential yields the Macmahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra.
-
-\parsec
-
-The specialization $t_1=t_2=r=1$ yields the single particle index
-\[
-f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
-\]
-
-\parsec The same change of variables in \eqref{eqn:special2} agrees with previously computed indices for single particle states for supergravity on $AdS_{7}\times S^{4}$
+%\parsec
+%
+%The specialization $t_1=t_2=r=1$ yields the single particle index
+%\[
+%f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
+%\]

### 2022-09-26 fivebranes/intro.tex
edits, reordering

@@
 Examples of such a quantity is the superconformal index, which is a generating function for some collection of $R$-charges of certain BPS local operators. 
-Crucial steps towards a more microscopic understanding of superconformal indices were taken in \brian{surya fill in this empty citation} \cite{}, articulated through the construction of twisting.
+Crucial steps towards a more mathematical understanding of superconformal indices were taken in \cite{HolomorphicCharacters}, articulated through the construction of twisting.
 
@@
 
-One of the insights of \brian{surya fill in this empty citation} \cite{} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
+One of the insights of \cite{HolomorphicCharacters} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
 Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. 
-Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set (for example, non-local operators obtained from local ones via a descent procedure).
+Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set including for example, non-local operators obtained from local ones via a descent procedure.
 
 A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
-As a factorization algebra encodes, in particular, the local operators of a theory we can extract from them familiar quantities like the superconformal index.
+As a factorization algebra encodes, in particular, the local operators of a theory, we can extract from them familiar quantities like the superconformal index.
+Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction.
+Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.
+
 %and three-dimensional $\cN=8$ superconformal field theories. 
-As is well-known, the six-dimensional~$\cN=(2,0)$ supersymmetric theory is quite elusive---it admits no known Lagrangian formulation, and outside of the abelian case, is not known to admit a field theoretic realization.
+Despite its ubiquity, the six-dimensional~$\cN=(2,0)$ supersymmetric theory is quite elusive---it admits no known Lagrangian formulation, and outside of the abelian case, is not known to admit a field theoretic realization.
 In light of this, we propose to access the minimal twist and its local operators via the proposal of \textit{twisted holography}.
-Before getting into the details of this proposal, we point out a collection of exceptional super Lie algebras which will play a pivotal role in our approach; and appear quite naturally from the point of view of twisted supergravity and twisted superconformal field theory.
-
-\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
-
-In \S\ref{s:twisted} we will recall a description of the minimal twist of eleven-dimensional supergravity, the low energy limit of $M$-theory, following \cite{RSW}.
-In this twist, the theory is holomorphic in a maximal number of directions, which is five complex directions, and topological in the remaining real direction. 
-Surprisingly, there is a novel relationship between this theory and a certain exceptional simple super Lie algebra called $E(5|10)$. 
-On flat space, $\R \times \C^5$ we have shown that our description yields a presentation of the algebra of local operators which takes the following form 
-\beqn
-\clie^\bu\left(\Hat{E(5|10)}\right) .
-\eeqn
-This is the Chevalley--Eilenberg complex (computing Lie algebra cohomology) of a particular central extension of the super Lie algebra $E(5|10)$. 
-We emphasize that this statement about local operators is only interesting when one works in the Batalin--Vilkovisky formalism taking into account all ghosts, fields, anti-fields, etc..
-
-There is another exceptional super Lie algebra around when one starts to consider fivebranes inside of eleven-dimensional supergravity. 
-In this twist, fivebranes are completely holomorphic objects which, in flat space, wrap three complex directions in the eleven-dimensional bulk theory
-\beqn
-\C^3 \subset \R \times \C^5 .
-\eeqn
-An important facet of the wordvolume theory associated to a stack of fivebranes in $M$-theory is that it is a superconformal theory with $\cN=(2,0)$ supersymmetry.
-
-In six dimensions (after complexifying) the superconformal algebra is the super Lie algebra $\lie{osp}(8|4)$, whose even part is $\lie{so}(8) \times \lie{sp}(4)$. 
-Twisting involves the choice of a holomorphic supercharge $Q$ which leaves three directions invariant and breaks this super Lie algebra down to the smaller super Lie algebra $\lie{osp}(6|2)$.
-The $Q$-twist of any six-dimensional superconformal field theory has a symmetry by this super Lie algebra.
-
-As we just pointed out, the super Lie algebra $E(5|10)$ (or rather its central extension) describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist. 
-It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $E(5|10)$. 
-In fact, $\lie{osp}(6|2)$ sits inside of a small (but still infinite-dimensional) super Lie algebra called $E(3|6)$.
-
-\begin{conj}[with Ingmar Saberi]
-After the holomorphic twist, the six-dimensional superconformal symmetry algebra gets enhanced to the exceptional simple super Lie algebra $E(3|6)$.
-As a consequence, after twisting, the space of local operators of any six-dimensional superconformal theory is a representation for $E(3|6)$.
-\end{conj}
-
-A consequence of this conjecture is that we can interpret, for example, the superconformal index as a character for $E(3|6)$. 
-For reference to future formulas, we point out that we choose a Cartan for $E(3|6)$ whose basis is labeled by the standard fugacities which are typically used to count the superconformal index.
-As we turn to holography, we would like to keep in mind this proposed large symmetry algebra which exists after twisting six-dimensional $\cN=(2,0)$ supersymmetry. 
-Fitting with this conjecture, we will identify our proposed spaces of local operators associated to the worldvolume theory on stacks of fivebranes with known representations for $E(3|6)$.
-
-We will see throughout this paper that the so-called Schur limit of our superconformal index agrees with the vacuum character of well-studied vertex algebras. 
-Field theoretically, the Schur limit corresponds to a certain deformation of a six-dimensional superconformal theory \cite{Beemetal}. 
-Upon performing this deformation, the super Lie algebra $E(3|6)$ deforms to a familiar object in chiral CFT: the Lie algebra of vector fields on the (formal) disk.
-So, if we were to deform the conjecture above according to this Schur limit we would recover the familiar consequence that a chiral conformal field theory has as part of its symmetries the Lie algebra of vector fields on the formal disk.
-Of course, there is a richer algebra around---the Virasoro algebra---which extends the Lie algebra of vector fields on the {\em punctured} disk. 
-We will say more about a six-dimensional lift of this object later on in this introduction.
 
@@
 Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of supersymmetric twists.
-Fundamentally, it conjectures a duality between the algebra of observables of the (twisted) gravitational theory and the algebra of observables of the gauge theory.
-There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory side.
-The type of twisted holography which is at play in this paper is a twisted version of the $AdS_7/CFT_6$ duality involving fivebranes inside of eleven-dimensional supergravity.
+Fundamentally, it conjectures a duality between the algebra of observables of a twisted gravitational theory and the algebra of observables of a twisted gauge theory describing the dynamics of a stack of branes coupled to the gravitational theory.
+There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory sides.
 
+To describe the kinds of theories on either side of the correspondence, we should comment on what it means to twist a theory of supergravity.
+We will provide more details in section \ref{sec:twisted}.
+Since the action of supersymmetry is gagued in theories of supergavity, the aforementioned twisting procedure does not quite make sense.
+Instead, Costello and Li define twisted supergravity to be the theory in perturbation theory around a background where the bosonic ghost for local supertranslations takes a nonzero nilpotent VEV.
+Coupling the worldvolume theory of a brane to such a background has the effect of twisting the worldvolume theory in the usual sense.
+
+It is expected that the 6d $\cN=(2,0)$ superconformal field theory of type $A_{N-1}$ describes the low energy dynamics of a stack of fivebranes in M-theory on flat space.
+Accordingly, there is a minimal twist of the low energy limit of M-theory, eleven-dimensional supergravity, which induces the minimal twist on a stack of fivebranes.
+We will be interested in a twisted version of the $AdS_{7}/CFT_{6}$ correspondence which will relate the large $N$ limit of the minimally twisted 6d $\cN=(2,0)$ theory with minimally twisted eleven-dimensional supergravity on $AdS_{7}\times S^{4}$.
+
+The twisted holography propoosal moreover posits that holography can be understood as a concrete algebaic operation at the level of observables.
 We mentioned that the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra.
 The predicted type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
-Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to a (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
+Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to an (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
 Following the work of \cite{CLsugra,CP1} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
@@
 While this heuristic definition sounds natural, it does not lend itself to an explicit description.
-However, for factorization algebras of bulk quantum field theories which can be expressed in a particular way we can refer to a local version of Noether's theorem in order to get our hands on it, see~\S\ref{s:noether}.
+However, for particular kinds of factorization algebras of bulk quantum field theories an explicit description is furnished by a local version of Noether's theorem, see~\S\ref{s:noether}.
 
 Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
-Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of the bulk gravitational theory. 
+Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
 Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
@@
 
-From the point of view of the bulk gravitational theory, one can understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the manifold $X - Y$ obtained by subtracting the brane.
-In most examples the above principle is too naive as we are forgetting a key ingredient, the so-called backreaction of the branes. 
-This deforms the geometric structure used to define the gravitational theory on $X - Y$---concretely, it will correspond to a certain deformation of the factorization algebra $(\Obs_{grav}|_{Y})^{!}$.
+It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS.
+A precise relation will be articulated in section \ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry.
+Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.
 
@@
 \begin{itemize}
-\item $D1$ branes in the topological string on the deformed conifold \cite{costello2021twisted}.
+  \item A stack of $D3$ branes in twisted $\Omega$-deformed type IIB supergravity on flat space.
+The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{CostelloGaiotto}.
+This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\cN=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$.
 Here, the duality is formulated in terms of vertex algebras which are avatars of holomorphic factorization algebras on a Riemann surface.
-This is also understood as a deformed version of the physical duality between 4d $\cN=4$ supersymmetric Yang--Mills and type IIB superstring theory on $AdS_5$. 
-\item A system of twisted $D1-D5$ branes in type IIB string theory on twisted $AdS_3 \times S^3 \times T^4$ \cite{CP1}. 
-Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a supersymmetric version.
+
+  \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory.
+Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace.
+The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.
+
   \item Membranes and fivebranes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}.
-In the particular $\Omega$-background membranes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras (and hence ordinary Koszul duality).
-The $\Omega$-background localizes fivebranes to a complex plane and the duality can be formulated in terms of vertex algebras (one-dimensional holomorphic factorization algebras). 
+In the particular $\Omega$-background, membranes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality.
+Moreover, the $\Omega$-background localizes fivebranes to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra.
+The holomorphic factorization algebras we seek in the present paper may be thought of as enhancements of these vertex algebras to three-complex dimensions.
 \end{itemize}
 
-A feature of the above examples is that via some method one can understand, independently, the algebra of observables on both sides of the duality. 
-For fivebranes in $M$-theory, before turning on the $\Omega$-background, there is no known description which is robust enough to fit inside of the factorization algebra formulation of a quantum field theory.
-So, rather than prove, or test, a version of the twisted holographic principle, the objective of this paper is to \textit{use} the twisted holographic principal to obtain an explicit description of the factorization algebra associated to the worldvolume theory on a stack of fivebranes (after performing the minimal, holomorphic, twist).
+In each of the above examples, there exist methods to characterize both sides of the duality independently and intrinsically.
+Indeed, conjectures of \cite{CLSugra} suggest that certain twists of type II superstrings are equivalent to certain topological strings.
+Utilizing such a description, one may characterize D-banes and associated open-string field theories in terms of categorical data.
 
+For membranes and fivebranes in $M$-theory, in the nonminimal twist or its further $\Omega$-deformation, one may appeal to dimensional reduction arguments to give similar characterizations of the twisted subsectors of the relevant worldvolume theories.
+
+However, for the minimal twist, we are not so lucky.
+The dimensional reduction of the nonminimal twist will necessarily involve subtle, nonperturbative effects making an intrinsic characterization along the lines of the above more difficult.
+We will offer some speculations in this direction at the end of the section below.
+
+Consequentially, rather than prove a version of the twisted holographic principle, the objective of this paper is to \textit{use} the twisted holographic principal to conjecture an explicit description of the factorization algebra associated to the worldvolume theory on a stack of minimally twisted fivebranes.
+Such an analysis reveals that twists of worldvolume theories of branes enjoy certain infinite dimensional symmetries, enhancing finite dimensional symmetries present in the untwisted theories.
+In the minimal twist of eleven dimensional supergravity, these infinite dimensional symmetries are provided by certain exceptional simplie lie superalgebras.
+
+\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
+
+In \S\ref{s:twisted} we will recall a description of the minimal twist of eleven-dimensional supergravity, following \cite{RSW}.
+In this twist, the theory is holomorphic in a maximal number of directions, which is five complex directions, and topological in the remaining real direction.
+The relation between the minimal twist and other twists is summarized in the following diagram:
+
+\[\begin{tikzcd}
+	{\text{physical theory}}\ar[d]\ar[rr, dashed] & & {\Omega-\text{deformed nonminimal twist}}\ar[d, squiggly] \\
+	{\text{minimal twist}}\ar[r]\ar[rr, "\text{superconformal deformation}" description, bend right = 12] & {\text{nonminimal twist}}\ar[r, dashed] & {\text{associated graded}}
+\end{tikzcd}\]
+
+Each of the above twists of supergravity on flat space admits a certain infinite dimensional algebra of symmetries.
+To begin with, the associated graded of the $\Omega$-deformed nonminimal twist is a holomorphic-topological theory in five dimensions.
+The theory on $\R\times \C^{2}$ depends on a holomorphic symplectic structure on $\C^{2}$, and the equations of motion include the Maurer-Cartan equation for an integrable deformation of such.
+Accordingly, the theory carries an action of the infinite dimensional lie algebra $\operatorname{Ham}(\C^{2})$ of hamiltonian vector fields on $\C^{2}$.
+
+Surprisingly, there is a lift of this relationship to the minimal twist.
+In \cite{RSW} a certain exceptional simple super lie algebra called was shown to act on the minimal twist on $\R\times \C^{5}$.
+The super lie algebra is a certain $L_{\infty}$ extension of an exceptional simplie lie super algebra called $E(5|10)$.
+The algebras of observables of various twists of eleven dimensional supergravity on flat space are recorded in the diagram below; the twist is indicated by the position of the entry in comparison with the diagram above.
+
+\[\begin{tikzcd}
+	{\text{physical theory}}\ar[d]\ar[rr, dashed] & & {\clie^{\bu}(\operatorname{Diff} (\C))}\ar[d, squiggly] \\
+	{\clie^{\bu}(\widehat {E(5|10)})}\ar[r]\ar[rr, "\text{superconformal deformation}" description, bend right = 12] & {\clie^{\bu}(\operatorname{Ham} (\C^{2}))}\ar[r, dashed] & {\clie^{\bu}(\operatorname{Ham}(\C^{2}))}
+\end{tikzcd}\]
+
+We note that the associated graded of the $\Omega$-deformed nonminimal twist and the nonminimal twist only differ by a tensor factor of the deRham complex on $\R^{6}$ - their algebras of local operators are quasi-isomorphic.
+
+%On flat space, $\R \times \C^5$ we have shown that our description yields a presentation of the algebra of local operators which takes the following form
+%\beqn
+%\clie^\bu\left(\Hat{E(5|10)}\right) .
+%\eeqn
+%This is the Chevalley--Eilenberg complex (computing Lie algebra cohomology) of a particular central extension of the super Lie algebra $E(5|10)$.
+This can be viewed as an enhancement of the fact that the local operators of the nonminimally twisted $\Omega$-deformed theory on flat space take the form $\clie^{\bu}\left(\operatorname{Ham} (\C^{2})\right)$ where $\Ham (\C^{2})$ denotes the lie algebra of hamiltonian vector fields on $\C^{2}$ -  a one-dimensional central extension of the lie algebra of symplectic vector fields.
+We emphasize that these statements about local operators are only interesting when one works in the Batalin--Vilkovisky formalism taking into account all ghosts, fields, anti-fields, etc..
+
+Strikingly, fivebranes in the minimal twist bring another exceptional super lie algebra into the spotlight.
+In the minimal twist, fivebranes are completely holomorphic objects which, in flat space, wrap three complex directions in the eleven-dimensional bulk theory
+\beqn
+\C^3 \subset \R \times \C^5 .
+\eeqn
+Recall that the wordvolume theory associated to a stack of fivebranes in $M$-theory on flat space is a superconformal theory with $\cN=(2,0)$ supersymmetry.
+In six dimensions (after complexifying) the superconformal algebra is the super Lie algebra $\lie{osp}(8|4)$, whose even part is $\lie{so}(8) \times \lie{sp}(4)$.
+Twisting involves the choice of a holomorphic supercharge $Q$ which leaves three directions invariant and breaks this super Lie algebra down to the smaller super Lie algebra $\lie{osp}(6|2)$.
+The $Q$-twist of any six-dimensional superconformal field theory has a symmetry by this super Lie algebra.
+
+As we just pointed out, the super Lie algebra $\widehat E(5|10)$ describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist.
+It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $\widehat E(5|10)$.
+In fact, $\lie{osp}(6|2)$ sits inside of a small (but still infinite-dimensional) super Lie algebra called $E(3|6)$.
+
+\begin{conj}[with Ingmar Saberi]
+After the holomorphic twist, the six-dimensional $\cN = (2,0) $superconformal algebra gets enhanced to the exceptional simple super Lie algebra $E(3|6)$.
+As a consequence, after twisting, the space of local operators of any six-dimensional $\cN=(2,0)$ superconformal theory is a representation for $E(3|6)$.
+\end{conj}
+
+A consequence of this conjecture is that we can interpret, for example, the superconformal index as a character for $E(3|6)$.
+Comparison to typical formulae in the literature is faciliated by a judicious choice of Cartan for $E(3|6)$.
+
+Upon performing the superconformal deformation, the super Lie algebra $E(3|6)$ deforms to a familiar object in chiral CFT: the Lie algebra of vector fields on the (formal) disk.
+So, if we were to deform the conjecture above according to this Schur limit we would recover the familiar consequence that a chiral conformal field theory has as part of its symmetries the Lie algebra of vector fields on the formal disk.
+Of course, there is a richer algebra around---the Virasoro algebra---which extends the Lie algebra of vector fields on the {\em punctured} disk. 
+We will say more about a six-dimensional lift of this object later on in this introduction.
+
+\subsection{The Fivebrane Decomposition}
 Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
@@
 
+\subsection{Modules and Instantons}
 One of the most attractive features of the six-dimensional theory associated to the Lie algebra of type $A_{N-1}$ is through its relationship to the famous correspondence of Alday, Gaiotto, and Tachikawa \cite{AGT}.

### 2022-09-26 fivebranes/intro.tex
merge error

--- 2022-09-20 fivebranes/intro.tex
@@
 \eeqn
-is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from monopole operators.
+is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnotes{The instanton charge turns out to be identical to the winding number around $S^1$.}
 In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.

### 2022-09-26 fivebranes/intro.tex
typo

--- 2022-09-26 fivebranes/intro.tex
@@
 \eeqn
-is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from monopole operators.
+is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnote\{The instanton charge turns out to be identical to the winding number around $S^1$.}
 In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.

### 2022-09-26 fivebranes/intro.tex
shit

@@
 \eeqn
-is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnote\{The instanton charge turns out to be identical to the winding number around $S^1$.}
+is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnote{The instanton charge turns out to be identical to the winding number around $S^1$.}
 In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.

### 2022-09-26 fivebranes/intro.tex
refs and style

@@
 Examples of such a quantity is the superconformal index, which is a generating function for some collection of $R$-charges of certain BPS local operators. 
-Crucial steps towards a more mathematical understanding of superconformal indices were taken in \cite{HolomorphicCharacters}, articulated through the construction of twisting.
+Crucial steps towards a more mathematical understanding of superconformal indices were taken in \cite{SWchar}, articulated through the construction of twisting.
 
@@
 
-One of the insights of \cite{HolomorphicCharacters} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
+One of the insights of \cite{SWchar} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
 Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. 
@@
 To describe the kinds of theories on either side of the correspondence, we should comment on what it means to twist a theory of supergravity.
-We will provide more details in section \ref{sec:twisted}.
+We will provide more details in \S \ref{s:twisted}.
 Since the action of supersymmetry is gagued in theories of supergavity, the aforementioned twisting procedure does not quite make sense.
@@
 
-It is expected that the 6d $\cN=(2,0)$ superconformal field theory of type $A_{N-1}$ describes the low energy dynamics of a stack of fivebranes in M-theory on flat space.
+It is expected that the six-dimensional $\cN=(2,0)$ superconformal field theory of type $A_{N-1}$ describes the low energy dynamics of a stack of fivebranes in M-theory on flat space.
 Accordingly, there is a minimal twist of the low energy limit of M-theory, eleven-dimensional supergravity, which induces the minimal twist on a stack of fivebranes.
-We will be interested in a twisted version of the $AdS_{7}/CFT_{6}$ correspondence which will relate the large $N$ limit of the minimally twisted 6d $\cN=(2,0)$ theory with minimally twisted eleven-dimensional supergravity on $AdS_{7}\times S^{4}$.
+We will be interested in a twisted version of the $AdS_{7}/CFT_{6}$ correspondence which will relate the large $N$ limit of the minimally twisted six-dimensional $\cN=(2,0)$ theory with minimally twisted eleven-dimensional supergravity on $AdS_{7}\times S^{4}$.
 
@@
   \item A stack of $D3$ branes in twisted $\Omega$-deformed type IIB supergravity on flat space.
-The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{CostelloGaiotto}.
+The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{costello2021twisted}.
 This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\cN=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$.
@@
 In each of the above examples, there exist methods to characterize both sides of the duality independently and intrinsically.
-Indeed, conjectures of \cite{CLSugra} suggest that certain twists of type II superstrings are equivalent to certain topological strings.
+Indeed, conjectures of \cite{CLsugra} suggest that certain twists of type II superstrings are equivalent to certain topological strings.
 Utilizing such a description, one may characterize D-banes and associated open-string field theories in terms of categorical data.
@@
 \begin{conj}[with Ingmar Saberi]
-After the holomorphic twist, the six-dimensional $\cN = (2,0) $superconformal algebra gets enhanced to the exceptional simple super Lie algebra $E(3|6)$.
+After the holomorphic twist, the six-dimensional $\cN = (2,0) $ superconformal algebra gets enhanced to the exceptional simple super Lie algebra $E(3|6)$.
 As a consequence, after twisting, the space of local operators of any six-dimensional $\cN=(2,0)$ superconformal theory is a representation for $E(3|6)$.
@@
 
-\subsection{The Fivebrane Decomposition}
+\subsection{The fivebrane decomposition}
 Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
@@
 In fact, this decomposition is intimately related to a certain decomposition of the exceptional simple super Lie algebra $E(5|10)$ that we have already mentioned plays an important role in the minimal twist of eleven-dimensional supergravity.
-The strange indexing conventions will be explained in \S\ref{eqn:fact}.
+The strange indexing conventions will be explained in \S\ref{s:fact}.
 
@@
 \eeqn
-Then, the avatar of our conjectural description in \eqref{eqn:finiteTensor} at the level of the superconformal index is
+Then, the avatar of our conjectural description in \eqref{eqn:finiteTensor} at the level of the single particle superconformal index is
 \beqn
@@
 \eeqn
-To obtain the superconformal index we simply apply the plethystic exponential
+To obtain the full superconformal index we simply apply the plethystic exponential
 \beqn

### 2022-09-28 fivebranes/intro.tex
agt

@@
 
-As we just pointed out, the super Lie algebra $\widehat E(5|10)$ describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist.
-It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $\widehat E(5|10)$.
+As we just pointed out, the super Lie algebra $\widehat {E(5|10)}$ describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist.
+It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $\widehat {E(5|10)}$.
 In fact, $\lie{osp}(6|2)$ sits inside of a small (but still infinite-dimensional) super Lie algebra called $E(3|6)$.
@@
 \subsection{The fivebrane decomposition}
-Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
+Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of minimally twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
 After taking a certain classical limit, this argument relies on a presentation of the $!$-dual as
@@
 In fact, this decomposition is intimately related to a certain decomposition of the exceptional simple super Lie algebra $E(5|10)$ that we have already mentioned plays an important role in the minimal twist of eleven-dimensional supergravity.
+This decomposition is a natural lift of the grading on $\operatorname{Ham}(\C^{2})$ induced from taking the associated graded with respect to the order filtration on $\operatorname{Diff} (\C^{2})$.
 The strange indexing conventions will be explained in \S\ref{s:fact}.
@@
 
-We want to emphasize that these expressions only hold after taking this classical limit and taking some truncation of the differential present which is present on the left-hand side.\footnote{An instructive avatar of this decomposition to keep in mind is the description of the $W_N$ vertex algebra as being generated by a collection of operators of spins $2,3,\ldots, N$.
+We want to emphasize that these expressions only hold after taking this classical limit and taking some truncation of the differential present on the left-hand side.\footnote{An instructive avatar of this decomposition to keep in mind is the description of the $W_N$ vertex algebra as being generated by a collection of operators of spins $2,3,\ldots, N$.
 Only in the classical limit does the $W_N$ vertex algebra decompose as a pure tensor product.}
@@
 
-As the formalism of Koszul duality and factorization algebras is rather abstract, it is useful to first indicate what our approach looks like at the level of the superconformal index. 
-On one hand, we have the index of multi-particle states of the supergravity theory on the manifold obtained by removing the location of the brane; we denote this by $\chi_{grav}({\bf x})$.
-It is a function of the fugacities ${\bf x}$ which in this setting are given by coordinate functions on the four-dimensional Cartan subalgebra of~$\lie{osp}(6|2)$.
+Though the formalism we employ of Koszul duality and factorization algebras is rather abstract, it has concrete and fruitful consequences at the level of the superconformal index.
+On one hand, we have the index of multi-particle states of the supergravity theory on the backreacted geometry; this is a generating function for masses of states.
+We denote this by $\chi_{grav}({\bf x})$, where ${\bf x}$ are fugacities given by coordinate functions on the four-dimensional Cartan subalgebra of~$\lie{osp}(6|2)$.
 Typically, this multi-particle index can be obtained from the single-particle index $f_{grav}({\bf x})$ of gravitational states through the plethystic exponential. 
 Since the index is only really sensitive to the minimal twist, it is reasonable that we can compute the index using our formulation of twisted eleven-dimensional supergravity.
-We will obtain known formulas for the index of eleven-dimensional supergravity states on $AdS_7$ in \S\ref{s:states} using our description of twisted supergravity.
+We will obtain known formulas as a character of the Hilbert space of eleven-dimensional supergravity on $AdS_7\times S^{4}$ in \S\ref{s:states} using our description of twisted supergravity.
 
-While we don't need to know the precise relationship at the moment, we can point out that the data of a factorization algebra encodes, in particular, the algebra of local operators of a system.
-This is convenient from the point of view of the superconformal index since as we have already pointed out we can compute it as the index of local operators of the twisted theory.
+Now we turn to the computation of superconformal indices of the type $A_{N-1}$ six-dimensional $\cN=(2,0)$ theory.
+As we have already pointed out, the superconformal index can be computed as a charater of local operators of the twisted theory.
+Moreover, the space of local operators is readily recovered from the data of the factorization algebra associated to the theory.
 We will see how the descriptions above lead to a presentation for the superconformal index $\chi_N({\bf x})$ of the worldvolume theory on a finite stack of $N$ fivebranes.
 
-If we are working simply on the worldvolume $\C^3 \cong \R^6$, our description in \eqref{eqn:finiteTensor} posits that after taking the classical limit the local operators on a stack of $N$ twisted fivebranes is
+If we are working simply on the worldvolume $\C^3 \cong \R^6$, our description in \eqref{eqn:finiteTensor} posits that after taking the classical limit the decomposition of factorization algebras associted to a stack of $N$ twisted fivebranes induces a decomposition at the level of local operators
 \beqn
@@
 Forgetting about the differentials for the time being, the local operators $\cF_k(0)$ are given as the free algebra on some vector space $V_k$ of linear local opeartors.
-Thus, to compute the index of local operators of $\Obs_{brane}(N)$ it suffices to compute the index of all of the $V_k$---this is the single particle index---and then apply the plethystic exponential.
+Thus, to compute the index of local operators of $\Obs_{brane}(N)$ it suffices to compute the index of each of the $V_k$---this is the single particle index---and then apply the plethystic exponential.
 For now, denote by $g_k({\bf x})$ the index of the vector space $V_k$.
@@
 From these formulas it is manifest that the holographic relation $\chi_{grav} = \lim_{N \to \infty} \chi_N$ holds.
-The next thing we turn to is evidence for our claim that $\chi_N({\bf x})$ really is the superconformal index associated to fivebranes. 
-In ~\S\ref{s:finite} we will show that for small values of $N$ our closed of formulas, when appropriately expanded, agree with approximations which have been found in the literature.
-We will also check that a number of specializations of the fugacities agree with certain unrefined indices which have been computed via other means.
-Even stronger evidence would involve the factorization algebras $\Obs_{brane}(N)$, and we will briefly sketch how this should go in later sections but leave a full treatment to future work.
 
-\subsection{Modules and Instantons}
-One of the most attractive features of the six-dimensional theory associated to the Lie algebra of type $A_{N-1}$ is through its relationship to the famous correspondence of Alday, Gaiotto, and Tachikawa \cite{AGT}.
-On the four-dimensional side, the key player is the equivariant cohomology of the moduli space of instantons of type $A_{N-1}$. 
-The six-dimensional theory of type $A_{N-1}$ explains a powerful relationship between this object and a certain chiral conformal field theory. 
-We anticipate, though do not prove any statements in the spirit of the AGT correspondence in this paper, that our factorization algebras $\Obs_{A_{N-1}}$ have the ability to \brian{not sure what's a good way to say this.}
-To state some explicit results and to make concrete conjectures at the level of the superconformal index we will take a look at small values of~$N$.
-
-\subsection*{The abelian $\cN=(2,0)$ theory}
-
-The abelian six-dimensional $\cN=(2,0)$ theory is the worldvolume theory on a single fivebrane. 
-It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
-In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given---it defines a complex three-dimensional factorization algebra that we will denote by $\Obs_1$.
-In this paper we only consider the classical limit of this factorization algebra, but there is a simple quantization of its natural shifted Poisson structure which we will use in this section.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}
-
-The superconformal index can be computed from the local character of the factorization aglebra $\Obs_1$. 
-We recover the standard formulas in the literature in terms of the five fugacities $y_1,y_2,y_3,y,q$ which satisfy the constraint $y_1 y_2 y_3 = 1$, see for instance \cite{Kim:2013nva}.
-
-Let us place this factorization algebra on the threefold $\C^\times \times \C^2$ and consider the reduction along the circle $S^1 \subset \C^\times$. 
-In \cite{SWtensor} we have shown that the naive dimensional reduction (where we throw out higher Kaluza--Klein modes along $S^1 \subset \C^\times$) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of perturbative supersymmetric Yang--Mills theory for the group $U(1)$.
-If we keep track of Kaluza--Klein modes, our ansatz is that the full dimensional reduction 
-\beqn
-\oint_{S^1} \Obs_1
-\eeqn
-is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnote{The instanton charge turns out to be identical to the winding number around $S^1$.}
-In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.
-
-There is a nice relationship to the AGT correspondence which we can remark on in this abelian case. 
-In the notation we are using for fugacities, the so-called Schur limit of the superconformal index is simply $y_1=y=1$.
-For the abelian theory this immediately gives the function $\frac{q}{1-q}$ which is the well-known vacuum character of the Heisenberg vertex algebra. 
-Geometrically, the Schur limit corresponds to working with an equivariant version of the Hilbert space.
-In this setting, this is the equivariant cohomology of the moduli space of instantons of rank one.
-This specialization then agrees with the famous result of Nakajima which characterizes the equivariant cohomology of the moduli space of rank one instantons (also known as the Hilbert scheme of points) with the Heisenberg vacuum module.
-
-If we return to six dimensions, one can use the radial direction in $\C^\times \times \C^2$ to endow the factorization algebra $\oint_{S^1} \Obs_1$ with the structure of an (dg) associative algebra. 
-This Schur limit corresponds to a particular deformation of this algebra by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$.
-We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}.
-One can identify (though we do not do that in this paper) this deformation of $\oint_{S^1} \Obs_1$ with the Heisenberg algebra. 
-Thus, we expect that the dg algebra $\oint_{S^1} \Obs_1$, {\em before} deforming, should act on the non-equivariant cohomology of the moduli space of instantons of rank one.
-
-\subsection*{The $\cN=(2,0)$ theory of type $A_1$}
-
-The first major conjecture that we make is for an expression for the algebra of local operators $\Obs_{A_1}(0)$, or really the factorization algebra $\Obs_{A_1}$, of the holomorphic twist of the $\cN=(2,0)$ theory associated to a Lie algebra of type $A_1$.
-At the level of the superconformal index, we can state the concrete expectation now.
+We highlight the expression that our prescription yields for the theory of type $A_{1}$:
 
@@
 \end{conj}
+
+We next provide some comparitive evidence for our claim that $\chi_N({\bf x})$ really is the superconformal index associated to fivebranes.
+In ~\S\ref{s:finite} we will show that for small values of $N$ of our closed formulas, appropriate expansions agree with expressions which have been found in the literature.
+We will also check that a number of specializations of the fugacities agree with certain unrefined indices which have been computed via other means.
+
+Even stronger evidence would involve the factorization algebras $\Obs_{brane}(N)$. We will outline some expectations in later sections but leave a full treatment to future work.
+
+\subsection{Modules and instantons}
+We conclude this introduction by outlining a further consistency check of our proposal that $\Obs_{A_{N-1}}$ describes the observables for the minimally twisted type $A_{N-1}$ six-dimensional $\cN=(2,0)$ theory, this time involving dimensional reduction.
+The statements outlined below will be pursued further in future work.
+We begin by giving a flavor of the desired statement at the level of the $\Omega$-deformed nonminimal twist.
+
+Recall that the $\Omega$-deformed nonminimal twist is a holomorphic theory in one complex dimension.
+We may place this theory on $\C^{\times}$ and attempt to dimensionally reduce along $S^{1}\subset \C^{\times}$.
+The result should be an $\Omega$-deformed A-twist of five-dimensional $\cN =2$ gauge theory for $SU(N)$- a perturbatively trivial theory.
+However, naively computing the dimensional reduction using a perturbative description of the fields yields an incorrect answer.
+This is not surprising: the gauge coupling in five-dimensions goes like the inverse of the radius of the circle we are reducing along.
+Since the twist still depends on the radius, the perturbative description is untrustworthy.
+
+The precise relationship between the $\Omega$-deformed nonminimal twist of the six-dimensional $\cN=(2,0)$ $A_{N-1}$ theory and five-dimensional $\cN=2$ gauge theory for $SU(N)$ is articulated through the AGT correspondence \cite{AGT}.
+As we intimated, the observables of the $\Omega$-deformed nonminimal twist are expected to be a one-dimensional holomorphic factorization algebra which agrees with the $W_{N}$ vertex algebra.
+In the language of factorization algebras, the dimensional reduction along $S^{1}\subset \C^{\times}$ amounts to passing to the algebra of modes.
+The AGT correspondence posits that this mode algebra acts on the equivariant cohomology of the moduli of instantons of the five dimensional theory.
+
+We propose similar statements at the level of the minimal twist.
+We fix a complex surface $X$ together with a pair of complex vector bundles $W, M \to X$ of ranks 2 and 1 respectively, satisfying the condition that $\wedge^{3}(W \oplus M) = \det X$.
+This condition ensures that $Tot (W\oplus M)$ is a Calabi-Yau 5-fold.
+
+\subsection*{The abelian $\cN=(2,0)$ theory}
+
+The abelian six-dimensional $\cN=(2,0)$ theory is the worldvolume theory on a single fivebrane. 
+It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
+In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given---it defines a complex three-dimensional factorization algebra that we will denote by $\Obs_1$.
+In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{brane}(1)$ above.
+We emphasize that we only consider the classical limit of this factorization algebra in this paper.
+However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}
+
+Let us place this factorization algebra on the three-fold $Tot (M)$.
+Choosing a fiberwise hermitian metric affords a norm map \[\pi : Tot (M) \to \R_{+}\] whose fibers away from $0$ are the unit $S^{1}$ bundle in $M$.
+The pushforward $\pi_{*}\Obs_{1}$ is a stratified factoization algebra on the half-line.
+This may be thought of as a pair consisting of an associative algebra, which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold $Tot (M)$, together with a module for the algebra of modes.
+
+In \cite{SWtensor} it is shown that in the case where $M$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.
+
+If we keep track of Kaluza--Klein modes, our expectation is that the full dimensional reduction $\pi_{*}\Obs_{1}|_{\R_{>0}}$ includes contributions from instanton operators.\footnote{The instanton charge turns out to be identical to the winding number around $S^1$.} Moreover, the module at zero $\pi_{*}\Obs_{1}|_{0}$ ought to be identified with the Hilbert space of the minimal twist of five-dimensional $\cN = 2$ gauge theory.
+We are left with the following conjecture.
+
+\begin{conj}
+The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ acts on $\cO (\operatorname{Higgs}^{W}_{GL(1)} X)$ where $\operatorname{Higgs}^{W}_{GL(1)} X$ denotes the moduli of $GL(1)$ Higgs bundles on $X$ whose higgs fields are $W[1]$-valued.
+\end{conj}
+
+While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities.
+
+Above, we have mentioned a particular deformation of the observables of the six-dimensional $\cN = (2,0)$ theory by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$.
+We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}.
+One can identify (though we do not do that in this paper) this deformation of $\pi_{*} \Obs_1|_{\R_{>0}}$ with the Heisenberg algebra.
+
+For a particular choice of $W, M, X$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
+\subsection*{The $\cN=(2,0)$ theory of type $A_1$}
 
@@
 
-\subsection{Outline}
-
-The paper is organized as follows. The first section is the present introduction.
-
 %\end{document}

### 2022-09-28 fivebranes/intro.tex
single edits

@@
 It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS.
-A precise relation will be articulated in section \ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry.
+A precise relation will be articulated in \S\ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry.
 Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.
@@
   \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory.
-Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace.
+Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace \cite{CP}.
 The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.
@@
 We propose similar statements at the level of the minimal twist. 
-We fix a complex surface $X$ together with a pair of complex vector bundles $W, M \to X$ of ranks 2 and 1 respectively, satisfying the condition that $\wedge^{3}(W \oplus M) = \det X$.
-This condition ensures that $Tot (W\oplus M)$ is a Calabi-Yau 5-fold.
+We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks $1$ and $2$ respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau 5-fold.
+The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.
 
@@
 
-The abelian six-dimensional $\cN=(2,0)$ theory is the worldvolume theory on a single fivebrane. 
+The abelian six-dimensional $\cN=(2,0)$ theory is also thought of as the worldvolume theory on a single fivebrane in $M$-theory. 
 It admits a field theoretic description as the so-called $\cN=(2,0)$ tensor multiplet. 
-In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given---it defines a complex three-dimensional factorization algebra that we will denote by $\Obs_1$.
+In \cite{SWtensor} an explicit description of the minimal, holomorphic, twist of this theory is given.
+At the level of this twist, the theory is defined on any complex three-fold (equipped with a square root of its canonical bundle). 
+In this section, we consider the $\cN=(2,0)$ theory on the threefold $Y = \text{Tot}(L \to S)$ as a single fivebrane supported on the closed submanifold
+\beqn
+Y \hookrightarrow \R \times X .
+\eeqn
+We will denote the corresponding factorization algebra of observables on $Y$ by $\Obs_1$.
+
 In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{brane}(1)$ above.
@@
 
-Let us place this factorization algebra on the three-fold $Tot (M)$.
-Choosing a fiberwise hermitian metric affords a norm map \[\pi : Tot (M) \to \R_{+}\] whose fibers away from $0$ are the unit $S^{1}$ bundle in $M$.
-The pushforward $\pi_{*}\Obs_{1}$ is a stratified factoization algebra on the half-line.
-This may be thought of as a pair consisting of an associative algebra, which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold $Tot (M)$, together with a module for the algebra of modes.
+We place this factorization algebra on the three-fold $Y$ which is the total space of the line bundle $L \to S$. 
+Choosing a fiberwise hermitian metric affords a norm map 
+\[
+\pi \colon Y \to \R_{+}
+\] 
+whose fiber away from $0$ is the total space of the unit sphere bundle.
+The pushforward factorization algebra $\pi_{*}\Obs_{1}$ is a stratified factorization algebra on the non-negative half-line $\R_+ = \{t \geq 0\}$. 
+We can tweak this factorization algebra slightly which gives rise to a constructible factorization algebra on $\R_+$.
+In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle) together with a module for this algebra.
 
-In \cite{SWtensor} it is shown that in the case where $M$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.
+In \cite{SWtensor} it is shown that in the case where $L$ is the trivial bundle, the naive dimensional reduction (where we discard higher Kaluza--Klein modes along the circle fiber) along 
+\beqn
+S \times \C \to S \times \R_+
+\eeqn
+agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ supersymmetric Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.
 
@@
 \begin{conj}
-The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ acts on $\cO (\operatorname{Higgs}^{W}_{GL(1)} X)$ where $\operatorname{Higgs}^{W}_{GL(1)} X$ denotes the moduli of $GL(1)$ Higgs bundles on $X$ whose higgs fields are $W[1]$-valued.
+Let $\operatorname{Higgs}_{GL(1)} (S,L)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields take values in the rank two bundle $W$.
+The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
+\beqn
+\cO \left(\operatorname{Higgs}_{GL(1)} (S,L)\right) .
+\eeqn
 \end{conj}
@@
 
-For a particular choice of $W, M, X$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
+For a particular choice of $S,L,W$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
+
 \subsection*{The $\cN=(2,0)$ theory of type $A_1$}

### 2022-09-29 fivebranes/finite.tex
merge

@@
 \section{Conjectures for operators on fivebranes}
+\label{s:finite}
 
@@
 \begin{conj} 
-The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$ is $\til \chi_{N}(y_1,y_2,y_3,y,q)$. 
+The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra of type $A_{N-1}$ is $\til \chi_{N}(y_1,y_2,y_3,y,q)$. 
 \end{conj}
@@
 
-The limit that we consider is 
+This minimally reduced index corresponds to taking the following limit in the new fugacities
 \beqn\label{eqn:limitgaitto}
@@
 g_k (z_i,w_a) \define & \left( z_1z_2z_3 p_k(w_1,w_2) (z_1+z_2+z_3) + p_{k+2}(w_1,w_2)  \right. \\
-&\displaystyle \frac{\left.  -z_1z_2z_3 p_{k-1}(w_1,w_2) - p_{k+2}(w_1,w_2) (z_1z_2+z_2z_3+z_1z_3) \right)}{(1-z_1)(1-z_2)(1-z_3)} .
+&\displaystyle \frac{\left.  -z_1z_2z_3 p_{k-1}(w_1,w_2) - p_{k+1}(w_1,w_2) (z_1z_2+z_2z_3+z_1z_3) \right)}{(1-z_1)(1-z_2)(1-z_3)} .
 \end{array}
@@
 
-The $z_3,w_2 \to 0$ limit of our index is quite similar, though not exactly, the index of a four-dimensional $\cN=1$ theory.
+The $z_3,w_2 \to 0$ limit of our index is quite similar, though not exactly, the index of a four-dimensional $\cN=1$ theory on $\C^2$ where the fugacities $z_1,z_2$ count holomorphic derivatives in each of the complex directions.
+Also, note that this minimally reduced index further reduces to the Schur limit (so the character of the $W_N$ vertex algebra) by specializing $z_1 = w_1$.
 
@@
 
-In the final section we would like to exhibit a series of direct consistency checks with our conjectural exact formula for the index of the non-abelian six-dimensional superconformal theory with a few expansions that have appeared in recent literature.
+In the final section we would like to exhibit a series of direct consistency checks with our conjectural exact formula for the index of the non-abelian six-dimensional superconformal theory with a number of expansions that have appeared in recent literature.
 
@@
 We proceed to compare expansions of our exact expression for the $\lie{gl}(3)$ theory to those in \cite{Kim:2013nva}. 
-Recall that the conjectural $\lie{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
+Recall that our conjectural $\lie{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
 \beqn

### 2022-09-29 fivebranes/main.tex
merge

@@
 
-\title{A holomorphic approach to branes in twisted~$M$-theory}
+%\title{A holomorphic approach to fivebranes}
+\title{A holographic approach to the six-dimensional superconformal index}
 \maketitle
@@
 \subsection*{Acknowledgements}
-We thank K.~Costello, D.~Gaiotto, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
+We thank K.~Costello, D.~Gaiotto, N.~Garner, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
 Special thanks are due to Ingmar Saberi for his collaborations on past, current, and future related projects.

### 2022-09-29 omega.tex
merge

@@
 \[
-S(\vep, \delta) \define \ep \, w_1 \d w_2 \wedge \d w_3 + \delta \, w_2 \d w_3 \wedge \d w_1 - (\ep + \delta) \, w_3 \d w_1 \wedge \d w_2 .
+S(\vep, \delta) \define \ep \, w_3 \d w_1 \wedge \d w_2 + \delta \, w_2 \d w_3 \wedge \d w_1 - (\ep + \delta) \, w_1 \d w_2 \wedge \d w_3 .
 \]
@@
 \CC[z_i, w_a] \{\del_{z_i}\} \oplus \CC\{\del_{w_a}\} .
+\]
+
+\subsection{Deformation of $M2$ and $M5$ branes}
+
+We argue that when restricted to $M2$ and $M5$ branes that the supercharge $S(\ep, \delta)$ becomes explicit superconformal elements which live in the holomorphic twist of the relevant $3d$ and $6d$ superconformal algebras, respectively.
+
+\parsec[]
+
+Let's first consider the $M2$ brane case. 
+In the notation of this section, let us take the $M2$ brane to live along $z_1 = z_2 = w_1 = w_2 = 0$:
+\[
+\{0\} \times \{0\} \times \CC_{w_3} \times \RR_t \subset \CC^2_{z_i} \times  \CC^3_{w_a} \times \RR_t .
+\]
+
+Recall that the odd part of the 3-dimensional superconformal algebra, which can be identified with $\lie{osp}(6|1)$, is 
+\[
+\wedge^2 W \otimes R 
+\]
+where $W$ is the defining $\lie{sl}(4)$ representation and $R$ is the defining $\lie{sl}(2)$ representation. 
+In \ref{s:m2embedding} we polarized $R$ and decomposed this as $(\wedge^2 W)_{+1} \oplus (\wedge^2 W)_{-1}$.
+
+Along the brane, the first summand $(\wedge^2 W)_{+1}$ corresponds to the residual supertranslations in the twist of the 3d $\cN=8$ supersymmetry algebra. 
+The second summand $(\wedge^2 W)_{-1}$ corresponds to residual superconformal transformations. 
+It is spanned by elements of the form 
+\[
+w_3 \otimes (v_\alpha \wedge v_\beta)
+\]
+where $w_3$ is the holomorphic coordinate along the $M2$ brane and $\{v_\alpha\}$ is a basis for $W \cong \CC^4$.
+In the notation of the 11-dimensional theory, $W$ is spanned by translation invariant holomorphic one-forms $\{\d z_1, \d z_2, \d w_1, \d w_2\}$.
+
+Restricting the element $S(\ep,\delta)$ to the $M2$ brane we obtain precisely an element of this form: 
+\[
+S(\ep,\delta)|_{M2} = \ep w_3 \otimes (v_3 \wedge v_4).
+\]
+Notice that the dependence on $\delta$ has completely dropped since $\delta$ is proportional to terms involving the linear functions $w_1,w_2$ which are set to zero along the brane.
+
+\parsec[]
+Next, let's consider the restriction of the element $S(\ep, \delta)$ to an $M5$ brane.
+
+We take the $M5$ brane to live along $z_2 = w_3 = t = 0$:
+\[
+\CC_{z_1} \times \{0\} \times \CC_{w_1} \times \CC_{w_2} \times \{0\} \subset \CC^2_{z_i} \times  \CC^3_{w_a} \times \RR_t .
+\]
+
+\brian{I'm using $R_{6d} = \CC.\d z_2 \oplus \CC. \d w_3$.}
+Recall that the odd part of twist of the 6-dimensional superconformal algebra (which is also $\lie{osp}(6|1)$) can be identified with 
+\[
+L \otimes R \oplus \wedge^2 L \otimes R 
+\]
+where $L \cong \CC^3$ is the defining $\lie{sl}(3)$ representation and $R \cong \CC^2$ is the defining $\lie{sl}(2)$ representation. 
+A basis for $L$ is given by the constant holomorphic one-forms along the brane, which in this notation is $\{\d z_1, \d w_1, \d w_3\}$. 
+A basis $\{r_1,r_2\}$ for $R$ corresponds in 11-dimensions to the constant holomorphic one-forms $\{\d z_1, \d w_3\}$.
+
+The first summand $L \otimes R$ corresponds to residual supertranslations of the 6d $\cN=(2,0)$ superconformal algebra after the holomorphic twist. 
+The second summand $\wedge^2 \otimes R$ corresponds to residual superconformal elements.
+
+Following our embedding from \S \ref{s:m5embedding} we find that the restriction of $S(\ep, \delta)$ is precisely one of these superconformal elements:
+\[
+S(\ep, \delta) = - \left(\delta w_2 \d w_1 + (\ep + \delta) w_1 \d w_2 \right) \otimes r_2 .
 \]
@@
 Notice that we can add to this $\gamma(a,b,c)$ any holomorphic one-form on $\CC^2_z$ and it will still satisfy \eqref{eqn:euler}.
+
+\subsection{Localization to 7d}
+
+Consider
+\[
+S(\ep) = \ep (w_1 \d w_2 \wedge \d w_3 + w_2 \d w_1 \wedge \d w_3) .
+\]
+
+The annihilator of $[S(\ep),-]$ in $E(5,10)$ is linearly spanned by the following elements
+\begin{itemize}
+\item Divergence-free vector fields of the form $f_i(z_1,z_2, w_3) \del_{z_i}$. 
+\item Vector fields of the form $(w_1 w_2)^n \del_{w_3}$. 
+\item $\cdots$
+\end{itemize}
 

### 2022-09-29 residual.tex
merge

@@
-% Created 2020-10-14 Wed 14:51
-% Intended LaTeX compiler: pdflatex
 \documentclass[11pt]{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{graphicx}
-\usepackage{grffile}
-\usepackage{longtable}
-\usepackage{wrapfig}
-\usepackage{rotating}
-\usepackage[normalem]{ulem}
-\usepackage{amsmath}
-\usepackage{textcomp}
-\usepackage{amssymb}
-\usepackage{capt-of}
-\usepackage{hyperref}
-\usepackage{amsfonts}
-\usepackage{macros-mtheory}
-\usepackage{cmupint}
+
+\usepackage{macros-mtheory,amsaddr}
+
+\addbibresource{cfs.bib}
+
+%\linespread{1.2} %for editing
+%\usepackage{mathpazo}
 
@@
 
-\def\pv{{\rm PV}}
-\def\PV{{\rm PV}}
-\def\T{{\rm T}}
-\def\del{\partial}
-\def\hotimes{\, \otimes \,}
-\def\ep{\epsilon}
-\def\div{\partial_{\Omega}}
-\def\m2{\mathfrak{m}2\mathfrak{brane}}
-\def\susy{\mathfrak{susy}}
-\def\so{\mathfrak{so}}
-\def\siso{\mathfrak{siso}}
-\def\fsl{\mathfrak{sl}}
-\def\lie#1{\ensuremath{\mathfrak{#1}}}
-
 \begin{document}
@@
 \maketitle
-\tableofcontents
+%\tableofcontents
 
@@
 
+\paragraph{
 Recall, the (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
@@
 \[
-  \siso_{11d} = \so(11 , \CC) \ltimes \ft_{11d} .
+  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
 \]
-The $R$-symmetry is trivial in 11-dimensional supersymmetry.
+The $R$-symmetry is trivial in 11-dimensional supersymmetry. }
 
+\paragraph{
 We recall the so-called M2 brane central extension of the super Poincar\'e algebra.
@@
 be the $\lie{so}(11,\CC)$-equivariant projection onto the $\wedge^2 V$ summand.
-
-The super dg Lie algebra $\m2$ is the central extension of $\siso_{11d}$ by the cocycle
+The super dg Lie algebra $\m2$ is the central extension of $\lie{siso}_{11d}$ by the cocycle
   \[
-    c_{M2} \in \clie^2\left(\siso_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
+    c_{M2} \in \clie^2\left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right)
   \]
@@
   \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
-  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$ as in the decomposition \eqref{eqn:decomp}.
+  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$ as in the decomposition \eqref{eqn:decomp}. }
 
-Notice that $\m2$ is a $\ZZ \times \ZZ/2$-graded Lie algebra and the differential is of bidegree $(1,0)$.
+We view $\m2$ as a $\ZZ \times \ZZ/2$-graded Lie algebra where the differential is of bidegree $(1,+)$.
 Fix a rank one supercharge $Q \in S$ satisfying $Q^2 = 0$ for which we use to perform the a holomorphic twist of 11-dimensional supergravity.  
@@
 
+\paragraph{
 Such a supercharge defines a maximal isotropic subspace $L \subset V$. 
-We can decompose the algebra into $\lie{sl}(5)$ representations, using the isomorphisms
+We can decompose the algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations by
 \deq{
@@
 }
-As $\fsl(L) = \fsl(5)$-modules we have
-\[
-V = L \oplus L^\vee \oplus \CC_t
-\]
-and $\so(11, \CC)$ decomposes as
+Also, $\lie{so}(11, \CC)$ decomposes as
 \[
@@
 Let ${\rm Stab}(Q) \subset \lie{so}(11,\CC)$ be the stabilizer of $Q$. 
-This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.
+This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$. }
 
@@
 \[
-[Q,-] \colon \lie{so}(11;\CC) \to S 
+[Q,-] \colon \lie{so}(11,\CC) \to S 
 \] 
@@
 In these references, the algebra $\m2$ is defined as an $L_\infty$  
-central extension of $\siso_{11d}$.
+central extension of $\lie{siso}_{11d}$.
 
@@
 In \cite{CLsugra} it is shown how $D2k$ branes couple to type IIA supergravity in the twisted situation. 
-We have already shown how the dimensional reduction of 11-dimensional supergravity along a holomorphic circle $S^1 \subset \CC^\times$ is equivalent to the $\SU(4)$ invariant twist of type IIA supergravity
+We have already shown how the dimensional reduction of 11-dimensional supergravity along a holomorphic circle $S^1 \subset \CC^\times$ is equivalent to the $SU(4)$ invariant twist of type IIA supergravity
 \[

### 2022-10-10 fivebranes/fact.tex
merge

@@
 
-Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloOmega,costello2021twisted,CP}.
+Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloM5,costello2021twisted,CP}.
 The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
@@
 The following proposition summarizes that this $\C^\times$-action is compatible with the $L_\infty$ structure on $\cL_{sugra}$.
+Its proof is an immediate computation.
 
@@
 \end{prop}
-\begin{proof}
-The only nontrivial bracket to check compatibility with the $\C^\times$ action is the one which takes two $\gamma$-type sections to a $\mu$-type section of the form
-\[
-[\gamma_1, \gamma_2] = \Omega^{-1} \vee (\del \gamma_1 \wedge \del \gamma_2) 
-\]
-where $\Omega \vee (-)$ is the operation which takes a four-form
 
-It suffices to check equivariance in local coordinates; there are three cases.
-Suppose $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^j(t;w,z) \d z_j$where $f^i,g^j$ are de Rham--Dolbeault forms for $i,j=1,2,3$. 
-Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = \lambda^{-1} g^j(\lambda t;\lambda w, z) \d z_j$. 
-Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
-\beqn
-\begin{array}{llll}
-\label{eqn:lambda1} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
-\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a} .
-\end{array}
-\eeqn
-We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
-\begin{multline}
-\del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z) \d w_a \d z_i \d z_l \d z_j + \del_{z_k} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d z_k \d z_i \d w_b \d z_j \\  + \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d w_a \d z_i \d w_b \d z_j .
-\end{multline}
-Thus in the notation above we have 
-\begin{align*}
-F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \\
-G^a(t;w,z) & = \ep_{ilj} \ep_{ab} \del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z)
-+ \ep_{kij} \ep_{ab} \del_{z_k} f^i(t;w,z) \del_{w_a} g^j(t;w,z)  .
-\end{align*}
-We compute the action of $\lambda \in \C^\times$ on $\mu = F^k \del_{z_k}$
-\[
-\lambda \cdot \left(F^k \del_{z_k} \right) = \ep_{ab} \ep_{ijk} \lambda^{-1} \del_{w_a} f^i(\lambda t;\lambda w,z) \lambda^{-1} \del_{w_b} g^j(\lambda t;\lambda w,z) \del_{z_k} .
-\]
-Thus the first part of \eqref{eqn:lambda1} is satisfied. 
-Similarly we observe that $\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right)  = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a}$.
-
-The next case is when $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^a(t;w,z) \d w_a$where $f^i,g^a$ are de Rham--Dolbeault forms for $i=1,2,3$ and $a=1,2$. 
-Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = g^a(\lambda t;\lambda w, z) \d w_a$. 
-Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
-\beqn
-\begin{array}{llll}
-\label{eqn:lambda2} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-1} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
-\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-1} G^a(\lambda t;\lambda w,z) \del_{w_a} .
-\end{array}
-\eeqn
-We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
-\begin{multline}
-\del_{w_b} f^i(t;w,z) \del_{z_j} g^a(t;w,z) \d w_b \d z_i \d z_j \d w_a + \del_{z_k} f^i(t;w,z) \del_{w_b} g^a(t;w,z) \d z_k \d z_i \d w_b \d w_a \\  + \del_{z_j} f^i(t;w,z) \del_{z_k} g^a(t;w,z) \d z_j \d z_i \d z_k \d w_a .
-\end{multline}
-Thus in the notation above we have 
-\begin{align*}
-F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{z_l} g^b(t;w,z) + \ep_{ab} \ep_{kij} \del_{z_k} f^i(t;w,z) \del_{w_a} g^b(t;w,z) \\
-G^a(t;w,z) & = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) .
-\end{align*}
-We compute the action of $\lambda \in \C^\times$ on $\mu = G^a \del_{z_a}$
-\[
-\lambda \cdot \left(G^a \del_{w_a} \right) = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) \lambda^{-1} \del_{w_a} .
-\]
-Thus the second part of \eqref{eqn:lambda2} is satisfied. 
-Similarly we observe that $\lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right)  = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k}$.
-
-The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
-The argument is nearly identical so we omit the details. 
-\end{proof}
+%\begin{proof}
+%The only nontrivial bracket to check compatibility with the $\C^\times$ action is the one which takes two $\gamma$-type sections to a $\mu$-type section of the form
+%\[
+%[\gamma_1, \gamma_2] = \Omega^{-1} \vee (\del \gamma_1 \wedge \del \gamma_2) 
+%\]
+%where $\Omega \vee (-)$ is the operation which takes a four-form 
+%
+%It suffices to check equivariance in local coordinates; there are three cases.
+%Suppose $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^j(t;w,z) \d z_j$where $f^i,g^j$ are de Rham--Dolbeault forms for $i,j=1,2,3$. 
+%Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = \lambda^{-1} g^j(\lambda t;\lambda w, z) \d z_j$. 
+%Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
+%\beqn
+%\begin{array}{llll}
+%\label{eqn:lambda1} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
+%\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a} .
+%\end{array}
+%\eeqn
+%We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
+%\begin{multline}
+%\del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z) \d w_a \d z_i \d z_l \d z_j + \del_{z_k} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d z_k \d z_i \d w_b \d z_j \\  + \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d w_a \d z_i \d w_b \d z_j .
+%\end{multline}
+%Thus in the notation above we have 
+%\begin{align*}
+%F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \\
+%G^a(t;w,z) & = \ep_{ilj} \ep_{ab} \del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z)
+%+ \ep_{kij} \ep_{ab} \del_{z_k} f^i(t;w,z) \del_{w_a} g^j(t;w,z)  .
+%\end{align*}
+%We compute the action of $\lambda \in \C^\times$ on $\mu = F^k \del_{z_k}$
+%\[
+%\lambda \cdot \left(F^k \del_{z_k} \right) = \ep_{ab} \ep_{ijk} \lambda^{-1} \del_{w_a} f^i(\lambda t;\lambda w,z) \lambda^{-1} \del_{w_b} g^j(\lambda t;\lambda w,z) \del_{z_k} .
+%\]
+%Thus the first part of \eqref{eqn:lambda1} is satisfied. 
+%Similarly we observe that $\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right)  = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a}$. 
+%
+%The next case is when $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^a(t;w,z) \d w_a$where $f^i,g^a$ are de Rham--Dolbeault forms for $i=1,2,3$ and $a=1,2$. 
+%Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = g^a(\lambda t;\lambda w, z) \d w_a$. 
+%Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that
+%\beqn
+%\begin{array}{llll}
+%\label{eqn:lambda2} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-1} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
+%\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-1} G^a(\lambda t;\lambda w,z) \del_{w_a} .
+%\end{array}
+%\eeqn
+%We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
+%\begin{multline}
+%\del_{w_b} f^i(t;w,z) \del_{z_j} g^a(t;w,z) \d w_b \d z_i \d z_j \d w_a + \del_{z_k} f^i(t;w,z) \del_{w_b} g^a(t;w,z) \d z_k \d z_i \d w_b \d w_a \\  + \del_{z_j} f^i(t;w,z) \del_{z_k} g^a(t;w,z) \d z_j \d z_i \d z_k \d w_a .
+%\end{multline}
+%Thus in the notation above we have 
+%\begin{align*}
+%F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{z_l} g^b(t;w,z) + \ep_{ab} \ep_{kij} \del_{z_k} f^i(t;w,z) \del_{w_a} g^b(t;w,z) \\
+%G^a(t;w,z) & = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) .
+%\end{align*}
+%We compute the action of $\lambda \in \C^\times$ on $\mu = G^a \del_{z_a}$
+%\[
+%\lambda \cdot \left(G^a \del_{w_a} \right) = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) \lambda^{-1} \del_{w_a} .
+%\]
+%Thus the second part of \eqref{eqn:lambda2} is satisfied. 
+%Similarly we observe that $\lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right)  = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k}$. 
+%
+%The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
+%The argument is nearly identical so we omit the details. 
+%\end{proof}
 

### 2022-10-10 fivebranes/index.tex
merge

@@
 Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$.
-A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{WittenHolography}.
+A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{WittenAdS}.
 Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values.
@@
 The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
-This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWe36}.
+This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWsuco2}.
 

### 2022-10-10 fivebranes/intro.tex
merge

@@
 Since the index is only really sensitive to the minimal twist, it is reasonable that we can compute the index using our formulation of twisted eleven-dimensional supergravity.
-We will obtain known formulas as a character of the Hilbert space of eleven-dimensional supergravity on $AdS_7\times S^{4}$ in \S\ref{s:states} using our description of twisted supergravity.
+We will obtain known formulas as a character of the Hilbert space of eleven-dimensional supergravity on $AdS_7\times S^{4}$ in \S\ref{sec:states} using our description of twisted supergravity.
 
@@
 \eeqn
-Then, the avatar of our conjectural description in \eqref{eqn:finiteTensor} at the level of the single particle superconformal index is
+Then, the avatar of our description in \eqref{eqn:finiteTensor} at the level of the single particle superconformal index is
 \beqn
@@
 \eeqn
-
 From these formulas it is manifest that the holographic relation $\chi_{grav} = \lim_{N \to \infty} \chi_N$ holds.
 
-We highlight the expression that our prescription yields for the theory of type $A_{1}$:
+We highlight the expression that our prescription yields for the theory of type~$A_{1}$.
 

### 2022-10-12 fivebranes/intro.tex
rank 2 agt and acknowledgements

@@
 At the level of this twist, the theory is defined on any complex three-fold (equipped with a square root of its canonical bundle). 
-In this section, we consider the $\cN=(2,0)$ theory on the threefold $Y = \text{Tot}(L \to S)$ as a single fivebrane supported on the closed submanifold
+In this section, we consider the $\cN=(2,0)$ theory on the threefold $Z = \text{Tot}(L \to S)$ as a single fivebrane supported on the closed submanifold
 \beqn
-Y \hookrightarrow \R \times X .
+Z \hookrightarrow \R \times X .
 \eeqn
-We will denote the corresponding factorization algebra of observables on $Y$ by $\Obs_1$.
+We will denote the corresponding factorization algebra of observables on $Z$ by $\Obs_1$.
 
@@
 
-We place this factorization algebra on the three-fold $Y$ which is the total space of the line bundle $L \to S$. 
 Choosing a fiberwise hermitian metric affords a norm map 
 \[
-\pi \colon Y \to \R_{+}
+\pi \colon Z \to \R_{+}
 \] 
@@
 \begin{conj}
-Let $\operatorname{Higgs}_{GL(1)} (S,L)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields take values in the rank two bundle $W$.
+Let $\operatorname{Higgs}_{GL(1)} (S,L)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields has coefficients in the rank two bundle $W$.
 The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
 \beqn
-\cO \left(\operatorname{Higgs}_{GL(1)} (S,L)\right) .
+\cO \left(\operatorname{Higgs}_{GL(1)} (S,W)\right) .
 \eeqn
@@
 
+We emphasize that the moduli space in question is really sensitive to the complex geometry of the entire fivefold $X$, at least in the neighborhood of the total space of $L$.
+
 While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities.
-
 Above, we have mentioned a particular deformation of the observables of the six-dimensional $\cN = (2,0)$ theory by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$.
 We point out that this deformation is of the same spirit considered in \cite{BeemEtAl}.
-One can identify (though we do not do that in this paper) this deformation of $\pi_{*} \Obs_1|_{\R_{>0}}$ with the Heisenberg algebra.
+For a particular choice of the fivefold $X$, one can identify (though we do not do that in this paper) this deformation of $\pi_{*} \Obs_1|_{\R_{>0}}$ with the Heisenberg algebra.
 
-For a particular choice of $S,L,W$, we expect the superconformal element will deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
+We expect that one may judiciously choose $X$ such that the superconformal element will also deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
 
@@
 
-Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactify $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
-From our conjectural description of $\Obs_{A_1}$ (we denote this factorization algebra by $\til\Obs_2$ in the body of the paper) given in \S \ref{s:fact}, one can see that this classical limit of the associative dg algebra is of the form
-\beqn
-U \left(\cE(3|6)|_{\C^\times \times \C^2}\right) .
-\eeqn
-This is meant to indicate the enveloping algebra of a super Lie algebra $\cE(3|6)|_{\C^\times \times \C^2}$ which is a `punctured' version of the exceptional simple super Lie algebra $E(3|6)$. 
-In particular, $E(3|6)$ sits inside this super Lie algebra as the positive modes.
-Again, in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory. 
-At the quantum level, we expect that the algebra gets deformed to the enveloping algebra of a certain ($L_\infty$) central extension of this super Lie algebra.
+Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $Z$ and pushforward along the norm map to obtain an associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$.
+We re-emphasize that in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory.
+At the quantum level, we expect that the algebra gets deformed twisted by a cocycle.
 
 \begin{conj}
-The associative dg algebra $\oint_{S^1} \Obs_{A_1}$ (after turning on this central extension) acts on the cohomology of the moduli space of $SU(2)$-instantons on flat space~$\C^2 = \R^4$. 
+  The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ (after turning on the twisting cocycle) acts on
+  \beqn
+  \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)
+  \eeqn
 \end{conj}
 
-Let us summarize some evidence for this claim which is in line with the AGT correspondence. 
-First off, the Hilbert space of the five-dimensional theory is simply given as the space of local operators $\Obs_{A_1}(0)$.
-The Schur limit of the superconformal index, which is the character of this space of local operators, is precisely the character of the Virasoro vacuum module $\frac{q^2}{1-q}$.
-Furthermore, the algebra $\oint_{S^1} \Obs_{A_1}$ naturally acts on this space, and we expect that deforming this algebra in accordance with the Schur limit is exactly the Virasoro algebra $U(\text{Vir})$.
+As in the abelian case, we may hilight some compatibilities with the usual AGT correspondence.
+For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ deforms the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$.
+We again expect that for a judicious choice of $X$, the Hilbert space deforms to the equivariant cohomology of the moduli of rank 2 instantons on $\C^{2}$, and the action compatibly deforms to the action in the rank 2 case of the AGT correspondence.
+
+A result in the main body of the paper may be viewed as a check of these conjectures in the case where $Z = \operatorname{Tot}(\cO(-1)\to \C\P^{2})$ and $W = K^{1/2}_{Z}\otimes \C^{2}$.
+In this case, the unit circle bundle in $L$ may be identified with the Hopf fibration $S^{5}\to \C\P^{2}$.
+In \cite{Kim:2013nva}, the superconformal index of the 6d $\cN=(2,0)$ theory is computed by identifying it with the $S^{1}\times S^{5}$ partition function, and reducing along the Hopf fiber of $S^{5}$ to further identify it with the superconformal index of 5d $\cN=2$ gauge theory on $\C\P^{2}$.
+The latter quantity is computed in terms of the Nekrasov instanton partition function, and is almost manifestly the character of $\cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$.
+The fact that we recover the same expressions as characters of the algebras of local operators $\Obs_{SL(2)}(0)$ corroborates the claim that $ \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$ is the vacuum module of $\pi_{*}\Obs_{SL(2)}|_{\R_{>0}}$.
 

### 2022-10-12 fivebranes/main.tex
rank 2 agt and acknowledgements

@@
 Special thanks are due to Ingmar Saberi for his collaborations on past, current, and future related projects.
-The work of S.R. ...
+The work of S.R.
+is supported by the Perimeter Institute for Theoretical Physics.
+Research at Perimeter Institute is supported in part by the Government of Canada, through the Department of Innovation, Science and Economic Development Canada, and by the Province of Ontario, through the Ministry of Colleges and Universities.
 The work of B.W. was supported by Boston University and the University of Edinburgh. 

### 2022-10-12 fivebranes/intro.tex
schur vs superconformal and notation

@@
 \end{tikzcd}\]
+We will elaborate on the meaning of the bottom arrow labeled ``superconformal deformation'' below.
 
@@
 As we just pointed out, the super Lie algebra $\widehat {E(5|10)}$ describes the ghost system for symmetries of eleven-dimensional supergravity after the minimal twist.
-It is quite easy to write down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $\widehat {E(5|10)}$.
+In \cite{RSW}, we wrote down an explicit realization of the residual superconformal algebra $\lie{osp}(6|2)$ on $\widehat {E(5|10)}$.
 In fact, $\lie{osp}(6|2)$ sits inside of a small (but still infinite-dimensional) super Lie algebra called $E(3|6)$.
@@
 
-Upon performing the superconformal deformation, the super Lie algebra $E(3|6)$ deforms to a familiar object in chiral CFT: the Lie algebra of vector fields on the (formal) disk.
-So, if we were to deform the conjecture above according to this Schur limit we would recover the familiar consequence that a chiral conformal field theory has as part of its symmetries the Lie algebra of vector fields on the formal disk.
+The superconformal deformation which takes the minimal twist to the nonminimal twist in the above diagrams is a certain superconformal transformation that is a Maurer-Cartan element in $\lie{osp}(6|2)$.
+This Maurer-Cartan element deforms the super Lie algebra $E(3|6)$ to a familiar object in chiral CFT: the Lie algebra of vector fields on the (formal) disk.
+So, if we were to accordingly deform the above conjecture, we would recover the familiar consequence that a chiral conformal field theory has as part of its symmetries the Lie algebra of vector fields on the formal disk.
 Of course, there is a richer algebra around---the Virasoro algebra---which extends the Lie algebra of vector fields on the {\em punctured} disk. 

### 2022-10-12 fivebranes/twisted.tex
schur vs superconformal and notation

@@
 
-\parsec[s:twistedsugra]
+%parsec[s:twistedsugra]
 
-Before proceeding with the appearance of fivebranes in the minimal twist of eleven-dimensional supergravity we discuss a related, but simpler, five-dimensional theory.
-This five-dimensional theory, as argued by Costello \cite{CostelloM5}, arises from placing eleven-dimensional supergravity in the so-called `twisted $\Omega$-background'.
-We will use this theory for the sake of highlighting more accessible examples of the constructions later on in the paper.
+%Before proceeding with the appearance of fivebranes in the minimal twist of eleven-dimensional supergravity we discuss a related, but simpler, five-dimensional theory.
+%This five-dimensional theory, as argued by Costello \cite{CostelloM5}, arises from placing eleven-dimensional supergravity in the so-called `twisted $\Omega$-background'.
+%We will use this theory for the sake of highlighting more accessible examples of the constructions later on in the paper.
 
-In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
-The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
-We do not recall the precise relationship between this five-dimensional theory and eleven-dimensional supergravity, but it will be helpful to recall some features of the five-dimensional theory.
+%In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
+%The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
+%We do not recall the precise relationship between this five-dimensional theory and eleven-dimensional supergravity, but it will be helpful to recall some features of the five-dimensional theory.
 
-This five-dimensional theory is formally similar to a non-commutative version of Chern--Simons theory.
-It exists on any manifold of the form
-\[
-  S\times Y
-\]
-where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.
-We denote the corresponding holomorphic two-form on $Y$ by $\Omega_Y$.
+%This five-dimensional theory is formally similar to a non-commutative version of Chern--Simons theory.
+%It exists on any manifold of the form
+%\[
+%  S\times Y
+%\]
+%where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.
+%We denote the corresponding holomorphic two-form on $Y$ by $\Omega_Y$.
 
-There are two parameters in this theory $\delta$ and $\ep$, see \textit{loc. cit.}.
-The parameter $\delta$ controls the coupling of the Chern--Simons action, which in this section and going forward we will simply set to be the unit. 
-The parameter $\ep$ measures the non-commutativity---
-it appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star_\ep$.
+%There are two parameters in this theory $\delta$ and $\ep$, see \textit{loc. cit.}.
+%The parameter $\delta$ controls the coupling of the Chern--Simons action, which in this section and going forward we will simply set to be the unit.
+%The parameter $\ep$ measures the non-commutativity---
+%it appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star_\ep$.
 
-We consider the following subalgebra of complex-valued forms on $S\times Y$:
-\[
-\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
-\]
-In local coordinates a general differential form in $\cL_{5d}$ admits a decomposition as
-\[
-\alpha = \alpha^{\Bar I} \d \zbar_{\Bar I} + \alpha^{\Bar I}_t \d t \d \zbar_{\Bar I} .
-\]
+%We consider the following subalgebra of complex-valued forms on $S\times Y$:
+%\[
+%\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
+%\]
+%In local coordinates a general differential form in $\cL_{5d}$ admits a decomposition as
+%\[
+%\alpha = \alpha^{\Bar I} \d \zbar_{\Bar I} + \alpha^{\Bar I}_t \d t \d \zbar_{\Bar I} .
+%\]
 %We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
-We can understand the Moyal product along the holomorphic symplectic surface $Y$ as endowing $\cL_{5d}[[\ep]]$ with the structure of a dg algebra. 
-Of course, we can forget down to a dg Lie algebra structure with respect to the Moyal commutator $[-,-]_{\star_{\ep}}$.
+%We can understand the Moyal product along the holomorphic symplectic surface $Y$ as endowing $\cL_{5d}[[\ep]]$ with the structure of a dg algebra.
+%Of course, we can forget down to a dg Lie algebra structure with respect to the Moyal commutator $[-,-]_{\star_{\ep}}$.
 
-In the BV formalism the space of fields of the five-dimensional theory is $\cL_{5d}[[\ep]] [1]$. 
-The fundamental field of the five-dimensional theory is a $\C[[\ep]]$ one-form on~$S \times Y$, which is a degree $0$ element in $\cL_{5d}[[\ep]] [1]$.
+%In the BV formalism the space of fields of the five-dimensional theory is $\cL_{5d}[[\ep]] [1]$.
+%The fundamental field of the five-dimensional theory is a $\C[[\ep]]$ one-form on~$S \times Y$, which is a degree $0$ element in $\cL_{5d}[[\ep]] [1]$.
 
-We can take a gauge condition where the $\d t$ component of the one-form $\alpha_t$ vanishes.
-In this case the equations of motion for the one-form field, in components, simply reads
-\beqn
-\del_{\zbar_{\Bar{i}}} \alpha^{\Bar{j}} + \alpha^{\Bar{i}} \star_\ep \alpha^{\Bar{j}} = 0,
-\eeqn
-together with the condition that $\del_t \alpha^{\Bar{i}} = 0$ for all $\Bar{i}, \Bar{j}$.
+%We can take a gauge condition where the $\d t$ component of the one-form $\alpha_t$ vanishes.
+%In this case the equations of motion for the one-form field, in components, simply reads
+%\beqn
+%\del_{\zbar_{\Bar{i}}} \alpha^{\Bar{j}} + \alpha^{\Bar{i}} \star_\ep \alpha^{\Bar{j}} = 0,
+%\eeqn
+%together with the condition that $\del_t \alpha^{\Bar{i}} = 0$ for all $\Bar{i}, \Bar{j}$.
 %Here $\star_{\ep}$ denotes the holomorphic Moyal product on $Y$ and $\del_t$, $$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.
@@
 
-Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $f \in C^\infty (S\times Y)[[\ep]]$. 
-Explicitly, the corresponding infinitesimal gauge transformation for the one-form component of $\alpha$ is given by
-\[
-\alpha \mapsto \alpha + \del_t f \d t +\del_{\zbar_{\Bar{i}}} f \d \zbar_{\Bar{i}} + [f, \alpha]_{\star_\ep} .
-\]
-Here, $[-,-]_{\star_{\ep}}$ is the commutator with respect to the Moyal product $\star_\ep$.
+%Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $f \in C^\infty (S\times Y)[[\ep]]$.
+%Explicitly, the corresponding infinitesimal gauge transformation for the one-form component of $\alpha$ is given by
+%\[
+%\alpha \mapsto \alpha + \del_t f \d t +\del_{\zbar_{\Bar{i}}} f \d \zbar_{\Bar{i}} + [f, \alpha]_{\star_\ep} .
+%\]
+%Here, $[-,-]_{\star_{\ep}}$ is the commutator with respect to the Moyal product $\star_\ep$.
 
-The full BV action functional describing this model is the non-commutative Chern--Simons action
-\beqn
-S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star_\ep \alpha \star_\ep \alpha \right) \wedge \Omega_Y .
-\eeqn
-Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$ (notice that that no holomorphic derivatives appear in the kinetic term due to the appearance of $\Omega_Y$).
+%The full BV action functional describing this model is the non-commutative Chern--Simons action
+%\beqn
+%S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star_\ep \alpha \star_\ep \alpha \right) \wedge \Omega_Y .
+%\eeqn
+%Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$ (notice that that no holomorphic derivatives appear in the kinetic term due to the appearance of $\Omega_Y$).
 
@@
 
-Associated to a foliation $F$, its normal bundle is the quotient bundle $Q = T^{\C}_{M}/F$.
-We assume in addition to having a THF structure that $M$ is equipped with the data of a trivialization $\wedge^{n} Q^* \cong \C_{M}$ which we will denote by~$\Omega_F$.
-We require that the trivialization is constant along the leaves of $F$, i.e.
-that $D\Omega_{F} = 0$.
-If $F \cap \Bar{F} = 0$, then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
-For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure.
-
 There is a notion of the sheaf of `holomorphic functions' $\cO_F$ on any manifold $M$ equipped with a THF~$F$---in the language of foliations these are the functions on $M$ which are constant along the leaves of $F$.
@@
 The fields of our eleven-dimensional theory may be described as sheaves of flat sections of some natural partially flat bundles on $M$.
-First, we note that the bundle normal bundle $Q$ and its dual $Q^{*}$ admit a natural connection defined along the leaves of $F$, the so-called Bott connection \cite{KamberTondeur}.
+Associated to a foliation $F$, its normal bundle is the quotient bundle $Q = T^{\C}_{M}/F$.
+The normal bundle $Q$ and its dual $Q^{*}$ admit natural connections defined along the leaves of $F$, the so-called Bott connection \cite{KamberTondeur}.
 
@@
 
-Let $\cA^k(Q), \cA^{k}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have fine resolutions
+Let $\cA^k_{F}(Q), \cA^{k}_{F}(Q^{*})$ be the sheaves of $C^\infty$-sections of the bundles $\wedge^k F^{*} \otimes Q$ and $\wedge^{k}F^{*}\otimes Q^{*}$ respectively. Then we have fine resolutions
 
 \beqn
-\vartheta_F \xto{\simeq} \cA^\bu(Q) \ \ \ \ \ \ \ \Omega^1_F \xto{\simeq}  \cA^\bu(Q^*)
+\vartheta_F \xto{\simeq} \cA_F^\bu(Q) \ \ \ \ \ \ \ \Omega^1_F \xto{\simeq}  \cA_F^\bu(Q^*)
 \eeqn
 The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(Q)$ the structure of a dg Lie algebra.
-Likewise, the sheaf $\Omega^{1}_{F}$ carries the contragradient action of $\vartheta_{F}$ which likewise extends to equip $\cA^{\bu}(Q^{*})$ with the structure of a dg-module over $\cA^{\bu}(Q)$.
+Likewise, the sheaf $\Omega^{1}_{F}$ carries the contragradient action of $\vartheta_{F}$ which likewise extends to equip $\cA^{\bu}(Q^{*})$ with the structure of a dg-module over $\cA_{F}^{\bu}(Q)$.
 
-The holomorphic derham and divergence operators also have analogues in the THF setting, which are now defined on the leaf space.
-First, for a vector bundle with  $\cA^{p,q}(Q)$ denote the sheaf of $C^{\infty}$ sections of $\wedge^{q} F^{*}\otimes \wedge^p Q$.
+The holomorphic deRham and divergence operators also have analogues in the THF setting, which are now defined on the leaf space.
+First, for a vector bundle with  $\cA_{F}^{p,q}(Q)$ denote the sheaf of $C^{\infty}$ sections of $\wedge^{q} F^{*}\otimes \wedge^p Q$.
 The fields of the eleven-dimensional theory, which we phrased in terms of a mixed type of de Rham and Dolbeault cohomology, can now be elegantly repackaged in terms of the above.
+
 For illustration, let us focus on the fields $\beta,\gamma$ which on $S \times X$ combine to form the complex
@@
 
+To make sense of a THF analogue of the holomorphic divergence operator, we will assume that in addition to having a THF structure that $M$ is equipped with the data of a trivialization $\wedge^{n} Q^* \cong \C_{M}$ which we will denote by~$\Omega_F$.
+We require that the trivialization is constant along the leaves of $F$, i.e.
+that $D\Omega_{F} = 0$.
+If $F \cap \Bar{F} = 0$, then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
+For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure
+
 Next we should say where the generalized $\mu$ and $\nu$ fields live. 
-The volume form $\Omega_F \colon \C \cong \wedge^n \theta_F^*$ determines an isomorphism $\cA^{p,q}_F \cong \cA^{n-p,q}_F$ for each $p,q$.
+The volume form $\Omega_F \colon \C \cong \wedge^n Q^*$ determines an isomorphism $\cA^{p,q}_F \cong \cA^{n-p,q}_F$ for each $p,q$.
 Via this isomorphism we can identify $D \colon \cA^{n-1,\bu}_F \to \cA^{n,\bu}_F$ with a differential operator
 \beqn
-\Div \colon \cA_F^{\bu}(\theta_F) \to \cA^\bu_F .
+\Div \colon \cA_F^{\bu}(Q) \to \cA^\bu_F .
 \eeqn
@@
 \beqn
-\beta \in \Pi \cA_F^\bu (M) , \quad \gamma \in \cA^{1,\bu}_F (M) , \quad \mu \in \Pi \cA^\bu_F(M, \theta_F), \quad \nu \in \cA_F^\bu (M)  .
+\beta \in \Pi \cA_F^\bu , \quad \gamma \in \cA^{\bu}_F (Q^*) , \quad \mu \in \Pi \cA^\bu_F(Q), \quad \nu \in \cA_F^\bu  .
 \eeqn
+
 Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$.
+
+For convenience, we will let $L$ denote the dg vector bundle
+\beqn
+\Pi (\C \oplus Q)\to Q^* \oplus \C
+\eeqn
+
+with differential given by the block matrix $\operatorname{diag}(D, \Div)$ and succinctly write the space of fields as $\cA^{\bu}_{F}(L)$.
+
 The free part of the action functional (cf. \eqref{eqn:free}) is 

### 2022-10-12 fivebranes/intro.tex
agt2

@@
 \beqn\label{eqn:finiteTensor}
-\Obs_{brane} (N) = \cF_{-1} \otimes \cF_2 \otimes \cdots \otimes \cF_{N-2} .
+\Obs_{N-branes} = \cF_{-1} \otimes \cF_2 \otimes \cdots \otimes \cF_{N-2} .
 \eeqn
@@
 \beqn
+\label{eqn:AN-1}
 \Obs_{A_{N-1}} = \cF_0 \otimes \cF_1 \otimes \cdots \otimes \cF_{N-2} .
@@
 
-Even stronger evidence would involve the factorization algebras $\Obs_{brane}(N)$. We will outline some expectations in later sections but leave a full treatment to future work.
+Even stronger evidence would involve the factorization algebras $\Obs_{N-branes}$. We will outline some expectations in later sections but leave a full treatment to future work.
 
@@
 
-In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{brane}(1)$ above.
+In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{1-brane}$.
 We emphasize that we only consider the classical limit of this factorization algebra in this paper.
@@
 \begin{conj}
-Let $\operatorname{Higgs}_{GL(1)} (S,L)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields has coefficients in the rank two bundle $W$.
+\label{conj:AGT1}
+Let $\operatorname{Higgs}_{GL(1)} (S,W)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields has coefficients in the rank two bundle $W$.
 The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
@@
 
-We emphasize that the moduli space in question is really sensitive to the complex geometry of the entire fivefold $X$, at least in the neighborhood of the total space of $L$.
+We emphasize that the moduli space in question is really sensitive to the complex geometry of the entire fivefold $X$, at least in the neighborhood of the total space of~$L$.
 
@@
 
-We expect that one may judiciously choose $X$ such that the superconformal element will also deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of $\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
+We expect that one may judiciously choose $X$ such that the superconformal element will also deform the Hilbert space of the minimal twist in five dimensions to the equivariant cohomology of the moduli of abelian instantons on $\C^{2}$, and that the action of~$\pi_{*}\Obs_{1}|_{\R_{>0}}$ compatibly deforms to the Heisenberg action studied by Grojnowski-Nakajima.
 
@@
 
+The next simplest application of our holographic approach is to describe the observables of the six-dimensional theory of type~$A_1$. 
 Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $Z$ and pushforward along the norm map to obtain an associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$.
@@
 \begin{conj}
+Let $\operatorname{Higgs}_{SL(2)} (S,W)$ denote the moduli space of $SL(2)$ Higgs bundles on the complex surface~$S$ where the Higgs fields has coefficients in the rank two bundle~$W$.
 The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ (after turning on the twisting cocycle) acts on
   \beqn
-  \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)
+  \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right) .
   \eeqn
@@
 
-A result in the main body of the paper may be viewed as a check of these conjectures in the case where $Z = \operatorname{Tot}(\cO(-1)\to \C\P^{2})$ and $W = K^{1/2}_{Z}\otimes \C^{2}$.
-In this case, the unit circle bundle in $L$ may be identified with the Hopf fibration $S^{5}\to \C\P^{2}$.
-In \cite{Kim:2013nva}, the superconformal index of the 6d $\cN=(2,0)$ theory is computed by identifying it with the $S^{1}\times S^{5}$ partition function, and reducing along the Hopf fiber of $S^{5}$ to further identify it with the superconformal index of 5d $\cN=2$ gauge theory on $\C\P^{2}$.
+A result in the main body of the paper may be viewed as a check of these conjectures in the case where $Z = \operatorname{Tot}(\cO(-1)\to \C\PP^{2})$ and $W = K^{1/2}_{Z}\otimes \C^{2}$.
+In this case, the unit circle bundle in $L$ may be identified with the Hopf fibration $S^{5}\to \C\PP^{2}$.
+In \cite{Kim:2013nva}, the superconformal index of the 6d $\cN=(2,0)$ theory is computed by identifying it with the $S^{1}\times S^{5}$ partition function, and reducing along the Hopf fiber of $S^{5}$ to further identify it with the superconformal index of 5d $\cN=2$ gauge theory on $\C\PP^{2}$.
 The latter quantity is computed in terms of the Nekrasov instanton partition function, and is almost manifestly the character of $\cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$.

### 2022-10-13 fivebranes/index.tex
section 3 stuff

@@
 
-\parsec[s:brkevin]
-As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory.
+This procedure is implemented at the level of the $\Omega$-deformed nonminimal twist on flat space in the appendix of \cite{CostelloM5}.
+%\parsec[s:brkevin]
+%As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory.
 The relevant local calculation can be found in the appendix of \cite{}; our goal here is to simply identify the salient global features that allow one to reduce to said local calculation.
 
-We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
-\[
-0 \times C \subset \R \times \T^* C .
-\]
-Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.
+%We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
+%\[
+%0 \times C \subset \R \times \T^* C .
+%\]
+%Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.
 
-Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.
+%Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.
 
-If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
+%If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection.
 The restriction $p| \mathring M$ equips $\mathring M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$.
@@
 
-Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$.
+%Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$.
 The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres.
@@
 
-Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.
+%Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.
 
-For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
-We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
-We first proceed before turning on the flux sourced by the brane.
+%For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
+%We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
+%We first proceed before turning on the flux sourced by the brane.
 
-The theory admits a natural `vacuum' boundary condition at $r=0$.
-In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.
+%The theory admits a natural `vacuum' boundary condition at $r=0$.
+%In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.
 
-The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
-The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
-Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.
+%The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
+%The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
+%Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.
 
-Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
-\[
-\alpha = f(w) \delta^{(r)}_{z=0}
-\]
-where $f$ is some holomorphic function.
-Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
-It is convenient to parameterize such boundary modifications algebraically by expressions of the form
-\[
-\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
-\]
-Linear combinations of such states form a dense subspace of all possible modifications at the boundary.
+%Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
+%\[
+%\alpha = f(w) \delta^{(r)}_{z=0}
+%\]
+%where $f$ is some holomorphic function.
+%Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
+%It is convenient to parameterize such boundary modifications algebraically by expressions of the form
+%\[
+%\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
+%\]
+%Linear combinations of such states form a dense subspace of all possible modifications at the boundary.
 
-The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
-The phase space at the boundary $C$ can be identified with the following cohomology
-\[
-\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
-\]
-where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
-We refer to the section below for a reminder on this geometric structure.
+%The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
+%The phase space at the boundary $C$ can be identified with the following cohomology
+%\[
+%\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
+%\]
+%where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
+%We refer to the section below for a reminder on this geometric structure.
 
-The phase space is equipped with a natural symplectic form given by
-\[
-\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
-\]
-There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
-The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
+%The phase space is equipped with a natural symplectic form given by
+%\[
+%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
+%\]
+%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
+%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
 
@@
 
-We now consider the situation of backreacting some number of (twisted) fivebranes in our eleven-dimensional model.
+We now carry out the above procedure to backreact fivebranes in our eleven-dimensional model.
 Let $Z$ be a three-fold that the fivebranes wrap.
@@
   \begin{tikzcd}
-    0 \ar[r] & F_{M}\cap T_{M/Z}^{\C}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
-    0 \ar[r] & T_{M/Z}^{\C}\ar[r] & T_{M}^{\C}\ar[r] & T_{Z}^{\C}\ar[r] & 0.
+    0 \ar[r] & F_{M}\cap T_{M/Z}\ar[r]\ar[d] & F_{M}\ar[r]\ar[d]  & \pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
+    0 \ar[r] & T_{M/Z}\ar[r] & T_{M}\ar[r] & T_{Z}\ar[r] & 0.
   \end{tikzcd}
 \]
+We note that all vector bundles in the above diagram are complexified.
 
@@
   \begin{tikzcd}
-    0 \ar[r] & F_{\mathring M}\cap T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r]\ar[d] & F_{\mathring M}\ar[r]\ar[d]  & h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
-    0 \ar[r] & T_{\mathring M/\R_{>0}\times Z}^{\C}\ar[r] & T_{\mathring M}^{\C}\ar[r] & h^{*}T_{\R_{>o}}\oplus T_{Z}^{\C}\ar[r] & 0.
+    0 \ar[r] & F_{\mathring M}\cap T_{\mathring M/\R_{>0}\times Z}\ar[r]\ar[d] & F_{\mathring M}\ar[r]\ar[d]  & h^{*}T_{\R_{>0}}\oplus\pi^{*}T^{0,1}_{Z}\ar[r]\ar[d] & 0 \\
+    0 \ar[r] & T_{\mathring M/\R_{>0}\times Z}\ar[r] & T_{\mathring M}\ar[r] & h^{*}T_{\R_{>o}}\oplus T_{Z}\ar[r] & 0.
   \end{tikzcd}
@@
 Explicitly, we set
+\[
+  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
+\]
+for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathing M}$ that are tangent to the fibers of $(p|\mathring M)$.
+
+Likewise, we let
+\[
+  F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}
+\] be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
+We will let $\cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.
+
+Our goal is to describe the derived pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
+
+We first note that the splitting gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
 \begin{align*}
-  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}} \\
-  F_{\R_{>0}\times Z} &  = T_{\R_{>0}}\oplus T^{0,1}_{Z} \text{ so }p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z} \\
-  \cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}} \text{ so }p^{*}\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{p^{*}F _{\R_{>0}\times Z}}
+  \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
+
+                         & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
+
 \end{align*}
 
-Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
+where we have just used that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathing M}$-modules.
 
-The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
+%Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the derived pushforward along $(p|\mathring M)_{*}$ coincides with the orinary pushforward.
+Moreover since the derived pushforward commutes with tensor product, we have that the $(p|\mathring M)_{*}\cL_{sugra}$ is given by
+
+By the projection formula, there is an isomorphism of $C^{\infty}_{\R_{>0}\times Z}$-modules
 \[
-  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L)
-\]
+\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\R_{>0}\times Z}} (p|\mathring M)_{*}\cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \to (p|\mathring M)_{*}\left ( (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\mathring M}} \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \right )\]
 
-Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the (a priori derived) functor $(p|\mathring M)_{*}$ has several nice properties.
-We may commute it past the tensor product above.
-Moreover, we may apply the functor term-wise.
-The result is that the pushforward is given by \surya{finish}
+%Now the unit of the adjunction between inverse and direct image of $C^{\infty}_{M}$-modules induces a map
+%\[
+%  \cA^{#}_{\R_{>0}\times Z} \to (p|\mathring M)_{*}(p|\mathring M)^{*}\cA ^{#}_{\R_{>0}\times Z}
+%\]
 
-We now analyze the THF differential $\thfd$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
-\surya{finish}
+ The left hand side of the above isomorphism has a canonical $\cA ^{#}_{\R_{>0}\times Z}$-modules structure.
+It remains to discuss compatibility with the differential along the base.
+The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$.
+We can construct such a connection from analyzing the behavior of the THF differential $\thfd$ under the splitting.
+
+ The THF differential induces a derivation of total degree 1 on the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ so it is determined by its restrictions
+
+\[\thfd_{i} :  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]
+
+We may understand the first few terms, along with the relations implied by $\thfd^{2} = 0$:
+\begin{itemize}
+  \item The first term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to (p|\mathring M_{*})\cA^{\bullet+1}_{\mathring M/\R_{>0}\times Z}(L)\] is the internal differential.
+
+  \item The second term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{1}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] is a partial connection.
+However, it is not flat.
+Rather the failure for flatness is captured by \[ \thfd_{1}^{2} + [\thfd_{0}, \thfd_{2}] = 0 \] where \[ \thfd_{2} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{2}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet-1}_{\mathring M/\R_{>0}\times Z}(L) \] is a nullhomotopy.
+\end{itemize}
+In particular, $\thfd_{1}$ induces a partial flat connection along $F_{\R_{>0}\times Z}$ the hypercohomology \[\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right )\].
+
+In \cite{KormanThesis} it is shown that though the above decomposition depends on the choice of splitting $\mathring \sigma$ initially chosen, the flat connection induced by $\thfd_{1}$ on the hypercohomology does not.
 
@@
 
-\begin{prop}
+\begin{prop}\label{p:dimred}
   The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
   \beqn
-  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu p_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
+  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
   \eeqn
 
-  The BV pairing is given by
-  \beqn
-  \eeqn
-
+  with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
 \end{prop}
 
-The previous result gives a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
+The BV pairing naturally descends to the above complex of sheaves.
+We can explicitly describe it as follows.
+First note that the fiber of $\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)$ at $(t,p)\in \R_{>0}\times Z$ can be computed as the cohomology of the complex
+\[
+H^{\bullet}\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right ).
+\]
+
+Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
+\[
+\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
+\]
+Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
 In particular, the result is local on $R_{>0}\times Z$.
+
 For computing the space of states, it will be useful to have a description of its global sections.
-For the computation of numerical invariants such as graded characters, of the space of states, a more drastic simplification is useful.
-Indeed, we may anticipate cohomological cancellations in the character and instead compute the character of any cochain complex that a spectral sequence whose first page is the global sections abuts to.
+The global sections of the sheaf in proposition \ref{p:dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
+\beqn
+E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q(p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
+\eeqn\label{thfss}
+We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.
 
-The global sections of the sheaf in proposition \ref{dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
+The $E_{2}$ page is similarly given by flat sections with respect to $\thfd_{1}$
 \beqn
-E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q p _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
+E_2^{p,q} = \Gamma_{\thfd_1} \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q (p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)
 \eeqn
-We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.
 
@@
 \eeqn
+In this case, the above spectral sequence clearly degenerates at the $E_{2}$-page.
 
@@
 \eeqn
-where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(\vartheta_{F})$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.
+where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(Q)$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.
 
 The relevant Maurer-Cartan element is a solution to the equations of motion for the eleven-dimensional theory deformed by this interaction.
-After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields the following equation for $\gamma$
+After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields an equation for $\gamma$ that to linear order reads:
 \beqn
-\thfd D \gamma + D_\Omega\left (\frac{\mu}{1-\nu}\right )\wedge D \gamma = N \delta_Z.
+\thfd D \gamma  = N \delta_Z.
 \eeqn
+
+The existence of a solution to this equation is a strong constraint on the THF manifold $M$.
+The relevant consequence for us is that it implies the degeneration of the spectral sequence \ref{thfss} at the $E_{2}$-page.
 
@@
 The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construciton of the Hilbert space.
-The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$.
+The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$ in proposition \ref{p:dimred}.
 We will construct the Hilbert space by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.

### 2022-10-13 fivebranes/index.tex
section 3

@@
 
-Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
-\[
-\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
-\]
+We denote the resulting infinite dimensional vector space.
+%Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
+%\[
+%\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
+%\]
 Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
@@
 \eeqn
+
+\surya{...}
 

### 2022-10-13 fivebranes/index.tex
small edits

@@
 
-We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a 2-step procedure:
+We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a two step procedure:
 
@@
   \item Place the eleven-dimensional theory on the complement of the zero section. 
-To do so, we will wish to describe the complement of the zero-section in a way that facilitates natural operations on holomorphic-topological local $L_{\infty}$-algebras.
+  To do so, we will wish to describe the complement of the zero-section in a way that facilitates a description of the perturbative theory in terms of natural operations on holomorphic-topological local $L_{\infty}$-algebras.
 
@@
 Consider the bundle $\R\oplus W$; this bundle has a canonical partially flat connection.
-We wish to consider our eleven dimensional model on $M = Tot (\R\oplus W)$ which is the total space of the \textit{real} rank five bundle $\R\oplus W$ over $Z$.
+We wish to consider our eleven dimensional model on $M = \text{Tot} (\R\oplus W)$ which is the total space of the \textit{real} rank five bundle $\R\oplus W$ over $Z$.
 The partially flat connection on $\R\oplus W$ equips $M$ with a canonical THF structure $F_{M}\subset T_{M}^{\C}$.
@@
 \]
-
-We may choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus W$ over $Z$ and a fiberwise partially hermitian metric.
-
-Explicitly, the corresponding norm defines a map
+We choose fiber coordinates of the bundle $t, w_{1}, w_{2}$ of $\R \oplus W$ over $Z$ and a fiberwise partially hermitian metric.
+The corresponding norm defines a map
 \begin{align*}
@@
 
-As we elaborated in section \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$.
+As we elaborated in \S \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$.
 Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$.
@@
 
-The existence of a partially flat connection amounts to a choice of splitting \[\sigma: \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row.
+The existence of a partially flat connection amounts to a choice of splitting \[\sigma \colon \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row.
 Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that $\sigma$ preserves the lie brackets on sections.
@@
 \[
-  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
+  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
 \]
-for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathing M}$ that are tangent to the fibers of $(p|\mathring M)$.
+for the complex resoling functions on $\mathring M$ constant in the directions of $F_{\mathring M}$ that are tangent to the fibers of $(p|\mathring M)$.
 
@@
   F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}
-\] be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
-We will let $\cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.
+\] 
+be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
+We will let $\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.
 
@@
   \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
-
                          & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
-
 \end{align*}
-
-where we have just used that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathing M}$-modules.
+where we have used the fact that pullback commutes with taking the exterior power. Here, the tensor product is take in $C^{\infty}_{\mathring M}$-modules.
 
@@
 
- The left hand side of the above isomorphism has a canonical $\cA ^{#}_{\R_{>0}\times Z}$-modules structure.
+The left hand side of the above isomorphism has a canonical $\cA ^{\#}_{\R_{>0}\times Z}$-module structure. 
 It remains to discuss compatibility with the differential along the base.
@@
 
-\[\thfd_{i} :  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]
+\[\thfd_{i} \colon  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]
 
@@
   \eeqn
-
 with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
@@
 \beqn
-M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
+M = \text{Tot} (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 - (0 \times \C^3).
 \eeqn

### 2022-10-13 fivebranes/finite.tex
merge

@@
 Combining these facts we see that $\Obs_{1}(0)$ is a module for $E(3|6)$. 
-
-In appendix \S \ref{s:kr} we will describe this module from a purely representation theoretic point of view and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
+This module turns out to be a one-dimensional extension of an irreducible $E(3|6)$-module which was classified in~\cite{KR2}. 
+%and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
 
@@
 And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.
+
+Just as in the abelian case, the local operators $\til \Obs_2(0)$ form a module over $E(3|6)$.
+It turns out that this module is irreducible~\cite{KR2}.
+
 We can now state a decategorified version of conjecture \ref{conj:fact} at the level of superconformal indices, or local characters.
@@
 \begin{conj}\label{conj:6dtwo}
-The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(2)$ is given by
+The superconformal index of the six-dimensional superconformal theory of type $A_1$ is given by
 \[
@@
 \eeqn
-The plethystic exponential of the right hand side is the vacuum character of the $W_{N}$ vertex algebra.
+The plethystic exponential of the right hand side agrees with the vacuum character of the $W_{N}$ vertex algebra.\footnote{By this we mean the principal $W$-algebra of type $A_{N-1}$.}
 \end{prop}
@@
 
-We would also like to point out compatibility of our expression with a certain ``minimally reduced'' index considered in \cite{GaiottoJihoon}. 
+We would also like to point out compatibility of our expression with a certain ``minimally reduced'' index considered in \cite{Gaiotto:2021xce}. 
 This minimal reduction is the result of sending certain parameters to zero while keeping some expression in the fugacities fixed.
@@
 \eeqn
+This yields an index which only accounts for operators which transform trivially with respect to the symmetries that the fugacities $z_3,w_2$ correspond to. 
 This will result in an index which has three remaining fugacities.
@@
 
-Next, we compare to expansions for the $\lie{sl}(N)$ theory computed in \cite{Imamura}.
+Next, we compare to expansions for the $\lie{sl}(N)$ theory computed in \cite{Imamura}, where the method of the `giant graviton' expansion is used.
 It will be convenient to change the variables $(y_i, y, q) \to (y_i,x,q)$ where 
@@
 We find $(1-x-x^3+x^6) / (1-x^2) = (1-x^3-x^4-x^5) / (1+x)$ whereas Imamura's result is $1 / (1+x)$.
-It would be interesting to explain the physical or representation theoretic source of this discrepancy.
 
 Similarly, we can obtain the $q$-expansions for the local character $\chi_3(y_i,x,q)$ of the factorization algebra $\Obs_3$ and compare it to the $q$-expansion for the superconformal index of the $\lie{sl}(3)$ theory in \cite{Imamura}.
-Up to order $q^3$ we have
+Up to order $q^2$ we have
 \begin{align*}
@@
 & + \left((-x -x^2 + x^5)\chi_{[0,1]}(y_i) + (x^2 + x^3 + x^4 + x^5+ x^6) \chi_{[2,0]}(y_i) \right) \frac{1}{(1-x^2)(1-x^3)} q^2 \\
-& + 
+& + O(q^3) .
 \end{align*}
+Again, we find a discrepancy of our expansion compared to \cite{Imamura} at order~$q^3$.
+It would be interesting to explain the physical or representation theoretic sources of these discrepancies in each of these cases.

### 2022-10-13 fivebranes/twisted.tex
merge

@@
 
-In this section we review the descriptions of twists of the key players in $M$-theory including eleven-dimensional supergravity as well as the three and six-dimensional superconformal field theories associated to the abelian Lie algebra~$\lie{gl}(1)$.
+In this section we review the descriptions of twists of the key players in $M$-theory including eleven-dimensional supergravity as well as the six-dimensional superconformal field theory associated to the abelian Lie algebra~$\lie{gl}(1)$.
 
@@
 \subsection{A more general background}
-
+\label{s:thfmflds}
 The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.

### 2022-10-13 fivebranes/fact.tex
merge
remove CS

@@
 Here, $\cG$ is a sheaf of $L_\infty$ algebras on $Z$ which is presented as the $C^\infty$-sections of an $\infty$-dimensional pro vector bundle.
-To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.
+%To get a sense of the construction of this factorization algebra we take a brief excursion to a simpler situation related to branes in five-dimensional Chern--Simons theory.
 
-\parsec[]
-
-In~\S \ref{s:twistedsugra} we recalled some features of a five-dimensional Chern--Simons type theory that Costello has shown to be the result of applying the $\Omega$-background to $M$-theory on a Taub--NUT space \cite{CostelloM5}.
-In this setting fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
-In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
-Denote by $\Obs_{CS}$ the classical observables\footnote{We treat the theory classically as a perturbative theory on $\R \times {\rm Tot}(K_C)$.
-We note that the theory is defined in terms of two parameters $\ep, \delta$ where $\delta$ is the Chern--Simons coupling and $\ep$ is the non-commutative parameter controlling the deformation quantization of the holomorphic symplectic manifold ${\rm Tot}(K_C)$.
-For convenience we set both $\ep, \delta$ to be one.}
-of the non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
-Let 
-\beqn
-\pi \colon \R \times {\rm Tot}(K_C) \to C
-\eeqn
-be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$.
-
-Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
-Using this we can look at the subfactorization algebra 
-\beqn\label{eqn:taylor1a}
-\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
-\eeqn
-which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.
-
-For the rank one abelian gauge group, the space of fields of the five-dimensional theory on $\R \times {\rm Tot}(K_C)$ is
-\[
-\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
-\]
-The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
-%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
-For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
-\[
-(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
-\]
-where $p \colon K_C \to C$.
-The Chevalley--Eilenberg complex is taken with respect to the dg Lie algebra structure coming from the holomorphic Poisson structure on the total space of~$K_C$. 
-If $U$ is a trivializing cover then
-\[
-(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
-\]
-On the other hand, we have
-\[
-(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
-\]
-Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
-Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
-The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is given by the Moyal commutator. 
-This is similar to the non-formal case---it is the natural bracket if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in~$K_C$.
+%\parsec[]
+%
+%In~\S \ref{s:twistedsugra} we recalled some features of a five-dimensional Chern--Simons type theory that Costello has shown to be the result of applying the $\Omega$-background to $M$-theory on a Taub--NUT space \cite{CostelloM5}.
+%In this setting fivebranes which hit the tip of the Taub--NUT are deformed into chiral defects supported along a Riemann surface~$C$ in the five-manifold. 
+%In analogy with our eleven-dimensional setup, we take the five-manifold to be $\R \times {\rm Tot}(K_C)$ with the deformed fivebranes wrapping the zero section.
+%Denote by $\Obs_{CS}$ the classical observables\footnote{We treat the theory classically as a perturbative theory on $\R \times {\rm Tot}(K_C)$.
+%We note that the theory is defined in terms of two parameters $\ep, \delta$ where $\delta$ is the Chern--Simons coupling and $\ep$ is the non-commutative parameter controlling the deformation quantization of the holomorphic symplectic manifold ${\rm Tot}(K_C)$.
+%For convenience we set both $\ep, \delta$ to be one.}
+%of the non-commmutative five-dimensional Chern--Simons theory on $\R \times {\rm Tot}(K_C)$.
+%Let 
+%\beqn
+%\pi \colon \R \times {\rm Tot}(K_C) \to C
+%\eeqn
+%be the natural projection and consider the factorization algebra $\pi_* \Obs_{CS}$ on $C$. 
+%
+%Notice that there is a $U(1)$ action on the fields of the five-dimensional theory induced by the $U(1)$ action on the five-manifold which scales the fiber of~$K_C$.
+%Using this we can look at the subfactorization algebra 
+%\beqn\label{eqn:taylor1a}
+%\Bar{\pi}_* \Obs_{CS} \subset \pi_* \Obs_{CS}
+%\eeqn
+%which to an open set $U \subset C$ assigns the complex of observables in $\Obs_{CS} (\pi^{-1} U)$ which are finite sums of integral eigenvectors for this $U(1)$ action.
+%
+%For the rank one abelian gauge group, the space of fields of the five-dimensional theory on $\R \times {\rm Tot}(K_C)$ is
+%\[
+%\Omega^\bu(\R) \otimes \Omega^{0,\bu}({\rm Tot}(K_C)) [1] .
+%\]
+%The interaction is encoded by the symplectic structure on ${\rm Tot}(K_C)$.
+%%For simplicity, let us assume that the canonical bundle on $C$ is trivializable. 
+%For $U \subset C$, the complex of observables is given in terms of the Lie algebra cohomology
+%\[
+%(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(p^{-1}U)\right)
+%\]
+%where $p \colon K_C \to C$.
+%The Chevalley--Eilenberg complex is taken with respect to the dg Lie algebra structure coming from the holomorphic Poisson structure on the total space of~$K_C$. 
+%If $U$ is a trivializing cover then
+%\[
+%(\pi_* \Obs_{CS})(U) \simeq \clie^\bu \left(\Omega^{0,\bu}(C) \otimes \cO^{hol}(\C)\right) .
+%\]
+%On the other hand, we have
+%\[
+%(\Bar{\pi}_* \Obs_{CS})(U) \simeq \clie^\bu\left(\Omega^{0,\bu}(C) [[w]] \right) .
+%\]
+%Here, $w$ plays the role of a formal coordinate on the fiber of $K_C$ and $w^{k}$ as parametrizes the weight $k$ eigenspace---locally, $w$ is simply the one-form $\d z$.
+%Using this notation, the embedding \eqref{eqn:taylor1a} is induced by the Taylor series expansion map $\cO(\C) \to \C[[w]]$.
+%The dg Lie algebra structure on $\Omega^{0,\bu}(C) [[w]]$ is given by the Moyal commutator. 
+%This is similar to the non-formal case---it is the natural bracket if we understand $\cO(C)[[w]]$ as functions on the formal neighborhood of the zero section in~$K_C$.
 
@@
 
-Let us return to the situation of a complex three-fold $Z$ as submanifold the eleven-manifold~$\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
-The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory as we just discussed.
-
-This time we consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
+We are in the situation of a complex three-fold $Z$ embedded as a submanifold of the eleven-manifold~$\R \times \text{Tot}(K_{Z}^{1/2} \otimes \C^2)$. 
+%The construction of the restricted factorization algebra $\Bar{\pi}_* \Obs_{sugra}$ is completely similar to the simple case of five-dimensional Chern--Simons theory as we just discussed.
+Consider the group $U(1) \times U(1)$ rotating the fibers of the rank two bundle $K_Z^{1/2} \otimes \C^2$. 
 Using this we can define the subfactorization algebra 
@@
 \[
-\pi_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
+\Bar{\pi}_*\Obs_{sugra} = \clie^\bu(\cG_Z) 
 \]
 where $\cG_Z$ is an infinite-rank local $L_\infty$ algebra on $Z$. 
-Just as in the case of five-dimensional Chern--Simons theory, the embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
+The embedding of factorization algebras \eqref{eqn:taylor1b} is induced by a partial Taylor expansion map
 \[
@@
 
-\subsection{A finite $N$ conjecture}
+\subsection{Finite $N$ factorization algebras}
 \label{sec:factsummary}

### 2022-10-13 fivebranes/index.tex
section 3

@@
 \]
-We note that all vector bundles in the above diagram are complexified.
+We will assume that the top left corner $F_{M}\cap T_{M/Z}$ is again a vector bundle. Moreover, we adopt the convention that all vector bundles are complex unless otherwise mentioned.
 
@@
 
-\surya{conditions for top left to be a vector bundle}
-
-We claim that the splitting $\sigma$ induces a splitting $\mathring \sigma : h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}\to F_{\mathring M}$.
-\surya{is this obvious?} It is clear that $\mathring \sigma$ preserves lie brackets.
+It follows from the assumption that $F_{M}\cap T_{M/Z}$ is a vector bundle that the top left hand corner of the above diagram is as well.
+Moreover, the splitting $\sigma$ can be extended to a splitting $\mathring \sigma : h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}\to F_{\mathring M}$; the extension is an adapted connection in the language of \cite{KamberTondeur}.
 
@@
 \] 
-be the subbundle of the tangent bundle of the base locally spanned by $\del_{}t, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
-We will let $\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the elaves of this foliation on the base.
+be the subbundle of the tangent bundle of the base locally spanned by $\del_{r}, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
+We will let $\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the leaves of this foliation on the base.
 
@@
 
-We first note that the splitting gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
+We first note that the splitting $\mathring \sigma$ gives us an isomorphism of $C^{\infty}_{\mathring M}$-modules
 \begin{align*}
@@
 The BV pairing naturally descends to the above complex of sheaves.
-We can explicitly describe it as follows.
+It is induced from an explicit fiberwise pairing, which we may write as follows.
 First note that the fiber of $\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)$ at $(t,p)\in \R_{>0}\times Z$ can be computed as the cohomology of the complex
@@
 
-We denote the resulting infinite dimensional vector space.
-%Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
-%\[
-%\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
-%\]
+Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
+\[
+\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right )
+\]
+
+where the fibers $\R\times \C^{2}_{(t,p)}$ are equipped with the obvious transversely holomorphic foliation.
+
+The cohomology of the last complex can be readily computed.
+
+\begin{lem}
+  The cohomology of
+
+  \[\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right ) \]
+
+    is the complex given by
+     \beqn
+  %\begin{tikzcd}
+  %  + & - \\ \hline
+%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
+%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}
+
+ %\end{tikzcd}
+\eeqn
+\end{lem}
+
+Now the THF cohomology
+\[\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\]
+has a natural pairing, which combines with the natural pairing between vector fields and one-forms to give the desired pairing.
+
+\surya{brian can you add something here?}
+
 Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.

### 2022-10-13 fivebranes/index.tex
index

@@
 \[
-\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right )
+\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right )
 \]
@@
 The cohomology of
-
-  \[\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}) \right ); \thfd \right ) \]
-
+\[
+\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right ) 
+\]
 is the complex given by
 \beqn
-  %\begin{tikzcd}
-  %  + & - \\ \hline
-%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
-%H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}
-
- %\end{tikzcd}
+\begin{tikzcd}
+  + & - \\ \hline
+H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
+H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}
+\end{tikzcd}
 \eeqn
@@
 Now the THF cohomology
-\[\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\]
+\[
+\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )
+\]
 has a natural pairing, which combines with the natural pairing between vector fields and one-forms to give the desired pairing.

### 2022-10-13 fivebranes/index.tex
diagram
polarize

@@
 \]
-
 where the fibers $\R\times \C^{2}_{(t,p)}$ are equipped with the obvious transversely holomorphic foliation.
@@
 is the complex given by
-\beqn
+\beqn\label{eqn:bigcplx}
 \begin{tikzcd}
   + & - \\ \hline
-H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & %H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3] \\
-H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  [z_1,z_2,z_3]\{dw_a, dz_i\}
+H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \\
+H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right ) \{dw_a, dz_i\}
 \end{tikzcd}
@@
 
-Now the THF cohomology
-\[
-\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )
-\]
-has a natural pairing, which combines with the natural pairing between vector fields and one-forms to give the desired pairing.
-
-\surya{brian can you add something here?}
+Now, the THF complex
+\beqn\label{eqn:thfcohomology1}
+\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}) \, , \, \thfd \right )
+\eeqn
+has a natural even pairing given by the residue along the four-sphere~$S^4$.
+This combines with the natural odd pairing between vector fields and one-forms to give an odd pairing on the complex~\eqref{eqn:bigcplx}.
+At the level of cohomology, the pairing on \eqref{eqn:thfcohomology1} is even symplectic and it is equipped with a standard polarization. 
+In degree zero, the cohomology can be identified with holomorphic functions $\cO(\C^2)$, and the full cohomology is of the form $\T^*[-4] \cO(\C^2)$. 
+So, as a $\Z/2$ graded object the cohomology of~\eqref{eqn:thfcohomology1} can be identified with $\T^* \cO(\C^2)$. 
+This endows the cohomology of the complex \eqref{eqn:bigcplx}, which has an odd shifted symplectic structure, with a polarization.
+Explicitly, we can describe this polarization at the first page in a spectral sequence which simply takes the $\thfd$-cohomology of \eqref{eqn:bigcplx} as follows. 
+Let $V$ be the super vector space $\C\{\del_{w_a}, \del_{z_i}\} \oplus \Pi \C$. 
+Then, this page in the spectral sequence is isomorphic to
+\beqn
+\Pi \T^* \left(\cO(\C^2) \otimes V\right) ,
+\eeqn
+where $\Pi \T^*$ denotes the odd shifted cotangent bundle.
+The differential on this page of the spectral sequence, given by turning on $D, D_\Omega$ preserves this polarization.
 
 Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
-In particular, the result is local on $R_{>0}\times Z$.
+In particular, the result is local on $\R_{>0}\times Z$.
 

### 2022-10-13 fivebranes/index.tex
br

@@
 The relevant consequence for us is that it implies the degeneration of the spectral sequence \ref{thfss} at the $E_{2}$-page.
+From this point onwards, we assume that there exists a solution $\gamma_{BR}$ to the above equation.
+
+Accordingly, the dimensional reduction takes the form
+
+\[
+\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \Pi T^{*} (\cO (\C^{2}) \otimes V) \right)
+\]
+
+Deforming by the Maurer-Cartan element turns on a differential given by bracketing with $\thf D\gamma_{BR}$. Thus the theory in the backreacted geometry is given by
+
+\[
+\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \cO (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\cO (\C^{2})\otimes V)^{*} \right )
+\]
 
@@
 \beqn
-(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}=
+(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}= \cA^\bullet_Z \otimes
 \eeqn
 
-There is a symplectic pairing given by
-\beqn
-\eeqn
-
-\surya{...}
+The polarization identified in section
 

### 2022-10-13 fivebranes/index.tex
hilbert space
merge

@@
 \begin{tikzcd}
-  + & - \\ \hline
+  \ul{even} & \ul{odd} \\ \hline
 H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \\
@@
   \begin{tikzcd}[row sep = 1 ex]
-    + & - \\ \hline
+    \ul{even} & \ul{odd} \\ \hline
 w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
@@
 
-Deforming by the Maurer-Cartan element turns on a differential given by bracketing with $\thf D\gamma_{BR}$. Thus the theory in the backreacted geometry is given by
+Deforming by the Maurer-Cartan element turns on a differential given by bracketing with $\thfd D\gamma_{BR}$. Thus the theory in the backreacted geometry is given by
 

### 2022-10-13 fivebranes/main.tex
abstract

@@
 Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
-From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional theories of type $A_{N-1}$.
+Strikingly, we find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$.
+From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type $A_{N-1}$.
 \end{abstract}

### 2022-10-13 fivebranes/finite.tex
merge all

@@
 
-It follows from the limit description in \eqref{eqn:lim} that the large $N$ limit of $\til{\chi}_N$ is precisely the multiparticle supergravity index we computed in proposition~\ref{prop:sugraindex1}.
+It follows from the limit description in \eqref{eqn:lim} that the large $N$ limit of $\chi_N$ is precisely the multiparticle supergravity index we computed in proposition~\ref{prop:sugraindex1}. 
 Alternatively, we have the following direct proof of this fact.
@@
 \beqn
-f_{sugra}(y_i, y, q) = \lim_{N \to \infty} \til{f}_N(y_i,y,q) ,
+f_{sugra}(y_i, y, q) = \lim_{N \to \infty} f_N(y_i,y,q) ,
 \eeqn
-where $\til{f}_N = \sum_{k = -1}^{N-2} g_k$.
+where $f_N = \sum_{k = -1}^{N-2} g_k$.
 

### 2022-10-13 fivebranes/index.tex
merge all

@@
 \parsec[s:hilbertspace]
-The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construciton of the Hilbert space.
+The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construction of the twisted supergravity states. 
 The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$ in proposition \ref{p:dimred}.
-We will construct the Hilbert space by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.
+We will construct the twisted supergravity states by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.
 
@@
 \beqn
-(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}= \cA^\bullet_Z \otimes
+(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}= \Omega^{0,\bu}_Z \otimes \left ( \cO (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\cO (\C^{2})\otimes V)^{*} \right )
 \eeqn
 
-The polarization identified in section
+There is an obvious polarization whose base is given by
+\beqn
+\Omega^{0,\bullet}_Z \otimes \left (\cO (\C^{2})\otimes V \right )
+\eeqn
+
+\begin{dfn}
+\label{dfn:states}
+  The space of twisted supergravity states is
+  \[ \cH_{sugra} = \Sym \left(\overline \Omega^{0,\bullet}_{Z, c} \otimes (\cO (\C^{2}) \otimes V)^{*} \right)\]
+where the source denotes compactly supported distributional sections.
+\end{dfn}
 
@@
 
+The embedding of $E(3|6)$ into our twisted description of supergravity immediately yields the following.
 \begin{prop}
@@
 \end{prop}
-\begin{proof}
-\brian{Surya can you fill this in}
-\end{proof}
+%\begin{proof}
+
+%\end{proof}
 
@@
 The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
-That is, we compute the expression
+
+The space of supergravity states given in definition \ref{dfn:states} is given in terms of compactly supported Dolbeault forms on $\C^3$. 
+On $Z = \C^3$, the compactly supported distributions defined by 
+\beqn
+\alpha \mapsto \del_{z_1}^{n_1} \del_{z_2}^{n_2} \del_{z_3}^{n_3} \alpha |_{z=0}
+\eeqn
+combine to span a dense subspace of $\Bar{\Omega}^{0,\bu}_c(\C^3)$.
+Using this topological basis for distributions and the explicit description of $\cH_{sugra}$ in definition \ref{dfn:states} the following proposition is an immediate computation.
 

### 2022-10-13 fivebranes/main.tex
merge all

@@
 \begin{abstract}
-We present a conjectural description of the algebra of operators on a stack of finitely many fivebranes in $M$-theory at the level of the holomorphic twist.
+We present a conjectural description of the algebra of classical operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
 Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
 Strikingly, we find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$.
-From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type $A_{N-1}$.
+From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type~$A_{N-1}$.
 \end{abstract}

### 2022-10-14 fivebranes/intro.tex
merge

@@
 We next provide some comparitive evidence for our claim that $\chi_N({\bf x})$ really is the superconformal index associated to fivebranes.
-In ~\S\ref{s:finite} we will show that for small values of $N$ of our closed formulas, appropriate expansions agree with expressions which have been found in the literature.
+In ~\S\ref{s:finite} we will show that for small values of $N$, appropriate expansions of our closed formulas agree with expressions which have been found in the literature.
 We will also check that a number of specializations of the fugacities agree with certain unrefined indices which have been computed via other means.

### 2022-10-14 fivebranes/main.tex
merge

@@
 
+\usepackage{breakurl}
+
 \addbibresource{references.bib}
@@
 \title{A holographic approach to the six-dimensional superconformal index}
+\author{Surya Raghavendran and Brian R. Williams}
 \maketitle
@@
 \begin{abstract}
-We present a conjectural description of the algebra of classical operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
+We present a conjectural description of a semi-classical limit of the algebra of operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
 Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
-Strikingly, we find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$.
+We find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$. 
 From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type~$A_{N-1}$.
@@
 \subsection*{Acknowledgements}
-We thank K.~Costello, D.~Gaiotto, N.~Garner, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
+We thank K.~Costello, B.~Davison, D.~Gaiotto, N.~Garner, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
 Special thanks are due to Ingmar Saberi for his collaborations on past, current, and future related projects.

### 2022-10-14 fivebranes/main.tex
abstract

@@
 \begin{abstract}
-We present a conjectural description of a semi-classical limit of the algebra of operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
+We present a conjectural description of the space of local operators on a stack of finitely many fivebranes in $M$ theory at the level of the holomorphic twist.
 Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
-We find that local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$. 
+We find that the spaces of local operators are modules for the exceptional linearly compact super Lie algebra $E(3|6)$.
 From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional $\cN=(2,0)$ theories of type~$A_{N-1}$.

### 2022-10-14 fivebranes/intro.tex
algebras -> spaces

@@
 
-One of the insights of \cite{SWchar} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the algebra of local operators in the minimal twist as categorifying the index.
-Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. 
+One of the insights of \cite{SWchar} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the space of local operators in the minimal twist as categorifying the index.
+Moreover, the space of local operators, together with its algebra structure under operator product expansion, is part of the richer structure of a \textit{factorization algebra}.
 Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set including for example, non-local operators obtained from local ones via a descent procedure.
@@
 A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
-As a factorization algebra encodes, in particular, the local operators of a theory, we can extract from them familiar quantities like the superconformal index.
+The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space.
+However, this inforamtion is enough to extract familiar quantities like the superconformal index.
+
 Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction.

### 2022-10-14 fivebranes/fact.tex
merge all
merge

@@
 
-In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal fivebrane theory after performing the holomorphic twist.
+In this section we use the formalism of factorization algebras to give a conjectural description of the space of observables of the universal fivebrane theory after performing the holomorphic twist.
 For the case at hand, our expectation for the universal theory can be understood as the worldvolume theory on a large number of fivebranes. 
@@
 Even in perturbation theory, the full quantum behavior of our proposal for the minimal twist of eleven-dimensional theory is an open question. 
-We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.
+We leave the problem to characterize the quantum algebra structure to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.
 
@@
 In \cite{SWtensor}, Saberi and the second author have given an explicit description of the holomorphic twist of the worldvolume theory on a single fivebrane, that is, the six-dimensional superconformal theory associated to the abelian Lie algebra~$\lie{gl}(1)$.
-We denote the corresponding factorization algebra on the three-fold~$Z$ by~$\Obs_1$.
+We denote the corresponding factorization algebra of classical observables on the three-fold~$Z$ by~$\Obs^{cl}_1$.
 
 We recollected the description of the holomorphic twist of the theory on a single fivebrane in~\S\ref{s:single}. 
-This is a free theory and the underlying $\Z \times \Z/2$ graded cochain complex of fields $\cE_{1}$ with linear BRST differential is
+This is a free theory and the underlying $\Z \times \Z/2$ graded cochain complex of fields $\cE_{\lie{gl(1)}}$ with linear BRST differential is
 \beqn
@@
 \[
-\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs_{1} .
+\clie_\bu(\cG_{1,c}) \xto{\simeq} \Obs^{cl}_{1} .
 \]
@@
 However, when $\lie{g}$ is abelian (so, a cochain complex) we can identify this complex with the symmetric algebra on the cochain complex $\fg^*[-1]$.
+In order to see the quantum observables on a single fivebrane from our holographic analysis we must include effects from the backreaction, which we do not do here.
 
-We now formulate a conjecture about the worldvolume theory on a stack of holomorphically twisted fivebranes.
-Evidence for this conjecture will be given in the remaining parts of this paper.
-In this conjecrture, we recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
+We now formulate an expectation about the worldvolume theory on a stack of holomorphically twisted fivebranes.
+Evidence for this description be given in the remaining parts of this paper, and we will formulate a more refined conjecture in the next section at the level of local operators.
 
-\begin{conj}
-\label{conj:fact}
-For $N \geq 1$, let $\Obs_{N}$ be the factorization algebra of classical observables of the holomorphic twist of the worldvolume theory on a stack of $N$ fivebranes. 
-Then, there is an equivalence of factorization algebras
+Recall that the holomorphic, or minimal, twist of a theory with six-dimensional $\cN=(2,0)$ supersymmetry exists on any complex three-fold $Z$ equipped with $K_Z^{1/2}$.
+For $N \geq 1$, let $\Obs_{N}$ be the factorization algebra of observables of the holomorphic twist of the worldvolume theory on a stack of $N$ fivebranes wrapping a threefold~$Z$. 
+For each open set $U \subset Z$ our expectation is that there is an isomorphism of vector spaces
 \beqn
-\Obs_N \simeq \clie_\bu(\cG_{N,c}) .
+H^\bu \left(\Obs_N(U) \right) \simeq H_\bu (\cG_{N,c}(U)) ,
 \eeqn
+where $H_\bu$ is the Lie algebra homology.
 
 Similarly, for $N > 1$, let $\til \Obs_N$ be the factorization algebra of classical observables of the holomorphic twist of the worldvolume theory on a stack of $N$ fivebranes with the center of mass degrees of freedom removed.
-Then, there is an equivalence of factorization algebras
+Then, for each open set $U \subset Z$ we similarly expect
 \beqn
-\til\Obs_N \simeq \clie_\bu(\til \cG_{N,c}) .
+H^\bu \left(\til\Obs_N(U) \right) \simeq H_\bu (\til \cG_{N,c}(U)) .
 \eeqn
-In the language of superconformal $\cN=(2,0)$ theories our conjecture is that $\clie_\bu(\til \cG_{N,c})$ is the factorization algebra of classical observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$.
-\end{conj}
+In the language of superconformal $\cN=(2,0)$ theories our conjecture is that the value of the factorization algebra $\clie_\bu(\til \cG_{N,c})$ on an open set $U$ is equivalent to the space of observables of the holomorphic twist of the six-dimensional superconformal field theory associated to the Lie algebra $\lie{sl}(N)$ supported on $U$.
+
+We leave the study of the full factorization algebra structure present in $\Obs_N$ for future work, and emphasize here that we are only making expectations for the space of observables supported an open set.
+In the next section we consider local operators, and we will formulate a refined conjecture of the space of local operators as a module for the exceptional super Lie algebra $E(3|6)$.
 

### 2022-10-14 fivebranes/finite.tex
merge

@@
 
-In conjecture \ref{conj:fact} we have formulated a conjectural description of the factorization algebra of classical observables $\Obs_{N}$ associated to the worldvolume theory on a stack of $N$ fivebranes in the holomorphic twist.
-In this section we begin to provide some evidence for this description at the level of local operators, which is just a small piece of the factorization algebra.
-As we reviewed just in the previous section, the space of local operators is what categorifies the specific superconformal index that we study in this paper.
+In conjecture \ref{conj:ops} we have formulated a conjectural description of the space of local operators $\Obs_{N}(0)$ associated to the worldvolume theory on a stack of $N$ fivebranes in the holomorphic twist.
+As we reviewed just in the previous section, the space of local operators is what categorifies the superconformal index that we study in this paper.
+In this section we begin to provide some evidence for this description at the level of characters.
+%Of course, this is just a small piece of the full algebra structure present in the local operators.
 %The structure of a three-dimensional holomorphic factorization algebra induces algebraic operations on the algebra of local operators
@@
 For a stack of $N=1$ fivebranes, which corresponds to the abelian six-dimensional superconformal field theory, we find that our local character matches exactly with the expressions in the literature. 
-This is not a surprise as we have shown that even at the level of factorization algebras $\clie_\bu(\cG_{1,c})$ is quasi-isomorphic to~$\Obs_1$, see Proposition~\ref{prop:factabelian}.
+This is not a surprise as we have shown that even at the level of factorization algebras $\clie_\bu(\cG_{1,c})$ is quasi-isomorphic to the classical limit of~$\Obs_1$, see Proposition~\ref{prop:factabelian}.
 
 The main computation of this section is a closed formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
-Following conjecture \ref{conj:fact} and the general discussion of \S \ref{sec:sucaindex} we are led to hypothesize a closed formula for the superconformal index for the theory on a finite number of fivebranes (in flat space).
+Following conjecture \ref{conj:ops} and the general discussion of \S \ref{sec:sucaindex} we are led to hypothesize a closed formula for the superconformal index for the theory on a finite number of fivebranes (in flat space).
 As far as the authors are aware of there is no closed formula for the refined superconformal index (with four independent fugacities) for the theory on a stack of $N > 1$ fivebranes.
@@
 
-Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
-In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
-For the case of the single fivebrane theory, this implies that the local operators $\Obs_{1}(0)$ form a representation for $E(3|6)$.
-
-This fact also follows from our holographic analysis. 
-In \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$.
-Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
-In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs_{1}$.
+In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs^{cl}_{1}$ encoding the classical observables  of the holomorphic twist on a single fivebrane.
 On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
@@
 This module turns out to be a one-dimensional extension of an irreducible $E(3|6)$-module which was classified in~\cite{KR2}.
+
 %and compare our expression for the character to the character of a certain irreducible module for the exceptional super Lie algebra $E(3|6)$ considered in~\cite{KR2}.
@@
 
-We can now state a decategorified version of conjecture \ref{conj:fact} at the level of superconformal indices, or local characters.
+We can now state a decategorified version of conjecture \ref{conj:ops} at the level of superconformal indices, or local characters.
 

### 2022-10-14 fivebranes/ops.tex
merge all
merge

@@
 The notion of a factorization algebra captures both the local operators of a theory together with the non-local operators that on can define from the local ones via descent.
-From the data of a factorization algebra, one can recover local operators by the following formal construction. 
+From the data of a factorization algebra, one can recover the space of local operators by the following formal construction. 
 Let $\Obs$ be the factorization algebra of observables of some theory defined on a smooth manifold $M$.
@@
 
+\subsection{Exceptional symmetry and a finite $N$ conjecture}
+
+Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
+We expect that the same occurs for any six-dimensional superconformal theory. 
+In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\lie{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
+For the case of the theory on a stack of $N$ fivebranes, whose factorization algebra we denote by $\Obs_N$, this implies that the local operators $\Obs_{N}(0)$ form a representation for $E(3|6)$.
+
+Our goal is to gain knowledge of the structure of $\Obs_N(0)$ as an $E(3|6)$-representation from our holographic analysis of the previous section.
+Indeed, in \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\cG$.
+Recall that we have a decomposition of local Lie algebras $\cG = \oplus_{j \geq -1} \cG^{(j)}$ on the three-fold $Z$. 
+From this decomposition we have defined a family of local Lie algebras $\cG_{N}$ on $Z = \C^3$ for $N=1,2,\ldots$.
+
+In \S \ref{sec:factsummary} we explained the expectation that to an open set $U \subset \C^3$, the Lie algebra cohomology of $\cG_{N,c}(U)$ is equivalent to the observables $\Obs_N(U)$ of the six-dimensional theory supported on $U$.
+Each $\cG_N$ is acted on by the local Lie algebra $\cG^{(0)} = \cE(3|6)$.
+The $\infty$-jets of $\cE(3|6)$ at $0 \in \C^3$ is exactly the exceptional super Lie algebra $E(3|6)$.  
+Thus, for every $N$, the space of local operators of the factorization algebra $\clie_\bu(\cG_{N,c})$ is naturally and $E(3|6)$-representation. 
+At the level of local operators we can make the following conjecture, which we will further elucidate at the level of characters for $E(3|6)$ in the next section.
+
+\begin{conj}
+\label{conj:ops}
+Let $\Obs_N(0)$ be the local operators of the theory on a stack of $N$ fivebranes wrapping $\C^3$ in $\R \times \C^5$. 
+There is an equivalence of $E(3|6)$-representations
+\beqn
+\Obs_N(0) \simeq \clie_\bu (\cG_{N,c}) (0) .
+\eeqn
+Similarly, let $\til \Obs_{N}(0)$ be the local operators of the theory on a stack of $N \geq 2$ fivebranes with the center of mass degrees of freedom removed. 
+There is an equivalence of $E(3|6)$-representations
+\beqn
+\til \Obs_N(0) \simeq \clie_\bu (\til\cG_{N,c}) (0) .
+\eeqn
+\end{conj}
+
 %The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
@@
 
-\subsection{Comparison to `states'}
+%\subsection{Comparison to `states'}
 

### 2022-10-14 fivebranes/intro.tex
intro

@@
 A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
-The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space.
-However, this inforamtion is enough to extract familiar quantities like the superconformal index.
+The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space---otherwise known as the space of local operators at the point.
+However, this information is enough to extract familiar quantities like the superconformal index.
 
-Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction.
+%Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction.
 Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.
@@
 Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
-Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{brane}(N)$.
-In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebra $\Obs_{brane}(N)$.
+Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{N-branes}$.
+In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebras $\Obs_{N-branes}$.
 
-Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{brane}(N)$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
+Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{N-branes}$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
 We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}
@@
 \begin{expect}[Twisted holographic principle following \cite{CLsugra}]
-There is a map of factorization algebras
+After taking into account the backreaction, there is a map of factorization algebras
 \[
-  (\Obs_{grav}|_{Y})^{!}\to \Obs_{brane}(N)
+  (\Obs_{grav}|_{Y})^{!}\to \Obs_{N-branes}
 \]
@@
 
-In the main body of the paper, we show that this agrees with the factorization algebra we denoted $\Obs_{1-brane}$.
+In the main body of the paper, we show that this agrees, in the classical limit, with the factorization algebra we denoted $\cF_{-1}$ above. 
 We emphasize that we only consider the classical limit of this factorization algebra in this paper. 
-However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.\footnote{From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction.}
+However as this is a free theory, there is a simple description of its quantization as a twisted enveloping algebra.
+From the holographic point of view, this quantum parameter corresponds to including effects from the backreaction, which we plan to do in future work.
 
@@
 The next simplest application of our holographic approach is to describe the observables of the six-dimensional theory of type~$A_1$.
+Our expectation is that the factorization algebra $\Obs_{A_1}$ is related to the gravitational-side factorization algebra that we denoted by $\cF_0$ above.
+Precisely, on each individual open set of the threefold $U \subset Z$, our conjecture in this paper is that the cohomology of $\cF_0(U)$ and of $\Obs_{A_1}(U)$ are the same.
+To obtain the full factorization algebra structure from the gravitational side we should again include effects of the backreaction.
+
 Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $Z$ and pushforward along the norm map to obtain an associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$.
-We re-emphasize that in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory.
-At the quantum level, we expect that the algebra gets deformed twisted by a cocycle.
 
@@
 Let $\operatorname{Higgs}_{SL(2)} (S,W)$ denote the moduli space of $SL(2)$ Higgs bundles on the complex surface~$S$ where the Higgs fields has coefficients in the rank two bundle~$W$.
-The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ (after turning on the twisting cocycle) acts on
+The associative dg algebra $\pi_{*} \Obs_{A_1}|_{\R_{>0}}$ acts on
   \beqn
@@
 
-As in the abelian case, we may hilight some compatibilities with the usual AGT correspondence.
+As in the abelian case, we may highlight some compatibilities with the usual AGT correspondence. 
 For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ deforms the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$.

### 2022-10-14 fivebranes/intro.tex
intro

@@
 \subsection{The fivebrane decomposition}
-Rather surprisingly, we will argue that in the classical limit the factorization algebra associated to the worldvolume theory on a finite number of minimally twisted fivebranes is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
+We will argue that the value of the factorization algebra associated to the worldvolume theory on a finite number of minimally twisted fivebranes on an arbitrary open set is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
 After taking a certain classical limit, this argument relies on a presentation of the $!$-dual as
@@
 
-Using this presentation, our conjecture for the factorization algebra associated to the worldvolume theory on a stack of $N$ twisted fivebranes, after taking the same classical limit, has the form
+Using this presentation, our conjecture for the value of the factorization algebra associated to the worldvolume theory on a stack of $N$ twisted fivebranes on an open set $U$ satisfies
 \beqn\label{eqn:finiteTensor}
-\Obs_{N-branes} = \cF_{-1} \otimes \cF_2 \otimes \cdots \otimes \cF_{N-2} .
+\Obs_{N-branes} (U) \simeq \cF_{-1}(U) \otimes \cF_2 (U) \otimes \cdots \otimes \cF_{N-2} (U) .
 \eeqn
-In other words, we simply truncate the tensor decomposition at order $N$.
-The surprising part is that the factorization algebras $\cF_k$ are directly identifiable from the point of view of the gravitational theory!
+In other words, to obtain the space of observables supported on an open set $U$ we simply truncate the tensor decomposition at order $N$.
+The surprising part is that the values of the factorization algebras $\cF_k$ are directly identifiable from the point of view of the gravitational theory!
 

### 2022-10-14 fivebranes/fact.tex
edits

@@
 We now formulate an expectation about the worldvolume theory on a stack of holomorphically twisted fivebranes.
-Evidence for this description be given in the remaining parts of this paper, and we will formulate a more refined conjecture in the next section at the level of local operators.
+Evidence for this description will be given in the remaining parts of this paper, and we will formulate a more refined conjecture in the next section at the level of local operators.
 

### 2022-10-14 fivebranes/finite.tex

@@
 %The structure of a three-dimensional holomorphic factorization algebra induces algebraic operations on the algebra of local operators
-
-For each $N$ we have constructed a local Lie algebra $\cG_N$ on the worldvolume three-fold $Z$. 
-Our conjecture is that the factorization algebra associated to a stack of $N$ holomorphically twisted fivebranes is $\Obs_N \simeq \clie_\bu(\cG_{N,c})$, where $\cG_{N,c}$ denotes the cosheaf of compactly supported sections.
-The main goal of this section is to extract the algebra of local operators from this factorization algebra and to then deduce explicit formulas for the local character, and hence the superconformal index.
 

### 2022-10-14 fivebranes/intro.tex
merge

@@
 A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
-The full factorization structure is extremely rich, and in this paper, we only discuss a small part of it: the costalk at a point as a vector space---otherwise known as the space of local operators at the point.
+The full factorization structure is extremely rich, and in this paper we only discuss a small part of it, namely the costalk at a point as a vector space.
+This is otherwise known as the space of local operators at the point. 
 However, this information is enough to extract familiar quantities like the superconformal index.
@@
 Since the action of supersymmetry is gagued in theories of supergavity, the aforementioned twisting procedure does not quite make sense.
-Instead, Costello and Li define twisted supergravity to be the theory in perturbation theory around a background where the bosonic ghost for local supertranslations takes a nonzero nilpotent VEV.
+Instead, Costello and Li define twisted supergravity to be the theory in perturbation theory around a background where the bosonic ghost for local supertranslations takes a nonzero nilpotent vacuum expectation value.
 Coupling the worldvolume theory of a brane to such a background has the effect of twisting the worldvolume theory in the usual sense.
@@
 We will argue that the value of the factorization algebra associated to the worldvolume theory on a finite number of minimally twisted fivebranes on an arbitrary open set is a particular piece of the $!$-dual of the factorization algebra associated to the bulk gravitational theory.
-After taking a certain classical limit, this argument relies on a presentation of the $!$-dual as
+After taking a certain limit, this argument relies on a presentation of the $!$-dual as
 \beqn
@@
 \label{eqn:AN-1}
-\Obs_{A_{N-1}} = \cF_0 \otimes \cF_1 \otimes \cdots \otimes \cF_{N-2} .
+\Obs_{A_{N-1}} (U) \simeq \cF_0 (U) \otimes \cF_1 (U) \otimes \cdots \otimes \cF_{N-2} (U).
 \eeqn
@@
 Only in the classical limit does the $W_N$ vertex algebra decompose as a pure tensor product.}
-This decomposition as a tensor product of factorization algebras will break down at the quantum level.
+This decomposition as a tensor product of graded vector spaces will break down at the quantum level and when we take into account the factorization algebra structure.
 Nevertheless, the description provides a very effective way to compute certain protected quantities like the superconformal index.
@@
 \eeqn
-where $\cF_k(0)$ stands for the algebra of local operators associated to the factorization algebra $\cF_k$.
-Forgetting about the differentials for the time being, the local operators $\cF_k(0)$ are given as the free algebra on some vector space $V_k$ of linear local opeartors.
-Thus, to compute the index of local operators of $\Obs_{brane}(N)$ it suffices to compute the index of each of the $V_k$---this is the single particle index---and then apply the plethystic exponential.
+where $\cF_k(0)$ stands for the space of local operators associated to the factorization algebra $\cF_k$.
+Forgetting about the differentials for the time being, the local operators $\cF_k(0)$ are given as the free symmetric algebra on some vector space $V_k$ of linear local opeartors.
+Thus, to compute the supersymmetric index of the space of local operators of $\Obs_{N-branes}$ it suffices to compute the index of each of the $V_k$---this is the single particle index---and then apply the plethystic exponential.
 For now, denote by $g_k({\bf x})$ the index of the vector space $V_k$.
@@
 
-Even stronger evidence would involve the factorization algebras $\Obs_{N-branes}$. We will outline some expectations in later sections but leave a full treatment to future work.
+Even stronger evidence would involve understanding what the gravitational side can say about the factorization algebras $\Obs_{N-branes}$. 
+We will return to a treatment of this in future work.
 
@@
 We propose similar statements at the level of the minimal twist. 
-We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks $1$ and $2$ respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau 5-fold.
+We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks one and two respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau fivefold.
 The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.
@@
 As in the abelian case, we may highlight some compatibilities with the usual AGT correspondence. 
-For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ deforms the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$.
+For a particular choice of the input geometric data, the same Maurer-Cartan element in $\lie{osp}(6|2)$ will deform the associative algebra $\pi_{*}\Obs_{A_{1}}|_{\R_{>0}}$ to the Virasoro algebra $U(\operatorname{Vir})$.
 We again expect that for a judicious choice of $X$, the Hilbert space deforms to the equivariant cohomology of the moduli of rank 2 instantons on $\C^{2}$, and the action compatibly deforms to the action in the rank 2 case of the AGT correspondence.
@@
 In this case, the unit circle bundle in $L$ may be identified with the Hopf fibration $S^{5}\to \C\PP^{2}$.
-In \cite{Kim:2013nva}, the superconformal index of the 6d $\cN=(2,0)$ theory is computed by identifying it with the $S^{1}\times S^{5}$ partition function, and reducing along the Hopf fiber of $S^{5}$ to further identify it with the superconformal index of 5d $\cN=2$ gauge theory on $\C\PP^{2}$.
+In \cite{Kim:2013nva}, the superconformal index of the six-dimensional $\cN=(2,0)$ theory is computed by identifying it with the $S^{1}\times S^{5}$ partition function, and reducing along the Hopf fiber of $S^{5}$ to further identify it with the superconformal index of five-dimensional $\cN=2$ gauge theory on $\C\PP^{2}$.
 The latter quantity is computed in terms of the Nekrasov instanton partition function, and is almost manifestly the character of $\cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$.
-The fact that we recover the same expressions as characters of the algebras of local operators $\Obs_{SL(2)}(0)$ corroborates the claim that $ \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$ is the vacuum module of $\pi_{*}\Obs_{SL(2)}|_{\R_{>0}}$.
+The fact that we recover the same expression as the character of the space of local operators $\Obs_{A_1}(0)$ corroborates the claim that $ \cO \left ( \operatorname{Higgs} _{SL(2)}(S, W)\right)$ is the vacuum module of $\pi_{*}\Obs_{A_1}|_{\R_{>0}}$.
 

### 2022-10-14 fivebranes/finite.tex
merge

@@
-\section{Conjectures for operators on fivebranes}
+\section{Conjectures for indices of operators on fivebranes}
 \label{s:finite}
@@
 
-Recall that our conjecture for the factorization algebra associated to the holomorphic twist of the six-dimensional worldvolume theory associated to a stack of two fivebranes is $\Obs_2 \simeq \clie_\bu(\cG_{2,c}) \cong \clie_\bu(\cG_{1,c}) \otimes \clie_\bu(\til \cG_{2,c})$.
+Recall that our conjecture for the space of local operators associated to the holomorphic twist of the six-dimensional worldvolume theory on a stack of two fivebranes is $\Obs_2 (0) \simeq \clie_\bu(\cG_{2,c})(0) \cong \clie_\bu(\cG_{1,c})(0) \otimes \clie_\bu(\til \cG_{2,c})(0)$.
 And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.

### 2022-10-14 fivebranes/index.tex
merge

@@
 In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$.
-This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
+This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{dfn:states} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
 

### 2022-12-27 aone/main.tex
elliptic

\documentclass{amsart}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[titletoc]{appendix}
\usepackage{hyperref}

%\usepackage{tikz} 	  % Replaced with tikz-cd, but am
\usepackage{tikz-cd}  % willing to learn tikz if necessary
	\usetikzlibrary{decorations.pathmorphing}

\usepackage[all]{xy}
\usepackage{stmaryrd}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{tabularx}

\usepackage{macros}

\renewcommand\tabularxcolumn[1]{m{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

\begin{document}

\title{A Pair of Holomorphic Fivebranes}

\date{\today}
\maketitle

%background

\section{A Single Fivebrane}

% descent of brane scan cocycle on \widehat{E(5|10)} = local anomaly polynomial from backreaction

% generators and relations for mode algebras on different 5-manifolds

% central charge matching

\section{Two Fivebranes}
% central extension of E(3|6)

% codimension 2 defects and the two different localizaitons

% dim red and comparison with 5d N=2 + oper type boundary condition

\section{Coproducts}

\end{document}

### 2022-12-27 fivebranes/elliptic.tex
elliptic

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

\section{The two-dimensional ``free boson''}

\subsection{A model for punctured affine space}

Let $\sfA$ be the graded algebra generated by the degree zero variables $z_1,z_2,\lambda_1,\lambda_2$ and the degree one variable $\omega$ subject to the relation
\beqn
z_1 \lambda_1 + z_2 \lambda_2 = 1 .
\eeqn

Define the linear map 
\beqn
\dbar \colon \sfA \to \sfA[1] 
\eeqn
by the rules
\begin{itemize}
	\item $\dbar(z_i) = 0$.
	\item $\dbar(\lambda_i) = \ep_{ij} z_j \omega$ ,
\end{itemize}
and extend its action to the entire graded algbra $\sfA$ by the rule that it is a graded derivation.
Notice that this differential is well-defined since
\beqn
\dbar(z_1 \lambda_1 + z_2 \lambda_2) = z_1 z_2 \omega + z_2 (-z_1 \omega) = 0 .
\eeqn

The cohomology $H^\bu(\sfA, \dbar)$ is concentrated in degrees zero and one. 
In degree zero, the cohomology is simply polynomials in the variables $z_1,z_2$
\beqn
H^0(\sfA) \cong \C[z_1,z_2].
\eeqn
And in degree one, the cohomology can be identified with
\beqn
H^1(\sfA) \cong \C[\lambda_1,\lambda_2] \omega .
\eeqn

\subsection{The higher residue}

Consider the subalgebra $R$ generated by $z_i, \lambda_i$. 
Define the linear map
\beqn
\Res \colon \sfA \to \sfA/R \cong \C[-1]
\eeqn
which simply projects onto the line spanned by the element $\omega$.
Notice that this linear map is of cohomological degree~$-1$, consistent with the fact that $\omega$ carries degree~$+1$.
An immediate consequence of the cohomology computation above is the following.
\begin{lem}\label{lem:res}
For any $f \in \sfA$ one has $\Res(\dbar f) = 0$.
\end{lem}

\subsection{The two-cocycle}
Consider the following three-linear map 
\beqn
\phi_3 \colon \sfA \times \sfA \times \sfA \to \C
\eeqn
defined by
\beqn
\phi_3 (f,g,h) = \ep_{ij} \Res(f \del_{z_i} g \del_{z_j} h) .
\eeqn

\begin{lem}
The map $\phi_3$ is totally graded skew symmetric and determines a total degree two cocycle on the abelian dg Lie algebra $\sfA$. 
\end{lem}

As a consequence of this lemma, we see that $\phi_3$ defines a central extension of the abelian dg Lie algebra $\sfA$ 
\beqn
\C \to \sfH \to \sfA .
\eeqn

A particular model for this dg Lie algebra as an $L_\infty$ algebra is the following. 
As a graded vector space $\sfA = \sfH \oplus \C$.
\begin{itemize} 
	\item The one-ary bracket $[-]_1$ is simlpy the differential $\dbar$ which we extend to $\sfH$ by declaring that it annihilate the central element. 
\item There are no two-ary brackets $[-,-]_2 = 0$. 
\item The three-ary bracket is given by 
\beqn
[f,g,h]_3 = \phi_3(f,g,h) = \ep_{ij} \Res(f \del_{z_i} g \del_{z_j} h) .
\eeqn
\end{itemize}

\subsection{Homotopy transfer}

Given any dg Lie algebra $(\lie{g}, \d, [-,-])$ its cohomology $H^\bu(\lie{g},\d)$ has the induced structure of a graded Lie algebra. 
Moreover, via homotopy transer, its cohomology can be given (a possibly inequivalent) structure of an $L_\infty$ algebra with the property that it is equivalent to the original dg Lie algebra.

The cohomology dg Lie algebra $\sfH$ thus has a canonical $L_\infty$ structure.

\begin{prop} 
The $L_\infty$ structure on 
\beqn
H^\bu(\sfH) \cong \C[z_i] \oplus \C[\lambda_i]\omega \oplus \C 
\eeqn
obtained by homotopy transfer has trivial $k$-ary operations for all $k \ne 3$.
When $k=3$ the operation is simply $[f,g,h]_3 = \phi_3(f,g,h)$.
\end{prop}

In this proposition, we recall that by Lemma \ref{lem:res} that the residue map descends to a map in $\dbar$-cohomology.

\subsection{Fock module}

Let $\sfA_- = H^1(\sfA)$ and let $\sfA_+ \subset \sfA$ be commutative dg algebra given by the kernel of the projection 
\beqn
\sfA \to \sfA_- . 
\eeqn
Notice that the cohomology of $\sfA_+$ is simply $H^0(\sfA) = \C[z_1,z_2]$.

\begin{dfn} 
For $\mu,k \in \C$ define the derived Fock module to be 
\beqn
U(\sfH) \otimes_{U(\sfA_+ \oplus \C\cdot K)} \C(\mu,k) .
\eeqn
Here $\C(\mu,k)$ is the $\sfA_+ \oplus \C \cdot K$-module where $1\in \sfA_+$ acts by $\mu$ and $K$ acts by $k$. 
\end{dfn}

\section{The higher `free fermion'}

\subsection{The underlying dg Lie algebra}

Let $\sfA$ be the commutative dg algebra as defined in the previous section. 
Consider the commutative dg algebra $\sfA \oplus \sfA[1]$ which is a square-zero extension of the commutative dg algebra $\sfA$. As a graded vector space it is concentrated in degrees $-1,0,1$. 
We will denote elements of this dg Lie algebra as $(\gamma,\beta)$ according to the direct sum decomposition.

Define the following bilinear functional $\phi_2$ on $\sfA \oplus \sfA[1]$ by the formula
\beqn
\phi_2(\gamma,\beta) = \phi_2(\beta,\gamma) = \Res(\gamma \beta) .
\eeqn

\begin{lem}
The bilinear functional $\phi_2$ is graded skew symmetric and hence determines a two-cocycle on the abelian dg Lie algebra $\sfA \oplus \sfA[1]$ .
\end{lem}

From the lemma, we see that $\phi_2$ determines a central extension of dg Lie algebras which we denote by
\beqn
\C \to \oint \sfF \to \sfA \oplus \sfA[1] .
\eeqn

\subsection{Vacuum module}

Consider the subalgebra
\beqn
\sfA_+ \oplus \sfA_+[1] \oplus \C \cdot K \subset \oint \sfF .
\eeqn
Let $\C_1$ be the module for this subalgebra where $\sfA_+,\sfA_+[1]$ act trivially and the central element $K$ acts by the unit.

\begin{dfn}
Let $\sfF$ be the induced dg module 
\beqn
U(\oint \sfF) \otimes_{U(\sfA_+ \oplus \sfA_+[1] \oplus \C \cdot K)} \C_1 .
\eeqn
\end{dfn}

Let $L_{0,j}$ be the generator for the action by the holomorphic vector fields $z_j\del_{z_j}$. 
Notice that the original dg Lie algebra $\oint \sfF$ has a symmetry by the group $U(1)$ which acts on $\gamma$ with weight $+1$ and $\beta$ with weight $-1$. 
Let $J_0$ be the infinitesimal generator for this action. 
We can then consider the character 
\beqn
\Tr_{\sfF} \left(p^{L_{0,1}} q^{L_{0,2}} u^{J_0}\right) 
\eeqn
where the trace denotes super trace.

\begin{prop}
As a series in $p,q,u$ one has
\beqn
\Tr_{\sfF} \left(p^{L_{0,1}} q^{L_{0,2}} u^{J_0}\right) = \Gamma_{ell}(p,q;u)
\eeqn
where $\Gamma_{ell}(p,q;u)$ is the elliptic Gamma function.
\end{prop}

\subsection{'Boson-fermion' correspondence}

Define an element $J \in \oint \sfF$ by the formula
\beqn
J = \sum_{n,m} \beta[n,m] \gamma[-n-1,-m-1] 
\eeqn

\brian{Some problems with this. First, these elements are in the cohomology of $\oint \sfF$.
Next, I think we need to do some normal ordering.}
\end{document}

### 2023-02-07 revisions/response/response.tex

\documentclass{amsart}

\usepackage{macros-mtheory}

\begin{document}

\title{Response to referee report \\ ``Twisted eleven-dimensional supergravity''}

\maketitle

We want to express our deep gratitude to the referee for the report on our manuscript. We believe that the referee's suggestions greatly improved the readability and clarity of our results and we hope that shows in the revised work.

Below, we summarize the edits that have been made to address the referee's suggestions.

\subsection*{Edits}
\begin{enumerate}
\item The referee asked why only the extension corresponding to the M2 brane is discussed in section 3.2. We have added a remark to address this at the end of section 3. \\

\item The referee requested elaboration on page 24, in the proof of proposition 3.6, in showing that the bracket between odd elements in the $Q$-twisted M2 brane algebra is compatible with the bracket induced by the cubic term in the action. We have added a paragraph in the proof of proposition 3.6 to address this.
\end{enumerate}

\subsection*{Clarifications}
\begin{enumerate}
\item The referee requested clarifications about the intuition and motivation which led us to study the model in the manuscript. This is stated both in the abstract and in the paragraph preceding Conjecture 0.1 on page 3. \\

\item The referee suggested that we formulate a conjecture relating $E(5|10)$ to shifted truncated Yangians. Though a detailed conjecture in this direction is outside of the scope of the submitted manuscript, we wish to point out that steps in this direction appear in follow-up work by the first and last author (see the introduction of \cite{RW22}). There, the authors amass character-level evidence for the claim that the M5 brane algebra in the minimal twist admits a deformation to the $\mathcal{W}_{1+\infty}$ algebra.

\end{enumerate}

\begin{thebibliography}{9}
\bibitem{RW22}
	S. Raghavendran and B. Williams,
	\textit{A holographic approach to the six-dimensional superconformal index},
	\url{arXiv:2210.07910},
	2022.

\end{thebibliography}

\end{document}

### 2023-02-07 fivebranes/membrane.tex

@@
 
+\subsection{Operators on a single membrane}
+
+\begin{prop}
+\label{prop:3done}
+The local character $\chi_{\lie{u}(1)}(q,t_1,t_2,r)$ of the holomorphic twist of the theory on a single membrane is given by the plethystic exponential of the single particle index
+\beqn\label{eqn:3done}
+f^{3d}_{\lie{u}(1)} (t_1,t_2,t_3,q) = \frac{q^{1/4} (t_1+t_2+t_3+ (t_1 t_2 t_3)^{-1}) - q^{3/4} (t_1^{-1} + t_2^{-1} + t_3^{-1} + t_1 t_2 t_3)}{1-q} .
+\eeqn
+\end{prop}
+
+This agrees with the membrane index computed in \cite[Equation (2.31)]{Bhattacharya:2008zy}.
+
+\subsection{A conjectural description for the theory two membranes}
+
+\begin{prop} \label{prop:3dtwo}
+The character of local operators of the factorization algebra $\clie_\bu(\cG_{2,c})$ on $\C^3$ is given by the following expression
+\begin{multline}\label{eqn:3dtwo1}
+(1-q) f^{3d}_{\lie{sl}(2)}(t_1,t_2,t_3,q) = q^2 + q (\chi_{\C^4}(t) \chi_{\C^4}(t^{-1}) - 1) \\ - q^{3/2} \frac12 (\chi_{\C^4}(t)^2 - \chi_{\C^4}(t^2)) - q^{1/2} \frac12 (\chi_{\C^4}(t)^2 + \chi_{\C^4}(t^2))
+\end{multline}
+\end{prop}
+
+The Higgs and Coloumb branch specializations are given by 
+\beqn
+t_1 t_2 = q^{\pm 1/2} .
+\eeqn
+This results in the following expression
+\beqn
+f^{3d}_{\lie{sl}(2)}|_{t_1 t_2 = q^{\pm 1/2}} = q^{-1/2} t_1^{-2} + 1 + q^{1/2} t_1^2 .
+\eeqn
+
+\subsection{The membrane decomposition}
+
+We briefly highlight an analogous construction of the restricted factorization algebra describing membranes.
+Recall that in the twist we are considering the worldvolume theory of membranes is a three-dimensional partially topological-holomorphic field theory which exist on a product $\R \times C$ where $C$ is a Riemann surface.
+
+We consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
+\[
+X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
+\]
+the total space of the rank four bundle $K_C^{1/4} \otimes \C^4$ over $C$.
+Denote by 
+\[
+\pi \colon V \to \R \times C
+\] 
+the pullback of this vector bundle along the projection $\R \times C \to C$.
+We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
+In this description, the twisted membranes will be supported along the zero section of $V$. 
+The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.
+
+As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
+Nevertheless there is a subfactorization algebra $\Bar{\pi}_* \Obs_{sugra}$ which admits a natural grading so that each filtered component can be understood as such.
+
+To construct this factorization algebra we consider the action of the compact torus $U(1)^{\times 4}$ which rotates the fibers of the bundle $K_C^{1/4} \otimes \C^4$.
+We let $\Bar{\pi}_* \Obs_{sugra}$ be the factorization algebra on $\R \times C$ consisting of observables which are finite sums of integral eigenvectors for this group action.
+Again, we find that $\Bar{\pi}_* \Obs_{sugra}$ is of the form $\clie^\bu(\cG_{\R \times C})$ for some $\infty$ sheaf of $L_\infty$ algebras $\cG_{\R \times C}$ on $\R \times C$ which is the sections of a pro vector bundle.
+
+Analogous to the decomposition determined by the $\C^\times$ action considered in \ref{s:cstarfive}, there is a decomposition of $\cG_{\R \times C}$ determined by a (different) $\C^\times$ acting on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$.
+
+In a local THF chart $U \subset \R \times C$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;z,w)$ where $(t;z) \in U \subset\R \times C$ is THF coordinate and $w=(w_1,w_2,w_3,w_4)$ is the holomorphic fiber coordinate of the rank four bundle $V$.
+
+%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
+%\[
+%0 \times 0 \times \C^3 \subset \C^5 .
+%\]
+%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
+%
+%\parsec[s:flatdecomp]
+%
+%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
+%%\[
+%%\C^3 \times (\R \times \C^2 - 0) .
+%%\]
+%%
+%%Let $\pi \colon \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
+%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
+%
+%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
+%
+%Let $\pi \colon \R \times \C^5 \to \C^3$ be the projection map.
+%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
+%\[
+%\pi_* \Obs_{sugra} 
+%\]
+%on $\C^3$.
+%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
+%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
+
+With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
+\begin{itemize}
+\item On the fields $\mu(t;w,z)$ the action is
+\[
+\lambda \cdot \mu(t;z,w) = \mu(t; z , \lambda w).
+\]
+\item On the fields $\nu(t;w,z)$ the action is
+\[
+\lambda \cdot \nu(t;z,w) = \nu(t;z ,\lambda w).
+\]
+\item On the fields $\beta(t;w,z)$ the action is
+\[
+\lambda \cdot \beta(t;z,w) = \lambda^{-2} \beta(t; z, \lambda w).
+\]
+\item On the fields $\gamma(t;w,z)$ the action is
+\[
+\lambda \cdot \gamma(t;z,w) = \lambda^{-2} \gamma(t; z ,\lambda w).
+\]
+\end{itemize}
+
+\begin{prop}
+The $L_\infty$ structure on $\cL_{sugra}$ is equivariant for this $\C^\times$ action. 
+%The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
+\end{prop}
+
+As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\cG_{\R \times C}$ into weights. 
+Similarly as above one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
+\[
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV^{(n)}\right)
+\]
+where $\cV^{(n)}$ is a holomorphic super vector bundle on $C$.
+
+We will state explicit descriptions of the first few eigenspaces without details of the proof. 
+The weight decomposition is concentrated in degrees $\geq -2$. 
+The lowest weight $n=-2$ is not very interesting, it is quasi-isomorphic just to the de Rham complex 
+\beqn
+\Omega^\bu (\R) \otimes \Omega^{\bu, \bu}(\C) \simeq \Omega^\bu (\R^3) .
+\eeqn
+
+The next nontrivial eigenspace is $n=-1$. 
+Here, one can see that 
+\[
+\cV^{(-1)} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
+\]
+For $n=0$ one has 
+\[
+\cV^{(0)} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
+\]
+As in the case of fivebranes, the $n=0$ eigenspace is equipped with the structure of a super Lie algebra whose exact form we do not state now.
+
 \end{document}

### 2023-02-07 g2twist.tex

@@
 
-There are two types of interactions in the original theory.
+In addition to the kinetic terms, there are two types of interactions in the original theory.
 The first is
@@
 \begin{equation} \label{eqn:int2}
-  \frac16\int_{X \times Z \times L} \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma .
+  \frac16\int_{X \times Z \times L} \gamma \partial \gamma \partial \gamma .
 \end{equation}
@@
 \[
-  \frac16 \int \frac{1}{1-\nu} \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma \partial \gamma\right) \wedge \omega_Z .
+  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \omega_Z .
 \]
@@
 \begin{multline}
-\frac16 \int \frac{1}{1-\nu} \left(\gamma_X \partial^Z \gamma_X \partial^Z \gamma_X +\gamma_X \partial^X \gamma_X \partial^Z \gamma_Z +  \gamma_X \partial^X \gamma_Z \partial^X \gamma_Z \right)
+\frac16 \int \left(\gamma_X \partial^Z \gamma_X \partial^Z \gamma_X +\gamma_X \partial^X \gamma_X \partial^Z \gamma_Z +  \gamma_X \partial^X \gamma_Z \partial^X \gamma_Z \right)
 \\
-\frac{\delta}{2} \int \frac{1}{1-\nu} \left(\gamma_X \partial^X \gamma_X \right) \wedge \omega_Z 
++ \frac{\delta}{2} \int \left(\gamma_X \partial^X \gamma_X \right) \wedge \omega_Z 
 \label{eqn:delta2}
@@
 
-We identify this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
+We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
 Consider the complex
@@
 
-There is a map from this smaller BRST complex to the original defined by the following equations 
+There is a non-linear map of BRST complexes from this one to the original one defined by the following equations 
 \begin{multline}
-\mu_Z = \omega_Z^{-1} \del^Z \alpha^0, \quad \mu_X = \Omega_X^{-1} \alpha^2, \quad \nu = \Omega_X^{-1} \alpha^3 \\
-\beta = \alpha^0, \quad \gamma_X = \alpha^1 , \quad \gamma_Z = 0 .
+\mu_Z = e^{-\til{\alpha}^3} \omega_Z^{-1} \del^Z \alpha^0, \quad \mu_X = e^{-\til{\alpha}^3} \Omega_X^{-1} \alpha^2, \quad \nu = e^{-\til{\alpha}^3} \til{\alpha}^3 \\
+\beta = e^{\til{\alpha}^3} (\alpha^0 + \Omega_X^{-1} \alpha^1 \alpha^2), \quad \gamma_X = e^{\til{\alpha}^3} \alpha^1 , \quad \gamma_Z = 0 .
+\label{eqn:g2map}
 \end{multline}
-This map is a quasi-isomorphism of linear BRST complexes.
+In the above equation we have introduced the notation $\til{\alpha}^3 = \Omega_X^{-1} \vee \alpha^3$. 
+The induced map of linear BRST complexes is a quasi-isomorphism. 
+We show that the full non-linear map intertwines the action functionals and hence defines an equivalence of BV theories.
 
-Restricting the deformed BV action $I(\gamma+\gamma^{1,0})$ along this map we obtain a new interaction $\Tilde{I}(\alpha)$. 
-It has the following form
+The restriction of the kinetic term $\beta \div \mu$ along \eqref{eqn:g2map} is
+\beqn
+\alpha^0 \alpha^2 \del^X \til{\alpha}^3 + \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \alpha^0 \del^X \alpha^2 + \alpha^1 \alpha^2 \del^X \alpha^2 .
+\eeqn
+
+Restricting the action \eqref{eqn:delta1} along the map \eqref{eqn:g2map} we obtain
+\begin{multline}
+\frac12 \alpha^1 (\alpha^2)^2 \del^X \til{\alpha}^3 + \frac12 \del^X \alpha^1 (\alpha^2)^2 
+\end{multline}
+
 \begin{multline}
@@
 \[
-\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_Z)] \{\alpha,\alpha\} 
+\{I_{CS}, K\} = \frac16 \int \frac{\omega_Z}{1-\Omega^{-1}_X \alpha} [\alpha \vee (\alpha \vee \Omega^{-1}_X)] \{\alpha,\alpha\} 
 \]

### 2023-03-22 fivebranes/fact.tex
merge

@@
 
+      v n                  
 At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.

### 2023-04-17 draft.tex
macros
bib; format; minor fixes; merge error

@@
-\documentclass[11pt]{amsart}
+\documentclass[11pt,a4paper]{amsart}
 
-\usepackage{macros-mtheory,amsaddr,tikz-feynman}
+\usepackage{macros-mtheory}
 
@@
 
+\DeclareUnicodeCharacter{0306}{\u{\i}}
+
 \begin{document}
@@
 \title{Twisted eleven-dimensional supergravity}
+
 \author{Surya Raghavendran}
@@
 \email{sraghavendran@perimeterinstitute.ca}
+
 \author{Ingmar Saberi}
@@
 \email{i.saberi@physik.uni-muenchen.de}
+
 \author{Brian R. Williams}
@@
 \email{brian.williams@ed.ac.uk}
+
 \begin{abstract}
 We construct a fully interacting holomorphic/topological theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
-%The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
-The theory describes a particular deformation of the cotangent bundle to the moduli space of complex structures on the fivefold.
+The theory describes a particular deformation of the cotangent bundle to the moduli space of Calabi--Yau structures on the fivefold.
 Its field content matches the holomorphic (or minimal) twist of the 
-%free 
 eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions correctly describe interacting twisted eleven-dimensional supergravity at the perturbative level.
@@
 \end{document}
-
-\end{document}

### 2023-04-17 revisions/revised/draft.tex

\documentclass[11pt,a4paper]{amsart}

\usepackage{macros-mtheory}

\addbibresource{references.bib}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\DeclareUnicodeCharacter{0306}{\u{\i}}

\begin{document}

\title{Twisted eleven-dimensional supergravity}

\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{sraghavendran@perimeterinstitute.ca}

\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}

\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}

\begin{abstract}
We construct a fully interacting holomorphic/topological theory in eleven dimensions that is defined on products of Calabi--Yau fivefolds with real one-manifolds. 
%The theory is a deformation of a BF theory based on divergence-free holomorphic vector fields on the fivefold. 
The theory describes a particular deformation of the cotangent bundle to the moduli space of complex structures on the fivefold.
Its field content matches the holomorphic (or minimal) twist of the 
%free 
eleven-dimensional supergravity multiplet recently computed by the second two authors, and we offer numerous consistency checks showing that the interactions correctly describe interacting twisted eleven-dimensional supergravity at the perturbative level. 
We prove that the global symmetry algebra of our model on flat space is an $L_\infty$ central extension of the infinite-dimensional simple exceptional super Lie algebra $E(5,10)$, following a recent suggestion of Cederwall in the context of the relevant pure spinor model. 
Twists of superconformal algebras map to the fields of our model on the complement of a stack of M2 or M5 branes, laying the groundwork for a fully holomorphic version of twisted holography in this context.
\end{abstract}
\maketitle

\vfill\eject

\setcounter{tocdepth}{1}
\tableofcontents

Twists of supersymmetric field theories have been a subject of active and fruitful study for many years. 
The notion of twisting was introduced by Witten and dates back to the first example~\cite{WittenTwist}, in which a topological field theory related to Donaldson invariants of four-manifolds was constructed as a twist of four-dimensional $\N=2$ supersymmetric gauge theory.
Shortly afterwards (thirty years ago), the field had expanded to include a diverse set of examples related to topological field theory~\cite{BlauThompson}.

For many years, twisting constructions were motivated by the goal of producing topological field theories, and correspondingly emphasized the role of particular modifications of  Lorentz symmetry via ``twisting homomorphisms'' designed to produce scalar supercharges.
From a more modern perspective, though, twisting a supersymmetric field theory is just a systematic way of taking invariants with respect to a fixed supercharge. This requires that the supercharge square to zero, so that the supercharge defines an odd abelian subalgebra of the supersymmetry algebra.\footnote{More generally, one could consider ``omega backgrounds'' by taking the derived invariants of a more general subalgebra in which the odd part is not necessarily abelian.}
The variety of appropriate square-zero elements was studied systematically in~\cite{NV}, and has deep relations not only to the  classification of  twists, but to the construction  of supersymmetric field theories via the pure spinor formalism~\cite{Cederwall,EHSW}. The name ``pure spinor'' originates because the  variety of  square-zero elements always contains a minimal stratum that is related to the space of Cartan pure spinors; in turn, these correspond to choices of complex structure on the  spacetime, at least when the dimension is even. 
As such, any $d$-dimensional  supersymmetric theory that admits a twist admits a \emph{minimal} or~\emph{holomorphic} twist, in which $n=\lfloor d/2\rfloor$ of the translations act nontrivially. Other twists can be understood as further twists of this holomorphic theory.
The importance and interest of holomorphic twists of supersymmetric gauge theories was emphasized in the work of Costello~\cite{CostelloHol}, who developed the notion mathematically, building on earlier work on holomorphic field theories in the physics literature~\cite[for example]{NekThesis,BCOV}.
Si Li pushed applications of holomorphic QFT further in his work on the higher genus $B$-model (see~\cite{SiThesis}, and later \cite{CLbcov1} together with Costello). 
In the physics literature, further constructions related to holomorphic twists had appeared in the context of supersymmetric indices; see~\cite{Romelsberger}, for example.

In a supergravity theory, local supersymmetry is already gauged, so that the standard notion of twisting is {\em a priori} not a sensible operation. Twisted supergravity thus needs to be  understood differently.
In their seminal paper~\cite{CLsugra}, Costello and Li gave a definition of twisted supergravity: it is supergravity in a background where the bosonic ghost field representing a twisting supercharge takes a nonzero value.
Twisting a supersymmetric field theory, in the classical sense, can then be  understood as coupling the theory to supergravity and placing it in such a background.

Using ideas related to string field theory and the topological B-model, Costello and Li provided conjectural descriptions of many examples of ten-dimensional theories of twisted supergravity. They used these descriptions to rigorously construct quantizations of open-closed string field theories~\cite{CLbcov1,CLtypeI}. 
A very active and promising direction of current research uses these twisted ten-dimensional models to formulate twisted versions of holography; see~\cite{CostelloM2, Costello_2021, costello2021twisted, Ishtiaque_2020, budzik2021giant, Gaiotto:2020vqj}, for example.
Supergravity in the $\Omega$-background was introduced in~\cite{CostelloM5}, and has been further studied in~\cite{Gaiotto:2019wcc, Oh:2020hph, Oh:2021bwi}.

In this paper, we provide perturbative descriptions of all twists of eleven-dimensional supergravity (before turning on any $\Omega$-background).
Thanks to a straightforward classification, which we recall below, there are essentially two types of twists which deform the flat background $\RR^{11}$: 
\begin{itemize}[leftmargin=\parindent,itemsep=\parskip]
\item The minimal (or holomorphic) twist. 
The resulting twisted theory is defined on $\CC^5 \times \RR$ and is holomorphic along $\CC^5$ and topological along the `time' direction~$\RR$. 
The twist is $SU(5)$ invariant and involves a fixed choice of a Calabi--Yau form on $\CC^5$. 
\item The non-minimal twist. 
The resulting twisted theory is defined on $\CC^2 \times \RR^7$ and is holomorphic along $\CC^2$ and topological along $\RR^7$.
The twist is $SU(2)$ invariant and involves a fixed choice of a hyperk\"ahler structure on $\CC^2$.  
\end{itemize}

In~\cite{SWspinor}, the last two authors used the pure spinor formalism to describe the {\em free field limit} of the minimal twist of eleven-dimensional supergravity on flat space, building on work of Cederwall~\cite{Ced-towards,Ced-11d} that constructed the eleven-dimensional theory in the pure spinor formalism. In fact, the result of~\cite{SWspinor} shows that the pure spinor formalism is compatible with twisting, so that the twist of any multiplet can be recovered from the algebraic geometry of a neighborhood of the corresponding point in the scheme of square-zero elements.
(In separate work~\cite{EagerHahner}, the free-field limit of the non-minimal twist was derived from the component-field multiplet as used in the physics literature.)
%\brian{also reference fabian and richard}
The resulting theory is $\ZZ/2$ graded; the grading is inherited from the totalization of ghost number and intrinsic parity in the original, untwisted, eleven-dimensional theory.
In \S\ref{s:dfn} we introduce a full interacting theory in the Batalin--Vilkovisky (BV) formalism, the free limit of which is the twist computed in \cite{SWspinor}.\footnote{One subtlety is that, unlike the usual BV formalism which involves a $\ZZ$-grading by ghost number, the eleven-dimensional theory is only $\ZZ/2$ graded.
As such, a division of the odd fields in the twisted theory into ``ghosts'' and ``antifields'' is not really meaningful.}
Our main conjecture is that this interacting BV theory is equivalent to the minimal twist of eleven-dimensional supergravity on flat space.

\begin{conj}
The eleven-dimensional  holomorphic-topological theory on $\CC^5 \times \RR$ that we will define in \S \ref{s:dfn} is equivalent to twisted supergravity on $\RR^{11}$, where the bosonic ghost takes a value corresponding to a holomorphic supercharge. 
\end{conj}

%\brian{Ingmar, maybe you can comment on the status of this conjecture.}
In this paper we will provide evidence for this conjecture on a variety of fronts:
\begin{itemize}[leftmargin=\parindent,itemsep=\parskip]
\item 
In \S\ref{sec:locchar}, we show that the character of the local operators in our 11-dimensional theory agrees with the index of 11-dimensional supergravity. 
\item
In \S\ref{sec:susy}, we will show that this theory has all of the expected residual supersymmetries present after performing the holomorphic twist.

\item
In \S\ref{s:nonmin}, we describe the non-minimal twist of eleven-dimensional supergravity as a background of our theory on $\CC^5 \times \RR$. 
This non-minimal twist is invariant for the group $G_2 \times SU(2)$. 
We find a match with a conjectural description of this $G_2 \times SU(2)$ invariant twist formulated by Costello in \cite{CostelloM5} and further developed in~\cite{RY}.  
\item In \S\ref{sec:dimred}, we compute dimensional reductions and show that our model is compatible with descriptions of twists of lower dimensional twists of supergravity. 
For instance, reducing along a circle in a complex plane agrees with the conjectural description of the $SU(4)$ twist of type IIA supergravity in~\cite{CLsugra}.
\item
Finally, in \S\ref{sec:ads}, we propose a description of supergravity in twisted versions of both the ${\rm AdS}_7$ and ${\rm AdS}_4$ backgrounds. 
We show that the residual symmetries of supergravity in these backgrounds are present in our twisted background.
\end{itemize}
%Surprisingly, at the twisted level these symmetries

\subsection*{A geometric description of the model}

Our eleven-dimensional theory is defined more generally on the product of manifolds 
\[
X \times S
\]
where $X$ is a Calabi--Yau five-fold and $S$ is a smooth oriented real one-dimensional manifold. 
The theory is of a holomorphic gravitational flavor as it describes ``partial'' deformations of complex structures along $X$. 
We will explain what we mean by this momentarily.

In our theory there is a field which encodes this partial deformation of complex structure on the Calabi--Yau manifold $X$.
It is an even field 
\[
\mu^{1,1} \in \Omega^{0,1} (X , \T_X) \otimes C^\infty(S) 
\]
where $\T_X$ denotes the holomorphic tangent bundle on $X$.
Locally, $\mu^{1,1}$ can be decomposed as Beltrami-like differential
\[
\mu^{1,1} = \mu^i_j (z,\zbar, t) \d \zbar_i \frac{\partial}{\partial z_j} .
\]
Physically speaking, $\mu^{1,1}$ is a component of the metric which survives in the twisted theory; see~\S\ref{s:components}.

Next, there are two fields 
\[
\gamma^{1,0} \in \Omega^{1,0} (X) \otimes C^\infty(S), \quad \gamma^{1,2} \in \Omega^{1,2}(X) \otimes C^\infty(S) .
\]
The field $\gamma^{1,2}$ is a component of the supergravity $3$-form $C$-field that survives in the twisted theory. 
The field $\gamma^{1,0}$ can be interpreted as a component of the one-form which is a ghost-for-a-ghost of the $C$-field.\footnote{The $C$-field has a gauge symmetry of the form $\delta C = \d B$ where $B$ is a two-form.
This ghost $B$ field has an additional gauge symmetry $\delta B = \d A$ for $A$ a one-form.
The field $\gamma^{1,0}$ is a component of $A$.}

There is a background where the equation of motion involving the fields $\mu^{1,1}$, $\gamma^{1,0}$,  and~$\gamma^{1,2}$ reads
\begin{align*}
\dbar \mu^{1,1} + \frac12 [\mu^{1,1}, \mu^{1,1}] + \Omega^{-1} \vee \left(\del \gamma^{1,0} \wedge \del \gamma^{1,2} \right) & = 0 \\
%(\dbar + \mu) \gamma^{1,0} = 
%(\dbar + \mu) \gamma^{1,2} & = 0 
%\\
%\div \mu & = 0 \\
%\d_S \mu = \d_S \gamma^{1,0} = \d_S \gamma^{1,2} = & = 0 .
\end{align*}
Additionally, there are the conditions that $\mu^{1,1}$ preserve the holomorphic volume form on $X$ and that all fields are locally constant along the topological direction $S$.  
%In the last line $\d_S$ is the de Rham differential on $L$ and implies that $\mu, \gamma^{1,0}$, and $\gamma^{1,2}$ are locally constant along $L$. 
Notice that this would be precisely the integrability equation for $\mu^{1,1}$ to determine a complex structure on $X$, were it not for the presence of the last term in the first equation.
%The second two equations resemble the conditions that $\gamma^{1,0}, \gamma^{1,2}$ be holomorphic with the complex structure determined by $\mu$. 
%Finally, the fourth equation constrains $\mu$ to preserve the holomorphic volume form on $X$.

If we work in a background where one of $\gamma^{1,0}$ or $\gamma^{1,2}$ is zero, then we see that $\mu^{1,1}$ is exactly a deformation of complex structure along $X$. 
In terms of the eleven-dimensional geometry, these field configurations describe deformations of the natural transverse holomorphic foliation (THF structure) on $X \times S$ which further preserve the holomorphic volume form along the leaves.
We further unpack the equations of motion in more general backgrounds in \S \ref{s:components}, but leave a complete study for future work.
%The equations of motion state that $\gamma$ is constant along $\RR$ and holomorphic along $\CC^5$. 
%Further, $\gamma$ is only defined up to the additional of a total holomorphic derivative $\gamma \sim \gamma + \del \beta$ where $\beta$ is a holomorphic function on $\CC^5$ which is constant along $\RR$.

\subsection*{Appearance of exceptional Lie superalgebras}

The gauge symmetries of a field configuration in any theory form a Lie algebra. 
In the Batalin--Vilkovisky formalism, one combines fields of all ghost number into a single object which, together with the linear BRST operator, has the structure of a dg Lie algebra.\footnote{In some models one actually obtains an $L_\infty$ algebra.} 
From the point of view of deformation theory, this dg Lie algebra describes the formal moduli space of deformations of the particular field configuration.

The simplest field configuration in the twisted theory is the flat background; this corresponds to considering to our eleven-dimensional theory on $\CC^5 \times \RR$, where we equip $\CC^5$ with the flat holomorphic volume form. 
In this case, we find a striking relationship to a certain infinite-dimensional simple super Lie algebra studied by Kac and collaborators \cite{KacBible,KacE510}.\footnote{The twist of the eleven-dimensional gravity multiplet was computed in~\cite{SWspinor} by reducing it to a particular pure spinor model based on $\Gr(2,5)$; a possible relationship between this pure spinor model and $E(5,10)$ was first pointed out by Martin Cederwall in~\cite{martinSL5}.}

\begin{thm}
The global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension of the exceptional simple super Lie algebra $E(5,10)$. 
\end{thm}

In particular, correlation functions involving observables of the eleven-dimensional theory will be constrained by the infinite-dimensional symmetry algebra $E(5,10)$. 
Given our main conjecture that the interacting eleven-dimensional BV theory on $\CC^5 \times \RR$ is the twist of supergravity, we obtain the following.

\begin{conj} 
A central extension of the super Lie algebra $E(5,10)$ is a symmetry of supergravity on $\RR^{11}$ which preserves the background where the bosonic ghost takes value equal to a holomorphic supercharge $Q$.
\end{conj}

\subsection*{Relationship to other twists of supergravity}

Motivated by the topological string, Costello and Li formulated conjectural descriptions of certain twists of 10-dimensional theories of supergravity. 
All of the descriptions center around the theory of Kodaira--Spencer gravity, otherwise known as BCOV theory. 
This theory was introduced in \cite{BCOV} as the closed-string field theory of the topological $B$-model on Calabi--Yau three-folds.
It was further extended to all Calabi--Yau manifolds in \cite{CLbcov1}. 
It is a sort of holomorphic version of gravity which at the genus zero  describes fluctuations of the complex structure of the Calabi--Yau manifold. 
We recall relevant aspects of Kodaira--Spencer gravity in \S\ref{s:BCOV}.

Through the dimensional reduction of our eleven-dimensional theory we will find a match with Costello and Li's descriptions of twists of 10-dimensional supergravity in terms of BCOV theory.
In Table \ref{diagram}, we provide a summary of the comparisons with twists of supergravity in lower dimensions we perform. The squiggly arrows denote further twists, and the solid arrows denote various kinds of reductions.

\begin{table}
\begin{center}
\[
\begin{tikzcd}[row sep=large,column sep = 3ex]
                                                                         &  \parbox{3cm}{\centering minimal twist of 11d} \arrow[ld, "\text{slab }" '] \arrow[d, "\text{topological }S^1" description] \arrow[rdd, "\text{CY3}" description, pos=.7, bend left = 5] \arrow[rr, rightsquigarrow] \arrow[rd, "\text{holomorphic }S^1"] &                                                             &  \parbox{3cm}{\centering non-minimal twist of 11d} \arrow[d, "\text{topological }S^1" description] \\
 \parbox{3cm}{\centering minimal twist of type I}  &  \parbox{3cm}{\centering minimal twist of type IIA}\arrow[l, "\text{orbifold}", start anchor={[xshift=1.5ex]west}, end anchor={[xshift=-1.5ex]east}]\arrow[r, rightsquigarrow, crossing over, end anchor = {[xshift=2ex]west}]                                                                                                                                                                                                &  \parbox{3cm}{\centering SU(4) twist of type IIA} \arrow[r, rightsquigarrow, start anchor={[xshift=-2ex]east}, end anchor={[xshift=2ex]west}] &  \parbox{3cm}{\centering SU(2) twist of type IIA}                                                 \\
                                                                         &                                                                                                                                                                                                                                                          & \parbox{3cm}{\centering minimal twist of 5d $\cN=1$}                   &                                                                                                
\end{tikzcd}
\]
\end{center}
\caption{Relations between various twists}
\label{diagram}
\end{table}

In \S\ref{s:su4red} we will show that the reduction along $\{0\} \times \RR \times \{0\} \subset \CC^4 \times \CC \times \RR$ is equivalent to the $SU(4)$ twist of type IIA supergravity. 
The topological string approach does not lead to a description of the minimal, or holomorphic, twist of type IIA supergravity. 
In \S \ref{s:su5IIA}, we describe the reduction along the line $\{0\} \times \RR \subset \CC^5 \times \RR$ to obtain a conjectural description of the holomorphic $SU(5)$ twist of type IIA supergravity. 
In \S \ref{s:Ired}, we show that the reduction along the interval $\{0\}\times [0,1]\subset \CC^5\times [0,1]$ with certain boundary conditions on the endpoints of the interval is equivalent to the twist of type I supergravity. We further observe in \S \ref{s:orbifold} that the twist of type I arises as the fixed points of a natural $\ZZ/2$ action on the minimal twist of IIA. Next, in \S \ref{s:CY3} we study the reduction along a Calabi-Yau 3 fold to obtain a conjectural description of the minimal twist of 5d $\cN=1$ supergravity. Finally, we show in \S \ref{s:nonmin} how the non-minimal twist of eleven-dimensional supergravity arises as a further twist of our holomorphic twist.

%\subsection*{Future work}

\subsection*{Acknowledgements}
We warmly thank I.~Brunner, M.~Cederwall, K.~Costello, R.~Eager, C.~Elliott, D.~Gaiotto, O.~Gwil\-liam, F.~Hahner, J.~Huerta, H.~Loosen, S.~Li, N.~Paquette, S.~R\"osch, J.~Walcher, P.~Yoo for conversation and inspiration of all kinds. I.S. and B.W. thank the University of Heidelberg, B.W. thanks the University of Edinburgh and the Mathematisches Forschungsinstitut Oberwolfach, and I.S. thanks the Krameterhof for hospitality while portions of this work were being completed. The work of S.R. is supported by the Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported in part by the Government of Canada, through the Department of Innovation, Science and Economic Development Canada, and by the Province of Ontario, through the Ministry of Colleges and Universities.
The work of I.S. is supported by the Free State of Bavaria. The work of B.W. is supported by the University of Edinburgh.
% Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the funding agencies.

\section{The minimal twist of eleven-dimensional supergravity} 
\label{s:dfn}

In this section we define the central theory of study within the Batalin--Vilkovisky (BV) formalism. 
The theory will be defined on any eleven-dimensional manifold of the form $X \times L$, where $X$ is a Calabi--Yau five-fold and $L$ is a smooth oriented one-manifold.

In \cite{SWspinor}, we showed that the underlying free limit of the theory we consider here is the free limit of the minimal twist of 11-dimensional supergravity on $\CC^5 \times \RR$. 
The goal of this section is to introduce interactions at the level of the minimal twist. 
The main result is Theorem \ref{thm:dfn} where we show that the theory is consistent within the BV formalism.

In the remainder of the paper we discuss further consistency with supersymmetry and string theory, but in this section we focus mostly on the theory as a partially holomorphic, partially topological, theory of gravity. 
Nevertheless, we do provide some preliminary justification towards the relationship to physical supergravity including a matching of indices in \S \ref{sec:locchar}.

\subsection{Divergence-free vector fields}

\subsubsection{}
\label{sec:divfree}
We set up some notations and conventions in the context of complex geometry. 
Let $V$ be a holomorphic vector bundle on a $d$ dimensional complex manifold $X$. 
If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on~$X$ with values in $V$.
The $\dbar$ operator $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X,V)$ defines the Dolbeault complex of $V$:
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] , \; \dbar\right) .
\]
This is a free (smooth) resolution for the sheaf of holomorphic sections of $V$.

Suppose $X$ is a Calabi--Yau manifold with holomorphic volume form $\Omega$.
The divergence $\div(\mu)$ of a holomorphic vector field $\mu$ is defined by the formula
\[
\div (\mu) \wedge \Omega = L_\mu (\Omega)
\]
where, on the right hand side, we mean the Lie derivative of $\Omega$ with respect to $\mu$.

Let $\T_X$ denote the holomorphic tangent bundle and consider its Dolbeault complex $\Omega^{0,\bu}(X , \T_X)$ resolving the sheaf of holomorphic vector fields. 
The divergence operator extends to the Dolbeault complex to yield a map of cochain complexes 
\[
\div \colon \Omega^{0,\bu}(X , \T_X) \to \Omega^{0,\bu}(X) .
\]
The resulting complex of sheaves
\beqn\label{eqn:cplx1}
\begin{tikzcd}
\ul{0} & \ul{1} \\
\Omega^{0,\bu}(X , \T_X) \ar[r, "\div"] & \Omega^{0,\bu}(X) ,
\end{tikzcd}
\eeqn
resolves the sheaf of holomorphic divergence-free vector fields $\Vect_0 (X)$.
The anti-holomorphic Dolbeault degrees and the $\dbar$ operator are left implicit. 
%By the holomorphic Poincar\'e lemma, the embedding of the sheaf $\Vect_0(X)$ into the degree zero piece of this complex is a quasi-isomorphism.

There is a direct way to extend the Lie bracket of vector fields to the complex \eqref{eqn:cplx1}. 
Denote by $\mu$ an element of $\Omega^{0,\bu}(X , \T_X)$ and $\nu$ an element of $\Omega^{0,\bu}(X)$ (for simplicity in notation, we will not expand the anti-holomorphic dependence). 
The Lie bracket defined by the formulas
\begin{align*}
[\mu, \mu'] & = L_\mu \mu' \\
[\mu, \nu] & = L_\mu \nu 
\end{align*}
is compatible with $\div$ and endows \eqref{eqn:cplx1} with the structure of a sheaf of dg Lie algebras.
We will refer to this sheaf by the symbol $\cL_0(X)$, or just $\cL_0$ if $X$ is understood.

The sheaf $\cL_0$ has the structure of a {\em local} dg Lie algebra~\cite[\S 3.1.3]{CG2}.
This means that, as a graded sheaf, $\cL_0$ is the smooth sections of a graded vector bundle, and its differential and Lie bracket are given by differential and bidifferential operators respectively.

\parsec[sec:Linfty]

Recall that an $L_\infty$ algebra is a $\ZZ$-graded vector space $\cL$ together with the datum of a square-zero, degree $+1$ derivation $\delta_\cL$ of the free commutative graded algebra $\Sym\left(\cL^\vee [-1] \right)$. 
The Chevalley--Eilenberg cochain complex is 
\[
\left(\Sym\left(\cL^\vee [-1] \right), \delta_\cL\right) .
\]
The Taylor components of $\delta_\cL$ define higher brackets $\{[-]_k\}_{k=1,2,\ldots}$ where $[-]_k \colon \cL^{\otimes k} \to \cL[2-k]$. 
The condition that the differential $\delta_\cL$ is square-zero is equivalent to the higher Jacobi relations.

An $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
\deq{
  \Phi^*: \clie^\bu(\cL') \to \clie^\bu(\cL)
}
between their respective Lie algebra cochains. It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra on $\cL^\vee[-1]$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\delta_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.

$\cL_0$ is the sheaf~\eqref{eqn:cplx1} resolving divergence-free vector fields equipped with the dg Lie algebra structure constructed in the previous section.
We consider the following automorphism of~$\Sym(\cL_0^\vee[-1])$, defined by its action on generators:
\deq[eq:newbase]{
    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^{-\nu} \mu.
}
This map defines a new model of the $L_\infty$ algebra with underlying graded vector space the same as \eqref{eqn:cplx1}, which we will call $\cL_\infty$.\footnote{We are being slightly abusive and using the symbols $\nu,\mu$ dually as coordinates, or operators, on the graded linear space $\cL[1]$.}
The formulas for the automorphism above clearly arise from maps of vector bundles and hence endow $\cL_\infty$ with the structure of a local $L_\infty$ algebra, meaning all operations are given by polydifferential operators.

The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. 
It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity.

%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.

%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
We can describe the $L_\infty$ structure on our new model $\cL_\infty$ explicitly.
Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. (Here, and in what follows, we will use the symbol $\PV^{i,\bu}$ for the Dolbeault resolution of \emph{holomorphic polyvector fields;} by definition, this is the complex $\Omega^{0,\bu}(X,\wedge^i \T_X)$.)
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \wedge \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \wedge \mu_2) 
%\\
%[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
For $k \geq 2$ the general formula for the $k$-ary brackets are 
\begin{align*}
[\nu_1, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} & = \div(\nu_1 \cdots \nu_k \mu_1 \wedge \mu_2) \\
[\nu_1,\ldots, \nu_{k-3}, \mu_1,\mu_2,\gamma]_k & = \nu_1 \cdots \nu_{k-3} (\mu \wedge \mu') \vee \del \gamma .\\
[\nu_1,\ldots,\nu_{k-2}, \mu, \gamma]_k & = \nu_1 \cdots \nu_{k-2} \mu \vee \del \gamma .
\end{align*}

%We describe the explicit $L_\infty$ automorphism $\Psi \colon (\cL_0)^{L_\infty} \rightsquigarrow (\cL_0)^{strict}$ intertwining the strict dg Lie structure on $\cL_0$ and this $L_\infty$ structure.
%The linear term $\Psi^{(1)} = \id$ is the identity map. 
%The higher terms $\Psi^{(n)}$ are defined by 
%\brian{someone check me}
%\begin{align*}
%\Psi^{(n)} (\nu_1,\ldots, \nu_{n-k},\mu_1,\ldots, \mu_k) & = \delta_{k=1} \nu_1 \cdots \nu_{n-1} \mu_1 . \\
%\end{align*}

%\parsec
%There is yet another $L_\infty$ model for divergence-free vector fields that we remark on here.
%\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}

\subsection{Theories of BF type}

\parsec
Suppose that $\cL$ is an $L_\infty$ algebra with $L_\infty$ operations $\{[-]^\cL_k\}_{k=1,2,\ldots}$ and that $(\cA, \d_\cA)$ is a commutative dg algebra. 
The graded vector space $\cL \otimes \cA$ is equipped with the natural structure of an $L_\infty$ algebra with operations $\{[-]_k\}_{k=1,2,\ldots}$ defined by
\begin{align*}
[x \otimes a]_1 & = [x]^\cL_1 \otimes a + (-1)^{|x|} x \otimes \d_\cA a \\
[x_1 \otimes a_1, \ldots , x_k \otimes a_k]_k & = [x_1,\ldots,x_k]^\cL_k \otimes (a_1 \cdots a_k), \qquad k \geq 2 .
\end{align*}

We apply this construction, taking $\cL$ to be the sheaf resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ equipped with either the strict dg Lie algebra structure $\cL_0(X)$ or its non-strict $L_\infty$ structure $\cL_\infty (X)$. 
The algebra $\cA$ will be the smooth de Rham complex $(\Omega^\bu(S) , \d_S)$ where $S$ is a smooth manifold.

We thus obtain the structure of an dg Lie algebra on $\cL_0(X) \otimes \Omega^{\bu}(S)$ or an $L_\infty$ algebra $\cL_\infty(X) \otimes \Omega^\bu(S)$.
These define equivalent local $L_\infty$ algebras on the product manifold~$X \times S$.

\parsec[s:bf]

Associated to any local $L_\infty$ algebra is a classical field theory in the BV formalism.
Let $\cL$ be a local $L_\infty$ algebra on some manifold $M$, it is the sheaf of sections of some graded vector bundle $L$. 
For a section $A \in \cL$, introduce the `higher curvature map' defined by the formula
\[
\mathsf{F}_A = [A]_1 + \frac12 [A,A]_2 + \frac{1}{3!} [A,A,A]_3 + \cdots .
\]

The fields of the associated BV theory are pairs
\[
  (A, B) \in \cL[1] \oplus \cL^{!}[-2] .
\]
Here $\cL^!$ denotes the sheaf of sections of the bundle $L^* \otimes {\rm Dens}$, where ${\rm Dens}$ is the bundle of densities. 
The shifted symplectic BV pairing is the obvious integration pairing between $A$ and $B$.

The action functional reads $S_{\rm BF} = \int_M B \, \mathsf{F}_{A}$ which leads to the equations of motion $\mathsf{F}_{A} = 0$ and $\mathsf{D}_A B= 0$ where $\mathsf{D}_A$ is the higher covariant derivative along $A$. 
We refer to this as the ``BF theory'' associated to $\cL$.

We thus obtain a theory in the BV formalism on the product manifold $X \times S$ associated to both local $L_\infty$ algebras $\cL_0(X) \otimes \Omega^{\bu}(S)$ and $\cL_\infty(X) \otimes \Omega^\bu(S)$.

\parsec
For concreteness, we spell out the fields of the theories we have constructed on $X \times S$.
In both cases, the space of fields equipped with the linear BRST operator is
\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    -n & -n + 1 & -1 & 0 \\ \hline
    \Omega^{0}(X;S) \ar[r, "\del"] & \Omega^{1}(X;S) & 
     \PV^{1}(X; S) \ar[r, "\div"] & \PV^{0}(X; S).
\end{tikzcd}
\end{equation}
We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.
We are using the shorthand notation
\begin{align*}
\Omega^{i}(X;S) & = \Omega^{i , \bu;\bu}(X;S) \\
 & = \oplus_{j,k} \PV^{i,j}(X) \otimes \Omega^k(S) [-j-k] .
\end{align*}
which is equipped with the $\dbar + \d_S$ operator and similarly for $\PV^{i}(X;S)$.

The natural pairing between $\PV^i(X;S)$ and~$\Omega^i(X;S)$ is of degree $-\dim_\C(X) -\dim_\R(S)$. 
As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a degree $(-1)$ pairing, provided that we choose the shift to be given by
\deq{
  n = \dim_\C(X) + \dim_\R(S) - 1.
}
The pairing is defined by the formula 
\[
\int^\Omega_{X \times S} \mu \vee \gamma + \int^\Omega_{X \times S} \nu \beta 
\]
where $\int^\Omega_{X \times S} \alpha \define \int_{X \times S} \alpha \wedge \Omega$.

We have constructed two equivalent descriptions of the BF theory which share the linear BRST complex \eqref{eq:sympfields}.
Explicitly, the action functional for BF theory associated to the local dg Lie algebra $\cL_0(X) \otimes \Omega^{\bu}(S)$ is
\deq{
  S_{BF,0} =  \int^\Omega \bigg[\beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +  \beta \wedge \partial_\Omega \mu +  \frac{1}{2} [\mu,\mu] \vee \gamma +  [\mu,\nu] \beta \bigg] .
}
As in the Lie algebra structure of this strict model, notice that the Schouten--Nijenhuis bracket appears explicitly.

The action functional of BF theory associated to $\cL_\infty(X) \otimes \Omega^{\bu}(S)$ is non polynomial. 
In fact, it is related to the BCOV action functional via dimensional reduction (see \S \ref{sec:dimred}).
Explicitly, this action functional is
\deq{
  S_{BF,\infty} =  \int^\Omega \bigg[ \beta \wedge (\dbar + \d_S) \nu +  \gamma \wedge (\dbar + \d_S) \mu +   \beta \wedge \partial_\Omega \mu + \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma \bigg] .
}

We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent. As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to an automorphism of BV theories.
Explicitly, the automorphism is
\begin{equation}\label{eqn:auto1}
  \mu \mapsto e^{-\nu} \mu, \qquad \nu \mapsto 1-e^{-\nu} , \qquad
  \beta \mapsto (\beta - \mu \vee \gamma) e^{\nu},\qquad \gamma \mapsto e^{\nu} \gamma .
\end{equation}

\parsec[]

In what follows, we specialize to the case that $X$ is a Calabi--Yau five-fold and that $S$ is a one-dimensional smooth orientable manifold. 
In this case, with $n = 5 + 1 - 1 = 5$ the theories described in this section are $\ZZ$-graded in the BV formalism.
Momentarily, we consider a new term in the action which will break this grading; as such, this integer shift will not play an essential role.

\subsection{A deformation of BF theory}

Let $X$ be a Calabi--Yau five-fold and $S$ be a smooth oriented one-dimensional real manifold. 
We will break the $\ZZ$-grading present in BF theory discussed in the previous section to a $\ZZ/2$ grading. 
For reference, this means that the linear cochain complex of fields of the model now takes the following form.

\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    {\rm odd} & {\rm even} & {\rm odd} & {\rm even} \\ \hline
    \Omega^{0}(X;S)_\beta \ar[r, "\del"] & \Omega^{1}(X;S)_\gamma & 
     \PV^{1}(X; S)_\mu \ar[r, "\div"] & \PV^{0}(X; S)_\nu.
\end{tikzcd}
\end{equation}

\parsec
%check CME

To define our classical field theory on $X \times S$, we consider  a deformation of BF theory $S_{BF}$ (this refers to either the presentation as $S_{BF,0}$ or $S_{BF,\infty}$). 
Such deformations are governed by the classical master equation: the parameterized family of actions 
\beqn\label{eqn:defaction}
S_{BF} + g J
\eeqn
defines a consistent theory in the BV formalism if and only if
\deq{
  \{S_{BF} + g J, S_{BF} + g J \} = 0.
}
Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the pair of conditions
\deq[eq:2cond]{
  \{S_{BF},J\} =  \{J,J\} = 0.
}

The form of $J$ depends on which presentation we use for BF theory.
To begin, we will use the presentation of BF theory $S_{BF, \infty}$ which uses the the non-strict $L_\infty$ structure on divergence-free holomorphic vector fields.
The deformation $J$ does not make reference to the Calabi--Yau structure explicitly, but it does involve the holomorphic de Rham operator $\del$ on $X$.

The main result of this section is the following.

\begin{thm}
\label{thm:dfn}
Let $X$ be a Calabi--Yau five-fold and $S$ a smooth one-dimensional manifold, and consider the BV theory $(\cE, S_{BF,\infty})$ on $X \times S$ defined above. The local functional 
  \deq{
    J = \frac16 \int_{X \times S} \gamma \wedge \del \gamma \wedge \del \gamma ,
  }
  where $\gamma \in \Omega^{1,\bu}(X;S)$, defines a deformation of~$(\cE,S_{BF,\infty})$ as a $\Z/2$-graded BV theory.
\end{thm}

\parsec[]

Before proceeding to the proof, we remark on grading issues. 
In the original $\Z$-grading on the BF theory given in \eqref{eq:sympfields} with $n=5$, the component 
\[
\gamma^{1,i;j} \in \Omega^{1,i}(X) \otimes \Omega^j(S) 
\]
sits in degree $-4+i+j$. 
Thus, we see that in the original $\Z$-grading on BF theory one has
  \deq{
    \deg(J) = 6.
  }
Thus $S_{BF} + J$ is not of homogenous $\ZZ$ grading (although it is even).

This is completely reasonable from the point of view of twisting supersymmetry in eleven dimensions. 
Indeed, the $R$-symmetry group is trivial, and there is not a way to regrade the fields of the twisted theory using twisting data~\label{CosHol,ESW}. 
Nevertheless, if we break to the obvious $\ZZ/2$ grading, the functional $S_{BF} + g J$ defines an even action functional.
Unless otherwise stated, we will work with this $\ZZ/2$ grading for the remainder of this section.

\parsec[]
We proceed to show that $S_{BF,\infty} + g J$ solves the classical master equation.
For notational simplicity we will omit the integral symbol $\int^\Omega$.

%By apparent field type reasons, the equation \eqref{eq:2cond} is equivalent to the following two equations
%\[
%\{S_{BF,\infty}, J\} = 0, \qquad \{J,J\} = 0.
%\] 
\begin{proof}

It is immediate from the form of the BV bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field. 
It remains to check that $\{S_{BF,\infty},J\} = 0$. 
For the quadratic term in the BF action, we note that 
  \deq{
    \{\beta \wedge \div\mu, J\} = \frac12 \del\beta \wedge \del \gamma \wedge \del \gamma = 0,
  }
  because total derivatives are equivalent to zero as local functionals.

The contribution from the remaining BF action takes the form
\[
    \left\{ \frac12 \frac{1}{1-\nu} \del\gamma \vee \mu^2, \frac16 \gamma \wedge \del\gamma \wedge \del \gamma \right\} =\frac12 (\mu \vee \del \gamma) \wedge \del \gamma \wedge \del \gamma .
\]
    %\frac12 \frac{1}{1-\nu} \bigg[ (\del\gamma\vee\mu) \wedge \del\gamma \wedge \del \gamma \pm \del\gamma \wedge (\del\gamma\vee\mu) \wedge \del \gamma \pm \del\gamma \wedge \del \gamma \wedge (\del\gamma\vee\mu) \bigg].
This expression is zero for symmetry reasons. 
Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional which is cubic in this two-form. We can ask whether such a  contraction exists just at the level of $\lie{sl}(5)$ representation theory. Let $\ydiagram{1}$ denote the fundamental representation of~$\lie{sl}(5)$, which we identify with constant one-forms. Since the term must be a scalar, the contraction $(\partial\gamma^3$ must sit in the fundamental representation again, since it is dual to a vector field. Computing the decomposition of the tensor cube of the two-form, we find
\deq{
  \Sym^3 \left( \ydiagram{1,1} \right) \cong \ydiagram{3,3} \oplus \ydiagram{2,2,1,1}\,.
}
(In fact, the absence  of the relevant irreducible representation does not  even depend on the parity of the  field $\gamma$, since 
  \deq{
    \wedge^3\left( \ydiagram{1,1} \right) \cong \ydiagram{3,1,1,1}  \oplus \ydiagram{2,2,2}\, ;
  }
the  fundamental representation has symmetry type $\ydiagram{2,1}$.) 
\end{proof}

\parsec[s:coupling]

We make note of the dependence on the coupling constant $g$ in the definition of the deformed action $S_{BF,\infty} + g J$.

When $g = 0$ we recover BF theory for the $L_\infty$ algebra $\cL_\infty(\CC^5) \otimes \Omega^\bu(\RR)$. 
For any $g \ne 0$ the theories are essentially equivalent in perturbation theory. 
Indeed, if $g \ne 0$ we can make the following field redefinition 
\[
\gamma \mapsto \sqrt{g} \gamma, \quad \beta \mapsto \sqrt{g} \beta 
\]
to write the action as 
\[
\frac{1}{\sqrt{g}} \left(S_{BF,\infty} + J \right)  .
\]

In perturbation theory, this has the affect of modifying the quantization parameter $\hbar$ to $\hbar / \sqrt{g}$.
Thus, after modifying $\hbar$ and making the above field redefinition, the perturbative expansion of any theory is equivalent to the one with $g = 1$.

\parsec[s:altdfn]

We remark on an alternative, equivalent, description of the deformed theory which involves the strict dg Lie algebra structure on divergence-free holomorphic vector fields.

We can replace $S_{BF,\infty}$ by $S_{BF,0}$ via applying the field automorphism \eqref{eqn:auto1}.
Doing this we see that $J$ becomes 
\[
\til{J} = \frac16 e^\nu \gamma \wedge \del (e^\nu \gamma) \wedge \del(e^\nu \gamma) .
\]
Since this automorphism preserves the odd BV bracket, the actions $S_{BF,\infty} + g J$ and $S_{BF, 0} + g \til{J}$ are both solutions to the classical master equation, and are equivalent as~$\ZZ/2$ graded BV theories.

\subsection{Equations of motion of the component fields} \label{s:components}

Soon, we will provide a series of justifications for the assertion that the deformed theory $S_{BF, \infty} + g J$ is the minimal twist of eleven-dimensional supergravity on flat space $X \times S = \CC^5 \times \RR$ where $\CC^5$ is equipped with its flat Calabi--Yau form. 
For the moment, we briefly read off the equations of motion of the general theory on $X \times S$.
Let $\Omega$ denote the Calabi--Yau form on $X$.

We consider the action $S_{BF, \infty} + gJ$.
The equation of motion obtained by varying $\beta$ is especially simple---in fact linear---since $\beta$ only appears in the action via a quadratic term. 
It is
\beqn\label{eqn:eombeta}
\dbar \nu + \d_S \nu + \div \mu = 0 .
\eeqn
Varying $\gamma$ we obtain the equation of motion
\beqn\label{eqn:eomgamma}
\dbar \mu + \d_S \mu + \frac12 \frac{1}{1-\nu} \div (\mu^2) + \frac12 (\del \gamma \wedge \del \gamma) \vee (g \Omega^{-1}) = 0 .
\eeqn
The last term represents the contraction of an element of $\Omega^{4,\bu}(X;S)$ with the nonvanishing section $\Omega^{-1} \in \PV^{5,\bu}(X;S)$ to yield an element of $\PV^{1,\bu}(X;S)$. 
If we vary the $\mu$ we obtain 
\beqn\label{eqn:eommu}
(\dbar + \d_S) \gamma + \del \beta + \frac{1}{1-\nu} (\mu \vee \del \gamma) = 0 .
\eeqn
Finally, if we vary $\nu$ we obtain
\beqn\label{eqn:eomnu}
(\dbar + \d_S) \beta + \frac12 \frac{1}{(1-\nu)^2} \mu^2 \vee \del \gamma = 0 .
\eeqn

The equation of motion must hold for any inhomogenous superfields.
We can get a better sense of the equations if we expand in components of these fields. 
The component fields of the eleven-dimensional theory on $X \times S$ have the following form: 
\begin{itemize}
\item $\mu = \sum_{i,j} \mu^{i;j}$ is a superfield where
\[
\mu^{i;j} \in \PV^{1,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
\]
The component $\mu^{i;j}$ has parity $i+j+1 \pmod 2$. 
\item $\nu = \sum_{i,j} \nu^{i;j}$ is a superfield where
\[
\nu^{i;j} \in \PV^{0,i}(X, \T_X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
\]
The component $\nu^{i;j}$ has parity $i+j \pmod 2$. 
%The linear equations of motion state that $\mu$ is constant along $\RR$ and holomorphic divergence-free as a vector field on $\CC^5$. 
\item 
$\gamma = \sum_{i,j} \gamma^{i;j}$ is a superfield where
\[
\gamma^{i;j} \in \Omega^{1,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
\]
The component $\gamma^{i;j}$ has parity $i+j\pmod 2$. 
\item 
\item $\beta = \sum_{i,j} \beta^{i;j}$ is a superfield where
\[
\beta^{i;j} \in \Omega^{0,i}(X) \otimes \Omega^j(\RR) ,\quad i=0,\ldots, 5, \quad j=0,1.
\]
The component $\beta^{i;j}$ has parity $i+j+1 \pmod 2$. 
\end{itemize}

We look closely at the geometric meaning of \eqref{eqn:eombeta}. 
Let's make the simplifying assumption that all components of $\mu$ are divergence-free, and further that all fields are locally constant along $S$: that is, $\div \mu = 0$ and $\d_S \mu = \d_S \gamma = 0$.
Then $\nu = 0$ is a solution to \eqref{eqn:eombeta} and we can assume that all fields are functions, or zero-forms, along $S$. 
Then, there is a component of \eqref{eqn:eomgamma} which can be written as 
\beqn\label{eqn:eomgamma1}
\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + \left(\frac12 \del \gamma^{1;0} \wedge \del \gamma^{1;0} + \del \gamma^{2;0} \wedge \del \gamma^{0;0}\right) \vee (g \Omega^{-1}) = 0 
\eeqn
where now $[-,-]$ stands for the Schouten bracket.

To further simplify \eqref{eqn:eomgamma1}, we can look for a solutions where  $\gamma^{1;0}$, the $(0,1)$ Dolbeault part of $\gamma$, is zero. 
Then, up to the term involving 
\[
\alpha \define \del \gamma^{0;0},
\]
we find precisely the integrability equation for the complex structure determined by Beltrami differential $\mu^{1;0} \in \PV^{1,1} \otimes \Omega^0$. 
If $\dbar \alpha = 0$, the holomorphic two-form $\alpha \in \Omega^{2,hol}(X)$ defines a map of sheaves
\[
\Omega^{2,hol}_X \xto{\wedge \alpha} \Omega^{4,hol}_X \cong_\Omega \cT^{hol}_X
\]
where $\cT^{hol}_X$ denotes the sheaf of holomorphic vector fields and the last isomorphism uses the Calabi--Yau form $\Omega$ on $X$.  
The image of $\Omega^{2,hol}_X$ defines a subsheaf $\cF_{\alpha} \subset \cT^{hol}_X$. 
Since $\del \alpha = 0$, this subsheaf is automatically integrable and hence determines a foliation.

Summarizing, see that there is a field configuration where the Beltrami diffrential $\xi = \mu^{1;0} \in \Omega^{0,1}(X, \T_X)$ satisfies the modified integrability condition
\[
\dbar \xi + \frac12  [\xi , \xi] = \alpha \vee \rho
\]
for some $\rho \in \PV^{2,2} (X)$. 
In other words, $\xi$ defines an integrable complex structure deformation along the leaf space associated to the foliation $\cF_\alpha$. 
We leave a more complete exploration of the moduli space of solutions of the equations of motion for future work.

In~\cite{SWspinor}, the second two authors showed that the free limit of the minimal twist of eleven-dimensional supergravity agrees with the free limit of the eleven-dimensional theory that we have introduced here. 
Given this result, we can recognize many fields in the twisted theory as components of the physical fields of supergravity which remain after we twist.

\begin{itemize}
\item 
The components 
\begin{align*}
\mu^{1;0} & = \mu^j_i(z,\zbar,t) \d \zbar_j \partial_{z_i} \\
\mu^{0;1} & = \mu^t_i (z,\zbar,t) \d t \partial_{z_i}
\end{align*}
of $\mu$ comprise components of the metric which remain after the twist. 
The components 
\[
\mu^{0;0} = \mu_i (z,\zbar,t) \partial_{z_i} 
\]
comprise the ghosts for infinitesimal (holomorphic) diffeomorphisms. 
\item 
The three-form fields
\begin{multline}
\beta^{3;0} = \beta^{ijk} (z,\zbar,t) \d \zbar_i \d \zbar_j \d \zbar_k , \quad \beta^{2;1} = \beta^{ij}_t (z,\zbar,t) \d \zbar_i \d \zbar_j \d t \\
\gamma^{2;0} = \gamma^{ijk} (z,\zbar,t) \d z_i \d \zbar_j \d \zbar_k , \quad \gamma^{1;1} = \gamma^{ij}_t (z,\zbar,t) \d z_i \d \zbar_j \d t .
\end{multline} 
comprise components of the supergravity $C$-field which remain after the twist. 
The two-form fields $\beta^{2;0}, \beta^{1;1}, \gamma^{1;0}, \gamma^{0;1}$, the one-form fields $\beta^{1;0}, \beta^{0;1}$, and the zero-form field $\beta^{0;0}$ is what remains of the ghost system (ghosts, ghosts for ghosts, etc.) for the supergravity $C$-field. 
\end{itemize}
%The most geometrically relevant component is the case where 
%\[
%\mu^{1;0} \in \PV^{1,1}(X) \otimes \Omega^0(S) 
%\]
%which is an even field in our $\ZZ/2$ graded BV theory.
%The superscript denotes anti-holomorphic; de Rham form type. 
%For this component of $\mu$, the only components of $\gamma$ which appear in the above equations of motion are $\gamma^{0;0}$, $\gamma^{1;0}$, and $\gamma^{2;0}$.
%Expanding these components out, we obtain
%\beqn\label{eqn:eomgamma1}
%\dbar \mu^{1;0} + \frac12 [\mu^{1;0},\mu^{1;0}] + (\del \gamma^{0;0} \wedge \del \gamma^{2;0}) \vee (g \Omega^{-1}) + \frac12 (\del \gamma^{1;0} \wedge \del \gamma^{1;0}) \vee (g \Omega^{-1}) = 0 .
%\eeqn

\subsection{Local character}\label{sec:locchar}

We consider the eleven-dimensional theory on the manifold $\CC^5 \times \RR$, where $\CC^5$ is equipped with its standard Calabi--Yau structure. 
On this background, the theory is manifestly $SU(5)$ invariant. 
In this section, we compute the corresponding character of the local operators at the origin.

The local character is only sensitive to the free limit of the theory.
Furthermore, the linear BRST operator is an $SU(5)$-invariant deformation of the $(\dbar + \d_{\RR})$ operator. 
Therefore, to compute the character it suffices to compute the $SU(5)$-equivariant character of the $\dbar$ cohomology.

The solutions to the $(\dbar + \d_{\RR})$-equations of motion simply say that all fields are holomorphic along $\CC^5$ and constant along $\RR$. 
Thus, the solutions can be identified with 
\begin{align*}
\mu^{i}\partial_{z_i} & \in \Vect(\CC^5) \cong \cO(\C^5)\partial_{z_i},\quad 
\nu \in \cO (\C^5) \\
\beta & \in \cO (\C^5), \quad \gamma^{i} \d z_i \in \Omega^{1}(\CC^5) \cong \cO (\C^5)\d z_i 
\end{align*}
where $z_i$ is a holomorphic coordinate on $\CC^5$.

Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_j) = (m_1, m_2, m_3, m_4, m_5)\in \Z^5_{\geq 0}$; these are given by
\begin{align*}
 \boldsymbol{\mu}^{i}_{(m_j)} &: \mu^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\mu^{i} (0) \\
\boldsymbol{\nu}_{(m_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\nu (0) \\
\boldsymbol{\gamma}^{i}_{(m_j)} &: \gamma^{i}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\gamma^{i} (0) \\
 \boldsymbol{\beta}_{(m_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{z_4}^{m_4}\partial_{z_5}^{m_5}\beta (0)
\end{align*}

\iffalse
We choose generators of the Cartan subgroup for the $SU(5)$ action with the following weights:

\[\begin{array}{|c|c|c|c|c|c|}
& z_1 & z_2 & z_3 & z_4 & z_5 \\
\hline
q & & & & 1 & -1 \\
t_1 & 1 & -1 & & & \\
t_2 & & 1 & -1 & & \\
y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
\end{array}\]
We are choosing the weights in this way as a matter of convenience for the later sections. 
For instance, upon performing the further twist of the eleven-dimensional theory, the $SU(5)$ symmetry is broken to an $SU(3)\times SU(2)$ symmetry; the Cartan of the unbroken symmetries corresponds to the fugacities $q, t_1, t_2$ in the above table.

We can now readily compute the characters.
\begin{prop}
The $SU(5)$ local character of the holomorphic twist of the eleven-dimensional theory on flat space is
\begin{multline}
\chi_{SU(5)} = 
\prod_ {(m_j)\in \Z^5_{\geq 0}} \frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} }
\\ 
\times \frac{t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2}}{t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2}}.
\end{multline}
\end{prop}
\begin{proof}
We compute the local character as the plethystic exponential of the character of linear local operators.

Note that the linear local operators $ \nu_{(m_j)}$ and $\beta_{(m_j)}$ are of the same weight but opposite parity so contribute to the character with opposite sign. These contributions therefore cancel. Next, there is a summand of the linear local operators of the form 
\[
\bigoplus _{(m_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\mu^{z_1}_{(m_j)}\partial_{z_1}\oplus \C\mu^{z_2}_{(m_j)}\partial_{z_2}\oplus \C\mu^{z_3}_{(m_j)}\partial_{z_3}\oplus\C\mu^{w_1}_{(m_j)}\partial_{w_1}\oplus \C\mu^{w_2}_{(m_j)}\partial_{w_2}\right).
\] 
This contributes 
\begin{multline}
\sum_{(m_j)\in \Z^5_{\geq 0 }}- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)} \times \\
\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right).
\end{multline}
Finally, there is a summand of the form 
\[
\bigoplus _{(m_i;n_j)\in \Z^5_{\geq 0 }} \Pi \left ( \C\gamma^{z_1}_{(m_i; n_j)}d{z_1}\oplus \C\gamma^{z_2}_{(m_i; n_j)}d{z_2}\oplus\C\gamma^{z_3}_{(m_i; n_j)}d{z_3}\oplus\C\gamma^{w_1}_{(m_i; n_j)}d{w_1}\oplus \C\gamma^{w_2}_{(m_i; n_j)}d {w_2}\right).
\] 
This likewise contributes 
\[
\sum_{(m_j)\in \Z^5_{\geq 0 }}t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right).
\] 
In sum, the character of linear local operators is the geometric series 
\[
\sum_{(m_j)\in \Z^5_{\geq 0 }}-t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (\begin{aligned}t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \\  - (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2})\end{aligned}\right).
\] 
The plethystic exponential returns the desired expression.

\end{proof}
\fi

It is easiest to label the Cartan subgroup of $SU(5)$ by fugacities $q_1,\ldots, q_5$ subject to the constraint that $\prod_{i=1}^5 q_i = 1$. 
We first compute the single particle index.
This is the $SU(5)$ character of the space of linear local operators.

\begin{lem}
The single particle index is 
\[
i(q_1,\ldots,q_5) = \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i^{-1}}{\prod_{i=1}^5 (1-q_i^{-1})}
\]
where the fugacities satisfy the constraint $\prod_{i=1} q_i = 1$. 
\end{lem}
\begin{proof}
The linear local operators $ \boldsymbol{\nu}_{(m_j)}$ and $\boldsymbol{\beta}_{(m_j)}$ are of the same $q$-weight but opposite parity.
Thus, they do not contribute to the single particle index.

The $q$-weight of the odd local operator $\boldsymbol{\mu}_{(m_j)}^i$ is 
\[
q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} .
\]
The $q$-weight of the even local operator $\boldsymbol{\gamma}_{(m_j)}^i$ is 
\[
q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} .
\]

Thus we find that the single particle index is given by the infinite series
\beqn\label{infseriesindex}
\sum_{i=1}^5\left ( \sum_{(m_i)\in \Z^5_{\geq 0}} q_1^{m_1} \cdots q_i^{m_i + 1} \cdots q_5^{m_5} - \sum_{(m_i)\in \Z^5_{\geq 0}} q_1^{m_1+1} \cdots q_i^{m_i} \cdots q_5^{m_5+1} \right)
\eeqn

which sums to the expression
\beqn\label{singleparticleindex}
- \frac{\sum_{i=1}^5 q_1 \cdots \Hat{q_i} \cdots q_5}{\prod_{i=1}^5 (1-q_i)} + \frac{\sum_{i=1}^5 q_i}{\prod_{i=1}^5 (1-q_i)} .
\eeqn

This simplifies to the stated expression.
\end{proof}

This single particle index for our space of local operators agrees with the one computed in \cite{NekrasovInstanton}. 
To obtain the full index of local operators we apply the plethystic exponential ${\rm PE}[f(x)] = \exp\left(\sum_n \frac1n f(x^n)\right)$.

\begin{prop}\label{prop:locchar}
The character of local operators of the eleven-dimensional theory on $\CC^5 \times \RR$ is 
\[
\prod_{i=1}^{5} \prod_{(m_i)\in \Z^5_{\geq 0}} \frac{1-q_1^{m_1+1}\cdots q_i^{m_i}\cdots q_5^{m_5+1}}{1-q_1^{m_1}\cdots q_i^{m_i+1}\cdots q_5^{m_5}}
\]
\end{prop}
\begin{proof}
Recall that the plethystic exponential takes sums to products and monomials to geometric series. Apply this to the infinite series \eqref{infseriesindex}.
\end{proof}
%\[
%\prod_ {(m_j)\in \Z^5_{\geq 0}}\frac{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-n_1+n_2}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1^{-1}y + t_1t_2^{-1}y + t_2y + q^{-1}y^{-\frac 3 2} + qy^{-\frac 3 2} \right)}{1- t_1^{-m_1+m_2}t_2^{-m_2+m_3}q^{-m_4+m_5}y^{m_1+m_2+m_3-\frac 3 2 (m_4+m_5)}\left (t_1y^{-1} + t_1^{-1}t_2y^{-1} + t_2^{-1}y^{-1} + q^{-1}y^{\frac 3 2} + qy^{\frac 3 2} \right)}.
%\]

%The linear equations of motion for the superfield $\mu$ read 
%\[
%\dbar \mu^{i;j} + \d_{S} \mu^{i+1, j-1} = 0, \quad \div \mu^{i,j} = 0
%\]
%for all $i,j$. 
%The operator $\dbar$ is the anti-holomorphic Dolbeault operator acting on $\CC^5$, $\d_S$ is the de Rham operator on $S$, and $\div$ is the divergence with respect to the fixed holomorphic volume form on $\CC^5$. 
%In particular, this states that $\mu^{i;0}$ is locally constant along $S$ and holomorphic divergence-free as a Dolbeault valued vector field on $\CC^5$.

\subsection{One-loop quantization}

In \cite{GRWthf} an existence result for one-loop quantizations of mixed topological-holomorphic theories was established. 
The crucial thing is that these results apply to more than just topological-holomorphic theories arising from twists of supersymmetric gauge theories.
They also apply to twists of supergravity theories. 
We apply this to the eleven-dimensional model at hand.

The eleven-dimensional theory is a mixed topological-holomorphic theory.
On flat space $\CC^5_z \times \RR_t$, this means that the theory is translation invariant and that the following act homotopically trivially:
\begin{itemize}
\item the vector fields $\del_{\zbar_1}, \ldots, \del_{\zbar_{5}}$ corresponding to infinitesimal anti-holomorphic translations,
\item the vector field $\partial_t$ corresponding to infinitesimal translations in the $\RR_t$ direction. 
\end{itemize}

Recall that the action functional of the eleven-dimensional theory is $S_{BF, \infty} + g J$. 
Since the cubic and higher interactions only involve holomorphic derivatives, we obtain the following directly from the main result of \cite{GRWthf}.

\begin{thm}
There exists a gauge fixing condition for the eleven-dimensional theory on $\CC^5 \times \RR$ which renders its one-loop quantization finite and anomaly-free. 
\end{thm}

When $g=0$, this result is actually exact,
since there are no Feynman diagrams present past one-loop order in this case. 
When $g \ne 0$, on the other hand, this result does not immediately imply the existence of a gauge-invariant perturbative quantization to higher orders in $\hbar$. 
The presence of the functional $J = \frac16 \int \gamma \del \gamma \del \gamma$ allows one to construct Feynman graphs at arbitrary loop order.

%see \S \ref{s:omega},
In \cite{CostelloM5}, Costello argues that, upon performing the $\Omega$-background, the theory localizes to a five-dimensional theory on $\CC^2 \times \RR$. 
Via a cohomological argument, it is shown that this effective five-dimensional theory exhibits an essentially unique quantization in perturbation theory. 
We will return to the existence and uniqueness of a higher order quantization of the eleven-dimensional theory (before turning on the $\Omega$-background) in future work.

%\section{Twisted matrix model}
\section{Infinite-dimensional symmetry in flat backgrounds}
\label{s:E(5,10)}

\subsection{Global symmetry algebra}
\label{sec:global}

In any field theory, the cohomology classes of states of odd ghost number have the structure of a Lie algebra. 
More generally, after shifting the cohomological degree by one, the full cohomology of states with respect to the linear BRST operator is naturally a graded Lie algebra. 
If we forget the grading to a $\ZZ/2$ grading, then this global symmetry algebra has the structure of a super Lie algebra.

In general, taking cohomology loses information. 
If the dg Lie (or $L_\infty$) algebra we start with is not formal, then there exist higher-order operations on the linearized BRST cohomology. 
We will refer to this $L_\infty$ algebra as the global symmetry algebra of the theory.

Before taking cohomology with respect to the linear BRST operator, we described the super $L_\infty$ structure on the parity shift of the eleven-dimensional fields in the previous section. 
This is encoded by the full BV action of the eleven-dimensional theory.
The cubic component of the full BV action induces the super Lie algebra structure present in the linearized BRST cohomology.

Our main result is to relate the global symmetry algebra of the minimal twist of eleven-dimensional supergravity on $\CC^5 \times \RR$ to a certain infinite-dimensional exceptional super Lie algebra studied by Kac \cite{KacBible,KacE510} called $E(5,10)$.
We recall the definition below.

\begin{thm}\label{thm:global}
Let $\Pi\cE(\CC^5 \times \RR)$ be the parity shift of the fields of eleven-dimensional supergravity on $\CC^5 \times \RR$ and denote by $\delta^{(1)}$ the linearized BRST operator. 
\begin{enumerate}
\item 
As a super Lie algebra, the $\delta^{(1)}$-cohomology of $\Pi\cE(\CC^5 \times \RR)$ is isomorphic to the trivial one-dimensional central extension of the super Lie algebra $E(5,10)$.
\item 
The global symmetry algebra is equivalent, as a super $L_\infty$ algebra, to the non-trivial central extension of $E(5,10)$ determined by the even cocycle defined in~\eqref{eqn:cocycle}. 
\end{enumerate}
\end{thm}

This result implies that the action functional $S_{BF, \infty} + J$ of the eleven-dimensional theory is invariant for the infinite-dimensional Lie algebra $E(5,10)$.

%defined by the even cocycle
%\begin{align*}
%E(5,10) \times E(5,10) \times E(5,10) & \to \CC \\
%(\mu,\mu',\alpha) & \mapsto \<\mu \wedge \mu', \alpha\>|_{z=0} .
%\end{align*}

%The parity of the functional in the theorem is odd, but it is also trilinear. 
%Thus, as a cocycle in the Chevalley--Eilenberg complex of $E(5,10)$ it is of total even parity.

%The super Lie algebra $E(5,10)$ is very closely related to the super Lie algebra $E(5,10)$ studied by Kac; there is a dense embedding of super Lie algebras $E(5,10) \hookrightarrow E(5,10)$.

\subsection{Linearized BRST cohomology}

We compute the linearized BRST cohomology of eleven-dimensional supergravity.
Then we will describe the induced structure of a super Lie algebra present in the parity shift of the cohomology, proving part (1) of Theorem~\ref{thm:global}.

\parsec[]

First we recall the definition of the exceptional simple super Lie algebra $E(5,10)$. 
Recall that $\Vect_0 (\CC^5)$ is the Lie algebra of divergence-free holomorphic vector fields on $\CC^5$.
Let $\Omega^{2}_{cl} (\CC^5)$ be the module of holomorphic $2$-forms that are closed for the holomorphic de Rham operator $\del$.

The even part of the super Lie algebra $E(5,10)$ is the Lie algebra
\[
E(5,10)_+ = \Vect_0(\CC^5)
\]
of divergence-free vector fields on $\CC^5$,
whose elements we continue to denote by $\mu$. 
The odd piece is the module 
\[
E(5,10)_- = \Omega^{2}_{cl} (\CC^5),
\]
whose elements we denote by $\alpha$. 
Besides the natural module structure, there is odd bracket $ E(5,10)_-\otimes E(5,10)_\to E(5,10)_+$
The bracket uses the isomorphism $\Omega^{-1} \vee (-) \colon \Omega^{4} \cong \Vect (\CC^5)$ induced by the standard Calabi--Yau form $\d^5 z$, and is defined by
\beqn\label{eqn:e510}
[\alpha, \alpha'] = \Omega^{-1} \vee (\alpha \wedge \alpha') .
\eeqn
Since both $\alpha, \alpha'$ are closed two-forms,  the resulting vector field on the right hand side is divergence free. 
In coordinates, if $f^{ij} \d z_i \wedge \d z_j$ and $g^{kl} \d z_k \wedge \d z_l$ are two closed two-forms, their bracket is the vector field $\ep_{ijklm} f^{ij}g^{kl} \partial_{z_m}$.

To be precise, Kac studied a more algebraic version of the algebra we have just introduced, where holomorphic functions are replaced by holomorphic polynomials.
As such, the simple super Lie algebra that appears in the classification in~\cite{KacBible} is a dense sub Lie algebra of what we call $E(5,10)$, consisting of those vector fields and two-forms that have polynomial coefficients.

\parsec[]

If $\cE$ is the space of fields of any theory in the BV or BRST formalism, the shift $\cL = \cE[-1]$ has the structure of a Lie, possibly $L_\infty$ algebra. 
In the $\ZZ/2$ graded world, the parity shifted object $\cL = \Pi \cE$ has the structure of a super $L_\infty$ algebra.

In this section, we use the description of the eleven-dimensional theory as the deformation of the BF action $S_{BF,\infty}$ by the functional $J$ of Theorem \ref{thm:dfn}. 
We set the coupling $g = 1$. For any other nonzero value of $g$, we will obtain an isomorphic super $L_\infty$ algebra as explained above.
We would also obtain equivalent  results if we used the other model of the eleven-dimensional theory explained in~\S\ref{s:altdfn}. 
%We remark on this below. %in~\S\ref{s:altglobal}.

The full differential on the cochain complex of observables of the theory is given by the BV bracket with the BV action. 
For us, this~is 
\[
\delta = \{S_{BF,\infty} + J, -\} .
\]
The linear BRST operator (dual to the differential on the cochain complex of fields) comes only from the quadratic summands in $S_{BF,\infty}$, and is of the form
\beqn\label{eqn:linearBRST}
\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma} .
\eeqn

To compute the cohomology with respect to $\delta^{(1)}$ we can use a spectral sequence, first taking the cohomology with respect to $\dbar + \d_{\RR}$ and then with respect to $\div$. 
By the $\dbar$ and de Rham Poincar\'e lemmas, the cohomology of the space of fields of the eleven-dimensional theory on $\CC^5 \times \RR$ with respect $\dbar + \d_{\RR}$ results in the cochain complex
\begin{equation}
  \label{eq:lin1} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + \\ \hline
    \Vect(\CC^5) \ar[r, "\div"] & \cO(\CC^5) \\ 
     \cO(\CC^5) \ar[r, "\del"] & \Omega^{1}(\CC^5).
\end{tikzcd}
\end{equation}
Recall that $\Vect(\CC^5), \cO(\CC^5)$, and $\Omega^1(\CC^5)$ denote the space of holomorphic vector fields, functions, and one-forms, respectively.

The cohomology with respect to the remaining linearized BRST operator consists of the space of triples $(\mu, [\gamma], b)$ where:
\begin{itemize}
\item $\mu$ is a divergence-free holomorphic vector field on $\CC^5$, which is constant along $\RR$
\[
\mu = \mu \otimes 1 \in \Pi \Vect_0(\CC^5) \otimes \Omega^0(\RR) .
\]
Note that $\mu$ is a ghost in the $\ZZ/2$ graded theory. 
\item $[\gamma]$ is an equivalence class of a holomorphic one-form modulo exact holomorphic one-forms along $\CC^5$, which are also constant along $\RR$
\[
[\gamma] = [\gamma] \otimes 1 \in \left(\Omega^{1}(\CC^5) / \d \cO(\CC^5) \right) \otimes \Omega^0(\RR) .
\]
\item A constant function $b \in \Pi \CC$ on $\CC^5 \times \RR$.
This is a $\beta$-type field in the eleven-dimensional theory, any constant function is closed for the de Rham differential. 
This element is also a ghost in the $\ZZ/2$-graded theory. 
\end{itemize}

\parsec[]

After parity shifting, we've identified the solutions to the linear equations of motion with triples
\[
(\mu, [\gamma], b) \in \Vect_0(\CC^5) \oplus \Pi \Omega^{1}(\CC^5) / \del \cO(\CC^5) \oplus \CC .
\]
The bracket induced by the cubic component of $S_{BF, \infty}$ in the classical BV action is the usual bracket on divergence-free vector fields together with the module structure on holomorphic one-forms by Lie derivative.
Notice that the Lie derivative commutes with the $\del$ operator, so this action descends to equivalence classes as above. 
The elements $b$ are central.

The final term in the BV action $J = \frac16\int \gamma \wedge \del \gamma \wedge \del \gamma$ induces the following Lie bracket on the solutions to the linearized equations of motion
\beqn\label{eqn:eqb}
\big[[\gamma], [\gamma'] \big] = \Omega^{-1} \vee (\del \gamma \wedge \del \gamma') \in \Vect_0(\CC^5) .
\eeqn
where $\Omega^{-1}$ denotes the section of $\PV^{5,hol}(\CC^5)$ which is inverse to the Calabi--Yau form $\Omega$ on $\CC^5$. 
Notice that this bracket is well-defined as it does not depend on the particular equivalence classes and that the resulting vector field is automatically divergence-free.

\parsec[]

Having described the linearized BRST cohomology as a super vector space, we turn to the proof of Theorem \ref{thm:global}.

\begin{proof}[Proof of Theorem \ref{thm:global}]
For the first part, we write down an explicit map between the cohomology computed above and the algebra $E(5,10)$.

The relationship of the $\mu$-elements in $E(5,10)$ and the eleven-dimensional theory is apparent.

Next, we need to relate the equivalence classes $[\gamma]$ with the closed two-forms $\alpha$ in $E(5,10)$. 
On flat space, any closed differential form is exact (this is a holomorphic version of the Poincar\'e lemma). 
In other words, there is an isomorphism
\[
\del \colon \Omega^1 (\CC^5) / \d \cO(\CC^5) \xto{\cong} \Omega^{2}_{cl}(\CC^5)
\]
induced by the holomorphic de Rham differential.
This gives the relationship between the equivalence class $[\gamma]$ in the eleven-dimensional theory and a closed two-form in $E(5,10)$ by $\alpha = \del \gamma$. 
It is clear from Equations \eqref{eqn:e510} and \eqref{eqn:eqb} that this assignment intertwines the Lie brackets in $E(5,10)$ and the twist of eleven-dimensional supergravity. 
This completes the proof of part (1).

For part (2), we first produce the following homotopy data:
\begin{equation}
\begin{tikzcd}
\arrow[loop left]{l}{K}(\Pi \cE , \delta^{(1)})\arrow[r, shift left, "q"] &(E(5,10) \oplus \CC_b \, , \, 0)\arrow[l, shift left, "i"] \: ,
\end{tikzcd}
\end{equation}

\begin{itemize}
\item On the $\nu$'s we take $K$ to be any operator $K \colon \cO \to \Vect$ such that $\div K \nu = \nu$. 
On the $\gamma$'s we take $K$ to be any operator $K \colon \Omega^1 \to \Omega^0$ which satisfies the homotopy relation
\beqn\label{eqn:htpy1}
\til{K} \del \gamma + \del K \gamma = \gamma
\eeqn
for some auxiliary operator $\til{K} \colon \Omega^2_{cl} \to \Omega^1$.

The precise form of each of these operators will not be needed.
The existence of such operators is guaranteed by the holomorphic Poincar\'e lemma.
The operator $K$ annihilates fields $\beta$ and $\mu$. 
\item 
The map $q$ is described as follows. 
First $q(\mu) = \mu - K \div (\mu)$.
Notice that $q(\mu)$ is automatically divergence-free.
Next, $q(\gamma) = \del \gamma$.
If $\beta$ is a holomorphic function, then $q(\beta) = \beta (z=0)$.
\item 
The map $i$ embeds $\mu$ and $b$ in the obvious way. On a closed two form $\alpha$, we have that $i(\alpha) = \til{K}\gamma$.
\end{itemize}

It is straightforward to check that this comprises well-defined homotopy data, the only nontrivial thing to check is the relation $\id - i \circ q = \delta^{(1)} K - K \delta^{(1)}$. 
Plugging in the field $\gamma$ we see that we must check that
\[
\gamma - \til{K} \del \gamma = \del K \gamma 
\]
which is precisely \eqref{eqn:htpy1}.

Given this homotopy data, we can compute the homotopy transferred $L_\infty$ structure on the linearized BRST cohomology. 
Since $\nu$ does not survive to cohomology and the fact that there are no nontrivial Lie brackets involving the field $\beta$, this transferred structure is easy to compute.

There is a single diagram which contributes to the transferred structure, it is given by
\begin{equation}
\begin{tikzpicture}
\begin{feynman}
%\vertex at (-2,0) {$\mu'_3 \ = $};
\vertex(a) at (-1,1) {$i(\mu)$};
\vertex(b) at (-1,0) {$i([\gamma])$};
\vertex(c) at (-1,-1) {$i(\mu')$};
\vertex(d) at (0,0.5);
\vertex(e) at (1,0);
\vertex(f) at (2,0) {$q$};
\diagram* {(a)--(d), (b)--(d), (d)--[edge label = $K$](e), (c)--(e), (f)--(e)};
\end{feynman}
\end{tikzpicture}
\end{equation}
together with a similar diagram with the $\mu$ and $\mu'$ flipped.

This diagram leads to a new $3$-ary bracket on $E(5,10) \oplus \CC_b$
\[
\big[\mu,\mu',[\gamma]\big]_3 = \varphi(\mu,\mu',[\gamma])
\]
where $\varphi \in \clie^\text{even} (E(5,10))$ is the even Lie algebra cocycle defined by the formula
\beqn
\begin{array}{rclr}
\varphi \colon E(5,10) \times E(5,10) \times E(5,10) & \to & \CC_b \\
\varphi(\mu,\mu',\alpha) & = & \<\mu \wedge \mu', \alpha\>|_{z=0} .
\label{eqn:cocycle}
\end{array}
\eeqn
Since $b$ is central, this cocycle defines a central extension of $E(5,10)$.
\end{proof}

\parsec[]
We briefly remark on Lie algebra cohomology for super Lie algebras.
The Lie algebra cohomology $\clie^{\bu,\bu}(\cL)$ of any super Lie algebra $\cL$ is graded by $\ZZ \times \ZZ/2$. 
The first grading is by the symmetric degree in the Chevalley--Eilenberg complex.
The second grading is the internal parity of the super Lie algebra $\cL$. 
The Chevalley--Eilenberg differential is degree $(1,+)$.

The cocycle $\varphi$ has homogenous bigrading $(3,-)$.
In the above discussion we forgot the bigrading to a totalized $\ZZ/2$ grading where 
\begin{align*}
\clie^\text{even} (\cL) & = \clie^{2\bu , +} (\cL) \oplus \clie^{2\bu+1, -}(\cL) \\
\clie^\text{odd} (\cL) & = \clie^{2\bu , -} (\cL) \oplus \clie^{2\bu+1, +}(\cL) .
\end{align*}
With this totalization, $\varphi$ is an even cocycle and hence determines a super $L_\infty$ central extension by the one-dimensional even vector space $\CC$.

%\parsec[s:altglobal]

\section{Residual supersymmetry} 
\label{sec:susy}

In this section we consider the minimal twist of eleven-dimensional supersymmetry explicitly. 
We compute the residual supersymmetry algebra given by taking the cohomology of the eleven-dimensional supersymmetry algebra with respect to the minimal twisting supercharge. 
In order for this to map to the gauge symmetries of the eleven-dimensional theory, it is necessary to consider an extension of the eleven-dimensional supersymmetry algebra corresponding to the M2 brane.
We will see how this extension is compatible, upon twisting by the minimal supercharge, with the central extension of $E(5,10)$ we found as the global symmetry algebra in the previous section.

\subsection{Supersymmetry in eleven dimensions}
\label{sec:11dsusy}

The (complexified) eleven-dimensional supertranslation algebra is a complex super Lie algebra of the form
\[
  \ft_{11d} = V \oplus \Pi S
\]
where $S$ is the (unique) spin representation and $V \cong \CC^{11}$ the complex vector representation, of~$\lie{so}(11, \CC)$. 
The bracket is the unique surjective $\lie{so}(11,\CC)$-equivariant map from the symmetric square of~$S$ to~$V$;
this decomposes into three irreducibles, 
\beqn\label{eqn:decomp}
  \Sym^2(S) \cong V \oplus \wedge^2 V \oplus \wedge^5 V.
\eeqn
Denote by $\Gamma_{\wedge^1}, \Gamma_{\wedge^2}, \Gamma_{\wedge^5}$ the projections onto each of the summands above. 
The bracket in $\ft_{11d}$ is defined using the first projection
\[
[\psi, \psi'] = \Gamma_{\wedge^1} (\psi, \psi') .
\]
The super Poincar\'{e} algebra is
\[
  \lie{siso}_{11d} = \lie{so}(11 , \CC) \ltimes \ft_{11d} .
\]
The $R$-symmetry is trivial in eleven-dimensional supersymmetry.

\subsection{Extensions of the supersymmetry algebra} 
\label{sec:m2brane}

Extensions of the supersymmetry algebra correspond to the existence of extended objects, such as branes, in the supergravity theory.
In eleven-dimensional supersymmetry, there are two such extensions corresponding to the M2 brane and the M5 brane.
We begin by describing a less standard dg Lie algebra model for the M2 brane algebra.
In the next section we will explain the relationship to other descriptions in terms of $L_\infty$ algebras \cite{Basu_2005,Bagger_2007,FSS}.

Our model for the M2 brane algebra is a dg Lie algebra extension of the super Poincar\'e algebra $\lie{siso}_{11d}$.

Introduce the cochain complex $\Omega^{\bu}(\RR^{11})$ of (complex valued) differential forms on $\RR^{11}$ equipped with the de Rham differential $\d$.
The M2 brane algebra arises as an extension of $\lie{siso}_{11d}$ by the cochain complex $\Omega^\bu(\RR^{11})[2]$ and is defined by a cocycle
\[
    c_{M2} \in \clie^{2,+} \left(\lie{siso}_{11d} \; ; \; \Omega^\bu (\RR^{11})[2]\right) .
\]
The formula is
  \[c_{M2} (\psi, \psi') = \Gamma_{\wedge^2}(\psi, \psi') \in \Omega^2(\RR^{11})\]
  where $\Gamma_{\wedge^2}$ is the projection onto $\wedge^2 V$, thought of as the space of constant coefficient two-forms, as in the decomposition \eqref{eqn:decomp}.

\begin{dfn}
The algebra $\m2$ is the $\ZZ \times \ZZ/2$-graded dg Lie algebra defined by the extension of $\lie{siso}_{11d}$ by the cocycle $c_{M2}$.  
\end{dfn}

Here, we are using a bigrading by $\ZZ \times \ZZ/2$. 
The super Poincar\'e algebra is concentrated in zero integer grading and carries its natural $\ZZ/2$ grading as a super Lie algebra.
The complex $\Omega^{\bu}(\RR^{11})[2]$ is concentrated in integer degrees $[-2,9]$ and has even parity.
The bracket in $\m2$ is bidegree $(0,+)$ and the differential is bidegree $(1,+)$.

\subsection{The minimal twist}
\label{sec:mintwist}

Fix a supercharge $Q \in S$ satisfying $Q^2 = 0$ that is in the lowest stratum of the nilpotence variety.
Such a supercharge has a six-dimensional image in the space of (complexified) translations on $\RR^{11}$ and defines the minimal twist of eleven-dimensional supersymmetry \cite{SWspinor}. 
We characterize the cohomology of the algebra $\m2$ with respect to this supercharge.

$Q$ defines a maximal isotropic subspace $L \subset V$. 
In turn, we will decompose the super Poincar\'e algebra into $\lie{sl}(L) = \lie{sl}(5)$ representations.
First, the defining and spinor representations decompose as
\deq{
  V = L \oplus L^\vee \oplus \CC_t, \qquad S = \wedge^\bu L.
}
In the expression for $S$, we are omitting factors of $\det(L)^{\frac12}$ for simplicity. 
Also, $\lie{so}(11, \CC)$ decomposes as
\[
\lie{sl}(L) \oplus \wedge^2 L \oplus \wedge^2 L^\vee \oplus L \oplus L^\vee \oplus \C .
\]
Furthermore, the spin representation can be identified with
\[
S = \wedge^\bu (L) = \CC \oplus L \oplus \wedge^2 L \oplus \wedge^3 L \oplus \wedge^4 L \oplus \wedge^5 L .
\]
The element $Q$ lives in the first summand.
Let 
\[
{\rm Stab}(Q) =  \lie{sl}(L) \oplus \wedge^2 L^\vee \oplus L^\vee \subset \lie{so}(11,\CC)
\]
 be the stabilizer of $Q$. 
This is a parabolic subalgebra whose Levi factor is $\lie{sl}(5)$.

\subsection{$Q$-cohomology of $\m2$}
\label{sec:m2branetwist}

Any element $Q \in S$ satisfying $Q^2 = 0$ determines a deformation of the dg Lie algebra $\m2$.
To deform $\d$ by $Q$ we must break the $\ZZ \times \ZZ/2$ bigrading.
The supercharge $Q$ is odd and of cohomological degree zero.
Recall, the original differential on $\m2$ is the de Rham differential $\d$ which just acts on the summand $\Omega^\bu(\R^{11})[2]$ and is even of cohomological degree $+1$.
Thus, only the totalized $\ZZ/2$ grading makes the differential $\d + [Q,-]$ homogenous.

\begin{dfn}
The $Q$-twist $\m2^Q$ of $\m2$ is the super dg Lie algebra whose differential is $\d + [Q,-]$.
The bracket is unchanged.
\end{dfn}

Let $Q$ be a minimal supercharge satisfying $Q^2 = 0$. We first determine $H^\bullet(\m2^q)$ as a super vector space.

\begin{lem}
As a $\ZZ/2$ graded space, the cohomology of the $Q$-twist $\m2^Q$ is
\beqn\label{eqn:susycoh}
L \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^2 L^\vee\right) \oplus \CC
\eeqn
whose elements we denote by $(v, m, \psi, c)$.
\end{lem}
\begin{proof}
The cohomology of the non-centrally extended algebra was computed in \cite{SWspinor}, we briefly recall the result. 
The element $Q$ only acts nontrivially on the summands $\wedge^4 L$ and $\wedge^5 L$ in $S$. 
The image of $\wedge^4 L \cong L^\vee$ trivializes the antiholomorphic translations while the image of $\wedge^5 L$ trivializes the time translation.
So, of the translations, only the holomorphic ones, which live in $L$, survive.
The map 
\[
[Q,-] \colon \lie{so}(11,\CC) \to S 
\] 
is the projection onto $\wedge^0 L \oplus \wedge^1 L \oplus \wedge^2 L$. 
The kernel of $[Q,-]$ is the stabilizer~${\rm Stab}(Q)$.

In summary, the space of odd translations which survive cohomology is $\wedge^3 L \cong \wedge^2 L^\vee$; two such elements bracket to a holomorphic translation by taking the wedge product to get an element of $\wedge^4 L^\vee \cong L$.
This completes the calculation of the cohomology. 
\end{proof}

The main result of this subsection is the following:
\begin{prop}\label{prop:susycoh}
The cohomology of the $Q$-twist $H^\bu(\m2^Q)$ has the following structures:
\begin{enumerate}
\item As a super Lie algebra, $H^\bu(\m2^Q)$ is the natural extension of ${\rm Stab}(Q)$ together with the bracket
\beqn\label{eqn:susy2bra}
[\psi, \psi']_2 = \psi \wedge \psi' \in \wedge^4 L^\vee \cong L_v \\
\eeqn
\item 
$\m2^Q$ is not formal as a super dg Lie algebra.
As a super $L_\infty$ algebra, the $Q$-twist is equivalent to \eqref{eqn:susycoh} with $2$-brackets described in (1) where we additionally introduce the $3$-ary bracket 
\beqn\label{eqn:susy3bra}
[v, v', \psi]_3 = 4 \<v \wedge v', \psi\> \in \CC_b .
\eeqn
\end{enumerate}
\end{prop}

It will be useful to list the formulas for the brackets in terms of coordinates. 
Let $\{z_i\}$ denote a basis for $L$, which we will also think of as a linear coordinate on $\CC^5$. 
Let $\{\partial_{z_i}\}$ be a dual basis for $L^\vee$, which we will also think of as translation invariant vector fields.
The $2$-ary bracket above is 
\[
[z_i \wedge z_j, z_k \wedge z_l]_2 = \ep_{ijklm} \partial_{z_m} 
\]
and the $3$-ary bracket is
\[
[\partial_{z_i}, \partial_{z_j}, z_{k} \wedge z_{\ell}]_3 = 4 (\delta^i_k \delta^j_\ell - \delta^i_\ell \delta^j_k) .
\]

\parsec[]

One way to prove the proposition above is to use homotopy transfer directly to $\m2^Q$, just as we did in the proof of Theorem \ref{thm:global} to deduce the form of the $3$-ary bracket. 
Instead, we will use the following minimal model for $\m2^Q$ to prove Proposition~\ref{prop:susycoh}.
This minimal model also has the advantage of being more directly related to the eleven-dimensional supergravity theory.

\begin{lem}
\label{lem:gmodel}
Let $\fg$ denote the following $\ZZ/2$ graded dg Lie algebra which as a cochain complex is
\[
H^\bu(\m2^Q) \oplus (L^\vee \xto{\id} \Pi L^\vee)  .
\]
Denote the elements of the second summand by $(\lambda, \til\lambda)$. 
The Lie structure extends the one on $H^\bu(\m2^Q)$ described in (1) of Proposition \ref{prop:susycoh} together with the brackets
\begin{align*}
[v,\lambda] & = \<v, \lambda\> \in \CC_b \\ 
[v,\psi] & = \<v, \psi\> \in \Pi L^\vee_{\Tilde{\lambda}}.
\end{align*}

There is an $L_\infty$ map 
\[
\fg \rightsquigarrow \m2^Q
\] 
which is a quasi-isomorphism of cochain complexes.  
\end{lem}
\begin{proof}
We embed $\fg$ into $\m2^Q$ in the following way: ${\rm Stab}(Q)$ and $L$ sit inside in the evident way.
The central element maps to $c \mapsto - 1 \in \Omega^0(\RR^{11})$.
The summand $L_\lambda$ is mapped to the linear functions in $\Omega^0(\RR^{11})$ and $\Pi L_{\Tilde{\lambda}}$ is sent to the constant coefficient one-forms in $\Pi \Omega^1(\RR^{11})$. 
It remains to define where $\psi \in \wedge^2 L$ is mapped.

Notice that, at least naively, $\psi \in \wedge^2 L$ is not $Q$-closed due to the presence of the central extension. 
To embed $\wedge^2 L$ we introduce the operator
\[
H \colon \Omega^2 (\RR^{11}) \to \Omega^1(\RR^{11}),
\]
which sends a two-form $\alpha$ to the one-form $H \alpha$ defined by the formula $(H \alpha) (x) = \int_0^x \alpha$
where we integrate over a straight line path from $0$ to $x$.

Notice that if $\alpha$ is $\d$-closed then $\d (H \alpha) = \alpha$. 
It follows that any element $\psi \in \wedge^2 L \subset S$ can be lifted to a closed element at the cochain level in $\m2^Q$ by the formula
\[
\Tilde{\psi} = \psi - H \Gamma_{\wedge^2} (Q, \psi) \in \Pi S \oplus \Pi \Omega^1 .
\]
Thus, sending $\psi \mapsto \Tilde{\psi}$ defines a cochain map $\fg \to \m2^Q$.

The Lie bracket $[\Tilde{\psi}, \Tilde{\psi}']$ agrees with $[\psi, \psi']$. 
On the other hand, in $\m2^Q$ there is the Lie bracket 
\[
[v,\Tilde{\psi}] = - L_v (H \Gamma_{\wedge^2} (Q, \psi)) = -\<v, \Gamma_{\wedge^2}(Q, \psi)\> - \d \<v, H \Gamma_{\wedge^2}(Q, \psi)\> .
\]
The first term agrees with the bracket $[v, \psi]_{\fg}$ in $\fg$. 
The other term is exact in $\m2^Q$ and can hence be corrected by the following bilinear  
\[
v \otimes \psi \mapsto \<v, H \Gamma_{\wedge^2} (Q,\psi) \> \in L_\lambda .
\] 
Together with the cochain map described above, this bilinear term prescribes the desired $L_\infty$ map.

\end{proof}

\parsec[]
We now proceed to the proof of proposition \ref{prop:susycoh}.

\begin{proof}[Proof of Proposition \ref{prop:susycoh}]
Using the model $\fg$, the first part of Proposition \ref{prop:susycoh} follows immediately. 
We deduce the second part using homotopy transfer.

Recall that we described the cohomology of $\m2^Q$ in \eqref{eqn:susycoh}.
Let $\delta$ denote the differential on $\fg$ which simply maps $\Pi L$ to $L$ by the identity map. 
We produce the homotopy data
\begin{equation}
\begin{tikzcd}
\arrow[loop left]{l}{K}(\fg , \delta)\arrow[r, shift left, "q"] &(H^\bu(\m2^Q) \, , \, 0)\arrow[l, shift left, "i"] \: ,
\end{tikzcd}
\end{equation}
as follows.
\begin{itemize}[leftmargin=\parindent]
\item The operator $K$ annihilates $H^\bu(\m2^Q)$ and is the identity map~$K \colon \Pi L_{\til \lambda} \to L_\lambda$. 
\item The map $q$ is the identity on $H^\bu(\m2^Q)$ and annihilates the summand~$L \to \Pi L$. 
\item The map $i$ embeds $H^\bu(\m2^Q)$ in the obvious way. 
\end{itemize}

It is immediate to verify this data prescribes valid homotopy data.
There is only a single term in the $L_\infty$ structure generated by homotopy transfer. 
It is determined by the following tree diagram
\begin{equation}
\begin{tikzpicture}
\begin{feynman}
%\vertex at (-2,0) {$\mu'_3 \ = $};
\vertex(a) at (-1,1) {$i(v)$};
\vertex(b) at (-1,0) {$i(\psi)$};
\vertex(c) at (-1,-1) {$i(v)$};
\vertex(d) at (0,0.5);
\vertex(e) at (1,0);
\vertex(f) at (2,0) {$q$};
\diagram* {(a)--(d), (b)--(d), (d)--[edge label = $K$](e), (c)--(e), (f)--(e)};
\end{feynman}
\end{tikzpicture}
\end{equation}
together with a similar diagram with the $v$ and $v'$ reversed. 
It is an immediate calculation to show that these trees recover the formula in (2) of Proposition \ref{prop:susycoh}.
\end{proof}

\subsection{Embedding supersymmetry into the eleven-dimensional theory} \label{s:residual}

Consider now the super $L_\infty$ algebra $\cL$ underlying the eleven-dimensional theory on $\CC^5 \times \RR$.

\begin{prop}
Endow the cohomology of $\m2^Q$ with the $L_\infty$ structure of Proposition \ref{prop:susycoh} and let $\cL(\CC^5 \times \RR)$ be the super $L_\infty$ algebra underlying eleven-dimensional supergravity on $\CC^5 \times \RR$. 
There is a map of super $L_\infty$ algebras 
\[
H^\bu(\m2^Q) \rightsquigarrow \cL (\CC^5 \times \RR)
\]
%where $\fg$ is the model for the $Q$-cohomology of the super Lie algebra $\m2$ from Proposition \ref{lem:gmodel}. 
In particular, the $Q$-twisted algebra $\m2^Q$ is a symmetry of eleven-dimensional theory on $\CC^5 \times \RR$. 
\end{prop}
\begin{proof}
Recall that the cohomology of $\m2^Q$ takes the following form
\beqn 
\begin{tikzcd}
\ul{even} & \ul{odd} & \ul{even} \\
 L^\vee & (\wedge^2 L^\vee)_2 & L \\
(\wedge^2 L^\vee)_1 & & \\
\lie{sl}(5) && \CC_b 
\end{tikzcd}
\eeqn
The lefthand column is ${\rm Stab}(Q)$. 
The subscripts are used to distinguish between the two copies of $\wedge^2 L^\vee$.

The $L_\infty$ map from the dg Lie model $\fg$ to the fields of the twisted eleven-dimensional supergravity theory has a linear piece $\Phi^{(1)}$ and a quadratic piece $\Phi^{(2)}$.
Define the linear map $\Phi^{(1)} \colon \fg \to \cL$ as follows:
\begin{align*}
 L^\vee & \mapsto 0 \\
 \wedge^2 L_1^\vee  & \mapsto 0 \\
z_i \wedge z_j \in \wedge^2 L^\vee_2 & \mapsto \frac12 (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0} (\CC^5) \hotimes \Omega^0 (\RR) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \PV^{1,0}(\CC^5) \hotimes \Omega^0(\RR) \\ \partial_{z_j} \in L & \mapsto
\partial_{z_i} \in \PV^{1,0} (\CC^5) \hotimes \Omega^0 (\RR^5) \\ %z_i \in %L_2 & \mapsto z_i \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
%z_i \in L_3 & \mapsto \d z_i \in \Omega^{1,0}(\CC^5) \hotimes \Omega^0 (\RR) \\
1 \in \CC_b & \mapsto 1 \in \Omega^{0,0}(\CC^5) \hotimes \Omega^0 (\RR) .
\end{align*}

It is immediate to check that this is a map of cochain complexes, since all elements in the image of this map lie in the kernel of the linearized BRST operator~\eqref{eqn:linearBRST}.

This map also preserves the bracket between odd elements in $\wedge^2 L_2^\vee$. 
In the cohomology of $\m2^Q$ we have the bracket
\[
[z_i\wedge z_j , z_k \wedge z_l] = \ep_{ijklm} \partial_{z_m}.
\]

On the other hand, the cubic term in the action $J = \frac16 \in \gamma \del \gamma \del \gamma$ induces a bracket on $\cL (\C^5\times \R)$ given by
\[
[\gamma, \gamma^\prime ] = (\del\gamma\wedge\del\gamma^\prime)\vee \Omega^{-1}.
\]
The map is easily seen to intertwine the two brackets.

This map does not preserve all of the brackets, however. 
Indeed, in the eleven-dimensional theory $\cL(\CC^5 \times \RR)$ there is the bracket 
\[
\left[\partial_{z_i}, z_j \d z_k - z_k \d z_j\right] = \delta^i_j \d z_k - \delta^i_k \d z_j 
\]
arising from the cubic term in $\frac12 \int \frac{1}{1-\nu} \mu^2 \del \gamma$. 
To remedy the failure for $\Phi^{(1)}$ to preserve the brackets, we introduce the odd bilinear map $\Phi^{(2)} \colon \fg \otimes \fg \to \Pi \cL$ defined by 
\beqn\label{eqn:phi2}
\Phi^{(2)} \left(\partial_{z_i} , z_j \wedge z_k\right) = \frac12 (\delta^i_j z_k - \delta^i_k z_j) .
\eeqn
Notice that the field on the right hand side is of type $\beta$.

The bilinear map $\Phi^{(2)}$ provides a homotopy trivialization for the failure for $\Phi^{(1)}$ to preserve the $2$-ary bracket: 
\[
[\Phi^{(1)} (\partial_{z_i}) , \Phi^{(1)}(z_j \wedge z_k)] = \del \Phi^{(2)}\left(\partial_{z_i} , z_j \wedge z_k\right).
\]
The lefthand side is $\frac12 (\delta_j^i \d z_k - \delta_k^i \d z_j)$ which is precisely the de Rham differential applied to \eqref{eqn:phi2}.

To define an $L_\infty$ morphism $\Phi^{(1)} + \Phi^{(2)}$ must satisfy additional higher relations. 
There is a single nontrivial cubic relation to verify:
\begin{multline} \label{eqn:cubicrln}
\Phi^{(1)}\left[\partial_{z_i}, \partial_{z_j}, z_k \wedge z_l\right]_3 = [\Phi^{(1)}(\partial_{z_i}), \Phi^{(1)}(\partial_{z_i}), \Phi^{(1)}(z_k \wedge z_l)]_3 \\ + [\del_{z_i}, \Phi^{(2)}(\partial_{z_j}, z_k \wedge z_l)] + [\del_{z_j}, \Phi^{(2)}(\del_{z_i}, z_k \wedge z_l)]
\end{multline}
where $[-]_3$ on the left hand side is the $3$-ary bracket defined in Proposition \ref{prop:susycoh} and $[-]_3$ on the right hand side is the $3$-ary bracket defined by the quartic part of the action $\frac12 \int \frac{1}{1-\nu} \mu^2 \vee \del \gamma$. 
The two terms in the second line of \eqref{eqn:cubicrln} cancel for symmetry reasons and the quartic term in the BV action induces precisely the correct $3$-ary bracket.

%$[\Phi^{(1)}(z_i \wedge z_j), \Phi^{(1)}(z_k \wedge z_l), \Phi^{(1)} (z_m \wedge z_n)]_3 = \Phi^{(2)} ([z_i \wedge z_j, z_k\wedge z_l)], z_m \wedge z_n) + $permutations, where $[-]_3$ is the $3$-ary bracket arising from the 
\end{proof}

\parsec[] From the previous proposition we can readily compare the super $L_\infty$ algebra $H^\bu(\m2^Q)$ with the global symmetry algebra of our theory.
\begin{cor}
There is a map of super $L_\infty$ algebras 
\[
H^\bu(\m2^Q)\to \Hat{E(5,10)},
\]
where $\Hat{E(5,10)}$ is a central extension of~$E(5,10)$ by the cocycle~\eqref{eqn:cocycle}.
\end{cor}
\begin{proof}
Because this map preserves differentials, it descends to a map in cohomology. 
We have already computed the cohomology of $\cL$ on $\CC^5 \times \RR$; it is the trivial one-dimensional central extension of $E (5,10)$. 
The Lie algebra structure present in the cohomology of $\m2^Q$ is described in part (1) of Proposition~\ref{prop:susycoh}. 
The map
\[
L \oplus {\rm Stab}(Q) \oplus \Pi \left(\wedge^3 L \right) \oplus \CC_b \to E (5,10) \oplus \CC_{b'}
\]
is defined by very similar formulas as above
\begin{align*}
 L^\vee_1 & \mapsto 0 \\
 \wedge^2 L^\vee_1 & \mapsto 0 \\
z_i \wedge z_j \in \wedge^2 L_2 & \mapsto \d z_i \wedge \d z_j \in \Omega^{2}_{cl} (\CC^5) \\
A_{ij} \in \lie{sl}(5) & \mapsto \sum_{ij} A_{ij} z_i \partial_{z_j} \in \Vect_0(\CC^5) \\ \partial_{z_i} \in L & \mapsto
\partial_{z_i} \in \Vect_0(\CC^5) \\
b \in \CC_b & \mapsto b \in \CC_{b'} .
\end{align*}

The relationship between the transferred $L_\infty$ structures can be described as follows. 
Recall that the linear BRST cohomology of the parity shift of the fields of the eleven-dimensional theory is equivalent to the super $L_\infty$ 
algebra $\Hat{E(5,10)}$.
Also, we described the $L_\infty$ structure present in the cohomology of $\m2^Q$ in part (2) of Proposition~\ref{prop:susycoh}. 
Each of these $L_\infty$ structure involved introducing a single new $3$-ary bracket, which are easily seen to be compatible. 
\end{proof}
\parsec[]

In this short section we compare to another description of the M2 brane algebra given as a one-dimensional $L_\infty$ central extension of the super Poincar\'e algebra.
Such central extensions were studied in~\cite{BHsusyII, SSS, FSS}, following~\cite{CDF}. 
In these references, the algebra $\m2$ is defined as an $L_\infty$  
central extension of $\lie{siso}_{11d}$.

Recall that given two spinors $\psi, \psi' \in S$ we can form the constant coefficient two-form $\Gamma_{\wedge^2} (\psi, \psi')$. 
Using this two-form we can define the following four-linear expression
\[
\mu_2 (\psi, \psi',v,v') = \<v \wedge v', \Gamma(\psi, \psi')\> .
\]
This expression is symmetric on the spinors and antisymmetric on the vectors, therefore it defines an element in $\clie^4(\lie{siso}_{11d})$. 
This expression defines a nontrivial class in $H^4(\lie{siso}_{11d})$ so defines a one dimensional central extension of $\lie{siso}_{11d}$ as a Lie 3-algebra. 
Instead of working with a one-dimensional central extension by $\CC[2]$, we work with a central extension by the resolution $\Omega^\bullet(\RR^{11})[2]$ determined by a cocycle $c_{M2}$, see \S \ref{sec:m2brane}. 
There is a quasi-isomorphism $\clie^\bu(\lie{siso}_{11d})\to \clie^\bu(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$ induced by the embedding of constant functions into the full de Rham complex.
The cocycles $\mu_2$ and $c_{M2}$ are cohomologous via a two-step zig-zag in the double complex $\clie^\bu(\lie{siso}_{11d}, \Omega^\bullet (\R^{11}))$.

\parsec[]
There is also a one-dimensional $L_\infty$ central extension of the M2 brane algebra corresponding to the M5 brane - in \cite{FSS} this extension is described by way of a nontrivial seven-cocycle on $\m2$ that is not a pullback of a cocycle on $\lie{siso}_{11d}$. The $Q$-twist of the M5 brane extension does not appear in the fields of the eleven-dimensional theory we study. The distinguished role of the M2 brane extension is analogous to that played by the F1 extension of twists of type II supergravities \cite{CLSugra}. In fact the dimensional reduction discussed in section \ref{sec:SU(4)twist} intertwines the two extensions.

The M5 brane extension however, does induce an interesting cocycle on the algebra of $\frac{1}{16}$-BPS operators on a single M5 brane. We leave computation of this induced cocycle to further work.

\section{The non-minimal twist}\label{s:nonmin}

We have provided numerous consistency checks that the eleven-dimensional theory defined on a manifold with $SU(5)$ holonomy is a twist of supergravity. 
We have referred to this theory as ``minimal,'' since it renders the minimal number of translations homotopically trivial, or (slightly improperly) as ``holomorphic.''
In this section we characterize the unique further twist of eleven-dimensional supergravity on flat space, as seen through the lens of the holomorphic theory.  
This further twist is invariant for the group $G_2 \times SU(2)$ and is fully topological along seven directions, as opposed to just a single direction as in the minimal twist. This is easiest to see by decomposing the eleven-dimensional spinor as a representation of $\Spin(4) \times \Spin(7)$; from this perspective, a square-zero element is a rank-one element in the tensor product of a chiral spin representation of~$\Spin(4)$ and the spin representation of~$\Spin(7)$. Elements of the latter fall into two distinct orbits under the $\Spin(7)$ action, the minimal orbit---``Cartan pure spinors''---and the generic orbit~\cite{Igusa}. The stabilizer of an element of the generic orbit is~$G_2$, almost by definition.

We will show that the non-minimal twist is equivalent to an interacting theory on $\CC^2 \times \RR^7$ that we call ``Poisson'' Chern--Simons theory, using a direct description of the further twist together with an indirect cohomological argument. This completes the confirmation of a conjecture in the literature~(\cite{CostelloM5}; see also~\cite{RY}); the result was checked at the level of the free theory in~\cite{EagerHahner} by computing the nonminimal twist of the eleven-dimensional multiplet directly at the component-field level.

In the BV formalism, the theory is $\ZZ/2$ graded, with fields given by
\[
A \in \Pi \Omega^{0,\bu}(\CC^2) \hotimes \Omega^\bu(\RR^7) ,
\]
where $\Pi$, as always, denotes parity shift.
The equations of motion are of the form
\[
\dbar A + \d_{\RR^7} A + \partial_{z_1} A \wedge \partial_{z_2} A = 0 .
\]
The action functional depends on the holomorphic symplectic structure on $\CC^2$ through the Poisson bracket on the algebra of holomorphic functions.
We give a precise definition below.

The main result of this section is the following.

\begin{thm}
\label{thm:nonmin}
The non-minimal twist of the eleven-dimensional theory is equivalent to Poisson Chern--Simons theory on 
\[
\CC^2 \times \RR^7 .
\]
\end{thm}

From the point of view of the untwisted theory, the non-minimal twist is defined by working in a background where the fermionic ghost in the physical theory is equal to a supertranslation of the form
\[
Q + Q_{nm} 
\]
where $Q$ is the supertranslation which defines the minimal twist, see \S \ref{sec:mintwist}.
The minimal twist of supergravity is obtained by setting a fermionic ghost equal to $Q$.

In the language of the minimal twist, the supercharge $Q_{nm}$ determines a square-zero element in the $Q$-cohomology of the original supersymmetry algebra (which we will denote by the same letter). 
The characterization of this cohomology in Proposition \ref{prop:susycoh} implies that $Q_{nm}$ is an element 
\[
Q_{nm} \in \wedge^2 \left(L^\vee\right)
\]
where $L \cong \CC^5$ is the defining $SU(5)$ representation. 
In other words, $Q$ is a translation invariant holomorphic two-form on $\CC^5$. 
The condition that $[Q_{nm}, Q_{nm}] = 0$ simply says that $Q_{nm}\wedge Q_{nm} = 0$ as a translation invariant four-form on $\CC^5$. 
By a linear change of coordinates, all such two-forms $Q$ are of the form $Q_{nm} = \d z_i \wedge \d z_j$ where $i,j=1,\ldots, 5$.

From hereon in this section we will rename coordinates by
\[
\CC^5 \times \RR = \CC^2_{z_i} \times \CC^3_{w_a} \times \RR
\]
which is most natural from the point of view of the non-minimal twist. 
We will fix the non-minimal supercharge 
\[
Q_{nm} = \d z_1 \wedge \d z_2 .
\]
Notice that this choice of supercharge breaks the holonomy of the eleven-dimensional theory from $SU(5)$ to $SU(2) \times SU(3)$.

\subsection{Index matching}
\label{sec:indexcheck}

As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and the nonminimal twist. We will find that the local character of the latter agrees with a specialization of the local character computed in~\S\ref{sec:locchar}

\begin{prop}
The  local character of the nonminimal twist of eleven-dimensional supergravity on flat space is given by
\[
\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
\] 
This agrees with the specializaiton of the local character computed in proposition \ref{prop:locchar}.
\end{prop}
\begin{proof}
The space of solutions to linearized equations of motion is parametrized by a holomorphic function $A$ on $\C^2_{w_j}$. The corresponding linear local operators are labeled by $(n_1,n_2)\in \Z^2_{\geq 0}$  and are given by 
\[
\boldsymbol{A}_{(n_1,n_2)} : A \mapsto \partial_{w_1}^{n_1}\partial_{w_2}^{n_2} A (0).
\]

The character of the linear span of these is given by the geometric series
\beqn\label{nonmin:singleparticle}
\sum _{(n_1,n_2)\in \Z^2_{\geq 0}} q^{-n_1+n_2}
\eeqn
with plethystic exponential given by 
\[
\prod _{(n_1,n_2)\in \Z^2_{\geq 0}} \frac{1}{1-q^{-n_1+n_2}}.
\]

For the last part, it suffices to observe the specialization at the level of single particle indices. A natural choice of fugacities for $SU(2)\times SU(3)$ is given in terms of the fugacities $q_i$ for $SU(5)$ chosen in~\S\ref{sec:locchar} by requiring the additional constraints \[q_1q_2 = 1, \ \ \ q_3q_4q_5=1.\]
After imposing the above constraints, the single particle index~\eqref{singleparticleindex} is
\[
i(q) = \frac{1}{(1-q)(1-q^{-1})}
\]
where $q = q_1=q_1^{-1}$. This is exactly the sum of the geometric series~\eqref{nonmin:singleparticle}.
\end{proof}

%Notice that changing the values of $i,j$ just has the affect of permuting the holomorphic copies of $\CC^2$ leftover in the further twist.

%The Lie algebra of gauge symmetries of this model on flat space is 
%\[
%\Omega^{0,\bu} (\CC_i \times \CC_j) \hotimes \Omega^\bu(\RR^7) 
%\]
%which is quasi-isomorphic to $\cO^{hol}(\CC^2)$ equipped with the Poisson bracket $\{-,-\}_{pb}$. 
%
%More generally, the twist can be defined \brian{finish}

\subsection{The non-minimal global symmetry algebra}

We constructed an embedding of the $Q$-cohomology of the supersymmetry algebra into the fields of our eleven-dimensional theory on $\CC^5 \times \RR$. 
The further twist is obtained by working in a background where a certain field on $\CC^5 \times \RR$ takes nonzero value $Q_{nm}$. 
Explicitly, the element $Q_{nm} \in \wedge^2 L$ corresponds to the image under $\del$ of a $\gamma$-field of type $\Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR)$. 
According to the embedding in \S \ref{s:residual} this is the $\gamma$-field 
\beqn\label{eqn:gammanm}
\gamma_{nm} = \frac12 (z_1 \d z_2 - z_2 \d z_1) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) 
\eeqn
Notice that $\del \gamma_{nm} = \d z_1 \wedge \d z_2$ as desired.

\parsec[sec:nmsymmetry]
Before proceeding to the proof of the theorem above, we perform a simple calculation of the global symmetry algebra present in the $Q_{nm}$-twisted theory.

Recall that up to a copy of constant functions, the global symmetry algebra of the holomorphic twist of the eleven-dimensional theory is the super Lie algebra $E(5,10)$.
From this point of view, the global symmetry algebra of the $Q_{nm}$-twisted theory is given by deformation of this super Lie algebra by the Maurer--Cartan element 
\[
\d z_1 \wedge \d z_2 \in \Omega^{2}_{cl}(\CC^5) .
\]
We recall that the space of closed two-forms on $\CC^5$ is precisely the odd part of the super Lie algebra $E(5,10)$.

We compute the cohomology of $E(5,10)$ with respect to the differential which is bracketing with this Maurer--Cartan element. 
Recall that we are using the holomorphic coordinates $(z_1,z_2,w_1,w_2,w_3)$ on $\CC^5$.

There are the following brackets in the super Lie algebra $E(5,10)$ 
\begin{align*}
[f_l \partial_{z_l} , \d z_1 \wedge \d z_2] & = \del f_i \wedge \d z_j - \del f_j \wedge \d z_i \\
[g_a \partial_{w_a} , \d z_1 \wedge \d z_2] & = 0 \\
[h^{ab} \d w_a \wedge \d w_b , \d z_1 \wedge \d z_2 ] & = \ep_{abc} h^{ab} \partial_{w_c} .
\end{align*}
where $f_l \partial_{z_l}$, $g_a \partial_{w_a}$ are divergence-free vector fields on $\CC^5$ and $h^{ab} \d w_a \wedge \d w_b$ is a closed two-form.

From these relations, we see that the following elements are in the kernel of $[\d z_1 \wedge \d z_2, -]$:
\begin{itemize}
\item $f(z_i, w_a)dz_1\wedge dz_2$ for $f$ a holomorphic function on $\CC^5$.
\item $f(z_i) \partial_{z_1} + g(z_i) \partial_{z_2}$ for holomorphic functions $f,g$ on $\CC_{z_1} \times \CC_{z_2}$ which satisfy 
\[
\del_{z_1} f + \del_{z_2} g = 0 .
\]
In other words, this is a divergence-free vector field on $\CC_{z_1} \times \CC_{z_2}$. 
\item $f_b(z_i, w_a) \partial_{w_b}$ for $f_b$ a holomorphic function on $\CC^5$ where $b=1,2,3$. 
\end{itemize}
It is immediate to check that these are the only nonzero elements in the kernel. 
Further, any element of the first type is clearly exact and any element of the last type is clearly exact by the closed two-form $\ep^{ijklm} f \d w_l \d w_m$.

Thus, the cohomology is the (purely bosonic) Lie algebra of divergence-free vector fields on $\CC^2 = \CC_i \times \CC_j$
\[
H^\bu\big(E(5,10), [\d z_1 \wedge \d z_2, -] \big) \simeq \Vect_0(\CC^2) .
\]

We proved in Theorem \ref{thm:global} that the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is equivalent to a central extension $\Hat{E(5,10)}$ of the super Lie algebra~$E(5,10)$.

The Lie algebra of divergence-free vector fields on $\CC^2$ also admits a central extension:
\beqn\label{eqn:centralvect}
0 \to \CC \to \cO (\CC^2) \to \Vect_0 (\CC^2) \to 0
\eeqn
where $\cO(\CC^2)$ is equipped with the Poisson bracket with respect to the symplectic form~$\d z_1 \wedge \d z_2$.
These two central extension are compatible.

%Thus, the Lie algebra of gauge symmetries of Poisson Chern--Simons theory on $\CC_i \times \CC_j \times \RR^7$ is a trivial one-dimensional central extension of the cohomology of $E(5,10)$.

\begin{prop}
\label{prop:ham}
Let $\Hat{E(5,10)}$ be the central extension of $E(5,10)$ which is equivalent to the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$. 
Then there is an isomorphism of Lie algebras 
\[
H^\bu \big(\Hat{E(5,10)} , [\d z_1 \wedge \d z_2, -] \big) \simeq \cO(\CC^2) .
\]
\end{prop}
\begin{proof}
The only thing to check is that, in cohomology, the cocycle defining the central extension of $E(5,10)$ is the cocycle exhibiting $\cO(\CC^2)$ as the central extension of divergence-free vector fields. 
Recall that the formula \eqref{eqn:cocycle} for the cocycle is 
\[
\varphi(\mu, \mu', \alpha) = \<\mu \wedge \mu', \alpha\>|_{z=0}.
\]

In cohomology, we obtain the cocycle for divergence-free vector fields by plugging in $\alpha = \d z_1 \wedge \d z_2$. 
This gives the cocycle on $\Vect_0(\CC^2)$ 
\[
(f_i \del_{z_i}, g_j \del_{z_j}) \mapsto (f_1 g_2 - f_2 g_1)(z_1=z_2=0) .
\]
This is the cocycle defining \eqref{eqn:centralvect}, as desired. 
\end{proof}.

This proposition implies that the global symmetry algebra of the non-minimal twist of eleven-dimensional supergravity is the Lie algebra $\cO(\CC^2)$. 
We will see that this is compatible with the calculation of the non-minimal twist of the full BV theory.

\subsection{The non-minimal twist of the eleven-dimensional theory}

Now, we turn to deducing the action functional of the non-minimal twist and hence the proof of Theorem \ref{thm:nonmin}. 
We will show that the eleven-dimensional theory on $\CC^5 \times \RR$ placed in the background where the $(1,0)$ component of $\gamma$ takes the value $\gamma_{nm}$ \eqref{eqn:gammanm} is equivalent to a theory with a purely Chern--Simons-like action functional that we referred to in the introduction to this section.

Poisson Chern--Simons theory is defined on any manifold of the form
\[
Z \times M
\]
where $Z$ is a hyper K\"ahler surface and $M$ is a smooth manifold of real dimension seven. 
The fundamental field of the theory is  
\[
\alpha \in \Pi \Omega^{0,\bu}(Z) \; \Hat{\otimes} \; \Omega^\bu(M)  .
\]
Just in our original eleven-dimensional theory, this theory is also only $\ZZ/2$ graded.

The holomorphic symplectic form $\omega_Z^{2,0}$ on $Z$ induces a Poisson bracket define on all Dolbeault forms $\Omega^{0,\bu}(Z)$ which we denote by $\{-,-\}_{pb}$. 
In local Darboux coordinates $(z_1,z_2)$, this bracket reads
\[
\{\alpha^I (z,\zbar) \d \zbar_I , \alpha'^J (z,\zbar) \d \zbar_J\}_{pb} = (\partial_{z_1} \alpha^I \partial_{z_2} \alpha^J \pm \partial_{z_2} \alpha^I \partial_{z_1} \alpha^J) \d \zbar_I \wedge \d \zbar_J . 
\]
The action functional of Poisson Chern--Simons theory is 
\beqn\label{eqn:pcsaction}
    \frac12 \int_{Z \times M} (\alpha \wedge \d\alpha) \wedge \omega^{2,0}_Z  + \frac16 \int_{Z\times M} \alpha \wedge \{\alpha, \alpha\}_{pb} \wedge \omega^{2,0}_Z
\eeqn
where $\{-,-\}$ is the Poisson bracket induced from the symplectic form $\omega_Z$ on $Z$.

For simplicity, we will work only on flat space $\CC^5 \times \RR = \CC^2_z \times (\CC^3_w \times \RR)$, where we view $Z = \CC^2_z$ as a hyper K\"ahler manifold with its standard holomorphic symplectic form $\omega^{2,0} = \d^2 z$.

We will decompose the fields according to these coordinates. 
\begin{proof}[Proof of Theorem \ref{thm:nonmin}]
Decompose the $\mu$-field as $\mu = \mu_z + \mu_w$ where
\begin{align*}
\mu_z  &\in \PV^{1,\bu}(\CC^2_z) \otimes \PV^{0,\bu}(\CC^3_w) \otimes \Omega^\bu(\RR) \\
\mu_w & \in \PV^{0,\bu}(\CC^2_z) \otimes \PV^{1,\bu}(\CC^3_w) \otimes \Omega^\bu(\RR)  .
\end{align*}
and similarly $\gamma = \gamma_z + \gamma_w$. 
We will also use the notation $\del^z$ for the holomorphic de Rham differential along $\CC_z^2$ and similarly $\del^w$ for the holomorphic de Rham differential along $\CC^3_w$.

To twist, we expand near the background where the field $\gamma_z$ takes value $\gamma_{nm}$ as in \eqref{eqn:gammanm}. 
This will generate new kinetic and interacting terms. 
%which we can extract by inserting a formal parameter $\delta$ and expressing the action functional in terms of the deformed field $\Tilde{\gamma} = \gamma + \delta \gamma^{1,0}$.

There are two types of interactions in the original theory.
The first is
\begin{equation}\label{eqn:int1}
  \frac12 \int_{\CC^2 \times \CC^3 \times \RR} \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\d^2 z \wedge \d^3 w)
\end{equation}
and the second is
\begin{equation} \label{eqn:int2}
  \frac16\int_{\CC^2 \times \CC^3 \times \RR} \gamma \partial \gamma \partial \gamma .
\end{equation}

%We can integrate Equation (\ref{eqn:int1}) by parts to put it in the form $\frac12 \int_{X \times Z \times L} \left[(\partial \gamma) \vee (\mu \wedge \mu) \right]$ where $\mu \wedge \mu$ is the wedge product of polvector fields.\brian{there might be some factors I'm being sloppy with here}
Expanding \eqref{eqn:int1} around the background where $\gamma$ takes value $\gamma_{nm}$, we obtain,
%\[
%  \frac12 \int \frac{1}{1-\nu} \left(\del \gamma \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_W) + \frac{\delta}{2} \int \frac{1}{1-\nu} \left(\omega_Z \vee \mu^2 \right) \wedge (\omega_Z \wedge \Omega_W) .
%\]
%Here, we have used the equation of motion $\partial \gamma^{1,0} = \Omega_Z$.
%It will be convenient to further expand this into the components $\mu_W, \mu_Y, \gamma_W, \gamma_Y$:
\begin{multline}
 \int \frac{1}{1-\nu} \left(\frac12 \del^w \gamma_w \vee \mu_w^2  + \del^z \gamma_w \vee \mu_w \mu_z + \del^w \gamma_z \vee \mu_w\mu_z + \frac12 \del^z \gamma_z \vee \mu_z^2 \right) \wedge (\d^2 z \wedge \d^3 w) 
 \\
  + \frac{1}{2} \int \frac{1}{1-\nu} \left(\d^2 z \vee \mu_z^2 \right) \wedge (\d^2 z \wedge \d^3 w) .
  \label{eqn:delta1}
\end{multline}

We similarly expand (\ref{eqn:int2}),
%\[
%  \frac16 \int \gamma \partial \gamma \partial \gamma + \frac{\delta}{2} \int \left(\gamma \partial \gamma\right) \wedge \omega_Z .
%\]
%Notice that there are no $\delta^2$ terms since $\partial \gamma^{1,0} \partial \gamma^{1,0} = 0$.
%Again, we further expand this into holomorphic components along $X,Z$:
\beqn
\frac16 \int \left(\gamma_w \partial^z \gamma_w \partial^z \gamma_w +\gamma_w \partial^w \gamma_w \partial^z \gamma_z +  \gamma_w \partial^w \gamma_z \partial^w \gamma_z \right) + \frac{1}{2} \int \left(\gamma_w \partial^w \gamma_w \right) \wedge \d^2 z
\label{eqn:delta2}
\eeqn

The new terms in the non-minimally twisted linearized BRST differential arise from the quadratic terms in the action in Equations \eqref{eqn:delta1} and \eqref{eqn:delta2}:
\begin{equation}\label{eqn:newterms}
  \frac{1}{2} \int (\d^2 z \vee \mu_z^2) \wedge (\d^2 z \wedge \d^3 w) + \frac{1}{2} \int \left(\gamma_w \wedge \partial^w \gamma_w \right) \wedge \d^2 z .
\end{equation}
The non-minimally twisted linear BRST complex thus takes the form
\beqn\label{eqn:twisteddiagram}
  \begin{tikzcd}
  & \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_W \ar[dr, "\div^z"] \ar[dashed, rounded corners, to path={ -- ([yshift=-2ex]\tikztostart.west) |- ([xshift=-1.5ex]\tikztotarget.west) -- (\tikztotarget)}, dddddr]\\
  & & \PV^{0,\bu}_Z \hotimes \PV^{0,\bu}_W \\
 & \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \ar[ur, "\div^w"'] & \\
\;_{\cong}  & & \Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_W \ar[ul, dashed, bend left = 10, "\Omega^{-1}_W \partial^w"]\\
 & \Omega^{0,\bu}_Z \hotimes \Omega^{0,\bu}_W \ar[ur, "\partial^w"] \ar[dr,"\partial^z"'] \\
  & & \Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_W
  %\ar[uuuuul, start anchor =  {[yshift = 0ex, xshift=0ex]}, end anchor = {[yshift=1.0ex, xshift=-5ex]}, bend left = 90, dotted] .
  \end{tikzcd}
\eeqn
Here, we write $Z = \CC^2_z$ and $X = \CC^3_w$ for notational simplicity.

Here, the dashed arrow along the outside of the diagram corresponds to the BV antibracket with the first term in (\ref{eqn:newterms}).
It is given by the isomorphism 
\[
\Omega^{1,\bu}_Z \hotimes \Omega^{0,\bu}_W \xto{\omega^{2,0}_Z \otimes \id} \PV^{1,\bu}_Z \hotimes \PV^{0,\bu}_W
\]
induced holomorphic symplectic form on $Z$. 
The other dashed arrow corresponds to the BV antibracket with the second term in (\ref{eqn:newterms}).
It is given by the composition
\[
\Omega^{0,\bu}_Z \hotimes \Omega^{1,\bu}_W \xto{\id \otimes \del^w} \Omega^{0,\bu}_Z \hotimes \Omega^{2,\bu}_W \xto{\id \otimes \Omega_W} \PV^{0,\bu}_Z \hotimes \PV^{1,\bu}_W
\]
given by applying the holomorphic de Rham operator along $X$ followed by contracting with the inverse holomorphic volume form along $X$. 
%\brian{introduce PCS}
%Explicitly, if $f,g$ are holomorphic functions on $\CC^2$ then
%\[
%\{f(z_1,z_2) , g(z_1,z_2)\}_{pb} = \partial_{z_i} f \partial_{z_j} g - \partial_{z_j} f \partial_{z_i} g .
%\]

We replace this linear BRST complex, up to quasi-isomorphism, with a smaller BRST complex. 
Consider the complex
\beqn\label{eqn:zw}
\Omega^{0,\bu}_Z \hotimes \Omega^{\bu,\bu}_W \hotimes \Omega^\bu_L = \oplus_{k =0}^3 \Omega^{0,\bu}_Z \hotimes \Omega^{k,\bu}_W \hotimes \Omega^\bu_L 
%[-k] 
\eeqn
which is equipped with the differential $\dbar^z + \dbar^w + \del^w + \d_{\RR}$. 
Write $\alpha = \alpha^0 + \cdots + \alpha^3$ for a field in this complex, using the decomposition on the right hand side. 
The full Poisson Chern--Simons action $S_{pCS}$ equips this complex with the structure of a dg Lie algebra.

Define the following non-linear map of BRST complexes from \eqref{eqn:zw} to the twisted theory \eqref{eqn:twisteddiagram}.
It is defined by the equations
\begin{multline}
\mu_z = (1-\til \alpha^3) (\del_{z_1} \wedge \del_{z_2}) \vee \del^z \alpha^0 , \quad \mu_w = (\del_{w_1} \wedge \del_{w_2} \wedge \del_{w_3}) \vee \alpha^2, \quad \nu = \til{\alpha}^3 \\
\beta = \alpha^0 , \quad \gamma_w = \alpha^1 , \quad \gamma_z = 0 .
\label{eqn:g2map}
\end{multline}
In the above equation we have introduced the notation $\til{\alpha}^3 = \Omega_X^{-1} \vee \alpha^3$. 
Notice the only non-linearity appears in the definition of $\mu_z$.

The restriction of the kinetic terms $\int \gamma (\dbar + \d_{\RR}) \mu + \beta (\dbar + \d_{\RR}) \nu$ along \eqref{eqn:g2map} is
\beqn\label{eqn:kin1}
\int \sum_{k=0}^3 \alpha^k (\dbar + \d_{\RR}) \alpha^{3-k} 
\eeqn
The restriction of the kinetic term $\int \beta \div \mu$ along \eqref{eqn:g2map} is
\beqn\label{eqn:kin2}
\int \alpha^0 \del^w \alpha^2 - \int \alpha^0 \del^z \alpha^0 \del^z \alpha^3 . 
\eeqn
Finally, the restriction of the kinetic term $\frac12 \int \gamma \del^w \gamma$ in \eqref{eqn:delta2} along \eqref{eqn:g2map} is 
\beqn\label{eqn:kin3} 
\int \frac12 \alpha^1 \del^w \alpha^1 . 
\eeqn
Together, \eqref{eqn:kin1}--\eqref{eqn:kin3} give the kinetic term in Poisson Chern--Simons theory.

The formulas above show that the linear terms in \eqref{eqn:g2map} define a map of linear BRST complexes.
Applying the apparent contracting homotopy, we see that this map is a quasi-isomorphism.
We will show that the full non-linear map intertwines the action functionals up to cohomologically exact terms, and hence defines an equivalence of BV theories.

We substitute the values for the fields in \eqref{eqn:g2map} into the original eleven-dimensional action. 
Notice that any terms involving $\gamma_z$ can be discarded. 
Restricting \eqref{eqn:delta1} along this map, we obtain the action functional
\beqn\label{eqn:rest1}
\frac12 \int \frac{1}{1-\til\alpha^3}  \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z + \int \alpha^2 \del^z \alpha^0 \del^z \alpha^1
+ \frac12 \int (1-\alpha^3) \del^z \alpha^0 \del^z \alpha^0 .
\eeqn
Here, $\til \alpha^2$ denotes the element of $\Omega^{0,\bu}_Z \hotimes \PV^{1,\bu}_W \hotimes \Omega^\bu_L$ corresponding to $\alpha^2$ determined by the Calabi--Yau form $\d^3 w$. 
Notice that the very last term is equivalent to the functional $-\frac12\int \alpha^3 \del^z \alpha^0 \del^z \alpha^0$ since the quadratic part is a total derivative.

There is only one cubic term left in \eqref{eqn:delta2} when we substitute the fields according to \eqref{eqn:g2map}.
It is
\beqn
\frac16 \int \alpha^1 \del^z \alpha^1 \del^z \alpha^1. 
\eeqn

Combining all of these terms, we see that the total action restricted along the map \eqref{eqn:g2map} is 
\beqn\label{eqn:pcs1}
S_{pCS} (\alpha) + \int \frac12 \frac{1}{1-\til\alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 \d^2 z
\eeqn
where $S_{pCS}$ is the Poisson Chern--Simons action in \eqref{eqn:pcsaction}.

We will show that the term not appearing in $S_{pCS}(\alpha)$ is cohomologically trivial. 
Consider the odd local functional
\beqn\label{eqn:triv1}
\frac16 \int \frac{1}{1 - \til \alpha^3} \alpha^2 (\til \alpha^2)^2 .
\eeqn
Applying the linearized BRST operator (in the non-minimal twist) this becomes 
\[
\frac12 \int \frac{1}{1 - \til \alpha^3} \del^w \alpha^1 (\til \alpha^2)^2 + \frac16 \int \frac{1}{1 - \til \alpha^3} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2 .
\]
The first term in this expression agrees the term in \eqref{eqn:pcs1} which is not in $S_{pCS}(\alpha)$.

The latter term $(1 - \til \alpha^3)^{-1} \del^w (\alpha^2) \alpha^2 (\til \alpha^2)^2$ is of polynomial degree $\geq 4$. 
Since this term has trivial self BV bracket, it determines a cocycle for the dg Lie algebra underlying Poisson Chern--Simons theory. 
Since it is manifestly translation invariant, it arises via descent from a cocycle in the dg Lie algebra of $\infty$-jets of fields at $0 \in\CC^2 \times \RR^7$.
This dg Lie algebra is quasi-isomorphic to the Lie algebra $\CC[[z_1,z_2]]$ equipped with the holomorphic Poisson bracket.
(This is the formal power series version of the Lie algebra from Proposition~\ref{prop:ham}.)

There is a weight grading on this Lie algebra, given by declaring $|z_1^{n+1} z_2^{m+1}| = n+m$; in turn, this induces a grading on the Gelfand--Fuks Lie algebra cohomology.  
The weight of the Gelfand--Fuks class corresponding to our deformation is $+2$, since no derivatives of $z_1$ or $z_2$ appear. 
Results from~\cite{Fuks} show that there is no cohomology in this weight. 
As such, the cocycle must define a trivial deformation of the dg Lie algebra up to equivalence.
This completes the proof that the non-minimal twist is equivalent to Poisson Chern--Simons theory. 
\end{proof}

\def\im{{\rm i}}

\section{Dimensional reduction and ten-dimensional supergravity}
\label{sec:dimred}

In this section we demonstrate that our proposal for the action of minimally twisted eleven-dimensional supergravity agrees with conjectural descriptions of twisted type IIA and type I supergravities due to Costello and Li.

The original motivation for M-theory was as the strong coupling limit for type IIA string theory.
Roughly, the radius of the M-theory circle plays the role of this coupling constant. 
Additionally, at low energies M-theory is expected to be approximated by eleven-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity. 
Combining these two pictures, various checks have been made that the dimensional reduction of eleven-dimensional supergravity along the M-theory circle is type IIA supergravity.

Motivated by the topological string, Costello and Li have laid out a series of conjectures for twists of type IIA/IIB supergravity \cite{CLsugra} and type I supergravity \cite{CLtypeI}. 
Their description was inspired by the model of the open and closed $B$-model topological string on a Calabi--Yau manifold. 
The open sector is holomorphic Chern--Simons theory \cite{WittenOpen} and the closed sector is called Kodaira--Spencer theory \cite{BCOV}. 
There are a few different versions of Kodaira--Spencer theory, but the shared characteristic is that they are all `gravitational' in nature; they describe fluctuations of the Calabi--Yau structure. 
From this point of view, Kodaira--Spencer theory is at the heart of the formulation of the various flavors of twisted ten-dimensional supergravity.

We begin by introducing certain variants of Kodaira--Spencer theory which will feature in the descriptions of twists of type IIA and type I supergravity.

\subsection{Kodaira--Spencer theory}
\label{s:BCOV}

Let $X$ be a Calabi--Yau manifold; for now it can be of arbitrary complex dimension $d$. 
Define
\deq{
  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
}
We will consider the graded space $\PV^{\bu,\bu}(X) = \oplus_{i,j} \PV^{i,j}(X)[-i-j]$ where the piece of type $(i,j)$ sits in degree $i+j$.

For each fixed $i$, while we let $j$ vary, the $\dbar$ operator defines a cochain complex $\PV^{i,\bu}(X) = (\oplus_j\PV^{i,j}(X) [-j], \dbar)$ which provides a resolution for the sheaf of holomorphic polyvector fields of type $i$. 
The divergence operator extends to an operator of the form
\[
\div \colon \PV^{i,\bu}(X) \to \PV^{i-1,\bu}(X) .
\]

Motivated by the states of the topological $B$-model, one defines the fields of Kodaira--Spencer gravity on $X$ to be the cochain complex
\beqn\label{eqn:ks1}
\left(\PV^{\bu,\bu} (X)[[u]] [2] \, , \, \dbar + u \div\right) .
\eeqn 
Here, $u$ is a parameter of cohomological degree $+2$, which turns $\delta_{KS}^{(1)} = \dbar + u \div$ into an operator of homogenous degree $+1$. 
We also have performed an overall cohomological shift by $2$ so that $u^k \PV^{i,j}$ sits in degree $i+j+2k-2$. 
More precisely, this is a model for the $S^1$-equivariant cohomology of the states of the $B$-model on a closed disk. 
We refer to \cite{CLtypeI, CLsugra} for detailed justification for this ansatz.

\parsec[s:poisson]
The original action for Kodaira--Spencer theory posited by \cite{BCOV} has a nonlocal kinetic term. In the BV formalism, this is codified by stipulating that the BV pairing is a degenerate odd Poisson tensor rather than an odd symplectic form. 
The Poisson kernel is given by the expression 
\[
(\div\otimes 1)\delta_{\Delta \subset X\times X} \in \left[\PV^{\bu,\bu}(X)\right]^{\hotimes 2} ,
\]
see \cite[{\S 1.4}]{CLbcov1}. 
Here, we view the $\delta$-distribution as a polyvector field using the Calabi--Yau form. 
Notice that the shifted Poisson tensor does not involve the parameter $u$ at all. 
For this reason, only the duals of a small number of fields pair nontrivially under the resulting odd BV bracket.

\parsec[s:ksaction]

There is a natural local interaction which equips the complex \eqref{eqn:ks1} with the structure of $\Z/2$ graded Poisson BV theory. Explicitly, it is given by 
\beqn
I_{BCOV}(\Sigma) = {\rm Tr}_X \, \langle \exp \Sigma\rangle_0 = \sum_{n\geq 0} {\rm Tr}_X \, \langle\Sigma^{\otimes n}\rangle_0
\eeqn
where ${\rm Tr}_X \, \Phi = \int_X (\Phi \vee \Omega) \wedge \Omega$ and where $\langle - \rangle_0$ denotes the genus zero Gromov-Witten invariant with marked points
\beqn
\langle u^{k_1}\mu_1 \otimes \cdots \otimes u^{k_m}\mu_m\rangle_0 := \left (\int _{\overline {\cM}_{0,m}} \psi_1^{k_1}\cdots \psi_m^{k_m}\right ) \mu_1\cdots \mu_m = \binom{m-3}{ k_1,\cdots, k_m}  \mu_1\cdots \mu_m.
\eeqn

This interaction is extremely natural from the point of view of string field theory. Indeed, the B-model localizes to the space of constant maps into $X$, which factors as a product of $\overline{\cM}_{0,m}\times X$. This is in keeping with finding an interaction that factors as an integral over $X$ times an integral over $\overline{\cM}_{0,m}$.

In \cite{BCOV} the authors show that the above interaction satisfies the classical master equation. Moreover, they show that the $L_\infty$ structure determined by the above action is equivalent to a natural dgla structure on the complex of fields with Lie bracket given by the Schouten bracket. Explicitly, the equivalence is given by the transcendental automorphism 
\[
\Sigma \mapsto [u(\exp (\Sigma/u)-1)]_+
\]
where $[-]_+$ denotes projection onto positive powers of $u$.

\parsec[s:minimalks]

We pointed out in \S\ref{s:poisson} that the majority of fields pair to zero under the Poisson tensor. Physically these correspond to closed string fields that do not propogate. In the supergravity approximation, the fields that survive are those closed string fields that propogate. In terms of our description of closed string field theory in terms of Kodaira--Spencer theory, this motivates us to consider the smallest cochain complex containing those fields thathave nonzero pairing under the Poisson tensor. This is referred to as minimal Kodaira--Spencer theory.

The fields of minimal Kodaira--Spencer theory are given by the subcomplex of \label{eqn:ks1}
\beqn
\left (\bigoplus_{i+j\leq d -1}u^i\PV^{j,\bu}(X)[2], \dbar + u \div\right).
\eeqn
We observe that the original odd Poisson tensor lives in this subcomplex. 
%here is a natural odd Poisson tensor on the above cochain complex such that the inclusion of this subcomplex into the fields of Kodaira--Spencer theory is a Poisson map. 
There is a natural action functional given by restricting $I_{BCOV}$ to this space.

\subsection{The $SU(4)$ twist of type IIA supergravity}\label{sec:SU(4)twist}

We recall the description of the $SU(4)$ twist of type IIA supergravity conjectured in \cite{CLsugra}. 
In principal, there is also a minimal, $SU(5)$ invariant, twist of type IIA supergravity but so far no description, even conjecturally, exists.
We turn to this in \S \ref{s:su5IIA}.

Let $X$ be a Calabi--Yau manifold of complex dimension four. 
The $\ZZ/2$ graded complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\beqn
\begin{tikzcd}
- & + & - & + \\ \hline
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Denote this complex by $\cE_{mKS}(X)$. 
Here, $u^\ell\PV^{k,i}$ is placed in parity $k + i -1 \mod 2$. 
%Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

With this in hand the conjecture of \cite{CLsugra} takes the following form.

\begin{conj}
The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields 
\beqn\label{eqn:IIAfields}
\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).
\eeqn
The classical interaction takes the form \[I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + \cdots\]
%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

We will need a more detailed description of the classical action. 
For the moment, let us introduce some notations for the fields of this IIA model. As always, we leave the internal Dolbeault degree implicit:
\begin{multline}
\eta \in \PV^{0,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2), \quad \mu + u \nu \in \PV^{1, \bu}(\CC^4) \otimes \Omega^\bu (\RR^2) \oplus u \PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) \\
\Pi \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2), \quad \sigma \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2) .
\end{multline}
We will not need an explicit notation for the remaining descendant fields.

With this notation in hand, we have the more precise form of the action appearing in the conjecture:
\beqn\label{eqn:IIAaction}
I_{IIA} = \frac12 {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \Pi + {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \sigma + \frac12 {\rm Tr}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \Pi^2 + \cdots 
\eeqn
where the $\cdots$ denotes terms involving higher-order descendants.

\subsection{Reduction to IIA supergravity}
\label{s:su4red}

We now turn back to our eleven-dimensional theory. 
The first goal is to compare the dimensional reduction of our eleven-dimensional theory on $\CC^5 \times \RR$
%where $X$ is a Calabi--Yau 4-fold 
with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times \CC^4$. 
Doing so will require a slight modification to the description of the $SU(4)$ twist of IIA supergravity recollected in \S \ref{sec:SU(4)twist}.

\parsec[sec:IIApot]

Recall that in the physical theory, the components of the $C$-field in eleven dimensions that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLsugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. 
We recalled in \S \ref{s:components} that components of the $C$-field become components of $\gamma_{11d}$ in $\cE$.
This suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

The fundamental fields of the $SU(4)$ twist of IIA supergravity were given in \eqref{eqn:IIAfields}. 
We modify the space of fields by introducing potentials for both the $\Pi$ and $\sigma$ fields. 
First, we introduce a field $\gamma \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ (not to be confused, yet, with the $\gamma$ field in our eleven-dimensional theory) which satisfies $\Pi \vee \Omega = \del \gamma$ where $\Omega$ is the Calabi--Yau form on $\CC^4$. 
This condition does not uniquely fix $\gamma$. 
There is a new linear gauge symmetry determined by $\gamma \to \gamma + \div \beta$ where $\beta$ is a ghost that we must also introduce. 
Similarly, we introduce a field $\theta \in \Omega^{0,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2)$ which satisfies $\sigma \vee \Omega = \del \theta$, there is no extra gauge symmetry present in this condition.\footnote{Using the Calabi--Yau form we have normalized the potential fields $\gamma, \beta,\theta$ to be written as differential forms instead of polyvector fields.}

In diagrammatic detail, the potential theory we are considering has underlying cochain complex of fields
\beqn\label{eqn:IIApot}
\begin{tikzcd}
- & + \\ \hline
& {\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) }_\eta  \\
{\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
u^{-1}{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\del"] & {\Omega^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
{\Omega^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
\end{tikzcd}
\eeqn.

The original space of fields of the twist of IIA supergravity on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
In other words, it did not define a theory in the conventional BV formalism. 
One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd nondegenerate pairing, thus equipping it with the structure of a theory in the conventional BV formalism.

The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \vee \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
\[
\int^\Omega_{\CC^4 \times \RR^2} \eta \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \vee \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \beta .
\]
This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$.

The type IIA action completely determines the action of this theory with potentials. 
One simply takes the \eqref{eqn:IIAaction} and replaces all appearances of $\Pi$ with $\div \gamma$ and all appearances of $\sigma$ with $\div \theta$. 
This yields the interaction of the potential theory
\beqn\label{eqn:IIAactionpot}
\til I_{IIA} = \frac12 \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\eta \wedge \mu) \vee \del \theta + \frac12 \int_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \del \gamma \wedge \del \gamma 
\eeqn
Notice that the terms involving higher descendants vanishes since these fields are set to zero in the potential theory.

%Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
%\beqn
%\begin{tikzcd}
%                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
%{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
%{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
%{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
%\end{tikzcd}.
%\eeqn
%This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation. Therefore, $I_{pot}$ determines an $L_{\infty}$ structure on $\cE_{pot}$, and hence one on $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$. In what follows, the $SU(4)$-invariant twist of IIA will refer to the BV theory $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.

\parsec[-]

We turn to the proof of the main result of this section that the dimensional reduction of our eleven-dimensional theory agrees with the twist of IIA supergravity just introduced.

We recall the notion of dimensional along a holomorphic direction following \cite{ESW}. 
Suppose that $V_\RR$ is a real vector space and denote by $V$ its complexification. 
We consider a field theory defined on $M \times V$, which is holomorphic along $V$ (in particular, this means that the theory is translation invariant along $V$).  
We consider the dimensional reduction along the projection 
\beqn\label{eqn:dimred}
M \times V \to M \times V_\RR
\eeqn
induced by ${\rm Re} \colon V \to V_\RR$.
Most relevant for us is the case when $V = \CC$ and $M$ is $\CC^4 \times \RR$, but the explicit form of the theory along $M$ is not important at the moment.

For illustrative purposes, let us first assume that $M$ is a point and that the space of fields is of the form $\Omega^{0,\bu}(V) \otimes W$ for $W$ some graded vector space. 
As properly formulated in \cite{ESW}, it is shown that the dimensional reduction along $V \to V_\RR$ is equivalent to the theory whose fields are $\Omega^\bu(V_\RR) \otimes W$. 
In other words, the dimensional reduction of the holomorphic theory on $V$ is a topological theory on $V_\RR$.

If we put $M$ back in, the result is similar. 
Suppose the original theory is of the form $\cE(M) \otimes \Omega^{0,\bu}(V) \otimes W$.
Then, the dimensional reduction along \eqref{eqn:dimred} is the theory whose space of fields is $\cE(M) \otimes \Omega^\bu(V_\RR) \otimes W$.

An explicit model for this reduction can be described as follows. 
Suppose $V \cong \CC^n$ and place the theory on $(\CC^\times)^{\times n} \subset \CC^n$. 
The dimensional reduction along $\CC^n \to \RR^n$ agrees with the compactification of the theory along $S^1 \times \cdots \times S^1$ where one throws away all nonzero winding modes around each circle.

\begin{prop}\label{prop:dimred}
The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is the dimensional reduction of the eleven-dimensional theory along  
\[
\CC^4 \times \CC \times \RR_t \to \CC^4 \times \RR_x \times \RR_t \cong \CC^4 \times \RR^2 .
\]
\end{prop}
\begin{proof}
Let us denote the holomorphic coordinate we are reducing along by $z_5 = x + \im y$. 
We first read off the dimensional reduction of each component field of the eleven-dimensional theory. 
Per the above discussion, this is obtained by taking all fields to be independent of $y$ and replacing $\d \zbar_5$ by $\d x$. 
To not confuse the notations of fields in ten and eleven dimensions, we use the notation $\alpha_{11d}$ to denote an eleven-dimensional field.

The reductions of the eleven-dimensional fields $\nu_{11d}, \beta_{11d}$ are easy to describe. 
Recall that 
\[
\nu_{11d} \in \PV^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR) .
\]
The reduction of this field is a ten-dimensional $\nu$ field
\[
\nu (z_i,x,t) = \nu_{11d} (z_i, x, y=0, t) |_{\d \zbar_5 = \d x}  .
\]
Similarly, the reduction of $\beta_{11d}$ is a ten-dimensional $\beta$ field
\[
\beta (z_i,x,t) = \beta_{11d} (z_i, x, y=0, t) |_{\d \zbar_5 = \d x}  .
\]

The reduction of the eleven-dimensional fields $\mu_{11d}$ and $\gamma_{11d}$ require a bit of massaging. 
We break the $SU(5)$ symmetry to $SU(4)$ to write
\[
\mu_{11d} = \mu^0_{11d} + \theta_{11d} \partial_{z_5} 
\]
where
\begin{align*}
\mu^0_{11d} & \in \PV^{1,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) \\
\theta_{11d} & \in \Omega^{0,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) .
\end{align*}
The dimensional reduction of $\mu^0_{11d}$ is a ten-dimensional $\mu$ field
\[
\mu(z_i,x,t) = \mu_{11d}^0 (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
\]
The dimensional reduction of $\theta_{11d}$ is a $\theta$ field
\[
\theta(z_i,x,t) = \theta_{11d} (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
\]

Finally, write the eleven-dimensional field $\gamma_{11d}$ as
\[
\gamma_{11d} = \gamma_{11d}^0 + \eta_{11d} \d z_5
\]
where
\begin{align*}
\gamma^0_{11d} & \in \Omega^{1,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) \\
\eta_{11d} & \in \PV^{0,\bu}(\CC^4) \otimes \Omega^{0,\bu}(\CC_{z_5}) \otimes \Omega^\bu(\RR_t) .
\end{align*}
The dimensional reduction of $\gamma^0_{11d}$ is a ten-dimensional $\gamma$ field
\[
\gamma(z_i,x,t) = \gamma_{11d}^0 (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
\]
The dimensional reduction of $\eta_{11d}$ is an $\eta$ field
\[
\eta(z_i,x,t) = \eta_{11d} (z_i, x,y=0,t)|_{\d \zbar_5 = \d x} .
\]

Next, we read off the dimensional reduction of the eleven-dimensional action. 
Let us first focus on the term present in BF theory which is
$\int^\Omega \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \vee \del \gamma_{11d}$.
Upon reduction, this becomes 
\beqn\label{eqn:bfred}
\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\theta \wedge \mu) \vee  \del \eta 
\eeqn

Next, consider the cubic term in the eleven-dimensional action $J = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
Upon reduction, this becomes 
\beqn\label{eqn:jred}
\int_{\CC^4 \times \RR^2} \eta \wedge \del \gamma \wedge \del \gamma .
\eeqn

The sum of the action functionals \eqref{eqn:bfred} and \eqref{eqn:jred} does not precisely agree with the IIA action $\til I_{IIA}$. 
To relate the two actions we must make the following field redefinition:
\[
\til \theta = \frac{1}{1-\nu} \theta, \quad \til \eta = (1- \nu) \eta, \quad \til \beta = \beta + \frac{1}{1-\nu} \eta \wedge \theta .
\]
Notice that this change of coordinates is compatible with the odd symplectic pairing on the fields. 
Under this field redefinition the total dimensionally reduced action can be written as
\begin{multline}
\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \vee \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til\eta \wedge \del \gamma \wedge \del \gamma + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} (\til\theta \wedge \mu) \vee  \del \left(\frac{1}{1-\nu} \til\eta\right) \\ + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \frac{1}{1-\nu} (\til \eta \wedge \til \theta) \div \mu  .
\end{multline}
The first line comes from plugging in the new fields into the interactions \eqref{eqn:bfred} and \eqref{eqn:jred}.
The second line comes from plugging in the new fields into the kinetic term $\int \beta \div \mu$, which because of the non-linear change of coordinates now contributes to the interaction. 
We observe that the first two terms agree with the first and third terms in \eqref{eqn:IIAactionpot}.

After integrating by parts, the remaining terms can be written as 
\[
- \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right) \div (\til\theta \mu) + \int_{\CC^4 \times \RR^2}^{\Omega_{\CC^4}} \left(\frac{1}{1-\nu} \til \eta\right) \til \theta \div \mu .
\]
Applying the identity $\div (\til \theta \mu) = \til \theta \div \mu + \del (\til \theta) \vee \mu$, we see that this agrees exactly with the second term in \eqref{eqn:IIAactionpot}.
% but they are still not quite the same. 
%They are, however, cohomologous. 
%Integrating by parts and applying the BV relation, we can write the second line as
%\[
%\int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \left(\frac{1}{1-\nu} \til\eta\right)\wedge \div (\til\theta \wedge \mu)  = \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} (\til\eta \wedge \mu) \vee \partial \til \theta + \int^{\Omega_{\CC^4}}_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \til \eta \wedge \div \mu \wedge \til \theta .
%\]
%The first term in this equation agrees precisely with the second term in \eqref{eqn:IIAactionpot}. 
%The final term is cohomologically trivial via the odd Lagrangian $\int^\Omega \log(1-\nu) \wedge \til \eta \wedge \til \theta$.
%
%Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$. Note that there is an isomorphism \[\int: \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] It is clear that this isomorphism presrves the BV pairings; we need only check that $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.
%
%We readily compute:
%\[\int^{*}I = \]
\end{proof}

\subsection{The twist of type I supergravity}

We now turn to a different type of redution of the eleven-dimensional theory, this time involving type I supergravity. 
We begin by briefly recalling the description of type I supergravity following \cite{CLtypeI} which was motivated by the unoriented $B$-model. 
In \cite{SWspinor}, the second two authors verified the conjectural description of the space of fields recalled below using the pure spinor formalism. 
Unlike type IIA supergravity, there only exists an $SU(5)$ invariant twist of type I supergravity and it is holomorphic in the maximal number of dimensions.

Concretely, the space of fields of the $SU(5)$ twist of type I supergravity is a subspace of minimal Kodaira--Spencer theory on $\CC^5$. 
The $\ZZ/2$ graded space of fields equipped with its linear BRST operator is 
\beqn\label{eqn:IIApot}
\begin{tikzcd}
- & + & - & +  \\[-1.7em] \hline
{\PV^{1,\bu}}(\CC^5) \arrow[r, "u\div"]    & {u\PV^{0,\bu}}(\CC^5) \\
{\PV^{3,\bu}} (\CC^5)\arrow[r, "u\div"] & {u\PV^{2,\bu}} (\CC^5)\arrow[r, "u\div"] & {u^2\PV^{1,\bu}}(\CC^5) \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}(\CC^5)
\end{tikzcd}.
\eeqn

Let us give a description of the classical action. 
Introduce notations for the fields of this type I model:
\beqn\label{eqn:Ifields}
\mu + u \nu \in \PV^{1, \bu}(\CC^5) \oplus u \PV^{0,\bu} (\CC^5), \quad \sigma \in \PV^{3,\bu}(\CC^5) .
\eeqn
We will not need an explicit notation for the remaining descendant fields.

\begin{conj}
The twist of type I supergravity on $\CC^5$ is the $\Z/2$-graded theory with fields $\mu+u\nu, \sigma$ as above and with classical action
\beqn\label{eqn:typeIaction}
I_{{\rm type\, I}} = {\rm Tr}_{\CC^5} \frac{1}{1-\nu} \mu^2 \vee \sigma + \cdots
\eeqn
where the $\cdots$ stands for terms involving the higher descendant fields. 
%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

\parsec[s:typeIpot]

Like in the type IIA discussion, there is a slight modification of the type I model above which is most directly related to eleven-dimensional supergravity.

This modification involves replacing the field $\sigma$ above by a potential $\til \gamma \in \Omega^{1,\bu}(\CC^5)$ which satisfies $\Omega \vee \sigma = \del \til \gamma$. 
This condition does not fix $\til \gamma$ uniquely, there is a gauge symmetry of the form $\til \gamma \to \til \gamma + \del \til \beta$.

In detail, this potential theory we are considering has underlying cochain complex of fields
\begin{equation}
  \label{eq:Ipot} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + & -\\ \hline
    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  \\
         & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} .
\end{tikzcd}
\end{equation} 
This space of fields is equipped with an odd nondegenerate pairing.
Like the eleven-dimensional theory, it is a classical BV theory in the $\ZZ/2$-graded sense.

The type I action \eqref{eqn:typeIaction} completely determines the action of this theory with potentials. 
One simply takes the action and replaces all appearances of $\sigma$ with $\Omega^{-1} \vee \del \til\gamma$. 
This yields the interaction of the potential theory
\beqn\label{eqn:Iactionpot}
\til I_{\text{type I}} = \frac12 \int^\Omega_{\CC^5} \frac{1}{1-\nu} \mu^2 \vee \del \til\gamma .
\eeqn
Notice that the terms involving higher descendants vanishes since these fields are set to zero in the potential theory.

\subsection{Slab compactification}\label{s:Ired}

We consider placing twisted eleven-dimensional supergravity on the manifold $\CC^5 \times [0,1]$. 
In order to do this, we must choose appropriate boundary conditions at $t=0$ and $t=1$.
Our eleven-dimensional theory on such manifolds fits nicely into the formalism of \cite{BY,Eugene} in that it is topological in the direction transverse to the boundary.

The phase space of the theory at $t=0$ or $t=1$ is 
\begin{equation}
  \label{eq:lin1} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + \\ \hline
    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu \\ 
     \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_\gamma.
\end{tikzcd}
\end{equation}
The wedge an integrate pairing between the top and bottom lines induces an {\em even} symplectic structure on the phase space. 
Denote this phase space by $\cE_{\del}$ for the moment.

The phase space is equipped with the restriction of the linear BRST operator of the full eleven-dimensional theory. 
There is also a non linear BRST operator, just like in the bulk theory.
The BV action induces a $L_\infty$ structure on the parity shift $\Pi\cE_{\del}$ whose cohomology is still a trivial central extension of $E(5,10)$.

A boundary condition is given by a Lagrangian subspace of $\cE_{\del}$ with respect to this even symplectic structure. 
To make sense of the theory on $\CC^5 \times [0,1]$ we must make the choice of two separate boundary conditions 
\[
\cM_{t=0} , \cM_{t=1} \subset \cE_{\del} .
\]
Moreover, these boundary conditions carry non linear BRST operators endowing their parity shifts $\Pi \cM_{t=0} , \Pi\cM_{t=1}$ with the structures of $L_\infty$ algebras. 
These $L_\infty$ structures must be compatible with the one on the phase space.
In fact, in our context these boundary conditions are abstractly isomorphic. 
We will explain the explicit boundary conditions momentarily.

An important thing to note is that the fields of the theory compactified on the slab is computed by the {\em derived} intersection of the two Lagrangians:
\[
\cM_{t=0} \overset{\LL}{\underset{\cE_{\del}}{\times}}\cM_{t=1}.
\]
To compute this derived intersection we must suitably resolve the boundary conditions.

\parsec[s:boundary]
At $t=0$, the boundary condition of the eleven-dimensional theory is determined by declaring 
\[
\cM_{t=0}: \quad \gamma|_{t=0} = \beta|_{t=0} = 0 .
\]
We will place the theory on $\CC^5 \times [0,1]$ by imposing the same boundary condition at $t=1$:
\[
\cM_{t=1}: \quad \gamma|_{t=1} = \beta|_{t=1} = 0 .
\]

\begin{prop}
With these boundary conditions for the classical eleven-dimensional theory on $\CC^5 \times [0,1]$, the dimensional reduction along 
\[
\CC^5 \times [0,1] \to \CC^5
\]
is equivalent to the twist of type I supergravity on $\CC^5$. 
\end{prop}
\begin{proof}
Notice that both $\cM_{t=0}$ and $\cM_{t=0}$ are abstractly isomorphic to the complex resolving divergence-free vector fields
\begin{equation}
  \label{eq:lin2} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + \\ \hline
    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  .
\end{tikzcd}
\end{equation}

To compute the derived intersection between the two Lagrangians at $t=0$ and $t=1$ we replace the Lagrangian morphism $\cM_{t=0} \hookrightarrow \cE_{\del}$. 
Consider the cochain complex $\til \cM_{t=0}$ defined by
\begin{equation}
  \label{eq:lin3} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + & - \\ \hline
    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu \\ 
     \Omega^{0,\bu}(\CC^5)_\beta \ar[dr,dotted,"\id"]\ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_\gamma \ar[dr,dotted,"\id"] \\
     & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} .
\end{tikzcd}
\end{equation}
Notice that as a graded vector space, this complex is of the form $\cE_{\del} \oplus (\Omega^{0,\bu} \oplus \Pi \Omega^{1,\bu})$. 
The $L_\infty$ structure on $\Pi \til \cM_{t=0}$ extends the one on $\cE_{\del}$ coming from the bulk BV action. 
Notice that the obvious embedding $\cM_{t=0} \hookrightarrow \til \cM_{t=0}$ is a quasi-isomorphism.

The projection map $\til \cM_{t=0} \twoheadrightarrow \cE_{\del}$ factors the original Lagrangian inclusion as
\[
\cM_{t=0} \hookrightarrow \til \cM_{t=0} \twoheadrightarrow \cE_{\del} .
\]
To compute the derived intersection of $\cM_{t=0}$ and $\cM_{t=1}$ we can compute the ordinary intersection of $\til \cM_{t=0}$ and $\cM_{t=1}$.

Let $\mu_{t=1}$ and $\nu_{t=1}$ denote the fields present in the other boundary condition $\cM_{t=1}$. 
The intersection $\til \cM_{t=0} \times_{\cE_{\del}} \cM_{t=1}$ is computed by setting the fields $\beta, \gamma$ to zero and $\mu=\mu_{t=1}$, $\nu = \nu_{t=1}$. 
Thus, we are left with
\begin{equation}
  \label{eq:lin3} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + & -\\ \hline
    \PV^{1,\bu}(\CC^5)_\mu \ar[r, "\div"] & \PV^{0,\bu}(\CC^5)_\nu  \\
         & \Omega^{0,\bu}(\CC^5)_{\til\beta} \ar[r, "\del"] & \Omega^{1,\bu}(\CC^5)_{\til\gamma} 
\end{tikzcd}
\end{equation}
This is precisely the underlying cochain complex of fields for the type I model with potentials. 
The odd nondegenerate pairing on this complex agrees with the one on this particular potential theory for the twist of type I supergravity. 
The $L_\infty$ structure on the parity shift of this complex is compatible with the one induced from the BV action in \eqref{eqn:Iactionpot}.
\end{proof}

\subsection{The $SU(5)$ twist of type IIA supergravity}
\label{s:su5IIA}

%\brian{Ingmar can you argue why this is the SU(5) twist on susy grounds?}

Thus, given that our eleven-dimensional theory correctly describes the $SU(5)$-invariant twist of supergravity on $\CC^5 \times \RR$, to obtain the $SU(5)$ twist of type IIA supergravity we should reduce along the topological $\RR$ direction. 
This results in a $SU(5)$ invariant, holomorphic, theory on $\CC^5$.

Let us briefly spell out the fields present in this dimensional reduction. 
The reduction is obtained by replacing $\Omega^\bu(\RR)$ with its translation invariant subalgebra $\CC[\ep] = \CC[\d t]$. 
Here, $\ep$ is an odd parameter playing the role of the translation invariant one-form $\d t \in \Omega^1(\RR)$. 
Equivalently, we are compactifying the theory along 
\[
\CC^5 \times S^1 \to \CC^5 .
\]

The field $\mu_{11d}$ is replaced by the field 
\[
\mu + \ep \mu' \in \Pi \PV^{1,\bu}(\CC^5) [\ep] .
\]
Notice that the lowest component of $\mu$ is odd (just like $\mu_{11d})$, but the lowest component of $\mu'$ is now even. 
Completely similarly, the remaining fields reduce as $\nu + \ep \nu'$, $\gamma + \ep \gamma'$, and $\beta + \ep \beta'$.

In summary, the linear complex of fields of the dimensionally reduced theory on $\CC^5$ is
\begin{equation}
  \label{eqn:IIAsu5} 
  \begin{tikzcd}[row sep = 1 ex]
    {\rm odd} & {\rm even} & {\rm even} & {\rm odd} \\ \hline
    \PV^{1,\bu}(\CC^5)_{\mu} \ar[r, "\del"] & \PV^{0,\bu}(\CC^5)_\nu & \\ 
     & \ep\Omega^{0,\bu}(\CC^5)_{\beta'} \ar[r, "\div"] & \ep\Omega^{1,\bu}(\CC^5)_{\gamma'} . \\
     &  \ep \PV^{1,\bu}(\CC^5)_{\mu'} \ar[r, "\div"] & \ep \PV^{0,\bu}(\CC^5)_{\nu'} \\
     & & \Omega^{0,\bu}(\CC^5)_\beta \ar[r, "\div"] & \Omega^{1,\bu}(\CC^5)_\gamma.
\end{tikzcd}
\end{equation}

We can compute the dimensional reduction of the eleven-dimensional action $S_{BF,\infty} + J$ in a similar way to how we have done in the past few sections. 
We arrive at the action functional described below.

\begin{conj}
\label{conj:IIAsu5}
The $SU(5)$ twist of type IIA supergravity on $\CC^5$ is equivalent to the theory whose linear BRST complex of fields is displayed in \eqref{eqn:IIAsu5}. 
The full action functional is 
\begin{multline}
\label{eqn:su5action}
\int^\Omega_{\CC^5}\bigg(\beta' \wedge \dbar \nu + \beta \wedge \dbar \nu' + \gamma' \wedge \dbar \mu + \gamma \wedge \dbar \mu' +  \beta' \wedge \div \mu + \beta \wedge \div \mu' \bigg) \\
+ \int^\Omega_{\CC^5} \bigg( \frac12 \frac{1}{1-\nu} \mu^2 \vee \del \gamma' +  \frac{1}{1-\nu} (\mu \wedge \mu') \vee \del \gamma' + \frac12 \frac{\nu'}{(1-\nu)^2} \mu^2 \vee \del \gamma \bigg) \\
+ \frac12 \int_{\CC^5} \gamma' \wedge \del \gamma \wedge \del \gamma .
\end{multline} 
\end{conj}

The first two lines in \eqref{eqn:su5action} arise from the reduction of the BF action $S_{BF,\infty}$. 
The final line arises from the reduction of $J = \frac16 \int \gamma_{11d} \del \gamma_{11d} \del \gamma_{11d}$.

%\parsec[]
%
%
%We obtain further evidence that this is the $SU(5)$ invariant twist of type IIA supergravity by checking that it has the expected residual supersymmetries. 
%The type IIA superstring algebra $\lie{string}_{IIA}$ is a central extension of the ten-dimensional $\cN=(1,1)$ super Poincar\'e algebra, for a definition we refer to \cite{BH,FSS}. 
%
%A minimal twisting supercharge $Q_{hol}$ in the $\cN=(1,1)$ super Poincar\'e algebra determines a maximal isotropic $L \subset \CC^{10}$. 
%In a completely analogous way to the calculation for the twist of the algebra $\m2$ or the $SU(4)$ twist of the as in \cite{CLsugra} one can prove the following. 
%
%\begin{prop}
%As an $\lie{sl}(5)$ representation the $Q_{hol}$-cohomology of $\lie{string}_{IIA}$ is equivalent
%\end{prop}

\parsec[]\label{s:orbifold}

The slab compactification of the previous section was one way to implement the $S^1 / \ZZ/2$ reduction of the eleven-dimensional theory. 
We offer another point of view of this $S^1 / \ZZ/2$ reduction.

First off, there is the following $\ZZ/2$ action on the eleven-dimensional theory on $\CC^5 \times S^1$ before compactifying. 
We obtain it by the following tensor product of $\ZZ/2$ actions. 
First, $\ZZ/2$ acts on $\Omega^\bu(S^1)$ by orientation reversing diffeomorphisms. 
Second, we declare that the eigenvalue of the $\ZZ/2$ action on $\PV^{k,\bu}(\CC^5)$, for $k=0,1$ is $+1$ and the eigenvalue of the $\ZZ/2$ action on $\Omega^{k,\bu}(\CC^5)$ for $k=0,1$ is $-1$. 
This determines a $\ZZ/2$ action on the full space of fields of the eleven-dimensional theory.

Upon $S^1$ compactification the $\ZZ/2$ action is easy to describe: $\mu,\nu$ both have eigenvalue $+1$, $\mu',\nu'$ both have eigenvalue $-1$, $\gamma,\beta$ both have eigenvalue $-1$, and $\gamma',\beta'$ both have eigenvalue $+1$. 
In particular, we see that the $\ZZ/2$ fixed points simply pick out the $\mu, \nu, \gamma', \beta'$ fields; this comprises the first two lines of \eqref{eqn:IIAsu5}.

The fields match precisely with the fields in the twist of type I supergravity that we recalled in \S \ref{s:typeIpot} (Under the relabeling $\gamma' \leftrightarrow \til \gamma, \beta' \leftrightarrow \til \beta$). 
Furthermore, restricting the action in the above conjecture agrees precisely with the action of this twisted type I model.

\subsection{Compactification along a CY3}\label{s:CY3}

In the first section we saw that the eleven-dimensional theory can be defined on any manifold that is a product of a Calabi--Yau five-fold with a smooth oriented one-manifold. 
In this section, we investigate an important compactification of the eleven-dimensional theory which involves the Calabi--Yau manifold $X \times \CC^2$ where $X$ is a simply connected compact Calabi--Yau three-fold.

The compactification of the theory along the three-fold $X$ 
\[
X \times \CC^2 \times \RR \to \CC^2 \times \RR
\]
yields an effective five-dimensional theory which is holomorphic along $\CC^2$ and topological along $\RR$. 
Upon compactification, we will find a match with a description of the twist of five-dimensional minimally supersymmetric supergravity.

\begin{prop}
\label{prop:5dsugra}
The compactification of the eleven-dimensional theory along a Calabi--Yau three-fold $X$ is equivalent to the twist of five-dimensional $\cN=1$ supergravity with $h^{1,1}(X)-1$ vector multiplets and $h^{1,2}(X) + 1$ hypermultiplets. 
\end{prop}

\parsec[s:5dsugra]

We give a conjectural capitulation of the twist of five-dimensional $\cN=1$ supergravity. 
Before twisting, a general five-dimensional $\cN=1$ supergravity contains a gravity multiplet coupled to some number of vector and hypermultiplets. 
The twist of the vector and hypermultiplet has been computed in \cite{ESW}, and we recall it below. 
The twist of the gravity multiplet is less clear. 
A thorough computation of the twist has yet to appear, though some checks have been established by Elliott and the last author in \cite{EWpoisson}. 
We give a description of the twist now, but leave a detailed computation from first principles to future work.

The gravity multiplet, see \cite{CCDF} for instance, consists of a graviton $e$, a gravitino $\psi$, and a one-form gauge field $\cA_{grav}$.
After twisting, the graviton and components of the gravitino decompose into two Dolbeault-de Rham valued fields 
\[
\alpha, \eta \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) ,
\]
whose lowest components both carry odd parity. 
The one-form gauge field $\cA_{grav}$ and the remaining components of the gravitino decompose into two more Dolbeault-de Rham valued fields
\[
A_{grav} , B_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) ,
\]
whose lowest components also both carry odd parity.

\begin{conj}
\label{conj:5dsugra}
The twist of five-dimensional supergravity (with nonzero Chern--Simons term) with vector multiplets valued in a Lie algebra $\fg$ and hypermultiplets valued in a representation $V$ has BV fields
\begin{itemize}
\item $\alpha, A_{grav} \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)$ with conjugate BV fields $\eta, B_{grav}$,
\item $A \in \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes \fg$ with conjugate BV field $B$,
\item $\chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \otimes V$ with conjugate BV field $\psi$.
\end{itemize}

The action is
\begin{multline}
\label{eqn:5daction} 
\int^\Omega_{\CC^2 \times \RR} \left(\eta \dbar \alpha + B_{grav} \dbar A_{grav} + B \dbar A + \psi \dbar \chi \right) \\
  + \int^\Omega_{\CC^2 \times \RR} \left( \frac12\eta \{\alpha, \alpha\} +  B_{grav} \{\alpha, A_{grav}\}+ B \{\alpha, A\} +  \psi \{\alpha, \chi \}\right) \\ 
+ \frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
\end{multline}
\end{conj}

%\brian{general background on susy. Why expect five-dimensional $\cN=1$ susy}

\parsec[-]

With this description of the twist of five-dimensional supergravity, we turn to the proof of Proposition \ref{prop:5dsugra}.

First, we set up some notation. 
Let $\Omega_X$ be the holomorphic volume form on $X$. 
To define the eleven-dimensional theory on $X \times \CC^2 \times \RR$ we use the Calabi--Yau form $\Omega_X \wedge \d z_1 \wedge \d z_2$, where $\{z_i\}$ is a holomorphic coordinate on $\CC^2$. 
Let $\omega \in \Omega^{1,1}(X)$ be a fixed K\"ahler form on $X$.
For any $k$, let $H^k(X, \Omega^k_X)_\perp$ denote the cohomology of the primitive elements.

\begin{proof}
Consider the eleven-dimensional field $\nu_{11d}$. 
Under the equivalence
\begin{align*}
\PV^{0,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq H^{\bu}(X, \cO) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & = \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Pi \Bar{\Omega}_X \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) 
\end{align*}
the $\nu_{11d}$ field decomposes as 
\[ 
\nu_{11d} = \nu + \Bar{\Omega}_X \til \nu .
\]
Here $\Bar{\Omega}_X$ is the complex conjugate to the holomorphic volume form on $X$. 
Notice that the zero form component of $\til \nu$ is a field with even parity.

Next, consider the eleven-dimensional field $\mu_{11d}$. 
Under the equivalence 
\begin{align*}
\Pi \PV^{1,\bu}(X \times \CC^2) \otimes \Omega^\bu(\RR) & \simeq \Pi H^{\bu}(X, \cO) \otimes \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus \Pi H^\bu(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & = \Pi \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Bar{\Omega}_X \PV^{1,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\ & \oplus H^{1}(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \oplus \Pi H^{2}(X, \T_X) \otimes \PV^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)
\end{align*}
the field $\mu_{11d}$ decomposes as 
\begin{align*}
\mu_{11d} & = \mu + \Bar{\Omega}_X \til \mu \\ 
& + e^i \chi_i + f^a A_a +  (\Omega_X^{-1} \vee \omega^2)A_{grav} .  
\end{align*} 
Here, $\{e^i\}_{i=1,\ldots, h^{2,1}}$ is a basis for $H^{1}(X, \T_X)$ and $\{f^a\}_{a=1,\ldots, h^{1,1}-1}$ is a basis for 
\[
H^2 (X, \Omega^2_X)_\perp \subset H^2(X, \Omega^2_X) \cong H^2(X, \T_X) . 
\]
Notice that the zero form part of $\til{\mu}$ is an even field, the zero form part of $\chi_i$ is an even field, the zero form part of $A_a$ is an odd field, and the zero form part of $\mu_\omega$ is an odd field.

The decomposition for the eleven-dimensional fields $\gamma_{11d}$ and $\beta_{11d}$ is similar. 
We record it here:
\begin{align*}
\beta_{11d} & = \beta + \Bar{\Omega}_X \til \beta \\ 
\gamma_{11d} & = \gamma + \Bar{\Omega}_X \til \gamma + e_i \psi^i + f_a B^a + \omega \wedge B_{grav}  . 
\end{align*}
Here, $\{e_i\}_{i=1,\ldots,h^{2,1}}$ is a basis for $H^2 (X, \Omega^1_X)$ dual to the basis $\{e^i\}$ under the Serre pairing.
Also, $\{f_a\}_{a=1,\ldots,h^{1,1}-1}$ is a basis for $H^{1}(X, \Omega^1_X)_\perp$ dual to the basis $\{f^a\}$.

To compare most directly to the description of the twist of five-dimensional $\cN=1$ supergravity we modestly modify the fields. 
Let $\del$ be the holomorphic de Rham differential along $\CC^2$. 
First, we introduce a potential for the fields $\mu$ and $\til \mu$. 
Let 
\[
\alpha, \chi \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR)
\]
be differential forms satisfying $\del \alpha = \mu \vee \Omega_{\CC^2}$ and $\del \chi = \til \mu \vee \Omega_{\CC^2}$. 
The fields $\nu, \til \nu$ are set to zero. 
Dually, we replace the fields $\gamma, \til \gamma$ their `field strengths', suitably renormalized with respect to the volume form
\[
\eta = (\d^2 z)^{-1} \vee \del \til \gamma , \quad \psi = (\d^2 z)^{-1} \vee \del \gamma \in \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) .
\]
The roles of $\beta, \til \beta$ were as gauge symmetries implementing $\gamma \to \gamma + \del \beta$ and $\til \gamma \to \til \gamma + \del \til \beta$. 
Since we are replacing $\gamma, \til \gamma$ by their images under the operator $\del$, these gauge symmetries are set to zero.

In summary, we are left with the following fields 
\[
\begin{array}{cccccccccc}
\alpha,A_{grav} & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & \eta, B_{grav} & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) \\
\chi, \chi_i & \in & \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR),  & \psi, \psi^i & \in & \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & i=1,\ldots, h^{2,1}  \\
A_a & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR), & B^a & \in & \Pi \Omega^{0,\bu}(\CC^2) \otimes \Omega^\bu(\RR) , & a = 1, \ldots, h^{1,1}-1.
\end{array}
\]

Let us plug these fields in to the eleven-dimensional action.
First, consider the BF term $\frac12 \int^{\Omega} \frac{1}{1-\nu_{11d}} \mu_{11d}^2 \gamma_{11d}$. 
With the field redefinitions above, this decomposes as
\begin{multline}\label{eqn:5dsugra1}
 \int_{\CC^2 \times \RR}^\Omega \left( \frac12 \del \alpha \wedge \del \alpha \wedge \eta + \del A_{grav} \wedge \del A_{grav} \wedge B_{grav} \right) \\
 + \int_{\CC^2 \times \RR}^\Omega \left( \del \alpha \wedge \del \chi \wedge \psi + \del \alpha \wedge \del \chi_i \wedge \psi^i + \del \alpha \wedge \del A_a \wedge B^a \right) .
\end{multline}
This term agrees with the second line in the five-dimensional action \eqref{eqn:5daction}.

Finally, consider the term in the eleven-dimensional action $J(\gamma_{11d}) = \frac16 \int \gamma_{11d} \wedge \del \gamma_{11d} \wedge \del \gamma_{11d}$. 
This induces the five-dimensional Chern--Simons term 
\beqn\label{eqn:5dsugra2}
\frac16 \int_{\CC^2 \times \RR} B_{grav} \del B_{grav} \del B_{grav} .
\eeqn
This completes the proof. 
\end{proof}

\parsec[s:5dglobal]

In \S \ref{sec:global} we computed the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ and found a close relationship to the exceptional super Lie algebra $E(5,10)$. 
In this section we deduce the form of the global symmetry algebra of the five-dimensional compactified theory on $\CC^2 \times \RR$.

Consider the full de Rham cohomology of $X$ by
\[
H^\bu (X, \Omega^\bu) = \oplus_{i,j} H^i (X, \Omega^j_X)  .
\]
This is a graded commutative algebra using the wedge product of differential forms. 
Next, consider the space of holomorphic functions $\cO(\CC^2)$ on $\CC^2$. 
The Poisson bracket $\{-,-,\}$ associated to the standard holomorphic symplectic structure on $\CC^2$ endows $\cO(\CC^2)$ with the structure of a Lie algebra. 
In particular, we can tensor $\cO(\CC^2)$ with $H^\bu (X, \Omega^\bu)$ to obtain the structure of a graded Lie algebra on 
\[
H^\bu (X, \Omega^\bu) \otimes \cO(\CC^2) .
\]
Let $[\omega] \in H^1(X, \Omega^1_X)$ be the class of the K\"ahler form on $X$.

The global symmetry algebra of the compactified theory along the Calabi--Yau three-fold $X$ is equivalent to a deformation of this graded Lie algebra. 
The deformation introduces the following Lie bracket 
\[
\big[ [\omega] \otimes f, [\omega] \otimes g\big] = [\omega^2] \otimes \{f,g\} \in H^{2,2}(X, \Omega^2) \otimes \cO(\CC^2) . 
\]

\section{Twisted supergravity on AdS space}
\label{sec:ads}

So far, we have mostly given evidence for the eleven-dimensional theory as a twist of supergravity in a flat background. 
We now turn to twisted versions of AdS backgrounds of eleven-dimensional supergravity.

In M-theory, AdS backgrounds arise from backreacting some number $N$ of branes. 
For M2 branes, the backreacted geometry is ${\rm AdS}_4 \times S^7$.
For the M5 branes, the backreacted geometry is ${\rm AdS}_7 \times S^4$.

According to the AdS/CFT correspondence, supergravity on such backgrounds should be dual to the relevant worldvolume theory in the large-$N$ limit. 
In this section, we do not directly refer to the worldvolume theories on the holomorphic twists of the M2 and M5 branes.
Rather, we identify the fields sourcing the branes at the level of the twisted eleven-dimensional theory.
In turn, we give a proposal for the twisted AdS background. 
We will show that the twist of the superconformal algebra is a global symmetry of this twisted background.

\subsection{Superconformal algebras}

The complex form of the algebra of isometries for supergravity in both the ${\rm AdS}_4$ and ${\rm AdS}_7$ backgrounds is $\lie{osp}(8|2)$ (though, their real forms differ). 
This agrees with the complex form of the 6d $\cN=(2,0)$ superconformal algebra and the 3d $\cN=8$ superconformal algebra. 
The bosonic part of this algebra is isomorphic to $\lie{so}(8) \oplus \lie{sp}(2) \cong \lie{so}(8) \oplus \lie{so}(5)$.

The minimal supercharge $Q$ acting on eleven-dimensional supersymmetry algebra is an element of this superconformal algebra. 
Its $Q$-cohomology is isomorphic to $\lie{osp}(6|1)$. (Twisted superconformal symmetry in six dimensions is studied in detail by the second  two authors  in~\cite{SWsuco2}.)
This super Lie algebra will play the role of the isometries in the twisted AdS background.

\subsection{The ${\rm AdS}_4 \times S^7$ background}

In this section we introduce the analog of the ${\rm AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of eleven-dimensional supergravity.

\parsec[]

Decompose the eleven-dimensional manifold $\CC^5 \times \RR$ as
\[
 \CC^4_w\times \CC_z \times \RR .
\]

Analogous to before, the ${\rm AdS}_4 \times S^7$ background arises from backreacting M2 branes. Consider a stack of $N$ M2 branes wrapping $\R\times \C_z$. A natural interaction to consider is 
\[
I_{M2}(\gamma) = N\int_{\C_z} \gamma + \cdots
\] 
which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$. Unlike the case of M5 branes, the coupling does not involve choosing a primitive for a field strength---it is an electric coupling.
We have only indicated the lowest order coupling, the $\cdots$ indicate higher-order couplings which will be higher order in the fields of the eleven-dimensional theory and explicitly involve the fields in the worldvolume theory.

This coupling is justified by comparison with the physical theory and by dimensional reduction. 
Indeed, as discussed in~\S\ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity. Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.

Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$. As is shown in \cite{CLsugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by 
\[
I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma + \cdots
\] 
where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA supergravity. It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.

\parsec[sec:m2backreact]

The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M2}(\gamma)$. 
Varying the deformed action with respect to $\gamma$,
we obtain the equation of motion
\beqn\label{eqn:ads4eom1}
\dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma = N \Omega^{-1} \delta_{w=0} .
\eeqn
Here $[-,-]$ is the Schouten bracket. 
Varying $\beta$, we obtain the equation of motion
\beqn\label{eqn:adseom2}
\div \mu = 0 .
\eeqn

\begin{lem}
Let
\[
 F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
\]
Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
satisfies the above equations of motion in the presence of a stack of $N$ M2 branes:
\begin{align*}
\dbar (N F_{M2}) + \frac12 [N F_{M2}, N F_{M2}] & = N \Omega^{-1} \delta_{w=0} \\
\div (N F_{M2}) & = 0  .
\end{align*}
Here we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

\begin{proof}
Upon specializing $\gamma = 0$, the last term in the first equation above vanishes. The equation $\dbar F_{M2} = \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
It is clear that $\div F_{M2} = 0$ and 
\[
[F_{M2}, F_{M2}] = 0
\] 
by simple type reasons. 
\end{proof}

\parsec[]

To provide evidence for the claim that this is the twisted analog of the AdS geometry, we will show that the twist of the symmetries present in the physical theory are witnessed in the twisted theory in this background.

We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
We will define an embedding of $\lie{osp}(6|1)$ into the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w=0\}$ which corresponds to the twist of the 3d superconformal algebra.
We first focus on the case where the flux $N=0$, for which the embedding can be extended to all of $\CC^5 \times \RR$.

\parsec[]

The bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra $\lie{sl}(4) \oplus \lie{sl}(2)$. 
The Lie algebra $\lie{sl}(2)$ represents (holomorphic) conformal transformations in $\CC_z$, which are inherited from the natural M\"obius group action on~$P^1(\C)$; the vector fields representing these transformations are not all divergence-free, and as such must be slightly adjusted. 
The Lie algebra $\lie{sl}(4)$ represents rotations along the plane $\CC^4_w$.

\begin{itemize}[leftmargin=\parindent]
\item The bosonic summand $\lie{sl}(2)$ is mapped to the vector fields:
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
Notice that these vector fields are divergence-free and reduce to the usual holomorphic conformal transformations along $w=0$.
\item The bosonic summand $\lie{sl}(4)$ is mapped to four-dimensional rotations: 
\[
\sum_{a,b=1}^4 B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad (B_{ab}) \in \lie{sl}(4) .
\]
\end{itemize}

The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
It is natural to split $R = \CC_{+1} \oplus \CC_{-1}$, so that the odd part decomposes as
\[
(\wedge^2 \CC^4)_{+1} \oplus (\wedge^2 \CC^4)_{-1} .
\]

\begin{itemize}[leftmargin=\parindent]
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ consists of the supertranslations. 
It is mapped to the fields: 
\[
\frac{1}{2} (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4 .
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ consists of the remaining superconformal transformations. 
It is mapped to the fields: 
\[
\frac{1}{2} z (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}

\begin{lem}\label{lem:m2emb}
These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the eleven-dimensional theory on $\CC^5 \times \RR$. 
Equivalently, it defines an embedding
\[
i_{M2} \colon \lie{osp}(6|1) \hookrightarrow E(5,10) .
\]
\end{lem} 
\begin{proof}
The second assertion follows from Theorem \ref{thm:global}, which shows that, as a super Lie algebra, the linearized BRST cohomology of the global symmetry algebra of the eleven-dimensional theory on $\CC^5 \times \RR$ is the trivial central extension of $E(5,10)$. 
Recall that the odd part of $E(5,10)$ is precisely the module of closed two-forms on $\CC^5$. 
To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
Recall, we are using the holomorphic coordinates $(z,w_1,\ldots,w_4)$ on $\CC^5$ where $z$ is the holomorphic coordinate along the M2 brane. 
\begin{itemize}[leftmargin=\parindent]
\item 
The fermionic summand $(\wedge^2 \CC^4)_{+1}$ embeds into closed two-forms as
\[
\d w_a \wedge \d w_b, \quad a,b=1,2,3,4. 
\] 
\item The fermionic summand $(\wedge^2 \CC^4)_{-1}$ embeds into closed two-forms as
\[
z \d w_a  \wedge \d w_b + \frac12 \d z \wedge (w_a \d w_b - w_b \d w_a) , \quad a,b=1,2,3,4. 
\] 
\end{itemize}
\end{proof}
\parsec[]

Next, we turn on $N \ne 0$ units of nontrivial flux. 
Since not all of the fields we wrote down above commute with the flux $N F_{M2}$, they are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w=0\}$. 
Nevertheless, we have the following.

\begin{prop}
\label{prop:brads4}
There exist $N$-dependent corrections to the fields defining the embedding of $\lie{osp}(6|1)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
Furthermore, these order $N$ corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of eleven-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N F_{M2},-]$.
\end{prop}

\begin{proof}
Let $\cL(\CC^5 \times \RR \setminus \{w=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the eleven-dimensional theory. 
We make the identification 
\[
(\CC^5 \times \RR) \setminus \{w=0\} \cong (\CC_w^4 \setminus 0) \times \CC_z \times \RR .
\]

Set $F = F_{M2}$ for notational convenience. Recall that we are viewing $F$ as an element of $\PV^{1,3}(\CC_w^4 \setminus 0) \otimes \Omega^{0,0}(\CC_z) \otimes \Omega^0(\RR)$. 
The operator $[F,-]$ acts on the fields according to two types of maps:
\begin{align*}
[F ,-] & \colon \PV^{i,\bu}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \PV^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \PV^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \\
[F,-] & \colon \Omega^{i,\bu}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR) \to \Omega^{i,\bu+3}(\CC^4_w \setminus 0) \otimes \Omega^{j,\bu} (\CC_z) \otimes \Omega^\bu (\RR).
\end{align*}

%\brian{get the filtration straight}

The first page of the spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$. 
Recall that the linearized BRST differential decomposes as
\[
\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma}  .
\]
To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
This first page of this auxiliary spectral sequence is simply given by the cohomology with respect to $\dbar + \d_{\RR}$. 
This cohomology is given by
\begin{equation}
  \label{eqn:ads4ss} 
  \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
H^\bu(\CC^4\setminus 0, \T) \otimes H^\bu(\CC, \cO) & H^\bu(\CC^4 \setminus 0, \cO) \otimes H^\bu(\CC, \cO) \\
H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \T) \\
H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \cO) & H^\bu(\CC^4\setminus 0, \cO) \otimes H^\bu(\CC, \Omega^1) \\ & H^\bu(\CC^4\setminus 0, \Omega^1) \otimes H^\bu(\CC, \cO)  
\end{tikzcd}
\end{equation}
where $\T$ denotes the holomorphic tangent sheaf, $\Omega^1$ denotes the sheaf of holomorphic one-forms, and $\cO$ is the sheaf of holomorphic functions.

The cohomology of $\CC$ is concentrated in degree zero and there is a dense embedding
\[
\CC[z] \hookrightarrow H^\bu(\CC, \cF) 
\]
for $\cF = \cO, \T$, or $\Omega^1$.

For $\cF = \cO, \T$, or $\Omega^1$, the cohomology $H^\bu(\CC^4 \setminus 0, \cF)$ is concentrated in degrees $0$ and $3$. 
There are the following dense embeddings 
\begin{align*}
\CC[w_1,\ldots, w_4] & \hookrightarrow H^0(\CC^4 \setminus 0, \cO) \\ 
\CC[w_1,\ldots, w_4] \{\partial_{w_i}\} & \hookrightarrow H^0(\CC^4 \setminus 0, \T) \\
\CC[w_1,\ldots, w_4] \{\d w_i\} & \hookrightarrow H^0(\CC^4 \setminus 0, \Omega^1) 
\end{align*}
and
\begin{align*}
(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^3(\CC^4 \setminus 0, \cO) \\ 
(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_i}\} & \hookrightarrow H^3(\CC^4 \setminus 0, \T) \\
(w_1\cdots w_4)^{-1} \CC[w_1^{-1},\ldots, w_4^{-1}] \{\d w_i\} & \hookrightarrow H^3(\CC^4 \setminus 0, \Omega^1) .
\end{align*}

It follows that (up to completion) the cohomology 
\[
H^\bu(\cL(\CC^5 \times \RR \setminus \{w=0\}) , \dbar)
\]
is the direct sum of $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with 
\begin{equation}
  \label{eqn:ads4ss2} 
  \begin{tikzcd}[row sep = 1 ex]
    - & + \\ \hline
H^3(\CC^4\setminus 0, \cO)[z] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & H^3(\CC^4 \setminus 0, \cO) [z] \\
H^3(\CC^4\setminus 0, \cO) [z] \partial_z \ar[ur, dotted, "\div"'] \\
H^3(\CC^4\setminus 0, \cO) [z] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"'] & H^3(\CC^4\setminus 0, \cO)[z] \d z \\ & H^3(\CC^4\setminus 0, \Omega^1)[z] \{\d w_i\} .
\end{tikzcd}
\end{equation}
The remaining piece of the original BRST operator is drawn in dotted lines. 
The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to the dotted-line operators. 
In this description, the image of the flux $F$ at this page in the spectral sequence corresponds to the class 
\[
[F] = (w_1 \cdots w_4)^{-1} \partial_z \in H^3(\CC^4\setminus 0, \cO) [z] \partial_z .
\]

The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. 
As observed above, this operator maps Dolbeault degree zero elements to Dolbeault degree three elements. 
For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.

The embedding of $\lie{osp}(6|1)$ we wrote down in lemma \ref{lem:m2emb} lands in the kernel of the original BRST operator $\delta^{(1)}$. 
To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [F] , - \big]$. 
This is a direct calculation. 
For instance, recall that an element in the image of the odd summand $(\wedge^2 \CC^2)_{-1}$ (which corresponds to a superconformal transformation) is of the form $z w_a \wedge \d w_b = z(w_a \d w_b - w_b \d w_a)$. 
We have
\[
\big[[F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
\]
since the class $(w_1\cdots w_4)^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for any $a = 1,\ldots 4$. 
\end{proof}

\subsection{The ${\rm AdS}_7 \times S^4$ background}

In this section we introduce the analog of the ${\rm AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity. Decompose the eleven dimensional spacetime as $\C^3_z\times \C^2_w\times \R$.

\parsec[sec:m5coupling]

Analogous to the physical theory, the ${\rm AdS}_7 \times S^4$ background in the holomorphic twist will arise by backreacting M5 branes. To this effect, we begin by discussing how the eleven-dimensional theory couples to M5 branes. 
Consider a stack of $N$ M5 branes wrapping 
\[
\{w_1=w_2=t=0\} \subset \C^3_z\times \C^2_w\times \R.
\] 
It is natural to consider the nonlocal interaction 
\[
I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega +\cdots 
\]
Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. 
We argue that this coupling is consistent with expectations from the physical theory and from dimensional reduction.

The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory (\S\ref{s:components}). 
In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the Hodge star of the $G$-flux and integrating it over the M5 worldvolume. Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.

\parsec[]

We obtain a deeper justification for this coupling through dimensional reduction to type IIA supergravity. 
Reducing on the circle along the directions the M5 branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\CC^4 \times \RR^2$ with $N$ $D4$ branes wrapping $\CC^2 \times \RR$.

In \cite{CLsugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
\[
N \int _{\C^2 \times \RR} \div^{-1} \mu \vee \Omega_{\C^4} + \cdots .
\]
Again, we have only explicitly indicated the first-order piece of the coupling.

\parsec[s:m5backreact]

The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M5}(\mu)$.

Varying the potential $\div^{-1} \mu$, we obtain the following equation of motion involving the field $\gamma$:
\beqn\label{eqn:m5eom1}
\dbar \del \gamma + \div \left(\frac{1}{1-\nu} \mu\right) \wedge \del \gamma = N \delta_{w_1=w_2=t=0} .
\eeqn
Notice that there is an extra derivative compared to the equation of motion arising from varying the field $\mu$. 
This equation only depends on $\gamma$ through its field strength $\del \gamma$.

Varying $\gamma$ we obtain the equation of motion 
\beqn\label{eqn:m5eom2}
(\dbar + \d_\RR) \mu + \del \gamma \del \gamma = 0 .
\eeqn 
Again, this only depends on $\gamma$ through its field strength $\del \gamma$.

\begin{lem}
\label{lem:ads7flux}
Let
\[
F_{M5} = \frac{1}{(2\pi i)^3} \frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
\]
Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
\begin{align*}
\dbar (NF_{M5}) + \d_{\RR} (NF_{M5}) & = N \delta_{w_1=w_2=t=0}  \\ 
(NF_{M5}) \wedge (NF_{M5}) & = 0 .
\end{align*}
Here, we set all components of the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

\begin{proof}
The first equation,
\[
\dbar F + \d_{\RR} F = N \delta_{w_1=w_2=t=0},
\]
characterizes the kernel representing $N$ times the residue class for a four-sphere in 
\[
(\CC^2 \times \RR) \setminus 0 \simeq S^4 \times \RR .
\] 
That is
\[
\oint_{S^4} N F = N 
\]
for any four-sphere centered at $0 \in \CC^2 \times \RR$.

The second equation $F \wedge F = 0$ follows by simple type reasons. 
\end{proof}

\parsec[s:m5embedding]

To provide evidence for the claim that this is the twisted analog of the AdS geometry, we will again show that the twist of the symmetries present in the physical theory on ${\rm AdS}_7 \times S^4$ appear in the twisted theory on this background.

We have recalled that the $Q$-cohomology of $\lie{osp}(8|2)$ is isomorphic to the super Lie algebra $\lie{osp}(6|1)$. 
We will define an embedding of $\lie{osp}(6|1)$ into the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$ which corresponds to the twist of the 6d superconformal algebra.

We first focus on the case where the flux $N=0$.
In this case the embedding can be extended to all of $\CC^5 \times \RR$.

Recall that we have chosen coordinates of the form
\[
\CC^5 \times \RR = \CC_z^3 \times \CC_w^2 \times \RR_t
\]
with $z_i, i=1,2,3$ and $w_a, a=1,2$.
The stack of M5 branes wrap $w_1=w_2=t=0$.

The embedding of the bosonic piece of $\lie{osp}(6|1)$ can be described as follows. Recall that the bosonic part of $\lie{osp}(6|1)$ is the direct sum Lie algebra
\[
\lie{sl}(4) \oplus \lie{sl}(2) .
\]
which we write as $\lie{sl}(W) \oplus \lie{sl}(R)$ with $W,R$ complex four, two dimensional complex vector spaces. The roles of the $\lie{sl}(4)$ and $\lie{sl}(2)$ summands are interchanged compared to the case of the M2 brane. 
The Lie algebra $\lie{sl}(4)$ represents (holomorphic) conformal transformations along the plane $\CC^3_z$, again coming from the natural action on $P^3(\C)$.
Since not all such infinitesimal transformations are divergence-free, the precise vector fields must be adjusted.   
The Lie algebra $\lie{sl}(2)$ represents rotations in $\CC^2_w$; the vector fields representing these transformations are automatically divergence-free.
In more detail, the embedding of the bosonic piece can be given by the following explicit formulas.

\begin{itemize}[leftmargin=\parindent]
\item
The bosonic abelian subalgebra $\CC^3 \subset \lie{sl}(4)$ of translations is mapped to the obvious vector fields 
\[
\frac{\del}{\del z_i} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) , \quad i=1,2,3.
\]

\item
The bosonic subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ is mapped to the 
rotations
\[
A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad (A_{ij}) \in \lie{sl}(3) .
\]

\item
The bosonic subalgebra $\CC \subset \lie{sl}(4)$ corresponding to rescaling $\C^3$ is mapped to the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR)  .
\] 
Notice that this vector field are divergence-free and restricts to the ordinary dilation (Euler vector field) along $w=0$. 
\item 
The bosonic subalgebra of $\lie{sl}(4)$ describing special conformal transformations on $\CC^3$ is mapped to the elements 
\[
z_j \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
\item 
The bosonic summand $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\CC^5) \otimes \Omega^0(\RR) .
\]
\end{itemize}

The odd part of the algebra $\lie{osp}(6|1)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\lie{sl}(4)$ representation and $R$ is the fundamental $\lie{sl}(2)$ representation. 
It is natural to split $W = L \oplus \CC$ with $L = \CC^3$ the fundamental $\lie{sl}(3) \subset \lie{sl}(4)$ representation. 
Then the odd part decomposes as
\[
L \otimes R \oplus \wedge^2 L \otimes R \cong \CC^3 \otimes \CC^2 \oplus \wedge^2 \CC^3 \otimes \CC .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d supertranslations. 
It is mapped to the fields 
\[
z_i \d w_a \in \Omega^{1,0}(\CC^5) \otimes \Omega^0(\RR) ,\quad a=1,2, \quad i =1,2,3.
\] 
\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. 
It is mapped to the fields
\[
\frac12 w_a (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\CC^5)\otimes \Omega^0(\RR) , \quad a = 1,2, \quad k = 1,2,3. 
\]
\end{itemize}

\begin{lem}
These assignments define an embedding of $\lie{osp}(6|1)$ into the linearized BRST cohomology of the fields of the eleven-dimensional theory on $\CC^5 \times \RR$. 
Equivalently, it defines an embedding
\[
i_{M5} \colon \lie{osp}(6|1) \hookrightarrow E(5,10) .
\]
\end{lem}

\begin{proof}
To explicitly describe the embedding into $E(5,10)$ we simply apply the de Rham differential to the last two formulas above.
Recall, we are using the holomorphic coordinates $(z_1,z_2,z_3, w_1,w_2)$ on $\CC^5$ where $z_i$ are the holomorphic coordinates along the M5 brane. 
\begin{itemize}
\item 
The fermionic summand $L \otimes R$ embeds into closed two-forms as
\[
\d z_i \wedge \d w_a, \quad i=1,2,3, \quad a=1,2. 
\] 
\item 
The fermionic summand $\wedge^2 L \otimes R$ embeds into closed two-forms as
\[
w_a \d z_i  \wedge \d z_j + \frac12 \d w_a \wedge (z_i \d z_j - z_j \d z_i) , \quad i,j=1,2,3, \quad a=1,2. 
\] 
\end{itemize}
\end{proof}
\parsec[]

Next, we turn on $N \ne 0$  units of nontrivial flux. 
Since not all of the fields we wrote down above commute with the flux $N F$, they are not compatible with the total differential $\delta^{(1)} + [N F, -]$ acting on the fields supported on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$. 
Nevertheless, we have the following.

\begin{prop}
\label{prop:brads7}
There exist $N$-dependent corrections to the embedding $i_{M5}$ which are compatible with the modified BRST differential $\delta^{(1)} + [N F_{M5},-]$. 
Furthermore, these $N$-dependent corrections define an embedding of $\lie{osp}(6|1)$ inside the cohomology of the fields of eleven-dimensional theory on $\CC^5 \times \RR \setminus \CC \times \RR$ with respect to the differential $\delta^{(1)} + [N  F_{M5},-]$.
\end{prop}

\parsec[s:thfcohomology]

The proof of the above proposition follows from another indirect cohomological argument. 
Before getting to the proof, we introduce the relevant cohomology.

The eleven-dimensional theory is built from fields which live in the tensor product of complexes 
\[
\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR).
\]
More precisely, this is where the  fields $\beta$ and~$\nu$ live. 
The $\mu$ and~$\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.

Another way to think about this complex is to first consider the full de Rham complex $\Omega^\bu(\CC^5 \times \RR)$, which includes both holomorphic and anti-holomorphic forms in the $\CC^5$ direction. 
The dg algebra of all de Rham forms on $\CC^5 \times \RR$ has an ideal generated by the holomorphic one forms $\{\d z_i\}_{i=1,\ldots,5}$.
There is an isomorphism of dg algebras
\[
\Omega^{0,\bu}(\CC^5) \otimes \Omega^\bu(\RR) \cong \Omega^\bu(\CC^5 \times \RR) \, / \, (\d z_1,\ldots, \d z_5) .
\]
The advantage of this presentation is that we can define a complex associated to more general manifolds that are not products of a complex manifold with a smooth manifold.\footnote{More generally, we are describing the cohomology of a manifold equipped with a topological holomorphic foliation.}

For the M5 brane, it was convenient to rename the holomorphic coordinates on $\CC^5$ to $z_1,z_2,z_3,w_1,w_2$. 
At the twisted level, the geometry arising from backreacting M5 branes is based on the manifold 
\[
\CC^5 \times \RR \setminus \CC^3 \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0) .
\]
The $\beta$ and~$\nu$ fields of the eleven-dimensional theory on this submanifold of $\CC^5 \times \RR$ live in the complex 
\[
\Omega^\bu\bigg(\CC^5 \times \RR \setminus \CC^3\bigg) \, / \, (\d z_1,\d z_2,\d z_3, \d w_1, \d w_2)  .
\]
The $\mu$ and~$\gamma$ fields live in similar complexes, where we introduce a (trivial) vector bundle on $\CC^5 \times \RR \setminus \CC^3$.

Since the $\CC^3$ wraps $w_1=w_2=t=0$ we can apply a version of the K\"unneth formula to identify this complex with 
\[
\Omega^{0,\bu}(\CC^3_z) \otimes \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
\]

The cohomology of the Dolbeault complex of $\CC^3_z$ is easy to compute. 
The cohomology of the bit in parentheses is concentrated in degrees zero and two. 
In degree zero, there is a dense embedding
\[
\CC[w_1,w_2] \hookrightarrow H^0 \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg)
\]
In degree two, there is a dense embedding
\[
w_{1}^{-1} w_2^{-1} \CC[w_1,w_2] \hookrightarrow H^2 \bigg( \Omega^\bu\left(\CC^2_w \times \RR \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
\]

It will be useful to explain this last embedding in more detail. 
Consider the homogenous element $w_1^{-1} w_2^{-1}$. 
This represents the class of the Dolbeault-de Rham two-form
\[
\frac{\wbar_1 \d \wbar_2 \wedge \d t - \wbar_2 \d \wbar_1 \wedge \d t + t \d \wbar_1 \wedge \d \wbar_2}{(\|w\|^2 + t^2)^{5/2}} .
\]
Notice that, if we wedge with the volume form $\d w_1 \d w_2$, this is the unit  flux ($N=1$) introduced in Lemma \ref{lem:ads7flux}. 
The homogenous element $w_1^{-n-1} w_2^{-m-1}$ represents the class of the holomorphic derivatives $\partial_{w_1}^n \partial_{w_2}^{m}$ applied to this two-form.

Observe that, when restricted to $\CC^5 \times \RR \setminus \CC^3$, the holomorphic tangent bundle along $\CC^5$ is still trivializable.

\parsec[]

Let's turn to the proof of Proposition~\ref{prop:brads7}.
We proceed completely analogously to the case of backreacted M2 branes as in the proof of Proposition \ref{prop:brads4}.

\begin{proof}[Proof of Proposition \ref{prop:brads7}]
Let $\cL (\CC^5 \times \RR \setminus \{w_1=w_2=t=0\})$ denote the super $L_\infty$ algebra obtained by parity shifting the fields of the eleven-dimensional theory on $\CC^5 \times \RR \setminus \{w_1=w_2=t=0\}$.

There is a spectral sequence which converges to the cohomology of the fields with respect to the deformed linear BRST differential $\delta^{(1)} + [N F_{M5},-]$ whose first page
is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$. 
Recall that the linearized BRST differential decomposes as
\[
\delta^{(1)} = \dbar + \d_{\RR} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma}  .
\]
To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
This first page of this auxiliary spectral sequence is simply given by the cohomology of the fields supported on 
\[
\CC^5 \times \RR \setminus \{w_1=w_2=t=0\} \cong \CC_z^3 \times (\CC^2_w \times \RR \setminus 0)
\]
with respect to $\dbar + \d_{\RR}$.

To compute this cohomology we follow the discussion in \S \ref{s:thfcohomology}.
Just as in the case of the M2 brane, we see that the $\dbar + \d_{\RR}$ cohomology is (up to completions) is the direct sum of the cohomology on flat space $H^\bu(\cL(\CC^5 \times \RR), \dbar)$ with
\begin{equation}
  \label{eqn:ads7ss2} 
  \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "\div"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "\div"'] \\
w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "\del"] \ar[dr, dotted, "\del"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
\end{tikzcd}
\end{equation}

Recall that the flux $F$ was defined as the image under $\del$ of some $\gamma$-type field. 
Therefore, the class $[F]$ does not live inside this page of the spectral sequence, but the operator $[[F], -]$ does act on this page nevertheless. 
For instance, if $f^i(z,w) \d z_i$ is a one-form living in $H^0(\CC^5, \Omega^1) \otimes H^0(\RR)$, then
\[
[ [F] , f^i (z,w) \d z_i ] = \ep_{ijk} w_1^{-1} w_2^{-1} \partial_{z_j} f^i(z,w) \del_{z_k} 
\]
which is an element in 
\[
\CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\del_{z_i}\} \subset H^0(\CC^3, \T) \otimes H^2 \big(\Omega^\bu(\CC^2 \times \RR \setminus 0) / (\d w_1 , \d w_2) \big) .
\]

The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\CC^5 \times \RR$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to the dotted-line operators in~\eqref{eqn:ads7ss2}.

The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. 
This operator maps Dolbeault-de Rham degree zero elements to Dolbeault-de Rham degree two elements. 
For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.

The embedding of $\lie{osp}(6|1)$ for $N=0$ lives in the kernel of the original BRST operator $\delta^{(1)}$. 
To see that it this embedding can be lifted to the full cohomology we need to check that any element in the image of the original embedding is annihilated by $\big[ N [F] , - \big]$. 
This is a direct calculation. 
For instance, recall that an element in the image of the odd summand $\wedge^2 L \otimes R = \wedge^2 \CC^3 \otimes \CC^2$ (which corresponds to a superconformal transformation) is of the form $w_a (z_i \d z_j - z_j \d z_i)$, $a=1,2, i,j=1,2,3$. 
We have
\[
\big[[F] , w_a (z_i \d z_j - z_j \d z_i)\big] = 2 \ep_{ijk} (w_1^{-1} w_2^{-1}) \cdot w_a \del_{z_k} = 0
\]
since the class $w_1^{-1} w_2^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for $a=1,2$.
Verifying that the remaining elements in the image of $i_{M5}$ are in the kernel of $\big[ [F], -\big]$ is similar.
This completes the proof.
\end{proof}

\printbibliography

\end{document}

### 2023-04-17 aone/main.tex
merge

@@
 \documentclass{amsart}
-\usepackage{fullpage}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{enumerate}
-\usepackage[titletoc]{appendix}
-\usepackage{hyperref}
+%\usepackage{fullpage}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
+%\usepackage{amsfonts}
+%\usepackage{amsthm}
+%\usepackage{enumerate}
+%\usepackage[titletoc]{appendix}
+%\usepackage{hyperref}
+%
+%%\usepackage{tikz} 	  % Replaced with tikz-cd, but am
+%\usepackage{tikz-cd}  % willing to learn tikz if necessary
+%	\usetikzlibrary{decorations.pathmorphing}
+%
+%\usepackage[all]{xy}
+%\usepackage{stmaryrd}
+%\usepackage{indentfirst}
+%\usepackage{graphicx}
+%\usepackage{tabularx}
 
-%\usepackage{tikz} 	  % Replaced with tikz-cd, but am
-\usepackage{tikz-cd}  % willing to learn tikz if necessary
-	\usetikzlibrary{decorations.pathmorphing}
+\usepackage{../macros-mtheory}
 
-\usepackage[all]{xy}
-\usepackage{stmaryrd}
-\usepackage{indentfirst}
-\usepackage{graphicx}
-\usepackage{tabularx}
-
-\usepackage{macros}
-
-\renewcommand\tabularxcolumn[1]{m{#1}}
-\newcolumntype{Y}{>{\centering\arraybackslash}X}
+%\renewcommand\tabularxcolumn[1]{m{#1}}
+%\newcolumntype{Y}{>{\centering\arraybackslash}X}
 
@@
 
+\appendix
+
+\section{Costello's treatment}
+
+Given a super vector space $V$ one can consider the free chiral conformal field theory of spin $1/2$ fields $\psi$ taking values in $V$ and $\chi$ taking values in $V^*$.
+When $V$ is purely odd then this describes a number of complex free fermions.
+When $V$ is purely even this is a version of the $\beta-\gamma$ system.
+
+Let $GL(V)$ (respectively, $\lie{gl}(V)$) be the super general linear group (respectively, Lie algebra) acting on the super vector space $V$.
+Then, along a Riemann surface defect we can couple this chiral CFT to $GL(V)$ valued five-dimensional Chern--Simons theory. 
+Explicitly, if we place five-dimensional Chern--Simons theory on $\R \times \C^2$ and the defect along
+\beqn
+0 \times \C_z \times 0 \subset \R \times \C^2
+\eeqn
+then the five-dimensional Chern--Simons gauge field $A \in \Omega^{0,\bu}(\R \times \C^2) \otimes \lie{gl}(V)$ couples via the Lagrangian
+\beqn
+\int_{\C_z} \chi (A \cdot \psi) .
+\eeqn
+
+For $N,M \geq 1$ we will take $V$ to be the dimension $N+M|M$ superspace~$\C^{N+M|M}$.
+Let $\cF(N+M|M)$ be the $GL(N+M|M)$-invariants of the vertex algebra corresponding to the free CFT along the defect.
+This is a sub vertex algebra of some tensor product of $M$ free $\beta-\gamma$ systems and $(N+M)$ pairs of chiral free fermions.
+Notice that for $M<M'$ the decomposition $\C^{N+M'|M} = \C^{N+M|M} \oplus \C^{M'-M|M'-M}$ determines a $GL(N+M'|M')$-invariant map of vertex algebras
+\beqn
+\cF (N+M'|M') \to \cF(N+M|M) .
+\eeqn
+Denote by $\cF(N+\infty|\infty)$ the resulting limit vertex algebra
+\beqn
+\cF(N+\infty|\infty) = \lim_{M<M'} \left(\cF (N+M'|M') \to \cF(N+M|M) \right) .
+\eeqn
+
+Consider the algebra 
+\beqn
+\cO_\ep (\C^\times \times \C) 
+\eeqn
+which as an underlying vector space is $\C[z,z^{-1},w]$ and the commutator is the $\star_\ep$ commutator.
+Viewing this as a Lie algebra, it admits a central extension that we denote by $\lie{w}_{1+\infty}(\ep)$.
+We denote the central element by~$K$.
+When $\ep = 1$ denote this simply by $\lie{w}_{1+\infty}$.
+Notice that for $\ep \ne 0$ there is an isomorphism of Lie algebras
+\beqn
+\lie{w}_{1+\infty} \xto{\simeq} \lie{w}_{1+\infty}(\ep) .
+\eeqn
+which sends $z \mapsto z$ and $w \mapsto \ep w$.
+By setting $w = \frac{\del}{\del z}$ observe that the Lie algebra $\lie{w}_{1+\infty}$ is a central extension of the Lie algebra of differential operators on $\C^\times$
+
+Let $\lie{w}_{1+\infty}(\ep)_+$ be the subalgebra of positive modes (in the variable $z$) and consider the module
+\beqn
+W_{1+\infty}(\ep) \define U(\lie{w}_{1+\infty}(\ep)) \slash {U(\lie{w}_{1+\infty}(\ep)_+)} .
+\eeqn
+This has the natural structure of a vertex algebra in the category of $\C[K]$-modules.
+For $c \in \C$ let $W_{1+\infty}(\ep,c)$ denote the vertex algebra which is the further quotient where we set the central element~$K = c$. 
+For $\ep \ne 1$, and for fixed $c$, the vertex algebras $W_{1+\infty}(\ep,c)$ are all isomorphic.
+Denote by $W_{1+\infty}(c) = W_{1+\infty}(1,c)$.
+
+When $c = N$ the vertex algebra $W_{1+\infty}(N)$ admits a quotient which is isomorphic to the vertex algebra~$W_N = W(\lie{sl}(N))$.
+
+\begin{prop}
+Let $W_{1+\infty}$
+There is an isomorphism of vertex algebras
+\beqn
+\cF(N+\infty|\infty) \simeq W_{1+\infty}(c=N) .
+\eeqn
+\end{prop}
+
+\section{Higher free fermion}
+
+Consider the line bundle on $\Sigma \times \C^2$
+\beqn
+L_r \define K^{r/2}_\Sigma \boxtimes \ul{\C} 
+\eeqn
+where $\ul{\C}$ denotes the trivial line bundle on $\C^2$.
+
+Consider the following $\Z \times\Z/2$ complex of sheaves $\cE_r$ whose even part is
+\beqn
+\cE_{r}^{ev} = \Omega^{0,\bu}(\Sigma \times \C^2 , K^{1/2} \otimes L_r) .
+\eeqn
+And whose odd part is 
+\beqn
+\cE_r^{odd} = \Omega^{0,\bu}(\Sigma \times \C^2 , L)[2] \xto{\del} \Omega^{1,\bu}(\Sigma,L)[1] .
+\eeqn
+
+There is a local action of $\cE(3|6)$.
+
+\subsection{Characters}
+
+The character for the chiral free fermion is 
+\beqn
+\ch_{\bF}(q,t) = \prod_{n \geq 1} (1+t q^{n-1/2})(1+t^{-1} q^{n-1/2}) = \sum_{m \in \Z} Z_m (q) t^m .
+\eeqn
+From this one can see that 
+\beqn
+Z_0(q) = \oint \frac{\d t}{2\pi i t} \ch_{\bF}(q,t) = \prod_{n \geq 1} \frac{1}{1 - q^{n}} .
+\eeqn
+This is the character level version of the statement that the $\C^\times$-invariants of the chiral free fermion is equivalent to the free chiral boson.
+
 \end{document}

### 2023-04-17 fivebranes/IIA.tex
IIA

Let $S$ be a complex surface.
Let $p_W \colon W \to S$ be a rank two holomorphic vector bundle on $S$ and let $p_L \colon L \to S$ be a holomorphic line bundle on $S$.
We require that these bundles satisfy
\beqn
\det (W \oplus L) = K_S 
\eeqn
where $K_S$ is the canonical bundle of $S$.
This condition guarauntees that
\beqn
X = \text{Tot}(W \oplus L)
\eeqn
is a Calabi--Yau five-fold.
We will also assume that $L$ has a real structure with compatible fiberwise hermitian metric.

We place the holomorphic twist of $M$-theory on 
\beqn
\R \times X
\eeqn
and consider fivebranes wrapping $Z = \text{Tot}(L)$.

Reduction to IIA is described by a diagram
\beqn
\begin{tikzcd}
S^1 \ar[r] \ar[d] & X \ar[d] & \ar[l] {pt} \ar[d] \\
(pt \ne 0, t, z) \ar[r] & \text{Tot}(\R_{\geq 0} \to \R \times \text{Tot}(W)) & \ar[l] (0,t,z) .
\end{tikzcd} .
\eeqn
When $L$ is trivial this is simply
\beqn
\R \times \C \to \text{Tot}(W) \to \R \times \R_+ \times \text{Tot}(W).
\eeqn
The fivebranes become fourbranes wrapping
\beqn
\text{Tot}(\R_+ \to \text{Tot}(W)) .
\eeqn
When $L$ is trivial then the fourbranes wrap
\beqn
0 \times \R_+ \times S .
\eeqn

Equations of motion for the open string theory describes moduli space of pairs $\{(\cL, \cF)\}$ where $\cL$ is a local system on $\R_+$ of rank one and $\cF$ is a perfect complex on $\text{Tot}(W)$ which is finite over $S$.
This space is naturally $(-3)$-shifted symplectic.
If we polarize $W = L_1 \oplus L_2$ to $L_1 \oplus L_2[2]$ then this becomes $(-1)$-shifted symplectic.
There is a forgetful functor to just remembering the perfect complex over $\text{Tot}(W)$ (which is fine over $S$), and the claim is that this is $0$-shifted symplectic.

### 2023-05-11 graviton spectra/content/OLD global.tex
graviton spectra

--- 2022-10-13 fivebranes/index.tex
@@
 \label{sec:states}
+\todo{Rewrite section to be less global}
 
-The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT.
-The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. 
-The state space on the twisted version of $AdS_{7}\times S^{4}$ has a remarkable property---it is naturally a module for a certain infinite-dimensional exceptional super Lie algebra. 
-We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
+%The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT.
+%The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. 
+%The state space on the twisted version of $AdS_{7}\times S^{4}$ has a remarkable property---it is naturally a module for a certain infinite-dimensional exceptional super Lie algebra. 
+%We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.
 
@@
 
-\subsection{Twisted Backreactions}
-We begin by describing the relevant backgrounds.
-In eleven-dimensional supergravity, the $AdS_7 \times S^4$ background is obtained by backreacting a number of fivebranes in flat space \cite{Maldacena:1997re,WittenAdS}.
-In \cite{RSW} we gave descriptions of twisted versions of this background. We will recall this construction, adapted to a slightly more global situation than considered previously.
-
-We will consider the eleven-dimensional theory on eleven-manifolds that arise as total spaces of vector bundles. Placing the theory in the backreacted geometry is a two step procedure:
-
-\begin{itemize}
-  \item Place the eleven-dimensional theory on the complement of the zero section. 
-  To do so, we will wish to describe the complement of the zero-section in a way that facilitates a description of the perturbative theory in terms of natural operations on holomorphic-topological local $L_{\infty}$-algebras.
-
-  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element.
-  The Maurer--Cartan element is thought of as the flux sourced by branes wrapping the zero section.
-\end{itemize}
-
-This procedure is implemented at the level of the $\Omega$-deformed nonminimal twist on flat space in the appendix of \cite{CostelloM5}.
 %\parsec[s:brkevin]
@@
 %\[
-%\Omega^{0,\bu}(C) \otimes \cA^{0;\bu}(\R \times \C - 0) [1]
+%\Omega^{0,\bullet}(C) \otimes \mc{A}^{0;\bullet}(\R \times \C - 0) [1]
 %\]
-%where $\cA^{0;\bu}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
+%where $\mc{A}^{0;\bullet}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
 %We refer to the section below for a reminder on this geometric structure.
@@
 %\]
-%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bu}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
+%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
 %The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
@@
 \begin{align*}
- h \colon  M & \to \R_{+} \\
+ h :  M & \to \R_{+} \\
   (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
 \end{align*}
-Letting $\pi \colon M \to Z$ be the natural projection, we obtain the projection
+Letting $\pi : M \to Z$ be the natural projection, we obtain the projection
 \[
-p \define (h,\pi) \colon M \to \R_{+}\times Z
+p \define (h,\pi) : M \to \R_{+}\times Z
 \]
-which restricts to an $S^4$ bundle $p|\mathring {M} \colon \mathring{M} \to \R_{>0} \times Z$.
+which restricts to an $S^4$ bundle $p|\mathring {M} : \mathring{M} \to \R_{>0} \times Z$.
 These embeddings and projections fit inside of the following commutative diagram
@@
 
-As we elaborated in \S \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\cL_{sugra}$ on $\mathring M$.
+As we elaborated in \S \ref{s:thfmflds}, the eleven-dimensional theory is defined on the THF manifold $\mathring M$---in the BV formalism this is encoded, in part, by the sheaf of $L_\infty$ algebras $\mc{L}_{sugra}$ on $\mathring M$.
 Compactification of this theory along the $S^4$ link corresponds to pushing forward this sheaf along $p|\mathring M$.
-The resulting sheaf of $L_\infty$ algebras $(p|\mathring M)_*\cL_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
+The resulting sheaf of $L_\infty$ algebras $(p|\mathring M)_*\mc{L}_{sugra}$ describes, in the BV formalism, the compactified theory on the seven-manifold $\R_{>0} \times Z$.
 
-We will compute the pushforward using the prescription for pushing forward a $\cA^{\bu}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}.
+We will compute the pushforward using the prescription for pushing forward a $\mc{A}^{\bullet}_{F}$-module along a compatible submersion outlined in \cite{KormanThesis}.
 Recall that we have a THF structure on $M$, given by an involutive subbundle $F_{M}\subset T^{\C}_{M}$, induced from a partially flat conneciton on $\R\oplus W$.
@@
 
-The existence of a partially flat connection amounts to a choice of splitting \[\sigma \colon \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row.
+The existence of a partially flat connection amounts to a choice of splitting \[\sigma : \pi^{*}T^{0,1}_{Z}\to F_{M}\] of the top row.
 Both $F_{M}$ and $\pi^{*}T^{1,0}_{Z}$ are involutive, and the flatness of the connection implies that $\sigma$ preserves the lie brackets on sections.
@@
 \[
-  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
+  \mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z} = \mc{A}^{\bullet}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}
 \]
@@
 be the subbundle of the tangent bundle of the base locally spanned by $\del_{r}, \del_{z_{i}}$ and $(p|\mathring M)^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z}$ the pullback, which is a subbundle of $T_{\mathring M}$.
-We will let $\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the leaves of this foliation on the base.
+We will let $\mc{A}^{\bullet}_{\R_{>0}\times Z} = \mc{A}^{\bullet}_{F _{\R_{>0}\times Z}}$ denote the THF complex resolving functions constant along the leaves of this foliation on the base.
 
-Our goal is to describe the derived pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.
+Our goal is to describe the derived pushforward $(p|\mathring M)_{*}\mc{L}_{sugra}$ as a $\mc{A}^{\bullet}_{\R_{>0}\times Z}$-module.
 
@@
 \begin{align*}
-  \cA^{\bu}_{\mathring M}(L) & \cong \cA^{\bu}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
-                         & \cong (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
+  \mc{A}^{\bullet}_{\mathring M}(L) & \cong \mc{A}^{\bullet}_{(p|\mathring M)^{*}F_{\R_{>0}\times Z}}\otimes \mc{A}^{\bullet}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
+                         & \cong (p|\mathring M)^{*}\mc{A} ^{\bullet}_{\R_{>0}\times Z}\otimes \mc{A}^{\bullet}_{{\mathring M/ \R_{>0}\times Z}}(L) \\
 \end{align*}
@@
 %Note that since we have a complex of locally free $C^{\infty}_{\mathring M}$-modules, the derived pushforward along $(p|\mathring M)_{*}$ coincides with the orinary pushforward.
-Moreover since the derived pushforward commutes with tensor product, we have that the $(p|\mathring M)_{*}\cL_{sugra}$ is given by
+Moreover since the derived pushforward commutes with tensor product, we have that the $(p|\mathring M)_{*}\mc{L}_{sugra}$ is given by
 
@@
 \[
-\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\R_{>0}\times Z}} (p|\mathring M)_{*}\cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \to (p|\mathring M)_{*}\left ( (p|\mathring M)^{*}\cA ^{\bu}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\mathring M}} \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L) \right )\]
+\mc{A} ^{\bullet}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\R_{>0}\times Z}} (p|\mathring M)_{*}\mc{A}^{\bullet}_{{\mathring M/ \R_{>0}\times Z}}(L) \to (p|\mathring M)_{*}\left ( (p|\mathring M)^{*}\mc{A} ^{\bullet}_{\R_{>0}\times Z}\otimes_{C^{\infty}_{\mathring M}} \mc{A}^{\bullet}_{{\mathring M/ \R_{>0}\times Z}}(L) \right )\]
 
@@
 %\[
-%  \cA^{#}_{\R_{>0}\times Z} \to (p|\mathring M)_{*}(p|\mathring M)^{*}\cA ^{#}_{\R_{>0}\times Z}
+%  \mc{A}^{#}_{\R_{>0}\times Z} \to (p|\mathring M)_{*}(p|\mathring M)^{*}\mc{A} ^{#}_{\R_{>0}\times Z}
 %\]
 
-The left hand side of the above isomorphism has a canonical $\cA ^{\#}_{\R_{>0}\times Z}$-module structure. 
+The left hand side of the above isomorphism has a canonical $\mc{A} ^{\#}_{\R_{>0}\times Z}$-module structure. 
 It remains to discuss compatibility with the differential along the base.
-The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$.
+The compatibility condition is expressed through the observation that the pro-vector bundle \[(p|\mathring M)_{*} \mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] will have the structure of a partial flat connection defined along the leaves of $F_{\R_{>0}\times Z}$.
 We can construct such a connection from analyzing the behavior of the THF differential $\thfd$ under the splitting.
 
- The THF differential induces a derivation of total degree 1 on the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ so it is determined by its restrictions
+ The THF differential induces a derivation of total degree 1 on the pushforward $(p|\mathring M)_{*}\mc{L}_{sugra}$ so it is determined by its restrictions
 
-\[\thfd_{i} \colon  (p|\mathring M)_{*} \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \cA^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \cA^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]
+\[\thfd_{i} :  (p|\mathring M)_{*} \mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \to \mc{A}^{i}_{\R_{\geq >0} \times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M)_{*} \mc{A}^{\bullet-i+1}_{\mathring M/\R_{>0}\times Z}(L).\]
 
@@
 \begin{itemize}
-  \item The first term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to (p|\mathring M_{*})\cA^{\bullet+1}_{\mathring M/\R_{>0}\times Z}(L)\] is the internal differential.
+  \item The first term \[\thfd_{0} : (p|\mathring M_{*})\mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to (p|\mathring M_{*})\mc{A}^{\bullet+1}_{\mathring M/\R_{>0}\times Z}(L)\] is the internal differential.
 
-  \item The second term \[\thfd_{0} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{1}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] is a partial connection.
+  \item The second term \[\thfd_{0} : (p|\mathring M_{*})\mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \mc{A}^{1}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\] is a partial connection.
 However, it is not flat.
-Rather the failure for flatness is captured by \[ \thfd_{1}^{2} + [\thfd_{0}, \thfd_{2}] = 0 \] where \[ \thfd_{2} : (p|\mathring M_{*})\cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \cA^{2}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\cA^{\bullet-1}_{\mathring M/\R_{>0}\times Z}(L) \] is a nullhomotopy.
+Rather the failure for flatness is captured by \[ \thfd_{1}^{2} + [\thfd_{0}, \thfd_{2}] = 0 \] where \[ \thfd_{2} : (p|\mathring M_{*})\mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L)\to \mc{A}^{2}_{\R_{\geq 0}\times Z}\otimes _{C^{\infty}_{\R_{>0}\times Z}}(p|\mathring M_{*})\mc{A}^{\bullet-1}_{\mathring M/\R_{>0}\times Z}(L) \] is a nullhomotopy.
 \end{itemize}
-In particular, $\thfd_{1}$ induces a partial flat connection along $F_{\R_{>0}\times Z}$ the hypercohomology \[\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right )\].
+In particular, $\thfd_{1}$ induces a partial flat connection along $F_{\R_{>0}\times Z}$ the hypercohomology \[\mathbb{R}^\bullet (p|\mathring M)_* \left (\mc{A}^\bullet_{\mathring M / \R_{>0}\times Z}(L)\right )\].
 
@@
 \begin{prop}\label{p:dimred}
-  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
-  \beqn
-  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
-  \eeqn
-with the $\cA^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
+  The pushforward $(p| \mathring M)_{*}\mc{L}_{sugra}$ is described by the following complex of sheaves
+  \begin{equation}
+  \mc{A}^\bullet_{\R_{>0}\times Z}\otimes \mathbb{R}^\bullet (p|\mathring M)_* \left (\mc{A}^\bullet_{\mathring M / \R_{>0}\times Z}(L) \right)
+  \end{equation}
+with the $\mc{A}^{\bullet}_{\R_{>0}\times Z}$-module structure coming from the partial flat connection induced by $\thfd_{1}$.
 \end{prop}
@@
 It is induced from an explicit fiberwise pairing, which we may write as follows.
-First note that the fiber of $\mathbb{R}^\bu (p|\mathring M)_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)$ at $(t,p)\in \R_{>0}\times Z$ can be computed as the cohomology of the complex
+First note that the fiber of $\mathbb{R}^\bullet (p|\mathring M)_* \left (\mc{A}^\bullet_{\mathring M / \R_{>0}\times Z}(L) \right)$ at $(t,p)\in \R_{>0}\times Z$ can be computed as the cohomology of the complex
 \[
-H^{\bullet}\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right ).
+H^{\bullet}\left (\Gamma \left (S^{4}_{(t,p)}, \mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right ).
 \]
@@
 \[
-\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right )
+\left (\Gamma \left (S^{4}_{(t,p)}, \mc{A}^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong \left ( \Gamma \left ( \mc{A}^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right )
 \]
@@
 \[
-\left ( \Gamma \left ( \cA^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right ) 
+\left ( \Gamma \left ( \mc{A}^{\bullet}_{(\R\times \C^{2})_{(t,p)} - 0}(L|_{{(\R\times \C^{2})_{(t,p)} - 0}}) \right ); \thfd \right ) 
 \]
 is the complex given by
-\beqn\label{eqn:bigcplx}
+\begin{equation}\label{eqn:bigcplx}
 \begin{tikzcd}
   \ul{even} & \ul{odd} \\ \hline
-H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \\
-H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bu \left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}), \thfd \right ) \{dw_a, dz_i\}
+H^\bullet \left ( \Gamma ( \mc{A}^{\bullet}_{(\R\times\C^2)-0}), \thfd \right )\{\partial_{w_a}, \partial_{z_i}\}  \ar[r, dotted, "D_{\Omega}"] & H^\bullet \left ( \Gamma ( \mc{A}^{\bullet}_{(\R\times\C^2)-0}), \thfd \right )  \\
+H^\bullet \left ( \Gamma ( \mc{A}^{\bullet}_{(\R\times\C^2)-0}), \thfd \right )  \ar[r, dotted, "D"] & H^\bullet \left ( \Gamma ( \mc{A}^{\bullet}_{(\R\times\C^2)-0}), \thfd \right ) \{dw_a, dz_i\}
 \end{tikzcd}
-\eeqn
+\end{equation}
 \end{lem}
@@
 Now, the THF complex
-\beqn\label{eqn:thfcohomology1}
-\left ( \Gamma ( \cA^{\bu}_{(\R\times\C^2)-0}) \, , \, \thfd \right )
-\eeqn
+\begin{equation}\label{eqn:thfcohomology1}
+\left ( \Gamma ( \mc{A}^{\bullet}_{(\R\times\C^2)-0}) \, , \, \thfd \right )
+\end{equation}
 has a natural even pairing given by the residue along the four-sphere~$S^4$.
@@
 At the level of cohomology, the pairing on \eqref{eqn:thfcohomology1} is even symplectic and it is equipped with a standard polarization. 
-In degree zero, the cohomology can be identified with holomorphic functions $\cO(\C^2)$, and the full cohomology is of the form $\T^*[-4] \cO(\C^2)$. 
-So, as a $\Z/2$ graded object the cohomology of~\eqref{eqn:thfcohomology1} can be identified with $\T^* \cO(\C^2)$. 
+In degree zero, the cohomology can be identified with holomorphic functions $\mc{O}(\C^2)$, and the full cohomology is of the form $\T^*[-4] \mc{O}(\C^2)$. 
+So, as a $\Z/2$ graded object the cohomology of~\eqref{eqn:thfcohomology1} can be identified with $\T^* \mc{O}(\C^2)$. 
 This endows the cohomology of the complex \eqref{eqn:bigcplx}, which has an odd shifted symplectic structure, with a polarization.
@@
 Then, this page in the spectral sequence is isomorphic to
-\beqn
-\Pi \T^* \left(\cO(\C^2) \otimes V\right) ,
-\eeqn
+\begin{equation}
+\Pi \T^* \left(\mc{O}(\C^2) \otimes V\right) ,
+\end{equation}
 where $\Pi \T^*$ denotes the odd shifted cotangent bundle.
@@
 
-Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
+Thus, we have a description of the compactification of $\mc{L}_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$.
 In particular, the result is local on $\R_{>0}\times Z$.
@@
 The global sections of the sheaf in proposition \ref{p:dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
-\beqn
-E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q(p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
-\eeqn\label{thfss}
+\begin{equation}
+E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \mc{A}^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q(p|\mathring M) _* \left (\mc{A}^\bullet_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\mc{A}^\bullet_{\mathring M}(L)).
+\end{equation}\label{thfss}
 We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.
@@
 The $E_{2}$ page is similarly given by flat sections with respect to $\thfd_{1}$
-\beqn
-E_2^{p,q} = \Gamma_{\thfd_1} \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q (p|\mathring M) _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)
-\eeqn
+\begin{equation}
+E_2^{p,q} = \Gamma_{\thfd_1} \left (\R_{>0}\times Z; \mc{A}^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q (p|\mathring M) _* \left (\mc{A}^\bullet_{\mathring M / \R_{>0}\times Z}(L)\right) \right)
+\end{equation}
 
-In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
-\beqn
+In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\mc{L}_{sugra}$ in the case where
+\begin{equation}
 M = \text{Tot} (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 - (0 \times \C^3).
-\eeqn
+\end{equation}
 In this case, the above spectral sequence clearly degenerates at the $E_{2}$-page.
@@
   Up to completion, the cohomology
-  \beqn
-  \mathbb H^{\bu} (\cA_{\mathring M}^\bu (L) ) = H^{\bu}\left (\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd\right)
-  \eeqn
-  is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA_{M}^{\bu}(L), \thfd)$ with the complex
+  \begin{equation}
+  \mathbb H^{\bullet} (\mc{A}_{\mathring M}^\bullet (L) ) = H^{\bullet}\left (\Gamma(\mc{A}_{\mathring M}^{\bullet}(L)), \thfd\right)
+  \end{equation}
+  is a direct sum of the cohomology on flat space $H^{\bullet}(\Gamma(\mc{A}_{M}^{\bullet}(L), \thfd)$ with the complex
 
-  \beqn
+  \begin{equation}
   \begin{tikzcd}[row sep = 1 ex]
     \ul{even} & \ul{odd} \\ \hline
-w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
-w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
-w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \CC[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
+w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "D_{\Omega}"] & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
+w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "D_{\Omega}"'] \\
+w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "D"] \ar[dr, dotted, "D"'] & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
 \end{tikzcd}
-\eeqn
+\end{equation}
 \end{prop}
@@
 \parsec[s:flux]
-The second step in the construction of the backreacted geometry involves deforming the pushforward $(p| \mathring{M})_{*}\cL_{sugra}$ by a certain Maurer-Cartan element.
+The second step in the construction of the backreacted geometry involves deforming the pushforward $(p| \mathring{M})_{*}\mc{L}_{sugra}$ by a certain Maurer-Cartan element.
 The Maurer-Cartan element is determined by the lowest order term in the coupling between the eleven dimensional theory and the stack of fivebranes.
 It was argued in \cite{RSW} that the relevant coupling is given by the nonlocal interaction
-\beqn\label{eqn:br1}
+\begin{equation}\label{eqn:br1}
 I_{fivebrane} = N\int_{Z} D_\Omega^{-1}\mu \vee \Omega +\cdots
-\eeqn
-where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \cA^{\bullet}_{F}(Q)$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.
+\end{equation}
+where $\mu \in \Omega^0 (\R) \hotimes \PV^{1,3}(X)\subset \mc{A}^{\bullet}_{F}(Q)$ is a component of a field in the eleven-dimensional theory which satisfies $\thfd_{\Omega} \mu = 0$.
 
@@
 After deforming with this interaction, varying with respect to $D_{\Omega}^{-1}\mu$ yields an equation for $\gamma$ that to linear order reads:
-\beqn
+\begin{equation}
 \thfd D \gamma  = N \delta_Z.
-\eeqn
+\end{equation}
 
@@
 \[
-\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \Pi T^{*} (\cO (\C^{2}) \otimes V) \right)
+\mc{A}^{\bullet}_{\R_{>0}\times Z} \otimes \left ( \Pi T^{*} (\mc{O} (\C^{2}) \otimes V) \right)
 \]
@@
 \[
-\cA^{\bu}_{\R_{>0}\times Z} \otimes \left ( \cO (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\cO (\C^{2})\otimes V)^{*} \right )
+\mc{A}^{\bullet}_{\R_{>0}\times Z} \otimes \left ( \mc{O} (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\mc{O} (\C^{2})\otimes V)^{*} \right )
 \]
@@
 %
-%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
+%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\mc{L}_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
 %
 %On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
-%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
+%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\mc{L}(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
 %\[
@@
 %\]
-%The odd part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
+%The odd part of the super Lie algebra $\mc{L}(\C^5 \times \R)$ is equivalent to the space of holomorphic one-forms on $\C^5$ modulo exact one-forms
 %\[
@@
 %\[
-%j_\infty \colon \cL_{sugra}(\C^5 \times \R) \to L_{sugra} .
+%j_\infty : \mc{L}_{sugra}(\C^5 \times \R) \to L_{sugra} .
 %\]
@@
 %\[
-%\Obs_{sugra} (0) \simeq \clie^\bu \left( \Hat{E(5|10)} \right) .
+%\Obs_{sugra} (0) \simeq \clie^\bullet \left( \Hat{E(5|10)} \right) .
 %\]
@@
 The description of the $S^{4}$ compactification of eleven dimensional supergravity obtained in the previous subsection facilitates a straightforward construction of the twisted supergravity states. 
-The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \cL_{sugra}$ on the seven-manifold $\R_{>0}\times Z$ in proposition \ref{p:dimred}.
+The compactification is described by the pro-local Lie algebra $(p|\mathring M)_{*} \mc{L}_{sugra}$ on the seven-manifold $\R_{>0}\times Z$ in proposition \ref{p:dimred}.
 We will construct the twisted supergravity states by applying geometric quantization ansatz to the phase space at $\infty \in \R_{>0}$.
@@
 The phase space at $\infty\in \R_{>0}$ is computed by restricting to a neighborhood $(a, \infty)\subset \R_{>0}$:
-\beqn
-(p| \mathring M)_* \cL_{sugra}|_{\infty \times Z}= \Omega^{0,\bu}_Z \otimes \left ( \cO (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\cO (\C^{2})\otimes V)^{*} \right )
-\eeqn
+\begin{equation}
+(p| \mathring M)_* \mc{L}_{sugra}|_{\infty \times Z}= \Omega^{0,\bullet}_Z \otimes \left ( \mc{O} (\C^{2})\otimes V \xrightarrow{D\gamma_{BR}} \Pi (\mc{O} (\C^{2})\otimes V)^{*} \right )
+\end{equation}
 
 There is an obvious polarization whose base is given by
-\beqn
-\Omega^{0,\bullet}_Z \otimes \left (\cO (\C^{2})\otimes V \right )
-\eeqn
+\begin{equation}
+\Omega^{0,\bullet}_Z \otimes \left (\mc{O} (\C^{2})\otimes V \right )
+\end{equation}
 
-\begin{dfn}
-\label{dfn:states}
+\begin{defn}
+\label{defn:states}
   The space of twisted supergravity states is
-  \[ \cH_{sugra} = \Sym \left(\overline \Omega^{0,\bullet}_{Z, c} \otimes (\cO (\C^{2}) \otimes V)^{*} \right)\]
+  \[ \mc{H}_{sugra} = \Sym \left(\overline \Omega^{0,\bullet}_{Z, c} \otimes (\mc{O} (\C^{2}) \otimes V)^{*} \right)\]
 where the source denotes compactly supported distributional sections.
-\end{dfn}
+\end{defn}
 
@@
 
-After complexification, the~six-dimensional superconformal algebra is isomorphic to $\lie{osp}(8|4)$.
-The even part of this algebra is $\lie{so}(8) \times \lie{sp}(4)$.
-This algebra contains the six-dimensional $\cN=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\lie{so}(6)$.
-%It also contains the three-dimensional $\cN=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\lie{so}(3)$.
+After complexification, the~six-dimensional superconformal algebra is isomorphic to $\mf{osp}(8|4)$.
+The even part of this algebra is $\mf{so}(8) \times \mf{sp}(4)$.
+This algebra contains the six-dimensional $\mc{N}=(2,0)$ supersymmetry algebra whose odd part is four copies of $S^{6d}_+$, the positive irreducible complex spin representation of $\mf{so}(6)$.
+%It also contains the three-dimensional $\mc{N}=8$ supersymmetry algebra whose odd part is eight copies of $S^{3d}$, the irreducible complex spin representation of $\mf{so}(3)$.
 
@@
 \[
-Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \lie{osp}(8|4)
+Q \in \Pi S^{6d}_+ \otimes \C^4 \subset \mf{osp}(8|4)
 \]
@@
 is three-dimensional (spanned by the anti-holomorphic translations). 
-The supercharge $Q$ acts on $\lie{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
-This cohomology can readily be identified with the subalgebra $\lie{osp}(6|2)$, see \cite{SWsuco2}.
+The supercharge $Q$ acts on $\mf{osp}(8|4)$ by commutator and the resulting cohomology will automatically act on the holomorphic twist of any six-dimensional superconformal field theory. 
+This cohomology can readily be identified with the subalgebra $\mf{osp}(6|2)$, see \cite{SWsuco2}.
 
-%Similarly, the minimal twisting supercharge in the three-dimensional $\cN=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
-The cohomology of $\lie{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\lie{osp}(6|2)$.
+%Similarly, the minimal twisting supercharge in the three-dimensional $\mc{N}=8$ supersymmetry algebra is an element $Q \in \Pi S^{3d} \otimes \C^8$ which is characterized (up to equivalence) by the property that $Q^2 = 0$ and that the image of $[Q,-]$ is two-dimensional.
+The cohomology of $\mf{osp}(8|4)$ with respect to this supercharge is also isomorphic to~$\mf{osp}(6|2)$.
 
-In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\lie{osp}(6|2)$.
-This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\lie{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\cH_{sugra}$ in~\ref{hilbert} is that the twisted symmetry algebra $\lie{osp}(6|2)$ acts on $\cH_{sugra}$.
+In \cite{RSW} we have shown that solutions to equations of motion of our eleven-dimensional theory in the twisted $AdS_{7}\times S^{4}$ background recalled in the previous subsection contains the symmetry algebra $\mf{osp}(6|2)$.
+This is precisely the twist of the superconformal algebra we just discussed, so this statement may be interpreted as the twisted avatar of the fact that $\mf{osp}(8|4)$ acts as isometries on $AdS_{7}\times S^{4}.$ An easy consequence of the result of \cite{RSW} and the definition of $\mc{H}_{sugra}$ in~\ref{defn:states} is that the twisted symmetry algebra $\mf{osp}(6|2)$ acts on $\mc{H}_{sugra}$.
 
@@
 We recall below how the bosonic piece of the algebra
-\beqn
+\begin{equation}
 \label{eqn:gut}
-\lie{sl}(4) \times \lie{sl}(2) \subset \lie{osp}(6|2) 
-\eeqn
+\mf{sl}(4) \times \mf{sl}(2) \subset \mf{osp}(6|2) 
+\end{equation}
 embeds as symmetries, or ghosts, of the eleven-dimensional theory in this twisted background.
 
-However, we first note that the state space $\cH_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
+However, we first note that the state space $\mc{H}_{sugra}$ in fact enjoys an action of a much larger symmetry algebra.
 
 \parsec
-Surprisingly, at the twisted level this symmetry by the super Lie algebra $\lie{osp}(6|2)$ is enhanced to a symmetry by an infinite-dimensional super Lie algebra called $E(3|6)$. 
+Surprisingly, at the twisted level this symmetry by the super Lie algebra $\mf{osp}(6|2)$ is enhanced to a symmetry by an infinite-dimensional super Lie algebra called $E(3|6)$. 
 This is an exceptional simple super Lie algebra and was classified by Kac in \cite{KacClass}. 
 The even part $E(3|6)_{even}$ of this super Lie algebra is a semi-direct product 
-\beqn\label{eqn:evenE36}
-\Vect(\Hat{D}^3) \oplus \lie{sl}(2) \otimes \cO(\Hat{D}^3) 
-\eeqn
-where $\Vect(\Hat{D}^3)$ stands for the Lie algebra of (holomorphic) formal vector fields on the three-disk and $\cO(\Hat{D}^3)$ is the algebra of formal power series in three variables.
+\begin{equation}\label{eqn:evenE36}
+\Vect(\Hat{D}^3) \oplus \mf{sl}(2) \otimes \mc{O}(\Hat{D}^3) 
+\end{equation}
+where $\Vect(\Hat{D}^3)$ stands for the Lie algebra of (holomorphic) formal vector fields on the three-disk and $\mc{O}(\Hat{D}^3)$ is the algebra of formal power series in three variables.
 The odd part $E(3|6)_{odd}$ is 
-\beqn\label{eqn:oddE36}
+\begin{equation}\label{eqn:oddE36}
 \Omega^{1}(\Hat{D}^3, K^{-1/2}) \otimes \C^2  .
-\eeqn
-This is the tensor product of the fundamental $\lie{sl}(2)$ representation with the space of one-forms on the formal three-disk twisted by the line bundle $K^{-1/2}$.
+\end{equation}
+This is the tensor product of the fundamental $\mf{sl}(2)$ representation with the space of one-forms on the formal three-disk twisted by the line bundle $K^{-1/2}$.
 For a description of the Lie bracket we refer to \cite{KacClass}.
@@
 
-The embedding $\lie{osp}(6|2)$ into $E(3|6)$ is described as follows.
-The even summand $\lie{sl}(4)$ simply embeds as the constant, linear, and quadratic vector fields which act on a formal neighborhood of $0 \in \C\mathbb{P}^3$.
-The even summand $\lie{sl}(2)$ embeds as the constant power series in $\lie{sl}(2) \otimes \cO(\Hat{D}^3)$. 
+The embedding $\mf{osp}(6|2)$ into $E(3|6)$ is described as follows.
+The even summand $\mf{sl}(4)$ simply embeds as the constant, linear, and quadratic vector fields which act on a formal neighborhood of $0 \in \C\mathbb{P}^3$.
+The even summand $\mf{sl}(2)$ embeds as the constant power series in $\mf{sl}(2) \otimes \mc{O}(\Hat{D}^3)$. 
 The odd summand $\C^3 \otimes \C^2$ embeds as the constant one-forms and the other odd summand embeds as the linear one-forms 
-\beqn
+\begin{equation}
 \frac12 (z_i \d z_j - z_j \d z_i) \otimes w_a
-\eeqn
-where, here $i \ne j$ and the fundamental $\lie{sl}(2)$ representation is spanned by $w_1,w_2$.
+\end{equation}
+where, here $i \ne j$ and the fundamental $\mf{sl}(2)$ representation is spanned by $w_1,w_2$.
 We are leaving out the twist by the $-1/2$ root of the canonical bundle for simplicity.
@@
 \begin{prop}
-The state space $\cH_{sugra}$ is a representation for $E(3|6)$.
-The representation restricts to the original $\lie{osp}(6|2)$ representation under the embedding above.
+The state space $\mc{H}_{sugra}$ is a representation for $E(3|6)$.
+The representation restricts to the original $\mf{osp}(6|2)$ representation under the embedding above.
 \end{prop}
+
+\todo{PROVE THIS}
 %\begin{proof}
@@
 
-We move on to enumerating the state space $\cH_{sugra}$ on the twisted version of $AdS_7 \times S^4$ in terms of the index. 
+We move on to enumerating the state space $\mc{H}_{sugra}$ on the twisted version of $AdS_7 \times S^4$ in terms of the index. 
 We choose coordinates on flat space as
@@
 The stack of fivebranes wrap 
-\beqn
+\begin{equation}
 w_1=w_2=t=0 .
-\eeqn
+\end{equation}
 Important for us is to recall that part of the ghost system for our eleven-dimensional theory consists of divergence-free vector fields on $\C^5$ which are locally constant along $\R$.
 
-The subalgebra \eqref{eqn:gut} of the twisted superconformal algebra $\lie{osp}(6|2)$ embeds as ghosts in our eleven-dimensional model as follows.
+The subalgebra \eqref{eqn:gut} of the twisted superconformal algebra $\mf{osp}(6|2)$ embeds as ghosts in our eleven-dimensional model as follows.
 \begin{itemize}
 \item
-The subalgebra $\lie{sl}(3) \subset \lie{sl}(4)$ embeds as vector fields rotating the plane $\C^3_z$
-\beqn
-\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \lie{sl}(3) .
-\eeqn
+The subalgebra $\mf{sl}(3) \subset \mf{sl}(4)$ embeds as vector fields rotating the plane $\C^3_z$
+\begin{equation}
+\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \mf{sl}(3) .
+\end{equation}
 By definition, these vector fields are automatically divergence-free.
@@
 \item 
-The subalgebra $\lie{sl}(2)$ ($R$-symmetry) is mapped to the triple
-\beqn
+The subalgebra $\mf{sl}(2)$ ($R$-symmetry) is mapped to the triple
+\begin{equation}
  w_1 \frac{\del}{\del w_2}, \quad w_2 \frac{\del}{\del w_1}, \quad \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
-\eeqn
+\end{equation}
 \item Scaling on the plane $\C^3$ embeds as the vector field
-\beqn\label{eqn:Delta}
+\begin{equation}\label{eqn:Delta}
         \Delta = \sum_{i=1}^3 z_i\frac{\del}{\del z_i} - \frac 32\sum_{a=1}^2 w_a\frac{\del}{\del w_a}\in \PV^{1,0}(\C^5)\otimes \Omega^0 (\R).
-\eeqn
+\end{equation}
 \end{itemize}
@@
 This describes an embedding of the algebra 
-\beqn\label{eqn:gut2}
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{sl}(4) \times \lie{sl}(2) 
-\eeqn
+\begin{equation}\label{eqn:gut2}
+\mf{sl}(3) \times \mf{sl}(2) \times \mf{gl}(1) \subset \mf{sl}(4) \times \mf{sl}(2) 
+\end{equation}
 into the ghosts of our model.
-The dimension of a Cartan subalgebra of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$ is four and accordingly, the equivariant character we study has four fugacities.
+The dimension of a Cartan subalgebra of $\mf{sl}(3) \times \mf{sl}(2) \times \mf{gl}(1)$ is four and accordingly, the equivariant character we study has four fugacities.
 We choose these explicitly as follows:
 \begin{itemize}
-  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\lie{sl}(3)$ which is spanned by the vector fields
-  \beqn
+  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\mf{sl}(3)$ which is spanned by the vector fields
+  \begin{equation}
   h_1 = z_1 \frac{\del}{\del {z_1}} - z_2 \frac{\del}{\del{z_2}} , \quad h_2 = z_2 \frac{\del}{\del{z_2}} - z_3 \frac{\del}{\del{z_3}}.
-  \eeqn
-  \item $r$ denotes a generator for the Cartan of a $\lie{sl}(2)$ which is generated by the element 
-  \beqn
+  \end{equation}
+  \item $r$ denotes a generator for the Cartan of a $\mf{sl}(2)$ which is generated by the element 
+  \begin{equation}
   \label{eqn:hCartan}
   h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
-  \eeqn
-\item $q$ denotes a generator for the Cartan of the~$\lie{gl}(1)$ which is generated by the element $\Delta$ from equation~$\eqref{eqn:Delta}$. 
+  \end{equation}
+\item $q$ denotes a generator for the Cartan of the~$\mf{gl}(1)$ which is generated by the element $\Delta$ from equation~$\eqref{eqn:Delta}$. 
 \end{itemize}
 
-The twisted supergravity states $\cH_{sugra}$ form a representation for $\lie{osp}(6|2)$. 
+The twisted supergravity states $\mc{H}_{sugra}$ form a representation for $\mf{osp}(6|2)$. 
 The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates on $\C^2_w \times \C^3_z$.
@@
 
-We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\cH_{sugra}$:
-\beqn
-f_{sugra}(t_1,t_2,r,q) = \Tr_{\cH_{sugra}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
-\eeqn
+We enumerate single particle supergravity states via computing the super trace of the operator $q^Y t_1^{h_1} t_2^{h_2} r^h$ acting on $\mc{H}_{sugra}$:
+\begin{equation}
+f_{sugra}(t_1,t_2,r,q) = \tr_{\mc{H}_{sugra}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
+\end{equation}
 The super trace means that there is an extra factor of $(-1)^F$, where $F$ is parity (fermion number), when computing the ordinary trace.
 
-The space of supergravity states given in definition \ref{dfn:states} is given in terms of compactly supported Dolbeault forms on $\C^3$. 
+The space of supergravity states given in definition \ref{defn:states} is given in terms of compactly supported Dolbeault forms on $\C^3$. 
 On $Z = \C^3$, the compactly supported distributions defined by 
-\beqn
+\begin{equation}
 \alpha \mapsto \del_{z_1}^{n_1} \del_{z_2}^{n_2} \del_{z_3}^{n_3} \alpha |_{z=0}
-\eeqn
-combine to span a dense subspace of $\Bar{\Omega}^{0,\bu}_c(\C^3)$.
-Using this topological basis for distributions and the explicit description of $\cH_{sugra}$ in definition \ref{dfn:states} the following proposition is an immediate computation.
+\end{equation}
+combine to span a dense subspace of $\Bar{\Omega}^{0,\bullet}_c(\C^3)$.
+Using this topological basis for distributions and the explicit description of $\mc{H}_{sugra}$ in definition \ref{defn:states} the following proposition is an immediate computation.
 
@@
 \label{prop:sugraindex1}
-The single particle index of the space of twisted supergravity states~$\cH_{sugra}$ is given by the following expression
-\beqn
+The single particle index of the space of twisted supergravity states~$\mc{H}_{sugra}$ is given by the following expression
+\begin{equation}
 \label{eqn:sugra_index}
 f_{sugra} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
-\eeqn
+\end{equation}
 The full (multiparticle) index is defined to be the plethystic exponential 
-\beqn
+\begin{equation}
 {\rm PExp}\left[f_{sugra}(t_1,t_2,r,q)\right] .
-\eeqn
+\end{equation}
 \end{prop}
 
-To simplify the form of this index we can introduce a different parametrization of the Cartan of $\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1)$.
-First, we can parameterize the Cartan of $\lie{sl}(3)$ by the vector fields
-  \beqn\label{eqn:ys}
+To simplify the form of this index we can introduce a different parametrization of the Cartan of $\mf{sl}(3) \times \mf{sl}(2) \times \mf{gl}(1)$.
+First, we can parameterize the Cartan of $\mf{sl}(3)$ by the vector fields
+  \begin{equation}\label{eqn:ys}
   -(\log y_1) z_1 \frac{\del}{\del {z_1}} - (\log y_2) z_2 \frac{\del}{\del{z_2}} - (\log y_3) z_3 \frac{\del}{\del{z_3}} .
-  \eeqn
+  \end{equation}
 where $y_1,y_2,y_3$ are parameters which satisfy the single constraint
-\beqn
+\begin{equation}
 y_1 y_2 y_3 = 1 .
-\eeqn
+\end{equation}
 In terms of the variables $t_1,t_2$ used above we have
-\beqn
+\begin{equation}
 y_1 = t_1^{-1},\quad y_2 = t_1 t_2^{-1}, \quad y_3 = t_2 .
-\eeqn
-Second, we can parametrize the Cartan of the remaining subalgebra $\lie{sl}(2) \times \lie{gl}(1)$ by the two vector fields
-\beqn
-\til{h} = h + \frac12 \Delta \quad \text{and} \quad \Delta
-\eeqn
+\end{equation}
+Second, we can parametrize the Cartan of the remaining subalgebra $\mf{sl}(2) \times \mf{gl}(1)$ by the two vector fields
+\begin{equation}
+\tilde{h} = h + \frac12 \Delta \quad \text{and} \quad \Delta
+\end{equation}
 where $\Delta$ is as in equation \eqref{eqn:Delta} and $h$ is as in \eqref{eqn:hCartan}.
-We denote by $y$ the generator of the Cartan corresponding to the vector field $\til{h}$ and by $q$ (as above) the generator corresponding to~$\Delta$.
+We denote by $y$ the generator of the Cartan corresponding to the vector field $\tilde{h}$ and by $q$ (as above) the generator corresponding to~$\Delta$.
 In terms of the variable~$r$ used above we have 
-\beqn
+\begin{equation}
 y = q^{1/2} r .
-\eeqn
+\end{equation}
 
 Using the paramterization fo the Cartan given by the variables $y_i,y,\Delta$ we obtain the equivalent expression for the index \eqref{eqn:sugra_index} as 
-\beqn
+\begin{equation}
 \label{eqn:Kim_sugra}
 f_{sugra} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
-\eeqn
+\end{equation}
 We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
-%\beqn
+%\begin{equation}
 %t_1 = y_1^{-1} , \quad t_2 = y_3, \quad r = q^{-1/2} y 
-%\eeqn
+%\end{equation}
 
 Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
-\beqn
+\begin{equation}
 q = x^4, \quad t_1 = y_2, \quad t_2 = y_1, \quad r^2 = z .
-\eeqn
+\end{equation}
 (Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
@@
 We consider the specialization of this index 
-\beqn
+\begin{equation}
 q=r^2, t_2=1 
-\eeqn
+\end{equation}
 which is known as the Schur limit.

### 2023-05-11 graviton spectra/content/br.tex
graviton spectra

\section{Twisted Backreactions}
\label{sec:ads}

As remarked above, in eleven-dimensional supergravity, the $AdS_7 \times S^4$ and $AdS_4\times S^7$ backgrounds are obtained by backreacting a number of M5 branes and M2 branes in flat space \cite{Maldacena:1997re,WittenAdS}. In this section, we wish to give an account of this procedure at the level of our twisted theory in eleven-dimensions. Before describing the specific examples of interest, we begin with some generalities.

Suppose we have a theory of gravity on the total space of a vector bundle. In this thesis, we are interested in holomorphic-topological field theories, and in this context, the bundle projection is a map of THF manifolds, and the gravitational theory is a local moduli problem that describes, in part, deformations of the THF structure on the total space. Operationally, producing the theory in the backreacted geometry is the output of the following two-step procedure.

\begin{itemize}
  \item Place the theory on the complement of the zero section. 
  \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element, thought of as the flux sourced by branes wrapping the zero section. More rigorously, the zero section determines a certain curved Maurer-Cartan equation, and the desired Maurer-Cartan element is a solution to this equation. 
\end{itemize}

This procedure is implemented at the level of the $\Omega$-deformed nonminimal twist on flat space in the appendix of \cite{CostelloM5}, and in \cite{raghavendran2022holographic} the procedure is carried about for M5 branes in our eleven-dimensional model in some global generality. For the purposes of this thesis however, we will content ourselves with examples on flat space.

\subsection{The ${\mr AdS}_4 \times S^7$ background}

In this section we introduce the analog of the ${\mr AdS}_4 \times S^7$ background in our conjectural description of the minimal twist of eleven-dimensional supergravity.

\parsec[]

We begin by viewing the eleven-dimensional manifold $\R\times \C^5$ as 
\[
\operatorname{Tot}(K^{1/4}_\C\otimes \C^4\to \R\times \C_z)
\]
where we have abusively used $K^{1/4}_\C\otimes \C^4$ to denote its pullback along the natural projection $\R\times \C\to \C$. Thinking of flat space in this way is simply a way to record weights under natural scaling actions. We will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/4}_\C\otimes \C^4$.

We carry out the above procedure. Consider a stack of $N$ M2 branes wrapping the zero section $\R\times \C_z$. A natural interaction to consider is 
\[
I_{M2}(\gamma) = N\int_{\C_z} \gamma + \cdots
\] 
which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$. We have only indicated the lowest order coupling, the $\cdots$ indicate higher-order couplings which will be higher order in the fields of the eleven-dimensional theory and explicitly involve the fields in the worldvolume theory.

This coupling is justified by comparison with the physical theory and by dimensional reduction. 
Indeed, as discussed in~\S\ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity. Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.

Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$. As is shown in \cite{CLsugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by 
\[
I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma + \cdots
\] 
where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA supergravity. It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.

\parsec[sec:m2backreact]

The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M2}(\gamma)$. 
Varying the deformed action with respect to $\gamma$,
we obtain the equation of motion
\begin{equation}\label{eqn:ads4eom1}
\dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma = N \Omega^{-1} \delta_{w=0} .
\end{equation}
Here $[-,-]$ is the Schouten bracket. 
Varying $\beta$, we obtain the equation of motion
\begin{equation}\label{eqn:adseom2}
\div \mu = 0 .
\end{equation}

\begin{lem}\label{lem:m2flux}
Let
\[
 F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \partial_z .
\]
Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
satisfies the above equations of motion in the presence of a stack of $N$ M2 branes:
\begin{align*}
\dbar (N F_{M2}) + \frac12 [N F_{M2}, N F_{M2}] & = N \Omega^{-1} \delta_{w=0} \\
\div (N F_{M2}) & = 0  .
\end{align*}
Here we set all components of the field $\gamma$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

\begin{proof}
Upon specializing $\gamma = 0$, the last term in the first equation above vanishes. The equation $\dbar F_{M2} = \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\C^4 \, \setminus \, 0$. 
It is clear that $\div F_{M2} = 0$ and 
\[
[F_{M2}, F_{M2}] = 0
\] 
by simple type reasons. 
\end{proof}

We summarize the output of our computation with a definition.

\begin{defn}\label{defn:ads4}
Let $\mc E^N_{AdS_4\times S^7}$ denote the classical BV theory on $\operatorname{Tot} (K_\C^{1/4}\otimes \C^4 \to \R\times \C_z)\setminus 0(\R\times \C)$ given by the sheaf of cochain complexes $\mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} )}$, with BV pairing induced from $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu + NF_{M2}, \nu, \beta, \gamma) + J(\gamma).\]
\end{defn}

\begin{rmk}
Note that upon expanding the interaction around $NF_{M2}$, the cubic term in $S_{BF,\infty}$ will contribute a differential which acts on $\gamma$ and $\mu$ by bracketing with $NF_{M2}$. We accordingly denote this differential $[NF_{M2}, - ] $, and we see that the sheaf of cochain complexes underlying $\mc E_{AdS_4\times S^7}$ is in fact \[\left ( \mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} ) }, \delta^{(1)} + [NF_{M2},-] \right )\] where $\delta^{(1)}$ denotes the original linearized BRST differential.
\end{rmk}

\begin{conj}\label{conj:ads4}
The minimal twist of eleven-dimensional supergravity on the $AdS_4\times S^7$ background with $N$ units of M2 brane flux supported on $S^7$ is perturbatively equivalent to $\mc E^N_{AdS_4\times S^7}$.
\end{conj}

To verify this conjecture, we should directly twist eleven-dimensional supergravity on the $AdS_4\times S^7$ spacetime. Doing so seems difficult - while it is likely not hard to identify the covariantly constant nilpotent spinors which define the twist, it seems more difficult to establish a perturbative equivalence with our description above. A modification of the pure spinor superfield formalism to symmetric spaces such as cosets for the superconformal group might make such checks more feasible. In lieu of such, we will instead pursue other consistency checks in the following two sections{}.

\subsection{The ${\mr AdS}_7 \times S^4$ background}

We similarly introduce an analog of the ${\mr AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity. As before, we begin by viewing our eleven-dimensional manifold $\R\times \C^5$ as 
\[
\operatorname{Tot}(\R \oplus K_{\C^3}^{1/2}\otimes \C^2 \to \C^3_z)
\]
to record weights under natural scaling actions. We once again will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/2}_{\C^3}\otimes \C^2$, and we use $t$ to denote a fiber coordinate on the trivial bundle $\R \to \C^3_z$.

\parsec[sec:m5coupling]

To repeat the procedure in the previous subsection, we begin by discussing how the eleven-dimensional theory couples to M5 branes. 
Consider a stack of $N$ M5 branes wrapping the zero section $\C^3_z$.

It is natural to consider the nonlocal interaction 
\[
I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega +\cdots 
\]
Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. 
We argue that this coupling is consistent with expectations from the physical theory and from dimensional reduction.

The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory (\S\ref{s:components}). 
In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the Hodge star of the $G$-flux and integrating it over the M5 worldvolume. Our twist contains no fields corresponding to components of such a primitive; hence such a magnetic coupling is reflected in the appearance of $\div^{-1}$.

We may once again justify this coupling by dimensional reduction to IIA supergravity. Reducing on the circle along the directions the M5 branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\C^4 \times \R^2$ with $N$ $D4$ branes wrapping $\C^2 \times \R$.

In \cite{CLsugra}, it is shown that the magnetic coupling of $D4$ branes to the $SU(4)$ twist of IIA is of the form
\[
N \int _{\C^2 \times \R} \div^{-1} \mu \vee \Omega_{\C^4} + \cdots .
\]
Again, we have only explicitly indicated the first-order piece of the coupling.

\parsec[s:m5backreact]

The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M5}(\mu)$.

Varying the potential $\div^{-1} \mu$, we obtain the following equation of motion involving the field $\gamma$:
\begin{equation}\label{eqn:m5eom1}
\dbar \del \gamma + \div \left(\frac{1}{1-\nu} \mu\right) \wedge \del \gamma = N \delta_{w_1=w_2=t=0} .
\end{equation}
Notice that there is an extra derivative compared to the equation of motion arising from varying the field $\mu$. 
This equation only depends on $\gamma$ through its field strength $\del \gamma$.

Varying $\gamma$ we obtain the equation of motion 
\begin{equation}\label{eqn:m5eom2}
(\dbar + \d_\R) \mu + \del \gamma \del \gamma = 0 .
\end{equation} 
Again, this only depends on $\gamma$ through its field strength $\del \gamma$.

\begin{lem}
\label{lem:ads7flux}
Let
\[
F_{M5} = \frac{1}{(2\pi i)^3} \frac{\bar{w}_1 \d \bar{w}_2 \wedge \d t - \bar{w}_2 \d \bar{w}_1 \wedge \d t + t \d \bar{w}_1 \wedge \d \bar{w}_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
\]
Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
\begin{align*}
\dbar (NF_{M5}) + \d_{\R} (NF_{M5}) & = N \delta_{w_1=w_2=t=0}  \\ 
(NF_{M5}) \wedge (NF_{M5}) & = 0 .
\end{align*}
Here, we set all components of the field $\mu$ equal to zero (as well as the fields $\nu,\beta$). 
\end{lem}

\begin{proof}
The first equation,
\[
\dbar F + \d_{\R} F = N \delta_{w_1=w_2=t=0},
\]
characterizes the kernel representing $N$ times the residue class for a four-sphere in 
\[
(\C^2 \times \R) \setminus 0 \simeq S^4 \times \R .
\] 
That is
\[
\oint_{S^4} N F = N 
\]
for any four-sphere centered at $0 \in \C^2 \times \R$.

The second equation $F \wedge F = 0$ follows by simple type reasons. 
\end{proof}

Once again, we summarize our findings in a definition. 
\begin{defn}\label{defn:ads7}
Let $\mc E^N_{AdS_7\times S^4}$ denote the classical BV theory on $\operatorname{Tot}(\R \oplus K_{\C^3}^{1/2}\otimes \C^2 \to \C^3_z)\setminus 0(\C^3_z)$ given by the sheaf of cochain complexes $\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}$, with BV pairing induced from that on $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu, \nu, \beta, \gamma +N\del^{-1} F_{M5}) + J(\gamma + N \del^{-1} F_{M5}).\]
\end{defn}

\begin{rmk}
Note that both terms in the action only depend on $\gamma$ through its holomorphic derivatives so the above expression for the action is indeed well-defined.

As before, upon expanding the interactions around $NF_{M5}$, the cubic terms in both $S_{BF,\infty}$ and $J$ will contribute differentials. From $S_{BF,\infty}$, we get a differential which takes a $\mu$ type field to the Schouten bracket $N[F_{M5}, \mu]$ and from $J$, we get a differential which acts as $\gamma\mapsto N F_{M5} \wedge \del \gamma$. We accordingly denote this differential $[NF_{M5}, - ] $, and the sheaf of cochain complexes underlying $\mc E_{AdS_7\times S^4}$ is in fact \[\left (\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}, \delta^{(1)} + [NF_{M5},-] \right )\] where $\delta^{(1)}$ denotes the original linearized BRST differential.
\end{rmk}

\begin{conj}\label{conj:ads7}
The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E_{AdS_7\times S^4}$. 
\end{conj}

### 2023-05-11 graviton spectra/content/e16.tex
graviton spectra

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

%\parsec[s:membraneobs]
%
%
%\parsec[s:fivebraneobs]
%
%Let $Z$ be a complex threefold. 
%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\mc{L}_{single}$ on $Z$. 
%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
%the cochain complex
%\[
%\clie^\bullet\left(\mc{L}_{single}(U)\right) .
%\]
%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bullet(\mc{L}_{single})$.
\section{$E(1|6)$ modules from gravitons on $AdS_4\times S^7$}\label{sec:e16}

Having justified that the spaces of supergravity states constructed in the previous subsection are in fact counting gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively, we turn to studying representation theoretic properties of these state spaces. In this section, we focus on the case of gravitons on $AdS_4\times S^7$, using the description of the state space afforded by proposition \ref{prop:altstates} which describes it as the costalk of a factorization envelopes of the boundary conditions $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$.

We construct a certain $\C^\times$-action on the boundary fields $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$ equipped with the $L_\infty$ structure from remark \label{rmk:nottransferred} with the feature that the zeroth weight spaces are a local version of another exceptional linearly compact super-Lie algebras, $E(1|6)$. This in particular readily gives a decomposition of the state space $\mc H_{AdS_4\times S^7}$ into $E(1|6)$-modules. We explicitly characterize the summands of this decomposition with their module structures and give closed form expressions for their characters.

\subsection{The graviton decomposition of twisted $AdS_4\times S^7$}
\parsec{}
We consider a particular decomposition of the space of states $\mc H_{AdS_4\times S^7}$. It is induced by a decomposition of the boundary fields $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{{r=0}}_{AdS_4\times S^7} )$ introduced in section \ref{sec:transversebc}  The decomposition is induced by a $\C^\times$ action on the boundary fieldsboundary fields $\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$ that mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.

Explicitly, the action is given as follows 
\begin{itemize}
\item On the fields 
\[
\mu(t; w_a,z) \in \C[w_1, \cdots, w_4]\{\del_{w_a}\} \otimes \Omega^\bullet_\R(I) \otimes \Omega^{0,\bullet}_{\C} (U) \oplus \C[w_1, \cdots, w_4]\otimes \Omega^\bullet_\R(I)\otimes \Omega^{0,\bullet}_{\C}(U, T)\] 
the action is
\[
\lambda \cdot \mu(t; w_a,z) = \mu(t; \lambda w_a , z).
\]
\item On the fields $\nu(t; w_a,z) \in \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes \Omega^{0,\bullet}_{\C}(U)$ the action is
\[
\lambda \cdot \nu(t; w_a,z) = \nu(t; \lambda w , z).
\]
\item On the fields $\beta(t; w_a,z) \in  \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes \Omega^{0,\bullet}_{\C}(U)$ the action is
\[
\lambda \cdot \beta(t; w_a,z) = \lambda^{-2} \beta(t; \lambda w_a , z).
\]
\item On the fields 
\[
\gamma(t; w_a,z) \in  \C[w_1, \cdots, w_4] \{\d w_a\} \otimes \Omega^{\bullet}_\R(I) \otimes\Omega^{0,\bullet}_{\C} (U) \oplus  \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes\Omega^{0,\bullet}_{\C}(U, \Omega^1)
\] 
the action is
\[
\lambda \cdot \gamma(t; w_a,z) = \lambda^{-2} \gamma(t; \lambda w _a, z).
\]
\end{itemize}

The following result is a straightforward if lengthy computation. We state it without proof.

\begin{prop}\label{prop:ads4decomp}
The $L_\infty$ structure on $\Pi\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} )$ identified in section \ref{sec:transversebc} is equivariant for this $\C^\times$ action.
\end{prop}

This result induces a product decomposition 
\[
\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} ) = \prod _{n\geq 2} \mc F^{(n)}_{\R\times \C}
\]

where for each open set $I\times U\subset\R\times \C$, we have that \[\mc F_{\R\times \C}^{(n)} (I\times U) \subset \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C (U, \mc L^{r=0}_{AdS_4\times S^7} )\] is the weight $n$ eigenspace with respect to the above $\C^\times$ action. In particular, we see that $\mc F^{(0)}_{\R\times \C}$ is itself a local dg-Lie algebra, for which  every $\mc F^{(n)}_{\R\times \C}$ is a module.

\subsection{The lowest piece: the holomorphic-topological twist of the 3d $\mc N=8$ BLG theory}\label{sec:BLG}
\parsec[] The first nontrivial case is the weight ${(-2)}$ piece. We have the following

\begin{lem}
There is a quasi-isomorphism \[\mc F^{(-2)}_{\R\times \C} \cong \Omega^\bullet_{\R\times \C}.\]
\end{lem}
\begin{proof}
The only sections which contribute are those of type $\beta$ or $\gamma$ with no form components along the fiber directions. Therefore, we see directly that \[\mc F^{(-2)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C ( \mc O \xrightarrow{\del} \Omega^1 ).\] 
\end{proof}

\parsec[] The next nontrivial case is the weight ${(-1)}$ piece.

\begin{lem}
There is a quasi-isomorphism \[ \mc F^{(-1)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
\end{lem}
\begin{proof}
On an open set of the form $I\times U$, the sections of the specified weight are:
\begin{itemize}
\item fields of type $\mu$ of the form $\mu_a(t; z) \del_{w_a}$. As the $w_a$ are fiber coordinates on $K^{1/4}_\C$, these fields transform as sections of $K^{1/4}_\C$.
\item fields of type $\gamma$ of the form $\gamma_a(t;z) \d w_a$. These fields transform as sections of $K^{3/4}_\C$. 
\end{itemize}
\end{proof}

\parsec[]
We wish to flag an appearance of $\mc F^{(-1)}_{\R\times \C}$ in supersymmetric physics in three-dimensions. There is a highly supersymmetric Chern-Simons-matter theory discovered independently by Bagger-Lambert \cite{Bagger_2007}, \cite{Bagger:2007jr} and Gustavsson \cite{Gustavsson:2007vu}. The aptly named BLG theory has $\mc N=8$ superconformal symmetry, and admits a holomorphic-topological twist that was computed by Garner in \cite{Garner2022vds}.

The sheaf of complexes $\mc F^{(-1)}_{\R\times \C}$ matches the field contents of the holmorphic-topological twist of the BLG theory, and as such, it can be equipped with an $L_\infty$ structure under which it is perturbatively equivalent to the twisted BLG theory. In work-in-progress with Garner and Williams, we show that the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ in fact preserves this $L_\infty$-structure.

\subsection{The zero-th piece: A local version of $E(1|6)$}
\parsec[] The next nontrivial case is the weight ${(0)}$ piece. This factor is special because it carries the induced structure of a local $L_\infty$ algebra on $\R\times \C$. We will prove that it is equivalent to a local Lie algebra version of the exceptional super-Lie algebra $E(1|6)$.

We first recall the definition of this super-Lie algebra \cite{KacBible}
\begin{defn}\label{defn:e(1|6)}
Let $E(1|6)$ be the following super-Lie algebra. 
\begin{itemize}
\item The even part of $E(1|6)_0$ given by the semidirect product Lie algebra $\Gamma (\hat D, T) \ltimes \left( \Gamma (\hat D, \mc O) \otimes \mf{sl}(4) \right )$
\item The odd part $E(1|6)_1$ is given by the (unique) nontrivial extension of $E(1|6)_0$-modules 
\[0\to \Sym^2 (\C^4)\otimes K^{1/2}_\C \to E(1|6)_1 \to \wedge^2 (\C^4) \otimes K^{-1/2}_\C \to 0.\]

\end{itemize}
The only remaining bracket to be specified, the odd bracket, is given as follows.
\begin{itemize}
\item Given sections $A \otimes f \d z^{1/2}\in \Sym^2 (\C^4)\otimes K^{1/2}_\C$ and $B\otimes g \del_z^{1/2}\in \wedge^2 (\C^4)\otimes K^{-1/2}_\C$, we have that
\[
[A \otimes f \d z^{1/2}, B\otimes g \del_z^{1/2}] = A*B \otimes fg \in \mf{sl}(4)\otimes \mc O.
\]
Here, $*$ refers to the hodge star of $B$ and we are viewing $A$ and $*B$ as symmetric and skew-symmetric $4\times 4$ matrices respectively; their product is traceless.

\item Given sections $A \otimes f \del_z^{1/2}, B\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have that 
\begin{align*}
[A\otimes f \d z^{-1/2} , B \otimes g \d z^{-1/2} ] & = \tr (A * B) \otimes fg \del_z + \frac12 (A*B)_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
& \in \Gamma (\hat D, T) \ltimes \left (\mf {sl}(4) \otimes \Gamma (\hat D, \mc O) \right ) .
\end{align*}
where again $*$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
\end{itemize}
\end{defn}

The relationship between this super-Lie algebra and our decomposition is established through the following result.

\begin{prop}
There is an equivalence of super-Lie algebras
\[
\mc F^{(0)}_{\R\times \C, c}  (0) \cong E(1|6).
\]
\end{prop}
\begin{proof}
We will begin by trying to characterize the local $L_\infty$-algebra $\mc F^{(0)}_{\R\times \C}$. We claim that it is quasi-isomorphic to a local version of $E(1|6)$.

Indeed, it is easy to see that the weight zero sections consists of the following cochain complex 
\begin{equation}
\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\C[w_a\del_{w_b}]\otimes \mc O\ar[r, "\del^W_\Omega"]  & \mc O \\ 
\T \ar[ur] & \\
\Sym^2 (\C^4)\ar[r, "\del_W"]\ar[dr] & \C[w_adw_b] \otimes K^{-1/2}\ \\
& \Sym^2 (\C^4)\otimes \Omega^1\otimes K^{-1/2}
\end{tikzcd} \right)
\end{equation}
Of course, the differentials are just appropriate components of the divergence operator and holomorphic deRham operator. We can compute cohomology by way of a spectral sequence whose first page is the cohomology with respect to $\del^W_\Omega + \del_W$. We see that the differential $\del^W$ maps surjectively onto functions and its kernel is isomorphic to $\mf{sl}(4)\otimes \mc O$. Likewise, the differential $\del_W$ is the canonical inclusion of $\mf{sl}(4)$ representations $\Sym^2 (\C^4)\to \C^4\otimes \C^4$. Its cokernel is a copy of $\wedge^2 \C^4$.

Thus, we see that this page of the spectral sequence is given by
\begin{equation}
\mc E(1|6) \define \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\T & \wedge^2 (\C^4) \otimes K^{-1/2} \\
\mf {sl}(4)\otimes \mc O & \Sym^2 (\C^4)\otimes K^{1/2}
\end{tikzcd} \right)
\end{equation}
and there are no non-zero differentials so the spectral sequence degenerates.

To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} )$ is in fact given by the same formulae as the brackets on $E(1|6)$ in equation \ref{defn:e(1|6)}, it will be useful to provide an explicit quasi-isomorphism $\Psi^{(0)} : \mc E(1|6) \to \mc F^{(0)}_{\R\times \C}$. On an open set $I\times D\subset \R\times \C$, this is defined as follows

\begin{itemize}
\item Given a section $g(t; z) \del_z \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C (D, T)$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I \times D$, we define
\begin{align*}
\Psi^{(0)} (g(t;z)\del_z) &= g(t;z)\del_z - \frac 14 (\del_z g(t; z)) w_a\del_{w_a} \\
&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, T \oplus \C\{w_a\del _{w_b} \} \right )
\end{align*}
\item Given a section $A_{ab} \otimes g(t; z) \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \mf{sl}(4)\otimes \mc O \right )$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I \times D$ and $A_{ab}\in \mf {sl}(4)$
\begin{align*}
\Psi^{(0)} (A_{ab} \otimes g(t;z)) &= g(t;z)A_{ab}w_a\del_{w_b} \\
&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \C\{w_a\del _{w_b}\} \right )
\end{align*}

\item Given a section $A_{ab} \otimes g(t; z)\d z^{-1/2} \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \wedge^2 (\C^4) \otimes K^{-1/2}\right )$
where $g(t;z)$ is a mixed deRham-Dolbeault form on $I\times D$ and $A_{ab} \in \wedge^2 (\C^4)$ we define
\begin{align*}
\Psi^{(0)} (A_{ab} \otimes g(t; z)\d z^{-1/2}) &= g(t;z)  A_{ab} w_a \del_{w_b} \\
&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \C\{w_a\del _{w_b} \}\otimes K^{-1/2} \right )
\end{align*}

\item Given a section 
$A_{ab} \otimes g(t; z)\d z^{1/2} \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \Sym^2 (\C^4) \otimes K^{1/2}\right )$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I\times D$ and $A_{ab} \in \Sym^2 (\C^4)$ we define
\begin{align*}
\Psi^{(0)} (A_{ab} \otimes g(t; z)\d z^{1/2}) &= g(t;z)  A_{ab} w_a w_b \d z \\
&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \Sym^2 (\C^4) \otimes \Omega^1 \otimes K^{-1/2} \right )
\end{align*}
\end{itemize}
It is easy to see that $\Psi^{(0)}$ is a quasi-isomorphism and a straightforward if lengthy check confirms that it preserves Lie brackets. The result then follows from computing the limit of $\mc E(1|6)_c (I\times D)$ over open sets containing the origin. 
\end{proof}

\begin{rmk}
We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4\times S^7} )$ over every open set containing the origin. The image of the map lands exactly in the step $\mc F^{(0)}_{\R\times \C}$ of the decomposition from proposition \ref{prop:ads4decomp}. Therefore we see that $E(1|6)$ contains $\mf{osp}(6|2)$ as a finite dimensional subalgebra.  
\end{rmk}

\subsection{General summands and $E(1|6)$-modules}
We now move on to giving an explicit description of the general summand $\mc F^{(j)}$ for $j \geq 1$.

We first fix some notation for irreducible highest weight representations of $\mf{sl}(4)$. Let $\mf {h}\subset \mf{sl}$ be the Cartan given by diagonal matrices and let $L_i\in \mf {h}^*$ be the linear functional that picks out the $i$-th diagonal entry. We may accordingly write $\mf h^* = \C \{L_1, L_2, L_3, L_4\}/(L_1+\cdots + L_4)$. We will write $\Gamma_{a_1,a_2, a_3}$ for the irreducible representation of $\mf {sl}(4)$ of highest weight $(a_1+a_2+a_3)L_1+(a_2+a_3)L_2 + a_3L_3$.

\begin{prop}
Let $j\geq 1$. The complex of vector bundles $\mc F^{(j)}_{\R\times \C}$ is quasi-isomorphic to 
\begin{equation}
\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C \left (
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\Gamma_{j,1,0} \otimes K^{-j/4} & \Sym^{j+2}(\C^4) \otimes \Omega^1 \otimes K^{-(j+2)/4} \\
\Sym^j (\C^4) \otimes \T \otimes K^{-j/4} & \Gamma_{j+1, 0, 1} \otimes K^{-(j+2)/4}
\end{tikzcd} \right )
\end{equation}

\end{prop}
\begin{proof}
We begin by noting that we can explicitly describe $\mc F_{\R\times \C}^{(j)}$ as $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C (F^{(j)})$ where $F^{(j)}$ denotes the following dg-vector bundle:
\begin{equation}
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\Sym^{j+1} (\C^4) \otimes (\C^4)^* \otimes K^{-j/4} \ar[dr, "\del^W_\Omega"] \\ & \Sym^j (\C^4) \otimes K^{-j/4} \\ 
\Sym^j (\C^4) \otimes \T \otimes K^{-j/4} \ar[ur, "\del^V_\Omega"'] & \\
& \Sym^{j+2}(\C^4) \otimes \T^*\otimes K^{-(j+2)/4}\\ 
\Sym^{j+2} (\C^4) \otimes K^{-(j+2)/4}\ar[ur, "\del_V"] \ar[dr, "\del_W"'] \\
& K^{-(j+2)/4}\otimes \Sym^{j+1}(\C^4) \otimes \C^4 . 
\end{tikzcd}
\end{equation}

Note that the differentials here are all $\mf{sl}(4)$ equivariant maps, tensored with a differential operator acting on sections of a bundle on $\C$. In particular

\begin{itemize}
\item The differential $\del^W_\Omega$ involves the canonical projection 
\[\Sym^{j+1} (\C^4)\otimes (\C^4)^* \to \Sym^j (\C^4).\] Its kernel is precisely the irreducible highest weight representation $\Gamma_{j+1, 0 ,1}$.

\item The differential $\del_W$ is the canonical inclusion 
\[\Sym^{j+2} (\C^4) \to \Sym^{j+1}(\C^4) \otimes \C^4.\] Its cokernel is the irreducible highest weight representation $\Gamma_{j, 1, 0}$.
\end{itemize}

We can compute the cohomology using a spectral sequence whose first page is given by the cohomology with respect to $\del^W_\Omega + \del_W$. There are no further differentials on this page so the result follows. 
\end{proof}

\subsection{Characters of $E(1|6)$-modules}
Note that the decomposition of the state space $\Sym (\mc H_{AdS_4\times S^7} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{}

\[\chi \left (\Sym (\mc H_{AdS_4\times S^7} ) \right )= \prod_{j\geq -2} \chi \left ( \mc U (\mc F^{(j)} _{\R\times \C} )(0)\right ).\]

We end this section by computing each of the characters $\chi \left ( \mc U (\mc F^{(j)} _{\R\times \C} )(0)\right )$. We will express our characters in terms of characters of highest weight respresentations of $\mf{sl(4)}$ which we denote $\chi^{\mf{sl}(4)}(\Gamma_{a_1,a_2, a_3} )$.

\parsec[]
From the characterization in \ref{}, the lowest step of the decomposition $\mc F^{(-2)}$ is just given by the deRham complex on $\R\times \C$, and accordingly the character of $\mc F^{(-2)}_{c}(0)$ is the constant function 1.

\parsec[]
We proceed to the next step of the decomposition, using the characterization in \ref{}.

\begin{prop}
The character $\chi \left ( \mc U(\mc F_{\R\times \C}^{(-1)})(0)\right )$ is given by the plethystic exponential of the following expression:
\begin{equation}
f_{-1}(t_1, t_2, t_3, q) = \frac{q\left (q^{-3/4}(t_1+ t_2+t_3 + t_1^{-1} t_2^{-1} t_3^{-1} )-q^{-1/4}(t_1^{-1} + t_2^{-1}+t_3^{-1} + t_1t_2t_3)\right )}{(1-q)}
\end{equation}
\end{prop}
\begin{proof}
The proof proceeds by the same trick as in the proof of proposition \ref{prop:altstates}. To describe the costalk, we wish to compute a limit of sections of $\mc F^{(-1)}_{\R\times \C,c}$ on open sets of the form $I\times D$ containing the origin in $\R\times \C$. Using ellipticity, we can describe such sections as a module over the ring generated by holomorphic derivatives of the delta function.

Accordingly, we have contributions from the following summands:
\begin{itemize}
\item An even copy of $\C^4\otimes \C\{\d z^{3/4}\} \otimes \C[\del_z]\delta_{z=0}$. The character of this summand is
\[
\frac{q\left (q^{-3/4}\chi^{\mf{sl}(4)}(\Gamma_{1,0,0}) \right )}{(1-q)} =\frac{q\left (q^{-3/4}(t_1+ t_2+t_3 + t_1^{-1} t_2^{-1} t_3^{-1} )\right )}{(1-q)}
\]
\item An odd copy of $\C^4\otimes \C\{\d z^{1/4}\} \otimes \C[\del_z]\delta_{z=0}$. The character of this summand is
\[
\frac{-q\left (q^{-1/4}\chi^{\mf{sl}(4)}(\Gamma_{0,0,1}) \right )}{(1-q)} =\frac{-q\left (q^{-3/4}(t_1^{-1} + t_2^{-1} +t_3^{-1}  + t_1 t_2 t_3)\right )}{(1-q)}
\]
\end{itemize}
\end{proof}

Note that under the change of fugacities in \ref{}, this matches exactly with the single particle index for the theory on a single M2 brane \cite[Eq. (2.32)]{Bhattacharya:2008zy}.

\parsec[]
We continue to the next step of the decomposition given by $\mc{F}^{(0)}_{\R\times \C}$.

Arguing similarly as in the proof of the previous proposition, we have the following.
\begin{prop}
The character $\chi \left ( \mc U (\mc{F}^{(0)}_{\R\times \C})(0)\right )$ is given by the plethystic exponential of the following expression:
\begin{equation}
f_0(t_1, t_2, t_3, q) = \frac{q}{(1-q)}\left ( q^{1/2}\chi^{\mf{sl}(4)}(\Gamma_{0,1,0})  + q^{-1/2}\chi^{\mf{sl}(4)}(\Gamma_{2,0,0})  - q - \chi^{\mf{sl}(4)}(\Gamma_{1,0,1}) \right)
\end{equation}
\end{prop}

\parsec[]
Finally, we continue to the general step of the decomposition.

\begin{prop}
Let $j\geq 1$. The character $\chi \left ( \mc U (\mc F^{(j)}_{\R\times \C} ) (0)\right )$ is the plethystic exponential of the following expression:
\begin{equation}
f_j(t_1, t_2, t_3, q) = \frac{q}{(1-q)}\left (\begin{aligned} q^{(j-2)/4}\chi^{\mf{sl}(4)}(\Gamma_{j+2,0,0})  &+ q^{(j+2)/4}\chi^{\mf{sl}(4)}(\Gamma_{j+1,0,1}) \\ - q^{j/4}\chi^{\mf{sl}(4)}(\Gamma_{j,1,0}) & - q^{(j+1)/4}\chi^{\mf{sl}(4)}(\Gamma_{j,0,0}) \end{aligned}\right)
\end{equation}
\end{prop}

\parsec[]
As a consequence, of the above we have that $f_{AdS_4\times S^7} (t_i, q) = \sum_{j\geq -2} f_j (t_i, q)$, or explicitly:
\begin{align*}
& \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}  \\ 
& =  1 + \frac{q}{1-q} \left (\begin{aligned} & q^{-3/4}\chi^{\mf{sl}(4)}(\Gamma_{1,0,0}) - q^{-1/4}\chi^{\mf{sl}(4)}(\Gamma_{0,0,1}) \\+ & q^{1/2}\chi^{\mf{sl}(4)}(\Gamma_{0,1,0})  + q^{-1/2}\chi^{\mf{sl}(4)}(\Gamma_{2,0,0})  - q - \chi^{\mf{sl}(4)}(\Gamma_{1,0,1}) \end{aligned}\right ) \\
& + \frac{q}{1-q} \sum_{j\geq 1} \left (\begin{aligned} q^{(j-2)/4}\chi^{\mf{sl}(4)}(\Gamma_{j+2,0,0})  &+ q^{(j+2)/4}\chi^{\mf{sl}(4)}(\Gamma_{j+1,0,1}) \\ - q^{j/4}\chi^{\mf{sl}(4)}(\Gamma_{j,1,0}) & - q^{(j+1)/4}\chi^{\mf{sl}(4)}(\Gamma_{j,0,0}) \end{aligned}\right ) 
\end{align*}

In \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4\times S^7}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}. Comparison with the above expansion suggests the following conjecture

\begin{conj}\label{conj:e16gravitonrep}
For $j\geq -1$, the minimal twist of the $j+2$nd graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
\end{conj}

\begin{rmk}\label{rmk:e16enhance}
This conjecture implies that the minimal twist of these graviton representations, which is a priori a module for the minimally twisted 3d $\mc N=8$ superconformal algebra $\mf{osp}(6|2)$, is in fact a module for the larger infinite dimensional super-Lie algebra $E(1|6)$. This can be thought of as analogous to the enhancement of conformal symmetries to the action of the Witt algebra of vector fields in 2d chiral conformal field theory. Such symmetry enhancements in 3 dimensions is the topic of joint work in progress with Garner and Williams.
\end{rmk}

### 2023-05-11 graviton spectra/content/e36.tex
graviton spectra

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

%\parsec[s:membraneobs]
%
%
%\parsec[s:fivebraneobs]
%
%Let $Z$ be a complex threefold. 
%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\mc{L}_{single}$ on $Z$. 
%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
%the cochain complex
%\[
%\clie^\bullet\left(\mc{L}_{single}(U)\right) .
%\]
%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bullet(\mc{L}_{single})$.
\section{$E(3|6)$-modules from gravitons on $AdS_7\times S^4$}\label{sec:e36}
We now repeat the analysis of the previous subsection for gravitons on $AdS_7\times S^4$ respectively, making use of the description of supergravity states on $AdS_7\times S^4$ as the costalk of the factorization envelopes of the boundary condition and $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4})$

As before, we construct certain $\C^\times$ actions on the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4})$; we find that the zeroth weight space is a local version of another exceptional linearly compact super-Lie algebra $E(3|6)$. The decomposition of $\mc H_{AdS_7\times S^4}$ as a direct sum of $E(3|6)$ modules incidentally turns out to be very closely related to a decomposition of $E(5|10)$ into $E(3|6)$ modules studied by Cheng-Kac \cite{}.

\subsection{The graviton decomposition of twisted $AdS_7\times S^4$}
We wish to consider a particular decomposition of the space of states $\mc H_{AdS_7\times S^4}$. It is induced by a decomposition of the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4} )$ introduced in section \ref{sec:transversebc}.

%For simplicity let us consider the eleven-dimensional theory on flat space $\R \times \C^5$ with some number of fivebranes supported on
%\[
%0 \times 0 \times \C^3 \subset \C^5 .
%\]
%is that (after taking into account the backreaction) the observables on a large number of fivebranes is Koszul dual to the factorization algebra 
%
%\parsec[s:flatdecomp]
%
%%In the simple case where $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ then the manifold obtained by removing the locus of the brane is homeomorphic to
%%\[
%%\C^3 \times (\R \times \C^2 - 0) .
%%\]
%%
%%Let $\pi : \R \times \C^5 - (0 \times \C^3) \to \C^3 \times \R_{>0}$ be the projection map whose fibers are homeomorphic to the sphere $S^4$ which links the location of the fivebranes.
%%We restrict the factorization algebra of the eleven dimensional theory $\Obs_{sugra}$ to the open set obtained by removing the locus of the brane.
%
%In the simple case that $Z = \C^3$ and we identify the total space of $K^{1/2}_Z \otimes \C^2$ with $\C^5$ there is a more direct construction of the factorization algebra $\Obs_{sugra}|_{Z}$. 
%
%Let $\pi : \R \times \C^5 \to \C^3$ be the projection map.
%Then, via $\pi$ we can pushforward the factorization algebra associated to the eleven-dimensional theory to obtain a factorization algebra
%\[
%\pi_* \Obs_{sugra} 
%\]
%on $\C^3$.
%This factorization algebra is not the factorization algebra associated to an ordinary sort of field theory on $\C^3$. 
%Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.

Let $U\subset \C^3$ be an open; explicitly, the $\C^\times$ action on $\Omega^{0,\bullet}_{\C^3} (U, \mc L^{{r=0}}_{AdS_7\times S^4} )$ is given as follows.
\begin{itemize}
\item On the fields $\mu(w_a,z_i) \in \C[w_1, w_2]\{\del_{w_a}\} \otimes \Omega^{0,\bullet}_{\C^3} (U) \oplus \C[w_1, w_2]\otimes \Omega^{0,\bullet}_{\C^3}(U, T)$ the action is
\[
\lambda \cdot \mu(w_a,z_i) = \mu(\lambda w_a , z_i).
\]
\item On the fields $\nu(w_a,z_i) \in \C[w_1, w_2] \otimes \Omega^{0,\bullet}_{\C^3}(U)$ the action is
\[
\lambda \cdot \nu(w_a,z_i) = \nu(\lambda w , z).
\]
\item On the fields $\beta(w_a,z_i) \in \C[w_1, w_2] \otimes \Omega^{0,\bullet}_{\C^3}(U)$ the action is
\[
\lambda \cdot \beta(w_a,z_i) = \lambda^{-1} \beta(\lambda w_a , z_i).
\]
\item On the fields $\gamma(w_a,z_i) \in \C[w_1, w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{\C^3} (U) \oplus \C[w_1, w_2]\otimes \Omega^{0,\bullet}_{\C^3}(U, \Omega^1)$ the action is
\[
\lambda \cdot \gamma(w_a,z_i) = \lambda^{-1} \gamma(\lambda w _a, z_i).
\]
\end{itemize}

The following proposition is a straightforward if lengthy computation - we state it without proof.
\begin{prop}\label{prop:ads7decomp}
The $L_\infty$ structure on $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4} )$ identified in remark \ref{} is equivariant for this $\C^\times$ action. 
\end{prop}

%\begin{proof}
%The only nontrivial bracket to check compatibility with the $\C^\times$ action is the one which takes two $\gamma$-type sections to a $\mu$-type section of the form
%\[
%[\gamma_1, \gamma_2] = \Omega^{-1} \vee (\del \gamma_1 \wedge \del \gamma_2) 
%\]
%where $\Omega \vee (-)$ is the operation which takes a four-form 
%
%It suffices to check equivariance in local coordinates; there are three cases.
%Suppose $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^j(t;w,z) \d z_j$where $f^i,g^j$ are de Rham--Dolbeault forms for $i,j=1,2,3$. 
%Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = \lambda^{-1} g^j(\lambda t;\lambda w, z) \d z_j$. 
%Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that 
%\begin{equation}
%\begin{array}{llll}
%\label{eqn:lambda1} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
%\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a} .
%\end{array}
%\end{equation}
%We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
%\begin{multline}
%\del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z) \d w_a \d z_i \d z_l \d z_j + \del_{z_k} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d z_k \d z_i \d w_b \d z_j \\  + \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d w_a \d z_i \d w_b \d z_j .
%\end{multline}
%Thus in the notation above we have 
%\begin{align*}
%F^k (t;w,z) & = \epsilon_{ab} \epsilon_{ijk} \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \\
%G^a(t;w,z) & = \epsilon_{ilj} \epsilon_{ab} \del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z)
%+ \epsilon_{kij} \epsilon_{ab} \del_{z_k} f^i(t;w,z) \del_{w_a} g^j(t;w,z)  .
%\end{align*}
%We compute the action of $\lambda \in \C^\times$ on $\mu = F^k \del_{z_k}$
%\[
%\lambda \cdot \left(F^k \del_{z_k} \right) = \epsilon_{ab} \epsilon_{ijk} \lambda^{-1} \del_{w_a} f^i(\lambda t;\lambda w,z) \lambda^{-1} \del_{w_b} g^j(\lambda t;\lambda w,z) \del_{z_k} .
%\]
%Thus the first part of \eqref{eqn:lambda1} is satisfied. 
%Similarly we observe that $\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right)  = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a}$. 
%
%The next case is when $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^a(t;w,z) \d w_a$where $f^i,g^a$ are de Rham--Dolbeault forms for $i=1,2,3$ and $a=1,2$. 
%Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = g^a(\lambda t;\lambda w, z) \d w_a$. 
%Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that 
%\begin{equation}
%\begin{array}{llll}
%\label{eqn:lambda2} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-1} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
%\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-1} G^a(\lambda t;\lambda w,z) \del_{w_a} .
%\end{array}
%\end{equation}
%We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
%\begin{multline}
%\del_{w_b} f^i(t;w,z) \del_{z_j} g^a(t;w,z) \d w_b \d z_i \d z_j \d w_a + \del_{z_k} f^i(t;w,z) \del_{w_b} g^a(t;w,z) \d z_k \d z_i \d w_b \d w_a \\  + \del_{z_j} f^i(t;w,z) \del_{z_k} g^a(t;w,z) \d z_j \d z_i \d z_k \d w_a .
%\end{multline}
%Thus in the notation above we have 
%\begin{align*}
%F^k (t;w,z) & = \epsilon_{ab} \epsilon_{ijk} \del_{w_a} f^i(t;w,z) \del_{z_l} g^b(t;w,z) + \epsilon_{ab} \epsilon_{kij} \del_{z_k} f^i(t;w,z) \del_{w_a} g^b(t;w,z) \\
%G^a(t;w,z) & = \epsilon_{ab} \epsilon_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) .
%\end{align*}
%We compute the action of $\lambda \in \C^\times$ on $\mu = G^a \del_{z_a}$
%\[
%\lambda \cdot \left(G^a \del_{w_a} \right) = \epsilon_{ab} \epsilon_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) \lambda^{-1} \del_{w_a} .
%\]
%Thus the second part of \eqref{eqn:lambda2} is satisfied. 
%Similarly we observe that $\lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right)  = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k}$. 
%
%The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
%The argument is nearly identical so we omit the details. 
%\end{proof}

This result induces a product decomposition 
\begin{equation}
\label{eqn:Gdecomp}
\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4}) = \prod_{n \geq -1} \mc{G}_{\C^3}^{(n)}
\end{equation}
where for each open set $U \subset \C^3$
\[
\mc{G}_\C^3(U)^{(n)}\subset \Omega^{0,\bullet}_{\C^3} (U, \mc L^{{r=0}}_{AdS_7\times S^4} )
\]
is the weight $n$ eigenspace with respect to the above $\C^\times$ action.  In particular, we see that $\mc{G}^{(0)}_{\C^3}$ is itself a local dg-Lie algebra (that we will soon describe). 
Moreover, every $\mc{G}_{\C^3}^{(n)}$, $n \geq -1$ is a (local) module for this local dg-Lie algebra.

%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\mc{L}_{sugra}$. 
%Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
%\[
%\mc{G}_Z (U)  \prod_{n \geq -1} (\pi_*\mc{L}_{sugra})(U)^{(n)}
%\]
%is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
%In this way, the assignment 
%\[
%\Bar{\pi}_* \mc{L}_{sugra} : U \mapsto (\Bar{\pi}_* \mc{L}_{sugra})(U) 
%\]
%defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

%\begin{lem}
%\label{lem:technical}
%For each $n$, $\mc{G}
%\[
%U \mapsto \Omega^{0,\bullet}(U, \mc{V}_{fivebrane}^{(n)})
%\]
%for some finite rank super holomorphic vector bundle $\mc{V}_{fivebrane}^{(n)}$ on $Z$.
%For each $n$, the differential is of the form $\dbar + Q^{hol}$.
%In particular, this endows $\Bar{\pi}_* \mc{L}_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
%\end{lem}
%
%\begin{proof}
%In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure. 
%Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
%For any open subset $U \subset Z$ of the threefold the value of $\mc{L}_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
%\[
%\Omega^\bullet(\R) \otimes \Omega^{0,\bullet}(p^{-1} U, L_{X_Z}),
%\]
%where $p : X_Z \to Z$ is the rank two bundle over $Z$. 
%The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$. 
%
%Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
%\[
%\mc{L}_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bullet}(p^{-1} U, L_{X_Z})
%\]
%for every $U \subset Z$. 
%Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
%\[
%L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
%\]
%where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
%Then, we can further identify this with a Dolbeault complex of the form
%\[
%\Omega^{0,\bullet} \left(U, L' \otimes \Omega^{0,\bullet}(\C^2, L'') \right) . 
%\]
%By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
%\[
%\Omega^{0,\bullet} \left(U, L' \otimes M\right) 
%\]
%where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
%the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.
%
%With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
%%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bullet}(\C^2, L'')$ where $M$ is a 
%\end{proof}

\subsection{The lowest piece: the holomorphic twist of the abelian 6d $\mc N=(2,0)$ tensor multiplet}\label{subsec:g-1}

The first non trivial case is the weight $(-1)$ piece.

\begin{lem}
There is an equivalence of abelian local Lie algebras 
\[
\mc{G}_{\C^3} ^{(-1)}\cong \Omega^{0,\bullet}_{\C^3} \left ( 
\begin{tikzcd}
\ul{+} & \ul{-} \\
\C^2\otimes K^{1/2}_{\C^3} & \\ 
\mc{O}_{\C^3} \ar[r, "\del"] & \Omega^1_{\C^3} 
\end{tikzcd}
\right )
\] 
\end{lem}
\begin{proof}
We readily see that the fields of weight $-1$ include
\begin{itemize}
\item 
fields of type $\mu$ of the form $\mu_a (z_i)\del_{w_a}$. As $w_a$ are fiber coordinates on $K^{1/2}_{\C^3}$, these fields transform as sections of $K^{1/2}_{\C^3}$. 
\item 
fields of type $\beta$ with no $w_a$-dependence. These fields constitute a copy of $\mc {O}_{\C^3}$.
\item 
fields of type $\gamma$ of the form $\gamma_i(z_i)\d z_i$. These fields constitute a copy of $\Pi \Omega^1_{\C^3}$. 
\end{itemize}
Since $\del$ is weight zero for this $\C^\times$ action, the fields of the last two type combine to give the complex of sheaves
\[
\mc{O}_{\C^3}  \xto{\del} \Pi \Omega^{1}_{\C^3}  .
\]

\end{proof}

\parsec[]
In \cite{SWtensor} Saberi and Williams, the authors studied the minimal twist of the 6d $\mc N=(2,0)$ abelian tensor multiplet. The twist is a free theory and can be defined on any complex three-fold admitting a square root of its canonical bundle. On $\C^3$, the $\Z\times \Z/2$ graded sheaf of complexes $\mc E_{tens}$ encoding its field content is given by

\begin{equation}
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Pi \C^2\otimes \Omega^{0,\bullet}_{\C^3} \otimes  K_{\C^3}^{1/2}  & \\
\Omega^{2,\bullet}_{\C^3} \ar[r,"\del"] & \Omega^{3,\bullet}_{\C^3} 
\end{tikzcd} 
\end{equation}
Here we recall in the $\Z \times \Z/2$ bigrading the differential has bidegree $(1,0)$.

We observe the following:
\begin{prop}
\label{prop:factabelian}
There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on $\C^3$
\[
\mc U (\mc G^{(-1)}_{\C^3} )\xto{\simeq} \clie^\bullet(\Pi \mc E_{tens})
\]
\end{prop}

\begin{proof}
Recall that the factorization algebra $\mc U(\mc{G}_{\C^3}^{(-1)})$ assigns to an open set $U\subset \C^3$ the graded symmetric algebra on the complex
\begin{equation}\label{eqn:weight-1}
\begin{tikzcd}
\ul{-} & \ul{+}\\
\Omega_{\C^3, c}^{0,\bullet}(U) \ar[r,"\del"] & \Omega_{\C^3, c}^{1,\bullet}(U) \\
\Omega_{\C^3, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
\end{tikzcd}
\end{equation}
On the other hand, if we totalize the $\Z\times\Z/2$-grading on $\mc E_{tens}$ to a $\Z/2$-grading, the factorization algebra $\clie^\bullet (\Pi \mc E_{tens})$ assigns to an open set $U\subset \C^3$ the symmetric algebra on the complex 
\begin{equation}
\begin{tikzcd}
\ul{-} & \ul{+}\\
\Omega_{\C^3}^{2,\bullet}(U)^\vee \ar[r,"\del"] & \Omega_{\C^3}^{3,\bullet}(U)^\vee \\
& \Omega_{\C^3}^{0,\bullet}(U, \C^2\otimes K^{1/2})^\vee \\
\end{tikzcd}
\end{equation}

Here the superscript refers to the topological dual, which is described in terms of compactly supported distributional sections of the Serre dual vector bundle. Thus, we see that the above complex is the same as

\begin{equation}
\begin{tikzcd}
\ul{-} & \ul{+}\\
\overline \Omega_{\C^3, c}^{0,\bullet}(U) \ar[r,"\del"] & \overline \Omega_{\C^3, c}^{1,\bullet}(U) \\
\overline \Omega_{\C^3, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
\end{tikzcd}
\end{equation}

where the degree shift is coming from Serre duality. The result then follows from the fact that by ellipticity, the natural inclusion $\Omega^{0,\bullet}_{\C^3,c}\to\overline \Omega^{0,\bullet}_{\C^3,c}$ is a quasi-isomorphism.
\end{proof}

\subsection{The zero-th piece: a local version of $E(3|6)$}

As before, the weight zero summand $\mc{G}_{\C^3} ^{(0)}$ is special because it carries the induced structure of a local $L_\infty$-algebra on ${\C^3} $ inherited from the $L_\infty$ structure on $\Pi\Omega^{0,\bullet} (\mc L^{r = 0}_{AdS_7\times S^4} )$ identified in section \ref{sec:transversebc}. We will prove that it is equivalent to a local Lie algebra version of the exceptional super-Lie algebra $E(3|6)$ \cite{KacBible}.

We first recall the definition of this super-Lie algebra.

\begin{defn}\label{defn:e(3|6)}
Let $E(3|6)$ be the following super-Lie algebra.
\begin{itemize}
\item The even part, $E(3|6)_0$ is given by the semidirect product Lie algebra $\Gamma(\widehat D, T) \ltimes \left ( \mf{sl}(2) \otimes \Gamma (\widehat D, \mc O) \right )$. 
\item The odd part, $E(3|6)_1$ is given by $\C^2\otimes \Gamma (\widehat D, \Omega^1(K^{-1/2} ))$. 
\end{itemize}
The remaining brackets to be specified, are as follows:
\begin{itemize}
\item The action of $E(3|6)_0$ on $E(3|6)_1$ is given by the Lie derivative, along with the fundamental action of $\mf{sl}(2)$. 
\item The bracket between two odd elements is given by 
\begin{align*}
[v_1\otimes f_i \d z_i \otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{1/2} &, v_2\otimes g_j \d z_j \otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{1/2} ]  \\ 
 = & \  \omega (v_1, v_2) \eps^{ijk} f_i g_j \del_{z_k}  \\
 + & \  (v_1 \odot v_2) \left ( \del (f_i \d z_i ) g_j \d z_j  - f_i \d z_i \del (g_j \d z_j)  \right )\vee (\del_{z_1}\del_{z_2}\del_{z_3} )
\end{align*}
where $\omega$ denotes a symplectic form on $\C^2$ and $\odot: \C^2\otimes \C^2 \to \mf{sl}(2)$ is the canonical $\mf {sl}(2)$-equivariant projection. 
\end{itemize}
\end{defn}

The relationship between this super-Lie algebra and our decomposition is established through the following result.

\begin{prop}\label{prop:g0e36}
There is an equivalence of super-Lie algebras
\[
\mc G^{(0)}_{\C^3, c} (0) \cong E(3|6)
\]
\end{prop}
\begin{proof}
We begin by characterizing the local $L_\infty$-algebra $\mc G^{(0)}_{\C^3}$. We claim that it is quasi-isomorphic to a local version of $E(3|6)$.

Indeed, we readily see that the weight zero sections consist of the following cochain complex

\begin{equation}
\Omega^{0,\bullet}_{\C^3} \left (
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\C\{w_a\del_{w_b}\}\otimes \mc O\ar[r, "\del^W_\Omega" description]  & \mc O \\ 
\T \ar[ur, "\del^Z_\Omega" description] & \\
\C^2\otimes \mc O \ar[r, "\del_W" description]\ar[dr, "\del_Z" description] & \C\{\d w_a\} \otimes K^{-1/2}\ \\
& \C^2 \otimes \Omega^1\otimes K^{-1/2}
\end{tikzcd} \right)
\end{equation}

The differentials are again components of the divergence operator and holomorphic deRham operator. We can compute cohomology by way of a spectral sequence whose first page is the cohomology with respect to $\del^W_\Omega + \del_W$. We see that the differential $\del^W_\Omega$ maps surjectively onto functions and its kernel is isomorphic to $\mf {sl}(2) \otimes \mc O$. Likewise, the differential $\del_W$ is just the identity map between $\C^2$ and $\C\{\d w_a\}$.

Thus we see that this page of the spectral sequence is given by 
\begin{equation}
\mc E(3|6) \define \Omega^{0,\bullet}_{\C^3} \left (
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\T & \C^2\otimes \Omega^1_{\C^3} (K^{-1/2}) \\
\mf {sl}(2)\otimes \mc O
\end{tikzcd} \right)
\end{equation}
and there are no non-zero differentials so the spectral sequence degenerates.

To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ is in fact given by the same formulae as the brackets on $E(3|6)$ given in \ref{defn:e(3|6)}, it will be useful to provide an explicit quasi-isomorphism $\Phi^{(0)} : \mc E(3|6) \to \mc G^{(0)}_{\C^3}$. On an open set $U\subset \C^3$, this is defined as follows.

\begin{itemize}
\item Given a section $g_i(z)\del_{z_i}\in \Omega^{0,\bullet}_{\C^3} (U, T)$ where $g_i(z)$ is a Dolbeault form on $U$, we define
\begin{align*}
\Phi^{(0)} (g_i (z) \del_{z_i} ) &= g_i (z) \del_{z_i} - \frac 12(\del_{z_i} g_i (z)) w_a \del_{w_a} \\
&\in \Omega^{0,\bullet}_{\C^3} \left ( U, T \oplus \C \{w_a \del_{w_b} \} \otimes \mc O \right ).  
\end{align*}

\item Given a section $A\otimes g(z)\in \Omega^{0,\bullet}_{\C^3} (U,\mf {sl}(2) \otimes \mc O)$ where $g(z)$ is a Dolbeault form on $U$, and $A_{ab}\in \mf {sl}(2)$ we define
\begin{align*}
\Phi^{(0)} (A_{ab}\otimes g(z) ) &=  g(z) A_{ab}w_a\del_{w_b}\\
&\in \Omega^{0,\bullet}_{\C^3} \left ( \C \{w_a \del_{w_b} \} \otimes \mc O \right ).  
\end{align*}

\item Given a section $v\otimes g_i(z)\d z_i (\del_{z_1}\del_{z_2}\del_{z_3} ) \in \Omega^{0,\bullet}_{\C^3} (U, \C^2\otimes \Omega^1\otimes K^{-1/2})$ where $g_i(z)$ is a Dolbeault form on $U$ and $v\in \C^2$, we define
\begin{align*}
\Phi^{(0)} (v\otimes g_i(z)\d z_i (\del_{z_1}\del_{z_2}\del_{z_3} ) ) &= (w_1(v)w_1+w_2(v)w_2) \otimes g_i(z)  \\
&\in \Omega^{0,\bullet}_{\C^3} \left ( \C^2\otimes \Omega^1\otimes K^{-1/2}  \right ).  
\end{align*}
\end{itemize}

The result then follows from computing the limit of $\mc E(3|6)_c (D^3)$ over open sets containing the origin.
\end{proof}

\begin{rmk}
We note that the map $i_{M5}$ from lemma \ref{lem:m5emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ over every open set containing the origin. The image of the map lands exactly in the step $\mc G^{(0)}_{\C^3}$ of the decomposition from proposition \ref{prop:ads7decomp}. Therefore we see that $E(3|6)$ contains $\mf{osp}(6|2)$ as a finite dimensional subalgebra.  
\end{rmk}
%\begin{rmk}
%In \cite{KacClass} an embedding of super Lie algebras from $E(3|6)$ into $E(5|10)$ is constructed.
%Recall that in the case $Z = \C^3$, the $\infty$-jets at $0 \in \C^3$ of the local Lie algebra $\mc{E}(3|6)$ is precisely the exceptional super Lie algebra $E(3|6)$.
%Similarly, the $\infty$-jets at $0 \in \C^3$ of the local $L_\infty$ algebra $\mc{G}_{\C^3}$ is $\widehat{E(5|10)}$.
%The embedding of local $L_\infty$ algebras on $Z$ from $\mc{E}(3|6)$ into $\mc{G}_Z$ that we just described agrees with the embedding of \cite{KacClass} upon taking $\infty$-jets.
%(Note that the central term in $\widehat{E(5|10)}$ plays no role herem since it sits in $\C^\times$-weight $-1$.)
%\end{rmk}

%\begin{itemize}
%\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
%This acts on the sections of $\mf{sl}(2) \otimes \mc{O}_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
%\item On sections of $\mf{sl}(2) \otimes \mc{O}_Z$ there is the matrix commutator. 
%This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\mf{sl}(2)$ representation. 
%\item Finally, and most interestingly, there is a bracket of the form
%\[
%\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \mf{sl}(2) \otimes \mc{O}_Z 
%\]
%given in coordinates by
%\begin{multline}
%[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \epsilon_{ijk} \epsilon_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \epsilon_{ijk} \epsilon_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \epsilon_{ijk} \epsilon_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
%\end{multline}
%The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\mf{sl}(2)$-valued holomorphic function on~$Z$.
%\end{itemize}

%\parsec[s:mainfact]
%
%Since $\mc{G}_Z$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
%\[
%U\subset Z \mapsto \clie^\bullet\left(\Bar{\pi}_* \mc{L}_{sugra}(U)\right) 
%\]
%has the structure of a factorization algebra on the three-fold $Z$. 
%We denote this factorization algebra on $Z$ by $\Obs_{sugra}|_Z$.

%\begin{prop}
%Let $Z$ be a Calabi--Yau three-fold and $\pi : Z \times \C^2 \times \R \to Z$ be the projection. 
%There is a pro local Lie algebra $\Bar{\pi}_*\mc{L}_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bullet(\Bar{\pi}_* \mc{L}_{sugra})$ on $Z$ such that:
%\begin{itemize}
%\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
%\[
%\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
%\]
%which is dense at the level of cohomology. 
%\item[(2)] there is a weight grading on $\mc{L}_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
%\begin{equation}\label{eqn:decomp3}
%\Bar{\pi}_{*} \mc{L}_{sugra} = \prod_{n \geq -1} \mc{V}_{n} 
%\end{equation}
%\item[(3)]
%In weight zero, there is an equivalence of local Lie algebras on $Z$ 
%\[
%\mc{V}_0 \simeq \mc{E}(3|6)|Z 
%\]
%where $\mc{E}(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
%\end{itemize}
%\end{prop}

%We want to argue that $\Obs_{sugra} |_{\C^3} \cong \Bar{\pi}_* \Obs_{sugra}$.

\subsection{General summands and $E(3|6)$-modules}

We move on to give the following general description of the weight $j$ component $\mc{G}_{\C^3} ^{(j)}$.
Since we have already described $j = -1,0$ we focus on $j \geq 1$.

\begin{prop}
\label{prop:Vj}
Let $j \geq 1$. 
The complex of vector bundles $\mc{G}^{(j)}$ is quasi-isomorphic to
\begin{equation}
\label{eqn:Gj}
\Omega^{0,\bullet}_{\C^3} \left (\begin{tikzcd}
\ul{even} & \ul{odd} \\
\Sym^{j}(\C^2) \otimes \T \otimes K^{-j/2} & \Sym^{j-1}(\C^2) \otimes K^{-(j+1)/2}\\
\Sym^{j+2}(\C^2) \otimes K^{-j/2} & \Sym^{j+1}(\C^2) \otimes \T^* \otimes K^{-(j+1)/2} .
\end{tikzcd}\right )
\end{equation}
\end{prop}

\begin{proof}
We begin by noting that we can explicitly describe the weight $j$ component $\mc G^{(j)}_{\C^3}$ as $\Omega^{0,\bullet}_{\C^3} (G^{(j)})$ where $G^{(j)}$ is the following dg-vector bundle
\begin{equation}
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\Sym^{j+1}(\C^2) \otimes \C^2 \ar[dr, "\del^W_\Omega"'] \otimes K^{-j/2}\\ 
& \Sym^j (\C^2) \otimes K^{-j/2} \\ 
\Sym^j (\C^2) \otimes  \T \otimes K^{-j/2} \ar[ur, "\del^Z_\Omega"]  & \\
& \Sym^{j+1}(\C^2)  \otimes  \Omega^1 \otimes K^{-(j+1)/2} \\ 
\Sym^{j+1}(\C^2) \otimes K^{-(j+1)/2} \ar[ur, "\del_Z"] \ar[dr, "\del_W"'] \\
& \Sym^j(\C^2) \otimes \C^2\otimes K^{-(j+1)/2} 
\end{tikzcd}
\end{equation}

Note that the differentials here are $\mf{sl}(2)$-equivariant maps, tensored with a differential operator acting on sections of a bundle on $\C^3$. In particular

\begin{itemize}
\item The differential $\del^W_\Omega$ is the canonical projection \[\Sym^{j+1}(\C^2) \otimes \C^2 \cong \Sym^{j+2} (\C^2) \oplus \Sym ^j (\C^2) \twoheadrightarrow \Sym^j (\C^2)\] tensored with the identity acting on $K^{-j/2}$.

\item The differential $\del_W$ is the canonical inclusion \[\Sym^{j+1}(\C^2) \hookrightarrow \Sym^{j-1}(\C^2) \oplus \Sym^{j+1}(\C^2) \cong \Sym^j(\C^2) \otimes \C^2 .\] tensored with the identity acting on $K^{-(j+1)/2}$.
\end{itemize}

There is a spectral sequence whose first term is computed by the $\del^W_\Omega +\del_W$-cohomology. The result is the complex of sheaves in equation \ref{eqn:Gj}. There are no further differentials so the spectral sequence collapses at this page and the result follows.
\end{proof}

\iffalse
\parsec[]
We wish to explicate the $E(3|6)$-module structure on each of the costalks $\Omega^{0,\bullet}_{\C^3, c} (G^{(j)} )(0)$. To do so, it will be useful to explicate the quasi-isomorphism whose existence was determined in the proof of the preceding proposition. To this end, we describe an explicit quasi-isomorphism 
\[\Phi: \Omega^{0,\bullet}_{\C^3} (G^{(j)} ) \to \mc G^{(j)}_{\C^3}\] 
as follows.

Let $U\subset \C^3$ be open. 
\begin{itemize}
\item Given a section
\[
f(w) \otimes g_i(z) \del_{z_i}\in \Omega^{0,\bullet}_{\C^3} \left (U, \Sym^j(\C^2) \otimes \T \otimes K^{-j/2} \right )
\] where $f(w) \in \Sym^j (\C^2)$ is a homogenous degree $j$ polynomial in $w_1,w_2$ and the $g_i(z)$'s are Dolbeault forms on $\C^3$, we define
\begin{align*}
\Phi(f(w) \otimes g_i(z) \del_{z_i}) &= f(w) g(z) \del_{z_i} - \frac{1}{j+2} \left(\del_{z_i} g_i(z)\right) f(w) w_a\del_{w_a} \\
&\in \Omega^{0,\bullet}_{\C^3} \left ( U, (\Sym^j (\C^2) \otimes T\otimes K^{-j/2} )\oplus ( \Sym^{j+1}(\C^2) \otimes \C^2 \otimes K^{-j/2} ) \right )
\end{align*}

\item Given a section
\[
f(w) \otimes g(z)\in \Omega^{0,\bullet}_{\C^3} \left (U, \Sym^{j+2} \otimes K^{-j/2} \right)
\] where $f(w) \in \Sym^{j+2} (\C^2)$ is a homogenous degree $j+2$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $\C^3$, we define
\begin{align*}
\Phi ( f(w) \otimes g(z) ) &= g(z) (\del _{w_1} f(w) \del_{w_2} - \del _{w_2} f(w) \del_{w_1} ) \\
&\in \Omega^{0,\bullet}_{\C^3} \left ( U, \Sym^{j+1} (\C^2) \otimes T \otimes K^{-j/2}\right )
\end{align*}

\item Given a section
\[
f(w) \otimes g(z)  \in \Omega^{0,\bullet}_{\C^3} \left (U, \Sym^{j-1}(\C^2) \otimes K^{-(j+1)/2} \right)
\]
where $f(w) \in \Sym^{j-1} (\C^2)$ is a homogenous degree $j-1$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $Z$ we define
\begin{align*}
\Phi( f(w) \otimes g(z) ) &= \frac12 g(z)f(w)(w_1 \d w_2 - w_2 \d w_1)  \\
& \in \Omega^{0,\bullet}_{\C^3}\left  (U, \Sym^j (\C^2) \otimes \C^2 \otimes K^{-(j+1)/2} \right )
\end{align*}

\item
Given a section
\[
f(w) \otimes g^i(z)  \d z_i\in \Omega^{0,\bullet}_{\C^3} \left (U, \Sym^{j+1}(\C^2) \otimes T^* \otimes K^{-(j+1)/2} \right)
\] 
where $f(w) \in \Sym^{j+1} (\C^2)$ and the $g^i(z)$'s are Dolbeault forms on $\C^3$, we define 
\begin{align*}
\Phi(f(w) \otimes g^i(z) \d z_i) & = f(w) g^i (z) \d z_i \\
& \in \Omega^{0,\bullet}_{\C^3} \left (U, \Sym^{j+1} (\C^2) \otimes \Omega^1 \otimes K^{-(j+1)/2} \right )
\end{align*}
\end{itemize}

The following is immediate:

\begin{lem}\label{lem:qisG}
The map $\Phi: \Omega^{0,\bullet}_{\C^3} (G^{(j)} ) \to \mc G^{(j)}_{\C^3}$ is a quasi-isomorphism.
\end{lem}

\parsec[]
Recall that as an immediate corollary of proposition \ref{prop:ads7decomp}, the local super-Lie algebra $\mc E(3|6)$ acts on the abelian local Lie algebras $\mc G^{(j)} _{\C^3}$. By way of the explicit quasi-isomorphisms  $\mc{G}^{(0)} \simeq \mc{E}(3|6)$ and $\mc{G}^{(j)} \simeq \Omega^{0,\bullet}_{\C^3}( G^{(j)})$ we can explicate this module structure.

Recall that $\mc{E}(3|6)$ was given by  $\Omega^{0,\bullet}_{\C^3} (G^{(0)})$ where 
\begin{equation}
G^{(0)} = 
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\T & \C^2\otimes \Omega^1_{\C^3} (K^{-1/2}) \\
\mf {sl}(2)\otimes \mc O
\end{tikzcd}
\end{equation}
The local Lie algebra structure on $\mc{E}(3|6)$ arises from a Lie algebra structure on the sheaf of holomorphic sections of $G^{(0)}$. Likewise, the $\mc{E}(3|6)$-module structure on $\mc{G}^{(j)} \simeq \Omega^{0,\bullet}_{\C^3} (G^{(j)})$ arises from an action of the sheaf of holomorphic sections of $G^{(0)}$ on the sheaf of holomorphic sections of $G^{(j)}$, where the action is expressed through holomorphic differential operators.

Let us explicate this action. It is easy to see how holomorphic sections of the even part of the super-vector bundle $G^{(0)}$ will act. Sections of $T$ are holomorphic vector fields and act by Lie derivative. Likewise, sections of $\mf{sl}(2) \otimes \mc O$ act via the corresponding $\mf{sl}(2)$-representation.

We need only explain how holomorphic sections of the odd component $\C^2 \otimes \T^* \otimes K^{-1/2}$ of $G^{(0)}$ act. We first give a global description of this action, and then we will write down the explicit formula in local coordinates. In local coordinates, we may express such a section as  $w_a g^i(z) \d z_i$ where $g^i(z)$ is a holomorphic function. The action is as follows:

\begin{itemize}
\item The odd part of $\mc{V}^{(0)}$ acts on the component $S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z$ through the composition
\begin{equation}
\begin{tikzcd}
\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j-1}(\C^2) \oplus S^{j+1}(\C^2)\right) \otimes \left(\T_Z \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z\right) \ar[dl] \ar[d] \\
S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z & S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z 
\end{tikzcd}
\end{equation}
Here, the leftmost downward arrow is the evident $\mf{sl}(2)$ projection together with the canonical pairing between sections of $\T_Z$ and $\T^*_Z$.
The rightmost downward arrow is the other $\mf{sl}(2)$ projection together with the Lie derivative of holomorphic one-forms.  
Given a local section $f(w) \otimes h_i(z) \del_{z_i}$ of $S^j(\C^2) \otimes \T_Z \otimes K_Z^{-j/2}$ an explicit formula for this action is
\begin{align*}
(w_a g^i(z) \d z_i) \cdot (f(w) \otimes h_k(z) \del_{z_k}) & = \epsilon_{ab} (\del_{w_b} f(w)) (g^i h_i)(z)  \\ & + w_a f(w) L_{h_k \del_{z_k}} (g^i \d z_i) .
\end{align*}
\item The odd part of $\mc{V}^{(0)}$ acts on the component $S^{j+2}(\C^2) \otimes K^{-j/2}_Z$ through the composition
\begin{equation}
\begin{tikzcd}
\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j+2}(\C^2) \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j+1}(\C^2) \oplus S^{j+3}(\C^2)\right) \otimes \left(\T^*_Z \otimes K^{-(j+1)/2}_Z\right) \ar[d] \\
& S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z
\end{tikzcd}
\end{equation}
where the downward arrow is induced by the evident $\mf{sl}(2)$ projection.
\item The odd part of $\mc{V}^{(0)}$ acts on the component $S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z$ through the composition
\begin{equation}
\begin{tikzcd}
\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j-1}(\C^2) \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j-2}(\C^2) \oplus S^{j}(\C^2)\right) \otimes \left(\T^*_Z \otimes K^{-1}_Z K^{-j/2}_Z\right) \ar[d] \\
& S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z
\end{tikzcd}
\end{equation}
where the downward arrow is induced by the evident $\mf{sl}(2)$ projection together with the holomorphic de Rham operator taking holomorphic one-forms to holomorphic two-forms. 
\item Finally, the odd part of $\mc{V}^{(0)}$ acts on the component $S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z$ through the composition
\begin{equation}
\begin{tikzcd}
\left(\T^*_Z \otimes K^{-1/2}_Z \otimes \C^2\right) \otimes \left(S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-j/2}_Z\right) \ar[r,"\cong"] & \left(S^{j}(\C^2) \oplus S^{j+2}(\C^2)\right) \otimes \left(\T^*_Z \otimes \T^*_Z \otimes K^{-1}_Z K^{-j/2}_Z\right) \ar[dl] \ar[d] \\
S^j (\C^2) \otimes \T_Z \otimes K_Z^{-j/2} & S^{j+2}(\C^2)  \otimes K^{-j/2}_Z
\end{tikzcd}
\end{equation}
where the leftmost downward arrow is induced by the evident $\mf{sl}(2)$ projection.
The rightmost downward arrow is induced by the remaining $\mf{sl}(2)$ projection together with the holomorphic de Rham operator taking holomorphic two-forms to holomorphic three-forms.
\end{itemize}
\fi

\parsec[s:kacrelation]

The decomposition of $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ in equation \eqref{eqn:Gdecomp} is closely related to a decomposition of the exceptional simple super Lie algebra $E(5|10)$ studied in \cite{KR2}. In \ref{thm:global}, we showed that the global sections of the parity shifted fields of our eleven-dimensional theory on flat space is quasi-isomorphic to a Lie 2-extension of $E(5|10)$, which we denoted $\widehat{E(5|10)}$. More precisely, we found a Lie 2-extension of a version of $E(5|10)$ built out of polynomials rather than Taylor series. Given that the $L_\infty$ structure on $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ is given by the same formulas as that on $\Pi \mc E$, it is easy to see that the space of $\infty$-jets of $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ at the origin, which following lemma \ref{} has underlying vector space $\mc H_{AdS_7\times S^4}$, is quasi-isomorphic to $\widehat{E(5|10)}$.

In \cite{KR2} the following weight decomposition of $E(5|10)$ is constructed. Splitting $\C^5 = \C^2_{w_a}\times \C^3_{z_i}$ as we have been doing, we stipulate that
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[\d w_1 \d z_1] \in \Omega^{2,cl}(\widehat{D}^5)$ carries weight $+1 - 1 = 0$. Viewing the odd part as the space of closed two-forms, then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.
\end{itemize}

It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$. Moreover, we see that similarly to the decomposition of $\mc H_{AdS_7\times S^4}$ induced by our $\C^\times$ action in \ref{prop:ads7decomp}, the weight grading is concentrated in degrees $\geq -1$.  In particular, there is a decomposition of super vector spaces
\begin{equation}\label{eqn:decomp1}
E(5|10) = \tilde U_{-1} \times \prod_{j \geq 0} U_j 
\end{equation}
Further, this decomposition also has the property that the 0-th piece $U_0$ is isomorphic to $E(3|6)$. As such, each $U_j$ is an $E(3|6)$-module; Kac characterizes these modules explicitly and identifies them as certain irreducible $E(3|6)$-modules. In the notation of \cite{KR2} we have that $U_{-1} = I(0,0;1;-1)^*$ and for $j\geq 1$, $U_j = I(0,0;j-1;j+1)^*$.

The decomposition of $\mc H_{AdS_7\times S^4}$ afforded by proposition \ref{prop:ads7decomp} induces a weight grading of $\widehat{E(5|10)}$ which extends the one on $E(5|10)$ that we have just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\begin{equation}\label{eqn:decomp2}
\widehat{E(5|10)} = \prod_{j \geq -1} U_j            
\end{equation}                      
were $U_{-1}$ is a $\C$-extension of $\tilde U_{-1}$ defined in the decomposition \eqref{eqn:decomp1} and for $j \geq 0$ the $U_j$'s are the same as in the non centrally extended case. As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible.

\subsection{Characters of $E(3|6)$-modules}\label{e36char}
The decomposition of the state space $\Sym \left (\mc H_{AdS_7\times S^4}\right ) = \prod_{j\geq -1} \mc U (\mc G^{(j)})(0)$ gives a product formula for the characters computed in proposition \ref{prop:sugraindex1}

\[ \chi \left ( \Sym \mc H_{AdS_7\times S^4} \right ) = \prod_{j\geq -1} \chi \left (\mc U (\mc G^{(j)})(0) \right ) \]

We end this section by computing each of the characters $\chi \left (\mc U (\mc G^{(j)})(0) \right )$. We will express our characters in terms of characters of highest weight representations of $\mf{sl}(2)$ and $\mf {sl}(3)$, which we denote by $\chi_k^{\mf{sl}(2)}$ and $\chi^{\mf{sl}(3)}_{[k,l]}$.

\parsec[]
We begin with the lowest step of the decomposition, using the characterization given in \ref{subsec:g-1}.

\begin{prop}
\label{prop:6done}
The character $\chi \left ( \mc U (\mc G^{(-1)}_{\C^3} ) (0)\right )$ is given by the plethystic exponential of the following expression:
\begin{equation}\label{eqn:6done}
g_{-1} (t_1,t_2,r,q) = \frac{q^{3/2}(r + r^{-1}) - q^2(t_1 + t_1^{-1} t_2 + t_2^{-1} ) + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
\end{equation}
\end{prop}
\begin{proof}
Note that in light of proposition \ref{prop:factabelian} we can equivalently compute the character of the costalk at the origin of $\clie^\bullet (\Pi \mc E_{tens})$. We first give a more explicit description of the costalk as a cochain complex. Proceeding exactly analogously to the proof of lemma \ref{lem:ads4states}, we see that the costalk is given by the symmetric algebra on the following cochain complex
\[
\begin{tikzcd}
\ul{-} & \ul{+}\\
\C\{\d z_i\d z_j\} \otimes \C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0} \ar[r,"\del"] & \C\{\d z_1\d z_2\d z_3\} \otimes \C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0} \\
& \C^2\otimes \C\{\d z_i^{1/2}\} \otimes \C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0} 
\end{tikzcd}
\]

Computing summand-by-summand, we see:
\begin{itemize}
\item the odd summand $\C\{\d z_i\d z_j\} \otimes \C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0}$ contributes
\[
- q^2 \frac{\chi^{\mf{sl}(3)}_{[0,1]}(t_1,t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = - q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}.
\]
where $\chi^{\mf{sl}(3)}_{[1,0]}(t_1,t_2)$ is the $\mf{sl}(3)$ character of highest weight $[1,0]$.
\item the even summand $\C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0}$ contributes
\[
q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}.
\]
\item the even summand $\C^2\otimes \C\{\d z_i^{1/2}\} \otimes \C [\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i = 0}$ contributes
\[
q^{3/2} \frac{\chi_{1}^{\mf{sl}(2)} (r)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}.
\]
where $\chi_{1}^{\mf{sl}(2)} (r)$ is the $\mf{sl}(2)$ character of highest weight one.
\end{itemize}
\end{proof}

In terms of the parameters $y_1,y_2,y_3,y,q$ introduced in \ref{} this single particle character reads
\begin{equation}
\label{eqn:6done1}
g_{-1} (y_i,y,q) = \frac{qy + q^2y^{-1} - q^2(y^{-1}_1+y^{-1}_2+y^{-1}_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
\end{equation}

The expression matches exactly with the index of the abelian six-dimensional superconformal theory. For example, compare with \cite[Eq. (3.1)]{Kim:2013nva} or \cite[Eq. (3.35)]{Bhattacharya:2008zy}.

From now on, we will give all formulas for the index in terms of the parameters $y_1,y_2,y_3,y,q$.

\parsec[]
We continue to the next step of the decomposition, which is given by  $\mc G^{(0)}_{\C^3}$.

\begin{prop}
The character $\chi \left( \mc U(\mc G^{(0)} _{\C^3}) (0)\right )$  is the plethystic exponential of following expression:
\begin{equation}\label{eqn:6dtwo}
g_{0} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
\end{equation}
\end{prop}
\begin{proof}
As usual, we wish to describe the costalk $\mc G^{(0)}_{\C^3, c} (0)$  more explicitly. By the same argument as in the proofs of propositions \ref{}, \ref{}, we may use elliptic regularity to describe the compactly supported smooth sections on a disc in terms of derivatives of the delta function at the origin in $\C^3$.

Accordingly, we have contributions from the following summands.
\begin{itemize}
\item An even copy of $\C\{\del_{z_i} \} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}] \delta_{z_i=0}$. The character of this summand is
\[
q^4 \frac{\chi^{\mf{sl}(3)}_{[1,0]}(y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = q^4 \frac{y_1 + y_2 + y_3}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
\]
\item An even copy of $\mf{sl}(2) \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}] \delta_{z_i=0}$. The character of this summand is
\[
q^3 \frac{\chi_2^{\mf{sl}(2)} (q^{-1/2}y)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = \frac{q^2 y^2 + q^3 + q^4 y^{-2}}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
\]
\item An odd copy of $\C^2\otimes \C\{\d z_i \} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}] \delta_{z_i=0}$. The character of this summand is 
\[
q^{7/2}\frac{\chi^{\mf{sl}(2)}_{1}(q^{-1/2} y) \, \chi_{[0,1]}^{\mf{sl}(3)} (y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)} = q^{3}\frac{(y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
\]
\end{itemize}
\end{proof}

\parsec[]
Finally, we continue to the general step of the decomposition.

\begin{prop}
Let $j\geq 1$. The character $\chi \left( \mc U(\mc G^{(j)} _{\C^3}) (0)\right )$  is the plethystic exponential of following expression:
\begin{equation}\label{eqn:6dtwo}
g_{j} (y_i,y,q) =  \frac{ q^{3} \left( \begin{aligned} q^{1 + 3 j/2} \chi^{\mf{sl}(2)}_{j}(q^{-1/2} y)\chi^{\mf{sl}(3)}_{[1,0]}(y_i) + \  & q^{3j/2} \chi^{\mf{sl}(2)}_{j+2}(q^{-1/2} y)  \\
 - q^{3(j+1)/2} \chi^{\mf{sl}(2)}_{j-1}(q^{-1/2}y) - \ & q^{-1 + 3(j+1)/2} \chi^{\mf{sl}(2)}_{j+1} (q^{-1/2} y) \chi^{\mf{sl}(3)}_{[0,1]}(y_i) \end{aligned} \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}.
\end{equation}
\end{prop}
\begin{proof}
We proceed exactly analogously to all the previous cases. Using elliptic regularity on sections of $\mc G^{(j)}_{\C^3}$ over a disc containing the origin, we see that $\mc U (\mc G^{(j)}_{\C^3} )(0)$ is a symmetric algebra on a cochain complex with the following summands

\begin{itemize}
\item An even copy of $\Sym^j (\C^2) \otimes \C\{\del_{z_i}\}\otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{-j/2}$ which contributes 
\begin{equation}
\frac{ q^{3} \left(  q^{1 + 3 j/2} \chi^{\mf{sl}(2)}_{j}(q^{-1/2} y)\chi^{\mf{sl}(3)}_{[1,0]}(y_i) \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}
\end{equation}

\item An even copy of $\Sym^{j+2} (\C^2) \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{-j/2}$ which contributes 
\begin{equation}
\frac{ q^{3} \left( q^{3j/2} \chi^{\mf{sl}(2)}_{j+2}(q^{-1/2} y)  \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}
\end{equation}

\item An odd copy of $\Sym^{j-1} (\C^2) \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{-(j+1)/2}$ which contributes 
\begin{equation}
\frac{ - q^{3} \left( q^{3(j+1)/2} \chi^{\mf{sl}(2)}_{j-1}(q^{-1/2}y) \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}
\end{equation}

\item An odd copy of $\Sym^{j+1} (\C^2) \otimes \C\{\d z_i\}\otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\otimes (\del_{z_1}\del_{z_2}\del_{z_3})^{-(j+1)/2}$ which contributes 
\begin{equation}
\frac{ - q^{3} \left( q^{-1 + 3(j+1)/2} \chi^{\mf{sl}(2)}_{j+1} (q^{-1/2} y) \chi^{\mf{sl}(3)}_{[0,1]}(y_i) \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}
\end{equation}

\end{itemize}
\end{proof}

\parsec[]
As a consequence, we have that $f_{AdS_7\times S^4} (y_i, y, q) = \sum_{j\geq -1} g_j (y_i, y, q)$, or explicitly:
\begin{align*}
& \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+ (1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)}  \\ 
& =  \frac{qy + q^2y^{-1} - q^2(y^{-1}_1+y^{-1}_2+y^{-1}_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} \\
& +  \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)} \\
& + \sum_{j\geq 1} \frac{ q^{3} \left( \begin{aligned} q^{1 + 3 j/2} \chi^{\mf{sl}(2)}_{j}(q^{-1/2} y)\chi^{\mf{sl}(3)}_{[1,0]}(y_i) + \  & q^{3j/2} \chi^{\mf{sl}(2)}_{j+2}(q^{-1/2} y)  \\
 - q^{3(j+1)/2} \chi^{\mf{sl}(2)}_{j-1}(q^{-1/2}y) - \ & q^{-1 + 3(j+1)/2} \chi^{\mf{sl}(2)}_{j+1} (q^{-1/2} y) \chi^{\mf{sl}(3)}_{[0,1]}(y_i) \end{aligned} \right)}{(1-y_1 q)(1-y_2q)(1-y_3q)}
\end{align*}

In \cite[Eq. (3.22, 3.23)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_7\times S^4}$ is expressed as a sum of characters of irreducible representations of the 6d $\mc N = (2,0)$ superconformal algebra. In \cite[Table 24]{cordova2016multiplets} these representations are labeled as $\mc D_1[0,0,0]^{(0,m)}_{2m}$ where $m \geq 1$. The characters of these modules have been computed (see for example \cite[Eq. (166)]{Arai_2020} and match exactly with $g_{m-2}(y_i, y, q)$ after a suitable change of variables. Thus, we conjecture the following

\begin{conj}
For $j\geq -1$, the minimal twist of $\mc D_1[0,0,0]^{(0,j+2)}_{2(j+2)}$ is exactly $\mc G^{(j)}_{\C^3, c}(0)$.
\end{conj}

\begin{rmk}\label{rmk:e36enhance}
As we remarked in \ref{rmk:e16enhance}, this conjecture implies that the minimal twist of $\mc D_1[0,0,0]^{(0,j+2)}_{2(j+2)}$ which is a priori a module for the minimally twisted 6d $\mc N=(2,0)$ superconformal algebra $\mf{osp}(6|2)$, is in fact a module for the larger infinite dimensional super-Lie algebra $E(3|6)$. This can be thought of as analogous to the enhancement of conformal symmetries to the action of the Witt algebra of vector fields in 2d chiral conformal field theory.
\end{rmk}
%The subalgebra $\mc{G}^{(\geq k)} = \oplus_{j \geq k} \mc{G}^{(j)}$ is an ideal for every $k$. 
%This sequence of ideals induces a limit diagram of vector bundles
%\begin{equation}\label{eqn:lim}
%0 = \mc{G} / \mc{G}^{(\geq -1)} \leftarrow \mc{G} / \mc{G}^{(\geq 0)} \leftarrow \mc{G} / \mc{G}^{(\geq 1)} \leftarrow \cdots ,
%\end{equation}
%where $0$ is the zero vector bundle.
%For each $k$, we point out that $\mc{G} / \mc{G}^{(\geq k)}$ is genuinely a finite rank vector bundle on the worldvolume.
%The resulting filtration of the $!$-dual
%\begin{equation}
%\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bullet(\mc{G}_{c})
%\end{equation} 
%of the factorization algebra \eqref{eqn:factgrad} is of the form
%\begin{equation}\label{eqn:fil1}
%\clie_\bullet (\mc{G}_{1,c}) \subset \clie_\bullet (\mc{G}_{2,c}) \subset \cdots \subset \clie_\bullet(\mc{G}_c) .
%\end{equation}
%Similarly, there is a filtration on the factorization algebra $\clie_\bullet (\tilde \mc{G}_c)$ of the form
%\begin{equation}
%\label{eqn:fil2}
%\clie_\bullet(\tilde \mc{G}_{2,c}) \subset \clie_\bullet(\tilde \mc{G}_{3,c}) \subset \cdots \subset \clie_\bullet(\tilde \mc{G}_c).
%\end{equation}

%\end{document}

### 2023-05-11 graviton spectra/content/finite.tex
graviton spectra

--- 2022-10-14 fivebranes/finite.tex
@@
 For a stack of $N=1$ fivebranes, which corresponds to the abelian six-dimensional superconformal field theory, we find that our local character matches exactly with the expressions in the literature. 
-This is not a surprise as we have shown that even at the level of factorization algebras $\clie_\bu(\cG_{1,c})$ is quasi-isomorphic to the classical limit of~$\Obs_1$, see Proposition~\ref{prop:factabelian}.
+This is not a surprise as we have shown that even at the level of factorization algebras $\clie_\bullet(\mc{G}_{1,c})$ is quasi-isomorphic to the classical limit of~$\Obs_1$, see Proposition~\ref{prop:factabelian}.
 
-The main computation of this section is a closed formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
+The main computation of this section is a closed formula for the local character of the factorization algebra $\clie_\bullet(\mc{G}_{N,c})$ for $N > 1$, see Theorem \ref{thm:finite}. 
 Following conjecture \ref{conj:ops} and the general discussion of \S \ref{sec:sucaindex} we are led to hypothesize a closed formula for the superconformal index for the theory on a finite number of fivebranes (in flat space).
@@
 
-We deduce the character of the holomorphic twist of the theory on a single fivebrane and will find an exact match with the index of the six-dimensional superconformal theory associated to the abelian Lie algebra $\lie{gl}(1)$.
-By the proposition \ref{prop:factabelian} we can compute this character either from a first principles description of the theory, or holographically by focusing on the weight $(-1)$ part of the decomposition of $\Bar{\pi}_* \Obs_{sugra}$.
-
-\begin{lem}
-\label{lem:single}
-The $\Z \times \Z/2$ graded algebra of local operators $\Obs_{1}(0)$ of the holomorphic twist of the worldvolume theory of a single fivebrane is quasi-isomorphic to the graded symmetric algebra on the linear dual of the topological vector space
-\beqn\label{eqn:localfree}
-V_0[[z_1,z_2,z_3]] \simeq \Omega^{2}_{cl} (\Hat{D}^3)[1] \oplus \Pi \Omega^0(\Hat{D}^3, K^{1/2}) \otimes \C^2 [1].
-\eeqn
-\end{lem}
-
-\begin{proof}
-The jet expansion at $0 \in \C^3$ determines a map from the sections of the abelian holomorphic-topological local Lie algebra on $\C^3$ to the cochain complex
-\beqn
-\begin{tikzcd}
-\ul{-1} & \ul{0} \\
-\Omega^{2}(\Hat{D}^3) \ar[r,"\del"] & \Omega^{3}(\Hat{D}^3) \\
-\Pi \Omega^0(\Hat{D}^3, K^{1/2}_{\Hat{D}^3}\otimes \C^2) . 
-\end{tikzcd} 
-\eeqn
-On the formal disk all closed two-forms are automatically exact, which implies the lemma.
-\end{proof}
-
-We present the character of $\Obs_1(0)$ as the plethystic exponential of the character $f_1(t_1,t_2,r,q)$ of the space of linear local operators
-\beqn
-\chi_{1} (t_1,t_2,r,q) = {\rm PExp} \big[f_1(t_1,t_2,r,q) \big] .
-\eeqn
-According to the weights listed above and using the description of local operators in Lemma \ref{lem:single} we have the following contributions to the single particle character~$f_{1}(t_1,t_2,r,q)$.
-
-\begin{itemize}
-\item Single particle operators on the odd copy of holomorphic two-forms $\Pi \Omega^{2,hol}$ contribute
-\[
-- q^2 \frac{\chi^{\lie{sl}(3)}_{[0,1]}(t_1,t_2)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = - q^2 \frac{t_1  + t_1^{-1} t_2  + t_2^{-1} }{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-where $\chi^{\lie{sl}(3)}_{[1,0]}(t_1,t_2)$ is the $\lie{sl}(3)$ character of highest weight $[1,0]$.
-\item Single particle operators on the even copy of holomorphic three-forms $\Omega^{3,hol}$ contribute
-\[
-q^3 \frac{1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-\]
-\item Single particle operators on $K^{1/2} \otimes \C^2$ contribute
-\[
-q^{3/2} \frac{\chi_{1}^{\lie{sl}(2)} (r)}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} = q^{3/2}\frac{(r + r^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)}
-\]
-where $\chi_{1}^{\lie{sl}(2)} (r)$ is the $\lie{sl}(2)$ character of highest weight one.
-\end{itemize}
-
-Putting this all together we obtain the following.
-
-\begin{prop}
-\label{prop:6done}
-The local character $\chi_{1}(t_1,t_2,r,q)$ of the holomorphic twist of the theory on a single fivebrane is given by the plethystic exponential of the single particle character
-\beqn\label{eqn:6done}
-f_{1} (t_1,t_2,r,q) = \frac{q^{3/2}(r + r^{-1}) - q^2(t_1 + t_1^{-1} t_2 + t_2^{-1} ) + q^3}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-\eeqn
-\end{prop}
-
-In terms of the parameters $y_1,y_2,y_3,y,q$ this single particle character reads
-\beqn
-\label{eqn:6done1}
-f_{1} (y_i,y,q) = \frac{qy + q^2y^{-1} - q^2(y^{-1}_1+y^{-1}_2+y^{-1}_3) + q^3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} .
-\eeqn
-The expression matches exactly with the index of the abelian six-dimensional superconformal theory.
-For example, compare with \cite[Eq. (3.1)]{Kim:2013nva} or \cite[Eq. (3.35)]{Bhattacharya:2008zy}.
-From now on, we will give all formulas for the index in terms of the parameters $y_1,y_2,y_3,y,q$.
-
-In Proposition \ref{lem:single} we have shown that $\clie_\bu (\cG_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs^{cl}_{1}$ encoding the classical observables  of the holomorphic twist on a single fivebrane.
-On $\C^3$, the global sections of the local Lie algebra $\cG^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\cG^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+In Proposition \ref{lem:single} we have shown that $\clie_\bullet (\mc{G}_{c}^{(-1)})$ is equivalent to the factorization algebra $\Obs^{cl}_{1}$ encoding the classical observables  of the holomorphic twist on a single fivebrane.
+On $\C^3$, the global sections of the local Lie algebra $\mc{G}^{(0)}$ is closely related to $E(3|6)$---the $\infty$-jets of $\mc{G}^{(0)}$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
 Combining these facts we see that $\Obs_{1}(0)$ is a module for $E(3|6)$. 
@@
 %One degeneration of this character involves specializing $t_1=t_2=1$ which results in the $U(1) \times SU(2)$ character:
-%\beqn
+%\begin{equation}
 %f_{1}(r,q) = \frac{(r+r^{-1})q^{3/2} - 3 q^{2} + q^3}{(1-q)^3} .
-%\eeqn
+%\end{equation}
 %They compute the absolute (non-super) character of the module $I(0,0;1;-1)$ where they additionally specialize $t_1=t_2=r=1$. 
@@
 
-Recall that after performing the holomorphic twist the residual superconformal algebra is~$\lie{osp}(6|2)$.
+Recall that after performing the holomorphic twist the residual superconformal algebra is~$\mf{osp}(6|2)$.
 We have recalled in \S\ref{s:global1} how the bosonic part of this algebra is represented by fields of the eleven-dimensional theory. 
-There are two types of odd elements of~$\lie{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
-The odd part of~$\lie{osp}(6|2)$ can be identified with the twelve-dimensional space
+There are two types of odd elements of~$\mf{osp}(6|2)$ that also have a natural interpretation in the eleven-dimensional theory.
+The odd part of~$\mf{osp}(6|2)$ can be identified with the twelve-dimensional space
 \[
@@
 \]
-where $\C^3, \C^2$ are the fundamental $\lie{sl}(3)$ and $\lie{sl}(2)$ representations, respectively. 
-The $\lie{gl}(1)$ factor in the bosonic part of $\lie{osp}(6|2)$ acts with weight $1/2$ on both summands.
+where $\C^3, \C^2$ are the fundamental $\mf{sl}(3)$ and $\mf{sl}(2)$ representations, respectively. 
+The $\mf{gl}(1)$ factor in the bosonic part of $\mf{osp}(6|2)$ acts with weight $1/2$ on both summands.
 
@@
 
-Both deformations break the global Cartan subalgebra down to $\lie{gl}(1) \times \lie{gl}(1)$ according to the specializations
-\beqn\label{eqn:special1}
+Both deformations break the global Cartan subalgebra down to $\mf{gl}(1) \times \mf{gl}(1)$ according to the specializations
+\begin{equation}\label{eqn:special1}
 y=1 , \quad y_3 = 1 .
-\eeqn
+\end{equation}
 Notice that due to the constraint $y_1y_2y_3=1$ this forces $y_1 = y_2^{-1}$.
@@
 
-In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\cG = \cG_Z$ on $Z$ induces a filtration of the factorization algebra $\clie_\bu(\cG_c)$. 
+In \S\ref{sec:factsummary} we saw that the decomposition of the local $L_\infty$ algebra $\mc{G} = \mc{G}_Z$ on $Z$ induces a filtration of the factorization algebra $\clie_\bullet(\mc{G}_c)$. 
 \[
-\clie_{\bu}(\cG_{1,c}) \subset \clie_{\bu}(\cG_{2,c}) \subset \cdots .
+\clie_{\bullet}(\mc{G}_{1,c}) \subset \clie_{\bullet}(\mc{G}_{2,c}) \subset \cdots .
 \]
-We now turn to the factorization algebra $\clie_{\bu}(\cG_{2,c})$.
+We now turn to the factorization algebra $\clie_{\bullet}(\mc{G}_{2,c})$.
 
-Recall that $\cG_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\cG_{2} = \cG / \cG^{\geq 1}$. 
-Since $\cG$ is concentrated in weights $\geq -1$ we see that $\til \cG_{2}$ is of the form
+Recall that $\mc{G}_{2}$ is the local $L_\infty$ algebra on $Z$ defined as $\mc{G}_{2} = \mc{G} / \mc{G}^{\geq 1}$. 
+Since $\mc{G}$ is concentrated in weights $\geq -1$ we see that $\tilde {\mc{G}}_{2}$ is of the form
 \[
-\cG_2 = \til \cG_2 \ltimes \cG_1 
+\mc{G}_2 = \tilde {\mc{G}}_2 \ltimes \mc{G}_1 
 \]
-where $\cG_1 = \cG^{(-1)}$ is the weight $(-1)$ piece and $\til \cG_2 = \cG^{\geq 0} / \cG^{\geq 1} = \cG^{(0)}$.  
-We focus mostly on the factorization algebra $\clie_\bu(\til \cG_{2,c})$.
+where $\mc{G}_1 = \mc{G}^{(-1)}$ is the weight $(-1)$ piece and $\tilde {\mc{G}}_2 = \mc{G}^{\geq 0} / \mc{G}^{\geq 1} = \mc{G}^{(0)}$.  
+We focus mostly on the factorization algebra $\clie_\bullet(\tilde {\mc{G}}_{2,c})$.
 
-We have already characterized the local dg Lie algebra $\til \cG_{2} = \cG^{(0)}$ as the weight zero part of $\cG$ on on any threefold $Z$ in \S\ref{s:weight0}. 
-We have also shown that $\cG^{(0)}$ is equivalent to the local Lie algebra $\cE(3|6)$. 
-The even part of $\cE(3|6)$ is
+We have already characterized the local dg Lie algebra $\tilde {\mc{G}}_{2} = \mc{G}^{(0)}$ as the weight zero part of $\mc{G}$ on on any threefold $Z$ in \S\ref{s:weight0}. 
+We have also shown that $\mc{G}^{(0)}$ is equivalent to the local Lie algebra $\mc{E}(3|6)$. 
+The even part of $\mc{E}(3|6)$ is
 \[
-\Omega^{0,\bu}(Z, \T_Z) \oplus \Omega^{0,\bu}(Z) \otimes \lie{sl}(2) 
+\Omega^{0,\bullet}(Z, \T_Z) \oplus \Omega^{0,\bullet}(Z) \otimes \mf{sl}(2) 
 \]
 with its natural cohomological grading by Dolbeault form type. 
-The odd part of $\cE(3|6)$ is
+The odd part of $\mc{E}(3|6)$ is
 \[
-\Omega^{1,\bu}(Z, K_Z^{-1/2}) \otimes \C^2 .
+\Omega^{1,\bullet}(Z, K_Z^{-1/2}) \otimes \C^2 .
 \]
@@
 %On $Z = \C^3$ this local dg Lie algebra is related to the exceptional simple super Lie algebra $E(3|6)$ classified by Kac \cite{KacClass}. 
-%Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\cG_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
+%Indeed, one can show (see the forthcoming work \cite{SW6d}) that the fiber of the $\infty$-jet bundle of $\mc{G}_2$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$.
 
@@
 
-We continue by computing the character of local operators associated to the factorization algebra $\clie_\bu(\cG_{2,c})$ using Lemma~\ref{lem:envelope}.
+We continue by computing the character of local operators associated to the factorization algebra $\clie_\bullet(\mc{G}_{2,c})$ using Lemma~\ref{lem:envelope}.
 For simplicity we will use the fugacities $y_i, y, q$.
-
-\begin{itemize}
-\item Single particle operators coming from the copy of holomorphic vector fields $\Vect^{hol}(\C^3)$ contribute
-\[
-q^4 \frac{\chi^{\lie{sl}(3)}_{[1,0]}(y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = q^4 \frac{y_1 + y_2 + y_3}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
-\]
-\item Single particle operators coming from $\lie{sl}(2)$-valued holomorphic functions $\lie{sl}(2) \otimes \cO^{hol}(\C^3)$ contribute
-\[
-q^3 \frac{\chi_2^{\lie{sl}(2)} (q^{-1/2}y)}{(1-y_1q) (1-y_2 q) (1-y_3 q)}  = \frac{q^2 y^2 + q^3 + q^4 y^{-2}}{(1-y_1q) (1-y_2 q) (1-y_3 q)} 
-\]
-%\[
-%q^3\frac{r^2 + r^{-2} + 1}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} 
-%\]
-\item Single particle operators coming from the odd piece of $E(3|6)$ which is $\Omega^{1,hol} \otimes K^{-1/2} \otimes \C^2$ contribute
-\[
-q^{7/2}\frac{\chi^{\lie{sl}(2)}_{1}(q^{-1/2} y) \, \chi_{[0,1]}^{\lie{sl}(3)} (y_i)}{(1-y_1q) (1-y_2 q) (1-y_3 q)} = q^{3}\frac{(y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}
-\]
-\end{itemize}
 
@@
 \begin{prop} \label{prop:6dtwo}
-The character of local operators of the factorization algebra $\clie_\bu(\til \cG_{2,c})$ on $\C^3$ is given by the plethystic exponential of the following expression
-\beqn\label{eqn:6dtwo}
-\til f_{2} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
-\eeqn
-%\beqn\label{eqn:6dtwo}
+The character of local operators of the factorization algebra $\clie_\bullet(\tilde {\mc{G}}_{2,c})$ on $\C^3$ is given by the plethystic exponential of the following expression
+\begin{equation}\label{eqn:6dtwo}
+\tilde f_{2} (y_i,y,q) = \frac{q^4(y_1+y_2+y_3) + q^2 (y^2 + q + q^2 y^{-2}) - q^{3} (y + q y^{-1})(y_1^{-1} + y_2^{-1} + y_3^{-1})}{(1-y_1q) (1-y_2 q) (1-y_3 q)}.
+\end{equation}
+%\begin{equation}\label{eqn:6dtwo}
 %f_{2} (t_1,t_2,r,q) = \frac{q^4(t_1^{-1} + t_1 t_2^{-1}  + t_2) + q^3 (r^2 + r^{-2} + 1) - q^{7/2} (r + r^{-1})(t_1 + t_1^{-1} t_2 + t_2^{-1})}{(1-t_1^{-1}q) (1-t_1 t_2^{-1} q) (1-t_2 q)} .
-%\eeqn
+%\end{equation}
 \end{prop}
 
-Recall that our conjecture for the space of local operators associated to the holomorphic twist of the six-dimensional worldvolume theory on a stack of two fivebranes is $\Obs_2 (0) \simeq \clie_\bu(\cG_{2,c})(0) \cong \clie_\bu(\cG_{1,c})(0) \otimes \clie_\bu(\til \cG_{2,c})(0)$.
-And after removing the center of mass degrees of freedom, our conjecture is $\til \Obs_2 \simeq \clie_\bu(\til \cG_{2,c})$.
+Recall that our conjecture for the space of local operators associated to the holomorphic twist of the six-dimensional worldvolume theory on a stack of two fivebranes is $\Obs_2 (0) \simeq \clie_\bullet(\mc{G}_{2,c})(0) \mc{O}ng \clie_\bullet(\mc{G}_{1,c})(0) \otimes \clie_\bullet(\tilde {\mc{G}}_{2,c})(0)$.
+And after removing the center of mass degrees of freedom, our conjecture is $\tilde \Obs_2 \simeq \clie_\bullet(\tilde {\mc{G}}_{2,c})$.
 
-Just as in the abelian case, the local operators $\til \Obs_2(0)$ form a module over $E(3|6)$.
+Just as in the abelian case, the local operators $\tilde \Obs_2(0)$ form a module over $E(3|6)$.
 It turns out that this module is irreducible~\cite{KR2}.
@@
 \[
-\til \chi_{2} (y_i,y,q) = {\rm PExp} \left[\til f_2(y_i,y,q) \right] .
+\tilde \chi_{2} (y_i,y,q) = {\rm PExp} \left[\tilde f_2(y_i,y,q) \right] .
 \]
-where $\til f_2(y_i,y,q)$ is as in \eqref{eqn:6dtwo}.
+where $\tilde f_2(y_i,y,q)$ is as in \eqref{eqn:6dtwo}.
 \end{conj}
 
-Similarly, the index associated to the $\lie{gl}(2)$ theory, which is the local character of $\clie_\bu(\cG_{2,c})$, is conjectured to be simply the product 
+Similarly, the index associated to the $\mf{gl}(2)$ theory, which is the local character of $\clie_\bullet(\mc{G}_{2,c})$, is conjectured to be simply the product 
 \[
@@
 \]
-where the character $\chi_{1}$ for the $\lie{gl}(1)$ theory is given in proposition~\ref{prop:6done}
-Equivalently, $\chi_2$ is the plethystic exponential of $f_2 = f_1 + \til f_2$.
+where the character $\chi_{1}$ for the $\mf{gl}(1)$ theory is given in proposition~\ref{prop:6done}
+Equivalently, $\chi_2$ is the plethystic exponential of $f_2 = f_1 + \tilde f_2$.
 
@@
 
-The Schur limit $y=1, y_3=1$ of $\til f_2$ in \eqref{eqn:special1} yields 
+The Schur limit $y=1, y_3=1$ of $\tilde f_2$ in \eqref{eqn:special1} yields 
 \[
-\til f_{2}(y_1, y_2, y_3=1, y=1, q) = \frac{q^2}{1-q} 
+\tilde f_{2}(y_1, y_2, y_3=1, y=1, q) = \frac{q^2}{1-q} 
 \]
@@
 
-Before exhibiting the general formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ on $\C^3$ we set up some notation. 
-As above, we let $\chi_k^{\lie{sl}(2)}$ and $\chi^{\lie{sl}(3)}_{[k,l]}$ denote the highest weight $\lie{sl}(2)$ and $\lie{sl}(3)$ characters. 
+Before exhibiting the general formula for the local character of the factorization algebra $\clie_\bullet(\mc{G}_{N,c})$ on $\C^3$ we set up some notation. 
+As above, we let $\chi_k^{\mf{sl}(2)}$ and $\chi^{\mf{sl}(3)}_{[k,l]}$ denote the highest weight $\mf{sl}(2)$ and $\mf{sl}(3)$ characters. 
 We also define the following expression which appears in the denominator in all of our characters
-\beqn
+\begin{equation}
 d(y_i,y,q) = (1-y_1 q)(1-y_2q)(1-y_3q) .
-\eeqn 
+\end{equation} 
 To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory $\Obs_1$ by 
-\beqn
+\begin{equation}
 g_{-1} (y_i,y,q) = f_1(y_i,y,q)
-\eeqn
+\end{equation}
 where $f_1(y_i,y,q)$ is as in equation \eqref{eqn:6done1} and also denote by 
-\beqn
-g_0 (y_i,y,q) = \til f_2(y_i,y,q)
-\eeqn
-where $\til f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
-Thus $g_2$ is the single particle local character of $\clie_\bu(\til \cG_{2,c}) = \clie_{\bu}(\cG_c^{(0)})$.
+\begin{equation}
+g_0 (y_i,y,q) = \tilde f_2(y_i,y,q)
+\end{equation}
+where $\tilde f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
+Thus $g_2$ is the single particle local character of $\clie_\bullet(\tilde {\mc{G}}_{2,c}) = \clie_{\bullet}(\mc{G}_c^{(0)})$.
 Finally, for $k \geq 1$ let
 %\begin{align*}
-%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
-%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
+%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\mf{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\mf{sl}(2)}_k(q^{-1/2} y) \right. \\
+%& \left.  - q \chi^{\mf{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\mf{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
 %\end{align*}
 %\begin{align*}
-%g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
-%& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
+%g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\mf{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\mf{sl}(2)}_k(q^{-1/2} y) \right. \\
+%& \frac{\left.  - q^{3(k-1)/2} \chi^{\mf{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\mf{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
 %\end{align*}
-\beqn
+\begin{equation}
 \label{eqn:gk}
 \begin{array}{lllll}
-g_k (y_i,y,q) \define & q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)\chi^{\lie{sl}(3)}_{[1,0]}(y_i) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
-&\displaystyle \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) \chi^{\lie{sl}(3)}_{[0,1]}(y_i) \right)}{d(y_i,y,q)} .
+g_k (y_i,y,q) \define & q^{3} \left(q^{1 + 3 k/2} \chi^{\mf{sl}(2)}_{k}(q^{-1/2} y)\chi^{\mf{sl}(3)}_{[1,0]}(y_i) + q^{3k/2} \chi^{\mf{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
+&\displaystyle \frac{\left.  - q^{3(k+1)/2} \chi^{\mf{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\mf{sl}(2)}_{k+1} (q^{-1/2} y) \chi^{\mf{sl}(3)}_{[0,1]}(y_i) \right)}{d(y_i,y,q)} .
 \end{array}
-\eeqn
-%and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.
+\end{equation}
+%and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\mf{sl}(2)$.
 
@@
 Let $N \geq 3$. 
-The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ is
-\beqn
+The local character of the factorization algebra $\clie_{\bullet}(\mc{G}_{N,c})$ is
+\begin{equation}
 \chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=-1}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
-\eeqn
-Similarly, the local character of the factorization algebra $\clie_\bu(\til{\cG}_{N,c})$ is 
-\beqn
-\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
-\eeqn
+\end{equation}
+Similarly, the local character of the factorization algebra $\clie_\bullet(\tilde{\mc{G}}_{N,c})$ is 
+\begin{equation}
+\tilde{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
+\end{equation}
 \end{thm}
 \begin{proof}
-By Lemma~\ref{lem:envelope} the character of $\clie_\bu (\cG_{N,c})$ is given by 
-\beqn
+By Lemma~\ref{lem:envelope} the character of $\clie_\bullet (\mc{G}_{N,c})$ is given by 
+\begin{equation}
 \chi_N = \text{PExp} \left[f_N\right]
-\eeqn
+\end{equation}
 where $f_N$ is the single particle local character.
@@
 Recall that from the description \eqref{eqn:gN} we have, as local Lie algebras:
-\beqn
-\cG_N = \cG / \cG^{(\geq N-2)} ,
-\eeqn 
+\begin{equation}
+\mc{G}_N = \mc{G} / \mc{G}^{(\geq N-2)} ,
+\end{equation} 
 for $N \geq 1$. 
@@
 \[
-\cG_N = \cG^{(-1)} \oplus \cG^{(0)} \oplus \cdots \oplus \cG^{(N-2)} .
+\mc{G}_N = \mc{G}^{(-1)} \oplus \mc{G}^{(0)} \oplus \cdots \oplus \mc{G}^{(N-2)} .
 \]
-%\beqn
-%\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \leftarrow \clie_\bu (\cG_{N,c}) .
-%\eeqn
-So, it suffices to observe that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG^{(k)}_c)$, which is a direct observation using the description of $\cG^{(k)}$ we have given in Proposition \ref{prop:Vj}.
+%\begin{equation}
+%\clie_{\bullet}(\mc{G}_{2,c}) \leftarrow \clie_{\bullet}(\mc{G}_{3,c}) \leftarrow \cdots \leftarrow \clie_\bullet (\mc{G}_{N,c}) .
+%\end{equation}
+So, it suffices to observe that $g_k$ is the single particle index of the factorization algebra $\clie_\bullet(\mc{G}^{(k)}_c)$, which is a direct observation using the description of $\mc{G}^{(k)}$ we have given in Proposition \ref{prop:Vj}.
 \end{proof}
 
-We thus arrive at the following conjecture for the index of the worldvolume theory on a stack of a finite number of fivebranes which we phrase in terms of the six-dimensional superconformal theory associated to the Lie algebra $\lie{sl}(N)$.
+We thus arrive at the following conjecture for the index of the worldvolume theory on a stack of a finite number of fivebranes which we phrase in terms of the six-dimensional superconformal theory associated to the Lie algebra $\mf{sl}(N)$.
 
 \begin{conj} 
-The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra of type $A_{N-1}$ is $\til \chi_{N}(y_1,y_2,y_3,y,q)$. 
+The superconformal index of the six-dimensional superconformal theory associated to the Lie algebra of type $A_{N-1}$ is $\tilde \chi_{N}(y_1,y_2,y_3,y,q)$. 
 \end{conj}
@@
 One has
-\beqn
+\begin{equation}
 \chi_{sugra}(y_i, y, q) = \lim_{N \to \infty} \chi_N(y_i,y,q)
-\eeqn
+\end{equation}
 \end{prop}
@@
 It suffices to show that at the level of single particle indices one has
-\beqn
+\begin{equation}
 f_{sugra}(y_i, y, q) = \lim_{N \to \infty} f_N(y_i,y,q) ,
-\eeqn
+\end{equation}
 where $f_N = \sum_{k = -1}^{N-2} g_k$.
@@
 We will use the following identity 
-\beqn
-\sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\lie{sl}(2)}(q^{-1/2}y) = \frac{1}{(1-q y)(1-q^2 y^{-1})} .
-\eeqn
+\begin{equation}
+\sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\mf{sl}(2)}(q^{-1/2}y) = \frac{1}{(1-q y)(1-q^2 y^{-1})} .
+\end{equation}
 We will denote this expression by $S(y,q)$.
@@
 %\begin{itemize}
-%\item $q^4 \sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\lie{sl}(2)}(q^{-1/2} y)(y_1+y_2+y_3) = \frac{q^4(y_1+y_2+y_3)}{(1-q y)(1-q^2 y^{-1})}$. 
+%\item $q^4 \sum_{k=0}^\infty q^{3k/2} \chi_{k}^{\mf{sl}(2)}(q^{-1/2} y)(y_1+y_2+y_3) = \frac{q^4(y_1+y_2+y_3)}{(1-q y)(1-q^2 y^{-1})}$. 
 %\end{itemize}
@@
 For any $N \geq 1$ one has
-\beqn
-\chi_{sugra}(y_i,y,q) = \til{\chi}_N(y_i,y,q) \mod q^{N+1} .
-\eeqn
+\begin{equation}
+\chi_{sugra}(y_i,y,q) = \tilde{\chi}_N(y_i,y,q) \mod q^{N+1} .
+\end{equation}
 \end{cor}
@@
 \end{proof}
-
-\parsec
-
-We can also apply the Schur limit  $y,y_3\to 1$ to $\chi_N$.
-\begin{prop}
-Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$) one has the following single particle index
-\beqn
-f_N (y_1,y_2, y_3=1,y=1,q) = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
-\eeqn
-The plethystic exponential of the right hand side agrees with the vacuum character of the $W_{N}$ vertex algebra.\footnote{By this we mean the principal $W$-algebra of type $A_{N-1}$.}
-\end{prop}
-\begin{proof}
-By induction it suffices to show that the specialization of the single particle local character $g_k$ of the factorization algebra $\clie_\bu(\cG^{(k)})$ is $q^{k+2} / (1-q)$. 
-We have already seen this in the case $k=-1,0$, so it suffices to show this when $k \geq 1$.
-
-First observe that the denominator becomes
-\beqn
-d(y_1,y_2,y_3=1,y=1,q) = (1-y_1 q)(1-y_2q) (1-q) .
-\eeqn
-
-Next, we observe that the numerator of $g_k (y_1,y_2,y_3=1,y=1,q)$ can be factored as
-\begin{align*}
-q^{3 + 3k/2} \left(q^{-(k+2)/2} + q^{-(k-2)/2} - q^{-k/2} (y_1+y_2) \right) 
-& = q^{k+2} (1 + q^2 - q (y_1 + y_2)) \\
-& = q^{k+2} (1 - y_1 q) (1-y_2 q) 
-\end{align*}
-where in the last line we have used $y_1 y_2 = 1$.
-The result follows.
-\end{proof}
-
-\parsec[]
-
-We would also like to point out compatibility of our expression with a certain ``minimally reduced'' index considered in \cite{Gaiotto:2021xce}. 
-This minimal reduction is the result of sending certain parameters to zero while keeping some expression in the fugacities fixed.
-To consider it it is useful to make the following change of variables: 
-\beqn
-z_i = y_i q, \quad w_1 = yq, \quad w_2 = y^{-1} q^2 .
-\eeqn
-These variables satisfy the constraint $z_1 z_2 z_3 = w_1 w_2$.
-
-This minimally reduced index corresponds to taking the following limit in the new fugacities
-\beqn\label{eqn:limitgaitto}
-z_3 , w_2 \to 0 .
-\eeqn
-This yields an index which only accounts for operators which transform trivially with respect to the symmetries that the fugacities $z_3,w_2$ correspond to. 
-This will result in an index which has three remaining fugacities.
-
-\begin{prop}
-\label{prop:gaiotto}
-The limit $z_3 , w_2 \to 0$ of the expression $\chi_{N}(z_i,w_a)$ is 
-\beqn
-\prod_{a=1}^N \prod_{b,c \geq 0} \frac{1-w_1^{a-1}z_1^{b+1} z_2^{c+1}}{1-w_1^a z_1^b z_2^c} .
-\eeqn
-\end{prop}
-\begin{proof}
-It is easy to see that the $z_3,w_2 \to 0$ limit of $g_{-1}$ is 
-\beqn
-g_{-1}(z_1,z_2,w_1) = \frac{w_1 - z_1 z_2}{(1-z_1)(1-z_2)} 
-\eeqn
-and the $z_3,w_2 \to 0$ limit of $g_0$ is 
-\beqn
-g_0(z_1,z_2,w_3) = w_1 g_{-1}(z_1,z_2,w_1) .
-\eeqn
-
-In the coordinates $z_i,w_a$ the expression $g_k$, for $k \geq 1$, in \eqref{eqn:gk} can be written as
-\beqn
-\label{eqn:gk}
-\begin{array}{lllll}
-g_k (z_i,w_a) \define & \left( z_1z_2z_3 p_k(w_1,w_2) (z_1+z_2+z_3) + p_{k+2}(w_1,w_2)  \right. \\
-&\displaystyle \frac{\left.  -z_1z_2z_3 p_{k-1}(w_1,w_2) - p_{k+1}(w_1,w_2) (z_1z_2+z_2z_3+z_1z_3) \right)}{(1-z_1)(1-z_2)(1-z_3)} .
-\end{array}
-\eeqn
-Here $p_k(w_1,w_2) = \sum_{i+j=k} w_1^i w_2^j$.
-
-From this expression it is easy to see that $\lim_{z_3,w_2 \to 0} g_k$ is 
-\beqn
-g_k(z_1,z_2,w_1) = w_1^{k+1} g_{-1}(z_1,z_2,w_1) .
-\eeqn
-The result follows from applying the plethystic exponential.
-\end{proof}
-
-The $z_3,w_2 \to 0$ limit of our index is quite similar, though not exactly, the index of a four-dimensional $\cN=1$ theory on $\C^2$ where the fugacities $z_1,z_2$ count holomorphic derivatives in each of the complex directions.
-Also, note that this minimally reduced index further reduces to the Schur limit (so the character of the $W_N$ vertex algebra) by specializing $z_1 = w_1$.
-
-\subsection{Comparisons to expansions of superconformal indices}
-
-In the final section we would like to exhibit a series of direct consistency checks with our conjectural exact formula for the index of the non-abelian six-dimensional superconformal theory with a number of expansions that have appeared in recent literature.
-
-\parsec
-Let us first focus on the superconformal theory associated to the Lie algebra $\lie{sl}(2)$ (so type $A_1$).
-Our conjecture for the superconformal index in this case is the plethystic exponential of $\til f_2 (y_i,y,q)$ from equation \eqref{eqn:6dtwo}.
-We expand the formal single particle index $\til f_2 (y_i, y, q)$ as a series in the variable~$q$, yielding
-\begin{align*}
-\til f_2 (y_i,y,q) & = y^2 q^2 + \left(1 - \chi_{[0,1]}(y_i) y + \chi_{[1,0]} y^2 \right) q^3 \\
-& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 \right) q^4 + O(q^5) .
-\end{align*}
-From this expression, we obtain the $q$-expansion of the index $\til \chi_2(y_i,y,q) = \text{PExp}[\til f_2]$ as 
-\begin{align*}
-\til \chi_2(y_i,y,q) & = 1 + y^2 q^2 + \left(1-\chi_{[0,1]}(y_i) y + \chi_{[1,0]}(y_i)y^2\right)q^3 \\ 
-& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 + y^4\right)q^4 + O(q^5)
-\end{align*}
-
-Similarly, for the $\lie{gl}(2)$ theory $\chi_2 = \text{PExp}[f_1 + \til f_2] = \chi_1 \cdot \til \chi_2$ we find the expansion
-\begin{align*}
-\chi_2 (y_i,y,q) & = y q + \left(y^{-1} - \chi_{[0,1]}(y_i) + \chi_{[1,0]}(y_i) y + 2y^2 \right) q^2 \\ 
-& + \left( \chi_{[1,0]}(y_i) y^{-1} - (\chi_{[1,1]}(y_i)-2) + (\chi_{[2,0]}(y_i) - 2 \chi_{[0,1]}(y_i)) y + 2 \chi_{[1,0]}(y_i) y^2 + 2y^3\right) q^3 \\ & + O(q^4) .
-\end{align*}
-
-We observe that these $q$-expansions agree precisely with the expansions in \cite{Kim:2013nva} for the $\lie{gl}(2)$ theory  
-(see equations (3.51) and (3.65) of \textit{loc. cit.}).
-
-\parsec
-
-We proceed to compare expansions of our exact expression for the $\lie{gl}(3)$ theory to those in \cite{Kim:2013nva}. 
-Recall that our conjectural $\lie{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
-\beqn
-\chi_3 (y_i,y,q) = \text{PExp}[f_3(y_i,y,q)] = \chi_2(y_i,y,q) \cdot \text{PExp}[g_3(y_i,y,q)]  .
-\eeqn
-Here, $f_3(y_i,y,q)$ is the single particle local character for the holomorphic factorization algebra $\Obs_3$ and $g_3(y_i,y,q)$ is given in equation \eqref{eqn:gk}.
-
-Since $g_3(y_i,y,q) = y^3 q^3 + O(q^4)$ we see that $\chi_3$ and $\chi_2$ agree up to order $q^2$ and the difference at order $q^3$ is simply
-\beqn
-\chi_3(y_i,y,q) - \chi_2(y_i,y,q) = y^3q^3 + O(q^4) .
-\eeqn
-This is again in exact agreement with the index for the $\lie{gl}(3)$ theory computed \cite{Kim:2013nva} up to order $q^3$ (see equation (3.79) of \textit{loc. cit.}).
-
-\parsec
-
-Next, we compare to expansions for the $\lie{sl}(N)$ theory computed in \cite{Imamura}, where the method of the `giant graviton' expansion is used.
-It will be convenient to change the variables $(y_i, y, q) \to (y_i,x,q)$ where 
-\beqn
-x = qy .
-\eeqn 
-We will again expand in powers of $q$.\footnote{To match precisely with the equations in \cite{Imamura} we note that it is necessary to relable the variables $y_i \leftrightarrow u_i$, $x \leftrightarrow \check{x}$, and $q \leftrightarrow y$ where the variable $y$ is distinct from the one we use in this paper!}
-
-Starting with the $\lie{sl}(2)$ theory we find that up to order $q^4$ the single particle index is
-\begin{align*}
-\til f_2 (y_i,x,q) & = x^2 + \chi_{[1,0]}(y_i) x^2 q \\
-& + \left(-\chi_{[0,1]}(y_i) x + \chi_{[2,0]}(y_i) x^2 \right) q^2 +  \left(1-x-\chi_{[1,1]}(y_i) x + \chi_{[3,0]}(y_i) x^2 \right) q^3 \\
-& + \left(2 \chi_{[1,0]}(y_i) - \chi_{[2,1]}(y_i) x + \chi_{[4,0]}(y_i)x^2 \right)q^4 + O(q^5) .
-\end{align*}
-
-It follows that the plethystic exponential $\til \chi_2(y_i,y,q)$ of this expression has $q$-expansion
-\begin{align*}
-\til \chi_2(y_i,y,q) & = \frac{1}{1-x^2} +  \frac{x^2}{1-x^2} \chi_{[1,0]}(y_i) q \\
-& + \left(- x \chi_{[0,1]}(y_i) +  x^2 (1+x^2)\chi_{[2,0]}(y_i)\right) \frac{1}{1-x^2} q^2 \\ 
-& + \left( 1 - x - x^3 + x^6 + (-x - x^3 + x^4) \chi_{[1,1]}(y_i)  + (x^2 + x^4 + x^6)\chi_{[3,0]}(y_i)  \right) \frac{1}{1-x^2} q^3 \\
-& + O(q^4) 
-\end{align*}
-This agrees with the expansion in \cite{Imamura} (see equation (68)) except for the $\lie{sl}(3)$-scalar term at order $q^3$. 
-We find $(1-x-x^3+x^6) / (1-x^2) = (1-x^3-x^4-x^5) / (1+x)$ whereas Imamura's result is $1 / (1+x)$.
-
-Similarly, we can obtain the $q$-expansions for the local character $\chi_3(y_i,x,q)$ of the factorization algebra $\Obs_3$ and compare it to the $q$-expansion for the superconformal index of the $\lie{sl}(3)$ theory in \cite{Imamura}.
-Up to order $q^2$ we have
-\begin{align*}
-\chi_3(y_i,x,q) & = \frac{1}{(1-x^2)(1-x^3)} + \frac{x^2}{(1-x)(1-x^3)} \chi_{[1,0]}(y_i) q \\
-& + \left((-x -x^2 + x^5)\chi_{[0,1]}(y_i) + (x^2 + x^3 + x^4 + x^5+ x^6) \chi_{[2,0]}(y_i) \right) \frac{1}{(1-x^2)(1-x^3)} q^2 \\
-& + O(q^3) .
-\end{align*}
-Again, we find a discrepancy of our expansion compared to \cite{Imamura} at order~$q^3$.
-It would be interesting to explain the physical or representation theoretic sources of these discrepancies in each of these cases.

### 2023-05-11 graviton spectra/content/holography.tex
graviton spectra

\section{Holographic Speculations}\label{sec:holspec}
We began this thesis with some remarks on how dualities between physical theories can often be used to uncover novel equivalences between the mathematical objects that describe them. In this final section of the thesis, we offer some speculations to this effect.
We caution the reader that a large portion of this section involves recalling constructions from physics without any attention to rigor for motivational purposes.

In sections \ref{sec:BLG}, \ref{subsec:g-1}, we commented on how minimal twists of the 3d $\mc N=8$ BLG theory and 6d $\mc N=(2,0)$ tensor multiplets are are visible as pieces of the graviton decompositions of twisted $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively. Famous instances of the AdS/CFT correspondence posit equivalences between the higher rank 3d $\mc N=8$ theories studied by ABJM and the higher rank 6d $\mc N=(2,0)$ theories of type $A_N$ with M-theory on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively. It is natural to wonder whether the twisted holograpahy proposal mentioned in the introduction can be applied to our descriptions of the twisted $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds to study the minimal twists of the higher rank 3d $\mc N=8$ and 6d $\mc N=(2,0)$ superconformal field theories respectively.

Our goal in this section is to posit some expectations regarding the minimal twist of the 6d $\mc N=(2,0)$ theory of type $A_N$. This theory is notorious for being both ubiquitous and nebulous. On the one hand, almost every superconformal field theory that has had interesting applications to geometry, topology, or representation theory occurs as one of its dimensional reductions, so it has long been expected to contain very rich mathematics. On the other hand, it does not admit a Lagrangian description. Its only free parameter is the rank of an ADE Lie algebra, and outside of the abelian case, a field realization is not even known.

We begin by recalling some features of the AdS/CFT correspondence. We will begin with a more physical language, and work towards some concrete mathematical expectations.

\subsection{The AdS/CFT correspondence}

Traditional formulations of the AdS/CFT correspondence relate two theories, schematically denoted $T_{CFT}$ and $T_{grav}$ on manifolds $M_{1}, M_{2}$ respectively, together with a conformal diffeomorphism $\del M_{2}\cong M_{1}$. The theories have the feature that boundary values of fields of $T_{grav}$ denoted $\phi |_{\del}$, may be identified with sources for $T_{CFT}$ denoted $J$. The two theories are considered to be holographically dual when their partition functions are equivalent $Z_{CFT}[J] = Z_{grav}[\phi |_{\del}]$.

In examples of stringy origin, $T_{CFT}$ describes the low energy dynamics of a stack of $N$ branes in supergravity, in the large $N$ limit, and $T_{grav}$ describes gravitational dynamics in the background the branes source.

\parsec[]
Let's identify some salient features of the primordial example of such a duality so as to inform our desiderata in the sequel.

\begin{conj}[Maldacena \cite{Maldacena:1997re}, \cite{WittenAdS}]
The following are equivalent:
\begin{itemize}
\item $\mc N=4$ super Yang-Mills theory with gauge group $SU(N)$. In addition to the rank of the gauge group, the theory has a parameter the Yang-Mills coupling constant $g_{YM}$.
\item type IIB superstring theory on $AdS_5\times S^5$ with $N$ units of five-form flux on $S^5$. The theory has two free parameters, the string coupling $g_s$ and a parameter $L/\ell_s$ which describes the scale of AdS relative to the length of the string. \end{itemize}

Under this equivalence, the parameters of the two sides are identified as follows $g_{YM}^2 = 2\pi g_s$ and $2g_{YM}^2N = (L/\ell_s)^4$. 
\end{conj}

It is convenient to introduce a parameter $\lambda = g^2_{YM} N$, the so-called \textit{'t Hooft coupling}; in the perturbative regime where the number of colors is also large (a limit that we will introduce momentarily), the $\beta$-function keeps $\lambda$ of the same order.

It is very difficult to perform explicit calculations of most observables associated to either theory at generic values of the parameters on either side. However, there are certain limits which afford more tractability.

\begin{itemize}
\item The first limit we can take involves sending the string coupling $g_s$ to zero and keeping the parameter $L/\ell_s$ fixed. In this limit, contributions from higher genus worldsheets in string perturbation theory are suppressed. Under the above identification of parameters, we see that this limit should involve taking $g_{YM}\to 0$ while keeping the 't Hooft coupling finite; that is, we must take the large $N$ limit of the gauge theory. This limit is traditionally referred to as the \textit{'t Hooft limit}. Corrections in $\frac{1}{N}$ then correspond to turning on quantum effects in string theory.

\item After taking the 't Hooft limit, we may further consider the limit where $L/\ell_s$ is large. In this limit, strings are small and particle like compared to the scale of AdS and the theory looks like classical type IIB supergravity on $AdS_5\times S^5$. On the gauge theory side, this corresponds to the limit where the 't Hooft coupling is large. As such, we see that even this simplified form of the AdS/CFT correspondence is extremely powerful as it relates strongly coupled gauge theory to classical perturbative supergravity!
\end{itemize}

\subsection{BPS observables in AdS/CFT}\label{bpsadscft}

Many checks of the AdS/CFT correspondence involve computing quantities on either side that are independent of the coupling and comparing them. Such quantities are typically BPS, and as such can be studied at the level of twists. We introduce two such quantities which we will further expand on in our relevant example below.

\parsec[]
Suppose that $T_{CFT}$ is superconformal, such as in the above example. In such examples, one expects that the superconformal algebra in fact acts on $M_2$ as isometries, at least asymptotically.

Superconformal field theories admit a plethora of protected quantities that can be computed exactly at weak coupling. One such quantity is the superconformal index, which in a Hamiltonian formulation of the theory can be thought of as a Witten-index in radial quantization. Schematically, such a quantity takes the form \[\operatorname{Tr} _{\mc H} \left ( (-1)^F \exp (-\beta \{ Q, \overline Q\} ) x_1^{J_1}\cdots x_n^{J_n}y_1^{H_1}\cdots y_n^{H_n} \right )\] where $(-1)^F$ is the fermion number operator, $\beta$ is an inverse temperature, $Q$ is a supercharge and the $x_i$ are fugacities keeping track of charges under angular momenta, and $y_i$ are fugacities keeping track of charges under R-symmetries. The superconformal index gives a generating function for the difference between bosonic and fermionic states annihilated by a particular supercharge. Under an operator-state correspondence, the superconformal index can also be thought of as a signed count of local operators preserved under a single supercharge.

In terms of partition functions, the superconformal index is gotten by a partition function on a twisted product $M_{1} = S^{1}\times_\omega S^{d-1}$ where the twisting $\omega$ is determined by a background connection for the global symmetries of the problem. The expectation that the AdS/CFT correspondence can be expressed as an equality of partition functions therefore suggests a recapitulation of the superconformal index in gravitational terms. An exciting body of work aims to make this gravitiational incarnation precise, see for example \cite{murthy2020growth} and references therein.

Note that by definition, the superconformal index provides a lower bound on the number of fractionally BPS states of $T_{CFT}$. It is often the case, however, that $T_{grav}$ includes in its spectrum, black holes, which are expected to have a thermodynamic entropy proportional to the event-horizon-area at leading order, as given by the Beckenstein-Hawking formula. As such, the growth of states in $T_{CFT}$, and hopefully the superconformal index, should reflect this.

\parsec[]
Another such quantity is the algebra of BPS local operators in $T_{CFT}$. This vector space underlying this algebra is precisely a costalk of the factorization algebra of observables of a twist of $T_{CFT}$. In light of the aforementioned operator-state correspondence, this can be thought of as categorifying the superconformal index. Under the AdS/CFT dictionary, local operators of $T_{CFT}$ are supposed to match with certain kinds of states in $T_{grav}$.

Moreover, both kinds of objects transform in representations of a superconformal algebra and the map between them preserves the actions. Local operators in the CFT are equipped with an interesting algebraic structure given by operator-product-expansion, and the AdS/CFT correspondence intertwines this algebraic structure with scattering of supergravity states. Indeed, the equality of partition functions along with the matching of sources for CFT local operators with boundary values of gravitational fields gives a prescription for computing correlation functions between CFT local operators by varying the gravitational action evaluated on field configurations subject to certain boundary values with respect to the boundary value. This recipe can be recast as a tree-level computation in the gravitational theory, involving computation of so-called Witten diagrams \cite{Witten:AdS}.

\subsection{Twisted holography}
Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of factorization algebras associated to supersymmetric twists of $T_{CFT}$ and $T_{grav}$. There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory sides.

\parsec{}
Concretely, the twisted holography proposal suggests that the type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.

Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to an (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
Following the work of \cite{CLsugra, CP1} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
If $A$ is the algebra of operators of some bulk quantum field theory (perturbatively we can even consider a theory of gravity) then $A^!$ is the algebra of operators on the universal topological line defect.
Universal here means that algebra of operators on any other line defect which couples to the bulk system admits a unique map of algebras from~$A^!$.

The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so here, but see \cite{LurieHA} for the case of $\mb E_n$-algebras and  \cite{gui2022quadratic}, \cite{tamarkin2003deformations} for the case of particular kinds of vertex algebras. This sort of duality would allow one to make sense of universality statements as above for higher dimensional, possibly non-topological, defects in an arbitrary bulk quantum field theory. Roughly, one expects the Koszul dual of a factorization algebra to be the factorization algebra corepresenting the functor of looking at solutions to a Maurer-Cartan equation in a tensor product.

\parsec{}
Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this thesis. Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory. Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{CFT}^N$.

Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{CFT}^N$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
We can, however, attempt to restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.

\begin{expect}[Twisted holographic principle following \cite{CLsugra}]\label{twistedholog}
There is a map of factorization algebras
\[
  (\Obs_{grav}|_{Y})^{!}\to \Obs_{CFT}^N
\]
that becomes an equivalence in the large $N$ limit.
\end{expect}

As we recalled in the previous subsection, traditional formulations of the AdS/CFT correspondence relate local operators of the gauge theory to states of the gravitational theory on AdS. Therefore, a natural desideratum in relating the above to more traditional statements is a precise relation between the source of the above map and gravitational states in $AdS$. Moreover, there is an operational definition of the operator-product-expansion on the costalk of a Koszul dual factorization algebra which realizes the expectation that Koszul duality corepresents the functor taking Maurer-Cartan elements in the tensor product. Another desideratum is to relate the output of this procedure with the scattering product on gravitational states computed by Witten diagrams.

\begin{rmk}
In this context, the definition of Koszul duality involves another ingredient, namely the backreaction of branes wrapping $Y$. This is meant to capture the fact that $(\Obs_{grav}|_Y)$ may not be canonically augmented, but we may try to deform it in a way that kills off the obstruction to being augmented. More precisely, one expects that the correct version of Koszul duality for application in holographic contexts is a version of \textit{curved} Koszul duality for factorization algebras. 
\end{rmk}

\begin{rmk}
For finite $N$, this map will in general be neither injective nor surjective. The kernel and cokernel of this map for finite $N$ correspond to interesting nonperturbative effects in the gravitational theory. For instance, in gauge theories:

\begin{itemize}
\item This map has a kernel given by trace relations. Syzygies between trace relations are conjecturally related to the worldvolume theories of certain other branes in the gravitational theory, so-called \textit{giant gravitons} \cite{Gaiotto:2021xce}, \cite{choi2023quantum}, \cite{Imamura} \footnote{We thank Ji-Hoon Lee for conversations related to this topic}

\item This map also has a cokernel. By fiat, these are classes that exist in the finite $N$ cohomology of the observables of a gauge theory that are not in the image of the natural map from the large $N$ theory. Recent developments in cohomological approaches to counting quantum microstates of $\frac{1}{16}$-BPS black holes in $AdS_5\times S^5$ \cite{choi2023quantum} \cite{Chang_2023} \cite{Chang_2013} can be cast as trying to characterize the cokernel of a specific example of this map. 
\end{itemize}
\end{rmk}

\parsec[]
The above expectation can be tested in instances where both sides of the duality admit explicit descriptions. This has been carried out in many examples including:
\begin{itemize}
  \item A stack of $D3$ branes in twisted $\Omega$-deformed type IIB supergravity on flat space. The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{costello2021twisted}. This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\mc{N}=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$. Here the duality can be formulated in terms of vertex algebras.

  \item M2 branes and M5 branes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}. In the particular $\Omega$-background, M2 branes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality. The koszul dual algebra bears close relations to the spherical Cherednik algebra. The $\Omega$-background localizes M5 to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra. Many celebrated features of the representation theory of these algebras and their relations with geometry have found natural explanations from the perspective of this twist of M-theory \cite{gaiotto2020miura}, \cite{Oh:2021wes}.
\end{itemize}

The example we consider is closely related to the second of these. Indeed, there is an odd nilpotent element in $\mf{osp}(6|2)$, which we refer to as $S$ in the sequel. Using the inner action of $\mf{osp}(6|2)$ on our eleven-dimensional model on twisted $AdS_7\times S^4$ as identified in proposition \ref{prop:brads7}, $S$ affords a deformation of our model. This is the deformation considered in \cite{BeemEtAl}, and it induces a specialization of characters called the Schur limit.
\parsec[]

\subsection{M5 branes, holomorphy, and holography}
The results in the second half of this thesis can be viewed as baby steps in investigating twisted holography for the minimal twist of the 6d $\mc N=(2,0)$ theory. Let us begin by spelling out the objects in expectation \ref{twistedholog} adapted to our setting.

\begin{itemize}
\item The 11d spacetime manifold $X$ is $\R\times \C^5$ and $Y$ is a copy of $\C^3$. 
\item The factorization algebra $\Obs_{grav}|_{\C^3}$ has the feature that its semiclassical free limit is the factorization algebra denoted $\clie ^\bullet \left ( \Pi \Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4})\right )$ in definition \ref{defn:ads7states}.
\item The factorization algebra $\Obs^N_{CFT}$ describes local observables in the minimal twist of the theory on a stack of $N$ M5 branes wrapping $\C^3$. 
\end{itemize}

Our goal is to try and use this map, and expectations about its kernel and cokernel, to give a concrete description of the target. There have been various approaches to try and characterize the spectrum of $\frac{1}{16}$-BPS states in the 6d $\mc N=(2,0)$ theories of type $A_{N-1}$, which furnish consistency checks to test our proposal against. Some of these involve applications of instanton counting techniques in 5d $\mc N=2$ gauge theory \cite{Kim2013nva} and some of them involve holographic techniques \cite{Imamura}.

As we remarked in subsection \ref{bpsadscft}, the first ingredient is a map of representations of the superconformal algebra between local operators of the CFT and supergravity states. In order to codify such a matching in terms of the kinds of data in the statement of expectation \ref{twistedholog}, we require a matching between supergravity states and the costalk at the origin of the factorization algebra $(\Obs_{grav}|_{\C^3})^!$. This is precisely the content of proposition \ref{prop:altstates}.

\parsec[]

We have the following conjectural large $N$ statements

\begin{conj}[R-Saberi-Williams]\label{conj:classical}
There is an equivalence of holomorphic $\mb{P}_0$-factorization algebras \[ \left( \clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a twisted factorization envelope of the local $L_\infty$-algebra $\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$. Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to a twisted factorization envelope of the local Lie algebra $\operatorname {Diff}_{\C}$ of holomorphic differential operators on $\C$. 
\end{conj}

Here, the twisting cocycle $\omega$ comes from the shifted Poisson tensor that was induced by the flux in section \ref{sec:ads}. The content in verifying this conjecture is to explicitly compute the twisting coming from the flux sourced by the brane, and check that upon deforming by the element $S$, it induces the correct cocycle on $\operatorname{Diff}(\C^\times)$

The comment in \ref{eqn:winfty} constitutes a very meager consistency check for the second part of this conjecture, where we observe that the Schur limit of the character of the costalk of $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} ) \right)$ recovers the vacuum character of the $W_{1+\infty}$ vertex algebra.

There is a deformation of the twisted factorization envelope of $\operatorname{Diff}_\C$ which yields the $\mc W_{1+\infty}$ vertex algebra, also referred to as the affine Yangian of $\mf {gl}(1)$. In \cite{CostelloM5}, Costello finds this deformation from a loop level computation in his 5d noncommutative gauge theory. We also expect to be able to lift this to the minimal twist. We summarize this expectation in a conjecture.

\begin{conj}[R-Saberi-Williams]
There is an equivalence of holomorphic factorization algebras \[ \left( \clie^\bullet_\hbar (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a deformation of the factorization algebra in the previous conjecture induced by loop-level effects in our eleven-dimensional model. Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to the $\mc {W}_{1+\infty}$ vertex algebra.
\end{conj}

\parsec[]
We now move on to finite $N$ statements. For the lowest steps of the filtration, we can make some very concrete statements.

\begin{conj}[R-Saberi-Williams]
Upon deforming by $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_\omega (\mc G^{(-1)}_{\C^3} )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Heisenberg vertex algebra.
\end{conj}
To check this conjecture, it remains to compute the pullback of the twisting cocycle $\omega$ under the inclusion of $\mc G^{(0)}$ and see that it deforms to the Heisenberg cocycle.

\parsec[]
There is a distinguished Lie sub-algebra of the algebra of differential operators on $\C^\times$ which is given by the Witt-algebra of vector fields. The central extension of $\operatorname{Diff} (\C^\times)$ induced by $\omega$ above restricts to the Virasoro central extension. Similarly, in proposition \ref{prop:g0e36} we have identified a distinguished local super-Lie algebra inside $\Pi\Omega^{0,\bullet} _{\C^3}(\mc L^{r=0} _{AdS_7\times S^4} )$ given by $\mc E(3|6)$.

Accordingly, we conjecture the following
\begin{conj}[R-Saberi-Williams]
Upon deforming by $S\in \mf{osp}(6|2)$, the factorization algebra $\mc U_\omega( \mc E(3|6) )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Virasoro vertex algebra.
\end{conj}

Again, to check this conjecture it remains to compute the pullback of the twisting cocycle $\omega$ along the inclusion $\mc E(3|6)\to \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ and compare its deformation with the cocycle giving the Virasoro central extension.

We can once again perform a consistency check at the level of characters of costalks. Indeed, we see that the plethystic exponential of the specialized character $g_0(y=1, y_3=1, q) = \frac{q^2}{1-q}$ is exactly the vacuum character of the Virasoro algebra.

Moreover, note that combining with conjecture \ref{conj:classical}, we expect maps 
\[\mc U_\omega( \mc E(3|6) )\to \left (\clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^! \to \Obs^N_{CFT}\] for every $N$. This map can be thought of as a Noether-type map associated to an  $\mc E(3|6)$-symmetry of the minimal twist of any finite rank 6d $\mc N=(2,0)$ theory \cite{CG2}.

\parsec[]
More generally, the $\mc W_{1+\infty}$ algebra has as quotients, the $\mc W_N$ algebras when the central charge is set equal to $N$. Accordingly, we dream of the following:

\begin{spec}
Under an integrality condition on the central charge, the map \[ (\Obs_{grav} |_{\C^3} )^! \to \Obs^N_{CFT}\] factors as
\[
\begin{tikzcd}
(\Obs_{grav} |_{\C^3} )^! \ar[r]\ar[d]  & \Obs^N_{CFT} \\
\mc U_{\hbar, \omega} (\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))/\mc U_{\hbar, \omega} (\prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3} ) \ar[ur]
\end{tikzcd}
\]
\end{spec}

We can perform a consistency check of the above speculation at the level of characters of costalks. It is expected that the superconformal deformation deforms $\Obs^N_{CFT}$ to the $\mc{W}_N$ vertex algebra. On the other hand, we have that

\begin{prop}
Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$), one has

\begin{align*}
\chi \left ( \Omega^{0,\bullet}_{\C^3,c} (\mc L^N_{AdS_7\times S^4})(0)/ \left ( \mc G^{(-1)}_{\C^3,c}\times \prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3,c}\right )(0)\right ) & = \sum_{j \geq 0}^{N-2} g_j (y_1,y_2, y_3=1,y=1,q) \\
& = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
\end{align*}

The plethystic exponential of the right hand side agrees with the vacuum character of the $W_{N}$ vertex algebra.
\end{prop}
\begin{proof}
By induction it suffices to show that the specialization of the single particle local character $g_j$ of the factorization algebra $\mc U(\mc{G}^{(j)})$ is $q^{j+2} / (1-q)$. 
We have already seen this in the case $j=-1,0$, so it suffices to show this when $k \geq 1$.

First observe that the denominator becomes
\begin{equation}
(1-y_1 q)(1-y_2q) (1-q) .
\end{equation}

Next, we observe that the numerator of $g_j (y_1,y_2,y_3=1,y=1,q)$ can be factored as
\begin{align*}
q^{3 + 3j/2} \left(q^{-(j+2)/2} + q^{-(j-2)/2} - q^{-j/2} (y_1+y_2) \right) 
& = q^{j+2} (1 + q^2 - q (y_1 + y_2)) \\
& = q^{j+2} (1 - y_1 q) (1-y_2 q) 
\end{align*}
where in the last line we have used $y_1 y_2 = 1$.
The result follows.
\end{proof}

\parsec{}
In \cite{raghavendran2022holographic} we try to explicitly characterize the discrepancy between the characters of $\mc U (\mc G^{(j)}_{\C^3})$ and expectations about the superconformal index of the finite rank 6d $\mc N=(2,0)$ theories computed via instanton counting techniques \cite{Kim:2013nva} and the "giant graviton expansion" \cite{Arai_2020,}, \cite{Imamura}. It would be interesting to try and categorify the discrepancies and identify them in terms of modules for $E(3|6)$.

\iffalse
\parsec{}

We would also like to point out compatibility of our expression with a certain ``minimally reduced'' index considered in \cite{Gaiotto:2021xce}. 
This minimal reduction is the result of sending certain parameters to zero while keeping some expression in the fugacities fixed.
To consider it it is useful to make the following change of variables: 
\begin{equation}
z_i = y_i q, \quad w_1 = yq, \quad w_2 = y^{-1} q^2 .
\end{equation}
These variables satisfy the constraint $z_1 z_2 z_3 = w_1 w_2$.

This minimally reduced index corresponds to taking the following limit in the new fugacities
\begin{equation}\label{eqn:limitgaitto}
z_3 , w_2 \to 0 .
\end{equation}
This yields an index which only accounts for operators which transform trivially with respect to the symmetries that the fugacities $z_3,w_2$ correspond to. 
This will result in an index which has three remaining fugacities.

\begin{prop}
\label{prop:gaiotto}
The limit $z_3 , w_2 \to 0$ of the expression $\chi_{N}(z_i,w_a)$ is 
\begin{equation}
\prod_{a=1}^N \prod_{b,c \geq 0} \frac{1-w_1^{a-1}z_1^{b+1} z_2^{c+1}}{1-w_1^a z_1^b z_2^c} .
\end{equation}
\end{prop}
\begin{proof}
It is easy to see that the $z_3,w_2 \to 0$ limit of $g_{-1}$ is 
\begin{equation}
g_{-1}(z_1,z_2,w_1) = \frac{w_1 - z_1 z_2}{(1-z_1)(1-z_2)} 
\end{equation}
and the $z_3,w_2 \to 0$ limit of $g_0$ is 
\begin{equation}
g_0(z_1,z_2,w_3) = w_1 g_{-1}(z_1,z_2,w_1) .
\end{equation}

In the coordinates $z_i,w_a$ the expression $g_k$, for $k \geq 1$, in \eqref{eqn:gk} can be written as
\begin{equation}
\label{eqn:gk}
\begin{array}{lllll}
g_k (z_i,w_a) \define & \left( z_1z_2z_3 p_k(w_1,w_2) (z_1+z_2+z_3) + p_{k+2}(w_1,w_2)  \right. \\
&\displaystyle \frac{\left.  -z_1z_2z_3 p_{k-1}(w_1,w_2) - p_{k+1}(w_1,w_2) (z_1z_2+z_2z_3+z_1z_3) \right)}{(1-z_1)(1-z_2)(1-z_3)} .
\end{array}
\end{equation}
Here $p_k(w_1,w_2) = \sum_{i+j=k} w_1^i w_2^j$.

From this expression it is easy to see that $\lim_{z_3,w_2 \to 0} g_k$ is 
\begin{equation}
g_k(z_1,z_2,w_1) = w_1^{k+1} g_{-1}(z_1,z_2,w_1) .
\end{equation}
The result follows from applying the plethystic exponential.
\end{proof}

The $z_3,w_2 \to 0$ limit of our index is quite similar, though not exactly, the index of a four-dimensional $\mc{N}=1$ theory on $\C^2$ where the fugacities $z_1,z_2$ count holomorphic derivatives in each of the complex directions.
Also, note that this minimally reduced index further reduces to the Schur limit (so the character of the $W_N$ vertex algebra) by specializing $z_1 = w_1$.

\subsection{Comparisons to expansions of superconformal indices}

In the final section we would like to exhibit a series of direct consistency checks with our conjectural exact formula for the index of the non-abelian six-dimensional superconformal theory with a number of expansions that have appeared in recent literature.

\parsec
Let us first focus on the superconformal theory associated to the Lie algebra $\mf{sl}(2)$ (so type $A_1$).
Our conjecture for the superconformal index in this case is the plethystic exponential of $\tilde f_2 (y_i,y,q)$ from equation \eqref{eqn:6dtwo}.
We expand the formal single particle index $\tilde f_2 (y_i, y, q)$ as a series in the variable~$q$, yielding
\begin{align*}
\tilde f_2 (y_i,y,q) & = y^2 q^2 + \left(1 - \chi_{[0,1]}(y_i) y + \chi_{[1,0]} y^2 \right) q^3 \\
& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 \right) q^4 + O(q^5) .
\end{align*}
From this expression, we obtain the $q$-expansion of the index $\tilde \chi_2(y_i,y,q) = \text{PExp}[\tilde f_2]$ as 
\begin{align*}
\tilde \chi_2(y_i,y,q) & = 1 + y^2 q^2 + \left(1-\chi_{[0,1]}(y_i) y + \chi_{[1,0]}(y_i)y^2\right)q^3 \\ 
& + \left(y^{-2} - \chi_{[0,1]}(y_i) y^{-1} + 2 \chi_{[1,0]}(y_i) - \chi_{[0,1]} (y_i) y + \chi_{[2,0]}(y_i) y^2 + y^4\right)q^4 + O(q^5)
\end{align*}

Similarly, for the $\mf{gl}(2)$ theory $\chi_2 = \text{PExp}[f_1 + \tilde f_2] = \chi_1 \cdot \tilde \chi_2$ we find the expansion
\begin{align*}
\chi_2 (y_i,y,q) & = y q + \left(y^{-1} - \chi_{[0,1]}(y_i) + \chi_{[1,0]}(y_i) y + 2y^2 \right) q^2 \\ 
& + \left( \chi_{[1,0]}(y_i) y^{-1} - (\chi_{[1,1]}(y_i)-2) + (\chi_{[2,0]}(y_i) - 2 \chi_{[0,1]}(y_i)) y + 2 \chi_{[1,0]}(y_i) y^2 + 2y^3\right) q^3 \\ & + O(q^4) .
\end{align*}

We observe that these $q$-expansions agree precisely with the expansions in \cite{Kim:2013nva} for the $\mf{gl}(2)$ theory  
(see equations (3.51) and (3.65) of \textit{loc. cit.}).

\parsec

We proceed to compare expansions of our exact expression for the $\mf{gl}(3)$ theory to those in \cite{Kim:2013nva}. 
Recall that our conjectural $\mf{gl}(3)$ index is given by the local character of the holomorphic factorization algebra $\Obs_3$:
\begin{equation}
\chi_3 (y_i,y,q) = \text{PExp}[f_3(y_i,y,q)] = \chi_2(y_i,y,q) \cdot \text{PExp}[g_3(y_i,y,q)]  .
\end{equation}
Here, $f_3(y_i,y,q)$ is the single particle local character for the holomorphic factorization algebra $\Obs_3$ and $g_3(y_i,y,q)$ is given in equation \eqref{eqn:gk}.

Since $g_3(y_i,y,q) = y^3 q^3 + O(q^4)$ we see that $\chi_3$ and $\chi_2$ agree up to order $q^2$ and the difference at order $q^3$ is simply
\begin{equation}
\chi_3(y_i,y,q) - \chi_2(y_i,y,q) = y^3q^3 + O(q^4) .
\end{equation}
This is again in exact agreement with the index for the $\mf{gl}(3)$ theory computed \cite{Kim:2013nva} up to order $q^3$ (see equation (3.79) of \textit{loc. cit.}).

\parsec

Next, we compare to expansions for the $\mf{sl}(N)$ theory computed in \cite{Imamura}, where the method of the `giant graviton' expansion is used.
It will be convenient to change the variables $(y_i, y, q) \to (y_i,x,q)$ where 
\begin{equation}
x = qy .
\end{equation} 
We will again expand in powers of $q$.\footnote{To match precisely with the equations in \cite{Imamura} we note that it is necessary to relable the variables $y_i \leftrightarrow u_i$, $x \leftrightarrow \check{x}$, and $q \leftrightarrow y$ where the variable $y$ is distinct from the one we use in this paper!}

Starting with the $\mf{sl}(2)$ theory we find that up to order $q^4$ the single particle index is
\begin{align*}
\tilde f_2 (y_i,x,q) & = x^2 + \chi_{[1,0]}(y_i) x^2 q \\
& + \left(-\chi_{[0,1]}(y_i) x + \chi_{[2,0]}(y_i) x^2 \right) q^2 +  \left(1-x-\chi_{[1,1]}(y_i) x + \chi_{[3,0]}(y_i) x^2 \right) q^3 \\
& + \left(2 \chi_{[1,0]}(y_i) - \chi_{[2,1]}(y_i) x + \chi_{[4,0]}(y_i)x^2 \right)q^4 + O(q^5) .
\end{align*}

It follows that the plethystic exponential $\tilde \chi_2(y_i,y,q)$ of this expression has $q$-expansion
\begin{align*}
\tilde \chi_2(y_i,y,q) & = \frac{1}{1-x^2} +  \frac{x^2}{1-x^2} \chi_{[1,0]}(y_i) q \\
& + \left(- x \chi_{[0,1]}(y_i) +  x^2 (1+x^2)\chi_{[2,0]}(y_i)\right) \frac{1}{1-x^2} q^2 \\ 
& + \left( 1 - x - x^3 + x^6 + (-x - x^3 + x^4) \chi_{[1,1]}(y_i)  + (x^2 + x^4 + x^6)\chi_{[3,0]}(y_i)  \right) \frac{1}{1-x^2} q^3 \\
& + O(q^4) 
\end{align*}
This agrees with the expansion in \cite{Imamura} (see equation (68)) except for the $\mf{sl}(3)$-scalar term at order $q^3$. 
We find $(1-x-x^3+x^6) / (1-x^2) = (1-x^3-x^4-x^5) / (1+x)$ whereas Imamura's result is $1 / (1+x)$.

Similarly, we can obtain the $q$-expansions for the local character $\chi_3(y_i,x,q)$ of the factorization algebra $\Obs_3$ and compare it to the $q$-expansion for the superconformal index of the $\mf{sl}(3)$ theory in \cite{Imamura}. 
Up to order $q^2$ we have
\begin{align*}
\chi_3(y_i,x,q) & = \frac{1}{(1-x^2)(1-x^3)} + \frac{x^2}{(1-x)(1-x^3)} \chi_{[1,0]}(y_i) q \\
& + \left((-x -x^2 + x^5)\chi_{[0,1]}(y_i) + (x^2 + x^3 + x^4 + x^5+ x^6) \chi_{[2,0]}(y_i) \right) \frac{1}{(1-x^2)(1-x^3)} q^2 \\
& + O(q^3) .
\end{align*}
Again, we find a discrepancy of our expansion compared to \cite{Imamura} at order~$q^3$.
It would be interesting to explain the physical or representation theoretic sources of these discrepancies in each of these cases.
\fi

### 2023-05-11 graviton spectra/content/index.tex
graviton spectra

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

\section{Twisted supergravity states}
\label{sec:states}

%The first entry of the AdS/CFT dictionary in traditional treatments is a matching between \textit{supergravity states} and local operators in the CFT.
%The goal of this section is to provide constructions of spaces of twisted supergravity states in our eleven-dimensional model, via geometric quantization. 
%The state space on the twisted version of $AdS_{7}\times S^{4}$ has a remarkable property---it is naturally a module for a certain infinite-dimensional exceptional super Lie algebra. 
%We conclude the section by computing characters for these modules and comparing them with large $N$ indices for fivebranes and membranes in the literature.

In this section, we pursue a check of conjectures \ref{conj:ads4} and \ref{conj:ads7}. We enumerate supergravity states in the twists of the $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds and compare them with expressions in the literature enumerating gravitons in these geometries.

We begin by giving a definition of supergravity states suited to our context. The definition is meant to codify the following situation. Suppose we have a theory of gravity defined on a background of the form $AdS_{d+1} \times S^{d^\prime}$ where the conformal boundary of $AdS_{d+1}$ is a $d$ manifold $M$. We can compactify the theory, retaining all the Kaluza-Klein harmonics, to get a theory on $AdS_{d+1}$. A supergravity state is traditionally defined to be a solution to linearized equations of motion in this compactified theory with a given boundary value on $M^{d}$ \cite{WittenAdS}. Often, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

\parsec[]

For twists of supergravity, we procedurally implement this as follows. First, we wish to describe a model for sphere compactification on twisted $AdS$ backgrounds. As we saw in the last section, our proposal for twists of backgrounds of the form $AdS_{d+1}\times S^{d^\prime}$ involve placing certain local $L_\infty$-algebras on certain manifolds of the form $X = \operatorname{Tot }(V\to Z)\setminus 0(Z)$. Note that $Z$ can be written as a sphere bundle over $\R_{>0}\times Z$ - the sphere compactification of our theory on $X$ is given by the pushforward to $\R_{>0}\times Z$. Such sphere compactifications can be described using a method for computing pushforwards of modules for Lie algebroids associated to foliations \cite[Sec. 4.2]{KormanThesis}, \cite{KamberTondeur}.

The compactified theory will admit a natural boundary condition at $\{\infty\}\times Z\subset \R_{>0}\times Z$, given by certain local $L_\infty$-algebras $\mc L$. In fact, the presence of extra differentials involving bracketing with the flux sourced by branes wrapping $Z$ will induce an interesting shifted-Poisosn structure on $\mc L$. Given a local $L_\infty$-algebra $\mc L$ underlying a perturbative classical field theory, the Chevalley-Eilenberg cochains $\clie^\bullet (\mc L)$ carry the structure of a $\mb{P}_0$-factorization algebra \cite{CG1}, \cite{CG2}. Associated to a factorization algebra, we can define a space of local operators, which is the costalk at a point of the underlying cosheaf. The sought-after spaces of supergravity states will be a space of local operators associated to $\clie^\bullet (\mc L)$.

\begin{rmk}
Crucially, we will only implement this procedure at the level of the free limits of the theories defined in \ref{defn:ads4}, \ref{defn:ads7} - this will suffice for the purposes of extracting spaces of states and will allow us to forgo discussion involving homotopy transfer of $L_\infty$ structure. As such, the boundary conditions we specify at $\{\infty\}\times Z$ will in fact be abelian local Lie algebras. On the other hand, in subsection \ref{sec:transversebc} we will identify boundary conditions for the pushforward of the \textit{interacting} theories that exist after turning off the flux, which yield the same spaces of supergravity states. 
\end{rmk}

Let us now carry out this construction for the theories defined in \ref{defn:ads4}, \ref{defn:ads7}.

%\parsec[s:brkevin]
%As a way to highlight the key aspects of the construction, we detail the ingredients in the simplified model of Costello's twisted $M$ theory. The relevant local calculation can be found in the appendix of \cite{}; our goal here is to simply identify the salient global features that allow one to reduce to said local calculation.

%We consider the theory on $M = \text{Tot} (\R\oplus K_{C})$, with some number of twisted `fivebranes' wrapping the zero section
%\[
%0 \times C \subset \R \times \T^* C .
%\]
%Denote by $t$ the real coordinate and by $w$ the fiber coordinate in $\T^* C$. We wish to describe the complement of the zero section $\mathring M = M - 0 \times C$.

%Note that the bundle $\R\oplus K_{C}$ is equipped with a partially flat connection - this data equips the total space $M$ with the data of a transversely holomorphic foliation (THF) \cite{DuchampKalka}.

%If we choose a fiberwise partially hermitian metric on the bundle $\R \oplus K_C$ we obtain a projection $p: \R \times \T^*C \to \R_{+} \times C$ which combines the fiberwise norm with the natural bundle projection. The restriction $p| \mathring M$ equips $\mathring M$ with the structure of an $S^{2}$-bundle over $\R_{>0}\times C$. Moreover, the partial flat connection on $\R\oplus K_{C}$ induces a partially flat connection on $\mathring M$. As part of this data, each of the fiber spheres is equipped with a complex foliation of rank 1.

%Compactification amounts to pushing forward a local $L_{\infty}$-algebra along $p| \mathring M$. The result is a theory with infinitely many Kaluza--Klein modes along the fiber spheres. In the holomorphic-topological setting, the Kaluza-Klein modes will be modeled by a variant of Cauchy-Riemann cohomology.

%Moreover, including the flux sourced by the brane deforms this structure. The lowest lying Kaluza-Klein modes in the deformed theory are equivalent to three-dimensional Chern-Simons theory.

%For sake of analogy, we think of the resulting deformation as being a twisted version of $AdS_3 \times S^2$.\footnote{It is an interesting question if this corresponds the actual twist of a five--dimensional supersymmetric background of this form.}
%We proceed to describe the twisted version of states at the boundary of this version of $AdS$.
%We first proceed before turning on the flux sourced by the brane.

%The theory admits a natural `vacuum' boundary condition at $r=0$.
%In local coordinates, these are fields $\alpha(t,z,w)$ on the complement to the brane which extend to regular functions along the brane.

%The `supergravity states' are, by definition, fields which satisfy the linearized equations of motion and satisfy the vacuum boundary condition except at a single point.
%The linearized equations of motion are simply $(\d_{dR} + \dbar) \alpha = 0$.
%Thus, up to equivalence, all solutions to the linearized equations of motion are constant in the real variable $t$, and holomorphic in $z,w$.

%Modifications of the boundary condition at the point~$z = 0$ on the boundary take the form
%\[
%\alpha = f(w) \delta^{(r)}_{z=0}
%\]
%where $f$ is some holomorphic function.
%Here $\delta^{(r)}_{z=0}$ denotes the $r$th derivative of the $\delta$-function at $z=0$.
%It is convenient to parameterize such boundary modifications algebraically by expressions of the form
%\[
%\alpha_{k,r} = w^k \delta^{(r)}_{z=0} .
%\]
%Linear combinations of such states form a dense subspace of all possible modifications at the boundary.

%The reason that the boundary modifications take this form can be seen by understanding in more explicit terms the vacuum boundary condition.
%The phase space at the boundary $C$ can be identified with the following cohomology
%\[
%\Omega^{0,\bullet}(C) \otimes \mc{A}^{0;\bullet}(\R \times \C - 0) [1]
%\]
%where $\mc{A}^{0;\bullet}$ denotes the mixed de Rham--Dolbeault cohomology of $\R \times \C - 0$ as a manifold equipped with a transversely holomorphic foliation \cite{DuchampKalka}.
%We refer to the section below for a reminder on this geometric structure.

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
\subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
Following the above prescription, we consider the $S^7$ bundle 
\[
\begin{tikzcd}
S^7 \ar[r] & \operatorname{Tot} (K^{1/4}_\C\otimes \C^4 \to \R\times \C) \setminus 0(\R\times \C) \ar[d, "p"] \\ & \R_{>0}\times \R\times \C
\end{tikzcd}
\]
We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4\times S^7}$ as a sheaf of cochain complexes on $\R_{>0}\times \R\times \C$.

\begin{prop}\label{prop:pushads4}
The pushforward is given by the sheaf of complexes $\Omega^\bullet_{\R_{>0}\times \R} \otimes \Omega^{0,\bullet}_{\C} (\mc V^N_\C)$ on $\R_{>0}\times \R\times \C$, where $\mc V^N_\C$ is the following dg-vector bundle on $\C$:

\begin{equation}
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet (\C^{4}\setminus 0, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet (\C^{4}\setminus 0) \otimes \mc O \\
H^\bullet (\C^{4}\setminus 0)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
H^\bullet (\C^{4}\setminus 0)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet (\C^{4}\setminus 0) \otimes \Omega^1 \\ & H^\bullet (\C^{4}\setminus 0, \Omega^1)  \otimes \mc O
\end{tikzcd}
\end{equation}

where the differentials are as follows:
\begin{itemize}
\item The differentials $\del_\Omega^Z$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
\item The differentials $\del_Z$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
\item  Internal to each summand is a differential given by bracketing with the flux $NF_{M2}$. 
\end{itemize}
\end{prop}

Before proceeding with the proof, we explicate the internal differential in the third item above. Recall that for $\mc{F} = \mc{O}, \T$, or $\Omega^1$, the cohomology $H^\bullet(\C^4 \setminus 0, \mc{F})$ is concentrated in degrees $0$ and $3$. We will make use of the following dense embeddings.
\begin{align*}
\C[w_1,\ldots, w_4] & \hookrightarrow H^0(\C^4 \setminus 0, \mc{O}) \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} & \hookrightarrow H^0(\C^4 \setminus 0, \T) \\
\C[w_1,\ldots, w_4] \{\d w_a\} & \hookrightarrow H^0(\C^4 \setminus 0, \Omega^1) 
\end{align*}
and
\begin{align*}
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] & \hookrightarrow H^3(\C^4 \setminus 0, \mc{O}) \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} & \hookrightarrow H^3(\C^4 \setminus 0, \T) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\} & \hookrightarrow H^3(\C^4 \setminus 0, \Omega^1) .
\end{align*}

The flux $NF_{M2}$ of lemma \ref{lem:m2flux} is represented by the section $N (w_1\cdots w_4)^{-1}\del_z \in H^3 (\C^4\setminus 0)\otimes \T$ and acts on each summand by Lie derivative along $z$ and multiplying by $(w_1\cdots w_4)^{-1}$

\begin{proof}
To compute the pushforward of the kind of local $L_\infty$-algebra associated to a holomorphic-topological field theory along a map of THF manifolds, we can use a result of \cite[Sec. 4.2]{KormanThesis}, \cite{KamberTondeur} for describing direct images of Lie algebroid modules along maps of Lie algebroids. Schematically, if we have a proper submersion $p : X\to Z$ of THF manifolds, and a sheaf of complexes $\mc E$ on $X$ which resolves sections of some bundle flat along the leaves of the foliation on $X$, then the pushforward $p_*\mc E$ has a model as a partially flat bundle on $Z$. The fiber of this partially flat bundle on $Z$ is the THF cohomology of the fiber of $p$, with respect to the induced foliation on the fiber, with coefficients in the pullback of the bundle to the fiber. In the case of a holomorphic submersion, this recovers the usual construction of the Gauss-Manin connection for instance.

In our case, the pushforward $p_* \mc E_{AdS_4\times S^7}$ is a complex of $\Omega^\bullet_{\R_{>0}} \otimes \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C$- modules given by

\begin{equation}
  \label{eqn:ads4ss} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet_{\mr{THF}}(S^7, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \mc O \\
H^\bullet_{\mr{THF}} (S^7)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
H^\bullet_{\mr{THF}} (S^7)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \Omega^1
 \\ & H^\bullet_{\mr{THF}} (S^7, \Omega^1)  \otimes \mc O
 \end{tikzcd}
\end{equation}

Then the proposition follows from the fact that the map $S^7\to \C^4\setminus \{0\}$ induces an isomorphism in THF cohomology.
\end{proof}

\parsec{}
Continuing, we wish to understand a natural boundary condition we can place on the fields at $\{\infty\} \times\R\times \C\subset \R_{>0} \times \R\times \C$. Such a boundary condition is specified by a Lagrangian in the phase space. The restriction $(p_* \mc E^N_{AdS_4\times S^7})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C})$. We wish to describe a shifted Lagrangian therein.

We begin by rewriting the phase space in the following form. Note that there is a higher residue pairing 
\[H^0(\C^4\setminus 0) \otimes H^3(\C^4\setminus 0) \to \C;\]
together with the natural pairings between $T, \Omega^1$ and the integration pairing along $\R\times \C_z$, this equips $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc V^N_{\C})$ with a local even-shifted symplectic structure.

Together with this shifted symplectic structure, we can identify the phase space with a twisted cotangent bundle
\[
 \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\]
For now, the subscript of $\Pi$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\Omega^\bullet_\R\otimes\Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7})$ where $\mc L^N_{AdS_4\times S^7}$ is the following dg-vector bundle

 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
       \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
\\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
\end{equation}

\begin{rmk}
The extra term in the differential in fact equips $\Omega^\bullet_\R\otimes \Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7} )$ with an interesting $N$ dependent odd-shifted Poisson structure. This will not play a significant role in the narrative of this thesis, but we flag it for later commentary nonetheless.
\end{rmk}

\begin{defn}\label{defn:ads4states}
 The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by $\clie^\bullet \left (  \Pi \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4\times S^7}) \right )$
\end{defn}

\parsec{}
Let us explicate definition \ref{defn:ads4states} a bit. We wish to first understand the space of supergravity states as a cochain complex.

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4\times S^7})$ where $\mc H_{AdS_4\times S^7}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

\begin{proof}
To compute the costalk at $0$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence. Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc. The sections of the sheaf of cochain complexes $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
\end{tikzcd}
\end{equation}

Now note that there is a canonical map $\mc O(D) \to \C[\![z]\!] $ given by taking the Taylor expansion at the origin. Given a functional on the fields that only depends on the value of their derivatives at the origin, then the functional must factor through the Taylor expansion. Therefore, we have that the costalk of our factorization algebra is given by

\begin{equation}
 \clie^\bullet \left (\begin{tikzcd}[row sep = 1 ex]
        \ul{-} & \ul{+} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \C[\![z]\!] \ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \C[\![z]\!] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \C[\![z]\!]\del_z\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\d z \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \C[\![z]\!]
\end{tikzcd} \right )
\end{equation}

The definition of the Chevalley-Eilenberg complex above involves the continuous linear dual of a chain complex of topological vector spaces. The duals of each of the tensor factors are as follows:

\begin{itemize}
\item There is an isomorphism between the continuous linear dual of $\C[\![ z]\!]$ and $\C[\del_z]\delta_{z=0}$: every continuous linear functional on $\C[\![ z]\!]$ is given by a derivative of the $\delta$-function at zero. 
\item The higher residue pairing lets us identify the continuous linear dual of $(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]$ with $\C[w_1,\cdots, w_4]$.
\item The tensor factors involving one-forms and vector fields are dual to each other in the obvious way.
\end{itemize}

Thus, we see that $\mc H_{AdS_4\times S^7}$ is indeed as claimed.
\end{proof}

\parsec{}
We proceed to computing a local character for the factorization algebra defined in \ref{defn:ads4states}; thanks to lemma \ref{lem:ads4states} we can compute this as a character of $\Sym(\mc H_{AdS_4\times S^7})$.

We first observe the following action of $\mf{sl}(4)\oplus \mf {sl}(2)$ on $\mc H_{AdS_4\times S^7}$. The $\mf{sl}(4)$ summand acts on the tensor factor $\C[w_1,w_2,w_3,w_4]$ in the obvious way - it's the symmetric algebra on the fundamental representation. The $\mf{sl}(2)$ summand acts by bracketing with the vector fields 
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right).
\]

We choose the following explicit generators for a choice of Cartan as follows:
\begin{itemize}
\item $t_1, t_2, t_3$ denote generators for the Cartan of $\mf {sl}_4$ which is spanned by the vector fields \[h_1 = w_1\frac{\del}{\del w_1}- w_4\frac{\del}{\del w_4}, \ \ \ \ \ h_2 = w_2\frac{\del}{\del w_2}- w_4\frac{\del}{\del w_4}, \ \ \ \ h_3 = w_3\frac{\del}{\del w_3}- w_4\frac{\del}{\del w_4}\]
\item $q$ denotes a generator for the Cartan of $\mf{sl}_2$ which is spanned by the vector field \[\Delta = \frac14\sum_{a=1}^4 w_a \frac{\del }{\del w_a}-z\frac{\del}{\del z}.\]
\end{itemize}

The weights of $\mc H_{AdS_4\times S^7}$ with respect to the generators of this Cartan subalgebra are entirely determined by the weights of the holomorphic coordinates $z, w_a, a= 1, \cdots, 4$, which we summarize in table \ref{tbl:sugraM2}

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z$ & $w_1$ & $w_2$ & $w_{3}$ & $w_{4}$ \\
  \hline
  $t_{1}$ & 0 & 1 & $0$ & 0 & -1 \\
  $t_{2}$ & 0 & 0 &  1 & 0 & -1 \\
  $t_{3}$ & 0 & 0 & 0 & 1 & $-1$ \\
  $q$ & $-1$ & $\frac14$ & $\frac14$ & $\frac14$ & $\frac14$
\end{tabular}
\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus (\R\times \C^2)$.}
\label{tbl:sugraM2}
\end{center}
\end{table}

With this in hand, we wish to compute the character of the space of supergravity states $\Sym (\mc H_{AdS_4\times S^7})$. Note that the space of supergravity states was defined to be a symmetric algebra - therefore its character can be computed using plethystic exponentiation of the character of $\mc H_{AdS_4\times S^7}$ - the latter may be referred to as a \textit{single particle index} and is defined by

\[
f_{AdS_4\times S^7} (t_1, t_2, t_3, q) = \tr_{\mc H_{AdS_4\times S^7}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} t_3^{h_3}.
\]

\begin{prop}
The single particle index of the space of supergravity states $\mc H_{AdS_4\times S^7}$ is given by 
\[
f_{AdS_4\times S^7} (t_1, t_2, t_3, q)  = \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}
\]
\end{prop}
\begin{proof}
The two summands not involving holomorphic vector fields or forms appear with opposite parity, so their contributions to the character cancel. For the remaining summands, It is straightforward to compute the character of each tensor factor:
\begin{itemize}
\item The factor $\C[\del_z]\delta_{z=0}$ contributes a factor of \[\frac{q}{1-q}.\]
\item The tensor factor $\C[w_1,\cdots, w_4]$ contributes a factor of \[\frac{1}{(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}.\]
\item The tensor factors involving vector fields and forms contribute a factor of \[-q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) + q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) - q + q^{-1}.\]
\end{itemize}
\end{proof}

\parsec[] Upon subtracting one and making the substitution
\[
q = x^2, \ \ \ \ \ t_1 = (y_2y_3)^{1/2}/y_1^{1/2}, \ \ \ \ \ t_2 = (y_1y_3)^{1/2}/y_2^{1/2}, \ \ \ \ \ t_3 = (y_1y_2)^{1/2}/y_3^{1/2}
\]
this character matches the expression in \cite[Eq. 2.17]{Bhattacharya:2008zy}. The discrepancy of one is accounted for by a zero mode that we have introduced in writing our theory in such a way that M2 branes couple electrically. Indeed, this is an avatar of the central element in the central extension $\widehat{E(5|10)}$ of section \ref{thm:global}.

\subsection{States on twisted $AdS_7\times S^{4}$}
\label{s:ads7states}
Next, we consider the sphere reduction of $\mc E^N_{AdS_7\times S^4}$ As before, we consider the $S^4$ bundle 
\[
\begin{tikzcd}
S^4 \ar[r] & \operatorname{Tot} (\R\oplus K^{1/2}\otimes \C^2\to \C^3) \setminus 0(\C^3) \ar[d, "p"] \\ & \R_{>0}\times \C^3
\end{tikzcd}
\]

We wish to describe the free limit of the pushforward $p_* \mc E_{AdS_7\times S^4}$ as a sheaf of cochain complexes on $\R_{>0}\times \C^3$.

\begin{prop}\label{prop:ads7push}
The pushforward $p_* \mc E^N_{AdS_7\times S^4}$ is given by the sheaf of cochain complexes $\Omega^\bullet_{\R_{>0}} \otimes \Omega^{0,\bullet}_{\C^3} (\mc V^N_{\C^3})$ where $\mc V^N_{\C^3}$ is the following dg-vector bundle on $\C^3$:

\begin{equation}
  \label{eqn:ads7push} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\
H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0, \T \right ) \otimes \mc{O}\ar[r, "\del^W_\Omega" description]\ar[ddr, dotted] & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right ) \otimes \mc O \\
H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right ) \otimes \Omega^1 \\ & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0, \Omega^1 \right )  \otimes \mc O\ar[uul, dotted]
\end{tikzcd}
\end{equation}

where the differentials are as follows:

\begin{itemize}
\item The differentials $\del_\Omega^Z$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
\item The differentials $\del_Z$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
\item The dotted arrows are $N$ dependent differentials roughly given by bracketing with the flux, and are explicated below. 
\end{itemize}
\end{prop}

Before proceeding with the proof, it will again be useful to explicate the internal differentials above. The THF cohomology of $(\R\times \C^2) \setminus 0$ possibly with coefficients in a sheaf $\mc F$ equipped with a partial flat connection along the leaves of the THF can be described as the cohomology of the following quotient of the deRham complex 
\[\Omega^\bullet \left ((\R\times \C^2) \setminus 0 \right) / (\d w_1, \d w_2) .\]

The cohomology is accordingly concentrated in degrees zero and two. We will make use of the dense embeddings
\begin{align*}
\C[w_1,w_2] \hookrightarrow & H^0 \bigg( \Omega^\bullet\left(\C^2_w \times \R \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg) \\
w_{1}^{-1} w_2^{-1} \C[w_1^{-1},w_2^{-1}] \hookrightarrow & H^2 \bigg( \Omega^\bullet\left(\C^2_w \times \R \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg)
\end{align*}
along with the analogous versions with coefficients in the sheaf $\mc F = \Omega^1, T$.

The flux $NF_{M5}$ is then represented by a class of the form $N(w_1w_2)^{-1} \d w_1 \d w_2 \in (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]\otimes \Omega^2$. The dotted differentials in equation \ref{eqn:ads7push} are then explicitly given by maps 
\begin{align*}
\C[w_1,w_2]\{\del_{w_a}\} \otimes \mc O &\to (w_1w_2)^{-1}\C[w_1^{-1}, w_2^{-1}] \{\d w_a\}\otimes \mc O \\
\C [w_1, w_2] \otimes \Omega^1 &\to (w_1w_2)^{-1}\C[w_1^{-1}, w_2^{-1}] \otimes \T  
\end{align*}
where the first map is given by contracting with $\d w_1 \d w_2$ and multiplying by $(w_1w_2)^{-1}$, while the second map is given by applying $\del_Z$, wedging with the $\d w_1 \d w_2$ and contracting with the inverse of the holomorphic volume form on $\C^5$ to get a vector field along $\C^3$.

\begin{proof}
The proof is exactly analogous to that of proposition \ref{prop:pushads4} . Using results from \cite[Sec. 4.2]{KormanThesis}, \cite{KamberTondeur}  to compute the pushforward, we find a sheaf of $\Omega^\bullet_{\R_{>0}}\otimes \Omega^{0,\bullet}_{\C^3}$-modules whose sections have a tensor factor given by the THF cohomology of $S^4$. Next, we use the isomorphism in THF cohomology afforded by the deformation retraction of $(\R\times \C^2)\setminus 0$ onto $S^4$. 
\end{proof}

\parsec{}

As in the previous subsection, we ask for a boundary condition we can place on the fields at $\{\infty\}\times \C^3\subset \R_{>0}\times \C^3$. The phase space, given by $(p_* \mc E^N_{AdS_7\times S^4})|_{\{\infty\} \times \C^3}$, is seen to be $\Omega^{0,\bullet}_{\C^3} (\mc V_{\C^3} )$, and we search for a shifted Lagrangian therein.

Completely analogously to before, we may rewrite the phase space as a shifted cotangent bundle. The higher residue pairing, the natural pairing between $T, \Omega^1$, and the integration pairing along $\C^3$, all conspire to give the phase space an even-shifted symplectic structure. Together with this, we may ionce again identify the phase space with a twisted cotangent bundle

\[
\Omega^{0,\bullet}_{\C^3} (\mc V_{\C^3}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex] 
\ul{-} & \ul{+} \\
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{\C^3} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3}  \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3} (\T)\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3} \ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{\C^3} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{\C^3} 
\end{tikzcd} \right) 
\]

Exactly analogously to the case of $AdS_4\times S^7$, $\Pi$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.

A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{\C^3} (\mc L_{AdS_7\times S^4})$ where $\mc L_{AdS_7\times S^4}$ is the dg-vector bundle given by  
\begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc O \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]  \otimes \Omega^1 \\ & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\d w_a\} \otimes \mc O
\end{tikzcd}
\end{equation}

\begin{defn}\label{defn:ads7states}
The space of supergravity states on twisted $AdS_7\times S^4$ is given by the costalk at zero of the factorization algebra on $\C^3$ given by $\clie^\bullet \left (\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4} ) \right )$.
\end{defn}

\parsec{}
An argument exactly analogous to the proof of lemma \ref{lem:ads4states} gives us the following

\begin{lem}
The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7\times S^4} )$ where $\mc H_{AdS_7\times S^4}$ is given by the cochain complex

 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    + & - \\ \hline
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,w_2]  \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0} \\
\C[w_1,w_2]  \{\del_{z_i}\}  \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,w_2] \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2] \{\d z_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0} \\ & \C[w_1, w_2] \{\d w_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}
\end{tikzcd}
\end{equation}
\end{lem}

\parsec{}
As before, we may compute the local character of the factorization algebra defined in \ref{defn:ads7states} as a character of $\Sym (\mc H_{AdS_7\times S^4})$.

We will use an action of $\mf{sl}(3)\oplus \mf {sl}(2)\oplus \mf{gl}(1)$ on $\mc H_{AdS_7\times S^4}$ which we may explicitly realize as follows:
\begin{itemize}\label{eqn:im5}
\item
The subalgebra $\mf{sl}(3)$ acts as vector fields rotating the plane $\C^3_z$
\begin{equation}
\sum_{ij} A_{ij} z_i \frac{\del}{\del z_j} \quad (A_{ij}) \in \mf{sl}(3) .
\end{equation}
\item 
The subalgebra $\mf{sl}(2)$ acts by the triple of vector fields
\begin{equation}
 w_1 \frac{\del}{\del w_2}, \quad w_2 \frac{\del}{\del w_1}, \quad \frac{1}{2}\left (w_1\frac{\del}{\del w_1}-w_2\frac{\del}{\del w_2}\right).
\end{equation}
\item The subalgebra $\mf{gl}(1)$ acts as the vector field
\begin{equation}\label{eqn:Delta}
        \Delta = \sum_{i=1}^3 z_i\frac{\del}{\del z_i} - \frac 32\sum_{a=1}^2 w_a\frac{\del}{\del w_a}.
\end{equation}
\end{itemize}

%\begin{rmk}
%In the classification of simple super Lie algebras, Kac makes use of a weight grading $\oplus_{j \geq -2} \fg_j$ of the exceptional Lie algebra $E(3|6)$ for which the finite-dimensional subalgebra above is the weight zero piece
%\cite{KacClass}.
%We will make use of this grading in \S \ref{s:kr}.
%\end{rmk}

The character will be a function on a Cartan in $\mf {sl}(3)\oplus \mf {sl}(2)\oplus \mf {gl}(1)$; we choose one whose generators are given as follows. 
\begin{itemize}
  \item $t_{1}, t_{2}$ denote generators for the Cartan of $\mf{sl}(3)$ which is spanned by the vector fields
  \begin{equation}
  h_1 = z_1 \frac{\del}{\del {z_1}} - z_2 \frac{\del}{\del{z_2}} , \quad h_2 = z_2 \frac{\del}{\del{z_2}} - z_3 \frac{\del}{\del{z_3}}.
  \end{equation}
  \item $r$ denotes a generator for the Cartan of a $\mf{sl}(2)$ which is generated by the element 
  \begin{equation}
  \label{eqn:hCartan}
  h = \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) .
  \end{equation}
\item $q$ denotes a generator for the Cartan of the~$\mf{gl}(1)$ which is generated by the element $\Delta$ from equation~$\eqref{eqn:Delta}$. 
\end{itemize}

The weights of twisted supergravity states with respect to the generators of the Cartan subalgebra above are completely determined by the weights of the holomorphic coordinates $w_1, w_2, z_1, z_2, z_3$, which we summarize in table \ref{tbl:sugraM5}.

\begin{table}
\begin{center}
\begin{tabular}{c c c c c c}
  & $z_{1}$ & $z_{2}$ & $z_{3}$ & $w_{1}$ & $w_{2}$ \\
  \hline
  $t_{1}$ & $1$ & 0 & $-1$ & 0 & 0 \\
  $t_{2}$ & 0 & 1 & $-1$ & 0 & 0 \\
  $r$ & 0 & 0 & 0 & 1 & $-1$ \\
  $q$ & $-1$ & $-1$ & $-1$ & $\frac{3}{2}$ & $\frac{3}{2}$
\end{tabular}
\caption{Fugacities for the fields of the holomorphic twist of eleven-dimensional supergravity for the geometry $\R \times \C^5 \setminus \C^3$.}
\label{tbl:sugraM5}
\end{center}
\end{table}

We enumerate single particle supergravity states via computing the super trace of the operator $q^\Delta t_1^{h_1} t_2^{h_2} r^h$ acting on $\mc{H}_{AdS_7\times S^4}$:
\begin{equation}
f_{AdS_7\times S^4}(t_1,t_2,r,q) = \tr_{\mc{H}_{AdS_7\times S^4}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} r^h  .
\end{equation}

\begin{prop}
\label{prop:sugraindex1}
The single particle index of the space of twisted supergravity states~$\mc{H}_{AdS_7\times S^4}$ is given by the following expression
\begin{equation}
\label{eqn:sugra_index}
f_{AdS_7\times S^4} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
\end{equation}
The full (multiparticle) index is defined to be the plethystic exponential 
\begin{equation}
{\rm PExp}\left[f_{AdS_7\times S^4}(t_1,t_2,r,q)\right] .
\end{equation}
\end{prop}

\begin{proof}
As before, the two summands not involving holomorphic vector fields or forms appear with opposite parity, so their contributions to the character will cancel. For the remaining summands, it is again straightforward to compute the character of each tensor factor.
\begin{itemize}
\item The factor $\C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}$ contributes a factor of \[ \frac{q^3}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)}.\]
\item The factor of $\C[w_1, w_2]$ contributes a factor of \[ \frac{1}{(1-rq^{3/2})(1-r^{-1}q^{3/2})}.\]
\item The tensor factors involving vector fields and forms contribute a factor of \[ q(t_1^{-1}+t_1t_2^{-1}+t_2)-q^{-1}(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{-3/2}-q^{3/2})(r+r^{-1})\] 
\end{itemize}
\end{proof}

\parsec{}
To simplify the form of this index we can introduce a different parametrization of the Cartan of $\mf{sl}(3) \oplus \mf{sl}(2) \oplus \mf{gl}(1)$.
First, we can parameterize the Cartan of $\mf{sl}(3)$ by the vector fields
  \begin{equation}\label{eqn:ys}
  -(\log y_1) z_1 \frac{\del}{\del {z_1}} - (\log y_2) z_2 \frac{\del}{\del{z_2}} - (\log y_3) z_3 \frac{\del}{\del{z_3}} .
  \end{equation}
where $y_1,y_2,y_3$ are parameters which satisfy the single constraint
\begin{equation}
y_1 y_2 y_3 = 1 .
\end{equation}
In terms of the variables $t_1,t_2$ used above we have
\begin{equation}
y_1 = t_1^{-1},\quad y_2 = t_1 t_2^{-1}, \quad y_3 = t_2 .
\end{equation}
Second, we can parametrize the Cartan of the remaining subalgebra $\mf{sl}(2) \oplus \mf{gl}(1)$ by the two vector fields
\begin{equation}
\tilde{h} = h + \frac12 \Delta \quad \text{and} \quad \Delta
\end{equation}
where $\Delta$ is as in equation \eqref{eqn:Delta} and $h$ is as in \eqref{eqn:hCartan}.
We denote by $y$ the generator of the Cartan corresponding to the vector field $\tilde{h}$ and by $q$ (as above) the generator corresponding to~$\Delta$.
In terms of the variable~$r$ used above we have 
\begin{equation}
y = q^{1/2} r .
\end{equation}

Using the parametrization of the Cartan given by the variables $y_i, y,\Delta$ we obtain the equivalent expression for the index \eqref{eqn:sugra_index} as 
\begin{equation}
\label{eqn:Kim_sugra}
f_{AdS_7\times S^4} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
\end{equation}
We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
%\begin{equation}
%t_1 = y_1^{-1} , \quad t_2 = y_3, \quad r = q^{-1/2} y 
%\end{equation}

Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
\begin{equation}
q = x^4, \quad t_1 = y_2, \quad t_2 = y_1, \quad r^2 = z .
\end{equation}
(Notice the variables $y_1,y_2$ used in \cite{Bhattacharya:2008zy} differ from the variables we introduced in \eqref{eqn:ys}.)
%We record a few specializations of this index which we will remark on further in~\S\ref{s:??}.

\parsec \label{eqn:winfty}
We consider the specialization of this index 
\begin{equation}
q=r^2, t_2=1 
\end{equation}
which is known as the Schur limit.
Applying this limit to \eqref{eqn:sugra_index} yields the plethystic exponential of the following single particle index
\[
f_{AdS_7\times S^4}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2} 
\]
This plethystic exponential yields the MacMahon function, which is the character of the vacuum module of the $W_{1+\infty}$-algebra. We will revisit this observation in section \ref{sec:holspec}.

\subsection{Transverse boundary conditions}\label{sec:transversebc}
In the previous subsections, we discussed boundary conditions in the phase spaces of the sphere compactifications $p_* \mc E^N_{AdS_4\times S^7}$ and $p_* \mc E^N_{AdS_7\times S^4}$ viewed as free theories, that exist for generic values of $N$. However, there are distinguished boundary conditions that exist for $N = 0$ that we will use in the sequel. Moreover, these distinguished boundary conditions are in fact boundary conditions for the interacting theory.

Indeed, recall that in equations \eqref{}, \eqref{} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux. When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4\times S^7}^{r=0}$ denote the following dg-vector bundle on $\C$ 
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}

The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4\times S^7})|_{\{\infty\} \times\R\times\C}$ is given by $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L_{AdS_4\times S^7}^{r=0})$.

\item Let $\mc L_{AdS_7\times S^4}^{r=0}$ denote the following dg-vector bundle on $\C^3$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{+} & \ul{-} \\
\C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
\C[w_1, w_2]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7\times S^4})|_{\{\infty\} \times\C^3}$ is given by $\Omega^{0,\bullet}_{\C^3} (\mc L_{AdS_7\times S^4}^{r=0})$.
\end{itemize}

Note that the same formulae defining the $L_\infty$ structure on the parity shift of the eleven-dimensional theory $\mc E$ \ref{thm:dfn} equip these Lagrangians in the $N=0$ phase spaces with $L_\infty$ structures. Moreover, the canonical maps
\[
\Omega^\bullet_{\R} \otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4\times S^7} ) \to (p_* \mc E^0 _{AdS_4\times S^7})|_{\{\infty\} \times \R\times \C}, \quad \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} ) \to (p_* \mc E^0 _{AdS_7\times S^4})|_{\{\infty\} \times \C^3}
\]
preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$

\begin{rmk}
These boundary conditions have a very natural physical interpretation. Recall that we constructed our avatars of the $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds by codifying their appearance as backreactions of M2 and M5 branes respectively. In the absence of the fluxes sourced by these branes, we may ask that the supergravity fields extend over the former locations of these branes. As such, we can think of the boundary conditions defined above as finite-type models for the restriction of the fields of the eleven-dimensional theory to the location of branes. 
\end{rmk}

\parsec[]

The following lemma illustrates that the state space of definitions \ref{defn:ads4states} \ref{defn:ads7states} can also be computed using these alternate boundary conditions.

These Lagrangians afford an alternative description of twisted supergravity states, which will be used to investigate their representation theoretic properties.

\begin{prop}\label{prop:altstates}
There are isomorphisms
\begin{center}
$\mc U \left ( \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L_{AdS_4\times S^7}^{r=0} ) \right )(0)\cong \Sym( \mc {H}_{AdS_4\times S^7} )$ \\
$\mc U \left ( \Omega^{0,\bullet}_{\C^3}(\mc L_{AdS_7\times S^S}^{r=0})\right )(0)\cong \Sym( \mc {H}_{AdS_7\times S^4} )$
\end{center}
\end{prop}
\begin{proof}
For a local $L_\infty$ algebra $\mc L$, its factorization envelope $\mc U(L)$ is defined to be $\clie_\bullet (\mc L_c)$ the Lie algebra chains on the cosheaf of compactly supported sections. Therefore, it suffices to show that in each case, the costalk of the cosheaf of comapctly supported sections is quasi-isomorphic to $\mc H_{AdS_4\times S^7}$ and $\mc H_{AdS_7\times S^4}$ respectively. This is a consequence of the following observations.

Note that by ellipticity, there are quasi-isomorphisms 
\[\overline \Omega^{0,\bullet}_{\C,c} (D) \to \Omega^{0,\bullet}_{\C,c} (D), \ \ \ \ \overline \Omega^{0,\bullet}_{\C^3,c} \to \Omega^{0,\bullet}_{\C^3,c} (D^3).\]
coming from the inclusion of compactly supported distributional sections into compactly supported smooth sections. Now contracting the Dolbeault resolution, there are quasi-isomorphisms
\[\C[\del_z]\delta_{z=0} \to \overline \Omega^{0,\bullet}_{\C,c} (D), \ \ \ \ \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z=0} \to \overline \Omega^{0,\bullet}_{\C^3,c} (D^3).\]
These results apply equally as well for sections of holomorphic bundles. Now, computing the limit in the definition of the costalk over a collection of open sets containing the origin gives the result.
\end{proof}

%\parsec
%
%The specialization $t_1=t_2=r=1$ yields the single particle index
%\[
%f_{sugra}^{6d} (q, t_1=t_2=r=1) = \frac{3 q^4 - 3 q^2 + 2 q^{3/2} - 2 q^{9/2}}{(1-q)^3 (1-q^{3/2})^2} .
%\]

### 2023-05-11 graviton spectra/content/ops.tex
graviton spectra

--- 2022-09-01 fivebranes/ops.tex
@@
 
-\section{Local operators in twisted $M$ theory}
-
-The notion of a factorization algebra captures both the local operators of a theory together with the non-local operators that on can define from the local ones via descent.
-From the data of a factorization algebra, one can recover local operators by the following formal construction. 
-Let $\Obs$ be the factorization algebra of observables of some theory defined on a smooth manifold $M$.
-The space of local operators at point $p \in M$ is, in a precise sense, the limiting behavior of the factorization algebra evaluated on the system of open sets which contain the point~$p$.
-
-Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
-For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point.
-
-In this section we recall the essentials of the theory of local operators for holomorphic-topological theories. 
-We consider a way of counting operators in a topological-holomorphic theory, called the `local character' of a holomorphic-topological theory \cite{SWchar}, and compare it to the superconformal index.
-We then present a few simple examples and then go on to set up the theory of local operators associated to factorization algebras~$\clie_\bu(\cG_{N,c})$ we constructed in \S \ref{s:fact}.
-
-\subsection{Local operators in topological-holomorphic theories}
-
-A factorization algebra encodes the many ways to combine observables supported on arbitrary open sets. 
-Local operators, on the other hand, exist just at a point in spacetime.
-From the factorization algebra perspective one can recover local operators by looking at observables which are supported on \text{every} open set which contains the given point; mathematically this is computed by a limit.
-
-Precisely, in \cite[Definition 10.1.0.1]{CG2} the space of local operators of a factorization algebra $\cF$ at a point $p \in M$ is defined by the limit $\cF(p) = \lim_{U \ni p} \cF(U)$ which runs over open sets $U \subset M$ containing~$p$.
-
-We will only consider local operators on affine space $\R^d$. 
-In this case, we will have the additional property that the factorization algebras are translation invariant.
-At the level of local operators this means that the translation map $\tau_{p \to p'}$ induces an isomorphism $\cF(p) \simeq \cF(p')$. 
-Without loss of generality, we will consider expressions for local operators at $0 \in \R^d$.
-
-For topological-holomorphic theories the local operators take a very familiar form.
-As an algebra they are generated by (holomorphic) derivatives of the fields evaluated at the specified point. 
-More precisely, the local operators depend only on the $\infty$-jets of the fields at a point.
-In this section we carefully formulate this result and give some examples.
-
-\parsec[s:free]
-
-%Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
-%Let $\cV$ denote its sheaf of holomorphic sections.
-%The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
-%\[
-%\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
-%\]
-%where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
-%Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.
-%
-%As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
-%\begin{itemize}
-%\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
-%\[
-%[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
-%\]
-%\end{itemize}
-%A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.
-%
-%\parsec
-A topological-holomorphic theory exists on spacetimes of the form $S \times X$ where $S$ is a smooth manifold and $X$ is a complex manifold (possibly equipped with some auxiliary geometric structures).
-The typical space of fields of a holomorphic-topological theory in the BV formalism is
-\beqn\label{eqn:cE}
-\cE = \Omega^\bu (S) \hotimes \Omega^{0,\bu}(X, V) 
-\eeqn
-where $V$ is a graded holomorphic vector bundle on $X$.
-The underlying free theory is described by a differential on the space of fields of the form
-\[
-\d_{dR} + \dbar + Q^{hol} .
-\]
-Here $\d_{dR}$ is the de Rham differential acting on $S$, $\dbar$ is the Dolbeault operator acting on $X$, and $Q^{hol} \colon V \to V[1]$ is a holomorphic differential operator of cohomological degree~$+1$.
-This means that the free, linear equations of motion for a field $\varphi$ take the form
-\[
-\d_{dR} \varphi + \dbar \varphi + Q^{hol} \varphi = 0 .
-\]
-Taking into account linear gauge symmetries corresponds to cohomology---solutions to the equations of motion modulo the image of $\d_{dR} + \dbar + Q^{hol}$.
-
-Notice that $\cE$ is a sheaf of cochain complexes---it makes sense to restrict the fields to any open set $U \subset S \times X$. 
-The factorization algebra of observables of the free theory whose fields are as above assigns to an open set $U \subset S \times X$ the cochain complex
-\[
-\Obs \colon U \mapsto \cO(\cE(U)) = \Sym \left(\cE(U)^\vee \right) 
-\]
-equipped with the induced differential.
-
-Some remarks are in order:
-\begin{itemize}
-\item If $V$ is a topological vector space then $\cO(V) = \Sym(V^\vee)$ denotes the algebra of polynomials on~$V$.
-Here~$V^\vee$ is the topological dual.
-\item The topological dual of $\cE(U)$ is $\cE(U)^\vee \simeq \overline{\cE}^!_c(U)$ where the bar denotes distributional sections, the subscript $c$ denotes compact support, and $!$ denotes the Serre dual.
-Explicitly, if $U = U' \times U'' \subset S \times X$ then 
-\[
-\overline{\cE}^!_c(U' \times U'') \simeq \overline{\Omega}^\bu(U') \otimes \overline{\Omega}^{n,\bu}(U'',V^*)[n+m] 
-\]
-where $\dim_\C (X) = n$ and $\dim_\R (S) = m$. 
-\end{itemize}
-
-Let's restrict to the case that $S \times X = \R^m \times \C^n$ and suppose that the bundle $V \to \C^n$ is translation invariant with fiber $V_0$ over $0 \in \R^m \times \C^n$.
-We also assume that the operator $Q^{hol}$ is translation invariant.
-
-The jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes
-\[
-\cE(\C^n \times \R^m) \to V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] 
-\]
-The differential on the right hand side is $\d_{dR} + \dbar + Q^{hol} = \d x_i \del_{x_i} + \d \zbar_j \del_{\zbar_j} + Q^{hol}$ where $Q^{hol}$ is some holomorphic differential operator in the $z_j$ variables.
-Since all structure maps are given by holomorphic polydifferential operators, the canonical map 
-\[
-V_0 [[x_i, \d x_i,z_j, \zbar_j, \d \zbar_j]] \xto{\simeq} V_0 [[z_j]] 
-\]
-which sends $x_i, \d x_i,\zbar_j \d \zbar_j \mapsto 0$ is a quasi-isomorphism. 
-The only remaining differential on the right hand side is~$Q^{hol}$. 
-In summary, we see that the jet expansion at $0 \in \R^m \times \C^n$ determines a map of cochain complexes $\cE(\R^m \times \C^n) \to V_0[[z_j]]$.
-
-\begin{lem}
-\label{lem:taylor}
-Suppose that $\cE$ is the sheaf of cochain complexes representing the free topological-holomorphic theory on $S \times X = \R^m \times \C^n$ and consider the factorization algebra of observables~$\Obs = \cO (\cE)$.
-Then, the Taylor expansion map
-\beqn\label{eqn:taylor}
-\cE(\C^n \times \R^m) \to V_0[[z_0,\ldots,z_n]]
-\eeqn
-induces a quasi-isomorphism of commutative dg algebras
-\[
-\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]] \right) .
-\]
-%Notice that when $\cL$ is abelian with differential $\d_{dR} + \dbar + Q^{hol}$, then there is a quasi-isomorphism
-%\[
-%\Obs(0) \simeq \cO \left( V_0[[z_1,\ldots,z_n]][1] \right) 
-%\]
-%where the right hand side is equipped with the differential $Q^{hol}$. 
-\end{lem}
-\begin{proof}
-Suppose that $D_\R \times D_\C \subset \R^m \times \C^n$ is a product of a real $m$-disk times a complex $n$-disk containing the origin.
-The algebra of observables supported on $D_\R \times D_\C$ is quasi-isomorphic to 
-\[
-\cO\left( \cO^{hol}(D_\C) \otimes V_0 \right) .
-\]
-
-Observe that there is a canonical map on fields 
-\[
-\cO^{hol}(D_\C) \otimes V_0 \to V_0[[z_1,\ldots,z_n]]
-\]
-given by taking the power series expansion at $0 \in D_\R \times D_\C$. 
-If an observables on $D_\R \times D_\C$ depends on only the value of the field and its derivatives at $0 \in D_\R \times D_\C$ then it automatically factors through this map. 
-In particular, this means that there is a quasi-isomorphism of local operators with functions on $V_0[[z_1,\ldots,z_n]]$,
-\[
-\Obs(0) \simeq \cO\left(V_0 [[z_1,\ldots,z_n]]\right).
-\] 
-\end{proof}
-
-Let's unpack this result explicitly. 
-Using the $n$-dimensional residue, we can identify the topological dual of $V_0[[z_1,\ldots,z_n]]$ with the vector space
-\beqn
-\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n} V_0^* [z_0^{-1}, \ldots,z_n^{-1}] .
-\eeqn
-This is the space of linear local operators. 
-If $\chi \colon V_0 \to \C$ is a dual vector in~$V_0^*$
-then we obtain a linear local operator at $0 \in \R^m \times \C^n$ on the space of fields by the assignment
-\[
-\varphi \mapsto \del_{z_1}^{k_1} \cdots \del_{z_n}^{k_n} \<\chi,\varphi\> (0) 
-\]
-where $k_i \geq 0$. 
-Under the quasi-isomorphism of the lemma above, this corresponds to the linear local operator 
-\[
-\frac{\d z_1}{z_1^{k_1+1}} \cdots \frac{\d z_n}{z_n^{k_n+1}} \chi .
-\]
-
-\parsec[s:interaction]
-
-It is not hard to turn on interactions in the description above. 
-An interacting theory in the BV formalism is described by a local $L_\infty$ algebra structure on $\cL = \cE[-1]$, where $\cE$ is the sheaf of fields.
-For a topological-holomorphic theory the higher $L_\infty$ structure maps $[\cdot]_k$ of the local $L_\infty$ algebra are required to be given by holomorphic polydifferential operators and $[\cdot]_1 = \d_{dR} + \dbar + Q^{hol}$.
-For more details we refer to the definitions in \cite{GRWthf}.
-
-In this situation, the factorization algebra of classical observables supported on an open set $U \subset S \times X$ is given by the Chevalley--Eilenberg cochains on the $L_\infty$ algebra $\cL(U)$. 
-This defines a factorization algebra 
-\[
-\Obs \colon U \mapsto \clie^\bu(\cL(U)) .
-\]
-We will now give a concise presentation for the {\em local} operators in a topological-holomorphic theory.
-
-On $S \times X = \R^m \times \C^n$ we can also ask that all $L_\infty$ structure maps be translation invariant. 
-If this is the case, one obtains the induced structure of an $L_\infty$ algebra on the (shift of the) jets of the fields supported at $0 \in \R^m \times \C^n$
-\[
-V_0 [[z_1,\ldots,z_n]] [-1] .
-\]
-The $[\cdot]_1$ operation is precisely $Q^{hol}$ as above.
-The Taylor expansion map \eqref{eqn:taylor} is a map of $L_\infty$ algebras. 
-Combining this with Lemma \ref{lem:taylor}, one gets a quasi-isomorphism of cochain complexes between the local operators of an interacting topological-holomorphic theory in terms of Lie algebra cohomology
-\[
-\Obs(0) \simeq \clie^\bu\left(V_0[[z_1,\ldots,z_n]][-1]\right) .
-\]
-
-%We recall the reader of the standard dictionary between the space of fields of a BV theory and the local $L_\infty$ algebra---
-%if the local Lie algebra is $\cL$, then the space of fields is $\cL[1]$. 
-%The Chevalley--Eilenberg complex of $\cL$ is then functions on the fields $\cO(\cL[1])$ equipped with the non-linear BRST operator.
-
-\parsec[s:envelope]
-
-There is another way that observables are presented in a degenerate version of the BV formalism.
-Suppose that~$\cE$ is the sheaf of sections of some graded vector bundle~$E$ on a manifold~$M$.
-We have seen that the observables~$\cO(\cE) = \Sym(\cE^*)$ has the structure of a factorization algebra---we now consider the $!$-dual factorization algebra.
-That is, we consider the factorization algebra 
-\[
-U \subset M \mapsto \Sym \left(\cE_c(U) \right) 
-\]
-where $U \to \cE_c(U)$ is the cosheaf of compactly supported sections of the bundle~$E$.
-
-%Suppose that $\cL$ is a local Lie algebra on a manifold $M$. 
-%Then, one can consider the factorization algebra
-%\[
-%\cF = \clie_\bu(\cL_c)
-%\]
-%which assigns to an open set $U$ the cochain complex $\clie_\bu(\cL_c(U))$.
-%This is the $!$-dual of the factorization algebra $\clie^\bu(\cL)$.
-%For topological-holomorphic local Lie algebras there is still an algorithm for computing $\cF(p)$ for a point~$p \in M$.
-%
-%We will assume that $\cL$ is a translation invariant topological-holomorphic local Lie algebra whose underlying sheaf of cochain complexes is
-%\[
-%\cL = \Omega^\bu (\R^m) \hotimes \Omega^{0,\bu}(\C^n, L)
-%\]
-%Here $L$ is a translation invariant holomorphic vector bundle on $\C^n$ and the differential in the complex is $\d_{dR} + \dbar + Q^{hol}$ as above.
-
-\begin{lem}
-\label{lem:envelope}
-Suppose that $\cE$ is the sheaf of fields of a free holomorphic theory as in~\eqref{eqn:cE} and consider the factorization algebra~$\cF = \Sym(\cE_c)$. 
-Then, the algebra of classical local operators at~$0 \in \C^n$ of the factorization algebra~$\cF$ is quasi-isomorphic to 
-\begin{align*}
-\cF(0) & \simeq {\rm Sym} \left(\Omega^{n,hol}(\Hat{D}^n,V_0^*)^\vee [-n]\right) \\ & \cong \cO\left(\Omega^{n,hol}(\Hat{D}^n,V_0^*) [n] \right) 
-\end{align*}
-where the differential on the right hand side is~$Q^{hol}$.
-\end{lem}
-
-%\begin{lem}
-%\label{lem:envelope}
-%Suppose that $\cL$ is a topological-holomorphic local Lie algebra on $S \times X = \R^m \times \C^n$ and let $\cF$ be the factorization algebra $\clie_\bu(\cL_c)$.
-%Moreover, assume that $Q^{hol}$ is an elliptic holomorphic differential operator. 
-%Then, there is a spectral sequence converging to $H^\bu(\cF(0))$ whose first page is the $Q^{hol}$ cohomology of
-%\[
-%\cO \left(\d^n z L_0^*[[z_1,\ldots,z_n]] [n+m-1] \right) .
-%\]
-%\end{lem}
-\begin{proof}
-First, notice that as graded topological vector spaces one has an isomorphism for any open set $U \subset M$ 
-\beqn\label{eqn:dist}
-\left(\overline{\cE}^!(U)\right)^\vee \simeq \cE_c(U) 
-\eeqn
-%
-%We use the spectral sequence induced by the filtration by the homogenous degree of a local operator.
-%The first page is the cohomology of 
-%\[
-%\lim_{U \ni 0} \Sym(\cL_c(U)[1]) 
-%\]
-%with respect to the linear differential $\d_{dR} + \dbar + Q^{hol}$ which acts on $\cL_c(U)$ and extends to the symmetric algebra by the rule that it is a derivation.
-This implies there is an isomorphism
-\beqn\label{eqn:dist2}
-\Sym(\cE_c(U)) \simeq \cO\left(\overline{\cE}^!(U)\right) 
-\eeqn
-for any open set $U$.
-By assumption, the linear differential $[\cdot]_1$ is elliptic, in particular the embedding of smooth sections into distributional sections
-\beqn\label{eqn:dist3}
-\cE^!(U) \hookrightarrow \overline{\cE}^! (U)
-\eeqn
-is a quasi-isomorphism for any open set~$U$.
-
-We can assume that $U \subset \C^n$ is a Stein open set containing~$0 \in \C^n$.
-%of the form $U' \times U'' \subset \R^m \times \C^n$ with $U' \subset \R^m$ contractible and $U''\subset \C^n$ Stein.
-Then we have a sequence of quasi-isomorphisms
-\begin{align*}
-\overline{\cE}^! (U) & \simeq \cE^!(U) \\ & \simeq \Omega^{n,\bu}(U, V^*)[n].
-\end{align*}
-The result now follows from Lemma~\ref{lem:taylor}.
-
-%Thus, the first page of this spectral sequence is isomorphic to the cohomology of the local operators $\Obs(0)$ of the free theory whose underlying cochain complex of fields is 
-%\[
-%\cE = \Omega^\bu(\R^m) \hotimes \Omega^{0,\bu}(\C^n , K_{\C^n} \otimes L^*[n+m-1]).
-%\]
-%In the notation of Equation \eqref{eqn:cE}, the holomorphic vector bundle $V$ is 
-%\[
-%K_{\C^n} \otimes L^*[n+m-1] .
-%\]
-%The result now follows from Lemma~\ref{lem:taylor} where we have used $\d^n z$ for basis for the line $K_{\C^n}|_0$. 
-\end{proof}
-
-\subsection{Local characters for topological-holomorphic theories}\label{s:localchar}
-
-Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
-We will restrict our attention to cases where $\cF$, as a graded vector space, is of the form $\Sym(\cE^*)$ or $\Sym(\cE_c)$ where $\cE$ is of the form \eqref{eqn:cE}.
-
-The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries $H$, see \cite{SWchar}.
-The particular group of symmetries depends on the theory, and we will present some examples momentarily.
-
-By assumption, as a graded algebra, the algebra of local operators $\cF(0)$ of a topological-holomorphic theory is of the form
-\beqn
-\cF(0) = \Sym (\lie{s})
-\eeqn
-where $\lie{s}$ is a graded topological vector space which we interpret as the linear local operators.
-
-We will also assume that the group of symmetries $H$ acting on $\cF(0)$ arises from an action of $H$ on the linear local operators $\lie{s}$. 
-Denote by $f_{\cF}({\bf q})$ the character of $\lie{s}$ with respect to this group action---this is the so-called `single particle' character. 
-The full character of $\cF(0)$ is then given as the plethystic exponential of this single particle character
-\beqn
-\chi_{\cF}({\bf q}) = {\rm PExp}\left[f_{\cF}({\bf q}) \right] .
-\eeqn
-
-\subsection{Examples}
-
-We present some simple examples.
-
-\begin{eg}
-Suppose that $V$ is the trivial bundle on $\C^n$ and consider the theory whose fields are
-\[
-\cE = \Omega^\bu(\R^m) \otimes \Omega^{0,\bu}(\C^n) 
-\]
-where the differential is just $\d_{dR} + \dbar$. 
-Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
-\[
-\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
-\]
-Via the $n$-dimensional residue one can identify the algebra of local operators with 
-\[
-\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) ,
-\]
-where $\lie{s} \simeq \frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]$ is (equivalent to) the space of linear local operators.
-
-Consider the standard torus action $\C^\times \times \cdots \times \C^\times$ on $\C^n$. 
-We would like to observe that the character of local operators with respect to this symmetry would be given by the plethystic exponential of the single particle index (the character of the space of linear local operators) which is immediate to compute:
-\[
-\frac{1}{(1-q_1)\cdots (1-q_n)} .
-\]
-However, the plethystic exponential cannot be applied to such an expression since as a power series in $q_1,\ldots,q_n$ there is a nonzero constant term.
-This is related to the fact that there is an infinite number of operators for which the fugacities satisfy $q_1=\ldots=q_n=1$, so counting local operators in this way is ill-defined. 
-One can remedy this by introducing a single extra variable fugacity $y$ and modify the single particle index to 
-\[
-\frac{y}{(1-q_1)\cdots (1-q_n)} .
-\]
-The plethystic exponential of such an expression returns the local character
-\[
-\chi(q_1,\ldots,q_n,y) = \prod_{k_1,\ldots,k_n \geq 0} \frac{1}{1-y q_1^{k_1}\cdots q_n^{k_n}}
-\]
-which now makes sense as a power series in the variables $y,q_1,\ldots,q_n$.
-\end{eg}
-
-Its instructive to see how local operators differ between $!$-dual factorization algebras.
-Let us first point out a simple example. 
-\begin{eg}
-Consider the sheaf of cochain complexes
-\[
-\cE = \Omega^{0,\bu}\left(\C, K_{\C}^{\otimes r}\right),
-\]
-where $r \in \Z$ and the differential is~$\dbar$. 
-Then, we can consider both the factorization algebra $\Obs = \cO(\cE)$ and its $!$-dual $\Obs^! = \Sym(\cE_c)$.
-
-The $\infty$-jets at $0 \in \C$ of $\cE$ is quasi-isomorphic to $\Gamma(\Hat{D}^n, K^{\otimes r}) = \d z^{\otimes r} \C[[z]]$. 
-Thus the algebra of local operators $\Obs(0)$ is quasi-isomorphic to 
-\[
-\Obs(0) \simeq \cO \left(\Gamma(\Hat{D}, K^{\otimes r})\right) .
-\]
-In particular, the character of local operators $\Obs(0)$ is the plethystic exponential of
-\[
-\frac{q^{r}}{1-q} 
-\]
-where $q$ represents the fugacity for the standard~$\C^\times$ action on~$\C$.
-Notice that when $r = 0$ we run into a similar problem as in the previous example. 
-It is therefore convenient to introduce an extra fugacity $y$ which enters the single particle character as
-\[
-\frac{y q^{r}}{1-q}  .
-\]
-
-%Then, we have the factorization algebra which assigns to $U \subset \C$ the complex
-%\begin{align*}
-%\cF(U) & = \clie_\bu(\cL_c(U)) \\ & = \Sym\left(\Omega^{0,\bu}_c\left(U, K_U^{\otimes r}\right) [1] \right)
-%\end{align*}
-%where the differential is $\dbar$.
-
-%Serre duality induces an isomorphism
-%\begin{align*}
-%\Omega^{0,\bu}_c(\C, K_\C^{\otimes r}) \cong \left( \Gamma^{hol} (\C , K_\C \otimes K_\C^{-r})\right)^* \\
-%= \left( \Gamma^{hol} (\C , K_\C^{1-r})\right)^* .
-%\end{align*}
-
-On the other hand, by Lemma \ref{lem:envelope} we see that the local operators associated to the $!$-dual $\Obs^!(0)$ is identified with the vector space
-\[
-\cO\left(\Gamma(\Hat{D}, K^{1-r})[1]\right) .
-\]
-In particular, the character of local operators $\Obs^!(0)$ is the plethystic exponential of
-\[
--\frac{q^{1-r}}{1-q} 
-\]
-where $q$ represents the fugacity for the standard $\C^\times$ action on $\C$.
-This time, when $r=1$ there is a problem with defining the plethystic exponential. 
-To get an expression that makes sense for all $r$ we can again introduce a variable $y$ which enters the single particle character as
-\[
-- \frac{y q^{1-r}}{1-q} .
-\]
-\end{eg}
-
 \subsection{Local characters for twisted superconformal theories}\label{s:localchar}
 
-Suppose that $\cF$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
-The local character $\chi_\cF ({\bf q})$ is, by definition, the graded character of algebra of local operators $\cF(0)$ with respect to some group of symmetries \cite{SWchar}.
+Suppose that $\mc{F}$ is the factorization algebra of observables of a topological-holomorphic theory on $\R^m \times \C^n$. 
+The local character $\chi_\mc{F} ({\bf q})$ is, by definition, the graded character of algebra of local operators $\mc{F}(0)$ with respect to some group of symmetries \cite{SWchar}.
 The particular group of symmetries depends on the theory.
-In this section we focus on local characters of factorization algebras that arise as twists of six-dimensional $\cN=(2,0)$ supersymmetric theories.
+In this section we focus on local characters of factorization algebras that arise as twists of six-dimensional $\mc{N}=(2,0)$ supersymmetric theories.
 
-The (complexified) superconformal algebra in dimension six is $\lie{osp}(8|4)$. 
-The holomorphic twist of this superconformal algebra is $\lie{osp}(6|2)$. 
+The (complexified) superconformal algebra in dimension six is $\mf{osp}(8|4)$. 
+The holomorphic twist of this superconformal algebra is $\mf{osp}(6|2)$. 
 We will consider the symmetry by the bosonic subalgebra
-\beqn\label{eqn:cartan3}
-\lie{sl}(3) \times \lie{sl}(2) \times \lie{gl}(1) \subset \lie{osp}(6|2)  .
-\eeqn
+\begin{equation}\label{eqn:cartan3}
+\mf{sl}(3) \times \mf{sl}(2) \times \mf{gl}(1) \subset \mf{osp}(6|2)  .
+\end{equation}
 The corresponding generators of the Cartan, as in \S \ref{sec:states}, were denoted $h_1,h_2,h,$ and $\Delta$ and the respective fugacities $t_1,t_2,r,q$.
@@
 In particular, the holomorphic twist of any six-dimensional superconformal theory will have as a symmetry the subalgebra \eqref{eqn:cartan3}.
-If the corresponding factorization algebra is $\cF$, and the local operators $\cF(0)$, the local character is then defined by the formal expression
-\beqn
-\chi_{\cF}(t_1,t_2,r,q) = {\rm Tr}_{\cF(0)} \left((-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta\right) .
-\eeqn
-In the next section we will compute these characters in the case that the factorization algebra $\cF$ is $\clie_\bu(\cG_{N,c})$ where $N = 1,2,\ldots$.
+If the corresponding factorization algebra is $\mc{F}$, and the local operators $\mc{F}(0)$, the local character is then defined by the formal expression
+\begin{equation}
+\chi_{\mc{F}}(t_1,t_2,r,q) = {\rm Tr}_{\mc{F}(0)} \left((-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta\right) .
+\end{equation}
+In the next section we will compute these characters in the case that the factorization algebra $\mc{F}$ is $\clie_\bullet(\mc{G}_{N,c})$ where $N = 1,2,\ldots$.
 
@@
 \label{sec:sucaindex}
-The local character for the holomorphic twist of a six-dimensional $\cN=(2,0)$ supersymmetric theory agrees with the well-known superconformal index.
-Generally, in any dimension, the superconformal index counts states $\cH^Q$ which are annihilated by a particular supercharge~$Q$.
+The local character for the holomorphic twist of a six-dimensional $\mc{N}=(2,0)$ supersymmetric theory agrees with the well-known superconformal index.
+Generally, in any dimension, the superconformal index counts states $\mc{H}^Q$ which are annihilated by a particular supercharge~$Q$.
 The index is defined as a function on the Cartan of a commuting subalgebra with respect to $Q$.
@@
 
-Recall that the odd part of the $\cN=(2,0)$ supersymmetry algebra is $S_+ \otimes R$ where $S_+$ is the positive irreducible spin representation of $\lie{so}(6)$ and $R \cong \C^4$.
+Recall that the odd part of the $\mc{N}=(2,0)$ supersymmetry algebra is $S_+ \otimes R$ where $S_+$ is the positive irreducible spin representation of $\mf{so}(6)$ and $R \cong \C^4$.
 Square-zero supercharges $Q \in S_+ \otimes R$ are stratified by the rank of the corresponding map $R \to (S_+)^* \cong S_-$.
@@
 Thus, the superconformal index counts precisely the states in the holomorphic twist.
-In the terminology above these states comprise the algebra of local operators $\cH^Q = \Obs(0)$ in the holomorphic twist of the six-dimensional $\cN=(2,0)$ theory.
+In the terminology above these states comprise the algebra of local operators $\mc{H}^Q = \Obs(0)$ in the holomorphic twist of the six-dimensional $\mc{N}=(2,0)$ theory.
 
-The six-dimensional superconformal algebra (before twisting) is~$\lie{osp}(8|4)$.
+The six-dimensional superconformal algebra (before twisting) is~$\mf{osp}(8|4)$.
 The Cartan of the Lie super algebra is six-dimensional generated by elements
@@
 \]
-The holomorphic twisting supercharge $Q \in \lie{osp}(8|4)$ and the (super) commuting subalgebra is $\lie{osp}(6|2)$ together with the element 
+The holomorphic twisting supercharge $Q \in \mf{osp}(8|4)$ and the (super) commuting subalgebra is $\mf{osp}(6|2)$ together with the element 
 \[
@@
 where $Q^\dagger$ denotes the superconformal partner to the supercharge $Q$. 
-The superconformal index counts states which saturate the BPS bound $\Delta \geq 0$ as a representation for the subalgebra $\lie{osp}(6|2)$. 
+The superconformal index counts states which saturate the BPS bound $\Delta \geq 0$ as a representation for the subalgebra $\mf{osp}(6|2)$. 
 To fit with the notation used in this paper, the superconformal index can be written as
-\beqn
-\cI(y_i,y,q) = \Tr_{\cH^Q} (-1)^F q^{H + \frac13 (J_1+J_2+J_3)} y_1^{J_1} y_2^{J_2} y_3^{J_3} y^{R_1 - R_2} .
-\eeqn
-This agrees precisely with the local character $\chi(y_i,y,q)$ with the evident change of coordinates for the Cartan of $\lie{osp}(6|2)$.
+\begin{equation}
+\mc{I}(y_i,y,q) = \tr_{\mc{H}^Q} (-1)^F q^{H + \frac13 (J_1+J_2+J_3)} y_1^{J_1} y_2^{J_2} y_3^{J_3} y^{R_1 - R_2} .
+\end{equation}
+This agrees precisely with the local character $\chi(y_i,y,q)$ with the evident change of coordinates for the Cartan of $\mf{osp}(6|2)$.
 
-%The Witten index is protected under twisting---in our setup the index $\cI(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
-%The minimal twist of the Hilbert space $\cH^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
-%Thus, the index $\cI(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
+\subsection{Exceptional symmetry and a finite $N$ conjecture}
+
+Generally speaking, after twisting there are enhancements of symmetries which are present in the original theory. 
+We expect that the same occurs for any six-dimensional superconformal theory. 
+In \cite{SW6d} we have shown that at the level of the holomorphic twist the twisted superconformal algebra $\mf{osp}(6|2)$ gets enhanced to the infinite-dimensional exceptional super Lie algebra $E(3|6)$ \cite{KacClass}.
+For the case of the theory on a stack of $N$ fivebranes, whose factorization algebra we denote by $\Obs_N$, this implies that the local operators $\Obs_{N}(0)$ form a representation for $E(3|6)$.
+
+Our goal is to gain knowledge of the structure of $\Obs_N(0)$ as an $E(3|6)$-representation from our holographic analysis of the previous section.
+Indeed, in \S \ref{s:fact} we have expressed the restriction of the factorization algebra of observables of twisted eleven-dimensional supergravity to the three-fold $Z$ as the Chevalley--Eilenberg cochains of a local $L_\infty$ algebra $\mc{G}$.
+Recall that we have a decomposition of local Lie algebras $\mc{G} = \oplus_{j \geq -1} \mc{G}^{(j)}$ on the three-fold $Z$. 
+From this decomposition we have defined a family of local Lie algebras $\mc{G}_{N}$ on $Z = \C^3$ for $N=1,2,\ldots$.
+
+In \S \ref{sec:factsummary} we explained the expectation that to an open set $U \subset \C^3$, the Lie algebra cohomology of $\mc{G}_{N,c}(U)$ is equivalent to the observables $\Obs_N(U)$ of the six-dimensional theory supported on $U$.
+Each $\mc{G}_N$ is acted on by the local Lie algebra $\mc{G}^{(0)} = \mc{E}(3|6)$.
+The $\infty$-jets of $\mc{E}(3|6)$ at $0 \in \C^3$ is exactly the exceptional super Lie algebra $E(3|6)$.  
+Thus, for every $N$, the space of local operators of the factorization algebra $\clie_\bullet(\mc{G}_{N,c})$ is naturally and $E(3|6)$-representation. 
+At the level of local operators we can make the following conjecture, which we will further elucidate at the level of characters for $E(3|6)$ in the next section.
+
+\begin{conj}
+\label{conj:ops}
+Let $\Obs_N(0)$ be the local operators of the theory on a stack of $N$ fivebranes wrapping $\C^3$ in $\R \times \C^5$. 
+There is an equivalence of $E(3|6)$-representations
+\begin{equation}
+\Obs_N(0) \simeq \clie_\bullet (\mc{G}_{N,c}) (0) .
+\end{equation}
+Similarly, let $\tilde \Obs_{N}(0)$ be the local operators of the theory on a stack of $N \geq 2$ fivebranes with the center of mass degrees of freedom removed. 
+There is an equivalence of $E(3|6)$-representations
+\begin{equation}
+\tilde \Obs_N(0) \simeq \clie_\bullet (\tilde{\mc{G}}_{N,c}) (0) .
+\end{equation}
+\end{conj}
+
+%The Witten index is protected under twisting---in our setup the index $\mc{I}(t_1,t_2,r,q)$ can be computed in the minimal twist of the superconformal theory we start with.
+%The minimal twist of the Hilbert space $\mc{H}^Q$ is exactly the space of holomorphic local operators at $0$ in $\C^3$, for details see~\cite{SWchar}. 
+%Thus, the index $\mc{I}(t_1,t_2,r,q)$ agrees with the holomorphic character $\chi(t_1,t_2,r,q)$ defined above.
 
 %The superconformal index of a superconformal field theory is the Witten index of the theory in the radial quantization.
-%In our situation we look at the Hilbert space $\cH$ of the theory on $S^{5}$ and consider the index heuristically of the form
-%\beqn
-%\Tr_{\cH} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
-%\eeqn
+%In our situation we look at the Hilbert space $\mc{H}$ of the theory on $S^{5}$ and consider the index heuristically of the form
+%\begin{equation}
+%\tr_{\mc{H}} (-1)^F  x_1^{G_1} \cdots x_n^{G_n} q^{\Delta}
+%\end{equation}
 %where $\{G_i\}$ are a collection of charges that commute with the holomorphic supercharge $Q$ and its superconformal adjoint $S = Q^\dagger$. 
@@
 %Thus we consider the following index
-%\beqn
-%\cI (t_1,t_2,r,q) \define \Tr_{\cH} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
-%\eeqn
-%After tracing over $\cH$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.
+%\begin{equation}
+%\mc{I} (t_1,t_2,r,q) \define \tr_{\mc{H}} (-1)^F t_1^{h_1} t_2^{h_2} r^h q^\Delta .
+%\end{equation}
+%After tracing over $\mc{H}$ one can identify the superconformal index with the partition function of the model on a space which is topologically equivalent to~$S^{5} \times S^1$.
 
@@
 %\[
-%|-| \colon \C^3 - 0 \to \RR_{>0} .
+%|-| : \C^3 - 0 \to \RR_{>0} .
 %\]
 %The fiber of this map over a point is $S^5$. 
-%By the nature of holomorphic QFT, we can extract from the OPE in the radial direction a canonical associative ($A_\infty$) algebra $\cA_{\lie{u}(1)} = \int_{\C^3 - 0} \Obs$ which is roughly the value of the theory on $S^5$.
+%By the nature of holomorphic QFT, we can extract from the OPE in the radial direction a canonical associative ($A_\infty$) algebra $\cA_{\mf{u}(1)} = \int_{\C^3 - 0} \Obs$ which is roughly the value of the theory on $S^5$.
 %There is a canonical boundary condition of the quantum mechanics theory at radius $r = 0$ given by the local operators $\Obs(0)$ at $0 \in \C^3$ which, in turn, has the structure of a $\cA$-module. 
@@
 %
-%In the case of both membranes and fivebranes we constructed a particular restriction of the local $L_\infty$ algebra $\cL_{sugra}$ to the respective worldvolume theories which we denoted by $\Bar{\pi}_* \cL_{sugra}$.
+%In the case of both membranes and fivebranes we constructed a particular restriction of the local $L_\infty$ algebra $\mc{L}_{sugra}$ to the respective worldvolume theories which we denoted by $\Bar{\pi}_* \mc{L}_{sugra}$.
 %There are two important sub local $L_\infty$ algebras 
@@
 %\begin{tikzcd}
-%& \Bar{\pi}_*\cL_{sugra} & \\
-%\Bar{\pi}_*\cL_{sugra}^{(-1)} \ar[ur] & & \Bar{\pi}_*\cL_{sugra}^{(0)} \ar[ul] .
+%& \Bar{\pi}_*\mc{L}_{sugra} & \\
+%\Bar{\pi}_*\mc{L}_{sugra}^{(-1)} \ar[ur] & & \Bar{\pi}_*\mc{L}_{sugra}^{(0)} \ar[ul] .
 %\end{tikzcd}
@@
 %& \left(\Obs_{sugra}|_Z\right)^! & \\
-%\clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(-1)}) \ar[ur] & & \clie_\bu(\Bar{\pi}_*\cL_{sugra,c}^{(0)}) \ar[ul].
+%\clie_\bullet(\Bar{\pi}_*\mc{L}_{sugra,c}^{(-1)}) \ar[ur] & & \clie_\bullet(\Bar{\pi}_*\mc{L}_{sugra,c}^{(0)}) \ar[ul].
 %\end{tikzcd}
@@
 %
-%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\cL_{sugra} = \Pi \cF_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
+%By the usual methods of the BV formalism the action functional $S_{sugra}$ described above endows the parity shift of the fields $\mc{L}_{sugra} = \Pi \mc{F}_{sugra}$ with the structure of a holomorphic-topological local $\Z/2$ graded $L_\infty$ algebra.
 %
 %On $\C^5 \times \R$ we can describe this super Lie algebra structure explicitly. 
-%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\cL(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
+%First, by the Dolbeault and de Rham Poincar\'e lemmas it is easy that the even part of the super Lie algebra $\mc{L}(\C^5 \times \R)$ is equivalent to a one-dimensional central summand $\C$ plus the Lie algebra of divergence-free vector fields on $\C^5$:
 %\[

### 2023-05-11 graviton spectra/content/suco.tex
graviton spectra

\section{Twisted global symmetries}
\label{sec:ads}
As we indicated in the beginning of this chapter, a feature of the physical $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds is that they have as isometries, the 3d $\mc N=8$ and 6d $\mc N=(2,0)$ superconformal algebras respectively. In fact, the complex forms of these two super-Lie algebras are the same.

In this section we provide evidence for conjectures \ref{conj:ads4}\ref{conj:ads7} by arguing that the global sections of the local moduli problems $p_*\mc E_{AdS_4\times S^7}$ and $p_* \mc E_{AdS_7\times S^4}$ carry actions by the minimal twists of the relevant superconformal algebras. We will find that the twist of the superconformal algebra is the same in each case, but the actions are slightly different.

\subsection{Superconformal algebras}

The complex form of the algebra of isometries for supergravity in both the ${\mr AdS}_4$ and ${\mr AdS}_7$ backgrounds is $\mf{osp}(8|4)$ (though, their real forms differ). 
This agrees with the complex form of the 6d $\mc{N}=(2,0)$ superconformal algebra and the 3d $\mc{N}=8$ superconformal algebra. The bosonic part of this algebra is isomorphic to $\mf{so}(8) \oplus \mf{sp}(2) \cong \mf{so}(8) \oplus \mf{so}(5)$.

The following is a mild rephrasing of a result in \cite{SWsuco2} where twisted superconformal symmetry in six dimensions is studied in some detail. 
\begin{thm}[Saberi-Williams]
There is a map of super-Lie algebras $\phi: \mf {siso}_{11d} \to \mf {osp}(8|4)$. Letting $Q\in \mf{siso}_{11d}$ be the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, there is an equivalence of dg super-Lie algebras \[\left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
\end{thm}

The super-Lie algebra $\mf{osp}(6|2)$ will therefore play the role of the residual isometries of the twisted AdS background. The bosonic part of $\mf{osp}(6|2)$ is the direct sum Lie algebra $\mf{sl}(4) \oplus \mf{sl}(2)$. The odd part of the algebra $\mf{osp}(6|2)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\mf{sl}(4)$ representation and $R$ is the fundamental $\mf{sl}(2)$ representation.

\subsection{Global symmetries of twisted ${\mr AdS}_4 \times S^7$}

To provide further evidence for conjecture \ref{conj:ads4} we wish to articulate a sense in which $\mf{osp}(6|2)$ is witnessed as a symmetry of $\mc E^N_{AdS_4\times S^7}$. To this end, we will provide evidence for the claim that there is a Lie map 
\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ).\]

We first focus on the case where the flux $N=0$. In this case, we will show that the embedding factors through the natural restriction map from the theory on flat space

\[ 
\begin{tikzcd}
& H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
\mf{osp}(6|2)\ar[ur, "i_{M2}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )
\end{tikzcd}
\]
\parsec[]

We begin by describing the map $i_{M2}$. As recalled above, the bosonic part of $\mf{osp}(6|2)$ is $\mf{sl}(4)\oplus \mf {sl}(2)$. In its incarnation as a twist of 3d $\mc N=8$ superconformal symmetry, it is useful to think of the $\mf{sl}(2)$-summand as describing conformal transformations on $\C_z$, while the Lie algebra $\mf{sl}(4)$ is a residual R-symmetry describing rotations on $\C^4_w$.

The restriction of $i_{M2}$ to the bosonic summand will actually realize $\mf{sl}(4)\oplus \mf {sl}(2)$ as the global symmetries corresponding to the vector fields in equation \ref{}.
\begin{itemize}
\item The image of the bosonic summand $\mf{sl}(2)$ under $i_{M2}$ is spanned by the vector fields
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R).
\]
These vector fields are divergence free and reduce to the usual holomorphic conformal transformations along $w=0$.
\item The image of $B_{ab}\in \mf{sl}(4)$ under $i_{M2}$ is given by the vector field
\[
B_{ab} w_a \frac{\del}{\del w_b} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R).
\]
\end{itemize}

To describe the image of the fermionic part of $\mf{osp}(6|2)$ under the map $i_{M2}$ It is natural to split $R = \C_{+1} \oplus \C_{-1}$, so that the odd part decomposes as
\[
(\wedge^2 \C^4)_{+1} \oplus (\wedge^2 \C^4)_{-1} .
\]
In terms of residual 3d $\mc N=8$ superconformal symmetries, the fermionic summand $(\wedge^2 \C^4)_{+1}$ consists of residual supertranslations, while the fermionic summand $(\wedge^2 \C^4)_{-1}$ consists of the remaining superconformal transformations.

\begin{itemize}
\item 
For $e_a\wedge e_b\in (\wedge^2 \C^4)_{+1}$ we have that 
\[
i_{M2} (e_a\wedge e_b) = \frac{1}{2} (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\C^5) \otimes \Omega^0(\R) .
\] 
\item For $e_a\wedge e_b\in (\wedge^2 \C^4)_{-1}$ we have that 
\[
i_{M2} (e_a\wedge e_b) = \frac{1}{2} z (w_a \d w_b - w_b \d w_a) \in \Omega^{1,0}(\C^5) \otimes \Omega^0(\R). 
\] 
\end{itemize}

The following is a straightforward check.

\begin{lem}\label{lem:m2emb}
The map $i_{M2}$ is a Lie map.
\end{lem}

It is clear that the image of the chain-level map $i_{M2}$ defined above is closed for the linearized BRST differential $\delta^{(1)}$ so descends to a map $i_{M2}: \mf{osp}(6|2) \to H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }$ as claimed. As such, the composition $\mr{res}\circ i_{M2}$ defines an inner action of $\mf{osp}(6|2)$ on the cohomology of global sections $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$.

\parsec[]

Next, we turn on $N \ne 0$ units of nontrivial flux. Note that not all fields in the image of the map $\mr{res}\circ i_{M2}$ commute with bracketing with the flux $N F_{M2}$, and as such are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ on $\Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right )$. Nevertheless, we have the following:

\begin{prop}
\label{prop:brads4}
There exist $N$-dependent corrections to the fields defining the embedding of $\mf{osp}(6|2)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M2},-]$. 
Furthermore, these order $N$ corrections define an embedding of 
\[\mf{osp}(6|2) \to H^\bullet \left ( \Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ) .\]
\end{prop}

\begin{proof}
For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $(\R\times \C) \times (\C^4\setminus \{0\} )$ given by $\Pi\mc E^N_{AdS_4\times S^7}$ and set $F = F_{M2}$. We will show that the image of the map $\mr{res}\circ i_{M2}$ survives to the last page of a spectral sequence that abuts to the target of the above map. The spectral sequence is the one associated to the bicomplex whose differentials are the linearized BRST differential $\delta^{(1)}$ and the operator $[F,- ]$ given by bracketing with the flux. Recall from \ref{} that $F$ is an element of  $\PV^{1,3}(\C_w^4 \setminus 0) \otimes \Omega^{0,0}(\C_z) \otimes \Omega^0(\R)$ and $[F,-]$ acts on the fields according to two types of maps:
\begin{align*}
[F ,-] & : \PV^{i,\bullet}(\C^4_w \setminus 0) \otimes \PV^{j,\bullet} (\C_z) \otimes \Omega^\bullet (\R) \to \PV^{i,\bullet+3}(\C^4_w \setminus 0) \otimes \PV^{j,\bullet} (\C_z) \otimes \Omega^\bullet (\R) \\
[F,-] & : \Omega^{i,\bullet}(\C^4_w \setminus 0) \otimes \Omega^{j,\bullet} (\C_z) \otimes \Omega^\bullet (\R) \to \Omega^{i,\bullet+3}(\C^4_w \setminus 0) \otimes \Omega^{j,\bullet} (\C_z) \otimes \Omega^\bullet (\R).
\end{align*}

The first page of the spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$. It will be useful to compute this page explicitly.

Recall that the linearized BRST differential decomposes as
\[
\delta^{(1)} = \dbar + \d_{\R} + \div |_{\mu \to \nu} + \del |_{\beta \to \gamma}  .
\]
To compute this page, we use an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
This first page of this auxiliary spectral sequence is simply given by the cohomology with respect to $\dbar + \d_{\R}$. 
This cohomology is given by
\begin{equation}
  \label{eqn:ads4ss} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
H^\bullet(\C^4\setminus 0, \T) \otimes H^\bullet(\C, \mc{O}) & H^\bullet(\C^4 \setminus 0, \mc{O}) \otimes H^\bullet(\C, \mc{O}) \\
H^\bullet(\C^4\setminus 0, \mc{O}) \otimes H^\bullet(\C, \T) \\
H^\bullet(\C^4\setminus 0, \mc{O}) \otimes H^\bullet(\C, \mc{O}) & H^\bullet(\C^4\setminus 0, \mc{O}) \otimes H^\bullet(\C, \Omega^1) \\ & H^\bullet(\C^4\setminus 0, \Omega^1) \otimes H^\bullet(\C, \mc{O})  
\end{tikzcd}
\end{equation}

The cohomology of $\C$ is of course concentrated in degree zero and there is a dense embedding $\C[z] \hookrightarrow H^\bullet(\C, \mc{F})$ for $\mc{F} = \mc{O}, \T$, or $\Omega^1$. It follows that up to completion, the cohomology $H^\bullet \left ( \mc L \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ); d+\dbar \right )$ is given by the direct sum of $H^\bullet \left ( \Pi \mc E  (\R\times \C^5 ); d+\dbar \right )$ with

\begin{equation}
  \label{eqn:ads4ss2} 
   \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\
(w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}][z] \{\partial_{w_i}\}  \ar[r, dotted, "\div^W"] & (w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}] [z] \\
(w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}] [z] \partial_z \ar[ur, dotted, "\div^Z"'] \\
(w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}] [z] \ar[r, dotted, "\del_Z"] \ar[dr, dotted, "\del_W"'] & (w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}][z] \d z \\ & (w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}][z] \{\d w_i\} .
\end{tikzcd}
\end{equation}

The remaining piece of the original BRST operator is drawn in dotted lines. 
The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is thus given by the cohomology of the global symmetry algebra on $\C^5 \times \R$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to the dotted-line operators. Indeed, this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$

Recall that the image of the flux $F$ at this page in the spectral sequence corresponds to the class 
\[
[F] = (w_1 \cdots w_4)^{-1} \partial_z \in (w_1\cdots w_4)^{-1}\C[w_1^{-1},\cdots, w_4^{-1}] [z] \partial_z
\]
The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. 
As observed above, this operator maps Dolbeault degree zero elements to Dolbeault degree three elements. 
For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.

We now wish to argue that the image of the map $res\circ i_{M2}$ is annihilated by $\big[ N [F] , - \big]$. This is a direct calculation. For instance, recall that an element in the image of the odd summand $(\wedge^2 \C^2)_{-1}$ (which corresponds to a superconformal transformation) is of the form $z w_a \wedge \d w_b = z(w_a \d w_b - w_b \d w_a)$. 
We have
\[
\big[[F] , z(w_a \d w_b - w_b \d w_a) \big] = (w_1\cdots w_4)^{-1} (w_a \d w_b - w_b \d w_a) = 0
\]
since the class $(w_1\cdots w_4)^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for any $a = 1,\ldots 4$. 
\end{proof}

\begin{rmk}\label{rmk:altss}
We comment on an alternate method to compute the first page of the auxiliary spectral sequence we used to compute the first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [NF, - ]$. We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_4\times S^7}$ from section \ref{prop:ads7push}. In this case, this Serre-type spectral sequence degenerates at the $E_2$-page.
\end{rmk}

\subsection{Global symmetries of twisted $AdS_7 \times S^4$}
We now wish to repeat the analysis of the previous section for the twisted $AdS_7\times S^4$ background so as to provide evidence for conjecture \ref{conj:ads7}. As before, we wish to provide evidence for the claim that there is a Lie map

\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right ).\]

We first focus on the case $N=0$ where once again the embedding factors through the natural restriction map from the theory on flat space

\[ 
\begin{tikzcd}
& H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
\mf{osp}(6|2)\ar[ur, "i_{M5}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right )
\end{tikzcd}
\]

\parsec[s:m5embedding]
We begin by describing the map $i_{M5}$. Recall that the bosonic part of $\mf{osp}(6|2)$ is the direct sum Lie algebra $\mf{sl}(4) \oplus \mf{sl}(2)$. In its incarnation as the minimal twist of the 6d $\mc N=(2,0)$ superconformal algebra,  the roles of the $\mf{sl}(4)$ and $\mf{sl}(2)$ summands are interchanged compared to the case of the M2 brane. Indeed, the Lie algebra $\mf{sl}(4)$ represents conformal transformations along $\C^3_z$, while $\mf{sl}(2)$ is a residual R-symmetry describing rotations on $\C^2_w$.

Moreover, the restriction of $i_{M5}$ to a copy of $\mf{sl}(3)\oplus\mf{gl}(1)\oplus \mf {sl}(2)\subset \mf {sl}(4) \oplus \mf {sl}(2)$ will realize this subalgebra as the global symmetries corresponding to the vector fields in equation \ref{eqn:im5}.

\begin{itemize}
\item
The bosonic abelian subalgebra $\C^3 \subset \mf{sl}(4)$ of translations is mapped to the obvious vector fields 
\[
\frac{\del}{\del z_i} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) , \quad i=1,2,3.
\]

\item
The image of $A_{ij}\in \mf{sl}(3) \subset \mf{sl}(4)$ under $i_{M5}$ is given by the vector field
\[
A_{ij} z_i \frac{\del}{\del z_j} \in \PV^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad (A_{ij}) \in \mf{sl}(3) .
\]

\item
The image of  $\mf{gl}(1) \subset \mf{sl}(4)$ corresponding to rescaling $\C^3$ under $i_{M5}$ is the element
\[
\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - \frac32 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R)  .
\]

\item 
The image of the remaining subalgebra of $\mf{sl}(4)$, which describes special conformal transformations on $\C^3$, is spanned by the elements
\[
z_j \left(\sum_{i=1}^3 z_i \frac{\del}{\del z_i} - 2 \sum_{a=1}^2 w_a \frac{\del}{\del w_a} \right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
\] 
Notice that these vector fields are divergence-free and restrict to the ordinary special conformal transformations along $w=0$. 
\item 
The image of the bosonic summand $\mf{sl}(2)$ corresponding to residual R-symmetry is spanned by the vector fields
\[
w_1 \frac{\del}{\del w_2}, w_2 \frac{\del}{\del w_1}, \frac12 \left(w_1 \frac{\del}{\del w_1} - w_2 \frac{\del}{\del w_2}\right) \in \PV^{1,0}(\C^5) \otimes \Omega^0(\R) .
\]
\end{itemize}

To describe the image of the fermionic part of $\mf{osp}(6|2)$, which is given by $\wedge^2 W \oplus R$ with $W$ the fundamental $\mf {sl}(4)$ representation and $R$ the fundamental $\mf{sl}(2)$ representation, it is natural to split $W = L \oplus \C$ with $L = \C^3$ the fundamental $\mf{sl}(3) \subset \mf{sl}(4)$ representation. 
The odd part then decomposes as
\[
L \otimes R \oplus \wedge^2 L \otimes R \cong \C^3 \otimes \C^2 \oplus \wedge^2 \C^3 \otimes \C .
\]

\begin{itemize} 
\item The summand $L \otimes R$ consists of the remaining 6d supertranslations. Its image under $i_{M5}$ is spanned by the fields
\[
z_i \d w_a \in \Omega^{1,0}(\C^5) \otimes \Omega^0(\R) ,\quad a=1,2, \quad i =1,2,3.
\]

\item The summand $\wedge^2 L \otimes R$ consists of the remaining 6d superconformal transformations. Its image under $i_{M5}$ is spanned by the fields
\[
\frac12 w_a (z_i \d z_j - z_j \d z_i) \in \Omega^{1,0}(\C^5)\otimes \Omega^0(\R) , \quad a = 1,2, \quad k = 1,2,3. 
\]
\end{itemize}

The following is a straightforward check.
\begin{lem}\label{lem:m5emb}
The map $i_{M5}$ is a Lie map.
\end{lem}

It is again clear that the image of the chain-level map $i_{M5}$ defined above is closed for the linearized BRST differential $\delta^{(1)}$ on $\Pi \mc E$ so descends to a map $i_{M5} : \mf{osp}(6|2) \to H^\bullet (\Pi \mc E (\R\times \C^5))\cong \widehat{E (5|10)}$ as claimed. As such, the composition $\mr{res}\circ i_{M5}$ will define an inner action of $\mf{osp}(6|2)$ on the cohomology of the global sections $H^\bullet \left ( \Pi \mc E^{0}_{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.

\parsec[]

Next, we turn on $N \ne 0$  units of nontrivial flux. Again, not all fields in the image of the map $\mr{res}\circ i_{M5}$ are compatible with the total differential $\delta^{(1)} + [N F, -]$ on $\Pi \mc E^{N}_{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )$. Nevertheless, we have the following version of proposition \ref{prop:brads4}

\begin{prop}
\label{prop:brads7}
There exist $N$-dependent corrections to the fields defining the embedding of $\mf {osp}(6|2)$ summarized above which are closed for the modified BRST differential $\delta^{(1)} + [N F_{M5},-]$. Furthermore, these $N$-dependent corrections define an embedding

\[ H^\bullet \left ( \Pi \mc E^N_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right). \]

\end{prop}

\iffalse
\parsec[s:thfcohomology]

The proof of the above proposition follows from another indirect cohomological argument. 
Before getting to the proof, we introduce the relevant cohomology.

The eleven-dimensional theory is built from fields which live in the tensor product of complexes 
\[
\Omega^{0,\bullet}(\C^5) \otimes \Omega^\bullet(\R).
\]
More precisely, this is where the  fields $\beta$ and~$\nu$ live. 
The $\mu$ and~$\gamma$ fields live in versions of this complex where we take Dolbeault forms with coefficients in the holomorphic tangent and cotangent bundles, respectively.

Another way to think about this complex is to first consider the full de Rham complex $\Omega^\bullet(\C^5 \times \R)$, which includes both holomorphic and anti-holomorphic forms in the $\C^5$ direction. 
The dg algebra of all de Rham forms on $\C^5 \times \R$ has an ideal generated by the holomorphic one forms $\{\d z_i\}_{i=1,\ldots,5}$.
There is an isomorphism of dg algebras
\[
\Omega^{0,\bullet}(\C^5) \otimes \Omega^\bullet(\R) \cong \Omega^\bullet(\C^5 \times \R) \, / \, (\d z_1,\ldots, \d z_5) .
\]
The advantage of this presentation is that we can define a complex associated to more general manifolds that are not products of a complex manifold with a smooth manifold.\footnote{More generally, we are describing the cohomology of a manifold equipped with a topological holomorphic foliation.}

For the M5 brane, it was convenient to rename the holomorphic coordinates on $\C^5$ to $z_1,z_2,z_3,w_1,w_2$. 
At the twisted level, the geometry arising from backreacting M5 branes is based on the manifold 
\[
\C^5 \times \R \setminus \C^3 \cong \C_z^3 \times (\C^2_w \times \R \setminus 0) .
\]
The $\beta$ and~$\nu$ fields of the eleven-dimensional theory on this submanifold of $\C^5 \times \R$ live in the complex 
\[
\Omega^\bullet\bigg(\C^5 \times \R \setminus \C^3\bigg) \, / \, (\d z_1,\d z_2,\d z_3, \d w_1, \d w_2)  .
\]
The $\mu$ and~$\gamma$ fields live in similar complexes, where we introduce a (trivial) vector bundle on $\C^5 \times \R \setminus \C^3$.

Since the $\C^3$ wraps $w_1=w_2=t=0$ we can apply a version of the K\"unneth formula to identify this complex with 
\[
\Omega^{0,\bullet}(\C^3_z) \otimes \bigg( \Omega^\bullet\left(\C^2_w \times \R \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
\]

The cohomology of the Dolbeault complex of $\C^3_z$ is easy to compute. 
The cohomology of the bit in parentheses is concentrated in degrees zero and two. 
In degree zero, there is a dense embedding
\[
\C[w_1,w_2] \hookrightarrow H^0 \bigg( \Omega^\bullet\left(\C^2_w \times \R \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg)
\]
In degree two, there is a dense embedding
\[
w_{1}^{-1} w_2^{-1} \C[w_1,w_2] \hookrightarrow H^2 \bigg( \Omega^\bullet\left(\C^2_w \times \R \setminus 0 \right) \, / \, (\d w_1, \d w_2) \bigg).
\]

It will be useful to explain this last embedding in more detail. 
Consider the homogenous element $w_1^{-1} w_2^{-1}$. 
This represents the class of the Dolbeault-de Rham two-form
\[
\frac{\bar{w}_1 \d \bar{w}_2 \wedge \d t - \bar{w}_2 \d \bar{w}_1 \wedge \d t + t \d \bar{w}_1 \wedge \d \bar{w}_2}{(\|w\|^2 + t^2)^{5/2}} .
\]
Notice that, if we wedge with the volume form $\d w_1 \d w_2$, this is the unit  flux ($N=1$) introduced in Lemma \ref{lem:ads7flux}. 
The homogenous element $w_1^{-n-1} w_2^{-m-1}$ represents the class of the holomorphic derivatives $\partial_{w_1}^n \partial_{w_2}^{m}$ applied to this two-form.

Observe that, when restricted to $\C^5 \times \R \setminus \C^3$, the holomorphic tangent bundle along $\C^5$ is still trivializable.

\parsec[]

Let's turn to the proof of Proposition~\ref{prop:brads7}.
We proceed completely analogously to the case of backreacted M2 branes as in the proof of Proposition \ref{prop:brads4}. 
\fi

\begin{proof}
We proceed exactly analogously to the proof of proposition \ref{prop:brads4}. For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $\C^3\times (\R\times \C^2)\setminus 0$ given by $\Pi\mc E^N_{AdS_7\times S^4}$ and set $F = F_{M5}$. We will show that the image of the map $\mr{res}\circ i_{M5}$ survives to the last page of a spectral sequence that abuts to the target of the above map. The spectral sequence is the one associated to the bicomplex whose differentials are the linearized BRST differential $\delta^{(1)}$ and the operator $[F,- ]$ given by bracketing with the flux.

The first page of this spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0 _{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$. It will be useful to compute this page explicitly.

We once again do so by way of an auxiliary spectral sequence which simply filters by the holomorphic form and polyvector field type. 
This first page of this auxiliary spectral sequence is simply given by the cohomology with respect to $\d_\R+\dbar$.

It follows that up to completions, the cohomology $H^\bullet \left ( \mc L\left ( \right ) ; \d_\R +\dbar\right )$  is the direct sum of the cohomology on flat space $H^\bullet(\Pi \mc E(\C^5 \times \R), \d_\R+\dbar)$ with
\begin{equation}
  \label{eqn:ads7ss2} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\ 
w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\partial_{w_i}\}  \ar[r, dotted, "\div^W"] & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \\
w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \{\del_{z_i}\} \ar[ur, dotted, "\div^Z"'] \\
w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}] [z_1,z_2,z_3] \ar[r, dotted, "\del_W"] \ar[dr, dotted, "\del_Z"'] & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d z_i\} \\ & w_1^{-1} w_2^{-1} \C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\d w_i\} .
\end{tikzcd}
\end{equation}

The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\C^5 \times \R$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to the dotted-line operators in~\eqref{eqn:ads7ss2}. This is indeed the cohomology of global sections $H^\bullet \left ( \Pi \mc E^0 _{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.

Recall that the flux $F$ was defined as the image under $\del$ of some $\gamma$-type field. Therefore, the class $[F]$ does not live inside this page of the spectral sequence, but the operator $[[F], -]$ does act on this page nevertheless. For instance, if $f^i(z,w) \d z_i$ is a one-form living in $H^0(\C^5, \Omega^1) \otimes H^0(\R)$, then
\[
[ [F] , f^i (z,w) \d z_i ] = \epsilon_{ijk} w_1^{-1} w_2^{-1} \partial_{z_j} f^i(z,w) \del_{z_k} 
\]
which is an element in 
\[
\C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\del_{z_i}\} \subset H^0(\C^3, \T) \otimes H^2 \big(\Omega^\bullet(\C^2 \times \R \setminus 0) / (\d w_1 , \d w_2) \big) .
\]

The next page of the spectral sequence is given by computing the cohomology with respect to the operator $[N F,-]$. This operator maps Dolbeault-de Rham degree zero elements to Dolbeault-de Rham degree two elements. For degree reasons, there are no further differentials and the spectral sequence collapses after the second page.

We now wish to argue that the image of the map $\mr{res}\circ i_{M5}$ is annihilated by $\big[ N [F] , - \big]$. This is a direct calculation. For instance, recall that an element in the image of the odd summand $\wedge^2 L \otimes R = \wedge^2 \C^3 \otimes \C^2$ (which corresponds to a superconformal transformation) is of the form $w_a (z_i \d z_j - z_j \d z_i)$, $a=1,2, i,j=1,2,3$. 
We have
\[
\big[[F] , w_a (z_i \d z_j - z_j \d z_i)\big] = 2 \epsilon_{ijk} (w_1^{-1} w_2^{-1}) \cdot w_a \del_{z_k} = 0
\]
since the class $w_1^{-1} w_2^{-1}$ is in the kernel of the operator given by multiplication by $w_a$ for $a=1,2$.
Verifying that the remaining elements in the image of $i_{M5}$ are in the kernel of $\big[ [F], -\big]$ is similar.
This completes the proof.
\end{proof}

\begin{rmk}
As in remark \ref{rmk:altss} comment on an alternate method to compute the first page of the auxiliary spectral sequence we used to compute the first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [NF, - ]$. We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_7\times S^4}$ from section \ref{prop:ads7push}. In this case, this Serre-type spectral sequence degenerates at the $E_2$-page. We will return to similarly flavored constructions in later work.
\end{rmk}

### 2023-05-11 graviton spectra/main.tex
graviton spectra

\documentclass{amsart}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\let\ref\hyperref
\let\hat\widehat
\usepackage{amsfonts} %necessary for Blackboard Bold
\usepackage{amsmath} %does A LOT
\usepackage{amssymb} %necessary for things like \partial
\usepackage{amsthm} %for thms and such
\usepackage{macros}
\usepackage{tikz-cd}
\usepackage{tikz-feynman}
\usepackage{xparse}
\usepackage[centerboxes,boxsize=1ex,nobaseline,aligntableaux=center]{ytableau}
\setcounter{secnumdepth}{4}

\title{Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$} 
\author{Surya Raghavendran and Brian R. Williams}
\begin{document}

\maketitle

\begin{abstract} %required
\end{abstract}

\tableofcontents

Having described our eleven-dimensional model on flat spacetimes, we now pursue descriptions on maximally symmetric spacetimes. We begin by describing twisted versions of the $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds. In eleven-dimensional supergravity, these backgrounds arise as near-horizon limits of the backgrounds sourced by some number of M2 and M5 branes in flat space respectively. In the first section of this chapter \ref{sec:ads}, we describe an analogous procedure natively in our twisted context.

To do so, we motivate ansatzae for the leading order couplings of our eleven-dimensional model to M2 and M5 branes. These couplings determine certain curved deformations of the $L_\infty$-algebra underlying our model - we conjecture that deforming the theory in the complement of the brane by a solution to the resulting curved Maurer-Cartan equation is perturbatively equivalent to the twist of the theory on $AdS_4\times S^7$ and $AdS_7\times S^4$.

The next two sections provide evidence for this conjecture. We begin in section \ref{sec:states} with numerical checks. We give definitions of supergravity states in our twisted $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds, which can be thought of as particular field configurations that are localized at points on the conformal boundary of $AdS$. We compute characters of the proposed state spaces and find exact matches with counts of gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively.

The next strand of evidence we pursue is by matching symmetries. In the physical theory, the $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds carry actions of the 3d $\mc N=8$ and 6d $\mc N=(2,0)$ superconformal algebras. We show that our conjectural descriptions of twists of these backgrounds carry actions of the minimal twists of the corresponding superconformal algebras.

With these pieces of evidence in hand, in sections \ref{sec:e16}, \ref{sec:e36},  we then turn to study some representation theoretic aspects of the state spaces constructed in section \ref{sec:states}. We identify certain $\C^\times$ actions on our eleven-dimensional model that combine rescalings in directions normal to branes with a certain rescaling of the space of fields - this induces a decomposition of the space of fields that we dub the \textit{graviton decomposition}. The weight $0$ parts of these decompositions are certain local $L_\infty$-algebras whose costalks recover the linearly compact super-Lie algebras $E(1|6)$ and $E(3|6)$. We thus see that these linearly compact super-Lie algebras act on the spaces of supergravity states constructed in section \ref{sec:states}. We explicate their action on nonzero weight spaces of the graviton decomposition.

In the final section of the chapter, we motivate some current work in progress that leverages the uncovered appearance of exceptional linearly compact super-Lie algebras for holographic means. Eleven-dimensional supergravity on $AdS_4\times S^7$ and $AdS_7\times S^4$ is expected to be equivalent to the large $N$ limit of the worldvolume theories of $N$ M2 branes and $N$ M5 branes respectively. 
%Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

\input{content/br}

\input{content/index}

\input{content/suco}

\input{content/e16}

\input{content/e36}

%\input{chapters/4-ads/ops}

%\input{chapters/4-ads/finite}

\input{content/holography}

\bibliographystyle{amsalpha}
\bibliography{bibliography.bib}

\end{document}

### 2023-05-18 graviton spectra/content/br.tex
merge

@@
-\section{Twisted Backreactions}
+\documentclass[../main.tex]{subfiles}
+
+\begin{document} 
+\section{Twisted AdS space}
 \label{sec:ads}
@@
 
+\subsection{Twisted supergravity}
+
+In \cite{CLsugra}, Costello and Li gave a rigorous definition of what it means to {\em twist} supergravity, which is nicely compatible with the mathematically more familiar notion of twisting supersymmetric gauge theories \cite{WittenTwist}.
+In physical terms, twisted supergravity is supergravity in a background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge.
+In principle, one can take the supercharge to be any square-zero covariantly constant spinor (so it satisfies the equations of motion of supergravity).
+A class of such supercharges lie in the supersymmetry algebra.
+
+The eleven-dimensional supersymmetry algebra admits two types of twists characterized by the number of invariant directions that the supercharge determines:
+\begin{itemize}
+\item 
+The $SU(5)$ twist. 
+This twist leaves six real directions invariant and is stabilized by the subgroup $SU(5)$ of the eleven-dimensional Lorentz group.\footnote{We always work in Euclidean signature.}
+\item 
+The $G_2$ twist.
+This twist leaves nine real directions invariant and is preserved by the subgroup $SU(2) \times G_2$ of the Lorentz group. 
+\end{itemize}
+
+In \cite{RSW} we have proposed a mathematical model for the $SU(5)$-twist of eleven-dimensional supergravity.
+Many tests of this proposal were performed, including a consistency check that the dimensional reduction of the model agrees with proposals for twists of type IIA supergravity given in terms of topological strings~\cite{CLsugra}.
+
+The eleven-dimensional theory exists on any manifold which is locally of the form 
+\[
+\R \times Z
+\] 
+where $Z$ is a Calabi--Yau fivefold.
+The model is topological along $\R$ in the sense that translations in this direction act in a homotopically trivial way on the theory.
+Likewise, locally on the Calabi--Yau fivefold, all anti-holomorphic translations act in a homotopically trivial way---in this sense, the theory is {\em holomorphic} along $Z$ \cite{BWhol}.
+More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
+
+In \cite{RSW,RWindex} we describe how physical fields in supergravity are manifest in the twisted model.
+\brian{expand this}
+Here, we will jump straight to describing the twisted model.
+Fields generally live in spaces of the form
+\beqn
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}(Z, V)
+\eeqn
+where $V$ is some holomorphic vector bundle on $Z$.\footnote{The tensor product $\otimes$ is the completed tensor product with respect to natural topologies present in the space of sections of a smooth vector bundle.}
+Since the theory is of topological/holomorphic nature, there is a linear part of the BRST differential of the form $\d + \dbar$ where $\d$ is the de Rham differential on $\R$ and $\dbar$ corresponds to the holomorphic structure on the bundle $V$.
+
+Deformations of the background metric which survive the twist can be identified with Beltrami differentials, that is, sections of 
+\[
+\Bar{\T}_Z^* \otimes \T_Z \cong \Bar{\T}^*_Z \otimes \Bar{\T}_Z^* . 
+\]
+More generally, the fields of this model include sections of the holomorphic tangent bundle with coefficients in Dolbeault forms on $Z$ of arbitrary Dolbeault type and de Rham forms on $\R$, which we can write in superfield notation as
+\[
+\mu = \mu^{\Bar{I}}_j (t;z,\zbar) \d \zbar_{\Bar{I}} \otimes \del_{z_j} + \mu^{\Bar{I}}_{t,j} (t;z,\zbar) \d t \d \zbar_{\Bar{I}} \otimes \del_{z_j}
+\]
+where the sum over the multi-index $\Bar{I}$ ranges over subsets of $\{1,\ldots,5\}$.
+We view this as a section
+\beqn
+\mu \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(Z, \Pi \T_Z) .
+\eeqn
+In this notation, the component $\mu^{\Bar{I}}_j$ is {\em odd} if $|\Bar{I}|=0,2,4$ is even and {\em even} if $|I| = 1,3,5$ is odd.
+The parity shift of the holomorphic tangent bundle is to ensure that deformations of the background metric which survive the twist are viewed as even fields.
+In particular we have odd fields $\mu_j(t;z,\zbar) \del_{z_j}$ which play the role of ghosts for infinitesimal changes of coordinates.
+
+Part of the linear equations of motion in our model imply that the field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$Z$.
+This condition is imposed, cohomologically, by adding another field which is simply a differential form
+\beqn
+\nu \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(Z) 
+\eeqn
+and a linear part of the differential $\delta \nu = \div \mu$ encoding the divergence-free condition.
+Another piece of the linear equations of motion imply that it $\mu$ be constant along~$\R$.
+
+Ordinarily, for $\mu$ to describe a deformation of complex structure in the $Z$ direction we would require that it satisfy the Maurer--Cartan equation.
+For twisted supergravity, however, we find a modification of this equation which involves the twisted analog of another familiar field---the higher form gauge field in supergravity.
+
+In the BV formalism one will see all types of differential forms corresponding to a tower of ghosts for this higher gauge field together with antifields and antighosts.
+In local coordinates, the only components of this tower of differential forms which survives the twist are
+\begin{align*}
+\beta & = \beta^{\Bar{I}} \d \zbar_{\Bar{I}} + \beta_t^{\Bar{J}} \d t \d \zbar_{\Bar{J}} \in \Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(Z) \\
+\gamma & = \gamma^{i \Bar{I}} \d z_i \d \zbar_{\Bar{I}} + \gamma_t^{j \Bar{J}} \d t \d z_j \d \zbar_{\Bar{J}} \in \Omega^{\bu} (\R) \otimes \Omega^{1,\bu}(Z).
+\end{align*}
+%When we want to be specific by the form type we use the notation $\beta^{k;q}(t;z,\zbar)$ for the $(k;0,q)$ component of the three-form and $\gamma^{k;q}(t;z,\zbar)$ for the $(k;1,q)$ component of the three-form.
+Fields $\beta^{\Bar{I}}, \gamma_t^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp.
+even) are {\em even} (resp.
+{\em odd}) and fields $\beta_t^{\Bar{I}}, \gamma^{i \Bar{I}}$ with $|\Bar{I}| = $odd (resp.
+even) are {\em odd} (resp.
+{\em even}).
+
+The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
+When $\div \mu = 0$ it takes the form
+\beqn\label{eqn:eom2}
+\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
+\eeqn
+Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.
+On the left hand side we are implicitly using an identification between the holomorphic tangent bundle $\T_Z$ and the bundle $\wedge^4 \T^*_Z$ granted by the holomorphic volume form on $Z$.
+
+In \cite{RSW} we find the above equation of motion together with its gauge symmetries by formulating the theory within the BV formalism.
+We briefly recount what this entails.
+In the BV formalism, the space of BV fields $\cE$ is given as the sections of some graded vector bundle on spacetime. 
+The grading is typically by the abelian group $\Z$, which is usually referred to as the cohomological grading.
+In cohomological degree zero of $\cE$ sit the usual (sometimes called {\em physical}) fields.
+The ghosts comprise the cohomological degree $-1$ part of $\cE$. 
+In cohomological degree one sit the antifields, etc..
+Another key piece of structure is a skew symmetric pairing $\omega_{BV}$ of cohomological degree $-1$ on $\cE$ which is concretely a pairing between the fields and antifields (and ghosts and antighosts).
+The full BV action functional $S_{BV}$ is a functional on the space of fields which encodes not only the original action functional on fields, but through its dependence on ghosts and antifields it also encodes the gauge symmetries (and gauge symmetries for gauge symmetries, etc.) of the theory.
+
+For our eleven-dimensional model the BV action functional takes the following form
+\begin{multline}
+S_{BV} = \int_{\R \times Z} \bigg[\beta \wedge (\dbar + \d) \nu + \gamma \wedge (\dbar + \d) \mu +  \beta \wedge \div \mu  \bigg] \\
++ \frac{1}{2} \int_{\R \times Z}  \mu^2 \vee \del \gamma + \int_{\R \times Z} \gamma \del \gamma \del \gamma + \cdots .
+\end{multline}
+Here:
+\begin{itemize}
+\item the first line is the free part of the action.
+The operator $\dbar$ is the $\dbar$-operator on $Z$, the operator $\d$ is the de Rham operator on $\R$, and the operator $\div$ is the holomorphic divergence operator on $Z$ corresponding to the holomorphic volume form.
+\item We implicitly use the holomorphic volume form in the above integrals.
+\item The term 
+\beqn\label{eqn:J}
+J(\gamma) \define \int_{\R \times Z} \gamma \del \gamma \del \gamma .
+\eeqn
+is the holomorphic avatar of the famous Chern--Simons term of the higher form gauge field present in supergravity.
+\item The $\cdots$ indicate additional terms needed so that this functional satisfies the classical master equation (in this presentation there are, in fact, infinitely many terms).
+They take a form which is reminiscent of the genus zero BCOV action for the fivefold $Z$ (we make a further comment on this below).
+\end{itemize}
+
+In what follows we will define $S_{BF}$ as
+\beqn
+S_{BV} = S_{BF} + J ,
+\eeqn
+with $J$ the Chern-Simons term \eqref{eqn:J}.
+We will not need an explicit formula for $S_{BF}$ but we remark that reason for the terminology $S_{BF}$ is that this term in the action is homotopy equivalent to a standard BF type action, see \cite{RSW}.
+
+In \cite{RSW} we have performed a number of consistency checks that this model indeed describes the $SU(5)$ twist of supergravity.
+Famously, $M$-theory on a circle is expected to be equivalent to type IIA string theory where the length of the circle is proportional to the string coupling constant.
+At the level of supergravity, the $S^1$-reduction of eleven-dimensional supergravity is ten-dimensional supergravity of type IIA.
+Here we utilize a description of the twist of type IIA strings using a version of Kodaira--Spencer theory developed in \cite{CLbcov1,CLsugra}.
+
+From the point of view of the $SU(5)$ twist there are essentially two types of circles one can consider.
+The first is a `holomorphic circle'.
+This is present when we assume our Calabi--Yau fivefold is of the form $Z = \C^\times \times Y$ with $Y$ a Calabi--Yau fourfold.
+We assume that $\C^\times$ is equipped with the standard volume form $\d z$.
+The $S^1$ reduction along a circle in $\C^\times$ results in a twist of type IIA supergravity with global symmetry $SU(4)$ on the manifold
+\beqn
+\R \times \R \times Y .
+\eeqn
+More generally, this twist can be defined when $\R^2$ is replaced by a smooth oriented two-dimensional manifold $M^2$.
+In \cite{CLsugra}, Costello and Li have given a conjectural description of this particular twist of type IIA (and many other twists) using methods of topological string theory.
+In this case, the conjecture of Costello and Li is that the twist is equivalent to a mixed topological string theory which is given by the A-model along $M^2$ and the B-model along $Y$.
+In perturbation theory, this admits a description in terms of Kodaira--Spencer theory along the fourfold $Y$.
+Via an explicit dimensional reduction of our model we find an exact match with this expectation \cite{RSW}.
+The dimensional reduction of our eleven-dimensional model on
+\beqn
+\R \times \C \times Y
+\eeqn
+along $S^1 \subset \C$ is equivalent to the mixed topological A-model along $\R^2$ and B-model along $Y$ as considered in \cite{CLsugra}.
+
+The other type of reduction one can consider is that along a `topological' circle.
+This corresponds to placing our eleven-dimensional model on
+\beqn
+S^1 \times Z
+\eeqn
+and performing reduction along $S^1 \times Z \to Z$.
+What results is a theory with $SU(5)$ global symmetry.
+We conjecture that this is the $SU(5)$ twist of type IIA supergravity.
+There is no expected description of the $SU(5)$ twist in terms of topological strings like in the $SU(4)$ or $SU(2)$ cases.
+
+%
+%There are two bosonic fields of particular importance.
+%First is a section
+%\beqn
+%\mu^{0;0,1} \in \Omega^0(\R) \otimes \Omega^{0,1}(X, \T_X) .
+%\eeqn
+%Here $\T_X$ is the holomorphic tangent bundle on $X$.
+%The linear part of the BRST differential requires this field be constant in the real direction.
+%Thus, this field has the same form as a Beltrami differential on $X$.
+%There are particular field configurations where the non-linear equations of motion for $\mu$ imply that it is a complex structure deformation of $X$, but the full equations of motion are more complicated.
+%Another bosonic field of importance is a section
+%\beqn
+%\gamma^{0;0,1} \in \Omega^0(\R) \otimes \Omega^{1,1}(X) .
+%\eeqn
+%
+%The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$.
+%This means that it is required to satisfy the equation
+%\beqn
+%\div \mu = 0
+%\eeqn
+%where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
+
+%\subsection{The $G_2$ twist}
+%
+%We will give a description to of the $G_2$ twist of eleven-dimensional supergravity.
+%Independent derivations of this twist have appeared in \cite{CostelloM5, EagerHahner}.
+%The theory is defined on any manifold of the form
+%\beqn
+%M \times Y
+%\eeqn
+%where $M$ is a manifold with $G_2$ holonomy and $Y$ is a manifold with $SU(2)$ holonomy.
+%Unfortunately, the perturbative description we are about to give depends in no way on the $G_2$ structure and can be defined when $M$ is any smooth seven-dimensional manifold.
+%To see the full $G_2$ structure appearing one must take into account non-perturbative effects (much like in the target space description of the topological A-model).
+%
+%The fundamental field is simply a differential form
+%\beqn
+%\alpha \in \Omega^\bu(M) \otimes \Omega^{0,\bu}(Y) [1] .
+%\eeqn
+%The linear BRST differential is simply $\d + \dbar$ where $\d$ is the de Rham differential on $M$ and $\dbar$ is the Dolbeault operator for $Y$.
+%
+%Being a manifold with $SU(2)$ holonomy, the algebra of holomorphic fnuctions on $Z$ is equipped with a holomorphic Poisson bracket $\{-,-\}$.
+%Since this bracket involves only holomorphic differntial operators, it can be extended to a Poisson bracket on the dg algebra $\Omega^{0,\bu}(Y)$.
+%The theory utilizes this bracket in an essential way.
+%Indeed, the full BV action is
+%\beqn
+%\frac12 \int_{M \times Y} \Omega \, \alpha \d \alpha + \frac16 \int_{M \times Y} \Omega \, \alpha \{\alpha, \alpha\} .
+%\eeqn
+%where $\Omega \in \Omega^{2,0}(Y)$ is the holomorphic volume form.
+%This description appeared in \cite{RYsduality} and was independently derived from a further twist of the $SU(5)$ twist in \cite{RSW}. 
+%
+%Like the $SU(5)$ twist, this theory is only $\Z/2$ graded.
+%Nevertheless, one convenient way to think about this theory is as a higher dimensional Chern--Simons theory for a particular (dg) Lie algebra.
+%Given any odd-dimensional smooth manifold $M$ and a Lie algebra $\lie{g}$ equipped with an invariant non-degenerate symmetric inner product one can consider a $\Z/2$ graded version of Chern--Simons theory whose BV action is given by the usual formula $\int_M CS(A)$.
+%It is only in the case that $\dim M = 3$ that this theory admits a $\Z$-grading.
+%The theory we are considering here can be interpreted as $\Z/2$ graded Chern--Simons theory on the seven-manifold $M$ for the Lie algebra of holomorphic functions on $Y$ equipped with the holomorphic Poisson bracket.
+%Here, the invariant pairing is given by integrating against the holomorphic volume form $\Omega$.
+
 \subsection{The ${\mr AdS}_4 \times S^7$ background}
@@
 
-We carry out the above procedure. Consider a stack of $N$ M2 branes wrapping the zero section $\R\times \C_z$. A natural interaction to consider is 
+We carry out the above procedure. 
+Consider a stack of $N$ twisted M2 branes wrapping the zero section $\R\times \C_z$.
+Our ansatz for this coupling is heuristically of the form
 \[
@@
 \begin{defn}\label{defn:ads4}
-Let $\mc E^N_{AdS_4\times S^7}$ denote the classical BV theory on $\operatorname{Tot} (K_\C^{1/4}\otimes \C^4 \to \R\times \C_z)\setminus 0(\R\times \C)$ given by the sheaf of cochain complexes $\mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} )}$, with BV pairing induced from $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu + NF_{M2}, \nu, \beta, \gamma) + J(\gamma).\]
+Let $\mc E^N_{AdS_4}$ denote the classical BV theory on 
+\beqn\label{eqn:totalm2}
+\operatorname{Tot} (K_\C^{1/4}\otimes \C^4 \to \R\times \C_z)\setminus 0(\R\times \C)
+\eeqn
+given by the sheaf of cochain complexes $\mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} )}$, with BV pairing induced from $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu + NF_{M2}, \nu, \beta, \gamma) + J(\gamma).\]
 \end{defn}
@@
 \begin{rmk}
-Note that upon expanding the interaction around $NF_{M2}$, the cubic term in $S_{BF,\infty}$ will contribute a differential which acts on $\gamma$ and $\mu$ by bracketing with $NF_{M2}$.
-We accordingly denote this differential $[NF_{M2}, - ] $, and we see that the sheaf of cochain complexes underlying $\mc E_{AdS_4\times S^7}$ is in fact \[\left ( \mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} ) }, \delta^{(1)} + [NF_{M2},-] \right )\] where $\delta^{(1)}$ denotes the original linearized BRST differential.
+By definition, the theory $\cE_{AdS_4}^N$ is a deformation of our eleven-dimensional model on \eqref{eqn:totalm2} by the $N$-dependent action functional $S_{BF, \infty}(\mu = N F_{M2})$.
+Upon expanding this action around $NF_{M2}$, the cubic term in $S_{BF,\infty}$ will contribute a differential which acts on $\gamma$ and $\mu$ by bracketing with $NF_{M2}$.
+We accordingly denote this differential $[NF_{M2}, - ] $, and we see that that linearized BRST complex underlying $\mc E_{AdS_4}$ is \[\left ( \mc E |_{(\R\times \C)\times (\C^4\setminus \{0\} ) }, \delta^{(1)} + [NF_{M2},-] \right )\] where $\delta^{(1)}$ denotes the original linearized BRST differential of the eleven-dimensional theory defined on flat space.
 \end{rmk}
@@
 \begin{conj}\label{conj:ads4}
-The minimal twist of eleven-dimensional supergravity on the $AdS_4\times S^7$ background with $N$ units of M2 brane flux supported on $S^7$ is perturbatively equivalent to $\mc E^N_{AdS_4\times S^7}$.
+The minimal twist of eleven-dimensional supergravity on the $AdS_4\times S^7$ background with $N$ units of M2 brane flux supported on $S^7$ is perturbatively equivalent to $\mc E^N_{AdS_4}$.
 \end{conj}
@@
 
-To repeat the procedure in the previous subsection, we begin by discussing how the eleven-dimensional theory couples to M5 branes. 
+To repeat the procedure in the previous subsection, we begin by defining our eleven-dimensional theory couples to M5 branes (to first order).
 Consider a stack of $N$ M5 branes wrapping the zero section $\C^3_z$. 
-
-It is natural to consider the nonlocal interaction 
+We consider the heuristic nonlocal coupling 
 \[
@@
 
-Once again, we summarize our findings in a definition. 
+Once again, we summarize the lemma above with a definition.
+
 \begin{defn}\label{defn:ads7}
-Let $\mc E^N_{AdS_7\times S^4}$ denote the classical BV theory on $\operatorname{Tot}(\R \oplus K_{\C^3}^{1/2}\otimes \C^2 \to \C^3_z)\setminus 0(\C^3_z)$ given by the sheaf of cochain complexes $\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}$, with BV pairing induced from that on $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu, \nu, \beta, \gamma +N\del^{-1} F_{M5}) + J(\gamma + N \del^{-1} F_{M5}).\]
+Let $\mc E^N_{AdS_7}$ denote the classical BV theory on 
+\beqn
+\operatorname{Tot}(\R \oplus K_{\C^3}^{1/2}\otimes \C^2 \to \C^3_z)\setminus 0(\C^3_z)
+\eeqn
+given by the sheaf of cochain complexes $\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}$, with BV pairing induced from that on $\mc E$, deformed by the interaction \[S_{BF,\infty}(\mu, \nu, \beta, \gamma +N\del^{-1} F_{M5}) + J(\gamma + N \del^{-1} F_{M5}).\]
 \end{defn}
@@
 From $S_{BF,\infty}$, we get a differential which takes a $\mu$ type field to the Schouten bracket $N[F_{M5}, \mu]$ and from $J$, we get a differential which acts as $\gamma\mapsto N F_{M5} \wedge \del \gamma$.
-We accordingly denote this differential $[NF_{M5}, - ] $, and the sheaf of cochain complexes underlying $\mc E_{AdS_7\times S^4}$ is in fact \[\left (\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}, \delta^{(1)} + [NF_{M5},-] \right )\] where $\delta^{(1)}$ denotes the original linearized BRST differential.
+We accordingly denote this differential $[NF_{M5}, - ] $, and linear BRST complex is
+\[
+\left (\mc E |_{\C^3\times (\R\times \C^2\setminus \{0\} )}, \delta^{(1)} + [NF_{M5},-] \right )
+\] where $\delta^{(1)}$ denotes the original linearized BRST differential.
 \end{rmk}
@@
 \begin{conj}\label{conj:ads7}
-The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E_{AdS_7\times S^4}$. 
+The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E_{AdS_7}$. 
 \end{conj}
+
+Part of our goal in the remainder of the paper is to justify conjectures \ref{conj:ads4} and \ref{conj:ads7}.
+\end{document}

### 2023-05-18 graviton spectra/content/e36.tex
merge

@@
-%\documentclass[11pt]{amsart}
-%
-%%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
-%
-%\begin{document}
+\documentclass[../main.tex]{subfiles}
 
-%\parsec[s:membraneobs]
-%
-%
-%\parsec[s:fivebraneobs]
-%
-%Let $Z$ be a complex threefold. 
-%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\mc{L}_{single}$ on $Z$.
-%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
-%the cochain complex
-%\[
-%\clie^\bullet\left(\mc{L}_{single}(U)\right) .
-%\]
-%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bullet(\mc{L}_{single})$.
+\begin{document}
+
 \section{$E(3|6)$-modules from gravitons on $AdS_7\times S^4$}\label{sec:e36}
+
 We now repeat the analysis of the previous subsection for gravitons on $AdS_7\times S^4$ respectively, making use of the description of supergravity states on $AdS_7\times S^4$ as the costalk of the factorization envelopes of the boundary condition and $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4})$
@@
 \end{rmk}
+
+\end{document}
+
 %The subalgebra $\mc{G}^{(\geq k)} = \oplus_{j \geq k} \mc{G}^{(j)}$ is an ideal for every $k$. 

### 2023-05-18 graviton spectra/main.tex
merge

@@
 \documentclass{amsart}
-\usepackage[utf8]{inputenc}
-\usepackage{hyperref}
-\let\ref\hyperref
-\let\hat\widehat
-\usepackage{amsfonts} %necessary for Blackboard Bold
-\usepackage{amsmath} %does A LOT
-\usepackage{amssymb} %necessary for things like \partial
-\usepackage{amsthm} %for thms and such
+\usepackage[dvipsnames]{xcolor}
+
 \usepackage{macros}
-\usepackage{tikz-cd}
-\usepackage{tikz-feynman}
-\usepackage{xparse}
-\usepackage[centerboxes,boxsize=1ex,nobaseline,aligntableaux=center]{ytableau}
 \setcounter{secnumdepth}{4}
+
+\usepackage{subfiles}
+
+\newcommand\brian[1]{\colorbox{BurntOrange}{#1}}
+\newcommand\surya{\todo[color={blue!100!green!33},author=Surya]}
 
@@
 
-To do so, we motivate ansatzae for the leading order couplings of our eleven-dimensional model to M2 and M5 branes.
+To do so, we motivate ansatz for the leading order couplings of our eleven-dimensional model to M2 and M5 branes.
 These couplings determine certain curved deformations of the $L_\infty$-algebra underlying our model - we conjecture that deforming the theory in the complement of the brane by a solution to the resulting curved Maurer-Cartan equation is perturbatively equivalent to the twist of the theory on $AdS_4\times S^7$ and $AdS_7\times S^4$.
@@
 
-\input{content/br}
+\subfile{content/br}
 
-\input{content/index}
+\subfile{content/index}
 
-\input{content/suco}
+\subfile{content/suco}
 
-\input{content/e16}
+\subfile{content/e16}
 
-\input{content/e36}
+\subfile{content/e36}
 

### 2023-05-22 graviton spectra/content/br.tex
almost done with index

@@
 Let
-\[
+\beqn\label{eqn:FM2}
  F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \partial_z .
-\]
+\eeqn
 Then the background where $\mu = N F_{M2}$ and $\gamma = 0$
@@
 Let
-\[
+\beqn\label{eqn:FM2}
 F_{M5} = \frac{1}{(2\pi i)^3} \frac{\bar{w}_1 \d \bar{w}_2 \wedge \d t - \bar{w}_2 \d \bar{w}_1 \wedge \d t + t \d \bar{w}_1 \wedge \d \bar{w}_2}{(\|w\|^2 + t^2)^{5/2}} \wedge \d w_1 \wedge \d w_2
-\]
+\eeqn
 Then, $\del\gamma = N F_{M5}$, $\mu = 0$, and $\nu = 0$ satisfies the equations of motion in the presence of a stack of $N$ M5 branes sourced by the term $N \delta_{w_1=w_2=t=0}$:
@@
 
-Part of our goal in the remainder of the paper is to justify conjectures \ref{conj:ads4} and \ref{conj:ads7}.
+%Part of our goal in the remainder of the paper is to justify conjectures \ref{conj:ads4} and \ref{conj:ads7}.
 \end{document}

### 2023-05-22 graviton spectra/content/index.tex
merge
almost done with index

@@
-%\documentclass[11pt]{amsart}
-%
-%%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
-%
-%\begin{document}
+\documentclass[../main.tex]{subfiles}
+
+\begin{document}
 
@@
 The definition is meant to codify the following situation. 
-Suppose we have a theory of gravity defined on a background of the form $AdS_{d+1} \times S^{d^\prime}$ where the conformal boundary of $AdS_{d+1}$ is a $d$ manifold $M$.
+Suppose we have a bulk gravitational theory defined on a background of the form $AdS_{d+1} \times S^{d^\prime}$ where the conformal boundary of $AdS_{d+1}$ is a $d$-dimensional manifold $M$. 
 We can compactify the theory, retaining all the Kaluza-Klein harmonics, to get a theory on $AdS_{d+1}$. 
-A supergravity state is traditionally defined to be a solution to linearized equations of motion in this compactified theory with a given boundary value on $M^{d}$ \cite{WittenAdS}.
+A gravitational state is traditionally defined to be a solution to linearized equations of motion in this compactified theory with a given boundary value on $M^{d}$ \cite{WittenAdS}.
 Often, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values.
@@
 
-\parsec[]
+For twists of supergravity, we procedurally implement this as follows. First, we wish to describe a model for sphere compactification on twisted $AdS$ backgrounds. 
+As we saw in the last section, our proposal for describing twists backgrounds of the form $AdS_{d+1}\times S^{d^\prime}$ involve elliptic complexes defined on certain manifolds of the form 
+\beqn
+X = \operatorname{Tot }(V\to Z)\setminus 0(Z)
+\eeqn
+Note that $Z$ can be written as a sphere bundle over $\R_{>0}\times Z$ - the sphere compactification of our theory on $X$ is given by the pushforward to $\R_{>0}\times Z$. 
+Such sphere compactifications can be described using a method for computing pushforwards of modules for Lie algebroids associated to foliations \cite[section 4.2]{KormanThesis}, \cite{KamberTondeur}.
 
-For twists of supergravity, we procedurally implement this as follows.
-First, we wish to describe a model for sphere compactification on twisted $AdS$ backgrounds.
-As we saw in the last section, our proposal for twists of backgrounds of the form $AdS_{d+1}\times S^{d^\prime}$ involve placing certain local $L_\infty$-algebras on certain manifolds of the form $X = \operatorname{Tot }(V\to Z)\setminus 0(Z)$.
-Note that $Z$ can be written as a sphere bundle over $\R_{>0}\times Z$ - the sphere compactification of our theory on $X$ is given by the pushforward to $\R_{>0}\times Z$.
-Such sphere compactifications can be described using a method for computing pushforwards of modules for Lie algebroids associated to foliations \cite[Sec.
-4.2]{KormanThesis}, \cite{KamberTondeur}.
-
-The compactified theory will admit a natural boundary condition at $\{\infty\}\times Z\subset \R_{>0}\times Z$, given by certain local $L_\infty$-algebras $\mc L$.
-In fact, the presence of extra differentials involving bracketing with the flux sourced by branes wrapping $Z$ will induce an interesting shifted-Poisosn structure on $\mc L$.
-Given a local $L_\infty$-algebra $\mc L$ underlying a perturbative classical field theory, the Chevalley-Eilenberg cochains $\clie^\bullet (\mc L)$ carry the structure of a $\mb{P}_0$-factorization algebra \cite{CG1}, \cite{CG2}.
+The compactified theory will admit a natural boundary condition at $\{\infty\}\times Z\subset \R_{>0}\times Z$.
+Such a boundary condition also admits a perturbative description in terms of some elliptic complex $\mc L$ on $Z$.
+In fact, the presence of extra differentials involving bracketing with the flux sourced by branes wrapping $Z$ will induce an odd Poisson structure on $\mc L$.
+Given an elliptic complex $\cL$ underlying a perturbative classical field theory, the algebra of observables $\cO(\cL)$ carries the structure of a $\mb{P}_0$-factorization algebra \cite{CG1}, \cite{CG2}.
 Associated to a factorization algebra, we can define a space of local operators, which is the costalk at a point of the underlying cosheaf.
-The sought-after spaces of supergravity states will be a space of local operators associated to $\clie^\bullet (\mc L)$.
+The sought-after spaces of supergravity states will be a space of local operators associated to $\cO(\cL)$.
 
@@
 \subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
+We begin more generally with the input being a three-manifold $M$ equipped with a THF structure of codimension one.
+As in \S \ref{s:??} the elliptic complex $\cA^\bu_M$ computes the THF cohomology of $M$.
+We denote by $K$ the holomorphic canonical bundle of $M$ which has a local frame given by $\d z$.
+The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we will do momentarily.
+
+We will also fix a fourth-root $K^{1/4}$ of this bundle.
 Following the above prescription, we consider the $S^7$ bundle 
@@
 \begin{tikzcd}
-S^7 \ar[r] & \operatorname{Tot} (K^{1/4}_\C\otimes \C^4 \to \R\times \C) \setminus 0(\R\times \C) \ar[d, "p"] \\ & \R_{>0}\times \R\times \C
+S^7 \ar[r] & \operatorname{Tot} (K^{1/4} \otimes \C^4 \to M) \setminus 0(M) \ar[d, "p"] \\ & \R_{>0}\times M
 \end{tikzcd}
 \]
-We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4\times S^7}$ as a sheaf of cochain complexes on $\R_{>0}\times \R\times \C$.
+We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4}$ as a sheaf of cochain complexes on $\R_{>0}\times M$.
 
 \begin{prop}\label{prop:pushads4}
-The pushforward is given by the sheaf of complexes $\Omega^\bullet_{\R_{>0}\times \R} \otimes \Omega^{0,\bullet}_{\C} (\mc V^N_\C)$ on $\R_{>0}\times \R\times \C$, where $\mc V^N_\C$ is the following dg-vector bundle on $\C$:
+The pushforward is given by the sheaf of complexes $\Omega^\bullet_{\R_{>0}} \otimes \cA^{\bullet}_{M} (\mc V^N)$ on $\R_{>0}\times M$, where $\mc V^N$ is the following complex of vector bundles on $M$:
 
@@
 H^\bullet (\C^{4}\setminus 0, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet (\C^{4}\setminus 0) \otimes \mc O \\
-H^\bullet (\C^{4}\setminus 0)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-H^\bullet (\C^{4}\setminus 0)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet (\C^{4}\setminus 0) \otimes \Omega^1 \\ & H^\bullet (\C^{4}\setminus 0, \Omega^1)  \otimes \mc O
+H^\bullet (\C^{4}\setminus 0)  \otimes \T\ar[ur, "\del^M_\Omega" description] \\
+H^\bullet (\C^{4}\setminus 0)\otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & H^\bullet (\C^{4}\setminus 0) \otimes \Omega^1 \\ & H^\bullet (\C^{4}\setminus 0, \Omega^1)  \otimes \mc O
 \end{tikzcd}
 \end{equation}
-
 where the differentials are as follows:
 \begin{itemize}
-\item The differentials $\del_\Omega^Z$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
-\item The differentials $\del_Z$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
-\item  Internal to each summand is a differential given by bracketing with the flux $NF_{M2}$. 
+\item The differentials $\del_\Omega^M$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
+\item The differentials $\del_M$ and $\del_W$ are components of the holomorphic de Rham differentials along the base and fiber respectively.
+\item  Internal to each summand is a differential given by bracketing with the flux $NF_{M2}$, see equation \eqref{eqn:FM2}. 
 \end{itemize}
@@
 
-The flux $NF_{M2}$ of lemma \ref{lem:m2flux} is represented by the section $N (w_1\cdots w_4)^{-1}\del_z \in H^3 (\C^4\setminus 0)\otimes \T$ and acts on each summand by Lie derivative along $z$ and multiplying by $(w_1\cdots w_4)^{-1}$
+The flux $NF_{M2}$ of lemma \ref{lem:m2flux} is represented by the section $N (w_1\cdots w_4)^{-1}\del_z \in H^3 (\C^4\setminus 0)\otimes \T$ and acts on each summand by Lie derivative along $z$ and multiplying by $(w_1\cdots w_4)^{-1}$.
 
 \begin{proof}
-To compute the pushforward of the kind of local $L_\infty$-algebra associated to a holomorphic-topological field theory along a map of THF manifolds, we can use a result of \cite[Sec.
-4.2]{KormanThesis}, \cite{KamberTondeur} for describing direct images of Lie algebroid modules along maps of Lie algebroids.
+To compute the pushforward of this sort of elliptic complex associated to a holomorphic-topological field theory along a map of THF manifolds, we can use a result of \cite[section 4.2]{KormanThesis}, \cite{KamberTondeur} for describing direct images of Lie algebroid modules along maps of Lie algebroids.
 Schematically, if we have a proper submersion $p : X\to Z$ of THF manifolds, and a sheaf of complexes $\mc E$ on $X$ which resolves sections of some bundle flat along the leaves of the foliation on $X$, then the pushforward $p_*\mc E$ has a model as a partially flat bundle on $Z$.
@@
 
-In our case, the pushforward $p_* \mc E_{AdS_4\times S^7}$ is a complex of $\Omega^\bullet_{\R_{>0}} \otimes \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C$- modules given by
+In our case, the pushforward $p_* \mc E_{AdS_4}$ is a complex of $\Omega^\bullet_{\R_{>0}} \otimes \cA^\bu_M$- modules given by
 
@@
 H^\bullet_{\mr{THF}}(S^7, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \mc O \\
-H^\bullet_{\mr{THF}} (S^7)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-H^\bullet_{\mr{THF}} (S^7)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \Omega^1
+H^\bullet_{\mr{THF}} (S^7)  \otimes \T\ar[ur, "\del^X_\Omega" description] \\
+H^\bullet_{\mr{THF}} (S^7)\otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \Omega^1
  \\ & H^\bullet_{\mr{THF}} (S^7, \Omega^1)  \otimes \mc O
@@
 \parsec{}
-Continuing, we wish to understand a natural boundary condition we can place on the fields at $\{\infty\} \times\R\times \C\subset \R_{>0} \times \R\times \C$.
-Such a boundary condition is specified by a Lagrangian in the phase space.
-The restriction $(p_* \mc E^N_{AdS_4\times S^7})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C})$.
-We wish to describe a shifted Lagrangian therein.
+We proceed to define a natural boundary condition of the twisted $AdS_4$-type theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
+Such a boundary condition is specified by a Lagrangian in the phase space whose symplectic structure uses Serre duality on the THF manifold $M$ together with the higher residue pairing along the THF structure of the sphere $S^7$.
+The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\cA_M^\bu (\mc V^N)$. We wish to describe a shifted Lagrangian therein.
 
-We begin by rewriting the phase space in the following form. Note that there is a higher residue pairing 
-\[H^0(\C^4\setminus 0) \otimes H^3(\C^4\setminus 0) \to \C;\]
-together with the natural pairings between $T, \Omega^1$ and the integration pairing along $\R\times \C_z$, this equips $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc V^N_{\C})$ with a local even-shifted symplectic structure.
+We begin by rewriting the phase space in the following form. 
+Using the holomorphic volume form, there is a higher residue pairing 
+\[H^0(\C^4\setminus 0, \cO) \otimes H^3(\C^4\setminus 0, \cO) \to \C;\]
+together with the natural pairings between $T, \Omega^1$ and the integration along $M$, this equips $\cA_M^\bu (\mc V^N)$ with a local even-shifted symplectic structure.
 
-Together with this shifted symplectic structure, we can identify the phase space with a twisted cotangent bundle
+Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
 \[
- \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex]
+\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
  \ul{-} & \ul{+} \\ 
 \C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
-\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^Z_\Omega" description] \\
+\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
 \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right)
 \]
-For now, the subscript of $\Pi$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.
+For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.
 
-Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\Omega^\bullet_\R\otimes\Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7})$ where $\mc L^N_{AdS_4\times S^7}$ is the following dg-vector bundle
+Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of vector bundles on $M$:
 
@@
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
-(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
+(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
@@
 
-\begin{rmk}
-The extra term in the differential in fact equips $\Omega^\bullet_\R\otimes \Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7} )$ with an interesting $N$ dependent odd-shifted Poisson structure.
-This will not play a significant role in the narrative of this thesis, but we flag it for later commentary nonetheless.
-\end{rmk}
+We now specialize to the case $M = \R \times \C$.
 
 \begin{defn}\label{defn:ads4states}
- The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by $\clie^\bullet \left (  \Pi \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4\times S^7}) \right )$
+ The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by 
+ \beqn
+ \cO\left(\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4}) \right ) .
+ \eeqn
 \end{defn}
@@
 \parsec{}
-Let us explicate definition \ref{defn:ads4states} a bit. We wish to first understand the space of supergravity states as a cochain complex.
+We explicate definition \ref{defn:ads4states} and characterize the cochain complex underlying the space of supergravity states.
 
 \begin{lem}\label{lem:ads4states}
-The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4\times S^7})$ where $\mc H_{AdS_4\times S^7}$ is the cochain complex
+The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4})$ where $\mc H_{AdS_4}$ is the cochain complex
  \begin{equation} 
@@
 \C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
-\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^Z_\Omega" description] \\
+\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
 \C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
@@
 \begin{proof}
-To compute the costalk at $0$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence.
+To characterize the costalk at $0 \in \R \times \C$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence.
 Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc.
@@
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
-(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^Z_\Omega" description] \\
+(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^M_\Omega" description] \\
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
@@
 \begin{equation}
- \clie^\bullet \left (\begin{tikzcd}[row sep = 1 ex]
-        \ul{-} & \ul{+} \\ 
+\cO\left (\begin{tikzcd}[row sep = 1 ex]
+        \ul{+} & \ul{-} \\ 
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \C[\![z]\!] \ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \C[\![z]\!] \\
-(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \C[\![z]\!]\del_z\ar[ur, "\del^Z_\Omega" description] \\
+(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \C[\![z]\!]\del_z\ar[ur, "\del^M_\Omega" description] \\
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\d z \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \C[\![z]\!]
@@
 
-The definition of the Chevalley-Eilenberg complex above involves the continuous linear dual of a chain complex of topological vector spaces. The duals of each of the tensor factors are as follows:
+The definition of algebraic functions $\cO(-)$ involves the continuous linear dual of a chain complex of topological vector spaces. 
+The duals of each of the tensor factors are as follows:
 
@@
 
-Thus, we see that $\mc H_{AdS_4\times S^7}$ is indeed as claimed.
+Thus, we see that $\mc H_{AdS_4}$ is indeed as claimed.
 \end{proof}
@@
 \parsec{}
-We proceed to computing a local character for the factorization algebra defined in \ref{defn:ads4states}; thanks to lemma \ref{lem:ads4states} we can compute this as a character of $\Sym(\mc H_{AdS_4\times S^7})$.
+We proceed to computing a local character for the factorization algebra defined in \ref{defn:ads4states}; thanks to lemma \ref{lem:ads4states} we can compute this as a character of $\Sym(\mc H_{AdS_4})$.
 
-We first observe the following action of $\mf{sl}(4)\oplus \mf {sl}(2)$ on $\mc H_{AdS_4\times S^7}$.
+We first observe the following action of $\mf{sl}(4)\oplus \mf {sl}(2)$ on $\mc H_{AdS_4}$.
 The $\mf{sl}(4)$ summand acts on the tensor factor $\C[w_1,w_2,w_3,w_4]$ in the obvious way - it's the symmetric algebra on the fundamental representation.
@@
 
-The weights of $\mc H_{AdS_4\times S^7}$ with respect to the generators of this Cartan subalgebra are entirely determined by the weights of the holomorphic coordinates $z, w_a, a= 1, \cdots, 4$, which we summarize in table \ref{tbl:sugraM2}
+The weights of $\mc H_{AdS_4}$ with respect to the generators of this Cartan subalgebra are entirely determined by the weights of the holomorphic coordinates $z, w_a, a= 1, \cdots, 4$, which we summarize in table \ref{tbl:sugraM2}
 
@@
 
-With this in hand, we wish to compute the character of the space of supergravity states $\Sym (\mc H_{AdS_4\times S^7})$.
-Note that the space of supergravity states was defined to be a symmetric algebra - therefore its character can be computed using plethystic exponentiation of the character of $\mc H_{AdS_4\times S^7}$ - the latter may be referred to as a \textit{single particle index} and is defined by
+With this in hand, we wish to compute the character of the space of supergravity states $\Sym (\mc H_{AdS_4})$.
+Note that the space of supergravity states was defined to be a symmetric algebra - therefore its character can be computed using plethystic exponentiation of the character of $\mc H_{AdS_4}$ - the latter may be referred to as a \textit{single particle index} and is defined by
 
 \[
-f_{AdS_4\times S^7} (t_1, t_2, t_3, q) = \tr_{\mc H_{AdS_4\times S^7}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} t_3^{h_3}.
+f_{AdS_4} (t_1, t_2, t_3, q) = \tr_{\mc H_{AdS_4}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} t_3^{h_3}.
 \]
@@
 \begin{prop}
-The single particle index of the space of supergravity states $\mc H_{AdS_4\times S^7}$ is given by 
+The single particle index of the space of supergravity states $\mc H_{AdS_4}$ is given by 
 \[
-f_{AdS_4\times S^7} (t_1, t_2, t_3, q)  = \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}
+f_{AdS_4} (t_1, t_2, t_3, q)  = \frac{q\left (\begin{aligned} q^{1/4}(t_1+ t_2 + t_3+t_1^{-1}t_2^{-1}t_3^{-1}) &+ q^{-1} \\- q^{-1/4}(t_1^{-1}+ t_2^{-1} + t_3^{-1}+t_1t_2t_3) &- q   \end{aligned}\right)}{(1-q)(1-q^{1/4}t_1)(1-q^{1/4}t_2)(1-q^{1/4}t_3)(1-q^{1/4}t_1^{-1}t_2^{-1}t_3^{-1})}
 \]
@@
 \]
-this character matches the expression in \cite[Eq.
-2.17]{Bhattacharya:2008zy}.
+this character matches the expression in \cite[equation (2.17)]{Bhattacharya:2008zy}.
 The discrepancy of one is accounted for by a zero mode that we have introduced in writing our theory in such a way that M2 branes couple electrically.
@@
 \label{s:ads7states}
-Next, we consider the sphere reduction of $\mc E^N_{AdS_7\times S^4}$ As before, we consider the $S^4$ bundle 
+Next, we consider the sphere reduction of $\mc E^N_{AdS_7}$.
+We begin more generally with the case that $X$ is an arbitrary complex three-fold equipped with a square-root of its canonical bundle.
+The case of twisted $AdS_7 \times S^4$ corresponds to $X = \C^3$.
+As before, we consider the $S^4$ bundle 
 \[
 \begin{tikzcd}
-S^4 \ar[r] & \operatorname{Tot} (\R\oplus K^{1/2}\otimes \C^2\to \C^3) \setminus 0(\C^3) \ar[d, "p"] \\ & \R_{>0}\times \C^3
+S^4 \ar[r] & \operatorname{Tot} (\R\oplus K^{1/2}\otimes \C^2\to X) \setminus 0(X) \ar[d, "p"] \\ & \R_{>0}\times X
 \end{tikzcd}
@@
 
-We wish to describe the free limit of the pushforward $p_* \mc E_{AdS_7\times S^4}$ as a sheaf of cochain complexes on $\R_{>0}\times \C^3$.
+We wish to describe the free limit of the pushforward $p_* \mc E_{AdS_7}$ as a sheaf of cochain complexes on $\R_{>0}\times X$.
 
 \begin{prop}\label{prop:ads7push}
-The pushforward $p_* \mc E^N_{AdS_7\times S^4}$ is given by the sheaf of cochain complexes $\Omega^\bullet_{\R_{>0}} \otimes \Omega^{0,\bullet}_{\C^3} (\mc V^N_{\C^3})$ where $\mc V^N_{\C^3}$ is the following dg-vector bundle on $\C^3$:
+The pushforward $p_* \mc E^N_{AdS_7}$ is given by the sheaf of cochain complexes $\Omega^\bullet_{\R_{>0}} \otimes \Omega^{0,\bullet}_{X} (\mc V^N_X)$ where $\mc V^N_{X}$ is the following complex of vector bundles on~$X$:
 
@@
 H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0, \T \right ) \otimes \mc{O}\ar[r, "\del^W_\Omega" description]\ar[ddr, dotted] & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right ) \otimes \mc O \\
-H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right ) \otimes \Omega^1 \\ & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0, \Omega^1 \right )  \otimes \mc O\ar[uul, dotted]
+H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )  \otimes \T\ar[ur, "\del^X_\Omega" description] \\
+H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right )\otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0 \right ) \otimes \Omega^1 \\ & H^\bullet_{\mr{THF}} \left ((\R\times \C^2)\setminus 0, \Omega^1 \right )  \otimes \mc O\ar[uul, dotted]
 \end{tikzcd}
@@
 \begin{itemize}
-\item The differentials $\del_\Omega^Z$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
-\item The differentials $\del_Z$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
-\item The dotted arrows are $N$ dependent differentials roughly given by bracketing with the flux, and are explicated below. 
+\item The differentials $\del_\Omega^X$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
+\item The differentials $\del_X$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
+\item The dotted arrows are $N$ dependent differentials roughly given by bracketing with the flux $N F_{M5}$, see \eqref{eqn:FM5}, and are explicated below. 
 \end{itemize}
@@
 \end{align*}
-where the first map is given by contracting with $\d w_1 \d w_2$ and multiplying by $(w_1w_2)^{-1}$, while the second map is given by applying $\del_Z$, wedging with the $\d w_1 \d w_2$ and contracting with the inverse of the holomorphic volume form on $\C^5$ to get a vector field along $\C^3$.
+where the first map is given by contracting with $\d w_1 \d w_2$ and multiplying by $(w_1w_2)^{-1}$, while the second map is given by applying $\del_X$, wedging with the $\d w_1 \d w_2$ and contracting with the inverse of the holomorphic volume form on $\C^5$ to get a vector field along $X$.
 
@@
 The proof is exactly analogous to that of proposition \ref{prop:pushads4} .
-Using results from \cite[Sec.
-4.2]{KormanThesis}, \cite{KamberTondeur}  to compute the pushforward, we find a sheaf of $\Omega^\bullet_{\R_{>0}}\otimes \Omega^{0,\bullet}_{\C^3}$-modules whose sections have a tensor factor given by the THF cohomology of $S^4$.
+Using results from \cite[section 4.2]{KormanThesis}, \cite{KamberTondeur}  to compute the pushforward, we find a sheaf of $\Omega^\bullet_{\R_{>0}}\otimes \Omega^{0,\bullet}_{X}$-modules whose sections have a tensor factor given by the THF cohomology of $S^4$.
 Next, we use the isomorphism in THF cohomology afforded by the deformation retraction of $(\R\times \C^2)\setminus 0$ onto $S^4$.
@@
 
-As in the previous subsection, we ask for a boundary condition we can place on the fields at $\{\infty\}\times \C^3\subset \R_{>0}\times \C^3$.
-The phase space, given by $(p_* \mc E^N_{AdS_7\times S^4})|_{\{\infty\} \times \C^3}$, is seen to be $\Omega^{0,\bullet}_{\C^3} (\mc V_{\C^3} )$, and we search for a shifted Lagrangian therein.
+As in the previous subsection, we ask for a boundary condition we can place on the fields at $\{\infty\}\times X\subset \R_{>0}\times X$.
+The phase space, given by $(p_* \mc E^N_{AdS_7})|_{\{\infty\} \times X}$, is seen to be $\Omega^{0,\bullet}_{X} (\mc V_{X} )$, and we search for a shifted Lagrangian therein.
 
 Completely analogously to before, we may rewrite the phase space as a shifted cotangent bundle.
-The higher residue pairing, the natural pairing between $T, \Omega^1$, and the integration pairing along $\C^3$, all conspire to give the phase space an even-shifted symplectic structure.
-Together with this, we may ionce again identify the phase space with a twisted cotangent bundle
+The higher residue pairing, the natural pairing between $T, \Omega^1$, and Serre duality along $X$, all conspire to give the phase space an even-shifted symplectic structure.
+Together with this, we may once again identify the phase space with a twisted cotangent bundle
 
 \[
-\Omega^{0,\bullet}_{\C^3} (\mc V_{\C^3}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex] 
+\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex] 
 \ul{-} & \ul{+} \\
-\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{\C^3} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3}  \\
-\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3} (\T)\ar[ur, "\del^Z_\Omega" description] \\
-\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{\C^3} \ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{\C^3} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{\C^3}
+\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X}  \\
+\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} (\T)\ar[ur, "\del^X_\Omega" description] \\
+\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{X} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{X}
 \end{tikzcd} \right) 
@@
 
-A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{\C^3} (\mc L_{AdS_7\times S^4})$ where $\mc L_{AdS_7\times S^4}$ is the dg-vector bundle given by  
+A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7})$ where $\mc L_{AdS_7}$ is the complex of vector bundles given by  
 \begin{equation}
@@
 (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc O \\
-(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]  \otimes \Omega^1 \\ & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\d w_a\} \otimes \mc O
+(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \T\ar[ur, "\del^X_\Omega" description] \\
+(w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}]  \otimes \Omega^1 \\ & (w_1w_2)^{-1} \C[w_1^{-1}, w_2^{-1}] \{\d w_a\} \otimes \mc O
 \end{tikzcd}
@@
 
+We now specialize to $X = \C^3$.
+
 \begin{defn}\label{defn:ads7states}
-The space of supergravity states on twisted $AdS_7\times S^4$ is given by the costalk at zero of the factorization algebra on $\C^3$ given by $\clie^\bullet \left (\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4} ) \right )$.
+The space of supergravity states on twisted $AdS_7\times S^4$ is given by the costalk at zero of the factorization algebra on $\C^3$ given by 
+\beqn
+\cO \left(\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7} ) \right ) .
+\eeqn
 \end{defn}
@@
 \begin{lem}
-The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7\times S^4} )$ where $\mc H_{AdS_7\times S^4}$ is given by the cochain complex
+The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
 
@@
 \C[w_1,w_2] \{\partial_{w_a}\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,w_2]  \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0} \\
-\C[w_1,w_2]  \{\del_{z_i}\}  \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[ur, "\del^Z_\Omega" description] \\
-\C[w_1,w_2] \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2] \{\d z_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0} \\ & \C[w_1, w_2] \{\d w_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}
+\C[w_1,w_2]  \{\del_{z_i}\}  \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[ur, "\del^X_\Omega" description] \\
+\C[w_1,w_2] \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2] \{\d z_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0} \\ & \C[w_1, w_2] \{\d w_a\} \otimes \C[\del_{z_1}, \del_{z_2}, \del_{z_3}]\delta_{z_i=0}
 \end{tikzcd}
@@
 \parsec{}
-As before, we may compute the local character of the factorization algebra defined in \ref{defn:ads7states} as a character of $\Sym (\mc H_{AdS_7\times S^4})$.
+As before, we may compute the local character of the factorization algebra defined in \ref{defn:ads7states} as a character of $\Sym (\mc H_{AdS_7})$.
 
-We will use an action of $\mf{sl}(3)\oplus \mf {sl}(2)\oplus \mf{gl}(1)$ on $\mc H_{AdS_7\times S^4}$ which we may explicitly realize as follows:
+We will use an action of $\mf{sl}(3)\oplus \mf {sl}(2)\oplus \mf{gl}(1)$ on $\mc H_{AdS_7}$ which we may explicitly realize as follows:
 \begin{itemize}\label{eqn:im5}
@@
 
-We enumerate single particle supergravity states via computing the super trace of the operator $q^\Delta t_1^{h_1} t_2^{h_2} r^h$ acting on $\mc{H}_{AdS_7\times S^4}$:
+We enumerate single particle supergravity states via computing the super trace of the operator $q^\Delta t_1^{h_1} t_2^{h_2} r^h$ acting on $\mc{H}_{AdS_7}$:
 \begin{equation}
-f_{AdS_7\times S^4}(t_1,t_2,r,q) = \tr_{\mc{H}_{AdS_7\times S^4}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} r^h  .
+f_{AdS_7}(t_1,t_2,r,q) = \tr_{\mc{H}_{AdS_7}} (-1)^F q^\Delta t_1^{h_1} t_2^{h_2} r^h  .
 \end{equation}
@@
 \label{prop:sugraindex1}
-The single particle index of the space of twisted supergravity states~$\mc{H}_{AdS_7\times S^4}$ is given by the following expression
+The single particle index of the space of twisted supergravity states~$\mc{H}_{AdS_7}$ is given by the following expression
 \begin{equation}
 \label{eqn:sugra_index}
-f_{AdS_7\times S^4} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
+f_{AdS_7} (t_1,t_2, r, q) = \frac{q^4(t_1^{-1}+t_1t_2^{-1}+t_2)-q^2(t_1+t_1^{-1}t_2+t_2^{-1})+(q^{3/2}-q^{9/2})(r+r^{-1})}{(1-t_{1}^{-1}q)(1-t_{2}q)(1-t_{1}t_{2}^{-1}q)(1-rq^{3/2})(1-r^{-1}q^{3/2})}.
 \end{equation}
@@
 \begin{equation}
-{\rm PExp}\left[f_{AdS_7\times S^4}(t_1,t_2,r,q)\right] .
+{\rm PExp}\left[f_{AdS_7}(t_1,t_2,r,q)\right] .
 \end{equation}
@@
 \label{eqn:Kim_sugra}
-f_{AdS_7\times S^4} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
+f_{AdS_7} (y_i, y, q) = \frac{q^4(y_1+y_2+y_3)-q^2(y_1^{-1} + y_2^{-1} + y_3^{-1})+(1-q^3)(yq + y^{-1} q^2)}{(1-y_1 q)(1-y_2 q)(1-y_3 q)(1-yq)(1-y^{-1} q^2)},
 \end{equation}
-We note that this matches exactly with the index computed in \cite[Eq. (3.23)]{Kim:2013nva} with the change of variables.
+We note that this matches exactly with the index computed in \cite[equation (3.23)]{Kim:2013nva} with the change of variables.
 %\begin{equation}
@@
 
-Our formula \eqref{eqn:sugra_index} also matches with \cite[Eq. (3.24)]{Bhattacharya:2008zy} where we use the change of variables
+Our formula \eqref{eqn:sugra_index} also matches with \cite[equation (3.24)]{Bhattacharya:2008zy} where we use the change of variables
 \begin{equation}
@@
 \[
-f_{AdS_7\times S^4}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2} 
+f_{AdS_7}(q, t_1, t_2=1, r = q^{1/2}) = \frac{q}{(1-q)^2} 
 \]
@@
 \subsection{Transverse boundary conditions}\label{sec:transversebc}
-In the previous subsections, we discussed boundary conditions in the phase spaces of the sphere compactifications $p_* \mc E^N_{AdS_4\times S^7}$ and $p_* \mc E^N_{AdS_7\times S^4}$ viewed as free theories, that exist for generic values of $N$.
+
+\brian{edit this section to emphasize that we aren't fully characterizing the interacting structure, just free limit.}
+
+In the previous subsections, we discussed boundary conditions in the phase spaces of the sphere compactifications $p_* \mc E^N_{AdS_4}$ and $p_* \mc E^N_{AdS_7}$ viewed as free theories, that exist for generic values of $N$.
 However, there are distinguished boundary conditions that exist for $N = 0$ that we will use in the sequel.
@@
 \begin{itemize}
-\item Let $\mc L_{AdS_4\times S^7}^{r=0}$ denote the following dg-vector bundle on $\C$ 
+\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $\C$ 
  \begin{equation}
@@
 \C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
-\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
+\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
+\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
 \end{tikzcd}
@@
 
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4\times S^7})|_{\{\infty\} \times\R\times\C}$ is given by $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L_{AdS_4\times S^7}^{r=0})$.
+The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times\R\times\C}$ is given by $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L_{AdS_4}^{r=0})$.
 
-\item Let $\mc L_{AdS_7\times S^4}^{r=0}$ denote the following dg-vector bundle on $\C^3$
+\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $\C^3$
  \begin{equation}
@@
 \C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
-\C[w_1, w_2]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
-\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
+\C[w_1, w_2]   \otimes \T\ar[ur, "\del^X_\Omega" description] \\
+\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
 \end{tikzcd}
 \end{equation}
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7\times S^4})|_{\{\infty\} \times\C^3}$ is given by $\Omega^{0,\bullet}_{\C^3} (\mc L_{AdS_7\times S^4}^{r=0})$.
+The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times\C^3}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
 \end{itemize}
@@
 \[
-\Omega^\bullet_{\R} \otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4\times S^7} ) \to (p_* \mc E^0 _{AdS_4\times S^7})|_{\{\infty\} \times \R\times \C}, \quad \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} ) \to (p_* \mc E^0 _{AdS_7\times S^4})|_{\{\infty\} \times \C^3}
+\Omega^\bullet_{\R} \otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4} ) \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times \R\times \C}, \quad \Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times \C^3}
 \]
@@
 \begin{prop}\label{prop:altstates}
-There are isomorphisms
+There are isomorphisms of cochain complexes
 \begin{center}
-$\mc U \left ( \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L_{AdS_4\times S^7}^{r=0} ) \right )(0)\cong \Sym( \mc {H}_{AdS_4\times S^7} )$ \\
-$\mc U \left ( \Omega^{0,\bullet}_{\C^3}(\mc L_{AdS_7\times S^S}^{r=0})\right )(0)\cong \Sym( \mc {H}_{AdS_7\times S^4} )$
+$\mc U \left ( \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L_{AdS_4}^{r=0} ) \right )(0)\cong \Sym( \mc {H}_{AdS_4} )$ \\
+$\mc U \left ( \Omega^{0,\bullet}_{X}(\mc L_{AdS_7}^{r=0})\right )(0)\cong \Sym( \mc {H}_{AdS_7} )$
 \end{center}
@@
 For a local $L_\infty$ algebra $\mc L$, its factorization envelope $\mc U(L)$ is defined to be $\clie_\bullet (\mc L_c)$ the Lie algebra chains on the cosheaf of compactly supported sections.
-Therefore, it suffices to show that in each case, the costalk of the cosheaf of comapctly supported sections is quasi-isomorphic to $\mc H_{AdS_4\times S^7}$ and $\mc H_{AdS_7\times S^4}$ respectively.
+Therefore, it suffices to show that in each case, the costalk of the cosheaf of comapctly supported sections is quasi-isomorphic to $\mc H_{AdS_4}$ and $\mc H_{AdS_7}$ respectively.
 This is a consequence of the following observations.
@@
 
+\end{document}
+
 %\parsec

### 2023-05-23 graviton spectra/content/br.tex
merge

@@
 
+\newcommand\til{\widetilde}
 \begin{document} 
@@
 
-As remarked above, in eleven-dimensional supergravity, the $AdS_7 \times S^4$ and $AdS_4\times S^7$ backgrounds are obtained by backreacting a number of M5 branes and M2 branes in flat space \cite{Maldacena:1997re,WittenAdS}.
-In this section, we wish to give an account of this procedure at the level of our twisted theory in eleven-dimensions.
+In eleven-dimensional supergravity the $AdS_7 \times S^4$ and $AdS_4\times S^7$ backgrounds are obtained by backreacting a number of M5 branes and M2 branes in flat space \cite{Maldacena:1997re,WittenAdS}.
+In this section, we will give an account of this procedure at the level of our twisted theory in eleven-dimensions.
+The main outcome is a geometric definition of twisted analogs of $AdS$ spaces. 
 Before describing the specific examples of interest, we begin with some generalities.
@@
 \begin{itemize}
-  \item Place the theory on the complement of the zero section. 
+  \item Restrict the theory on the complement of the zero section. 
+  If the theory is defined on flat space $\R^d$ to begin with, and the brane lives a long a coordinate plane $\R^{n} \subset \R^d$, then this amounts to restricting the theory on $\R^d \setminus \R^n$.
   \item Deform the theory on the complement of the zero section by a certain Maurer--Cartan element, thought of as the flux sourced by branes wrapping the zero section.
@@
 This procedure is implemented at the level of the $\Omega$-deformed nonminimal twist on flat space in the appendix of \cite{CostelloM5}, and in \cite{raghavendran2022holographic} the procedure is carried about for M5 branes in our eleven-dimensional model in some global generality.
-For the purposes of this thesis however, we will content ourselves with examples on flat space.
+As another example, in \cite{CGhol} the authors show that carrying out this procedure for branes in the topological $B$-model on $\C^3$ results in the deformed conifold.
+For the purposes of this thesis, we will mostly content ourselves with examples on flat space.
 
@@
 The eleven-dimensional theory exists on any manifold which is locally of the form 
-\[
+\beqn\label{eqn:local}
 \R \times Z
-\] 
+\eeqn
 where $Z$ is a Calabi--Yau fivefold.
@@
 
+As examples, we point out two classes of THF eleven-manifolds which we will consider in this paper, depending on whether we consider stack of M2 or M5 branes respectively:
+\begin{itemize}
+\item Let $M$ be a three-manifold equipped with a THF of real codimension two. 
+Locally such a manifold is of the form $\R \times \C$.
+Let $K_M$ be the canonical bundle of $M$ and suppose we have fixed a fourth-root $K^{1/4}$.\footnote{If $\cF$ is a THF of codimension two then $\T_M / \T_\cF \otimes_\R \C = Q \oplus \bar{Q}$ for the bundle $Q$ which is locally spanned by $\del_z$.
+We let $K = Q^\vee$.}
+Then we consider the THF eleven-manifold 
+\beqn\label{eqn:thfm2}
+\text{Tot} \left(K_M^{1/4} \otimes \C^4 \to M\right) .
+\eeqn
+The M2 branes will wrap the zero section of this total bundle.
+Notice that the power of $1/4$ is to guarantee the Calabi--Yau condition.
+\item Let $X$ be a complex threefold equipped with $K_X^{1/2}$.
+We can consider the THF eleven-manifold
+\beqn\label{eqn:thfm5}
+\R \times \text{Tot} \left(K_X^{1/2} \otimes \C^2 \to X \right) .
+\eeqn
+The M5 branes will wrap the zero section and lie at a point in $\R$.
+Notice that in this case the manifold is globally of the form $\R \times Z$ where $Z$ is a Calabi--Yau fivefold.
+\end{itemize}
+
 In \cite{RSW,RWindex} we describe how physical fields in supergravity are manifest in the twisted model.
-\brian{expand this}
-Here, we will jump straight to describing the twisted model.
-Fields generally live in spaces of the form
+We review a small part of this.
+If $\til{Z}$ is an eleven-manifold equipped with a THF structure as above, the fields will live in a space of the form
+\beqn
+\cA^\bu(\til{Z}, \til{V})
+\eeqn
+where
+\begin{itemize}
+\item The graded bundle $\til{V}$ is holomorphic with respect to the THF structure.
+\item $\cA^\bu (\til{Z}, \til{V})$ denotes the THF cohomology of $\til{Z}$ with coefficients in $\til{V}$.
+\end{itemize}
+To simplify discussion in the remainder of this section we will only work in the local model~\eqref{eqn:local} where $\til{Z} = \R \times Z$ for $Z$ a Calabi--Yau fivefold.
+Then, the space of fields is of the form
 \beqn
@@
 {\em even}).
+The three-forms $\beta^{\Bar{i}\Bar{j}\Bar{k}} \d \zbar_{\Bar{i}} \d \zbar_{\Bar{j}} \d \zbar_{\Bar{k}}$, $\beta_t^{\Bar{i}\Bar{j}} \d t \ \zbar_{\Bar{i}} \d \zbar_{\Bar{j}}$, $\gamma^{i \Bar{j} \Bar{k}} \d z_i \d \zbar_{\Bar{j}} \d \zbar_{\Bar{k}}$, and $\gamma_t^{i \Bar{j}} \d t \d z_i \d \zbar_{\Bar{j}}$ comprise components of the supergravity three-form $C$ which survive the $SU(5)$ twist.
 
@@
 
-From the point of view of the $SU(5)$ twist there are essentially two types of circles one can consider.
-The first is a `holomorphic circle'.
-This is present when we assume our Calabi--Yau fivefold is of the form $Z = \C^\times \times Y$ with $Y$ a Calabi--Yau fourfold.
-We assume that $\C^\times$ is equipped with the standard volume form $\d z$.
-The $S^1$ reduction along a circle in $\C^\times$ results in a twist of type IIA supergravity with global symmetry $SU(4)$ on the manifold
-\beqn
-\R \times \R \times Y .
-\eeqn
-More generally, this twist can be defined when $\R^2$ is replaced by a smooth oriented two-dimensional manifold $M^2$.
-In \cite{CLsugra}, Costello and Li have given a conjectural description of this particular twist of type IIA (and many other twists) using methods of topological string theory.
-In this case, the conjecture of Costello and Li is that the twist is equivalent to a mixed topological string theory which is given by the A-model along $M^2$ and the B-model along $Y$.
-In perturbation theory, this admits a description in terms of Kodaira--Spencer theory along the fourfold $Y$.
-Via an explicit dimensional reduction of our model we find an exact match with this expectation \cite{RSW}.
-The dimensional reduction of our eleven-dimensional model on
-\beqn
-\R \times \C \times Y
-\eeqn
-along $S^1 \subset \C$ is equivalent to the mixed topological A-model along $\R^2$ and B-model along $Y$ as considered in \cite{CLsugra}.
-
-The other type of reduction one can consider is that along a `topological' circle.
-This corresponds to placing our eleven-dimensional model on
-\beqn
-S^1 \times Z
-\eeqn
-and performing reduction along $S^1 \times Z \to Z$.
-What results is a theory with $SU(5)$ global symmetry.
-We conjecture that this is the $SU(5)$ twist of type IIA supergravity.
-There is no expected description of the $SU(5)$ twist in terms of topological strings like in the $SU(4)$ or $SU(2)$ cases.
+%From the point of view of the $SU(5)$ twist there are essentially two types of circles one can consider.
+%The first is a `holomorphic circle'.
+%This is present when we assume our Calabi--Yau fivefold is of the form $Z = \C^\times \times Y$ with $Y$ a Calabi--Yau fourfold.
+%We assume that $\C^\times$ is equipped with the standard volume form $\d z$.
+%The $S^1$ reduction along a circle in $\C^\times$ results in a twist of type IIA supergravity with global symmetry $SU(4)$ on the manifold
+%\beqn
+%\R \times \R \times Y .
+%\eeqn
+%More generally, this twist can be defined when $\R^2$ is replaced by a smooth oriented two-dimensional manifold $M^2$.
+%In \cite{CLsugra}, Costello and Li have given a conjectural description of this particular twist of type IIA (and many other twists) using methods of topological string theory.
+%In this case, the conjecture of Costello and Li is that the twist is equivalent to a mixed topological string theory which is given by the A-model along $M^2$ and the B-model along $Y$.
+%In perturbation theory, this admits a description in terms of Kodaira--Spencer theory along the fourfold $Y$.
+%Via an explicit dimensional reduction of our model we find an exact match with this expectation \cite{RSW}.
+%The dimensional reduction of our eleven-dimensional model on
+%\beqn
+%\R \times \C \times Y
+%\eeqn
+%along $S^1 \subset \C$ is equivalent to the mixed topological A-model along $\R^2$ and B-model along $Y$ as considered in \cite{CLsugra}.
+%
+%The other type of reduction one can consider is that along a `topological' circle.
+%This corresponds to placing our eleven-dimensional model on
+%\beqn
+%S^1 \times Z
+%\eeqn
+%and performing reduction along $S^1 \times Z \to Z$.
+%What results is a theory with $SU(5)$ global symmetry.
+%We conjecture that this is the $SU(5)$ twist of type IIA supergravity.
+%There is no expected description of the $SU(5)$ twist in terms of topological strings like in the $SU(4)$ or $SU(2)$ cases.
 
@@
 
-We begin by viewing the eleven-dimensional manifold $\R\times \C^5$ as 
+We begin by viewing the eleven-dimensional manifold
 \[
-\operatorname{Tot}(K^{1/4}_\C\otimes \C^4\to \R\times \C_z)
+\operatorname{Tot}(K^{1/4}_M \otimes \C^4\to M)
 \]
-where we have abusively used $K^{1/4}_\C\otimes \C^4$ to denote its pullback along the natural projection $\R\times \C\to \C$.
-Thinking of flat space in this way is simply a way to record weights under natural scaling actions.
-We will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/4}_\C\otimes \C^4$.
+as in \eqref{eqn:thfm2}.
+Even when we restrict ourselves to flat space $M = \R \times \C$ this way of presenting the eleven-manifold $\R \times \C^5$ is a convenient mechanism to record weights under natural scaling actions. 
+We will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/4}_M \otimes \C^4$.
 
 We carry out the above procedure. 
-Consider a stack of $N$ twisted M2 branes wrapping the zero section $\R\times \C_z$.
+Consider a stack of $N$ twisted M2 branes wrapping the zero section $M$.
 Our ansatz for this coupling is heuristically of the form
 \[
-I_{M2}(\gamma) = N\int_{\C_z} \gamma + \cdots
+I_{M2}(\gamma) = N\int_{M} \gamma + \cdots
 \] 
-which is nonzero only on the component of $\gamma$ in $\Omega^1(\R)\otimes \Omega^{1,1}(\C^5)$.
+which is nonzero only on the component of $\gamma$ which is a top form along $M$.
 We have only indicated the lowest order coupling, the $\cdots$ indicate higher-order couplings which will be higher order in the fields of the eleven-dimensional theory and explicitly involve the fields in the worldvolume theory.
@@
 This coupling is justified by comparison with the physical theory and by dimensional reduction. 
-Indeed, as discussed in~\S\ref{s:components}, the component of $\gamma$ which participates in the above coupling is a component of the $C$-field of eleven dimensional supergravity.
+Indeed, as discussed in the previous section, the component of $\gamma$ which participates in the above coupling is a component of the three-form $C$-field of eleven dimensional supergravity. 
 Thus, the proposal mirrors electric couplings of M2 branes in the physical theory, which simply involves integrating the $C$-field over the worldvolume of the brane.
 
-Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of type IIA supergravity on $\R^2\times \C_z\times \C^3$ with $N$ $D2$ branes wrapping $\R\times \C_z$.
+Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of type IIA supergravity with $N$ $D2$ branes wrapping $M$. 
 As is shown in \cite{CLsugra}, an electric coupling of D2 branes to the $SU(4)$ twist of type IIA supergravity is given by 
 \[
-I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma + \cdots
+I_{D2}(\gamma) = N \int_{M} \gamma + \cdots
 \] 
@@
 The backreacted geometry will be given by a solution to the equations of motion upon deforming the eleven-dimensional action by the interaction $I_{M2}(\gamma)$.
+For the twisted version of $AdS$ space we should start with the three-manifold $M$ being just $\R \times \C$, so that the resulting theory is defined originally just on flat space.
+
 Varying the deformed action with respect to $\gamma$,
@@
 \beqn\label{eqn:FM2}
- F_{M2} = \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \partial_z .
+ F_{M2} = \Omega^{-1} \frac{6}{(2\pi i)^4} \frac{\sum_{a=1}^4 \bar{w}_a \d \bar{w}_1 \cdots \widehat{\d \bar{w}_a} \cdots \d \bar{w}_4}{\|w\|^{8}} \d w_1 \d w_2 \d w_3 \d w_4 .
 \eeqn
@@
 We similarly introduce an analog of the ${\mr AdS}_7 \times S^4$ background in our description of the minimal twist of eleven-dimensional supergravity.
-As before, we begin by viewing our eleven-dimensional manifold $\R\times \C^5$ as
+We begin with our twisted theory defined on
 \[
-\operatorname{Tot}(\R \oplus K_{\C^3}^{1/2}\otimes \C^2 \to \C^3_z)
+\R \times \operatorname{Tot}(K_{\C^3}^{1/2}\otimes \C^2 \to X)
 \]
-to record weights under natural scaling actions.
-We once again will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/2}_{\C^3}\otimes \C^2$, and we use $t$ to denote a fiber coordinate on the trivial bundle $\R \to \C^3_z$.
+with $X$ a complex threefold as in \eqref{eqn:thfm5}.
+As above, we will momentarily be only concerned with flat space which means taking $X = \C^3$.
+We once again will use $w_a$ to denote holomorphic fiber coordinates on $K^{1/2}_{X}\otimes \C^2$, and we use $t$ to denote a fiber coordinate on $\R$.
 
@@
 To repeat the procedure in the previous subsection, we begin by defining our eleven-dimensional theory couples to M5 branes (to first order).
-Consider a stack of $N$ M5 branes wrapping the zero section $\C^3_z$. 
+Consider a stack of $N$ M5 branes wrapping the zero section $X$. 
 We consider the heuristic nonlocal coupling 
 \[
-I_{M5} = N\int_{\C^3_z} \div^{-1}\mu \vee \Omega +\cdots 
+I_{M5} = N\int_{X} \div^{-1}\mu \vee \Omega +\cdots 
 \]
-Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}$. 
+Note that this expression is only nonzero on the component of $\mu$ in $\PV^{1,3}(X)$. 
 We argue that this coupling is consistent with expectations from the physical theory and from dimensional reduction.
 
-The twisted field $\mu^{1,3}$ is a component of the Hodge star of the $G$-flux in the physical theory (\S\ref{s:components}). 
+The twisted field $\mu^{1,3}$ is a component of the Hodge star of the metric flux in the physical theory.
 In the physical theory, M5 branes magnetically couple to the $C$-field; the coupling involves choosing a primitive for the Hodge star of the $G$-flux and integrating it over the M5 worldvolume.
@@
 We may once again justify this coupling by dimensional reduction to IIA supergravity. 
-Reducing on the circle along the directions the M5 branes wrap yields the $SU(4)$ invariant twist of type IIA supergravity on $\C^4 \times \R^2$ with $N$ $D4$ branes wrapping $\C^2 \times \R$.
+When $X = \C^2 \times \C$ we reduce on the circle along the last copy of $\C$ that the M5 branes wrap to get the $SU(4)$ invariant twist of type IIA supergravity on $\C^4 \times \R^2$ with $N$ $D4$ branes wrapping $\C^2 \times \R$.
 
@@
 Again, this only depends on $\gamma$ through its field strength $\del \gamma$.
+It is at this point that we restrict ourselves to the case $X = \C^3$.
 

### 2023-05-23 graviton spectra/content/index.tex
merge

@@
 Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
-\[
+\beqn\label{eqn:cotm2}
 \cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
@@
 \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right)
-\]
+\eeqn
 For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.
@@
 
-\[
-\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex] 
+\beqn\label{eqn:cotm5}
+\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex] 
 \ul{-} & \ul{+} \\
@@
 \end{tikzcd} \right) 
-\]
-
-Exactly analogously to the case of $AdS_4\times S^7$, $\Pi$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.
+\eeqn
+Analogously to the case of $AdS_4\times S^7$, $\alpha$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.
 
@@
 
-\brian{edit this section to emphasize that we aren't fully characterizing the interacting structure, just free limit.}
-
 In the previous subsections, we discussed boundary conditions in the phase spaces of the sphere compactifications $p_* \mc E^N_{AdS_4}$ and $p_* \mc E^N_{AdS_7}$ viewed as free theories, that exist for generic values of $N$.
@@
 
-Indeed, recall that in equations \eqref{}, \eqref{} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux.
+Indeed, recall that in equations \eqref{eqn:cotm2}, \eqref{eqn:cotm5} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux.
 When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.
@@
 \C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
-\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
+\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
 \end{tikzcd}

### 2023-05-25 graviton spectra/content/e16.tex
merge
e16

@@
-%\documentclass[11pt]{amsart}
-%
-%%\usepackage{../macros-master}
-%\usepackage{macros-fivebrane}
-%
-%\begin{document}
+\documentclass[../main.tex]{subfiles}
 
-%\parsec[s:membraneobs]
-%
-%
-%\parsec[s:fivebraneobs]
-%
-%Let $Z$ be a complex threefold. 
-%In \ref{s:single} we have described the holomorphic twist of a theory on a single fivebrane within the (degenerate) BV formalism in terms of the (abelian) local $L_\infty$ algebra $\mc{L}_{single}$ on $Z$.
-%The factorization algebra of classical observables of the holomorphic twist of the single fivebrane theory assigns to an open set $U \subset Z$
-%the cochain complex
-%\[
-%\clie^\bullet\left(\mc{L}_{single}(U)\right) .
-%\]
-%We will denote the entire factorization algebra on $Z$ of classical observables by~$\clie^\bullet(\mc{L}_{single})$.
+\begin{document}
+
 \section{$E(1|6)$ modules from gravitons on $AdS_4\times S^7$}\label{sec:e16}
@@
 Having justified that the spaces of supergravity states constructed in the previous subsection are in fact counting gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively, we turn to studying representation theoretic properties of these state spaces.
-In this section, we focus on the case of gravitons on $AdS_4\times S^7$, using the description of the state space afforded by proposition \ref{prop:altstates} which describes it as the costalk of a factorization envelopes of the boundary conditions $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$.
+In this section, we focus on the case of gravitons on $AdS_4\times S^7$, using the description of the state space afforded by proposition \ref{prop:altstates} which describes it as the costalk of a factorization envelopes of the boundary conditions $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4} )$.
 
-We construct a certain $\C^\times$-action on the boundary fields $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$ equipped with the $L_\infty$ structure from remark \label{rmk:nottransferred} with the feature that the zeroth weight spaces are a local version of another exceptional linearly compact super-Lie algebras, $E(1|6)$.
-This in particular readily gives a decomposition of the state space $\mc H_{AdS_4\times S^7}$ into $E(1|6)$-modules.
+We construct a certain $\C^\times$-action on the boundary fields $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4} )$ equipped with the $L_\infty$ structure from remark \label{rmk:nottransferred} with the feature that the zeroth weight spaces are a local version of another exceptional linearly compact super-Lie algebras, $E(1|6)$.
+This in particular readily gives a decomposition of the state space $\mc H_{AdS_4}$ into $E(1|6)$-modules.
 We explicitly characterize the summands of this decomposition with their module structures and give closed form expressions for their characters.
@@
 \parsec{}
-We consider a particular decomposition of the space of states $\mc H_{AdS_4\times S^7}$.
-It is induced by a decomposition of the boundary fields $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{{r=0}}_{AdS_4\times S^7} )$ introduced in section \ref{sec:transversebc}  The decomposition is induced by a $\C^\times$ action on the boundary fieldsboundary fields $\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4\times S^7} )$ that mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
+We define a decomposition of the space of states $\mc H_{AdS_4}$. 
+It is induced by a decomposition of the boundary fields $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{{r=0}}_{AdS_4} )$ introduced in section \ref{sec:transversebc}  arising from a $\C^\times$ action which mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
 
@@
 
-The following result is a straightforward if lengthy computation. We state it without proof.
+The following result is straightforward.
 
 \begin{prop}\label{prop:ads4decomp}
-The $L_\infty$ structure on $\Pi\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} )$ identified in section \ref{sec:transversebc} is equivariant for this $\C^\times$ action.
+The $L_\infty$ structure on $\Pi\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} )$ identified in section \ref{sec:transversebc} is equivariant for this $\C^\times$ action.
 \end{prop}
@@
 \[
-\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} ) = \prod _{n\geq 2} \mc F^{(n)}_{\R\times \C}
+\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} ) = \prod _{n\geq -2} \mc F^{(n)}_{\R\times \C}
 \]
 
-where for each open set $I\times U\subset\R\times \C$, we have that \[\mc F_{\R\times \C}^{(n)} (I\times U) \subset \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C (U, \mc L^{r=0}_{AdS_4\times S^7} )\] is the weight $n$ eigenspace with respect to the above $\C^\times$ action.
-In particular, we see that $\mc F^{(0)}_{\R\times \C}$ is itself a local dg-Lie algebra, for which  every $\mc F^{(n)}_{\R\times \C}$ is a module.
+where for each open set $I\times U\subset\R\times \C$, we have that \[\mc F_{\R\times \C}^{(n)} (I\times U) \subset \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C (U, \mc L^{r=0}_{AdS_4} )\] is the weight $n$ eigenspace with respect to the above $\C^\times$ action.
+In particular, we see that $\mc F^{(0)}_{\R\times \C}$ is itself a local dg Lie algebra, for which  every $\mc F^{(n)}_{\R\times \C}$ is a module.
 
-\subsection{The lowest piece: the holomorphic-topological twist of the 3d $\mc N=8$ BLG theory}\label{sec:BLG}
+\subsection{The lowest pieces and 3d $\mc N=8$ BLG theory}\label{sec:BLG}
 \parsec[] The first nontrivial case is the weight ${(-2)}$ piece. We have the following
@@
 \begin{lem}
-There is a quasi-isomorphism \[\mc F^{(-2)}_{\R\times \C} \cong \Omega^\bullet_{\R\times \C}.\]
+There is an isomorphism of elliptic complexes \[\mc F^{(-2)}_{\R\times \C} \simeq \Omega^\bullet_{\R\times \C}.\]
 \end{lem}
@@
 The only sections which contribute are those of type $\beta$ or $\gamma$ with no form components along the fiber directions.
-Therefore, we see directly that \[\mc F^{(-2)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C ( \mc O \xrightarrow{\del} \Omega^1 ).\]
+Therefore, we see directly that \[\mc F^{(-2)}_{\R\times \C} \simeq \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C ( \mc O \xrightarrow{\del} \Omega^1 ).\]
 \end{proof}
@@
 \begin{lem}
-There is a quasi-isomorphism \[ \mc F^{(-1)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
+There is an isomorphism of elliptic complexes 
+\[ \mc F^{(-1)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
 \end{lem}
@@
 There is a highly supersymmetric Chern-Simons-matter theory discovered independently by Bagger-Lambert \cite{Bagger_2007}, \cite{Bagger:2007jr} and Gustavsson \cite{Gustavsson:2007vu}.
-The aptly named BLG theory has $\mc N=8$ superconformal symmetry, and admits a holomorphic-topological twist that was computed by Garner in \cite{Garner2022vds}.
+The aptly named BLG theory has $\mc N=8$ superconformal symmetry, and admits a holomorphic-topological twist that was characterized by Garner in \cite{Garner2022vds}.
 
@@
 In work-in-progress with Garner and Williams, we show that the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ in fact preserves this $L_\infty$-structure.
+
+\brian{it's an abelian L-infinity structure right? So we can just say complexes.}
+
+\brian{The thing we don't mention so much is the BV structure.}
+
+\brian{I think we can at least comment that the BV structure comes from the BR.}
 
@@
 
-We first recall the definition of this super-Lie algebra \cite{KacBible}
-\begin{defn}\label{defn:e(1|6)}
-Let $E(1|6)$ be the following super-Lie algebra. 
+We first recall the definition of this super Lie algebra \cite{KacBible}. 
+The even part $E(1|6)_0$ is the semidirect product Lie algebra 
+\beqn
+\Vect(\Hat{D}) \ltimes \left( \cO(\Hat{D}) \otimes \mf{sl}(4) \right )
+\eeqn
+where $\Vect(\Hat{D})$ and $\cO(\Hat{D})$ denote vector fields and functions on the formal disk.
+
+The odd part is the (unique) nontrivial extension of $E(1|6)_0$-modules 
+\[0\to \Sym^2 (\C^4)\otimes \Gamma(\Hat{D}, K^{1/2}_{\Hat{D}}) \to E(1|6)_1 \to \wedge^2 (\C^4) \otimes \Gamma(\Hat{D}, K^{-1/2}_{\Hat{D}}) \to 0 
+\]
+where $K^{\pm 1/2}_{\Hat{D}}$ are positive and negative square roots of the canonical bundle on $\Hat{D}$.
+
+To characterize this super Lie algebra we must define the following brackets.
 \begin{itemize}
-\item The even part of $E(1|6)_0$ given by the semidirect product Lie algebra $\Gamma (\hat D, T) \ltimes \left( \Gamma (\hat D, \mc O) \otimes \mf{sl}(4) \right )$
-\item The odd part $E(1|6)_1$ is given by the (unique) nontrivial extension of $E(1|6)_0$-modules 
-\[0\to \Sym^2 (\C^4)\otimes K^{1/2}_\C \to E(1|6)_1 \to \wedge^2 (\C^4) \otimes K^{-1/2}_\C \to 0.\]
+\item Given elements $A \otimes f \d z^{1/2}\in \Sym^2 (\C^4)\otimes K^{1/2}_\C$ and $B\otimes g \del_z^{1/2}\in \wedge^2 (\C^4)\otimes K^{-1/2}_\C$, we have that
+\[
+[A \otimes f \d z^{1/2}, B\otimes g \del_z^{1/2}] = A \star B \otimes fg \in \mf{sl}(4)\otimes \mc O.
+\]
+Here, $\star$ refers to the hodge star of $B$ and we are viewing $A$ and $*B$ as symmetric and skew-symmetric $4\times 4$ matrices respectively; their product is traceless.
 
-\end{itemize}
-The only remaining bracket to be specified, the odd bracket, is given as follows.
-\begin{itemize}
-\item Given sections $A \otimes f \d z^{1/2}\in \Sym^2 (\C^4)\otimes K^{1/2}_\C$ and $B\otimes g \del_z^{1/2}\in \wedge^2 (\C^4)\otimes K^{-1/2}_\C$, we have that
-\[
-[A \otimes f \d z^{1/2}, B\otimes g \del_z^{1/2}] = A*B \otimes fg \in \mf{sl}(4)\otimes \mc O.
-\]
-Here, $*$ refers to the hodge star of $B$ and we are viewing $A$ and $*B$ as symmetric and skew-symmetric $4\times 4$ matrices respectively; their product is traceless.
-
-\item Given sections $A \otimes f \del_z^{1/2}, B\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have that 
+\item The final nontrivial bracket is more complicated. 
+Given elements $A \otimes f \del_z^{1/2}, B\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have that 
 \begin{align*}
-[A\otimes f \d z^{-1/2} , B \otimes g \d z^{-1/2} ] & = \tr (A * B) \otimes fg \del_z + \frac12 (A*B)_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
+[A\otimes f \d z^{-1/2} , B \otimes g \d z^{-1/2} ] & = \tr (A \star B) \otimes fg \del_z \\ & + \frac12 (A*B)_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
 & \in \Gamma (\hat D, T) \ltimes \left (\mf {sl}(4) \otimes \Gamma (\hat D, \mc O) \right ) .
 \end{align*}
-where again $*$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
+where again $\star$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
 \end{itemize}
-\end{defn}
 
-The relationship between this super-Lie algebra and our decomposition is established through the following result.
+The relationship between this super Lie algebra and our decomposition is established through the following result.
+
+\brian{Need to be careful about holomorphic versus formal disks in this proposition.}
+
+\brian{Did we define what $\mc F (0)$ means?}
+
+\brian{I'm confused by the appearance of compact support.}
+
+\brian{I would have said that the jets at 0 of $\cF^{(0)}$ is quasi-isomorphic to $E(1|6)$.}
 
 \begin{prop}
-There is an equivalence of super-Lie algebras
+There is a quasi-isomorphism of super Lie algebras
 \[
-\mc F^{(0)}_{\R\times \C, c}  (0) \cong E(1|6).
+\mc F^{(0)}_{\R\times \C, c}  (0) \simeq E(1|6).
 \]
@@
 
-To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4\times S^7} )$ is in fact given by the same formulae as the brackets on $E(1|6)$ in equation \ref{defn:e(1|6)}, it will be useful to provide an explicit quasi-isomorphism $\Psi^{(0)} : \mc E(1|6) \to \mc F^{(0)}_{\R\times \C}$.
+To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} )$ is in fact given by the same formulae as the brackets on $E(1|6)$ in equation \ref{defn:e(1|6)}, it will be useful to provide an explicit quasi-isomorphism $\Psi^{(0)} : \mc E(1|6) \to \mc F^{(0)}_{\R\times \C}$.
 On an open set $I\times D\subset \R\times \C$, this is defined as follows
@@
 \begin{rmk}
-We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4\times S^7} )$ over every open set containing the origin.
+We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4} )$ over every open set containing the origin.
 The image of the map lands exactly in the step $\mc F^{(0)}_{\R\times \C}$ of the decomposition from proposition \ref{prop:ads4decomp}.
@@
 \subsection{Characters of $E(1|6)$-modules}
-Note that the decomposition of the state space $\Sym (\mc H_{AdS_4\times S^7} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{}
 
-\[\chi \left (\Sym (\mc H_{AdS_4\times S^7} ) \right )= \prod_{j\geq -2} \chi \left ( \mc U (\mc F^{(j)} _{\R\times \C} )(0)\right ).\]
+Note that the decomposition of the state space $\Sym (\mc H_{AdS_4} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{??}
+
+\brian{which proposition?}
+
+\brian{Might be useful to point out that a systematic characterization of irreps of $E(1|6)$ is incomplete.}
+
+\brian{But, we expect the modules appearing above to be irreducible.}
+
+\[\chi \left (\Sym (\mc H_{AdS_4} ) \right )= \prod_{j\geq -2} \chi \left ( \mc U (\mc F^{(j)} _{\R\times \C} )(0)\right ).\]
 
@@
 \parsec[]
-As a consequence, of the above we have that $f_{AdS_4\times S^7} (t_i, q) = \sum_{j\geq -2} f_j (t_i, q)$, or explicitly:
+As a consequence, of the above we have that $f_{AdS_4} (t_i, q) = \sum_{j\geq -2} f_j (t_i, q)$, or explicitly:
 \begin{align*}
@@
 In \cite[Eq.
-(2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4\times S^7}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}.
+(2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}.
 Comparison with the above expansion suggests the following conjecture
@@
 \end{rmk}
+
+\end{document}

### 2023-05-25 graviton spectra/content/e16.tex
support conditions

@@
 
+\surya{i thought the BLG theory has a quartic superpotential.}
+
 \brian{The thing we don't mention so much is the BV structure.}
@@
 
-\brian{Did we define what $\mc F (0)$ means?}
-
-\brian{I'm confused by the appearance of compact support.}
-
-\brian{I would have said that the jets at 0 of $\cF^{(0)}$ is quasi-isomorphic to $E(1|6)$.}
-
 \begin{prop}
@@
 \[
-\mc F^{(0)}_{\R\times \C, c}  (0) \simeq E(1|6).
+J^\infty_0\mc F^{(0)}_{\R\times \C} \simeq E(1|6).
 \]
 \end{prop}
+where the left hand side denotes the $\infty$-jets at $0\in \R\times \C$ of the local super-Lie algebra $\mc F^{(0)}_{\R\times \C}$. 
 \begin{proof}
@@
 \ul{even} & \ul{odd} \\
-\C[w_a\del_{w_b}]\otimes \mc O\ar[r, "\del^W_\Omega"]  & \mc O \\ 
+\C\{w_a\del_{w_b}\}\otimes \mc O\ar[r, "\del^W_\Omega"]  & \mc O \\ 
 \T \ar[ur] & \\
-\Sym^2 (\C^4)\ar[r, "\del_W"]\ar[dr] & \C[w_adw_b] \otimes K^{-1/2}\ \\
+\Sym^2 (\C^4)\ar[r, "\del_W"]\ar[dr] & \C\{w_a\d w_b\} \otimes K^{-1/2}\ \\
 & \Sym^2 (\C^4)\otimes \Omega^1\otimes K^{-1/2}
@@
 It is easy to see that $\Psi^{(0)}$ is a quasi-isomorphism and a straightforward if lengthy check confirms that it preserves Lie brackets.
-The result then follows from computing the limit of $\mc E(1|6)_c (I\times D)$ over open sets containing the origin.
+The result then follows from computing the limit of $\mc E(1|6)(I\times D)$ over open sets containing the origin.
 \end{proof}
@@
 
-Note that the decomposition of the state space $\Sym (\mc H_{AdS_4} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{??}
-
-\brian{which proposition?}
+Note that the decomposition of the state space $\Sym (\mc H_{AdS_4} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{prop:ads4index}
 

### 2023-05-25 graviton spectra/content/e36.tex
support conditions

@@
 \[
-\mc G^{(0)}_{\C^3, c} (0) \cong E(3|6)
+J^\infty_0\mc G^{(0)}_{\C^3} \cong E(3|6)
 \]
 \end{prop}
+where the left-hand side denotes the $\infty$-jets at zero of the local $L_\infty$ algebra $\mc G^{(0)}_{\C^3}$. 
 \begin{proof}
@@
 
-The result then follows from computing the limit of $\mc E(3|6)_c (D^3)$ over open sets containing the origin.
+The result then follows from computing the limit of $\mc E(3|6) (D^3)$ over open sets containing the origin.
 \end{proof}
@@
 \begin{itemize} 
-\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
-\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
+\item the coordinate $z_i$ has weight zero. 
+\item the coordinate $w_a$ has weight $+1$.
 \item the parity of an element carries an additional weight of $-1$. 
@@
 As such, each $U_j$ is an $E(3|6)$-module; Kac characterizes these modules explicitly and identifies them as certain irreducible $E(3|6)$-modules.
-In the notation of \cite{KR2} we have that $U_{-1} = I(0,0;1;-1)^*$ and for $j\geq 1$, $U_j = I(0,0;j-1;j+1)^*$.
+In the notation of \cite{KR2} we have that $\tilde U_{-1} = I(0,0;1;-1)^*$ and for $j\geq 1$, $U_j = I(0,0;j-1;j+1)^*$.
 
-The decomposition of $\mc H_{AdS_7\times S^4}$ afforded by proposition \ref{prop:ads7decomp} induces a weight grading of $\widehat{E(5|10)}$ which extends the one on $E(5|10)$ that we have just described by declaring that the central term have weight $-1$.
+The decomposition of the local $L_\infty$-algebra $\Omega^{0,\bullet}_{\C^3}(\mc L^{r=0}_{AdS_7} )$ afforded by proposition \ref{prop:ads7decomp} induces a weight grading of $\widehat{E(5|10)}$ which extends the one on $E(5|10)$ that we have just described by declaring that the central term have weight $-1$.
 In this way, we get a related decomposition of super $L_\infty$ algebras
@@
 were $U_{-1}$ is a $\C$-extension of $\tilde U_{-1}$ defined in the decomposition \eqref{eqn:decomp1} and for $j \geq 0$ the $U_j$'s are the same as in the non centrally extended case.
-As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible.
+As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible \surya{is this last sentence actually true?
+these aren't the same modules}
 

### 2023-05-25 graviton spectra/main.tex
merge

@@
 
-Having described our eleven-dimensional model on flat spacetimes, we now pursue descriptions on maximally symmetric spacetimes.
-We begin by describing twisted versions of the $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds.
-In eleven-dimensional supergravity, these backgrounds arise as near-horizon limits of the backgrounds sourced by some number of M2 and M5 branes in flat space respectively.
-In the first section of this chapter \ref{sec:ads}, we describe an analogous procedure natively in our twisted context.
+In \cite{CLsugra}, Costello and Li gave a rigorous definition of what it means to {\em twist} a theory of supergravity, which is nicely compatible with the mathematically more familiar notion of twisting supersymmetric gauge theories \cite{WittenTwist}.
+In physical terms, twisted supergravity is supergravity in a background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge.
+In principle, one can take the supercharge to be any square-zero covariantly constant spinor (so it satisfies the equations of motion of supergravity).
+A class of such supercharges lie in the supersymmetry algebra, which is of the sort that we will focus on in this paper.
 
-To do so, we motivate ansatz for the leading order couplings of our eleven-dimensional model to M2 and M5 branes.
-These couplings determine certain curved deformations of the $L_\infty$-algebra underlying our model - we conjecture that deforming the theory in the complement of the brane by a solution to the resulting curved Maurer-Cartan equation is perturbatively equivalent to the twist of the theory on $AdS_4\times S^7$ and $AdS_7\times S^4$.
+Following this procedure, we have given a proposal for the twists of eleven-dimensional supergravity on flat space in \cite{RSW,SWspinor}.
+See also \cite{EHsugra} for details on the further topological, non-minimal, twist.
+The model is akin to models of ten-dimensional twisted supergravity in terms of a certain part of topological string theory proposed in \cite{CLsugra} and further pursued in \cite{CLtypeI,CLbcov,CPkoszul} which generalizes the use of Kodaira--Spencer theory of Calabi--Yau manifolds in the ordinary $B$-model on Calabi--Yau threefolds \cite{bcov}.
+The goal of this paper is to give a descriptions of the minimally twisted model of eleven-dimensional supergravity placed on maximally symmetric spacetimes; thus providing further evidence for our model as a twist of supergravity.
+Insomuch, we produce definitions of twisted versions of the $AdS_4\times S^7$ and $AdS_7\times S^4$ spacetimes.
 
-The next two sections provide evidence for this conjecture.
-We begin in section \ref{sec:states} with numerical checks.
+In supergravity, these backgrounds arise as near-horizon limits of the backgrounds sourced by some number of M2 and M5 branes in flat space respectively. 
+To follow an analogous procedure natively in our twisted context we introduce leading order couplings of our eleven-dimensional model to twisted M2 and M5 branes. 
+These couplings determine explicit deformations of formal moduli problem described by our twisted model on complement of the brane in flat spacetime.
+Perturbatively, the undeformed formal moduli space can be captured by the data of an $L_\infty$ algebra; we conjecture that deforming the theory in the complement of the brane by a solution to the resulting curved Maurer-Cartan equation is perturbatively equivalent to the twist of the theory on $AdS_4\times S^7$ and $AdS_7\times S^4$.
+
 We give definitions of supergravity states in our twisted $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds, which can be thought of as particular field configurations that are localized at points on the conformal boundary of $AdS$.
-We compute characters of the proposed state spaces and find exact matches with counts of gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively.
+We compute graded characters of the proposed state spaces and find exact matches with counts of gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively.
+
+One of the insights of \cite{SWchar} was that supersymmetric indices count exactly local operators in the minimal twist---accordingly, we may think of the space of local operators in the minimal twist as categorifying the index.
+Of course, combining observables also endows local operators with an algebraic structure.
+In the approach to quantum field theory developed by Costello and Gwilliam \cite{fact2} that we follow here, the local operators quantum field theory are endowed with the structure of a factorization algebra.
+Therefore, an appealing aspect of our approach is that the space of supergravity states is obtained as the value of a factorization algebra on a small open disk.
+A complete characterization of this factorization algebra would follow, in principle, from the twisted holography proposal of by Costello, Gaiotto, Li, and Paquette in \cite{CLsugra,CGhol,CPkoszul} which is a highly structured avatar of the AdS/CFT correspondence that is expected to hold at the level of supersymmetric twists.
+We do not pursue that proposal in our context here.
 
@@
 
-With these pieces of evidence in hand, in sections \ref{sec:e16}, \ref{sec:e36},  we then turn to study some representation theoretic aspects of the state spaces constructed in section \ref{sec:states}.
-We identify certain $\C^\times$ actions on our eleven-dimensional model that combine rescalings in directions normal to branes with a certain rescaling of the space of fields - this induces a decomposition of the space of fields that we dub the \textit{graviton decomposition}.
+With these pieces of evidence in hand, in sections \ref{sec:e16}, \ref{sec:e36},  we then turn to study some representation theoretic aspects of the state spaces constructed in section~\ref{sec:states}.
+We identify certain $\C^\times$ actions on our eleven-dimensional model that combine rescalings in directions normal to branes withoh a certain rescaling of the space of fields---this induces a decomposition of the space of fields that we dub the \textit{graviton decomposition}.
 The weight $0$ parts of these decompositions are certain local $L_\infty$-algebras whose costalks recover the linearly compact super-Lie algebras $E(1|6)$ and $E(3|6)$.
@@
 %Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values.
-Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.
+Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at
 

### 2023-05-26 graviton spectra/content/br.tex
merge

@@
 
-\newcommand\til{\widetilde}
 \begin{document} 
@@
 \subsection{Twisted supergravity}
-
-In \cite{CLsugra}, Costello and Li gave a rigorous definition of what it means to {\em twist} supergravity, which is nicely compatible with the mathematically more familiar notion of twisting supersymmetric gauge theories \cite{WittenTwist}.
-In physical terms, twisted supergravity is supergravity in a background where a bosonic ghost for supersymmetry takes a nonzero value $Q$, where $Q$ is a nilpotent supercharge.
-In principle, one can take the supercharge to be any square-zero covariantly constant spinor (so it satisfies the equations of motion of supergravity).
-A class of such supercharges lie in the supersymmetry algebra.
 
@@
 \[
-\R \times \operatorname{Tot}(K_{\C^3}^{1/2}\otimes \C^2 \to X)
+\R \times \operatorname{Tot}(K_{X}^{1/2}\otimes \C^2 \to X)
 \]

### 2023-05-26 graviton spectra/content/suco.tex
merge

@@
+\documentclass[../main.tex]{subfiles}
+
+\begin{document}
+
 \section{Twisted global symmetries}
@@
 
-In this section we provide evidence for conjectures \ref{conj:ads4}\ref{conj:ads7} by arguing that the global sections of the local moduli problems $p_*\mc E_{AdS_4\times S^7}$ and $p_* \mc E_{AdS_7\times S^4}$ carry actions by the minimal twists of the relevant superconformal algebras.
+In this section we provide evidence for conjectures \ref{conj:ads4} and \ref{conj:ads7} by arguing that the global sections of the local moduli problems $p_*\mc E_{AdS_4}$ and $p_* \mc E_{AdS_7}$ carry actions by the minimal twists of the relevant superconformal algebras.
 We will find that the twist of the superconformal algebra is the same in each case, but the actions are slightly different.
@@
 
-The complex form of the algebra of isometries for supergravity in both the ${\mr AdS}_4$ and ${\mr AdS}_7$ backgrounds is $\mf{osp}(8|4)$ (though, their real forms differ). 
+The complex form of the algebra of isometries for supergravity in both the ${\mr AdS}_4 \times S^7$ and ${\mr AdS}_7 \times S^4$ backgrounds is $\mf{osp}(8|4)$ (though, their real forms differ). 
 This agrees with the complex form of the 6d $\mc{N}=(2,0)$ superconformal algebra and the 3d $\mc{N}=8$ superconformal algebra.
@@
 
-The following is a mild rephrasing of a result in \cite{SWsuco2} where twisted superconformal symmetry in six dimensions is studied in some detail. 
-\begin{thm}[Saberi-Williams]
-There is a map of super-Lie algebras $\phi: \mf {siso}_{11d} \to \mf {osp}(8|4)$.
-Letting $Q\in \mf{siso}_{11d}$ be the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, there is an equivalence of dg super-Lie algebras \[\left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
-\end{thm}
+%The following is a mild rephrasing of a result in \cite{SWsuco2} where twisted superconformal symmetry in six dimensions is studied in some detail.
+There is a map of super Lie algebras $\phi: \mf {siso}_{11d} \to \mf {osp}(8|4)$. 
+Further, it is observed in \cite{SWsuco2} that if $Q\in \mf{siso}_{11d}$ is the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, then there is an equivalence of dg super-Lie algebras \[\left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
 
@@
 
-To provide further evidence for conjecture \ref{conj:ads4} we wish to articulate a sense in which $\mf{osp}(6|2)$ is witnessed as a symmetry of $\mc E^N_{AdS_4\times S^7}$.
+To provide further evidence for conjecture \ref{conj:ads4} we wish to articulate a sense in which $\mf{osp}(6|2)$ is witnessed as a symmetry of $\mc E^N_{AdS_4}$.
 To this end, we will provide evidence for the claim that there is a Lie map
-\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ).\]
+\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ).\]
 
@@
 & H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
-\mf{osp}(6|2)\ar[ur, "i_{M2}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )
+\mf{osp}(6|2)\ar[ur, "i_{M2}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )
 \end{tikzcd}
@@
 It is clear that the image of the chain-level map $i_{M2}$ defined above is closed for the linearized BRST differential $\delta^{(1)}$ so descends to a map $i_{M2}: \mf{osp}(6|2) \to H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }$ as claimed.
-As such, the composition $\mr{res}\circ i_{M2}$ defines an inner action of $\mf{osp}(6|2)$ on the cohomology of global sections $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$.
+As such, the composition $\mr{res}\circ i_{M2}$ defines an inner action of $\mf{osp}(6|2)$ on the cohomology of global sections
+\beqn
+H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ) .
+\eeqn
 
@@
 Next, we turn on $N \ne 0$ units of nontrivial flux.
-Note that not all fields in the image of the map $\mr{res}\circ i_{M2}$ commute with bracketing with the flux $N F_{M2}$, and as such are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ on $\Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right )$.
+Note that not all fields in the image of the map $\mr{res}\circ i_{M2}$ commute with bracketing with the flux $N F_{M2}$, and as such are not compatible with the total differential $\delta^{(1)} + [N F_{M2}, -]$ on $\Pi \mc E^N_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right )$.
 Nevertheless, we have the following:
@@
 Furthermore, these order $N$ corrections define an embedding of 
-\[\mf{osp}(6|2) \to H^\bullet \left ( \Pi \mc E^N_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ) .\]
+\[\mf{osp}(6|2) \to H^\bullet \left ( \Pi \mc E^N_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ) .\]
 \end{prop}
@@
 \begin{proof}
-For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $(\R\times \C) \times (\C^4\setminus \{0\} )$ given by $\Pi\mc E^N_{AdS_4\times S^7}$ and set $F = F_{M2}$.
+For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $(\R\times \C) \times (\C^4\setminus \{0\} )$ given by $\Pi\mc E^N_{AdS_4}$ and set $F = F_{M2}$.
 We will show that the image of the map $\mr{res}\circ i_{M2}$ survives to the last page of a spectral sequence that abuts to the target of the above map.
@@
 
-The first page of the spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$.
+The first page of the spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$.
 It will be useful to compute this page explicitly.
@@
 The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is thus given by the cohomology of the global symmetry algebra on $\C^5 \times \R$, which we computed in \S \ref{sec:global}, plus the cohomology of the above complex with respect to the dotted-line operators.
-Indeed, this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4\times S^7} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$
+Indeed, this is exactly $H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )$
 
@@
 We comment on an alternate method to compute the first page of the auxiliary spectral sequence we used to compute the first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [NF, - ]$.
-We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_4\times S^7}$ from section \ref{prop:ads7push}.
+We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_4}$ from section \ref{prop:ads7push}.
 In this case, this Serre-type spectral sequence degenerates at the $E_2$-page.
@@
 
-\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right ).\]
+\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_7} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right ).\]
 
@@
 & H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
-\mf{osp}(6|2)\ar[ur, "i_{M5}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right )
+\mf{osp}(6|2)\ar[ur, "i_{M5}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_7} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right )
 \end{tikzcd}
@@
 It is again clear that the image of the chain-level map $i_{M5}$ defined above is closed for the linearized BRST differential $\delta^{(1)}$ on $\Pi \mc E$ so descends to a map $i_{M5} : \mf{osp}(6|2) \to H^\bullet (\Pi \mc E (\R\times \C^5))\cong \widehat{E (5|10)}$ as claimed.
-As such, the composition $\mr{res}\circ i_{M5}$ will define an inner action of $\mf{osp}(6|2)$ on the cohomology of the global sections $H^\bullet \left ( \Pi \mc E^{0}_{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
+As such, the composition $\mr{res}\circ i_{M5}$ will define an inner action of $\mf{osp}(6|2)$ on the cohomology of the global sections $H^\bullet \left ( \Pi \mc E^{0}_{AdS_7} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
 
@@
 Next, we turn on $N \ne 0$  units of nontrivial flux.
-Again, not all fields in the image of the map $\mr{res}\circ i_{M5}$ are compatible with the total differential $\delta^{(1)} + [N F, -]$ on $\Pi \mc E^{N}_{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )$.
+Again, not all fields in the image of the map $\mr{res}\circ i_{M5}$ are compatible with the total differential $\delta^{(1)} + [N F, -]$ on $\Pi \mc E^{N}_{AdS_7} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )$.
 Nevertheless, we have the following version of proposition \ref{prop:brads4}
@@
 
-\[ H^\bullet \left ( \Pi \mc E^N_{AdS_7\times S^4} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right). \]
+\[ H^\bullet \left ( \Pi \mc E^N_{AdS_7} \left ( \C^3 \times (\R\times \C^2)\setminus 0 \right ) \right). \]
 
@@
 We proceed exactly analogously to the proof of proposition \ref{prop:brads4}.
-For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $\C^3\times (\R\times \C^2)\setminus 0$ given by $\Pi\mc E^N_{AdS_7\times S^4}$ and set $F = F_{M5}$.
+For notational convenience, we will let $\mc L$ denote the local $L_\infty$ algebra on  $\C^3\times (\R\times \C^2)\setminus 0$ given by $\Pi\mc E^N_{AdS_7}$ and set $F = F_{M5}$.
 We will show that the image of the map $\mr{res}\circ i_{M5}$ survives to the last page of a spectral sequence that abuts to the target of the above map.
@@
 
-The first page of this spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0 _{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
+The first page of this spectral sequence is the cohomology with respect to the original linearized BRST differential $\delta^{(1)}$; this is exactly $H^\bullet \left ( \Pi \mc E^0 _{AdS_7} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
 It will be useful to compute this page explicitly.
@@
 The first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [N F, -]$ is given by the cohomology of the global symmetry algebra on $\C^5 \times \R$, which we computed in \S \ref{sec:global}, plus the cohomology with respect to the dotted-line operators in~\eqref{eqn:ads7ss2}.
-This is indeed the cohomology of global sections $H^\bullet \left ( \Pi \mc E^0 _{AdS_7\times S^4} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
+This is indeed the cohomology of global sections $H^\bullet \left ( \Pi \mc E^0 _{AdS_7} \left ( \C^3\times (\R\times \C^2)\setminus 0\right )\right )$.
 
@@
 \[
-\C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\del_{z_i}\} \subset H^0(\C^3, \T) \otimes H^2 \big(\Omega^\bullet(\C^2 \times \R \setminus 0) / (\d w_1 , \d w_2) \big) .
+\C[w_1^{-1}, w_2^{-1}][z_1,z_2,z_3] \{\del_{z_i}\} \subset \text{Vect}(\C^3) \otimes H^2 \big(\Omega^\bullet(\C^2 \times \R \setminus 0) / (\d w_1 , \d w_2) \big) .
 \]
@@
 As in remark \ref{rmk:altss} comment on an alternate method to compute the first page of the auxiliary spectral sequence we used to compute the first page of the spectral sequence converging to the cohomology with respect to $\delta^{(1)} + [NF, - ]$.
-We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_7\times S^4}$ from section \ref{prop:ads7push}.
+We could have used a Serre-type spectral sequence for certain kinds of sheaves on THF manifolds \cite{KamberTondeur}, \cite{KormanThesis}, applied to the pushforward $ p_* \Pi \mc E^N_{AdS_7}$ from section \ref{prop:ads7push}.
 In this case, this Serre-type spectral sequence degenerates at the $E_2$-page.

### 2023-05-30 graviton spectra/content/e16.tex
merge
e16

@@
 We define a decomposition of the space of states $\mc H_{AdS_4}$.
-It is induced by a decomposition of the boundary fields $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{{r=0}}_{AdS_4} )$ introduced in section \ref{sec:transversebc}  arising from a $\C^\times$ action which mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
+It is induced by a decomposition of the boundary fields $\cA^\bu_{M} (\mc L^{{r=0}}_{AdS_4} )$ introduced in section \ref{sec:transversebc}  arising from a $\C^\times$ action which mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
+We first consider a general three-manifold $M$ equipped with a THF; we specialize to $M = \R \times \C$ shortly.
 
-Explicitly, the action is given as follows 
+Define the $\C^*$-action on holomorphic sections of $\cL_{AdS_4}^{r=0}$:
 \begin{itemize}
-\item On the fields 
+\item On the sections 
 \[
-\mu(t; w_a,z) \in \C[w_1, \cdots, w_4]\{\del_{w_a}\} \otimes \Omega^\bullet_\R(I) \otimes \Omega^{0,\bullet}_{\C} (U) \oplus \C[w_1, \cdots, w_4]\otimes \Omega^\bullet_\R(I)\otimes \Omega^{0,\bullet}_{\C}(U, T)\]
+\mu(w_a,z) \in \C[w_1, \cdots, w_4]\{\del_{w_a}\} \otimes \cO_M \oplus \C[w_1, \cdots, w_4]\otimes T_M \] 
 the action is
 \[
-\lambda \cdot \mu(t; w_a,z) = \mu(t; \lambda w_a , z).
+\lambda \cdot \mu(w_a,z) = \mu(\lambda w_a , z).
 \]
-\item On the fields $\nu(t; w_a,z) \in \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes \Omega^{0,\bullet}_{\C}(U)$ the action is
+\item On the fields $\nu(w_a,z) \in \C[w_1, \cdots, w_4] \otimes \cO_M$ the action is
 \[
-\lambda \cdot \nu(t; w_a,z) = \nu(t; \lambda w , z).
+\lambda \cdot \nu(w_a,z) = \nu(\lambda w , z).
 \]
-\item On the fields $\beta(t; w_a,z) \in  \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes \Omega^{0,\bullet}_{\C}(U)$ the action is
+\item On the fields $\beta(w_a,z) \in  \C[w_1, \cdots, w_4] \otimes \cO_M$ the action is
 \[
-\lambda \cdot \beta(t; w_a,z) = \lambda^{-2} \beta(t; \lambda w_a , z).
+\lambda \cdot \beta(w_a,z) = \lambda^{-2} \beta(\lambda w_a , z).
 \]
@@
 \[
-\gamma(t; w_a,z) \in  \C[w_1, \cdots, w_4] \{\d w_a\} \otimes \Omega^{\bullet}_\R(I) \otimes\Omega^{0,\bullet}_{\C} (U) \oplus  \C[w_1, \cdots, w_4] \otimes \Omega^{\bullet}_\R(I) \otimes\Omega^{0,\bullet}_{\C}(U, \Omega^1)
+\gamma(w_a,z) \in  \C[w_1, \cdots, w_4] \{\d w_a\} \otimes \cO_M \oplus  \C[w_1, \cdots, w_4] \otimes \Omega^1_M
 \] 
@@
 \[
-\lambda \cdot \gamma(t; w_a,z) = \lambda^{-2} \gamma(t; \lambda w _a, z).
+\lambda \cdot \gamma(w_a,z) = \lambda^{-2} \gamma(\lambda w _a, z).
 \]
@@
 
-The following result is straightforward.
+This $\C^*$-action on holomorphic sections extends to an action on the de Rham--Dolbeault complex $\cA^\bu_M(\cL_{AdS_7}^{r=0})$ in such a way that preserves the de Rham--Dolbeault operator.
+In fact, this $\C^*$-action preserves the full local $L_\infty$ structure present on the parity shift of this complex of vector bundles.
 
 \begin{prop}\label{prop:ads4decomp}
-The $L_\infty$ structure on $\Pi\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} )$ identified in section \ref{sec:transversebc} is equivariant for this $\C^\times$ action.
+The $L_\infty$ structure on $\Pi \cA_M^\bu(\mc L^{r=0}_{AdS_4} )$ identified in section \ref{sec:transversebc} is equivariant for this $\C^\times$ action.
 \end{prop}
@@
 \[
-\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} ) = \prod _{n\geq -2} \mc F^{(n)}_{\R\times \C}
+ \cA_M^\bu(\mc L^{r=0}_{AdS_4} ) = \prod _{n\geq -2} \mc F^{(n)}_{M}
 \]
-
-where for each open set $I\times U\subset\R\times \C$, we have that \[\mc F_{\R\times \C}^{(n)} (I\times U) \subset \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C (U, \mc L^{r=0}_{AdS_4} )\] is the weight $n$ eigenspace with respect to the above $\C^\times$ action.
-In particular, we see that $\mc F^{(0)}_{\R\times \C}$ is itself a local dg Lie algebra, for which  every $\mc F^{(n)}_{\R\times \C}$ is a module.
+\brian{gradings again}
+where $\cF^{(n)}_M \subset \cA_M^\bu(\mc L^{r=0}_{AdS_4} )$ is the weight $n$ eigenspace with respect to the above $\C^\times$ action thought of as a complex of super vector bundles on $M$. 
+In particular, we see that $\mc F^{(0)}_{M}$ is itself a local dg Lie algebra, for which  every $\mc F^{(n)}_{M}$ is a module.
 
@@
 \begin{lem}
-There is an isomorphism of elliptic complexes \[\mc F^{(-2)}_{\R\times \C} \simeq \Omega^\bullet_{\R\times \C}.\]
+There is an isomorphism of elliptic complexes \[\mc F^{(-2)}_{M} \simeq \Omega^\bullet_{M}.\]
 \end{lem}
@@
 The only sections which contribute are those of type $\beta$ or $\gamma$ with no form components along the fiber directions.
-Therefore, we see directly that \[\mc F^{(-2)}_{\R\times \C} \simeq \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C ( \mc O \xrightarrow{\del} \Omega^1 ).\]
+Therefore, we see directly that \[\mc F^{(-2)}_{M} \simeq \cA^\bu_M \xrightarrow{\del} \cA^\bu_M(\Omega^1) = \Omega^\bu_M.\]
 \end{proof}
@@
 There is an isomorphism of elliptic complexes 
-\[ \mc F^{(-1)}_{\R\times \C} \cong \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
+\[ \mc F^{(-1)}_{M} \cong \cA^\bu_M \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
 \end{lem}
 \begin{proof}
-On an open set of the form $I\times U$, the sections of the specified weight are:
+The sections of this specified weight are:
 \begin{itemize}
-\item fields of type $\mu$ of the form $\mu_a(t; z) \del_{w_a}$. As the $w_a$ are fiber coordinates on $K^{1/4}_\C$, these fields transform as sections of $K^{1/4}_\C$.
-\item fields of type $\gamma$ of the form $\gamma_a(t;z) \d w_a$. These fields transform as sections of $K^{3/4}_\C$. 
+\item sections of type $\mu$ of the form $\mu_a(z) \del_{w_a}$. 
+As the $w_a$ are fiber coordinates on $K^{1/4}$, these fields transform as sections of $K^{1/4}_\C$.
+\item sections of type $\gamma$ of the form $\gamma_a(z) \d w_a$. 
+These fields transform as sections of $K^{3/4}$. 
 \end{itemize}
@@
 \subsection{The zero-th piece: A local version of $E(1|6)$}
-\parsec[] The next nontrivial case is the weight ${(0)}$ piece.
-This factor is special because it carries the induced structure of a local $L_\infty$ algebra on $\R\times \C$.
-We will prove that it is equivalent to a local Lie algebra version of the exceptional super-Lie algebra $E(1|6)$.
+\parsec[] The next nontrivial case is the weight zero piece $\cF^{(0)}_M$. 
+This factor is special because it carries the induced structure of a local $L_\infty$ algebra on $M$. 
+We will prove that it is equivalent to a local Lie algebra version of the exceptional super Lie algebra $E(1|6)$.
 
@@
 \item The final nontrivial bracket is more complicated. 
-Given elements $A \otimes f \del_z^{1/2}, B\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have that 
+Given elements $B \otimes f \del_z^{1/2}, B'\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have
 \begin{align*}
-[A\otimes f \d z^{-1/2} , B \otimes g \d z^{-1/2} ] & = \tr (A \star B) \otimes fg \del_z \\ & + \frac12 (A*B)_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
+[B\otimes f \d z^{-1/2} , B' \otimes g \d z^{-1/2} ] & = \tr (B \star B') \otimes fg \del_z \\ & + \frac12 (B \star B')_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
 & \in \Gamma (\hat D, T) \ltimes \left (\mf {sl}(4) \otimes \Gamma (\hat D, \mc O) \right ) .
@@
 where again $\star$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
+\brian{simplify last line so it is obviously a vector field}
+
+\brian{Choose $\d z^{-1/2}$ or $\del_z^{1/2}$}
 \end{itemize}
@@
 
-\brian{Need to be careful about holomorphic versus formal disks in this proposition.}
-
 \begin{prop}
+Consider the case $M = \R \times \C$.
 There is a quasi-isomorphism of super Lie algebras
@@
 \]
+where the left hand side denotes the $\infty$-jets at $0\in \R\times \C$ of the local super-Lie algebra $\mc F^{(0)}_{\R\times \C}$. 
 \end{prop}
-where the left hand side denotes the $\infty$-jets at $0\in \R\times \C$ of the local super-Lie algebra $\mc F^{(0)}_{\R\times \C}$. 
 \begin{proof}
-We will begin by trying to characterize the local $L_\infty$-algebra $\mc F^{(0)}_{\R\times \C}$. We claim that it is quasi-isomorphic to a local version of $E(1|6)$.
+We will characterize the local $L_\infty$-algebra $\mc F^{(0)}_{M}$ for general $M$. 
+We will show that it is quasi-isomorphic to a local version of $E(1|6)$ where sections over the formal disk can be upgraded to sections over any open set in the THF manifold $M$.
 
-Indeed, it is easy to see that the weight zero sections consists of the following cochain complex 
+The underlying complex of vector bundles $\mc F^{(0)}_{M}$ is the de Rham--Dolbeault complex of the complex of bundles 
 \begin{equation}
-\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (
 \begin{tikzcd}
@@
 & \Sym^2 (\C^4)\otimes \Omega^1\otimes K^{-1/2}
-\end{tikzcd} \right)
+\end{tikzcd}
 \end{equation}
@@
 \begin{equation}
-\mc E(1|6) \define \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C \left (
+\mc E_M(1|6) \define \cA^\bu_M \left (
 \begin{tikzcd}
@@
 
-To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L^{r=0}_{AdS_4} )$ is in fact given by the same formulae as the brackets on $E(1|6)$ in equation \ref{defn:e(1|6)}, it will be useful to provide an explicit quasi-isomorphism $\Psi^{(0)} : \mc E(1|6) \to \mc F^{(0)}_{\R\times \C}$.
-On an open set $I\times D\subset \R\times \C$, this is defined as follows
+To see that the Lie structure induced from the $L_\infty$-structure on $\cA_M^\bu (\mc L^{r=0}_{AdS_4} )$ is in fact given by the same formulae as the brackets on $E(1|6)$ in equation \ref{defn:e(1|6)}, we provide an explicit quasi-isomorphism $\Psi^{(0)} \colon \mc E_M(1|6) \to \mc F^{(0)}_{M}$.
+This quasi-isomorphism arises from a map on holomorphic sections.
 
 \begin{itemize}
-\item Given a section $g(t; z) \del_z \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C (D, T)$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I \times D$, we define
+\item Given a section $\mu$ of $\T_M$ define
 \begin{align*}
-\Psi^{(0)} (g(t;z)\del_z) &= g(t;z)\del_z - \frac 14 (\del_z g(t; z)) w_a\del_{w_a} \\
-&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, T \oplus \C\{w_a\del _{w_b} \} \right )
+\Psi^{(0)} (\mu) &= \mu - \frac 14 (\del_\Omega \mu) w_a\del_{w_a} 
 \end{align*}
-\item Given a section $A_{ab} \otimes g(t; z) \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \mf{sl}(4)\otimes \mc O \right )$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I \times D$ and $A_{ab}\in \mf {sl}(4)$
+where we view the right hand side as a section of $\T \oplus \C\{w_a \del_{w_a}\} \otimes \cO$.
+\item Given a section $C = (C_{ab})$ of $\mf{sl}(4)\otimes \mc O$ define
+\[
+\Psi^{(0)} (C) = C_{ab}w_a\del_{w_b}
+\]
+which we view as a section of $\C\{w_a \del_{w_a}\} \otimes \cO$.
+\item Given a section $B = (B_{ab})$ of $\wedge^2 (\C^4) \otimes K^{-1/2}$ define
+\[
+\Psi^{(0)} (B) = B_{ab} w_a \d w_b .
+\]
+which we view as a section of $\C\{w_{[a} \d w_{b]}\} \otimes K^{-1/2} = \wedge^2 \C^4 \otimes K^{-1/2}$.
+\item Given a section 
+$A=(A_{ab})$ of $\Sym^2 (\C^4) \otimes K^{1/2}$ define
 \begin{align*}
-\Psi^{(0)} (A_{ab} \otimes g(t;z)) &= g(t;z)A_{ab}w_a\del_{w_b} \\
-&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \C\{w_a\del _{w_b}\} \right )
+\Psi^{(0)} (A_{ab}) = A_{ab} w_a w_b 
 \end{align*}
+which we view as a section of $\Sym^2 (\C^4) \otimes \Omega^1 \otimes K^{-1/2}$.
+\end{itemize}
+It is easy to see that $\Psi^{(0)}$ is a quasi-isomorphism and a straightforward if lengthy check confirms that it preserves brackets.
 
-\item Given a section $A_{ab} \otimes g(t; z)\d z^{-1/2} \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \wedge^2 (\C^4) \otimes K^{-1/2}\right )$
-where $g(t;z)$ is a mixed deRham-Dolbeault form on $I\times D$ and $A_{ab} \in \wedge^2 (\C^4)$ we define
-\begin{align*}
-\Psi^{(0)} (A_{ab} \otimes g(t; z)\d z^{-1/2}) &= g(t;z)  A_{ab} w_a \del_{w_b} \\
-&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \C\{w_a\del _{w_b} \}\otimes K^{-1/2} \right )
-\end{align*}
-
-\item Given a section 
-$A_{ab} \otimes g(t; z)\d z^{1/2} \in \Omega^\bullet_\R (I)\otimes \Omega^{0,\bullet}_\C \left (D, \Sym^2 (\C^4) \otimes K^{1/2}\right )$ where $g(t;z)$ is a mixed deRham-Dolbeault form on $I\times D$ and $A_{ab} \in \Sym^2 (\C^4)$ we define
-\begin{align*}
-\Psi^{(0)} (A_{ab} \otimes g(t; z)\d z^{1/2}) &= g(t;z)  A_{ab} w_a w_b \d z \\
-&\in \Omega^\bullet_\R (I) \otimes \Omega^{0,\bullet}_\C \left ( D, \Sym^2 (\C^4) \otimes \Omega^1 \otimes K^{-1/2} \right )
-\end{align*}
-\end{itemize}
-It is easy to see that $\Psi^{(0)}$ is a quasi-isomorphism and a straightforward if lengthy check confirms that it preserves Lie brackets.
-The result then follows from computing the limit of $\mc E(1|6)(I\times D)$ over open sets containing the origin.
+The result about $\infty$-jets at $0$ in affine space $M = \R \times \C$ follows immediately.
 \end{proof}
@@
 \begin{rmk}
-We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4} )$ over every open set containing the origin.
+We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\cA_{\R \times \C}^\bu (\mc L^{r=0}_{AdS_4} )$ over every open set containing the origin.
 The image of the map lands exactly in the step $\mc F^{(0)}_{\R\times \C}$ of the decomposition from proposition \ref{prop:ads4decomp}. 

### 2023-05-30 graviton spectra/content/index.tex
support conditions
e16

@@
 We denote by $K$ the holomorphic canonical bundle of $M$ which has a local frame given by $\d z$.
-The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we will do momentarily.
+The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we do throughout this section.
 
@@
 Following the above prescription, we consider the $S^7$ bundle 
-\[
+\beqn\label{eqn:geomads4}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\eeqn
 We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4}$ as a sheaf of cochain complexes on $\R_{>0}\times M$.
@@
 \parsec{}
-We proceed to define a natural boundary condition of the twisted $AdS_4$-type theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
+We proceed to define a natural boundary condition of the twisted $AdS_4$ theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
 Such a boundary condition is specified by a Lagrangian in the phase space whose symplectic structure uses Serre duality on the THF manifold $M$ together with the higher residue pairing along the THF structure of the sphere $S^7$.
-The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\cA_M^\bu (\mc V^N)$. We wish to describe a shifted Lagrangian therein.
+The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be the complex of vector bundles $\cA_M^\bu (\mc V^N)$. 
+We wish to describe a shifted Lagrangian therein.
 
@@
 
-Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of vector bundles on $M$:
+Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of holomorphic vector bundles on $M$:
 
@@
 
-We now specialize to the case $M = \R \times \C$.
+We denote by $\cF_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
+\beqn
+ \cF_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
+\eeqn
+%Here, $\cA^\bu(U, \cL^N_{AdS_4}$
+
+\brian{what's the dependence on $N$?}
 
 \begin{defn}\label{defn:ads4states}
- The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by 
+The \emph{space of supergravity states} $\cS_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_4}$:
 \beqn
- \cO\left(\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4}) \right ) .
+\cS_{AdS_4} \define \cF_{AdS_4} (0) .
 \eeqn
@@
 \begin{lem}\label{lem:ads4states}
-The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4})$ where $\mc H_{AdS_4}$ is the cochain complex
+The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra 
+\beqn
+\cS_{AdS_4} = \Sym (\mc H_{AdS_4})
+\eeqn
+where $\mc H_{AdS_4}$ is the cochain complex
  \begin{equation} 
@@
 
-\begin{prop}
+\begin{prop}\label{prop:ads4index}
 The single particle index of the space of supergravity states $\mc H_{AdS_4}$ is given by 
@@
 As before, we consider the $S^4$ bundle 
-\[
+\beqn\label{eqn:geomads7}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\eeqn
 
@@
 \beqn\label{eqn:cotm5}
-\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex] 
+\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha_N} \left (\begin{tikzcd}[row sep = 1 ex] 
 \ul{-} & \ul{+} \\
@@
 \eeqn
-Analogously to the case of $AdS_4\times S^7$, $\alpha$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.
+Analogously to the case of $AdS_4\times S^7$, $\alpha_N$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.
 
-A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7})$ where $\mc L_{AdS_7}$ is the complex of vector bundles given by  
+A natural Lagrangian in the phase space is thus given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7})$ where $\mc L^N_{AdS_7}$ is the complex of vector bundles given by  
 \begin{equation}
@@
 
-We now specialize to $X = \C^3$.
+We denote by $\cF_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
+\beqn
+ \cF_{AdS_7} (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
+\eeqn
+\brian{what's the dependence on $N$?}
+%Here, $\cA^\bu(U, \cL^N_{AdS_4}$
 
 \begin{defn}\label{defn:ads7states}
-The space of supergravity states on twisted $AdS_7\times S^4$ is given by the costalk at zero of the factorization algebra on $\C^3$ given by 
+The \emph{space of supergravity states} $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
 \beqn
-\cO \left(\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7} ) \right ) .
+\cS_{AdS_7} \define \cF_{AdS_7} (0) .
 \eeqn
@@
 \begin{lem}
-The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
+The space of supergravity states $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
 
@@
 When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.
+Since the back reactions do not appear, these boundary conditions make sense for arbitrary THF three-manifold $M$ in \eqref{eqn:geomads4} and arbitrary threefold $X$ in \eqref{eqn:geomads7}.
+We will specialize to $M = \R \times \C$ and $X =\C^3$ again momentarily.
 
@@
 \begin{itemize}
-\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $\C$ 
+\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $M$
  \begin{equation}
@@
 \end{equation}
+The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.
 
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times\R\times\C}$ is given by $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc L_{AdS_4}^{r=0})$.
-
-\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $\C^3$
+\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $X$
  \begin{equation}
@@
 \end{equation}
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times\C^3}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
+The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
 \end{itemize}
 
-Note that the same formulae defining the $L_\infty$ structure on the parity shift of the eleven-dimensional theory $\mc E$ \ref{thm:dfn} equip these Lagrangians in the $N=0$ phase spaces with $L_\infty$ structures.
-Moreover, the canonical maps
-\[
-\Omega^\bullet_{\R} \otimes \Omega^{0,\bullet}_{\C} (\mc L^{r=0}_{AdS_4} ) \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times \R\times \C}, \quad \Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times \C^3}
-\]
+These Lagrangians exist in the fully interacting eleven-dimensional model, which we can encode perturbatively in terms of an $L_\infty$ structure.
+In particular, the parity shift of these Lagrangians are equipped with $L_\infty$ structures compatible with the interacting bulk theory in the sense that the morphisms
+\begin{align*}
+\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times M}\\
+\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times X}
+\end{align*}
 preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. 
-Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$
+%Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$
 
@@
 
-The following lemma illustrates that the state space of definitions \ref{defn:ads4states} \ref{defn:ads7states} can also be computed using these alternate boundary conditions.
+We restrict to the case $M = \R \times \C$ and $X = \C^3$.
+The following lemma illustrates that the state space of definitions \ref{defn:ads4states}, \ref{defn:ads7states} can also be computed using these alternate boundary conditions.
+These Lagrangians afford an alternative description of twisted supergravity states, which will be used to investigate their representation theoretic properties.
 
-These Lagrangians afford an alternative description of twisted supergravity states, which will be used to investigate their representation theoretic properties.
+Given any local $L_\infty$ algebra $\cL$ we can consider the factorization algebra $\clie_\bu(\cL_c)$ which assigns to an open set $U$ the cochain complex computing the Lie algebra homology of the $L_\infty$ algebra of compactly supported sections $\clie_\bu (\cL_c(U))$.
+
+\brian{I think gradings need to be fixed.}
+
+\brian{The dependence on $N$ on the RHS is implicit in above definitions. Explain we are setting $N=0$.}
 
@@
 There are isomorphisms of cochain complexes
-\begin{center}
-$\mc U \left ( \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc L_{AdS_4}^{r=0} ) \right )(0)\cong \Sym( \mc {H}_{AdS_4} )$ \\
-$\mc U \left ( \Omega^{0,\bullet}_{X}(\mc L_{AdS_7}^{r=0})\right )(0)\cong \Sym( \mc {H}_{AdS_7} )$
-\end{center}
+\begin{align*}
+ \left ( \clie_\bu(\cA^\bu_c (\mc L_{AdS_4}^{r=0} )) \right )(0) & \cong \Sym( \mc {H}_{AdS_4} ) \\
+\left ( \clie_\bu ( \Omega^{0,\bullet}_{c}(\mc L_{AdS_7}^{r=0})) \right )(0) & \cong \Sym( \mc {H}_{AdS_7} )
+\end{align*}
 \end{prop}

### 2023-05-30 graviton spectra/content/br.tex
merge

@@
 \item The graded bundle $\til{V}$ is holomorphic with respect to the THF structure.
-\item $\cA^\bu (\til{Z}, \til{V})$ denotes the THF cohomology of $\til{Z}$ with coefficients in $\til{V}$.
+\item $\cA^\bu (\til{Z}, \til{V})$ denotes the THF cohomology of $\til{Z}$ with coefficients in $\til{V}$. \brian{elaborate}
 \end{itemize}
@@
 \begin{conj}\label{conj:ads7}
-The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E_{AdS_7}$. 
+The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E^N_{AdS_7}$. 
 \end{conj}

### 2023-05-30 graviton spectra/content/e16.tex
merge

@@
 \]
-\brian{gradings again}
 where $\cF^{(n)}_M \subset \cA_M^\bu(\mc L^{r=0}_{AdS_4} )$ is the weight $n$ eigenspace with respect to the above $\C^\times$ action thought of as a complex of super vector bundles on $M$. 
@@
 \item sections of type $\mu$ of the form $\mu_a(z) \del_{w_a}$. 
-As the $w_a$ are fiber coordinates on $K^{1/4}$, these fields transform as sections of $K^{1/4}_\C$.
+As the $w_a$ are fiber coordinates on $K^{1/4}$, these fields transform as sections of $K^{1/4}$.
 \item sections of type $\gamma$ of the form $\gamma_a(z) \d w_a$. 

### 2023-05-30 graviton spectra/content/index.tex
merge

@@
  \ul{-} & \ul{+} \\ 
-\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
-\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
-\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right)
+\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \cA_M^\bu \ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \cA_M^\bu  \\
+\C[w_1,\ldots, w_4] \otimes \cA_M^\bu (\T) \ar[ur, "\del^M_\Omega" description] \\
+\C[w_1,\ldots, w_4] \otimes \cA_M^\bu \ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \cA_M^\bu(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \cA_M^\bu  \end{tikzcd} \right)
 \eeqn
@@
 (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
-(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
+(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
 \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
@@
 
-We denote by $\cF_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
+We denote by $\Obs_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
 \beqn
- \cF_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
+ \Obs^N_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
 \eeqn
@@
 \begin{defn}\label{defn:ads4states}
-The \emph{space of supergravity states} $\cS_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_4}$:
+The \emph{space of supergravity states} $\cS^N_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of $\Obs_{AdS_4}^N$:
 \beqn
-\cS_{AdS_4} \define \cF_{AdS_4} (0) .
+\cS^N_{AdS_4} \define \Obs^N_{AdS_4} (0) .
 \eeqn
@@
 \beqn
-\cS_{AdS_4} = \Sym (\mc H_{AdS_4})
+\cS^N_{AdS_4} = \Sym (\mc H_{AdS_4})
 \eeqn
@@
 Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc.
-The sections of the sheaf of cochain complexes $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
+The sections of the sheaf of cochain complexes $\cA^\bu_{\R \times \C}(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
@@
 
-We denote by $\cF_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
+We denote by $\Obs_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
 \beqn
- \cF_{AdS_7} (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
+ \Obs_{AdS_7}^N (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
 \eeqn
@@
 \begin{defn}\label{defn:ads7states}
-The \emph{space of supergravity states} $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
+The \emph{space of supergravity states} $\cS^N_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
 \beqn
-\cS_{AdS_7} \define \cF_{AdS_7} (0) .
+\cS_{AdS_7}^N \define \cF_{AdS_7} (0) .
 \eeqn
@@
 \begin{lem}
-The space of supergravity states $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
+The space of supergravity states $\cS_{AdS_7}^N$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
 
@@
 \end{equation}
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.
+The desired Lagrangian in $(p_*\mc E^{N=0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.
 
@@
  \begin{tikzcd}[row sep = 1 ex]
-   \ul{+} & \ul{-} \\
+   \ul{-} & \ul{+} \\
 \C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
@@
 \end{equation}
-The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
+The desired Lagrangian in $(p_*\mc E^{N=0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
 \end{itemize}
@@
 \begin{align*}
-\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times M}\\
-\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times X}
+\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^{N=0} _{AdS_4})|_{\{\infty\} \times M}\\
+\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^{N=0} _{AdS_7})|_{\{\infty\} \times X}
 \end{align*}
@@
 Given any local $L_\infty$ algebra $\cL$ we can consider the factorization algebra $\clie_\bu(\cL_c)$ which assigns to an open set $U$ the cochain complex computing the Lie algebra homology of the $L_\infty$ algebra of compactly supported sections $\clie_\bu (\cL_c(U))$.
-
-\brian{I think gradings need to be fixed.}
-
-\brian{The dependence on $N$ on the RHS is implicit in above definitions. Explain we are setting $N=0$.}
 

### 2023-06-07 graviton spectra/content/br.tex
merge

@@
 Likewise, locally on the Calabi--Yau fivefold, all anti-holomorphic translations act in a homotopically trivial way---in this sense, the theory is {\em holomorphic} along $Z$ \cite{BWhol}.
-More generally, the eleven-dimensional theory can be constructed on any eleven-manifold equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
+More generally, the eleven-dimensional theory can be constructed on any eleven-manifold $\til Z$ equipped with a transversely holomorphic foliation which is equipped with an appropriate holomorphic volume form on the leaves of the foliation.
 
@@
 \beqn\label{eqn:thfm2}
-\text{Tot} \left(K_M^{1/4} \otimes \C^4 \to M\right) .
+\til Z = \text{Tot} \left(K_M^{1/4} \otimes \C^4 \to M\right) .
 \eeqn
@@
 \beqn\label{eqn:thfm5}
-\R \times \text{Tot} \left(K_X^{1/2} \otimes \C^2 \to X \right) .
+\til Z = \R \times \text{Tot} \left(K_X^{1/2} \otimes \C^2 \to X \right) .
 \eeqn
 The M5 branes will wrap the zero section and lie at a point in $\R$.
-Notice that in this case the manifold is globally of the form $\R \times Z$ where $Z$ is a Calabi--Yau fivefold.
+Notice that in this case the manifold is globally of the form $\R \times Z$ where $Z$ is the Calabi--Yau fivefold above.
 \end{itemize}
@@
 In \cite{RSW,RWindex} we describe how physical fields in supergravity are manifest in the twisted model.
-We review a small part of this.
+We review part of this.
 If $\til{Z}$ is an eleven-manifold equipped with a THF structure as above, the fields will live in a space of the form
@@
 \end{itemize}
-To simplify discussion in the remainder of this section we will only work in the local model~\eqref{eqn:local} where $\til{Z} = \R \times Z$ for $Z$ a Calabi--Yau fivefold.
+To simplify discussion we point out the explicit form of the fields in the split case~\eqref{eqn:local} where $\til{Z} = \R \times Z$ for $Z$ a Calabi--Yau fivefold.
 Then, the space of fields is of the form
@@
 \begin{multline}
-S_{BV} = \int_{\R \times Z} \bigg[\beta \wedge (\dbar + \d) \nu + \gamma \wedge (\dbar + \d) \mu +  \beta \wedge \div \mu  \bigg] \\
-+ \frac{1}{2} \int_{\R \times Z}  \mu^2 \vee \del \gamma + \int_{\R \times Z} \gamma \del \gamma \del \gamma + \cdots .
+S_{BV} = \int_{\til Z}^\Omega \bigg[\beta \wedge (\dbar + \d) \nu + \gamma \wedge (\dbar + \d) \mu +  \beta \wedge \div \mu  \bigg] \\
++ \frac{1}{2} \int_{\til Z}^\Omega  \mu^2 \vee \del \gamma + \int_{\til Z} \gamma \del \gamma \del \gamma + \cdots .
 \end{multline}
@@
 The operator $\dbar$ is the $\dbar$-operator on $Z$, the operator $\d$ is the de Rham operator on $\R$, and the operator $\div$ is the holomorphic divergence operator on $Z$ corresponding to the holomorphic volume form.
-\item We implicitly use the holomorphic volume form in the above integrals.
+Together with the BV pairing, then, this first line defines the following linearized BRST complex
+\beqn
+\begin{tikzcd}
+\underline{-} & \underline{+} \\
+\cA^\bu(\til Z , \T_{\til Z})_\mu \ar[r,"\div"] & \cA^\bu(\til Z)_\nu \\
+\cA^\bu(\til Z)_\beta \ar[r,"\del"] & \cA^\bu(\til Z, \T^*_{\til Z})_\gamma .
+\end{tikzcd}
+\eeqn
+\item We implicitly use the holomorphic volume form in the integrals denoted~$\int^\Omega$.
 \item The term 
@@
 
-%From the point of view of the $SU(5)$ twist there are essentially two types of circles one can consider.
-%The first is a `holomorphic circle'.
-%This is present when we assume our Calabi--Yau fivefold is of the form $Z = \C^\times \times Y$ with $Y$ a Calabi--Yau fourfold.
-%We assume that $\C^\times$ is equipped with the standard volume form $\d z$.
-%The $S^1$ reduction along a circle in $\C^\times$ results in a twist of type IIA supergravity with global symmetry $SU(4)$ on the manifold
-%\beqn
-%\R \times \R \times Y .
-%\eeqn
-%More generally, this twist can be defined when $\R^2$ is replaced by a smooth oriented two-dimensional manifold $M^2$.
-%In \cite{CLsugra}, Costello and Li have given a conjectural description of this particular twist of type IIA (and many other twists) using methods of topological string theory.
-%In this case, the conjecture of Costello and Li is that the twist is equivalent to a mixed topological string theory which is given by the A-model along $M^2$ and the B-model along $Y$.
-%In perturbation theory, this admits a description in terms of Kodaira--Spencer theory along the fourfold $Y$.
-%Via an explicit dimensional reduction of our model we find an exact match with this expectation \cite{RSW}.
-%The dimensional reduction of our eleven-dimensional model on
-%\beqn
-%\R \times \C \times Y
-%\eeqn
-%along $S^1 \subset \C$ is equivalent to the mixed topological A-model along $\R^2$ and B-model along $Y$ as considered in \cite{CLsugra}.
-%
-%The other type of reduction one can consider is that along a `topological' circle.
-%This corresponds to placing our eleven-dimensional model on
-%\beqn
-%S^1 \times Z
-%\eeqn
-%and performing reduction along $S^1 \times Z \to Z$.
-%What results is a theory with $SU(5)$ global symmetry.
-%We conjecture that this is the $SU(5)$ twist of type IIA supergravity.
-%There is no expected description of the $SU(5)$ twist in terms of topological strings like in the $SU(4)$ or $SU(2)$ cases.
-
-%
-%There are two bosonic fields of particular importance.
-%First is a section
-%\beqn
-%\mu^{0;0,1} \in \Omega^0(\R) \otimes \Omega^{0,1}(X, \T_X) .
-%\eeqn
-%Here $\T_X$ is the holomorphic tangent bundle on $X$.
-%The linear part of the BRST differential requires this field be constant in the real direction.
-%Thus, this field has the same form as a Beltrami differential on $X$.
-%There are particular field configurations where the non-linear equations of motion for $\mu$ imply that it is a complex structure deformation of $X$, but the full equations of motion are more complicated.
-%Another bosonic field of importance is a section
-%\beqn
-%\gamma^{0;0,1} \in \Omega^0(\R) \otimes \Omega^{1,1}(X) .
-%\eeqn
-%
-%The field $\mu$ satisfies a condition that it be {\em divergence-free} for the Calabi--Yau structure on the fivefold~$X$.
-%This means that it is required to satisfy the equation
-%\beqn
-%\div \mu = 0
-%\eeqn
-%where $\div(-)$ is the divergence with respect to the holomorphic volume form $\Omega$ on $X$.
-
-%\subsection{The $G_2$ twist}
-%
-%We will give a description to of the $G_2$ twist of eleven-dimensional supergravity.
-%Independent derivations of this twist have appeared in \cite{CostelloM5, EagerHahner}.
-%The theory is defined on any manifold of the form
-%\beqn
-%M \times Y
-%\eeqn
-%where $M$ is a manifold with $G_2$ holonomy and $Y$ is a manifold with $SU(2)$ holonomy.
-%Unfortunately, the perturbative description we are about to give depends in no way on the $G_2$ structure and can be defined when $M$ is any smooth seven-dimensional manifold.
-%To see the full $G_2$ structure appearing one must take into account non-perturbative effects (much like in the target space description of the topological A-model).
-%
-%The fundamental field is simply a differential form
-%\beqn
-%\alpha \in \Omega^\bu(M) \otimes \Omega^{0,\bu}(Y) [1] .
-%\eeqn
-%The linear BRST differential is simply $\d + \dbar$ where $\d$ is the de Rham differential on $M$ and $\dbar$ is the Dolbeault operator for $Y$.
-%
-%Being a manifold with $SU(2)$ holonomy, the algebra of holomorphic fnuctions on $Z$ is equipped with a holomorphic Poisson bracket $\{-,-\}$.
-%Since this bracket involves only holomorphic differntial operators, it can be extended to a Poisson bracket on the dg algebra $\Omega^{0,\bu}(Y)$.
-%The theory utilizes this bracket in an essential way.
-%Indeed, the full BV action is
-%\beqn
-%\frac12 \int_{M \times Y} \Omega \, \alpha \d \alpha + \frac16 \int_{M \times Y} \Omega \, \alpha \{\alpha, \alpha\} .
-%\eeqn
-%where $\Omega \in \Omega^{2,0}(Y)$ is the holomorphic volume form.
-%This description appeared in \cite{RYsduality} and was independently derived from a further twist of the $SU(5)$ twist in \cite{RSW}. 
-%
-%Like the $SU(5)$ twist, this theory is only $\Z/2$ graded.
-%Nevertheless, one convenient way to think about this theory is as a higher dimensional Chern--Simons theory for a particular (dg) Lie algebra.
-%Given any odd-dimensional smooth manifold $M$ and a Lie algebra $\lie{g}$ equipped with an invariant non-degenerate symmetric inner product one can consider a $\Z/2$ graded version of Chern--Simons theory whose BV action is given by the usual formula $\int_M CS(A)$.
-%It is only in the case that $\dim M = 3$ that this theory admits a $\Z$-grading.
-%The theory we are considering here can be interpreted as $\Z/2$ graded Chern--Simons theory on the seven-manifold $M$ for the Lie algebra of holomorphic functions on $Y$ equipped with the holomorphic Poisson bracket.
-%Here, the invariant pairing is given by integrating against the holomorphic volume form $\Omega$.
-
 \subsection{The ${\mr AdS}_4 \times S^7$ background}
@@
 \[
-\operatorname{Tot}(K^{1/4}_M \otimes \C^4\to M)
+\til Z = \operatorname{Tot}(K^{1/4}_M \otimes \C^4\to M)
 \]

### 2023-06-07 graviton spectra/content/e16.tex
merge

@@
 Having justified that the spaces of supergravity states constructed in the previous subsection are in fact counting gravitons on $AdS_4\times S^7$ and $AdS_7\times S^4$ respectively, we turn to studying representation theoretic properties of these state spaces.
-In this section, we focus on the case of gravitons on $AdS_4\times S^7$, using the description of the state space afforded by proposition \ref{prop:altstates} which describes it as the costalk of a factorization envelopes of the boundary conditions $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4} )$.
 
-We construct a certain $\C^\times$-action on the boundary fields $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4} )$ equipped with the $L_\infty$ structure from remark \label{rmk:nottransferred} with the feature that the zeroth weight spaces are a local version of another exceptional linearly compact super-Lie algebras, $E(1|6)$.
-This in particular readily gives a decomposition of the state space $\mc H_{AdS_4}$ into $E(1|6)$-modules.
+A feature of the physical $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds is that they have as isometries, the 3d $\mc N=8$ and 6d $\mc N=(2,0)$ superconformal algebras respectively.
+In each case, the complex form of the superconformal algebra is $\lie{osp}(8|4)$ (though their real forms differ).
+In both the $AdS_4$ and $AdS_7$ cases there is a map of super Lie algebras 
+\[
+\phi \colon \mf {siso}_{11d} \to \mf {osp}(8|4).
+\]
+Further, it is observed in \cite{SWsuco2} that if $Q\in \mf{siso}_{11d}$ is the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, then the $\phi(Q)$-cohomology of the superconformal algebra is
+\[ H^\bu \left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
+
+The super Lie algebra $\mf{osp}(6|2)$ plays the role of the residual isometries of the twisted $AdS$ background. 
+The bosonic part of $\mf{osp}(6|2)$ is the direct sum Lie algebra $\mf{sl}(4) \oplus \mf{sl}(2)$.
+The odd part of the algebra $\mf{osp}(6|2)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\mf{sl}(4)$ representation and $R$ is the fundamental $\mf{sl}(2)$ representation.
+The super Lie bracket is determined by the natural invariant symmetric-symmetric and anti-symmetric-anti-symmetric pairings.
+
+In this section we will focus on $AdS_4$.
+In \cite{RSW} we have witnessed the super Lie algebra $\lie{osp}(6|2)$ as symmetries of our eleven-dimensional model on the eleven-manifold obtained by subtracting the location of the brane
+\beqn
+\til Z = \R \times \C^5 - (\R \times \C \times 0) .
+\eeqn
+We have further checked that these symmetries extend to symmetries in the theory $\mc E^N_{AdS_4}$ for nonzero flux $N \ne 0$; thus providing evidence that $\lie{osp}(6|2)$ is a global symmetry of twisted $AdS$ space.
+
+As a consequence, the space of twisted supergravity states $\cH_{AdS_4}$ as a representation for $\lie{osp}(6|2)$.
+In this section we argue that the symmetries of twisted $AdS$ space enhance to an infinite-dimensional symmetry algebra called $E(1|6)$, which is also of exceptional type \cite{KacClass}.
+As a consequence, we understand $\cH_{AdS_4}$ as a representation for this infinite-dimensional enhancement of the three-dimensional twisted superconformal algebra.
+
+%In this section, we focus on the case of gravitons on $AdS_4\times S^7$, using the description of the state space afforded by proposition \ref{prop:altstates} which describes it as the costalk of a factorization envelopes of the boundary conditions $\Omega^\bullet _\R\otimes \Omega^{0,\bullet}_\C (\mc L^{{r=0}}_{AdS_4} )$.
+
+To this end, we construct a $\C^\times$-action on our eleven-dimensional model on twisted $AdS_4$ space.
+The homogenous components of this $\C^\times$-action should be understood as a twisted version of excited gravitational states at a particular charge.
+The weight zero part of this $\C^\times$-action is endowed with the structure of a Lie algebra, and we will see that it is precisely $E(1|6)$.
+This action readily gives a decomposition of the state space $\mc H_{AdS_4}$ into $E(1|6)$-representations.
 We explicitly characterize the summands of this decomposition with their module structures and give closed form expressions for their characters.
 
+%As is usual in the perturbative BV formalism, the BV action functional equips the parity shift of the fields $\Pi \cE$ with the structure of an $L_\infty$ algebra.
+%Consider the eleven-dimensional model that we introduced in the first section describing the putative holomorphic twist of supergravity.
+%On flat space $\til Z = \R \times \C^5$ we have shown in \cite{RSW} that there is a quasi-isomorphism of $\Pi \cE (\R \times \C^5)$ with a central extension of the exceptional super Lie algebra $E(5|10)$.
+%In this section we will deduce the analogous symmetry algebra on the twisted analogs of AdS space.
+
 \subsection{The graviton decomposition of twisted $AdS_4\times S^7$}
-\parsec{}
-We define a decomposition of the space of states $\mc H_{AdS_4}$.
-It is induced by a decomposition of the boundary fields $\cA^\bu_{M} (\mc L^{{r=0}}_{AdS_4} )$ introduced in section \ref{sec:transversebc}  arising from a $\C^\times$ action which mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
-We first consider a general three-manifold $M$ equipped with a THF; we specialize to $M = \R \times \C$ shortly.
 
-Define the $\C^*$-action on holomorphic sections of $\cL_{AdS_4}^{r=0}$:
+Recall the boundary condition at zero in twisted $AdS$ space $\cA^\bu(\cL_{AdS_4}^{r=0})$ that we introduced in section \ref{sec:transversebc}.
+Recall that this boundary condition makes sense for any three-manifold $M$ equipped with a THF.
+The parity shift of these boundary fields $\cA^\bu(\Pi \cL_{AdS_4}^{r=0})$ is equipped with an $L_\infty$ structure inherited from the BV action of the eleven-dimensional theory.
+
+%We define a decomposition of the space of states $\mc H_{AdS_4}$.
+%It is induced by a decomposition of the boundary fields $\cA^\bu_{M} (\mc L^{{r=0}}_{AdS_4} )$ introduced in section \ref{sec:transversebc}  arising from a $\C^\times$ action which mixes fiberwise rescalings on spacetime with a fiberwise rescaling of the space of fields.
+%We first consider a general three-manifold $M$ equipped with a THF; we specialize to $M = \R \times \C$ shortly.
+
+Define the $\C^\times$-action on holomorphic sections of $\cL_{AdS_4}^{r=0}$:
 \begin{itemize}
@@
 
-This $\C^*$-action on holomorphic sections extends to an action on the de Rham--Dolbeault complex $\cA^\bu_M(\cL_{AdS_7}^{r=0})$ in such a way that preserves the de Rham--Dolbeault operator.
-In fact, this $\C^*$-action preserves the full local $L_\infty$ structure present on the parity shift of this complex of vector bundles.
+This $\C^\times$-action on holomorphic sections extends to an action on the de Rham--Dolbeault complex $\cA^\bu_M(\cL_{AdS_7}^{r=0})$ in such a way that preserves the de Rham--Dolbeault operator.
+In fact, this $\C^\times$-action preserves the full local $L_\infty$ structure present on the parity shift of this complex of vector bundles.
 
@@
 
-\begin{rmk}
-We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\cA_{\R \times \C}^\bu (\mc L^{r=0}_{AdS_4} )$ over every open set containing the origin.
-The image of the map lands exactly in the step $\mc F^{(0)}_{\R\times \C}$ of the decomposition from proposition \ref{prop:ads4decomp}. 
-Therefore we see that $E(1|6)$ contains $\mf{osp}(6|2)$ as a finite dimensional subalgebra.  
-\end{rmk}
+%\begin{rmk}
+%We note that the map $i_{M2}$ from lemma \ref{lem:m2emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\cA_{\R \times \C}^\bu (\mc L^{r=0}_{AdS_4} )$ over every open set containing the origin.
+%The image of the map lands exactly in the step $\mc F^{(0)}_{\R\times \C}$ of the decomposition from proposition \ref{prop:ads4decomp}. 
+%Therefore we see that $E(1|6)$ contains $\mf{osp}(6|2)$ as a finite dimensional subalgebra.  
+%\end{rmk}
 
@@
 \begin{conj}\label{conj:e16gravitonrep}
-For $j\geq -1$, the minimal twist of the $j+2$nd graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
+For $j\geq -1$, the minimal twist of the $(j+2)$-weight graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
 \end{conj}

### 2023-06-07 graviton spectra/content/e36.tex
merge

@@
 
-We now repeat the analysis of the previous subsection for gravitons on $AdS_7\times S^4$ respectively, making use of the description of supergravity states on $AdS_7\times S^4$ as the costalk of the factorization envelopes of the boundary condition and $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4})$
+We now repeat the analysis of the previous subsection for gravitons on $AdS_7\times S^4$ respectively, making use of the description of supergravity states on $AdS_7\times S^4$ as the costalk of the factorization envelopes of the boundary condition and $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7})$
 
-As before, we construct certain $\C^\times$ actions on the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4})$; we find that the zeroth weight space is a local version of another exceptional linearly compact super-Lie algebra $E(3|6)$.
-The decomposition of $\mc H_{AdS_7\times S^4}$ as a direct sum of $E(3|6)$ modules incidentally turns out to be very closely related to a decomposition of $E(5|10)$ into $E(3|6)$ modules studied by Cheng-Kac \cite{}.
+As before, we construct certain $\C^\times$ actions on the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7})$; we find that the zeroth weight space is a local version of another exceptional linearly compact super-Lie algebra $E(3|6)$.
+The decomposition of $\mc H_{AdS_7}$ as a direct sum of $E(3|6)$ modules incidentally turns out to be very closely related to a decomposition of $E(5|10)$ into $E(3|6)$ modules studied in \cite{KacRudakov}.
 
 \subsection{The graviton decomposition of twisted $AdS_7\times S^4$}
-We wish to consider a particular decomposition of the space of states $\mc H_{AdS_7\times S^4}$.
-It is induced by a decomposition of the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4} )$ introduced in section \ref{sec:transversebc}.
+%We wish to consider a particular decomposition of the space of states $\mc H_{AdS_7}$.
+It is induced by a decomposition of the boundary fields $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7} )$ introduced in section \ref{sec:transversebc}.
 
@@
 
-Let $U\subset \C^3$ be an open; explicitly, the $\C^\times$ action on $\Omega^{0,\bullet}_{\C^3} (U, \mc L^{{r=0}}_{AdS_7\times S^4} )$ is given as follows.
+Recall the boundary condition at zero in twisted $AdS$ space $\Omega^{0,\bu}(\cL_{AdS_7}^{r=0})$ that we introduced in section \ref{sec:transversebc}.
+Recall that this boundary condition makes sense for any complex threefold $X$ equipped with $K^{1/2}_X$.
+The parity shift of these boundary fields $\Omega^{0,\bu}(\Pi \cL_{AdS_7}^{r=0})$ is equipped with an $L_\infty$ structure inherited from the BV action of the eleven-dimensional theory.
+
+Define the $\C^\times$ action on $\mc L^{{r=0}}_{AdS_7}$ as follows.
 \begin{itemize}
-\item On the fields $\mu(w_a,z_i) \in \C[w_1, w_2]\{\del_{w_a}\} \otimes \Omega^{0,\bullet}_{\C^3} (U) \oplus \C[w_1, w_2]\otimes \Omega^{0,\bullet}_{\C^3}(U, T)$ the action is
+\item On the fields $\mu(w_a,z_i) \in \C[w_1, w_2]\{\del_{w_a}\} \otimes \cO_X \oplus \C[w_1, w_2] \otimes \T_X$ the action is
 \[
@@
 \]
-\item On the fields $\nu(w_a,z_i) \in \C[w_1, w_2] \otimes \Omega^{0,\bullet}_{\C^3}(U)$ the action is
+\item On the fields $\nu(w_a,z_i) \in \C[w_1, w_2]\otimes \cO_X$ the action is
 \[
-\lambda \cdot \nu(w_a,z_i) = \nu(\lambda w , z).
+\lambda \cdot \nu(w_a,z_i) = \nu(\lambda w_a , z).
 \]
-\item On the fields $\beta(w_a,z_i) \in \C[w_1, w_2] \otimes \Omega^{0,\bullet}_{\C^3}(U)$ the action is
+\item On the fields $\beta(w_a,z_i) \in \C[w_1, w_2]\otimes \cO_X$ the action is
 \[
@@
 \]
-\item On the fields $\gamma(w_a,z_i) \in \C[w_1, w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{\C^3} (U) \oplus \C[w_1, w_2]\otimes \Omega^{0,\bullet}_{\C^3}(U, \Omega^1)$ the action is
+\item On the fields $\gamma(w_a,z_i) \in \C[w_1, w_2] \{\d w_a\}\otimes \cO_X \oplus \C[w_1, w_2]\otimes \Omega^1_X$ the action is
 \[
@@
 \begin{prop}\label{prop:ads7decomp}
-The $L_\infty$ structure on $\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4} )$ identified in remark \ref{} is equivariant for this $\C^\times$ action. 
+The $L_\infty$ structure on $\Omega^{0,\bullet}_{X} (\mc L^{{r=0}}_{AdS_7} )$ is equivariant for this $\C^\times$ action. 
 \end{prop}
@@
 \label{eqn:Gdecomp}
-\Omega^{0,\bullet}_{\C^3} (\mc L^{{r=0}}_{AdS_7\times S^4}) = \prod_{n \geq -1} \mc{G}_{\C^3}^{(n)}
+\Omega^{0,\bullet}_{X} (\mc L^{{r=0}}_{AdS_7}) = \prod_{n \geq -1} \mc{G}_{X}^{(n)}
 \end{equation}
-where for each open set $U \subset \C^3$
+where
 \[
-\mc{G}_\C^3(U)^{(n)}\subset \Omega^{0,\bullet}_{\C^3} (U, \mc L^{{r=0}}_{AdS_7\times S^4} )
+\mc{G}_X^{(n)}\subset \Omega^{0,\bullet}_{X} (\mc L^{{r=0}}_{AdS_7} )
 \]
-is the weight $n$ eigenspace with respect to the above $\C^\times$ action.  In particular, we see that $\mc{G}^{(0)}_{\C^3}$ is itself a local dg-Lie algebra (that we will soon describe). 
-Moreover, every $\mc{G}_{\C^3}^{(n)}$, $n \geq -1$ is a (local) module for this local dg-Lie algebra.
+is the weight $n$ eigenspace with respect to the above $\C^\times$ action.  
+In particular, we see that $\mc{G}^{(0)}_{X}$ is itself a local Lie algebra (that we will soon describe). 
+Moreover, every $\mc{G}_{X}^{(n)}$, $n \geq -1$ is a (local) module for this local dg-Lie algebra.
 
@@
 
-\subsection{The lowest piece: the holomorphic twist of the abelian 6d $\mc N=(2,0)$ tensor multiplet}\label{subsec:g-1}
+\subsection{The lowest piece}
 
@@
 \[
-\mc{G}_{\C^3} ^{(-1)}\cong \Omega^{0,\bullet}_{\C^3} \left ( 
+\mc{G}_{X} ^{(-1)}\cong \Omega^{0,\bullet}_{X} \left ( 
 \begin{tikzcd}
 \ul{+} & \ul{-} \\
-\C^2\otimes K^{1/2}_{\C^3} & \\ 
-\mc{O}_{\C^3} \ar[r, "\del"] & \Omega^1_{\C^3} 
+\C^2\otimes K^{1/2}_{X} & \\ 
+\mc{O}_{X} \ar[r, "\del"] & \Omega^1_{X} 
 \end{tikzcd}
@@
 \item 
-fields of type $\mu$ of the form $\mu_a (z_i)\del_{w_a}$. As $w_a$ are fiber coordinates on $K^{1/2}_{\C^3}$, these fields transform as sections of $K^{1/2}_{\C^3}$. 
+fields of type $\mu$ of the form $\mu_a (z_i)\del_{w_a}$. As $w_a$ are fiber coordinates on $K^{1/2}_{X}$, these fields transform as sections of $K^{1/2}_{X}$. 
 \item 
-fields of type $\beta$ with no $w_a$-dependence. These fields constitute a copy of $\mc {O}_{\C^3}$.
+fields of type $\beta$ with no $w_a$-dependence. These fields constitute a copy of $\mc {O}_{X}$.
 \item 
-fields of type $\gamma$ of the form $\gamma_i(z_i)\d z_i$. These fields constitute a copy of $\Pi \Omega^1_{\C^3}$. 
+fields of type $\gamma$ of the form $\gamma_i(z_i)\d z_i$. These fields constitute a copy of $\Pi \Omega^1_{X}$. 
 \end{itemize}
@@
 \[
-\mc{O}_{\C^3}  \xto{\del} \Pi \Omega^{1}_{\C^3}  .
+\mc{O}_{X}  \xto{\del} \Pi \Omega^{1}_{X}  .
 \]
@@
 The twist is a free theory and can be defined on any complex three-fold admitting a square root of its canonical bundle.
-On $\C^3$, the $\Z\times \Z/2$ graded sheaf of complexes $\mc E_{tens}$ encoding its field content is given by
+On $X$, the $\Z\times \Z/2$ graded sheaf of complexes $\mc E_{tens}$ encoding its field content is given by
 
@@
 \ul{-1} & \ul{0} \\
-\Pi \C^2\otimes \Omega^{0,\bullet}_{\C^3} \otimes  K_{\C^3}^{1/2}  & \\
-\Omega^{2,\bullet}_{\C^3} \ar[r,"\del"] & \Omega^{3,\bullet}_{\C^3} 
+\Pi \C^2\otimes \Omega^{0,\bullet}_{X} \otimes  K_{X}^{1/2}  & \\
+\Omega^{2,\bullet}_{X} \ar[r,"\del"] & \Omega^{3,\bullet}_{X} 
 \end{tikzcd} 
@@
 \label{prop:factabelian}
-There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on $\C^3$
+There is a quasi-isomorphism of factorization algebras valued in $\Z/2$ graded commutative dg algebras on $X$
 \[
-\mc U (\mc G^{(-1)}_{\C^3} )\xto{\simeq} \clie^\bullet(\Pi \mc E_{tens})
+\mc U (\mc G^{(-1)}_{X} )\xto{\simeq} \clie^\bullet(\Pi \mc E_{tens})
 \]
@@
 \begin{proof}
-Recall that the factorization algebra $\mc U(\mc{G}_{\C^3}^{(-1)})$ assigns to an open set $U\subset \C^3$ the graded symmetric algebra on the complex
+Recall that the factorization algebra $\mc U(\mc{G}_{X}^{(-1)})$ assigns to an open set $U\subset X$ the graded symmetric algebra on the complex
 \begin{equation}\label{eqn:weight-1}
@@
 \ul{-} & \ul{+}\\
-\Omega_{\C^3, c}^{0,\bullet}(U) \ar[r,"\del"] & \Omega_{\C^3, c}^{1,\bullet}(U) \\
-\Omega_{\C^3, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
+\Omega_{X, c}^{0,\bullet}(U) \ar[r,"\del"] & \Omega_{X, c}^{1,\bullet}(U) \\
+\Omega_{X, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
 \end{tikzcd}
 \end{equation}
-On the other hand, if we totalize the $\Z\times\Z/2$-grading on $\mc E_{tens}$ to a $\Z/2$-grading, the factorization algebra $\clie^\bullet (\Pi \mc E_{tens})$ assigns to an open set $U\subset \C^3$ the symmetric algebra on the complex
+On the other hand, if we totalize the $\Z\times\Z/2$-grading on $\mc E_{tens}$ to a $\Z/2$-grading, the factorization algebra $\clie^\bullet (\Pi \mc E_{tens})$ assigns to an open set $U\subset X$ the symmetric algebra on the complex
 \begin{equation}
@@
 \ul{-} & \ul{+}\\
-\Omega_{\C^3}^{2,\bullet}(U)^\vee \ar[r,"\del"] & \Omega_{\C^3}^{3,\bullet}(U)^\vee \\
-& \Omega_{\C^3}^{0,\bullet}(U, \C^2\otimes K^{1/2})^\vee \\
+\Omega_{X}^{2,\bullet}(U)^\vee \ar[r,"\del"] & \Omega_{X}^{3,\bullet}(U)^\vee \\
+& \Omega_{X}^{0,\bullet}(U, \C^2\otimes K^{1/2})^\vee \\
 \end{tikzcd}
@@
 \ul{-} & \ul{+}\\
-\overline \Omega_{\C^3, c}^{0,\bullet}(U) \ar[r,"\del"] & \overline \Omega_{\C^3, c}^{1,\bullet}(U) \\
-\overline \Omega_{\C^3, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
+\overline \Omega_{X, c}^{0,\bullet}(U) \ar[r,"\del"] & \overline \Omega_{X, c}^{1,\bullet}(U) \\
+\overline \Omega_{X, c}^{0,\bullet}(U, \C^2\otimes K^{1/2}) & 
 \end{tikzcd}
 \end{equation}
-
 where the degree shift is coming from Serre duality.
-The result then follows from the fact that by ellipticity, the natural inclusion $\Omega^{0,\bullet}_{\C^3,c}\to\overline \Omega^{0,\bullet}_{\C^3,c}$ is a quasi-isomorphism.
+The result then follows from the fact that by ellipticity, the natural inclusion $\Omega^{0,\bullet}_{X,c}\to\overline \Omega^{0,\bullet}_{X,c}$ is a quasi-isomorphism.
 \end{proof}
@@
 
-As before, the weight zero summand $\mc{G}_{\C^3} ^{(0)}$ is special because it carries the induced structure of a local $L_\infty$-algebra on ${\C^3} $ inherited from the $L_\infty$ structure on $\Pi\Omega^{0,\bullet} (\mc L^{r = 0}_{AdS_7\times S^4} )$ identified in section \ref{sec:transversebc}.
+As before, the weight zero summand $\mc{G}_{X} ^{(0)}$ is special because it carries the induced structure of a local $L_\infty$-algebra on ${X} $ inherited from the $L_\infty$ structure on $\Pi\Omega^{0,\bullet} (\mc L^{r = 0}_{AdS_7} )$ identified in section \ref{sec:transversebc}.
 We will prove that it is equivalent to a local Lie algebra version of the exceptional super-Lie algebra $E(3|6)$ \cite{KacBible}.
@@
 
-To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ is in fact given by the same formulae as the brackets on $E(3|6)$ given in \ref{defn:e(3|6)}, it will be useful to provide an explicit quasi-isomorphism $\Phi^{(0)} : \mc E(3|6) \to \mc G^{(0)}_{\C^3}$.
+To see that the Lie structure induced from the $L_\infty$-structure on $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7} )$ is in fact given by the same formulae as the brackets on $E(3|6)$ given in \ref{defn:e(3|6)}, it will be useful to provide an explicit quasi-isomorphism $\Phi^{(0)} : \mc E(3|6) \to \mc G^{(0)}_{\C^3}$.
 On an open set $U\subset \C^3$, this is defined as follows.
@@
 \end{proof}
-
-\begin{rmk}
-We note that the map $i_{M5}$ from lemma \ref{lem:m5emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ over every open set containing the origin.
+%
+%\begin{rmk}
+%We note that the map $i_{M5}$ from lemma \ref{lem:m5emb} in fact defines a Lie map from $\mf{osp}(6|2)$ to the sections of the boundary condition $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7} )$ over every open set containing the origin.
 The image of the map lands exactly in the step $\mc G^{(0)}_{\C^3}$ of the decomposition from proposition \ref{prop:ads7decomp}.
 Therefore we see that $E(3|6)$ contains $\mf{osp}(6|2)$ as a finite dimensional subalgebra.
-\end{rmk}
+%\end{rmk}
 %\begin{rmk}
@@
 \label{eqn:Gj}
-\Omega^{0,\bullet}_{\C^3} \left (\begin{tikzcd}
+\Omega^{0,\bullet}_{X} \left (\begin{tikzcd}
 \ul{even} & \ul{odd} \\
@@
 \begin{proof}
-We begin by noting that we can explicitly describe the weight $j$ component $\mc G^{(j)}_{\C^3}$ as $\Omega^{0,\bullet}_{\C^3} (G^{(j)})$ where $G^{(j)}$ is the following dg-vector bundle
+We begin by noting that we can explicitly describe the weight $j$ component $\mc G^{(j)}_{X}$ as $\Omega^{0,\bullet}_{X} (G^{(j)})$ where $G^{(j)}$ is the following dg-vector bundle
 \begin{equation}
@@
 
-Note that the differentials here are $\mf{sl}(2)$-equivariant maps, tensored with a differential operator acting on sections of a bundle on $\C^3$. In particular
+Note that the differentials here are $\mf{sl}(2)$-equivariant maps, tensored with a differential operator acting on sections of a bundle on $X$. In particular
 
@@
 
-The decomposition of $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ in equation \eqref{eqn:Gdecomp} is closely related to a decomposition of the exceptional simple super Lie algebra $E(5|10)$ studied in \cite{KR2}.
+In the case $X = \C^3$, the decomposition of $\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7} )$ in equation \eqref{eqn:Gdecomp} is closely related to a decomposition of the exceptional simple super Lie algebra $E(5|10)$ studied in \cite{KR2}.
 In \ref{thm:global}, we showed that the global sections of the parity shifted fields of our eleven-dimensional theory on flat space is quasi-isomorphic to a Lie 2-extension of $E(5|10)$, which we denoted $\widehat{E(5|10)}$.
 More precisely, we found a Lie 2-extension of a version of $E(5|10)$ built out of polynomials rather than Taylor series.
-Given that the $L_\infty$ structure on $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ is given by the same formulas as that on $\Pi \mc E$, it is easy to see that the space of $\infty$-jets of $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ at the origin, which following lemma \ref{} has underlying vector space $\mc H_{AdS_7\times S^4}$, is quasi-isomorphic to $\widehat{E(5|10)}$.
+Given that the $L_\infty$ structure on $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7} )$ is given by the same formulas as that on $\Pi \mc E$, it is easy to see that the space of $\infty$-jets of $\Pi \Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7} )$ at the origin, which following lemma \ref{} has underlying vector space $\mc H_{AdS_7}$, is quasi-isomorphic to $\widehat{E(5|10)}$.
 
@@
 It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$.
-Moreover, we see that similarly to the decomposition of $\mc H_{AdS_7\times S^4}$ induced by our $\C^\times$ action in \ref{prop:ads7decomp}, the weight grading is concentrated in degrees $\geq -1$.
+Moreover, we see that similarly to the decomposition of $\mc H_{AdS_7}$ induced by our $\C^\times$ action in \ref{prop:ads7decomp}, the weight grading is concentrated in degrees $\geq -1$.
 In particular, there is a decomposition of super vector spaces
@@
 \subsection{Characters of $E(3|6)$-modules}\label{e36char}
-The decomposition of the state space $\Sym \left (\mc H_{AdS_7\times S^4}\right ) = \prod_{j\geq -1} \mc U (\mc G^{(j)})(0)$ gives a product formula for the characters computed in proposition \ref{prop:sugraindex1}
+The decomposition of the state space 
+\[
+\Sym \left (\mc H_{AdS_7}\right ) = \prod_{j\geq -1} \mc U (\mc G^{(j)})(0) 
+\] 
+gives a product formula for the characters computed in proposition \ref{prop:sugraindex1}
 
-\[ \chi \left ( \Sym \mc H_{AdS_7\times S^4} \right ) = \prod_{j\geq -1} \chi \left (\mc U (\mc G^{(j)})(0) \right ) \]
+\[ \chi \left ( \Sym \mc H_{AdS_7} \right ) = \prod_{j\geq -1} \chi \left (\mc U (\mc G^{(j)})(0) \right ) \]
 
@@
 \parsec[]
-As a consequence, we have that $f_{AdS_7\times S^4} (y_i, y, q) = \sum_{j\geq -1} g_j (y_i, y, q)$, or explicitly:
+As a consequence, we have that $f_{AdS_7} (y_i, y, q) = \sum_{j\geq -1} g_j (y_i, y, q)$, or explicitly:
 \begin{align*}
@@
 In \cite[Eq.
-(3.22, 3.23)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_7\times S^4}$ is expressed as a sum of characters of irreducible representations of the 6d $\mc N = (2,0)$ superconformal algebra.
+(3.22, 3.23)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_7}$ is expressed as a sum of characters of irreducible representations of the 6d $\mc N = (2,0)$ superconformal algebra.
 In \cite[Table 24]{cordova2016multiplets} these representations are labeled as $\mc D_1[0,0,0]^{(0,m)}_{2m}$ where $m \geq 1$.

### 2023-06-07 graviton spectra/content/suco.tex
merge

@@
 \label{sec:ads}
+
 As we indicated in the beginning of this chapter, a feature of the physical $AdS_4\times S^7$ and $AdS_7\times S^4$ backgrounds is that they have as isometries, the 3d $\mc N=8$ and 6d $\mc N=(2,0)$ superconformal algebras respectively.
-In fact, the complex forms of these two super-Lie algebras are the same.
+In fact, the complex forms of these two super Lie algebras are the same.
 
-In this section we provide evidence for conjectures \ref{conj:ads4} and \ref{conj:ads7} by arguing that the global sections of the local moduli problems $p_*\mc E_{AdS_4}$ and $p_* \mc E_{AdS_7}$ carry actions by the minimal twists of the relevant superconformal algebras.
+In this section we provide evidence for conjectures \ref{conj:ads4} and \ref{conj:ads7} by arguing that the global sections of the local moduli problems $p_*\mc E_{AdS_4}$ and $p_* \mc E_{AdS_7}$ obtained by sphere compactification carry actions by the minimal twists of the relevant superconformal algebras.
 We will find that the twist of the superconformal algebra is the same in each case, but the actions are slightly different.
@@
 There is a map of super Lie algebras $\phi: \mf {siso}_{11d} \to \mf {osp}(8|4)$. 
-Further, it is observed in \cite{SWsuco2} that if $Q\in \mf{siso}_{11d}$ is the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, then there is an equivalence of dg super-Lie algebras \[\left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
+Further, it is observed in \cite{SWsuco2} that if $Q\in \mf{siso}_{11d}$ is the odd square-zero element used to define the minimal twist of eleven-dimensional supergravity, then the $\phi(Q)$-cohomology of the superconformal algebra is
+\[ H^\bu \left ( \mf {osp}(8|4), [\phi(Q), - ]\right )\cong \mf {osp}(6|2).\]
 
-The super-Lie algebra $\mf{osp}(6|2)$ will therefore play the role of the residual isometries of the twisted AdS background.
+The super Lie algebra $\mf{osp}(6|2)$ will therefore play the role of the residual isometries of the twisted $AdS$ background.
 The bosonic part of $\mf{osp}(6|2)$ is the direct sum Lie algebra $\mf{sl}(4) \oplus \mf{sl}(2)$.
 The odd part of the algebra $\mf{osp}(6|2)$ is $\wedge^4 W \otimes R$ where $W$ is the fundamental $\mf{sl}(4)$ representation and $R$ is the fundamental $\mf{sl}(2)$ representation.
+The super Lie bracket is determined by the natural invariant symmetric-symmetric and anti-symmetric-anti-symmetric pairings.
 
@@
 
-To provide further evidence for conjecture \ref{conj:ads4} we wish to articulate a sense in which $\mf{osp}(6|2)$ is witnessed as a symmetry of $\mc E^N_{AdS_4}$.
-To this end, we will provide evidence for the claim that there is a Lie map
-\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right ).\]
+To provide further evidence for conjecture \ref{conj:ads4} we will articulate a sense in which $\mf{osp}(6|2)$ can be witnessed as a symmetry of $\mc E^N_{AdS_4}$ on the eleven-manifold obtained by subtracting the location of the brane
+\beqn
+\til Z = \R \times \C^5 - (\R \times \C \times 0) .
+\eeqn
+To this end, we will provide evidence for the claim that $\lie{osp}(6|2)$ sits inside of the eleven-dimensional theory on this space as symmetries.
+We denote by $(t,z)$ coordinates along the brane and $(w_1,\ldots,w_4)$ the holomorphic coordinates transverse to the brane.
+%\[\mf{osp}(6|2)\to H^\bullet \left ( \Pi \mc E^N_{AdS_4} \left ( \til Z \right ) \right ).\]
 
-We first focus on the case where the flux $N=0$. In this case, we will show that the embedding factors through the natural restriction map from the theory on flat space
+We first focus on the case where the flux is zero $N=0$. 
+%In this case, we will show that the embedding factors through the natural restriction map from the theory on flat space.
 
-\[ 
-\begin{tikzcd}
-& H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
-\mf{osp}(6|2)\ar[ur, "i_{M2}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )
-\end{tikzcd}
-\]
+%\[ 
+%\begin{tikzcd}
+%& H^\bullet \left ( \Pi \mc E (R\times \C^5)\right )\cong\widehat{E(5|10) }\ar[d, "\mr{res}"] \\
+%\mf{osp}(6|2)\ar[ur, "i_{M2}"]\ar[r] & H^\bullet \left ( \Pi \mc E^0_{AdS_4} \left ( (\R\times \C) \times \C^4\setminus \{0\} \right ) \right )
+%\end{tikzcd}
+%\]
 \parsec[]

### 2023-06-09 graviton spectra/content/e16.tex
adressed orange comments, modules in conjecture 4.11

@@
 
-\subsection{The lowest pieces and 3d $\mc N=8$ BLG theory}\label{sec:BLG}
+\subsection{The lowest pieces and minimally twisted rank 1 ABJM}\label{sec:BLG}
 \parsec[] The first nontrivial case is the weight ${(-2)}$ piece. We have the following
@@
 We wish to flag an appearance of $\mc F^{(-1)}_{\R\times \C}$ in supersymmetric physics in three-dimensions.
-There is a highly supersymmetric Chern-Simons-matter theory discovered independently by Bagger-Lambert \cite{Bagger_2007}, \cite{Bagger:2007jr} and Gustavsson \cite{Gustavsson:2007vu}.
-The aptly named BLG theory has $\mc N=8$ superconformal symmetry, and admits a holomorphic-topological twist that was characterized by Garner in \cite{Garner2022vds}.
+There is a highly supersymmetric Chern-Simons-matter theory discovered by \cite{} which describes the low-energy dynamics of a single M2 brane probing the origin in $\C^4$.
+The aptly named ABJM theory has a manifest $\mc N=6$ superconformal symmetry, and admits a holomorphic-topological twist that was characterized by Garner in \cite{Garner2022vds}.
+Non-perturbatively, it has an $\mc N=8$ superconformal symmetry, the enhancement to which is furnished by monopole operators.
 
-The sheaf of complexes $\mc F^{(-1)}_{\R\times \C}$ matches the field contents of the holmorphic-topological twist of the BLG theory, and as such, it can be equipped with an $L_\infty$ structure under which it is perturbatively equivalent to the twisted BLG theory.
-In work-in-progress with Garner and Williams, we show that the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ in fact preserves this $L_\infty$-structure.
-
-\brian{it's an abelian L-infinity structure right? So we can just say complexes.}
-
-\surya{i thought the BLG theory has a quartic superpotential.}
-
-\brian{The thing we don't mention so much is the BV structure.}
-
-\brian{I think we can at least comment that the BV structure comes from the BR.}
+The sheaf of complexes $\mc F^{(-1)}_{\R\times \C}$ matches the field contents of the holmorphic-topological twist of the rank 1 ABJM theory at level 1.
+In work-in-progress with Garner and Williams, we explicate the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ at the level of local operators in terms of currents.
+As we describe in the next subsection, the infinity jets at the origin of $\mc F^{(0)}_{\R\times \C}$ contain a copy of the minimally twisted three-dimensional $\mc N=8$ superconformal algebra.
+In keeping with the fact that the rank 1 level 1 ABJM theory only admits three-dimensional $\mc N=8$ superconformal symmetry after taking into account monopoles, we see that the currents realizing the $\mc F^{(0)}_{\R\times \C}$ action involves monopoles.
+The fact that the action is manifest from the perspective of this paper articulates a sense in which perturbative gravity may contain information about non-perturbative brane dynamics.
 
@@
 \brian{simplify last line so it is obviously a vector field}
-
+\surya{isnt the last line an $\mf{sl}_4$ current ?}
 \brian{Choose $\d z^{-1/2}$ or $\del_z^{1/2}$}
@@
 \subsection{General summands and $E(1|6)$-modules}
-We now move on to giving an explicit description of the general summand $\mc F^{(j)}$ for $j \geq 1$.
+We now move on to giving an explicit description of the general summand $\mc F^{(j)}_{\R\times \C}$ for $j \geq 1$.
+By proposition \ref{prrop:ads4decomp} the costalks $\mc F^{(j)}_{\R\times \C, c} (0)$ are $E(1|6)$-modules.
+A full classification of irreducible $E(1|6)$-modules is incomplete.
+Nevertheless, we expect the modules we find are irreducible.
+
+\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}
 
@@
 Note that the decomposition of the state space $\Sym (\mc H_{AdS_4} ) = \prod_{j\geq -2} \mc U (\mc F^{(j)} _{\R\times \C} )(0)$ gives a product formula for the characters computed in proposition \ref{prop:ads4index}
-
-\brian{Might be useful to point out that a systematic characterization of irreps of $E(1|6)$ is incomplete.}
-
-\brian{But, we expect the modules appearing above to be irreducible.}
 
@@
 (2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}.
+In \cite[Table 9]{cordova2016multiplets} these representations are examples of short representations labeled $B_1(0)_{\Delta}^{(R_1,\cdots, R_4)}$.
+Here the superscripts and subscript denote the $\mf{so}(8)_R$ weights and scaling dimensions of a superconformal primary respectively.
+
+\surya{we should pin down what values of $\Delta, R_i$ appear for us}
+
 Comparison with the above expansion suggests the following conjecture

### 2023-06-09 graviton spectra/content/e36.tex
adressed orange comments, modules in conjecture 4.11

@@
 were $U_{-1}$ is a $\C$-extension of $\tilde U_{-1}$ defined in the decomposition \eqref{eqn:decomp1} and for $j \geq 0$ the $U_j$'s are the same as in the non centrally extended case.
-As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible \surya{is this last sentence actually true?
+As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible \surya{is this actually a corollary?
 these aren't the same modules}

### 2023-09-08 graviton spectra/content/e16.tex
merg

@@
 
-\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}
+%\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}
 
@@
 
-\surya{we should pin down what values of $\Delta, R_i$ appear for us}
-
 Comparison with the above expansion suggests the following conjecture
@@
 \begin{conj}\label{conj:e16gravitonrep}
-For $j\geq -1$, the minimal twist of the $(j+2)$-weight graviton representation in \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy} is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$. 
+For $j\geq -1$, the minimal twist of the $(j+2)$-weight graviton representation in \cite[Eq.
+(2.15, 2.16)]{Bhattacharya:2008zy} (denoted $B[0]_{j/2+1}^{(0,0,0,j+2)}$ in \cite{cordova2016multiplets}) is exactly $\mc F^{(j)}_{\R\times \C, c}(0)$.
 \end{conj}
@@
 This can be thought of as analogous to the enhancement of conformal symmetries to the action of the Witt algebra of vector fields in 2d chiral conformal field theory.
-Such symmetry enhancements in 3 dimensions is the topic of joint work in progress with Garner and Williams.
+Such symmetry enhancements in 3 dimensions is discussed in \cite{GRW}.
 \end{rmk}

### 2023-09-20 index 2/intro.tex
index rewrite, intro

--- 2022-10-14 fivebranes/intro.tex
@@
 \section{Introduction}
-Superconformal field theories admit a plethora of exactly computable, protected quantities, giving them a distinguished role in supersymmetric physics. 
-Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories. 
-Examples of such a quantity is the superconformal index, which is a generating function for some collection of $R$-charges of certain BPS local operators. 
-Crucial steps towards a more mathematical understanding of superconformal indices were taken in \cite{SWchar}, articulated through the construction of twisting.
+Superconformal field theories admit a plethora of protected quantities that can be computed exactly at weak coupling.
+One such quantity is the superconformal index, which in a Hamiltonian formulation of the theory can be thought of as a Witten-index in radial quantization.
+Schematically, such a quantity takes the form \[\operatorname{Tr} _{\mc H} \left ( (-1)^F \exp (-\beta \{ Q, \overline Q\} ) x_1^{J_1}\cdots x_n^{J_n}y_1^{H_1}\cdots y_n^{H_n} \right )\] where $(-1)^F$ is the fermion number operator, $\beta$ is an inverse temperature, $Q$ is a supercharge and the $x_i$ are fugacities keeping track of charges under angular momenta, and $y_i$ are fugacities keeping track of charges under R-symmetries.
+The superconformal index gives a generating function for the difference between bosonic and fermionic states annihilated by a particular supercharge.
+Under an operator-state correspondence, the superconformal index can also be thought of as a signed count of local operators preserved under a single supercharge.
 
-Introduced by Witten \cite{WittenTwist} and further developed by Costello \cite{CostelloHol}, twisting refers to a localization, or fixed-point, construction for theories equipped with an action of a supersymmetry algebra.
-Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge---the result is a theory for which the infinitesimal translations in the image of the nilpotent supercharge act homotopically trivially.
-When a twist exists (which is almost always) a supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.
+In terms of partition functions, the superconformal index is gotten by a partition function on a twisted product $M_{1} = S^{1}\times_\omega S^{d-1}$ where the twisting $\omega$ is determined by a background connection for the global symmetries of the problem.
+Prefactors of exponentiated casimir energies that appear in the partition function are accounted for by central charges which appear in the action of angular momenta on $\mc H$.
+In superconformal field theories with a holographic dual, one expects a recapitulation of the superconformal index in gravitational terms.
 
-One of the insights of \cite{SWchar} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the space of local operators in the minimal twist as categorifying the index.
-Moreover, the space of local operators, together with its algebra structure under operator product expansion, is part of the richer structure of a \textit{factorization algebra}.
-Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set including for example, non-local operators obtained from local ones via a descent procedure.
+In this article, we revisit the problem of computing the superconformal index of the nebulous six-dimensional superconformal field theory of type $A_{N-1}$ from its holographic dual, eleven-dimensional supergravity on $AdS_7\times S^4$.
+Recently, we identified a twisted avatar of the $AdS_7\times S^4$ background conjecturally furnished by a $\frac{1}{16}$-BPS field configuration in the physical theory.
+This background admits an asymptotic symmetry by the infinite dimensional exceptional simple super-Lie algebra $E(3|6)$ and we propose that the full superconformal index ought to be an $E(3|6)$-character.
 
-A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories.
-The full factorization structure is extremely rich, and in this paper we only discuss a small part of it, namely the costalk at a point as a vector space.
-This is otherwise known as the space of local operators at the point. 
-However, this information is enough to extract familiar quantities like the superconformal index.
+\parsec[]
+Let us recall the interpretation of superconformal indices offered by the AdS/CFT dictionary.
+traditional formulations of the AdS/CFT correspondence relate two theories, schematically denoted $T_{CFT}$ and $T_{grav}$ on manifolds $M_{1}, M_{2}$ respectively, together with a conformal diffeomorphism $\del M_{2}\cong M_{1}$.
+The theories have the feature that boundary values of fields of $T_{grav}$ denoted $\phi |_{\del}$, may be identified with sources for $T_{CFT}$ denoted $J$.
+The two theories are considered to be holographically dual when their partition functions are equivalent $Z_{CFT}[J] = Z_{grav}[\phi |_{\del}]$.
+In examples of stringy origin, $T_{CFT}$ describes the low energy dynamics of a stack of $N$ branes in supergravity, in the large $N$ limit, and $T_{grav}$ describes gravitational dynamics in the background the branes source.
+In such examples, the gravitational counterpart of the superconformal index involves summing over geometries which asymptote to $AdS_{d+1} \times K$, where $K$ is compact and the conformal boundary of $AdS_{d+1}$ is identified with $S^1\times_\omega S^{d-1}$.
+An exciting body of work aims to make this gravitiational incarnation precise, see for example \cite{murthy2020growth} and references therein.
 
-%Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction.
-Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.
+Note that by definition, the superconformal index provides a lower bound on the number of fractionally BPS states of $T_{CFT}$.
+It is often the case, however, that $T_{grav}$ includes in its spectrum, black holes, which are expected to have a thermodynamic entropy proportional to the event-horizon-area at leading order, as given by the Bekenstein-Hawking formula.
+As such, the growth of states in $T_{CFT}$, and hopefully the superconformal index, should reflect this.
 
-%and three-dimensional $\cN=8$ superconformal field theories. 
-Despite its ubiquity, the six-dimensional~$\cN=(2,0)$ supersymmetric theory is quite elusive---it admits no known Lagrangian formulation, and outside of the abelian case, is not known to admit a field theoretic realization.
-In light of this, we propose to access the minimal twist and its local operators via the proposal of \textit{twisted holography}.
+\parsec[]
+Another protected quantity of a superconformal field theory is the algebra of BPS local operators.
+The vector space underlying this algebra is precisely a costalk of the factorization algebra of observables of a twist.
+In light of the aforementioned operator-state correspondence, this can be thought of as categorifying the superconformal index.
+For theories with a holographic dual, local operators of $T_{CFT}$ are supposed to match with certain kinds of states in $T_{grav}$.
 
-\subsection{Our approach via twisted holography}
-Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of supersymmetric twists.
-Fundamentally, it conjectures a duality between the algebra of observables of a twisted gravitational theory and the algebra of observables of a twisted gauge theory describing the dynamics of a stack of branes coupled to the gravitational theory.
+Moreover, both kinds of objects transform in representations of a superconformal algebra and the map between them preserves the actions.
+Local operators in the CFT are equipped with an interesting algebraic structure given by operator-product-expansion, and the AdS/CFT correspondence intertwines this algebraic structure with scattering of supergravity states.
+Indeed, the equality of partition functions along with the matching of sources for CFT local operators with boundary values of gravitational fields gives a prescription for computing correlation functions between CFT local operators by varying the gravitational action evaluated on field configurations subject to certain boundary values with respect to the boundary value.
+This recipe can be recast as a tree-level computation in the gravitational theory, involving computation of so-called Witten diagrams.\cite{WittenAdS}.
+
+\subsection{Twisted holography}
+Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of factorization algebras associated to supersymmetric twists of $T_{CFT}$ and $T_{grav}$.
 There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory sides.
 
-To describe the kinds of theories on either side of the correspondence, we should comment on what it means to twist a theory of supergravity.
-We will provide more details in \S \ref{s:twisted}.
-Since the action of supersymmetry is gagued in theories of supergavity, the aforementioned twisting procedure does not quite make sense.
-Instead, Costello and Li define twisted supergravity to be the theory in perturbation theory around a background where the bosonic ghost for local supertranslations takes a nonzero nilpotent vacuum expectation value.
-Coupling the worldvolume theory of a brane to such a background has the effect of twisting the worldvolume theory in the usual sense.
+\parsec{}
+Concretely, the twisted holography proposal suggests that the type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
 
-It is expected that the six-dimensional $\cN=(2,0)$ superconformal field theory of type $A_{N-1}$ describes the low energy dynamics of a stack of fivebranes in M-theory on flat space.
-Accordingly, there is a minimal twist of the low energy limit of M-theory, eleven-dimensional supergravity, which induces the minimal twist on a stack of fivebranes.
-We will be interested in a twisted version of the $AdS_{7}/CFT_{6}$ correspondence which will relate the large $N$ limit of the minimally twisted six-dimensional $\cN=(2,0)$ theory with minimally twisted eleven-dimensional supergravity on $AdS_{7}\times S^{4}$.
-
-The twisted holography propoosal moreover posits that holography can be understood as a concrete algebaic operation at the level of observables.
-We mentioned that the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra.
-The predicted type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
 Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to an (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
-Following the work of \cite{CLsugra,CP1} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
+Following the work of \cite{CLsugra, Costello_2021, CostelloM2} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
 If $A$ is the algebra of operators of some bulk quantum field theory (perturbatively we can even consider a theory of gravity) then $A^!$ is the algebra of operators on the universal topological line defect.
@@
 
-The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so in this paper.
+The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so here, but see \cite{LurieHA} for the case of $\mb E_n$-algebras and  \cite{gui2022quadratic}, \cite{tamarkin2003deformations} for the case of particular kinds of vertex algebras.
 This sort of duality would allow one to make sense of universality statements as above for higher dimensional, possibly non-topological, defects in an arbitrary bulk quantum field theory.
-Nevertheless, we can make the following ansatz for the Koszul dual $\cF^!$, which we refer to as the $!$-dual in this paper to avoid confusion, of a factorization algebra~$\cF$ of observables of some bulk quantum field theory.
-It is the universal factorization algebra, along a specified defect, which couples to the bulk quantum field theory.
-While this heuristic definition sounds natural, it does not lend itself to an explicit description.
-However, for particular kinds of factorization algebras of bulk quantum field theories an explicit description is furnished by a local version of Noether's theorem, see~\S\ref{s:noether}.
+Roughly, one expects the Koszul dual of a factorization algebra to be the factorization algebra corepresenting the functor of looking at solutions to a Maurer-Cartan equation in a tensor product.
 
+\parsec{}
 Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
 Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
-Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{N-branes}$.
-In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebras $\Obs_{N-branes}$.
+Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{CFT}^N$.
 
-Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{N-branes}$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
-We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}
+Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{CFT}^N$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
+We can, however, attempt to restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.
 
-\begin{expect}[Twisted holographic principle following \cite{CLsugra}]
-After taking into account the backreaction, there is a map of factorization algebras
+\begin{expect}[Twisted holographic principle following \cite{CLsugra}]\label{twistedholog}
+There is a map of factorization algebras
 \[
-  (\Obs_{grav}|_{Y})^{!}\to \Obs_{N-branes}
+  (\Obs_{grav}|_{Y})^{!}\to \Obs_{CFT}^N
 \]
@@
 
-It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS.
-A precise relation will be articulated in \S\ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry.
-Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.
+As we recalled in the previous subsection, traditional formulations of the AdS/CFT correspondence relate local operators of the gauge theory to states of the gravitational theory on AdS.
+Therefore, a natural desideratum in relating the above to more traditional statements is a precise relation between the source of the above map and gravitational states in $AdS$.
+Moreover, there is an operational definition of the operator-product-expansion on the costalk of a Koszul dual factorization algebra which realizes the expectation that Koszul duality corepresents the functor taking Maurer-Cartan elements in the tensor product.
+Another desideratum is to relate the output of this procedure with the scattering product on gravitational states computed by Witten diagrams.
 
-The above expectation can be tested in instances where both sides of the duality admit explicit descriptions.
-This has been carried out in many examples including:
+\begin{rmk}
+In this context, the definition of Koszul duality involves another ingredient, namely the backreaction of branes wrapping $Y$.
+This is meant to capture the fact that $(\Obs_{grav}|_Y)$ may not be canonically augmented, but we may try to deform it in a way that kills off the obstruction to being augmented.
+More precisely, one expects that the correct version of Koszul duality for application in holographic contexts is a version of \textit{curved} Koszul duality for factorization algebras.
+\end{rmk}
+
+\begin{rmk}
+For finite $N$, this map will in general be neither injective nor surjective.
+The kernel and cokernel of this map for finite $N$ correspond to interesting nonperturbative effects in the gravitational theory.
+For instance, in gauge theories:
+
+\begin{itemize}
+\item This map has a kernel given by trace relations.
+Syzygies between trace relations are conjecturally related to the worldvolume theories of certain other branes in the gravitational theory, so-called \textit{giant gravitons} \cite{Gaiotto:2021xce}, \cite{choi2023quantum}, \cite{Imamura} \footnote{We thank Ji-Hoon Lee for conversations related to this topic}
+
+\item This map also has a cokernel.
+By fiat, these are classes that exist in the finite $N$ cohomology of the observables of a gauge theory that are not in the image of the natural map from the large $N$ theory.
+Recent developments in cohomological approaches to counting quantum microstates of $\frac{1}{16}$-BPS black holes in $AdS_5\times S^5$ \cite{choi2023quantum} \cite{Chang_2023} \cite{Chang_2013} can be cast as trying to characterize the cokernel of a specific example of this map.
+\end{itemize}
+\end{rmk}
+
+\parsec[]
+The above expectation can be tested in instances where both sides of the duality admit explicit descriptions. This has been carried out in many examples including:
 \begin{itemize}
@@
 The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{costello2021twisted}.
-This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\cN=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$.
-Here, the duality is formulated in terms of vertex algebras which are avatars of holomorphic factorization algebras on a Riemann surface.
+This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\mc{N}=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$.
+Here the duality can be formulated in terms of vertex algebras.
 
-  \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory.
-Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace \cite{CP}.
-The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.
-
-  \item Membranes and fivebranes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}.
-In the particular $\Omega$-background, membranes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality.
-Moreover, the $\Omega$-background localizes fivebranes to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra.
-The holomorphic factorization algebras we seek in the present paper may be thought of as enhancements of these vertex algebras to three-complex dimensions.
+  \item M2 branes and M5 branes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}.
+In the particular $\Omega$-background, M2 branes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality.
+The koszul dual algebra bears close relations to the spherical Cherednik algebra.
+The $\Omega$-background localizes M5 to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra.
+Many celebrated features of the representation theory of these algebras and their relations with geometry have found natural explanations from the perspective of this twist of M-theory \cite{gaiotto2020miura}, \cite{Oh:2021wes}.
 \end{itemize}
 
-In each of the above examples, there exist methods to characterize both sides of the duality independently and intrinsically.
-Indeed, conjectures of \cite{CLsugra} suggest that certain twists of type II superstrings are equivalent to certain topological strings.
-Utilizing such a description, one may characterize D-banes and associated open-string field theories in terms of categorical data.
+The example we consider is closely related to the second of these. \surya{more}
+\iffalse
+Indeed, there is an odd nilpotent element in $\mf{osp}(6|2)$, which we refer to as $S$ in the sequel.
+Using the inner action of $\mf{osp}(6|2)$ on our eleven-dimensional model on twisted $AdS_7\times S^4$ as identified in proposition \ref{prop:brads7}, $S$ affords a deformation of our model.
+This is the deformation considered in \cite{BeemEtAl}, and it induces a specialization of characters called the Schur limit.
+\fi
 
-For membranes and fivebranes in $M$-theory, in the nonminimal twist or its further $\Omega$-deformation, one may appeal to dimensional reduction arguments to give similar characterizations of the twisted subsectors of the relevant worldvolume theories.
+\subsection{M5 branes, holomorphy, and holography}
+Let us begin by spelling out the objects in expectation \ref{twistedholog} adapted to our setting.
 
-However, for the minimal twist, we are not so lucky.
-The dimensional reduction of the nonminimal twist will necessarily involve subtle, nonperturbative effects making an intrinsic characterization along the lines of the above more difficult.
-We will offer some speculations in this direction at the end of the section below.
+\begin{itemize}
+\item The 11d spacetime manifold $X$ is $\R\times \C^5$ and $Y$ is a copy of $\C^3$. 
+\item The factorization algebra $\Obs_{grav}|_{\C^3}$ has the feature that its semiclassical free limit is the factorization algebra denoted $\clie ^\bullet \left ( \Pi \Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4})\right )$ in definition \ref{defn:ads7states}.
+\item The factorization algebra $\Obs^N_{CFT}$ describes local observables in the minimal twist of the theory on a stack of $N$ M5 branes wrapping $\C^3$. 
+\end{itemize}
 
-Consequentially, rather than prove a version of the twisted holographic principle, the objective of this paper is to \textit{use} the twisted holographic principal to conjecture an explicit description of the factorization algebra associated to the worldvolume theory on a stack of minimally twisted fivebranes.
-Such an analysis reveals that twists of worldvolume theories of branes enjoy certain infinite dimensional symmetries, enhancing finite dimensional symmetries present in the untwisted theories.
-In the minimal twist of eleven dimensional supergravity, these infinite dimensional symmetries are provided by certain exceptional simplie lie superalgebras.
+Our goal is to try and use this map, and expectations about its kernel and cokernel, to give a concrete description of the target.
+There have been various approaches to try and characterize the spectrum of $\frac{1}{16}$-BPS states in the 6d $\mc N=(2,0)$ theories of type $A_{N-1}$, which furnish consistency checks to test our proposal against.
+Some of these involve applications of instanton counting techniques in 5d $\mc N=2$ gauge theory \cite{Kim:2013nva} and some of them involve holographic techniques \cite{Imamura}.
 
+As we remarked in subsection \ref{bpsadscft}, the first ingredient is a map of representations of the superconformal algebra between local operators of the CFT and supergravity states.
+In order to codify such a matching in terms of the kinds of data in the statement of expectation \ref{twistedholog}, we require a matching between supergravity states and the costalk at the origin of the factorization algebra $(\Obs_{grav}|_{\C^3})^!$.
+
+\surya{need to add minimal recollections from graviton paper}
+\parsec[]
+
+We have the following conjectural large $N$ statements
+
+\begin{conj}[R-Saberi-Williams]\label{conj:classical}
+There is an equivalence of holomorphic $\mb{P}_0$-factorization algebras \[ \left( \clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a twisted factorization envelope of the local $L_\infty$-algebra $\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$.
+Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to a twisted factorization envelope of the local Lie algebra $\operatorname {Diff}_{\C}$ of holomorphic differential operators on $\C$.
+\end{conj}
+
+Here, the twisting cocycle $\omega$ comes from the shifted Poisson tensor that was induced by the flux in section \ref{sec:ads}.
+The content in verifying this conjecture is to explicitly compute the twisting coming from the flux sourced by the brane, and check that upon deforming by the element $S$, it induces the correct cocycle on $\operatorname{Diff}(\C^\times)$
+
+The comment in \ref{eqn:winfty} constitutes a very meager consistency check for the second part of this conjecture, where we observe that the Schur limit of the character of the costalk of $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} ) \right)$ recovers the vacuum character of the $W_{1+\infty}$ vertex algebra.
+
+There is a deformation of the twisted factorization envelope of $\operatorname{Diff}_\C$ which yields the $\mc W_{1+\infty}$ vertex algebra, also referred to as the affine Yangian of $\mf {gl}(1)$.
+In \cite{CostelloM5}, Costello finds this deformation from a loop level computation in his 5d noncommutative gauge theory.
+We also expect to be able to lift this to the minimal twist.
+We summarize this expectation in a conjecture.
+
+\begin{conj}[R-Saberi-Williams]
+There is an equivalence of holomorphic factorization algebras \[ \left( \clie^\bullet_\hbar (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a deformation of the factorization algebra in the previous conjecture induced by loop-level effects in our eleven-dimensional model.
+Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to the $\mc {W}_{1+\infty}$ vertex algebra.
+\end{conj}
+
+\parsec[]
+We now move on to finite $N$ statements. For the lowest steps of the filtration, we can make some very concrete statements.
+
+\begin{conj}[R-Saberi-Williams]
+Upon deforming by $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_\omega (\mc G^{(-1)}_{\C^3} )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Heisenberg vertex algebra.
+\end{conj}
+To check this conjecture, it remains to compute the pullback of the twisting cocycle $\omega$ under the inclusion of $\mc G^{(0)}$ and see that it deforms to the Heisenberg cocycle.
+
+\parsec[]
+There is a distinguished Lie sub-algebra of the algebra of differential operators on $\C^\times$ which is given by the Witt-algebra of vector fields.
+The central extension of $\operatorname{Diff} (\C^\times)$ induced by $\omega$ above restricts to the Virasoro central extension.
+Similarly, in proposition \ref{prop:g0e36} we have identified a distinguished local super-Lie algebra inside $\Pi\Omega^{0,\bullet} _{\C^3}(\mc L^{r=0} _{AdS_7\times S^4} )$ given by $\mc E(3|6)$.
+
+Accordingly, we conjecture the following
+\begin{conj}[R-Saberi-Williams]
+Upon deforming by $S\in \mf{osp}(6|2)$, the factorization algebra $\mc U_\omega( \mc E(3|6) )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Virasoro vertex algebra.
+\end{conj}
+
+Again, to check this conjecture it remains to compute the pullback of the twisting cocycle $\omega$ along the inclusion $\mc E(3|6)\to \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ and compare its deformation with the cocycle giving the Virasoro central extension.
+
+We can once again perform a consistency check at the level of characters of costalks.
+Indeed, we see that the plethystic exponential of the specialized character $g_0(y=1, y_3=1, q) = \frac{q^2}{1-q}$ is exactly the vacuum character of the Virasoro algebra.
+
+Moreover, note that combining with conjecture \ref{conj:classical}, we expect maps 
+\[\mc U_\omega( \mc E(3|6) )\to \left (\clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!
+\to \Obs^N_{CFT}\] for every $N$.
+This map can be thought of as a Noether-type map associated to an  $\mc E(3|6)$-symmetry of the minimal twist of any finite rank 6d $\mc N=(2,0)$ theory \cite{CG2}.
+
+\parsec[]
+More generally, the $\mc W_{1+\infty}$ algebra has as quotients, the $\mc W_N$ algebras when the central charge is set equal to $N$. Accordingly, we dream of the following:
+
+\begin{spec}
+Under an integrality condition on the central charge, the map \[ (\Obs_{grav} |_{\C^3} )^! \to \Obs^N_{CFT}\] factors as
+\[
+\begin{tikzcd}
+(\Obs_{grav} |_{\C^3} )^! \ar[r]\ar[d]  & \Obs^N_{CFT} \\
+\mc U_{\hbar, \omega} (\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))/\mc U_{\hbar, \omega} (\prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3} ) \ar[ur]
+\end{tikzcd}
+\]
+\end{spec}
+
+We can perform a consistency check of the above speculation at the level of characters of costalks.
+It is expected that the superconformal deformation deforms $\Obs^N_{CFT}$ to the $\mc{W}_N$ vertex algebra.
+On the other hand, we have that
+
+\begin{prop}
+Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$), one has
+
+\begin{align*}
+\chi \left ( \Omega^{0,\bullet}_{\C^3,c} (\mc L^N_{AdS_7\times S^4})(0)/ \left ( \mc G^{(-1)}_{\C^3,c}\times \prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3,c}\right )(0)\right ) & = \sum_{j \geq 0}^{N-2} g_j (y_1,y_2, y_3=1,y=1,q) \\
+& = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
+\end{align*}
+
+The plethystic exponential of the right hand side agrees with the vacuum character of the $W_{N}$ vertex algebra.
+\end{prop}
+\begin{proof}
+By induction it suffices to show that the specialization of the single particle local character $g_j$ of the factorization algebra $\mc U(\mc{G}_{\C^3}^{(j)})$ is $q^{j+2} / (1-q)$. 
+We have already seen this in the case $j=-1,0$, so it suffices to show this when $k \geq 1$.
+
+First observe that the denominator becomes
+\begin{equation}
+(1-y_1 q)(1-y_2q) (1-q) .
+\end{equation}
+
+Next, we observe that the numerator of $g_j (y_1,y_2,y_3=1,y=1,q)$ can be factored as
+\begin{align*}
+q^{3 + 3j/2} \left(q^{-(j+2)/2} + q^{-(j-2)/2} - q^{-j/2} (y_1+y_2) \right) 
+& = q^{j+2} (1 + q^2 - q (y_1 + y_2)) \\
+& = q^{j+2} (1 - y_1 q) (1-y_2 q) 
+\end{align*}
+where in the last line we have used $y_1 y_2 = 1$.
+The result follows.
+\end{proof}
+
+\parsec{}
+In this article, we analyze the discrepancy between the characters of $\mc U (\mc G^{(j)}_{\C^3})$ and expectations about the superconformal index of the finite rank 6d $\mc N=(2,0)$ theories computed via instanton counting techniques \cite{Kim:2013nva} and the "giant graviton expansion" \cite{Arai_2020, Imamura}.
+We propose that the discrepancies can be categorified by modules for $E(3|6)$.
+
+\surya{haven't edited below}
 \subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}

### 2023-12-15 index 2/intro.tex
agt

@@
 We propose similar statements at the level of the minimal twist. 
-We fix a complex surface $S$ together with a pair of complex vector bundles $L,W \to S$ of ranks one and two respectively, satisfying the condition that $X = \text{Tot} (L \oplus W)$ is a Calabi--Yau fivefold.
+We fix a complex surface $S$ together with a triple of complex line bundles $L, L_1, L_2\to S$ satisfying the condition that $X = \text{Tot} (L \oplus L_1 \oplus L_2)$ is a Calabi--Yau fivefold. 
 The twisted eleven-dimensional supergravity lives on the eleven-manifold $\R \times X$.
@@
 The pushforward factorization algebra $\pi_{*}\Obs_{1}$ is a stratified factorization algebra on the non-negative half-line $\R_+ = \{t \geq 0\}$.
-We can tweak this factorization algebra slightly which gives rise to a constructible factorization algebra on $\R_+$.
-In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle) together with a module for this algebra.
+
+In turn, this is equivalent to a pair of an associative algebra (which may be thought of as the algebra of modes of $\Obs_{1}$ along the five-manifold which is the total space of the unit sphere bundle in $L$) together with a module for this algebra.
 
@@
 agrees with the factorization algebra associated to the minimal twist of five-dimensional $\cN = 2$ supersymmetric Yang--Mills theory on $\R\times M$ for the group $U(1)$ in perturbation theory around the zero instanton sector.
+Keeping track of Kaluza-Klein modes, one expects that the dimensional reduction $\pi_{*}\Obs_{1}|_{\R_{>0}}$ receives contributions from instanton operators codified by way of a certain Chern-Simons term.
+Let us explicate how these contributions manifest in the dimensionally reduced factorization algebra.
 
-If we keep track of Kaluza--Klein modes, our expectation is that the full dimensional reduction $\pi_{*}\Obs_{1}|_{\R_{>0}}$ includes contributions from instanton operators.\footnote{The instanton charge turns out to be identical to the winding number around $S^1$.} Moreover, the module at zero $\pi_{*}\Obs_{1}|_{0}$ ought to be identified with the Hilbert space of the minimal twist of five-dimensional $\cN = 2$ gauge theory.
-We are left with the following conjecture.
+Nonperturbatively, five-dimensional $\cN=2$ super Yang-Mills has a topological $U(1)$ symmetry, charges under which are instanton number.
+This charge can be measured by introducing a background gauge field $\theta$ for this symmetry and adding a Chern-Simons term of the form
+\[
+\int Tr (\theta\wedge F\wedge F) = \int c_1 (L) \wedge CS (A)
+\]
+ to the action, where $F$ is the curvature of the five dimensional gauge field $A$ and $CS(A)$ denotes the corresponding Chern-Simons three-form.
+An ingredient in identifying the dimensional reduction of the six-dimensional $\cN=(2,0)$ theory on a circle with five-dimensional $\cN= (2,0)$ is an identification of the above $U(1)$-charge with one keeping track of Kaluza-Klein modes along the circle fiber of $Z \to S\times \R_{>0}$.
+Accordingly, the dimensional reduction along the circle fiber of a nontrivial line bundle will include the above term in the action.
+
+We claim that this term crucially enters into the description of the module at zero $\pi_{*}\Obs_{1}|_{0}$.
+This module ought to be identified with the Hilbert space of the minimal twist of five-dimensional $\cN = 2$ gauge theory, which can be calculated by geometrically quantizing the phase space.
+We will see that the phase space can naturally be written as a twisted cotangent bundle, where the twist depends on the above Chern-Simons term.
+
+Perturbatively, the phase space is described by the following local Lie algebra. 
+\beqn
+\begin{tikzcd}
+\underline{-2} & \underline{-1} & \underline{0} \\
+& \Omega_S^{0,\bullet}\arrow[dd, "c_1(L)\wedge\partial"] & \\
+\Omega_S^{0,\bullet}(L_2)& & \Omega^{0,\bullet}_S(L_1\otimes L_2) \\
+& \Omega_S^{0,\bullet}(K_S)  &
+\end{tikzcd}
+\eeqn
+
+We thus see that the phase space has a natural polarization whose base is given by $\Omega^{0,\bullet}_S(L_2)[2] \oplus \Omega^{0,\bullet}[1]$.
+The differential made explicit deforms the symplectic structure to that of a twisted cotangent bundle.
+
+Globally, we can describe an algebro-geometric model for the polarized phase space as 
+\[
+T^*_\Pi \operatorname{Higgs} _{GL(1)} (S, L_2)
+\]
+where $\operatorname{Higgs}_{GL(1)} (S, L_2)$ is the moduli of pairs of a rank 1 torsion free sheaf $Z$ on $S$ and a section $\phi \in \Gamma (Z\otimes L_2)$.
+We will call these \textit{rank 1 $L_2$ twisted Higgs sheaves}.
+Letting $TFS_1(S)$ denote the moduli of rank 1 torsion free sheaves on $S$, there is a natural projection
+\[\operatorname{Higgs}_{GL(1)} (S, L_2)\] and a diagram
+\beqn
+\begin{tikzcd}
+S\times TFS_1 (S)\ar[r, "\pi_2"]\ar[d, "\pi_1"] & TFS_1 (S) \\
+S
+\end{tikzcd}
+\eeqn
+The global symplectic form on the phase space is given by 
+\[
+p^*{\pi_2}_*\left (\pi_1^* c_1 (L) \wedge ch_2 (Z_{univ})\right )
+\]
+where $Z_{univ}$ denotes the universal rank 1 torsion free sheaf.
+
+We are thus left with the following conjecture.
 
@@
 \label{conj:AGT1}
-Let $\operatorname{Higgs}_{GL(1)} (S,W)$ denote the moduli space of $GL(1)$ Higgs bundles on the complex surface $S$ where the Higgs fields has coefficients in the rank two bundle $W$.
-The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ that we have just discussed acts on the space of functions on this moduli space
+Let $\operatorname{Higgs}_{GL(1)} (S,L_2)$ denote the moduli space of rank 1 $L_2$-twisted Higgs sheaves on $S$. The mode algebra $\pi_{*}\Obs_{1}|_{\R_{>0}}$ acts on the coherent cohomology 
 \beqn
-\cO \left(\operatorname{Higgs}_{GL(1)} (S,W)\right) .
+H^\bullet \left(\operatorname{Higgs}_{GL(1)} (S,L_2), \Theta \right) .
 \eeqn
+of a certain line bundle $\Theta$ whose first chern class is the above symplectic form.
 \end{conj}
 
-We emphasize that the moduli space in question is really sensitive to the complex geometry of the entire fivefold $X$, at least in the neighborhood of the total space of~$L$.
-
-While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities.
+While we leave the precise relationship of this conjectural action with the usual abelian AGT correspondence to future work, we can highlight some compatibilities \surya{FINISH}.
 Above, we have mentioned a particular deformation of the observables of the six-dimensional $\cN = (2,0)$ theory by an explicit Maurer--Cartan element in the residual superconformal algebra $\lie{osp}(6|2)$.

### 2024-08-12 agt/survey.tex
agt

\documentclass[11pt]{amsart}

\usepackage{macros-master,amsaddr,physics,amssymb}

\addbibresource{refs}

\renewcommand{\div}{\del_{\Omega}}
\renewcommand{\PV}{\mathrm{PV}}
\renewcommand{\op}{\operatorname}

\setcounter{tocdepth}{1}

\begin{document}
\title{Notes on agt}
\maketitle

\section{The twisted brane construction}

We will use the fact that the minimal twist of $M$-theory exists on geometries of the form
\beqn
Z \times \R
\eeqn
where $Z$ is a Calabi--Yau fivefold.

We consider familiar extended objects, which in the twisted setting have the following flavor.
\begin{itemize}
\item[(M5)] Twisted fivebranes wrap an embedded threefold
\beqn
X \subset Z
\eeqn
with the property that $K_X \simeq \wedge^2 N_{X \subset Z}$ where $N_{X \subset Z}$ is the normal bundle to $X$ in $Z$.
\item[(M2)] Twisted membranes wrap the real line times an embedded curve $\Sigma \subset Z$:
\beqn
\Sigma \times \R \subset Z \times \R
\eeqn
with the property that $K_\Sigma \simeq \wedge^4 N_{\Sigma \subset Z}$.
\end{itemize}

Some special cases of such twisted geometries are worth addressing.

\begin{itemize}
\item[(1)] First, consider the following local fivefold geometry
\beqn
Z = \op{Tot} \begin{pmatrix} W \\ \downarrow \\ X \end{pmatrix} 
\eeqn
where $W$ is a rank two vector bundle on a threefold $X$, which satisfies $\wedge^2 W = K_X$.
The case $X = \C^3$ and $W = K^{1/2}_{\C^3} \otimes \C^2$.
The worldvolume theory on $\C^3$ in this geometry is the (minimal) holomorphic twist of six-dimensional $\cN=(2,0)$ supersymmetry.
More generally, if a threefold $X$ admits a square root of its canonical bundle $K^{1/2}_X$, then we can consider the geometry 
\beqn
Z = \op{Tot} \begin{pmatrix} K^{1/2}_X \otimes \C^2 \\ \downarrow \\ X \end{pmatrix} ,
\eeqn
with fivebranes wrapping the zero section $X \subset Z$.
\item[(2)]
Notice that in the above example there is a global $SU(2)$ symmetry.
We can break this to $U(1)$ by assuming that $W = L_1 \oplus L_2$ where $L_1,L_2$ are line bundles on $X$ satisfying $L_1 \otimes L_2 = K_X$.
Note that necessarily we have $L_2 = L^{-1} \otimes K_X$, $L=L_1$.
\item[(3)] Suppose that $Y$ is a Calabi--Yau threefold with an embedded holomorphic curve $C$, and $S$ is a Calabi--Yau surface.
Then $Z = Y \times S$ determines a twisted $M$-theory geometry with fivebranes that wrap 
\beqn
X = C \times S \subset Y \times S \times \R = Z \times \R .
\eeqn
\item[(4)]
As a special case of (3), consider the Calabi--Yau threefold
\beqn
Y = \op{Tot} \begin{pmatrix} \C \oplus \T^*_C \\ \downarrow \\ C \end{pmatrix} \simeq \C \times \T^* C ,
\eeqn
where $C$ is an arbitrary Riemann surface.
To phrase this as a special case of (2) one takes $W$ to be the rank two bundle obtained by restricting $\C \oplus \T^*_C$ along $C \times S \to C$.
In this geometry, one can allow for $C$ to have punctures.
The four-dimensional theory one obtains by compactifying the six-dimensional worldvolume theory of fivebranes along
\beqn
X = C \times S \to S 
\eeqn
in this geometry gives rise to the holomorphic twist of four-dimensional theories of class $\cS$ \cite{GaiottoS,GMN}.
\item[(5)] 
Again, as a special case of (3) (but more general than the last example), consider the Calabi--Yau threefold
\beqn
Y = \op{Tot} \begin{pmatrix} V \\ \downarrow \\ C \end{pmatrix} ,
\eeqn
where $V$ is an $SU(2)$ bundle over $C$.
Compactification along $X = C \times S \to S$ gives rise to holomorphic twists of four-dimensional superconformal theories \cite{BeemM5}.
This fits as a special case of (1) by taking $W$ to be the restriction of the bundle $V$ along the projection $X \to C$.
\end{itemize}

\section{Twisted fivebranes}

We will work in the generality of the geometry in (1) where the fivefold is of the form $\op{Tot}(W \to X)$ with $\wedge^2 W = K_X$.

The theory of a twisted fivebrane in this geometry admits the following description.
In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\mathbb{V})$ where $\mathbb{V}$ is the following super complex of holomorphic vector bundles
\beqn
\mathbb{V} \;\;\;\left\{
\begin{tikzcd}
& \ul{-1} & \ul{0} \\
\ul{\text{even}} & \Omega^2_X \ar[r,"\del"] & \Omega^3_X \\
\ul{\text{odd}} & \Pi W  
\end{tikzcd} \right.
\eeqn
We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$.

The Poisson BV structure is determined by\brian{finish}

\subsection{Five-dimensional supersymmetric Yang--Mills theory}

Let $S$ be a complex surface and $W$ a rank two vector bundle on $S$ satisfying $\wedge^2 W = K_S$.
Given any Lie algebra~$\lie{g}$ equipped with a non-degenerate invariant pairing, we consider the following $\Z \times \Z/2$ graded five-dimensional gauge theory which we refer to as generalized twisted five-dimensional $\cN=2$ Yang--Mills theory.

The fields are
\begin{itemize}
\item Hybrid $BF$ theory with fields
\begin{align*}
A & \in \Omega^{\bu}(\R) \otimes \Omega^{0,\bu}(S) \otimes \lie{g} [1] \\
B & \in \Omega^{\bu}(\R) \otimes \Omega^{2,\bu}(S)\otimes \lie{g} [1] .
\end{align*}
\item Hypermultiplet fields
\beqn
\phi \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) [1] .
\eeqn
In other words, $\phi^{0,0}$ is an odd field of cohomological degree $-1$.
\end{itemize}
The action functional is
\beqn
\int_{\R \times S} (B , F_A) + \frac12 \int_{\R \times S} (\phi, \dbar_A \phi) .
\eeqn

Alternatively, this theory is hybrid Chern--Simons theory associated to the cyclic, holomorphic, local Lie superalgebra
\beqn
\lie{g} \otimes \wedge^\bu W ,
\eeqn
where $\wedge^0, \wedge^2$ are even and $\wedge^1$ is odd.
Here, we view $\wedge^\bu W$ as a bundle of commutative super algebras.
Explicitly, the nonzero brackets $[-,-]$ in this Lie superalgebra is of the form
\begin{align*}
\lie{g} \otimes \wedge^0 W \times \lie{g} \otimes \wedge^0 W & \to \lie{g} \otimes \wedge^0 W  \\
\lie{g} \otimes \wedge^0 W \times \lie{g} \otimes \wedge^1 W & \to \lie{g} \otimes \wedge^1 W \\
\lie{g} \otimes \wedge^1 W \times \lie{g} \otimes \wedge^1 W & \to \lie{g} \otimes \wedge^2 W .
\end{align*}

The perturbative phase space on $S$ is the $\Z \times \Z/2$ even symplectic space
\beqn
\T^* \left( \lie{g} \otimes \Omega^{0,\bu}(S)[1] \right) \oplus \Pi \left(\lie{g} \otimes \Omega^{0,\bu}(S,W)[1] \right) .
\eeqn
A moduli theoretic interpretation of this is as follows.
%Consider the moduli stack $\op{Bun}_G(S)$ of holomorphic $G$-bundles on $S$.
%Let $\T^*_{\op{Bun}_G(S)}$ be its cotangent complex.
Consider the moduli of triples
\beqn
(P, \eta, \phi)
\eeqn
where $P$ is a holomorphic $G$-bundle on $S$, $\eta \in \Omega^{2,1}(S, \op{ad} P)$, and $\phi \in \Omega^{0,1}(S,\op{ad}(P) \otimes W)$ which satisfy \brian{equations}.

Let us now assume we have a polarization of $W = L_1 \oplus L_2$ into a sum of two line bundles on $S$ satisfying $L_1 \otimes L_2 = K_S$.
Without loss of generality we set $L = L_1$ and $L_2 = L^{-1} \otimes K_S$.
This allows us to consider a tilted (regraded) perturbative phase space\footnote{We should explain $\Pi W[1] \to L_2[2] \oplus L_1$.}
\beqn
\begin{tikzcd}
\ul{-2} & \ul{-1} & \ul{0} \\
& \Omega^{0,\bu}(S, \lie{g}) & \\
\Omega^{2,\bu}(S,\lie{g} \otimes L^{-1}) & & \Omega^{0,\bu}(S, \lie{g} \otimes L) \\
& \Omega^{2,\bu}(S, \lie{g}) & .
\end{tikzcd}
\eeqn
Then, the perturbative phase space of generalized, twisted, five-dimensional $\cN=2$ supersymmetric Yang--Mills theory can be written as
\beqn
\op{Higgs}_G (S,L) .
\eeqn
Here $\op{Higgs}_G (S,L)$ is the moduli stack of quadruples $(P,\varphi, \varphi^*,B)$ where $P$ is a holomorphic $G$-bundle,
\begin{align*}
\varphi & \in \Gamma(S, \op{ad}(P) \otimes L) \\
\varphi^* & \in \Omega^{2,2}(S, \op{ad}(P) \otimes L^{-1}) \\
B & \in \Omega^{2,1}(S, \op{ad} P) 
\end{align*}
satisfying
\begin{align*}
\dbar \varphi = \dbar \varphi^* & = 0 \\
\dbar B + [\varphi, \varphi^*] & = 0 .
\end{align*}
We can furthermore write this as a \textit{twisted} cotangent bundle to the moduli stack $\cM_{G}(S,L)$ of pairs $(P,\varphi)$ where $P$ is a holomorphic principal $G$-bundle and $\varphi \in \Gamma(S, \lie{g} \otimes L)$ satisfying $\dbar \varphi = 0$.
The twist is by the two form \brian{finish}.

\section{AGT statements}

Let $S$ be a projective surface and $L_1,L_2,L_3$ line bundles on $S$ satisfying 
\beqn
L_1 \otimes L_2 \otimes L_3 = K_S .
\eeqn
We consider a special case of the geometry (2) where the threefold that twisted fivebranes $X$ is of the form
\beqn
X = \op{Tot} \begin{pmatrix} L_3 \\ \downarrow \\ S \end{pmatrix},
\eeqn
and where $W = L_1 \oplus L_2$ (or rather, the restrictions of these line bundles to $X$).
In this case, the local Calabi--Yau fivefold geometry is $Z = \op{Tot}(L_1 \oplus L_2 \oplus L_3).$
\end{document}

### 2024-08-13 agt/survey.tex
survey

@@
 The theory of a twisted fivebrane in this geometry admits the following description.
-In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\mathbb{V})$ where $\mathbb{V}$ is the following super complex of holomorphic vector bundles
+In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
 \beqn
-\mathbb{V} \;\;\;\left\{
+\bV \;\;\;\left\{
 \begin{tikzcd}
@@
 \beqn
-\phi \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) [1] .
+\phi \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) \otimes \lie{g} [1] .
 \eeqn
@@
 Consider the moduli of triples
-\beqn
-(P, \eta, \phi)
+\beqn\label{eqn:pertphase1}
+(P, B, \phi)
 \eeqn
-where $P$ is a holomorphic $G$-bundle on $S$, $\eta \in \Omega^{2,1}(S, \op{ad} P)$, and $\phi \in \Omega^{0,1}(S,\op{ad}(P) \otimes W)$ which satisfy \brian{equations}.
+where $P$ is a holomorphic $G$-bundle on $S$, $\eta \in \Omega^{2,1}(S, \op{ad} P)$, and $\phi \in \Omega^{0,1}(S,\op{ad}(P) \otimes W)$ which satisfy 
+\begin{align*}
+\dbar \phi = 0 \\
+\dbar B + \frac12 [\phi,\phi] = 0 .
+\end{align*}
+The perturbative phase space in \eqref{eqn:pertphase1} is the tangent complex to this moduli stack at the trivial $G$-bundle (and $B = \phi = 0$).
 
@@
 \eeqn
-Then, the perturbative phase space of generalized, twisted, five-dimensional $\cN=2$ supersymmetric Yang--Mills theory can be written as
+Then, the perturbative phase space of generalized, twisted, five-dimensional $\cN=2$ supersymmetric Yang--Mills theory can be written as the moduli stack
 \beqn
@@
 \eeqn
-Here $\op{Higgs}_G (S,L)$ is the moduli stack of quadruples $(P,\varphi, \varphi^*,B)$ where $P$ is a holomorphic $G$-bundle,
+of quadruples $(P,\varphi, \varphi^*,B)$ where $P$ is a holomorphic $G$-bundle, and
 \begin{align*}
@@
 \end{align*}
-satisfying
+which satisfy
 \begin{align*}
@@
 \end{align*}
-We can furthermore write this as a \textit{twisted} cotangent bundle to the moduli stack $\cM_{G}(S,L)$ of pairs $(P,\varphi)$ where $P$ is a holomorphic principal $G$-bundle and $\varphi \in \Gamma(S, \lie{g} \otimes L)$ satisfying $\dbar \varphi = 0$.
-The twist is by the two form \brian{finish}.
+We can furthermore write this as the cotangent bundle to the moduli stack $\cM_{G}(S,L)$ of pairs $(P,\varphi)$ where $P$ is a holomorphic principal $G$-bundle on $S$ and $\varphi \in \Gamma(S, \lie{g} \otimes L)$ satisfying $\dbar \varphi = 0$.
+
+In this example, the Hilbert space of states coming from geometric quantization is functions on the base of this cotangent bundle
+\beqn
+\cO \left( \cM_{G}(S,L) \right) .
+\eeqn 
+Notice that when $L = K_S$ we have the Hilbert space
+\beqn
+\cO \left( \T[1] \op{Bun}_G(S) \right) \simeq \Omega^{\bu}(\op{Bun}_G(S)) .
+\eeqn
+
+\subsection{Chern--Simons deformation}
+
+Let $\omega \in \Omega^{1,1}(S)$ be a $(1,1)$-form on $S$ with the property that $\dbar \omega = 0$ and $\del \omega = 0$.
+In other words, $\omega$ defines an element in $H^1(S, \Omega^{1,cl})$.
+Then, consider the deformation of generalized twisted five-dimensional $\cN=2$ Yang--Mills theory defined by
+\beqn
+S_\theta = \frac12 \int_{\R \times S} \omega \wedge (A, \del A) .
+\eeqn
+Locally, we can find a primitive $\omega = \del \theta$ and this deformation takes the more symmetric form $\frac12 \int \theta \wedge (\del A, \del A)$.
+
+Turning on this deformation leads to the deformed perturbative phase space
+\beqn
+\begin{tikzcd}
+\ul{-2} & \ul{-1} & \ul{0} \\
+& \Omega^{0,\bu}(S, \lie{g}) \ar[dd,dotted,"\omega \wedge \del"] & \\
+\Omega^{2,\bu}(S,\lie{g} \otimes L^{-1}) & & \Omega^{0,\bu}(S, \lie{g} \otimes L) \\
+& \Omega^{2,\bu}(S, \lie{g}) & .
+\end{tikzcd}
+\eeqn
+A more invariant way to construct this perturbative phase space is the following.
+By transgression, we can view the invariant form as a one-form on the moduli stack $\op{Bun}_G(S)$ of cohomological degree $-1$.
+We can pull this one-form back to get a one-form on $S \times \op{Bun}_G(S)$ also of cohomological degree $-1$.
+Integration of this one-form against $\omega$ along the fibers of $S \times \op{Bun}_G(S) \to \op{Bun}_G(S)$ yields a two-form on $\op{Bun}_G(S)$ (of cohomological degree zero).
+We can, in turn, further restrict this to a two-form on $\cM_{G}(S,L)$ that we will abusively still denote by $\omega$.
+The phase space is then the twisted cotangent bundle
+\beqn
+\T_{\omega}^* \left(\cM_{G}(S,L) \right) .
+\eeqn
+
+\section{The abelian case}
+
+We will work in the generality of the geometry in (1) where the fivefold is of the form $\op{Tot}(W \to X)$ with $\wedge^2 W = K_X$.
+
+\subsection{Nakajima, Grojnowksi, and the Heisenberg vertex algebra}
+
+Assume that $S$ is a projective surface equipped with a rank two vector bundle $V$ satisfying $\wedge^2 W = K_S$.
+Consider the resulting twisted fivebrane worldvolume theory on $X = S \times C$ where $W = V \boxtimes K_C^{1/2}$ (here, we are assuming that $C$ is equipped with a spin structure).
+In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(S \times C,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
+\beqn
+\bV \colon \;\;\;\left\{
+\begin{tikzcd}
+& \ul{-1} & \ul{0} \\
+\ul{\text{even}} & \Omega^2_{S \times C} \ar[r,"\del"] & \Omega^3_{S \times C} \\
+\ul{\text{odd}} & \Pi p^* W  
+\end{tikzcd} \right.
+\eeqn
+We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$, as we did above.
+The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S,W}$.
+Its compactification, or factorization homology, along $S$
+\beqn
+\int_S \Obs_{S,W} 
+\eeqn
+is a holomorphic factorization algebra on $C$.
+On $C = \C$ this determines a vertex algebra that we denote $\VV_{S,W}$.
+
+We describe this vertex algebra explicitly.
+Notice that since $S$ is projective there is a quasi-isomorphism of sheaves on $C$:
+\begin{align*}
+\Omega^{2,\bu}_{S \times C} & \simeq H^{\bu} (S, K_S) \otimes \Omega^{0,\bu}_C  \oplus H^\bu(S, \Omega^1_S) \otimes \Omega^{1,\bu}_C \\
+\Omega^{3,\bu}_{S \times C} & \simeq H^{\bu} (S, K_S) \otimes \Omega^{1,\bu}_C  \\
+\Omega^{0,\bu}_{S \times C}(W \boxtimes K_{C}^{1/2}) & \simeq H^\bu(S, W) \otimes \Omega^{0,\bu}_C(K^{1/2}_C) .
+\end{align*}
+
+Suppose that $V$ is a graded vector space equipped with a graded symmetric pairing of total degree zero.
+Let $\{e_i\}$ be a basis for $V$.
+There is a vertex algebra $\cC\cB(V)$ generated by fields $e_i(z)$ of spin one and with OPEs
+\beqn
+e_i(z) e_j(w) \simeq \frac{(e_i,e_j)}{(z-w)^2} .
+\eeqn
+This is a graded vertex algebra with grading inherited from that of $V$.
+Notice when $V = \C$ with the obvious pairing this is simply the chiral boson vertex algebra.
+
+Similarly, suppose that $U$ is a $\Z \times \Z/2$ vector space equipped with a graded totally anti-symmetric pairing $\<-,-\>$ of total degree zero.
+Then we can consider the symplectic boson vertex algebra valued in $U$ that we denote $\cS\cB(U)$.
+If $\{f_i\}$ is a basis for $U$ then the vertex algebra is generated by free fields $f_i(z)$ of spin $1/2$ and with OPEs
+\beqn
+f_i(z) f_j(w) \simeq \frac{\<f_i,f_j\>}{z-w} .
+\eeqn
+This vertex algebra inherits a $\Z \times \Z/2$ grading from $U$.
+
+\begin{prop}
+The vertex algebra $\VV_{S,W}$ is quasi-isomorphic to the vertex algebra
+\beqn
+\cC\cB(H^\bu(S,\Omega^1_S)) \otimes \cS\cB(\Pi H^\bu(S,W)[1]) \otimes T
+\eeqn 
+where $T$ is the vector space
+\beqn
+\Sym(H^\bu(S,K_S)[1])
+\eeqn
+equipped with the trivial vertex algebra structure.
+\end{prop}
 

### 2024-08-13 agt/survey.tex
GN statement

@@
 \renewcommand{\op}{\operatorname}
+\newcommand{\CB}{\mathbb{C}\mathbb{B}}
+\newcommand{\SB}{\mathbb{S}\mathbb{B}}
 
@@
 A more invariant way to construct this perturbative phase space is the following.
-By transgression, we can view the invariant form as a one-form on the moduli stack $\op{Bun}_G(S)$ of cohomological degree $-1$.
-We can pull this one-form back to get a one-form on $S \times \op{Bun}_G(S)$ also of cohomological degree $-1$.
-Integration of this one-form against $\omega$ along the fibers of $S \times \op{Bun}_G(S) \to \op{Bun}_G(S)$ yields a two-form on $\op{Bun}_G(S)$ (of cohomological degree zero).
-We can, in turn, further restrict this to a two-form on $\cM_{G}(S,L)$ that we will abusively still denote by $\omega$.
+The non-degenerate invariant pairing determines a four-form $\kappa$ on $BG$.
+This pulls back, along the evaluation map
+\beqn
+\op{ev} \colon S \times \op{Bun}_G(S) \to BG 
+\eeqn
+to a four-form on $S \times \op{Bun}_G(S)$.
+Integration of the six-form $\omega \wedge \op{ev}^*\kappa$ along $S$ yields a two-form $\omega_{\kappa} = \int_S \omega \wedge \op{ev}^*\kappa$ on $\op{Bun}_G(S)$.
+We can, in turn, further restrict this to a two-form on $\cM_{G}(S,L)$ that we will abusively still denote by $\omega_{\kappa}$.
 The phase space is then the twisted cotangent bundle
 \beqn
-\T_{\omega}^* \left(\cM_{G}(S,L) \right) .
+\T_{\omega_{\kappa}}^* \left(\cM_{G}(S,L) \right) .
 \eeqn
@@
 Let $\{e_i\}$ be a basis for $V$.
-There is a vertex algebra $\cC\cB(V)$ generated by fields $e_i(z)$ of spin one and with OPEs
+There is a vertex algebra $\CB[V]$ generated by fields $e_i(z)$ of spin one and with OPEs
 \beqn
@@
 Similarly, suppose that $U$ is a $\Z \times \Z/2$ vector space equipped with a graded totally anti-symmetric pairing $\<-,-\>$ of total degree zero.
-Then we can consider the symplectic boson vertex algebra valued in $U$ that we denote $\cS\cB(U)$.
+Then we can consider the symplectic boson vertex algebra valued in $U$ that we denote $\SB[U]$.
 If $\{f_i\}$ is a basis for $U$ then the vertex algebra is generated by free fields $f_i(z)$ of spin $1/2$ and with OPEs
@@
 \beqn
-\cC\cB(H^\bu(S,\Omega^1_S)) \otimes \cS\cB(\Pi H^\bu(S,W)[1]) \otimes T
+\CB[H^\bu(S,\Omega^1_S)] \otimes \SB[\Pi H^\bu(S,W)[1]] \otimes T
 \eeqn 
@@
 \end{prop}
+
+We now focus on a different, more familiar, choice of bundle data.
+Suppose $S$ is a projective surface as before.
+This time, we choose 
+\beqn
+W = \cO_S \boxtimes K_C \oplus K_S \boxtimes \cO_C .
+\eeqn
+and further regrade using the fact that $SU(2)$ has been broken to $U(1)$.
+This six-dimensional theory is of the Dolbeault complex of the $\Z$-graded complex of holomorphic vector bundles
+\beqn
+\begin{tikzcd}
+\ul{-2} & \ul{-1} & \ul{0} \\
+& \Omega^2_{S \times C} \ar[r,"\del"] & \Omega^3_{S \times C} \\
+\cO_{S} \boxtimes \Omega^1_C & & \Omega^2_S \boxtimes \cO_C .
+\end{tikzcd} 
+\eeqn
+The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S}^{NG}$.
+Its compactification, or factorization homology, along $S$
+\beqn
+\int_S \Obs^{NG}_{S}
+\eeqn
+is a holomorphic factorization algebra on $C$.
+On $C = \C$ this determines a vertex algebra that we denote $\VV_{S}^{NG}$.
+
+\begin{prop}
+The vertex algebra $\VV_{S}^{NG}$ is quasi-isomorphic to
+\beqn
+\CB[H^\bu(S,\Omega^1_S)] \otimes \beta\gamma[H^\bu(S,K)] \otimes T
+\eeqn 
+where $T$ is the vector space
+\beqn
+\Sym(H^\bu(S,K_S)[1])
+\eeqn
+equipped with the trivial vertex algebra structure.
+The character of this vertex algebra (whose fugacities we explain in the proof) recovers G\"ottsche's formula for the Hodge-Poincar\'e polynomial of the Hilbert schemes of $S$:
+\beqn
+\chi(\VV_S^{NG}) = \prod_{m \geq 1} \prod_{k,\ell =0}^2 \left(1 - (-1)^{k+\ell} x^{k+m-1} y^{\ell + m - 1} q^m \right)^{(-1)^{k+\ell+1} h^{k,\ell}(S)} .
+\eeqn
+\end{prop}
+\begin{proof}
+Let $\til q$ be the fugacity associated to the conformal weight operator $L_0$.
+Let $u$ be the fugacity for cohomological degree.
+Let $v$ be the `flavor' fugacity, where $\gamma$ is of weight one and $\beta$ is opposite.
+Finally, let $w$ be a fugacity corresponding to the rather trivial symmetry which scales the generators of the commutative part of the vertex algebra with weight one.
+
+Then the single particle characters of each of the fields is computed directly as follows (here $h^{k,\ell} = h^{k,\ell}(S)$).
+\begin{itemize}
+\item The $\gamma$ field in the $\beta\gamma$ system valued contributes
+\beqn
+\frac{v}{1-\til q} \left(h^{2,0} - u h^{2,1} + u^2 h^{2,2}\right) .
+\eeqn
+\item The $\beta$ field in the $\beta\gamma$ system valued contributes
+\beqn
+\frac{v^{-1} \til q}{1- \til q} \left(u^{-2} h^{0,0} - u^{-1} h^{0,1} + h^{0,2}\right) .
+\eeqn
+\item The chiral boson field contributes
+\beqn
+\frac{\til q}{1-\til q} \left(-u^{-1} h^{1,0} + h^{1,1} - u h^{1,2} \right) .
+\eeqn
+\item The commutative part of the vertex algebra contributes
+\beqn
+w \left(-u^{-1} h^{2,0} + h^{2,1} - u h^{2,2}\right) .
+\eeqn
+\end{itemize}
+To recover G\"ottsche's formula we specialize
+\beqn
+\til q = xy q, \quad u = y, \quad v = x y^{-1}, \quad w = x .
+\eeqn
+\end{proof}
 

### 2024-08-14 agt/survey.tex
modes

@@
 In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
-\beqn
+\beqn\label{eqn:fivebranes}
 \bV \;\;\;\left\{
@@
 The phase space is then the twisted cotangent bundle
-\beqn
+
+\beqn\label{eqn:5dphase}
 \T_{\omega_{\kappa}}^* \left(\cM_{G}(S,L) \right) .
@@
 In this case, the local Calabi--Yau fivefold geometry is $Z = \op{Tot}(L_1 \oplus L_2 \oplus L_3).$
+
+We will consider a variant of the factorization algebra $\Obs_{S, W}$ in the case where $L_3$ is possibly a nontrivial line bundle.
+Indeed, BV quantization of the fields \eqref{eqn:fivebrane} of a twisted fivebrane on $X$ yields a holomorphic factorization algebra $\Obs_{X, W}$ that specializes to $\Obs_{S, W}$ in the case where $L_3$ is the trivial line bundle on $S$ \surya{introduce earlier}
+
+From the factorization algebra $\Obs_{X, W}$, we will produce a pair of an associative algebra and a module. To do so, we choose a Hermitian metric on $L_3$. Doing so gives us a norm map
+
+\beqn
+X\to X\times_S X \to S\times \C
+\eeqn
+
+which factors through the trivial $\R_{\geq 0}$-bundle on $S$ since a Hermitian metric is in particular positive definite.
+Let $p$ denote the composition of this map with the projection onto $\R_{\geq 0}$.
+
+The geometry of the situation can be summarized in the following diagram
+
+\[
+\begin{tikzcd}
+X\setminus S \ar[d,"\mathring p"'] \ar[r,hook] & X \ar[d,"p"] & \ar[l,hook',"0"'] S \ar[d] \\
+\R_{>0} \ar[r,hook] & \R_{\geq 0} & \ar[l,hook'] \{0\}.
+\end{tikzcd}
+\]
+
+The pushforward
+\beqn
+p_* \Obs_{X,W}
+\eeqn
+
+is therefore a factorization algebra on $\R_{\geq 0}$.
+
+We may extract from this data, an associative algebra and a module as follows.
+
+\begin{itemize}
+\item Let $(a,b)\subset \R_{\geq 0}$. The sections $(p_* \Obs_{X, W})(a,b)$ are an associative algebra, which we will denote as $\AA(X, W)$.
+
+This associative algebra can equivalently be computed by restricting away from $S$, and pushing forward along $\mathring p$.
+The fiber of this map at $r \in \R_{>0}$ is a copy of $S_r(L_3)\subset X$, the total space of the radius $r$ circle bundle in $L_3$.
+Notice that in the case when $L_3$ is trivial, this associative algebra is exactly the modes algebra of the vertex algebra $\VV_{S,W}$.
+
+\item The costalk at zero $(p_*\Obs{X,W})_0$ is a module, which we denote as $\MM (X, W)$. 
+\end{itemize}
+
+The AGT relation asserts that $\MM(X,W)$ may equivalently be computed as the geometric quantization of \eqref{eqn:5dphase}
+
 \end{document}

### 2024-09-30 agt/survey.tex
merge

@@
 The theory of a twisted fivebrane in this geometry admits the following description.
-In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
+In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following complex of holomorphic super vector bundles
 \beqn\label{eqn:fivebranes}
@@
 We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$. 
+We emphasize that there is both a $\Z/2$ and a $\Z$ grading; for example, the $(0,1)$ component of the field $\phi$ is of odd parity and of cohomological degree zero.
 
@@
 
-\subsection{Five-dimensional supersymmetric Yang--Mills theory}
+\section{Five-dimensional Yang--Mills theory}
+
+In this section we describe the twist of $\cN=2$ supersymmetric Yang--Mills theory which is relevant to our analysis of holomorphic fivebranes.
+We then describe how the compactification of Yang--Mills theory along a circle leads to ...
+
+\subsection{The twisted phase space}
 
 Let $S$ be a complex surface and $W$ a rank two vector bundle on $S$ satisfying $\wedge^2 W = K_S$.
-Given any Lie algebra~$\lie{g}$ equipped with a non-degenerate invariant pairing, we consider the following $\Z \times \Z/2$ graded five-dimensional gauge theory which we refer to as generalized twisted five-dimensional $\cN=2$ Yang--Mills theory.
+For now, we assume that $S$ is projective.
+Given any Lie algebra~$\lie{g}$ equipped with a non-degenerate invariant pairing, we consider the following $\Z \times \Z/2$ graded five-dimensional gauge theory which we refer refer to as twisted five-dimensional $\cN=2$ Yang--Mills theory.
+Here, $\Z$ is the `cohomological' grading and $\Z/2$ is parity.
 
-The fields are
+In the perturbative BV formalism, the fields are:
 \begin{itemize}
@@
 \end{align*}
+Note that these are the fields present in the twist of pure five-dimensional $\cN=1$ gauge theory on $\R \times S$ \cite{ESW}.
 \item Hypermultiplet fields
 \beqn
-\phi \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) \otimes \lie{g} [1] .
+\varphi \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) \otimes \lie{g} [1] .
 \eeqn
-In other words, $\phi^{0,0}$ is an odd field of cohomological degree $-1$.
+In particular, the $(0;0,1)$ component of $\varphi$ is an odd field of cohomological degree zero in this description.
 \end{itemize}
-The action functional is
+The action functional, which is obtained as the twist of the physical $\cN=2$ supersymmetric action takes the simple form
 \beqn
-\int_{\R \times S} (B , F_A) + \frac12 \int_{\R \times S} (\phi, \dbar_A \phi) .
+\int_{\R \times S} (B , F_A) + \frac12 \int_{\R \times S} (\varphi, \d_A \varphi) .
 \eeqn
+Note that $\d_A$ acting on a $k$-form in $\Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) \otimes \lie{g} [1]$ will produce a $(k+1)$-form in
+\beqn
+\Omega^\bu(\R) \otimes \Omega^{0,\bu}(S,\Pi W) \otimes \lie{g} [1] \oplus \Omega^\bu(\R) \otimes \Omega^{1,\bu}(S,\Pi W) \otimes \lie{g} [1] .
+\eeqn
+Only components of $\d_A \varphi$ which live in the first summand appear in the action functional above.
+Similarly, only the components of $F_A$ which live in $\Omega^\bu(\R) \otimes \Omega^{0,\bu}(S) \otimes \lie{g}[1]$ appear in the first term of the action.
+This is all to say that no \textit{holomorphic} derivatives along $S$ appear in the action functional above.
 
-Alternatively, this theory is hybrid Chern--Simons theory associated to the cyclic, holomorphic, local Lie superalgebra
+Alternatively, this theory is hybrid Chern--Simons theory associated to the cyclic, holomorphic, Lie superalgebra
 \beqn
@@
 where $\wedge^0, \wedge^2$ are even and $\wedge^1$ is odd.
+This Lie superalgebra lives entirely in cohomological degree zero.
 Here, we view $\wedge^\bu W$ as a bundle of commutative super algebras.
@@
 
-The perturbative phase space on $S$ is the $\Z \times \Z/2$ even symplectic space
+For a fixed time slice, the perturbative phase space on $S$ is the $\Z \times \Z/2$ even symplectic space
 \beqn
@@
 \eeqn
-A moduli theoretic interpretation of this is as follows.
+A global moduli theoretic interpretation of this is as follows.
 %Consider the moduli stack $\op{Bun}_G(S)$ of holomorphic $G$-bundles on $S$.
@@
 \beqn\label{eqn:pertphase1}
-(P, B, \phi)
+(P, B, \varphi)
 \eeqn
-where $P$ is a holomorphic $G$-bundle on $S$, $\eta \in \Omega^{2,1}(S, \op{ad} P)$, and $\phi \in \Omega^{0,1}(S,\op{ad}(P) \otimes W)$ which satisfy 
+where $P$ is a holomorphic $G$-bundle on $S$, $\eta \in \Omega^{2,1}(S, \op{ad} P)$, and $\varphi \in \Omega^{0,1}(S,\op{ad}(P) \otimes W)$ which satisfy 
 \begin{align*}
-\dbar \phi = 0 \\
-\dbar B + \frac12 [\phi,\phi] = 0 .
+\dbar \varphi = 0 \\
+\dbar B + \frac12 [\varphi,\varphi] = 0 .
 \end{align*}
-The perturbative phase space in \eqref{eqn:pertphase1} is the tangent complex to this moduli stack at the trivial $G$-bundle (and $B = \phi = 0$).
+The perturbative phase space in \eqref{eqn:pertphase1} is the tangent complex to this moduli stack at the trivial $G$-bundle (and $B = \varphi = 0$).
 
@@
 Without loss of generality we set $L = L_1$ and $L_2 = L^{-1} \otimes K_S$.
-This allows us to consider a tilted (regraded) perturbative phase space\footnote{We should explain $\Pi W[1] \to L_2[2] \oplus L_1$.}
+This allows us to consider a tilted (regraded) perturbative phase space\brian{We should explain $\Pi W[1] \to L_2[2] \oplus L_1$.}
 \beqn
@@
 \eeqn
-of quadruples $(P,\varphi, \varphi^*,B)$ where $P$ is a holomorphic $G$-bundle, and
+of quadruples $(P,f, f^*,B)$ where $P$ is a holomorphic $G$-bundle, and
 \begin{align*}
-\varphi & \in \Gamma(S, \op{ad}(P) \otimes L) \\
-\varphi^* & \in \Omega^{2,2}(S, \op{ad}(P) \otimes L^{-1}) \\
+\varphi_1 & \in \Gamma(S, \op{ad}(P) \otimes L) \\
+\varphi_2 & \in \Omega^{2,2}(S, \op{ad}(P) \otimes L^{-1}) \\
 B & \in \Omega^{2,1}(S, \op{ad} P) 
@@
 \begin{align*}
-\dbar \varphi = \dbar \varphi^* & = 0 \\
-\dbar B + [\varphi, \varphi^*] & = 0 .
+\dbar \varphi_1 = \dbar \varphi_2^* & = 0 \\
+\dbar B + [\varphi_1,\varphi_2] & = 0 .
 \end{align*}
-We can furthermore write this as the cotangent bundle to the moduli stack $\cM_{G}(S,L)$ of pairs $(P,\varphi)$ where $P$ is a holomorphic principal $G$-bundle on $S$ and $\varphi \in \Gamma(S, \lie{g} \otimes L)$ satisfying $\dbar \varphi = 0$.
+We can furthermore write this as the cotangent bundle to the moduli stack $\cM_{G}(S,L)$ of pairs $(P,\varphi_1)$ where $P$ is a holomorphic principal $G$-bundle on $S$ and $\varphi_1 \in \Gamma(S, \lie{g} \otimes L)$ satisfying $\dbar \varphi_1 = 0$.
 
@@
 \eeqn 
-Notice that when $L = K_S$ we have the Hilbert space
+As a special case, note that when $L = K_S$ we have $\cM_{G}(S,L) \simeq \T[1] \op{Bun}_G(S)$, so that the Hilbert space is the algebra of de Rham forms on the moduli stack of principal $G$-bundles
 \beqn
 \cO \left( \T[1] \op{Bun}_G(S) \right) \simeq \Omega^{\bu}(\op{Bun}_G(S)) .
+\eeqn
+
+\subsection{Circle compactification}
+
+We consider the twisted six-dimensional theory on the threefold
+\beqn
+X = \C^\times \times S 
+\eeqn
+where $S$, as above, is a projective surface.
+The compactification of this theory along $X \to \R_{>0} \to S$, induced by the radial projection $\C^\times \to \R_{>0}$, yields a five-dimensional theory with an infinite-dimensional space of fields.
+
+Recall that the data which defines the six-dimensional theory on $X$ is a rank two vector bundle $W$ satisfying $\wedge^2 W = K_X$.
+We will assume first that $W$ takes the specific form
+\beqn
+W = \cO_C \boxtimes L_1 \oplus K_C \otimes L_2
+\eeqn
+where $L_1,L_2$ are line bundles on $S$ with the property that $L_1 \otimes L_2 = K_S$.
+
+The compactification of the twisted free hypermultiplet field is easy to describe.
+For this choice of $W$, the fundamental fields are
+\begin{align*}
+\phi_1 & \in \Omega^{0,\bu}(\C^\times) \hotimes \Omega^{0,\bu}(S, \Pi L_1) [1] \\
+\phi_2 \frac{\d z}{2 \pi \im z} & \in \Omega^{1,\bu}(\C^\times) \hotimes \Omega^{0,\bu}(S, \Pi L_2) [1] .
+\end{align*}
+The six-dimensional action is simply $\int_{C \times S} \frac{\d z}{2 \pi \im z} \phi_1 \dbar \phi_2 $.
+
+We use polar coordinates for $\C^\times$, $(r = |z|, \theta)$.
+The six-dimensional fields $\phi_i$ can be written, in these coordinates, as
+\beqn
+\phi_i(r,\theta) = \sum_n \varphi_{i,n} (r) e^{2 \pi \im n \theta} , 
+\eeqn
+where we are viewing $\varphi_{i,n} (r) \in \Omega^{\bu}(\R_{>0}) \hotimes \Omega^{0,\bu}(S, \Pi L_i)[1]$ as a form-valued section over $\C^\times \times S$ by restriction along $\C^\times \times S \to \R_{>0} \times S$.
+
+The free action functional for these fields can be written, in five-dimensional language, as
+\begin{align*}
+\sum_{n,m} \int_{\C^\times \times S} \frac{\d z}{2 \pi \im z} \varphi_{1,n} \dbar \varphi_{2,m} & =  ...\\ & = \sum_{n} \int_{\R_{>0} \times S} \left(\varphi_{1,n} \d \varphi_{2,-n} + n \varphi_{1,n} \varphi_{2,-n}\frac{\d r}{r} \right) .
+\end{align*}
+
+We can formally view the collections $\{\varphi_{i,n}\}_{n \in \Z}$ as Laurent series-valued fields
+\beqn
+\varphi_{i}(t) = \sum_{n} \varphi_{i,n} t^n \in \Omega^{\bu}(\R) \hotimes \Omega^{0,\bu}(S, \Pi L_i) [1] \otimes \C((t)) .
+\eeqn
+The action then takes the simple form
+\beqn
+\int_{\R \times S} \op{Res}_t \frac{\d t}{t} \left( \varphi_1 (t) \d \varphi_2 (t) + \varphi_1 (t) t \frac{\del}{\del t} \varphi_2 (t) \frac{\d r}{r}  \right) .
 \eeqn
@@
 
-\section{The abelian case}
+\section{Vertex algebras from six dimensions}
 
-We will work in the generality of the geometry in (1) where the fivefold is of the form $\op{Tot}(W \to X)$ with $\wedge^2 W = K_X$.
+\subsection{Twisted compactification}
+
+We will start with the twist of the six-dimensional theory on a threefold of the form 
+\beqn
+X = C \times S ,
+\eeqn
+where $S$ is projective.
+Recall that the input data for the twisted fivebrane theory is a rank two holomorphic vector bundle $W$ on $X$ satisfying $\wedge^2 W$.
+We consider two cases:
+\begin{itemize}
+\item[(1)] $W = \cO_C \boxtimes L_1 \oplus K_C \otimes L_2$ where $L_1,L_2$ are line bundles on $S$ with the property that $L_1 \otimes L_2 = K_S$.
+\item[(2)] $W = K^{1/2}_C \boxtimes V$ where $V$ is a rank two vector bundle on $S$ which satisfies $\wedge^2 V = K_S$. Note that $W$ depends on the choice of a spin structure on $C$.
+\end{itemize}
+
+The compactification of the twisted six-dimensional theory along $S$ will yield a two-dimensional chiral conformal field theory on $C$.
+In each of the cases we can describe the CFT explicitly.
+The associated vertex algebras are vacuum modules for the associative algebra of modes.
+Furthermore, local operators are identified, explicitly, with the Hilbert space of the five-dimensional theory obtained by the twisted circle compactification $\C^\times \to \R_{>0}$ described in section \ref{s:circle1}.
 
@@
 
-Assume that $S$ is a projective surface equipped with a rank two vector bundle $V$ satisfying $\wedge^2 W = K_S$.
-Consider the resulting twisted fivebrane worldvolume theory on $X = S \times C$ where $W = V \boxtimes K_C^{1/2}$ (here, we are assuming that $C$ is equipped with a spin structure).
-In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(S \times C,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
+We start with a familiar choice of bundle data to define the twisted six-dimensional theory.
+Let $S$ be a projective surface as before and suppose
 \beqn
-\bV \colon \;\;\;\left\{
+W = \cO_C \boxtimes K_S \oplus K_C \boxtimes \cO_S .
+\eeqn
+and further regrade using the fact that $SU(2)$ has been broken to $U(1)$. \brian{explain this}
+This six-dimensional theory is of the Dolbeault complex of the $\Z$-graded complex of holomorphic vector bundles
+\beqn
 \begin{tikzcd}
-& \ul{-1} & \ul{0} \\
-\ul{\text{even}} & \Omega^2_{S \times C} \ar[r,"\del"] & \Omega^3_{S \times C} \\
-\ul{\text{odd}} & \Pi p^* W  
-\end{tikzcd} \right.
+\ul{-2} & \ul{-1} & \ul{0} \\
+& \Omega^2_{S \times C} \ar[r,"\del"] & \Omega^3_{C \times S} \\
+\Omega^1_C \boxtimes \cO_S & & \cO_C \boxtimes \Omega^2_S .
+\end{tikzcd} 
 \eeqn
-We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$, as we did above.
-The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S,W}$.
-Its compactification, or factorization homology, along $S$
+The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S}^{NG}$.
+The compactification, or factorization homology, along $S$
 \beqn
-\int_S \Obs_{S,W} 
+\int_S \Obs^{NG}_{S}
 \eeqn
 is a holomorphic factorization algebra on $C$.
-On $C = \C$ this determines a vertex algebra that we denote $\VV_{S,W}$.
+On $C = \C$ this determines a vertex algebra that we denote $\VV_{S}^{NG}$.
 
-We describe this vertex algebra explicitly.
-Notice that since $S$ is projective there is a quasi-isomorphism of sheaves on $C$:
-\begin{align*}
-\Omega^{2,\bu}_{S \times C} & \simeq H^{\bu} (S, K_S) \otimes \Omega^{0,\bu}_C  \oplus H^\bu(S, \Omega^1_S) \otimes \Omega^{1,\bu}_C \\
-\Omega^{3,\bu}_{S \times C} & \simeq H^{\bu} (S, K_S) \otimes \Omega^{1,\bu}_C  \\
-\Omega^{0,\bu}_{S \times C}(W \boxtimes K_{C}^{1/2}) & \simeq H^\bu(S, W) \otimes \Omega^{0,\bu}_C(K^{1/2}_C) .
-\end{align*}
-
-Suppose that $V$ is a graded vector space equipped with a graded symmetric pairing of total degree zero.
-Let $\{e_i\}$ be a basis for $V$.
-There is a vertex algebra $\CB[V]$ generated by fields $e_i(z)$ of spin one and with OPEs
+To describe this vertex algebra, we introduce some familiar notations.
+Suppose that~$V$ is a graded vector space equipped with a graded symmetric pairing of total degree zero.
+Let $\{e_i\}$ be a basis for~$V$.
+There is a vertex algebra $\CB[V]$, called the `chiral boson' vertex algebra, generated by fields $e_i(z)$ of spin one and with OPEs
 \beqn
@@
 Notice when $V = \C$ with the obvious pairing this is simply the chiral boson vertex algebra.
+Of course, this vertex algebra does not depend on the chosen basis.
 
-Similarly, suppose that $U$ is a $\Z \times \Z/2$ vector space equipped with a graded totally anti-symmetric pairing $\<-,-\>$ of total degree zero.
-Then we can consider the symplectic boson vertex algebra valued in $U$ that we denote $\SB[U]$.
-If $\{f_i\}$ is a basis for $U$ then the vertex algebra is generated by free fields $f_i(z)$ of spin $1/2$ and with OPEs
+Next, we introduce the $\beta\gamma$ vertex algebra.
+If $V$ is any graded vector space with basis $\{e_i\}$ then $\beta\gamma[V]$ is the vertex algebra generated by fields $\gamma_i(z)$ of spin zero and $\beta^j(z)$ of spin $1$ with OPEs
 \beqn
-f_i(z) f_j(w) \simeq \frac{\<f_i,f_j\>}{z-w} .
+\beta^j(z) \gamma_i(w) \simeq \frac{\delta_{i}^j}{z-w} .
 \eeqn
-This vertex algebra inherits a $\Z \times \Z/2$ grading from $U$.
-
-\begin{prop}
-The vertex algebra $\VV_{S,W}$ is quasi-isomorphic to the vertex algebra
-\beqn
-\CB[H^\bu(S,\Omega^1_S)] \otimes \SB[\Pi H^\bu(S,W)[1]] \otimes T
-\eeqn 
-where $T$ is the vector space
-\beqn
-\Sym(H^\bu(S,K_S)[1])
-\eeqn
-equipped with the trivial vertex algebra structure.
-\end{prop}
-
-We now focus on a different, more familiar, choice of bundle data.
-Suppose $S$ is a projective surface as before.
-This time, we choose 
-\beqn
-W = \cO_S \boxtimes K_C \oplus K_S \boxtimes \cO_C .
-\eeqn
-and further regrade using the fact that $SU(2)$ has been broken to $U(1)$.
-This six-dimensional theory is of the Dolbeault complex of the $\Z$-graded complex of holomorphic vector bundles
-\beqn
-\begin{tikzcd}
-\ul{-2} & \ul{-1} & \ul{0} \\
-& \Omega^2_{S \times C} \ar[r,"\del"] & \Omega^3_{S \times C} \\
-\cO_{S} \boxtimes \Omega^1_C & & \Omega^2_S \boxtimes \cO_C .
-\end{tikzcd} 
-\eeqn
-The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S}^{NG}$.
-Its compactification, or factorization homology, along $S$
-\beqn
-\int_S \Obs^{NG}_{S}
-\eeqn
-is a holomorphic factorization algebra on $C$.
-On $C = \C$ this determines a vertex algebra that we denote $\VV_{S}^{NG}$.
+This vertex algebra is also independent of the chosen basis.
 
@@
 \beqn
-\chi(\VV_S^{NG}) = \prod_{m \geq 1} \prod_{k,\ell =0}^2 \left(1 - (-1)^{k+\ell} x^{k+m-1} y^{\ell + m - 1} q^m \right)^{(-1)^{k+\ell+1} h^{k,\ell}(S)} .
+\chi(\VV_S^{NG}) = \sum_{n \geq 0}\sum_{i,j=0}^{2n} q^n h^{i,j}(S^{[n]}) (-x)^i (-y)^j = \prod_{m \geq 1} \prod_{k,\ell =0}^2 \left(1 - (-1)^{k+\ell} x^{k+m-1} y^{\ell + m - 1} q^m \right)^{(-1)^{k+\ell+1} h^{k,\ell}(S)} .
 \eeqn
@@
 \begin{proof}
+Let $\pi \colon C \times S \to C$ be the projection.
+Notice that since $S$ is projective there is a quasi-isomorphism of sheaves on $C$:
+\begin{align*}
+\pi_*\Omega^{2,\bu}_{C \times S} & \simeq  \Omega^{0,\bu}_C \otimes H^{\bu} (S, K_S)  \oplus \Omega^{1,\bu}_C \otimes H^\bu(S, \Omega^1_S)  \\
+\pi_* \Omega^{3,\bu}_{C \times S} & \simeq \Omega^{1,\bu}_C \otimes H^{\bu} (S, K_S) \\
+\pi_* \Omega^{0,\bu}_{C} \otimes \Omega^{2,\bu}_S & \simeq \Omega^{0,\bu}_C \otimes H^\bu(S,K_S) \\
+\pi_* \Omega^{1,\bu}_{C} \otimes \Omega^{0,\bu}_S & \simeq \Omega^{1,\bu}_C \otimes H^\bu(S,\cO_S) .
+\end{align*}
+
 Let $\til q$ be the fugacity associated to the conformal weight operator $L_0$.
@@
 \end{proof}
+
+\brian{I think the following is true by some boson-boson correspondence}
+\begin{prop}
+There is an isomorphism of vertex algebras
+\beqn
+\VV_{S}^{NG} \simeq \CB\left[H_{dR}^\bu(S)\right] .
+\eeqn
+\end{prop}
+
+This vertex algebra was associated to a specific choice of rank two vector bundle \eqref{eqn:ng1}.
+More generally, we can consider the following vector bundle
+\beqn
+W = \cO_C \boxtimes L \oplus K_C \boxtimes L^!
+\eeqn
+where $L^! = L^* \otimes K_S$.
+We will denote the associated vertex algebra by $\VV_{S,L}^{NG}$.
+In the same way as we just did for $L = K_S$, we arrive at the following description.
+
+\begin{prop}
+The vertex algebra $\VV_{S,L}^{NG}$ is quasi-isomorphic to
+\beqn
+\CB[H^\bu(S,\Omega^1_S)] \otimes \beta\gamma[H^\bu(S,L)] \otimes T
+\eeqn 
+where $T$ is the vector space
+\beqn
+\Sym(H^\bu(S,K_S)[1])
+\eeqn
+equipped with the trivial vertex algebra structure.
+
+The character of this vertex algebra is
+\begin{multline}
+\chi(\VV_{S,L}^{NG}) = \frac{(1-(xy^{-1})^{h^{2,0}}) (1- (xy)^{h^{2,2}})}{1-x^{h^{2,1}}} \prod_{m \geq 1} \prod_{\ell =0}^2 \left(1 - (-1)^{\ell+1} x^{m} y^{\ell + m - 1} q^m \right)^{(-1)^{\ell} h^{1,\ell}(S)} \\
+\times \left[(1-x^{m+1}y^{m+\ell-1} q^m)(1-x^m y^{m-\ell+2} q^{m+1})\right]^{(-1)^{\ell+1} h_L^\ell} .
+\end{multline}
+\end{prop}
+\begin{proof}
+We adjust the computation of the character to this case, the remainder of the proof is a straightforward generalization.
+The only bit that needs modification is the character of the $\beta\gamma$ system.
+In this case, the $\beta\gamma$ system is based on the graded vector space $H^\bu(S,L)$.
+Let $h^{i}_L$ denote the dimensions of this cohomology.
+Then:
+\begin{itemize}
+\item The $\gamma$ field contributes
+\beqn
+\frac{v}{1-\til q} (h^{0}_L - u h^{1}_L + u^2 h^{2}_L) .
+\eeqn
+\item The $\beta$ field contributes
+\beqn
+\frac{v^{-1} \til q}{1 - \til q} (u^{-2} h^{2}L - u^{-1} h^1_L + h^0_L) .
+\eeqn
+\end{itemize}
+\end{proof}
+
+\subsection{A spin version}
+
+Assume that $S$ is a projective surface equipped with a rank two vector bundle $V$ satisfying $\wedge^2 V = K_S$.
+Consider the resulting twisted six-dimensional theory on $X = S \times C$ where 
+\beqn
+W = K_C^{1/2} \boxtimes V.
+\eeqn
+Here, we are assuming that $C$ is equipped with a spin structure.
+In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(S \times C,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
+\beqn
+\bV \colon \;\;\;\left\{
+\begin{tikzcd}
+& \ul{-1} & \ul{0} \\
+\ul{\text{even}} & \Omega^2_{C \times S} \ar[r,"\del"] & \Omega^3_{C \times S} \\
+\ul{\text{odd}} & \Pi p^* V  
+\end{tikzcd} \right.
+\eeqn
+We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$, as we did above.
+The BV quantization of this theory yields a factorization algebra on $S \times C$ that we will denote $\Obs_{S,V}$.
+Its compactification, or factorization homology, along $S$
+\beqn
+\int_S \Obs_{S,V} 
+\eeqn
+is a holomorphic factorization algebra on $C$.
+On $C = \C$ this determines a vertex algebra that we denote $\VV_{S,V}$.
+
+We describe this vertex algebra explicitly.
+Suppose that $U$ is any $\Z \times \Z/2$ vector space equipped with a graded totally anti-symmetric pairing $\<-,-\>$ of total degree zero.
+Then we can consider the symplectic boson vertex algebra valued in $U$ that we denote $\SB[U]$.
+If $\{f_i\}$ is a basis for $U$ then the vertex algebra is generated by free fields $f_i(z)$ of spin $1/2$ and with OPEs
+\beqn
+f_i(z) f_j(w) \simeq \frac{\<f_i,f_j\>}{z-w} .
+\eeqn
+This vertex algebra inherits a $\Z \times \Z/2$ grading from $U$.
+
+Notice that since $S$ is projective there is a quasi-isomorphism of sheaves on $C$:
+\begin{align*}
+\pi_*\Omega^{2,\bu}_{C \times S} & \simeq  \Omega^{0,\bu}_C \otimes H^{\bu} (S, K_S)  \oplus \Omega^{1,\bu}_C \otimes H^\bu(S, \Omega^1_S)  \\
+\pi_* \Omega^{3,\bu}_{C \times S} & \simeq \Omega^{1,\bu}_C \otimes H^{\bu} (S, K_S) \\
+\pi_* \Omega^{0,\bu}_{C \times S}( K_{C}^{1/2}\boxtimes V) & \simeq \Omega^{0,\bu}_C(K^{1/2}_C) \otimes H^\bu(S, V) .
+\end{align*}
+
+\begin{prop}
+The vertex algebra $\VV_{S,V}$ is quasi-isomorphic to the vertex algebra
+\beqn
+\CB[H^\bu(S,\Omega^1_S)] \otimes \SB\left[\Pi H^\bu(S,V)[1]\right] \otimes T
+\eeqn 
+where $T$ is the vector space
+\beqn
+\Sym(H^\bu(S,K_S)[1])
+\eeqn
+equipped with the trivial vertex algebra structure.
+\end{prop}
 
